### 2021-03-24 Draft/Draft.Rmd
draft

---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##ABSTRACT

The interaction between plants and pollinators can be studied at different scales, from species level interactions (micro-scale) to the full network structure (macro-scale). However, condensing to species level and the holistic view of the full network involves missing relevant information for the understanding of ecological processes. Intermediate levels to study plant-pollinator networks (meso-scale) have been little explored but can shed light of ecological processes not captured by the traditional approaches used in plant-pollinator network studies. On the meso-scale, smaller versions of the full network are considered with a reduced number of species and are also known as motifs. Exploring with motifs plant-pollinator interactions could help our understanding of species interactions due to motifs consider both direct and indirect species interactions. In this study, we have defined for 29 plant-pollinator networks plant's and pollinator's functional groups and explored the most common pattern of motifs between them. We found [...]

### 2021-03-24 Scripts/Scripts_Funtional_Groups/1_Merge_Spp_Names_Long_format.R

@@ -27,7 +27,7 @@ library(tidyverse)
 #1) LOAD NETWORK DATA
 ########################################################################################################################################################
 #Set working directory to read files
-setwd("~/R_Projects/Reproductive traits/Data/Data_networks_quantitative") 
+setwd("~/R_Projects/FunctionalMotifs/Data/Data_networks_quantitative") 
 
 temp <- list.files(pattern="*.csv")
 my.list <- list(for (i in 1:length(temp)) assign(temp[i], read.csv(temp[i])))
@@ -58,7 +58,7 @@ colnames(all_long) <- c("Plant_species", "Id", "Pollinator_species", "Interactio
 #BECAUSE OF SOME NETWORKS WERE ADDED LATE)
 #PLANT SPECIES NAMES HAS BEEN ALSO BEEN SEARCHED BUT PREVIOUSLY WITH TAXSIZE
 
-setwd("~/R_Projects/Reproductive traits") 
+setwd("~/R_Projects/FunctionalMotifs") 
 poll_names <- read.csv("Data/Data_processing/pollinator_species_names/poll_spp_names_corrected.csv")
 #select unique word in order to meger
 all_long$genus_old <- word(all_long$Pollinator_species)

### 2021-03-24 Scripts/Scripts_Funtional_Groups/3_Functional_Groups.R

@@ -49,14 +49,14 @@ trait_data[,c(4,7:13,16)] <- scale(mutate_all(trait_data[,c(4,7:13,16)], functio
 ########################################################################################################################################################
 
 #Give weights to the different traits
-w <- c(0.1428,	#breeding system
-       0.0476,	0.0476,	0.0476, #selfing/compatibility
-       0.0714,	0.0714, #flower morphology/symmetry
-       0.0285,0.0285,0.0285,0.0285,0.0285, #floral investment  	
-       0.1428, #style length
-       0.1428, #ovule number
-       0.0476,0.0476,0.0476, #life form
-       0.1428) #nectar
+w <- c(0.125,	#breeding system
+       0.042,	0.042,0.042, #selfing/compatibility
+       0.063,	0.063, #flower morphology/symmetry
+       0.025,0.025,0.025,0.025,0.025, #floral investment  	
+       0.125, #style length
+       0.125, #ovule number
+       0.042,0.042,0.042, #life form
+       0.125) #nectar
 
 #calculate gowers distance for all species
 g.dist <- gowdis(trait_data)
@@ -90,11 +90,105 @@ tsne_obj <- Rtsne(g.dist, is_distance = TRUE)
 tsne_data <- tsne_obj$Y %>%data.frame() %>%setNames(c("X", "Y")) %>%mutate(cluster = as.factor(e.gr_5))
 ggplot(aes(x = X, y = Y), data = tsne_data) + geom_point(aes(color = cluster))
 
+
+
+
+#Plot dendro
+library("ggplot2")
+library("reshape2")
+library("purrr")
+library("dplyr")
+# let's start with a dendrogram
+library("dendextend")
+dendro <- as.dendrogram(e.clust_5)
+dendro.col <- dendro %>%
+  set("branches_k_color", k = 5, value =   c("black", "grey", "brown4", "orange", "gold2")) %>%
+  set("branches_lwd", 0.6) %>%
+  set("labels_colors", 
+      value = c("darkslategray")) %>% 
+  set("labels_cex", 0.1)
+ggd1 <- as.ggdend(dendro.col)
+
+
+
+ggplot(ggd1, theme = theme_minimal()) +
+  labs(x = "Num. observations", y = "Height", title = "Dendrogram, k = 5")
+
+
+# Radial plot looks less cluttered (and cooler)
+ggplot(ggd1, labels = T) + 
[…]

### 2021-03-24 Draft/Draft.Rmd
Abstract

@@
 Intermediate levels to study plant-pollinator networks (meso-scale) have been little explored but can shed light of ecological processes not captured by the traditional approaches used in plant-pollinator network studies.
-On the meso-scale, smaller versions of the full network are considered with a reduced number of species and are also known as motifs.
-Exploring with motifs plant-pollinator interactions could help our understanding of species interactions due to motifs consider both direct and indirect species interactions.
-In this study, we have defined for 29 plant-pollinator networks plant's and pollinator's functional groups and explored the most common pattern of motifs between them.
-We found [...]
+On the meso-scale, smaller versions of the full network are considered with a reduced number of species which are also known as motifs.
+Exploring the different and most frequent motifs could help our understanding of species interactions due to motifs consider direct and indirect interactions not accounted in single species metrics.
+In order to progress knowledge in plant-pollinator networks we have compiled 60 networks from 29 different studies and defined plant functional groups by using a comprehensive dataset with several reproductive traits and pollinator functional groups as the main differentiated guilds in life form and behaviour.
+Then, we explored the main motifs of these networks and we found [...]
+
+Analysis:
+
+__Ranking de motifs__
+Alfonso en slack
+1) reemplazar en cada red los "nodos especie" de plantas y visitantes florales por su correspondiente "nodo de grupo funcional"
+2) colapsar en cada red todos los nodos del mismo grupo funcional en uno solo
+3) descomponer en motifs (de hasta 5 nodos) la estructura resultante del paso 2
+Los rankings absolutos (contando enlaces [Motifs 1-17] y sin contar enlaces [Motifs 2-17]) quedan así
+
+##INTRODUCTION
+
+##METHODS
+
+We have compiled 60 plant-pollinator networks from 29 different studies [...]
+
+##RESULTS

### 2021-05-17 Draft/Draft.Rmd
Start drafting things

--- 2021-03-24 Draft/Draft.Rmd
@@
 ---
-title: "Untitled"
+title: "Plant-pollintor networks worldwide are composed by the same specific building blocks"
 output: html_document
@@
 
-##ABSTRACT
+##Abstract
+
+Ecological processes leave distinct structural imprints on indirect interactions in mutualistic networks.
+Detecting those relationships is not trivial since they go beyond pair-wise interactions, but may get blurred when considering full network descriptors.
+However, recent work has shown the network meso-scale can capture this important information.
+The meso-scale describes network subgraphs representing patterns of interactions between a small number of species (i.e.
+motifs) and those constitute the building blocks of the whole network.
+Here we have compiled 60 networks from 29 different studies and show that some motifs are consitently over-represented worldwide, suggesting that the building blocks of plant-pollintor networks are not random and are associated to ...
+Second, we show that the position of pollinator guilds and plant reproductive strategies is not random with respect to the positions occupied within each motif.
+...
+Hence, we show that species ecology is shaping the building blocks that conform the web of life.
+
+##INTRODUCTION
 
@@
 Intermediate levels to study plant-pollinator networks (meso-scale) have been little explored but can shed light of ecological processes not captured by the traditional approaches used in plant-pollinator network studies.
-On the meso-scale, smaller versions of the full network are considered with a reduced number of species and are also known as motifs.
-Exploring with motifs plant-pollinator interactions could help our understanding of species interactions due to motifs consider both direct and indirect species interactions.
-In this study, we have defined for 29 plant-pollinator networks plant's and pollinator's functional groups and explored the most common pattern of motifs between them.
-We found [...]
+[Explain what macro-descriptors have found i.e.
+Bascompte, and what pairwise interactions descriptors have accomplished i.e.
+trait-matching.
+End explaining Benno simmons work]
+
+Exploring the different and most frequent motifs could help our understanding of species interactions due to motifs consider direct and indirect interactions not accounted in single species metrics.
+[Explain this: https://besjournals.onlinelibrary.wiley.com/doi/full/10.1111/1365-2435.13736 and say we don't know how motif distribution really looks like in the real world.
+Which is the expected pattern?]
+
+However, motifs are abstract representations often decoupled from species ecology.
+[explain here the importance of relating reproductive strategies and pollinators behaviours to their positions within a motif.
+This is interesting because bridges pairwise interactions to the emergent network via motifs]
+
+Here, we used ...
+blah...
+and fined plant functional groups by using a comprehensive dataset with several reproductive traits and pollinator functional groups as the main differentiated guilds in life form and behaviour.
+Then, we explored the main motifs of these networks and we found [...]
+
+##METHODS
+
+We have compiled 60 plant-pollinator networks from 29 different studies [...]
+
+Plants were grouped into reproductive strategies [justify and explain the process]
+
+Pollintors were grouped into guilds, because [justify and explain, it's important to convince the reader that Order level for pollinators and FG for plants makes sense].
+
+We follow Simmons et al.
+to decompose networks on their constituent motifs.
+We compare observed motif frecuancies to vaznull model, which constrains the number of plants, pollinators and the network connectance.
+For each network we compared the observed motif frequency with the expected frecuancies and ...
+.
+To summarize general patterns across networks we used a GLMM per motif with the percentile per network, ...
+
+Next, we calculated which functional groups were over or under-represented in different motif positions by comparing with ... . Again, we tested ...
+
+[potential additions: 
+Finally,for each motif, we recover the number of times a given combination of functional groups emerges ...
+Finally, we draw a network collapsing nodes per FG...]
+
+##RESULTS
+
+0) Description of guilds and FG.
+
+1) over and under represented motifs
+```{r}
+library(lme4)
+d <- read.csv("../Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
+str(d)
+head(d)
+hist(d$percentil_sizeclass) #wow! 
+hist(subset(d, motif == 2)[,"percentil_sizeclass"]) #motif 2 tend to be over-represented
+hist(subset(d, motif == 3)[,"percentil_sizeclass"]) #motif 3 tend to be under-represented
+#quick and dirty 
+mean(subset(d, motif == 3)[,"percentil_sizeclass"]) #mean on 0.18
+#more elegant, taking into account the study system
+unique(d$Network_id) #we need to recover study_id
+m <- lmer(percentil_sizeclass ~ 1+(1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
+                       data = subset(d, motif == 2))  
+#plot(m)
+summary(m) #estimated mean taking into account the random str is 0.XX +- 0.XX (look at the (Intercept) estimate)
+
+#Fig 1 Should be a dot plot (or forest plot) of the mean +- SE of the 15 motifs.
+```
+2) FG-position associations.
+```{r}
+library(lme4)
+d <- read.csv("../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
+str(d)
+head(d)
+hist(d$percentil_its_GF) #wow!
+
+#quick and dirty 
+mean(subset(d, position == "np3" & Node_FG == 1)[,"percentil_its_GF"], na.rm = TRUE) #mean of 0.61
+#more elegant, taking into account the study system
+unique(d$Network_id) #we need to recover study_id
+m <- lmer(percentil_its_GF ~ 1+(1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
+                       data = subset(d, position == "np3" & Node_FG == 1))  
+#plot(m)
+summary(m) #estimated mean taking into account the random str is 0.XX +- 0.XX (look at the (Intercept) estimate)
+
+#Fig 2 may be the same, but for the each positions-FG combination? Maybe heatmap (but we lose the SE's)
+
+```

### 2021-05-18 Scripts/Scripts_Alfonso/4_GLMM_Positions_Connectance_Fixed.R
Update 4_GLMM_Positions_Connectance_Fixed.R

@@ -84,12 +84,19 @@ results_pollinator_position$evaluation[results_pollinator_position$percentil_all
 
 ggplot(results_pollinator_position, 
        aes(x = position, y = percentil_all_GF, color = evaluation))+
-  geom_point(alpha=0.3)+
+  geom_boxplot(alpha=0.3)+
   facet_wrap(~Node_FG)+
   theme_bw()+
   theme(axis.text.x=element_text(angle=45,hjust=1))+#,legend.position="bottom")+
   labs(x=NULL, color = "Percentile's C.I.")
 
+ggplot(results_pollinator_position, 
+       aes(x = Node_FG, y = percentil_all_GF, color = evaluation))+
+  geom_boxplot(alpha=0.3)+
+  facet_wrap(~position)+
+  theme_bw()+
+  theme(axis.text.x=element_text(angle=45,hjust=1))+#,legend.position="bottom")+
+  labs(x=NULL, color = "Percentile's C.I.")
 
 library(RColorBrewer)
 ggplot(results_pollinator_position %>%
@@ -117,8 +124,53 @@ ggplot(results_pollinator_position %>%
   facet_wrap(~Node_FG)+
   theme_bw()+
   theme(axis.text.x=element_text(angle=45,hjust=1))+#,legend.position="bottom")+
+  labs(x=NULL, y = "Percentage of observations", fill = "Percentile's C.I.")
+
+ggplot(results_pollinator_position %>% 
+         mutate(evaluation = factor(evaluation, 
+                                    levels=c("(97.5,100]", "[2.5,97.5]", "[0,2.5)")),
+                position = factor(position),
+                Node_FG = factor(Node_FG),
+                counts = 1), 
+       aes(x = Node_FG, y = counts, fill = evaluation))+
+  geom_bar(position="stack", stat="identity")+
+  scale_fill_brewer(palette = "RdYlBu") +
+  facet_wrap(~position)+
+  theme_bw()+
+  theme(axis.text.x=element_text(angle=45,hjust=1))+#,legend.position="bottom")+
   labs(x=NULL, y = "Number of observations", fill = "Percentile's C.I.")
 
+ggplot(results_pollinator_position %>% 
+         mutate(evaluation = factor(evaluation, 
+                                    levels=c("(97.5,100]", "[2.5,97.5]", "[0,2.5)")),
+                position = factor(position),
+                Node_FG = factor(Node_FG),
+                counts = 1), 
[…]

### 2021-05-18 Draft/Draft.Rmd
Update Draft.Rmd

@@
 library(lme4)
-d <- read.csv("../Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
+library(tidyverse)
+source("../Scripts/Scripts_Alfonso/add_study_id.R")
+d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
+d <- add_study_id(d)
 str(d)
 head(d)
-hist(d$percentil_sizeclass) #wow! 
-hist(subset(d, motif == 2)[,"percentil_sizeclass"]) #motif 2 tend to be over-represented
-hist(subset(d, motif == 3)[,"percentil_sizeclass"]) #motif 3 tend to be under-represented
-#quick and dirty 
-mean(subset(d, motif == 3)[,"percentil_sizeclass"]) #mean on 0.18
-#more elegant, taking into account the study system
-unique(d$Network_id) #we need to recover study_id
+
+ggplot(d %>% filter(motif != 1), aes(percentil_sizeclass))+
+  geom_histogram(color="black", fill="white")+
+  facet_wrap(~motif)+
+  theme_bw()+
+  labs(x="Sizeclass percentile")
+
+# Motifs tend to be over- and under-represensented in real networks
+
+# Mean percentile and SE taking into account the study system
+motif_codes <- d %>% filter(motif != 1) %>% # We remove links (motif code: 1)
+  select(motif) %>% unique() %>% pull()
+motif_means <- tibble(motif = motif_codes)
+motif_means$mean <- NA
+motif_means$SE <- NA
+
+for(i.motif in 1:length(motif_codes)){
+
   m <- lmer(percentil_sizeclass ~ 1+(1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-                       data = subset(d, motif == 2))  
-#plot(m)
-summary(m) #estimated mean taking into account the random str is 0.XX +- 0.XX (look at the (Intercept) estimate)
+            data = subset(d, motif == motif_codes[i.motif]))
+
+  motif_means$mean[i.motif] <- fixed.effects(m) %>% unname()
+  motif_means$SE[i.motif] <- sqrt(diag(vcov(m)))
+
+}
+
+ggplot(NULL) + 
+  geom_point(data = d %>% filter(motif != 1),
+             aes(x=as.factor(motif), y=percentil_sizeclass, 
+                 color = as.factor(motif)),
+             position = "jitter",alpha=0.5)+
+  geom_errorbar(data = motif_means,aes(x = as.factor(motif), ymin=mean-SE, ymax=mean+SE), 
+                width=1.0,size=1)+
+  geom_point(data = motif_means,aes(x = as.factor(motif), y=mean), 
+                size=2)+
+  labs(x="Motif", y = "Percentile")+
+  theme_bw()+
+  theme(legend.position = "none")
 
@@
 library(lme4)
-d <- read.csv("../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
-str(d)
-head(d)
-hist(d$percentil_its_GF) #wow!
+library(tidyverse)
+source("../Scripts/Scripts_Alfonso/add_study_id.R")
 
-#quick and dirty 
-mean(subset(d, position == "np3" & Node_FG == 1)[,"percentil_its_GF"], na.rm = TRUE) #mean of 0.61
-#more elegant, taking into account the study system
-unique(d$Network_id) #we need to recover study_id
+all_position_percentiles <- read_csv("../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
+
+all_position_percentiles <- add_study_id(all_position_percentiles)
+str(all_position_percentiles)
+head(all_position_percentiles)
+
+list_plants_FG <- as.character(1:10)
+
+plant_position_percentiles_filtered <- all_position_percentiles %>% 
+  filter(Node_FG %in% list_plants_FG, !position %in% c("np1","np2"),
+         !is.na(expected_freq_its_GF))
+pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
+  filter(!Node_FG %in% list_plants_FG, !position %in% c("np1","np2"),
+         !is.na(expected_freq_its_GF))
+
+ggplot(plant_position_percentiles_filtered, aes(percentil_its_GF))+
+  geom_histogram(color="black", fill="white")+
+  facet_wrap(~position)+
+  theme_bw()+
+  labs(x="Sizeclass percentile", title = "Histograms: Percentiles for plant positions")
+
+ggplot(pollinator_position_percentiles_filtered, aes(percentil_its_GF))+
+  geom_histogram(color="black", fill="white")+
+  facet_wrap(~position)+
+  theme_bw()+
+  labs(x="Sizeclass percentile",title = "Histograms: Percentiles for pollinator positions")
+
+# estimated mean taking into account the random str is 0.XX +- 0.XX (look at the (Intercept) estimate)
+
+# Plants-------------
+
+# Mean percentile and SE taking into account the study system
+plant_codes <- plant_position_percentiles_filtered$position %>% unique()
+plant_means <- tibble(position = plant_codes)
+plant_means$mean <- NA
+plant_means$SE <- NA
+
+for(i.pos in 1:length(plant_codes)){
+
   m <- lmer(percentil_its_GF ~ 1+(1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-                       data = subset(d, position == "np3" & Node_FG == 1))  
-#plot(m)
-summary(m) #estimated mean taking into account the random str is 0.XX +- 0.XX (look at the (Intercept) estimate)
+            data = subset(plant_position_percentiles_filtered,
+                          position == plant_codes[i.pos]))
+
+  plant_means$mean[i.pos] <- fixed.effects(m) %>% unname()
+  plant_means$SE[i.pos] <- sqrt(diag(vcov(m)))
+
+}
+
+ggplot(NULL) + 
+  geom_point(data = plant_position_percentiles_filtered,
+             aes(x=as.factor(position), y=percentil_its_GF, 
+                 color = as.factor(position)),
+             position = "jitter",alpha=0.5)+
+  facet_wrap(~Node_FG)+
+  geom_errorbar(data = plant_means,aes(x = as.factor(position), ymin=mean-SE, ymax=mean+SE), 
+                width=1.0,size=1)+
+  geom_point(data = plant_means,aes(x = as.factor(position), y=mean), 
+                size=2)+
+  labs(x="Position", y = "Percentile",title = "Pollinators")+
+  theme_bw()+
+  theme(legend.position = "none",axis.text.x=element_text(angle=90,vjust=0.5, hjust=1))
+
+# Pollinators--------
+
+# Mean percentile and SE taking into account the study system
+pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
+pollinator_means <- tibble(position = pollinator_codes)
+pollinator_means$mean <- NA
+pollinator_means$SE <- NA
+
+for(i.pos in 1:length(pollinator_codes)){
+
+  m <- lmer(percentil_its_GF ~ 1+(1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
+            data = subset(pollinator_position_percentiles_filtered,
+                          position == pollinator_codes[i.pos]))
+
+  pollinator_means$mean[i.pos] <- fixed.effects(m) %>% unname()
+  pollinator_means$SE[i.pos] <- sqrt(diag(vcov(m)))
+
+}
+
+ggplot(NULL) + 
+  geom_point(data = pollinator_position_percentiles_filtered,
+             aes(x=as.factor(position), y=percentil_its_GF, 
+                 color = as.factor(position)),
+             position = "jitter",alpha=0.5)+
+  facet_wrap(~Node_FG)+
+  geom_errorbar(data = pollinator_means,aes(x = as.factor(position), ymin=mean-SE, ymax=mean+SE), 
+                width=1.0,size=1)+
+  geom_point(data = pollinator_means,aes(x = as.factor(position), y=mean), 
+                size=2)+
+  labs(x="Position", y = "Percentile", title = "Pollinators")+
+  theme_bw()+
+  theme(legend.position = "none",axis.text.x=element_text(angle=90,vjust=0.5, hjust=1))
 

### 2021-05-18 Scripts/Scripts_Alfonso/1_create_null_networks_Connectance_Fixed.R
Update 1_create_null_networks_Connectance_Fixed.R

@@ -190,11 +190,11 @@ for (i.network in 1:length(list_Network_id)){
   }
   
   # Save results in folder
-  folder_motifs_pos <- "Data/Csv/Motifs positions and null models"
+  folder_motifs_pos <- "Data/Csv/Motifs_positions_and_null_models"
   file_motifs_pos <- paste0(folder_motifs_pos,"/Binary_Mat_Sp_Motifs_positions_null_Conn_FiX_",list_Network_id[i.network],".csv") 
   write_csv(node_positions_i,file_motifs_pos)
   
-  folder_motifs_fre <- "Data/Csv/Motifs frequencies and null models"
+  folder_motifs_fre <- "Data/Csv/Motifs_frequencies_and_null_models"
   file_motifs_fre <- paste0(folder_motifs_fre,"/Binary_Mat_Sp_Motifs_frequencies_null_Conn_FiX_",list_Network_id[i.network],".csv") 
   write_csv(freq_motifs_i,file_motifs_fre)
   

### 2021-05-18 Scripts/Scripts_Alfonso/4_GLMM_Positions_Connectance_Fixed.R
Update 4_GLMM_Positions_Connectance_Fixed.R

@@ -4,7 +4,7 @@ library(lme4)
 library(nlme)
 
 # List the files with information about the positions
-file_pos <- "Data/Csv/Motifs positions and null models/GF_positions_frequency_percentile.csv"
+file_pos <- "Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv"
 all_position_percentiles <- read_csv(file_pos)
 
 # Create different dataframes for plant and pollinators, and remove data for postions np1 and np2,

### 2021-05-18 Scripts/Scripts_Alfonso/add_study_id.R
Create add_study_id.R

@@ -1,0 +1,38 @@
+
+add_study_id <- function(dataframe_input){
+  
+  col_names_dataframe <- colnames(dataframe_input)
+  
+  dataframe_input$study_id <- dataframe_input$Network_id
+  
+  dataframe_input$study_id <- as.character(dataframe_input$study_id)
+  
+  dataframe_input$study_id[grepl("peralta_2006", dataframe_input$study_id)] <- "peralta_2006"
+  dataframe_input$study_id[grepl("small_1976", dataframe_input$study_id)] <- "small_1976"
+  dataframe_input$study_id[grepl("arroyo_correa_new_zealand", dataframe_input$study_id)] <- "arroyo_correa_2019"
+  dataframe_input$study_id[grepl("fang_2008", dataframe_input$study_id)] <- "fang_2008"
+  dataframe_input$study_id[grepl("kaiser-bunbury_2017", dataframe_input$study_id)] <- "kaiser-bunbury_2017"
+  dataframe_input$study_id[grepl("inouye_1988", dataframe_input$study_id)] <- "inouye_1988"
+  dataframe_input$study_id[grepl("kaiser-bunbury_2010", dataframe_input$study_id)] <- "kaiser-bunbury_2010"
+  dataframe_input$study_id[grepl("kaiser-bunbury_2011", dataframe_input$study_id)] <- "kaiser-bunbury_2011"
+  dataframe_input$study_id[grepl("burkle_usa_2013", dataframe_input$study_id)] <- "burkle_2013"
+  dataframe_input$study_id[grepl("dicks_2002", dataframe_input$study_id)] <- "dicks_2002"
+  dataframe_input$study_id[grepl("dupont_2009", dataframe_input$study_id)] <- "dupont_2009"
+  dataframe_input$study_id[grepl("bartomeus_spain_2008_medca", dataframe_input$study_id)] <- "bartomeus_2008"
+  dataframe_input$study_id[grepl("bartomeus_spain_2008_batca", dataframe_input$study_id)] <- "bartomeus_2008"
+  dataframe_input$study_id[grepl("bartomeus_spain_2008_selop", dataframe_input$study_id)] <- "bartomeus_2008"
+  dataframe_input$study_id[grepl("bartomeus_spain_2008_miqop", dataframe_input$study_id)] <- "bartomeus_2008"
[…]

### 2021-05-18 Scripts/Scripts_Alfonso/2_processing_positions_null_Connectance_Fixed.R
Update 2_processing_positions_null_Connectance_Fixed.R

@@ -28,7 +28,7 @@ library(tidyverse)
 source("Scripts/Scripts_Alfonso/sizeclass_normalization.R") # To normalize frequencies of FGs
 
 # List the files with information about the positions
-folder_motif_data <- "Data/Csv/Motifs positions and null models"
+folder_motif_data <- "Data/Csv/Motifs_positions_and_null_models"
 
 motif_files <- list.files(folder_motif_data) 
 motif_link_files <-  motif_files[grep("Binary_Mat_Sp_Motifs_positions_null_Conn_FiX_",motif_files)]
@@ -211,7 +211,7 @@ for(i in 1:length(motif_link_files)){
 # Save every Position_quantiles_Conn_Fixed in a single file
 
 # List the files with information about the positions
-folder_motif_data <- "Data/Csv/Motifs positions and null models"
+folder_motif_data <- "Data/Csv/Motifs_positions_and null_models"
 
 motif_files <- list.files(folder_motif_data) 
 quant_link_files <-  motif_files[grep("Position_quantiles_Conn_Fixed_",motif_files)]

### 2021-05-18 Scripts/Scripts_Alfonso/3_processing_frequencies_null_Connectance_Fixed.R
Update 3_processing_frequencies_null_Connectance_Fixed.R

@@ -27,7 +27,7 @@
 library(tidyverse)
 
 # List the files with information about the frequencies of motifs
-folder_motif_data <- "Data/Csv/Motifs frequencies and null models"
+folder_motif_data <- "Data/Csv/Motifs_frequencies_and_null_models"
 
 motif_files <- list.files(folder_motif_data) 
 motif_freq_files <-  motif_files[grep("Binary_Mat_Sp_Motifs_frequencies_null_Conn_FiX_",
@@ -87,7 +87,7 @@ for(i in 1:length(motif_freq_files)){
 # Save every Motif_quantiles_Conn_Fixed_ in a single file
 
 # List the files with information about the positions
-folder_motif_data <- "Data/Csv/Motifs frequencies and null models"
+folder_motif_data <- "Data/Csv/Motifs_frequencies_and_null_models"
 
 motif_files <- list.files(folder_motif_data) 
 quant_link_files <-  motif_files[grep("Motif_quantiles_Conn_Fixed_",motif_files)]

### 2021-05-18 Draft/Draft.Rmd
Update Draft.Rmd

@@
 library(tidyverse)
+library(stringi)
 source("../Scripts/Scripts_Alfonso/add_study_id.R")
@@
 all_position_percentiles <- read_csv("../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
+
+all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
+                                                              "[0-9]+") %>% as.numeric()
 
@@
 plant_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(Node_FG %in% list_plants_FG, !position %in% c("np1","np2"),
+  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
          !is.na(expected_freq_its_GF))
 pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(!Node_FG %in% list_plants_FG, !position %in% c("np1","np2"),
+  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
          !is.na(expected_freq_its_GF))

### 2021-05-18 Draft/Draft.Rmd
Minimal edits + Fig 2 do not work

@@
 output: html_document
+editor_options: 
+  chunk_output_type: console
 ---
@@
 library(lme4)
+library(nlme)
 library(tidyverse)
@@
   geom_point(data = d %>% filter(motif != 1),
-             aes(x=as.factor(motif), y=percentil_sizeclass, 
+             aes(y=as.factor(motif), x=percentil_sizeclass, 
                  color = as.factor(motif)),
              position = "jitter",alpha=0.5)+
-  geom_errorbar(data = motif_means,aes(x = as.factor(motif), ymin=mean-SE, ymax=mean+SE), 
+  geom_errorbar(data = motif_means,aes(y = as.factor(motif), xmin=mean-SE, xmax=mean+SE), 
                 width=1.0,size=1)+
-  geom_point(data = motif_means,aes(x = as.factor(motif), y=mean), 
+  geom_point(data = motif_means,aes(y = as.factor(motif), x=mean), 
                 size=2)+
-  labs(x="Motif", y = "Percentile")+
+  labs(y="Motif", x = "Percentile")+
   theme_bw()+
@@
 #Fig 1 Should be a dot plot (or forest plot) of the mean +- SE of the 15 motifs.
+#NICE! Can we put motifs in Y axes, and % in X?
 ```
@@
   filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF))
+         !is.na(expected_freq_its_GF)) #ME DA ERROR
 pollinator_position_percentiles_filtered <- all_position_percentiles %>% 

### 2021-05-18 Draft/Draft.Rmd
Update Draft.Rmd

@@
 library(stringi)
+library(ggpubr)
 source("../Scripts/Scripts_Alfonso/add_study_id.R")
@@
 
-ggplot(NULL) + 
+GF_plant_pos <- ggplot(NULL) + 
   geom_point(data = plant_position_percentiles_filtered,
@@
   theme_bw()+
-  theme(legend.position = "none",axis.text.x=element_text(angle=90,vjust=0.5, hjust=1))
+  theme(legend.position = "none",axis.text.x=element_text(angle=90,vjust=0.5, hjust=1))+
+  library(lme4)
+library(nlme)
+library(tidyverse)
+library(stringi)
+library(ggpubr)
+source("Scripts/Scripts_Alfonso/add_study_id.R")
+
+all_position_percentiles <- read_csv("Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
+
+all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
+                                                              "[0-9]+") %>% as.numeric()
+
+all_position_percentiles <- add_study_id(all_position_percentiles)
+str(all_position_percentiles)
+head(all_position_percentiles)
+
+list_plants_FG <- as.character(1:10)
+
+plant_position_percentiles_filtered <- all_position_percentiles %>% 
+  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
+         !is.na(expected_freq_its_GF)) #ME DA ERROR
+pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
+  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
+         !is.na(expected_freq_its_GF))
+
+ggplot(plant_position_percentiles_filtered, aes(percentil_its_GF))+
+  geom_histogram(color="black", fill="white")+
+  facet_wrap(~position)+
+  theme_bw()+
+  labs(x="Sizeclass percentile", title = "Histograms: Percentiles for plant positions")
+
+ggplot(pollinator_position_percentiles_filtered, aes(percentil_its_GF))+
+  geom_histogram(color="black", fill="white")+
+  facet_wrap(~position)+
+  theme_bw()+
+  labs(x="Sizeclass percentile",title = "Histograms: Percentiles for pollinator positions")
+
+# estimated mean taking into account the random str is 0.XX +- 0.XX (look at the (Intercept) estimate)
+
+# Plants-------------
+
+# Mean percentile and SE taking into account the study system
+plant_codes <- plant_position_percentiles_filtered$position %>% unique()
+plant_means <- tibble(position = plant_codes)
+plant_means$mean <- NA
+plant_means$SE <- NA
+
+for(i.pos in 1:length(plant_codes)){
+
+  m <- lmer(percentil_its_GF ~ 1+(1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
+            data = subset(plant_position_percentiles_filtered,
+                          position == plant_codes[i.pos]))
+
+  plant_means$mean[i.pos] <- fixed.effects(m) %>% unname()
+  plant_means$SE[i.pos] <- sqrt(diag(vcov(m)))
+
+}
+
+GF_plant_pos <- ggplot(NULL) + 
+  geom_point(data = plant_position_percentiles_filtered,
+             aes(x=as.factor(position), y=percentil_its_GF, 
+                 color = as.factor(position)),
+             position = "jitter",alpha=0.5)+
+  facet_wrap(~Node_FG,ncol = 5)+
+  geom_errorbar(data = plant_means,aes(x = as.factor(position), ymin=mean-SE, ymax=mean+SE), 
+                width=1.0,size=1)+
+  geom_point(data = plant_means,aes(x = as.factor(position), y=mean), 
+             size=2)+
+  labs(x="Position", y = "Percentile",title = "Plants")+
+  theme_bw()+
+  theme(legend.position = "none")+#,axis.text.x=element_text(angle=90,vjust=0.5, hjust=1))+
+  coord_flip()
 
@@
 
-ggplot(NULL) + 
+GF_poll_pos <- ggplot(NULL) + 
   geom_point(data = pollinator_position_percentiles_filtered,
@@
              position = "jitter",alpha=0.5)+
-  facet_wrap(~Node_FG)+
+  facet_wrap(~Node_FG,ncol = 5)+
   geom_errorbar(data = pollinator_means,aes(x = as.factor(position), ymin=mean-SE, ymax=mean+SE), 
@@
   theme_bw()+
-  theme(legend.position = "none",axis.text.x=element_text(angle=90,vjust=0.5, hjust=1))
+  theme(legend.position = "none")+#,axis.text.x=element_text(angle=90,vjust=0.5, hjust=1))+
+  coord_flip()
+
+# Plant and Pollinators--------
+
+ggarrange(GF_plant_pos,GF_poll_pos,
+          ncol = 1, nrow = 2,heights = c(.9, 1.4))
 

### 2021-05-18 Draft/Draft.Rmd
Update Draft.Rmd

@@
              position = "jitter",alpha=0.5)+
-  facet_wrap(~Node_FG)+
-  geom_errorbar(data = plant_means,aes(x = as.factor(position), ymin=mean-SE, ymax=mean+SE), 
-                width=1.0,size=1)+
-  geom_point(data = plant_means,aes(x = as.factor(position), y=mean), 
-             size=2)+
-  labs(x="Position", y = "Percentile",title = "Pollinators")+
-  theme_bw()+
-  theme(legend.position = "none",axis.text.x=element_text(angle=90,vjust=0.5, hjust=1))+
-  library(lme4)
-library(nlme)
-library(tidyverse)
-library(stringi)
-library(ggpubr)
-source("Scripts/Scripts_Alfonso/add_study_id.R")
-
-all_position_percentiles <- read_csv("Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
-
-all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
-                                                              "[0-9]+") %>% as.numeric()
-
-all_position_percentiles <- add_study_id(all_position_percentiles)
-str(all_position_percentiles)
-head(all_position_percentiles)
-
-list_plants_FG <- as.character(1:10)
-
-plant_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF)) #ME DA ERROR
-pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF))
-
-ggplot(plant_position_percentiles_filtered, aes(percentil_its_GF))+
-  geom_histogram(color="black", fill="white")+
-  facet_wrap(~position)+
-  theme_bw()+
-  labs(x="Sizeclass percentile", title = "Histograms: Percentiles for plant positions")
-
-ggplot(pollinator_position_percentiles_filtered, aes(percentil_its_GF))+
-  geom_histogram(color="black", fill="white")+
-  facet_wrap(~position)+
-  theme_bw()+
-  labs(x="Sizeclass percentile",title = "Histograms: Percentiles for pollinator positions")
-
-# estimated mean taking into account the random str is 0.XX +- 0.XX (look at the (Intercept) estimate)
-
-# Plants-------------
-
-# Mean percentile and SE taking into account the study system
-plant_codes <- plant_position_percentiles_filtered$position %>% unique()
-plant_means <- tibble(position = plant_codes)
-plant_means$mean <- NA
-plant_means$SE <- NA
-
-for(i.pos in 1:length(plant_codes)){
-
-  m <- lmer(percentil_its_GF ~ 1+(1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = subset(plant_position_percentiles_filtered,
-                          position == plant_codes[i.pos]))
-
-  plant_means$mean[i.pos] <- fixed.effects(m) %>% unname()
-  plant_means$SE[i.pos] <- sqrt(diag(vcov(m)))
-
-}
-
-GF_plant_pos <- ggplot(NULL) + 
-  geom_point(data = plant_position_percentiles_filtered,
-             aes(x=as.factor(position), y=percentil_its_GF, 
-                 color = as.factor(position)),
-             position = "jitter",alpha=0.5)+
   facet_wrap(~Node_FG,ncol = 5)+

### 2021-05-18 Draft/Draft.Rmd
I think I did what I wanted to do. Not clean.

@@
   filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF)) #ME DA ERROR
+         !is.na(expected_freq_its_GF)) 
 pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
@@
 # Mean percentile and SE taking into account the study system
+combinations <- paste(plant_position_percentiles_filtered$position,
+                           plant_position_percentiles_filtered$Node_FG, sep = "_")
+combinations_codes <- combinations %>% unique()
+plant_means <- tibble(position = combinations_codes)
 plant_codes <- plant_position_percentiles_filtered$position %>% unique()
-plant_means <- tibble(position = plant_codes)
+#plant_means <- tibble(position = plant_codes)
 plant_means$mean <- NA
@@
 
+j <-  1
 for(i.pos in 1:length(plant_codes)){
 
-  m <- lmer(percentil_its_GF ~ 1+(1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
+  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), 
             data = subset(plant_position_percentiles_filtered,
                           position == plant_codes[i.pos]))  
-
-  plant_means$mean[i.pos] <- fixed.effects(m) %>% unname()
-  plant_means$SE[i.pos] <- sqrt(diag(vcov(m)))
+  #summary(m)
+  temp <- fixed.effects(m) %>% unname()
+  plant_means$mean[c(j:(j+4))] <- c(temp[1], #to get real means per FG
+                                    temp[1]+temp[2],
+                                    temp[1]+temp[3],
+                                    temp[1]+temp[4],
+                                    temp[1]+temp[5])
+  temp <- sqrt(diag(vcov(m)))
+  plant_means$SE[c(j:(j+4))] <- c(temp[1], 
+                                    temp[1]+temp[2],
+                                    temp[1]+temp[3],
+                                    temp[1]+temp[4],
+                                    temp[1]+temp[5]) #Alfonso, los errores se suman tambien??
+  j <- j+5 #esto puede que sea una guarrada
 
@@
 
+#NO SE PLOTEAR ESTO... 
+plant_means$true_position <- seq(1,220, 2)
+plant_means$FG <- seq(1,220, 2)
+plant_means$true_position <- unlist(strsplit(plant_means$position, "_", TRUE))[seq(1,220, 2)]
+plant_means$FG <- unlist(strsplit(plant_means$position, "_", TRUE))[seq(2,220, 2)]
+
 GF_plant_pos <- ggplot(NULL) + 
-  geom_point(data = plant_position_percentiles_filtered,
-             aes(x=as.factor(position), y=percentil_its_GF, 
-                 color = as.factor(position)),
-             position = "jitter",alpha=0.5)+
-  facet_wrap(~Node_FG,ncol = 5)+
-  geom_errorbar(data = plant_means,aes(x = as.factor(position), ymin=mean-SE, ymax=mean+SE), 
+  #geom_point(data = plant_means, #AQUI NO SE PONER LOS PUNTITOS :(
+             #aes(x=as.factor(position), y=percentil_its_GF, 
+              #   color = as.factor(position)),
+             #position = "jitter",alpha=0.5)+
+  facet_wrap(~FG)+
+  geom_errorbar(data = plant_means,aes(x = as.factor(true_position), ymin=mean-SE, ymax=mean+SE), 
                 width=1.0,size=1)+
-  geom_point(data = plant_means,aes(x = as.factor(position), y=mean), 
+  geom_point(data = plant_means,aes(x = as.factor(true_position), y=mean), 
              size=2)+
@@
   theme_bw()+
+  #theme(legend.position = "none",axis.text.x=element_text(angle=90,vjust=0.5, hjust=1))+
   theme(legend.position = "none")+#,axis.text.x=element_text(angle=90,vjust=0.5, hjust=1))+
@@
 
-# Pollinators--------
+GF_plant_pos #vaya kk de plot
+
+#mejor para comparar por posiciones?
+GF_plant_pos2 <- ggplot(NULL) + 
+  facet_wrap(~true_position)+
+  geom_errorbar(data = plant_means,aes(x = as.factor(FG), ymin=mean-SE, ymax=mean+SE), 
+                width=1.0,size=1)+
+  geom_point(data = plant_means,aes(x = as.factor(FG), y=mean), 
+             size=2)+
+  labs(x="FG", y = "Percentile",title = "Plants")+
+  theme_bw()+
+  #theme(legend.position = "none",axis.text.x=element_text(angle=90,vjust=0.5, hjust=1))+
+  theme(legend.position = "none")+#,axis.text.x=element_text(angle=90,vjust=0.5, hjust=1))+
+  coord_flip()
+
+GF_plant_pos2 #creo que mejor... me sigue sorprendiendo el e.g. GF 4. que esta asociado con muchas posiciones...
+
+# Pollinators-------- NOT UPDATED
 

### 2021-05-19 Draft/Draft.Rmd
Update Draft.Rmd

--- 2021-05-18 Draft/Draft.Rmd
@@
 plant_codes <- plant_position_percentiles_filtered$position %>% unique()
-plant_means <- tibble(position = plant_codes)
+plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
 plant_means$mean <- NA
@@
 
-  m <- lmer(percentil_its_GF ~ 1+(1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = subset(plant_position_percentiles_filtered,
-                          position == plant_codes[i.pos]))
+  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
+            data = plant_position_percentiles_filtered %>%
+                          filter(position == plant_codes[i.pos]))
 
-  plant_means$mean[i.pos] <- fixed.effects(m) %>% unname()
-  plant_means$SE[i.pos] <- sqrt(diag(vcov(m)))
+  temp <- fixed.effects(m) %>% unname()
+  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
+                                                                     temp[1]+temp[2],
+                                                                     temp[1]+temp[3],
+                                                                     temp[1]+temp[4],
+                                                                     temp[1]+temp[5]) ## to get real means per FG
+  temp <- sqrt(diag(vcov(m)))
+  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
+                                                                  temp[1]+temp[2],
+                                                                  temp[1]+temp[3],
+                                                                  temp[1]+temp[4],
+                                                                  temp[1]+temp[5])
 
@@
              position = "jitter",alpha=0.5)+
-  facet_wrap(~Node_FG,ncol = 5)+
   geom_errorbar(data = plant_means,aes(x = as.factor(position), ymin=mean-SE, ymax=mean+SE), 
                 width=1.0,size=1)+
+  facet_wrap(~Node_FG,ncol = 5)+
   geom_point(data = plant_means,aes(x = as.factor(position), y=mean), 
@@
 pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
-pollinator_means <- tibble(position = pollinator_codes)
+pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
 pollinator_means$mean <- NA
 pollinator_means$SE <- NA
+pollinator_means_reordered <- NULL
+for(i.pos in 1:length(pollinator_codes)){
+  print(i.pos)
+  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
+            data = pollinator_position_percentiles_filtered %>%
+                          filter(position == pollinator_codes[i.pos]))
 
-for(i.pos in 1:length(pollinator_codes)){
+  temp <- fixed.effects(m) %>% unname()
+  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)
 
-  m <- lmer(percentil_its_GF ~ 1+(1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = subset(pollinator_position_percentiles_filtered,
-                          position == pollinator_codes[i.pos]))
+  pollinator_means_aux$mean <- c(temp[1],
+                                 temp[1]+temp[2],
+                                 temp[1]+temp[3],
+                                 temp[1]+temp[4],
+                                 temp[1]+temp[5],
+                                 temp[1]+temp[6],
+                                 temp[1]+temp[7],
+                                 temp[1]+temp[8],
+                                 temp[1]+temp[9]) ## to get real means per FG
 
-  pollinator_means$mean[i.pos] <- fixed.effects(m) %>% unname()
-  pollinator_means$SE[i.pos] <- sqrt(diag(vcov(m)))
+  temp <- sqrt(diag(vcov(m)))
+  pollinator_means_aux$SE <- c(temp[1],
+                               temp[1]+temp[2],
+                               temp[1]+temp[3],
+                               temp[1]+temp[4],
+                               temp[1]+temp[5],
+                               temp[1]+temp[6],
+                               temp[1]+temp[7],
+                               temp[1]+temp[8],
+                               temp[1]+temp[9])
+
+  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)
 
 }
+
+# There are lower limits (mean - SE) smaller than 0 (see Other insects)
+# We set the lower limit of those error bars to zero
+
+pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
+pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
 
@@
              position = "jitter",alpha=0.5)+
+  geom_errorbar(data = pollinator_means_reordered, aes(x = as.factor(position), ymin=lower,
+                                                       ymax=mean+SE), 
+                width=1.0,size=1)+
   facet_wrap(~Node_FG,ncol = 5)+
-  geom_errorbar(data = pollinator_means,aes(x = as.factor(position), ymin=mean-SE, ymax=mean+SE), 
-                width=1.0,size=1)+
-  geom_point(data = pollinator_means,aes(x = as.factor(position), y=mean), 
+  geom_point(data = pollinator_means_reordered,aes(x = as.factor(position), y=mean), 
              size=2)+
@@
 ggarrange(GF_plant_pos,GF_poll_pos,
-          ncol = 1, nrow = 2,heights = c(.9, 1.4))
+          ncol = 1, nrow = 2,heights = c(.90, 1.4))
 

### 2021-05-19 Draft/Draft.Rmd
Update Draft.Rmd

@@
 pollinator_means_reordered <- NULL
+
 for(i.pos in 1:length(pollinator_codes)){
-  print(i.pos)
+
   m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 

### 2021-05-19 Draft/Draft.Rmd
Update Draft.Rmd

@@
             data = pollinator_position_percentiles_filtered %>%
-                          filter(position == pollinator_codes[i.pos]))
+                          filter(position == pollinator_codes[i.pos]),
+            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
 

### 2021-05-27 Draft/Draft.Rmd
Table S1 and figure S1 (list of studies and plant functional groups). Starting also with methods...

@@
 ---
-title: "Plant-pollintor networks worldwide are composed by the same specific building blocks"
-output: html_document
+title: Plant-pollintor networks worldwide are composed by the same specific building
+  blocks
+output:
+  html_document: default
+  pdf_document: default
 editor_options:
   chunk_output_type: console
+bibliography: bibliography.bib
 ---
@@
 motifs) and those constitute the building blocks of the whole network.
-Here we have compiled 60 networks from 29 different studies and show that some motifs are consitently over-represented worldwide, suggesting that the building blocks of plant-pollintor networks are not random and are associated to ...
+Here we have compiled 60 networks from 18 different studies and show that some motifs are consitently over-represented worldwide, suggesting that the building blocks of plant-pollintor networks are not random and are associated to ...
 Second, we show that the position of pollinator guilds and plant reproductive strategies is not random with respect to the positions occupied within each motif.
@@
 Intermediate levels to study plant-pollinator networks (meso-scale) have been little explored but can shed light of ecological processes not captured by the traditional approaches used in plant-pollinator network studies.
-[Explain what macro-descriptors have found i.e.
-Bascompte, and what pairwise interactions descriptors have accomplished i.e.
-trait-matching.
-End explaining Benno simmons work]
+
+[Explain what macro-descriptors have found i.e. Bascompte, and what pairwise interactions descriptors have accomplished i.e. trait-matching. End explaining Benno simmons work]
 
@@
 
-We have compiled 60 plant-pollinator networks from 29 different studies [...]
+We have compiled 60 plant-pollinator networks from 18 different studies (Table S1).
+All studies sampled plant-pollinator interactions in natural systems and were selected based on wide geographical coverage and the presence of interaction frequency as a measure of interaction strength.
+In total, there were 503 plant species, 1111 pollinator species and 6248 of plant-pollinator interactions counted.
+For ease of data manipulation plant and pollinator species names were standardize with the help of the package taxize version 0.9.99 [@chamberlain2020].
 
@@
 1) over and under represented motifs
-```{r}
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
 library(lme4)
@@
 2) FG-position associations.
-```{r}
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
 library(lme4)
@@
 ```
+
+##REFERENCES
+
+<div id ="refs"></div>
+
+##SUPPLEMENTARY MATERIAL
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align = "left"}
+##############################
+#TABLE S1. List of studies
+##############################
+
+#Load libraries
+library(kableExtra)
+library(dplyr)
+
+#Create data.frame with references
+
+#vector with number of netw per study
+`Number of networks` <- c("6", "2", "3", "1", "1", "1", "1", "2", "1", "1", "8", "16", "6", "2", "4", "1", "3", "1")
+
+#`Network structure` <- c(rep("Web", 22), rep("Metaweb",6))
+
+`First author` <- c("Bartomeus", "Dicks", "Dupont", "Elberling", "Fang", "Inouye", "Lundgren", "Olesen", "Small", "Souza", "Kaiser-Bunbury", "Bartomeus", 
+                    "Kaiser-Bunbury", "Kaiser-Bunbury", "Peralta", "Burkle", "Arroyo-Correa", "Bundgaard")
+
+Year <- c(2008,2002,2003,1999,2008,1988, 2005,2002,1976,2017,2017,2008,2011,2010,2006,2013,2019,2003)
+
+#Country <- c("Spain", "England", "Denmark", "Sweden", "China", "Australia", "Greenland", "Mauritius and Azores", #"Canada", "Brasil", "Seychelles", "Spain", "Seychelles",
+#"Mauritius", "Argentina", "USA", "New Zealand", "Denmark",  "Denmark", "Japan", "Canada", "Venezuela", "Japan", #"Ecuador", "New Zealand", "Venezuela",
+#"USA", "Ecuador")
+
+DOI <- c("https://doi.org/10.1007/s00442-007-0946-1", "https://doi.org/10.1046/j.0021-8790.2001.00572.x", "https://doi.org/10.1111/j.1365-2656.2008.01501.x",
+         "https://doi.org/10.1111/j.1600-0587.1999.tb00507.x", "https://doi.org/10.1111/1749-4877.12190", "https://doi.org/10.1111/j.1442-9993.1988.tb00968.x",
+         "https://doi.org/10.1657/1523-0430(2005)037[0514:TDAHCW]2.0.CO;2", "https://doi.org/10.1046/j.1472-4642.2002.00148.x",
+         "/13960/t4km08d21", "https://doi.org/10.1111/1365-2745.12978", "https://doi.org/10.1038/nature21071", "https://github.com/ibartomeus/BeeFunData",
+         "https://doi.org/10.1111/j.1365-2745.2010.01732.x", "https://doi.org/10.1016/j.ppees.2009.04.001", "https://doi.org/10.1111/ele.13510",
+         "https://doi.org/10.1126/science.1232728", "https://doi.org/10.1111/1365-2745.13332", "Unpublished, Master thesis")
+
+references <- data.frame(`First author`, Year, `Number of networks`,   DOI)
+
+colnames(references) <- c("First author", "Year", "Number of networks",  "DOI")
+
+#Check number of studies
+#nrow(references) # 18 studies
+#check number of networks
+#sum(as.numeric(references$`Number of networks`)) #60
+
+references %>%
+  arrange(`First author`)%>%
+  kable( longtable = T, booktabs = T,linesep = "\\addlinespace",align = c("cccc"),caption = "Table S1.
+List of studies ordered by author with the year of publication, number of contributed networks and digital object identifier") %>%
+  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = c("left"))
+
+```
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=13, fig.cap="Figure S1.
+Plant functional groups composition separated in qualitative and quantitative variables.
+Panel A) shows the percentage of the different categories within trait represented with different colours for each functional group.
+Plot B) shows the radar plot of the different quantitative variables standardize on the same scale also coloured with the same patterns of colours as qualitative variables per cluster."}
+
+#CODE TO PLOT FUNCTIONAL GROUPS
+#IT CAN BE PLOT WITH MUCH LESS CODE BUT NO TIME FOR CLEANING IT
+
+##########################################
+#Visualization of plant functional groups#
+##########################################
+
+library(cowplot)
+library(ggplot2)
+library(tidyr)
+library(dplyr)
+library(reshape2)
+library(data.table)
+library(patchwork)
+
+#LOAD DATA
+#read unscaled trait data in order to visualize better the clusters
+d <- read.csv("../Data/Csv/all_species_imputed_trait_data_forest_data.csv")
+
+dat_1 <- read.csv("../Data/Csv/imputed_trait_data_hclust_5_clusters_forest_data.csv", row.names = "X")
+
+d$Clusters <- dat_1$Clusters
+
+#select columns of interest
+t <- d[c("Breeding_system","IMPUTED_Compatibility","Autonomous_selfing_level",
+         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Flowers_per_inflorescence",
+         "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean", "STYLE_IMPUTED", "OVULES_IMPUTED", "life_form", "lifespan",
+         "IMPUTED_plant_height_mean_m", "Nectar_presence_absence", "Clusters")]
+
+##############################################################################################################################
+#Prepare table qualitative variables
+##############################################################################################################################
+
+##############################################################################################################################
+#Breeding system
+t$Breeding_system <- factor(t$Breeding_system, levels=c("Dioecious", "Monoecious", "Hermaphrodite"))
+
+#Summary to create table
+breeding <- t %>%
+  group_by(Clusters,Breeding_system) %>%
+  summarise (n = n()) %>%
+  mutate(Percentage = n / sum(n)*100)
+
+breeding <- breeding[,-3]
+
+breeding <- spread(breeding, Clusters, Percentage)
+
+colnames(breeding)[1] <- "Category"
+
+Trait <- data.frame(Trait= c(rep("Breeding system", 3)))
+
+Breeding_system <- cbind(Trait, breeding)
+
+##############################################################################################################################
+#Compatibility
+str(t)
+t$IMPUTED_Compatibility <- as.character(t$IMPUTED_Compatibility)
+t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="dioecious"] <- "Unisexual flower"
+t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="monoecious"] <- "Unisexual flower"
+t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_incompatible"] <- "Self incompatible"
+t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="partially_self_compatible"] <- "Partially self compatible"
+t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_compatible"] <- "Self compatible"
+
+t$IMPUTED_Compatibility <- factor(t$IMPUTED_Compatibility, levels=c("Unisexual flower", "Self incompatible", "Partially self compatible", "Self compatible"))
+#Summary to create table
+comp <- t %>%
+  group_by(Clusters,IMPUTED_Compatibility) %>%
+  summarise (n = n()) %>%
+  mutate(Percentage = n / sum(n)*100)
+
+comp <- comp[,-3]
+
+comp <- spread(comp, Clusters, Percentage)
+#Replace Na's with zeros
+comp[is.na(comp)] <- 0
+#Set call name os categories per trait
+colnames(comp)[1] <- "Category"
+#Create new column
+Trait <- data.frame(Trait= c(rep("Compatibility system", 4)))
+#Add column
+Compatibility_system <- cbind(Trait, comp)
+#Bind rows
+bind_rows(Breeding_system, Compatibility_system)
+
+############################################################################################################################################
+#Life form
+t$life_form <- as.character(t$life_form)
+t$life_form[t$life_form =="vine"] <- "Shrub"
+t$life_form[t$life_form =="tree"] <- "Tree"
+t$life_form[t$life_form =="herb"] <- "Herb"
+t$life_form[t$life_form =="shrub"] <- "Shrub"
+#Order levels
+t$life_form <- factor(t$life_form, levels=c("Tree", "Shrub", "Herb"))
+#Summary to create table
+life_form <- t %>%
+  group_by(Clusters,life_form) %>%
+  summarise (n = n()) %>%
+  mutate(Percentage = n / sum(n)*100)
+#delete column to convert to wide
+life_form <- life_form[,-3]
+#convert to wide
+life_form <- spread(life_form, Clusters, Percentage)
+#Set call name os categories per trait
+colnames(life_form)[1] <- "Category"
+#Create new column
+Trait <- data.frame(Trait= c(rep("Life form", 3)))
+#Add column
+Life_form<- cbind(Trait, life_form)
+#Bind rows
+bind_rows(Breeding_system, Compatibility_system, Life_form)
+
+############################################################################################################################################
+t$lifespan <- factor(t$lifespan, levels=c("Perennial","Short lived"))
+#Summary to create table
+life_span <- t %>%
+  group_by(Clusters,lifespan) %>%
+  summarise (n = n()) %>%
+  mutate(Percentage = n / sum(n)*100)
+#delete column to convert to wide
+life_span <- life_span[,-3]
+#convert to wide
+life_span <- spread(life_span, Clusters, Percentage)
+#Set call name os categories per trait
+colnames(life_span)[1] <- "Category"
+#Create new column
+Trait <- data.frame(Trait= c(rep("Life span", 2)))
+#Add column
+Life_span<- cbind(Trait, life_span)
+#Bind rows
+bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span)
+
+############################################################################################################################################
+t$Flower_morphology <- as.character(t$Flower_morphology)
+t$Flower_morphology[t$Flower_morphology=="Funnelform"] <- "Campanulate"
+t$Flower_morphology[t$Flower_morphology=="Spike"] <- "Brush"
+
+Flower_morphology <- t %>%
+  group_by(Clusters,Flower_morphology) %>%
+  summarise (n = n()) %>%
+  mutate(Percentage = n / sum(n)*100)
+#delete column to convert to wide
+Flower_morphology <- Flower_morphology[,-3]
+#convert to wide
+Flower_morphology <- spread(Flower_morphology, Clusters, Percentage)
+#Set call name os categories per trait
+colnames(Flower_morphology)[1] <- "Category"
+#Create new column
+Trait <- data.frame(Trait= c(rep("Flower shape", 6)))
+#Add column
+Flower_morphology<- cbind(Trait, Flower_morphology)
+#Replace Na's with zeros
+Flower_morphology[is.na(Flower_morphology)] <- 0
+#Bind rows
+bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology)
+
+############################################################################################################################################
+t$Flower_symmetry <- as.character(t$Flower_symmetry)
+t$Flower_symmetry[t$Flower_symmetry =="actinomorphic"] <- "Actinomorphic"
+t$Flower_symmetry[t$Flower_symmetry =="zygomorphic"] <- "Zygomorphic"
+
+Flower_symmetry <- t %>%
+  group_by(Clusters,Flower_symmetry) %>%
+  summarise (n = n()) %>%
+  mutate(Percentage = n / sum(n)*100)
+#delete column to convert to wide
+Flower_symmetry <- Flower_symmetry[,-3]
+#convert to wide
+Flower_symmetry <- spread(Flower_symmetry, Clusters, Percentage)
+#Set call name os categories per trait
+colnames(Flower_symmetry)[1] <- "Category"
+#Create new column
+Trait <- data.frame(Trait= c(rep("Flower symmetry", 2)))
+#Add column
+Flower_symmetry<- cbind(Trait, Flower_symmetry)
+#Bind rows
+bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology,Flower_symmetry)
+############################################################################################################################################
+t$Autonomous_selfing_level <- as.character(t$Autonomous_selfing_level)
+t$Autonomous_selfing_level[t$Autonomous_selfing_level =="none"] <- "None"
+t$Autonomous_selfing_level[t$Autonomous_selfing_level =="low"] <- "Low"
+t$Autonomous_selfing_level[t$Autonomous_selfing_level =="medium"] <- "Medium"
+t$Autonomous_selfing_level[t$Autonomous_selfing_level =="high"] <- "High"
+
+#Order levels
+t$Autonomous_selfing_level <- factor(t$Autonomous_selfing_level, levels=c("High", "Medium", "Low", "None"))
+
+Selfing <- t %>%
+  group_by(Clusters,Autonomous_selfing_level) %>%
+  summarise (n = n()) %>%
+  mutate(Percentage = n / sum(n)*100)
+
+#delete column to convert to wide
+Selfing <- Selfing[,-3]
+#convert to wide
+Selfing <- spread(Selfing, Clusters, Percentage)
+#Set call name os categories per trait
+colnames(Selfing)[1] <- "Category"
+#Create new column
+Trait <- data.frame(Trait= c(rep("Selfing level", 2)))
+#Replace Na's with zeros
+Selfing[is.na(Selfing)] <- 0
+#Add column
+Selfing_1 <- cbind(Trait, Selfing)
+#Bind rows
+bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology, Selfing_1)
+
+############################################################################################################################################
+t$Nectar_presence_absence <- as.character(t$Nectar_presence_absence)
+t$Nectar_presence_absence[t$Nectar_presence_absence =="yes"] <- "Yes"
+t$Nectar_presence_absence[t$Nectar_presence_absence =="no"] <- "No"
+
+Nectar <- t %>%
+  group_by(Clusters,Nectar_presence_absence) %>%
+  summarise (n = n()) %>%
+  mutate(Percentage = n / sum(n)*100)
+
+#delete column to convert to wide
+Nectar <- Nectar[,-3]
+#convert to wide
+Nectar <- spread(Nectar, Clusters, Percentage)
+#Set call name os categories per trait
+colnames(Nectar)[1] <- "Category"
+#Create new column
+Trait <- data.frame(Trait= c(rep("Nectar", 2)))
+#Replace Na's with zeros
+Nectar[is.na(Nectar)] <- 0
+#Add column
+Nectar <- cbind(Trait, Nectar)
+#Bind rows
+bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology, Flower_symmetry,Selfing_1, Nectar)
+
+##############################################################################################################################
+#Prepare table quantitative variables
+##############################################################################################################################
+
+Selfing <-  t %>% group_by(Clusters)%>% 
+  select(Autonomous_selfing_level_fruit_set) %>% # select variables to summarise
+  summarise_each(funs(min = min,
+                     # q25 = quantile(., 0.25), 
+                      median = median, 
+                      #q75 = quantile(., 0.75), 
+                      max = max,
+                      mean = mean, 
+                    sd = sd))
+
+s1 <- as.data.frame(t(Selfing))
+#set colnames
+colnames(s1) <- c("1","2","3","4","5")
+#remove the cluster row
+s1 <- s1[-1,]
+#convert rownames to 1st columns
+s1 <- setDT(s1, keep.rownames = "TRUE")[]
+colnames(s1)[1] <- "Category"
+#Create data frame to add grouping variable
+Trait <- data.frame(Trait= c(rep("Autonomous selfing", 5)))
+#Add column
+Selfing <- cbind(Trait, s1)
+
+##############################################################################################################################
+flower_number <-  t %>% group_by(Clusters)%>% 
+  select(Flowers_per_plant) %>% # select variables to summarise
+  summarise_each(funs(min = min,
+                      # q25 = quantile(., 0.25), 
+                      median = median, 
+                      #q75 = quantile(., 0.75), 
+                      max = max,
+                      mean = mean, 
+                      sd = sd))
+
+f1 <- as.data.frame(t(flower_number))
+#set colnames
+colnames(f1) <- c("1","2","3","4","5")
+#remove the cluster row
+f1 <- f1[-1,]
+#convert rownames to 1st columns
+f1 <- setDT(f1, keep.rownames = "TRUE")[]
+colnames(f1)[1] <- "Category"
+#Create data frame to add grouping variable
+Trait <- data.frame(Trait= c(rep("Flower number", 5)))
+#Add column
+Flower_number <- cbind(Trait, f1)
+
+##############################################################################################################################
+Flowers_per_inflorescence <-  t %>% group_by(Clusters)%>% 
+  select(Flowers_per_inflorescence) %>% # select variables to summarise
+  summarise_each(funs(min = min,
+                      # q25 = quantile(., 0.25), 
+                      median = median, 
+                      #q75 = quantile(., 0.75), 
+                      max = max,
+                      mean = mean, 
+                      sd = sd))
+
+f_i_1 <- as.data.frame(t(Flowers_per_inflorescence))
+#set colnames
+colnames(f_i_1) <- c("1","2","3","4","5")
+#remove the cluster row
+f_i_1 <- f_i_1[-1,]
+#convert rownames to 1st columns
+f_i_1 <- setDT(f_i_1, keep.rownames = "TRUE")[]
+colnames(f_i_1)[1] <- "Category"
+#Create data frame to add grouping variable
+Trait <- data.frame(Trait= c(rep("Flowers per inflorescence", 5)))
+#Add column
+Flower_per_inflo <- cbind(Trait, f_i_1)
+
+bind_rows(Selfing, Flower_number, Flower_per_inflo)
+
+##############################################################################################################################
+Floral_unit_width <-  t %>% group_by(Clusters)%>% 
+  select(Floral_unit_width) %>% # select variables to summarise
+  summarise_each(funs(min = min,
+                      # q25 = quantile(., 0.25), 
+                      median = median, 
+                      #q75 = quantile(., 0.75), 
+                      max = max,
+                      mean = mean, 
+                      sd = sd))
+
+f_u_w_1 <- as.data.frame(t(Floral_unit_width))
+#set colnames
+colnames(f_u_w_1) <- c("1","2","3","4","5")
+#remove the cluster row
+f_u_w_1 <- f_u_w_1[-1,]
+#convert rownames to 1st columns
+f_u_w_1 <- setDT(f_u_w_1, keep.rownames = "TRUE")[]
+colnames(f_u_w_1)[1] <- "Category"
+#Create data frame to add grouping variable
+Trait <- data.frame(Trait= c(rep("Inflorescence width", 5)))
+#Add column
+Inflo_width <- cbind(Trait, f_u_w_1)
+
+bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width)
+
+##############################################################################################################################
+Corolla_diameter_mean <-  t %>% group_by(Clusters)%>% 
+  select(Corolla_diameter_mean) %>% # select variables to summarise
+  summarise_each(funs(min = min,
+                      # q25 = quantile(., 0.25), 
+                      median = median, 
+                      #q75 = quantile(., 0.75), 
+                      max = max,
+                      mean = mean, 
+                      sd = sd))
+
+c_w_1 <- as.data.frame(t(Corolla_diameter_mean))
+#set colnames
+colnames(c_w_1) <- c("1","2","3","4","5")
+#remove the cluster row
+c_w_1 <- c_w_1[-1,]
+#convert rownames to 1st columns
+c_w_1 <- setDT(c_w_1, keep.rownames = "TRUE")[]
+colnames(c_w_1)[1] <- "Category"
+#Create data frame to add grouping variable
+Trait <- data.frame(Trait= c(rep("Flower width", 5)))
+#Add column
+Flower_width <- cbind(Trait, c_w_1)
+
+bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width)
+
+##############################################################################################################################
+Corolla_length_mean <-  t %>% group_by(Clusters)%>% 
+  select(Corolla_length_mean) %>% # select variables to summarise
+  summarise_each(funs(min = min,
+                      # q25 = quantile(., 0.25), 
+                      median = median, 
+                      #q75 = quantile(., 0.75), 
+                      max = max,
+                      mean = mean, 
+                      sd = sd))
+
+c_l_1 <- as.data.frame(t(Corolla_length_mean))
+#set colnames
+colnames(c_l_1) <- c("1","2","3","4","5")
+#remove the cluster row
+c_l_1 <- c_l_1[-1,]
+#convert rownames to 1st columns
+c_l_1 <- setDT(c_l_1, keep.rownames = "TRUE")[]
+colnames(c_l_1)[1] <- "Category"
+#Create data frame to add grouping variable
+Trait <- data.frame(Trait= c(rep("Flower length", 5)))
+#Add column
+Flower_length<- cbind(Trait, c_l_1)
+
+bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length)
+
+##############################################################################################################################
+STYLE_IMPUTED <-  t %>% group_by(Clusters)%>% 
+  select(STYLE_IMPUTED) %>% # select variables to summarise
+  summarise_each(funs(min = min,
+                      # q25 = quantile(., 0.25), 
+                      median = median, 
+                      #q75 = quantile(., 0.75), 
+                      max = max,
+                      mean = mean, 
+                      sd = sd))
+
+s_l_1 <- as.data.frame(t(STYLE_IMPUTED))
+#set colnames
+colnames(s_l_1) <- c("1","2","3","4","5")
+#remove the cluster row
+s_l_1 <- s_l_1[-1,]
+#convert rownames to 1st columns
+s_l_1 <- setDT(s_l_1, keep.rownames = "TRUE")[]
+colnames(s_l_1)[1] <- "Category"
+#Create data frame to add grouping variable
+Trait <- data.frame(Trait= c(rep("Style length", 5)))
+#Add column
+Style_length<- cbind(Trait, s_l_1)
+
+bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length, Style_length)
+
+##############################################################################################################################
+
+OVULES_IMPUTED <-  t %>% group_by(Clusters)%>% 
+  select(OVULES_IMPUTED) %>% # select variables to summarise
+  summarise_each(funs(min = min,
+                      # q25 = quantile(., 0.25), 
+                      median = median, 
+                      #q75 = quantile(., 0.75), 
+                      max = max,
+                      mean = mean, 
+                      sd = sd))
+
+o_n_1 <- as.data.frame(t(OVULES_IMPUTED))
+#set colnames
+colnames(o_n_1) <- c("1","2","3","4","5")
+#remove the cluster row
+o_n_1 <- o_n_1[-1,]
+#convert rownames to 1st columns
+o_n_1 <- setDT(o_n_1, keep.rownames = "TRUE")[]
+colnames(o_n_1)[1] <- "Category"
+#Create data frame to add grouping variable
+Trait <- data.frame(Trait= c(rep("Ovule number", 5)))
+#Add column
+Ovule_number <- cbind(Trait, o_n_1)
+
+bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length, Ovule_number)
+
+##############################################################################################################################
+
+IMPUTED_plant_height_mean_m <-  t %>% group_by(Clusters)%>% 
+  select(IMPUTED_plant_height_mean_m) %>% # select variables to summarise
+  summarise_each(funs(min = min,
+                      # q25 = quantile(., 0.25), 
+                      median = median, 
+                      #q75 = quantile(., 0.75), 
+                      max = max,
+                      mean = mean, 
+                      sd = sd))
+
+p_h_1 <- as.data.frame(t(IMPUTED_plant_height_mean_m))
+#set colnames
+colnames(p_h_1) <- c("1","2","3","4","5")
+#remove the cluster row
+p_h_1 <- p_h_1[-1,]
+#convert rownames to 1st columns
+p_h_1 <- setDT(p_h_1, keep.rownames = "TRUE")[]
+colnames(p_h_1)[1] <- "Category"
+#Create data frame to add grouping variable
+Trait <- data.frame(Trait= c(rep("Plant height", 5)))
+#Add column
+Plant_height <- cbind(Trait, p_h_1)
+
+#Bind quantitative and qualitative variables
+Table_all_traits <- bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology, Flower_symmetry,Selfing_1, Nectar,
+          Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length, Style_length, Ovule_number, Plant_height)
+
+#Select just two decimals
+is.num <- sapply(Table_all_traits, is.numeric)
+Table_all_traits[is.num] <- lapply(Table_all_traits[is.num], round, 2)
+
+colnames(Table_all_traits) <- c("Trait", "Category", "Cluster 1", "Cluster 2", "Cluster 3", "Cluster 4", "Cluster 5")
+
+#LOAD LIBRARIES
+#devtools::install_github("ricardo-bion/ggradar", dependencies=TRUE)
+suppressPackageStartupMessages(library(dplyr))
+library(scales)
+library(tibble)
+library(ggradar)
+library(janitor)
+library(grid)
+library(dplyr)
+library(lubridate)
+#QUANTITATIVVE VARIABLES
+
+#generate subset of quantitative variables for plotting
+quant_median <- subset(Table_all_traits, Category=="median")
+
+#delete col number 2
+quant_median <- quant_median[,-2]
+
+#transpose dataframe
+final_df <- as.data.frame(t(quant_median))
+
+#rownames to colnames (1st one)
+final_df_1 <- final_df %>% row_to_names(row_number = 1)
+
+#Convert all variables to numeric
+final_df_2 <- sapply(final_df_1, function(x) as.numeric(as.character(x)))
+
+#set back the missed rownames in the processing
+rownames(final_df_2) <- rownames(final_df_1)
+
+# Convert to dataframe
+final_df_2 <- as.data.frame(final_df_2)
+
+# Scale values and set rowname as column
+final_df_3 <-final_df_2 %>% rownames_to_column( var = "group" ) %>%   mutate_at(vars(-group),funs(rescale))
+
+#Plot Radar
+#ggradar(final_df_3)
+
+#QUALITATIVE VARIABLES
+
+#LOAD DATA
+#read unscaled trait data in order to visualize better the clusters
+d <- read.csv("../Data/Csv/all_species_imputed_trait_data_forest_data.csv")
+
+dat_1 <- read.csv("../Data/Csv/imputed_trait_data_hclust_5_clusters_forest_data.csv", row.names = "X")
+
+d$Clusters <- dat_1$Clusters
+
+#select columns of interest
+t <- d[c("Breeding_system","IMPUTED_Compatibility","Autonomous_selfing_level",
+         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Flowers_per_inflorescence",
+         "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean", "STYLE_IMPUTED", "OVULES_IMPUTED", "life_form", "lifespan",
+         "IMPUTED_plant_height_mean_m", "Nectar_presence_absence", "Clusters")]
+
+##############################################################################################################################
+#Prepare table qualitative variables
+##############################################################################################################################
+
+##############################################################################################################################
+#Breeding system
+t$Breeding_system <- factor(t$Breeding_system, levels=c("Dioecious", "Monoecious", "Hermaphrodite"))
+
+#Summary to create table
+breeding <- t %>%
+  group_by(Clusters,Breeding_system) %>%
+  summarise (n = n()) %>%
+  mutate(Percentage = n / sum(n)*100)
+
+breeding <- breeding[,-3]
+
+breeding <- spread(breeding, Clusters, Percentage)
+
+colnames(breeding)[1] <- "Category"
+
+Trait <- data.frame(Trait= c(rep("Breeding system", 3)))
+
+Breeding_system <- cbind(Trait, breeding)
+
+##############################################################################################################################
+#Compatibility
+str(t)
+t$IMPUTED_Compatibility <- as.character(t$IMPUTED_Compatibility)
+t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="dioecious"] <- "Self incompatible"
+t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="monoecious"] <- "Self incompatible"
+t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_incompatible"] <- "Self incompatible"
+t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="partially_self_compatible"] <- "Partially self compatible"
+t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_compatible"] <- "Self compatible"
+
+t$IMPUTED_Compatibility <- factor(t$IMPUTED_Compatibility, levels=c("Self incompatible", "Partially self compatible", "Self compatible"))
+#Summary to create table
+comp <- t %>%
+  group_by(Clusters,IMPUTED_Compatibility) %>%
+  summarise (n = n()) %>%
+  mutate(Percentage = n / sum(n)*100)
+
+comp <- comp[,-3]
+
+comp <- spread(comp, Clusters, Percentage)
+#Replace Na's with zeros
+comp[is.na(comp)] <- 0
+#Set call name os categories per trait
+colnames(comp)[1] <- "Category"
+#Create new column
+Trait <- data.frame(Trait= c(rep("Compatibility system", 3)))
+#Add column
+Compatibility_system <- cbind(Trait, comp)
+#Bind rows
+bind_rows(Breeding_system, Compatibility_system)
+
+############################################################################################################################################
+#Life form
+t$life_form <- as.character(t$life_form)
+t$life_form[t$life_form =="vine"] <- "Shrub"
+t$life_form[t$life_form =="tree"] <- "Tree"
+t$life_form[t$life_form =="herb"] <- "Herb"
+t$life_form[t$life_form =="shrub"] <- "Shrub"
+#Order levels
+t$life_form <- factor(t$life_form, levels=c("Tree", "Shrub", "Herb"))
+#Summary to create table
+life_form <- t %>%
+  group_by(Clusters,life_form) %>%
+  summarise (n = n()) %>%
+  mutate(Percentage = n / sum(n)*100)
+#delete column to convert to wide
+life_form <- life_form[,-3]
+#convert to wide
+life_form <- spread(life_form, Clusters, Percentage)
+#Set call name os categories per trait
+colnames(life_form)[1] <- "Category"
+#Create new column
+Trait <- data.frame(Trait= c(rep("Life form", 3)))
+#Add column
+Life_form<- cbind(Trait, life_form)
+#Bind rows
+bind_rows(Breeding_system, Compatibility_system, Life_form)
+
+############################################################################################################################################
+t$lifespan <- factor(t$lifespan, levels=c("Perennial","Short lived"))
+#Summary to create table
+life_span <- t %>%
+  group_by(Clusters,lifespan) %>%
+  summarise (n = n()) %>%
+  mutate(Percentage = n / sum(n)*100)
+#delete column to convert to wide
+life_span <- life_span[,-3]
+#convert to wide
+life_span <- spread(life_span, Clusters, Percentage)
+#Set call name os categories per trait
+colnames(life_span)[1] <- "Category"
+#Create new column
+Trait <- data.frame(Trait= c(rep("Life span", 2)))
+#Add column
+Life_span<- cbind(Trait, life_span)
+#Bind rows
+bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span)
+
+############################################################################################################################################
+#t$Flower_morphology <- as.character(t$Flower_morphology)
+#t$Flower_morphology[t$Flower_morphology=="Funnelform"] <- "Campanulate"
+#t$Flower_morphology[t$Flower_morphology=="Spike"] <- "Brush"
+#
+#Flower_morphology <- t %>%
+#  group_by(Clusters,Flower_morphology) %>%
+#  summarise (n = n()) %>%
+#  mutate(Percentage = n / sum(n)*100)
+##delete column to convert to wide
+#Flower_morphology <- Flower_morphology[,-3]
+##convert to wide
+#Flower_morphology <- spread(Flower_morphology, Clusters, Percentage)
+##Set call name os categories per trait
+#colnames(Flower_morphology)[1] <- "Category"
+##Create new column
+#Trait <- data.frame(Trait= c(rep("Flower shape", 6)))
+##Add column
+#Flower_morphology<- cbind(Trait, Flower_morphology)
+##Replace Na's with zeros
+#Flower_morphology[is.na(Flower_morphology)] <- 0
+##Bind rows
+#bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology)
+#
+############################################################################################################################################
+t$Flower_symmetry <- as.character(t$Flower_symmetry)
+t$Flower_symmetry[t$Flower_symmetry =="actinomorphic"] <- "Actinomorphic"
+t$Flower_symmetry[t$Flower_symmetry =="zygomorphic"] <- "Zygomorphic"
+
+Flower_symmetry <- t %>%
+  group_by(Clusters,Flower_symmetry) %>%
+  summarise (n = n()) %>%
+  mutate(Percentage = n / sum(n)*100)
+#delete column to convert to wide
+Flower_symmetry <- Flower_symmetry[,-3]
+#convert to wide
+Flower_symmetry <- spread(Flower_symmetry, Clusters, Percentage)
+#Set call name os categories per trait
+colnames(Flower_symmetry)[1] <- "Category"
+#Create new column
+Trait <- data.frame(Trait= c(rep("Flower symmetry", 2)))
+#Add column
+Flower_symmetry<- cbind(Trait, Flower_symmetry)
+#Bind rows
+bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology,Flower_symmetry)
+############################################################################################################################################
+#t$Autonomous_selfing_level <- as.character(t$Autonomous_selfing_level)
+#t$Autonomous_selfing_level[t$Autonomous_selfing_level =="none"] <- "None"
+#t$Autonomous_selfing_level[t$Autonomous_selfing_level =="low"] <- "Low"
+#t$Autonomous_selfing_level[t$Autonomous_selfing_level =="medium"] <- "Medium"
+#t$Autonomous_selfing_level[t$Autonomous_selfing_level =="high"] <- "High"
+#
+##Order levels
+#t$Autonomous_selfing_level <- factor(t$Autonomous_selfing_level, levels=c("High", "Medium", "Low", "None"))
+#
+#Selfing <- t %>%
+#  group_by(Clusters,Autonomous_selfing_level) %>%
+#  summarise (n = n()) %>%
+#  mutate(Percentage = n / sum(n)*100)
+#
+##delete column to convert to wide
+#Selfing <- Selfing[,-3]
+##convert to wide
+#Selfing <- spread(Selfing, Clusters, Percentage)
+##Set call name os categories per trait
+#colnames(Selfing)[1] <- "Category"
+##Create new column
+#Trait <- data.frame(Trait= c(rep("Selfing level", 2)))
+##Replace Na's with zeros
+#Selfing[is.na(Selfing)] <- 0
+##Add column
+#Selfing_1 <- cbind(Trait, Selfing)
+##Bind rows
+#bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology, Selfing_1)
+#
+#############################################################################################################################################
+t$Nectar_presence_absence <- as.character(t$Nectar_presence_absence)
+t$Nectar_presence_absence[t$Nectar_presence_absence =="yes"] <- "Yes"
+t$Nectar_presence_absence[t$Nectar_presence_absence =="no"] <- "No"
+
+Nectar <- t %>%
+  group_by(Clusters,Nectar_presence_absence) %>%
+  summarise (n = n()) %>%
+  mutate(Percentage = n / sum(n)*100)
+
+#delete column to convert to wide
+Nectar <- Nectar[,-3]
+#convert to wide
+Nectar <- spread(Nectar, Clusters, Percentage)
+#Set call name os categories per trait
+colnames(Nectar)[1] <- "Category"
+#Create new column
+Trait <- data.frame(Trait= c(rep("Nectar", 2)))
+#Replace Na's with zeros
+Nectar[is.na(Nectar)] <- 0
+#Add column
+Nectar <- cbind(Trait, Nectar)
+#Bind rows
+data <- bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span, Flower_symmetry, Nectar)
+
+#remove first col
+data_1 <- data[,-1]
+colnames(data_1) <- c("Category", "Cluster 1", "Cluster 2", "Cluster 3", "Cluster 4", "Cluster 5")
+
+#transpose dataframe
+data_2 <- as.data.frame(t(data_1))
+
+#rownames to colnames (1st one)
+data_3 <- data_2 %>% row_to_names(row_number = 1)
+
+#Convert all variables to numeric
+data_4 <- sapply(data_3, function(x) as.numeric(as.character(x)))
+
+#set back the missed rownames in the processing
+rownames(data_4) <- rownames(data_3)
+
+# Convert to dataframe
+data_4 <- as.data.frame(data_4)
+
+# Scale values and set rowname as column
+data_5 <-data_4 %>% rownames_to_column( var = "group" )
+
+data_6 <- melt(data_5)
+
+cluster1 <- subset(data_6, group=="Cluster 1")
+
+cluster1$traits <- c(rep("Breeding system",3), rep("Compatibility",3), rep("Life form",3),
+                     rep("Life span",2), rep("Flower symmetry",2), rep("Nectar",2))
+
+#Try to achieve the desire output with plot_grid
+
+c1 <- cluster1 %>% 
+  ggplot(aes(x = variable,  y = value, fill = group))  +  
+  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values="#00AFBB")+
+  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())+scale_y_continuous(expand = c(0,0)) +
+  theme(axis.title.x = element_blank(), axis.text.x=element_blank(),plot.title = element_text(size = 18))+ ylab("")+
+  ggtitle("A) Qualitative variables")
+
+cluster2 <- subset(data_6, group=="Cluster 2")
+
+cluster2$traits <- c(rep("Breeding system",3), rep("Compatibility",3), rep("Life form",3),
+                     rep("Life span",2), rep("Flower symmetry",2), rep("Nectar",2))
+
+c2 <- cluster2 %>% 
+  ggplot(aes(x = variable,  y = value, fill = group))  +  
+  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values="#E69F00")+
+  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())+scale_y_continuous(expand = c(0,0)) +
+  theme(strip.background = element_blank(), strip.text = element_blank())+
+  theme(axis.title.x = element_blank(), axis.text.x=element_blank())+ylab("")
+
+cluster3 <- subset(data_6, group=="Cluster 3")
+
+cluster3$traits <- c(rep("Breeding system",3), rep("Compatibility",3), rep("Life form",3),
+                     rep("Life span",2), rep("Flower symmetry",2), rep("Nectar",2))
+
+c3 <- cluster3 %>% 
+  ggplot(aes(x = variable,  y = value, fill = group))  +  
+  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values="#FC4E07")+
+  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())+scale_y_continuous(expand = c(0,0)) +
+  theme(axis.title.x = element_blank(), axis.text.x=element_blank())+
+  theme(strip.background = element_blank(), strip.text = element_blank())+ylab("Percentage")
+
+cluster4 <- subset(data_6, group=="Cluster 4")
+
+cluster4$traits <- c(rep("Breeding system",3), rep("Compatibility",3), rep("Life form",3),
+                     rep("Life span",2), rep("Flower symmetry",2), rep("Nectar",2))
+
+c4 <- cluster4 %>% 
+  ggplot(aes(x = variable,  y = value, fill = group))  +  
+  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values="#000000")+
+  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())+scale_y_continuous(expand = c(0,0)) +
+  theme(axis.title.x = element_blank(), axis.text.x=element_blank())+
+  theme(strip.background = element_blank(), strip.text = element_blank())+ylab("")
+
+cluster5 <- subset(data_6, group=="Cluster 5")
+
+cluster5$traits <- c(rep("Breeding system",3), rep("Compatibility",3), rep("Life form",3),
+                     rep("Life span",2), rep("Flower symmetry",2), rep("Nectar",2))
+c5 <- cluster5 %>% 
+  ggplot(aes(x = variable,  y = value, fill = group))  +  
+  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values="darkgreen")+
+  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
+  scale_y_continuous(expand = c(0,0)) +
+  theme(axis.text.x = element_text(angle = 45,vjust = 1, hjust=1))+
+  theme(strip.background = element_blank(), strip.text = element_blank())+ylab("")+xlab("")
+
+A <- c1 + c2 + c3 + c4 + c5 + plot_layout(ncol = 1)
+B <- ggradar(final_df_3, group.colours=c("#00AFBB", "#E69F00", "#FC4E07","#000000", "darkgreen"),
+             legend.text.size=5, grid.label.size = 0,legend.position = "none",axis.label.size=3)+ 
+  guides(shape = guide_legend(override.aes = list(size = 0.5)))+ ggtitle("B) Quantitative variables")+
+  theme(plot.title = element_text(size = 18))
+
+patch <- A | B
+
+patch + plot_annotation(title = "Plant functional groups",theme = theme(plot.title = element_text(size = 20,face="bold")))
+
+```

### 2021-05-27 Scripts/Supplementary_Material/Table_S1.R

@@ -1,0 +1,45 @@
+##############################
+#TABLE S1. List of studies
+##############################
+
+#Load libraries
+library(kableExtra)
+library(dplyr)
+
+#Create data.frame with references
+
+#vector with number of netw per study
+`Number of networks` <- c("6", "2", "3", "1", "1", "1", "1", "2", "1", "1", "8", "16", "6", "2", "4", "1", "3", "1")
+
+#`Network structure` <- c(rep("Web", 22), rep("Metaweb",6))
+
+`First author` <- c("Bartomeus", "Dicks", "Dupont", "Elberling", "Fang", "Inouye", "Lundgren", "Olesen", "Small", "Souza", "Kaiser-Bunbury", "Bartomeus", 
+                    "Kaiser-Bunbury", "Kaiser-Bunbury", "Peralta", "Burkle", "Arroyo-Correa", "Bundgaard")
+
+Year <- c(2008,2002,2003,1999,2008,1988, 2005,2002,1976,2017,2017,2008,2011,2010,2006,2013,2019,2003)
+
+#Country <- c("Spain", "England", "Denmark", "Sweden", "China", "Australia", "Greenland", "Mauritius and Azores", #"Canada", "Brasil", "Seychelles", "Spain", "Seychelles",
+#"Mauritius", "Argentina", "USA", "New Zealand", "Denmark",  "Denmark", "Japan", "Canada", "Venezuela", "Japan", #"Ecuador", "New Zealand", "Venezuela",
+#"USA", "Ecuador")
+
+DOI <- c("https://doi.org/10.1007/s00442-007-0946-1", "https://doi.org/10.1046/j.0021-8790.2001.00572.x", "https://doi.org/10.1111/j.1365-2656.2008.01501.x",
+         "https://doi.org/10.1111/j.1600-0587.1999.tb00507.x", "https://doi.org/10.1111/1749-4877.12190", "https://doi.org/10.1111/j.1442-9993.1988.tb00968.x",
+         "https://doi.org/10.1657/1523-0430(2005)037[0514:TDAHCW]2.0.CO;2", "https://doi.org/10.1046/j.1472-4642.2002.00148.x",
+         "/13960/t4km08d21", "https://doi.org/10.1111/1365-2745.12978", "https://doi.org/10.1038/nature21071", "https://github.com/ibartomeus/BeeFunData",
[…]

### 2021-05-27 Draft/Draft.Rmd
some more edits

@@
 
+**Plant-pollinator studies**
+
 We have compiled 60 plant-pollinator networks from 18 different studies (Table S1).
 All studies sampled plant-pollinator interactions in natural systems and were selected based on wide geographical coverage and the presence of interaction frequency as a measure of interaction strength.
-In total, there were 503 plant species, 1111 pollinator species and 6248 of plant-pollinator interactions counted.
+In total, there were 503 plant species, 1111 pollinator species and 6248 of pairwise interactions registered.
 For ease of data manipulation plant and pollinator species names were standardize with the help of the package taxize version 0.9.99 [@chamberlain2020].
 
+**Plant functional groups and pollinator guilds**
+
+First, we grouped plant species into five functional groups that summarized the main plant reproductive strategies.
+This was done with the help of the plant trait dataset built in Lanuza et al., (unpublished) that consisted of 16 plant functional traits (x floral, x reproductive and x vegetative; Table S2).
+
+Second,...
+
+This dataset had 16 traits
+
+The high number of plant orders in this dataset (38) makes difficult to summarize plants on functional groups
+
+reproductive strategies with the help of hierarchical clustering analysis. This was done by using a dataset compiled on the same set of networks that had 16
+
 Plants were grouped into reproductive strategies [justify and explain the process]
+
+Functional groups
+We calculated the distance of the different functional traits with the function gowdis from the package FD (Laliberté et al., 2014) with the method ward.D2 used for non-squared distances (Murtagh & Legendre, 2014).
+All the numerical traits were previously scaled.
+Then, we applied  a hierarchical cluster analysis with the function hclust from the R stats package and we found the optimal number of clusters with the function kgs that conducts the penalty function of Kelley et al., (1996) from the package maptree (White & Gramacy, 2009).
 

### 2021-05-27 Scripts/Scripts_Funtional_Groups/5_Plotting_Functional_Groups.R
Some work on methods

@@ -1,347 +1,6 @@
----
-title: Plant-pollintor networks worldwide are composed by the same specific building
-  blocks
-output:
-  html_document: default
-  pdf_document: default
-editor_options:
-  chunk_output_type: console
-bibliography: bibliography.bib
----
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
-
-##Abstract
-
-Ecological processes leave distinct structural imprints on indirect interactions in mutualistic networks. Detecting those relationships is not trivial since they go beyond pair-wise interactions, but may get blurred when considering full network descriptors. However, recent work has shown the network meso-scale can capture this important information. The meso-scale describes network subgraphs representing patterns of interactions between a small number of species (i.e. motifs) and those constitute the building blocks of the whole network. Here we have compiled 60 networks from 18 different studies and show that some motifs are consitently over-represented worldwide, suggesting that the building blocks of plant-pollintor networks are not random and are associated to ... Second, we show that the position of pollinator guilds and plant reproductive strategies is not random with respect to the positions occupied within each motif. ... Hence, we show that species ecology is shaping the building blocks that conform the web of life.
-
-##INTRODUCTION
-
-The interaction between plants and pollinators can be studied at different scales, from species level interactions (micro-scale) to the full network structure (macro-scale). However, condensing to species level and the holistic view of the full network involves missing relevant information for the understanding of ecological processes. Intermediate levels to study plant-pollinator networks (meso-scale) have been little explored but can shed light of ecological processes not captured by the traditional approaches used in plant-pollinator network studies. 
-
-
-[Explain what macro-descriptors have found i.e. Bascompte, and what pairwise interactions descriptors have accomplished i.e. trait-matching. End explaining Benno simmons work]
-
[…]

### 2021-05-28 Draft/Draft.Rmd
A bit of intro and playing with heatmaps

--- 2021-05-27 Draft/Draft.Rmd
@@
 The interaction between plants and pollinators can be studied at different scales, from species level interactions (micro-scale) to the full network structure (macro-scale).
-However, condensing to species level and the holistic view of the full network involves missing relevant information for the understanding of ecological processes.
-Intermediate levels to study plant-pollinator networks (meso-scale) have been little explored but can shed light of ecological processes not captured by the traditional approaches used in plant-pollinator network studies.
+However, condensing to species level and the holistic view of the full network involves missing relevant information for the understanding of ecological processes [@delmas2019; @simmons2019].
+Intermediate levels that investigate plant-pollinator networks (meso-scale) have been little explored but can shed light of ecological processes not captured by the traditional approaches used in plant-pollinator network studies.
+
+Several studies have evaluated the structure of plant-pollinator interactions.
+These studies have found common structural properties across networks that can help the understanding of the determinats of biodiversity [@bastolla2009].
+One of the major findings is the nested structure of mutualistic networks [@bascompte2003] which describes the topological structure where the specialist interact with subgroups of the interacting species of the generalist.
+Further, the degree distribution (number of links per species) of plant-pollinator networks have been shown to generally follow a power-law truncated distribution [@jordano2003].
+Moreover, at the species level ...
+
+Trait matching
 
@@
 
+**Plant-pollinator studies**
+
 We have compiled 60 plant-pollinator networks from 18 different studies (Table S1).
 All studies sampled plant-pollinator interactions in natural systems and were selected based on wide geographical coverage and the presence of interaction frequency as a measure of interaction strength.
-In total, there were 503 plant species, 1111 pollinator species and 6248 of plant-pollinator interactions counted.
+In total, there were 503 plant species, 1111 pollinator species and 6248 of pairwise interactions registered.
 For ease of data manipulation plant and pollinator species names were standardize with the help of the package taxize version 0.9.99 [@chamberlain2020].
 
-Plants were grouped into reproductive strategies [justify and explain the process]
-
-Pollintors were grouped into guilds, because [justify and explain, it's important to convince the reader that Order level for pollinators and FG for plants makes sense].
+**Plant and pollinator functional groups**
+
+First, plant species were grouped into the optimal number of functional groups that summarized the main plant reproductive strategies.
+This was done with the help of hierarchical cluster analysis by using the trait dataset compiled in Lanuza et al., (unpublished).
+This dataset consisted on x floral, x reproductive and x vegetative traits (Table S2).
+For this, we calculated the distance of the different functional traits with the function gowdis from the package FD version 1.0-12 (Laliberté et al., 2014) with the method ward.D2 used for non-squared distances (Murtagh & Legendre, 2014).
+All the numerical traits were previously scaled.
+Finally, we applied a hierarchical cluster analysis with the function hclust from the R stats package version 4.0.5 and calculated the optimal number of clusters with the function kgs from the package maptree version 1.4-7 (White & Gramacy, 2009).
+
+Second, pollinators were grouped into functional groups based on taxonomic rank.
+We opted to divide pollinators on the taxonomic rank level and not with functional traits because (i) they main taxonomic orders differ in form and behaviour and (ii) the lower complexity of higher taxonomic ranks (i.e., pollinators had 6 orders versus plants that had 38).
+Hence, we grouped pollinators into 6 functional groups: (i) Hymenoptera-Anthophila (bees), (ii) Hymenoptera-non-Anthophila (other non-bee Hymenoptera), (iii) Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera and (vi) Coleoptera.
+
+**Meso-scale analysis**
 
@@
 1) over and under represented motifs
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="Figure 1."}
 library(lme4)
@@
 d <- add_study_id(d)
-str(d)
-head(d)
-
-ggplot(d %>% filter(motif != 1), aes(percentil_sizeclass))+
-  geom_histogram(color="black", fill="white")+
-  facet_wrap(~motif)+
-  theme_bw()+
-  labs(x="Sizeclass percentile")
-
+#str(d)
+#head(d)
+
+#ggplot(d %>% filter(motif != 1), aes(percentil_sizeclass))+
+#  geom_histogram(color="black", fill="white")+
+#  facet_wrap(~motif)+
+#  theme_bw()+
+#  labs(x="Sizeclass percentile")
+#
 # Motifs tend to be over- and under-represensented in real networks

### 2021-05-28 Scripts/trial.R

@@ -1,0 +1,179 @@
+library(lme4)
+library(nlme)
+library(tidyverse)
+library(stringi)
+library(ggpubr)
+source("Scripts/Scripts_Alfonso/add_study_id.R")
+
+all_position_percentiles <- read_csv("Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
+
+all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
+                                                              "[0-9]+") %>% as.numeric()
+
+all_position_percentiles <- add_study_id(all_position_percentiles)
+str(all_position_percentiles)
+head(all_position_percentiles)
+
+list_plants_FG <- as.character(1:10)
+
+plant_position_percentiles_filtered <- all_position_percentiles %>% 
+  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
+         !is.na(expected_freq_its_GF)) #ME DA ERROR
+pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
+  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
+         !is.na(expected_freq_its_GF))
+
+ggplot(plant_position_percentiles_filtered, aes(percentil_its_GF))+
+  geom_histogram(color="black", fill="white")+
+  facet_wrap(~position)+
+  theme_bw()+
+  labs(x="Sizeclass percentile", title = "Histograms: Percentiles for plant positions")
+
+ggplot(pollinator_position_percentiles_filtered, aes(percentil_its_GF))+
+  geom_histogram(color="black", fill="white")+
+  facet_wrap(~position)+
+  theme_bw()+
+  labs(x="Sizeclass percentile",title = "Histograms: Percentiles for pollinator positions")
+
+
+
+# estimated mean taking into account the random str is 0.XX +- 0.XX (look at the (Intercept) estimate)
+
+
+# Plants-------------
+
+# Mean percentile and SE taking into account the study system
+plant_codes <- plant_position_percentiles_filtered$position %>% unique()
+plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
+plant_means$mean <- NA
+plant_means$SE <- NA
+
+
+for(i.pos in 1:length(plant_codes)){
+  
+  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
+            data = plant_position_percentiles_filtered %>%
[…]

### 2021-05-29 Draft/Draft.Rmd
a bit more of the intro

@@
 However, condensing to species level and the holistic view of the full network involves missing relevant information for the understanding of ecological processes [@delmas2019; @simmons2019].
-Intermediate levels that investigate plant-pollinator networks (meso-scale) have been little explored but can shed light of ecological processes not captured by the traditional approaches used in plant-pollinator network studies.
-
-Several studies have evaluated the structure of plant-pollinator interactions.
-These studies have found common structural properties across networks that can help the understanding of the determinats of biodiversity [@bastolla2009].
-One of the major findings is the nested structure of mutualistic networks [@bascompte2003] which describes the topological structure where the specialist interact with subgroups of the interacting species of the generalist.
-Further, the degree distribution (number of links per species) of plant-pollinator networks have been shown to generally follow a power-law truncated distribution [@jordano2003].
-Moreover, at the species level ...
+Intermediate levels that investigate plant-pollinator networks (meso-scale) have been little explored but can shed light on ecological processes not captured by the traditional approaches used in plant-pollinator network studies.
+
+Research on the network topology of plant-pollinator networks have proven common invariant structural properties across networks.
+Mutualistic networks tend to be nested [@bascompte2003] and the degree distribution (number of links per species) generally follows a truncated power law distribution [@jordano2003].
+Thus, these different properties can be linked to function and help our understanding of the determinants of biodiversity [@bastolla2009].
+At the species level, species phenology, abundances and morphological matching have progressed knowledge of our understanding of species interactions (REFs).
+However, these approaches does not account for indirect interactions (i.e., competitive or facilitative interactions for pollinators).
+
+both macro and micro scale approaches does not account for indirect interactions. The study
+
+little is known about of indirect interactions
+
+the ecological analysis of network structure or species interactions involves the use of indices that discard indirect interactions.
+For instance, considering indirect interactions can provide additional information of the competitive effects or facilittative that plants exert on others
+
+[@simmons2019].
+
+In addition, at the species level we have progressed our understanding of pairwise interactions. Phenological mismacthes
+
+the study of the microstructure of mutualistic networks have progressed the understanding of pairwise interactions (e.g., trait matching).
 

### 2021-05-29 Scripts/trial.R

@@ -161,11 +161,13 @@ ggarrange(GF_plant_pos,GF_poll_pos,
 
 
 
-str(pollinator_position_percentiles_filtered)
 
+#Install package
+#devtools::install_github("jbengler/tidyheatmap")
 
-library(tidyHeatmap)
+library(tidyheatmap)
 
+#Example of the capability of the package
 tidy_heatmap(data_exprs,
              rows = external_gene_name,
              columns = sample,
@@ -175,5 +177,28 @@ tidy_heatmap(data_exprs,
              annotation_row = c(is_immune_gene, direction),
              gaps_row = direction,
              gaps_col = group
+)
+
+
+
+tidy_heatmap(pollinator_means_reordered,
+             rows = position,
+             columns = Node_FG,
+             values = mean,
+             gaps_col = Node_FG,
+             cluster_cols = TRUE,
+             cluster_rows = TRUE,
+             display_numbers = TRUE
+)
+
+
+tidy_heatmap(plant_means,
+             rows = position,
+             columns = Node_FG,
+             values = mean,
+             gaps_col = Node_FG,
+             cluster_cols = TRUE,
+             cluster_rows = TRUE,
+             display_numbers = TRUE
 )
 

### 2021-05-30 Draft/Draft.Rmd
a bit more of intro

--- 2021-05-28 Draft/Draft.Rmd
@@
 However, condensing to species level and the holistic view of the full network involves missing relevant information for the understanding of ecological processes [@delmas2019; @simmons2019].
-Intermediate levels that investigate plant-pollinator networks (meso-scale) have been little explored but can shed light of ecological processes not captured by the traditional approaches used in plant-pollinator network studies.
-
-Several studies have evaluated the structure of plant-pollinator interactions.
-These studies have found common structural properties across networks that can help the understanding of the determinats of biodiversity [@bastolla2009].
-One of the major findings is the nested structure of mutualistic networks [@bascompte2003] which describes the topological structure where the specialist interact with subgroups of the interacting species of the generalist.
-Further, the degree distribution (number of links per species) of plant-pollinator networks have been shown to generally follow a power-law truncated distribution [@jordano2003].
-Moreover, at the species level ...
+Intermediate levels that investigate plant-pollinator networks (meso-scale) have been little explored but can shed light on ecological processes not captured by the traditional approaches used in plant-pollinator network studies.
+
+Research of plant-pollinator networks have proven common invariant structural properties across networks.
+Mutualistic networks tend to be nested [@bascompte2003], the degree distribution (number of links per species) generally follows a truncated power law distribution [@jordano2003] and there is an imbalance with approximately four times more pollinator species than plant species [@vazquez2009].
+In addition, phenological overlap, morphological matching and species abundances have been shown to be determinant for the understanding of plant-pollinator interactions and network structure [@stang2006; @peralta2020].
+Despite progress in plant-pollinator interactions, indirect interactions such as the competitive and facilitative interactions between plants for pollinators have been rarely investigated [@simmons2020].
+However, the recent advances in analytical tools [..To be continued..]
 

### 2021-05-30 Draft/Draft.Rmd
meso-scale analyses update

--- 2021-05-29 Draft/Draft.Rmd
@@
 
-We follow Simmons et al.
-to decompose networks on their constituent motifs.
-We compare observed motif frecuancies to vaznull model, which constrains the number of plants, pollinators and the network connectance.
-For each network we compared the observed motif frequency with the expected frecuancies and ...
-.
-To summarize general patterns across networks we used a GLMM per motif with the percentile per network, ...
-
-Next, we calculated which functional groups were over or under-represented in different motif positions by comparing with ... . Again, we tested ...
+Following Simmons et al.
+[@simmons2019,@simmons2020], we broke down the plant-pollinator networks into their constituent motifs.
+Prior to analyses, we selected only robust links, that is, interactions whose frequency was greater than one (64.94 % interactions); and, then, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.
+
+We calculated the frequency of all motifs up to five nodes (see motif topologies in Figure 3 in [@simmons2019]) for each empirical and simulated network, by using the ‘bmotif’ package [@bmotifsimmons2019].
+To control for variation in network size and for the fact that smaller motifs can be nested within larger motifs, motif frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains).
+Like [@simmons2020], we just used five-node motifs in our analyses for visualisation, interpretation and computational reasons.
+In addition, we excluded from our analyses two-node motifs (or links) because their normalised frequency would always equal one.
+
+To assess the significance of the observed frequencies, we created 1,000 simulated networks for each binary network using the ‘nullmodel’ function and the ‘vaznull’ model in the bipartite package [@dormann2009].
+Generated networks had the same number of plants and pollinators, and the same connectance of their corresponding empirical networks.
+After extracting the motif frequencies from the simulated networks, we calculated the percentage of simulated networks whose motif frequencies were smaller than the observed frequency for each motif type and empirical network, that is, we estimated the percentile of the observed motif frequencies.
+Motifs whose percentile is close to zero or 100 are under- or over-represented in the empirical networks, respectively, and, thus, they cannot be predicted by connectance and the number of species alone.
+To summarize general patterns across networks, we used an intercept-only linear mixed model (LMM) per motif, where the response variable was the observed motif percentile per network.
+In these models, we used the study identifiers in Table S1 as a random intercept.
+By doing so, we obtained estimates of the average motif frequency, in which we controlled the variation at the study level.
+
+Next, we calculated which functional groups were over or under-represented in different motif positions by comparing position frequencies of empirical networks with those of their corresponding simulated networks.
+For each network, we extracted the position frequencies of all motifs from three to five nodes for each species by using the ‘bmotif’ package [@bmotifsimmons2019].
+To estimate the position frequencies of each functional in a given network, we added the frequencies of those species that belong to the same group and we normalised the resulting frequencies by dividing the position measure for each group by the total number of times that a group appears in any position within the same motif size class.
+Then, we calculated the percentile of the observed position frequencies for each group and network, just like we did motif frequencies.
+To  outline the general patterns of position frequencies across networks and functional groups, we fit a LMM per motif position, where the response variable was the observed position percentile per network.
+We used the functional group identifier as an explanatory variable and the study identifiers as a random intercept.
+By adding the functional group estimates to the model intercept, we assessed the average motif frequency, after controlling the variation at the study level.
+To fit the LMMs models in our analyses, we used the ‘lmer’ package [@bates2015].
 

### 2021-05-30 Draft/Draft.Rmd

@@
 
-Research on the network topology of plant-pollinator networks have proven common invariant structural properties across networks.
-Mutualistic networks tend to be nested [@bascompte2003] and the degree distribution (number of links per species) generally follows a truncated power law distribution [@jordano2003].
-Thus, these different properties can be linked to function and help our understanding of the determinants of biodiversity [@bastolla2009].
-At the species level, species phenology, abundances and morphological matching have progressed knowledge of our understanding of species interactions (REFs).
-However, these approaches does not account for indirect interactions (i.e., competitive or facilitative interactions for pollinators).
-
-both macro and micro scale approaches does not account for indirect interactions. The study
-
-little is known about of indirect interactions
-
-the ecological analysis of network structure or species interactions involves the use of indices that discard indirect interactions.
-For instance, considering indirect interactions can provide additional information of the competitive effects or facilittative that plants exert on others
-
-[@simmons2019].
-
-In addition, at the species level we have progressed our understanding of pairwise interactions. Phenological mismacthes
-
-the study of the microstructure of mutualistic networks have progressed the understanding of pairwise interactions (e.g., trait matching).
+Research of plant-pollinator networks have proven common invariant structural properties across networks.
+Mutualistic networks tend to be nested [@bascompte2003], the degree distribution (number of links per species) generally follows a truncated power law distribution [@jordano2003] and there is an imbalance with approximately four times more pollinator species than plant species [@vazquez2009].
+In addition, phenological overlap, morphological matching and species abundances have been shown to be determinant for the understanding of plant-pollinator interactions and network structure [@stang2006; @peralta2020].
+Despite progress in plant-pollinator interactions, indirect interactions such as the competitive and facilitative interactions between plants for pollinators have been rarely investigated [@simmons2020].
+However, the recent advances in analytical tools [..To be continued..]
 

### 2021-05-30 Draft/Draft.Rmd
Update Draft.Rmd

@@
 
-We calculated the frequency of all motifs up to five nodes (see motif topologies in Figure 3 in [@simmons2019]) for each empirical and simulated network, by using the ‘bmotif’ package [@bmotifsimmons2019].
+We calculated the frequency of all motifs up to five nodes (see motif topologies in Figure 3 in [@simmons2019]) for each empirical network, by using the ‘bmotif’ package [@bmotifsimmons2019].
 To control for variation in network size and for the fact that smaller motifs can be nested within larger motifs, motif frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains).
 Like [@simmons2020], we just used five-node motifs in our analyses for visualisation, interpretation and computational reasons.
-In addition, we excluded from our analyses two-node motifs (or links) because their normalised frequency would always equal one.
+In addition, we also excluded two-node motifs (or links) from our analyses because their normalised frequencies would always equal one.
 
 To assess the significance of the observed frequencies, we created 1,000 simulated networks for each binary network using the ‘nullmodel’ function and the ‘vaznull’ model in the bipartite package [@dormann2009].
-Generated networks had the same number of plants and pollinators, and the same connectance of their corresponding empirical networks.
-After extracting the motif frequencies from the simulated networks, we calculated the percentage of simulated networks whose motif frequencies were smaller than the observed frequency for each motif type and empirical network, that is, we estimated the percentile of the observed motif frequencies.
+Generated networks had the same number of plants and pollinators, as well as the same connectance of their corresponding empirical networks.
+After extracting the motif frequencies from the simulated networks, for each motif type and empirical network, we calculated the percentage of simulated networks whose motif frequencies were smaller than the observed frequency, that is, we estimated the percentile of the observed motif frequencies.
 Motifs whose percentile is close to zero or 100 are under- or over-represented in the empirical networks, respectively, and, thus, they cannot be predicted by connectance and the number of species alone.

### 2021-05-30 Draft/Draft.Rmd
Update Draft.Rmd

@@
 Next, we calculated which functional groups were over or under-represented in different motif positions by comparing position frequencies of empirical networks with those of their corresponding simulated networks.
-For each network, we extracted the position frequencies of all motifs from three to five nodes for each species by using the ‘bmotif’ package [@bmotifsimmons2019].
-To estimate the position frequencies of each functional in a given network, we added the frequencies of those species that belong to the same group and we normalised the resulting frequencies by dividing the position measure for each group by the total number of times that a group appears in any position within the same motif size class.
+We extracted the position frequencies of all motifs from three to five nodes for each network and species by using the ‘bmotif’ package [@bmotifsimmons2019].
+To estimate the position frequencies of each functional group in a given network, we added the frequencies of those species that belong to the same group, and, then, we normalised the resulting frequencies by dividing the position measure for each group by the total number of times that a group appears in any position within the same motif size class.
 Then, we calculated the percentile of the observed position frequencies for each group and network, just like we did motif frequencies.

### 2021-05-30 Draft/Draft.Rmd
Update Draft.Rmd

@@
 We calculated the frequency of all motifs up to five nodes (see motif topologies in Figure 3 in [@simmons2019]) for each empirical network, by using the ‘bmotif’ package [@bmotifsimmons2019].
-To control for variation in network size and for the fact that smaller motifs can be nested within larger motifs, motif frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains).
+To control for variation in network size and for the fact that smaller motifs can be nested within larger motifs, the frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains).
 Like [@simmons2020], we just used five-node motifs in our analyses for visualisation, interpretation and computational reasons.

### 2021-05-30 Draft/Draft.Rmd
Update Draft.Rmd

@@
 Generated networks had the same number of plants and pollinators, as well as the same connectance of their corresponding empirical networks.
-After extracting the motif frequencies from the simulated networks, for each motif type and empirical network, we calculated the percentage of simulated networks whose motif frequencies were smaller than the observed frequency, that is, we estimated the percentile of the observed motif frequencies.
+After extracting the motif frequencies from the simulated networks, for each motif type and empirical network, we calculated the percentage of simulated networks whose frequencies were smaller than the ones observed, that is, we estimated the percentile of the observed motif frequencies.
 Motifs whose percentile is close to zero or 100 are under- or over-represented in the empirical networks, respectively, and, thus, they cannot be predicted by connectance and the number of species alone.
@@
 We extracted the position frequencies of all motifs from three to five nodes for each network and species by using the ‘bmotif’ package [@bmotifsimmons2019].
-To estimate the position frequencies of each functional group in a given network, we added the frequencies of those species that belong to the same group, and, then, we normalised the resulting frequencies by dividing the position measure for each group by the total number of times that a group appears in any position within the same motif size class.
+To estimate the position frequencies of each functional group in a given network, we added the frequencies of those species that belong to the group, and, then, we normalised the resulting frequencies by dividing the position measure for each group by the total number of times that a group appears in any position within the same motif size class.
 Then, we calculated the percentile of the observed position frequencies for each group and network, just like we did motif frequencies.

### 2021-05-31 Draft/Draft.Rmd
Update Draft.Rmd

@@
 
-Next, we calculated which functional groups were over or under-represented in different motif positions by comparing position frequencies of empirical networks with those of their corresponding simulated networks.
+Next, we calculated which functional groups were over or under-represented in different motif positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
 We extracted the position frequencies of all motifs from three to five nodes for each network and species by using the ‘bmotif’ package [@bmotifsimmons2019].

### 2021-05-31 Draft/Draft.Rmd
Hopefully improving the intro

@@
 The interaction between plants and pollinators can be studied at different scales, from species level interactions (micro-scale) to the full network structure (macro-scale).
-However, condensing to species level and the holistic view of the full network involves missing relevant information for the understanding of ecological processes [@delmas2019; @simmons2019].
-Intermediate levels that investigate plant-pollinator networks (meso-scale) have been little explored but can shed light on ecological processes not captured by the traditional approaches used in plant-pollinator network studies.
-
-Research of plant-pollinator networks have proven common invariant structural properties across networks.
-Mutualistic networks tend to be nested [@bascompte2003], the degree distribution (number of links per species) generally follows a truncated power law distribution [@jordano2003] and there is an imbalance with approximately four times more pollinator species than plant species [@vazquez2009].
+Research of the network structure have proven common invariant structural properties across them including nestedness [@jordano2003], the imbalance between plants and pollinators with approximately four times more pollinator species [@vazquez2009] and a degree distribution that decays as a power law [@jordano2003].
 In addition, phenological overlap, morphological matching and species abundances have been shown to be determinant for the understanding of plant-pollinator interactions and network structure [@stang2006; @peralta2020].
-Despite progress in plant-pollinator interactions, indirect interactions such as the competitive and facilitative interactions between plants for pollinators have been rarely investigated [@simmons2020].
-However, the recent advances in analytical tools [..To be continued..]
-
-Trait matching
+However, condensing to species level and the holistic view of the full network involves missing relevant information for the understanding of ecological processes [@simmons2019].
 

### 2021-05-31 Draft/Draft.Rmd
Intro

@@
 
-[Explain what macro-descriptors have found i.e. Bascompte, and what pairwise interactions descriptors have accomplished i.e. trait-matching. End explaining Benno simmons work]
-
-Exploring the different and most frequent motifs could help our understanding of species interactions due to motifs consider direct and indirect interactions not accounted in single species metrics.
-[Explain this: https://besjournals.onlinelibrary.wiley.com/doi/full/10.1111/1365-2435.13736 and say we don't know how motif distribution really looks like in the real world.
-Which is the expected pattern?]
-
-However, motifs are abstract representations often decoupled from species ecology.
+Indirect interactions are a widespread phenomenon in ecological communities [@strauss1991].
+For instance, plant species can facilitate or compete for pollinator's visitation.
+Despite their relevance in ecological communities, plant-pollinator research fails to capture indirect interactions with the traditional analytical tools that condense the information in single indices (e.g., netedness or interaction frequency).
+Nonetheless, the emerging framework of network motifs in plant-pollinator research allows to consider both direct and indirect interactions [@simmons2019].
+Motifs are cosidered the building blocks that depict subsets of interactions of the network.
+The work of @simmons2020 have shown that the different processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions However, we still ignore what are the general patterns of indirect interactions of plant-pollinator networks in natural systems.
+
+Motifs are abstract representations often decoupled from species ecology.
+
 [explain here the importance of relating reproductive strategies and pollinators behaviours to their positions within a motif.
@@
 all_position_percentiles <- add_study_id(all_position_percentiles)
-str(all_position_percentiles)
-head(all_position_percentiles)
+#str(all_position_percentiles)
+#head(all_position_percentiles)
 
@@
 
+**TABLES**
+
 ```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align = "left"}
@@
 ```
+
+**FIGURES**
 

### 2021-06-01 Scripts/Scripts_Alfonso/example_plot_motifs_and_positions.R
Example plot motif positions

@@ -1,0 +1,9 @@
+library(tidyverse)
+library(RColorBrewer)
+source("Scripts/Scripts_Alfonso/plot_motif_positions.R")
+
+motif_number <- 16
+plot_motif_positions(motif_number)
+
+motif_number <- 9
+plot_motif_positions(motif_number)

### 2021-06-01 Scripts/Scripts_Alfonso/plot_motif_positions.R

@@ -1,0 +1,82 @@
+
+plot_motif_positions <- function(motif_number){
+  
+  motifs_raw_data <- read_csv("Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
+  
+  motif_data <- motifs_raw_data %>% filter(motif_id == motif_number)
+  
+  
+  # Create dataframe with node positions
+  
+  labdown = motif_data$plant %>% unique()
+  
+  if(length(labdown)==2){
+    
+    xdown = c(0.75,2.25)
+    
+  }else if(length(labdown)==3){
+    
+    xdown = c(0,1.5,3)
+    
+  }else{
+    
+    xdown = c(1.5)
+  }
+  
+  ydown = rep(0,length(labdown))
+  
+  labup = motif_data$pollinator %>% unique()
+  
+  if(length(labup)==2){
+    
+    xup = c(0.75,2.25)
+    
+  }else if(length(labup)==3){
+    
+    xup = c(0,1.5,3)
+    
+  }else{
+    
+    xup = c(1.5)
+  }
+  
+  yup = rep(1,length(labup))
+  
+  d_nodes=data.frame(x=c(xdown,xup),
+                     y=c(ydown,yup),
+                     label = c(labdown,labup))
+  
+  
+  # Create a dataframe with links
+  
+  plant_positions <- data.frame(plant = labdown,
+                                xdown = xdown,
+                                ydown = ydown)
+  
+  pollinator_positions <- data.frame(pollinator = labup,
+                                     xup = xup,
+                                     yup = yup)
+  
+  link_df <- motif_data %>% left_join(plant_positions, by = "plant") %>% 
+    left_join(pollinator_positions, by = "pollinator")
+  
+  # Before plotting the motif, we remove letters from the node position id
+  
+  d_nodes$label <- gsub("[^0-9.-]", "", d_nodes$label)
+  
+  ggplot(data=d_nodes, aes(x, y)) +
+    scale_shape_identity() +
+    geom_segment(data = link_df, aes(x=xdown, y=ydown, xend = xup, yend = yup), size = 2, color = "grey")+
+    geom_point(aes(color = as.factor(label)),size=20)+
+    geom_text(aes(x, y , label = label),size=6)+
+    scale_color_brewer(palette = "Set2")+
+    xlim(-1,4)+ ylim(-0.5,1.5)+
+    theme(panel.background = element_blank(),
+          axis.text.x=element_blank(),
[…]

### 2021-06-01 Scripts/Scripts_Alfonso/example_plot_motifs_and_positions.R
Preparing panel

@@ -2,8 +2,60 @@ library(tidyverse)
 library(RColorBrewer)
 source("Scripts/Scripts_Alfonso/plot_motif_positions.R")
 
-motif_number <- 16
-plot_motif_positions(motif_number)
+
+motif_number <- 1
+p1 <- plot_motif_positions(motif_number)
+
+motif_number <- 2
+p2 <- plot_motif_positions(motif_number)
+
+motif_number <- 3
+p3 <- plot_motif_positions(motif_number)
+
+motif_number <- 4
+p4 <- plot_motif_positions(motif_number)
+
+motif_number <- 5
+p5 <- plot_motif_positions(motif_number)
+
+motif_number <- 6
+p6 <- plot_motif_positions(motif_number)
+
+motif_number <- 7
+p7 <- plot_motif_positions(motif_number)
+
+motif_number <- 8   
+p8 <- plot_motif_positions(motif_number)
 
 motif_number <- 9
-plot_motif_positions(motif_number)
+p9 <- plot_motif_positions(motif_number)
+
+motif_number <- 10
+p10 <- plot_motif_positions(motif_number)
+
+motif_number <- 11
+p11 <- plot_motif_positions(motif_number)
+
+motif_number <- 12
+p12 <- plot_motif_positions(motif_number)
+
+motif_number <- 13
+p13 <- plot_motif_positions(motif_number)
+
+motif_number <- 14
+p14 <- plot_motif_positions(motif_number)
+
+motif_number <- 15
+p15 <- plot_motif_positions(motif_number)
+
+motif_number <- 16
+p16 <- plot_motif_positions(motif_number)
+
+motif_number <- 17
+p17 <- plot_motif_positions(motif_number)
+
+library(patchwork)
+
+
+(p1 + p2 + p3)/ (p4 | p5 | p6 | p7)/ (p8 | p9 | p10 | p11 | p12) / (p13 | p14 | p15 | p16 | p17)+
+ plot_annotation(tag_levels = '1')

### 2021-06-01 Scripts/Scripts_Alfonso/plot_motif_positions.R

@@ -18,6 +18,10 @@ plot_motif_positions <- function(motif_number){
     
     xdown = c(0,1.5,3)
     
+  }else if(length(labdown)==4){
+    
+    xdown = c(0,1.5,3,4.5)
+    
   }else{
     
     xdown = c(1.5)
@@ -34,6 +38,10 @@ plot_motif_positions <- function(motif_number){
   }else if(length(labup)==3){
     
     xup = c(0,1.5,3)
+    
+  }else if(length(labup)==4){
+    
+    xup = c(0,1.5,3,4.5)
     
   }else{
     

### 2021-06-01 Scripts/trial.R

@@ -1,204 +1,0 @@
-library(lme4)
-library(nlme)
-library(tidyverse)
-library(stringi)
-library(ggpubr)
-source("Scripts/Scripts_Alfonso/add_study_id.R")
-
-all_position_percentiles <- read_csv("Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
-
-all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
-                                                              "[0-9]+") %>% as.numeric()
-
-all_position_percentiles <- add_study_id(all_position_percentiles)
-str(all_position_percentiles)
-head(all_position_percentiles)
-
-list_plants_FG <- as.character(1:10)
-
-plant_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF)) #ME DA ERROR
-pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF))
-
-ggplot(plant_position_percentiles_filtered, aes(percentil_its_GF))+
-  geom_histogram(color="black", fill="white")+
-  facet_wrap(~position)+
-  theme_bw()+
-  labs(x="Sizeclass percentile", title = "Histograms: Percentiles for plant positions")
-
-ggplot(pollinator_position_percentiles_filtered, aes(percentil_its_GF))+
-  geom_histogram(color="black", fill="white")+
-  facet_wrap(~position)+
-  theme_bw()+
-  labs(x="Sizeclass percentile",title = "Histograms: Percentiles for pollinator positions")
-
-
-
-# estimated mean taking into account the random str is 0.XX +- 0.XX (look at the (Intercept) estimate)
-
-
-# Plants-------------
-
-# Mean percentile and SE taking into account the study system
-plant_codes <- plant_position_percentiles_filtered$position %>% unique()
-plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-plant_means$mean <- NA
-plant_means$SE <- NA
-
-
-for(i.pos in 1:length(plant_codes)){
-  
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
-            data = plant_position_percentiles_filtered %>%
[…]

### 2021-06-01 Scripts/Scripts_Alfonso/example_plot_motifs_and_positions.R
panel with motifs

@@ -54,8 +54,9 @@ p16 <- plot_motif_positions(motif_number)
 motif_number <- 17
 p17 <- plot_motif_positions(motif_number)
 
+
 library(patchwork)
 
+(p1 & ylab("2 species")| p2 & ylab("3 species") | p3 )/ (p4 & ylab("4 species")| p5 | p6 | p7)/ (p8  & ylab("5 species")| p9 | p10 | p11 | p12) / (p13 & ylab("5 species")| p14 | p15 | p16 | p17)+
+ plot_annotation(tag_levels = '1') & theme(axis.title.y = element_text(color="black", size=14, face="bold"))
 
-(p1 + p2 + p3)/ (p4 | p5 | p6 | p7)/ (p8 | p9 | p10 | p11 | p12) / (p13 | p14 | p15 | p16 | p17)+
- plot_annotation(tag_levels = '1')

### 2021-06-01 Scripts/Scripts_Alfonso/plot_motif_positions.R
same positions

@@ -20,7 +20,7 @@ plot_motif_positions <- function(motif_number){
     
   }else if(length(labdown)==4){
     
-    xdown = c(0,1.5,3,4.5)
+    xdown = c(-0.75,0.75,2.25,3.75)
     
   }else{
     
@@ -41,7 +41,7 @@ plot_motif_positions <- function(motif_number){
     
   }else if(length(labup)==4){
     
-    xup = c(0,1.5,3,4.5)
+    xup = c(-0.75,0.75,2.25,3.75)
     
   }else{
     
@@ -78,7 +78,7 @@ plot_motif_positions <- function(motif_number){
     geom_point(aes(color = as.factor(label)),size=20)+
     geom_text(aes(x, y , label = label),size=6)+
     scale_color_brewer(palette = "Set2")+
-    xlim(-1,4)+ ylim(-0.5,1.5)+
+    xlim(-1.5,4)+ ylim(-0.5,1.5)+
     theme(panel.background = element_blank(),
           axis.text.x=element_blank(),
           axis.ticks.x=element_blank(),

### 2021-06-01 Scripts/Scripts_Alfonso/example_plot_motifs_and_positionsV2.R
Update figure motifs positions

@@ -1,0 +1,64 @@
+library(tidyverse)
+library(RColorBrewer)
+source("Scripts/Scripts_Alfonso/plot_motif_positionsV2.R")
+
+
+motif_number <- 1
+p1 <- plot_motif_positions(motif_number)
+
+motif_number <- 2
+p2 <- plot_motif_positions(motif_number)
+
+motif_number <- 3
+p3 <- plot_motif_positions(motif_number)
+
+motif_number <- 4
+p4 <- plot_motif_positions(motif_number)
+
+motif_number <- 5
+p5 <- plot_motif_positions(motif_number)
+
+motif_number <- 6
+p6 <- plot_motif_positions(motif_number)
+
+motif_number <- 7
+p7 <- plot_motif_positions(motif_number)
+
+motif_number <- 8   
+p8 <- plot_motif_positions(motif_number)
+
+motif_number <- 9
+p9 <- plot_motif_positions(motif_number)
+
+motif_number <- 10
+p10 <- plot_motif_positions(motif_number)
+
+motif_number <- 11
+p11 <- plot_motif_positions(motif_number)
+
+motif_number <- 12
+p12 <- plot_motif_positions(motif_number)
+
+motif_number <- 13
+p13 <- plot_motif_positions(motif_number)
+
+motif_number <- 14
+p14 <- plot_motif_positions(motif_number)
+
+motif_number <- 15
+p15 <- plot_motif_positions(motif_number)
+
+motif_number <- 16
+p16 <- plot_motif_positions(motif_number)
+
+motif_number <- 17
+p17 <- plot_motif_positions(motif_number)
+
+
+library(patchwork)
+
+(p1 & ylab("2 species")| p2 & ylab("3 species") | p3 )/ (p4 & ylab("4 species")| p5 | p6 | p7)/ (p8  & ylab("5 species")| p9 | p10 | p11 | p12) / (p13 & ylab("5 species")| p14 | p15 | p16 | p17) &
+ # plot_annotation(tag_levels = '1') & theme(axis.title.y = element_text(color="black", size=14, face="bold"))+
+ #  theme(plot.tag.position = "top")
+  theme(axis.title.y = element_text(color="black", size=14, face="bold"))
+

### 2021-06-01 Scripts/Scripts_Alfonso/plot_motif_positionsV2.R

@@ -1,0 +1,82 @@
+
+equidistribution <- function(number_nodes){
+  
+  x_width <- 5.5/(number_nodes+1)
+  
+  x_result <- rep(-1.5,number_nodes)
+  
+  for(i in 1:number_nodes){
+    
+    x_result[i] <- x_result[i] + i*x_width
+    
+  }
+  
+  return(x_result)
+  
+}
+
+
+
+plot_motif_positions <- function(motif_number){
+  
+  motifs_raw_data <- read_csv("Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
+  
+  motif_data <- motifs_raw_data %>% filter(motif_id == motif_number)
+  
+  
+  # Create dataframe with node positions
+  
+  labdown = motif_data$plant %>% unique()
+  
+  
+  xdown = equidistribution(length(labdown))
+  
+  ydown = rep(0,length(labdown))
+  
+  labup = motif_data$pollinator %>% unique()
+  
+  xup = equidistribution(length(labup))
+  
+  yup = rep(1,length(labup))
+  
+  d_nodes=data.frame(x=c(xdown,xup),
+                     y=c(ydown,yup),
+                     label = c(labdown,labup))
+  
+  
+  # Create a dataframe with links
+  
+  plant_positions <- data.frame(plant = labdown,
+                                xdown = xdown,
+                                ydown = ydown)
+  
+  pollinator_positions <- data.frame(pollinator = labup,
+                                     xup = xup,
+                                     yup = yup)
+  
+  link_df <- motif_data %>% left_join(plant_positions, by = "plant") %>% 
+    left_join(pollinator_positions, by = "pollinator")
+  
+  # Before plotting the motif, we remove letters from the node position id
+  
+  d_nodes$label <- gsub("[^0-9.-]", "", d_nodes$label)
+  
+  ggplot(data=d_nodes, aes(x, y)) +
+    scale_shape_identity() +
+    geom_segment(data = link_df, aes(x=xdown, y=ydown, xend = xup, yend = yup), size = 2, color = "grey")+
+    geom_point(aes(color = as.factor(label)),size=12)+
+    geom_text(aes(x, y , label = label),size=4)+
+    scale_color_brewer(palette = "Set2")+
+    xlim(-1.5,4)+ ylim(-0.5,1.5)+
+    theme(panel.background = element_blank(),
+          axis.text.x=element_blank(),
[…]

### 2021-06-01 Draft/Draft.Rmd
Probando sin color

@@
 
-Here, we used ...
-blah...
-and fined plant functional groups by using a comprehensive dataset with several reproductive traits and pollinator functional groups as the main differentiated guilds in life form and behaviour.
+Here, we used 60 plant-pollinator networks from 18 different studies and grouped the different plant species into functional groups that represented different reproductive strategies by using a comprehensive dataset with several floral, reproductive and vegetative traits.
+In addition, we classified pollinator species based on life form and bevavior into different functional groups.
+Then, we used explored the general patterns of motifs in these plant-pollinator networks
+
+plant functional groups by using a comprehensive dataset with several reproductive traits and pollinator functional groups as the main differentiated guilds in life form and behaviour.
 Then, we explored the main motifs of these networks and we found [...]
@@
 
-We calculated the frequency of all motifs up to five nodes (see motif topologies in Figure 3 in [@simmons2019]) for each empirical network, by using the ‘bmotif’ package [@bmotifsimmons2019].
+We calculated the frequency of all motifs up to five nodes (see Figure 1) for each empirical network, by using the ‘bmotif’ package [@bmotifsimmons2019].
 To control for variation in network size and for the fact that smaller motifs can be nested within larger motifs, the frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains).
@@
 In addition, we also excluded two-node motifs (or links) from our analyses because their normalised frequencies would always equal one.
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="Figure 1.
+Adapted figure of Simmons et al., 2019 with all the possible motifs from two to five species in bipartite plant-pollinator networks", fig.width=10,fig.height=8}
+library(tidyverse)
+library(RColorBrewer)
+source("../Scripts/Scripts_Alfonso/plot_motif_positionsV2.R")
+
+motif_number <- 1
+p1 <- plot_motif_positions(motif_number)
+
+motif_number <- 2
+p2 <- plot_motif_positions(motif_number)
+
+motif_number <- 3
+p3 <- plot_motif_positions(motif_number)
+
+motif_number <- 4
+p4 <- plot_motif_positions(motif_number)
+
+motif_number <- 5
+p5 <- plot_motif_positions(motif_number)
+
+motif_number <- 6
+p6 <- plot_motif_positions(motif_number)
+
+motif_number <- 7
+p7 <- plot_motif_positions(motif_number)
+
+motif_number <- 8   
+p8 <- plot_motif_positions(motif_number)
+
+motif_number <- 9
+p9 <- plot_motif_positions(motif_number)
+
+motif_number <- 10
+p10 <- plot_motif_positions(motif_number)
+
+motif_number <- 11
+p11 <- plot_motif_positions(motif_number)
+
+motif_number <- 12
+p12 <- plot_motif_positions(motif_number)
+
+motif_number <- 13
+p13 <- plot_motif_positions(motif_number)
+
+motif_number <- 14
+p14 <- plot_motif_positions(motif_number)
+
+motif_number <- 15
+p15 <- plot_motif_positions(motif_number)
+
+motif_number <- 16
+p16 <- plot_motif_positions(motif_number)
+
+motif_number <- 17
+p17 <- plot_motif_positions(motif_number)
+
+library(patchwork)
+
+(p1 & ylab("2 species")| p2 & ylab("3 species") | p3 )/ (p4 & ylab("4 species")| p5 | p6 | p7)/ (p8  & ylab("5 species")| p9 | p10 | p11 | p12) / (p13 & ylab("5 species")| p14 | p15 | p16 | p17)+
+ plot_annotation(tag_levels = '1') & theme(axis.title.y = element_text(color="black", size=14, face="bold"))
+
+```
 
@@
 
-ggplot(plant_position_percentiles_filtered, aes(percentil_its_GF))+
-  geom_histogram(color="black", fill="white")+
-  facet_wrap(~position)+
-  theme_bw()+
-  labs(x="Sizeclass percentile", title = "Histograms: Percentiles for plant positions")
-
-ggplot(pollinator_position_percentiles_filtered, aes(percentil_its_GF))+
-  geom_histogram(color="black", fill="white")+
-  facet_wrap(~position)+
-  theme_bw()+
-  labs(x="Sizeclass percentile",title = "Histograms: Percentiles for pollinator positions")
+#ggplot(plant_position_percentiles_filtered, aes(percentil_its_GF))+
+#  geom_histogram(color="black", fill="white")+
+#  facet_wrap(~position)+
+#  theme_bw()+
+#  labs(x="Sizeclass percentile", title = "Histograms: Percentiles for plant positions")
+#
+#ggplot(pollinator_position_percentiles_filtered, aes(percentil_its_GF))+
+#  geom_histogram(color="black", fill="white")+
+#  facet_wrap(~position)+
+#  theme_bw()+
+#  labs(x="Sizeclass percentile",title = "Histograms: Percentiles for pollinator positions")
+#
 

### 2021-06-01 Scripts/Scripts_Alfonso/plot_motif_positions.R

@@ -1,7 +1,7 @@
 
 plot_motif_positions <- function(motif_number){
   
-  motifs_raw_data <- read_csv("Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
+  motifs_raw_data <- read_csv("../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
   
   motif_data <- motifs_raw_data %>% filter(motif_id == motif_number)
   
@@ -74,11 +74,11 @@ plot_motif_positions <- function(motif_number){
   
   ggplot(data=d_nodes, aes(x, y)) +
     scale_shape_identity() +
-    geom_segment(data = link_df, aes(x=xdown, y=ydown, xend = xup, yend = yup), size = 2, color = "grey")+
-    geom_point(aes(color = as.factor(label)),size=20)+
-    geom_text(aes(x, y , label = label),size=6)+
-    scale_color_brewer(palette = "Set2")+
-    xlim(-1.5,4)+ ylim(-0.5,1.5)+
+    geom_segment(data = link_df, aes(x=xdown, y=ydown, xend = xup, yend = yup), size = 1, color = "grey25")+
+    geom_point(aes(color = as.factor(label)),size=10,color = "azure2")+
+    geom_text(aes(x, y , label = label),size=3)+
+  #  scale_colour_manual(values = c("cornflowerblue"))+
+    xlim(-1.5,4.5)+ ylim(-0.5,1.5)+
     theme(panel.background = element_blank(),
           axis.text.x=element_blank(),
           axis.ticks.x=element_blank(),

### 2021-06-01 Scripts/Scripts_Alfonso/plot_motif_positionsV2.R

@@ -19,7 +19,7 @@ equidistribution <- function(number_nodes){
 
 plot_motif_positions <- function(motif_number){
   
-  motifs_raw_data <- read_csv("Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
+  motifs_raw_data <- read_csv("../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
   
   motif_data <- motifs_raw_data %>% filter(motif_id == motif_number)
   
@@ -63,10 +63,10 @@ plot_motif_positions <- function(motif_number){
   
   ggplot(data=d_nodes, aes(x, y)) +
     scale_shape_identity() +
-    geom_segment(data = link_df, aes(x=xdown, y=ydown, xend = xup, yend = yup), size = 2, color = "grey")+
-    geom_point(aes(color = as.factor(label)),size=12)+
-    geom_text(aes(x, y , label = label),size=4)+
-    scale_color_brewer(palette = "Set2")+
+    geom_segment(data = link_df, aes(x=xdown, y=ydown, xend = xup, yend = yup), size = 1, color = "grey20")+
+    geom_point(aes(color = as.factor(label)),size=10, color = "azure2")+
+    geom_text(aes(x, y , label = label),size=3)+
+ #   scale_color_brewer(palette = "Set2")+
     xlim(-1.5,4)+ ylim(-0.5,1.5)+
     theme(panel.background = element_blank(),
           axis.text.x=element_blank(),

### 2021-06-01 Draft/Draft.Rmd
some edits

@@
 Motifs are cosidered the building blocks that depict subsets of interactions of the network.
-The work of @simmons2020 have shown that the different processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions However, we still ignore what are the general patterns of indirect interactions of plant-pollinator networks in natural systems.
-
-Motifs are abstract representations often decoupled from species ecology.
-
-[explain here the importance of relating reproductive strategies and pollinators behaviours to their positions within a motif.
-This is interesting because bridges pairwise interactions to the emergent network via motifs]
+The work of @simmons2020 have shown that the different processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions However, we still ignore what are the general patterns of indirect interactions in plant-pollinator networks.
+
+Although past studies have evaluated the ecological implications of motifs [@stouffer2012; @simmons2019], motifs are abstract representations often decoupled from species ecology.
+Species with different reproductive strategies may occupy different positions and be represented in different motifs.
+At the micro-scale, @tur2013 have linked the degree of pollinator dependence with specialization.
+However, meso-scale studies have not evaluated the implications and potential of considering the species reproductive strategy.
 
@@
 Then, we used explored the general patterns of motifs in these plant-pollinator networks
-
-plant functional groups by using a comprehensive dataset with several reproductive traits and pollinator functional groups as the main differentiated guilds in life form and behaviour.
-Then, we explored the main motifs of these networks and we found [...]
 

### 2021-06-02 Draft/Draft.Rmd
Remove plot_annotation from motif's figure

@@
 
-(p1 & ylab("2 species")| p2 & ylab("3 species") | p3 )/ (p4 & ylab("4 species")| p5 | p6 | p7)/ (p8  & ylab("5 species")| p9 | p10 | p11 | p12) / (p13 & ylab("5 species")| p14 | p15 | p16 | p17)+
- plot_annotation(tag_levels = '1') & theme(axis.title.y = element_text(color="black", size=14, face="bold"))
+(p1 & ylab("2 species")| p2 & ylab("3 species") | p3 )/ (p4 & ylab("4 species")| p5 | p6 | p7)/ (p8  & ylab("5 species")| p9 | p10 | p11 | p12) / (p13 & ylab("5 species")| p14 | p15 | p16 | p17) & theme(axis.title.y = element_text(color="black", size=14, face="bold")) #+
+ #plot_annotation(tag_levels = '1')
 

### 2021-06-02 Draft/Draft.Rmd
Intro... More or less everything there. Needs some deep reading

@@
 Nonetheless, the emerging framework of network motifs in plant-pollinator research allows to consider both direct and indirect interactions [@simmons2019].
-Motifs are cosidered the building blocks that depict subsets of interactions of the network.
-The work of @simmons2020 have shown that the different processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions However, we still ignore what are the general patterns of indirect interactions in plant-pollinator networks.
-
-Although past studies have evaluated the ecological implications of motifs [@stouffer2012; @simmons2019], motifs are abstract representations often decoupled from species ecology.
-Species with different reproductive strategies may occupy different positions and be represented in different motifs.
-At the micro-scale, @tur2013 have linked the degree of pollinator dependence with specialization.
-However, meso-scale studies have not evaluated the implications and potential of considering the species reproductive strategy.
-
-Here, we used 60 plant-pollinator networks from 18 different studies and grouped the different plant species into functional groups that represented different reproductive strategies by using a comprehensive dataset with several floral, reproductive and vegetative traits.
-In addition, we classified pollinator species based on life form and bevavior into different functional groups.
-Then, we used explored the general patterns of motifs in these plant-pollinator networks
+Motifs are commonly referred as the building blocks that depict subsets of interactions of the network [@milo2002].
+The work of @simmons2020 have shown that the different processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions.
+However, we still ignore what are the general patterns of indirect interactions in plant-pollinator networks.
+
+Linking the structural porperties of the meso-scale with the species ecology can help the understanding of ecological processes.
+For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species functional role [@stouffer2012; @baker2015].
+However, motifs are abstract representations often decoupled from species ecology.
+Remarkably, recent empirical findings indicate that the meso-scale is the best descriptor of plant reproductive success [@allen2021].
+Further, although some studies have evaluated plant reproductive strategies in plant-pollinator networks [tur2013; @lazaro2020], they are often overlooked [@devaux2014].
+Hence, exploring how the main species reproductive groups integrate with the emergent motif framework can shed light of key aspects of ecosystem functioning.
+
+Here, we used 60 plant-pollinator networks from 18 different studies and grouped the different plant and pollinator species into functional groups that summarized the main reproductive strategies.
+Plants were grouped based on a comprehensive dataset that included floral, reproductive and vegetative traits compiled in Lanuza et al., (unpublished) on a larger set of plant-pollinator networks.
+Pollinators were grouped into the main taxonomical groups that differed in life form and behaviour.
+Then, we explored the frequency of motifs up to five nodes in these set of plant-pollinator networks.
+Finally, we explore if the different plants and pollinators functional groups are over- or under-represented by comparing their frequencies with simulated networks.
 
@@
 This dataset consisted on x floral, x reproductive and x vegetative traits (Table S2).
-For this, we calculated the distance of the different functional traits with the function gowdis from the package FD version 1.0-12 (Laliberté et al., 2014) with the method ward.D2 used for non-squared distances (Murtagh & Legendre, 2014).
+For this, we calculated the distance of the different functional traits with the function gowdis from the package FD version 1.0-12 [@laliberte2014] with the method ward.D2 used for non-squared distances [@murtagh2014].
 All the numerical traits were previously scaled.
-Finally, we applied a hierarchical cluster analysis with the function hclust from the R stats package version 4.0.5 and calculated the optimal number of clusters with the function kgs from the package maptree version 1.4-7 (White & Gramacy, 2009).
+Finally, we applied a hierarchical cluster analysis with the function hclust from the R stats package version 4.0.5 and calculated the optimal number of clusters with the function kgs from the package maptree version 1.4-7 [@white2009].
 
@@
 Following Simmons et al.
-[@simmons2019,@simmons2020], we broke down the plant-pollinator networks into their constituent motifs.
+[@simmons2019; @simmons2020], we broke down the plant-pollinator networks into their constituent motifs.
 Prior to analyses, we selected only robust links, that is, interactions whose frequency was greater than one (64.94 % interactions); and, then, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="Figure 1.
-Adapted figure of Simmons et al., 2019 with all the possible motifs from two to five species in bipartite plant-pollinator networks", fig.width=10,fig.height=8}
+Adapted figure of Simmons et al., 2019 with all the possible motifs from two to five species in bipartite networks", fig.width=10,fig.height=8}
 library(tidyverse)
@@
 0) Description of guilds and FG.
+
+Figure S1
 

### 2021-06-02 Scripts/Figure_1_coloured_by_categories.R
just checking if it is more informative

@@ -1,0 +1,60 @@
+library(lme4)
+library(nlme)
+library(tidyverse)
+source("Scripts/Scripts_Alfonso/add_study_id.R")
+d <- read_csv("Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
+d <- add_study_id(d)
+#str(d)
+#head(d)
+
+#ggplot(d %>% filter(motif != 1), aes(percentil_sizeclass))+
+#  geom_histogram(color="black", fill="white")+
+#  facet_wrap(~motif)+
+#  theme_bw()+
+#  labs(x="Sizeclass percentile")
+#
+# Motifs tend to be over- and under-represensented in real networks
+
+# Mean percentile and SE taking into account the study system
+motif_codes <- d %>% filter(motif != 1) %>% # We remove links (motif code: 1)
+  select(motif) %>% unique() %>% pull()
+motif_means <- tibble(motif = motif_codes)
+motif_means$mean <- NA
+motif_means$SE <- NA
+
+for(i.motif in 1:length(motif_codes)){
+  
+  m <- lmer(percentil_sizeclass ~ 1+(1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
+            data = subset(d, motif == motif_codes[i.motif]))  
+  
+  motif_means$mean[i.motif] <- fixed.effects(m) %>% unname()
+  motif_means$SE[i.motif] <- sqrt(diag(vcov(m)))
+  
+}
+
+
+d$Broad_categories 
+
+d$Broad_categories[d$motif==2 | d$motif==7 | d$motif==17 | d$motif==3|d$motif==4|d$motif==8] <- "Fan" 
+
+d$Broad_categories[d$motif==15 | d$motif==11] <- "Medium-weak" 
+
+d$Broad_categories[d$motif==6 | d$motif==16 |  d$motif==12] <- "Strong" 
+
+d$Broad_categories[d$motif==5 | d$motif==9 |  d$motif==14|  d$motif==13|  d$motif==10] <- "Weak" 
+
+
+ggplot(NULL) + 
+  geom_point(data = d %>% filter(motif != 1),
+             aes(y=as.factor(motif), x=percentil_sizeclass, 
+                 color = as.factor(Broad_categories)),
+             position = "jitter",alpha=0.5)+
+  geom_errorbar(data = motif_means,aes(y = as.factor(motif), xmin=mean-SE, xmax=mean+SE), 
[…]

### 2021-06-02 Draft/Draft.Rmd
Adding motif categories of Simmons 2021 Fun.Ecol.

@@
 
+#Add categories based on path length set by Simmons 2021 et al., Functional Ecology
+d$Broad_categories[d$motif==2 | d$motif==7 | d$motif==17 | d$motif==3|d$motif==4|d$motif==8] <- "Fan"
+
+d$Broad_categories[d$motif==15 | d$motif==11] <- "Medium-weak"
+
+d$Broad_categories[d$motif==6 | d$motif==16 |  d$motif==12] <- "Strong"
+
+d$Broad_categories[d$motif==5 | d$motif==9 |  d$motif==14|  d$motif==13|  d$motif==10] <- "Weak"
+
 ggplot(NULL) + 
@@
              aes(y=as.factor(motif), x=percentil_sizeclass, 
-                 color = as.factor(motif)),
+                 color = as.factor(Broad_categories)),
              position = "jitter",alpha=0.5)+
@@
                 size=2)+
-  labs(y="Motif", x = "Percentile")+
-  theme_bw()+
-  theme(legend.position = "none")
+  labs(y="Motif", x = "Percentile",colour="Motif classification")+
+  theme_bw()
 

### 2021-06-02 Scripts/Figure_1_coloured_by_categories.R

@@ -1,60 +1,0 @@
-library(lme4)
-library(nlme)
-library(tidyverse)
-source("Scripts/Scripts_Alfonso/add_study_id.R")
-d <- read_csv("Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
-d <- add_study_id(d)
-#str(d)
-#head(d)
-
-#ggplot(d %>% filter(motif != 1), aes(percentil_sizeclass))+
-#  geom_histogram(color="black", fill="white")+
-#  facet_wrap(~motif)+
-#  theme_bw()+
-#  labs(x="Sizeclass percentile")
-#
-# Motifs tend to be over- and under-represensented in real networks
-
-# Mean percentile and SE taking into account the study system
-motif_codes <- d %>% filter(motif != 1) %>% # We remove links (motif code: 1)
-  select(motif) %>% unique() %>% pull()
-motif_means <- tibble(motif = motif_codes)
-motif_means$mean <- NA
-motif_means$SE <- NA
-
-for(i.motif in 1:length(motif_codes)){
-  
-  m <- lmer(percentil_sizeclass ~ 1+(1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = subset(d, motif == motif_codes[i.motif]))  
-  
-  motif_means$mean[i.motif] <- fixed.effects(m) %>% unname()
-  motif_means$SE[i.motif] <- sqrt(diag(vcov(m)))
-  
-}
-
-
-d$Broad_categories 
-
-d$Broad_categories[d$motif==2 | d$motif==7 | d$motif==17 | d$motif==3|d$motif==4|d$motif==8] <- "Fan" 
-
-d$Broad_categories[d$motif==15 | d$motif==11] <- "Medium-weak" 
-
-d$Broad_categories[d$motif==6 | d$motif==16 |  d$motif==12] <- "Strong" 
-
-d$Broad_categories[d$motif==5 | d$motif==9 |  d$motif==14|  d$motif==13|  d$motif==10] <- "Weak" 
-
-
-ggplot(NULL) + 
-  geom_point(data = d %>% filter(motif != 1),
-             aes(y=as.factor(motif), x=percentil_sizeclass, 
-                 color = as.factor(Broad_categories)),
-             position = "jitter",alpha=0.5)+
-  geom_errorbar(data = motif_means,aes(y = as.factor(motif), xmin=mean-SE, xmax=mean+SE), 
[…]

### 2021-06-03 Draft/Draft.Rmd
some edits

@@
 
-Indirect interactions are a widespread phenomenon in ecological communities [@strauss1991].
+Indirect interactions (i.e., motifs) commonly referred as the building blocks that depict subsets of interactions of the network [@milo2002] are a widespread phenomenon in ecological communities [@strauss1991].
 For instance, plant species can facilitate or compete for pollinator's visitation.
@@
 Nonetheless, the emerging framework of network motifs in plant-pollinator research allows to consider both direct and indirect interactions [@simmons2019].
-Motifs are commonly referred as the building blocks that depict subsets of interactions of the network [@milo2002].
-The work of @simmons2020 have shown that the different processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions.
+The study of @simmons2020 have shown that the different processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions.
 However, we still ignore what are the general patterns of indirect interactions in plant-pollinator networks.
@@
 Further, although some studies have evaluated plant reproductive strategies in plant-pollinator networks [tur2013; @lazaro2020], they are often overlooked [@devaux2014].
-Hence, exploring how the main species reproductive groups integrate with the emergent motif framework can shed light of key aspects of ecosystem functioning.
+Hence, exploring how the main reproductive groups integrate with the emergent motif framework can shed light of key aspects of ecosystem functioning.
 
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="Figure 1.
-Adapted figure of Simmons et al., 2019 with all the possible motifs from two to five species in bipartite networks", fig.width=10,fig.height=8}
+Adapted figure of Simmons et al., 2019 with all the possible motifs from two to five species in bipartite networks.
+There is a total of 17 possible motifs with 46 different positions denoted within each node.", fig.width=10,fig.height=8}
 library(tidyverse)
@@
 1) over and under represented motifs
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="Figure 1."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="Figure 2.
+Comparison of the motif frequencies between empirical and simulated networks.
+Average percentages of motifs close to 0 and 100 indicate under- and over- representation in empirical networks.
+The different motifs are coloured by the mean path length as done in @simmons2020.", fig.width=8,fig.height=5}
 library(lme4)
@@
                  color = as.factor(Broad_categories)),
-             position = "jitter",alpha=0.5)+
+             position = "jitter",alpha=0.55)+
   geom_errorbar(data = motif_means,aes(y = as.factor(motif), xmin=mean-SE, xmax=mean+SE), 
@@
                 size=2)+
-  labs(y="Motif", x = "Percentile",colour="Motif classification")+
-  theme_bw()
+  labs(y="Motif", x = "Percentile",colour="Path length classification")+
+  theme_bw() + scale_color_manual(labels = c('Fan' = expression(paste("Fan (", bar(x), " = 1.48)")), 'Medium-weak' = expression(paste("Asymmetric complete (", bar(x), " = 1.60)")),
+    'Strong' = expression(paste("Complete (", bar(x), " = 1.38)")), "Weak" =expression(paste("Core-peripheral (", bar(x), " = 1.85)"))), name = "Path length classification",values = c("deepskyblue3","maroon","darkgoldenrod2","grey25")) +
+theme(legend.text.align = 0)
 

### 2021-06-03 Draft/Draft.Rmd
playing with colors

@@
 
+#order the categories from short to long path length
+d$Broad_categories <- factor(d$Broad_categories, levels = c("Strong", "Fan", "Medium-weak", "Weak"))
+
 ggplot(NULL) + 
@@
                  color = as.factor(Broad_categories)),
-             position = "jitter",alpha=0.55)+
+             position = "jitter",alpha=0.5)+
   geom_errorbar(data = motif_means,aes(y = as.factor(motif), xmin=mean-SE, xmax=mean+SE), 
@@
   labs(y="Motif", x = "Percentile",colour="Path length classification")+
-  theme_bw() + scale_color_manual(labels = c('Fan' = expression(paste("Fan (", bar(x), " = 1.48)")), 'Medium-weak' = expression(paste("Asymmetric complete (", bar(x), " = 1.60)")),
-    'Strong' = expression(paste("Complete (", bar(x), " = 1.38)")), "Weak" =expression(paste("Core-peripheral (", bar(x), " = 1.85)"))), name = "Path length classification",values = c("deepskyblue3","maroon","darkgoldenrod2","grey25")) +
+  theme_bw() + scale_color_manual(labels = c('Strong' = expression(paste("Complete (", bar(x), " = 1.38)")),'Fan' = expression(paste("Fan (", bar(x), " = 1.48)")), 'Medium-weak' = expression(paste("Asymmetric complete (", bar(x), " = 1.60)")), "Weak" =expression(paste("Core-peripheral (", bar(x), " = 1.85)"))), name = "Path length classification",values = c("grey25","springgreen4","sienna2","goldenrod2")) +
 theme(legend.text.align = 0)
+
+#Trying to maintain a gradient from low to high in colors
 

### 2021-06-03 Draft/alternative_fig2_heatmaps.R
Create alternative_fig2_heatmaps.R

@@ -1,0 +1,320 @@
+
+library(lme4)
+library(nlme)
+library(tidyverse)
+library(stringi)
+source("../Scripts/Scripts_Alfonso/add_study_id.R")
+
+#############################################
+# EXTRACT MEAN VALUES
+#############################################
+
+
+all_position_percentiles <- read_csv("../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
+
+all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
+                                                              "[0-9]+") %>% as.numeric()
+
+all_position_percentiles <- add_study_id(all_position_percentiles)
+#str(all_position_percentiles)
+#head(all_position_percentiles)
+
+list_plants_FG <- as.character(1:10)
+
+plant_position_percentiles_filtered <- all_position_percentiles %>% 
+  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
+         !is.na(expected_freq_its_GF)) #ME DA ERROR
+pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
+  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
+         !is.na(expected_freq_its_GF))
+
+
+# Plants-------------
+
+# Mean percentile and SE taking into account the study system
+plant_codes <- plant_position_percentiles_filtered$position %>% unique()
+plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
+plant_means$mean <- NA
+plant_means$SE <- NA
+
+
+for(i.pos in 1:length(plant_codes)){
+  
+  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
+            data = plant_position_percentiles_filtered %>%
+              filter(position == plant_codes[i.pos]))  
+  
+  temp <- fixed.effects(m) %>% unname()
+  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
+                                                                    temp[1]+temp[2],
+                                                                    temp[1]+temp[3],
+                                                                    temp[1]+temp[4],
[…]

### 2021-06-04 Draft/Draft.Rmd
Some edits on the heatmap. I have to think how to best describe the functional groups

@@
 
-0) Description of guilds and FG.
+**Functional groups**
+
+The hierarchical cluster analysis divided the 1506 species in 5 different groups (Figure S1) with different and overlapping characteristics (Figure 1, Table S1).
+The first and largest cluster, Cluster A, was constituted by 710 species.
+The species of this cluster had the shortest plant heights (Median = 0.5m, Mean = 0.84m), were mostly herbs (89.58%) with short lived life span (68.23%) and the lowest number of flowers per plant (Median = 30, Mean = 197.15); the flowers were mostly hermaphrodite (97.40%) with actinomorphic symmetry (99.48%), the morphology was variant but the predominant shapes were ‘open’ (51.56%) and ‘capitulum’ (23.44%); most of the species were self compatible (96.35%) and had the higher levels of autonomous selfing of all clusters from low-medium selfing (47.92%) to high selfing (52.08%) with nectar production for 83.85% of the species.
+Cluster B, had 588 species and was the the second in plant height (Median = 0.8m, Mean = 1.98m), number of flowers per plant (Median = 75; Mean = 1559) and flowers per inflorescence (Median = 15; Mean = 58), it had diverse life forms (herbs 52.89%, shrubs 34.52% and trees 12.59%) and the species were mostly perennial (97.96%); the flowers were the second largest (flower length Median = 10mm, Mean = 10.08mm; flower width Median = 5.10mm, Mean = 16.88mm) and it had mostly hermaphroditic breeding system (95.41%), actinomorphic symmetry (99.15%) and a predominant flower morphology of ‘open’ (50.17%) and ‘tube’ shapes (20.07); the majority of species were self compatible (70.24%) and partially self compatible (20.24%) and had low selfing levels (88.95%) with nectar production for 78.40%.
+Cluster C was constituted by 323 species, had similar plant heights to cluster B (Median = 0.75, Mean = 1.85) with also diverse life forms (61.61% herbs, 28.79% shrubs, 9.60% trees) with mostly perennial species (95.36%) with the largest flower size (flower length Median =9.10mm , Mean =13.95mm; flower width Median =15mm, Mean =20.18mm) and number of ovules per flower of all clusters (Median = 30, Mean  = 527.87); flowers were mostly hermaphroditic (97.83%) with actinomorphic flowers (78.95%) and predominant ‘open’ (28.48%) ‘capitulum’ (27.55%) and ‘tube’ (26.01%) flower morphology; this was the cluster with greater proportion of self incompatible species (76.47%) and it had negligible autonomous selfing level (Median = 0,  Mean = 0.30) with the highest proportion of nectar secreting species (92.26%).
+Cluster D had 164 species, they were the tallest plants (Median =2.88m, Mean =5.19m) and had the largest proportion of shrubs (41.46%) and trees (31.71%) of all clusters, the species were mainly perennial (92.07%) and differentiated from the rest of the clusters by having principally dioecious (63.41%) and monoecious (35.98%) breeding system; this cluster had the largest number of flower per plant (Median = 1000, Mean = 6803) and per inflorescence (Median = 30 , Mean = 258) but the smaller flower size of all clusters (flower length Median =2.71, Mean =6.53; flower width Median = 3.62; Mean = 8.23) with ‘open’ (53.66%) and ‘brush’ (21.34%) morphology as the most representative flower shapes of this group; in addition, this cluster had the shortest styles (Median = 1mm; Mean = 3.05mm) and lower number of ovules (Median = 4.50, Mean = 110.47) along with cluster A; thus, the flowers were unisexual (98.78%), actinomorphic (95.12%), had no selfing (98.17%) and had the lowest proportion of nectar secreting species (69.51%) of all clusters.
+Finally, 239 species integrated Cluster E which had the second shortest species of all clusters (Median = 0.55m; Mean = 1.23m), the species were mainly herbs (83.26%) and perennial (70.29%) but also had a representative proportion of short lived species (29.71%); this cluster was the only one with mainly zygomorphic flowers (97.07%) with tubular (55.65%) and papilionaceous (24.69%) flower shapes, the species had mostly hermaphroditic breeding system (96.65%) and the flowers had the longest styles of all clusters (Median = 5mm; Mean = 8.74mm); species were mostly self compatible (88.28%) and nectar secreting (88.28%) with low autonomous selfing levels (61.92%) but also had species with high (18.41%) medium (15.06%) and lack of autonomous selfing (4.60%).
 
@@
 
-1) over and under represented motifs
+**Overall meso-scale patterns**
+
 ```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="Figure 2.
@@
 ```
+
+**Meso-scale functional groups position**
+
 2) FG-position associations.
@@
 #Fig 2 may be the same, but for the each positions-FG combination? Maybe heatmap (but we lose the SE's)
+
+```
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8}
+
+library(lme4)
+library(nlme)
+library(tidyverse)
+library(stringi)
+source("../Scripts/Scripts_Alfonso/add_study_id.R")
+
+#############################################
+# EXTRACT MEAN VALUES
+#############################################
+
+all_position_percentiles <- read_csv("../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
+
+all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
+                                                              "[0-9]+") %>% as.numeric()
+
+all_position_percentiles <- add_study_id(all_position_percentiles)
+#str(all_position_percentiles)
+#head(all_position_percentiles)
+
+list_plants_FG <- as.character(1:10)
+
+plant_position_percentiles_filtered <- all_position_percentiles %>% 
+  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
+         !is.na(expected_freq_its_GF)) #ME DA ERROR
+pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
+  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
+         !is.na(expected_freq_its_GF))
+
+# Plants-------------
+
+# Mean percentile and SE taking into account the study system
+plant_codes <- plant_position_percentiles_filtered$position %>% unique()
+plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
+plant_means$mean <- NA
+plant_means$SE <- NA
+
+for(i.pos in 1:length(plant_codes)){
+
+  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
+            data = plant_position_percentiles_filtered %>%
+              filter(position == plant_codes[i.pos]))
+
+  temp <- fixed.effects(m) %>% unname()
+  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
+                                                                    temp[1]+temp[2],
+                                                                    temp[1]+temp[3],
+                                                                    temp[1]+temp[4],
+                                                                    temp[1]+temp[5]) ## to get real means per FG
+  temp <- sqrt(diag(vcov(m)))
+  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
+                                                                  temp[1]+temp[2],
+                                                                  temp[1]+temp[3],
+                                                                  temp[1]+temp[4],
+                                                                  temp[1]+temp[5])
+
+}
+
+# Pollinators--------
+
+# Mean percentile and SE taking into account the study system
+pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
+pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
+pollinator_means$mean <- NA
+pollinator_means$SE <- NA
+pollinator_means_reordered <- NULL
+
+for(i.pos in 1:length(pollinator_codes)){
+
+  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
+            data = pollinator_position_percentiles_filtered %>%
+              filter(position == pollinator_codes[i.pos]),
+            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
+
+  temp <- fixed.effects(m) %>% unname()
+  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)
+
+  pollinator_means_aux$mean <- c(temp[1],
+                                 temp[1]+temp[2],
+                                 temp[1]+temp[3],
+                                 temp[1]+temp[4],
+                                 temp[1]+temp[5],
+                                 temp[1]+temp[6],
+                                 temp[1]+temp[7],
+                                 temp[1]+temp[8],
+                                 temp[1]+temp[9]) ## to get real means per FG
+
+  temp <- sqrt(diag(vcov(m)))
+  pollinator_means_aux$SE <- c(temp[1],
+                               temp[1]+temp[2],
+                               temp[1]+temp[3],
+                               temp[1]+temp[4],
+                               temp[1]+temp[5],
+                               temp[1]+temp[6],
+                               temp[1]+temp[7],
+                               temp[1]+temp[8],
+                               temp[1]+temp[9])
+
+  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)
+
+}
+
+# There are lower limits (mean - SE) smaller than 0 (see Other insects)
+# We set the lower limit of those error bars to zero
+
+pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
+pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
+
+#############################################
+# ADDING BROAD MOTIF CATEGORIES TO POSITIONS
+#############################################
+
+motifs_raw_data <- read_csv("../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
+
+motifs_raw_data$Broad_categories <- NA
+
+motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(5,9,14,13,10)] <- "Core-peripherical"
+motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(6,16,12)] <- "Complete"
+motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(2,3,7,4,17,8)] <- "Fan"
+motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(15,11)] <- "Asymmetric complete"
+
+motifs_raw_data$plant <- gsub("[^0-9.-]", "", motifs_raw_data$plant)
+motifs_raw_data$pollinator <- gsub("[^0-9.-]", "", motifs_raw_data$pollinator)
+motifs_raw_data$plant <- as.numeric(motifs_raw_data$plant)
+motifs_raw_data$pollinator <- as.numeric(motifs_raw_data$pollinator)
+motifs_raw_data <- motifs_raw_data %>% filter(!is.na(Broad_categories))
+
+fan_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
+core_per_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
+complete_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
+asymm_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
+
+pollinator_means_reordered$Broad_categories <- NA
+
+pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% fan_pollinator] <- "Fan" 
+pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% asymm_pollinator] <- "Medium-weak" 
+pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% complete_pollinator] <- "Strong" 
+pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% core_per_pollinator] <- "Weak"
+
+fan_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
+core_per_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
+complete_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
+asymm_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
+
+plant_means$Broad_categories <- NA
+
+plant_means$Broad_categories[plant_means$position %in% fan_plant] <- "Fan" 
+plant_means$Broad_categories[plant_means$position %in% asymm_plant] <- "Medium-weak" 
+plant_means$Broad_categories[plant_means$position %in% complete_plant] <- "Strong" 
+plant_means$Broad_categories[plant_means$position %in% core_per_plant] <- "Weak"
+
+########################################
+# CREATE HEATMAPS
+########################################
+
+library(ComplexHeatmap)
+
+# PLANTS-----
+
+# Prepare data for heatmap
+heat_plants_aux <- plant_means %>% spread(Node_FG,mean) %>% select(-SE)
+
+heat_plants <- heat_plants_aux %>%
+  group_by(position,Broad_categories) %>% 
+  summarise_all(sum,na.rm = T)
+
+heat_plants_fan <- heat_plants %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
+  as.matrix()
+
+rownames(heat_plants_fan) <- heat_plants_fan[,1]
+
+heat_plants_Weak <- heat_plants %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
+  as.matrix()
+
+rownames(heat_plants_Weak) <- heat_plants_Weak[,1]
+
+heat_plants_Strong <- heat_plants %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
+  as.matrix()
+
+rownames(heat_plants_Strong) <- heat_plants_Strong[,1]
+
+heat_plants_Medium_weak <- heat_plants %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
+  as.matrix()
+
+rownames(heat_plants_Medium_weak) <- heat_plants_Medium_weak[,1]
+
+# POLLINATORS-----------
+
+filter_rare_groups <- T
+
+if(filter_rare_groups == T){
+  heat_pollinators_aux <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds",
+                                                                                "Lizards",
+                                                                                "Other_insects")) %>% 
+    spread(Node_FG,mean) %>% select(-SE,-lower)
+
+  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bee",            
+                                      "Coleoptera","Lepidoptera","Non-bee\nHymenoptera", 
+                                      "Non-syrphids\ndiptera","Syrphids")
+}else{
+  heat_pollinators_aux <- pollinator_means_reordered %>% spread(Node_FG,mean) %>% select(-SE,-lower)
+
+  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bee","Birds",            
+                                      "Coleoptera","Lepidoptera","Lizards","Non-bee\nHymenoptera", 
+                                      "Non-syrphids\ndiptera","Other insects","Syrphids")
+}
+
+heat_pollinators <- heat_pollinators_aux %>%
+  group_by(position,Broad_categories) %>% 
+  summarise_all(sum,na.rm = T)
+
+heat_pollinators_fan <- heat_pollinators %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
+  as.matrix()
+
+rownames(heat_pollinators_fan) <- heat_pollinators_fan[,1]
+
+heat_pollinators_Weak <- heat_pollinators %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
+  as.matrix()
+
+rownames(heat_pollinators_Weak) <- heat_pollinators_Weak[,1]
+
+heat_pollinators_Strong <- heat_pollinators %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
+  as.matrix()
+
+rownames(heat_pollinators_Strong) <- heat_pollinators_Strong[,1]
+
+heat_pollinators_Medium_weak <- heat_pollinators %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
+  as.matrix()
+
+rownames(heat_pollinators_Medium_weak) <- heat_pollinators_Medium_weak[,1]
+
+##################
+
+#Do not know how to handle this multiplot for creating a panel
+
+# I'm going to create the 4 plots in one, 
+# I'm not sure that the grouping of the functional group is correct
+# when is done separately
+
+#sorry for the mess of libraries that I do below
+
+ #Prepare first pollinators
+
+library(tidyr)
+library(data.table)
+long <- melt(setDT(heat_pollinators), id.vars = c("position","Broad_categories"), variable.name = "guilds")
+
+long_1 <- long %>% select(-Broad_categories)
+
+library(reshape2)
+long_m <- acast(long_1, position~guilds, value.var="value")
+
+#set manually the divisions, so far this is the best way I have seen to split the rows by categories
+
+r_split <- c(rep(c("Fan"), 3),rep(c("Core-peripheral"), 2),"Complete",rep(c("Fan"),2),rep(c("Core-peripheral"), 4),
+             rep(c("Asymmetric complete"), 2), "Complete", rep(c("Core-peripheral"), 3),rep(c("Asymmetric complete"), 2),
+             "Complete", "Fan")
+
+#set order of labels that avoids overlapping
+r_split <- factor(r_split, levels=c("Core-peripheral","Complete","Fan","Asymmetric complete"))
+
+#plat a bit with colors, a bit of a more complex set but looks nicer
+library(circlize)
+col_fun = colorRamp2(c(0.05644663,0.25, 0.4673256,0.75, 0.8782047), c("blue","cadetblue3", "azure2", "gold","red"))
+
+h_pol <- Heatmap(long_m, name = "Mean\npercentile", row_split=r_split,cluster_row_slices = FALSE, 
+        column_title = "Pollinator functional\ Groups",row_names_gp = gpar(fontsize = 12),col = col_fun)
+
+ #Prepare plants
+
+#long format
+long_plants <- melt(setDT(heat_plants), id.vars = c("position","Broad_categories"), variable.name = "Functional_groups")
+
+#filter for creating matrix
+long_plants_1 <- long_plants %>% select(-Broad_categories)
+
+#set better colnames
+long_plants_1$Functional_groups <- as.character(long_plants_1$Functional_groups)
+
+long_plants_1$Functional_groups[long_plants_1$Functional_groups==1] <- "Cluster 1" 
+long_plants_1$Functional_groups[long_plants_1$Functional_groups==2] <- "Cluster 2" 
+long_plants_1$Functional_groups[long_plants_1$Functional_groups==3] <- "Cluster 3" 
+long_plants_1$Functional_groups[long_plants_1$Functional_groups==4] <- "Cluster 4" 
+long_plants_1$Functional_groups[long_plants_1$Functional_groups==5] <- "Cluster 5"
+
+long_plants_1$Functional_groups <- factor(long_plants_1$Functional_groups, levels=c("Cluster 1",
+"Cluster 2" ,"Cluster 3","Cluster 4" ,"Cluster 5" ))
+
+#create matrix with reshape
+long_plants_m <- acast(long_plants_1, position~Functional_groups, value.var="value")
+
+r_split_plants <- c(rep(c("Fan"), 3),rep(c("Core-peripheral"), 2),"Complete",rep(c("Fan"),2),rep(c("Core-peripheral"), 3),
+             rep(c("Asymmetric complete"), 2), "Complete", rep(c("Core-peripheral"), 4),rep(c("Asymmetric complete"), 2),
+             "Complete", "Fan")
+
+r_split_plants <- factor(r_split, levels=c("Core-peripheral","Complete","Fan","Asymmetric complete"))
+
+h_plan <- Heatmap(long_plants_m, name = "Mean\npercentile", row_split=r_split_plants,cluster_row_slices = FALSE, 
+        column_title = "Plant functional\ Groups",row_names_gp = gpar(fontsize = 12),col = col_fun)
+
+library(patchwork)
+h_pol+h_plan
 

### 2021-06-04 Draft/alternative_fig2_heatmaps.R

@@ -3,14 +3,14 @@ library(lme4)
 library(nlme)
 library(tidyverse)
 library(stringi)
-source("../Scripts/Scripts_Alfonso/add_study_id.R")
+source("Scripts/Scripts_Alfonso/add_study_id.R")
 
 #############################################
 # EXTRACT MEAN VALUES
 #############################################
 
 
-all_position_percentiles <- read_csv("../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
+all_position_percentiles <- read_csv("Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
 
 all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
                                                               "[0-9]+") %>% as.numeric()
@@ -115,7 +115,7 @@ pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
 # ADDING BROAD MOTIF CATEGORIES TO POSITIONS
 #############################################
 
-motifs_raw_data <- read_csv("../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
+motifs_raw_data <- read_csv("Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
 
 motifs_raw_data$Broad_categories <- NA
 
@@ -244,7 +244,7 @@ hp4 <- Heatmap(heat_plants_Medium_weak[,c(2:ncol(heat_plants_Medium_weak))],
         row_names_gp = gpar(fontsize = 12) # Text size for row names
 )
 
-hp1 %v% hp2 %v% hp3 %v% hp4
+ hp1 %v% hp2 %v% hp3 %v% hp4
 
 # POLLINATORS-----------     
 
@@ -317,4 +317,76 @@ h4 <- Heatmap(heat_pollinators_Medium_weak[,c(2:ncol(heat_pollinators_Medium_wea
               row_names_gp = gpar(fontsize = 12) # Text size for row names
 )
 
-h1 %v% h2 %v% h3 %v% h4
+ h1 %v% h2 %v% h3 %v% h4
+
+
+
+##################
+
+#Do not know how to handle this multiplot for creating a panel 
+ 
+# I'm going to create the 4 plots in one, 
+# I'm not sure that the grouping of the functional group is correct
+# when is done separately
+ 
+#sorry for the mess of libraries that I do below 
+
[…]

### 2021-06-04 Draft/Draft.Rmd
last added edits

@@
 Average percentages of motifs close to 0 and 100 indicate under- and over- representation in empirical networks.
-The different motifs are coloured by the mean path length as done in @simmons2020.", fig.width=8,fig.height=5}
+The different motifs are coloured by the mean path length as done in @simmons2020.", fig.width=9,fig.height=5}
 library(lme4)
@@
 
-2) FG-position associations.
 ```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
@@
 # Plant and Pollinators--------
-
-ggarrange(GF_plant_pos,GF_poll_pos,
-          ncol = 1, nrow = 2,heights = c(.90, 1.4))
-
+#
+#ggarrange(GF_plant_pos,GF_poll_pos,
+#          ncol = 1, nrow = 2,heights = c(.90, 1.4))
+#
 #Fig 2 may be the same, but for the each positions-FG combination? Maybe heatmap (but we lose the SE's)
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8}
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8, fig.cap="Figure 3.
+.
+Comparison of the motif frequencies between empirical and simulated networks collapsing the networks nodes by functional plant and pollinator functional groups.
+Mean percentiles close to 0 and 1 indicate under- and over- representation respectively."}
 
@@
 ```
+
+Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions.
+The different motif positions are dividied by the average path length clasification by @simmons2020
 

### 2021-06-04 Draft/alternative_fig2_heatmaps.R
edits on heatmaps

@@ -359,16 +359,29 @@ Heatmap(long_m, name = "mean\npercentile", row_split=r_split,cluster_row_slices 
 library(circlize)
 col_fun = colorRamp2(c(0.05644663,0.25, 0.4673256,0.75, 0.8782047), c("blue","cadetblue3", "azure2", "gold","red"))
 
-h_pol <- Heatmap(long_m, name = "mean\npercentile", row_split=r_split,cluster_row_slices = FALSE, 
+h_pol <- Heatmap(long_m, name = "Mean\npercentile", row_split=r_split,cluster_row_slices = FALSE, 
         column_title = "Pollinator functional\ Groups",row_names_gp = gpar(fontsize = 12),col = col_fun)
 
  #Prepare plants
 
-long_plants <- melt(setDT(heat_plants), id.vars = c("position","Broad_categories"), variable.name = "Functiona_groups")
+long_plants <- melt(setDT(heat_plants), id.vars = c("position","Broad_categories"), variable.name = "Functional_groups")
 
 long_plants_1 <- long_plants %>% select(-Broad_categories)  
 
-long_plants_m <- acast(long_plants_1, position~Functiona_groups, value.var="value")
+str(long_plants_1)
+
+long_plants_1$Functional_groups <- as.character(long_plants_1$Functional_groups)
+
+long_plants_1$Functional_groups[long_plants_1$Functional_groups==1] <- "Cluster 1" 
+long_plants_1$Functional_groups[long_plants_1$Functional_groups==2] <- "Cluster 2" 
+long_plants_1$Functional_groups[long_plants_1$Functional_groups==3] <- "Cluster 3" 
+long_plants_1$Functional_groups[long_plants_1$Functional_groups==4] <- "Cluster 4" 
+long_plants_1$Functional_groups[long_plants_1$Functional_groups==5] <- "Cluster 5" 
+
+long_plants_1$Functional_groups <- factor(long_plants_1$Functional_groups, levels=c("Cluster 1",
+"Cluster 2" ,"Cluster 3","Cluster 4" ,"Cluster 5" ))
+
+long_plants_m <- acast(long_plants_1, position~Functional_groups, value.var="value")
 
 r_split_plants <- c(rep(c("Fan"), 3),rep(c("Core-peripheral"), 2),"Complete",rep(c("Fan"),2),rep(c("Core-peripheral"), 3),
[…]

### 2021-06-06 Draft/Draft.Rmd
Update Draft.Rmd

@@
   geom_point(data = d %>% filter(motif != 1),
-             aes(y=as.factor(motif), x=percentil_sizeclass, 
+             aes(y=as.factor(motif), x=100*percentil_sizeclass, 
                  color = as.factor(Broad_categories)),
              position = "jitter",alpha=0.5)+
-  geom_errorbar(data = motif_means,aes(y = as.factor(motif), xmin=mean-SE, xmax=mean+SE), 
+  geom_errorbar(data = motif_means,aes(y = as.factor(motif), xmin=100*(mean-SE), xmax=100*(mean+SE)), 
                 width=1.0,size=1)+
-  geom_point(data = motif_means,aes(y = as.factor(motif), x=mean), 
+  geom_point(data = motif_means,aes(y = as.factor(motif), x=100*mean), 
                 size=2)+
-  labs(y="Motif", x = "Percentile",colour="Path length classification")+
-  theme_bw() + scale_color_manual(labels = c('Strong' = expression(paste("Complete (", bar(x), " = 1.38)")),'Fan' = expression(paste("Fan (", bar(x), " = 1.48)")), 'Medium-weak' = expression(paste("Asymmetric complete (", bar(x), " = 1.60)")), "Weak" =expression(paste("Core-peripheral (", bar(x), " = 1.85)"))), name = "Path length classification",values = c("grey25","springgreen4","sienna2","goldenrod2")) +
-theme(legend.text.align = 0)
+  labs(y="Motif", x = "Percentile (%)",colour="Path length classification")+
+  theme_bw() + scale_color_manual(labels = c('Strong' = expression(paste("Complete (", bar(x), " = 1.38)")),'Fan' = expression(paste("Fan (", bar(x), " = 1.48)")), 'Medium-weak' = expression(paste("Asymmetric complete (", bar(x), " = 1.60)")), "Weak" =expression(paste("Core-peripheral (", bar(x), " = 1.85)"))), name = "Path length classification",values = c("grey25","springgreen4","sienna2","goldenrod2"),guide = guide_legend(title.position = "top",nrow = 2)) +
+theme(legend.text.align = 0)+
+  theme(legend.position="bottom")
 

### 2021-06-07 Draft/Draft.Rmd
last edits

@@
 
-Indirect interactions (i.e., motifs) commonly referred as the building blocks that depict subsets of interactions of the network [@milo2002] are a widespread phenomenon in ecological communities [@strauss1991].
+Indirect interactions (i.e., motifs), commonly referred as the building blocks that depict subsets of interactions of the network [@milo2002], are a widespread phenomenon in ecological communities [@strauss1991].
 For instance, plant species can facilitate or compete for pollinator's visitation.
@@
 First, plant species were grouped into the optimal number of functional groups that summarized the main plant reproductive strategies.
-This was done with the help of hierarchical cluster analysis by using the trait dataset compiled in Lanuza et al., (unpublished).
-This dataset consisted on x floral, x reproductive and x vegetative traits (Table S2).
+This was done with the help of hierarchical cluster analysis by using the trait dataset collated in Lanuza et al., (unpublished) that comprised 1,506 plant species.
+This dataset consisted on 8 floral, 4 reproductive and 3 vegetative traits (Table S2).
 For this, we calculated the distance of the different functional traits with the function gowdis from the package FD version 1.0-12 [@laliberte2014] with the method ward.D2 used for non-squared distances [@murtagh2014].

### 2021-06-07 Draft/Draft.Rmd
update percentage of robust interactions

@@
 [@simmons2019; @simmons2020], we broke down the plant-pollinator networks into their constituent motifs.
-Prior to analyses, we selected only robust links, that is, interactions whose frequency was greater than one (64.94 % interactions); and, then, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.
+Prior to analyses, we selected only robust links, that is, interactions whose frequency was greater than one (64.98 % interactions); and, then, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.
 

### 2021-06-07 Draft/Draft.Rmd
EDITS

--- 2021-06-07 Draft/Draft.Rmd
@@
 bibliography: bibliography.bib
+header-includes:
+- \usepackage{booktabs}
+- \usepackage{longtable}
+- \usepackage{array}
+- \usepackage{multirow}
+- \usepackage{wrapfig}
+- \usepackage{float}
+- \usepackage{colortbl}
+- \usepackage{pdflscape}
+- \usepackage{tabu}
+- \usepackage{threeparttable}
+- \usepackage{threeparttablex}
+- \usepackage[normalem]{ulem}
+- \usepackage{makecell}
+- \usepackage{xcolor}
 ---
@@
 All studies sampled plant-pollinator interactions in natural systems and were selected based on wide geographical coverage and the presence of interaction frequency as a measure of interaction strength.
-In total, there were 503 plant species, 1111 pollinator species and 6248 of pairwise interactions registered.
+In total, there were 503 plant species, 1,111 pollinator species and 6248 of pairwise interactions registered.
 For ease of data manipulation plant and pollinator species names were standardize with the help of the package taxize version 0.9.99 [@chamberlain2020].
@@
 **Functional groups**
+
+Condense and summarize information
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align = 'center',fig.width=6,fig.height=3.5}
 library(lme4)
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8, fig.cap="Figure 3.
-.
-Comparison of the motif frequencies between empirical and simulated networks collapsing the networks nodes by functional plant and pollinator functional groups.
-Mean percentiles close to 0 and 1 indicate under- and over- representation respectively."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="Figure 3.
+Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions.
+The different motif positions are dividied by the average path length clasification by @simmons2020."}
 
@@
 
-Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions.
-The different motif positions are dividied by the average path length clasification by @simmons2020
-
 ##REFERENCES
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align = "left"}
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
 ##############################
@@
 List of studies ordered by author with the year of publication, number of contributed networks and digital object identifier") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = c("left"))
+  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = c("center"))
+
+```
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=12, fig.width=12}
+setwd("~/R_Projects/Reproductive Traits")
+
+library(kableExtra)
+
+library(dplyr)
+library(readxl) #read excel file (trait data)
+library(dplyr) #data manipulation
+library(visdat) #VISUALIZE MISSING DATA
+library(naniar)
+library(tidyverse)
+########################################################################################################################################################
+#1) READ TRAIT DATA
+########################################################################################################################################################
+
+Trait <- c("Plant height (m)", "Flower width (mm)", "Flower length (mm)", "Inflorescence width (mm)", "Style length (mm)", "Ovules per flower",
+           "Flowers per plant",  "Autonomous selfing (fruit set)")
+
+Trait1 <- c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Autonomous selfing", "Compatibility system", "Breeding system", "")
+
+T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub \n Tree", "Brush \n Campanulate \n Capitulum \n Open \n Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic", "None \n Low \n Medium \n High", "Self-incomp.
+\n Partially self-comp.
+\n Self-comp.", "Hermaphrodite \n Monoecious \n Dioecious",""),align = c("l"))
+
+Type <- c("Vegetative", "Floral", "Floral", "Floral", "Floral", "Floral", "Floral","Reproductive")
+
+Type_1 <- c("Vegetative", "Vegetative", "Floral", "Floral", "Reproductive", "Reproductive", "Reproductive", "")
+
+dat <- data.frame(Type, Trait,Type_1, Trait1)
+
+colnames(dat) <- c("Type","Traits","Type", "Traits")
+
+kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c"),caption = "Table S2.
+Traits used to delimit the different plant functional groups divided in quantitative and categorical traits.") %>%
+kable_styling(full_width = F) %>%
+add_header_above(c("Quantitative traits" = 2,"Categorical traits" = 2),bold=T)  %>%
+    column_spec(c(1,4), bold = T) %>% row_spec(0, bold=T)
 

### 2021-06-07 Draft/Supplementary_Material/Traits_Table.Rmd
EDITS

--- 2021-06-07 Draft/Draft.Rmd
@@
 ---
-title: Plant-pollintor networks worldwide are composed by the same specific building
-  blocks
+title: ""
 output:
+  pdf_document: default
   html_document: default
-  pdf_document: default
-editor_options:
-  chunk_output_type: console
-bibliography: bibliography.bib
 header-includes:
@@
 ---
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
-
-##Abstract
-
-Ecological processes leave distinct structural imprints on indirect interactions in mutualistic networks.
-Detecting those relationships is not trivial since they go beyond pair-wise interactions, but may get blurred when considering full network descriptors.
-However, recent work has shown the network meso-scale can capture this important information.
-The meso-scale describes network subgraphs representing patterns of interactions between a small number of species (i.e.
-motifs) and those constitute the building blocks of the whole network.
-Here we have compiled 60 networks from 18 different studies and show that some motifs are consitently over-represented worldwide, suggesting that the building blocks of plant-pollintor networks are not random and are associated to ...
-Second, we show that the position of pollinator guilds and plant reproductive strategies is not random with respect to the positions occupied within each motif.
-...
-Hence, we show that species ecology is shaping the building blocks that conform the web of life.
-
-##INTRODUCTION
-
-The interaction between plants and pollinators can be studied at different scales, from species level interactions (micro-scale) to the full network structure (macro-scale).
-Research of the network structure have proven common invariant structural properties across them including nestedness [@jordano2003], the imbalance between plants and pollinators with approximately four times more pollinator species [@vazquez2009] and a degree distribution that decays as a power law [@jordano2003].
-In addition, phenological overlap, morphological matching and species abundances have been shown to be determinant for the understanding of plant-pollinator interactions and network structure [@stang2006; @peralta2020].
-However, condensing to species level and the holistic view of the full network involves missing relevant information for the understanding of ecological processes [@simmons2019].
-
-Indirect interactions (i.e., motifs), commonly referred as the building blocks that depict subsets of interactions of the network [@milo2002], are a widespread phenomenon in ecological communities [@strauss1991].
-For instance, plant species can facilitate or compete for pollinator's visitation.
-Despite their relevance in ecological communities, plant-pollinator research fails to capture indirect interactions with the traditional analytical tools that condense the information in single indices (e.g., netedness or interaction frequency).
-Nonetheless, the emerging framework of network motifs in plant-pollinator research allows to consider both direct and indirect interactions [@simmons2019].
-The study of @simmons2020 have shown that the different processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions.
-However, we still ignore what are the general patterns of indirect interactions in plant-pollinator networks.
-
-Linking the structural porperties of the meso-scale with the species ecology can help the understanding of ecological processes.
-For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species functional role [@stouffer2012; @baker2015].
-However, motifs are abstract representations often decoupled from species ecology.
-Remarkably, recent empirical findings indicate that the meso-scale is the best descriptor of plant reproductive success [@allen2021].
-Further, although some studies have evaluated plant reproductive strategies in plant-pollinator networks [tur2013; @lazaro2020], they are often overlooked [@devaux2014].
-Hence, exploring how the main reproductive groups integrate with the emergent motif framework can shed light of key aspects of ecosystem functioning.
-
-Here, we used 60 plant-pollinator networks from 18 different studies and grouped the different plant and pollinator species into functional groups that summarized the main reproductive strategies.
-Plants were grouped based on a comprehensive dataset that included floral, reproductive and vegetative traits compiled in Lanuza et al., (unpublished) on a larger set of plant-pollinator networks.
-Pollinators were grouped into the main taxonomical groups that differed in life form and behaviour.
-Then, we explored the frequency of motifs up to five nodes in these set of plant-pollinator networks.
-Finally, we explore if the different plants and pollinators functional groups are over- or under-represented by comparing their frequencies with simulated networks.
-
-##METHODS
-
-**Plant-pollinator studies**
-
-We have compiled 60 plant-pollinator networks from 18 different studies (Table S1).
-All studies sampled plant-pollinator interactions in natural systems and were selected based on wide geographical coverage and the presence of interaction frequency as a measure of interaction strength.
-In total, there were 503 plant species, 1,111 pollinator species and 6248 of pairwise interactions registered.
-For ease of data manipulation plant and pollinator species names were standardize with the help of the package taxize version 0.9.99 [@chamberlain2020].
-
-**Plant and pollinator functional groups**
-
-First, plant species were grouped into the optimal number of functional groups that summarized the main plant reproductive strategies.
-This was done with the help of hierarchical cluster analysis by using the trait dataset collated in Lanuza et al., (unpublished) that comprised 1,506 plant species.
-This dataset consisted on 8 floral, 4 reproductive and 3 vegetative traits (Table S2).
-For this, we calculated the distance of the different functional traits with the function gowdis from the package FD version 1.0-12 [@laliberte2014] with the method ward.D2 used for non-squared distances [@murtagh2014].
-All the numerical traits were previously scaled.
-Finally, we applied a hierarchical cluster analysis with the function hclust from the R stats package version 4.0.5 and calculated the optimal number of clusters with the function kgs from the package maptree version 1.4-7 [@white2009].
-
-Second, pollinators were grouped into functional groups based on taxonomic rank.
-We opted to divide pollinators on the taxonomic rank level and not with functional traits because (i) they main taxonomic orders differ in form and behaviour and (ii) the lower complexity of higher taxonomic ranks (i.e., pollinators had 6 orders versus plants that had 38).
-Hence, we grouped pollinators into 6 functional groups: (i) Hymenoptera-Anthophila (bees), (ii) Hymenoptera-non-Anthophila (other non-bee Hymenoptera), (iii) Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera and (vi) Coleoptera.
-
-**Meso-scale analysis**
-
-Following Simmons et al.
-[@simmons2019; @simmons2020], we broke down the plant-pollinator networks into their constituent motifs.
-Prior to analyses, we selected only robust links, that is, interactions whose frequency was greater than one (64.94 % interactions); and, then, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.
-
-We calculated the frequency of all motifs up to five nodes (see Figure 1) for each empirical network, by using the ‘bmotif’ package [@bmotifsimmons2019].
-To control for variation in network size and for the fact that smaller motifs can be nested within larger motifs, the frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains).
-Like [@simmons2020], we just used five-node motifs in our analyses for visualisation, interpretation and computational reasons.
-In addition, we also excluded two-node motifs (or links) from our analyses because their normalised frequencies would always equal one.
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="Figure 1.
-Adapted figure of Simmons et al., 2019 with all the possible motifs from two to five species in bipartite networks.
-There is a total of 17 possible motifs with 46 different positions denoted within each node.", fig.width=10,fig.height=8}
-library(tidyverse)
-library(RColorBrewer)
-source("../Scripts/Scripts_Alfonso/plot_motif_positionsV2.R")
-
-motif_number <- 1
-p1 <- plot_motif_positions(motif_number)
-
-motif_number <- 2
-p2 <- plot_motif_positions(motif_number)
-
-motif_number <- 3
-p3 <- plot_motif_positions(motif_number)
-
-motif_number <- 4
-p4 <- plot_motif_positions(motif_number)
-
-motif_number <- 5
-p5 <- plot_motif_positions(motif_number)
-
-motif_number <- 6
-p6 <- plot_motif_positions(motif_number)
-
-motif_number <- 7
-p7 <- plot_motif_positions(motif_number)
-
-motif_number <- 8   
-p8 <- plot_motif_positions(motif_number)
-
-motif_number <- 9
-p9 <- plot_motif_positions(motif_number)
-
-motif_number <- 10
-p10 <- plot_motif_positions(motif_number)
-
-motif_number <- 11
-p11 <- plot_motif_positions(motif_number)
-
-motif_number <- 12
-p12 <- plot_motif_positions(motif_number)
-
-motif_number <- 13
-p13 <- plot_motif_positions(motif_number)
-
-motif_number <- 14
-p14 <- plot_motif_positions(motif_number)
-
-motif_number <- 15
-p15 <- plot_motif_positions(motif_number)
-
-motif_number <- 16
-p16 <- plot_motif_positions(motif_number)
-
-motif_number <- 17
-p17 <- plot_motif_positions(motif_number)
-
-library(patchwork)
-
-(p1 & ylab("2 species")| p2 & ylab("3 species") | p3 )/ (p4 & ylab("4 species")| p5 | p6 | p7)/ (p8  & ylab("5 species")| p9 | p10 | p11 | p12) / (p13 & ylab("5 species")| p14 | p15 | p16 | p17) & theme(axis.title.y = element_text(color="black", size=14, face="bold")) #+
- #plot_annotation(tag_levels = '1')
-
-```
-
-To assess the significance of the observed frequencies, we created 1,000 simulated networks for each binary network using the ‘nullmodel’ function and the ‘vaznull’ model in the bipartite package [@dormann2009].
-Generated networks had the same number of plants and pollinators, as well as the same connectance of their corresponding empirical networks.
-After extracting the motif frequencies from the simulated networks, for each motif type and empirical network, we calculated the percentage of simulated networks whose frequencies were smaller than the ones observed, that is, we estimated the percentile of the observed motif frequencies.
-Motifs whose percentile is close to zero or 100 are under- or over-represented in the empirical networks, respectively, and, thus, they cannot be predicted by connectance and the number of species alone.
-To summarize general patterns across networks, we used an intercept-only linear mixed model (LMM) per motif, where the response variable was the observed motif percentile per network.
-In these models, we used the study identifiers in Table S1 as a random intercept.
-By doing so, we obtained estimates of the average motif frequency, in which we controlled the variation at the study level.
-
-Next, we calculated which functional groups were over or under-represented in different motif positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
-We extracted the position frequencies of all motifs from three to five nodes for each network and species by using the ‘bmotif’ package [@bmotifsimmons2019].
-To estimate the position frequencies of each functional group in a given network, we added the frequencies of those species that belong to the group, and, then, we normalised the resulting frequencies by dividing the position measure for each group by the total number of times that a group appears in any position within the same motif size class.
-Then, we calculated the percentile of the observed position frequencies for each group and network, just like we did motif frequencies.
-To outline the general patterns of position frequencies across networks and functional groups, we fit a LMM per motif position, where the response variable was the observed position percentile per network.
-We used the functional group identifier as an explanatory variable and the study identifiers as a random intercept.
-By adding the functional group estimates to the model intercept, we assessed the average motif frequency, after controlling the variation at the study level.
-To fit the LMMs models in our analyses, we used the ‘lmer’ package [@bates2015].
-
-[potential additions: 
-Finally,for each motif, we recover the number of times a given combination of functional groups emerges ...
-Finally, we draw a network collapsing nodes per FG...]
-
-##RESULTS
-
-**Functional groups**
-
-Condense and summarize information
-
-The hierarchical cluster analysis divided the 1506 species in 5 different groups (Figure S1) with different and overlapping characteristics (Figure 1, Table S1).
-The first and largest cluster, Cluster A, was constituted by 710 species.
-The species of this cluster had the shortest plant heights (Median = 0.5m, Mean = 0.84m), were mostly herbs (89.58%) with short lived life span (68.23%) and the lowest number of flowers per plant (Median = 30, Mean = 197.15); the flowers were mostly hermaphrodite (97.40%) with actinomorphic symmetry (99.48%), the morphology was variant but the predominant shapes were ‘open’ (51.56%) and ‘capitulum’ (23.44%); most of the species were self compatible (96.35%) and had the higher levels of autonomous selfing of all clusters from low-medium selfing (47.92%) to high selfing (52.08%) with nectar production for 83.85% of the species.
-Cluster B, had 588 species and was the the second in plant height (Median = 0.8m, Mean = 1.98m), number of flowers per plant (Median = 75; Mean = 1559) and flowers per inflorescence (Median = 15; Mean = 58), it had diverse life forms (herbs 52.89%, shrubs 34.52% and trees 12.59%) and the species were mostly perennial (97.96%); the flowers were the second largest (flower length Median = 10mm, Mean = 10.08mm; flower width Median = 5.10mm, Mean = 16.88mm) and it had mostly hermaphroditic breeding system (95.41%), actinomorphic symmetry (99.15%) and a predominant flower morphology of ‘open’ (50.17%) and ‘tube’ shapes (20.07); the majority of species were self compatible (70.24%) and partially self compatible (20.24%) and had low selfing levels (88.95%) with nectar production for 78.40%.
-Cluster C was constituted by 323 species, had similar plant heights to cluster B (Median = 0.75, Mean = 1.85) with also diverse life forms (61.61% herbs, 28.79% shrubs, 9.60% trees) with mostly perennial species (95.36%) with the largest flower size (flower length Median =9.10mm , Mean =13.95mm; flower width Median =15mm, Mean =20.18mm) and number of ovules per flower of all clusters (Median = 30, Mean  = 527.87); flowers were mostly hermaphroditic (97.83%) with actinomorphic flowers (78.95%) and predominant ‘open’ (28.48%) ‘capitulum’ (27.55%) and ‘tube’ (26.01%) flower morphology; this was the cluster with greater proportion of self incompatible species (76.47%) and it had negligible autonomous selfing level (Median = 0,  Mean = 0.30) with the highest proportion of nectar secreting species (92.26%).
-Cluster D had 164 species, they were the tallest plants (Median =2.88m, Mean =5.19m) and had the largest proportion of shrubs (41.46%) and trees (31.71%) of all clusters, the species were mainly perennial (92.07%) and differentiated from the rest of the clusters by having principally dioecious (63.41%) and monoecious (35.98%) breeding system; this cluster had the largest number of flower per plant (Median = 1000, Mean = 6803) and per inflorescence (Median = 30 , Mean = 258) but the smaller flower size of all clusters (flower length Median =2.71, Mean =6.53; flower width Median = 3.62; Mean = 8.23) with ‘open’ (53.66%) and ‘brush’ (21.34%) morphology as the most representative flower shapes of this group; in addition, this cluster had the shortest styles (Median = 1mm; Mean = 3.05mm) and lower number of ovules (Median = 4.50, Mean = 110.47) along with cluster A; thus, the flowers were unisexual (98.78%), actinomorphic (95.12%), had no selfing (98.17%) and had the lowest proportion of nectar secreting species (69.51%) of all clusters.
-Finally, 239 species integrated Cluster E which had the second shortest species of all clusters (Median = 0.55m; Mean = 1.23m), the species were mainly herbs (83.26%) and perennial (70.29%) but also had a representative proportion of short lived species (29.71%); this cluster was the only one with mainly zygomorphic flowers (97.07%) with tubular (55.65%) and papilionaceous (24.69%) flower shapes, the species had mostly hermaphroditic breeding system (96.65%) and the flowers had the longest styles of all clusters (Median = 5mm; Mean = 8.74mm); species were mostly self compatible (88.28%) and nectar secreting (88.28%) with low autonomous selfing levels (61.92%) but also had species with high (18.41%) medium (15.06%) and lack of autonomous selfing (4.60%).
-
-Figure S1
-
-**Overall meso-scale patterns**
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="Figure 2.
-Comparison of the motif frequencies between empirical and simulated networks.
-Average percentages of motifs close to 0 and 100 indicate under- and over- representation in empirical networks.
-The different motifs are coloured by the mean path length as done in @simmons2020.", fig.width=9,fig.height=5}
-library(lme4)
-library(nlme)
-library(tidyverse)
-source("../Scripts/Scripts_Alfonso/add_study_id.R")
-d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
-d <- add_study_id(d)
-#str(d)
-#head(d)
-
-#ggplot(d %>% filter(motif != 1), aes(percentil_sizeclass))+
-#  geom_histogram(color="black", fill="white")+
-#  facet_wrap(~motif)+
-#  theme_bw()+
-#  labs(x="Sizeclass percentile")
-#
-# Motifs tend to be over- and under-represensented in real networks
-
-# Mean percentile and SE taking into account the study system
-motif_codes <- d %>% filter(motif != 1) %>% # We remove links (motif code: 1)
-  select(motif) %>% unique() %>% pull()
-motif_means <- tibble(motif = motif_codes)
-motif_means$mean <- NA
-motif_means$SE <- NA
-
-for(i.motif in 1:length(motif_codes)){
-
-  m <- lmer(percentil_sizeclass ~ 1+(1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = subset(d, motif == motif_codes[i.motif]))
-
-  motif_means$mean[i.motif] <- fixed.effects(m) %>% unname()
-  motif_means$SE[i.motif] <- sqrt(diag(vcov(m)))
-
-}
-
-#Add categories based on path length set by Simmons 2021 et al., Functional Ecology
-d$Broad_categories[d$motif==2 | d$motif==7 | d$motif==17 | d$motif==3|d$motif==4|d$motif==8] <- "Fan"
-
-d$Broad_categories[d$motif==15 | d$motif==11] <- "Medium-weak"
-
-d$Broad_categories[d$motif==6 | d$motif==16 |  d$motif==12] <- "Strong"
-
-d$Broad_categories[d$motif==5 | d$motif==9 |  d$motif==14|  d$motif==13|  d$motif==10] <- "Weak"
-
-#order the categories from short to long path length
-d$Broad_categories <- factor(d$Broad_categories, levels = c("Strong", "Fan", "Medium-weak", "Weak"))
-
-ggplot(NULL) + 
-  geom_point(data = d %>% filter(motif != 1),
-             aes(y=as.factor(motif), x=100*percentil_sizeclass, 
-                 color = as.factor(Broad_categories)),
-             position = "jitter",alpha=0.5)+
-  geom_errorbar(data = motif_means,aes(y = as.factor(motif), xmin=100*(mean-SE), xmax=100*(mean+SE)), 
-                width=1.0,size=1)+
-  geom_point(data = motif_means,aes(y = as.factor(motif), x=100*mean), 
-                size=2)+
-  labs(y="Motif", x = "Percentile (%)",colour="Path length classification")+
-  theme_bw() + scale_color_manual(labels = c('Strong' = expression(paste("Complete (", bar(x), " = 1.38)")),'Fan' = expression(paste("Fan (", bar(x), " = 1.48)")), 'Medium-weak' = expression(paste("Asymmetric complete (", bar(x), " = 1.60)")), "Weak" =expression(paste("Core-peripheral (", bar(x), " = 1.85)"))), name = "Path length classification",values = c("grey25","springgreen4","sienna2","goldenrod2"),guide = guide_legend(title.position = "top",nrow = 2)) +
-theme(legend.text.align = 0)+
-  theme(legend.position="bottom")
-
-#Trying to maintain a gradient from low to high in colors
-
-#Fig 1 Should be a dot plot (or forest plot) of the mean +- SE of the 15 motifs.
-#NICE! Can we put motifs in Y axes, and % in X?
-```
-
-**Meso-scale functional groups position**
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align = 'center',fig.width=6,fig.height=3.5}
-library(lme4)
-library(nlme)
-library(tidyverse)
-library(stringi)
-library(ggpubr)
-source("../Scripts/Scripts_Alfonso/add_study_id.R")
-
-all_position_percentiles <- read_csv("../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
-
-all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
-                                                              "[0-9]+") %>% as.numeric()
-
-all_position_percentiles <- add_study_id(all_position_percentiles)
-#str(all_position_percentiles)
-#head(all_position_percentiles)
-
-list_plants_FG <- as.character(1:10)
-
-plant_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF)) #ME DA ERROR
-pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF))
-
-#ggplot(plant_position_percentiles_filtered, aes(percentil_its_GF))+
-#  geom_histogram(color="black", fill="white")+
-#  facet_wrap(~position)+
-#  theme_bw()+
-#  labs(x="Sizeclass percentile", title = "Histograms: Percentiles for plant positions")
-#
-#ggplot(pollinator_position_percentiles_filtered, aes(percentil_its_GF))+
-#  geom_histogram(color="black", fill="white")+
-#  facet_wrap(~position)+
-#  theme_bw()+
-#  labs(x="Sizeclass percentile",title = "Histograms: Percentiles for pollinator positions")
-#
-
-# estimated mean taking into account the random str is 0.XX +- 0.XX (look at the (Intercept) estimate)
-
-# Plants-------------
-
-# Mean percentile and SE taking into account the study system
-plant_codes <- plant_position_percentiles_filtered$position %>% unique()
-plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-plant_means$mean <- NA
-plant_means$SE <- NA
-
-for(i.pos in 1:length(plant_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
-            data = plant_position_percentiles_filtered %>%
-                          filter(position == plant_codes[i.pos]))
-
-  temp <- fixed.effects(m) %>% unname()
-  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
-                                                                     temp[1]+temp[2],
-                                                                     temp[1]+temp[3],
-                                                                     temp[1]+temp[4],
-                                                                     temp[1]+temp[5]) ## to get real means per FG
-  temp <- sqrt(diag(vcov(m)))
-  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
-                                                                  temp[1]+temp[2],
-                                                                  temp[1]+temp[3],
-                                                                  temp[1]+temp[4],
-                                                                  temp[1]+temp[5])
-
-}
-
-GF_plant_pos <- ggplot(NULL) + 
-  geom_point(data = plant_position_percentiles_filtered,
-             aes(x=as.factor(position), y=percentil_its_GF, 
-                 color = as.factor(position)),
-             position = "jitter",alpha=0.5)+
-  geom_errorbar(data = plant_means,aes(x = as.factor(position), ymin=mean-SE, ymax=mean+SE), 
-                width=1.0,size=1)+
-  facet_wrap(~Node_FG,ncol = 5)+
-  geom_point(data = plant_means,aes(x = as.factor(position), y=mean), 
-             size=2)+
-  labs(x="Position", y = "Percentile",title = "Plants")+
-  theme_bw()+
-  theme(legend.position = "none")+#,axis.text.x=element_text(angle=90,vjust=0.5, hjust=1))+
-  coord_flip()
-
-# Pollinators--------
-
-# Mean percentile and SE taking into account the study system
-pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
-pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-pollinator_means$mean <- NA
-pollinator_means$SE <- NA
-pollinator_means_reordered <- NULL
-
-for(i.pos in 1:length(pollinator_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = pollinator_position_percentiles_filtered %>%
-                          filter(position == pollinator_codes[i.pos]),
-            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
-
-  temp <- fixed.effects(m) %>% unname()
-  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)
-
-  pollinator_means_aux$mean <- c(temp[1],
-                                 temp[1]+temp[2],
-                                 temp[1]+temp[3],
-                                 temp[1]+temp[4],
-                                 temp[1]+temp[5],
-                                 temp[1]+temp[6],
-                                 temp[1]+temp[7],
-                                 temp[1]+temp[8],
-                                 temp[1]+temp[9]) ## to get real means per FG
-
-  temp <- sqrt(diag(vcov(m)))
-  pollinator_means_aux$SE <- c(temp[1],
-                               temp[1]+temp[2],
-                               temp[1]+temp[3],
-                               temp[1]+temp[4],
-                               temp[1]+temp[5],
-                               temp[1]+temp[6],
-                               temp[1]+temp[7],
-                               temp[1]+temp[8],
-                               temp[1]+temp[9])
-
-  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)
-
-}
-
-# There are lower limits (mean - SE) smaller than 0 (see Other insects)
-# We set the lower limit of those error bars to zero
-
-pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
-pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
-
-GF_poll_pos <- ggplot(NULL) + 
-  geom_point(data = pollinator_position_percentiles_filtered,
-             aes(x=as.factor(position), y=percentil_its_GF, 
-                 color = as.factor(position)),
-             position = "jitter",alpha=0.5)+
-  geom_errorbar(data = pollinator_means_reordered, aes(x = as.factor(position), ymin=lower,
-                                                       ymax=mean+SE), 
-                width=1.0,size=1)+
-  facet_wrap(~Node_FG,ncol = 5)+
-  geom_point(data = pollinator_means_reordered,aes(x = as.factor(position), y=mean), 
-             size=2)+
-  labs(x="Position", y = "Percentile", title = "Pollinators")+
-  theme_bw()+
-  theme(legend.position = "none")+#,axis.text.x=element_text(angle=90,vjust=0.5, hjust=1))+
-  coord_flip()
-
-# Plant and Pollinators--------
-#
-#ggarrange(GF_plant_pos,GF_poll_pos,
-#          ncol = 1, nrow = 2,heights = c(.90, 1.4))
-#
-#Fig 2 may be the same, but for the each positions-FG combination? Maybe heatmap (but we lose the SE's)
-
-```
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="Figure 3.
-Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions.
-The different motif positions are dividied by the average path length clasification by @simmons2020."}
-
-library(lme4)
-library(nlme)
-library(tidyverse)
-library(stringi)
-source("../Scripts/Scripts_Alfonso/add_study_id.R")
-
-#############################################
-# EXTRACT MEAN VALUES
-#############################################
-
-all_position_percentiles <- read_csv("../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
-
-all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
-                                                              "[0-9]+") %>% as.numeric()
-
-all_position_percentiles <- add_study_id(all_position_percentiles)
-#str(all_position_percentiles)
-#head(all_position_percentiles)
-
-list_plants_FG <- as.character(1:10)
-
-plant_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF)) #ME DA ERROR
-pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF))
-
-# Plants-------------
-
-# Mean percentile and SE taking into account the study system
-plant_codes <- plant_position_percentiles_filtered$position %>% unique()
-plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-plant_means$mean <- NA
-plant_means$SE <- NA
-
-for(i.pos in 1:length(plant_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
-            data = plant_position_percentiles_filtered %>%
-              filter(position == plant_codes[i.pos]))
-
-  temp <- fixed.effects(m) %>% unname()
-  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
-                                                                    temp[1]+temp[2],
-                                                                    temp[1]+temp[3],
-                                                                    temp[1]+temp[4],
-                                                                    temp[1]+temp[5]) ## to get real means per FG
-  temp <- sqrt(diag(vcov(m)))
-  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
-                                                                  temp[1]+temp[2],
-                                                                  temp[1]+temp[3],
-                                                                  temp[1]+temp[4],
-                                                                  temp[1]+temp[5])
-
-}
-
-# Pollinators--------
-
-# Mean percentile and SE taking into account the study system
-pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
-pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-pollinator_means$mean <- NA
-pollinator_means$SE <- NA
-pollinator_means_reordered <- NULL
-
-for(i.pos in 1:length(pollinator_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = pollinator_position_percentiles_filtered %>%
-              filter(position == pollinator_codes[i.pos]),
-            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
-
-  temp <- fixed.effects(m) %>% unname()
-  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)
-
-  pollinator_means_aux$mean <- c(temp[1],
-                                 temp[1]+temp[2],
-                                 temp[1]+temp[3],
-                                 temp[1]+temp[4],
-                                 temp[1]+temp[5],
-                                 temp[1]+temp[6],
-                                 temp[1]+temp[7],
-                                 temp[1]+temp[8],
-                                 temp[1]+temp[9]) ## to get real means per FG
-
-  temp <- sqrt(diag(vcov(m)))
-  pollinator_means_aux$SE <- c(temp[1],
-                               temp[1]+temp[2],
-                               temp[1]+temp[3],
-                               temp[1]+temp[4],
-                               temp[1]+temp[5],
-                               temp[1]+temp[6],
-                               temp[1]+temp[7],
-                               temp[1]+temp[8],
-                               temp[1]+temp[9])
-
-  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)
-
-}
-
-# There are lower limits (mean - SE) smaller than 0 (see Other insects)
-# We set the lower limit of those error bars to zero
-
-pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
-pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
-
-#############################################
-# ADDING BROAD MOTIF CATEGORIES TO POSITIONS
-#############################################
-
-motifs_raw_data <- read_csv("../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-motifs_raw_data$Broad_categories <- NA
-
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(5,9,14,13,10)] <- "Core-peripherical"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(6,16,12)] <- "Complete"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(2,3,7,4,17,8)] <- "Fan"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(15,11)] <- "Asymmetric complete"
-
-motifs_raw_data$plant <- gsub("[^0-9.-]", "", motifs_raw_data$plant)
-motifs_raw_data$pollinator <- gsub("[^0-9.-]", "", motifs_raw_data$pollinator)
-motifs_raw_data$plant <- as.numeric(motifs_raw_data$plant)
-motifs_raw_data$pollinator <- as.numeric(motifs_raw_data$pollinator)
-motifs_raw_data <- motifs_raw_data %>% filter(!is.na(Broad_categories))
-
-fan_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-pollinator_means_reordered$Broad_categories <- NA
-
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% fan_pollinator] <- "Fan" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% asymm_pollinator] <- "Medium-weak" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% complete_pollinator] <- "Strong" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% core_per_pollinator] <- "Weak"
-
-fan_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-plant_means$Broad_categories <- NA
-
-plant_means$Broad_categories[plant_means$position %in% fan_plant] <- "Fan" 
-plant_means$Broad_categories[plant_means$position %in% asymm_plant] <- "Medium-weak" 
-plant_means$Broad_categories[plant_means$position %in% complete_plant] <- "Strong" 
-plant_means$Broad_categories[plant_means$position %in% core_per_plant] <- "Weak"
-
-########################################
-# CREATE HEATMAPS
-########################################
-
-library(ComplexHeatmap)
-
-# PLANTS-----
-
-# Prepare data for heatmap
-heat_plants_aux <- plant_means %>% spread(Node_FG,mean) %>% select(-SE)
-
-heat_plants <- heat_plants_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-heat_plants_fan <- heat_plants %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_fan) <- heat_plants_fan[,1]
-
-heat_plants_Weak <- heat_plants %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Weak) <- heat_plants_Weak[,1]
-
-heat_plants_Strong <- heat_plants %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Strong) <- heat_plants_Strong[,1]
-
-heat_plants_Medium_weak <- heat_plants %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Medium_weak) <- heat_plants_Medium_weak[,1]
-
-# POLLINATORS-----------
-
-filter_rare_groups <- T
-
-if(filter_rare_groups == T){
-  heat_pollinators_aux <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds",
-                                                                                "Lizards",
-                                                                                "Other_insects")) %>% 
-    spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bee",            
-                                      "Coleoptera","Lepidoptera","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\ndiptera","Syrphids")
-}else{
-  heat_pollinators_aux <- pollinator_means_reordered %>% spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bee","Birds",            
-                                      "Coleoptera","Lepidoptera","Lizards","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\ndiptera","Other insects","Syrphids")
-}
-
-heat_pollinators <- heat_pollinators_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-heat_pollinators_fan <- heat_pollinators %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_fan) <- heat_pollinators_fan[,1]
-
-heat_pollinators_Weak <- heat_pollinators %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Weak) <- heat_pollinators_Weak[,1]
-
-heat_pollinators_Strong <- heat_pollinators %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Strong) <- heat_pollinators_Strong[,1]
-
-heat_pollinators_Medium_weak <- heat_pollinators %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Medium_weak) <- heat_pollinators_Medium_weak[,1]
-
-##################
-
-#Do not know how to handle this multiplot for creating a panel
-
-# I'm going to create the 4 plots in one, 
-# I'm not sure that the grouping of the functional group is correct
-# when is done separately
-
-#sorry for the mess of libraries that I do below
-
- #Prepare first pollinators
-
-library(tidyr)
-library(data.table)
-long <- melt(setDT(heat_pollinators), id.vars = c("position","Broad_categories"), variable.name = "guilds")
-
-long_1 <- long %>% select(-Broad_categories)
-
-library(reshape2)
-long_m <- acast(long_1, position~guilds, value.var="value")
-
-#set manually the divisions, so far this is the best way I have seen to split the rows by categories
-
-r_split <- c(rep(c("Fan"), 3),rep(c("Core-peripheral"), 2),"Complete",rep(c("Fan"),2),rep(c("Core-peripheral"), 4),
-             rep(c("Asymmetric complete"), 2), "Complete", rep(c("Core-peripheral"), 3),rep(c("Asymmetric complete"), 2),
-             "Complete", "Fan")
-
-#set order of labels that avoids overlapping
-r_split <- factor(r_split, levels=c("Core-peripheral","Complete","Fan","Asymmetric complete"))
-
-#plat a bit with colors, a bit of a more complex set but looks nicer
-library(circlize)
-col_fun = colorRamp2(c(0.05644663,0.25, 0.4673256,0.75, 0.8782047), c("blue","cadetblue3", "azure2", "gold","red"))
-
-h_pol <- Heatmap(long_m, name = "Mean\npercentile", row_split=r_split,cluster_row_slices = FALSE, 
-        column_title = "Pollinator functional\ Groups",row_names_gp = gpar(fontsize = 12),col = col_fun)
-
- #Prepare plants
-
-#long format
-long_plants <- melt(setDT(heat_plants), id.vars = c("position","Broad_categories"), variable.name = "Functional_groups")
-
-#filter for creating matrix
-long_plants_1 <- long_plants %>% select(-Broad_categories)
-
-#set better colnames
-long_plants_1$Functional_groups <- as.character(long_plants_1$Functional_groups)
-
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==1] <- "Cluster 1" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==2] <- "Cluster 2" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==3] <- "Cluster 3" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==4] <- "Cluster 4" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==5] <- "Cluster 5"
-
-long_plants_1$Functional_groups <- factor(long_plants_1$Functional_groups, levels=c("Cluster 1",
-"Cluster 2" ,"Cluster 3","Cluster 4" ,"Cluster 5" ))
-
-#create matrix with reshape
-long_plants_m <- acast(long_plants_1, position~Functional_groups, value.var="value")
-
-r_split_plants <- c(rep(c("Fan"), 3),rep(c("Core-peripheral"), 2),"Complete",rep(c("Fan"),2),rep(c("Core-peripheral"), 3),
-             rep(c("Asymmetric complete"), 2), "Complete", rep(c("Core-peripheral"), 4),rep(c("Asymmetric complete"), 2),
-             "Complete", "Fan")
-
-r_split_plants <- factor(r_split, levels=c("Core-peripheral","Complete","Fan","Asymmetric complete"))
-
-h_plan <- Heatmap(long_plants_m, name = "Mean\npercentile", row_split=r_split_plants,cluster_row_slices = FALSE, 
-        column_title = "Plant functional\ Groups",row_names_gp = gpar(fontsize = 12),col = col_fun)
-
-library(patchwork)
-h_pol+h_plan
-
-```
-
-##REFERENCES
-
-<div id ="refs"></div>
-
-##SUPPLEMENTARY MATERIAL
-
-**TABLES**
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
-##############################
-#TABLE S1. List of studies
-##############################
-
-#Load libraries
-library(kableExtra)
-library(dplyr)
-
-#Create data.frame with references
-
-#vector with number of netw per study
-`Number of networks` <- c("6", "2", "3", "1", "1", "1", "1", "2", "1", "1", "8", "16", "6", "2", "4", "1", "3", "1")
-
-#`Network structure` <- c(rep("Web", 22), rep("Metaweb",6))
-
-`First author` <- c("Bartomeus", "Dicks", "Dupont", "Elberling", "Fang", "Inouye", "Lundgren", "Olesen", "Small", "Souza", "Kaiser-Bunbury", "Bartomeus", 
-                    "Kaiser-Bunbury", "Kaiser-Bunbury", "Peralta", "Burkle", "Arroyo-Correa", "Bundgaard")
-
-Year <- c(2008,2002,2003,1999,2008,1988, 2005,2002,1976,2017,2017,2008,2011,2010,2006,2013,2019,2003)
-
-#Country <- c("Spain", "England", "Denmark", "Sweden", "China", "Australia", "Greenland", "Mauritius and Azores", #"Canada", "Brasil", "Seychelles", "Spain", "Seychelles",
-#"Mauritius", "Argentina", "USA", "New Zealand", "Denmark",  "Denmark", "Japan", "Canada", "Venezuela", "Japan", #"Ecuador", "New Zealand", "Venezuela",
-#"USA", "Ecuador")
-
-DOI <- c("https://doi.org/10.1007/s00442-007-0946-1", "https://doi.org/10.1046/j.0021-8790.2001.00572.x", "https://doi.org/10.1111/j.1365-2656.2008.01501.x",
-         "https://doi.org/10.1111/j.1600-0587.1999.tb00507.x", "https://doi.org/10.1111/1749-4877.12190", "https://doi.org/10.1111/j.1442-9993.1988.tb00968.x",
-         "https://doi.org/10.1657/1523-0430(2005)037[0514:TDAHCW]2.0.CO;2", "https://doi.org/10.1046/j.1472-4642.2002.00148.x",
-         "/13960/t4km08d21", "https://doi.org/10.1111/1365-2745.12978", "https://doi.org/10.1038/nature21071", "https://github.com/ibartomeus/BeeFunData",
-         "https://doi.org/10.1111/j.1365-2745.2010.01732.x", "https://doi.org/10.1016/j.ppees.2009.04.001", "https://doi.org/10.1111/ele.13510",
-         "https://doi.org/10.1126/science.1232728", "https://doi.org/10.1111/1365-2745.13332", "Unpublished, Master thesis")
-
-references <- data.frame(`First author`, Year, `Number of networks`,   DOI)
-
-colnames(references) <- c("First author", "Year", "Number of networks",  "DOI")
-
-#Check number of studies
-#nrow(references) # 18 studies
-#check number of networks
-#sum(as.numeric(references$`Number of networks`)) #60
-
-references %>%
-  arrange(`First author`)%>%
-  kable( longtable = T, booktabs = T,linesep = "\\addlinespace",align = c("cccc"),caption = "Table S1.
-List of studies ordered by author with the year of publication, number of contributed networks and digital object identifier") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = c("center"))
-
-```
 
@@
 
-dat <- data.frame(Type, Trait,Type_1, Trait1)
+dat <- data.frame(Type, Trait,Type_1, Trait1, T.cat)
 
-colnames(dat) <- c("Type","Traits","Type", "Traits")
+colnames(dat) <- c("Type","Traits","Type", "Traits", "Categories")
 
-kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c"),caption = "Table S2.
-Traits used to delimit the different plant functional groups divided in quantitative and categorical traits.") %>%
-kable_styling(full_width = F) %>%
-add_header_above(c("Quantitative traits" = 2,"Categorical traits" = 2),bold=T)  %>%
+kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c")) %>%
+kable_styling(full_width = T) %>%
+add_header_above(c("Quantitative traits" = 2,"Categorical traits" = 3),bold=T)  %>%
     column_spec(c(1,4), bold = T) %>% row_spec(0, bold=T)
@@
 ```
-
-**FIGURES**
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=13, fig.cap="Figure S1.
-Plant functional groups composition separated in qualitative and quantitative variables.
-Panel A) shows the percentage of the different categories within trait represented with different colours for each functional group.
-Plot B) shows the radar plot of the different quantitative variables standardize on the same scale also coloured with the same patterns of colours as qualitative variables per cluster."}
-
-#CODE TO PLOT FUNCTIONAL GROUPS
-#IT CAN BE PLOT WITH MUCH LESS CODE BUT NO TIME FOR CLEANING IT
-
-##########################################
-#Visualization of plant functional groups#
-##########################################
-
-library(cowplot)
-library(ggplot2)
-library(tidyr)
-library(dplyr)
-library(reshape2)
-library(data.table)
-library(patchwork)
-
-#LOAD DATA
-#read unscaled trait data in order to visualize better the clusters
-d <- read.csv("../Data/Csv/all_species_imputed_trait_data_forest_data.csv")
-
-dat_1 <- read.csv("../Data/Csv/imputed_trait_data_hclust_5_clusters_forest_data.csv", row.names = "X")
-
-d$Clusters <- dat_1$Clusters
-
-#select columns of interest
-t <- d[c("Breeding_system","IMPUTED_Compatibility","Autonomous_selfing_level",
-         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Flowers_per_inflorescence",
-         "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean", "STYLE_IMPUTED", "OVULES_IMPUTED", "life_form", "lifespan",
-         "IMPUTED_plant_height_mean_m", "Nectar_presence_absence", "Clusters")]
-
-##############################################################################################################################
-#Prepare table qualitative variables
-##############################################################################################################################
-
-##############################################################################################################################
-#Breeding system
-t$Breeding_system <- factor(t$Breeding_system, levels=c("Dioecious", "Monoecious", "Hermaphrodite"))
-
-#Summary to create table
-breeding <- t %>%
-  group_by(Clusters,Breeding_system) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-breeding <- breeding[,-3]
-
-breeding <- spread(breeding, Clusters, Percentage)
-
-colnames(breeding)[1] <- "Category"
-
-Trait <- data.frame(Trait= c(rep("Breeding system", 3)))
-
-Breeding_system <- cbind(Trait, breeding)
-
-##############################################################################################################################
-#Compatibility
-str(t)
-t$IMPUTED_Compatibility <- as.character(t$IMPUTED_Compatibility)
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="dioecious"] <- "Unisexual flower"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="monoecious"] <- "Unisexual flower"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_incompatible"] <- "Self incompatible"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="partially_self_compatible"] <- "Partially self compatible"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_compatible"] <- "Self compatible"
-
-t$IMPUTED_Compatibility <- factor(t$IMPUTED_Compatibility, levels=c("Unisexual flower", "Self incompatible", "Partially self compatible", "Self compatible"))
-#Summary to create table
-comp <- t %>%
-  group_by(Clusters,IMPUTED_Compatibility) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-comp <- comp[,-3]
-
-comp <- spread(comp, Clusters, Percentage)
-#Replace Na's with zeros
-comp[is.na(comp)] <- 0
-#Set call name os categories per trait
-colnames(comp)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Compatibility system", 4)))
-#Add column
-Compatibility_system <- cbind(Trait, comp)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system)
-
-############################################################################################################################################
-#Life form
-t$life_form <- as.character(t$life_form)
-t$life_form[t$life_form =="vine"] <- "Shrub"
-t$life_form[t$life_form =="tree"] <- "Tree"
-t$life_form[t$life_form =="herb"] <- "Herb"
-t$life_form[t$life_form =="shrub"] <- "Shrub"
-#Order levels
-t$life_form <- factor(t$life_form, levels=c("Tree", "Shrub", "Herb"))
-#Summary to create table
-life_form <- t %>%
-  group_by(Clusters,life_form) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-life_form <- life_form[,-3]
-#convert to wide
-life_form <- spread(life_form, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(life_form)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Life form", 3)))
-#Add column
-Life_form<- cbind(Trait, life_form)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form)
-
-############################################################################################################################################
-t$lifespan <- factor(t$lifespan, levels=c("Perennial","Short lived"))
-#Summary to create table
-life_span <- t %>%
-  group_by(Clusters,lifespan) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-life_span <- life_span[,-3]
-#convert to wide
-life_span <- spread(life_span, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(life_span)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Life span", 2)))
-#Add column
-Life_span<- cbind(Trait, life_span)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span)
-
-############################################################################################################################################
-t$Flower_morphology <- as.character(t$Flower_morphology)
-t$Flower_morphology[t$Flower_morphology=="Funnelform"] <- "Campanulate"
-t$Flower_morphology[t$Flower_morphology=="Spike"] <- "Brush"
-
-Flower_morphology <- t %>%
-  group_by(Clusters,Flower_morphology) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-Flower_morphology <- Flower_morphology[,-3]
-#convert to wide
-Flower_morphology <- spread(Flower_morphology, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(Flower_morphology)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Flower shape", 6)))
-#Add column
-Flower_morphology<- cbind(Trait, Flower_morphology)
-#Replace Na's with zeros
-Flower_morphology[is.na(Flower_morphology)] <- 0
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology)
-
-############################################################################################################################################
-t$Flower_symmetry <- as.character(t$Flower_symmetry)
-t$Flower_symmetry[t$Flower_symmetry =="actinomorphic"] <- "Actinomorphic"
-t$Flower_symmetry[t$Flower_symmetry =="zygomorphic"] <- "Zygomorphic"
-
-Flower_symmetry <- t %>%
-  group_by(Clusters,Flower_symmetry) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-Flower_symmetry <- Flower_symmetry[,-3]
-#convert to wide
-Flower_symmetry <- spread(Flower_symmetry, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(Flower_symmetry)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Flower symmetry", 2)))
-#Add column
-Flower_symmetry<- cbind(Trait, Flower_symmetry)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology,Flower_symmetry)
-############################################################################################################################################
-t$Autonomous_selfing_level <- as.character(t$Autonomous_selfing_level)
-t$Autonomous_selfing_level[t$Autonomous_selfing_level =="none"] <- "None"
-t$Autonomous_selfing_level[t$Autonomous_selfing_level =="low"] <- "Low"
-t$Autonomous_selfing_level[t$Autonomous_selfing_level =="medium"] <- "Medium"
-t$Autonomous_selfing_level[t$Autonomous_selfing_level =="high"] <- "High"
-
-#Order levels
-t$Autonomous_selfing_level <- factor(t$Autonomous_selfing_level, levels=c("High", "Medium", "Low", "None"))
-
-Selfing <- t %>%
-  group_by(Clusters,Autonomous_selfing_level) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-#delete column to convert to wide
-Selfing <- Selfing[,-3]
-#convert to wide
-Selfing <- spread(Selfing, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(Selfing)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Selfing level", 2)))
-#Replace Na's with zeros
-Selfing[is.na(Selfing)] <- 0
-#Add column
-Selfing_1 <- cbind(Trait, Selfing)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology, Selfing_1)
-
-############################################################################################################################################
-t$Nectar_presence_absence <- as.character(t$Nectar_presence_absence)
-t$Nectar_presence_absence[t$Nectar_presence_absence =="yes"] <- "Yes"
-t$Nectar_presence_absence[t$Nectar_presence_absence =="no"] <- "No"
-
-Nectar <- t %>%
-  group_by(Clusters,Nectar_presence_absence) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-#delete column to convert to wide
-Nectar <- Nectar[,-3]
-#convert to wide
-Nectar <- spread(Nectar, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(Nectar)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Nectar", 2)))
-#Replace Na's with zeros
-Nectar[is.na(Nectar)] <- 0
-#Add column
-Nectar <- cbind(Trait, Nectar)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology, Flower_symmetry,Selfing_1, Nectar)
-
-##############################################################################################################################
-#Prepare table quantitative variables
-##############################################################################################################################
-
-Selfing <-  t %>% group_by(Clusters)%>% 
-  select(Autonomous_selfing_level_fruit_set) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                     # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                    sd = sd))
-
-s1 <- as.data.frame(t(Selfing))
-#set colnames
-colnames(s1) <- c("1","2","3","4","5")
-#remove the cluster row
-s1 <- s1[-1,]
-#convert rownames to 1st columns
-s1 <- setDT(s1, keep.rownames = "TRUE")[]
-colnames(s1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Autonomous selfing", 5)))
-#Add column
-Selfing <- cbind(Trait, s1)
-
-##############################################################################################################################
-flower_number <-  t %>% group_by(Clusters)%>% 
-  select(Flowers_per_plant) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-f1 <- as.data.frame(t(flower_number))
-#set colnames
-colnames(f1) <- c("1","2","3","4","5")
-#remove the cluster row
-f1 <- f1[-1,]
-#convert rownames to 1st columns
-f1 <- setDT(f1, keep.rownames = "TRUE")[]
-colnames(f1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Flower number", 5)))
-#Add column
-Flower_number <- cbind(Trait, f1)
-
-##############################################################################################################################
-Flowers_per_inflorescence <-  t %>% group_by(Clusters)%>% 
-  select(Flowers_per_inflorescence) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-f_i_1 <- as.data.frame(t(Flowers_per_inflorescence))
-#set colnames
-colnames(f_i_1) <- c("1","2","3","4","5")
-#remove the cluster row
-f_i_1 <- f_i_1[-1,]
-#convert rownames to 1st columns
-f_i_1 <- setDT(f_i_1, keep.rownames = "TRUE")[]
-colnames(f_i_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Flowers per inflorescence", 5)))
-#Add column
-Flower_per_inflo <- cbind(Trait, f_i_1)
-
-bind_rows(Selfing, Flower_number, Flower_per_inflo)
-
-##############################################################################################################################
-Floral_unit_width <-  t %>% group_by(Clusters)%>% 
-  select(Floral_unit_width) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-f_u_w_1 <- as.data.frame(t(Floral_unit_width))
-#set colnames
-colnames(f_u_w_1) <- c("1","2","3","4","5")
-#remove the cluster row
-f_u_w_1 <- f_u_w_1[-1,]
-#convert rownames to 1st columns
-f_u_w_1 <- setDT(f_u_w_1, keep.rownames = "TRUE")[]
-colnames(f_u_w_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Inflorescence width", 5)))
-#Add column
-Inflo_width <- cbind(Trait, f_u_w_1)
-
-bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width)
-
-##############################################################################################################################
-Corolla_diameter_mean <-  t %>% group_by(Clusters)%>% 
-  select(Corolla_diameter_mean) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-c_w_1 <- as.data.frame(t(Corolla_diameter_mean))
-#set colnames
-colnames(c_w_1) <- c("1","2","3","4","5")
-#remove the cluster row
-c_w_1 <- c_w_1[-1,]
-#convert rownames to 1st columns
-c_w_1 <- setDT(c_w_1, keep.rownames = "TRUE")[]
-colnames(c_w_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Flower width", 5)))
-#Add column
-Flower_width <- cbind(Trait, c_w_1)
-
-bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width)
-
-##############################################################################################################################
-Corolla_length_mean <-  t %>% group_by(Clusters)%>% 
-  select(Corolla_length_mean) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-c_l_1 <- as.data.frame(t(Corolla_length_mean))
-#set colnames
-colnames(c_l_1) <- c("1","2","3","4","5")
-#remove the cluster row
-c_l_1 <- c_l_1[-1,]
-#convert rownames to 1st columns
-c_l_1 <- setDT(c_l_1, keep.rownames = "TRUE")[]
-colnames(c_l_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Flower length", 5)))
-#Add column
-Flower_length<- cbind(Trait, c_l_1)
-
-bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length)
-
-##############################################################################################################################
-STYLE_IMPUTED <-  t %>% group_by(Clusters)%>% 
-  select(STYLE_IMPUTED) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-s_l_1 <- as.data.frame(t(STYLE_IMPUTED))
-#set colnames
-colnames(s_l_1) <- c("1","2","3","4","5")
-#remove the cluster row
-s_l_1 <- s_l_1[-1,]
-#convert rownames to 1st columns
-s_l_1 <- setDT(s_l_1, keep.rownames = "TRUE")[]
-colnames(s_l_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Style length", 5)))
-#Add column
-Style_length<- cbind(Trait, s_l_1)
-
-bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length, Style_length)
-
-##############################################################################################################################
-
-OVULES_IMPUTED <-  t %>% group_by(Clusters)%>% 
-  select(OVULES_IMPUTED) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-o_n_1 <- as.data.frame(t(OVULES_IMPUTED))
-#set colnames
-colnames(o_n_1) <- c("1","2","3","4","5")
-#remove the cluster row
-o_n_1 <- o_n_1[-1,]
-#convert rownames to 1st columns
-o_n_1 <- setDT(o_n_1, keep.rownames = "TRUE")[]
-colnames(o_n_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Ovule number", 5)))
-#Add column
-Ovule_number <- cbind(Trait, o_n_1)
-
-bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length, Ovule_number)
-
-##############################################################################################################################
-
-IMPUTED_plant_height_mean_m <-  t %>% group_by(Clusters)%>% 
-  select(IMPUTED_plant_height_mean_m) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-p_h_1 <- as.data.frame(t(IMPUTED_plant_height_mean_m))
-#set colnames
-colnames(p_h_1) <- c("1","2","3","4","5")
-#remove the cluster row
-p_h_1 <- p_h_1[-1,]
-#convert rownames to 1st columns
-p_h_1 <- setDT(p_h_1, keep.rownames = "TRUE")[]
-colnames(p_h_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Plant height", 5)))
-#Add column
-Plant_height <- cbind(Trait, p_h_1)
-
-#Bind quantitative and qualitative variables
-Table_all_traits <- bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology, Flower_symmetry,Selfing_1, Nectar,
-          Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length, Style_length, Ovule_number, Plant_height)
-
-#Select just two decimals
-is.num <- sapply(Table_all_traits, is.numeric)
-Table_all_traits[is.num] <- lapply(Table_all_traits[is.num], round, 2)
-
-colnames(Table_all_traits) <- c("Trait", "Category", "Cluster 1", "Cluster 2", "Cluster 3", "Cluster 4", "Cluster 5")
-
-#LOAD LIBRARIES
-#devtools::install_github("ricardo-bion/ggradar", dependencies=TRUE)
-suppressPackageStartupMessages(library(dplyr))
-library(scales)
-library(tibble)
-library(ggradar)
-library(janitor)
-library(grid)
-library(dplyr)
-library(lubridate)
-#QUANTITATIVVE VARIABLES
-
-#generate subset of quantitative variables for plotting
-quant_median <- subset(Table_all_traits, Category=="median")
-
-#delete col number 2
-quant_median <- quant_median[,-2]
-
-#transpose dataframe
-final_df <- as.data.frame(t(quant_median))
-
-#rownames to colnames (1st one)
-final_df_1 <- final_df %>% row_to_names(row_number = 1)
-
-#Convert all variables to numeric
-final_df_2 <- sapply(final_df_1, function(x) as.numeric(as.character(x)))
-
-#set back the missed rownames in the processing
-rownames(final_df_2) <- rownames(final_df_1)
-
-# Convert to dataframe
-final_df_2 <- as.data.frame(final_df_2)
-
-# Scale values and set rowname as column
-final_df_3 <-final_df_2 %>% rownames_to_column( var = "group" ) %>%   mutate_at(vars(-group),funs(rescale))
-
-#Plot Radar
-#ggradar(final_df_3)
-
-#QUALITATIVE VARIABLES
-
-#LOAD DATA
-#read unscaled trait data in order to visualize better the clusters
-d <- read.csv("../Data/Csv/all_species_imputed_trait_data_forest_data.csv")
-
-dat_1 <- read.csv("../Data/Csv/imputed_trait_data_hclust_5_clusters_forest_data.csv", row.names = "X")
-
-d$Clusters <- dat_1$Clusters
-
-#select columns of interest
-t <- d[c("Breeding_system","IMPUTED_Compatibility","Autonomous_selfing_level",
-         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Flowers_per_inflorescence",
-         "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean", "STYLE_IMPUTED", "OVULES_IMPUTED", "life_form", "lifespan",
-         "IMPUTED_plant_height_mean_m", "Nectar_presence_absence", "Clusters")]
-
-##############################################################################################################################
-#Prepare table qualitative variables
-##############################################################################################################################
-
-##############################################################################################################################
-#Breeding system
-t$Breeding_system <- factor(t$Breeding_system, levels=c("Dioecious", "Monoecious", "Hermaphrodite"))
-
-#Summary to create table
-breeding <- t %>%
-  group_by(Clusters,Breeding_system) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-breeding <- breeding[,-3]
-
-breeding <- spread(breeding, Clusters, Percentage)
-
-colnames(breeding)[1] <- "Category"
-
-Trait <- data.frame(Trait= c(rep("Breeding system", 3)))
-
-Breeding_system <- cbind(Trait, breeding)
-
-##############################################################################################################################
-#Compatibility
-str(t)
-t$IMPUTED_Compatibility <- as.character(t$IMPUTED_Compatibility)
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="dioecious"] <- "Self incompatible"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="monoecious"] <- "Self incompatible"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_incompatible"] <- "Self incompatible"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="partially_self_compatible"] <- "Partially self compatible"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_compatible"] <- "Self compatible"
-
-t$IMPUTED_Compatibility <- factor(t$IMPUTED_Compatibility, levels=c("Self incompatible", "Partially self compatible", "Self compatible"))
-#Summary to create table
-comp <- t %>%
-  group_by(Clusters,IMPUTED_Compatibility) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-comp <- comp[,-3]
-
-comp <- spread(comp, Clusters, Percentage)
-#Replace Na's with zeros
-comp[is.na(comp)] <- 0
-#Set call name os categories per trait
-colnames(comp)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Compatibility system", 3)))
-#Add column
-Compatibility_system <- cbind(Trait, comp)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system)
-
-############################################################################################################################################
-#Life form
-t$life_form <- as.character(t$life_form)
-t$life_form[t$life_form =="vine"] <- "Shrub"
-t$life_form[t$life_form =="tree"] <- "Tree"
-t$life_form[t$life_form =="herb"] <- "Herb"
-t$life_form[t$life_form =="shrub"] <- "Shrub"
-#Order levels
-t$life_form <- factor(t$life_form, levels=c("Tree", "Shrub", "Herb"))
-#Summary to create table
-life_form <- t %>%
-  group_by(Clusters,life_form) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-life_form <- life_form[,-3]
-#convert to wide
-life_form <- spread(life_form, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(life_form)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Life form", 3)))
-#Add column
-Life_form<- cbind(Trait, life_form)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form)
-
-############################################################################################################################################
-t$lifespan <- factor(t$lifespan, levels=c("Perennial","Short lived"))
-#Summary to create table
-life_span <- t %>%
-  group_by(Clusters,lifespan) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-life_span <- life_span[,-3]
-#convert to wide
-life_span <- spread(life_span, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(life_span)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Life span", 2)))
-#Add column
-Life_span<- cbind(Trait, life_span)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span)
-
-############################################################################################################################################
-#t$Flower_morphology <- as.character(t$Flower_morphology)
-#t$Flower_morphology[t$Flower_morphology=="Funnelform"] <- "Campanulate"
-#t$Flower_morphology[t$Flower_morphology=="Spike"] <- "Brush"
-#
-#Flower_morphology <- t %>%
-#  group_by(Clusters,Flower_morphology) %>%
-#  summarise (n = n()) %>%
-#  mutate(Percentage = n / sum(n)*100)
-##delete column to convert to wide
-#Flower_morphology <- Flower_morphology[,-3]
-##convert to wide
-#Flower_morphology <- spread(Flower_morphology, Clusters, Percentage)
-##Set call name os categories per trait
-#colnames(Flower_morphology)[1] <- "Category"
-##Create new column
-#Trait <- data.frame(Trait= c(rep("Flower shape", 6)))
-##Add column
-#Flower_morphology<- cbind(Trait, Flower_morphology)
-##Replace Na's with zeros
-#Flower_morphology[is.na(Flower_morphology)] <- 0
-##Bind rows
-#bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology)
-#
-############################################################################################################################################
-t$Flower_symmetry <- as.character(t$Flower_symmetry)
-t$Flower_symmetry[t$Flower_symmetry =="actinomorphic"] <- "Actinomorphic"
-t$Flower_symmetry[t$Flower_symmetry =="zygomorphic"] <- "Zygomorphic"
-
-Flower_symmetry <- t %>%
-  group_by(Clusters,Flower_symmetry) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-Flower_symmetry <- Flower_symmetry[,-3]
-#convert to wide
-Flower_symmetry <- spread(Flower_symmetry, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(Flower_symmetry)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Flower symmetry", 2)))
-#Add column
-Flower_symmetry<- cbind(Trait, Flower_symmetry)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology,Flower_symmetry)
-############################################################################################################################################
-#t$Autonomous_selfing_level <- as.character(t$Autonomous_selfing_level)
-#t$Autonomous_selfing_level[t$Autonomous_selfing_level =="none"] <- "None"
-#t$Autonomous_selfing_level[t$Autonomous_selfing_level =="low"] <- "Low"
-#t$Autonomous_selfing_level[t$Autonomous_selfing_level =="medium"] <- "Medium"
-#t$Autonomous_selfing_level[t$Autonomous_selfing_level =="high"] <- "High"
-#
-##Order levels
-#t$Autonomous_selfing_level <- factor(t$Autonomous_selfing_level, levels=c("High", "Medium", "Low", "None"))
-#
-#Selfing <- t %>%
-#  group_by(Clusters,Autonomous_selfing_level) %>%
-#  summarise (n = n()) %>%
-#  mutate(Percentage = n / sum(n)*100)
-#
-##delete column to convert to wide
-#Selfing <- Selfing[,-3]
-##convert to wide
-#Selfing <- spread(Selfing, Clusters, Percentage)
-##Set call name os categories per trait
-#colnames(Selfing)[1] <- "Category"
-##Create new column
-#Trait <- data.frame(Trait= c(rep("Selfing level", 2)))
-##Replace Na's with zeros
-#Selfing[is.na(Selfing)] <- 0
-##Add column
-#Selfing_1 <- cbind(Trait, Selfing)
-##Bind rows
-#bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology, Selfing_1)
-#
-#############################################################################################################################################
-t$Nectar_presence_absence <- as.character(t$Nectar_presence_absence)
-t$Nectar_presence_absence[t$Nectar_presence_absence =="yes"] <- "Yes"
-t$Nectar_presence_absence[t$Nectar_presence_absence =="no"] <- "No"
-
-Nectar <- t %>%
-  group_by(Clusters,Nectar_presence_absence) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-#delete column to convert to wide
-Nectar <- Nectar[,-3]
-#convert to wide
-Nectar <- spread(Nectar, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(Nectar)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Nectar", 2)))
-#Replace Na's with zeros
-Nectar[is.na(Nectar)] <- 0
-#Add column
-Nectar <- cbind(Trait, Nectar)
-#Bind rows
-data <- bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span, Flower_symmetry, Nectar)
-
-#remove first col
-data_1 <- data[,-1]
-colnames(data_1) <- c("Category", "Cluster 1", "Cluster 2", "Cluster 3", "Cluster 4", "Cluster 5")
-
-#transpose dataframe
-data_2 <- as.data.frame(t(data_1))
-
-#rownames to colnames (1st one)
-data_3 <- data_2 %>% row_to_names(row_number = 1)
-
-#Convert all variables to numeric
-data_4 <- sapply(data_3, function(x) as.numeric(as.character(x)))
-
-#set back the missed rownames in the processing
-rownames(data_4) <- rownames(data_3)
-
-# Convert to dataframe
-data_4 <- as.data.frame(data_4)
-
-# Scale values and set rowname as column
-data_5 <-data_4 %>% rownames_to_column( var = "group" )
-
-data_6 <- melt(data_5)
-
-cluster1 <- subset(data_6, group=="Cluster 1")
-
-cluster1$traits <- c(rep("Breeding system",3), rep("Compatibility",3), rep("Life form",3),
-                     rep("Life span",2), rep("Flower symmetry",2), rep("Nectar",2))
-
-#Try to achieve the desire output with plot_grid
-
-c1 <- cluster1 %>% 
-  ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values="#00AFBB")+
-  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())+scale_y_continuous(expand = c(0,0)) +
-  theme(axis.title.x = element_blank(), axis.text.x=element_blank(),plot.title = element_text(size = 18))+ ylab("")+
-  ggtitle("A) Qualitative variables")
-
-cluster2 <- subset(data_6, group=="Cluster 2")
-
-cluster2$traits <- c(rep("Breeding system",3), rep("Compatibility",3), rep("Life form",3),
-                     rep("Life span",2), rep("Flower symmetry",2), rep("Nectar",2))
-
-c2 <- cluster2 %>% 
-  ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values="#E69F00")+
-  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())+scale_y_continuous(expand = c(0,0)) +
-  theme(strip.background = element_blank(), strip.text = element_blank())+
-  theme(axis.title.x = element_blank(), axis.text.x=element_blank())+ylab("")
-
-cluster3 <- subset(data_6, group=="Cluster 3")
-
-cluster3$traits <- c(rep("Breeding system",3), rep("Compatibility",3), rep("Life form",3),
-                     rep("Life span",2), rep("Flower symmetry",2), rep("Nectar",2))
-
-c3 <- cluster3 %>% 
-  ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values="#FC4E07")+
-  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())+scale_y_continuous(expand = c(0,0)) +
-  theme(axis.title.x = element_blank(), axis.text.x=element_blank())+
-  theme(strip.background = element_blank(), strip.text = element_blank())+ylab("Percentage")
-
-cluster4 <- subset(data_6, group=="Cluster 4")
-
-cluster4$traits <- c(rep("Breeding system",3), rep("Compatibility",3), rep("Life form",3),
-                     rep("Life span",2), rep("Flower symmetry",2), rep("Nectar",2))
-
-c4 <- cluster4 %>% 
-  ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values="#000000")+
-  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())+scale_y_continuous(expand = c(0,0)) +
-  theme(axis.title.x = element_blank(), axis.text.x=element_blank())+
-  theme(strip.background = element_blank(), strip.text = element_blank())+ylab("")
-
-cluster5 <- subset(data_6, group=="Cluster 5")
-
-cluster5$traits <- c(rep("Breeding system",3), rep("Compatibility",3), rep("Life form",3),
-                     rep("Life span",2), rep("Flower symmetry",2), rep("Nectar",2))
-c5 <- cluster5 %>% 
-  ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values="darkgreen")+
-  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
-  scale_y_continuous(expand = c(0,0)) +
-  theme(axis.text.x = element_text(angle = 45,vjust = 1, hjust=1))+
-  theme(strip.background = element_blank(), strip.text = element_blank())+ylab("")+xlab("")
-
-A <- c1 + c2 + c3 + c4 + c5 + plot_layout(ncol = 1)
-B <- ggradar(final_df_3, group.colours=c("#00AFBB", "#E69F00", "#FC4E07","#000000", "darkgreen"),
-             legend.text.size=5, grid.label.size = 0,legend.position = "none",axis.label.size=3)+ 
-  guides(shape = guide_legend(override.aes = list(size = 0.5)))+ ggtitle("B) Quantitative variables")+
-  theme(plot.title = element_text(size = 18))
-
-patch <- A | B
-
-patch + plot_annotation(title = "Plant functional groups",theme = theme(plot.title = element_text(size = 20,face="bold")))
-
-```

### 2021-06-07 Scripts/Scripts_Funtional_Groups/3_Functional_Groups.R

@@ -26,6 +26,14 @@ library(missMDA)
 library(Rtsne)
 library(dplyr)
 library(ggplot2)
+#Plot dendro
+library("ggplot2")
+library("reshape2")
+library("purrr")
+library("dplyr")
+# let's start with a dendrogram
+library("dendextend")
+
 ########################################################################################################################################################
 #1)READ TRAIT DATA
 ########################################################################################################################################################
@@ -76,7 +84,7 @@ plot(names (b), b, xlab="Number of Clusters", ylab="Penalty score")
 # HCLUST 5 clusters 
 #########
 e.clust_5 <- hclust(g.dist, method="ward.D2")
-plot(e.clust_5, main = "Cluster dengrogram based on effect traits",cex = 0.08)
+plot(e.clust_5, main = "Cluster dengrogram based on effect traits",cex = 0.08,labels =  row.names(e.clust_5))
 cut.g_5 <- readline("5")
 cut.g_5 <- as.integer(cut.g_5)
 e.gr_5 <- cutree(e.clust_5, k = 5)
@@ -92,86 +100,41 @@ ggplot(aes(x = X, y = Y), data = tsne_data) + geom_point(aes(color = cluster))
 
 
 
-
-#Plot dendro
-library("ggplot2")
-library("reshape2")
-library("purrr")
-library("dplyr")
-# let's start with a dendrogram
-library("dendextend")
-dendro <- as.dendrogram(e.clust_5)
-dendro.col <- dendro %>%
-  set("branches_k_color", k = 5, value =   c("black", "grey", "brown4", "orange", "gold2")) %>%
-  set("branches_lwd", 0.6) %>%
-  set("labels_colors", 
-      value = c("darkslategray")) %>% 
-  set("labels_cex", 0.1)
-ggd1 <- as.ggdend(dendro.col)
-
-
-
-ggplot(ggd1, theme = theme_minimal()) +
-  labs(x = "Num. observations", y = "Height", title = "Dendrogram, k = 5")
-
-
-# Radial plot looks less cluttered (and cooler)
-ggplot(ggd1, labels = T) + 
-  scale_y_reverse(expand = c(0.1, 0)) +
-  coord_polar(theta="x")+theme(axis.text.x = element_text(
-    angle= -90 - 360 / length(x) * seq_along(x)))
-
-str(e.clust_5)
-ggd1 <- as.ggdend(e.clust_5)
-
-
[…]

### 2021-06-07 Scripts/Scripts_Funtional_Groups/3_Functional_Groups.R
Update 3_Functional_Groups.R

@@ -114,6 +114,33 @@ ggplot(aes(x = X, y = Y), data = tsne_data) + geom_point(aes(color = cluster))
 #Plot dendrogram
 ########################################################################################################################################################
 
+
+#Plot dendro
+library("ggplot2")
+library("reshape2")
+library("purrr")
+library("dplyr")
+# let's start with a dendrogram
+library("dendextend")
+dendro <- as.dendrogram(e.clust_5)
+dendro.col <- dendro %>%
+  set("branches_k_color", k = 5, value =   c("black", "grey", "brown4", "orange", "gold2")) %>%
+  set("branches_lwd", 0.6) %>%
+  set("labels_colors", 
+      value = c("darkslategray")) %>% 
+  set("labels_cex", 0.1)
+
+labels_colors(dendro.col) <- get_leaves_branches_col(dendro.col)
+ggd1 <- as.ggdend(dendro.col)
+
+
+
+ggplot(ggd1, theme = theme_minimal()) +
+  labs(x = "Num. observations", y = "Height", title = "Dendrogram, k = 5")
+
+
+
+
 #notas que quizás sirvan para algo o no:
 # en e.clust_5$labels podemos acceder a las especies, e.clust_5$order indican el orden
 # todas estas son 1506 especies
@@ -131,6 +158,7 @@ plant_species <- unique(final_d_1$Plant_species)
 
 dendro <- as.dendrogram(e.clust_5)
 
+
 gdend <- dendextend::as.ggdend(dendro %>%
                                  set('branches_k_color', k = 5) %>%
                                  set('branches_lwd', 0.25) %>%
@@ -138,6 +166,9 @@ gdend <- dendextend::as.ggdend(dendro %>%
                                  set('labels_cex', 0.037),
                                theme = theme_minimal(),
                                horiz = TRUE)
+
+labels_colors(gdend) <- get_leaves_branches_col(gdend)
+
 gdend$labels$angle <- seq(90, -270, length = nrow(gdend$labels))
 gdend$labels$vjust <- cos(gdend$labels$angle * pi) / (180)
 gdend$labels$hjust <- sin(gdend$labels$angle * pi) / (180)

### 2021-06-07 Scripts/Scripts_Funtional_Groups/3_Functional_Groups.R
Update 3_Functional_Groups.R

@@ -131,6 +131,14 @@ dendro.col <- dendro %>%
   set("labels_cex", 0.1)
 
 labels_colors(dendro.col) <- get_leaves_branches_col(dendro.col)
+
+# We use "darkgrey" to color some species
+list_species_out <- names(labels_colors(dendro.col)[c(1:100,200:250,1000:1100)])
+
+index_species_out <- which(names(labels_colors(dendro.col)) %in% list_species_out)
+
+labels_colors(dendro.col)[index_species_out] <- "darkslategray"
+
 ggd1 <- as.ggdend(dendro.col)
 
 

### 2021-06-07 Scripts/Scripts_Funtional_Groups/3_Functional_Groups.R
Update 3_Functional_Groups.R

@@ -133,9 +133,11 @@ dendro.col <- dendro %>%
 labels_colors(dendro.col) <- get_leaves_branches_col(dendro.col)
 
 # We use "darkgrey" to color some species
-list_species_out <- names(labels_colors(dendro.col)[c(1:100,200:250,1000:1100)])
+final_d_1 <- read.csv("Data/Csv/data_for_motifs_analysis_1.csv")
 
-index_species_out <- which(names(labels_colors(dendro.col)) %in% list_species_out)
+plant_species <- unique(final_d_1$Plant_species)
+
+index_species_out <- which(names(labels_colors(dendro.col)) %in% plant_species)
 
 labels_colors(dendro.col)[index_species_out] <- "darkslategray"
 

### 2021-06-07 Draft/Draft.Rmd
Adding dendrogram to the main draft and starting  results

@@
 First, plant species were grouped into the optimal number of functional groups that summarized the main plant reproductive strategies.
-This was done with the help of hierarchical cluster analysis by using the trait dataset collated in Lanuza et al., (unpublished) that comprised 1,506 plant species.
+This was done with the help of hierarchical cluster analysis by using the trait dataset collated in Lanuza et al., (unpublished) that comprised 1,506 plant species and contained the same 60 plant-pollinator networks used in this study plus some non-weighted and weighted metawebs (see Table S1 Lanuza et al., unpublished).
 This dataset consisted on 8 floral, 4 reproductive and 3 vegetative traits (Table S2).
+We opted to calculate the plant functional groups on this larger set of species because of the higher accuracy when delimiting the functional groups with that many variables @dolnicar2014.
 For this, we calculated the distance of the different functional traits with the function gowdis from the package FD version 1.0-12 [@laliberte2014] with the method ward.D2 used for non-squared distances [@murtagh2014].
@@
 
-Condense and summarize information
-
-The hierarchical cluster analysis divided the 1506 species in 5 different groups (Figure S1) with different and overlapping characteristics (Figure 1, Table S1).
+The hierarchical cluster analysis divided the dataset with 1506 species and 15 traits into five different clusters with different and overlapping characteristics (Figure S1).
+The subset of plant species used in this study were distributed evenly across these different five groups (see Figure S1).
+The first cluster [...]
+
 The first and largest cluster, Cluster A, was constituted by 710 species.
@@
 library(patchwork)
+library(shades)
 
@@
   ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values="#00AFBB")+
+  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("sandybrown"))+
   facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
@@
   ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values="#E69F00")+
+  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("#7BB0A3"))+
   facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
@@
   ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values="#FC4E07")+
+  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("lightsteelblue2"))+
   facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
@@
   ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values="#000000")+
+  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("thistle"))+
   facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
@@
   ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values="darkgreen")+
+  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("lightgoldenrod2"))+
   facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
@@
 A <- c1 + c2 + c3 + c4 + c5 + plot_layout(ncol = 1)
-B <- ggradar(final_df_3, group.colours=c("#00AFBB", "#E69F00", "#FC4E07","#000000", "darkgreen"),
+B <- ggradar(final_df_3, group.colours=c("sandybrown", "#7BB0A3","lightsteelblue2", "thistle", "lightgoldenrod2"),
              legend.text.size=5, grid.label.size = 0,legend.position = "none",axis.label.size=3)+ 
-  guides(shape = guide_legend(override.aes = list(size = 0.5)))+ ggtitle("B) Quantitative variables")+
+  guides(shape = guide_legend(override.aes = list(size = 0.75)))+ ggtitle("B) Quantitative variables")+
   theme(plot.title = element_text(size = 18))
@@
 
-patch + plot_annotation(title = "Plant functional groups",theme = theme(plot.title = element_text(size = 20,face="bold")))
+patch + plot_annotation(title = "Plant functional group composition",theme = theme(plot.title = element_text(size = 20,face="bold")))
 
 ```
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=13, fig.cap="Figure S2.
+Hierarchical clustering dendrogram with the branches coloured by the optimal number of clusters (5).
+The labels of the subgroup of species (N = 524) used in this study are coloured in black in order to show the evenness of the distribution of the species across clusters.
+The rest of species labels are omitted for visualization purposes (N = 982)."}
+
+library(ggplot2)
+library(dendextend)
+library(dplyr)
+
+e.clust_5 <- readRDS("../Data/RData/e.clust_5.rds")
+
+dendro <- as.dendrogram(e.clust_5)
+dendro.col <- dendro %>%
+  set("branches_k_color", k = 5, value =   c("lightsteelblue2", "thistle", "sandybrown", "#7BB0A3", "lightgoldenrod2")) %>%
+  set("branches_lwd", 0.7) %>%
+  set("labels_colors", 
+      value = c("darkslategray")) %>% 
+  set("labels_cex", 0.075)
+
+labels_colors(dendro.col) <- get_leaves_branches_col(dendro.col)
+
+# We use "darkgrey" to color some species
+final_d_1 <- read.csv("../Data/Csv/data_for_motifs_analysis_1.csv")
+
+plant_species <- unique(final_d_1$Plant_species)
+
+index_species_out <- which(names(labels_colors(dendro.col)) %in% plant_species)
+
+'%ni%' <- Negate('%in%')
+
+index_species_in <- which(names(labels_colors(dendro.col)) %ni% plant_species)
+
+labels_colors(dendro.col)[index_species_out] <- "black"
+labels_colors(dendro.col)[index_species_in] <- "white"
+
+ggd1 <- as.ggdend(dendro.col)
+
+ggd1$labels$angle <- 90
+ggd1$labels$vjust <- 1
+ggd1$labels$hjust <- 1
+
+ggplot(ggd1,offset_labels=-0.05) + theme(panel.grid.major = element_blank(),
+ axis.text = element_blank(),axis.title = element_blank()) +
+  ggtitle("Plant functional groups")+
+  theme(plot.title = element_text(hjust = 0.5, vjust = -2,size = 20,face="bold"))
+
+```

### 2021-06-07 Scripts/Scripts_Funtional_Groups/3_Functional_Groups.R

@@ -98,37 +98,23 @@ tsne_obj <- Rtsne(g.dist, is_distance = TRUE)
 tsne_data <- tsne_obj$Y %>%data.frame() %>%setNames(c("X", "Y")) %>%mutate(cluster = as.factor(e.gr_5))
 ggplot(aes(x = X, y = Y), data = tsne_data) + geom_point(aes(color = cluster))
 
-
-
-#
-##
-###
-####
-#A PARTIR DE AQUI ALFONSO
-####
-###
-##
-#
-
 ########################################################################################################################################################
 #Plot dendrogram
 ########################################################################################################################################################
 
+#saveRDS(e.clust_5, "Data/RData/e.clust_5.rds")
 
-#Plot dendro
-library("ggplot2")
-library("reshape2")
-library("purrr")
-library("dplyr")
-# let's start with a dendrogram
-library("dendextend")
+
+e.clust_5 <- readRDS("Data/RData/e.clust_5.rds")
+
 dendro <- as.dendrogram(e.clust_5)
 dendro.col <- dendro %>%
-  set("branches_k_color", k = 5, value =   c("black", "grey", "brown4", "orange", "gold2")) %>%
-  set("branches_lwd", 0.6) %>%
+  set("branches_k_color", k = 5, value =   c("lightsteelblue2", "thistle", "lightsalmon2", "#7BB0A3", "#CDB533")) %>%
+  set("branches_lwd", 0.7) %>%
   set("labels_colors", 
       value = c("darkslategray")) %>% 
-  set("labels_cex", 0.1)
+  set("labels_cex", 0.105) 
+
 
 labels_colors(dendro.col) <- get_leaves_branches_col(dendro.col)
 
@@ -139,69 +125,50 @@ plant_species <- unique(final_d_1$Plant_species)
 
 index_species_out <- which(names(labels_colors(dendro.col)) %in% plant_species)
 
-labels_colors(dendro.col)[index_species_out] <- "darkslategray"
+'%ni%' <- Negate('%in%')
+
+index_species_in <- which(names(labels_colors(dendro.col)) %ni% plant_species)
+
+labels_colors(dendro.col)[index_species_out] <- "black"
+labels_colors(dendro.col)[index_species_in] <- "lavender"
 
 ggd1 <- as.ggdend(dendro.col)
 
[…]

### 2021-06-08 Draft/Draft.Rmd
deleting setwd

@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=12, fig.width=12}
-setwd("~/R_Projects/Reproductive Traits")
 
@@
 library(patchwork)
-library(shades)
 

### 2021-06-08 Draft/Draft.Rmd
Nacho's edits on Intro and MM. Good job!

@@
 
-Ecological processes leave distinct structural imprints on indirect interactions in mutualistic networks.
+Ecological processes leave distinct structural imprints on species interactions shaping  the topology of mutualistic networks.
 Detecting those relationships is not trivial since they go beyond pair-wise interactions, but may get blurred when considering full network descriptors.
@@
 The interaction between plants and pollinators can be studied at different scales, from species level interactions (micro-scale) to the full network structure (macro-scale).
-Research of the network structure have proven common invariant structural properties across them including nestedness [@jordano2003], the imbalance between plants and pollinators with approximately four times more pollinator species [@vazquez2009] and a degree distribution that decays as a power law [@jordano2003].
-In addition, phenological overlap, morphological matching and species abundances have been shown to be determinant for the understanding of plant-pollinator interactions and network structure [@stang2006; @peralta2020].
-However, condensing to species level and the holistic view of the full network involves missing relevant information for the understanding of ecological processes [@simmons2019].
+Research of the network structure have proven common invariant structural properties across them including a degree distribution that decays as a power law [@jordano2003](idem, aqui molaria citar el original del 98, si no me equivoco), nestedness [@jordano2003](Aqui la cita seria Bascompte PNAS), or the imbalance between plants and pollinators with approximately four times more pollinator species [@vazquez2009](Esta no estoy seguro no sea un artefacto del muestreo...
+quizas la quitamos?
+buscamos otra?).
+In addition, species phenological overlap, morphological matching and species abundances have been shown to be determinant for the understanding of pairwise plant-pollinator interactions [@bartomeus2016, @stang2006; @peralta2020].
+However, both species level information or an holistic view of the full network involves missing relevant information for the understanding of ecological processes [@simmons2019].
 
 Indirect interactions (i.e., motifs), commonly referred as the building blocks that depict subsets of interactions of the network [@milo2002], are a widespread phenomenon in ecological communities [@strauss1991].
-For instance, plant species can facilitate or compete for pollinator's visitation.
-Despite their relevance in ecological communities, plant-pollinator research fails to capture indirect interactions with the traditional analytical tools that condense the information in single indices (e.g., netedness or interaction frequency).
+For instance, plant species can facilitate or compete for pollinator's visitation when two species are visited by the same pollinator [@Gazoul200XJEcol?].
+Despite the relevance of indirect interactions in ecological communities, plant-pollinator research often fails to finely capture those indirect interactions with the traditional analytical tools that condense the information either by species (e.g.
+interaction frequency) or in single topological indices (e.g.
+nestedness).
 Nonetheless, the emerging framework of network motifs in plant-pollinator research allows to consider both direct and indirect interactions [@simmons2019].
 The study of @simmons2020 have shown that the different processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions.
-However, we still ignore what are the general patterns of indirect interactions in plant-pollinator networks.
-
-Linking the structural porperties of the meso-scale with the species ecology can help the understanding of ecological processes.
+However, we still ignore which are the general patterns observed in the distribution of plant-pollinator motifs worldwide.
+
+Motifs are abstract representations often decoupled from species ecology.
+Hence, linking the structural properties of the meso-scale with the species ecology can help the understanding of ecological processes.
 For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species functional role [@stouffer2012; @baker2015].
-However, motifs are abstract representations often decoupled from species ecology.
-Remarkably, recent empirical findings indicate that the meso-scale is the best descriptor of plant reproductive success [@allen2021].
-Further, although some studies have evaluated plant reproductive strategies in plant-pollinator networks [tur2013; @lazaro2020], they are often overlooked [@devaux2014].
-Hence, exploring how the main reproductive groups integrate with the emergent motif framework can shed light of key aspects of ecosystem functioning.
-
-Here, we used 60 plant-pollinator networks from 18 different studies and grouped the different plant and pollinator species into functional groups that summarized the main reproductive strategies.
+However, it is unclear if species ecological and life history traits strongly determines its role within the network of interactions [@coux201X?].
+For example, bees are more specialized foragers [Jose, aquí por ejemplo, pueden decir que abejas pequeñas y generalistas, pueden comportarse muy diferente que grandes y especialistas...
+si tienes una lista de pollintors, con su familia, pasamela, y le hecho un ojo](), usually alble to open complex zygomorphic flowers which are not accessible to fly pollinators.
+How this different behaviors translate into their interaction topology is unknown.
+Similarly, recent empirical findings indicate that the meso-scale is the best descriptor of plant reproductive success [@allen2021], but little is known on how plants reproductive strategies shape their position within the network of interactions.
+Although some studies have evaluated plant reproductive strategies in plant-pollinator networks [@tur2013; @lazaro2020], they are often overlooked in a community context [@devaux2014] and rarely incorporated into plant-pollinator network studies.
+Hence, exploring how the main plant reproductive strategies integrate with the emergent motif framework can shed light on key aspects of ecosystem functioning.
+
+Here, we used 60 plant-pollinator networks from 18 different studies distributed worldwide, alongside a detailed grouping of plants into reproductive strategies and pollinator species into functional groups.
 Plants were grouped based on a comprehensive dataset that included floral, reproductive and vegetative traits compiled in Lanuza et al., (unpublished) on a larger set of plant-pollinator networks.
 Pollinators were grouped into the main taxonomical groups that differed in life form and behaviour.
-Then, we explored the frequency of motifs up to five nodes in these set of plant-pollinator networks.
-Finally, we explore if the different plants and pollinators functional groups are over- or under-represented by comparing their frequencies with simulated networks.
+Then, we explored which motifs up to five nodes in these set of plant-pollinator networks were over and under-represented.
+Finally, we explore if the different plants and pollinators functional groups are over- or under-represented in certain positions.
 
@@
 [potential additions: 
-Finally,for each motif, we recover the number of times a given combination of functional groups emerges ...
-Finally, we draw a network collapsing nodes per FG...]
+Finally,for each motif, we recover the number of times a given combination of functional groups emerges ...]
 

### 2021-06-08 Draft/Draft.Rmd
small extra change

@@
 Prior to analyses, we selected only robust links, that is, interactions whose frequency was greater than one (64.98 % interactions); and, then, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.
+[Here I would present maybe full analysis, and without singletones in sup mat, especially if they are consistent]()
 
@@
 We extracted the position frequencies of all motifs from three to five nodes for each network and species by using the ‘bmotif’ package [@bmotifsimmons2019].
-To estimate the position frequencies of each functional group in a given network, we added the frequencies of those species that belong to the group, and, then, we normalised the resulting frequencies by dividing the position measure for each group by the total number of times that a group appears in any position within the same motif size class.
+To estimate the position frequencies of each functional group in a given network, we added the frequencies of those species that belong to the group, and then, we normalised the resulting frequencies by dividing the position measure for each group by the total number of times that a group appears in any position within the same motif size class.
 Then, we calculated the percentile of the observed position frequencies for each group and network, just like we did motif frequencies.
@@
 
-Year <- c(2008,2002,2003,1999,2008,1988, 2005,2002,1976,2017,2017,2008,2011,2010,2006,2013,2019,2003)
+Year <- c(2008,2002,2003,1999,2008,1988, 2005,2002,1976,2017,2017,2008,2011,2010,2006,2013,2019,2003) ###JOSE! This method is prone to error, My Beefun dataset is 2015 and not 2008. ###
 
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=13, fig.cap="Figure S1.
-Plant functional groups composition separated in qualitative and quantitative variables.
+Plant functional group composition separated in qualitative and quantitative variables.
 Panel A) shows the percentage of the different categories within trait represented with different colours for each functional group.

### 2021-06-08 Draft/Draft.Rmd
Add no_singletons files and figures

@@
 ```
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="Figure 2.
+Comparison of the motif frequencies between empirical and simulated networks.
+Average percentages of motifs close to 0 and 100 indicate under- and over- representation in empirical networks.
+The different motifs are coloured by the mean path length as done in @simmons2020.", fig.width=9,fig.height=5}
+library(lme4)
+library(nlme)
+library(tidyverse)
+source("../Scripts/Scripts_Alfonso/add_study_id.R")
+d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models_NOSING/Motifs_frequency_percentile_NOSING.csv")
+d <- add_study_id(d)
+#str(d)
+#head(d)
+
+#ggplot(d %>% filter(motif != 1), aes(percentil_sizeclass))+
+#  geom_histogram(color="black", fill="white")+
+#  facet_wrap(~motif)+
+#  theme_bw()+
+#  labs(x="Sizeclass percentile")
+#
+# Motifs tend to be over- and under-represensented in real networks
+
+# Mean percentile and SE taking into account the study system
+motif_codes <- d %>% filter(motif != 1) %>% # We remove links (motif code: 1)
+  select(motif) %>% unique() %>% pull()
+motif_means <- tibble(motif = motif_codes)
+motif_means$mean <- NA
+motif_means$SE <- NA
+
+for(i.motif in 1:length(motif_codes)){
+
+  m <- lmer(percentil_sizeclass ~ 1+(1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
+            data = subset(d, motif == motif_codes[i.motif]))
+
+  motif_means$mean[i.motif] <- fixed.effects(m) %>% unname()
+  motif_means$SE[i.motif] <- sqrt(diag(vcov(m)))
+
+}
+
+#Add categories based on path length set by Simmons 2021 et al., Functional Ecology
+d$Broad_categories[d$motif==2 | d$motif==7 | d$motif==17 | d$motif==3|d$motif==4|d$motif==8] <- "Fan"
+
+d$Broad_categories[d$motif==15 | d$motif==11] <- "Medium-weak"
+
+d$Broad_categories[d$motif==6 | d$motif==16 |  d$motif==12] <- "Strong"
+
+d$Broad_categories[d$motif==5 | d$motif==9 |  d$motif==14|  d$motif==13|  d$motif==10] <- "Weak"
+
+#order the categories from short to long path length
+d$Broad_categories <- factor(d$Broad_categories, levels = c("Strong", "Fan", "Medium-weak", "Weak"))
+
+ggplot(NULL) + 
+  geom_point(data = d %>% filter(motif != 1),
+             aes(y=as.factor(motif), x=100*percentil_sizeclass, 
+                 color = as.factor(Broad_categories)),
+             position = "jitter",alpha=0.5)+
+  geom_errorbar(data = motif_means,aes(y = as.factor(motif), xmin=100*(mean-SE), xmax=100*(mean+SE)), 
+                width=1.0,size=1)+
+  geom_point(data = motif_means,aes(y = as.factor(motif), x=100*mean), 
+                size=2)+
+  labs(y="Motif", x = "Percentile (%)",colour="Path length classification")+
+  theme_bw() + scale_color_manual(labels = c('Strong' = expression(paste("Complete (", bar(x), " = 1.38)")),'Fan' = expression(paste("Fan (", bar(x), " = 1.48)")), 'Medium-weak' = expression(paste("Asymmetric complete (", bar(x), " = 1.60)")), "Weak" =expression(paste("Core-peripheral (", bar(x), " = 1.85)"))), name = "Path length classification",values = c("grey25","springgreen4","sienna2","goldenrod2"),guide = guide_legend(title.position = "top",nrow = 2)) +
+theme(legend.text.align = 0)+
+  theme(legend.position="bottom")
+
+#Trying to maintain a gradient from low to high in colors
+
+#Fig 1 Should be a dot plot (or forest plot) of the mean +- SE of the 15 motifs.
+#NICE! Can we put motifs in Y axes, and % in X?
+```
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="Figure 3.
+Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions.
+The different motif positions are dividied by the average path length clasification by @simmons2020."}
+
+library(lme4)
+library(nlme)
+library(tidyverse)
+library(stringi)
+source("../Scripts/Scripts_Alfonso/add_study_id.R")
+
+#############################################
+# EXTRACT MEAN VALUES
+#############################################
+
+all_position_percentiles <- read_csv("../Data/Csv/Motifs_positions_and_null_models_NOSING/GF_positions_frequency_percentile_NOSING.csv")
+
+all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
+                                                              "[0-9]+") %>% as.numeric()
+
+all_position_percentiles <- add_study_id(all_position_percentiles)
+#str(all_position_percentiles)
+#head(all_position_percentiles)
+
+list_plants_FG <- as.character(1:10)
+
+plant_position_percentiles_filtered <- all_position_percentiles %>% 
+  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
+         !is.na(expected_freq_its_GF)) #ME DA ERROR
+pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
+  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
+         !is.na(expected_freq_its_GF))
+
+# Plants-------------
+
+# Mean percentile and SE taking into account the study system
+plant_codes <- plant_position_percentiles_filtered$position %>% unique()
+plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
+plant_means$mean <- NA
+plant_means$SE <- NA
+
+for(i.pos in 1:length(plant_codes)){
+
+  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
+            data = plant_position_percentiles_filtered %>%
+              filter(position == plant_codes[i.pos]))
+
+  temp <- fixed.effects(m) %>% unname()
+  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
+                                                                    temp[1]+temp[2],
+                                                                    temp[1]+temp[3],
+                                                                    temp[1]+temp[4],
+                                                                    temp[1]+temp[5]) ## to get real means per FG
+  temp <- sqrt(diag(vcov(m)))
+  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
+                                                                  temp[1]+temp[2],
+                                                                  temp[1]+temp[3],
+                                                                  temp[1]+temp[4],
+                                                                  temp[1]+temp[5])
+
+}
+
+# Pollinators--------
+
+# Mean percentile and SE taking into account the study system
+pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
+pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
+pollinator_means$mean <- NA
+pollinator_means$SE <- NA
+pollinator_means_reordered <- NULL
+
+for(i.pos in 1:length(pollinator_codes)){
+
+  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
+            data = pollinator_position_percentiles_filtered %>%
+              filter(position == pollinator_codes[i.pos]),
+            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
+
+  temp <- fixed.effects(m) %>% unname()
+  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)
+
+  pollinator_means_aux$mean <- c(temp[1],
+                                 temp[1]+temp[2],
+                                 temp[1]+temp[3],
+                                 temp[1]+temp[4],
+                                 temp[1]+temp[5],
+                                 temp[1]+temp[6],
+                                 temp[1]+temp[7],
+                                 temp[1]+temp[8],
+                                 temp[1]+temp[9]) ## to get real means per FG
+
+  temp <- sqrt(diag(vcov(m)))
+  pollinator_means_aux$SE <- c(temp[1],
+                               temp[1]+temp[2],
+                               temp[1]+temp[3],
+                               temp[1]+temp[4],
+                               temp[1]+temp[5],
+                               temp[1]+temp[6],
+                               temp[1]+temp[7],
+                               temp[1]+temp[8],
+                               temp[1]+temp[9])
+
+  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)
+
+}
+
+# There are lower limits (mean - SE) smaller than 0 (see Other insects)
+# We set the lower limit of those error bars to zero
+
+pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
+pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
+
+#############################################
+# ADDING BROAD MOTIF CATEGORIES TO POSITIONS
+#############################################
+
+motifs_raw_data <- read_csv("../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
+
+motifs_raw_data$Broad_categories <- NA
+
+motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(5,9,14,13,10)] <- "Core-peripherical"
+motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(6,16,12)] <- "Complete"
+motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(2,3,7,4,17,8)] <- "Fan"
+motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(15,11)] <- "Asymmetric complete"
+
+motifs_raw_data$plant <- gsub("[^0-9.-]", "", motifs_raw_data$plant)
+motifs_raw_data$pollinator <- gsub("[^0-9.-]", "", motifs_raw_data$pollinator)
+motifs_raw_data$plant <- as.numeric(motifs_raw_data$plant)
+motifs_raw_data$pollinator <- as.numeric(motifs_raw_data$pollinator)
+motifs_raw_data <- motifs_raw_data %>% filter(!is.na(Broad_categories))
+
+fan_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
+core_per_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
+complete_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
+asymm_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
+
+pollinator_means_reordered$Broad_categories <- NA
+
+pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% fan_pollinator] <- "Fan" 
+pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% asymm_pollinator] <- "Medium-weak" 
+pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% complete_pollinator] <- "Strong" 
+pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% core_per_pollinator] <- "Weak"
+
+fan_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
+core_per_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
+complete_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
+asymm_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
+
+plant_means$Broad_categories <- NA
+
+plant_means$Broad_categories[plant_means$position %in% fan_plant] <- "Fan" 
+plant_means$Broad_categories[plant_means$position %in% asymm_plant] <- "Medium-weak" 
+plant_means$Broad_categories[plant_means$position %in% complete_plant] <- "Strong" 
+plant_means$Broad_categories[plant_means$position %in% core_per_plant] <- "Weak"
+
+########################################
+# CREATE HEATMAPS
+########################################
+
+library(ComplexHeatmap)
+
+# PLANTS-----
+
+# Prepare data for heatmap
+heat_plants_aux <- plant_means %>% spread(Node_FG,mean) %>% select(-SE)
+
+heat_plants <- heat_plants_aux %>%
+  group_by(position,Broad_categories) %>% 
+  summarise_all(sum,na.rm = T)
+
+heat_plants_fan <- heat_plants %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
+  as.matrix()
+
+rownames(heat_plants_fan) <- heat_plants_fan[,1]
+
+heat_plants_Weak <- heat_plants %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
+  as.matrix()
+
+rownames(heat_plants_Weak) <- heat_plants_Weak[,1]
+
+heat_plants_Strong <- heat_plants %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
+  as.matrix()
+
+rownames(heat_plants_Strong) <- heat_plants_Strong[,1]
+
+heat_plants_Medium_weak <- heat_plants %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
+  as.matrix()
+
+rownames(heat_plants_Medium_weak) <- heat_plants_Medium_weak[,1]
+
+# POLLINATORS-----------
+
+filter_rare_groups <- T
+
+if(filter_rare_groups == T){
+  heat_pollinators_aux <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds",
+                                                                                "Lizards",
+                                                                                "Other_insects")) %>% 
+    spread(Node_FG,mean) %>% select(-SE,-lower)
+
+  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bee",            
+                                      "Coleoptera","Lepidoptera","Non-bee\nHymenoptera", 
+                                      "Non-syrphids\ndiptera","Syrphids")
+}else{
+  heat_pollinators_aux <- pollinator_means_reordered %>% spread(Node_FG,mean) %>% select(-SE,-lower)
+
+  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bee","Birds",            
+                                      "Coleoptera","Lepidoptera","Lizards","Non-bee\nHymenoptera", 
+                                      "Non-syrphids\ndiptera","Other insects","Syrphids")
+}
+
+heat_pollinators <- heat_pollinators_aux %>%
+  group_by(position,Broad_categories) %>% 
+  summarise_all(sum,na.rm = T)
+
+heat_pollinators_fan <- heat_pollinators %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
+  as.matrix()
+
+rownames(heat_pollinators_fan) <- heat_pollinators_fan[,1]
+
+heat_pollinators_Weak <- heat_pollinators %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
+  as.matrix()
+
+rownames(heat_pollinators_Weak) <- heat_pollinators_Weak[,1]
+
+heat_pollinators_Strong <- heat_pollinators %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
+  as.matrix()
+
+rownames(heat_pollinators_Strong) <- heat_pollinators_Strong[,1]
+
+heat_pollinators_Medium_weak <- heat_pollinators %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
+  as.matrix()
+
+rownames(heat_pollinators_Medium_weak) <- heat_pollinators_Medium_weak[,1]
+
+##################
+
+#Do not know how to handle this multiplot for creating a panel
+
+# I'm going to create the 4 plots in one, 
+# I'm not sure that the grouping of the functional group is correct
+# when is done separately
+
+#sorry for the mess of libraries that I do below
+
+ #Prepare first pollinators
+
+library(tidyr)
+library(data.table)
+long <- melt(setDT(heat_pollinators), id.vars = c("position","Broad_categories"), variable.name = "guilds")
+
+long_1 <- long %>% select(-Broad_categories)
+
+library(reshape2)
+long_m <- acast(long_1, position~guilds, value.var="value")
+
+#set manually the divisions, so far this is the best way I have seen to split the rows by categories
+
+r_split <- c(rep(c("Fan"), 3),rep(c("Core-peripheral"), 2),"Complete",rep(c("Fan"),2),rep(c("Core-peripheral"), 4),
+             rep(c("Asymmetric complete"), 2), "Complete", rep(c("Core-peripheral"), 3),rep(c("Asymmetric complete"), 2),
+             "Complete", "Fan")
+
+#set order of labels that avoids overlapping
+r_split <- factor(r_split, levels=c("Core-peripheral","Complete","Fan","Asymmetric complete"))
+
+#plat a bit with colors, a bit of a more complex set but looks nicer
+library(circlize)
+col_fun = colorRamp2(c(0.05644663,0.25, 0.4673256,0.75, 0.8782047), c("blue","cadetblue3", "azure2", "gold","red"))
+
+h_pol <- Heatmap(long_m, name = "Mean\npercentile", row_split=r_split,cluster_row_slices = FALSE, 
+        column_title = "Pollinator functional\ Groups",row_names_gp = gpar(fontsize = 12),col = col_fun)
+
+ #Prepare plants
+
+#long format
+long_plants <- melt(setDT(heat_plants), id.vars = c("position","Broad_categories"), variable.name = "Functional_groups")
+
+#filter for creating matrix
+long_plants_1 <- long_plants %>% select(-Broad_categories)
+
+#set better colnames
+long_plants_1$Functional_groups <- as.character(long_plants_1$Functional_groups)
+
+long_plants_1$Functional_groups[long_plants_1$Functional_groups==1] <- "Cluster 1" 
+long_plants_1$Functional_groups[long_plants_1$Functional_groups==2] <- "Cluster 2" 
+long_plants_1$Functional_groups[long_plants_1$Functional_groups==3] <- "Cluster 3" 
+long_plants_1$Functional_groups[long_plants_1$Functional_groups==4] <- "Cluster 4" 
+long_plants_1$Functional_groups[long_plants_1$Functional_groups==5] <- "Cluster 5"
+
+long_plants_1$Functional_groups <- factor(long_plants_1$Functional_groups, levels=c("Cluster 1",
+"Cluster 2" ,"Cluster 3","Cluster 4" ,"Cluster 5" ))
+
+#create matrix with reshape
+long_plants_m <- acast(long_plants_1, position~Functional_groups, value.var="value")
+
+r_split_plants <- c(rep(c("Fan"), 3),rep(c("Core-peripheral"), 2),"Complete",rep(c("Fan"),2),rep(c("Core-peripheral"), 3),
+             rep(c("Asymmetric complete"), 2), "Complete", rep(c("Core-peripheral"), 4),rep(c("Asymmetric complete"), 2),
+             "Complete", "Fan")
+
+r_split_plants <- factor(r_split, levels=c("Core-peripheral","Complete","Fan","Asymmetric complete"))
+
+h_plan <- Heatmap(long_plants_m, name = "Mean\npercentile", row_split=r_split_plants,cluster_row_slices = FALSE, 
+        column_title = "Plant functional\ Groups",row_names_gp = gpar(fontsize = 12),col = col_fun)
+
+library(patchwork)
+h_pol+h_plan
+
+```

### 2021-06-08 Scripts/Scripts_Alfonso/1_create_null_networks_Connectance_Fixed_NOSING.R

@@ -1,0 +1,201 @@
+
+# Extract motif positions for the nodes in the networks in
+# "Data/Csv/data_for_motifs_analysis_1.csv"
+# To do so, the script calculates the incidence matrices of
+# the BINARY networks
+
+# Besides, the script storage the position of 1000 null models where
+# the connectance is conserved. We used 'vaznull', which is described
+# as The algorithm was described as follows: "The algorithm randomized 
+# the total number of individual interactions observed in the original 
+# interaction matrix, F. To this end, the algorithm first created a 
+# binary matrix, assigning interspecific interactions according to 
+# species-specific probabilities, requiring that each species had at 
+# least one interaction. As in Vazquez et al. (2005b), the 
+# species-specific probabilities were proportional to species' relative 
+# abundances (probabilities are in fact approximately proportional and 
+# not equal to relative abundances because of the requirement that each 
+# species receives at least one interaction; this requirement causes 
+# probabilities to deviate from relative abundances, especially for rare 
+# species). Once the number of filled cells in the original matrix was 
+# reached, the remaining interactions were distributed among the filled 
+# cells, so that connectance in the original and randomized matrices was 
+# the same." (Vazquez et al. 2007, page 1122-1123).
+
+# Load libraries
+library(tidyverse)
+library(igraph)
+library(bmotif)
+
+
+# CLEANING----------
+# Load data networks raw data and select those interactions whose Interaction frequency is 
+# greater than a given threshold
+  
+int.threshold <- 1
+
+networks <- read_csv("Data/Csv/data_for_motifs_analysis_1.csv") %>% select(-X1) %>%
+  filter(Interaction >= int.threshold)
+
+# MOTIF MINING --------
+
+# Get the list of networks and motif patterns that are available to iterate
+list_Network_id <- networks$Network_id %>% unique()
+
+
+# CONFIGURATION OF BMOTIF PACKAGE----
+# We are not using weigths to estimate motif info
+mean_weight_i <-  F
+weights_method_i <-  'none'
+normalisation_method_i = "none" #Here we dont use normalization. We will normalize once we
+# sum the frequecies of the nodes that belong to a given functional group by sizeclass
[…]

### 2021-06-08 Scripts/Scripts_Alfonso/2_processing_positions_null_Connectance_Fixed_NOSING.R

@@ -1,0 +1,231 @@
+# We wnat to know:
+#   1) Is the network structure significant?
+#   2) Are FG linked to positions?
+
+# NOTES
+# 
+# para los cálculos de cuantiles he decidido asignarle un NA a las "posiciones de polinizadores"
+# cuando analizo GF de plantas, y vice versa (a las posiciones de plantas, cuando analizo
+#                                             polinizadores).
+# El motivo es que la frecuencia con la que una posición de polinizadores aparece en un nodo planta es cero tanto en las redes observadas como en el modelo nulo, y ello genera este tipo de resultados:
+#   x <- rep(0,7)
+# quantile(x, type=1)
+# 0%  25%  50%  75% 100%
+# 0     0   0     0   0
+# Es decir, el cero observado se corresponde con todos los percentiles de la distribución random.
+# 
+# Para poder reportar un único valor de percentil y distinguir los 0% y 100% que realmente
+# son significativos de los que aparecen como un artefacto de una distribución uniforme,
+# la asignación de los NAs es la única manera que se me ha ocurrido.
+# 
+# Si no me equivoco, una posible consecuencia de la introducción de los NAs es,
+# por ejemplo, la necesidad de ajustar 2 GLMMs para las posiciones: uno de polinizadores
+# y otro para las plantas.
+
+
+# Load libraries
+library(tidyverse)
+source("Scripts/Scripts_Alfonso/sizeclass_normalization.R") # To normalize frequencies of FGs
+
+# List the files with information about the positions
+folder_motif_data <- "Data/Csv/Motifs_positions_and_null_models_NOSING"
+
+motif_files <- list.files(folder_motif_data) 
+motif_link_files <-  motif_files[grep("Binary_Mat_Sp_Motifs_positions_null_Conn_FiX_",motif_files)]
+pollinator_positions_codes <- c("np2","np4","np6","np8","np11","np12","np14","np16",
+                                "np18","np21","np22","np24","np25","np28","np29","np31",
+                                "np34","np35","np38","np41","np42","np44","np46")
+plant_positions_codes <- c("np1","np3","np5","np7","np9","np10","np13","np15",
+                                "np17","np19","np20","np23","np26","np27","np30","np32",
[…]

### 2021-06-08 Scripts/Scripts_Alfonso/3_processing_frequencies_null_Connectance_Fixed_NOSING.R

@@ -1,0 +1,107 @@
+# We wnat to know:
+#   1) Is the network structure significant?
+#   2) Are FG linked to positions?
+
+# NOTES
+# 
+# para los cálculos de cuantiles he decidido asignarle un NA a las "posiciones de polinizadores"
+# cuando analizo GF de plantas, y vice versa (a las posiciones de plantas, cuando analizo
+#                                             polinizadores).
+# El motivo es que la frecuencia con la que una posición de polinizadores aparece en un nodo planta es cero tanto en las redes observadas como en el modelo nulo, y ello genera este tipo de resultados:
+#   x <- rep(0,7)
+# quantile(x, type=1)
+# 0%  25%  50%  75% 100%
+# 0     0   0     0   0
+# Es decir, el cero observado se corresponde con todos los percentiles de la distribución random.
+# 
+# Para poder reportar un único valor de percentil y distinguir los 0% y 100% que realmente
+# son significativos de los que aparecen como un artefacto de una distribución uniforme,
+# la asignación de los NAs es la única manera que se me ha ocurrido.
+# 
+# Si no me equivoco, una posible consecuencia de la introducción de los NAs es,
+# por ejemplo, la necesidad de ajustar 2 GLMMs para las posiciones: uno de polinizadores
+# y otro para las plantas.
+
+
+# Load libraries
+library(tidyverse)
+
+# List the files with information about the frequencies of motifs
+folder_motif_data <- "Data/Csv/Motifs_frequencies_and_null_models_NOSING"
+
+motif_files <- list.files(folder_motif_data) 
+motif_freq_files <-  motif_files[grep("Binary_Mat_Sp_Motifs_frequencies_null_Conn_FiX_NOSING_",
+                                      motif_files)]
+
+for(i in 1:length(motif_freq_files)){
+  
+  start_time <- Sys.time()
+  print(motif_freq_files[i])
+  
+  # Open link file and rearrange it
+  file_i <- paste0(folder_motif_data, "/", motif_freq_files[i])
+  freq_i <- read_csv(file_i)
+  freq_i_observed <- freq_i %>% filter(Type_network=="observed") %>% 
+    select(Network_id,motif,nodes,normalise_sizeclass) %>% 
+    rename(observed_freq_sizeclass = normalise_sizeclass)
+  
+  
[…]

### 2021-06-08 Draft/Draft.Rmd
Update captions S3 S4 draft

@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="Figure 2.
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="Figure S3.
 Comparison of the motif frequencies between empirical and simulated networks.
-Average percentages of motifs close to 0 and 100 indicate under- and over- representation in empirical networks.
+Average percentages of motifs close to 0 and 100 indicate under- and over- representation in empirical networks, after removing non-robust links, that is, interactions whose frequency was equal to one.
 The different motifs are coloured by the mean path length as done in @simmons2020.", fig.width=9,fig.height=5}
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="Figure 3.
-Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions.
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="Figure S4.
+Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions, after removing non-robust links, that is, interactions whose frequency was equal to one.
 The different motif positions are dividied by the average path length clasification by @simmons2020."}

### 2021-06-15 Draft/Draft.Rmd
Adding refs and functional groups names

@@
 The interaction between plants and pollinators can be studied at different scales, from species level interactions (micro-scale) to the full network structure (macro-scale).
-Research of the network structure have proven common invariant structural properties across them including a degree distribution that decays as a power law [@jordano2003](idem, aqui molaria citar el original del 98, si no me equivoco), nestedness [@jordano2003](Aqui la cita seria Bascompte PNAS), or the imbalance between plants and pollinators with approximately four times more pollinator species [@vazquez2009](Esta no estoy seguro no sea un artefacto del muestreo...
-quizas la quitamos?
-buscamos otra?).
-In addition, species phenological overlap, morphological matching and species abundances have been shown to be determinant for the understanding of pairwise plant-pollinator interactions [@bartomeus2016, @stang2006; @peralta2020].
+Research of the network structure have proven common invariant structural properties across them including a degree distribution that decays as a power law [@jordano1987], nestedness [@bascompte2003], or the higher number of pollinator species than plant species [@bluthgen2007].
+In addition, species phenological overlap, morphological matching and species abundances have been shown to be determinant for the understanding of pairwise plant-pollinator interactions [@bartomeus2016; @stang2006; @peralta2020].
 However, both species level information or an holistic view of the full network involves missing relevant information for the understanding of ecological processes [@simmons2019].
@@
 Indirect interactions (i.e., motifs), commonly referred as the building blocks that depict subsets of interactions of the network [@milo2002], are a widespread phenomenon in ecological communities [@strauss1991].
-For instance, plant species can facilitate or compete for pollinator's visitation when two species are visited by the same pollinator [@Gazoul200XJEcol?].
+For instance, plant species can facilitate or compete for pollinator's visitation when two species are visited by the same pollinator [@ghazoul2006].
 Despite the relevance of indirect interactions in ecological communities, plant-pollinator research often fails to finely capture those indirect interactions with the traditional analytical tools that condense the information either by species (e.g.
@@
 For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species functional role [@stouffer2012; @baker2015].
-However, it is unclear if species ecological and life history traits strongly determines its role within the network of interactions [@coux201X?].
+However, it is unclear if species ecological and life history traits strongly determines its role within the network of interactions [@coux2016].
 For example, bees are more specialized foragers [Jose, aquí por ejemplo, pueden decir que abejas pequeñas y generalistas, pueden comportarse muy diferente que grandes y especialistas...
@@
 The hierarchical cluster analysis divided the dataset with 1506 species and 15 traits into five different clusters with different and overlapping characteristics (Figure S1).
-The subset of plant species used in this study were distributed evenly across these different five groups (see Figure S1).
-The first cluster [...]
+The subset of plant species used in this study (N = 503) were distributed evenly across these different larger five groups (see Figure S1).
+The first cluster "short-lived selfers"
 
@@
   ggtitle("Plant functional groups")+
-  theme(plot.title = element_text(hjust = 0.5, vjust = -2,size = 20,face="bold"))
+  theme(plot.title = element_text(hjust = 0.5, vjust = -2,size = 20,face="bold"))+
+  annotate("text", x=140, y=1.65, label= "Perennials self-incompatible large flowers ", size=2.5)+
+  annotate("text", x=380, y=2.15, label= "Tall plants small unisexual flowers", size=2.5) +
+  annotate("text", x=600, y=3.85, label= "Short-lived selfers", size=2.5) +
+  annotate("text", x=1400, y=2.05, label= "Short-lived non-selfers \n long zygomorphic flowers", size=2.5) +annotate("text", x=950, y=2.05, label= "Small non-selfers perennials", size=2.5)
 

### 2021-06-15 Scripts/Scripts_Funtional_Groups/Unique_Cases_Pollinators.R

@@ -1,0 +1,12 @@
+
+library(dplyr)
+
+final_d_1 <- read.csv("Data/Csv/data_for_motifs_analysis_1.csv")
+
+distinct_poll <- final_d_1 %>% distinct(Pollinator_species, .keep_all = T)
+
+poll_info <- distinct_poll %>% select(Pollinator_order, Pollinator_family, Pollinator_genus,Pollinator_species, Pollinator_functional_group)
+
+write.csv(poll_info, "Data/Csv/unique_cases_poll_species.csv")
+
+str(poll_info)

### 2021-06-15 Draft/Draft.Rmd
edits on heatmap

@@
 
+cite complexheatmap https://doi.org/10.1093/bioinformatics/btw313
+
 **Plant-pollinator studies**
@@
 h_pol <- Heatmap(long_m, name = "Mean\npercentile", row_split=r_split,cluster_row_slices = FALSE, 
-        column_title = "Pollinator functional\ Groups",row_names_gp = gpar(fontsize = 12),col = col_fun)
+                 column_title = "Pollinator functional groups",row_names_gp = gpar(fontsize = 10),
+                 col = col_fun,column_names_rot = 45,  column_names_gp = grid::gpar(fontsize = 10),
+                 column_title_gp = gpar(fontsize = 15, fontface = "bold"),
+                 row_title_gp = gpar(fontsize = 10, fontface = "bold"))
 
@@
 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==1] <- "Cluster 1" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==2] <- "Cluster 2" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==3] <- "Cluster 3" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==4] <- "Cluster 4" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==5] <- "Cluster 5"
-
-long_plants_1$Functional_groups <- factor(long_plants_1$Functional_groups, levels=c("Cluster 1",
-"Cluster 2" ,"Cluster 3","Cluster 4" ,"Cluster 5" ))
+long_plants_1$Functional_groups[long_plants_1$Functional_groups==1] <- "Short-lived selfers" 
+long_plants_1$Functional_groups[long_plants_1$Functional_groups==2] <- "Small outcrossing\nperennials" 
+long_plants_1$Functional_groups[long_plants_1$Functional_groups==3] <- "Self-incomp. perennials\nwith large flowers" 
+long_plants_1$Functional_groups[long_plants_1$Functional_groups==4] <- "Tall plants with small\nunisexual flowers" 
+long_plants_1$Functional_groups[long_plants_1$Functional_groups==5] <- "Short-lived outcrossers with\nlong zygomorphic flowers"
+
+long_plants_1$Functional_groups <- factor(long_plants_1$Functional_groups, levels=c("Short-lived selfers",
+"Small outcrossing\nperennials" ,"Self-incomp. perennials\nwith large flowers",
+"Tall plants with small\nunisexual flowers" ,"Short-lived outcrossers with\nlong zygomorphic flowers" ))
 
@@
 
-h_plan <- Heatmap(long_plants_m, name = "Mean\npercentile", row_split=r_split_plants,cluster_row_slices = FALSE, 
-        column_title = "Plant functional\ Groups",row_names_gp = gpar(fontsize = 12),col = col_fun)
+h_plan <- Heatmap(long_plants_m, name = "Mean\npercentile", row_split=r_split_plants,cluster_row_slices = F, 
+                  column_title = "Plant functional groups",row_names_gp = gpar(fontsize = 10),col = col_fun,column_names_rot = 45,  
+                  column_names_gp = grid::gpar(fontsize = 10),column_title_gp = gpar(fontsize = 15, fontface = "bold"),
+                  row_title_gp = gpar(fontsize = 10, fontface = "bold"))
 
 library(patchwork)
-h_pol+h_plan
+ht_list <- h_pol+h_plan
+
+draw(ht_list, auto_adjust = FALSE, cluster_rows = F)
 
@@
   theme(plot.title = element_text(hjust = 0.5, vjust = -2,size = 20,face="bold"))+
-  annotate("text", x=140, y=1.65, label= "Perennials self-incompatible large flowers ", size=2.5)+
-  annotate("text", x=380, y=2.15, label= "Tall plants small unisexual flowers", size=2.5) +
+  annotate("text", x=140, y=1.65, label= "Self-incomp. perennials with large flowers ", size=2.5)+
+  annotate("text", x=380, y=2.15, label= "Tall plants with small unisexual flowers", size=2.5) +
   annotate("text", x=600, y=3.85, label= "Short-lived selfers", size=2.5) +
-  annotate("text", x=1400, y=2.05, label= "Short-lived non-selfers \n long zygomorphic flowers", size=2.5) +annotate("text", x=950, y=2.05, label= "Small non-selfers perennials", size=2.5)
+  annotate("text", x=1400, y=2.05, label= "Short-lived outcrossers with \n long zygomorphic flowers", size=2.5) +annotate("text", x=950, y=2.05, label= "Small outcrossing perennials", size=2.5)
 

### 2021-06-15 Draft/trial.Rmd
edits on heatmap

--- 2021-06-08 Draft/Draft.Rmd
@@
 ---
-title: Plant-pollintor networks worldwide are composed by the same specific building
-  blocks
+title: "Untitled"
 output:
@@
   pdf_document: default
-editor_options:
-  chunk_output_type: console
-bibliography: bibliography.bib
-header-includes:
-- \usepackage{booktabs}
-- \usepackage{longtable}
-- \usepackage{array}
-- \usepackage{multirow}
-- \usepackage{wrapfig}
-- \usepackage{float}
-- \usepackage{colortbl}
-- \usepackage{pdflscape}
-- \usepackage{tabu}
-- \usepackage{threeparttable}
-- \usepackage{threeparttablex}
-- \usepackage[normalem]{ulem}
-- \usepackage{makecell}
-- \usepackage{xcolor}
 ---
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
-
-##Abstract
-
-Ecological processes leave distinct structural imprints on species interactions shaping  the topology of mutualistic networks.
-Detecting those relationships is not trivial since they go beyond pair-wise interactions, but may get blurred when considering full network descriptors.
-However, recent work has shown the network meso-scale can capture this important information.
-The meso-scale describes network subgraphs representing patterns of interactions between a small number of species (i.e.
-motifs) and those constitute the building blocks of the whole network.
-Here we have compiled 60 networks from 18 different studies and show that some motifs are consitently over-represented worldwide, suggesting that the building blocks of plant-pollintor networks are not random and are associated to ...
-Second, we show that the position of pollinator guilds and plant reproductive strategies is not random with respect to the positions occupied within each motif.
-...
-Hence, we show that species ecology is shaping the building blocks that conform the web of life.
-
-##INTRODUCTION
-
-The interaction between plants and pollinators can be studied at different scales, from species level interactions (micro-scale) to the full network structure (macro-scale).
-Research of the network structure have proven common invariant structural properties across them including a degree distribution that decays as a power law [@jordano2003](idem, aqui molaria citar el original del 98, si no me equivoco), nestedness [@jordano2003](Aqui la cita seria Bascompte PNAS), or the imbalance between plants and pollinators with approximately four times more pollinator species [@vazquez2009](Esta no estoy seguro no sea un artefacto del muestreo...
-quizas la quitamos?
-buscamos otra?).
-In addition, species phenological overlap, morphological matching and species abundances have been shown to be determinant for the understanding of pairwise plant-pollinator interactions [@bartomeus2016, @stang2006; @peralta2020].
-However, both species level information or an holistic view of the full network involves missing relevant information for the understanding of ecological processes [@simmons2019].
-
-Indirect interactions (i.e., motifs), commonly referred as the building blocks that depict subsets of interactions of the network [@milo2002], are a widespread phenomenon in ecological communities [@strauss1991].
-For instance, plant species can facilitate or compete for pollinator's visitation when two species are visited by the same pollinator [@Gazoul200XJEcol?].
-Despite the relevance of indirect interactions in ecological communities, plant-pollinator research often fails to finely capture those indirect interactions with the traditional analytical tools that condense the information either by species (e.g.
-interaction frequency) or in single topological indices (e.g.
-nestedness).
-Nonetheless, the emerging framework of network motifs in plant-pollinator research allows to consider both direct and indirect interactions [@simmons2019].
-The study of @simmons2020 have shown that the different processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions.
-However, we still ignore which are the general patterns observed in the distribution of plant-pollinator motifs worldwide.
-
-Motifs are abstract representations often decoupled from species ecology.
-Hence, linking the structural properties of the meso-scale with the species ecology can help the understanding of ecological processes.
-For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species functional role [@stouffer2012; @baker2015].
-However, it is unclear if species ecological and life history traits strongly determines its role within the network of interactions [@coux201X?].
-For example, bees are more specialized foragers [Jose, aquí por ejemplo, pueden decir que abejas pequeñas y generalistas, pueden comportarse muy diferente que grandes y especialistas...
-si tienes una lista de pollintors, con su familia, pasamela, y le hecho un ojo](), usually alble to open complex zygomorphic flowers which are not accessible to fly pollinators.
-How this different behaviors translate into their interaction topology is unknown.
-Similarly, recent empirical findings indicate that the meso-scale is the best descriptor of plant reproductive success [@allen2021], but little is known on how plants reproductive strategies shape their position within the network of interactions.
-Although some studies have evaluated plant reproductive strategies in plant-pollinator networks [@tur2013; @lazaro2020], they are often overlooked in a community context [@devaux2014] and rarely incorporated into plant-pollinator network studies.
-Hence, exploring how the main plant reproductive strategies integrate with the emergent motif framework can shed light on key aspects of ecosystem functioning.
-
-Here, we used 60 plant-pollinator networks from 18 different studies distributed worldwide, alongside a detailed grouping of plants into reproductive strategies and pollinator species into functional groups.
-Plants were grouped based on a comprehensive dataset that included floral, reproductive and vegetative traits compiled in Lanuza et al., (unpublished) on a larger set of plant-pollinator networks.
-Pollinators were grouped into the main taxonomical groups that differed in life form and behaviour.
-Then, we explored which motifs up to five nodes in these set of plant-pollinator networks were over and under-represented.
-Finally, we explore if the different plants and pollinators functional groups are over- or under-represented in certain positions.
-
-##METHODS
-
-**Plant-pollinator studies**
-
-We have compiled 60 plant-pollinator networks from 18 different studies (Table S1).
-All studies sampled plant-pollinator interactions in natural systems and were selected based on wide geographical coverage and the presence of interaction frequency as a measure of interaction strength.
-In total, there were 503 plant species, 1,111 pollinator species and 6248 of pairwise interactions registered.
-For ease of data manipulation plant and pollinator species names were standardize with the help of the package taxize version 0.9.99 [@chamberlain2020].
-
-**Plant and pollinator functional groups**
-
-First, plant species were grouped into the optimal number of functional groups that summarized the main plant reproductive strategies.
-This was done with the help of hierarchical cluster analysis by using the trait dataset collated in Lanuza et al., (unpublished) that comprised 1,506 plant species and contained the same 60 plant-pollinator networks used in this study plus some non-weighted and weighted metawebs (see Table S1 Lanuza et al., unpublished).
-This dataset consisted on 8 floral, 4 reproductive and 3 vegetative traits (Table S2).
-We opted to calculate the plant functional groups on this larger set of species because of the higher accuracy when delimiting the functional groups with that many variables @dolnicar2014.
-For this, we calculated the distance of the different functional traits with the function gowdis from the package FD version 1.0-12 [@laliberte2014] with the method ward.D2 used for non-squared distances [@murtagh2014].
-All the numerical traits were previously scaled.
-Finally, we applied a hierarchical cluster analysis with the function hclust from the R stats package version 4.0.5 and calculated the optimal number of clusters with the function kgs from the package maptree version 1.4-7 [@white2009].
-
-Second, pollinators were grouped into functional groups based on taxonomic rank.
-We opted to divide pollinators on the taxonomic rank level and not with functional traits because (i) they main taxonomic orders differ in form and behaviour and (ii) the lower complexity of higher taxonomic ranks (i.e., pollinators had 6 orders versus plants that had 38).
-Hence, we grouped pollinators into 6 functional groups: (i) Hymenoptera-Anthophila (bees), (ii) Hymenoptera-non-Anthophila (other non-bee Hymenoptera), (iii) Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera and (vi) Coleoptera.
-
-**Meso-scale analysis**
-
-Following Simmons et al.
-[@simmons2019; @simmons2020], we broke down the plant-pollinator networks into their constituent motifs.
-Prior to analyses, we selected only robust links, that is, interactions whose frequency was greater than one (64.98 % interactions); and, then, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.
-[Here I would present maybe full analysis, and without singletones in sup mat, especially if they are consistent]()
-
-We calculated the frequency of all motifs up to five nodes (see Figure 1) for each empirical network, by using the ‘bmotif’ package [@bmotifsimmons2019].
-To control for variation in network size and for the fact that smaller motifs can be nested within larger motifs, the frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains).
-Like [@simmons2020], we just used five-node motifs in our analyses for visualisation, interpretation and computational reasons.
-In addition, we also excluded two-node motifs (or links) from our analyses because their normalised frequencies would always equal one.
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="Figure 1.
-Adapted figure of Simmons et al., 2019 with all the possible motifs from two to five species in bipartite networks.
-There is a total of 17 possible motifs with 46 different positions denoted within each node.", fig.width=10,fig.height=8}
-library(tidyverse)
-library(RColorBrewer)
-source("../Scripts/Scripts_Alfonso/plot_motif_positionsV2.R")
-
-motif_number <- 1
-p1 <- plot_motif_positions(motif_number)
-
-motif_number <- 2
-p2 <- plot_motif_positions(motif_number)
-
-motif_number <- 3
-p3 <- plot_motif_positions(motif_number)
-
-motif_number <- 4
-p4 <- plot_motif_positions(motif_number)
-
-motif_number <- 5
-p5 <- plot_motif_positions(motif_number)
-
-motif_number <- 6
-p6 <- plot_motif_positions(motif_number)
-
-motif_number <- 7
-p7 <- plot_motif_positions(motif_number)
-
-motif_number <- 8   
-p8 <- plot_motif_positions(motif_number)
-
-motif_number <- 9
-p9 <- plot_motif_positions(motif_number)
-
-motif_number <- 10
-p10 <- plot_motif_positions(motif_number)
-
-motif_number <- 11
-p11 <- plot_motif_positions(motif_number)
-
-motif_number <- 12
-p12 <- plot_motif_positions(motif_number)
-
-motif_number <- 13
-p13 <- plot_motif_positions(motif_number)
-
-motif_number <- 14
-p14 <- plot_motif_positions(motif_number)
-
-motif_number <- 15
-p15 <- plot_motif_positions(motif_number)
-
-motif_number <- 16
-p16 <- plot_motif_positions(motif_number)
-
-motif_number <- 17
-p17 <- plot_motif_positions(motif_number)
-
-library(patchwork)
-
-(p1 & ylab("2 species")| p2 & ylab("3 species") | p3 )/ (p4 & ylab("4 species")| p5 | p6 | p7)/ (p8  & ylab("5 species")| p9 | p10 | p11 | p12) / (p13 & ylab("5 species")| p14 | p15 | p16 | p17) & theme(axis.title.y = element_text(color="black", size=14, face="bold")) #+
- #plot_annotation(tag_levels = '1')
-
-```
-
-To assess the significance of the observed frequencies, we created 1,000 simulated networks for each binary network using the ‘nullmodel’ function and the ‘vaznull’ model in the bipartite package [@dormann2009].
-Generated networks had the same number of plants and pollinators, as well as the same connectance of their corresponding empirical networks.
-After extracting the motif frequencies from the simulated networks, for each motif type and empirical network, we calculated the percentage of simulated networks whose frequencies were smaller than the ones observed, that is, we estimated the percentile of the observed motif frequencies.
-Motifs whose percentile is close to zero or 100 are under- or over-represented in the empirical networks, respectively, and, thus, they cannot be predicted by connectance and the number of species alone.
-To summarize general patterns across networks, we used an intercept-only linear mixed model (LMM) per motif, where the response variable was the observed motif percentile per network.
-In these models, we used the study identifiers in Table S1 as a random intercept.
-By doing so, we obtained estimates of the average motif frequency, in which we controlled the variation at the study level.
-
-Next, we calculated which functional groups were over or under-represented in different motif positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
-We extracted the position frequencies of all motifs from three to five nodes for each network and species by using the ‘bmotif’ package [@bmotifsimmons2019].
-To estimate the position frequencies of each functional group in a given network, we added the frequencies of those species that belong to the group, and then, we normalised the resulting frequencies by dividing the position measure for each group by the total number of times that a group appears in any position within the same motif size class.
-Then, we calculated the percentile of the observed position frequencies for each group and network, just like we did motif frequencies.
-To outline the general patterns of position frequencies across networks and functional groups, we fit a LMM per motif position, where the response variable was the observed position percentile per network.
-We used the functional group identifier as an explanatory variable and the study identifiers as a random intercept.
-By adding the functional group estimates to the model intercept, we assessed the average motif frequency, after controlling the variation at the study level.
-To fit the LMMs models in our analyses, we used the ‘lmer’ package [@bates2015].
-
-[potential additions: 
-Finally,for each motif, we recover the number of times a given combination of functional groups emerges ...]
-
-##RESULTS
-
-**Functional groups**
-
-The hierarchical cluster analysis divided the dataset with 1506 species and 15 traits into five different clusters with different and overlapping characteristics (Figure S1).
-The subset of plant species used in this study were distributed evenly across these different five groups (see Figure S1).
-The first cluster [...]
-
-The first and largest cluster, Cluster A, was constituted by 710 species.
-The species of this cluster had the shortest plant heights (Median = 0.5m, Mean = 0.84m), were mostly herbs (89.58%) with short lived life span (68.23%) and the lowest number of flowers per plant (Median = 30, Mean = 197.15); the flowers were mostly hermaphrodite (97.40%) with actinomorphic symmetry (99.48%), the morphology was variant but the predominant shapes were ‘open’ (51.56%) and ‘capitulum’ (23.44%); most of the species were self compatible (96.35%) and had the higher levels of autonomous selfing of all clusters from low-medium selfing (47.92%) to high selfing (52.08%) with nectar production for 83.85% of the species.
-Cluster B, had 588 species and was the the second in plant height (Median = 0.8m, Mean = 1.98m), number of flowers per plant (Median = 75; Mean = 1559) and flowers per inflorescence (Median = 15; Mean = 58), it had diverse life forms (herbs 52.89%, shrubs 34.52% and trees 12.59%) and the species were mostly perennial (97.96%); the flowers were the second largest (flower length Median = 10mm, Mean = 10.08mm; flower width Median = 5.10mm, Mean = 16.88mm) and it had mostly hermaphroditic breeding system (95.41%), actinomorphic symmetry (99.15%) and a predominant flower morphology of ‘open’ (50.17%) and ‘tube’ shapes (20.07); the majority of species were self compatible (70.24%) and partially self compatible (20.24%) and had low selfing levels (88.95%) with nectar production for 78.40%.
-Cluster C was constituted by 323 species, had similar plant heights to cluster B (Median = 0.75, Mean = 1.85) with also diverse life forms (61.61% herbs, 28.79% shrubs, 9.60% trees) with mostly perennial species (95.36%) with the largest flower size (flower length Median =9.10mm , Mean =13.95mm; flower width Median =15mm, Mean =20.18mm) and number of ovules per flower of all clusters (Median = 30, Mean  = 527.87); flowers were mostly hermaphroditic (97.83%) with actinomorphic flowers (78.95%) and predominant ‘open’ (28.48%) ‘capitulum’ (27.55%) and ‘tube’ (26.01%) flower morphology; this was the cluster with greater proportion of self incompatible species (76.47%) and it had negligible autonomous selfing level (Median = 0,  Mean = 0.30) with the highest proportion of nectar secreting species (92.26%).
-Cluster D had 164 species, they were the tallest plants (Median =2.88m, Mean =5.19m) and had the largest proportion of shrubs (41.46%) and trees (31.71%) of all clusters, the species were mainly perennial (92.07%) and differentiated from the rest of the clusters by having principally dioecious (63.41%) and monoecious (35.98%) breeding system; this cluster had the largest number of flower per plant (Median = 1000, Mean = 6803) and per inflorescence (Median = 30 , Mean = 258) but the smaller flower size of all clusters (flower length Median =2.71, Mean =6.53; flower width Median = 3.62; Mean = 8.23) with ‘open’ (53.66%) and ‘brush’ (21.34%) morphology as the most representative flower shapes of this group; in addition, this cluster had the shortest styles (Median = 1mm; Mean = 3.05mm) and lower number of ovules (Median = 4.50, Mean = 110.47) along with cluster A; thus, the flowers were unisexual (98.78%), actinomorphic (95.12%), had no selfing (98.17%) and had the lowest proportion of nectar secreting species (69.51%) of all clusters.
-Finally, 239 species integrated Cluster E which had the second shortest species of all clusters (Median = 0.55m; Mean = 1.23m), the species were mainly herbs (83.26%) and perennial (70.29%) but also had a representative proportion of short lived species (29.71%); this cluster was the only one with mainly zygomorphic flowers (97.07%) with tubular (55.65%) and papilionaceous (24.69%) flower shapes, the species had mostly hermaphroditic breeding system (96.65%) and the flowers had the longest styles of all clusters (Median = 5mm; Mean = 8.74mm); species were mostly self compatible (88.28%) and nectar secreting (88.28%) with low autonomous selfing levels (61.92%) but also had species with high (18.41%) medium (15.06%) and lack of autonomous selfing (4.60%).
-
-Figure S1
-
-**Overall meso-scale patterns**
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="Figure 2.
-Comparison of the motif frequencies between empirical and simulated networks.
-Average percentages of motifs close to 0 and 100 indicate under- and over- representation in empirical networks.
-The different motifs are coloured by the mean path length as done in @simmons2020.", fig.width=9,fig.height=5}
-library(lme4)
-library(nlme)
-library(tidyverse)
-source("../Scripts/Scripts_Alfonso/add_study_id.R")
-d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
-d <- add_study_id(d)
-#str(d)
-#head(d)
-
-#ggplot(d %>% filter(motif != 1), aes(percentil_sizeclass))+
-#  geom_histogram(color="black", fill="white")+
-#  facet_wrap(~motif)+
-#  theme_bw()+
-#  labs(x="Sizeclass percentile")
-#
-# Motifs tend to be over- and under-represensented in real networks
-
-# Mean percentile and SE taking into account the study system
-motif_codes <- d %>% filter(motif != 1) %>% # We remove links (motif code: 1)
-  select(motif) %>% unique() %>% pull()
-motif_means <- tibble(motif = motif_codes)
-motif_means$mean <- NA
-motif_means$SE <- NA
-
-for(i.motif in 1:length(motif_codes)){
-
-  m <- lmer(percentil_sizeclass ~ 1+(1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = subset(d, motif == motif_codes[i.motif]))
-
-  motif_means$mean[i.motif] <- fixed.effects(m) %>% unname()
-  motif_means$SE[i.motif] <- sqrt(diag(vcov(m)))
-
-}
-
-#Add categories based on path length set by Simmons 2021 et al., Functional Ecology
-d$Broad_categories[d$motif==2 | d$motif==7 | d$motif==17 | d$motif==3|d$motif==4|d$motif==8] <- "Fan"
-
-d$Broad_categories[d$motif==15 | d$motif==11] <- "Medium-weak"
-
-d$Broad_categories[d$motif==6 | d$motif==16 |  d$motif==12] <- "Strong"
-
-d$Broad_categories[d$motif==5 | d$motif==9 |  d$motif==14|  d$motif==13|  d$motif==10] <- "Weak"
-
-#order the categories from short to long path length
-d$Broad_categories <- factor(d$Broad_categories, levels = c("Strong", "Fan", "Medium-weak", "Weak"))
-
-ggplot(NULL) + 
-  geom_point(data = d %>% filter(motif != 1),
-             aes(y=as.factor(motif), x=100*percentil_sizeclass, 
-                 color = as.factor(Broad_categories)),
-             position = "jitter",alpha=0.5)+
-  geom_errorbar(data = motif_means,aes(y = as.factor(motif), xmin=100*(mean-SE), xmax=100*(mean+SE)), 
-                width=1.0,size=1)+
-  geom_point(data = motif_means,aes(y = as.factor(motif), x=100*mean), 
-                size=2)+
-  labs(y="Motif", x = "Percentile (%)",colour="Path length classification")+
-  theme_bw() + scale_color_manual(labels = c('Strong' = expression(paste("Complete (", bar(x), " = 1.38)")),'Fan' = expression(paste("Fan (", bar(x), " = 1.48)")), 'Medium-weak' = expression(paste("Asymmetric complete (", bar(x), " = 1.60)")), "Weak" =expression(paste("Core-peripheral (", bar(x), " = 1.85)"))), name = "Path length classification",values = c("grey25","springgreen4","sienna2","goldenrod2"),guide = guide_legend(title.position = "top",nrow = 2)) +
-theme(legend.text.align = 0)+
-  theme(legend.position="bottom")
-
-#Trying to maintain a gradient from low to high in colors
-
-#Fig 1 Should be a dot plot (or forest plot) of the mean +- SE of the 15 motifs.
-#NICE! Can we put motifs in Y axes, and % in X?
-```
-
-**Meso-scale functional groups position**
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align = 'center',fig.width=6,fig.height=3.5}
-library(lme4)
-library(nlme)
-library(tidyverse)
-library(stringi)
-library(ggpubr)
-source("../Scripts/Scripts_Alfonso/add_study_id.R")
-
-all_position_percentiles <- read_csv("../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
-
-all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
-                                                              "[0-9]+") %>% as.numeric()
-
-all_position_percentiles <- add_study_id(all_position_percentiles)
-#str(all_position_percentiles)
-#head(all_position_percentiles)
-
-list_plants_FG <- as.character(1:10)
-
-plant_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF)) #ME DA ERROR
-pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF))
-
-#ggplot(plant_position_percentiles_filtered, aes(percentil_its_GF))+
-#  geom_histogram(color="black", fill="white")+
-#  facet_wrap(~position)+
-#  theme_bw()+
-#  labs(x="Sizeclass percentile", title = "Histograms: Percentiles for plant positions")
-#
-#ggplot(pollinator_position_percentiles_filtered, aes(percentil_its_GF))+
-#  geom_histogram(color="black", fill="white")+
-#  facet_wrap(~position)+
-#  theme_bw()+
-#  labs(x="Sizeclass percentile",title = "Histograms: Percentiles for pollinator positions")
-#
-
-# estimated mean taking into account the random str is 0.XX +- 0.XX (look at the (Intercept) estimate)
-
-# Plants-------------
-
-# Mean percentile and SE taking into account the study system
-plant_codes <- plant_position_percentiles_filtered$position %>% unique()
-plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-plant_means$mean <- NA
-plant_means$SE <- NA
-
-for(i.pos in 1:length(plant_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
-            data = plant_position_percentiles_filtered %>%
-                          filter(position == plant_codes[i.pos]))
-
-  temp <- fixed.effects(m) %>% unname()
-  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
-                                                                     temp[1]+temp[2],
-                                                                     temp[1]+temp[3],
-                                                                     temp[1]+temp[4],
-                                                                     temp[1]+temp[5]) ## to get real means per FG
-  temp <- sqrt(diag(vcov(m)))
-  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
-                                                                  temp[1]+temp[2],
-                                                                  temp[1]+temp[3],
-                                                                  temp[1]+temp[4],
-                                                                  temp[1]+temp[5])
-
-}
-
-GF_plant_pos <- ggplot(NULL) + 
-  geom_point(data = plant_position_percentiles_filtered,
-             aes(x=as.factor(position), y=percentil_its_GF, 
-                 color = as.factor(position)),
-             position = "jitter",alpha=0.5)+
-  geom_errorbar(data = plant_means,aes(x = as.factor(position), ymin=mean-SE, ymax=mean+SE), 
-                width=1.0,size=1)+
-  facet_wrap(~Node_FG,ncol = 5)+
-  geom_point(data = plant_means,aes(x = as.factor(position), y=mean), 
-             size=2)+
-  labs(x="Position", y = "Percentile",title = "Plants")+
-  theme_bw()+
-  theme(legend.position = "none")+#,axis.text.x=element_text(angle=90,vjust=0.5, hjust=1))+
-  coord_flip()
-
-# Pollinators--------
-
-# Mean percentile and SE taking into account the study system
-pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
-pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-pollinator_means$mean <- NA
-pollinator_means$SE <- NA
-pollinator_means_reordered <- NULL
-
-for(i.pos in 1:length(pollinator_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = pollinator_position_percentiles_filtered %>%
-                          filter(position == pollinator_codes[i.pos]),
-            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
-
-  temp <- fixed.effects(m) %>% unname()
-  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)
-
-  pollinator_means_aux$mean <- c(temp[1],
-                                 temp[1]+temp[2],
-                                 temp[1]+temp[3],
-                                 temp[1]+temp[4],
-                                 temp[1]+temp[5],
-                                 temp[1]+temp[6],
-                                 temp[1]+temp[7],
-                                 temp[1]+temp[8],
-                                 temp[1]+temp[9]) ## to get real means per FG
-
-  temp <- sqrt(diag(vcov(m)))
-  pollinator_means_aux$SE <- c(temp[1],
-                               temp[1]+temp[2],
-                               temp[1]+temp[3],
-                               temp[1]+temp[4],
-                               temp[1]+temp[5],
-                               temp[1]+temp[6],
-                               temp[1]+temp[7],
-                               temp[1]+temp[8],
-                               temp[1]+temp[9])
-
-  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)
-
-}
-
-# There are lower limits (mean - SE) smaller than 0 (see Other insects)
-# We set the lower limit of those error bars to zero
-
-pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
-pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
-
-GF_poll_pos <- ggplot(NULL) + 
-  geom_point(data = pollinator_position_percentiles_filtered,
-             aes(x=as.factor(position), y=percentil_its_GF, 
-                 color = as.factor(position)),
-             position = "jitter",alpha=0.5)+
-  geom_errorbar(data = pollinator_means_reordered, aes(x = as.factor(position), ymin=lower,
-                                                       ymax=mean+SE), 
-                width=1.0,size=1)+
-  facet_wrap(~Node_FG,ncol = 5)+
-  geom_point(data = pollinator_means_reordered,aes(x = as.factor(position), y=mean), 
-             size=2)+
-  labs(x="Position", y = "Percentile", title = "Pollinators")+
-  theme_bw()+
-  theme(legend.position = "none")+#,axis.text.x=element_text(angle=90,vjust=0.5, hjust=1))+
-  coord_flip()
-
-# Plant and Pollinators--------
-#
-#ggarrange(GF_plant_pos,GF_poll_pos,
-#          ncol = 1, nrow = 2,heights = c(.90, 1.4))
-#
-#Fig 2 may be the same, but for the each positions-FG combination? Maybe heatmap (but we lose the SE's)
-
-```
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="Figure 3.
-Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions.
-The different motif positions are dividied by the average path length clasification by @simmons2020."}
-
-library(lme4)
-library(nlme)
-library(tidyverse)
-library(stringi)
-source("../Scripts/Scripts_Alfonso/add_study_id.R")
-
-#############################################
-# EXTRACT MEAN VALUES
-#############################################
-
-all_position_percentiles <- read_csv("../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
-
-all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
-                                                              "[0-9]+") %>% as.numeric()
-
-all_position_percentiles <- add_study_id(all_position_percentiles)
-#str(all_position_percentiles)
-#head(all_position_percentiles)
-
-list_plants_FG <- as.character(1:10)
-
-plant_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF)) #ME DA ERROR
-pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF))
-
-# Plants-------------
-
-# Mean percentile and SE taking into account the study system
-plant_codes <- plant_position_percentiles_filtered$position %>% unique()
-plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-plant_means$mean <- NA
-plant_means$SE <- NA
-
-for(i.pos in 1:length(plant_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
-            data = plant_position_percentiles_filtered %>%
-              filter(position == plant_codes[i.pos]))
-
-  temp <- fixed.effects(m) %>% unname()
-  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
-                                                                    temp[1]+temp[2],
-                                                                    temp[1]+temp[3],
-                                                                    temp[1]+temp[4],
-                                                                    temp[1]+temp[5]) ## to get real means per FG
-  temp <- sqrt(diag(vcov(m)))
-  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
-                                                                  temp[1]+temp[2],
-                                                                  temp[1]+temp[3],
-                                                                  temp[1]+temp[4],
-                                                                  temp[1]+temp[5])
-
-}
-
-# Pollinators--------
-
-# Mean percentile and SE taking into account the study system
-pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
-pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-pollinator_means$mean <- NA
-pollinator_means$SE <- NA
-pollinator_means_reordered <- NULL
-
-for(i.pos in 1:length(pollinator_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = pollinator_position_percentiles_filtered %>%
-              filter(position == pollinator_codes[i.pos]),
-            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
-
-  temp <- fixed.effects(m) %>% unname()
-  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)
-
-  pollinator_means_aux$mean <- c(temp[1],
-                                 temp[1]+temp[2],
-                                 temp[1]+temp[3],
-                                 temp[1]+temp[4],
-                                 temp[1]+temp[5],
-                                 temp[1]+temp[6],
-                                 temp[1]+temp[7],
-                                 temp[1]+temp[8],
-                                 temp[1]+temp[9]) ## to get real means per FG
-
-  temp <- sqrt(diag(vcov(m)))
-  pollinator_means_aux$SE <- c(temp[1],
-                               temp[1]+temp[2],
-                               temp[1]+temp[3],
-                               temp[1]+temp[4],
-                               temp[1]+temp[5],
-                               temp[1]+temp[6],
-                               temp[1]+temp[7],
-                               temp[1]+temp[8],
-                               temp[1]+temp[9])
-
-  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)
-
-}
-
-# There are lower limits (mean - SE) smaller than 0 (see Other insects)
-# We set the lower limit of those error bars to zero
-
-pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
-pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
-
-#############################################
-# ADDING BROAD MOTIF CATEGORIES TO POSITIONS
-#############################################
-
-motifs_raw_data <- read_csv("../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-motifs_raw_data$Broad_categories <- NA
-
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(5,9,14,13,10)] <- "Core-peripherical"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(6,16,12)] <- "Complete"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(2,3,7,4,17,8)] <- "Fan"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(15,11)] <- "Asymmetric complete"
-
-motifs_raw_data$plant <- gsub("[^0-9.-]", "", motifs_raw_data$plant)
-motifs_raw_data$pollinator <- gsub("[^0-9.-]", "", motifs_raw_data$pollinator)
-motifs_raw_data$plant <- as.numeric(motifs_raw_data$plant)
-motifs_raw_data$pollinator <- as.numeric(motifs_raw_data$pollinator)
-motifs_raw_data <- motifs_raw_data %>% filter(!is.na(Broad_categories))
-
-fan_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-pollinator_means_reordered$Broad_categories <- NA
-
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% fan_pollinator] <- "Fan" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% asymm_pollinator] <- "Medium-weak" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% complete_pollinator] <- "Strong" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% core_per_pollinator] <- "Weak"
-
-fan_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-plant_means$Broad_categories <- NA
-
-plant_means$Broad_categories[plant_means$position %in% fan_plant] <- "Fan" 
-plant_means$Broad_categories[plant_means$position %in% asymm_plant] <- "Medium-weak" 
-plant_means$Broad_categories[plant_means$position %in% complete_plant] <- "Strong" 
-plant_means$Broad_categories[plant_means$position %in% core_per_plant] <- "Weak"
-
-########################################
-# CREATE HEATMAPS
-########################################
-
-library(ComplexHeatmap)
-
-# PLANTS-----
-
-# Prepare data for heatmap
-heat_plants_aux <- plant_means %>% spread(Node_FG,mean) %>% select(-SE)
-
-heat_plants <- heat_plants_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-heat_plants_fan <- heat_plants %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_fan) <- heat_plants_fan[,1]
-
-heat_plants_Weak <- heat_plants %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Weak) <- heat_plants_Weak[,1]
-
-heat_plants_Strong <- heat_plants %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Strong) <- heat_plants_Strong[,1]
-
-heat_plants_Medium_weak <- heat_plants %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Medium_weak) <- heat_plants_Medium_weak[,1]
-
-# POLLINATORS-----------
-
-filter_rare_groups <- T
-
-if(filter_rare_groups == T){
-  heat_pollinators_aux <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds",
-                                                                                "Lizards",
-                                                                                "Other_insects")) %>% 
-    spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bee",            
-                                      "Coleoptera","Lepidoptera","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\ndiptera","Syrphids")
-}else{
-  heat_pollinators_aux <- pollinator_means_reordered %>% spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bee","Birds",            
-                                      "Coleoptera","Lepidoptera","Lizards","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\ndiptera","Other insects","Syrphids")
-}
-
-heat_pollinators <- heat_pollinators_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-heat_pollinators_fan <- heat_pollinators %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_fan) <- heat_pollinators_fan[,1]
-
-heat_pollinators_Weak <- heat_pollinators %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Weak) <- heat_pollinators_Weak[,1]
-
-heat_pollinators_Strong <- heat_pollinators %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Strong) <- heat_pollinators_Strong[,1]
-
-heat_pollinators_Medium_weak <- heat_pollinators %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Medium_weak) <- heat_pollinators_Medium_weak[,1]
-
-##################
-
-#Do not know how to handle this multiplot for creating a panel
-
-# I'm going to create the 4 plots in one, 
-# I'm not sure that the grouping of the functional group is correct
-# when is done separately
-
-#sorry for the mess of libraries that I do below
-
- #Prepare first pollinators
-
-library(tidyr)
-library(data.table)
-long <- melt(setDT(heat_pollinators), id.vars = c("position","Broad_categories"), variable.name = "guilds")
-
-long_1 <- long %>% select(-Broad_categories)
-
-library(reshape2)
-long_m <- acast(long_1, position~guilds, value.var="value")
-
-#set manually the divisions, so far this is the best way I have seen to split the rows by categories
-
-r_split <- c(rep(c("Fan"), 3),rep(c("Core-peripheral"), 2),"Complete",rep(c("Fan"),2),rep(c("Core-peripheral"), 4),
-             rep(c("Asymmetric complete"), 2), "Complete", rep(c("Core-peripheral"), 3),rep(c("Asymmetric complete"), 2),
-             "Complete", "Fan")
-
-#set order of labels that avoids overlapping
-r_split <- factor(r_split, levels=c("Core-peripheral","Complete","Fan","Asymmetric complete"))
-
-#plat a bit with colors, a bit of a more complex set but looks nicer
-library(circlize)
-col_fun = colorRamp2(c(0.05644663,0.25, 0.4673256,0.75, 0.8782047), c("blue","cadetblue3", "azure2", "gold","red"))
-
-h_pol <- Heatmap(long_m, name = "Mean\npercentile", row_split=r_split,cluster_row_slices = FALSE, 
-        column_title = "Pollinator functional\ Groups",row_names_gp = gpar(fontsize = 12),col = col_fun)
-
- #Prepare plants
-
-#long format
-long_plants <- melt(setDT(heat_plants), id.vars = c("position","Broad_categories"), variable.name = "Functional_groups")
-
-#filter for creating matrix
-long_plants_1 <- long_plants %>% select(-Broad_categories)
-
-#set better colnames
-long_plants_1$Functional_groups <- as.character(long_plants_1$Functional_groups)
-
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==1] <- "Cluster 1" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==2] <- "Cluster 2" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==3] <- "Cluster 3" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==4] <- "Cluster 4" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==5] <- "Cluster 5"
-
-long_plants_1$Functional_groups <- factor(long_plants_1$Functional_groups, levels=c("Cluster 1",
-"Cluster 2" ,"Cluster 3","Cluster 4" ,"Cluster 5" ))
-
-#create matrix with reshape
-long_plants_m <- acast(long_plants_1, position~Functional_groups, value.var="value")
-
-r_split_plants <- c(rep(c("Fan"), 3),rep(c("Core-peripheral"), 2),"Complete",rep(c("Fan"),2),rep(c("Core-peripheral"), 3),
-             rep(c("Asymmetric complete"), 2), "Complete", rep(c("Core-peripheral"), 4),rep(c("Asymmetric complete"), 2),
-             "Complete", "Fan")
-
-r_split_plants <- factor(r_split, levels=c("Core-peripheral","Complete","Fan","Asymmetric complete"))
-
-h_plan <- Heatmap(long_plants_m, name = "Mean\npercentile", row_split=r_split_plants,cluster_row_slices = FALSE, 
-        column_title = "Plant functional\ Groups",row_names_gp = gpar(fontsize = 12),col = col_fun)
-
-library(patchwork)
-h_pol+h_plan
-
-```
-
-##REFERENCES
-
-<div id ="refs"></div>
-
-##SUPPLEMENTARY MATERIAL
-
-**TABLES**
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
-##############################
-#TABLE S1. List of studies
-##############################
-
-#Load libraries
-library(kableExtra)
-library(dplyr)
-
-#Create data.frame with references
-
-#vector with number of netw per study
-`Number of networks` <- c("6", "2", "3", "1", "1", "1", "1", "2", "1", "1", "8", "16", "6", "2", "4", "1", "3", "1")
-
-#`Network structure` <- c(rep("Web", 22), rep("Metaweb",6))
-
-`First author` <- c("Bartomeus", "Dicks", "Dupont", "Elberling", "Fang", "Inouye", "Lundgren", "Olesen", "Small", "Souza", "Kaiser-Bunbury", "Bartomeus", 
-                    "Kaiser-Bunbury", "Kaiser-Bunbury", "Peralta", "Burkle", "Arroyo-Correa", "Bundgaard")
-
-Year <- c(2008,2002,2003,1999,2008,1988, 2005,2002,1976,2017,2017,2008,2011,2010,2006,2013,2019,2003) ###JOSE! This method is prone to error, My Beefun dataset is 2015 and not 2008. ###
-
-#Country <- c("Spain", "England", "Denmark", "Sweden", "China", "Australia", "Greenland", "Mauritius and Azores", #"Canada", "Brasil", "Seychelles", "Spain", "Seychelles",
-#"Mauritius", "Argentina", "USA", "New Zealand", "Denmark",  "Denmark", "Japan", "Canada", "Venezuela", "Japan", #"Ecuador", "New Zealand", "Venezuela",
-#"USA", "Ecuador")
-
-DOI <- c("https://doi.org/10.1007/s00442-007-0946-1", "https://doi.org/10.1046/j.0021-8790.2001.00572.x", "https://doi.org/10.1111/j.1365-2656.2008.01501.x",
-         "https://doi.org/10.1111/j.1600-0587.1999.tb00507.x", "https://doi.org/10.1111/1749-4877.12190", "https://doi.org/10.1111/j.1442-9993.1988.tb00968.x",
-         "https://doi.org/10.1657/1523-0430(2005)037[0514:TDAHCW]2.0.CO;2", "https://doi.org/10.1046/j.1472-4642.2002.00148.x",
-         "/13960/t4km08d21", "https://doi.org/10.1111/1365-2745.12978", "https://doi.org/10.1038/nature21071", "https://github.com/ibartomeus/BeeFunData",
-         "https://doi.org/10.1111/j.1365-2745.2010.01732.x", "https://doi.org/10.1016/j.ppees.2009.04.001", "https://doi.org/10.1111/ele.13510",
-         "https://doi.org/10.1126/science.1232728", "https://doi.org/10.1111/1365-2745.13332", "Unpublished, Master thesis")
-
-references <- data.frame(`First author`, Year, `Number of networks`,   DOI)
-
-colnames(references) <- c("First author", "Year", "Number of networks",  "DOI")
-
-#Check number of studies
-#nrow(references) # 18 studies
-#check number of networks
-#sum(as.numeric(references$`Number of networks`)) #60
-
-references %>%
-  arrange(`First author`)%>%
-  kable( longtable = T, booktabs = T,linesep = "\\addlinespace",align = c("cccc"),caption = "Table S1.
-List of studies ordered by author with the year of publication, number of contributed networks and digital object identifier") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = c("center"))
-
-```
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=12, fig.width=12}
-
-library(kableExtra)
-
-library(dplyr)
-library(readxl) #read excel file (trait data)
-library(dplyr) #data manipulation
-library(visdat) #VISUALIZE MISSING DATA
-library(naniar)
-library(tidyverse)
-########################################################################################################################################################
-#1) READ TRAIT DATA
-########################################################################################################################################################
-
-Trait <- c("Plant height (m)", "Flower width (mm)", "Flower length (mm)", "Inflorescence width (mm)", "Style length (mm)", "Ovules per flower",
-           "Flowers per plant",  "Autonomous selfing (fruit set)")
-
-Trait1 <- c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Autonomous selfing", "Compatibility system", "Breeding system", "")
-
-T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub \n Tree", "Brush \n Campanulate \n Capitulum \n Open \n Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic", "None \n Low \n Medium \n High", "Self-incomp.
-\n Partially self-comp.
-\n Self-comp.", "Hermaphrodite \n Monoecious \n Dioecious",""),align = c("l"))
-
-Type <- c("Vegetative", "Floral", "Floral", "Floral", "Floral", "Floral", "Floral","Reproductive")
-
-Type_1 <- c("Vegetative", "Vegetative", "Floral", "Floral", "Reproductive", "Reproductive", "Reproductive", "")
-
-dat <- data.frame(Type, Trait,Type_1, Trait1)
-
-colnames(dat) <- c("Type","Traits","Type", "Traits")
-
-kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c"),caption = "Table S2.
-Traits used to delimit the different plant functional groups divided in quantitative and categorical traits.") %>%
-kable_styling(full_width = F) %>%
-add_header_above(c("Quantitative traits" = 2,"Categorical traits" = 2),bold=T)  %>%
-    column_spec(c(1,4), bold = T) %>% row_spec(0, bold=T)
-
-```
-
-**FIGURES**
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=13, fig.cap="Figure S1.
-Plant functional group composition separated in qualitative and quantitative variables.
-Panel A) shows the percentage of the different categories within trait represented with different colours for each functional group.
-Plot B) shows the radar plot of the different quantitative variables standardize on the same scale also coloured with the same patterns of colours as qualitative variables per cluster."}
-
-#CODE TO PLOT FUNCTIONAL GROUPS
-#IT CAN BE PLOT WITH MUCH LESS CODE BUT NO TIME FOR CLEANING IT
-
-##########################################
-#Visualization of plant functional groups#
-##########################################
-
-library(cowplot)
-library(ggplot2)
-library(tidyr)
-library(dplyr)
-library(reshape2)
-library(data.table)
-library(patchwork)
-
-#LOAD DATA
-#read unscaled trait data in order to visualize better the clusters
-d <- read.csv("../Data/Csv/all_species_imputed_trait_data_forest_data.csv")
-
-dat_1 <- read.csv("../Data/Csv/imputed_trait_data_hclust_5_clusters_forest_data.csv", row.names = "X")
-
-d$Clusters <- dat_1$Clusters
-
-#select columns of interest
-t <- d[c("Breeding_system","IMPUTED_Compatibility","Autonomous_selfing_level",
-         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Flowers_per_inflorescence",
-         "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean", "STYLE_IMPUTED", "OVULES_IMPUTED", "life_form", "lifespan",
-         "IMPUTED_plant_height_mean_m", "Nectar_presence_absence", "Clusters")]
-
-##############################################################################################################################
-#Prepare table qualitative variables
-##############################################################################################################################
-
-##############################################################################################################################
-#Breeding system
-t$Breeding_system <- factor(t$Breeding_system, levels=c("Dioecious", "Monoecious", "Hermaphrodite"))
-
-#Summary to create table
-breeding <- t %>%
-  group_by(Clusters,Breeding_system) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-breeding <- breeding[,-3]
-
-breeding <- spread(breeding, Clusters, Percentage)
-
-colnames(breeding)[1] <- "Category"
-
-Trait <- data.frame(Trait= c(rep("Breeding system", 3)))
-
-Breeding_system <- cbind(Trait, breeding)
-
-##############################################################################################################################
-#Compatibility
-str(t)
-t$IMPUTED_Compatibility <- as.character(t$IMPUTED_Compatibility)
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="dioecious"] <- "Unisexual flower"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="monoecious"] <- "Unisexual flower"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_incompatible"] <- "Self incompatible"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="partially_self_compatible"] <- "Partially self compatible"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_compatible"] <- "Self compatible"
-
-t$IMPUTED_Compatibility <- factor(t$IMPUTED_Compatibility, levels=c("Unisexual flower", "Self incompatible", "Partially self compatible", "Self compatible"))
-#Summary to create table
-comp <- t %>%
-  group_by(Clusters,IMPUTED_Compatibility) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-comp <- comp[,-3]
-
-comp <- spread(comp, Clusters, Percentage)
-#Replace Na's with zeros
-comp[is.na(comp)] <- 0
-#Set call name os categories per trait
-colnames(comp)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Compatibility system", 4)))
-#Add column
-Compatibility_system <- cbind(Trait, comp)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system)
-
-############################################################################################################################################
-#Life form
-t$life_form <- as.character(t$life_form)
-t$life_form[t$life_form =="vine"] <- "Shrub"
-t$life_form[t$life_form =="tree"] <- "Tree"
-t$life_form[t$life_form =="herb"] <- "Herb"
-t$life_form[t$life_form =="shrub"] <- "Shrub"
-#Order levels
-t$life_form <- factor(t$life_form, levels=c("Tree", "Shrub", "Herb"))
-#Summary to create table
-life_form <- t %>%
-  group_by(Clusters,life_form) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-life_form <- life_form[,-3]
-#convert to wide
-life_form <- spread(life_form, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(life_form)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Life form", 3)))
-#Add column
-Life_form<- cbind(Trait, life_form)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form)
-
-############################################################################################################################################
-t$lifespan <- factor(t$lifespan, levels=c("Perennial","Short lived"))
-#Summary to create table
-life_span <- t %>%
-  group_by(Clusters,lifespan) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-life_span <- life_span[,-3]
-#convert to wide
-life_span <- spread(life_span, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(life_span)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Life span", 2)))
-#Add column
-Life_span<- cbind(Trait, life_span)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span)
-
-############################################################################################################################################
-t$Flower_morphology <- as.character(t$Flower_morphology)
-t$Flower_morphology[t$Flower_morphology=="Funnelform"] <- "Campanulate"
-t$Flower_morphology[t$Flower_morphology=="Spike"] <- "Brush"
-
-Flower_morphology <- t %>%
-  group_by(Clusters,Flower_morphology) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-Flower_morphology <- Flower_morphology[,-3]
-#convert to wide
-Flower_morphology <- spread(Flower_morphology, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(Flower_morphology)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Flower shape", 6)))
-#Add column
-Flower_morphology<- cbind(Trait, Flower_morphology)
-#Replace Na's with zeros
-Flower_morphology[is.na(Flower_morphology)] <- 0
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology)
-
-############################################################################################################################################
-t$Flower_symmetry <- as.character(t$Flower_symmetry)
-t$Flower_symmetry[t$Flower_symmetry =="actinomorphic"] <- "Actinomorphic"
-t$Flower_symmetry[t$Flower_symmetry =="zygomorphic"] <- "Zygomorphic"
-
-Flower_symmetry <- t %>%
-  group_by(Clusters,Flower_symmetry) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-Flower_symmetry <- Flower_symmetry[,-3]
-#convert to wide
-Flower_symmetry <- spread(Flower_symmetry, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(Flower_symmetry)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Flower symmetry", 2)))
-#Add column
-Flower_symmetry<- cbind(Trait, Flower_symmetry)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology,Flower_symmetry)
-############################################################################################################################################
-t$Autonomous_selfing_level <- as.character(t$Autonomous_selfing_level)
-t$Autonomous_selfing_level[t$Autonomous_selfing_level =="none"] <- "None"
-t$Autonomous_selfing_level[t$Autonomous_selfing_level =="low"] <- "Low"
-t$Autonomous_selfing_level[t$Autonomous_selfing_level =="medium"] <- "Medium"
-t$Autonomous_selfing_level[t$Autonomous_selfing_level =="high"] <- "High"
-
-#Order levels
-t$Autonomous_selfing_level <- factor(t$Autonomous_selfing_level, levels=c("High", "Medium", "Low", "None"))
-
-Selfing <- t %>%
-  group_by(Clusters,Autonomous_selfing_level) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-#delete column to convert to wide
-Selfing <- Selfing[,-3]
-#convert to wide
-Selfing <- spread(Selfing, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(Selfing)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Selfing level", 2)))
-#Replace Na's with zeros
-Selfing[is.na(Selfing)] <- 0
-#Add column
-Selfing_1 <- cbind(Trait, Selfing)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology, Selfing_1)
-
-############################################################################################################################################
-t$Nectar_presence_absence <- as.character(t$Nectar_presence_absence)
-t$Nectar_presence_absence[t$Nectar_presence_absence =="yes"] <- "Yes"
-t$Nectar_presence_absence[t$Nectar_presence_absence =="no"] <- "No"
-
-Nectar <- t %>%
-  group_by(Clusters,Nectar_presence_absence) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-#delete column to convert to wide
-Nectar <- Nectar[,-3]
-#convert to wide
-Nectar <- spread(Nectar, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(Nectar)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Nectar", 2)))
-#Replace Na's with zeros
-Nectar[is.na(Nectar)] <- 0
-#Add column
-Nectar <- cbind(Trait, Nectar)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology, Flower_symmetry,Selfing_1, Nectar)
-
-##############################################################################################################################
-#Prepare table quantitative variables
-##############################################################################################################################
-
-Selfing <-  t %>% group_by(Clusters)%>% 
-  select(Autonomous_selfing_level_fruit_set) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                     # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                    sd = sd))
-
-s1 <- as.data.frame(t(Selfing))
-#set colnames
-colnames(s1) <- c("1","2","3","4","5")
-#remove the cluster row
-s1 <- s1[-1,]
-#convert rownames to 1st columns
-s1 <- setDT(s1, keep.rownames = "TRUE")[]
-colnames(s1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Autonomous selfing", 5)))
-#Add column
-Selfing <- cbind(Trait, s1)
-
-##############################################################################################################################
-flower_number <-  t %>% group_by(Clusters)%>% 
-  select(Flowers_per_plant) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-f1 <- as.data.frame(t(flower_number))
-#set colnames
-colnames(f1) <- c("1","2","3","4","5")
-#remove the cluster row
-f1 <- f1[-1,]
-#convert rownames to 1st columns
-f1 <- setDT(f1, keep.rownames = "TRUE")[]
-colnames(f1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Flower number", 5)))
-#Add column
-Flower_number <- cbind(Trait, f1)
-
-##############################################################################################################################
-Flowers_per_inflorescence <-  t %>% group_by(Clusters)%>% 
-  select(Flowers_per_inflorescence) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-f_i_1 <- as.data.frame(t(Flowers_per_inflorescence))
-#set colnames
-colnames(f_i_1) <- c("1","2","3","4","5")
-#remove the cluster row
-f_i_1 <- f_i_1[-1,]
-#convert rownames to 1st columns
-f_i_1 <- setDT(f_i_1, keep.rownames = "TRUE")[]
-colnames(f_i_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Flowers per inflorescence", 5)))
-#Add column
-Flower_per_inflo <- cbind(Trait, f_i_1)
-
-bind_rows(Selfing, Flower_number, Flower_per_inflo)
-
-##############################################################################################################################
-Floral_unit_width <-  t %>% group_by(Clusters)%>% 
-  select(Floral_unit_width) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-f_u_w_1 <- as.data.frame(t(Floral_unit_width))
-#set colnames
-colnames(f_u_w_1) <- c("1","2","3","4","5")
-#remove the cluster row
-f_u_w_1 <- f_u_w_1[-1,]
-#convert rownames to 1st columns
-f_u_w_1 <- setDT(f_u_w_1, keep.rownames = "TRUE")[]
-colnames(f_u_w_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Inflorescence width", 5)))
-#Add column
-Inflo_width <- cbind(Trait, f_u_w_1)
-
-bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width)
-
-##############################################################################################################################
-Corolla_diameter_mean <-  t %>% group_by(Clusters)%>% 
-  select(Corolla_diameter_mean) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-c_w_1 <- as.data.frame(t(Corolla_diameter_mean))
-#set colnames
-colnames(c_w_1) <- c("1","2","3","4","5")
-#remove the cluster row
-c_w_1 <- c_w_1[-1,]
-#convert rownames to 1st columns
-c_w_1 <- setDT(c_w_1, keep.rownames = "TRUE")[]
-colnames(c_w_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Flower width", 5)))
-#Add column
-Flower_width <- cbind(Trait, c_w_1)
-
-bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width)
-
-##############################################################################################################################
-Corolla_length_mean <-  t %>% group_by(Clusters)%>% 
-  select(Corolla_length_mean) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-c_l_1 <- as.data.frame(t(Corolla_length_mean))
-#set colnames
-colnames(c_l_1) <- c("1","2","3","4","5")
-#remove the cluster row
-c_l_1 <- c_l_1[-1,]
-#convert rownames to 1st columns
-c_l_1 <- setDT(c_l_1, keep.rownames = "TRUE")[]
-colnames(c_l_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Flower length", 5)))
-#Add column
-Flower_length<- cbind(Trait, c_l_1)
-
-bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length)
-
-##############################################################################################################################
-STYLE_IMPUTED <-  t %>% group_by(Clusters)%>% 
-  select(STYLE_IMPUTED) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-s_l_1 <- as.data.frame(t(STYLE_IMPUTED))
-#set colnames
-colnames(s_l_1) <- c("1","2","3","4","5")
-#remove the cluster row
-s_l_1 <- s_l_1[-1,]
-#convert rownames to 1st columns
-s_l_1 <- setDT(s_l_1, keep.rownames = "TRUE")[]
-colnames(s_l_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Style length", 5)))
-#Add column
-Style_length<- cbind(Trait, s_l_1)
-
-bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length, Style_length)
-
-##############################################################################################################################
-
-OVULES_IMPUTED <-  t %>% group_by(Clusters)%>% 
-  select(OVULES_IMPUTED) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-o_n_1 <- as.data.frame(t(OVULES_IMPUTED))
-#set colnames
-colnames(o_n_1) <- c("1","2","3","4","5")
-#remove the cluster row
-o_n_1 <- o_n_1[-1,]
-#convert rownames to 1st columns
-o_n_1 <- setDT(o_n_1, keep.rownames = "TRUE")[]
-colnames(o_n_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Ovule number", 5)))
-#Add column
-Ovule_number <- cbind(Trait, o_n_1)
-
-bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length, Ovule_number)
-
-##############################################################################################################################
-
-IMPUTED_plant_height_mean_m <-  t %>% group_by(Clusters)%>% 
-  select(IMPUTED_plant_height_mean_m) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-p_h_1 <- as.data.frame(t(IMPUTED_plant_height_mean_m))
-#set colnames
-colnames(p_h_1) <- c("1","2","3","4","5")
-#remove the cluster row
-p_h_1 <- p_h_1[-1,]
-#convert rownames to 1st columns
-p_h_1 <- setDT(p_h_1, keep.rownames = "TRUE")[]
-colnames(p_h_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Plant height", 5)))
-#Add column
-Plant_height <- cbind(Trait, p_h_1)
-
-#Bind quantitative and qualitative variables
-Table_all_traits <- bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology, Flower_symmetry,Selfing_1, Nectar,
-          Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length, Style_length, Ovule_number, Plant_height)
-
-#Select just two decimals
-is.num <- sapply(Table_all_traits, is.numeric)
-Table_all_traits[is.num] <- lapply(Table_all_traits[is.num], round, 2)
-
-colnames(Table_all_traits) <- c("Trait", "Category", "Cluster 1", "Cluster 2", "Cluster 3", "Cluster 4", "Cluster 5")
-
-#LOAD LIBRARIES
-#devtools::install_github("ricardo-bion/ggradar", dependencies=TRUE)
-suppressPackageStartupMessages(library(dplyr))
-library(scales)
-library(tibble)
-library(ggradar)
-library(janitor)
-library(grid)
-library(dplyr)
-library(lubridate)
-#QUANTITATIVVE VARIABLES
-
-#generate subset of quantitative variables for plotting
-quant_median <- subset(Table_all_traits, Category=="median")
-
-#delete col number 2
-quant_median <- quant_median[,-2]
-
-#transpose dataframe
-final_df <- as.data.frame(t(quant_median))
-
-#rownames to colnames (1st one)
-final_df_1 <- final_df %>% row_to_names(row_number = 1)
-
-#Convert all variables to numeric
-final_df_2 <- sapply(final_df_1, function(x) as.numeric(as.character(x)))
-
-#set back the missed rownames in the processing
-rownames(final_df_2) <- rownames(final_df_1)
-
-# Convert to dataframe
-final_df_2 <- as.data.frame(final_df_2)
-
-# Scale values and set rowname as column
-final_df_3 <-final_df_2 %>% rownames_to_column( var = "group" ) %>%   mutate_at(vars(-group),funs(rescale))
-
-#Plot Radar
-#ggradar(final_df_3)
-
-#QUALITATIVE VARIABLES
-
-#LOAD DATA
-#read unscaled trait data in order to visualize better the clusters
-d <- read.csv("../Data/Csv/all_species_imputed_trait_data_forest_data.csv")
-
-dat_1 <- read.csv("../Data/Csv/imputed_trait_data_hclust_5_clusters_forest_data.csv", row.names = "X")
-
-d$Clusters <- dat_1$Clusters
-
-#select columns of interest
-t <- d[c("Breeding_system","IMPUTED_Compatibility","Autonomous_selfing_level",
-         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Flowers_per_inflorescence",
-         "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean", "STYLE_IMPUTED", "OVULES_IMPUTED", "life_form", "lifespan",
-         "IMPUTED_plant_height_mean_m", "Nectar_presence_absence", "Clusters")]
-
-##############################################################################################################################
-#Prepare table qualitative variables
-##############################################################################################################################
-
-##############################################################################################################################
-#Breeding system
-t$Breeding_system <- factor(t$Breeding_system, levels=c("Dioecious", "Monoecious", "Hermaphrodite"))
-
-#Summary to create table
-breeding <- t %>%
-  group_by(Clusters,Breeding_system) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-breeding <- breeding[,-3]
-
-breeding <- spread(breeding, Clusters, Percentage)
-
-colnames(breeding)[1] <- "Category"
-
-Trait <- data.frame(Trait= c(rep("Breeding system", 3)))
-
-Breeding_system <- cbind(Trait, breeding)
-
-##############################################################################################################################
-#Compatibility
-str(t)
-t$IMPUTED_Compatibility <- as.character(t$IMPUTED_Compatibility)
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="dioecious"] <- "Self incompatible"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="monoecious"] <- "Self incompatible"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_incompatible"] <- "Self incompatible"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="partially_self_compatible"] <- "Partially self compatible"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_compatible"] <- "Self compatible"
-
-t$IMPUTED_Compatibility <- factor(t$IMPUTED_Compatibility, levels=c("Self incompatible", "Partially self compatible", "Self compatible"))
-#Summary to create table
-comp <- t %>%
-  group_by(Clusters,IMPUTED_Compatibility) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-comp <- comp[,-3]
-
-comp <- spread(comp, Clusters, Percentage)
-#Replace Na's with zeros
-comp[is.na(comp)] <- 0
-#Set call name os categories per trait
-colnames(comp)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Compatibility system", 3)))
-#Add column
-Compatibility_system <- cbind(Trait, comp)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system)
-
-############################################################################################################################################
-#Life form
-t$life_form <- as.character(t$life_form)
-t$life_form[t$life_form =="vine"] <- "Shrub"
-t$life_form[t$life_form =="tree"] <- "Tree"
-t$life_form[t$life_form =="herb"] <- "Herb"
-t$life_form[t$life_form =="shrub"] <- "Shrub"
-#Order levels
-t$life_form <- factor(t$life_form, levels=c("Tree", "Shrub", "Herb"))
-#Summary to create table
-life_form <- t %>%
-  group_by(Clusters,life_form) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-life_form <- life_form[,-3]
-#convert to wide
-life_form <- spread(life_form, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(life_form)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Life form", 3)))
-#Add column
-Life_form<- cbind(Trait, life_form)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form)
-
-############################################################################################################################################
-t$lifespan <- factor(t$lifespan, levels=c("Perennial","Short lived"))
-#Summary to create table
-life_span <- t %>%
-  group_by(Clusters,lifespan) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-life_span <- life_span[,-3]
-#convert to wide
-life_span <- spread(life_span, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(life_span)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Life span", 2)))
-#Add column
-Life_span<- cbind(Trait, life_span)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span)
-
-############################################################################################################################################
-#t$Flower_morphology <- as.character(t$Flower_morphology)
-#t$Flower_morphology[t$Flower_morphology=="Funnelform"] <- "Campanulate"
-#t$Flower_morphology[t$Flower_morphology=="Spike"] <- "Brush"
-#
-#Flower_morphology <- t %>%
-#  group_by(Clusters,Flower_morphology) %>%
-#  summarise (n = n()) %>%
-#  mutate(Percentage = n / sum(n)*100)
-##delete column to convert to wide
-#Flower_morphology <- Flower_morphology[,-3]
-##convert to wide
-#Flower_morphology <- spread(Flower_morphology, Clusters, Percentage)
-##Set call name os categories per trait
-#colnames(Flower_morphology)[1] <- "Category"
-##Create new column
-#Trait <- data.frame(Trait= c(rep("Flower shape", 6)))
-##Add column
-#Flower_morphology<- cbind(Trait, Flower_morphology)
-##Replace Na's with zeros
-#Flower_morphology[is.na(Flower_morphology)] <- 0
-##Bind rows
-#bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology)
-#
-############################################################################################################################################
-t$Flower_symmetry <- as.character(t$Flower_symmetry)
-t$Flower_symmetry[t$Flower_symmetry =="actinomorphic"] <- "Actinomorphic"
-t$Flower_symmetry[t$Flower_symmetry =="zygomorphic"] <- "Zygomorphic"
-
-Flower_symmetry <- t %>%
-  group_by(Clusters,Flower_symmetry) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-Flower_symmetry <- Flower_symmetry[,-3]
-#convert to wide
-Flower_symmetry <- spread(Flower_symmetry, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(Flower_symmetry)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Flower symmetry", 2)))
-#Add column
-Flower_symmetry<- cbind(Trait, Flower_symmetry)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology,Flower_symmetry)
-############################################################################################################################################
-#t$Autonomous_selfing_level <- as.character(t$Autonomous_selfing_level)
-#t$Autonomous_selfing_level[t$Autonomous_selfing_level =="none"] <- "None"
-#t$Autonomous_selfing_level[t$Autonomous_selfing_level =="low"] <- "Low"
-#t$Autonomous_selfing_level[t$Autonomous_selfing_level =="medium"] <- "Medium"
-#t$Autonomous_selfing_level[t$Autonomous_selfing_level =="high"] <- "High"
-#
-##Order levels
-#t$Autonomous_selfing_level <- factor(t$Autonomous_selfing_level, levels=c("High", "Medium", "Low", "None"))
-#
-#Selfing <- t %>%
-#  group_by(Clusters,Autonomous_selfing_level) %>%
-#  summarise (n = n()) %>%
-#  mutate(Percentage = n / sum(n)*100)
-#
-##delete column to convert to wide
-#Selfing <- Selfing[,-3]
-##convert to wide
-#Selfing <- spread(Selfing, Clusters, Percentage)
-##Set call name os categories per trait
-#colnames(Selfing)[1] <- "Category"
-##Create new column
-#Trait <- data.frame(Trait= c(rep("Selfing level", 2)))
-##Replace Na's with zeros
-#Selfing[is.na(Selfing)] <- 0
-##Add column
-#Selfing_1 <- cbind(Trait, Selfing)
-##Bind rows
-#bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology, Selfing_1)
-#
-#############################################################################################################################################
-t$Nectar_presence_absence <- as.character(t$Nectar_presence_absence)
-t$Nectar_presence_absence[t$Nectar_presence_absence =="yes"] <- "Yes"
-t$Nectar_presence_absence[t$Nectar_presence_absence =="no"] <- "No"
-
-Nectar <- t %>%
-  group_by(Clusters,Nectar_presence_absence) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-#delete column to convert to wide
-Nectar <- Nectar[,-3]
-#convert to wide
-Nectar <- spread(Nectar, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(Nectar)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Nectar", 2)))
-#Replace Na's with zeros
-Nectar[is.na(Nectar)] <- 0
-#Add column
-Nectar <- cbind(Trait, Nectar)
-#Bind rows
-data <- bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span, Flower_symmetry, Nectar)
-
-#remove first col
-data_1 <- data[,-1]
-colnames(data_1) <- c("Category", "Cluster 1", "Cluster 2", "Cluster 3", "Cluster 4", "Cluster 5")
-
-#transpose dataframe
-data_2 <- as.data.frame(t(data_1))
-
-#rownames to colnames (1st one)
-data_3 <- data_2 %>% row_to_names(row_number = 1)
-
-#Convert all variables to numeric
-data_4 <- sapply(data_3, function(x) as.numeric(as.character(x)))
-
-#set back the missed rownames in the processing
-rownames(data_4) <- rownames(data_3)
-
-# Convert to dataframe
-data_4 <- as.data.frame(data_4)
-
-# Scale values and set rowname as column
-data_5 <-data_4 %>% rownames_to_column( var = "group" )
-
-data_6 <- melt(data_5)
-
-cluster1 <- subset(data_6, group=="Cluster 1")
-
-cluster1$traits <- c(rep("Breeding system",3), rep("Compatibility",3), rep("Life form",3),
-                     rep("Life span",2), rep("Flower symmetry",2), rep("Nectar",2))
-
-#Try to achieve the desire output with plot_grid
-
-c1 <- cluster1 %>% 
-  ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("sandybrown"))+
-  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())+scale_y_continuous(expand = c(0,0)) +
-  theme(axis.title.x = element_blank(), axis.text.x=element_blank(),plot.title = element_text(size = 18))+ ylab("")+
-  ggtitle("A) Qualitative variables")
-
-cluster2 <- subset(data_6, group=="Cluster 2")
-
-cluster2$traits <- c(rep("Breeding system",3), rep("Compatibility",3), rep("Life form",3),
-                     rep("Life span",2), rep("Flower symmetry",2), rep("Nectar",2))
-
-c2 <- cluster2 %>% 
-  ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("#7BB0A3"))+
-  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())+scale_y_continuous(expand = c(0,0)) +
-  theme(strip.background = element_blank(), strip.text = element_blank())+
-  theme(axis.title.x = element_blank(), axis.text.x=element_blank())+ylab("")
-
-cluster3 <- subset(data_6, group=="Cluster 3")
-
-cluster3$traits <- c(rep("Breeding system",3), rep("Compatibility",3), rep("Life form",3),
-                     rep("Life span",2), rep("Flower symmetry",2), rep("Nectar",2))
-
-c3 <- cluster3 %>% 
-  ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("lightsteelblue2"))+
-  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())+scale_y_continuous(expand = c(0,0)) +
-  theme(axis.title.x = element_blank(), axis.text.x=element_blank())+
-  theme(strip.background = element_blank(), strip.text = element_blank())+ylab("Percentage")
-
-cluster4 <- subset(data_6, group=="Cluster 4")
-
-cluster4$traits <- c(rep("Breeding system",3), rep("Compatibility",3), rep("Life form",3),
-                     rep("Life span",2), rep("Flower symmetry",2), rep("Nectar",2))
-
-c4 <- cluster4 %>% 
-  ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("thistle"))+
-  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())+scale_y_continuous(expand = c(0,0)) +
-  theme(axis.title.x = element_blank(), axis.text.x=element_blank())+
-  theme(strip.background = element_blank(), strip.text = element_blank())+ylab("")
-
-cluster5 <- subset(data_6, group=="Cluster 5")
-
-cluster5$traits <- c(rep("Breeding system",3), rep("Compatibility",3), rep("Life form",3),
-                     rep("Life span",2), rep("Flower symmetry",2), rep("Nectar",2))
-c5 <- cluster5 %>% 
-  ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("lightgoldenrod2"))+
-  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
-  scale_y_continuous(expand = c(0,0)) +
-  theme(axis.text.x = element_text(angle = 45,vjust = 1, hjust=1))+
-  theme(strip.background = element_blank(), strip.text = element_blank())+ylab("")+xlab("")
-
-A <- c1 + c2 + c3 + c4 + c5 + plot_layout(ncol = 1)
-B <- ggradar(final_df_3, group.colours=c("sandybrown", "#7BB0A3","lightsteelblue2", "thistle", "lightgoldenrod2"),
-             legend.text.size=5, grid.label.size = 0,legend.position = "none",axis.label.size=3)+ 
-  guides(shape = guide_legend(override.aes = list(size = 0.75)))+ ggtitle("B) Quantitative variables")+
-  theme(plot.title = element_text(size = 18))
-
-patch <- A | B
-
-patch + plot_annotation(title = "Plant functional group composition",theme = theme(plot.title = element_text(size = 20,face="bold")))
-
-```
 
@@
       value = c("darkslategray")) %>% 
-  set("labels_cex", 0.075)
+  set("labels_cex", 0.065)
 
@@
   ggtitle("Plant functional groups")+
-  theme(plot.title = element_text(hjust = 0.5, vjust = -2,size = 20,face="bold"))
+  theme(plot.title = element_text(hjust = 0.5, vjust = -2,size = 20,face="bold"))+
+  geom_text(aes(x = x, y = y, label = label, angle = -90, hjust = 0), data= label(ddata))
 
 ```
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="Figure S3.
-Comparison of the motif frequencies between empirical and simulated networks.
-Average percentages of motifs close to 0 and 100 indicate under- and over- representation in empirical networks, after removing non-robust links, that is, interactions whose frequency was equal to one.
-The different motifs are coloured by the mean path length as done in @simmons2020.", fig.width=9,fig.height=5}
-library(lme4)
-library(nlme)
-library(tidyverse)
-source("../Scripts/Scripts_Alfonso/add_study_id.R")
-d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models_NOSING/Motifs_frequency_percentile_NOSING.csv")
-d <- add_study_id(d)
-#str(d)
-#head(d)
-
-#ggplot(d %>% filter(motif != 1), aes(percentil_sizeclass))+
-#  geom_histogram(color="black", fill="white")+
-#  facet_wrap(~motif)+
-#  theme_bw()+
-#  labs(x="Sizeclass percentile")
-#
-# Motifs tend to be over- and under-represensented in real networks
-
-# Mean percentile and SE taking into account the study system
-motif_codes <- d %>% filter(motif != 1) %>% # We remove links (motif code: 1)
-  select(motif) %>% unique() %>% pull()
-motif_means <- tibble(motif = motif_codes)
-motif_means$mean <- NA
-motif_means$SE <- NA
-
-for(i.motif in 1:length(motif_codes)){
-
-  m <- lmer(percentil_sizeclass ~ 1+(1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = subset(d, motif == motif_codes[i.motif]))
-
-  motif_means$mean[i.motif] <- fixed.effects(m) %>% unname()
-  motif_means$SE[i.motif] <- sqrt(diag(vcov(m)))
-
-}
-
-#Add categories based on path length set by Simmons 2021 et al., Functional Ecology
-d$Broad_categories[d$motif==2 | d$motif==7 | d$motif==17 | d$motif==3|d$motif==4|d$motif==8] <- "Fan"
-
-d$Broad_categories[d$motif==15 | d$motif==11] <- "Medium-weak"
-
-d$Broad_categories[d$motif==6 | d$motif==16 |  d$motif==12] <- "Strong"
-
-d$Broad_categories[d$motif==5 | d$motif==9 |  d$motif==14|  d$motif==13|  d$motif==10] <- "Weak"
-
-#order the categories from short to long path length
-d$Broad_categories <- factor(d$Broad_categories, levels = c("Strong", "Fan", "Medium-weak", "Weak"))
-
-ggplot(NULL) + 
-  geom_point(data = d %>% filter(motif != 1),
-             aes(y=as.factor(motif), x=100*percentil_sizeclass, 
-                 color = as.factor(Broad_categories)),
-             position = "jitter",alpha=0.5)+
-  geom_errorbar(data = motif_means,aes(y = as.factor(motif), xmin=100*(mean-SE), xmax=100*(mean+SE)), 
-                width=1.0,size=1)+
-  geom_point(data = motif_means,aes(y = as.factor(motif), x=100*mean), 
-                size=2)+
-  labs(y="Motif", x = "Percentile (%)",colour="Path length classification")+
-  theme_bw() + scale_color_manual(labels = c('Strong' = expression(paste("Complete (", bar(x), " = 1.38)")),'Fan' = expression(paste("Fan (", bar(x), " = 1.48)")), 'Medium-weak' = expression(paste("Asymmetric complete (", bar(x), " = 1.60)")), "Weak" =expression(paste("Core-peripheral (", bar(x), " = 1.85)"))), name = "Path length classification",values = c("grey25","springgreen4","sienna2","goldenrod2"),guide = guide_legend(title.position = "top",nrow = 2)) +
-theme(legend.text.align = 0)+
-  theme(legend.position="bottom")
-
-#Trying to maintain a gradient from low to high in colors
-
-#Fig 1 Should be a dot plot (or forest plot) of the mean +- SE of the 15 motifs.
-#NICE! Can we put motifs in Y axes, and % in X?
-```
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="Figure S4.
-Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions, after removing non-robust links, that is, interactions whose frequency was equal to one.
-The different motif positions are dividied by the average path length clasification by @simmons2020."}
-
-library(lme4)
-library(nlme)
-library(tidyverse)
-library(stringi)
-source("../Scripts/Scripts_Alfonso/add_study_id.R")
-
-#############################################
-# EXTRACT MEAN VALUES
-#############################################
-
-all_position_percentiles <- read_csv("../Data/Csv/Motifs_positions_and_null_models_NOSING/GF_positions_frequency_percentile_NOSING.csv")
-
-all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
-                                                              "[0-9]+") %>% as.numeric()
-
-all_position_percentiles <- add_study_id(all_position_percentiles)
-#str(all_position_percentiles)
-#head(all_position_percentiles)
-
-list_plants_FG <- as.character(1:10)
-
-plant_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF)) #ME DA ERROR
-pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF))
-
-# Plants-------------
-
-# Mean percentile and SE taking into account the study system
-plant_codes <- plant_position_percentiles_filtered$position %>% unique()
-plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-plant_means$mean <- NA
-plant_means$SE <- NA
-
-for(i.pos in 1:length(plant_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
-            data = plant_position_percentiles_filtered %>%
-              filter(position == plant_codes[i.pos]))
-
-  temp <- fixed.effects(m) %>% unname()
-  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
-                                                                    temp[1]+temp[2],
-                                                                    temp[1]+temp[3],
-                                                                    temp[1]+temp[4],
-                                                                    temp[1]+temp[5]) ## to get real means per FG
-  temp <- sqrt(diag(vcov(m)))
-  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
-                                                                  temp[1]+temp[2],
-                                                                  temp[1]+temp[3],
-                                                                  temp[1]+temp[4],
-                                                                  temp[1]+temp[5])
-
-}
-
-# Pollinators--------
-
-# Mean percentile and SE taking into account the study system
-pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
-pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-pollinator_means$mean <- NA
-pollinator_means$SE <- NA
-pollinator_means_reordered <- NULL
-
-for(i.pos in 1:length(pollinator_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = pollinator_position_percentiles_filtered %>%
-              filter(position == pollinator_codes[i.pos]),
-            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
-
-  temp <- fixed.effects(m) %>% unname()
-  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)
-
-  pollinator_means_aux$mean <- c(temp[1],
-                                 temp[1]+temp[2],
-                                 temp[1]+temp[3],
-                                 temp[1]+temp[4],
-                                 temp[1]+temp[5],
-                                 temp[1]+temp[6],
-                                 temp[1]+temp[7],
-                                 temp[1]+temp[8],
-                                 temp[1]+temp[9]) ## to get real means per FG
-
-  temp <- sqrt(diag(vcov(m)))
-  pollinator_means_aux$SE <- c(temp[1],
-                               temp[1]+temp[2],
-                               temp[1]+temp[3],
-                               temp[1]+temp[4],
-                               temp[1]+temp[5],
-                               temp[1]+temp[6],
-                               temp[1]+temp[7],
-                               temp[1]+temp[8],
-                               temp[1]+temp[9])
-
-  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)
-
-}
-
-# There are lower limits (mean - SE) smaller than 0 (see Other insects)
-# We set the lower limit of those error bars to zero
-
-pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
-pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
-
-#############################################
-# ADDING BROAD MOTIF CATEGORIES TO POSITIONS
-#############################################
-
-motifs_raw_data <- read_csv("../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-motifs_raw_data$Broad_categories <- NA
-
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(5,9,14,13,10)] <- "Core-peripherical"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(6,16,12)] <- "Complete"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(2,3,7,4,17,8)] <- "Fan"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(15,11)] <- "Asymmetric complete"
-
-motifs_raw_data$plant <- gsub("[^0-9.-]", "", motifs_raw_data$plant)
-motifs_raw_data$pollinator <- gsub("[^0-9.-]", "", motifs_raw_data$pollinator)
-motifs_raw_data$plant <- as.numeric(motifs_raw_data$plant)
-motifs_raw_data$pollinator <- as.numeric(motifs_raw_data$pollinator)
-motifs_raw_data <- motifs_raw_data %>% filter(!is.na(Broad_categories))
-
-fan_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-pollinator_means_reordered$Broad_categories <- NA
-
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% fan_pollinator] <- "Fan" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% asymm_pollinator] <- "Medium-weak" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% complete_pollinator] <- "Strong" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% core_per_pollinator] <- "Weak"
-
-fan_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-plant_means$Broad_categories <- NA
-
-plant_means$Broad_categories[plant_means$position %in% fan_plant] <- "Fan" 
-plant_means$Broad_categories[plant_means$position %in% asymm_plant] <- "Medium-weak" 
-plant_means$Broad_categories[plant_means$position %in% complete_plant] <- "Strong" 
-plant_means$Broad_categories[plant_means$position %in% core_per_plant] <- "Weak"
-
-########################################
-# CREATE HEATMAPS
-########################################
-
-library(ComplexHeatmap)
-
-# PLANTS-----
-
-# Prepare data for heatmap
-heat_plants_aux <- plant_means %>% spread(Node_FG,mean) %>% select(-SE)
-
-heat_plants <- heat_plants_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-heat_plants_fan <- heat_plants %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_fan) <- heat_plants_fan[,1]
-
-heat_plants_Weak <- heat_plants %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Weak) <- heat_plants_Weak[,1]
-
-heat_plants_Strong <- heat_plants %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Strong) <- heat_plants_Strong[,1]
-
-heat_plants_Medium_weak <- heat_plants %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Medium_weak) <- heat_plants_Medium_weak[,1]
-
-# POLLINATORS-----------
-
-filter_rare_groups <- T
-
-if(filter_rare_groups == T){
-  heat_pollinators_aux <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds",
-                                                                                "Lizards",
-                                                                                "Other_insects")) %>% 
-    spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bee",            
-                                      "Coleoptera","Lepidoptera","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\ndiptera","Syrphids")
-}else{
-  heat_pollinators_aux <- pollinator_means_reordered %>% spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bee","Birds",            
-                                      "Coleoptera","Lepidoptera","Lizards","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\ndiptera","Other insects","Syrphids")
-}
-
-heat_pollinators <- heat_pollinators_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-heat_pollinators_fan <- heat_pollinators %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_fan) <- heat_pollinators_fan[,1]
-
-heat_pollinators_Weak <- heat_pollinators %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Weak) <- heat_pollinators_Weak[,1]
-
-heat_pollinators_Strong <- heat_pollinators %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Strong) <- heat_pollinators_Strong[,1]
-
-heat_pollinators_Medium_weak <- heat_pollinators %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Medium_weak) <- heat_pollinators_Medium_weak[,1]
-
-##################
-
-#Do not know how to handle this multiplot for creating a panel
-
-# I'm going to create the 4 plots in one, 
-# I'm not sure that the grouping of the functional group is correct
-# when is done separately
-
-#sorry for the mess of libraries that I do below
-
- #Prepare first pollinators
-
-library(tidyr)
-library(data.table)
-long <- melt(setDT(heat_pollinators), id.vars = c("position","Broad_categories"), variable.name = "guilds")
-
-long_1 <- long %>% select(-Broad_categories)
-
-library(reshape2)
-long_m <- acast(long_1, position~guilds, value.var="value")
-
-#set manually the divisions, so far this is the best way I have seen to split the rows by categories
-
-r_split <- c(rep(c("Fan"), 3),rep(c("Core-peripheral"), 2),"Complete",rep(c("Fan"),2),rep(c("Core-peripheral"), 4),
-             rep(c("Asymmetric complete"), 2), "Complete", rep(c("Core-peripheral"), 3),rep(c("Asymmetric complete"), 2),
-             "Complete", "Fan")
-
-#set order of labels that avoids overlapping
-r_split <- factor(r_split, levels=c("Core-peripheral","Complete","Fan","Asymmetric complete"))
-
-#plat a bit with colors, a bit of a more complex set but looks nicer
-library(circlize)
-col_fun = colorRamp2(c(0.05644663,0.25, 0.4673256,0.75, 0.8782047), c("blue","cadetblue3", "azure2", "gold","red"))
-
-h_pol <- Heatmap(long_m, name = "Mean\npercentile", row_split=r_split,cluster_row_slices = FALSE, 
-        column_title = "Pollinator functional\ Groups",row_names_gp = gpar(fontsize = 12),col = col_fun)
-
- #Prepare plants
-
-#long format
-long_plants <- melt(setDT(heat_plants), id.vars = c("position","Broad_categories"), variable.name = "Functional_groups")
-
-#filter for creating matrix
-long_plants_1 <- long_plants %>% select(-Broad_categories)
-
-#set better colnames
-long_plants_1$Functional_groups <- as.character(long_plants_1$Functional_groups)
-
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==1] <- "Cluster 1" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==2] <- "Cluster 2" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==3] <- "Cluster 3" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==4] <- "Cluster 4" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==5] <- "Cluster 5"
-
-long_plants_1$Functional_groups <- factor(long_plants_1$Functional_groups, levels=c("Cluster 1",
-"Cluster 2" ,"Cluster 3","Cluster 4" ,"Cluster 5" ))
-
-#create matrix with reshape
-long_plants_m <- acast(long_plants_1, position~Functional_groups, value.var="value")
-
-r_split_plants <- c(rep(c("Fan"), 3),rep(c("Core-peripheral"), 2),"Complete",rep(c("Fan"),2),rep(c("Core-peripheral"), 3),
-             rep(c("Asymmetric complete"), 2), "Complete", rep(c("Core-peripheral"), 4),rep(c("Asymmetric complete"), 2),
-             "Complete", "Fan")
-
-r_split_plants <- factor(r_split, levels=c("Core-peripheral","Complete","Fan","Asymmetric complete"))
-
-h_plan <- Heatmap(long_plants_m, name = "Mean\npercentile", row_split=r_split_plants,cluster_row_slices = FALSE, 
-        column_title = "Plant functional\ Groups",row_names_gp = gpar(fontsize = 12),col = col_fun)
-
-library(patchwork)
-h_pol+h_plan
-
-```

### 2021-06-16 Draft/Draft.Rmd
First full description of funtional goups with their respecting names added

@@
 However, it is unclear if species ecological and life history traits strongly determines its role within the network of interactions [@coux2016].
-For example, bees are more specialized foragers [Jose, aquí por ejemplo, pueden decir que abejas pequeñas y generalistas, pueden comportarse muy diferente que grandes y especialistas...
-si tienes una lista de pollintors, con su familia, pasamela, y le hecho un ojo](), usually alble to open complex zygomorphic flowers which are not accessible to fly pollinators.
-How this different behaviors translate into their interaction topology is unknown.
+For example, large pollinators can forage larger distances [@greenleaf2007], deposit greater pollen quantities [@foldesi2021] and handle complex zygomorphic flowers in comparison with small pollinators that are restricted to lower floral complexity [@gong2009].
+How this different pollinator behaviors translate into their interaction topology is unknown.
 Similarly, recent empirical findings indicate that the meso-scale is the best descriptor of plant reproductive success [@allen2021], but little is known on how plants reproductive strategies shape their position within the network of interactions.
@@
 ##METHODS
-
-cite complexheatmap https://doi.org/10.1093/bioinformatics/btw313
 
@@
 To fit the LMMs models in our analyses, we used the ‘lmer’ package [@bates2015].
+Finally, we visualized with the help of the package ComplexHeatmap version 2.6.2 [@gu2016] over- and under- representation of plant and pollinator functional groups on the different motif positions.
 
@@
 
-The hierarchical cluster analysis divided the dataset with 1506 species and 15 traits into five different clusters with different and overlapping characteristics (Figure S1).
-The subset of plant species used in this study (N = 503) were distributed evenly across these different larger five groups (see Figure S1).
-The first cluster "short-lived selfers"
-
-The first and largest cluster, Cluster A, was constituted by 710 species.
-The species of this cluster had the shortest plant heights (Median = 0.5m, Mean = 0.84m), were mostly herbs (89.58%) with short lived life span (68.23%) and the lowest number of flowers per plant (Median = 30, Mean = 197.15); the flowers were mostly hermaphrodite (97.40%) with actinomorphic symmetry (99.48%), the morphology was variant but the predominant shapes were ‘open’ (51.56%) and ‘capitulum’ (23.44%); most of the species were self compatible (96.35%) and had the higher levels of autonomous selfing of all clusters from low-medium selfing (47.92%) to high selfing (52.08%) with nectar production for 83.85% of the species.
-Cluster B, had 588 species and was the the second in plant height (Median = 0.8m, Mean = 1.98m), number of flowers per plant (Median = 75; Mean = 1559) and flowers per inflorescence (Median = 15; Mean = 58), it had diverse life forms (herbs 52.89%, shrubs 34.52% and trees 12.59%) and the species were mostly perennial (97.96%); the flowers were the second largest (flower length Median = 10mm, Mean = 10.08mm; flower width Median = 5.10mm, Mean = 16.88mm) and it had mostly hermaphroditic breeding system (95.41%), actinomorphic symmetry (99.15%) and a predominant flower morphology of ‘open’ (50.17%) and ‘tube’ shapes (20.07); the majority of species were self compatible (70.24%) and partially self compatible (20.24%) and had low selfing levels (88.95%) with nectar production for 78.40%.
-Cluster C was constituted by 323 species, had similar plant heights to cluster B (Median = 0.75, Mean = 1.85) with also diverse life forms (61.61% herbs, 28.79% shrubs, 9.60% trees) with mostly perennial species (95.36%) with the largest flower size (flower length Median =9.10mm , Mean =13.95mm; flower width Median =15mm, Mean =20.18mm) and number of ovules per flower of all clusters (Median = 30, Mean  = 527.87); flowers were mostly hermaphroditic (97.83%) with actinomorphic flowers (78.95%) and predominant ‘open’ (28.48%) ‘capitulum’ (27.55%) and ‘tube’ (26.01%) flower morphology; this was the cluster with greater proportion of self incompatible species (76.47%) and it had negligible autonomous selfing level (Median = 0,  Mean = 0.30) with the highest proportion of nectar secreting species (92.26%).
-Cluster D had 164 species, they were the tallest plants (Median =2.88m, Mean =5.19m) and had the largest proportion of shrubs (41.46%) and trees (31.71%) of all clusters, the species were mainly perennial (92.07%) and differentiated from the rest of the clusters by having principally dioecious (63.41%) and monoecious (35.98%) breeding system; this cluster had the largest number of flower per plant (Median = 1000, Mean = 6803) and per inflorescence (Median = 30 , Mean = 258) but the smaller flower size of all clusters (flower length Median =2.71, Mean =6.53; flower width Median = 3.62; Mean = 8.23) with ‘open’ (53.66%) and ‘brush’ (21.34%) morphology as the most representative flower shapes of this group; in addition, this cluster had the shortest styles (Median = 1mm; Mean = 3.05mm) and lower number of ovules (Median = 4.50, Mean = 110.47) along with cluster A; thus, the flowers were unisexual (98.78%), actinomorphic (95.12%), had no selfing (98.17%) and had the lowest proportion of nectar secreting species (69.51%) of all clusters.
-Finally, 239 species integrated Cluster E which had the second shortest species of all clusters (Median = 0.55m; Mean = 1.23m), the species were mainly herbs (83.26%) and perennial (70.29%) but also had a representative proportion of short lived species (29.71%); this cluster was the only one with mainly zygomorphic flowers (97.07%) with tubular (55.65%) and papilionaceous (24.69%) flower shapes, the species had mostly hermaphroditic breeding system (96.65%) and the flowers had the longest styles of all clusters (Median = 5mm; Mean = 8.74mm); species were mostly self compatible (88.28%) and nectar secreting (88.28%) with low autonomous selfing levels (61.92%) but also had species with high (18.41%) medium (15.06%) and lack of autonomous selfing (4.60%).
-
-Figure S1
+The hierarchical cluster analysis divided the dataset with 1506 species and 15 traits into five different clusters with different and overlapping characteristics (Figure S1 and Figure S2).
+The subset of plant species used in this study (N = 503) were distributed evenly across these different larger five groups (see subset of species labels within cluster in Figure S1).
+The first cluster was dominated by herbs with hermaphrodite flowers with high levels of autonomous selfing and we we refer to this group as "selfing herbs".
+The second cluster was characterized by small perennial species with a mixed of life forms (trees shrubs and herbs) with outcrossing hermaphroditic flowers and we refer to this group of species as "small outcrossing perennials".
+The third cluster was dominated by also perennial species with a mixed of life forms too and had large self-incompatible hermaphroditic flowers with high number of ovules and we named this group "self-incompatible perennials with large flowers".
+The fourth cluster had the tallest species, highest proportion of shrub and tree life forms, dioecious and monoecious breeding system with small flowers but the highest number of flowers per plant and inflorescence and we refer to this set of species as "tall plants with small unisexual flowers".
+Finally, the last cluster of species was dominated by small perennial and shot-lived herbs with long self-compatible zygomorphic flowers unable to self-pollinate and we refer to this group as "short-lived outcrossers with long zygomorphic flowers".
 
@@
 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==1] <- "Short-lived selfers" 
+long_plants_1$Functional_groups[long_plants_1$Functional_groups==1] <- "Selfing herbs" 
 long_plants_1$Functional_groups[long_plants_1$Functional_groups==2] <- "Small outcrossing\nperennials" 
@@
 
-long_plants_1$Functional_groups <- factor(long_plants_1$Functional_groups, levels=c("Short-lived selfers",
+long_plants_1$Functional_groups <- factor(long_plants_1$Functional_groups, levels=c("Selfing herbs",
 "Small outcrossing\nperennials" ,"Self-incomp. perennials\nwith large flowers",

### 2021-06-16 Scripts/Scripts_Funtional_Groups/Playing_with_Correspondence_Analysis.R

@@ -1,0 +1,60 @@
+
+
+
+library("FactoMineR")
+library("factoextra")
+
+data(housetasks)
+
+dt <- as.table(as.matrix(housetasks))
+
+chisq <- chisq.test(housetasks)
+
+
+res.ca <- CA(housetasks, graph = FALSE)
+
+fviz_ca_biplot(res.ca, repel = TRUE)
+
+
+fviz_ca_biplot(res.ca, 
+               map ="rowprincipal", arrow = c(TRUE, TRUE),
+               repel = TRUE)
+
+
+
+######READ NOW MY DATA######
+library(tidyverse)
+library(igraph)
+library(bmotif)
+networks <- read_csv("Data/Csv/data_for_motifs_analysis_1.csv") %>% select(-X1) %>%
+  filter(Interaction >= int.threshold)
+
+str(networks)
+
+
+d = networks %>% select(Pollinator_functional_group,Plant_functional_groups)
+
+library(reshape2)
+
+d_tab <- dcast(data=d,
+      Pollinator_functional_group ~ Plant_functional_groups,
+      fun.aggregate = length,
+      value.var = "Plant_functional_groups")
+
+rownames(d_tab) <- d_tab$Pollinator_functional_group
+
+d_tab = d_tab %>% select(-Pollinator_functional_group)
+
+d_mat <- as.table(as.matrix(d_tab))
+
+chisq <- chisq.test(d_mat)
+
+res.ca <- CA(d_mat, graph = FALSE)
+
+fviz_ca_biplot(res.ca, 
+               map ="rowprincipal", arrow = c(TRUE, TRUE),
+               repel = TRUE)
+fviz_ca_biplot(res.ca, map ="colgreen", arrow = c(TRUE, FALSE),
+               repel = TRUE)
+
+fviz_ca_biplot(res.ca, repel = TRUE)

### 2021-06-16 Draft/Draft.Rmd
Edits on functional groups pie charts

@@
 The interaction between plants and pollinators can be studied at different scales, from species level interactions (micro-scale) to the full network structure (macro-scale).
-Research of the network structure have proven common invariant structural properties across them including a degree distribution that decays as a power law [@jordano1987], nestedness [@bascompte2003], or the higher number of pollinator species than plant species [@bluthgen2007].
+Research of the plant-pollinator network structure have proven common invariant structural properties across them including a degree distribution that decays as a power law [@jordano1987], nestedness [@bascompte2003], or the higher number of pollinator species than plant species [@bluthgen2007].
 In addition, species phenological overlap, morphological matching and species abundances have been shown to be determinant for the understanding of pairwise plant-pollinator interactions [@bartomeus2016; @stang2006; @peralta2020].

### 2021-06-16 Scripts/Scripts_Alfonso/5_piecharts_absolute_frequencies.R

@@ -326,23 +326,27 @@ plot_pie_motif_positions <- function(motif_number){
   
   # Define the number of colors you want
   nb.cols <- 5
-  mycolors <- c(brewer.pal(5, "Dark2"),brewer.pal(9, "Paired"))
+  mycolors <- c(brewer.pal(9, "Paired"),brewer.pal(5, "Dark2"))
   
   ggplot() +
     scale_shape_identity() +
     geom_segment(data = link_df, aes(x=xdown, y=ydown, xend = xup, yend = yup), 
-                 size = 1, color = "grey20")+
+                 size = 1, color = "grey20")+  geom_scatterpie(aes(x=x, y=y, group=position,r=.3), 
+    data = d_nodes_pollinator, cols=as.character(c("Bee","Birds","Coleoptera","Lepidoptera",
+     "Lizards","Non-bee-Hymenoptera", "Non-syrphids-diptera","Other_insects",
+     "Syrphids"))) +
     geom_scatterpie(aes(x=x, y=y, group=position,r=0.3), 
                     data = d_nodes_plant,
                     cols=as.character(c("1","2","3","4","5")))+
-    geom_scatterpie(aes(x=x, y=y, group=position,r=.3), 
-                    data = d_nodes_pollinator,
-                    cols=as.character(c("Bee","Birds","Coleoptera","Lepidoptera",
-                                        "Lizards","Non-bee-Hymenoptera",
-                                        "Non-syrphids-diptera","Other_insects",
-                                        "Syrphids")))+
-    coord_equal()+
-    scale_fill_manual(values = mycolors)+
+    coord_fixed()+
+    scale_fill_manual(values = mycolors,"test",
+      breaks=c("Bee","Birds","Coleoptera","Lepidoptera",
+               "Lizards","Non-bee-Hymenoptera", "Non-syrphids-diptera","Other_insects",
+               "Syrphids","1","2","3","4","5"), labels=c("Bee","Birds","Coleoptera","Lepidoptera",
+                                                        "Lizards","Non-bee-Hymenoptera", "Non-syrphids-diptera","Other_insects",
+                                                        "Syrphids", 
+          "Selfing herbs","Small outcrossing perennials","Self-incomp. perennials\nwith large flowers",
[…]

### 2021-07-20 Draft/Draft.Rmd
Edits on the first 2 paragraphs

--- 2021-06-16 Draft/Draft.Rmd
@@
   blocks
-output:
-  html_document: default
-  pdf_document: default
 editor_options:
   chunk_output_type: console
-bibliography: bibliography.bib
 header-includes:
@@
 - \usepackage{xcolor}
+output:
+  html_document: default
+  pdf_document: default
+  word_document: default
+always_allow_html: true
+bibliography: bibliography.bib
 ---
@@
 motifs) and those constitute the building blocks of the whole network.
-Here we have compiled 60 networks from 18 different studies and show that some motifs are consitently over-represented worldwide, suggesting that the building blocks of plant-pollintor networks are not random and are associated to ...
+Here, we have compiled 60 networks from 18 different studies and show that some motifs are consitently over-represented worldwide, suggesting that the building blocks of plant-pollintor networks are not random and are associated to ...
 Second, we show that the position of pollinator guilds and plant reproductive strategies is not random with respect to the positions occupied within each motif.
@@
 The interaction between plants and pollinators can be studied at different scales, from species level interactions (micro-scale) to the full network structure (macro-scale).
-Research of the network structure have proven common invariant structural properties across them including a degree distribution that decays as a power law [@jordano1987], nestedness [@bascompte2003], or the higher number of pollinator species than plant species [@bluthgen2007].
+Research of the plant-pollinator network structure have proven common invariant structural properties across them including a degree distribution that decays as a power law [@jordano1987], nestedness [@bascompte2003], or modularity in large networks [@olesen2007].
 In addition, species phenological overlap, morphological matching and species abundances have been shown to be determinant for the understanding of pairwise plant-pollinator interactions [@bartomeus2016; @stang2006; @peralta2020].
-However, both species level information or an holistic view of the full network involves missing relevant information for the understanding of ecological processes [@simmons2019].
-
-Indirect interactions (i.e., motifs), commonly referred as the building blocks that depict subsets of interactions of the network [@milo2002], are a widespread phenomenon in ecological communities [@strauss1991].
-For instance, plant species can facilitate or compete for pollinator's visitation when two species are visited by the same pollinator [@ghazoul2006].
-Despite the relevance of indirect interactions in ecological communities, plant-pollinator research often fails to finely capture those indirect interactions with the traditional analytical tools that condense the information either by species (e.g.
+However, both species level information and the holistic view of the full network involves missing relevant information for the understanding of ecological processes [@cirtwill2018; @simmons2019].
+
+Traditionally, plant-pollinator research has focused on direct interactions and overlooked indirect interactions such as facilitative or competitive interactions between plants for pollinators [@moeller2004; @sargent2008].
+Despite the widespread nature of indirect interactions in ecological communities [@strauss1991], plant-pollinator research often fails to finely capture those indirect interactions with the traditional analytical tools that condense the information either by species (e.g.
 interaction frequency) or in single topological indices (e.g.
@@
 Nonetheless, the emerging framework of network motifs in plant-pollinator research allows to consider both direct and indirect interactions [@simmons2019].
-The study of @simmons2020 have shown that the different processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions.
-However, we still ignore which are the general patterns observed in the distribution of plant-pollinator motifs worldwide.
+Motifs are commonly referred to as the building blocks of a network that depict subsets of interactions or subnetworks [@milo2002].
+Motif analysis in plant-pollinator networks (meso-scale) have shown that the different ecological processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions [@simmons2020].
+Despite this recent progress in the understanding of ecological processes that shape indirect interactions in plant-pollinator networks, global patterns of indirect interactions (over- and under- representation of motifs) are still unknown.
 

### 2021-07-21 Draft/Draft.Rmd
edits on the intro

@@
 nestedness).
-Nonetheless, the emerging framework of network motifs in plant-pollinator research allows to consider both direct and indirect interactions [@simmons2019].
-Motifs are commonly referred to as the building blocks of a network that depict subsets of interactions or subnetworks [@milo2002].
-Motif analysis in plant-pollinator networks (meso-scale) have shown that the different ecological processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions [@simmons2020].
-Despite this recent progress in the understanding of ecological processes that shape indirect interactions in plant-pollinator networks, global patterns of indirect interactions (over- and under- representation of motifs) are still unknown.
+Nonetheless, the emerging framework of network motifs in plant-pollinator research, the building blocks of a network that depict subsets of interactions [@milo2002], allows to consider both direct and indirect interactions [@simmons2019].
+The analysis of the meso-scale in plant-pollinator networks have revealed that the different ecological processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions [@simmons2020].
+However, the global patterns of indirect interactions in plant-pollinator networks (over- and under- representation of motifs) are still unknown.
 

### 2021-07-26 Draft/Draft.Rmd
Minor edits on intro and table s1

@@
 Traditionally, plant-pollinator research has focused on direct interactions and overlooked indirect interactions such as facilitative or competitive interactions between plants for pollinators [@moeller2004; @sargent2008].
-Despite the widespread nature of indirect interactions in ecological communities [@strauss1991], plant-pollinator research often fails to finely capture those indirect interactions with the traditional analytical tools that condense the information either by species (e.g.
+Despite the widespread nature of indirect interactions in ecological communities [@strauss1991], plant-pollinator research often fails to finely capture those indirect interactions with the conventional analytical tools that condense the information either by species (e.g.
 interaction frequency) or in single topological indices (e.g.
@@
 Nonetheless, the emerging framework of network motifs in plant-pollinator research, the building blocks of a network that depict subsets of interactions [@milo2002], allows to consider both direct and indirect interactions [@simmons2019].
-The analysis of the meso-scale in plant-pollinator networks have revealed that the different ecological processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions [@simmons2020].
+The analysis of motifs (meso-scale) in plant-pollinator networks have revealed that the different ecological processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions [@simmons2020].
 However, the global patterns of indirect interactions in plant-pollinator networks (over- and under- representation of motifs) are still unknown.
@@
 For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species functional role [@stouffer2012; @baker2015].
-However, it is unclear if species ecological and life history traits strongly determines its role within the network of interactions [@coux2016].
+However, it is unclear how the species ecology and life history traits determines the species functional role within the network of interactions [@coux2016].
 For example, large pollinators can forage larger distances [@greenleaf2007], deposit greater pollen quantities [@foldesi2021] and handle complex zygomorphic flowers in comparison with small pollinators that are restricted to lower floral complexity [@gong2009].
@@
 #vector with number of netw per study
-`Number of networks` <- c("6", "2", "3", "1", "1", "1", "1", "2", "1", "1", "8", "16", "6", "2", "4", "1", "3", "1")
-
-#`Network structure` <- c(rep("Web", 22), rep("Metaweb",6))
-
-`First author` <- c("Bartomeus", "Dicks", "Dupont", "Elberling", "Fang", "Inouye", "Lundgren", "Olesen", "Small", "Souza", "Kaiser-Bunbury", "Bartomeus", 
-                    "Kaiser-Bunbury", "Kaiser-Bunbury", "Peralta", "Burkle", "Arroyo-Correa", "Bundgaard")
-
-Year <- c(2008,2002,2003,1999,2008,1988, 2005,2002,1976,2017,2017,2008,2011,2010,2006,2013,2019,2003) ###JOSE! This method is prone to error, My Beefun dataset is 2015 and not 2008. ###
-
-#Country <- c("Spain", "England", "Denmark", "Sweden", "China", "Australia", "Greenland", "Mauritius and Azores", #"Canada", "Brasil", "Seychelles", "Spain", "Seychelles",
-#"Mauritius", "Argentina", "USA", "New Zealand", "Denmark",  "Denmark", "Japan", "Canada", "Venezuela", "Japan", #"Ecuador", "New Zealand", "Venezuela",
-#"USA", "Ecuador")
-
-DOI <- c("https://doi.org/10.1007/s00442-007-0946-1", "https://doi.org/10.1046/j.0021-8790.2001.00572.x", "https://doi.org/10.1111/j.1365-2656.2008.01501.x",
-         "https://doi.org/10.1111/j.1600-0587.1999.tb00507.x", "https://doi.org/10.1111/1749-4877.12190", "https://doi.org/10.1111/j.1442-9993.1988.tb00968.x",
-         "https://doi.org/10.1657/1523-0430(2005)037[0514:TDAHCW]2.0.CO;2", "https://doi.org/10.1046/j.1472-4642.2002.00148.x",
-         "/13960/t4km08d21", "https://doi.org/10.1111/1365-2745.12978", "https://doi.org/10.1038/nature21071", "https://github.com/ibartomeus/BeeFunData",
-         "https://doi.org/10.1111/j.1365-2745.2010.01732.x", "https://doi.org/10.1016/j.ppees.2009.04.001", "https://doi.org/10.1111/ele.13510",
-         "https://doi.org/10.1126/science.1232728", "https://doi.org/10.1111/1365-2745.13332", "Unpublished, Master thesis")
-
-references <- data.frame(`First author`, Year, `Number of networks`,   DOI)
-
-colnames(references) <- c("First author", "Year", "Number of networks",  "DOI")
+`Number of networks` <- c("6", #1
+                          "2", #2
+                          "3",#3
+                          "1",#4
+                          "1",#5
+                          "1",#6
+                          "1",#7
+                          "2",#8
+                          "1",#9
+                          "1",#10
+                          "8",#11
+                          "16",#12
+                          "6",#13
+                          "2",#14
+                          "4",#15
+                          "1",#16
+                          "3",#17
+                          "1"#18
+                          )
+
+`First author` <- c("Bartomeus", #1
+                    "Dicks",#2
+                    "Dupont",#3
+                    "Elberling",#4
+                    "Fang",#5
+                    "Inouye",#6
+                    "Lundgren",#7
+                    "Olesen",#8
+                    "Small",#9
+                    "Souza",#10
+                    "Kaiser-Bunbury",#11
+                    "Bartomeus",#12
+                    "Kaiser-Bunbury",#13
+                    "Kaiser-Bunbury",#14
+                    "Peralta",#15
+                    "Burkle",#16
+                    "Arroyo-Correa",#17
+                    "Bundgaard"#18
+                    )
+
+Year <- c(2008,#1
+          2002,#2
+          2003,#3
+          1999,#4
+          2008,#5
+          1988,#6
+          2005,#7
+          2002,#8
+          1976,#9
+          2017,#10
+          2017,#11
+          2015,#12
+          2011,#13
+          2010,#14
+          2006,#15
+          2013,#16
+          2019,#17
+          2003#18
+          )
+
+Country <- c("Spain", #1
+               "England", #2
+               "Denmark", #3
+               "Sweden", #4
+               "China", #5
+               "United States", #6
+               "Denmark (Greenland)", #7
+               "Mauritius and Portugal (Azores)", #8
+               "Japan", #9
+               "Brazil", #10
+               "Seychelles", #11
+               "Spain", #12
+               "Seychelles", #13
+               "Mauritius", #14
+               "Argentina", # 15
+               "United States", #16
+               "New Zealand", #17
+               "Denmark" #18
+               )
+
+DOI <- c("https://doi.org/10.1007/s00442-007-0946-1", #1
+         "https://doi.org/10.1046/j.0021-8790.2001.00572.x", #2
+         "https://doi.org/10.1111/j.1365-2656.2008.01501.x", #3
+         "https://doi.org/10.1111/j.1600-0587.1999.tb00507.x", #4
+         "https://doi.org/10.1111/1749-4877.12190", #5
+         "https://doi.org/10.1111/j.1442-9993.1988.tb00968.x", #6
+         "https://doi.org/10.1657/1523-0430(2005)037[0514:TDAHCW]2.0.CO;2", #7
+         "https://doi.org/10.1046/j.1472-4642.2002.00148.x", #8
+         "/13960/t4km08d21", #9
+         "https://doi.org/10.1111/1365-2745.12978", #10
+         "https://doi.org/10.1038/nature21071", #11
+         "https://github.com/ibartomeus/BeeFunData", #12
+         "https://doi.org/10.1111/j.1365-2745.2010.01732.x", #13
+         "https://doi.org/10.1016/j.ppees.2009.04.001", #14
+         "https://doi.org/10.1111/ele.13510", #15
+         "https://doi.org/10.1126/science.1232728", #16
+         "https://doi.org/10.1111/1365-2745.13332", #17
+         "Unpublished, Master thesis" #18
+         )
+
+references <- data.frame(`First author`, Year, `Number of networks`, Country,   DOI)
+
+colnames(references) <- c("First author", "Year", "Number of networks", "Country",  "DOI")
 

### 2021-07-26 Scripts/Scripts_Alfonso/9_observed_VS_expected_probabilities_SIMULATION.R
z-score for observed probabilities

@@ -41,6 +41,8 @@ write_csv(samples_random_probability,"Data/Csv/motifs_samples_random_probability
 # EXTRACT CIs FROM SIMULATED PROBABILITIES
 #################################################
 
+samples_random_probability <- read_csv("Data/Csv/motifs_samples_random_probability_SIMU.csv")
+
 # Variable to storage CI 95%
 motifs_observed_probability_CI <- motifs_probability
 motifs_observed_probability_CI$round_motif_observed_probability <- 
@@ -48,6 +50,9 @@ motifs_observed_probability_CI$round_motif_observed_probability <-
 motifs_observed_probability_CI$percentil_observed <- NA
 motifs_observed_probability_CI$lower_CI <- NA
 motifs_observed_probability_CI$upper_CI <- NA
+motifs_observed_probability_CI$mean_sim <- NA
+motifs_observed_probability_CI$sd_sim <- NA
+motifs_observed_probability_CI$z_score <- NA
 
 motifs_ID_list <- motifs_probability$motif_functional_ID
 
@@ -58,6 +63,12 @@ for(i.motif in 1:length(motifs_ID_list)){
   random_samples_motif <- samples_random_probability %>% ungroup() %>%
     filter(motif_functional_ID == motifs_ID_list[i.motif]) %>% 
     dplyr::select(random_probability) %>% pull()
+  
+  motifs_observed_probability_CI$mean_sim[i.motif] <- mean(random_samples_motif)
+  motifs_observed_probability_CI$sd_sim[i.motif] <- sd(random_samples_motif)
+  motifs_observed_probability_CI$z_score[i.motif] <- 
+    (motifs_observed_probability_CI$round_motif_observed_probability[i.motif]-
+       motifs_observed_probability_CI$mean_sim[i.motif])/motifs_observed_probability_CI$sd_sim[i.motif]
   
   if(length(random_samples_motif) < simulations){
     
@@ -77,8 +88,14 @@ for(i.motif in 1:length(motifs_ID_list)){
 
 write_csv(motifs_observed_probability_CI,"Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
 
+# percentage of entries with sd = 0
+motifs_observed_probability_CI %>% filter(sd_sim == 0) %>% nrow()*100/nrow(motifs_observed_probability_CI)
+
 underrepresented_motifs <-  motifs_observed_probability_CI %>% filter(round_motif_observed_probability<lower_CI)
[…]

### 2021-07-26 Draft/Draft.Rmd

@@
 
-Here, we used 60 plant-pollinator networks from 18 different studies distributed worldwide, alongside a detailed grouping of plants into reproductive strategies and pollinator species into functional groups.
+Here, we used 60 plant-pollinator networks from 18 different studies and 14 countries, alongside a detailed grouping of plants into reproductive strategies and pollinator species into functional groups.
 Plants were grouped based on a comprehensive dataset that included floral, reproductive and vegetative traits compiled in Lanuza et al., (unpublished) on a larger set of plant-pollinator networks.

### 2021-07-26 Scripts/Z-score_percentile_histogram_plot.R
on the way ti hist plot for z-scores and percentiles

@@ -1,0 +1,36 @@
+
+#load library
+library(dplyr)
+library(ggplot2)
+#Read data
+data <- read.csv("Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
+
+#Check NA's per column
+data %>%
+  summarise_all(funs(sum(is.na(.))))
+
+# At the moment this is just -2 and 2 but check how to find critical value of z-score
+data_1 <- data %>%
+  mutate(infra_over_represented = case_when(
+    z_score < -2 ~ "infra",
+    between(z_score, -2, 2) ~ "no_diff",
+    z_score > 2 ~ "over"
+  ))
+     
+#check levels
+levels(factor(data_1$infra_over_represented))
+
+#Check proportion of infra/over and no statistical difference
+data_1 %>% 
+  group_by(infra_over_represented) %>%
+  summarise(no_rows = length(infra_over_represented)) %>%
+  mutate(proportion = no_rows / sum(no_rows))
+
+data_2 <- filter(data_1, z_score<3000) 
+
+#Plot histogram of Z-scores
+ggplot(data_2, aes(x=z_score)) + 
+  geom_histogram(color="black", fill="white")
+
+
+

### 2021-07-27 Scripts/Z-score_percentile_histogram_plot.R
Update Z-score_percentile_histogram_plot.R

@@ -30,7 +30,42 @@ data_2 <- filter(data_1, z_score<3000)
 
 #Plot histogram of Z-scores
 ggplot(data_2, aes(x=z_score)) + 
-  geom_histogram(color="black", fill="white")
+  geom_histogram(color="black", fill="white",bins = 28)+
+  geom_vline(xintercept = -2)+
+  geom_vline(xintercept = 2)+
+  xlim(-50,50)
 
 
+###############
+# PERCENTILES
+###############
 
+data_perc <- as.tibble(data)
+
+# There are 827 motifs with upper and lower CI equal to zero
+data_perc %>% filter(lower_CI == upper_CI)
+data_perc %>% filter(lower_CI == upper_CI, lower_CI>0)
+
+data_perc$infra_over_represented <- "no_diff"
+data_perc$infra_over_represented[data_perc$round_motif_observed_probability<data_perc$lower_CI] <- "infra"
+data_perc$infra_over_represented[data_perc$round_motif_observed_probability>data_perc$upper_CI] <- "over"
+
+# There are 19514 motifs whose observed probability (0) is expected and equal to the lower bound (0)
+data_perc %>% filter(percentil_observed == 0, infra_over_represented == "no_diff")
+
+min(data_perc$percentil_observed[data_perc$infra_over_represented=="infra"])
+max(data_perc$percentil_observed[data_perc$infra_over_represented=="infra"])
+
+min(data_perc$percentil_observed[data_perc$infra_over_represented=="over"])
+max(data_perc$percentil_observed[data_perc$infra_over_represented=="over"])
+
+min(data_perc$percentil_observed[data_perc$infra_over_represented=="no_diff"])
+max(data_perc$percentil_observed[data_perc$infra_over_represented=="no_diff"])
+
+data_perc %>% group_by(infra_over_represented) %>% count()
+
+#Plot histogram of percentil
+ggplot(data, aes(x=percentil_observed)) + 
+  geom_histogram(color="black", fill="white",bins = 100)+
+  geom_vline(xintercept = 0.025)+
+  geom_vline(xintercept = 0.975)

### 2021-07-27 Scripts/Scripts_Alfonso/9_observed_VS_expected_probabilities_SIMULATION.R
Update 9_observed_VS_expected_probabilities_SIMULATION.R

@@ -88,6 +88,8 @@ for(i.motif in 1:length(motifs_ID_list)){
 
 write_csv(motifs_observed_probability_CI,"Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
 
+motifs_observed_probability_CI <- read_csv("Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
+
 # percentage of entries with sd = 0
 motifs_observed_probability_CI %>% filter(sd_sim == 0) %>% nrow()*100/nrow(motifs_observed_probability_CI)
 

### 2021-07-27 Scripts/Z-score_percentile_histogram_plot.R
Edit on histogram, thanks Alfonso for helping with it!

@@ -2,6 +2,7 @@
 #load library
 library(dplyr)
 library(ggplot2)
+library(tidyverse)
 #Read data
 data <- read.csv("Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
 
@@ -27,13 +28,17 @@ data_1 %>%
   mutate(proportion = no_rows / sum(no_rows))
 
 data_2 <- filter(data_1, z_score<3000) 
-
+str(data_2)
 #Plot histogram of Z-scores
-ggplot(data_2, aes(x=z_score)) + 
-  geom_histogram(color="black", fill="white",bins = 28)+
+ggplot(data_2, aes(x=z_score, color=infra_over_represented, fill=infra_over_represented)) + 
+  geom_histogram(bins = 50, alpha = 0.5, position = "identity",lwd = 0.25)+
   geom_vline(xintercept = -2)+
   geom_vline(xintercept = 2)+
-  xlim(-50,50)
+  xlim(-20,20) + ylab("Frequency")+  theme_bw() +
+  scale_fill_manual(name="Motif frequencies" ,values=c("coral2", "palegreen3", "cyan3"), labels=c("Under-represented",
+                    "No statistical difference", "Over-represented")) +
+  scale_color_manual(name="Motif frequencies" ,values=c("coral2", "palegreen3", "cyan3"), labels=c("Under-represented",
+                     "No statistical difference", "Over-represented"))
 
 
 ###############
@@ -69,3 +74,5 @@ ggplot(data, aes(x=percentil_observed)) +
   geom_histogram(color="black", fill="white",bins = 100)+
   geom_vline(xintercept = 0.025)+
   geom_vline(xintercept = 0.975)
+
+str(data)

### 2021-07-27 Scripts/Z-score_percentile_histogram_plot.R
Update Z-score_percentile_histogram_plot.R

@@ -27,11 +27,11 @@ data_1 %>%
   summarise(no_rows = length(infra_over_represented)) %>%
   mutate(proportion = no_rows / sum(no_rows))
 
-data_2 <- filter(data_1, z_score<3000) 
+data_2 <- filter(data_1, abs(z_score)<2000) 
 str(data_2)
 #Plot histogram of Z-scores
-ggplot(data_2, aes(x=z_score, color=infra_over_represented, fill=infra_over_represented)) + 
-  geom_histogram(bins = 50, alpha = 0.5, position = "identity",lwd = 0.25)+
+ggplot(data_2 %>% filter(round_motif_observed_probability>0), aes(x=z_score, color=infra_over_represented, fill=infra_over_represented)) + 
+  geom_histogram(bins = 51, alpha = 0.5, position = "identity",lwd = 0.25)+
   geom_vline(xintercept = -2)+
   geom_vline(xintercept = 2)+
   xlim(-20,20) + ylab("Frequency")+  theme_bw() +
@@ -40,39 +40,3 @@ ggplot(data_2, aes(x=z_score, color=infra_over_represented, fill=infra_over_repr
   scale_color_manual(name="Motif frequencies" ,values=c("coral2", "palegreen3", "cyan3"), labels=c("Under-represented",
                      "No statistical difference", "Over-represented"))
 
-
-###############
-# PERCENTILES
-###############
-
-data_perc <- as.tibble(data)
-
-# There are 827 motifs with upper and lower CI equal to zero
-data_perc %>% filter(lower_CI == upper_CI)
-data_perc %>% filter(lower_CI == upper_CI, lower_CI>0)
-
-data_perc$infra_over_represented <- "no_diff"
-data_perc$infra_over_represented[data_perc$round_motif_observed_probability<data_perc$lower_CI] <- "infra"
-data_perc$infra_over_represented[data_perc$round_motif_observed_probability>data_perc$upper_CI] <- "over"
-
-# There are 19514 motifs whose observed probability (0) is expected and equal to the lower bound (0)
-data_perc %>% filter(percentil_observed == 0, infra_over_represented == "no_diff")
-
-min(data_perc$percentil_observed[data_perc$infra_over_represented=="infra"])
-max(data_perc$percentil_observed[data_perc$infra_over_represented=="infra"])
-
-min(data_perc$percentil_observed[data_perc$infra_over_represented=="over"])
[…]

### 2021-07-27 Scripts/Z-score_percentile_histogram_plot.R
Update Z-score_percentile_histogram_plot.R

@@ -29,7 +29,12 @@ data_1 %>%
 
 data_2 <- filter(data_1, abs(z_score)<2000) 
 str(data_2)
-#Plot histogram of Z-scores
+#Plot histogram of Z-scores of those motifs with observed probability > 0
+
+# Justificación: si son observados 0 (o incluso 1 vez) no es muy interesante lo que les pase.
+# Podrian estar underrepresented, pero como con la Chi, si el expected es super bajo, 
+# diferenciar si esta under-represented sera dificil de detectar .
+
 ggplot(data_2 %>% filter(round_motif_observed_probability>0), aes(x=z_score, color=infra_over_represented, fill=infra_over_represented)) + 
   geom_histogram(bins = 51, alpha = 0.5, position = "identity",lwd = 0.25)+
   geom_vline(xintercept = -2)+

### 2021-07-27 Scripts/Z-score_percentile_histogram_plot.R
Critical value z-score added

@@ -11,11 +11,15 @@ data %>%
   summarise_all(funs(sum(is.na(.))))
 
 # At the moment this is just -2 and 2 but check how to find critical value of z-score
+
+p <- 0.05 #cutoff probability 95% confidence
+critical_value <- qnorm(p/2) #double tail probability divide by 2
+
 data_1 <- data %>%
   mutate(infra_over_represented = case_when(
-    z_score < -2 ~ "infra",
-    between(z_score, -2, 2) ~ "no_diff",
-    z_score > 2 ~ "over"
+    z_score < -abs(critical_value) ~ "infra",
+    between(z_score, -abs(critical_value), abs(critical_value)) ~ "no_diff",
+    z_score > abs(critical_value) ~ "over"
   ))
      
 #check levels
@@ -37,8 +41,8 @@ str(data_2)
 
 ggplot(data_2 %>% filter(round_motif_observed_probability>0), aes(x=z_score, color=infra_over_represented, fill=infra_over_represented)) + 
   geom_histogram(bins = 51, alpha = 0.5, position = "identity",lwd = 0.25)+
-  geom_vline(xintercept = -2)+
-  geom_vline(xintercept = 2)+
+  geom_vline(xintercept = -abs(critical_value))+
+  geom_vline(xintercept = abs(critical_value))+
   xlim(-20,20) + ylab("Frequency")+  theme_bw() +
   scale_fill_manual(name="Motif frequencies" ,values=c("coral2", "palegreen3", "cyan3"), labels=c("Under-represented",
                     "No statistical difference", "Over-represented")) +

### 2021-07-27 Scripts/Z-score_percentile_histogram_plot.R
minor edit

@@ -10,8 +10,7 @@ data <- read.csv("Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
 data %>%
   summarise_all(funs(sum(is.na(.))))
 
-# At the moment this is just -2 and 2 but check how to find critical value of z-score
-
+#Find critical value of Z-score
 p <- 0.05 #cutoff probability 95% confidence
 critical_value <- qnorm(p/2) #double tail probability divide by 2
 

### 2021-07-27 Scripts/Z-score_percentile_histogram_plot.R
Update Z-score_percentile_histogram_plot.R

@@ -39,7 +39,7 @@ str(data_2)
 # diferenciar si esta under-represented sera dificil de detectar .
 
 ggplot(data_2 %>% filter(round_motif_observed_probability>0), aes(x=z_score, color=infra_over_represented, fill=infra_over_represented)) + 
-  geom_histogram(bins = 51, alpha = 0.5, position = "identity",lwd = 0.25)+
+  geom_histogram(bins = 52, alpha = 0.5, position = "identity",lwd = 0.25)+
   geom_vline(xintercept = -abs(critical_value))+
   geom_vline(xintercept = abs(critical_value))+
   xlim(-20,20) + ylab("Frequency")+  theme_bw() +

### 2021-07-27 Scripts/Z-score_percentile_histogram_plot.R
extended x-axis to -60:60

@@ -39,10 +39,10 @@ str(data_2)
 # diferenciar si esta under-represented sera dificil de detectar .
 
 ggplot(data_2 %>% filter(round_motif_observed_probability>0), aes(x=z_score, color=infra_over_represented, fill=infra_over_represented)) + 
-  geom_histogram(bins = 51, alpha = 0.5, position = "identity",lwd = 0.25)+
+  geom_histogram(bins = 100, alpha = 0.5, position = "identity",lwd = 0.25)+
   geom_vline(xintercept = -abs(critical_value))+
   geom_vline(xintercept = abs(critical_value))+
-  xlim(-20,20) + ylab("Frequency")+  theme_bw() +
+  xlim(-60,60) + ylab("Frequency")+  theme_bw() +
   scale_fill_manual(name="Motif frequencies" ,values=c("coral2", "palegreen3", "cyan3"), labels=c("Under-represented",
                     "No statistical difference", "Over-represented")) +
   scale_color_manual(name="Motif frequencies" ,values=c("coral2", "palegreen3", "cyan3"), labels=c("Under-represented",

### 2021-07-27 Scripts/Z-score_percentile_histogram_plot.R
X label

@@ -46,5 +46,5 @@ ggplot(data_2 %>% filter(round_motif_observed_probability>0), aes(x=z_score, col
   scale_fill_manual(name="Motif frequencies" ,values=c("coral2", "palegreen3", "cyan3"), labels=c("Under-represented",
                     "No statistical difference", "Over-represented")) +
   scale_color_manual(name="Motif frequencies" ,values=c("coral2", "palegreen3", "cyan3"), labels=c("Under-represented",
-                     "No statistical difference", "Over-represented"))
+                     "No statistical difference", "Over-represented")) + xlab("Z-score")
 

### 2021-07-27 Draft/Draft.Rmd
Minor edits on intro and methods
Pie charts figure 4 added

@@
 Then, we explored which motifs up to five nodes in these set of plant-pollinator networks were over and under-represented.
-Finally, we explore if the different plants and pollinators functional groups are over- or under-represented in certain positions.
+Finally, we explored if the different plants and pollinators functional groups were over- or under-represented in certain positions.
 
@@
 draw(ht_list, auto_adjust = FALSE, cluster_rows = F)
+
+```
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="Figure 4."}
+
+plant_means_reordered <- read_csv("../Data/Csv/plant_abs_freq_means.csv")
+pollinator_means_reordered <- read_csv("../Data/Csv/pollinator_abs_freq_means.csv")
+
+library(ggplot2)
+library(scatterpie)
+library(RColorBrewer)
+
+# Pollinator--------
+pollinator_pies <- pollinator_means_reordered %>% select(-mean, -SE) %>% 
+  spread(Node_FG,mean_natural_units)
+
+pollinator_pies$x <- 0
+pollinator_pies$y <- 0
+
+#ggplot() + geom_scatterpie(aes(x=x, y=y, group=position,r=5), 
+#                           data = pollinator_pies,
+#                           cols=as.character(c("Bee","Birds","Coleoptera","Lepidoptera",
+#                                               "Lizards","Non-bee-Hymenoptera",
+#                                               "Non-syrphids-diptera","Other_insects",
+#                                               "Syrphids")))+
+#  coord_equal()+
+#  scale_fill_brewer(palette = "Paired")+
+#  facet_wrap(~position,nrow = 3)+
+#  theme_bw()+
+#    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+#          panel.background = element_blank(),
+#          axis.title.x=element_blank(),axis.text.x=element_blank(),
+#          axis.ticks.x=element_blank(),axis.title.y=element_blank(),
+#          axis.text.y=element_blank(),axis.ticks.y=element_blank(),
+#          legend.position="bottom")+
+#  labs(title = "Pollinator positions",fill=NULL)
+#    
+# plant--------
+plant_pies <- plant_means_reordered %>% select(-mean, -SE) %>% 
+  spread(Node_FG,mean_natural_units)
+
+plant_pies$x <- 0
+plant_pies$y <- 0
+
+#ggplot() + geom_scatterpie(aes(x=x, y=y, group=position,r=5), 
+#                           data = plant_pies,
+#                           cols=as.character(c("1","2","3","4","5")))+
+#  coord_equal()+
+#  scale_fill_brewer(palette = "Dark2")+
+#  facet_wrap(~position,nrow = 3)+
+#  theme_bw()+
+#  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+#        panel.background = element_blank(),
+#        axis.title.x=element_blank(),axis.text.x=element_blank(),
+#        axis.ticks.x=element_blank(),axis.title.y=element_blank(),
+#        axis.text.y=element_blank(),axis.ticks.y=element_blank(),
+#        legend.position="bottom")+
+#  labs(title = "Plant positions",fill=NULL)
+#
+
+#################################
+# CREATE PIE-MOTIFS
+#################################
+
+equidistribution <- function(number_nodes){
+
+  x_width <- 5.5/(number_nodes+1)
+
+  x_result <- rep(-1.5,number_nodes)
+
+  for(i in 1:number_nodes){
+
+    x_result[i] <- x_result[i] + i*x_width
+
+  }
+
+  return(x_result)
+
+}
+
+plot_pie_motif_positions <- function(motif_number){
+  motifs_raw_data <- read_csv("../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
+
+  motif_data <- motifs_raw_data %>% filter(motif_id == motif_number)
+
+  # Create dataframe with node positions
+
+  labdown = motif_data$plant %>% unique()
+
+  xdown = equidistribution(length(labdown))
+
+  ydown = rep(0,length(labdown))
+
+  labup = motif_data$pollinator %>% unique()
+
+  xup = equidistribution(length(labup))
+
+  yup = rep(1,length(labup))
+
+  d_nodes=data.frame(x=c(xdown,xup),
+                     y=c(ydown,yup),
+                     label = c(labdown,labup))
+
+  # Create a dataframe with links
+
+  plant_positions <- data.frame(plant = labdown,
+                                xdown = xdown,
+                                ydown = ydown)
+
+  pollinator_positions <- data.frame(pollinator = labup,
+                                     xup = xup,
+                                     yup = yup)
+
+  link_df <- motif_data %>% left_join(plant_positions, by = "plant") %>% 
+    left_join(pollinator_positions, by = "pollinator")
+
+  # Before plotting the motif, we remove letters from the node position id
+
+  d_nodes$label <- gsub("[^0-9.-]", "", d_nodes$label)
+  plant_pies_aux <- plant_pies %>% select(-x,-y) %>% mutate(position = as.character(position))
+
+  d_nodes_plant <- d_nodes %>% rename(position = label) %>% 
+    left_join(plant_pies_aux, by = "position") %>% as_tibble() %>%
+    filter(!is.na(`1`))
+
+  pollinator_pies_aux <- pollinator_pies %>% select(-x,-y) %>% mutate(position = as.character(position))
+
+  d_nodes_pollinator <- d_nodes %>% rename(position = label) %>% 
+    left_join(pollinator_pies_aux, by = "position") %>% as_tibble() %>%
+    filter(!is.na(Bee))
+
+  # Define the number of colors you want
+  nb.cols <- 5
+  mycolors <- c(brewer.pal(9, "Paired"),brewer.pal(5, "Dark2"))
+
+  ggplot() +
+    scale_shape_identity() +
+    geom_segment(data = link_df, aes(x=xdown, y=ydown, xend = xup, yend = yup), 
+                 size = 1, color = "grey20")+  geom_scatterpie(aes(x=x, y=y, group=position,r=.4), 
+    data = d_nodes_pollinator, cols=as.character(c("Bee","Birds","Coleoptera","Lepidoptera",
+     "Lizards","Non-bee-Hymenoptera", "Non-syrphids-diptera","Other_insects",
+     "Syrphids"))) +
+    geom_scatterpie(aes(x=x, y=y, group=position,r=0.4), 
+                    data = d_nodes_plant,
+                    cols=as.character(c("1","2","3","4","5")))+
+    coord_fixed()+
+    scale_fill_manual(values = mycolors,"test",
+      breaks=c("Bee","Birds","Coleoptera","Lepidoptera",
+               "Lizards","Non-bee-Hymenoptera", "Non-syrphids-diptera","Other_insects",
+               "Syrphids","1","2","3","4","5"), labels=c("Bee","Birds","Coleoptera","Lepidoptera",
+                                                        "Lizards","Non-bee-Hymenoptera", "Non-syrphids-diptera","Other_insects",
+                                                        "Syrphids", 
+          "Selfing herbs","Small outcrossing perennials","Self-incomp. perennials\nwith large flowers",
+          "Tall plants with small\nunisexual flowers","Short-lived outcrossers with\nlong zygomorphic flowers"))+
+    xlim(-1.5,4)+ ylim(-0.5,1.5)+
+    theme(panel.background = element_blank(),
+          axis.text.x=element_blank(),
+          axis.ticks.x=element_blank(),
+          axis.text.y=element_blank(),
+          axis.ticks.y=element_blank())+
+    labs(x=NULL,y=NULL)+
+    guides(color = FALSE,fill=guide_legend(title="Functional groups"))+
+    ggtitle(paste0("Motif ",motif_number))+
+    theme(plot.title = element_text(hjust = 0.5),legend.key.size = unit(0.5, 'cm'))+
+    theme(plot.margin=unit(c(0,0,0,0),"cm"))
+}
+
+motif_number <- 1
+p1 <- plot_pie_motif_positions(motif_number)
+
+motif_number <- 2
+p2 <- plot_pie_motif_positions(motif_number)
+
+motif_number <- 3
+p3 <- plot_pie_motif_positions(motif_number)
+
+motif_number <- 4
+p4 <- plot_pie_motif_positions(motif_number)
+
+motif_number <- 5
+p5 <- plot_pie_motif_positions(motif_number)
+
+motif_number <- 6
+p6 <- plot_pie_motif_positions(motif_number)
+
+motif_number <- 7
+p7 <- plot_pie_motif_positions(motif_number)
+
+motif_number <- 8   
+p8 <- plot_pie_motif_positions(motif_number)
+
+motif_number <- 9
+p9 <- plot_pie_motif_positions(motif_number)
+
+motif_number <- 10
+p10 <- plot_pie_motif_positions(motif_number)
+
+motif_number <- 11
+p11 <- plot_pie_motif_positions(motif_number)
+
+motif_number <- 12
+p12 <- plot_pie_motif_positions(motif_number)
+
+motif_number <- 13
+p13 <- plot_pie_motif_positions(motif_number)
+
+motif_number <- 14
+p14 <- plot_pie_motif_positions(motif_number)
+
+motif_number <- 15
+p15 <- plot_pie_motif_positions(motif_number)
+
+motif_number <- 16
+p16 <- plot_pie_motif_positions(motif_number)
+
+motif_number <- 17
+p17 <- plot_pie_motif_positions(motif_number)
+
+library(patchwork)
+
+(p1 & ylab("2 species")| p2 & ylab("3 species") | p3  |plot_spacer()|plot_spacer())/ 
+  (p4 & ylab("4 species")| p5 | p6 | p7|plot_spacer())/ 
+  (p8  & ylab("5 species")| p9 | p10 | p11 | p12) / 
+  (p13 & ylab("5 species")| p14 | p15 | p16 | p17) + plot_layout(guides = 'collect') &
+  theme(axis.title.y = element_text(color="black", size=14, face="bold"),legend.position = "bottom")
 

### 2021-07-28 Scripts/Scripts_Alfonso/10_plot_motif_label.R
Update 10_plot_motif_label.R

@@ -118,6 +118,12 @@ plot_motif_label <- function(label){
   
 }
 
+# Data with pollinator/plant labels
+
+plant_means_reordered <- read_csv("Data/Csv/plant_abs_freq_means.csv")
+pollinator_means_reordered <- read_csv("Data/Csv/pollinator_abs_freq_means.csv")
+
+
 
 # Examples
 

### 2021-07-28 Draft/Draft.Rmd

@@
 
-  yup = rep(1,length(labup))
+  yup = rep(2,length(labup))
 
@@
     geom_segment(data = link_df, aes(x=xdown, y=ydown, xend = xup, yend = yup), 
-                 size = 1, color = "grey20")+  geom_scatterpie(aes(x=x, y=y, group=position,r=.4), 
+                 size = 1, color = "grey20")+  geom_scatterpie(aes(x=x, y=y, group=position,r=.45), 
     data = d_nodes_pollinator, cols=as.character(c("Bee","Birds","Coleoptera","Lepidoptera",
@@
      "Syrphids"))) +
-    geom_scatterpie(aes(x=x, y=y, group=position,r=0.4), 
+    geom_scatterpie(aes(x=x, y=y, group=position,r=0.45), 
                     data = d_nodes_plant,
@@
           "Tall plants with small\nunisexual flowers","Short-lived outcrossers with\nlong zygomorphic flowers"))+
-    xlim(-1.5,4)+ ylim(-0.5,1.5)+
+    xlim(-1.5,4)+ ylim(-0.5,2.5)+
     theme(panel.background = element_blank(),

### 2021-07-28 Scripts/Plot_motif_label.R
Thinking on the main motifs to select for the plot

@@ -1,0 +1,190 @@
+library(tidyverse)
+library(RColorBrewer)
+
+equidistribution <- function(number_nodes){
+  
+  x_width <- 5.5/(number_nodes+1)
+  
+  x_result <- rep(-1.5,number_nodes)
+  
+  for(i in 1:number_nodes){
+    
+    x_result[i] <- x_result[i] + i*x_width
+    
+  }
+  
+  return(x_result)
+  
+}
+
+plot_motif_label <- function(label){
+  
+  label_split <- str_split(label,"_")[[1]]
+  motif_number <- as.numeric(label_split[1])
+  nodes <- label_split[2:length(label_split)]
+  plant_nodes <- nodes[nodes %in% plant_means_reordered$Node_FG]
+  pollinator_nodes <- nodes[nodes %in% pollinator_means_reordered$Node_FG]
+  
+  motifs_raw_data <- read_csv("Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
+  
+  motif_data <- motifs_raw_data %>% filter(motif_id == motif_number)
+  
+  
+  # Create dataframe with node positions
+  
+  labdown = motif_data$plant %>% unique()
+  
+  
+  xdown = equidistribution(length(labdown))
+  
+  ydown = rep(0,length(labdown))
+  
+  labup = motif_data$pollinator %>% unique()
+  
+  xup = equidistribution(length(labup))
+  
+  yup = rep(1,length(labup))
+  
+  d_nodes=data.frame(x=c(xdown,xup),
+                     y=c(ydown,yup),
+                     label = c(labdown,labup))
+  
+  
+  # Create a dataframe with links
+  
+  plant_positions <- data.frame(plant = labdown,
+                                xdown = xdown,
+                                ydown = ydown)
+  
+  pollinator_positions <- data.frame(pollinator = labup,
+                                     xup = xup,
+                                     yup = yup)
+  
+  link_df <- motif_data %>% left_join(plant_positions, by = "plant") %>% 
+    left_join(pollinator_positions, by = "pollinator")
+  
+  
+  # Add FG IDs to nodes
+  FG_IDs <- tibble(label = c(sort(labdown),sort(labup)),
+                   FG = c(plant_nodes,pollinator_nodes))
+  
+  d_nodes_FG <- d_nodes %>% left_join(FG_IDs, by = "label")
+  levels_FG <- c("Bee","Birds","Coleoptera","Lepidoptera",
[…]

### 2021-08-03 Draft/Draft.Rmd
Update Draft.Rmd

@@
 [@simmons2019; @simmons2020], we broke down the plant-pollinator networks into their constituent motifs.
-Prior to analyses, we selected only robust links, that is, interactions whose frequency was greater than one (64.98 % interactions); and, then, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.
-[Here I would present maybe full analysis, and without singletones in sup mat, especially if they are consistent]()
+Prior to analyses, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.
 
@@
 By adding the functional group estimates to the model intercept, we assessed the average motif frequency, after controlling the variation at the study level.
+Finally, we visualized with the help of the package ComplexHeatmap version 2.6.2 [@gu2016] over- and under- representation of plant and pollinator functional groups on the different motif positions.
+
+To test the effect of singletones on the frequencies of motif and those of functional groups' positions, in Appendices XXX, we applied the previous analyzes to the robust versions of the networks in table S1, namely: networks that, prior to binarization, only contained interactions whose frequency was greater than one (64.98 % interactions).
+
+Finally, we studied which motif combinations of functional groups (up to five nodes) are over or under-represented in 95% of our empirical networks (57 out of 60 arrangements, due to computational limitations to extract all motif combinations in the three networks with the highest number of links).
+To do so, for each of the 53,250 possible motif combinations, we estimated the observed and the expected probability of finding that combination in empirical networks, respectively.
+Then, we determined whether the observed probabilities are likely to come from the expected probabilities or not.
+To calculate the observed probability of a given combination $i$, $p_i^O$, we divided the number of times $i$ appears in our set empirical networks ($n_i^O$) by the sum of the number of times each possible combination appeared ($\sum_{k=1}^{53250} n_k^O$): $p_i^O = n_i^O / \sum_{k=1}^{53250} n_k^O$.
+Consequently, $\sum_{k=1}^{53250} p_k^O = 1$.
+To estimate the expected probability of a given motif combination $i$, $p_i^E$, firstly, we calculated the probability of finding a given functional group $x$ in the position $\alpha$ of $i$ ($p_i(x,\alpha)$).
+Then, by assuming the independency of $p_i(x,\alpha)$, we calculated the expected probability of the combination $i$ is equal to the product of the pairs $(x,\alpha)$ in $i$: $p_i^E = \prod _{(x,\alpha )\in i} p_i(x,\alpha)$.
+To obtain $p_i(x,\alpha)$, we calculated the number of times (or absolute frequency) that the functional group $x$ appears in the position $\alpha$ in 95% of our empirical networks, denoted as $n_i(x,\alpha)$.
+We controlled the variation at the network level and assessed the average value of $n_i(x,\alpha)$ by fitting a LMM per motif position, where the response variable is the number of times that a given position is observed per network, the explanatory variable is functional group identifier, and the random intercept is given by network identifiers nested within the study identifiers.
 To fit the LMMs models in our analyses, we used the ‘lmer’ package [@bates2015].
-Finally, we visualized with the help of the package ComplexHeatmap version 2.6.2 [@gu2016] over- and under- representation of plant and pollinator functional groups on the different motif positions.
-
-[potential additions: 
-Finally,for each motif, we recover the number of times a given combination of functional groups emerges ...]
+
+Once we obtained $p_i^O$ and $p_i^E$, we used simulation to determine whether the former is likely to come from the latter or not, since the large number of possible motif combinations and the small probabilities for some of them advise against using an Exact test of goodness-of-fit or a Chi-square one.
+Specifically, we created 1,000 random samples with repetition of possible motif combinations, where each sample contains 10 million elements and, for each combination, the probability of being selected is equal to its expected probability.
+From those random samples, we extracted the mean and the standard deviation of the expected probability of $i$, $E\left [ p_i^E \right ]$ and $\sigma\left [ p_i^E \right ]$, respectively, and calculated the z-scores of $p_i^O$ as $z_i^O = \left ( p_i^O - E\left [ p_i^E \right ] \right )/\sigma \left [ p_i^E \right ]$, for those motif combinations with $p_i^O > 0$.
+Following the usual interpretation for z-scores, motif combinations with $z_i^O > 1.96$ are over-represented, and those with $z_i^O < -1.96$ are under-represented, at the 95%  confidence level.
+Notice that we focused on combinations with $p_i^O > 10^{-7}$ because, beyond the interest that can arouse the combinations that appear at most once, we do not have enough numerical resolution to accurately detect whether or not those combinations are under-represented (due to the limited size of our random samples).
 

### 2021-08-03 Draft/Draft.Rmd
Update Draft.Rmd

@@
 Then, we determined whether the observed probabilities are likely to come from the expected probabilities or not.
-To calculate the observed probability of a given combination $i$, $p_i^O$, we divided the number of times $i$ appears in our set empirical networks ($n_i^O$) by the sum of the number of times each possible combination appeared ($\sum_{k=1}^{53250} n_k^O$): $p_i^O = n_i^O / \sum_{k=1}^{53250} n_k^O$.
-Consequently, $\sum_{k=1}^{53250} p_k^O = 1$.
+To calculate the observed probability of a given combination $i$, $p_i^O$, we divided the number of times $i$ appears in our set empirical networks ($n_i^O$) by the sum of the number of times each possible combination appeared: $p_i^O = n_i^O / \sum_{k=1}^{53250} n_k^O$, where $\sum_{k=1}^{53250} p_k^O = 1$.
 To estimate the expected probability of a given motif combination $i$, $p_i^E$, firstly, we calculated the probability of finding a given functional group $x$ in the position $\alpha$ of $i$ ($p_i(x,\alpha)$).
@@
 To obtain $p_i(x,\alpha)$, we calculated the number of times (or absolute frequency) that the functional group $x$ appears in the position $\alpha$ in 95% of our empirical networks, denoted as $n_i(x,\alpha)$.
-We controlled the variation at the network level and assessed the average value of $n_i(x,\alpha)$ by fitting a LMM per motif position, where the response variable is the number of times that a given position is observed per network, the explanatory variable is functional group identifier, and the random intercept is given by network identifiers nested within the study identifiers.
+Then, by controlling the variation at the network level, we assessed the average value of $n_i(x,\alpha)$, $E\left [ n_i(x,\alpha) \right ]$, and estimated $p_i(x,\alpha)$ as $p_i(x,\alpha)=E\left [ n_i(x,\alpha) \right ]/\sum_{k}E\left [ n_i(k,\alpha) \right ]$.
+To obtain $E\left [ n_i(x,\alpha) \right ]$, we fitted a LMM per motif position, where the response variable is the number of times that a given position is observed per network, the explanatory variable is functional group identifier, and the random intercept is given by network identifiers nested within the study identifiers.
 To fit the LMMs models in our analyses, we used the ‘lmer’ package [@bates2015].

### 2021-08-03 Draft/Draft.Rmd
Update Draft.Rmd

@@
 Once we obtained $p_i^O$ and $p_i^E$, we used simulation to determine whether the former is likely to come from the latter or not, since the large number of possible motif combinations and the small probabilities for some of them advise against using an Exact test of goodness-of-fit or a Chi-square one.
-Specifically, we created 1,000 random samples with repetition of possible motif combinations, where each sample contains 10 million elements and, for each combination, the probability of being selected is equal to its expected probability.
+Specifically, we created 1,000 random samples with repetition of possible motif combinations, where each sample contained 10 million elements and, for each combination, the probability of being selected was equal to its expected probability.
 From those random samples, we extracted the mean and the standard deviation of the expected probability of $i$, $E\left [ p_i^E \right ]$ and $\sigma\left [ p_i^E \right ]$, respectively, and calculated the z-scores of $p_i^O$ as $z_i^O = \left ( p_i^O - E\left [ p_i^E \right ] \right )/\sigma \left [ p_i^E \right ]$, for those motif combinations with $p_i^O > 0$.
-Following the usual interpretation for z-scores, motif combinations with $z_i^O > 1.96$ are over-represented, and those with $z_i^O < -1.96$ are under-represented, at the 95%  confidence level.
+Following the usual interpretation for z-scores, combinations with $z_i^O > 1.96$ are over-represented, whereas those with $z_i^O < -1.96$ are under-represented, at the 95%  confidence level.
 Notice that we focused on combinations with $p_i^O > 10^{-7}$ because, beyond the interest that can arouse the combinations that appear at most once, we do not have enough numerical resolution to accurately detect whether or not those combinations are under-represented (due to the limited size of our random samples).

### 2021-08-03 Draft/Draft.Rmd
Update Draft.Rmd

@@
 To estimate the expected probability of a given motif combination $i$, $p_i^E$, firstly, we calculated the probability of finding a given functional group $x$ in the position $\alpha$ of $i$ ($p_i(x,\alpha)$).
-Then, by assuming the independency of $p_i(x,\alpha)$, we calculated the expected probability of the combination $i$ is equal to the product of the pairs $(x,\alpha)$ in $i$: $p_i^E = \prod _{(x,\alpha )\in i} p_i(x,\alpha)$.
+Then, by assuming the independency of $p_i(x,\alpha)$, we calculated the expected probability of the combination $i$ as the product of the probability of the pairs $(x,\alpha)$ in $i$: $p_i^E = \prod _{(x,\alpha )\in i} p_i(x,\alpha)$.
 To obtain $p_i(x,\alpha)$, we calculated the number of times (or absolute frequency) that the functional group $x$ appears in the position $\alpha$ in 95% of our empirical networks, denoted as $n_i(x,\alpha)$.

### 2021-08-03 Draft/Draft.Rmd
Update Draft.Rmd

--- 2021-08-03 Draft/Draft.Rmd
@@
 
-Finally, we studied which motif combinations of functional groups (up to five nodes) are over or under-represented in 95% of our empirical networks (57 out of 60 arrangements, due to computational limitations to extract all motif combinations in the three networks with the highest number of links).
+Finally, we studied which motif combinations of functional groups (up to five nodes) are over or under-represented in 95% of our empirical networks (57 out of 60 arrangements, due to computational limitations to identify the nodes of the motif in the three networks with the highest number of links).
 To do so, for each of the 53,250 possible motif combinations, we estimated the observed and the expected probability of finding that combination in empirical networks, respectively.
@@
 To calculate the observed probability of a given combination $i$, $p_i^O$, we divided the number of times $i$ appears in our set empirical networks ($n_i^O$) by the sum of the number of times each possible combination appeared: $p_i^O = n_i^O / \sum_{k=1}^{53250} n_k^O$, where $\sum_{k=1}^{53250} p_k^O = 1$.
-To estimate the expected probability of a given motif combination $i$, $p_i^E$, firstly, we calculated the probability of finding a given functional group $x$ in the position $\alpha$ of $i$ ($p_i(x,\alpha)$).
-Then, by assuming the independency of $p_i(x,\alpha)$, we calculated the expected probability of the combination $i$ is equal to the product of the pairs $(x,\alpha)$ in $i$: $p_i^E = \prod _{(x,\alpha )\in i} p_i(x,\alpha)$.
+To estimate the expected probability of a given motif combination $i$, $p_i^E$, firstly, we calculated the probability of finding a given functional group $x$ in the position $\alpha$ of $i$, $p_i(x,\alpha)$.
+Then, by assuming the independency of $p_i(x,\alpha)$, we computed the expected probability of the combination $i$ as the product of the probability of the pairs $(x,\alpha)$ in the combination $i$: $p_i^E = \prod _{(x,\alpha )\in i} p_i(x,\alpha)$.
 To obtain $p_i(x,\alpha)$, we calculated the number of times (or absolute frequency) that the functional group $x$ appears in the position $\alpha$ in 95% of our empirical networks, denoted as $n_i(x,\alpha)$.
 Then, by controlling the variation at the network level, we assessed the average value of $n_i(x,\alpha)$, $E\left [ n_i(x,\alpha) \right ]$, and estimated $p_i(x,\alpha)$ as $p_i(x,\alpha)=E\left [ n_i(x,\alpha) \right ]/\sum_{k}E\left [ n_i(k,\alpha) \right ]$.
-To obtain $E\left [ n_i(x,\alpha) \right ]$, we fitted a LMM per motif position, where the response variable is the number of times that a given position is observed per network, the explanatory variable is functional group identifier, and the random intercept is given by network identifiers nested within the study identifiers.
-To fit the LMMs models in our analyses, we used the ‘lmer’ package [@bates2015].
+To obtain $E\left [ n_i(x,\alpha) \right ]$, we fitted a LMM per motif position, where the response variable was the number of times that a given position was observed per network, the explanatory variable was functional group identifier, and the random intercept was given by network identifiers nested within the study identifiers.
+We used the ‘lmer’ package [@bates2015] to fit the LMMs models in our analyses.
 

### 2021-08-03 Draft/Draft.Rmd
Update Draft.Rmd

@@
 
-Finally, we studied which motif combinations of functional groups (up to five nodes) are over or under-represented in 95% of our empirical networks (57 out of 60 arrangements, due to computational limitations to identify the nodes of the motif in the three networks with the highest number of links).
+Finally, we studied which motif combinations of functional groups (up to five nodes) are over or under-represented in 95% of our empirical networks (57 out of 60 arrangements, due to computational limitations to identify all the nodes in the motifs of the three networks with the highest number of links).
 To do so, for each of the 53,250 possible motif combinations, we estimated the observed and the expected probability of finding that combination in empirical networks, respectively.
 Then, we determined whether the observed probabilities are likely to come from the expected probabilities or not.
-To calculate the observed probability of a given combination $i$, $p_i^O$, we divided the number of times $i$ appears in our set empirical networks ($n_i^O$) by the sum of the number of times each possible combination appeared: $p_i^O = n_i^O / \sum_{k=1}^{53250} n_k^O$, where $\sum_{k=1}^{53250} p_k^O = 1$.
+To calculate the observed probability of a given combination $i$, $p_i^O$, we divided the number of times that $i$ appears in our set empirical networks ($n_i^O$) by the sum of the number of times that each possible combination appeared: $p_i^O = n_i^O / \sum_{k=1}^{53250} n_k^O$, where $\sum_{k=1}^{53250} p_k^O = 1$.
 To estimate the expected probability of a given motif combination $i$, $p_i^E$, firstly, we calculated the probability of finding a given functional group $x$ in the position $\alpha$ of $i$, $p_i(x,\alpha)$.
-Then, by assuming the independency of $p_i(x,\alpha)$, we computed the expected probability of the combination $i$ as the product of the probability of the pairs $(x,\alpha)$ in the combination $i$: $p_i^E = \prod _{(x,\alpha )\in i} p_i(x,\alpha)$.
-To obtain $p_i(x,\alpha)$, we calculated the number of times (or absolute frequency) that the functional group $x$ appears in the position $\alpha$ in 95% of our empirical networks, denoted as $n_i(x,\alpha)$.
+Then, by assuming the independency of $p_i(x,\alpha)$, we computed the expected probability of the combination $i$ as the product of the probability of its pairs $(x,\alpha)$, that is, $p_i^E = \prod _{(x,\alpha )\in i} p_i(x,\alpha)$.
+To obtain $p_i(x,\alpha)$, we used the ‘bmotif’ package [@bmotifsimmons2019] to calculate the number of times (or absolute frequency) that the functional group $x$ appears in the position $\alpha$ in 95% of our empirical networks, denoted as $n_i(x,\alpha)$.
 Then, by controlling the variation at the network level, we assessed the average value of $n_i(x,\alpha)$, $E\left [ n_i(x,\alpha) \right ]$, and estimated $p_i(x,\alpha)$ as $p_i(x,\alpha)=E\left [ n_i(x,\alpha) \right ]/\sum_{k}E\left [ n_i(k,\alpha) \right ]$.

### 2021-08-03 Draft/Draft.Rmd
Update Draft.Rmd

@@
 Then, we determined whether the observed probabilities are likely to come from the expected probabilities or not.
-To calculate the observed probability of a given combination $i$, $p_i^O$, we divided the number of times that $i$ appears in our set empirical networks ($n_i^O$) by the sum of the number of times that each possible combination appeared: $p_i^O = n_i^O / \sum_{k=1}^{53250} n_k^O$, where $\sum_{k=1}^{53250} p_k^O = 1$.
+To calculate the observed probability of a given combination $i$, $p_i^O$, we divided the number of times that $i$ appears in our set of empirical networks ($n_i^O$) by the sum of the number of times that each possible combination appeared: $p_i^O = n_i^O / \sum_{k=1}^{53250} n_k^O$, where $\sum_{k=1}^{53250} p_k^O = 1$.
 To estimate the expected probability of a given motif combination $i$, $p_i^E$, firstly, we calculated the probability of finding a given functional group $x$ in the position $\alpha$ of $i$, $p_i(x,\alpha)$.
 Then, by assuming the independency of $p_i(x,\alpha)$, we computed the expected probability of the combination $i$ as the product of the probability of its pairs $(x,\alpha)$, that is, $p_i^E = \prod _{(x,\alpha )\in i} p_i(x,\alpha)$.
-To obtain $p_i(x,\alpha)$, we used the ‘bmotif’ package [@bmotifsimmons2019] to calculate the number of times (or absolute frequency) that the functional group $x$ appears in the position $\alpha$ in 95% of our empirical networks, denoted as $n_i(x,\alpha)$.
-Then, by controlling the variation at the network level, we assessed the average value of $n_i(x,\alpha)$, $E\left [ n_i(x,\alpha) \right ]$, and estimated $p_i(x,\alpha)$ as $p_i(x,\alpha)=E\left [ n_i(x,\alpha) \right ]/\sum_{k}E\left [ n_i(k,\alpha) \right ]$.
-To obtain $E\left [ n_i(x,\alpha) \right ]$, we fitted a LMM per motif position, where the response variable was the number of times that a given position was observed per network, the explanatory variable was functional group identifier, and the random intercept was given by network identifiers nested within the study identifiers.
+To obtain $p_i(x,\alpha)$, we used the ‘bmotif’ package [@bmotifsimmons2019] to calculate the number of times (or absolute frequency) that the functional group $x$ appears in the position $\alpha$ in each empirical network $\eta$, denoted as $n_i^{\eta}(x,\alpha)$.
+Then, by controlling the variation at the network level, we assessed the average value of the absolute frequency of functional group $x$ appears in the position $\alpha$, $n_i(x,\alpha) = E\left [ n_i^{\eta}(x,\alpha) \right ]$, and estimated $p_i(x,\alpha)$ as $p_i(x,\alpha) = n_i(x,\alpha)/\sum_{k}n_i(k,\alpha)$.
+To obtain $n_i(x,\alpha)$, we fitted a LMM per motif position, where the response variable was the number of times that a given position was observed per network, the explanatory variable was functional group identifier, and the random intercept was given by network identifiers nested within the study identifiers.
 We used the ‘lmer’ package [@bates2015] to fit the LMMs models in our analyses.

### 2021-08-03 Draft/Draft.Rmd
Update Draft.Rmd

@@
 Then, we determined whether the observed probabilities are likely to come from the expected probabilities or not.
-To calculate the observed probability of a given combination $i$, $p_i^O$, we divided the number of times that $i$ appears in our set of empirical networks ($n_i^O$) by the sum of the number of times that each possible combination appeared: $p_i^O = n_i^O / \sum_{k=1}^{53250} n_k^O$, where $\sum_{k=1}^{53250} p_k^O = 1$.
+To calculate the observed probability of a given combination $i$, $p_i^O$, we divided the number of times that $i$ appears in our set of empirical networks ($n_i^O$) by the sum of the number of times that each possible combination appeared: $p_i^O = n_i^O / \sum_{k=1}^{53,250} n_k^O$, and, consequently, $\sum_{k=1}^{53,250} p_k^O = 1$.
 To estimate the expected probability of a given motif combination $i$, $p_i^E$, firstly, we calculated the probability of finding a given functional group $x$ in the position $\alpha$ of $i$, $p_i(x,\alpha)$.

### 2021-08-03 Draft/Draft.Rmd
Update Draft.Rmd

@@
 Then, by assuming the independency of $p_i(x,\alpha)$, we computed the expected probability of the combination $i$ as the product of the probability of its pairs $(x,\alpha)$, that is, $p_i^E = \prod _{(x,\alpha )\in i} p_i(x,\alpha)$.
-To obtain $p_i(x,\alpha)$, we used the ‘bmotif’ package [@bmotifsimmons2019] to calculate the number of times (or absolute frequency) that the functional group $x$ appears in the position $\alpha$ in each empirical network $\eta$, denoted as $n_i^{\eta}(x,\alpha)$.
+To obtain $p_i(x,\alpha)$, we proceeded as follows.
+First, we used the ‘bmotif’ package [@bmotifsimmons2019] to calculate the number of times (or absolute frequency) that the functional group $x$ appears in the position $\alpha$ in each empirical network $\eta$, denoted as $n_i^{\eta}(x,\alpha)$.
 Then, by controlling the variation at the network level, we assessed the average value of the absolute frequency of functional group $x$ appears in the position $\alpha$, $n_i(x,\alpha) = E\left [ n_i^{\eta}(x,\alpha) \right ]$, and estimated $p_i(x,\alpha)$ as $p_i(x,\alpha) = n_i(x,\alpha)/\sum_{k}n_i(k,\alpha)$.

### 2021-08-03 Draft/Draft.Rmd
Update Draft.Rmd

@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="Figure 4."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="Figure 4.
+Graphical representation of the probability of finding a given functional group $x$ in the position $\alpha$ of motif $i$, $p_i(x,\alpha)$, for all the possible motifs from two to five species in bipartite networks.
+The slices in the nodes for a given functional group $x$ are proportional to the corresponding value of $p_i(x,\alpha)$."}
 

### 2021-08-03 Draft/Draft.Rmd
Update Draft.Rmd

--- 2021-08-03 Draft/Draft.Rmd
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="Figure 4."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="Figure 4.
+Graphical representation of the probability of finding a given functional group $x$ in the position $\\alpha$ of motif $i$, $p_i(x,\\alpha)$, for all the possible motifs from two to five species in bipartite networks.
+The slices in the nodes for a given functional group $x$ are proportional to the corresponding value of $p_i(x,\\alpha)$."}
 

### 2021-08-03 Draft/Draft.Rmd
Update Draft.Rmd

@@
 To obtain $p_i(x,\alpha)$, we proceeded as follows.
-First, we used the ‘bmotif’ package [@bmotifsimmons2019] to calculate the number of times (or absolute frequency) that the functional group $x$ appears in the position $\alpha$ in each empirical network $\eta$, denoted as $n_i^{\eta}(x,\alpha)$.
+First, we calculated the number of times that the functional group $x$ appears in the position $\alpha$ in each empirical network $\eta$, denoted as $n_i^{\eta}(x,\alpha)$.
 Then, by controlling the variation at the network level, we assessed the average value of the absolute frequency of functional group $x$ appears in the position $\alpha$, $n_i(x,\alpha) = E\left [ n_i^{\eta}(x,\alpha) \right ]$, and estimated $p_i(x,\alpha)$ as $p_i(x,\alpha) = n_i(x,\alpha)/\sum_{k}n_i(k,\alpha)$.

### 2021-08-04 Draft/Draft.Rmd
Update Draft.Rmd

@@
 Specifically, we created 1,000 random samples with repetition of possible motif combinations, where each sample contained 10 million elements and, for each combination, the probability of being selected was equal to its expected probability.
-From those random samples, we extracted the mean and the standard deviation of the expected probability of $i$, $E\left [ p_i^E \right ]$ and $\sigma\left [ p_i^E \right ]$, respectively, and calculated the z-scores of $p_i^O$ as $z_i^O = \left ( p_i^O - E\left [ p_i^E \right ] \right )/\sigma \left [ p_i^E \right ]$, for those motif combinations with $p_i^O > 0$.
-Following the usual interpretation for z-scores, combinations with $z_i^O > 1.96$ are over-represented, whereas those with $z_i^O < -1.96$ are under-represented, at the 95%  confidence level.
+From those random samples, we extracted the mean and the standard deviation of the expected probability of $i$, denoted as $E\left [ p_i^E \right ]$ and $\sigma\left [ p_i^E \right ]$, respectively, and calculated the z-scores of $p_i^O$ as $z_i^O = \left ( p_i^O - E\left [ p_i^E \right ] \right )/\sigma \left [ p_i^E \right ]$, for those motif combinations with $p_i^O > 0$.
+According to the usual interpretation of z-scores, combinations with $z_i^O > 1.96$ are over-represented, whereas those with $z_i^O < -1.96$ are under-represented, at the 95%  confidence level.
 Notice that we focused on combinations with $p_i^O > 10^{-7}$ because, beyond the interest that can arouse the combinations that appear at most once, we do not have enough numerical resolution to accurately detect whether or not those combinations are under-represented (due to the limited size of our random samples).

### 2021-08-05 Draft/Draft.Rmd
fig 5 added thinking of headings for methods and results...

--- 2021-08-03 Draft/Draft.Rmd
@@
 The analysis of motifs (meso-scale) in plant-pollinator networks have revealed that the different ecological processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions [@simmons2020].
-However, the global patterns of indirect interactions in plant-pollinator networks (over- and under- representation of motifs) are still unknown.
+Yet, the global patterns of indirect interactions in plant-pollinator networks (over- and under- representation of motifs) are still unknown.
 
 Motifs are abstract representations often decoupled from species ecology.
-Hence, linking the structural properties of the meso-scale with the species ecology can help the understanding of ecological processes.
+Thus, linking the structural properties of the meso-scale with the species ecology can help the understanding of ecological processes.
 For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species functional role [@stouffer2012; @baker2015].
@@
 In total, there were 503 plant species, 1,111 pollinator species and 6248 of pairwise interactions registered.
-For ease of data manipulation plant and pollinator species names were standardize with the help of the package taxize version 0.9.99 [@chamberlain2020].
+For ease of data manipulation plant and pollinator species names were standardize with the help of the package _taxize_ version 0.9.99 [@chamberlain2020].
 
@@
 We opted to calculate the plant functional groups on this larger set of species because of the higher accuracy when delimiting the functional groups with that many variables @dolnicar2014.
-For this, we calculated the distance of the different functional traits with the function gowdis from the package FD version 1.0-12 [@laliberte2014] with the method ward.D2 used for non-squared distances [@murtagh2014].
+For this, we calculated the distance of the different functional traits with the function _gowdis_ from the package _FD_ version 1.0-12 [@laliberte2014] with the method ward.D2 used for non-squared distances [@murtagh2014].
 All the numerical traits were previously scaled.
-Finally, we applied a hierarchical cluster analysis with the function hclust from the R stats package version 4.0.5 and calculated the optimal number of clusters with the function kgs from the package maptree version 1.4-7 [@white2009].
+Finally, we applied a hierarchical cluster analysis with the function _hclust_ from the _R_ stats package version 4.0.5 and calculated the optimal number of clusters with the function _kgs_ from the package _maptree_ version 1.4-7 [@white2009].
 
 Second, pollinators were grouped into functional groups based on taxonomic rank.
-We opted to divide pollinators on the taxonomic rank level and not with functional traits because (i) they main taxonomic orders differ in form and behaviour and (ii) the lower complexity of higher taxonomic ranks (i.e., pollinators had 6 orders versus plants that had 38).
+We opted to divide pollinators on the taxonomic rank level and not with functional traits because (i) the main taxonomic orders differ in form and behaviour and (ii) the lower complexity of higher taxonomic ranks (i.e., pollinators had 6 orders versus plants that had 38).
 Hence, we grouped pollinators into 6 functional groups: (i) Hymenoptera-Anthophila (bees), (ii) Hymenoptera-non-Anthophila (other non-bee Hymenoptera), (iii) Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera and (vi) Coleoptera.
@@
 
-We calculated the frequency of all motifs up to five nodes (see Figure 1) for each empirical network, by using the ‘bmotif’ package [@bmotifsimmons2019].
+We calculated the frequency of all motifs up to five nodes (see Figure 1) for each empirical network, by using the _bmotif_ package [@bmotifsimmons2019].
 To control for variation in network size and for the fact that smaller motifs can be nested within larger motifs, the frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains).
@@
 
-To assess the significance of the observed frequencies, we created 1,000 simulated networks for each binary network using the ‘nullmodel’ function and the ‘vaznull’ model in the bipartite package [@dormann2009].
+To assess the significance of the observed frequencies, we created 1,000 simulated networks for each binary network using the _nullmodel_ function and the _vaznull_ model in the _bipartite_ package [@dormann2009].
 Generated networks had the same number of plants and pollinators, as well as the same connectance of their corresponding empirical networks.
@@
 Next, we calculated which functional groups were over or under-represented in different motif positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
-We extracted the position frequencies of all motifs from three to five nodes for each network and species by using the ‘bmotif’ package [@bmotifsimmons2019].
+We extracted the position frequencies of all motifs from three to five nodes for each network and species by using the _bmotif_ package [@bmotifsimmons2019].
 To estimate the position frequencies of each functional group in a given network, we added the frequencies of those species that belong to the group, and then, we normalised the resulting frequencies by dividing the position measure for each group by the total number of times that a group appears in any position within the same motif size class.
@@
 
-To test the effect of singletones on the frequencies of motif and those of functional groups' positions, in Appendices XXX, we applied the previous analyzes to the robust versions of the networks in table S1, namely: networks that, prior to binarization, only contained interactions whose frequency was greater than one (64.98 % interactions).
+To test the effect of singletones on the frequencies of motif and those of functional groups' positions, in Appendices XXX, we applied the previous analyzes to the robust versions of the networks in table S1, namely: networks that, prior to binarization, only contained interactions whose frequency was greater than one (64.98% of interactions).
 
@@
 To obtain $p_i(x,\alpha)$, we proceeded as follows.
-First, we calculated the number of times that the functional group $x$ appears in the position $\alpha$ in each empirical network $\eta$, denoted as $n_i^{\eta}(x,\alpha)$.
+First, we used the _bmotif_ package [@bmotifsimmons2019] to calculate the number of times (or absolute frequency) that the functional group $x$ appears in the position $\alpha$ in each empirical network $\eta$, denoted as $n_i^{\eta}(x,\alpha)$.
 Then, by controlling the variation at the network level, we assessed the average value of the absolute frequency of functional group $x$ appears in the position $\alpha$, $n_i(x,\alpha) = E\left [ n_i^{\eta}(x,\alpha) \right ]$, and estimated $p_i(x,\alpha)$ as $p_i(x,\alpha) = n_i(x,\alpha)/\sum_{k}n_i(k,\alpha)$.
@@
   theme(axis.title.y = element_text(color="black", size=14, face="bold"),legend.position = "bottom")
+
+```
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="Figure 5."}
+
+library(tidyverse)
+library(RColorBrewer)
+
+equidistribution <- function(number_nodes){
+
+  x_width <- 5.5/(number_nodes+1)
+
+  x_result <- rep(-1.5,number_nodes)
+
+  for(i in 1:number_nodes){
+
+    x_result[i] <- x_result[i] + i*x_width
+
+  }
+
+  return(x_result)
+
+}
+
+plot_motif_label <- function(label){
+
+  label_split <- str_split(label,"_")[[1]]
+  motif_number <- as.numeric(label_split[1])
+  nodes <- label_split[2:length(label_split)]
+  plant_nodes <- nodes[nodes %in% plant_means_reordered$Node_FG]
+  pollinator_nodes <- nodes[nodes %in% pollinator_means_reordered$Node_FG]
+
+  motifs_raw_data <- read_csv("../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
+
+  motif_data <- motifs_raw_data %>% filter(motif_id == motif_number)
+
+  # Create dataframe with node positions
+
+  labdown = motif_data$plant %>% unique()
+
+  xdown = equidistribution(length(labdown))
+
+  ydown = rep(0,length(labdown))
+
+  labup = motif_data$pollinator %>% unique()
+
+  xup = equidistribution(length(labup))
+
+  yup = rep(1,length(labup))
+
+  d_nodes=data.frame(x=c(xdown,xup),
+                     y=c(ydown,yup),
+                     label = c(labdown,labup))
+
+  # Create a dataframe with links
+
+  plant_positions <- data.frame(plant = labdown,
+                                xdown = xdown,
+                                ydown = ydown)
+
+  pollinator_positions <- data.frame(pollinator = labup,
+                                     xup = xup,
+                                     yup = yup)
+
+  link_df <- motif_data %>% left_join(plant_positions, by = "plant") %>% 
+    left_join(pollinator_positions, by = "pollinator")
+
+  # Add FG IDs to nodes
+  FG_IDs <- tibble(label = c(sort(labdown),sort(labup)),
+                   FG = c(plant_nodes,pollinator_nodes))
+
+  d_nodes_FG <- d_nodes %>% left_join(FG_IDs, by = "label")
+  levels_FG <- c("Bee","Birds","Coleoptera","Lepidoptera",
+                 "Lizards","Non-bee-Hymenoptera", "Non-syrphids-diptera","Other_insects",
+                 "Syrphids","1","2","3","4","5")
+
+  d_nodes_FG$FG <- factor(d_nodes_FG$FG, levels = levels_FG)
+
+  levels(d_nodes_FG$FG) <- c("Bee","Birds","Coleoptera","Lepidoptera",
+                             "Lizards","Non-bee-Hymenoptera", "Non-syrphids-diptera","Other_insects",
+                             "Syrphids","1","2","3","4","5")
+
+  # Before plotting the motif, we remove letters from the node position id
+
+  d_nodes_FG$label <- gsub("[^0-9.-]", "", d_nodes_FG$label)
+
+  # Define the number of colors you want
+  mycolors <- c(brewer.pal(9, "Paired"),brewer.pal(5, "Dark2"))
+
+  ggplot(data=d_nodes_FG, aes(x, y)) +
+    scale_shape_identity() +
+    geom_segment(data = link_df, aes(x=xdown, y=ydown, xend = xup, yend = yup), size = 1, color = "grey20")+
+    geom_point(aes(color = FG), size=7.5)+
+    geom_text(aes(x, y , label = label), size=3)+
+    scale_color_manual(drop = FALSE, values = mycolors,
+                       breaks=c("Bee","Birds","Coleoptera","Lepidoptera",
+                                "Lizards","Non-bee-Hymenoptera", "Non-syrphids-diptera","Other_insects",
+                                "Syrphids","1","2","3","4","5"), 
+                       labels=c("Bee","Birds","Coleoptera","Lepidoptera",
+                                "Lizards","Non-bee-Hymenoptera", "Non-syrphids-diptera",
+                                "Other insects", "Syrphids", 
+                                "Selfing herbs","Small outcrossing perennials",
+                                "Self-incomp. perennials\nwith large flowers",
+                                "Tall plants with small\nunisexual flowers",
+                                "Short-lived outcrossers with\nlong zygomorphic flowers"))+
+    xlim(-1.5,4)+ ylim(-0.5,1.5)+
+    theme(panel.background = element_blank(),
+          axis.text.x=element_blank(),
+          axis.ticks.x=element_blank(),
+          axis.text.y=element_blank(),
+          axis.ticks.y=element_blank())+
+    labs(x=NULL,y=NULL)+
+    ggtitle(paste0("Motif ",motif_number))+
+    theme(plot.title = element_text(hjust = 0.5,size=10))+
+    guides(color=guide_legend(title="Functional groups"))
+
+}
+
+# Data with pollinator/plant labels
+
+plant_means_reordered <- read_csv("../Data/Csv/plant_abs_freq_means.csv")
+pollinator_means_reordered <- read_csv("../Data/Csv/pollinator_abs_freq_means.csv")
+
+####################################################################################################
+#Read data to check top 5 motif of each category of observed propabilities
+
+#Under, No signi, Over-rep
+####################################################################################################
+# Check top Z-scores of each group (Under, No diff, Over)
+
+#Read data
+data <- read.csv("../Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
+
+#Find critical value of Z-score
+p <- 0.05 #cutoff probability 95% confidence
+critical_value <- qnorm(p/2) #double tail probability divide by 2
+
+data_1 <- data %>%
+  mutate(infra_over_represented = case_when(
+    z_score < -abs(critical_value) ~ "infra",
+    between(z_score, -abs(critical_value), abs(critical_value)) ~ "no_diff",
+    z_score > abs(critical_value) ~ "over"
+  ))
+
+#data_2 <- filter(data_1, abs(z_score)<2000) 
+#str(data_2)
+
+#Select under-represented by the ones with highest porbability of being observed (top10)
+under_data <- filter(data_1, infra_over_represented=="infra")
+
+under_top_5 <- filter(under_data, row_number(desc(abs(motif_observed_probability)))<= 5) %>%
+  select(motif_functional_ID,motif_observed_probability,counts_observed,z_score)
+
+#Select no statistical difference by the ones with highest porbability of being observed (top5)
+no_diff_data <- filter(data_1, infra_over_represented=="no_diff")
+
+no_diff_top_5 <- filter(no_diff_data, row_number(desc(abs(motif_observed_probability)))<= 5) %>%
+  select(motif_functional_ID,motif_observed_probability,counts_observed,z_score)
+
+#Select over-represenetd by the ones with highest porbability of being observed (top5)
+over_data <- filter(data_1, infra_over_represented=="over")
+
+over_top_5 <- filter(over_data, row_number(desc(abs(motif_observed_probability)))<= 5) %>%
+  select(motif_functional_ID,motif_observed_probability,counts_observed,z_score)
+####################################################################################################
+#Now plot it 
+####################################################################################################
+
+library(patchwork)
+
+#Prepare list of 5 plots for each group
+#Under
+labels_under <- under_top_5$motif_functional_ID
+p_under <- list()
+
+for (i in 1:5){
+
+  p_under[[i]] <- plot_motif_label(labels_under[[i]])
+}
+
+#No signficance
+labels_nodiff <- no_diff_top_5$motif_functional_ID
+p_nodiff <- list()
+
+for (i in 1:5){
+
+  p_nodiff[[i]] <- plot_motif_label(labels_nodiff[[i]])
+}
+
+#Over
+labels_over <- over_top_5$motif_functional_ID
+p_over <- list()
+
+for (i in 1:5){
+
+  p_over[[i]] <- plot_motif_label(labels_over[[i]])
+}
+
+#Run Script with histogram plot
+source("../Scripts/Z-score_percentile_histogram_plot.R")
+
+hist <- ggplot(data_2 %>% filter(round_motif_observed_probability>0), aes(x=z_score, color=infra_over_represented, fill=infra_over_represented)) + 
+  geom_histogram(bins = 93, alpha = 0.5, position = "identity",lwd = 0.25)+
+  geom_vline(xintercept = -abs(critical_value))+
+  geom_vline(xintercept = abs(critical_value))+
+  xlim(-60,60) + ylab("Frequency")+  theme_bw() +
+  scale_fill_manual(name="Motif frequencies" ,values=c("coral2", "palegreen3", "cyan3"), labels=c("Under-represented",
+                                                                                                  "No statistical difference", "Over-represented")) +
+  scale_color_manual(name="Motif frequencies" ,values=c("coral2", "palegreen3", "cyan3"), labels=c("Under-represented",
+                                                                                                   "No statistical difference", "Over-represented")) + xlab("Z-score")
+
+t_col <- function(color, percent = 50, name = NULL) {
+  #      color = color name
+  #    percent = % transparency
+  #       name = an optional name for the color
+
+  ## Get RGB values for named color
+  rgb.val <- col2rgb(color)
+
+  ## Make new color using input color as base and alpha set by transparency
+  t.col <- rgb(rgb.val[1], rgb.val[2], rgb.val[3],
+               max = 255,
+               alpha = (100 - percent) * 255 / 100,
+               names = name)
+
+  ## Save the color
+  invisible(t.col)
+}
+## END
+
+#Prepare panel of plots
+hist / ((p_under[[1]]/p_under[[2]]/p_under[[3]]/p_under[[4]] & theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_rect(fill=t_col("coral2")))) | 
+          (p_nodiff[[1]]/p_nodiff[[2]]/p_nodiff[[3]]/p_nodiff[[4]]& theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_rect(fill=t_col("palegreen3")))) |
+          (p_over[[1]]/p_over[[2]]/p_over[[3]]/p_over[[4]] & theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_rect(fill=t_col("cyan3"))))) + plot_layout(guides = 'collect')
 

### 2021-08-05 Scripts/Z-score_percentile_histogram_plot.R

@@ -4,7 +4,7 @@ library(dplyr)
 library(ggplot2)
 library(tidyverse)
 #Read data
-data <- read.csv("Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
+data <- read.csv("../Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
 
 #Check NA's per column
 data %>%

### 2021-08-05 Draft/Draft.Rmd

@@
 To obtain $p_i(x,\alpha)$, we proceeded as follows.
-First, we used the _bmotif_ package [@bmotifsimmons2019] to calculate the number of times (or absolute frequency) that the functional group $x$ appears in the position $\alpha$ in each empirical network $\eta$, denoted as $n_i^{\eta}(x,\alpha)$.
+First, we calculated the number of times that the functional group $x$ appears in the position $\alpha$ in each empirical network $\eta$, denoted as $n_i^{\eta}(x,\alpha)$.
 Then, by controlling the variation at the network level, we assessed the average value of the absolute frequency of functional group $x$ appears in the position $\alpha$, $n_i(x,\alpha) = E\left [ n_i^{\eta}(x,\alpha) \right ]$, and estimated $p_i(x,\alpha)$ as $p_i(x,\alpha) = n_i(x,\alpha)/\sum_{k}n_i(k,\alpha)$.

### 2021-08-05 Scripts/Z-score_percentile_histogram_plot.R
edit on source file that was reading to avoid readed code

@@ -7,8 +7,8 @@ library(tidyverse)
 data <- read.csv("../Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
 
 #Check NA's per column
-data %>%
-  summarise_all(funs(sum(is.na(.))))
+#data %>%
+ # summarise_all(funs(sum(is.na(.))))
 
 #Find critical value of Z-score
 p <- 0.05 #cutoff probability 95% confidence
@@ -22,7 +22,7 @@ data_1 <- data %>%
   ))
      
 #check levels
-levels(factor(data_1$infra_over_represented))
+#levels(factor(data_1$infra_over_represented))
 
 #Check proportion of infra/over and no statistical difference
 data_1 %>% 
@@ -31,7 +31,7 @@ data_1 %>%
   mutate(proportion = no_rows / sum(no_rows))
 
 data_2 <- filter(data_1, abs(z_score)<2000) 
-str(data_2)
+#str(data_2)
 #Plot histogram of Z-scores of those motifs with observed probability > 0
 
 # Justificación: si son observados 0 (o incluso 1 vez) no es muy interesante lo que les pase.

### 2021-08-06 Draft/Draft.Rmd
Some minor edits

@@
 All studies sampled plant-pollinator interactions in natural systems and were selected based on wide geographical coverage and the presence of interaction frequency as a measure of interaction strength.
-In total, there were 503 plant species, 1,111 pollinator species and 6248 of pairwise interactions registered.
-For ease of data manipulation plant and pollinator species names were standardize with the help of the package _taxize_ version 0.9.99 [@chamberlain2020].
+In total, there were 503 plant species, 1,111 floral visitors species and 6248 of pairwise interactions registered.
+For ease of data manipulation plant and floral visitors species names were standardize with the help of the package _taxize_ version 0.9.99 [@chamberlain2020].
 
@@
 We opted to calculate the plant functional groups on this larger set of species because of the higher accuracy when delimiting the functional groups with that many variables @dolnicar2014.
-For this, we calculated the distance of the different functional traits with the function _gowdis_ from the package _FD_ version 1.0-12 [@laliberte2014] with the method ward.D2 used for non-squared distances [@murtagh2014].
-All the numerical traits were previously scaled.
+For this, we calculated the distance of the different functional traits with the function _gowdis_ from the package _FD_ version 1.0-12 [@laliberte2014] with the method _ward.D2_ used for non-squared distances [@murtagh2014].
+All numerical traits were previously scaled.
 Finally, we applied a hierarchical cluster analysis with the function _hclust_ from the _R_ stats package version 4.0.5 and calculated the optimal number of clusters with the function _kgs_ from the package _maptree_ version 1.4-7 [@white2009].
 
-Second, pollinators were grouped into functional groups based on taxonomic rank.
-We opted to divide pollinators on the taxonomic rank level and not with functional traits because (i) the main taxonomic orders differ in form and behaviour and (ii) the lower complexity of higher taxonomic ranks (i.e., pollinators had 6 orders versus plants that had 38).
-Hence, we grouped pollinators into 6 functional groups: (i) Hymenoptera-Anthophila (bees), (ii) Hymenoptera-non-Anthophila (other non-bee Hymenoptera), (iii) Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera and (vi) Coleoptera.
+Second, floral visitors were grouped into functional groups based on taxonomic rank.
+We opted to divide floral visitors on the taxonomic rank level and not with functional traits because (i) the main taxonomic orders differ in form and behaviour and (ii) the lower complexity of higher taxonomic ranks (i.e., floral visitors had 6 orders versus plants that had 38).
+Hence, we grouped floral visitors into 6 functional groups that represented the main life strategies: (i) Hymenoptera-Anthophila (bees), (ii) Hymenoptera-non-Anthophila (other non-bee Hymenoptera), (iii) Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera and (vi) Coleoptera.
 
@@
 We calculated the frequency of all motifs up to five nodes (see Figure 1) for each empirical network, by using the _bmotif_ package [@bmotifsimmons2019].
-To control for variation in network size and for the fact that smaller motifs can be nested within larger motifs, the frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains).
-Like [@simmons2020], we just used five-node motifs in our analyses for visualisation, interpretation and computational reasons.
+To control for variation in network size, motif frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains).
+Like @simmons2020, we just used five-node motifs in our analyses for visualisation, interpretation and computational reasons.
 In addition, we also excluded two-node motifs (or links) from our analyses because their normalised frequencies would always equal one.

### 2021-08-06 Draft/Draft.Rmd
Minor edits on the text

@@
 First, plant species were grouped into the optimal number of functional groups that summarized the main plant reproductive strategies.
-This was done with the help of hierarchical cluster analysis by using the trait dataset collated in Lanuza et al., (unpublished) that comprised 1,506 plant species and contained the same 60 plant-pollinator networks used in this study plus some non-weighted and weighted metawebs (see Table S1 Lanuza et al., unpublished).
-This dataset consisted on 8 floral, 4 reproductive and 3 vegetative traits (Table S2).
-We opted to calculate the plant functional groups on this larger set of species because of the higher accuracy when delimiting the functional groups with that many variables @dolnicar2014.
+This was done with the help of hierarchical clustering by using the trait dataset collated in Lanuza et al., (unpublished) that comprised 1,506 plant species and contained the same 60 plant-pollinator networks used in this study plus some non-weighted and weighted metawebs (see Table S1 Lanuza et al., unpublished).
+This dataset consisted on 8 floral, 4 reproductive and 3 vegetative traits excluding the the traits with high percentage of missing values (over 30%; Table S2).
+We opted to calculate the plant functional groups on this larger set of species because of the higher accuracy when delimiting the functional groups with that many variables and species @dolnicar2014.
 For this, we calculated the distance of the different functional traits with the function _gowdis_ from the package _FD_ version 1.0-12 [@laliberte2014] with the method _ward.D2_ used for non-squared distances [@murtagh2014].
 All numerical traits were previously scaled.
-Finally, we applied a hierarchical cluster analysis with the function _hclust_ from the _R_ stats package version 4.0.5 and calculated the optimal number of clusters with the function _kgs_ from the package _maptree_ version 1.4-7 [@white2009].
+Finally, we conducted hierarchical clustering with the function _hclust_ from the _R_ stats package version 4.0.5 and calculated the optimal number of clusters with the function _kgs_ from the package _maptree_ version 1.4-7 [@white2009].
 
@@
 After extracting the motif frequencies from the simulated networks, for each motif type and empirical network, we calculated the percentage of simulated networks whose frequencies were smaller than the ones observed, that is, we estimated the percentile of the observed motif frequencies.
-Motifs whose percentile is close to zero or 100 are under- or over-represented in the empirical networks, respectively, and, thus, they cannot be predicted by connectance and the number of species alone.
+Motifs whose percentile is close to 0 or 100 are under- or over-represented in the empirical networks, respectively, and thus they cannot be predicted by connectance and the number of species alone.
 To summarize general patterns across networks, we used an intercept-only linear mixed model (LMM) per motif, where the response variable was the observed motif percentile per network.

### 2021-08-09 Draft/Draft.Rmd
Some edits... I keep later with this

@@
 
-We have compiled 60 plant-pollinator networks from 18 different studies (Table S1).
+We have compiled 60 plant-pollinator networks from 18 different studies (**Table S1**).
 All studies sampled plant-pollinator interactions in natural systems and were selected based on wide geographical coverage and the presence of interaction frequency as a measure of interaction strength.
@@
 
-First, plant species were grouped into the optimal number of functional groups that summarized the main plant reproductive strategies.
-This was done with the help of hierarchical clustering by using the trait dataset collated in Lanuza et al., (unpublished) that comprised 1,506 plant species and contained the same 60 plant-pollinator networks used in this study plus some non-weighted and weighted metawebs (see Table S1 Lanuza et al., unpublished).
-This dataset consisted on 8 floral, 4 reproductive and 3 vegetative traits excluding the the traits with high percentage of missing values (over 30%; Table S2).
-We opted to calculate the plant functional groups on this larger set of species because of the higher accuracy when delimiting the functional groups with that many variables and species @dolnicar2014.
-For this, we calculated the distance of the different functional traits with the function _gowdis_ from the package _FD_ version 1.0-12 [@laliberte2014] with the method _ward.D2_ used for non-squared distances [@murtagh2014].
-All numerical traits were previously scaled.
+First, plant species were grouped thorugh hierarchical clustering into the optimal number of functional groups that summarized the main plant reproductive strategies.
+For this, we used the trait dataset collated in Lanuza et al., (unpublished) that comprised 1,506 plant species and contained the same 60 plant-pollinator networks used in this study plus some non-weighted and weighted metawebs (see **Table S1** Lanuza et al., unpublished).
+This dataset consisted on 8 floral, 4 reproductive and 3 vegetative traits excluding traits with high percentage of missing values (over 30%; **Table S2**).
+We opted to calculate the plant functional groups on this larger set of species because of the higher accuracy when delimiting functional groups with that many variables and species @dolnicar2014.
+Previous to the clustering analysis, we calculated on the qualitative and scaled quantitative variables the distance between the different functional traits with the function _gowdis_ with the method _ward.D2_ from the package _FD_ version 1.0-12 [@laliberte2014].
 Finally, we conducted hierarchical clustering with the function _hclust_ from the _R_ stats package version 4.0.5 and calculated the optimal number of clusters with the function _kgs_ from the package _maptree_ version 1.4-7 [@white2009].
@@
 Second, floral visitors were grouped into functional groups based on taxonomic rank.
-We opted to divide floral visitors on the taxonomic rank level and not with functional traits because (i) the main taxonomic orders differ in form and behaviour and (ii) the lower complexity of higher taxonomic ranks (i.e., floral visitors had 6 orders versus plants that had 38).
+We opted to divide floral visitors on the taxonomic rank level and not with functional traits because (i) the main taxonomic orders differ in form and behaviour and (ii) have lower complexity of higher taxonomic ranks (i.e., floral visitors had 6 orders versus plants that had 38).
 Hence, we grouped floral visitors into 6 functional groups that represented the main life strategies: (i) Hymenoptera-Anthophila (bees), (ii) Hymenoptera-non-Anthophila (other non-bee Hymenoptera), (iii) Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera and (vi) Coleoptera.
@@
 To assess the significance of the observed frequencies, we created 1,000 simulated networks for each binary network using the _nullmodel_ function and the _vaznull_ model in the _bipartite_ package [@dormann2009].
-Generated networks had the same number of plants and pollinators, as well as the same connectance of their corresponding empirical networks.
-After extracting the motif frequencies from the simulated networks, for each motif type and empirical network, we calculated the percentage of simulated networks whose frequencies were smaller than the ones observed, that is, we estimated the percentile of the observed motif frequencies.
+Generated networks had the same number of plants and floral visitors, as well as the same connectance of their corresponding empirical networks.
+After extracting the motif frequencies [how?
+Maybe we need to describe it bmotif?](Jose) from the simulated networks, for each motif type and empirical network, we calculated the percentage of simulated networks whose frequencies were smaller than the ones observed, that is, we estimated the percentile of the observed motif frequencies.
 Motifs whose percentile is close to 0 or 100 are under- or over-represented in the empirical networks, respectively, and thus they cannot be predicted by connectance and the number of species alone.
 To summarize general patterns across networks, we used an intercept-only linear mixed model (LMM) per motif, where the response variable was the observed motif percentile per network.
-In these models, we used the study identifiers in Table S1 as a random intercept.
+In these models, we used the study identifiers in **Table S1** as a random intercept.
 By doing so, we obtained estimates of the average motif frequency, in which we controlled the variation at the study level.
@@
 
-To test the effect of singletones on the frequencies of motif and those of functional groups' positions, in Appendices XXX, we applied the previous analyzes to the robust versions of the networks in table S1, namely: networks that, prior to binarization, only contained interactions whose frequency was greater than one (64.98% of interactions).
+To test the effect of singletones on the motif frequencies and motif functional groups' positions, we applied the previous analyses to the same set of networks (**Table S1**) but considering only interactions whose frequency was greater than one (64.98% of interactions; see **Figures S3 and S4**).
 
@@
 
-The hierarchical cluster analysis divided the dataset with 1506 species and 15 traits into five different clusters with different and overlapping characteristics (Figure S1 and Figure S2).
-The subset of plant species used in this study (N = 503) were distributed evenly across these different larger five groups (see subset of species labels within cluster in Figure S1).
+The hierarchical cluster analysis divided the dataset with 1506 species and 15 traits into five different clusters with different and overlapping characteristics (**Figure S3** and **Figure S4**).
+The subset of plant species used in this study (N = 503) were distributed evenly across these different larger five groups (see subset of species labels within cluster in **Figure S3**).
 The first cluster was dominated by herbs with hermaphrodite flowers with high levels of autonomous selfing and we we refer to this group as "selfing herbs".
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=13, fig.cap="Figure S1.
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="Figure S1.
+Comparison of the motif frequencies between empirical and simulated networks.
+Average percentages of motifs close to 0 and 100 indicate under- and over- representation in empirical networks, after removing non-robust links, that is, interactions whose frequency was equal to one.
+The different motifs are coloured by the mean path length as done in @simmons2020.", fig.width=9,fig.height=5}
+library(lme4)
+library(nlme)
+library(tidyverse)
+source("../Scripts/Scripts_Alfonso/add_study_id.R")
+d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models_NOSING/Motifs_frequency_percentile_NOSING.csv")
+d <- add_study_id(d)
+#str(d)
+#head(d)
+
+#ggplot(d %>% filter(motif != 1), aes(percentil_sizeclass))+
+#  geom_histogram(color="black", fill="white")+
+#  facet_wrap(~motif)+
+#  theme_bw()+
+#  labs(x="Sizeclass percentile")
+#
+# Motifs tend to be over- and under-represensented in real networks
+
+# Mean percentile and SE taking into account the study system
+motif_codes <- d %>% filter(motif != 1) %>% # We remove links (motif code: 1)
+  select(motif) %>% unique() %>% pull()
+motif_means <- tibble(motif = motif_codes)
+motif_means$mean <- NA
+motif_means$SE <- NA
+
+for(i.motif in 1:length(motif_codes)){
+
+  m <- lmer(percentil_sizeclass ~ 1+(1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
+            data = subset(d, motif == motif_codes[i.motif]))
+
+  motif_means$mean[i.motif] <- fixed.effects(m) %>% unname()
+  motif_means$SE[i.motif] <- sqrt(diag(vcov(m)))
+
+}
+
+#Add categories based on path length set by Simmons 2021 et al., Functional Ecology
+d$Broad_categories[d$motif==2 | d$motif==7 | d$motif==17 | d$motif==3|d$motif==4|d$motif==8] <- "Fan"
+
+d$Broad_categories[d$motif==15 | d$motif==11] <- "Medium-weak"
+
+d$Broad_categories[d$motif==6 | d$motif==16 |  d$motif==12] <- "Strong"
+
+d$Broad_categories[d$motif==5 | d$motif==9 |  d$motif==14|  d$motif==13|  d$motif==10] <- "Weak"
+
+#order the categories from short to long path length
+d$Broad_categories <- factor(d$Broad_categories, levels = c("Strong", "Fan", "Medium-weak", "Weak"))
+
+ggplot(NULL) + 
+  geom_point(data = d %>% filter(motif != 1),
+             aes(y=as.factor(motif), x=100*percentil_sizeclass, 
+                 color = as.factor(Broad_categories)),
+             position = "jitter",alpha=0.5)+
+  geom_errorbar(data = motif_means,aes(y = as.factor(motif), xmin=100*(mean-SE), xmax=100*(mean+SE)), 
+                width=1.0,size=1)+
+  geom_point(data = motif_means,aes(y = as.factor(motif), x=100*mean), 
+                size=2)+
+  labs(y="Motif", x = "Percentile (%)",colour="Path length classification")+
+  theme_bw() + scale_color_manual(labels = c('Strong' = expression(paste("Complete (", bar(x), " = 1.38)")),'Fan' = expression(paste("Fan (", bar(x), " = 1.48)")), 'Medium-weak' = expression(paste("Asymmetric complete (", bar(x), " = 1.60)")), "Weak" =expression(paste("Core-peripheral (", bar(x), " = 1.85)"))), name = "Path length classification",values = c("grey25","springgreen4","sienna2","goldenrod2"),guide = guide_legend(title.position = "top",nrow = 2)) +
+theme(legend.text.align = 0)+
+  theme(legend.position="bottom")
+
+#Trying to maintain a gradient from low to high in colors
+
+#Fig 1 Should be a dot plot (or forest plot) of the mean +- SE of the 15 motifs.
+#NICE! Can we put motifs in Y axes, and % in X?
+```
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="Figure S2.
+Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions, after removing non-robust links, that is, interactions whose frequency was equal to one.
+The different motif positions are dividied by the average path length clasification by @simmons2020."}
+
+library(lme4)
+library(nlme)
+library(tidyverse)
+library(stringi)
+source("../Scripts/Scripts_Alfonso/add_study_id.R")
+
+#############################################
+# EXTRACT MEAN VALUES
+#############################################
+
+all_position_percentiles <- read_csv("../Data/Csv/Motifs_positions_and_null_models_NOSING/GF_positions_frequency_percentile_NOSING.csv")
+
+all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
+                                                              "[0-9]+") %>% as.numeric()
+
+all_position_percentiles <- add_study_id(all_position_percentiles)
+#str(all_position_percentiles)
+#head(all_position_percentiles)
+
+list_plants_FG <- as.character(1:10)
+
+plant_position_percentiles_filtered <- all_position_percentiles %>% 
+  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
+         !is.na(expected_freq_its_GF)) #ME DA ERROR
+pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
+  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
+         !is.na(expected_freq_its_GF))
+
+# Plants-------------
+
+# Mean percentile and SE taking into account the study system
+plant_codes <- plant_position_percentiles_filtered$position %>% unique()
+plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
+plant_means$mean <- NA
+plant_means$SE <- NA
+
+for(i.pos in 1:length(plant_codes)){
+
+  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
+            data = plant_position_percentiles_filtered %>%
+              filter(position == plant_codes[i.pos]))
+
+  temp <- fixed.effects(m) %>% unname()
+  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
+                                                                    temp[1]+temp[2],
+                                                                    temp[1]+temp[3],
+                                                                    temp[1]+temp[4],
+                                                                    temp[1]+temp[5]) ## to get real means per FG
+  temp <- sqrt(diag(vcov(m)))
+  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
+                                                                  temp[1]+temp[2],
+                                                                  temp[1]+temp[3],
+                                                                  temp[1]+temp[4],
+                                                                  temp[1]+temp[5])
+
+}
+
+# Pollinators--------
+
+# Mean percentile and SE taking into account the study system
+pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
+pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
+pollinator_means$mean <- NA
+pollinator_means$SE <- NA
+pollinator_means_reordered <- NULL
+
+for(i.pos in 1:length(pollinator_codes)){
+
+  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
+            data = pollinator_position_percentiles_filtered %>%
+              filter(position == pollinator_codes[i.pos]),
+            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
+
+  temp <- fixed.effects(m) %>% unname()
+  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)
+
+  pollinator_means_aux$mean <- c(temp[1],
+                                 temp[1]+temp[2],
+                                 temp[1]+temp[3],
+                                 temp[1]+temp[4],
+                                 temp[1]+temp[5],
+                                 temp[1]+temp[6],
+                                 temp[1]+temp[7],
+                                 temp[1]+temp[8],
+                                 temp[1]+temp[9]) ## to get real means per FG
+
+  temp <- sqrt(diag(vcov(m)))
+  pollinator_means_aux$SE <- c(temp[1],
+                               temp[1]+temp[2],
+                               temp[1]+temp[3],
+                               temp[1]+temp[4],
+                               temp[1]+temp[5],
+                               temp[1]+temp[6],
+                               temp[1]+temp[7],
+                               temp[1]+temp[8],
+                               temp[1]+temp[9])
+
+  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)
+
+}
+
+# There are lower limits (mean - SE) smaller than 0 (see Other insects)
+# We set the lower limit of those error bars to zero
+
+pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
+pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
+
+#############################################
+# ADDING BROAD MOTIF CATEGORIES TO POSITIONS
+#############################################
+
+motifs_raw_data <- read_csv("../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
+
+motifs_raw_data$Broad_categories <- NA
+
+motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(5,9,14,13,10)] <- "Core-peripherical"
+motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(6,16,12)] <- "Complete"
+motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(2,3,7,4,17,8)] <- "Fan"
+motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(15,11)] <- "Asymmetric complete"
+
+motifs_raw_data$plant <- gsub("[^0-9.-]", "", motifs_raw_data$plant)
+motifs_raw_data$pollinator <- gsub("[^0-9.-]", "", motifs_raw_data$pollinator)
+motifs_raw_data$plant <- as.numeric(motifs_raw_data$plant)
+motifs_raw_data$pollinator <- as.numeric(motifs_raw_data$pollinator)
+motifs_raw_data <- motifs_raw_data %>% filter(!is.na(Broad_categories))
+
+fan_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
+core_per_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
+complete_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
+asymm_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
+
+pollinator_means_reordered$Broad_categories <- NA
+
+pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% fan_pollinator] <- "Fan" 
+pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% asymm_pollinator] <- "Medium-weak" 
+pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% complete_pollinator] <- "Strong" 
+pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% core_per_pollinator] <- "Weak"
+
+fan_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
+core_per_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
+complete_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
+asymm_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
+
+plant_means$Broad_categories <- NA
+
+plant_means$Broad_categories[plant_means$position %in% fan_plant] <- "Fan" 
+plant_means$Broad_categories[plant_means$position %in% asymm_plant] <- "Medium-weak" 
+plant_means$Broad_categories[plant_means$position %in% complete_plant] <- "Strong" 
+plant_means$Broad_categories[plant_means$position %in% core_per_plant] <- "Weak"
+
+########################################
+# CREATE HEATMAPS
+########################################
+
+library(ComplexHeatmap)
+
+# PLANTS-----
+
+# Prepare data for heatmap
+heat_plants_aux <- plant_means %>% spread(Node_FG,mean) %>% select(-SE)
+
+heat_plants <- heat_plants_aux %>%
+  group_by(position,Broad_categories) %>% 
+  summarise_all(sum,na.rm = T)
+
+heat_plants_fan <- heat_plants %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
+  as.matrix()
+
+rownames(heat_plants_fan) <- heat_plants_fan[,1]
+
+heat_plants_Weak <- heat_plants %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
+  as.matrix()
+
+rownames(heat_plants_Weak) <- heat_plants_Weak[,1]
+
+heat_plants_Strong <- heat_plants %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
+  as.matrix()
+
+rownames(heat_plants_Strong) <- heat_plants_Strong[,1]
+
+heat_plants_Medium_weak <- heat_plants %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
+  as.matrix()
+
+rownames(heat_plants_Medium_weak) <- heat_plants_Medium_weak[,1]
+
+# POLLINATORS-----------
+
+filter_rare_groups <- T
+
+if(filter_rare_groups == T){
+  heat_pollinators_aux <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds",
+                                                                                "Lizards",
+                                                                                "Other_insects")) %>% 
+    spread(Node_FG,mean) %>% select(-SE,-lower)
+
+  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bee",            
+                                      "Coleoptera","Lepidoptera","Non-bee\nHymenoptera", 
+                                      "Non-syrphids\ndiptera","Syrphids")
+}else{
+  heat_pollinators_aux <- pollinator_means_reordered %>% spread(Node_FG,mean) %>% select(-SE,-lower)
+
+  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bee","Birds",            
+                                      "Coleoptera","Lepidoptera","Lizards","Non-bee\nHymenoptera", 
+                                      "Non-syrphids\ndiptera","Other insects","Syrphids")
+}
+
+heat_pollinators <- heat_pollinators_aux %>%
+  group_by(position,Broad_categories) %>% 
+  summarise_all(sum,na.rm = T)
+
+heat_pollinators_fan <- heat_pollinators %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
+  as.matrix()
+
+rownames(heat_pollinators_fan) <- heat_pollinators_fan[,1]
+
+heat_pollinators_Weak <- heat_pollinators %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
+  as.matrix()
+
+rownames(heat_pollinators_Weak) <- heat_pollinators_Weak[,1]
+
+heat_pollinators_Strong <- heat_pollinators %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
+  as.matrix()
+
+rownames(heat_pollinators_Strong) <- heat_pollinators_Strong[,1]
+
+heat_pollinators_Medium_weak <- heat_pollinators %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
+  as.matrix()
+
+rownames(heat_pollinators_Medium_weak) <- heat_pollinators_Medium_weak[,1]
+
+##################
+
+#Do not know how to handle this multiplot for creating a panel
+
+# I'm going to create the 4 plots in one, 
+# I'm not sure that the grouping of the functional group is correct
+# when is done separately
+
+#sorry for the mess of libraries that I do below
+
+ #Prepare first pollinators
+
+library(tidyr)
+library(data.table)
+long <- melt(setDT(heat_pollinators), id.vars = c("position","Broad_categories"), variable.name = "guilds")
+
+long_1 <- long %>% select(-Broad_categories)
+
+library(reshape2)
+long_m <- acast(long_1, position~guilds, value.var="value")
+
+#set manually the divisions, so far this is the best way I have seen to split the rows by categories
+
+r_split <- c(rep(c("Fan"), 3),rep(c("Core-peripheral"), 2),"Complete",rep(c("Fan"),2),rep(c("Core-peripheral"), 4),
+             rep(c("Asymmetric complete"), 2), "Complete", rep(c("Core-peripheral"), 3),rep(c("Asymmetric complete"), 2),
+             "Complete", "Fan")
+
+#set order of labels that avoids overlapping
+r_split <- factor(r_split, levels=c("Core-peripheral","Complete","Fan","Asymmetric complete"))
+
+#plat a bit with colors, a bit of a more complex set but looks nicer
+library(circlize)
+col_fun = colorRamp2(c(0.05644663,0.25, 0.4673256,0.75, 0.8782047), c("blue","cadetblue3", "azure2", "gold","red"))
+
+h_pol <- Heatmap(long_m, name = "Mean\npercentile", row_split=r_split,cluster_row_slices = FALSE, 
+                 column_title = "Pollinator functional groups",row_names_gp = gpar(fontsize = 10),
+                 col = col_fun,column_names_rot = 45,  column_names_gp = grid::gpar(fontsize = 10),
+                 column_title_gp = gpar(fontsize = 15, fontface = "bold"),
+                 row_title_gp = gpar(fontsize = 10, fontface = "bold"))
+
+ #Prepare plants
+
+#long format
+long_plants <- melt(setDT(heat_plants), id.vars = c("position","Broad_categories"), variable.name = "Functional_groups")
+
+#filter for creating matrix
+long_plants_1 <- long_plants %>% select(-Broad_categories)
+
+#set better colnames
+long_plants_1$Functional_groups <- as.character(long_plants_1$Functional_groups)
+
+long_plants_1$Functional_groups[long_plants_1$Functional_groups==1] <- "Selfing herbs" 
+long_plants_1$Functional_groups[long_plants_1$Functional_groups==2] <- "Small outcrossing\nperennials" 
+long_plants_1$Functional_groups[long_plants_1$Functional_groups==3] <- "Self-incomp. perennials\nwith large flowers" 
+long_plants_1$Functional_groups[long_plants_1$Functional_groups==4] <- "Tall plants with small\nunisexual flowers" 
+long_plants_1$Functional_groups[long_plants_1$Functional_groups==5] <- "Short-lived outcrossers with\nlong zygomorphic flowers"
+
+long_plants_1$Functional_groups <- factor(long_plants_1$Functional_groups, levels=c("Selfing herbs",
+"Small outcrossing\nperennials" ,"Self-incomp. perennials\nwith large flowers",
+"Tall plants with small\nunisexual flowers" ,"Short-lived outcrossers with\nlong zygomorphic flowers" ))
+
+#create matrix with reshape
+long_plants_m <- acast(long_plants_1, position~Functional_groups, value.var="value")
+
+r_split_plants <- c(rep(c("Fan"), 3),rep(c("Core-peripheral"), 2),"Complete",rep(c("Fan"),2),rep(c("Core-peripheral"), 3),
+                    rep(c("Asymmetric complete"), 2), "Complete", rep(c("Core-peripheral"), 4),rep(c("Asymmetric complete"), 2),
+                    "Complete", "Fan")
+
+r_split_plants <- factor(r_split, levels=c("Core-peripheral","Complete","Fan","Asymmetric complete"))
+
+h_plan <- Heatmap(long_plants_m, name = "Mean\npercentile", row_split=r_split_plants,cluster_row_slices = F, 
+                  column_title = "Plant functional groups",row_names_gp = gpar(fontsize = 10),col = col_fun,column_names_rot = 45,  
+                  column_names_gp = grid::gpar(fontsize = 10),column_title_gp = gpar(fontsize = 15, fontface = "bold"),
+                  row_title_gp = gpar(fontsize = 10, fontface = "bold"))
+
+library(patchwork)
+ht_list <- h_pol+h_plan
+
+draw(ht_list, auto_adjust = FALSE, cluster_rows = F)
+
+```
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=13, fig.cap="Figure S3.
 Plant functional group composition separated in qualitative and quantitative variables.
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=13, fig.cap="Figure S2.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=13, fig.cap="Figure S4.
 Hierarchical clustering dendrogram with the branches coloured by the optimal number of clusters (5).
@@
 ```
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="Figure S3.
-Comparison of the motif frequencies between empirical and simulated networks.
-Average percentages of motifs close to 0 and 100 indicate under- and over- representation in empirical networks, after removing non-robust links, that is, interactions whose frequency was equal to one.
-The different motifs are coloured by the mean path length as done in @simmons2020.", fig.width=9,fig.height=5}
-library(lme4)
-library(nlme)
-library(tidyverse)
-source("../Scripts/Scripts_Alfonso/add_study_id.R")
-d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models_NOSING/Motifs_frequency_percentile_NOSING.csv")
-d <- add_study_id(d)
-#str(d)
-#head(d)
-
-#ggplot(d %>% filter(motif != 1), aes(percentil_sizeclass))+
-#  geom_histogram(color="black", fill="white")+
-#  facet_wrap(~motif)+
-#  theme_bw()+
-#  labs(x="Sizeclass percentile")
-#
-# Motifs tend to be over- and under-represensented in real networks
-
-# Mean percentile and SE taking into account the study system
-motif_codes <- d %>% filter(motif != 1) %>% # We remove links (motif code: 1)
-  select(motif) %>% unique() %>% pull()
-motif_means <- tibble(motif = motif_codes)
-motif_means$mean <- NA
-motif_means$SE <- NA
-
-for(i.motif in 1:length(motif_codes)){
-
-  m <- lmer(percentil_sizeclass ~ 1+(1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = subset(d, motif == motif_codes[i.motif]))
-
-  motif_means$mean[i.motif] <- fixed.effects(m) %>% unname()
-  motif_means$SE[i.motif] <- sqrt(diag(vcov(m)))
-
-}
-
-#Add categories based on path length set by Simmons 2021 et al., Functional Ecology
-d$Broad_categories[d$motif==2 | d$motif==7 | d$motif==17 | d$motif==3|d$motif==4|d$motif==8] <- "Fan"
-
-d$Broad_categories[d$motif==15 | d$motif==11] <- "Medium-weak"
-
-d$Broad_categories[d$motif==6 | d$motif==16 |  d$motif==12] <- "Strong"
-
-d$Broad_categories[d$motif==5 | d$motif==9 |  d$motif==14|  d$motif==13|  d$motif==10] <- "Weak"
-
-#order the categories from short to long path length
-d$Broad_categories <- factor(d$Broad_categories, levels = c("Strong", "Fan", "Medium-weak", "Weak"))
-
-ggplot(NULL) + 
-  geom_point(data = d %>% filter(motif != 1),
-             aes(y=as.factor(motif), x=100*percentil_sizeclass, 
-                 color = as.factor(Broad_categories)),
-             position = "jitter",alpha=0.5)+
-  geom_errorbar(data = motif_means,aes(y = as.factor(motif), xmin=100*(mean-SE), xmax=100*(mean+SE)), 
-                width=1.0,size=1)+
-  geom_point(data = motif_means,aes(y = as.factor(motif), x=100*mean), 
-                size=2)+
-  labs(y="Motif", x = "Percentile (%)",colour="Path length classification")+
-  theme_bw() + scale_color_manual(labels = c('Strong' = expression(paste("Complete (", bar(x), " = 1.38)")),'Fan' = expression(paste("Fan (", bar(x), " = 1.48)")), 'Medium-weak' = expression(paste("Asymmetric complete (", bar(x), " = 1.60)")), "Weak" =expression(paste("Core-peripheral (", bar(x), " = 1.85)"))), name = "Path length classification",values = c("grey25","springgreen4","sienna2","goldenrod2"),guide = guide_legend(title.position = "top",nrow = 2)) +
-theme(legend.text.align = 0)+
-  theme(legend.position="bottom")
-
-#Trying to maintain a gradient from low to high in colors
-
-#Fig 1 Should be a dot plot (or forest plot) of the mean +- SE of the 15 motifs.
-#NICE! Can we put motifs in Y axes, and % in X?
-```
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="Figure S4.
-Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions, after removing non-robust links, that is, interactions whose frequency was equal to one.
-The different motif positions are dividied by the average path length clasification by @simmons2020."}
-
-library(lme4)
-library(nlme)
-library(tidyverse)
-library(stringi)
-source("../Scripts/Scripts_Alfonso/add_study_id.R")
-
-#############################################
-# EXTRACT MEAN VALUES
-#############################################
-
-all_position_percentiles <- read_csv("../Data/Csv/Motifs_positions_and_null_models_NOSING/GF_positions_frequency_percentile_NOSING.csv")
-
-all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
-                                                              "[0-9]+") %>% as.numeric()
-
-all_position_percentiles <- add_study_id(all_position_percentiles)
-#str(all_position_percentiles)
-#head(all_position_percentiles)
-
-list_plants_FG <- as.character(1:10)
-
-plant_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF)) #ME DA ERROR
-pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF))
-
-# Plants-------------
-
-# Mean percentile and SE taking into account the study system
-plant_codes <- plant_position_percentiles_filtered$position %>% unique()
-plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-plant_means$mean <- NA
-plant_means$SE <- NA
-
-for(i.pos in 1:length(plant_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
-            data = plant_position_percentiles_filtered %>%
-              filter(position == plant_codes[i.pos]))
-
-  temp <- fixed.effects(m) %>% unname()
-  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
-                                                                    temp[1]+temp[2],
-                                                                    temp[1]+temp[3],
-                                                                    temp[1]+temp[4],
-                                                                    temp[1]+temp[5]) ## to get real means per FG
-  temp <- sqrt(diag(vcov(m)))
-  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
-                                                                  temp[1]+temp[2],
-                                                                  temp[1]+temp[3],
-                                                                  temp[1]+temp[4],
-                                                                  temp[1]+temp[5])
-
-}
-
-# Pollinators--------
-
-# Mean percentile and SE taking into account the study system
-pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
-pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-pollinator_means$mean <- NA
-pollinator_means$SE <- NA
-pollinator_means_reordered <- NULL
-
-for(i.pos in 1:length(pollinator_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = pollinator_position_percentiles_filtered %>%
-              filter(position == pollinator_codes[i.pos]),
-            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
-
-  temp <- fixed.effects(m) %>% unname()
-  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)
-
-  pollinator_means_aux$mean <- c(temp[1],
-                                 temp[1]+temp[2],
-                                 temp[1]+temp[3],
-                                 temp[1]+temp[4],
-                                 temp[1]+temp[5],
-                                 temp[1]+temp[6],
-                                 temp[1]+temp[7],
-                                 temp[1]+temp[8],
-                                 temp[1]+temp[9]) ## to get real means per FG
-
-  temp <- sqrt(diag(vcov(m)))
-  pollinator_means_aux$SE <- c(temp[1],
-                               temp[1]+temp[2],
-                               temp[1]+temp[3],
-                               temp[1]+temp[4],
-                               temp[1]+temp[5],
-                               temp[1]+temp[6],
-                               temp[1]+temp[7],
-                               temp[1]+temp[8],
-                               temp[1]+temp[9])
-
-  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)
-
-}
-
-# There are lower limits (mean - SE) smaller than 0 (see Other insects)
-# We set the lower limit of those error bars to zero
-
-pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
-pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
-
-#############################################
-# ADDING BROAD MOTIF CATEGORIES TO POSITIONS
-#############################################
-
-motifs_raw_data <- read_csv("../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-motifs_raw_data$Broad_categories <- NA
-
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(5,9,14,13,10)] <- "Core-peripherical"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(6,16,12)] <- "Complete"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(2,3,7,4,17,8)] <- "Fan"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(15,11)] <- "Asymmetric complete"
-
-motifs_raw_data$plant <- gsub("[^0-9.-]", "", motifs_raw_data$plant)
-motifs_raw_data$pollinator <- gsub("[^0-9.-]", "", motifs_raw_data$pollinator)
-motifs_raw_data$plant <- as.numeric(motifs_raw_data$plant)
-motifs_raw_data$pollinator <- as.numeric(motifs_raw_data$pollinator)
-motifs_raw_data <- motifs_raw_data %>% filter(!is.na(Broad_categories))
-
-fan_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-pollinator_means_reordered$Broad_categories <- NA
-
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% fan_pollinator] <- "Fan" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% asymm_pollinator] <- "Medium-weak" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% complete_pollinator] <- "Strong" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% core_per_pollinator] <- "Weak"
-
-fan_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-plant_means$Broad_categories <- NA
-
-plant_means$Broad_categories[plant_means$position %in% fan_plant] <- "Fan" 
-plant_means$Broad_categories[plant_means$position %in% asymm_plant] <- "Medium-weak" 
-plant_means$Broad_categories[plant_means$position %in% complete_plant] <- "Strong" 
-plant_means$Broad_categories[plant_means$position %in% core_per_plant] <- "Weak"
-
-########################################
-# CREATE HEATMAPS
-########################################
-
-library(ComplexHeatmap)
-
-# PLANTS-----
-
-# Prepare data for heatmap
-heat_plants_aux <- plant_means %>% spread(Node_FG,mean) %>% select(-SE)
-
-heat_plants <- heat_plants_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-heat_plants_fan <- heat_plants %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_fan) <- heat_plants_fan[,1]
-
-heat_plants_Weak <- heat_plants %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Weak) <- heat_plants_Weak[,1]
-
-heat_plants_Strong <- heat_plants %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Strong) <- heat_plants_Strong[,1]
-
-heat_plants_Medium_weak <- heat_plants %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Medium_weak) <- heat_plants_Medium_weak[,1]
-
-# POLLINATORS-----------
-
-filter_rare_groups <- T
-
-if(filter_rare_groups == T){
-  heat_pollinators_aux <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds",
-                                                                                "Lizards",
-                                                                                "Other_insects")) %>% 
-    spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bee",            
-                                      "Coleoptera","Lepidoptera","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\ndiptera","Syrphids")
-}else{
-  heat_pollinators_aux <- pollinator_means_reordered %>% spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bee","Birds",            
-                                      "Coleoptera","Lepidoptera","Lizards","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\ndiptera","Other insects","Syrphids")
-}
-
-heat_pollinators <- heat_pollinators_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-heat_pollinators_fan <- heat_pollinators %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_fan) <- heat_pollinators_fan[,1]
-
-heat_pollinators_Weak <- heat_pollinators %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Weak) <- heat_pollinators_Weak[,1]
-
-heat_pollinators_Strong <- heat_pollinators %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Strong) <- heat_pollinators_Strong[,1]
-
-heat_pollinators_Medium_weak <- heat_pollinators %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Medium_weak) <- heat_pollinators_Medium_weak[,1]
-
-##################
-
-#Do not know how to handle this multiplot for creating a panel
-
-# I'm going to create the 4 plots in one, 
-# I'm not sure that the grouping of the functional group is correct
-# when is done separately
-
-#sorry for the mess of libraries that I do below
-
- #Prepare first pollinators
-
-library(tidyr)
-library(data.table)
-long <- melt(setDT(heat_pollinators), id.vars = c("position","Broad_categories"), variable.name = "guilds")
-
-long_1 <- long %>% select(-Broad_categories)
-
-library(reshape2)
-long_m <- acast(long_1, position~guilds, value.var="value")
-
-#set manually the divisions, so far this is the best way I have seen to split the rows by categories
-
-r_split <- c(rep(c("Fan"), 3),rep(c("Core-peripheral"), 2),"Complete",rep(c("Fan"),2),rep(c("Core-peripheral"), 4),
-             rep(c("Asymmetric complete"), 2), "Complete", rep(c("Core-peripheral"), 3),rep(c("Asymmetric complete"), 2),
-             "Complete", "Fan")
-
-#set order of labels that avoids overlapping
-r_split <- factor(r_split, levels=c("Core-peripheral","Complete","Fan","Asymmetric complete"))
-
-#plat a bit with colors, a bit of a more complex set but looks nicer
-library(circlize)
-col_fun = colorRamp2(c(0.05644663,0.25, 0.4673256,0.75, 0.8782047), c("blue","cadetblue3", "azure2", "gold","red"))
-
-h_pol <- Heatmap(long_m, name = "Mean\npercentile", row_split=r_split,cluster_row_slices = FALSE, 
-                 column_title = "Pollinator functional groups",row_names_gp = gpar(fontsize = 10),
-                 col = col_fun,column_names_rot = 45,  column_names_gp = grid::gpar(fontsize = 10),
-                 column_title_gp = gpar(fontsize = 15, fontface = "bold"),
-                 row_title_gp = gpar(fontsize = 10, fontface = "bold"))
-
- #Prepare plants
-
-#long format
-long_plants <- melt(setDT(heat_plants), id.vars = c("position","Broad_categories"), variable.name = "Functional_groups")
-
-#filter for creating matrix
-long_plants_1 <- long_plants %>% select(-Broad_categories)
-
-#set better colnames
-long_plants_1$Functional_groups <- as.character(long_plants_1$Functional_groups)
-
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==1] <- "Selfing herbs" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==2] <- "Small outcrossing\nperennials" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==3] <- "Self-incomp. perennials\nwith large flowers" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==4] <- "Tall plants with small\nunisexual flowers" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==5] <- "Short-lived outcrossers with\nlong zygomorphic flowers"
-
-long_plants_1$Functional_groups <- factor(long_plants_1$Functional_groups, levels=c("Selfing herbs",
-"Small outcrossing\nperennials" ,"Self-incomp. perennials\nwith large flowers",
-"Tall plants with small\nunisexual flowers" ,"Short-lived outcrossers with\nlong zygomorphic flowers" ))
-
-#create matrix with reshape
-long_plants_m <- acast(long_plants_1, position~Functional_groups, value.var="value")
-
-r_split_plants <- c(rep(c("Fan"), 3),rep(c("Core-peripheral"), 2),"Complete",rep(c("Fan"),2),rep(c("Core-peripheral"), 3),
-                    rep(c("Asymmetric complete"), 2), "Complete", rep(c("Core-peripheral"), 4),rep(c("Asymmetric complete"), 2),
-                    "Complete", "Fan")
-
-r_split_plants <- factor(r_split, levels=c("Core-peripheral","Complete","Fan","Asymmetric complete"))
-
-h_plan <- Heatmap(long_plants_m, name = "Mean\npercentile", row_split=r_split_plants,cluster_row_slices = F, 
-                  column_title = "Plant functional groups",row_names_gp = gpar(fontsize = 10),col = col_fun,column_names_rot = 45,  
-                  column_names_gp = grid::gpar(fontsize = 10),column_title_gp = gpar(fontsize = 15, fontface = "bold"),
-                  row_title_gp = gpar(fontsize = 10, fontface = "bold"))
-
-library(patchwork)
-ht_list <- h_pol+h_plan
-
-draw(ht_list, auto_adjust = FALSE, cluster_rows = F)
-
-```

### 2021-08-09 Draft/Draft.Rmd
Some edits

@@
 We have compiled 60 plant-pollinator networks from 18 different studies (**Table S1**).
-All studies sampled plant-pollinator interactions in natural systems and were selected based on wide geographical coverage and the presence of interaction frequency as a measure of interaction strength.
+All studies sampled plant-pollinator interactions in natural systems and were selected based on wide geographical coverage and presence of interaction frequency as a measure of interaction strength.
 In total, there were 503 plant species, 1,111 floral visitors species and 6248 of pairwise interactions registered.
@@
 
-**Plant and pollinator functional groups**
+**Plant and floral visitors functional groups**
 
@@
 
+[I may have to think for better headings to guide through analysis and results, specially the second section](Jose)
+
+_Overall motif patterns_
+
 Following Simmons et al.
@@
 
-We calculated the frequency of all motifs up to five nodes (see Figure 1) for each empirical network, by using the _bmotif_ package [@bmotifsimmons2019].
+We calculated the frequency of all motifs up to five nodes (see **Figure 1**) for each empirical network, by using the _bmotif_ package [@bmotifsimmons2019].
 To control for variation in network size, motif frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains).
@@
 Generated networks had the same number of plants and floral visitors, as well as the same connectance of their corresponding empirical networks.
-After extracting the motif frequencies [how?
-Maybe we need to describe it bmotif?](Jose) from the simulated networks, for each motif type and empirical network, we calculated the percentage of simulated networks whose frequencies were smaller than the ones observed, that is, we estimated the percentile of the observed motif frequencies.
+After extracting the motif frequencies from the simulated networks, for each motif type and empirical network, we calculated the percentage of simulated networks whose frequencies were smaller than the ones observed, that is, we estimated the percentile of the observed motif frequencies.
 Motifs whose percentile is close to 0 or 100 are under- or over-represented in the empirical networks, respectively, and thus they cannot be predicted by connectance and the number of species alone.
@@
 
-Next, we calculated which functional groups were over or under-represented in different motif positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
+_Motif functional groups position_
+
+We calculated which functional groups were over or under-represented in different motif positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
 We extracted the position frequencies of all motifs from three to five nodes for each network and species by using the _bmotif_ package [@bmotifsimmons2019].
 To estimate the position frequencies of each functional group in a given network, we added the frequencies of those species that belong to the group, and then, we normalised the resulting frequencies by dividing the position measure for each group by the total number of times that a group appears in any position within the same motif size class.
-Then, we calculated the percentile of the observed position frequencies for each group and network, just like we did motif frequencies.
+Then, we calculated the percentile of the observed position frequencies for each group and network, just like we did with motif frequencies.
 To outline the general patterns of position frequencies across networks and functional groups, we fit a LMM per motif position, where the response variable was the observed position percentile per network.
@@
 
+[Maybe we need to link this with the plot of the scatterpie](Jose)
+
 Finally, we studied which motif combinations of functional groups (up to five nodes) are over or under-represented in 95% of our empirical networks (57 out of 60 arrangements, due to computational limitations to identify all the nodes in the motifs of the three networks with the highest number of links).
-To do so, for each of the 53,250 possible motif combinations, we estimated the observed and the expected probability of finding that combination in empirical networks, respectively.
+To do so, for each of the 53,250 possible motif combinations, we estimated the observed and the expected probability of finding those combination in empirical networks, respectively.
 Then, we determined whether the observed probabilities are likely to come from the expected probabilities or not.
-To calculate the observed probability of a given combination $i$, $p_i^O$, we divided the number of times that $i$ appears in our set of empirical networks ($n_i^O$) by the sum of the number of times that each possible combination appeared: $p_i^O = n_i^O / \sum_{k=1}^{53,250} n_k^O$, and, consequently, $\sum_{k=1}^{53,250} p_k^O = 1$.
+To calculate the observed probability ($p_i^O$) of functional groups within a motif ($i$; e.g., motif 3, bee + bee + functional group 2), we divided the number of times that $i$ appears in our set of empirical networks ($n_i^O$) by the sum of the number of times that each possible combination appeared: $p_i^O = n_i^O / \sum_{k=1}^{53,250} n_k^O$.
 To estimate the expected probability of a given motif combination $i$, $p_i^E$, firstly, we calculated the probability of finding a given functional group $x$ in the position $\alpha$ of $i$, $p_i(x,\alpha)$.
@@
 
-Once we obtained $p_i^O$ and $p_i^E$, we used simulation to determine whether the former is likely to come from the latter or not, since the large number of possible motif combinations and the small probabilities for some of them advise against using an Exact test of goodness-of-fit or a Chi-square one.
+Once we obtained $p_i^O$ and $p_i^E$, we used simulation to determine whether the former is likely to come from the latter or not, since the large number of possible motif combinations and the small probabilities for some of them advise against using an exact test of goodness-of-fit or a Chi-square one.
 Specifically, we created 1,000 random samples with repetition of possible motif combinations, where each sample contained 10 million elements and, for each combination, the probability of being selected was equal to its expected probability.
@@
 The hierarchical cluster analysis divided the dataset with 1506 species and 15 traits into five different clusters with different and overlapping characteristics (**Figure S3** and **Figure S4**).
-The subset of plant species used in this study (N = 503) were distributed evenly across these different larger five groups (see subset of species labels within cluster in **Figure S3**).
+The subset of plant species used in this study (N = 503) were distributed evenly across these different larger five groups (see subset of the 503 species labels within cluster for all species in **Figure S3**).
 The first cluster was dominated by herbs with hermaphrodite flowers with high levels of autonomous selfing and we we refer to this group as "selfing herbs".
@@
 The third cluster was dominated by also perennial species with a mixed of life forms too and had large self-incompatible hermaphroditic flowers with high number of ovules and we named this group "self-incompatible perennials with large flowers".
-The fourth cluster had the tallest species, highest proportion of shrub and tree life forms, dioecious and monoecious breeding system with small flowers but the highest number of flowers per plant and inflorescence and we refer to this set of species as "tall plants with small unisexual flowers".
+The fourth cluster had the tallest species, highest proportion of shrub and tree life forms, dioecious and monoecious breeding system with small flowers but the highest number of flowers per plant and inflorescences, and, we refer to this set of species as "tall plants with small unisexual flowers".
 Finally, the last cluster of species was dominated by small perennial and shot-lived herbs with long self-compatible zygomorphic flowers unable to self-pollinate and we refer to this group as "short-lived outcrossers with long zygomorphic flowers".
 
-**Overall meso-scale patterns**
+**Overall motif patterns**
 
@@
 
-**Meso-scale functional groups position**
+**Motif functional groups position**
 

### 2021-08-10 Draft/Draft.Rmd
starting with results...

@@
 First, plant species were grouped thorugh hierarchical clustering into the optimal number of functional groups that summarized the main plant reproductive strategies.
-For this, we used the trait dataset collated in Lanuza et al., (unpublished) that comprised 1,506 plant species and contained the same 60 plant-pollinator networks used in this study plus some non-weighted and weighted metawebs (see **Table S1** Lanuza et al., unpublished).
+We used the trait dataset collated in Lanuza et al., (unpublished) that comprised 1,506 plant species and contained the same 60 plant-pollinator networks used in this study plus some non-weighted and weighted metawebs (see **Table S1** Lanuza et al., unpublished).
 This dataset consisted on 8 floral, 4 reproductive and 3 vegetative traits excluding traits with high percentage of missing values (over 30%; **Table S2**).
 We opted to calculate the plant functional groups on this larger set of species because of the higher accuracy when delimiting functional groups with that many variables and species @dolnicar2014.
-Previous to the clustering analysis, we calculated on the qualitative and scaled quantitative variables the distance between the different functional traits with the function _gowdis_ with the method _ward.D2_ from the package _FD_ version 1.0-12 [@laliberte2014].
+Previous to the clustering analysis, we calculated the distance between the different qualitative and scaled quantitative variables with Gower distance wich can handle mixed data [@gower1971].
+For this, we used the function _gowdis_ with method _ward.D2_ from the package _FD_ version 1.0-12 [@laliberte2014].
 Finally, we conducted hierarchical clustering with the function _hclust_ from the _R_ stats package version 4.0.5 and calculated the optimal number of clusters with the function _kgs_ from the package _maptree_ version 1.4-7 [@white2009].
@@
 
+_Plants_
+
 The hierarchical cluster analysis divided the dataset with 1506 species and 15 traits into five different clusters with different and overlapping characteristics (**Figure S3** and **Figure S4**).
@@
 
+_Floral visitors_
+
+[Describe poll funcional groups?](Jose)
+
+[I'm calling them functional groups because is easier to refer as FG to both but maybe is more accurate to refer them as guilds?](Jose)
+
 **Overall motif patterns**
+
+Most motifs were under and over-represented (close to the 1st and 99th percentile, respectively) in the comparison between empirical and simulated networks (**Figure 2**).
+Motifs 3, 5, 9, 10 and 14 were under-represented in empirical networks, that is, all under the 25th percentile and the closest motifs to the 1st percentile.
+Remarkably, four out of five of these motifs belonged to the largest path length classification (i.e., core-peripheral).
+In addition, motifs 2, 6, 7, 16 and 17 were over-represented, all over the 75th percentile and thus the closest to the 99th percentile.
+In contrast to the under-represented motifs, over-represented motifs belonged to the two shortest path length groups (i.e., complete and fan).
+The remaining motifs (i.e., 4, 8, 11, 12, 13, and 15) were between the 25th and 75th percentile with a tendency for most motifs to be over-represented (closest to the 75th percentile).
 
@@
 Average percentages of motifs close to 0 and 100 indicate under- and over- representation in empirical networks.
-The different motifs are coloured by the mean path length as done in @simmons2020.", fig.width=9,fig.height=5}
+The different motifs are coloured by the mean motif path length as done in @simmons2020.", fig.width=9,fig.height=5}
 library(lme4)
@@
                 size=2)+
-  labs(y="Motif", x = "Percentile (%)",colour="Path length classification")+
-  theme_bw() + scale_color_manual(labels = c('Strong' = expression(paste("Complete (", bar(x), " = 1.38)")),'Fan' = expression(paste("Fan (", bar(x), " = 1.48)")), 'Medium-weak' = expression(paste("Asymmetric complete (", bar(x), " = 1.60)")), "Weak" =expression(paste("Core-peripheral (", bar(x), " = 1.85)"))), name = "Path length classification",values = c("grey25","springgreen4","sienna2","goldenrod2"),guide = guide_legend(title.position = "top",nrow = 2)) +
+  labs(y="Two to five node motifs", x = "Percentile",colour="Path length classification")+
+  theme_bw() + scale_color_manual(labels = c('Strong' = expression(paste("Complete (", bar(x), " = 1.38)")),'Fan' = expression(paste("Fan (", bar(x), " = 1.48)")), 'Medium-weak' = expression(paste("Asymmetric complete (", bar(x), " = 1.60)")), "Weak" =expression(paste("Core-peripheral (", bar(x), " = 1.85)"))), name = "Path length classification",values = c("grey25","springgreen4","sienna2","goldenrod2"),guide = guide_legend(title.position = "top",ncol = 1)) +
 theme(legend.text.align = 0)+
-  theme(legend.position="bottom")
+  theme(legend.position="right")
 

### 2021-08-17 Draft/Draft.Rmd
some edits on draft

@@
 
-Here, we used 60 plant-pollinator networks from 18 different studies and 14 countries, alongside a detailed grouping of plants into reproductive strategies and pollinator species into functional groups.
-Plants were grouped based on a comprehensive dataset that included floral, reproductive and vegetative traits compiled in Lanuza et al., (unpublished) on a larger set of plant-pollinator networks.
-Pollinators were grouped into the main taxonomical groups that differed in life form and behaviour.
-Then, we explored which motifs up to five nodes in these set of plant-pollinator networks were over and under-represented.
-Finally, we explored if the different plants and pollinators functional groups were over- or under-represented in certain positions.
+Here, we used 60 plant-pollinator networks from 18 different studies and 14 countries, alongside functional groups of plants and floral visitors based on functional traits and taxonomic rank, respectively.
+To obtain plant functional groups, we used a comprehensive dataset that included floral, reproductive and vegetative traits compiled on a larger set of networks (Lanuza et al., unpublished).
+Floral visitor functional groups were divided by the main taxonomical groups that differed in life form and behaviour.
+Once we split the different plant-pollinator networks into their motif elements, we explored: (i) over and under-represented motifs; (ii) over and under-represented functional groups in the different motif positions; (iii) the probability of finding plant and floral visitor functional groups in the different motif positions; and, (iv) over- and under- represented functional group combinations within the different motifs.
 
@@
 All studies sampled plant-pollinator interactions in natural systems and were selected based on wide geographical coverage and presence of interaction frequency as a measure of interaction strength.
-In total, there were 503 plant species, 1,111 floral visitors species and 6248 of pairwise interactions registered.
+In total, there were 503 plant species, 1,111 floral visitors species and 6248 pairwise interactions registered.
 For ease of data manipulation plant and floral visitors species names were standardize with the help of the package _taxize_ version 0.9.99 [@chamberlain2020].
@@
 Previous to the clustering analysis, we calculated the distance between the different qualitative and scaled quantitative variables with Gower distance wich can handle mixed data [@gower1971].
-For this, we used the function _gowdis_ with method _ward.D2_ from the package _FD_ version 1.0-12 [@laliberte2014].
-Finally, we conducted hierarchical clustering with the function _hclust_ from the _R_ stats package version 4.0.5 and calculated the optimal number of clusters with the function _kgs_ from the package _maptree_ version 1.4-7 [@white2009].
+For this, we used the function _gowdis_ with method _ward.D2_ from the package _FD_ version _1.0-12_ [@laliberte2014].
+Finally, we conducted hierarchical clustering with the function _hclust_ from the _R_ stats package version _4.0.5_ and calculated the optimal number of clusters with the function _kgs_ from the package _maptree_ version _1.4-7_ [@white2009].
 
@@
 We opted to divide floral visitors on the taxonomic rank level and not with functional traits because (i) the main taxonomic orders differ in form and behaviour and (ii) have lower complexity of higher taxonomic ranks (i.e., floral visitors had 6 orders versus plants that had 38).
-Hence, we grouped floral visitors into 6 functional groups that represented the main life strategies: (i) Hymenoptera-Anthophila (bees), (ii) Hymenoptera-non-Anthophila (other non-bee Hymenoptera), (iii) Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera and (vi) Coleoptera.
+Hence, we grouped floral visitors into 6 functional groups, as done similarly in past studies [@fenster2004; @ollerton2009], that represented the main life strategies: (i) Hymenoptera-Anthophila (bees), (ii) Hymenoptera-non-Anthophila (other non-bee Hymenoptera), (iii) Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera and (vi) Coleoptera.
 
@@
 
-[I may have to think for better headings to guide through analysis and results, specially the second section](Jose)
-
-_Overall motif patterns_
+*Over- and under-represented motifs*
 
@@
 
-_Motif functional groups position_
+*Over and under-represented functional groups on motif positions*
 
@@
 
-[Maybe we need to link this with the plot of the scatterpie](Jose)
+*Over- and under-represented funtional group combinations of motifs*
 
@@
 
-**Functional groups**
-
-_Plants_
-
-The hierarchical cluster analysis divided the dataset with 1506 species and 15 traits into five different clusters with different and overlapping characteristics (**Figure S3** and **Figure S4**).
-The subset of plant species used in this study (N = 503) were distributed evenly across these different larger five groups (see subset of the 503 species labels within cluster for all species in **Figure S3**).
-The first cluster was dominated by herbs with hermaphrodite flowers with high levels of autonomous selfing and we we refer to this group as "selfing herbs".
-The second cluster was characterized by small perennial species with a mixed of life forms (trees shrubs and herbs) with outcrossing hermaphroditic flowers and we refer to this group of species as "small outcrossing perennials".
-The third cluster was dominated by also perennial species with a mixed of life forms too and had large self-incompatible hermaphroditic flowers with high number of ovules and we named this group "self-incompatible perennials with large flowers".
-The fourth cluster had the tallest species, highest proportion of shrub and tree life forms, dioecious and monoecious breeding system with small flowers but the highest number of flowers per plant and inflorescences, and, we refer to this set of species as "tall plants with small unisexual flowers".
-Finally, the last cluster of species was dominated by small perennial and shot-lived herbs with long self-compatible zygomorphic flowers unable to self-pollinate and we refer to this group as "short-lived outcrossers with long zygomorphic flowers".
-
-_Floral visitors_
-
-[Describe poll funcional groups?](Jose)
-
-[I'm calling them functional groups because is easier to refer as FG to both but maybe is more accurate to refer them as guilds?](Jose)
+**Plant and floral visitor functional groups**
+
+The hierarchical cluster analysis divided the dataset into five different clusters with different and overlapping characteristics (**Figure S3** and **Figure S4**): cluster 1 (selfing herbs) consisted on herbs with hermaphrodite flowers with high levels of autonomous selfing; cluster 2 (small outcrossing perennials) had small perennial species with a mixed of life forms (trees shrubs and herbs) with outcrossing hermaphroditic flowers; cluster 3 (self-incompatible perennials with large flowers) comprised perennial species with a mixed of life forms and had large self-incompatible hermaphroditic flowers with high number of ovules; cluster 4 (tall plants with small unisexual flowers) had the tallest species, highest proportion of shrub and tree life forms, dioecious and monoecious breeding system with small flowers but the highest number of flowers per plant and inflorescences; finally, cluster 5 (short-lived outcrossers with long zygomorphic flowers) was dominated by small perennial and short-lived herbs with long self-compatible zygomorphic flowers that were unable to self-pollinate.
+
+In total, there were 1126 pollinator species and were divided into 9 different taxonomical groups.
+From highest to lowest number of interactions of the different functional groups with plants: bees (2256), non-syrphid Diptera (1768), syrphids (845), Lepidoptera (437), Coleoptera (432), non-bee Hymenoptera (362), lizards (105), birds (80) and other insects (40).
 

### 2021-08-17 Draft/Draft.Rmd
overall motif patterns results

@@
 
-**Meso-scale analysis**
-
-*Over- and under-represented motifs*
+**Overall motif patterns**
 
@@
 
-*Over and under-represented functional groups on motif positions*
+**Over and under-represented functional groups on motif positions**
 
@@
 
-*Over- and under-represented funtional group combinations of motifs*
+**Over- and under-represented funtional group combinations of motifs**
 
@@
 
-The hierarchical cluster analysis divided the dataset into five different clusters with different and overlapping characteristics (**Figure S3** and **Figure S4**): cluster 1 (selfing herbs) consisted on herbs with hermaphrodite flowers with high levels of autonomous selfing; cluster 2 (small outcrossing perennials) had small perennial species with a mixed of life forms (trees shrubs and herbs) with outcrossing hermaphroditic flowers; cluster 3 (self-incompatible perennials with large flowers) comprised perennial species with a mixed of life forms and had large self-incompatible hermaphroditic flowers with high number of ovules; cluster 4 (tall plants with small unisexual flowers) had the tallest species, highest proportion of shrub and tree life forms, dioecious and monoecious breeding system with small flowers but the highest number of flowers per plant and inflorescences; finally, cluster 5 (short-lived outcrossers with long zygomorphic flowers) was dominated by small perennial and short-lived herbs with long self-compatible zygomorphic flowers that were unable to self-pollinate.
-
-In total, there were 1126 pollinator species and were divided into 9 different taxonomical groups.
-From highest to lowest number of interactions of the different functional groups with plants: bees (2256), non-syrphid Diptera (1768), syrphids (845), Lepidoptera (437), Coleoptera (432), non-bee Hymenoptera (362), lizards (105), birds (80) and other insects (40).
+The hierarchical cluster analysis divided the dataset into five different clusters with different and overlapping characteristics (**Figure S3** and **Figure S4**): cluster 1 referred to as 'selfing herbs' consisted on herbs with hermaphroditic flowers with high levels of autonomous selfing; cluster 2 or 'small outcrossing perennials' had small perennial species with a mixed of life forms (trees shrubs and herbs) with outcrossing hermaphroditic flowers; cluster 3 referred to as 'self-incompatible perennials with large flowers' comprised perennial species with a mixed of life forms and large self-incompatible hermaphroditic flowers with high number of ovules; cluster 4 or 'tall plants with small unisexual flowers' had the tallest species, highest proportion of shrub and tree life forms, dioecious and monoecious breeding systems with small flowers but the highest numbers of flowers and inflorescences per plant; finally, cluster 5  referred to as 'short-lived outcrossers with long zygomorphic flowers' consisted on small perennial and short-lived herbs with long self-compatible zygomorphic flowers that were unable to self-pollinate.
+
+In total, there were 1126 species of floral visitor with 6325 interactions recorded with plants.
+We divided them into 9 different taxonomical groups: bees with 2256 interactions with plants, non-syrphid Diptera with 1768 interactions, syrphids with 845 interactions, Lepidoptera with 437 interactions, Coleoptera with 432 interactions, non-bee Hymenoptera with 362 interactions and lizards, birds and other insects with a total of 225 interactions.
 

### 2021-09-27 Draft/Draft.Rmd
Edits on figures, 6 functional groups considered now and starting to decsribe the heatmaps...

@@
 - \usepackage{xcolor}
+- \usepackage{caption,setspace}
+- \captionsetup[figure]{labelformat=empty}
+- \floatplacement{figure}{H}
+- \usepackage[skip=3pt]{caption}
+- \captionsetup[figure]{labelformat=empty}
+
 output:
+  pdf_document: default
   html_document: default
-  pdf_document: default
   word_document: default
@@
 ---
+
+\captionsetup[table]{labelformat=empty}
 
@@
 
-Traditionally, plant-pollinator research has focused on direct interactions and overlooked indirect interactions such as facilitative or competitive interactions between plants for pollinators [@moeller2004; @sargent2008].
+Traditionally, plant-pollinator research has focused on direct interactions but overlooked indirect interactions (the mediated effect between two species by a third species), such as facilitative or competitive interactions between plants for pollinators [@moeller2004; @sargent2008].
 Despite the widespread nature of indirect interactions in ecological communities [@strauss1991], plant-pollinator research often fails to finely capture those indirect interactions with the conventional analytical tools that condense the information either by species (e.g.
@@
 The analysis of motifs (meso-scale) in plant-pollinator networks have revealed that the different ecological processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions [@simmons2020].
-Yet, the global patterns of indirect interactions in plant-pollinator networks (over- and under- representation of motifs) are still unknown.
+Yet, the global patterns of indirect interactions in plant-pollinator networks (over- and under- represented motifs) are still unknown.
 
@@
 In total, there were 503 plant species, 1,111 floral visitors species and 6248 pairwise interactions registered.
-For ease of data manipulation plant and floral visitors species names were standardize with the help of the package _taxize_ version 0.9.99 [@chamberlain2020].
+For ease of data manipulation, plant and floral visitors species names were standardize with the help of the package _taxize_ version 0.9.99 [@chamberlain2020].
 
@@
 This dataset consisted on 8 floral, 4 reproductive and 3 vegetative traits excluding traits with high percentage of missing values (over 30%; **Table S2**).
-We opted to calculate the plant functional groups on this larger set of species because of the higher accuracy when delimiting functional groups with that many variables and species @dolnicar2014.
-Previous to the clustering analysis, we calculated the distance between the different qualitative and scaled quantitative variables with Gower distance wich can handle mixed data [@gower1971].
+We opted to calculate the plant functional groups on this larger set of species because of the higher accuracy when delimiting functional groups with that many variables and species [@dolnicar2014].
+Previous to the clustering analysis, we calculated the distance between the different qualitative and scaled quantitative variables with Gower distance [@gower1971].
 For this, we used the function _gowdis_ with method _ward.D2_ from the package _FD_ version _1.0-12_ [@laliberte2014].
@@
 
-Second, floral visitors were grouped into functional groups based on taxonomic rank.
-We opted to divide floral visitors on the taxonomic rank level and not with functional traits because (i) the main taxonomic orders differ in form and behaviour and (ii) have lower complexity of higher taxonomic ranks (i.e., floral visitors had 6 orders versus plants that had 38).
-Hence, we grouped floral visitors into 6 functional groups, as done similarly in past studies [@fenster2004; @ollerton2009], that represented the main life strategies: (i) Hymenoptera-Anthophila (bees), (ii) Hymenoptera-non-Anthophila (other non-bee Hymenoptera), (iii) Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera and (vi) Coleoptera.
+Second, floral visitors were grouped into functional groups based on taxonomic rank as done similarly in past plant-pollinator studies [@fenster2004; @ollerton2009].
+We opted to divide floral visitors on the taxonmoic rank level and not with functional traits because the main orders of floral visitors differed clearly in form and behaviour and had lower lower complexity of higher taxnomic ranks than plants (i.e., floral visitors had 6 orders versus plants that had 38).
+Thus, this allowed us to group floral visitors into functional groups that represented adequately the main life strategies: (i) Hymenoptera-Anthophila (bees), (ii) Hymenoptera-non-Anthophila (other non-bee Hymenoptera), (iii) Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera, (vi) Coleoptera, (vii).
+Further, other 3 functional groups (i.e., lizards, birds and other insects) were considered for analysis but excluded from results because of their low representation in the set of networks.
 
@@
 
-Following Simmons et al.
-[@simmons2019; @simmons2020], we broke down the plant-pollinator networks into their constituent motifs.
+Following previous work [@simmons2019; @simmons2020], we broke down the plant-pollinator networks into their constituent motifs.
 Prior to analyses, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="Figure 1.
-Adapted figure of Simmons et al., 2019 with all the possible motifs from two to five species in bipartite networks.
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="**Figure 1.** Adapted figure of Simmons et al., 2019 with all the possible motifs from two to five species in bipartite networks.
 There is a total of 17 possible motifs with 46 different positions denoted within each node.", fig.width=10,fig.height=8}
@@
 
-The hierarchical cluster analysis divided the dataset into five different clusters with different and overlapping characteristics (**Figure S3** and **Figure S4**): cluster 1 referred to as 'selfing herbs' consisted on herbs with hermaphroditic flowers with high levels of autonomous selfing; cluster 2 or 'small outcrossing perennials' had small perennial species with a mixed of life forms (trees shrubs and herbs) with outcrossing hermaphroditic flowers; cluster 3 referred to as 'self-incompatible perennials with large flowers' comprised perennial species with a mixed of life forms and large self-incompatible hermaphroditic flowers with high number of ovules; cluster 4 or 'tall plants with small unisexual flowers' had the tallest species, highest proportion of shrub and tree life forms, dioecious and monoecious breeding systems with small flowers but the highest numbers of flowers and inflorescences per plant; finally, cluster 5  referred to as 'short-lived outcrossers with long zygomorphic flowers' consisted on small perennial and short-lived herbs with long self-compatible zygomorphic flowers that were unable to self-pollinate.
+The hierarchical cluster analysis divided the dataset into five different clusters with different and overlapping characteristics (**Figure S3** and **Figure S4**).
+Cluster 1 referred to as 'selfing herbs' consisted on herbs with hermaphroditic flowers with high levels of autonomous selfing.
+Cluster 2 or 'small outcrossing perennials' had small perennial species with a mixed of life forms (i.e., trees shrubs and herbs) with outcrossing hermaphroditic flowers.
+Cluster 3 referred to as 'self-incompatible perennials with large flowers' comprised perennial species with a mixed of life forms and large self-incompatible hermaphroditic flowers with high number of ovules.
+Cluster 4 or 'tall plants with small unisexual flowers' had the tallest species, highest proportion of shrub and tree life forms, dioecious and monoecious breeding systems with small flowers but the highest numbers of flowers and inflorescences per plant.
+Finally, cluster 5 or 'short-lived outcrossers with long zygomorphic flowers' consisted on small perennial and short-lived herbs with long self-compatible zygomorphic flowers that were unable to self-pollinate.
 
 In total, there were 1126 species of floral visitor with 6325 interactions recorded with plants.
-We divided them into 9 different taxonomical groups: bees with 2256 interactions with plants, non-syrphid Diptera with 1768 interactions, syrphids with 845 interactions, Lepidoptera with 437 interactions, Coleoptera with 432 interactions, non-bee Hymenoptera with 362 interactions and lizards, birds and other insects with a total of 225 interactions.
+We divided them into 6 main different taxonomical groups: bees with 2256 interactions with plants, non-syrphid Diptera with 1768 interactions, syrphids with 845 interactions, Lepidoptera with 437 interactions, Coleoptera with 432 interactions and non-bee Hymenoptera with 362 interactions.
 
@@
 
-Most motifs were under and over-represented (close to the 1st and 99th percentile, respectively) in the comparison between empirical and simulated networks (**Figure 2**).
+Most motifs were under- and over-represented (close to the 1st and 99th percentile, respectively) in the comparison between empirical and simulated networks (**Figure 2**).
+Further, the exclusion of singletones did not change these results (**Figure S1**).
 Motifs 3, 5, 9, 10 and 14 were under-represented in empirical networks, that is, all under the 25th percentile and the closest motifs to the 1st percentile.
@@
 In contrast to the under-represented motifs, over-represented motifs belonged to the two shortest path length groups (i.e., complete and fan).
-The remaining motifs (i.e., 4, 8, 11, 12, 13, and 15) were between the 25th and 75th percentile with a tendency for most motifs to be over-represented (closest to the 75th percentile).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="Figure 2.
-Comparison of the motif frequencies between empirical and simulated networks.
+The remaining motifs (i.e., 4, 8, 11, 12, 13, and 15) were between the 25th and 75th percentile but closest to over-representation.
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=9,fig.height=5, fig.cap="**Figure 2.** Comparison of the motif frequencies between empirical and simulated networks.
 Average percentages of motifs close to 0 and 100 indicate under- and over- representation in empirical networks.
-The different motifs are coloured by the mean motif path length as done in @simmons2020.", fig.width=9,fig.height=5}
+The different motifs are coloured by the mean motif path length as done in Simmons et al.
+(2020)."}
 library(lme4)
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align = 'center',fig.width=6,fig.height=3.5}
+Although motifs positions determined over- and under- representation independently of the identity of functional groups for most cases (rows in **Figure 3**), we found differences in the average percentile within floral visitors and pollinators functional groups (columns in **Figure 3**).
+Remarkably, the same patterns were observed but with lower average percentiles when singletones were exluded (**Figure S2**).
+Thus,
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="\\textbf{Figure 3.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions.
+The different motif positions are dividied by the average path length clasification by @simmons2020."}
+
 library(lme4)
@@
 library(stringi)
-library(ggpubr)
 source("../Scripts/Scripts_Alfonso/add_study_id.R")
+
+#############################################
+# EXTRACT MEAN VALUES
+#############################################
 
@@
          !is.na(expected_freq_its_GF))
-
-#ggplot(plant_position_percentiles_filtered, aes(percentil_its_GF))+
-#  geom_histogram(color="black", fill="white")+
-#  facet_wrap(~position)+
-#  theme_bw()+
-#  labs(x="Sizeclass percentile", title = "Histograms: Percentiles for plant positions")
-#
-#ggplot(pollinator_position_percentiles_filtered, aes(percentil_its_GF))+
-#  geom_histogram(color="black", fill="white")+
-#  facet_wrap(~position)+
-#  theme_bw()+
-#  labs(x="Sizeclass percentile",title = "Histograms: Percentiles for pollinator positions")
-#
-
-# estimated mean taking into account the random str is 0.XX +- 0.XX (look at the (Intercept) estimate)
 
@@
 
-GF_plant_pos <- ggplot(NULL) + 
-  geom_point(data = plant_position_percentiles_filtered,
-             aes(x=as.factor(position), y=percentil_its_GF, 
-                 color = as.factor(position)),
-             position = "jitter",alpha=0.5)+
-  geom_errorbar(data = plant_means,aes(x = as.factor(position), ymin=mean-SE, ymax=mean+SE), 
-                width=1.0,size=1)+
-  facet_wrap(~Node_FG,ncol = 5)+
-  geom_point(data = plant_means,aes(x = as.factor(position), y=mean), 
-             size=2)+
-  labs(x="Position", y = "Percentile",title = "Plants")+
-  theme_bw()+
-  theme(legend.position = "none")+#,axis.text.x=element_text(angle=90,vjust=0.5, hjust=1))+
-  coord_flip()
-
 # Pollinators--------
@@
 
-GF_poll_pos <- ggplot(NULL) + 
-  geom_point(data = pollinator_position_percentiles_filtered,
-             aes(x=as.factor(position), y=percentil_its_GF, 
-                 color = as.factor(position)),
-             position = "jitter",alpha=0.5)+
-  geom_errorbar(data = pollinator_means_reordered, aes(x = as.factor(position), ymin=lower,
-                                                       ymax=mean+SE), 
-                width=1.0,size=1)+
-  facet_wrap(~Node_FG,ncol = 5)+
-  geom_point(data = pollinator_means_reordered,aes(x = as.factor(position), y=mean), 
-             size=2)+
-  labs(x="Position", y = "Percentile", title = "Pollinators")+
-  theme_bw()+
-  theme(legend.position = "none")+#,axis.text.x=element_text(angle=90,vjust=0.5, hjust=1))+
-  coord_flip()
-
-# Plant and Pollinators--------
-#
-#ggarrange(GF_plant_pos,GF_poll_pos,
-#          ncol = 1, nrow = 2,heights = c(.90, 1.4))
-#
-#Fig 2 may be the same, but for the each positions-FG combination? Maybe heatmap (but we lose the SE's)
-
-```
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="Figure 3.
-Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions.
-The different motif positions are dividied by the average path length clasification by @simmons2020."}
-
-library(lme4)
-library(nlme)
-library(tidyverse)
-library(stringi)
-source("../Scripts/Scripts_Alfonso/add_study_id.R")
-
-#############################################
-# EXTRACT MEAN VALUES
-#############################################
-
-all_position_percentiles <- read_csv("../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
-
-all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
-                                                              "[0-9]+") %>% as.numeric()
-
-all_position_percentiles <- add_study_id(all_position_percentiles)
-#str(all_position_percentiles)
-#head(all_position_percentiles)
-
-list_plants_FG <- as.character(1:10)
-
-plant_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF)) #ME DA ERROR
-pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF))
-
-# Plants-------------
-
-# Mean percentile and SE taking into account the study system
-plant_codes <- plant_position_percentiles_filtered$position %>% unique()
-plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-plant_means$mean <- NA
-plant_means$SE <- NA
-
-for(i.pos in 1:length(plant_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
-            data = plant_position_percentiles_filtered %>%
-              filter(position == plant_codes[i.pos]))
-
-  temp <- fixed.effects(m) %>% unname()
-  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
-                                                                    temp[1]+temp[2],
-                                                                    temp[1]+temp[3],
-                                                                    temp[1]+temp[4],
-                                                                    temp[1]+temp[5]) ## to get real means per FG
-  temp <- sqrt(diag(vcov(m)))
-  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
-                                                                  temp[1]+temp[2],
-                                                                  temp[1]+temp[3],
-                                                                  temp[1]+temp[4],
-                                                                  temp[1]+temp[5])
-
-}
-
-# Pollinators--------
-
-# Mean percentile and SE taking into account the study system
-pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
-pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-pollinator_means$mean <- NA
-pollinator_means$SE <- NA
-pollinator_means_reordered <- NULL
-
-for(i.pos in 1:length(pollinator_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = pollinator_position_percentiles_filtered %>%
-              filter(position == pollinator_codes[i.pos]),
-            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
-
-  temp <- fixed.effects(m) %>% unname()
-  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)
-
-  pollinator_means_aux$mean <- c(temp[1],
-                                 temp[1]+temp[2],
-                                 temp[1]+temp[3],
-                                 temp[1]+temp[4],
-                                 temp[1]+temp[5],
-                                 temp[1]+temp[6],
-                                 temp[1]+temp[7],
-                                 temp[1]+temp[8],
-                                 temp[1]+temp[9]) ## to get real means per FG
-
-  temp <- sqrt(diag(vcov(m)))
-  pollinator_means_aux$SE <- c(temp[1],
-                               temp[1]+temp[2],
-                               temp[1]+temp[3],
-                               temp[1]+temp[4],
-                               temp[1]+temp[5],
-                               temp[1]+temp[6],
-                               temp[1]+temp[7],
-                               temp[1]+temp[8],
-                               temp[1]+temp[9])
-
-  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)
-
-}
-
-# There are lower limits (mean - SE) smaller than 0 (see Other insects)
-# We set the lower limit of those error bars to zero
-
-pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
-pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
-
 #############################################
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="Figure 4.
-Graphical representation of the probability of finding a given functional group $x$ in the position $\\alpha$ of motif $i$, $p_i(x,\\alpha)$, for all the possible motifs from two to five species in bipartite networks.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 4.** Graphical representation of the probability of finding a given functional group $x$ in the position $\\alpha$ of motif $i$, $p_i(x,\\alpha)$, for all the possible motifs from two to five species in bipartite networks.
 The slices in the nodes for a given functional group $x$ are proportional to the corresponding value of $p_i(x,\\alpha)$."}
-
-plant_means_reordered <- read_csv("../Data/Csv/plant_abs_freq_means.csv")
-pollinator_means_reordered <- read_csv("../Data/Csv/pollinator_abs_freq_means.csv")
 
@@
 library(RColorBrewer)
+library(tidyverse)
+
+plant_means_reordered <- read_csv("../Data/Csv/plant_abs_freq_means.csv")
+pollinator_means_reordered <- read_csv("../Data/Csv/pollinator_abs_freq_means.csv")
+#Filter out in order to have just 6 FG'S
+pollinator_means_reordered <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds", "Lizards", "Other_insects"))
 
@@
   nb.cols <- 5
-  mycolors <- c(brewer.pal(9, "Paired"),brewer.pal(5, "Dark2"))
+  mycolors <- c(brewer.pal(6, "Paired"),brewer.pal(5, "Dark2"))
 
@@
                  size = 1, color = "grey20")+  geom_scatterpie(aes(x=x, y=y, group=position,r=.45), 
-    data = d_nodes_pollinator, cols=as.character(c("Bee","Birds","Coleoptera","Lepidoptera",
-     "Lizards","Non-bee-Hymenoptera", "Non-syrphids-diptera","Other_insects",
-     "Syrphids"))) +
+    data = d_nodes_pollinator, cols=as.character(c("Bee","Coleoptera","Lepidoptera","Non-bee-Hymenoptera", "Non-syrphids-diptera","Syrphids"))) +
     geom_scatterpie(aes(x=x, y=y, group=position,r=0.45), 
@@
     scale_fill_manual(values = mycolors,"test",
-      breaks=c("Bee","Birds","Coleoptera","Lepidoptera",
-               "Lizards","Non-bee-Hymenoptera", "Non-syrphids-diptera","Other_insects",
-               "Syrphids","1","2","3","4","5"), labels=c("Bee","Birds","Coleoptera","Lepidoptera",
-                                                        "Lizards","Non-bee-Hymenoptera", "Non-syrphids-diptera","Other_insects",
-                                                        "Syrphids", 
+      breaks=c("Bee","Coleoptera","Lepidoptera",
+               "Non-bee-Hymenoptera", "Non-syrphids-diptera",
+               "Syrphids","1","2","3","4","5"), labels=c("Bee","Coleoptera","Lepidoptera",
+"Non-bee-Hymenoptera", "Non-syrphids-diptera","Syrphids", 
           "Selfing herbs","Small outcrossing perennials","Self-incomp. perennials\nwith large flowers",
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="Figure 5."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 5.**"}
 
@@
   d_nodes_FG <- d_nodes %>% left_join(FG_IDs, by = "label")
-  levels_FG <- c("Bee","Birds","Coleoptera","Lepidoptera",
-                 "Lizards","Non-bee-Hymenoptera", "Non-syrphids-diptera","Other_insects",
+  levels_FG <- c("Bee","Coleoptera","Lepidoptera",
+                 "Non-bee-Hymenoptera", "Non-syrphids-diptera",
                  "Syrphids","1","2","3","4","5")
@@
 
-  levels(d_nodes_FG$FG) <- c("Bee","Birds","Coleoptera","Lepidoptera",
-                             "Lizards","Non-bee-Hymenoptera", "Non-syrphids-diptera","Other_insects",
+  levels(d_nodes_FG$FG) <- c("Bee","Coleoptera","Lepidoptera",
+                             "Non-bee-Hymenoptera", "Non-syrphids-diptera",
                              "Syrphids","1","2","3","4","5")
@@
   # Define the number of colors you want
-  mycolors <- c(brewer.pal(9, "Paired"),brewer.pal(5, "Dark2"))
+  mycolors <- c(brewer.pal(6, "Paired"),brewer.pal(5, "Dark2"))
 
@@
     scale_color_manual(drop = FALSE, values = mycolors,
-                       breaks=c("Bee","Birds","Coleoptera","Lepidoptera",
-                                "Lizards","Non-bee-Hymenoptera", "Non-syrphids-diptera","Other_insects",
+                       breaks=c("Bee","Coleoptera","Lepidoptera",
+                                "Non-bee-Hymenoptera", "Non-syrphids-diptera",
                                 "Syrphids","1","2","3","4","5"), 
-                       labels=c("Bee","Birds","Coleoptera","Lepidoptera",
-                                "Lizards","Non-bee-Hymenoptera", "Non-syrphids-diptera",
-                                "Other insects", "Syrphids", 
+                       labels=c("Bee","Coleoptera","Lepidoptera",
+                                "Non-bee-Hymenoptera", "Non-syrphids-diptera",
+                                "Syrphids", 
                                 "Selfing herbs","Small outcrossing perennials",
@@
 pollinator_means_reordered <- read_csv("../Data/Csv/pollinator_abs_freq_means.csv")
+#Filter out in order to have just 6 FG'S
+pollinator_means_reordered <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds", "Lizards", "Other_insects"))
 
@@
 <div id ="refs"></div>
+
+\newpage
 
@@
   arrange(`First author`)%>%
-  kable( longtable = T, booktabs = T,linesep = "\\addlinespace",align = c("cccc"),caption = "Table S1.
-List of studies ordered by author with the year of publication, number of contributed networks and digital object identifier") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = c("center"))
+  kable( longtable = T, booktabs = T,linesep = "\\addlinespace",align = c("cccc"),escape = FALSE, caption= "\\textbf{Table S1.} List of studies ordered by author with the year of publication, number of contributed networks and digital object identifier") %>%
+  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=T,position = c("center"))
 
 ```
+
+\newpage
 
@@
 
-kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c"),caption = "Table S2.
-Traits used to delimit the different plant functional groups divided in quantitative and categorical traits.") %>%
-kable_styling(full_width = F) %>%
+kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c"),caption = "\\textbf{Table S2.} Traits used to delimit the different plant functional groups divided in quantitative and categorical traits.") %>%
+kable_styling(full_width = T) %>%
 add_header_above(c("Quantitative traits" = 2,"Categorical traits" = 2),bold=T)  %>%
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="Figure S1.
-Comparison of the motif frequencies between empirical and simulated networks.
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="**Figure S1.** Comparison of the motif frequencies between empirical and simulated networks excluding singletones.
 Average percentages of motifs close to 0 and 100 indicate under- and over- representation in empirical networks, after removing non-robust links, that is, interactions whose frequency was equal to one.
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="Figure S2.
-Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions, after removing non-robust links, that is, interactions whose frequency was equal to one.
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="\\textbf{Figure S2.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions excluding singletones, after removing non-robust links, that is, interactions whose frequency was equal to one.
 The different motif positions are dividied by the average path length clasification by @simmons2020."}
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=13, fig.cap="Figure S3.
-Plant functional group composition separated in qualitative and quantitative variables.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=13, fig.cap="**Figure S3.** Plant functional group composition separated in qualitative and quantitative variables.
 Panel A) shows the percentage of the different categories within trait represented with different colours for each functional group.
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=13, fig.cap="Figure S4.
-Hierarchical clustering dendrogram with the branches coloured by the optimal number of clusters (5).
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=13, fig.cap="**Figure S4.** Hierarchical clustering dendrogram with the branches coloured by the optimal number of clusters (5).
 The labels of the subgroup of species (N = 524) used in this study are coloured in black in order to show the evenness of the distribution of the species across clusters.

### 2021-09-28 Draft/Draft.Rmd
Caption figure 2

@@
 Here, we used 60 plant-pollinator networks from 18 different studies and 14 countries, alongside functional groups of plants and floral visitors based on functional traits and taxonomic rank, respectively.
-To obtain plant functional groups, we used a comprehensive dataset that included floral, reproductive and vegetative traits compiled on a larger set of networks (Lanuza et al., unpublished).
+To obtain plant functional groups, we used a comprehensive dataset that included floral, reproductive and vegetative traits compiled on a larger set of networks.
 Floral visitor functional groups were divided by the main taxonomical groups that differed in life form and behaviour.
@@
 Second, floral visitors were grouped into functional groups based on taxonomic rank as done similarly in past plant-pollinator studies [@fenster2004; @ollerton2009].
-We opted to divide floral visitors on the taxonmoic rank level and not with functional traits because the main orders of floral visitors differed clearly in form and behaviour and had lower lower complexity of higher taxnomic ranks than plants (i.e., floral visitors had 6 orders versus plants that had 38).
-Thus, this allowed us to group floral visitors into functional groups that represented adequately the main life strategies: (i) Hymenoptera-Anthophila (bees), (ii) Hymenoptera-non-Anthophila (other non-bee Hymenoptera), (iii) Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera, (vi) Coleoptera, (vii).
-Further, other 3 functional groups (i.e., lizards, birds and other insects) were considered for analysis but excluded from results because of their low representation in the set of networks.
+We opted to divide floral visitors on the taxonomic rank level and not with functional traits because the main orders of floral visitors differed in form and behaviour and had lower superior taxonomical complexity (i.e., floral visitors had 6 orders versus plants that had 38).
+Thus, this allowed us to group floral visitors into functional groups that represented adequately the main life strategies of the possible pollinators: (i) Hymenoptera-Anthophila (bees), (ii) Hymenoptera-non-Anthophila (other non-bee Hymenoptera), (iii) Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera, (vi) Coleoptera, (vii).
+However, a minor set of species belonged to other functional groups that were considered in the analysis as lizards, birds and other insects but not discussed further because of their low representation in the set of analysed networks.
 
@@
 Cluster 3 referred to as 'self-incompatible perennials with large flowers' comprised perennial species with a mixed of life forms and large self-incompatible hermaphroditic flowers with high number of ovules.
-Cluster 4 or 'tall plants with small unisexual flowers' had the tallest species, highest proportion of shrub and tree life forms, dioecious and monoecious breeding systems with small flowers but the highest numbers of flowers and inflorescences per plant.
+Cluster 4 or 'tall plants with small unisexual flowers' had the tallest species, highest proportion of shrub and tree life forms, dioecious and monoecious breeding systems, small flowers and the highest numbers of flowers and inflorescences per plant.
 Finally, cluster 5 or 'short-lived outcrossers with long zygomorphic flowers' consisted on small perennial and short-lived herbs with long self-compatible zygomorphic flowers that were unable to self-pollinate.
@@
 In total, there were 1126 species of floral visitor with 6325 interactions recorded with plants.
-We divided them into 6 main different taxonomical groups: bees with 2256 interactions with plants, non-syrphid Diptera with 1768 interactions, syrphids with 845 interactions, Lepidoptera with 437 interactions, Coleoptera with 432 interactions and non-bee Hymenoptera with 362 interactions.
+From highest to lowest records of interactions of floral visitors with plants we found: bees with 2256 interactions, non-syrphid Diptera with 1768 interactions, syrphids with 845 interactions, Lepidoptera with 437 interactions, Coleoptera with 432 interactions and non-bee Hymenoptera with 362 interactions.
 
@@
 Most motifs were under- and over-represented (close to the 1st and 99th percentile, respectively) in the comparison between empirical and simulated networks (**Figure 2**).
-Further, the exclusion of singletones did not change these results (**Figure S1**).
-Motifs 3, 5, 9, 10 and 14 were under-represented in empirical networks, that is, all under the 25th percentile and the closest motifs to the 1st percentile.
+Motifs 3, 5, 9, 10 and 14 were under-represented in empirical networks, that is, all were close to the 1st percentile and under the 25th percentile.
 Remarkably, four out of five of these motifs belonged to the largest path length classification (i.e., core-peripheral).
@@
 The remaining motifs (i.e., 4, 8, 11, 12, 13, and 15) were between the 25th and 75th percentile but closest to over-representation.
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=9,fig.height=5, fig.cap="**Figure 2.** Comparison of the motif frequencies between empirical and simulated networks.
-Average percentages of motifs close to 0 and 100 indicate under- and over- representation in empirical networks.
-The different motifs are coloured by the mean motif path length as done in Simmons et al.
+Remarkably, the exclusion of singletones from this analysis did not change the observed results (**Figure S1**).
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=9,fig.height=5, fig.cap="**Figure 2.** Comparison of motif frequencies between empirical and simulated networks.
+This is shown with the mean percentage of motif frequencies in empirical networks that were over the motif frequencies of the simulated ones (percentiles).
+This was done by network (coloured dots) and then averaged for all networks (black dots with error bars that correspond to the standard deviation).
+The different motifs are coloured by the four categories of path length determined in Simmons et al.
 (2020)."}
@@
                  color = as.factor(Broad_categories)),
-             position = "jitter",alpha=0.5)+
+             position = "jitter",alpha=0.8)+
   geom_errorbar(data = motif_means,aes(y = as.factor(motif), xmin=100*(mean-SE), xmax=100*(mean+SE)), 
@@
   labs(y="Two to five node motifs", x = "Percentile",colour="Path length classification")+
-  theme_bw() + scale_color_manual(labels = c('Strong' = expression(paste("Complete (", bar(x), " = 1.38)")),'Fan' = expression(paste("Fan (", bar(x), " = 1.48)")), 'Medium-weak' = expression(paste("Asymmetric complete (", bar(x), " = 1.60)")), "Weak" =expression(paste("Core-peripheral (", bar(x), " = 1.85)"))), name = "Path length classification",values = c("grey25","springgreen4","sienna2","goldenrod2"),guide = guide_legend(title.position = "top",ncol = 1)) +
+  theme_bw() + scale_color_manual(labels = c('Strong' = expression(paste("Complete (", bar(x), " = 1.38)")),'Fan' = expression(paste("Fan (", bar(x), " = 1.48)")), 'Medium-weak' = expression(paste("Asymmetric complete (", bar(x), " = 1.60)")), "Weak" =expression(paste("Core-peripheral (", bar(x), " = 1.85)"))), name = "Path length classification",values = c("grey36","lightblue3","navajowhite2","darkorange4"),guide = guide_legend(title.position = "top",ncol = 1)) +
 theme(legend.text.align = 0)+
   theme(legend.position="right")
-
 #Trying to maintain a gradient from low to high in colors
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="\\textbf{Figure 3.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions.
-The different motif positions are dividied by the average path length clasification by @simmons2020."}
+The different motif positions are dividied by the average path length clasification determined by Simmons et al.
+(2020)."}
 
@@
                 size=2)+
-  labs(y="Motif", x = "Percentile (%)",colour="Path length classification")+
-  theme_bw() + scale_color_manual(labels = c('Strong' = expression(paste("Complete (", bar(x), " = 1.38)")),'Fan' = expression(paste("Fan (", bar(x), " = 1.48)")), 'Medium-weak' = expression(paste("Asymmetric complete (", bar(x), " = 1.60)")), "Weak" =expression(paste("Core-peripheral (", bar(x), " = 1.85)"))), name = "Path length classification",values = c("grey25","springgreen4","sienna2","goldenrod2"),guide = guide_legend(title.position = "top",nrow = 2)) +
+  labs(y="Two to five node motifs", x = "Percentile",colour="Path length classification")+
+  theme_bw() + scale_color_manual(labels = c('Strong' = expression(paste("Complete (", bar(x), " = 1.38)")),'Fan' = expression(paste("Fan (", bar(x), " = 1.48)")), 'Medium-weak' = expression(paste("Asymmetric complete (", bar(x), " = 1.60)")), "Weak" =expression(paste("Core-peripheral (", bar(x), " = 1.85)"))), name = "Path length classification",values = c("grey36","lightblue3","navajowhite2","darkorange4"),guide = guide_legend(title.position = "top",ncol = 1)) +
 theme(legend.text.align = 0)+
-  theme(legend.position="bottom")
+  theme(legend.position="right")
 

### 2021-09-28 Draft/Draft.Rmd
Edit on figure 2, hopefully better now?

@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=9,fig.height=5, fig.cap="**Figure 2.** Comparison of motif frequencies between empirical and simulated networks.
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure 2.** Comparison of motif frequencies between empirical and simulated networks divided by average path length (plots a, b, c and d) as determined in Simmons et al.
+(2020).
 This is shown with the mean percentage of motif frequencies in empirical networks that were over the motif frequencies of the simulated ones (percentiles).
-This was done by network (coloured dots) and then averaged for all networks (black dots with error bars that correspond to the standard deviation).
-The different motifs are coloured by the four categories of path length determined in Simmons et al.
-(2020)."}
+This was done by network (light blue dots) and then averaged for all networks (black dots with error bars that correspond to the standard deviation)."}
 library(lme4)
@@
 
-ggplot(NULL) + 
-  geom_point(data = d %>% filter(motif != 1),
-             aes(y=as.factor(motif), x=100*percentil_sizeclass, 
-                 color = as.factor(Broad_categories)),
-             position = "jitter",alpha=0.8)+
-  geom_errorbar(data = motif_means,aes(y = as.factor(motif), xmin=100*(mean-SE), xmax=100*(mean+SE)), 
-                width=1.0,size=1)+
-  geom_point(data = motif_means,aes(y = as.factor(motif), x=100*mean), 
-                size=2)+
-  labs(y="Two to five node motifs", x = "Percentile",colour="Path length classification")+
-  theme_bw() + scale_color_manual(labels = c('Strong' = expression(paste("Complete (", bar(x), " = 1.38)")),'Fan' = expression(paste("Fan (", bar(x), " = 1.48)")), 'Medium-weak' = expression(paste("Asymmetric complete (", bar(x), " = 1.60)")), "Weak" =expression(paste("Core-peripheral (", bar(x), " = 1.85)"))), name = "Path length classification",values = c("grey36","lightblue3","navajowhite2","darkorange4"),guide = guide_legend(title.position = "top",ncol = 1)) +
-theme(legend.text.align = 0)+
-  theme(legend.position="right")
+#Ffilter out two node motifs
+d_1 <- d %>% filter(motif != 1)
+#Merge dataframes to bl able to create facets
+d_2 <- merge(d_1, motif_means, by="motif")
+
+arr <- list('Strong' = expression(bold(paste("(a) Complete (strong, ", bar(x), " = 1.38)"))),
+             'Fan' = expression(bold(paste("(b) Fan (medium-strong, ", bar(x), " = 1.48)"))), 
+             'Medium-weak' = expression(bold(paste("(c) Asymmetric complete (medium-weak, ", bar(x), " = 1.60)"))), 
+             "Weak" =expression(bold(paste("(d) Core-peripheral (weak, ", bar(x), " = 1.85)"))))
+mylabel <- function(val) { return(lapply(val, function(x) arr[x])) }
+
+library(ggforce) #workaround with ggforce to have facets with same sizes
+
+p <- ggplot()+geom_point(data = d_2, aes(y=factor(motif), 100*percentil_sizeclass), shape=21,color="black",fill="azure2",size=1.75, alpha=1)+
+  geom_errorbar(data = d_2,aes(y = factor(motif), xmin=100*(mean-SE), xmax=100*(mean+SE)), 
+                width=0.8,size=0.8,color="black") +theme_bw()+
+  geom_point(data = d_2,aes(y = as.factor(motif), x=100*mean), 
+             size=2,color="black")+labs(y="Two to five node motifs", x = "Percentile")+
+  theme( strip.background = element_blank())+
+  theme(strip.text = element_text(face="bold", size=10, hjust=0),
+        panel.border=element_rect(color="black",size=1.2))
+
+p + ggforce::facet_col(vars(Broad_categories), scales = 'free', space = 'free',labeller=mylabel)
+
 #Trying to maintain a gradient from low to high in colors
@@
 Although motifs positions determined over- and under- representation independently of the identity of functional groups for most cases (rows in **Figure 3**), we found differences in the average percentile within floral visitors and pollinators functional groups (columns in **Figure 3**).
-Remarkably, the same patterns were observed but with lower average percentiles when singletones were exluded (**Figure S2**).
-Thus,
+These differences were more marked for floral visitors functional groups.
+Bees had a tendency to be over-represented in the different motif positions.
+This was also observed in lower degree for non-syrphids Diptera.
+In contrast, Lepidoptera were generally under-represented in the different motif positions and non-bee hymenoptera showed also the same tendency but with lower average percentiles.
+For plants, these differences across functional groups were less marked.
 
@@
                                       "Coleoptera","Lepidoptera","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\ndiptera","Syrphids")
+                                      "Non-syrphids\nDiptera","Syrphids")
 }else{
@@
 Average percentages of motifs close to 0 and 100 indicate under- and over- representation in empirical networks, after removing non-robust links, that is, interactions whose frequency was equal to one.
-The different motifs are coloured by the mean path length as done in @simmons2020.", fig.width=9,fig.height=5}
+The different motifs are coloured by the mean path length as done in @simmons2020.", fig.width=4.5,fig.height=6.5}
 library(lme4)
@@
 
-ggplot(NULL) + 
-  geom_point(data = d %>% filter(motif != 1),
-             aes(y=as.factor(motif), x=100*percentil_sizeclass, 
-                 color = as.factor(Broad_categories)),
-             position = "jitter",alpha=0.8)+
-  geom_errorbar(data = motif_means,aes(y = as.factor(motif), xmin=100*(mean-SE), xmax=100*(mean+SE)), 
-                width=1.0,size=1)+
-  geom_point(data = motif_means,aes(y = as.factor(motif), x=100*mean), 
-                size=2)+
-  labs(y="Two to five node motifs", x = "Percentile",colour="Path length classification")+
-  theme_bw() + scale_color_manual(labels = c('Strong' = expression(paste("Complete (", bar(x), " = 1.38)")),'Fan' = expression(paste("Fan (", bar(x), " = 1.48)")), 'Medium-weak' = expression(paste("Asymmetric complete (", bar(x), " = 1.60)")), "Weak" =expression(paste("Core-peripheral (", bar(x), " = 1.85)"))), name = "Path length classification",values = c("grey36","lightblue3","navajowhite2","darkorange4"),guide = guide_legend(title.position = "top",ncol = 1)) +
-theme(legend.text.align = 0)+
-  theme(legend.position="right")
+#Ffilter out two node motifs
+d_1 <- d %>% filter(motif != 1)
+#Merge dataframes to bl able to create facets
+d_2 <- merge(d_1, motif_means, by="motif")
+
+arr <- list('Strong' = expression(bold(paste("Complete (strong, ", bar(x), " = 1.38)"))),
+             'Fan' = expression(bold(paste("Fan (medium-strong, ", bar(x), " = 1.48)"))), 
+             'Medium-weak' = expression(bold(paste("Asymmetric complete (medium-weak, ", bar(x), " = 1.60)"))), 
+             "Weak" =expression(bold(paste("Core-peripheral (weak, ", bar(x), " = 1.85)"))))
+mylabel <- function(val) { return(lapply(val, function(x) arr[x])) }
+
+library(ggforce) #workaround with ggforce to have facets with same sizes
+
+p <- ggplot()+geom_point(data = d_2, aes(y=factor(motif), 100*percentil_sizeclass), shape=21,color="black",fill="azure2",size=2, alpha=1)+
+  geom_errorbar(data = d_2,aes(y = factor(motif), xmin=100*(mean-SE), xmax=100*(mean+SE)), 
+                width=1.0,size=1,color="grey20") +theme_bw()+
+  geom_point(data = d_2,aes(y = as.factor(motif), x=100*mean), 
+             size=2,color="grey20")+labs(y="Two to five node motifs", x = "Percentile")+
+  theme( strip.background = element_blank())+
+  theme(strip.text = element_text(face="bold", size=10, hjust=0),
+        panel.border=element_rect(color="black",size=1.2))
+
+p + ggforce::facet_col(vars(Broad_categories), scales = 'free', space = 'free',labeller=mylabel)
 

### 2021-09-28 Draft/Draft.Rmd
Figure update and results from heatmaps

@@
 
-**Motif functional groups position**
+**Over and under-represented functional groups on motif positions**
 
@@
 These differences were more marked for floral visitors functional groups.
-Bees had a tendency to be over-represented in the different motif positions.
-This was also observed in lower degree for non-syrphids Diptera.
-In contrast, Lepidoptera were generally under-represented in the different motif positions and non-bee hymenoptera showed also the same tendency but with lower average percentiles.
-For plants, these differences across functional groups were less marked.
+The group of Bees was the most over-represented, followed by non-syrphids Diptera, syrphids, Coleoptera, non-bee hymenoptera and finally Lepidoptera which was the most under-represent functional group on the different motif positions.
+Although for plants the differences across groups were less pronounced, from most represented to lowest we found self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.
 
@@
 ```
+
+**Over- and under-represented funtional group combinations of motifs**
 

### 2021-09-29 Draft/Draft.Rmd
Results of figure 4 commented

@@
 
+__Jose B. Lanuza^1,2^__  | __Alfonso Allen-Perkins^2,3^__ |  __Romina Rader^1^__ | __Ignasi Bartomeus^2^__
+
+1 School of Environmental and Rural Science, University of New England, Armidale, New South Wales 2350, Australia.
+
+2 Estación Biológica de Doñana (EBD-CSIC), E-41092 Seville, Spain.
+
+3 Departamento de Ingeniería Eléctrica, Electrónica, Automática y Física Aplicada, ETSIDI, Universidad Politécnica de Madrid, 28040 Madrid, Spain.
+
 \captionsetup[table]{labelformat=empty}
@@
 
+\doublespacing
+
 ##INTRODUCTION
@@
 
-Traditionally, plant-pollinator research has focused on direct interactions but overlooked indirect interactions (the mediated effect between two species by a third species), such as facilitative or competitive interactions between plants for pollinators [@moeller2004; @sargent2008].
-Despite the widespread nature of indirect interactions in ecological communities [@strauss1991], plant-pollinator research often fails to finely capture those indirect interactions with the conventional analytical tools that condense the information either by species (e.g.
-interaction frequency) or in single topological indices (e.g.
-nestedness).
+Traditionally, plant-pollinator research has focused on direct interactions but overlooked indirect interactions (i.e., the mediated effect between two species by a third species), such as facilitative or competitive interactions between plants for pollinators [@moeller2004; @sargent2008].
+Despite the widespread nature of indirect interactions in ecological communities [@strauss1991], plant-pollinator research often fails to finely capture those indirect interactions with the conventional analytical tools that condense the information either by species (e.g., interaction frequency) or in single topological indices (e.g., nestedness).
 Nonetheless, the emerging framework of network motifs in plant-pollinator research, the building blocks of a network that depict subsets of interactions [@milo2002], allows to consider both direct and indirect interactions [@simmons2019].
@@
 Floral visitor functional groups were divided by the main taxonomical groups that differed in life form and behaviour.
-Once we split the different plant-pollinator networks into their motif elements, we explored: (i) over and under-represented motifs; (ii) over and under-represented functional groups in the different motif positions; (iii) the probability of finding plant and floral visitor functional groups in the different motif positions; and, (iv) over- and under- represented functional group combinations within the different motifs.
+Once we split the different plant-pollinator networks into their motif elements, we explored: (i) the overall motif patterns (over and under-represented motifs); (ii) over and under-represented functional groups in the different motif positions; (iii) the probability of finding plant and floral visitor functional groups in the different motif positions; and, (iv) over- and under- represented functional group combinations within the different motifs.
+
+---
+# THIS IS A COMMENT
+# Each os this points (i to iv) corresponds to a figure
+# I think that ideally we can have that structure on methods and results (excluding functional groups)
+# so far we have (i), (ii) and (iv) on methods
+# we lack an explicit mention to (iii) 
+# maybe merge it with another research question and just have 3?
+# What do you think? 
+---
 
@@
 
-First, plant species were grouped thorugh hierarchical clustering into the optimal number of functional groups that summarized the main plant reproductive strategies.
-We used the trait dataset collated in Lanuza et al., (unpublished) that comprised 1,506 plant species and contained the same 60 plant-pollinator networks used in this study plus some non-weighted and weighted metawebs (see **Table S1** Lanuza et al., unpublished).
+First, plant species were grouped through hierarchical clustering into the optimal number of functional groups that summarized the main plant reproductive strategies.
+We used the trait dataset collated in Lanuza et al., (unpublished) that comprised 1,506 plant species and contained the same 60 weighted plant-pollinator networks used in this study plus 4 additional large unweighted metawebs (see **Table S1** Lanuza et al., unpublished).
 This dataset consisted on 8 floral, 4 reproductive and 3 vegetative traits excluding traits with high percentage of missing values (over 30%; **Table S2**).
@@
 We opted to divide floral visitors on the taxonomic rank level and not with functional traits because the main orders of floral visitors differed in form and behaviour and had lower superior taxonomical complexity (i.e., floral visitors had 6 orders versus plants that had 38).
-Thus, this allowed us to group floral visitors into functional groups that represented adequately the main life strategies of the possible pollinators: (i) Hymenoptera-Anthophila (bees), (ii) Hymenoptera-non-Anthophila (other non-bee Hymenoptera), (iii) Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera, (vi) Coleoptera, (vii).
-However, a minor set of species belonged to other functional groups that were considered in the analysis as lizards, birds and other insects but not discussed further because of their low representation in the set of analysed networks.
+Thus, this allowed us to group floral visitors into functional groups that represented adequately the main life strategies of the possible pollinators: (i) Hymenoptera-Anthophila (bees), (ii) Hymenoptera-non-Anthophila (other non-bee Hymenoptera), (iii) Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera and (vi) Coleoptera.
+However, a minor set of species belonged to other functional groups that were considered in analyses but not discussed further because of their low representation (3.55% of the total interactions recorded in the full set of networks).
+These functional groups were 'lizards', 'birds' and 'other insects'.
+This last group was formed by a mix of uncommon insect taxa on the full set of networks.
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="**Figure 1.** Adapted figure of Simmons et al., 2019 with all the possible motifs from two to five species in bipartite networks.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, fig.pos="t", warning=FALSE,out.width="75%",fig.align="center", fig.cap="\\textbf{Figure 1.} Adapted figure of Simmons et al., 2019 with all the possible motifs from two to five species in bipartite networks.
 There is a total of 17 possible motifs with 46 different positions denoted within each node.", fig.width=10,fig.height=8}
@@
 
-To test the effect of singletones on the motif frequencies and motif functional groups' positions, we applied the previous analyses to the same set of networks (**Table S1**) but considering only interactions whose frequency was greater than one (64.98% of interactions; see **Figures S3 and S4**).
+To test the effect of singletones on the motif frequencies and motif functional groups' positions, we applied the previous analyses to the same set of networks (**Table S1**) but considering only interactions whose frequency was greater than one (64.98% of interactions; see **Figures S1 and S2**).
 
@@
 In total, there were 1126 species of floral visitor with 6325 interactions recorded with plants.
-From highest to lowest records of interactions of floral visitors with plants we found: bees with 2256 interactions, non-syrphid Diptera with 1768 interactions, syrphids with 845 interactions, Lepidoptera with 437 interactions, Coleoptera with 432 interactions and non-bee Hymenoptera with 362 interactions.
+There were 2256 bee interactions with plants, 1768 non-syrphid Diptera interactions, 845  syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee Hymenoptera interactions.
 
@@
 Motifs 3, 5, 9, 10 and 14 were under-represented in empirical networks, that is, all were close to the 1st percentile and under the 25th percentile.
-Remarkably, four out of five of these motifs belonged to the largest path length classification (i.e., core-peripheral).
+Further, four out of five of these motifs belonged to the largest path length classification (i.e., core-peripheral).
 In addition, motifs 2, 6, 7, 16 and 17 were over-represented, all over the 75th percentile and thus the closest to the 99th percentile.
@@
 The remaining motifs (i.e., 4, 8, 11, 12, 13, and 15) were between the 25th and 75th percentile but closest to over-representation.
-Remarkably, the exclusion of singletones from this analysis did not change the observed results (**Figure S1**).
+Notably, the exclusion of singletones from this analysis did not change the observed results (**Figure S1**).
 
@@
 
-p <- ggplot()+geom_point(data = d_2, aes(y=factor(motif), 100*percentil_sizeclass), shape=21,color="black",fill="azure2",size=1.75, alpha=1)+
+p <- ggplot()+geom_point(data = d_2, aes(y=factor(motif), 100*percentil_sizeclass), shape=21,color="black",fill="azure2",size=1.75, alpha=0.3)+
   geom_errorbar(data = d_2,aes(y = factor(motif), xmin=100*(mean-SE), xmax=100*(mean+SE)), 
@@
 The group of Bees was the most over-represented, followed by non-syrphids Diptera, syrphids, Coleoptera, non-bee hymenoptera and finally Lepidoptera which was the most under-represent functional group on the different motif positions.
-Although for plants the differences across groups were less pronounced, from most represented to lowest we found self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.
+Although for plants the differences across groups were less pronounced, from most represented functional group on the different motif positions to lowest we found self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.
 
@@
 
-**Over- and under-represented funtional group combinations of motifs**
+The different observed frequencies on the different motif positions showed a hirarchical order of probabilities for floral visitors (**Figure 4**).
+That is, the functional group of 'bees' was the most abundant one on all motif positions followed by non-syrphid Diptera which was after bees, the second most frequent functional group on all positions.
+Then, the group of syrphids was the most abundant in all positions but two (positions 28 and 31 from motifs 11 and 12, respectively).
+After syrphids, Coleoptera was the most frequent group on the different positions followed by non-bee Hymenoptera and finally, Lepidoptera which was the less frequent group on all positions but two (positions 12 and 22 from motifs 5 and 9, respectively).
+Remarkably, plant functional groups were more variable on the different motif positions.
+However, there were also predominant functional groups found across the different motif positions.
+The three most frequent groups were 'tall plants with small unisexual flowers', 'self-incompatible perennials with large flowers' and 'small outcrossing perennials'.
+On the contrary, the groups of 'selfing herbs' and 'short lived outcxrossers with long zygomorphic flowers' had the lowest probability to be present on the different motifs plant positions.
 
@@
   # Define the number of colors you want
-  nb.cols <- 5
-  mycolors <- c(brewer.pal(6, "Paired"),brewer.pal(5, "Dark2"))
+ mycolors <- c("#A6CEE3", "chocolate2",  "gold2", "#1F78B4","#B2DF8A",
+                     "gray58", "lightgoldenrod2","thistle2", "burlywood","lightcoral", "olivedrab3")
 
@@
           axis.text.y=element_blank(),
-          axis.ticks.y=element_blank())+
+          axis.ticks.y=element_blank(),
+          legend.title = element_text(size=12, face="bold"),legend.background = element_rect(size=0.5, linetype="solid",colour ="black"))+
     labs(x=NULL,y=NULL)+
@@
 
+**Over- and under-represented funtional group combinations of motifs**
+
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 5.**"}
@@
   # Define the number of colors you want
-  mycolors <- c(brewer.pal(6, "Paired"),brewer.pal(5, "Dark2"))
+ mycolors <- c("#A6CEE3", "chocolate2",  "gold2", "#1F78B4","#B2DF8A",
+                     "gray58", "lightgoldenrod2","thistle2", "burlywood","lightcoral", "olivedrab3")
 
@@
 ```
+
+##DISCUSSION
 

### 2021-10-05 Draft/Draft.Rmd
Caption of figure 5 and edits on results

@@
 Nonetheless, the emerging framework of network motifs in plant-pollinator research, the building blocks of a network that depict subsets of interactions [@milo2002], allows to consider both direct and indirect interactions [@simmons2019].
-The analysis of motifs (meso-scale) in plant-pollinator networks have revealed that the different ecological processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions [@simmons2020].
-Yet, the global patterns of indirect interactions in plant-pollinator networks (over- and under- represented motifs) are still unknown.
+The analysis of motifs on this intermediate level of complexity (meso-scale) in plant-pollinator networks have revealed that the different ecological processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions [@simmons2020].
+Yet, the global patterns of indirect interactions in plant-pollinator networks are still unknown (e.g., over- and under- represented motifs).
 
@@
 We extracted the position frequencies of all motifs from three to five nodes for each network and species by using the _bmotif_ package [@bmotifsimmons2019].
-To estimate the position frequencies of each functional group in a given network, we added the frequencies of those species that belong to the group, and then, we normalised the resulting frequencies by dividing the position measure for each group by the total number of times that a group appears in any position within the same motif size class.
+To estimate the position frequencies of each functional group in a given network, we added the frequencies of those species that belong to the group, and then, we normalised the resulting frequencies by dividing the position measure [Sum of position frequencies?]() for each group by the total number of times that a group appears in any position within the same motif size class.
 Then, we calculated the percentile of the observed position frequencies for each group and network, just like we did with motif frequencies.
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure 2.** Comparison of motif frequencies between empirical and simulated networks divided by average path length (plots a, b, c and d) as determined in Simmons et al.
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure 2.** Comparison of motif frequencies between empirical and simulated networks grouped by average path length (plots a, b, c and d) as determined in Simmons et al.
 (2020).
@@
 
-Although motifs positions determined over- and under- representation independently of the identity of functional groups for most cases (rows in **Figure 3**), we found differences in the average percentile within floral visitors and pollinators functional groups (columns in **Figure 3**).
-These differences were more marked for floral visitors functional groups.
-The group of Bees was the most over-represented, followed by non-syrphids Diptera, syrphids, Coleoptera, non-bee hymenoptera and finally Lepidoptera which was the most under-represent functional group on the different motif positions.
-Although for plants the differences across groups were less pronounced, from most represented functional group on the different motif positions to lowest we found self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="\\textbf{Figure 3.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions.
+The comparison of the frequencies between the positions of motifs of empirical and simulated networks showed that motifs positions determined over- and under- representation independently of the identity of functional groups for most cases (rows in **Figure 3**).
+However, we also found differences in the average percentile within floral visitors and plant functional groups on the different motif positions (columns in **Figure 3**).
+These differences were more marked for floral visitors functional groups, and thus the groupings by average path length were less informative for floral visitors than for plants.
+In other words, for plants motifs by themselves were more descriptive than for floral visitors.
+From most over- to under-represented floral visitors functional groups, we found: bees, non-syrphids Diptera, syrphids, Coleoptera, non-bee hymenoptera and Lepidoptera.
+Although plant functional groups showed less differences between them, there were also more represented functional groups than others, thus from most over- to under-represented groups on the different motif positions we found: self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', out.width="95%",fig.cap="\\textbf{Figure 3.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions.
 The different motif positions are dividied by the average path length clasification determined by Simmons et al.
@@
 The three most frequent groups were 'tall plants with small unisexual flowers', 'self-incompatible perennials with large flowers' and 'small outcrossing perennials'.
-On the contrary, the groups of 'selfing herbs' and 'short lived outcxrossers with long zygomorphic flowers' had the lowest probability to be present on the different motifs plant positions.
+On the contrary, the groups of 'selfing herbs' and 'short lived outcrossers with long zygomorphic flowers' had the lowest probability to be present on the different motifs plant positions.
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 5.**"}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 5.** Z-score comparison (95% confidence level) of the observed and expected frequencies motif combinations with four specific graphical examples of the most probable motifs of being observed for each category delimitid by the z-score critical values: under-represented, no statistical difference and over-represented."}
 
@@
 
+\newpage
+
 **FIGURES**
@@
 ```
+
+\newpage
 
@@
 
+\newpage
+
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=13, fig.cap="**Figure S4.** Hierarchical clustering dendrogram with the branches coloured by the optimal number of clusters (5).

### 2021-10-05 Draft/Draft.Rmd
Parragraph for figure 5

@@
 - \captionsetup[figure]{labelformat=empty}
+- \usepackage{lscape}
+- \newcommand{\blandscape}{\begin{landscape}}
+- \newcommand{\elandscape}{\end{landscape}}
 
@@
 
+The statistical comparison with z-scores between the observed functional group combinations and the expected ones showed a Gausian distribution with 65% of under-represented group combinations, 20% of no statistical difference and 15% of under-represented ones (**Figure 5**).
+Remarkably, motifs with small node combinations (i.e., 2 and 3 nodes) only appeared as under-represented.
+Motifs with 4 and 5 node combinations appeared in the three statistical categories but 4 node motifs had a higher porportion in the under-represented category (10% in comparison with the 1% and the 3% of the no statiscal difference and over-represented categories, respectively).
+Finally, 5 node motifs were in similar prportions in the no statistical difference and over-represented categories (99% and 97%, respectively) but they appeared in lower porportion in the under-represented category (89%).
+When, we explore the identity on the different positions of the most probable motif combinations we find as expected that the most common functional groups rule these positions on the most probable motif combiantions (lower panel **Figure 5**).
+
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 5.** Z-score comparison (95% confidence level) of the observed and expected frequencies motif combinations with four specific graphical examples of the most probable motifs of being observed for each category delimitid by the z-score critical values: under-represented, no statistical difference and over-represented."}
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
+```{r, echo=FALSE, message=FALSE, cache=FALSE,fig.width=12,  warning=FALSE}
 ##############################
@@
   kable( longtable = T, booktabs = T,linesep = "\\addlinespace",align = c("cccc"),escape = FALSE, caption= "\\textbf{Table S1.} List of studies ordered by author with the year of publication, number of contributed networks and digital object identifier") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=T,position = c("center"))
+  kable_styling(latex_options = c("repeat_header","striped"),  full_width=F,position = c("center"))
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=12, fig.width=12}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=16, fig.width=12}
 
@@
 kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c"),caption = "\\textbf{Table S2.} Traits used to delimit the different plant functional groups divided in quantitative and categorical traits.") %>%
-kable_styling(full_width = T) %>%
+kable_styling(full_width = T,latex_options = c("striped")) %>%
 add_header_above(c("Quantitative traits" = 2,"Categorical traits" = 2),bold=T)  %>%
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="**Figure S1.** Comparison of the motif frequencies between empirical and simulated networks excluding singletones.
-Average percentages of motifs close to 0 and 100 indicate under- and over- representation in empirical networks, after removing non-robust links, that is, interactions whose frequency was equal to one.
-The different motifs are coloured by the mean path length as done in @simmons2020.", fig.width=4.5,fig.height=6.5}
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure S1.** Comparison of motif frequencies between empirical and simulated networks grouped by average path length (plots a, b, c and d) as determined in Simmons et al.
+(2020) without considering singletones.
+This is shown with the mean percentage of motif frequencies in empirical networks that were over the motif frequencies of the simulated ones (percentiles).
+This was done by network (light blue dots) and then averaged for all networks (black dots with error bars that correspond to the standard deviation)."}
 library(lme4)
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="\\textbf{Figure S2.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions excluding singletones, after removing non-robust links, that is, interactions whose frequency was equal to one.
-The different motif positions are dividied by the average path length clasification by @simmons2020."}
+The different motif positions are dividied by the average path length clasification by Simmons et al.
+(2020)"}
 
@@
 \newpage
+
+\blandscape
 
@@
 ```
+
+\elandscape

### 2021-10-05 Draft/Draft.Rmd
Update of abstract

@@
 motifs) and those constitute the building blocks of the whole network.
-Here, we have compiled 60 networks from 18 different studies and show that some motifs are consitently over-represented worldwide, suggesting that the building blocks of plant-pollintor networks are not random and are associated to ...
-Second, we show that the position of pollinator guilds and plant reproductive strategies is not random with respect to the positions occupied within each motif.
-...
-Hence, we show that species ecology is shaping the building blocks that conform the web of life.
+Here, we have compiled 60 networks from 18 different studies and show that some motifs are consitently under- and over-represented worldwide, suggesting that the building blocks of plant-pollintor networks are not random and are associated depending on the motif position and trophic level to specific fucntional groups.
+For instance, bees are the predominant group found on all motif positions but for plants there are three functional groups associated with corss-pollination that are similarly found on all motif positions.
+Hence, the distribution of funtional groups on the different positions is not random either which determine in last instance different probabilities of the overall functional group combinations of motifs.
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', out.width="95%",fig.cap="\\textbf{Figure 3.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions.
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', out.width="90%",fig.cap="\\textbf{Figure 3.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions.
 The different motif positions are dividied by the average path length clasification determined by Simmons et al.
@@
 
+\newpage
+
 **Over- and under-represented funtional group combinations of motifs**
 
-The statistical comparison with z-scores between the observed functional group combinations and the expected ones showed a Gausian distribution with 65% of under-represented group combinations, 20% of no statistical difference and 15% of under-represented ones (**Figure 5**).
+The statistical comparison with z-scores between the observed functional group combinations and the expected ones showed a modified Gaussian distribution (Johnson's $S_U$) with 65% of under-represented group combinations, 20% of no statistical difference and 15% of under-represented ones (**Figure 5**).
 Remarkably, motifs with small node combinations (i.e., 2 and 3 nodes) only appeared as under-represented.
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 5.** Z-score comparison (95% confidence level) of the observed and expected frequencies motif combinations with four specific graphical examples of the most probable motifs of being observed for each category delimitid by the z-score critical values: under-represented, no statistical difference and over-represented."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 5.** Z-score comparison (95% confidence level) of the observed and expected frequencies motif combinations with four specific graphical examples of the most probable motifs of being observed for each category delimited by the z-score critical values: under-represented, no statistical difference and over-represented."}
 
@@
 
+**Table S1** List of plant-pollinator network studies.
+
+**Table S2** Type of plant traits used in this study.
+
+**FIGURES**
+
+**Figure S1** Over and under-estimated motif frequencies.
+
+**Figure S2** Over and under-estimated functional groups on motif positions.
+
+**Figure S3** Plant trait composition of functional groups.
+
+**Figure S4** Plant dendrogram with functional groups.
+
+\blandscape
+
 ```{r, echo=FALSE, message=FALSE, cache=FALSE,fig.width=12,  warning=FALSE}
@@
 
+\elandscape
+
 \newpage
@@
 
-\newpage
-
-**FIGURES**
+\clearpage
 

### 2021-10-05 Scripts/Data_Exploration_Figure_5.R

@@ -1,0 +1,99 @@
+
+
+library(tidyverse)
+library(RColorBrewer)
+
+# Data with pollinator/plant labels
+
+plant_means_reordered <- read_csv("Data/Csv/plant_abs_freq_means.csv")
+pollinator_means_reordered <- read_csv("Data/Csv/pollinator_abs_freq_means.csv")
+#Filter out in order to have just 6 FG'S
+pollinator_means_reordered <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds", "Lizards", "Other_insects"))
+
+
+####################################################################################################
+#Read data to check top 5 motif of each category of observed propabilities
+
+#Under, No signi, Over-rep
+####################################################################################################
+# Check top Z-scores of each group (Under, No diff, Over)
+
+#Read data
+data <- read.csv("Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
+
+#Find critical value of Z-score
+p <- 0.05 #cutoff probability 95% confidence
+critical_value <- qnorm(p/2) #double tail probability divide by 2
+
+data_1 <- data %>%
+  mutate(infra_over_represented = case_when(
+    z_score < -abs(critical_value) ~ "infra",
+    between(z_score, -abs(critical_value), abs(critical_value)) ~ "no_diff",
+    z_score > abs(critical_value) ~ "over"
+  ))
+
+
+#data_2 <- filter(data_1, abs(z_score)<2000) 
+#str(data_2)
+
+
+#Add number of nodes of each motif
+data_1$N_node
+data_1$N_node[data_1$motif=="1"] <- 2 # 2 SPECIES
+data_1$N_node[data_1$motif=="2"] <- 3 # 3 SPECIES
+data_1$N_node[data_1$motif=="3"] <- 3
+data_1$N_node[data_1$motif=="4"] <- 4 # 4 SPECIES
+data_1$N_node[data_1$motif=="5"] <- 4
+data_1$N_node[data_1$motif=="6"] <- 4
+data_1$N_node[data_1$motif=="7"] <- 4
+data_1$N_node[data_1$motif=="8"] <- 5 # 5 SPECIES 
+data_1$N_node[data_1$motif=="9"] <- 5
+data_1$N_node[data_1$motif=="10"] <- 5
+data_1$N_node[data_1$motif=="11"] <- 5
+data_1$N_node[data_1$motif=="12"] <- 5
[…]

### 2021-10-08 Draft/Draft.Rmd
Alfonso's comments on pdf added to markdown, also some edits done accordingly

@@
 
-The interaction between plants and pollinators can be studied at different scales, from species level interactions (micro-scale) to the full network structure (macro-scale).
-Research of the plant-pollinator network structure have proven common invariant structural properties across them including a degree distribution that decays as a power law [@jordano1987], nestedness [@bascompte2003], or modularity in large networks [@olesen2007].
+Because of the tremendous complexity of ecological networks, species interactions are generally condensed in metrics that summarize this information [@guimaraes2020].
+Plant-pollinator interactions are no exception, and they are often studied with indices that aggregate the information at the species (micro-scale) or network level (macro-scale).
+Plant-pollinator network level approcahes have proven common invariant structural properties across them including a degree distribution that decays as a power law [@jordano1987], nestedness [@bascompte2003], or modularity in large networks [@olesen2007].
 In addition, species phenological overlap, morphological matching and species abundances have been shown to be determinant for the understanding of pairwise plant-pollinator interactions [@bartomeus2016; @stang2006; @peralta2020].
-However, both species level information and the holistic view of the full network involves missing relevant information for the understanding of ecological processes [@cirtwill2018; @simmons2019].
+Despite the unquestionable progress with the use of these metrics at both species and network level, condensing the information into a single metric implies the loss of relevant ecological information that obscure the understanding of the ecological processes [@cirtwill2018; @simmons2019].
+
+---
+THIS IS A COMMENT
+Sugerencia Alfonso (Talking about the last phrase "however,...""): Esta parte de la frase me ha dejado con la pregunta de ¿por qué implica perder info?
+Intentaría dar algún dato que ilustre lo anterior, o la importancia de las relaciones indirectas, aunque esto último lo metes en el siguiente párrafo
+
+Sugerencia Alfonso (next paragraph, desde inicio a "(e.g., nestedness)"):Quizás esto lo intentaría sintetizar y meter al final del párrafo anterior y ya empezar en el segundo párrafo a hablar de motifs, como marco de trabajo/nivel de análisis complementario a los anteriores.
+---
 
@@
 Despite the widespread nature of indirect interactions in ecological communities [@strauss1991], plant-pollinator research often fails to finely capture those indirect interactions with the conventional analytical tools that condense the information either by species (e.g., interaction frequency) or in single topological indices (e.g., nestedness).
-Nonetheless, the emerging framework of network motifs in plant-pollinator research, the building blocks of a network that depict subsets of interactions [@milo2002], allows to consider both direct and indirect interactions [@simmons2019].
-The analysis of motifs on this intermediate level of complexity (meso-scale) in plant-pollinator networks have revealed that the different ecological processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions [@simmons2020].
-Yet, the global patterns of indirect interactions in plant-pollinator networks are still unknown (e.g., over- and under- represented motifs).
+Nonetheless, the emerging framework of network motifs (small networks recorded in a given network) in plant-pollinator research, often referred to as the building blocks of a network that depict subsets of interactions [@milo2002], allows to consider both direct and indirect interactions [@simmons2019].
+The analysis of motifs in plant-pollinator networks have revealed that the different ecological processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions [@simmons2020].
+Yet, the global patterns of indirect interactions in real plant-pollinator networks are still unknown (e.g., over- and under- represented motifs).
+
+---
+THIS IS A COMMENT
+Sugerencia Alfonso: Yo haría un único párrafo hablando del marco de motifs y de sus principales obstáculos: (i) el desconocimiento de los patrones de relaciones indirectas en redes de plantas polinizadores reales y (ii) la desconexión entre las estructuras de los motifs y la ecología de las especies (sus comportamientos, estrategias, etc.).
+Luego pasaría al párrafo de qué hacemos en este trabajo.
+Digo esto porque la última frase del párrafo anterior me parecía que se quedaba algo colgada.
+---
 
@@
 ---
-# THIS IS A COMMENT
+# THIS IS A COMMENT (Jose)
 # Each os this points (i to iv) corresponds to a figure
@@
 We extracted the position frequencies of all motifs from three to five nodes for each network and species by using the _bmotif_ package [@bmotifsimmons2019].
-To estimate the position frequencies of each functional group in a given network, we added the frequencies of those species that belong to the group, and then, we normalised the resulting frequencies by dividing the position measure [Sum of position frequencies?]() for each group by the total number of times that a group appears in any position within the same motif size class.
+To estimate the position frequencies of each functional group in a given network, we added the frequencies of those species that belong to the group, and then, we normalised the resulting frequencies by dividing the position measure for each group by the total number of times that a group appears in any position within the same motif size class.
 Then, we calculated the percentile of the observed position frequencies for each group and network, just like we did with motif frequencies.
@@
 Then, we determined whether the observed probabilities are likely to come from the expected probabilities or not.
-To calculate the observed probability ($p_i^O$) of functional groups within a motif ($i$; e.g., motif 3, bee + bee + functional group 2), we divided the number of times that $i$ appears in our set of empirical networks ($n_i^O$) by the sum of the number of times that each possible combination appeared: $p_i^O = n_i^O / \sum_{k=1}^{53,250} n_k^O$.
+To calculate the observed probability ($p_i^O$) of functional groups within a motif $i$ (e.g., motif 3, bee + bee + functional group 2), we divided the number of times that $i$ appears in our set of empirical networks ($n_i^O$) by the sum of the number of times that each possible combination appeared: $p_i^O = n_i^O / \sum_{k=1}^{53,250} n_k^O$.
 To estimate the expected probability of a given motif combination $i$, $p_i^E$, firstly, we calculated the probability of finding a given functional group $x$ in the position $\alpha$ of $i$, $p_i(x,\alpha)$.
@@
 
-The hierarchical cluster analysis divided the dataset into five different clusters with different and overlapping characteristics (**Figure S3** and **Figure S4**).
-Cluster 1 referred to as 'selfing herbs' consisted on herbs with hermaphroditic flowers with high levels of autonomous selfing.
-Cluster 2 or 'small outcrossing perennials' had small perennial species with a mixed of life forms (i.e., trees shrubs and herbs) with outcrossing hermaphroditic flowers.
-Cluster 3 referred to as 'self-incompatible perennials with large flowers' comprised perennial species with a mixed of life forms and large self-incompatible hermaphroditic flowers with high number of ovules.
-Cluster 4 or 'tall plants with small unisexual flowers' had the tallest species, highest proportion of shrub and tree life forms, dioecious and monoecious breeding systems, small flowers and the highest numbers of flowers and inflorescences per plant.
-Finally, cluster 5 or 'short-lived outcrossers with long zygomorphic flowers' consisted on small perennial and short-lived herbs with long self-compatible zygomorphic flowers that were unable to self-pollinate.
-
-In total, there were 1126 species of floral visitor with 6325 interactions recorded with plants.
-There were 2256 bee interactions with plants, 1768 non-syrphid Diptera interactions, 845  syrphids interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions and 362 non-bee Hymenoptera interactions.
+The hierarchical cluster analysis divided the dataset into five different groups with different and overlapping characteristics (**Figure S3** and **Figure S4**).
+Group 1 referred to as 'selfing herbs' consisted on herbs with hermaphroditic flowers with high levels of autonomous selfing.
+Group 2 or 'small outcrossing perennials' had small perennial species with a mixed of life forms (i.e., trees shrubs and herbs) with outcrossing hermaphroditic flowers.
+Group 3 referred to as 'self-incompatible perennials with large flowers' comprised perennial species with a mixed of life forms and large self-incompatible hermaphroditic flowers with high number of ovules.
+Group 4 or 'tall plants with small unisexual flowers' had the tallest species, highest proportion of shrub and tree life forms, dioecious and monoecious breeding systems, small flowers and the highest numbers of flowers and inflorescences per plant.
+Finally, group 5 or 'short-lived outcrossers with long zygomorphic flowers' consisted on small perennial and short-lived herbs with long self-compatible zygomorphic flowers that were unable to self-pollinate.
+
+In total, there were 1,126 species of floral visitor with 6,325 interactions recorded with plants.
+Most plants interacted with bees (2,256 interactions) and non-syrphid Diptera (1,768) followed by syrphids (845), Lepidoptera (437), Coleoptera (432) and non-bee Hymenoptera (362).
 
@@
 
+---
+THIS IS A COMMENT
+Alfonso sobre la frase "These differences were more marked for floral visitors...": Cómo se infiere esto? Es viendo el dendrograma?
+
+Jose: He modidficado el texto y creo que ahora está más claro
+---
+
 The comparison of the frequencies between the positions of motifs of empirical and simulated networks showed that motifs positions determined over- and under- representation independently of the identity of functional groups for most cases (rows in **Figure 3**).
 However, we also found differences in the average percentile within floral visitors and plant functional groups on the different motif positions (columns in **Figure 3**).
-These differences were more marked for floral visitors functional groups, and thus the groupings by average path length were less informative for floral visitors than for plants.
-In other words, for plants motifs by themselves were more descriptive than for floral visitors.
-From most over- to under-represented floral visitors functional groups, we found: bees, non-syrphids Diptera, syrphids, Coleoptera, non-bee hymenoptera and Lepidoptera.
+These differences were more marked for floral visitors than for plant functional groups (the differences between min and max percentiles per position were generally two-three times larger for floral visitors).
+Hence, the average percentile per position in plants was determined in a larger extent by the position itself rather than the functional group in contrast to floral visitors.
+From most over- to under-represented floral visitors functional groups on the different motif positions (indicated with the dendrogram order in **Figure 3**), we found: bees, non-syrphids Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.
 Although plant functional groups showed less differences between them, there were also more represented functional groups than others, thus from most over- to under-represented groups on the different motif positions we found: self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.
@@
 The different motif positions are dividied by the average path length clasification determined by Simmons et al.
-(2020)."}
+(2020).
+The superior dendrogram indicates the differences across groups with the more separated groups showing larger differences."}
 
@@
 draw(ht_list, auto_adjust = FALSE, cluster_rows = F)
+
+#Exploration of min max differences in the percentile position for plants and poll.
+#heat_pollinators[3:8]
+#
+#
+#heat_plants[3:7]
+#
+#
+#library(dplyr)
+#heat_pollinators %>%
+#  mutate(d = pmin())
+#
+#
+#colnames(heat_pollinators)<- c("position", "Broad_categories", "Bee",
+#                               "Coleoptera", "Lepidoptera","non_bee_hymenop",
+#                               "non_syrphid_dip", "syrphid")
+#
+#h <- heat_pollinators %>%
+#  mutate(min = pmin(Bee,
+#                  Coleoptera, Lepidoptera,non_bee_hymenop,
+#                  non_syrphid_dip, syrphid))%>%
+#  mutate(max = pmax(Bee,
+#                    Coleoptera, Lepidoptera,non_bee_hymenop,
+#                    non_syrphid_dip, syrphid))
+#
+#diff <- h$max-h$min
+#
+##################################################################################
+##################################################################################
+#
+#colnames(heat_plants)<- c("position", "Broad_categories", "one",
+#                               "two", "three","four",
+#                               "five")
+#
+#f <- heat_plants %>%
+#  mutate(min = pmin(1,
+#                    one, two,three,
+#                    four, five))%>%
+#  mutate(max = pmax(one,
+#                    two, three,four,
+#                    five))
+#
+#diff_1 <- f$max-f$min
+#
+#cbind(diff,diff_1)
+#
 
@@
 The statistical comparison with z-scores between the observed functional group combinations and the expected ones showed a modified Gaussian distribution (Johnson's $S_U$) with 65% of under-represented group combinations, 20% of no statistical difference and 15% of under-represented ones (**Figure 5**).
-Remarkably, motifs with small node combinations (i.e., 2 and 3 nodes) only appeared as under-represented.
+In addition, motifs with small node combinations (i.e., 2 and 3 nodes) only appeared as under-represented.
 Motifs with 4 and 5 node combinations appeared in the three statistical categories but 4 node motifs had a higher porportion in the under-represented category (10% in comparison with the 1% and the 3% of the no statiscal difference and over-represented categories, respectively).
@@
 When, we explore the identity on the different positions of the most probable motif combinations we find as expected that the most common functional groups rule these positions on the most probable motif combiantions (lower panel **Figure 5**).
+
+---
+THIS IS A COMMENT
+
+Alfonso (comentario después de fig 5 donde tenía remarkably y ahora un in addition): Yo creo que todo esto es expected.
+Sin embargo, las explicaciones de por qué lo es probablemente van en la discusión.
+Lo mismo que el ajuste de la Johnson's SU: la cola larga de la derecha la producen la sobreabundancia de motifs de 4 y 5 nodos, en comparación con los de 3.
+---
 
@@
 
-p <- ggplot()+geom_point(data = d_2, aes(y=factor(motif), 100*percentil_sizeclass), shape=21,color="black",fill="azure2",size=2, alpha=1)+
+p <- ggplot()+geom_point(data = d_2, aes(y=factor(motif), 100*percentil_sizeclass), shape=21,color="black",fill="azure2",size=1.75, alpha=0.3)+
   geom_errorbar(data = d_2,aes(y = factor(motif), xmin=100*(mean-SE), xmax=100*(mean+SE)), 
-                width=1.0,size=1,color="grey20") +theme_bw()+
+                width=0.8,size=0.8,color="black") +theme_bw()+
   geom_point(data = d_2,aes(y = as.factor(motif), x=100*mean), 
-             size=2,color="grey20")+labs(y="Two to five node motifs", x = "Percentile")+
+             size=2,color="black")+labs(y="Two to five node motifs", x = "Percentile")+
   theme( strip.background = element_blank())+
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="\\textbf{Figure S2.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions excluding singletones, after removing non-robust links, that is, interactions whose frequency was equal to one.
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="\\textbf{Figure S2.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions after removing non-robust links (singletones).
 The different motif positions are dividied by the average path length clasification by Simmons et al.
-(2020)"}
+(2020).
+The superior dendrogram indicates the differences across groups with the more separated groups showing larger differences."}
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=13, fig.cap="**Figure S3.** Plant functional group composition separated in qualitative and quantitative variables.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=7, fig.width=12, fig.cap="**Figure S3.** Plant functional group composition separated in qualitative and quantitative variables.
 Panel A) shows the percentage of the different categories within trait represented with different colours for each functional group.
@@
 A <- c1 + c2 + c3 + c4 + c5 + plot_layout(ncol = 1)
+
+colnames(final_df_3) <- c("group","Autonomous selfing", "Flower number", "Flowers per \n inflorescence",
+                "Inflorescence \n width", "Flower length", "Style length", "Ovule number",
+                "Plant height")
+
 B <- ggradar(final_df_3, group.colours=c("sandybrown", "#7BB0A3","lightsteelblue2", "thistle", "lightgoldenrod2"),

### 2021-10-08 Draft/Draft.Rmd
Intro ready.

@@
 motifs) and those constitute the building blocks of the whole network.
-Here, we have compiled 60 networks from 18 different studies and show that some motifs are consitently under- and over-represented worldwide, suggesting that the building blocks of plant-pollintor networks are not random and are associated depending on the motif position and trophic level to specific fucntional groups.
-For instance, bees are the predominant group found on all motif positions but for plants there are three functional groups associated with corss-pollination that are similarly found on all motif positions.
-Hence, the distribution of funtional groups on the different positions is not random either which determine in last instance different probabilities of the overall functional group combinations of motifs.
+Here, we have compiled 60 networks from 18 different studies and show that some motifs are consitently under- and over-represented worldwide, suggesting that the building blocks of plant-pollintor networks are not random.
+Interestingly, different functional groups are associated to specific motif position across  both trophic levels.
+HERE I WOULD PUT AN EXAMPLE OF E.G.
+FAN POSITIONS, DEFINED BY, TEND TO BE OCCUPIED BY BEES AND WHATEVER TYPE OF PLANTS, RESPECTIVELY.
+This findings open the door to predict how novel interactions will be formed within a community context.
 
@@
 
-Because of the tremendous complexity of ecological networks, species interactions are generally condensed in metrics that summarize this information [@guimaraes2020].
+Ecological communities are formed by a plethora of interacting species.
+Because of the tremendous complexity of this ecological networks, species interactions are generally condensed in metrics that summarize this information [@guimaraes2020].
 Plant-pollinator interactions are no exception, and they are often studied with indices that aggregate the information at the species (micro-scale) or network level (macro-scale).
-Plant-pollinator network level approcahes have proven common invariant structural properties across them including a degree distribution that decays as a power law [@jordano1987], nestedness [@bascompte2003], or modularity in large networks [@olesen2007].
-In addition, species phenological overlap, morphological matching and species abundances have been shown to be determinant for the understanding of pairwise plant-pollinator interactions [@bartomeus2016; @stang2006; @peralta2020].
+For example, plant-pollinator network level approcahes have identified common invariant structural properties across networks, including a degree distribution that decays as a power law [@jordano1987], nestedness [@bascompte2003], or modularity [@olesen2007].
+In addition, the local species position within the network can define its degree of specialization [@bluthegXX] or its role connecting the rest of the community [@olesen2007].
 Despite the unquestionable progress with the use of these metrics at both species and network level, condensing the information into a single metric implies the loss of relevant ecological information that obscure the understanding of the ecological processes [@cirtwill2018; @simmons2019].
@@
 Sugerencia Alfonso (next paragraph, desde inicio a "(e.g., nestedness)"):Quizás esto lo intentaría sintetizar y meter al final del párrafo anterior y ya empezar en el segundo párrafo a hablar de motifs, como marco de trabajo/nivel de análisis complementario a los anteriores.
+
+He modificado un poco el texto, yo creo que se lee bien.
 ---
@@
 Traditionally, plant-pollinator research has focused on direct interactions but overlooked indirect interactions (i.e., the mediated effect between two species by a third species), such as facilitative or competitive interactions between plants for pollinators [@moeller2004; @sargent2008].
-Despite the widespread nature of indirect interactions in ecological communities [@strauss1991], plant-pollinator research often fails to finely capture those indirect interactions with the conventional analytical tools that condense the information either by species (e.g., interaction frequency) or in single topological indices (e.g., nestedness).
-Nonetheless, the emerging framework of network motifs (small networks recorded in a given network) in plant-pollinator research, often referred to as the building blocks of a network that depict subsets of interactions [@milo2002], allows to consider both direct and indirect interactions [@simmons2019].
+Despite the widespread nature of indirect interactions in ecological communities [@strauss1991], plant-pollinator research often fails to finely capture those indirect interactions with the conventional analytical tools that condense the information either by species (e.g., interaction frequency) or in global topological indices (e.g., nestedness).
+Nonetheless, the emerging framework of network motifs (small sub-networks recorded within a given network) in plant-pollinator research allows to consider both direct and indirect interactions [@simmons2019].
+Motifs are often referred to as the building blocks of a network that depict subsets of interactions [@milo2002].
 The analysis of motifs in plant-pollinator networks have revealed that the different ecological processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions [@simmons2020].
@@
 Luego pasaría al párrafo de qué hacemos en este trabajo.
-Digo esto porque la última frase del párrafo anterior me parecía que se quedaba algo colgada.
+Digo esto porque la última frase del párrafo anterior me parecía que se quedaba algo colgada.+
+
+Yo para esta version lo veo bien. Se puede mejorar la estructura quizas, pero no se si vale la pena ahora.
 ---
 
-Motifs are abstract representations often decoupled from species ecology.
-Thus, linking the structural properties of the meso-scale with the species ecology can help the understanding of ecological processes.
+Despite motifs are abstract representations often decoupled from species ecology, linking the structural properties of the meso-scale with the species ecology can help the understanding of ecological processes.
 For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species functional role [@stouffer2012; @baker2015].
@@
 Similarly, recent empirical findings indicate that the meso-scale is the best descriptor of plant reproductive success [@allen2021], but little is known on how plants reproductive strategies shape their position within the network of interactions.
-Although some studies have evaluated plant reproductive strategies in plant-pollinator networks [@tur2013; @lazaro2020], they are often overlooked in a community context [@devaux2014] and rarely incorporated into plant-pollinator network studies.
+Although some studies have evaluated plant reproductive strategies in plant-pollinator networks [@tur2013; @lazaro2020], this is an  often overlooked aspect in a community context [@devaux2014] and rarely incorporated into plant-pollinator network studies.
 Hence, exploring how the main plant reproductive strategies integrate with the emergent motif framework can shed light on key aspects of ecosystem functioning.
@@
 Floral visitor functional groups were divided by the main taxonomical groups that differed in life form and behaviour.
-Once we split the different plant-pollinator networks into their motif elements, we explored: (i) the overall motif patterns (over and under-represented motifs); (ii) over and under-represented functional groups in the different motif positions; (iii) the probability of finding plant and floral visitor functional groups in the different motif positions; and, (iv) over- and under- represented functional group combinations within the different motifs.
+Once we split the different plant-pollinator networks into their motif elements, we explored: (i) if there are common invariant structural properties in the overall motif patterns (i.e.
+over and under-represented motifs); (ii) which functional groups  are over and under-represented in the different motif positions; and, (iii) if there are over and under-reprsented functional group combinations within a motif.
 
@@
 # What do you think? 
+#IB: I already unified questions before reading your comment :D
 ---

### 2021-10-08 Draft/Draft.Rmd
Methods done!

@@
 First, plant species were grouped through hierarchical clustering into the optimal number of functional groups that summarized the main plant reproductive strategies.
-We used the trait dataset collated in Lanuza et al., (unpublished) that comprised 1,506 plant species and contained the same 60 weighted plant-pollinator networks used in this study plus 4 additional large unweighted metawebs (see **Table S1** Lanuza et al., unpublished).
+We used the trait dataset collated in Lanuza et al., (unpublished) that comprised 1,506 plant species (including all plants used in this study) (see **Table S1** Lanuza et al., unpublished).
 This dataset consisted on 8 floral, 4 reproductive and 3 vegetative traits excluding traits with high percentage of missing values (over 30%; **Table S2**).
 We opted to calculate the plant functional groups on this larger set of species because of the higher accuracy when delimiting functional groups with that many variables and species [@dolnicar2014].
-Previous to the clustering analysis, we calculated the distance between the different qualitative and scaled quantitative variables with Gower distance [@gower1971].
+To feed the clustering analysis, we calculated the distance between the different qualitative and scaled quantitative variables with Gower distance [@gower1971].
 For this, we used the function _gowdis_ with method _ward.D2_ from the package _FD_ version _1.0-12_ [@laliberte2014].
@@
 
-Second, floral visitors were grouped into functional groups based on taxonomic rank as done similarly in past plant-pollinator studies [@fenster2004; @ollerton2009].
+Second, floral visitors were grouped into functional groups based on taxonomic rank as done similarly in past plant-pollinato   r studies [@fenster2004; @ollerton2009].
 We opted to divide floral visitors on the taxonomic rank level and not with functional traits because the main orders of floral visitors differed in form and behaviour and had lower superior taxonomical complexity (i.e., floral visitors had 6 orders versus plants that had 38).
@@
 Prior to analyses, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.
+To test the effect of singletones, we ran all analysis to the same set of networks but considering only interactions whose frequency was greater than one (64.98% of interactions).
+Results are qualitatively consistent and are not further discussed in the main text (**Figures S1 and S2**).
 
 We calculated the frequency of all motifs up to five nodes (see **Figure 1**) for each empirical network, by using the _bmotif_ package [@bmotifsimmons2019].
-To control for variation in network size, motif frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains).
+To control for variation in network [network or subnetwork or mitif?
+Yo creo que motif, no?]() size, motif frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains).
 Like @simmons2020, we just used five-node motifs in our analyses for visualisation, interpretation and computational reasons.
@@
 In these models, we used the study identifiers in **Table S1** as a random intercept.
-By doing so, we obtained estimates of the average motif frequency, in which we controlled the variation at the study level.
+By doing so, we obtained estimates of the average motif frequency, but controling the variation at the study level.
 
@@
 
-To test the effect of singletones on the motif frequencies and motif functional groups' positions, we applied the previous analyses to the same set of networks (**Table S1**) but considering only interactions whose frequency was greater than one (64.98% of interactions; see **Figures S1 and S2**).
-
 **Over- and under-represented funtional group combinations of motifs**
 
-Finally, we studied which motif combinations of functional groups (up to five nodes) are over or under-represented in 95% of our empirical networks (57 out of 60 arrangements, due to computational limitations to identify all the nodes in the motifs of the three networks with the highest number of links).
+Finally, we studied which combinations of functional groups tend to appear toguether within the same motifs (up to five nodes).
+That is which combinations are over or under-represented.
+This analysis use 57 out of the 60 networks available due to computational limitations to identify all the nodes in the motifs of the three networks with the highest number of links.
 To do so, for each of the 53,250 possible motif combinations, we estimated the observed and the expected probability of finding those combination in empirical networks, respectively.
@@
 We used the ‘lmer’ package [@bates2015] to fit the LMMs models in our analyses.
-
-Once we obtained $p_i^O$ and $p_i^E$, we used simulation to determine whether the former is likely to come from the latter or not, since the large number of possible motif combinations and the small probabilities for some of them advise against using an exact test of goodness-of-fit or a Chi-square one.
+[IB: EL paquete muevelo al inicio o al final, cuando dices que todo es en R, y el codigo esta disponible en git...]()
+
+Once we obtained $p_i^O$ and $p_i^E$, we used a simulation [IB: Simulation or null model?]() approach to determine whether the former is likely to come from the latter or not.
+This approach was preferred since the large number of possible motif combinations and the small probabilities for some of them advise against using an exact test of goodness-of-fit or a Chi-square one.
 Specifically, we created 1,000 random samples with repetition of possible motif combinations, where each sample contained 10 million elements and, for each combination, the probability of being selected was equal to its expected probability.
@@
 According to the usual interpretation of z-scores, combinations with $z_i^O > 1.96$ are over-represented, whereas those with $z_i^O < -1.96$ are under-represented, at the 95%  confidence level.
-Notice that we focused on combinations with $p_i^O > 10^{-7}$ because, beyond the interest that can arouse the combinations that appear at most once, we do not have enough numerical resolution to accurately detect whether or not those combinations are under-represented (due to the limited size of our random samples).
+Notice that we focused on combinations with $p_i^O > 10^{-7}$ because, beyond the interest that can arouse the combinations that appear at most once, we do not have enough numerical resolution to accurately detect whether or not those combinations are under-represented (due to the limited size [ib: size or possible combinations]() of our random samples).
 

### 2021-10-08 Draft/Draft.Rmd
Results done!

@@
 Then, we determined whether the observed probabilities are likely to come from the expected probabilities or not.
-To calculate the observed probability ($p_i^O$) of functional groups within a motif $i$ (e.g., motif 3, bee + bee + functional group 2), we divided the number of times that $i$ appears in our set of empirical networks ($n_i^O$) by the sum of the number of times that each possible combination appeared: $p_i^O = n_i^O / \sum_{k=1}^{53,250} n_k^O$.
+To calculate the observed probability ($p_i^O$) of functional groups within a motif $i$ (e.g., motif 3, 'bee' + 'bee' + 'selfing herbs'), we divided the number of times that $i$ appears in our set of empirical networks ($n_i^O$) by the sum of the number of times that each possible combination appeared: $p_i^O = n_i^O / \sum_{k=1}^{53,250} n_k^O$.
 To estimate the expected probability of a given motif combination $i$, $p_i^E$, firstly, we calculated the probability of finding a given functional group $x$ in the position $\alpha$ of $i$, $p_i(x,\alpha)$.
@@
 
+[IB: Note that along the ms (abstract, discusion, etc...), I would discuss the group names ('selfing herbs') and not numbers (Group 1) otherwise we will lost the readers.]()
+
 In total, there were 1,126 species of floral visitor with 6,325 interactions recorded with plants.
@@
 Motifs 3, 5, 9, 10 and 14 were under-represented in empirical networks, that is, all were close to the 1st percentile and under the 25th percentile.
-Further, four out of five of these motifs belonged to the largest path length classification (i.e., core-peripheral).
+Interestingly, four out of five of these motifs belonged to the largest path length classification (i.e., core-peripheral).
 In addition, motifs 2, 6, 7, 16 and 17 were over-represented, all over the 75th percentile and thus the closest to the 99th percentile.
 In contrast to the under-represented motifs, over-represented motifs belonged to the two shortest path length groups (i.e., complete and fan).
-The remaining motifs (i.e., 4, 8, 11, 12, 13, and 15) were between the 25th and 75th percentile but closest to over-representation.
+The remaining motifs (i.e., 4, 8, 11, 12, 13, and 15) were between the 25th and 75th percentile.
 Notably, the exclusion of singletones from this analysis did not change the observed results (**Figure S1**).
@@
 
-The comparison of the frequencies between the positions of motifs of empirical and simulated networks showed that motifs positions determined over- and under- representation independently of the identity of functional groups for most cases (rows in **Figure 3**).
-However, we also found differences in the average percentile within floral visitors and plant functional groups on the different motif positions (columns in **Figure 3**).
-These differences were more marked for floral visitors than for plant functional groups (the differences between min and max percentiles per position were generally two-three times larger for floral visitors).
-Hence, the average percentile per position in plants was determined in a larger extent by the position itself rather than the functional group in contrast to floral visitors.
+The comparison of the functional group frequencies per motif position between empirical and simulated networks showed a [X%]() of over- or under- representated functional groups in different position.
+We found stronger differences in the average percentile across functional groups (columns in **Figure 3**) than among positions (rows in **Figure 3**) [IB: esto no lo tengo muy claro, no entendia la frase inicial y he intentado ir al grafico, y no se si la estoy liando]().
+Note that differences across functional groups were more marked for floral visitors than for plant functional groups (the differences between min and max percentiles per position were generally two-three times larger for floral visitors).
+Hence, the average percentile per position in plants was determined to a larger extent by the position itself rather than the functional group in contrast to floral visitors.
 From most over- to under-represented floral visitors functional groups on the different motif positions (indicated with the dendrogram order in **Figure 3**), we found: bees, non-syrphids Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.
@@
 
+[IB: De aqui hay que sacar un ejemplo para el abstract.
+No hace falta que este en los resultados, pero sí podemos usarlo en la discusión.
+Por ejemplo.
+Bees and self icop.
+perenials are over repsented in fan positions, while ...]()
 ```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', out.width="90%",fig.cap="\\textbf{Figure 3.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions.
@@
 
-The statistical comparison with z-scores between the observed functional group combinations and the expected ones showed a modified Gaussian distribution (Johnson's $S_U$) with 65% of under-represented group combinations, 20% of no statistical difference and 15% of under-represented ones (**Figure 5**).
+[IB: Me pregunto si el ultimo parrafo es mejor meterlo aquí, por que de hecho, la figura 4 son las expected probabilities, no?
+Se podria empezar diciendo eso, y meter la figura de expected probabilities]()
+
+The statistical comparison with z-scores between the observed and expected functional group combinations showed that we can not recover the observed combinations from its probability of ocurrence.
+In fact, most combinations are under- or over- representedm and follow a modified Gaussian distribution (Johnson's $S_U$) with 65% of under-represented group combinations, 20% of no statistical difference and 15% of under-represented ones (**Figure 5**).
 In addition, motifs with small node combinations (i.e., 2 and 3 nodes) only appeared as under-represented.
-Motifs with 4 and 5 node combinations appeared in the three statistical categories but 4 node motifs had a higher porportion in the under-represented category (10% in comparison with the 1% and the 3% of the no statiscal difference and over-represented categories, respectively).
-Finally, 5 node motifs were in similar prportions in the no statistical difference and over-represented categories (99% and 97%, respectively) but they appeared in lower porportion in the under-represented category (89%).
+Motifs with 4 and 5-node combinations appeared in the three statistical categories but 4 node motifs had a higher porportion in the under-represented category (10% in comparison with the 1% and the 3% of the no statiscal difference and over-represented categories, respectively).
+Finally, 5-node motifs were in similar prportions in the no statistical difference and over-represented categories (99% and 97%, respectively) but they appeared in lower porportion in the under-represented category (89%).
 When, we explore the identity on the different positions of the most probable motif combinations we find as expected that the most common functional groups rule these positions on the most probable motif combiantions (lower panel **Figure 5**).
+
+[IB: Me falta un take home message.
+Yo creo que es que no podemos predecir las combinciones por sus probabilidades y eso es muy bestia!
+Lo he añadido ya al inicio de este parrafo, pero dejo el comentario por que es un paper complejo y hay que guiar mucho.
+Cada sección deberia tener un mensage claro ( y ese it a abstract) 1) Los motifs no son al azar.
+2) hay posiciones usadas principalmente por ciertos FG.
+3) Hay combinaciones de FG que van más alla de pura probabilidad.
+Fin.]()
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 5.** Z-score comparison (95% confidence level) of the observed and expected frequencies motif combinations with four specific graphical examples of the most probable motifs of being observed for each category delimited by the z-score critical values: under-represented, no statistical difference and over-represented."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 5.** Z-score comparison (95% confidence level) of the observed and expected frequencies of motif combinations with four specific graphical examples of the most probable motifs of being observed for each category delimited by the z-score critical values: under-represented, no statistical difference and over-represented."}
 

### 2021-10-09 Draft/Draft.Rmd
Some edits after Nacho's comments

@@
 
-Ecological communities are formed by a plethora of interacting species.
-Because of the tremendous complexity of this ecological networks, species interactions are generally condensed in metrics that summarize this information [@guimaraes2020].
+Ecological communities are formed by a plethora of interacting species that form networks of interactions.
+Because of the tremendous complexity of these ecological networks, species interactions are generally condensed in metrics that summarize this information [@guimaraes2020].
 Plant-pollinator interactions are no exception, and they are often studied with indices that aggregate the information at the species (micro-scale) or network level (macro-scale).
-For example, plant-pollinator network level approcahes have identified common invariant structural properties across networks, including a degree distribution that decays as a power law [@jordano1987], nestedness [@bascompte2003], or modularity [@olesen2007].
-In addition, the local species position within the network can define its degree of specialization [@bluthegXX] or its role connecting the rest of the community [@olesen2007].
+For example, plant-pollinator network level approaches have identified common invariant structural properties across networks, including a degree distribution that decays as a power law [@jordano1987], nestedness [@bascompte2003], or modularity [@olesen2007].
+In addition, the local species position within the network can define its degree of specialization [@bluthgen2006] or its role connecting the rest of the community [@olesen2007].
 Despite the unquestionable progress with the use of these metrics at both species and network level, condensing the information into a single metric implies the loss of relevant ecological information that obscure the understanding of the ecological processes [@cirtwill2018; @simmons2019].
@@
 Motifs are often referred to as the building blocks of a network that depict subsets of interactions [@milo2002].
-The analysis of motifs in plant-pollinator networks have revealed that the different ecological processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions [@simmons2020].
+The analysis of network motifs in plant-pollinator networks have revealed that the different ecological processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions [@simmons2020].
 Yet, the global patterns of indirect interactions in real plant-pollinator networks are still unknown (e.g., over- and under- represented motifs).
@@
 For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species functional role [@stouffer2012; @baker2015].
-However, it is unclear how the species ecology and life history traits determines the species functional role within the network of interactions [@coux2016].
+However, it is unclear how the species ecology and life history traits determines the species' functional role within the network of interactions [@coux2016].
 For example, large pollinators can forage larger distances [@greenleaf2007], deposit greater pollen quantities [@foldesi2021] and handle complex zygomorphic flowers in comparison with small pollinators that are restricted to lower floral complexity [@gong2009].
-How this different pollinator behaviors translate into their interaction topology is unknown.
-Similarly, recent empirical findings indicate that the meso-scale is the best descriptor of plant reproductive success [@allen2021], but little is known on how plants reproductive strategies shape their position within the network of interactions.
+How this different pollinator behavior translates into their interaction topology is unknown.
+Similarly, recent empirical findings indicate that the meso-scale is the best descriptor of plant reproductive success [@allen2021], but little is known about how plants reproductive strategies shape their position within the network of interactions.
 Although some studies have evaluated plant reproductive strategies in plant-pollinator networks [@tur2013; @lazaro2020], this is an often overlooked aspect in a community context [@devaux2014] and rarely incorporated into plant-pollinator network studies.
@@
 Here, we used 60 plant-pollinator networks from 18 different studies and 14 countries, alongside functional groups of plants and floral visitors based on functional traits and taxonomic rank, respectively.
-To obtain plant functional groups, we used a comprehensive dataset that included floral, reproductive and vegetative traits compiled on a larger set of networks.
-Floral visitor functional groups were divided by the main taxonomical groups that differed in life form and behaviour.
-Once we split the different plant-pollinator networks into their motif elements, we explored: (i) if there are common invariant structural properties in the overall motif patterns (i.e.
+To obtain plant functional groups, we used a comprehensive dataset that included floral, reproductive and vegetative traits compiled in a larger set of networks.
+Floral visitor functional groups were divided by the main taxonomic groups that differed in life form and behaviour.
+Once we split the different plant-pollinator networks into their motif elements, we explored: (i) if there is a common invariant structural property in the overall motif networks (i.e.
 over and under-represented motifs); (ii) which functional groups are over and under-represented in the different motif positions; and, (iii) if there are over and under-reprsented functional group combinations within a motif.
-
----
-# THIS IS A COMMENT (Jose)
-# Each os this points (i to iv) corresponds to a figure
-# I think that ideally we can have that structure on methods and results (excluding functional groups)
-# so far we have (i), (ii) and (iv) on methods
-# we lack an explicit mention to (iii) 
-# maybe merge it with another research question and just have 3?
-# What do you think? 
-#IB: I already unified questions before reading your comment :D
----
 
@@
 All studies sampled plant-pollinator interactions in natural systems and were selected based on wide geographical coverage and presence of interaction frequency as a measure of interaction strength.
-In total, there were 503 plant species, 1,111 floral visitors species and 6248 pairwise interactions registered.
-For ease of data manipulation, plant and floral visitors species names were standardize with the help of the package _taxize_ version 0.9.99 [@chamberlain2020].
+In total, there were 503 plant species, 1,111 floral visitors species and 6,248 pairwise interactions registered.
+For ease of data manipulation, plant and floral visitors species names were standardize with the help of the R package _taxize version 0.9.99_ [@chamberlain2020].
+All analyses and data manipulation were conducted in R _version 4.0.5_ [@R].
 
@@
 First, plant species were grouped through hierarchical clustering into the optimal number of functional groups that summarized the main plant reproductive strategies.
-We used the trait dataset collated in Lanuza et al., (unpublished) that comprised 1,506 plant species (including all plants used in this study) (see **Table S1** Lanuza et al., unpublished).
+For this, we used the trait dataset collated in Chapter 1 that comprised a total of 1506 species including the 503 species considered in this study (Supplementary material Chapter 1 **Table S1**).
 This dataset consisted on 8 floral, 4 reproductive and 3 vegetative traits excluding traits with high percentage of missing values (over 30%; **Table S2**).
@@
 
-Second, floral visitors were grouped into functional groups based on taxonomic rank as done similarly in past plant-pollinato   r studies [@fenster2004; @ollerton2009].
+Second, floral visitors were grouped into functional groups based on taxonomic rank as done similarly in past plant-pollinator studies [@fenster2004; @ollerton2009].
 We opted to divide floral visitors on the taxonomic rank level and not with functional traits because the main orders of floral visitors differed in form and behaviour and had lower superior taxonomical complexity (i.e., floral visitors had 6 orders versus plants that had 38).
-Thus, this allowed us to group floral visitors into functional groups that represented adequately the main life strategies of the possible pollinators: (i) Hymenoptera-Anthophila (bees), (ii) Hymenoptera-non-Anthophila (other non-bee Hymenoptera), (iii) Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera and (vi) Coleoptera.
-However, a minor set of species belonged to other functional groups that were considered in analyses but not discussed further because of their low representation (3.55% of the total interactions recorded in the full set of networks).
+Thus, this allowed us to group floral visitors into functional groups that represented adequately the main life strategies of the possible pollinators: (i) bees (Hymenoptera-Anthophila), (ii) non-bee Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Syrphidae-Diptera), (iv) non-syrphids-Diptera, (v) Lepidoptera and (vi) Coleoptera.
+However, a minor set of species belonged to other functional groups that were considered in analyses but not discussed further because of their low representation in the full set of networks (3.55% of the total interactions recorded).
 These functional groups were 'lizards', 'birds' and 'other insects'.
@@
 Motifs whose percentile is close to 0 or 100 are under- or over-represented in the empirical networks, respectively, and thus they cannot be predicted by connectance and the number of species alone.
-To summarize general patterns across networks, we used an intercept-only linear mixed model (LMM) per motif, where the response variable was the observed motif percentile per network.
+To summarize general patterns across networks, we used an intercept-only linear mixed model (LMM) per motif with the help of the package _lmer version xxx_ [@bates2015], where the response variable was the observed motif percentile per network.
 In these models, we used the study identifiers in **Table S1** as a random intercept.
@@
 
-Finally, we studied which combinations of functional groups tend to appear toguether within the same motifs (up to five nodes).
+Finally, we studied which combinations of functional groups tend to appear together within the same motifs (up to five nodes).
 That is which combinations are over or under-represented.
@@
 To obtain $n_i(x,\alpha)$, we fitted a LMM per motif position, where the response variable was the number of times that a given position was observed per network, the explanatory variable was functional group identifier, and the random intercept was given by network identifiers nested within the study identifiers.
-We used the ‘lmer’ package [@bates2015] to fit the LMMs models in our analyses.
-[IB: EL paquete muevelo al inicio o al final, cuando dices que todo es en R, y el codigo esta disponible en git...]()
 
@@
 
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bee",            
+  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees",            
                                       "Coleoptera","Lepidoptera","Non-bee\nHymenoptera", 
@@
 
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bee","Birds",            
+  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees","Birds",            
                                       "Coleoptera","Lepidoptera","Lizards","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\ndiptera","Other insects","Syrphids")
+                                      "Non-syrphids\nDiptera","Other insects","Syrphids")
 }
@@
                "Non-bee-Hymenoptera", "Non-syrphids-diptera",
-               "Syrphids","1","2","3","4","5"), labels=c("Bee","Coleoptera","Lepidoptera",
-"Non-bee-Hymenoptera", "Non-syrphids-diptera","Syrphids", 
+               "Syrphids","1","2","3","4","5"), labels=c("Bees","Coleoptera","Lepidoptera",
+"Non-bee-Hymenoptera", "Non-syrphids-Diptera","Syrphids", 
           "Selfing herbs","Small outcrossing perennials","Self-incomp. perennials\nwith large flowers",
@@
                                 "Syrphids","1","2","3","4","5"), 
-                       labels=c("Bee","Coleoptera","Lepidoptera",
-                                "Non-bee-Hymenoptera", "Non-syrphids-diptera",
+                       labels=c("Bees","Coleoptera","Lepidoptera",
+                                "Non-bee-Hymenoptera", "Non-syrphids-Diptera",
                                 "Syrphids", 
@@
 ##DISCUSSION
+
+1) Emphasis on Global commonalities in ntw patterns, Our main contribution is showing which motifs are under or over repsented.
+Link this to simmons imprints of which processes are opperating.
+End with a generality about those process en nature (e.g.
+niche or neutral process in other systems).
+
+2) Role of FG . Emphasis on fan positions, dig a bit on explaining what this positions imply. Comment that bees are, as expected, prevalent, …
+
+3) Ecology is complex, combinations not recovered by positions. This is a very cool result, because imply that knowing the probabilities of each position is not enough to predict network realizations.
+
+4) Limitations (but keep it short and simple): FG are hard to describe, bias in sampling worldwide, …
+
+5) Future direction and conclusions (also short).
+This opens the door to help predicting novel interactions beyond pairwise interactions.
+We not only know now how the building blocks are structures, but also that who conform this building blocks is not random.
 
@@
 
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bee",            
+  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees",            
                                       "Coleoptera","Lepidoptera","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\ndiptera","Syrphids")
+                                      "Non-syrphids\nDiptera","Syrphids")
 }else{

### 2021-10-09 Draft/Draft.Rmd
Responses Alf

@@
 Yo para esta version lo veo bien. Se puede mejorar la estructura quizas, pero no se si vale la pena ahora.
+
+Alf: Probablemente no valga la pena.
 ---
@@
 To control for variation in network [network or subnetwork or mitif?
-Yo creo que motif, no?]() size, motif frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains).
+Yo creo que motif, no?
+Alf: No, es network.
+Su tamaño -cantidad de nodos- condiciona las frecuencias posibles de motifs.
+De hecho, la frase la saqué de los métodos de simmons 2020]() size, motif frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains).
 Like @simmons2020, we just used five-node motifs in our analyses for visualisation, interpretation and computational reasons.
@@
 
-Once we obtained $p_i^O$ and $p_i^E$, we used a simulation [IB: Simulation or null model?]() approach to determine whether the former is likely to come from the latter or not.
+Once we obtained $p_i^O$ and $p_i^E$, we used a simulation [IB: Simulation or null model?
+Alf: Yo diría simulación por consistencia con las secciones anteriores, en las que decíamos que habíamos simulado 1,000 redes usando el vaznull de bipartite.
+Aquí simulamos una muestra de motifs usando las prob.
+esperadas.]() approach to determine whether the former is likely to come from the latter or not.
 This approach was preferred since the large number of possible motif combinations and the small probabilities for some of them advise against using an exact test of goodness-of-fit or a Chi-square one.
@@
 According to the usual interpretation of z-scores, combinations with $z_i^O > 1.96$ are over-represented, whereas those with $z_i^O < -1.96$ are under-represented, at the 95%  confidence level.
-Notice that we focused on combinations with $p_i^O > 10^{-7}$ because, beyond the interest that can arouse the combinations that appear at most once, we do not have enough numerical resolution to accurately detect whether or not those combinations are under-represented (due to the limited size [ib: size or possible combinations]() of our random samples).
+Notice that we focused on combinations with $p_i^O > 10^{-7}$ because, beyond the interest that can arouse the combinations that appear at most once, we do not have enough numerical resolution to accurately detect whether or not those combinations are under-represented (due to the limited size [ib: size or possible combinations.
+Alf: yo diria size porque el hecho de solo usar 10 millones de elementos en cada muestra nos impide tener la suficiente resolución numérica para valorar la representación de combinaciones con probabilidades de 10e-8 o menores]() of our random samples).
 

### 2021-10-09 Draft/Draft.Rmd
edits

--- 2021-10-09 Draft/Draft.Rmd
@@
 In total, there were 503 plant species, 1,111 floral visitors species and 6,248 pairwise interactions registered.
-For ease of data manipulation, plant and floral visitors species names were standardize with the help of the R package _taxize version 0.9.99_ [@chamberlain2020].
+For ease of data manipulation, plant and floral visitors species names were standardize with the help of the R package _taxize_ version _0.9.99_ [@chamberlain2020].
 All analyses and data manipulation were conducted in R _version 4.0.5_ [@R].
@@
 Prior to analyses, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.
-To test the effect of singletones, we ran all analysis to the same set of networks but considering only interactions whose frequency was greater than one (64.98% of interactions).
+To test the effect of singletones, we ran all analysis to the same set of networks, but considering only interactions whose frequency was greater than one (64.98% of interactions).
 Results are qualitatively consistent and are not further discussed in the main text (**Figures S1 and S2**).
 
-We calculated the frequency of all motifs up to five nodes (see **Figure 1**) for each empirical network, by using the _bmotif_ package [@bmotifsimmons2019].
-To control for variation in network [network or subnetwork or mitif?
-Yo creo que motif, no?]() size, motif frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains).
+We calculated the frequency of all motifs up to five nodes (see **Figure 1**) for each empirical network, by using the _bmotif_ package version _2.0.2_ [@bmotifsimmons2019].
+To control for variation in network size, motif frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains).
 Like @simmons2020, we just used five-node motifs in our analyses for visualisation, interpretation and computational reasons.
 In addition, we also excluded two-node motifs (or links) from our analyses because their normalised frequencies would always equal one.
+
+---
+SOLVED COMMENT
+IB: "To control for variation in network, maybe motif?"
+AA-P: "Network it's fine, it ultimately condition motif frequencies"
+---
 
@@
 
-To assess the significance of the observed frequencies, we created 1,000 simulated networks for each binary network using the _nullmodel_ function and the _vaznull_ model in the _bipartite_ package [@dormann2009].
+To assess the significance of the observed frequencies, we created 1,000 simulated networks for each binary network using the _nullmodel_ function and the _vaznull_ model in the _bipartite_ package version _xxx_ [@dormann2009].
 Generated networks had the same number of plants and floral visitors, as well as the same connectance of their corresponding empirical networks.
@@
 Motifs whose percentile is close to 0 or 100 are under- or over-represented in the empirical networks, respectively, and thus they cannot be predicted by connectance and the number of species alone.
-To summarize general patterns across networks, we used an intercept-only linear mixed model (LMM) per motif with the help of the package _lmer version xxx_ [@bates2015], where the response variable was the observed motif percentile per network.
+To summarize general patterns across networks, we used an intercept-only linear mixed model (LMM) per motif with the help of the package lmer version _1.1-21_ [@bates2015], where the response variable was the observed motif percentile per network.
 In these models, we used the study identifiers in **Table S1** as a random intercept.
@@
 We calculated which functional groups were over or under-represented in different motif positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
-We extracted the position frequencies of all motifs from three to five nodes for each network and species by using the _bmotif_ package [@bmotifsimmons2019].
 To estimate the position frequencies of each functional group in a given network, we added the frequencies of those species that belong to the group, and then, we normalised the resulting frequencies by dividing the position measure for each group by the total number of times that a group appears in any position within the same motif size class.
@@
 By adding the functional group estimates to the model intercept, we assessed the average motif frequency, after controlling the variation at the study level.
-Finally, we visualized with the help of the package ComplexHeatmap version 2.6.2 [@gu2016] over- and under- representation of plant and pollinator functional groups on the different motif positions.
+Finally, we visualized with the help of the package _ComplexHeatmap_ version _2.6.2_ [@gu2016] over- and under- representation of plant and pollinator functional groups on the different motif positions.
 
@@
 
-Once we obtained $p_i^O$ and $p_i^E$, we used a simulation [IB: Simulation or null model?]() approach to determine whether the former is likely to come from the latter or not.
+Once we obtained $p_i^O$ and $p_i^E$, we used a simulation approach to determine whether the former is likely to come from the latter or not.
 This approach was preferred since the large number of possible motif combinations and the small probabilities for some of them advise against using an exact test of goodness-of-fit or a Chi-square one.
@@
 According to the usual interpretation of z-scores, combinations with $z_i^O > 1.96$ are over-represented, whereas those with $z_i^O < -1.96$ are under-represented, at the 95%  confidence level.
-Notice that we focused on combinations with $p_i^O > 10^{-7}$ because, beyond the interest that can arouse the combinations that appear at most once, we do not have enough numerical resolution to accurately detect whether or not those combinations are under-represented (due to the limited size [ib: size or possible combinations]() of our random samples).
+Notice that we focused on combinations with $p_i^O > 10^{-7}$ because, beyond the interest that can arouse the combinations that appear at most once, we do not have enough numerical resolution to accurately detect whether or not those combinations are under-represented (due to the limited size of our random samples).
+
+---
+SOLVED COMMENTS
+IB comment: simulation or null model?
+AA-P: I'd say simulation for consistency with the other sections.
+
+IB: size or possible combinations
+AA-P: I'd say size because we are using 10 million elements that are not sufficiently representative of the numerical resolution
+---
 
@@
 The hierarchical cluster analysis divided the dataset into five different groups with different and overlapping characteristics (**Figure S3** and **Figure S4**).
-Group 1 referred to as 'selfing herbs' consisted on herbs with hermaphroditic flowers with high levels of autonomous selfing.
-Group 2 or 'small outcrossing perennials' had small perennial species with a mixed of life forms (i.e., trees shrubs and herbs) with outcrossing hermaphroditic flowers.
-Group 3 referred to as 'self-incompatible perennials with large flowers' comprised perennial species with a mixed of life forms and large self-incompatible hermaphroditic flowers with high number of ovules.
-Group 4 or 'tall plants with small unisexual flowers' had the tallest species, highest proportion of shrub and tree life forms, dioecious and monoecious breeding systems, small flowers and the highest numbers of flowers and inflorescences per plant.
-Finally, group 5 or 'short-lived outcrossers with long zygomorphic flowers' consisted on small perennial and short-lived herbs with long self-compatible zygomorphic flowers that were unable to self-pollinate.
-
-[IB: Note that along the ms (abstract, discusion, etc...), I would discuss the group names ('selfing herbs') and not numbers (Group 1) otherwise we will lost the readers.]()
+The first group referred to as 'selfing herbs' consisted on herbs with hermaphroditic flowers with high levels of autonomous selfing.
+The second group named 'small outcrossing perennials' had small perennial species with a mixed of life forms (i.e., trees shrubs and herbs) with outcrossing hermaphroditic flowers.
+The third group referred to as 'self-incompatible perennials with large flowers' comprised perennial species with a mixed of life forms and large self-incompatible hermaphroditic flowers with high number of ovules.
+The fourth group named 'tall plants with small unisexual flowers' had the tallest species, highest proportion of shrub and tree life forms, dioecious and monoecious breeding systems, small flowers and the highest numbers of flowers and inflorescences per plant.
+Finally, the fifth group named 'short-lived outcrossers with long zygomorphic flowers' consisted on small perennial and short-lived herbs with long self-compatible zygomorphic flowers that were unable to self-pollinate.
+
+---
+COMMENT
+IB: Note that along the ms (abstract, discusion, etc...), I would discuss the group names ('selfing herbs') and not numbers (Group 1) otherwise we will lost the readers.
+---
 
@@
 
-The comparison of the functional group frequencies per motif position between empirical and simulated networks showed a [X%]() of over- or under- representated functional groups in different position.
-We found stronger differences in the average percentile across functional groups (columns in **Figure 3**) than among positions (rows in **Figure 3**) [IB: esto no lo tengo muy claro, no entendia la frase inicial y he intentado ir al grafico, y no se si la estoy liando]().
-Note that differences across functional groups were more marked for floral visitors than for plant functional groups (the differences between min and max percentiles per position were generally two-three times larger for floral visitors).
-Hence, the average percentile per position in plants was determined to a larger extent by the position itself rather than the functional group in contrast to floral visitors.
+```{r , include=FALSE}
+
+#SAME SCRIPT AS THE PLOTTING FOR THE HEATMAP BUT I NEED IT HERE TO LOAD THE VARIABLES WITH VALUES ON RESULTS
+
+library(lme4)
+library(nlme)
+library(tidyverse)
+library(stringi)
+source("../Scripts/Scripts_Alfonso/add_study_id.R")
+
+#############################################
+# EXTRACT MEAN VALUES
+#############################################
+all_position_percentiles <- read_csv("../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
+
+all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
+                                                              "[0-9]+") %>% as.numeric()
+
+all_position_percentiles <- add_study_id(all_position_percentiles)
+#str(all_position_percentiles)
+#head(all_position_percentiles)
+
+list_plants_FG <- as.character(1:10)
+
+plant_position_percentiles_filtered <- all_position_percentiles %>% 
+  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
+         !is.na(expected_freq_its_GF)) #ME DA ERROR
+pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
+  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
+         !is.na(expected_freq_its_GF))
+
+# Plants-------------
+
+# Mean percentile and SE taking into account the study system
+plant_codes <- plant_position_percentiles_filtered$position %>% unique()
+plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
+plant_means$mean <- NA
+plant_means$SE <- NA
+
+for(i.pos in 1:length(plant_codes)){
+
+  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
+            data = plant_position_percentiles_filtered %>%
+              filter(position == plant_codes[i.pos]))
+
+  temp <- fixed.effects(m) %>% unname()
+  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
+                                                                    temp[1]+temp[2],
+                                                                    temp[1]+temp[3],
+                                                                    temp[1]+temp[4],
+                                                                    temp[1]+temp[5]) ## to get real means per FG
+  temp <- sqrt(diag(vcov(m)))
+  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
+                                                                  temp[1]+temp[2],
+                                                                  temp[1]+temp[3],
+                                                                  temp[1]+temp[4],
+                                                                  temp[1]+temp[5])
+
+}
+
+# Pollinators--------
+
+# Mean percentile and SE taking into account the study system
+pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
+pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
+pollinator_means$mean <- NA
+pollinator_means$SE <- NA
+pollinator_means_reordered <- NULL
+
+for(i.pos in 1:length(pollinator_codes)){
+
+  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
+            data = pollinator_position_percentiles_filtered %>%
+              filter(position == pollinator_codes[i.pos]),
+            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
+
+  temp <- fixed.effects(m) %>% unname()
+  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)
+
+  pollinator_means_aux$mean <- c(temp[1],
+                                 temp[1]+temp[2],
+                                 temp[1]+temp[3],
+                                 temp[1]+temp[4],
+                                 temp[1]+temp[5],
+                                 temp[1]+temp[6],
+                                 temp[1]+temp[7],
+                                 temp[1]+temp[8],
+                                 temp[1]+temp[9]) ## to get real means per FG
+
+  temp <- sqrt(diag(vcov(m)))
+  pollinator_means_aux$SE <- c(temp[1],
+                               temp[1]+temp[2],
+                               temp[1]+temp[3],
+                               temp[1]+temp[4],
+                               temp[1]+temp[5],
+                               temp[1]+temp[6],
+                               temp[1]+temp[7],
+                               temp[1]+temp[8],
+                               temp[1]+temp[9])
+
+  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)
+
+}
+
+# There are lower limits (mean - SE) smaller than 0 (see Other insects)
+# We set the lower limit of those error bars to zero
+
+pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
+pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
+
+#############################################
+# ADDING BROAD MOTIF CATEGORIES TO POSITIONS
+#############################################
+
+motifs_raw_data <- read_csv("../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
+
+motifs_raw_data$Broad_categories <- NA
+
+motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(5,9,14,13,10)] <- "Core-peripherical"
+motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(6,16,12)] <- "Complete"
+motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(2,3,7,4,17,8)] <- "Fan"
+motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(15,11)] <- "Asymmetric complete"
+
+motifs_raw_data$plant <- gsub("[^0-9.-]", "", motifs_raw_data$plant)
+motifs_raw_data$pollinator <- gsub("[^0-9.-]", "", motifs_raw_data$pollinator)
+motifs_raw_data$plant <- as.numeric(motifs_raw_data$plant)
+motifs_raw_data$pollinator <- as.numeric(motifs_raw_data$pollinator)
+motifs_raw_data <- motifs_raw_data %>% filter(!is.na(Broad_categories))
+
+fan_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
+core_per_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
+complete_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
+asymm_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
+
+pollinator_means_reordered$Broad_categories <- NA
+
+pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% fan_pollinator] <- "Fan" 
+pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% asymm_pollinator] <- "Medium-weak" 
+pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% complete_pollinator] <- "Strong" 
+pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% core_per_pollinator] <- "Weak"
+
+fan_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
+core_per_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
+complete_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
+asymm_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
+
+plant_means$Broad_categories <- NA
+
+plant_means$Broad_categories[plant_means$position %in% fan_plant] <- "Fan" 
+plant_means$Broad_categories[plant_means$position %in% asymm_plant] <- "Medium-weak" 
+plant_means$Broad_categories[plant_means$position %in% complete_plant] <- "Strong" 
+plant_means$Broad_categories[plant_means$position %in% core_per_plant] <- "Weak"
+
+################################################################################
+# Alternative code to HEATMAPS to create variables with values to load on text
+# in a reproducible/automated way
+################################################################################
+
+# PLANTS-----
+
+# Prepare data for heatmap
+heat_plants_aux <- plant_means %>% spread(Node_FG,mean) %>% select(-SE)
+
+heat_plants <- heat_plants_aux %>%
+  group_by(position,Broad_categories) %>% 
+  summarise_all(sum,na.rm = T)
+
+# POLLINATORS-----------
+
+filter_rare_groups <- T
+
+if(filter_rare_groups == T){
+  heat_pollinators_aux <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds",
+                                                                                "Lizards",
+                                                                                "Other_insects")) %>% 
+    spread(Node_FG,mean) %>% select(-SE,-lower)
+
+  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees",            
+                                      "Coleoptera","Lepidoptera","Non-bee\nHymenoptera", 
+                                      "Non-syrphids\nDiptera","Syrphids")
+}else{
+  heat_pollinators_aux <- pollinator_means_reordered %>% spread(Node_FG,mean) %>% select(-SE,-lower)
+
+  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees","Birds",            
+                                      "Coleoptera","Lepidoptera","Lizards","Non-bee\nHymenoptera", 
+                                      "Non-syrphids\nDiptera","Other insects","Syrphids")
+}
+
+heat_pollinators <- heat_pollinators_aux %>%
+  group_by(position,Broad_categories) %>% 
+  summarise_all(sum,na.rm = T)
+
+specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))
+
+#Check percentage of over and under represented
+colMeans(heat_pollinators[,c(3:8)] < 0.25)
+poll_under_25 <- colMeans(heat_pollinators[,c(3:8)] < 0.25)
+poll_under_25 <- specify_decimal((poll_under_25[[1]] + poll_under_25[[2]] + poll_under_25[[3]] +
+poll_under_25[[4]] + poll_under_25[[5]] + poll_under_25[[6]])/6*100,2)
+#[1] 32.57576
+
+colMeans(heat_pollinators[,c(3:8)] > 0.75)
+poll_over_75 <- colMeans(heat_pollinators[,c(3:8)] > 0.75)
+poll_over_75 <- specify_decimal((poll_over_75[[1]] + poll_over_75[[2]] + poll_over_75[[3]] +
+    poll_over_75[[4]] + poll_over_75[[5]] + poll_over_75[[6]])/6*100,2)
+#[1] 4.545455
+
+#################################################################################
+#################################################################################
+
+colnames(heat_plants)<- c("position", "Broad_categories", "one",
+                               "two", "three","four",
+                               "five")
+f <- heat_plants %>%
+  mutate(min = pmin(1,
+                    one, two,three,
+                    four, five))%>%
+  mutate(max = pmax(one,
+                    two, three,four,
+                    five))
+
+diff_1 <- f$max-f$min
+
+cbind(diff,diff_1)
+
+#Check percentage of over and under represented per FG
+colMeans(heat_plants[,c(3:7)] < 0.25)
+plant_under_25 <- colMeans(heat_plants[,c(3:7)] < 0.25)
+plant_under_25 <- specify_decimal((plant_under_25[[1]] + plant_under_25[[2]] + plant_under_25[[3]] + 
+    plant_under_25[[4]] + plant_under_25[[5]])/5*100,2)
+#[1] 18.18182
+colMeans(heat_plants[,c(3:7)] > 0.75)
+plant_over_75 <- colMeans(heat_plants[,c(3:7)] > 0.75)
+plant_over_75 <- specify_decimal((plant_over_75[[1]] + plant_over_75[[2]] + plant_over_75[[3]] + 
+    plant_over_75[[4]] + plant_over_75[[5]])/5*100,2)
+#[1] 8.181818
+
+#overall percentages
+under <- specify_decimal((as.numeric(poll_under_25) + as.numeric(plant_under_25))/2,2)
+over <- specify_decimal((as.numeric(poll_over_75) + as.numeric(plant_over_75))/2,2)
+
+```
+
+The comparison of the functional group frequencies per motif position between empirical and simulated networks showed a `r over`% and `r under`% of over- (>75$^{th}$) and under- (<25th) represented functional groups in the different positions, respectively (**Figure 3**).
+Floral visitors showed a total of `r poll_over_75`% and `r poll_under_25`% of over- and under-represented functional groups in the different positions and plants `r plant_over_75`% and `r plant_under_25`% of over and under-represented, respectively.
+Notably, the differences across functional groups were more marked for floral visitors than for plant functional groups (the differences between min and max percentiles per position were generally two-three times larger for floral visitors).
 From most over- to under-represented floral visitors functional groups on the different motif positions (indicated with the dendrogram order in **Figure 3**), we found: bees, non-syrphids Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.

### 2021-10-10 Scripts/Scripts_Alfonso/3_specificity_VS_position_frequencies.R
Create 3_specificity_VS_position_frequencies.R

@@ -1,0 +1,220 @@
+
+# Load libraries
+
+library(lme4)
+library(nlme)
+library(tidyverse)
+library(stringi)
+source("Scripts/Scripts_Alfonso/add_study_id.R")
+
+
+pollinator_positions_codes <- c("np2","np4","np6","np8","np11","np12","np14","np16",
+                                "np18","np21","np22","np24","np25","np28","np29","np31",
+                                "np34","np35","np38","np41","np42","np44","np46")
+plant_positions_codes <- c("np1","np3","np5","np7","np9","np10","np13","np15",
+                                "np17","np19","np20","np23","np26","np27","np30","np32",
+                                "np33","np36","np37","np39","np40","np43","np45")
+
+
+#############################################
+# EXTRACT MEAN VALUES
+#############################################
+all_position_percentiles <- read_csv("Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
+
+all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
+                                                              "[0-9]+") %>% as.numeric()
+
+all_position_percentiles <- add_study_id(all_position_percentiles)
+#str(all_position_percentiles)
+#head(all_position_percentiles)
+
+list_plants_FG <- as.character(1:10)
+
+plant_position_percentiles_filtered <- all_position_percentiles %>% 
+  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
+         !is.na(expected_freq_its_GF)) #ME DA ERROR
+pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
+  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
+         !is.na(expected_freq_its_GF))
+
+
+# Plants-------------
+
+# Mean percentile and SE taking into account the study system
+plant_codes <- plant_position_percentiles_filtered$position %>% unique()
+plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
+plant_means$mean <- NA
+plant_means$SE <- NA
+
+
+for(i.pos in 1:length(plant_codes)){
+  
+  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
+            data = plant_position_percentiles_filtered %>%
+              filter(position == plant_codes[i.pos]))  
+  
[…]

### 2021-10-10 Draft/Draft.Rmd
Starting with the discussion, I keep after lunch

@@
 The comparison of the functional group frequencies per motif position between empirical and simulated networks showed a `r over`% and `r under`% of over- (>75$^{th}$) and under- (<25th) represented functional groups in the different positions, respectively (**Figure 3**).
-Floral visitors showed a total of `r poll_over_75`% and `r poll_under_25`% of over- and under-represented functional groups in the different positions and plants `r plant_over_75`% and `r plant_under_25`% of over and under-represented, respectively.
+Floral visitors showed a total of `r poll_over_75`% and `r poll_under_25`% of over- and under-represented functional groups in the different positions and plants `r plant_over_75`% and `r plant_under_25`% of over and under-represented groups, respectively.
 Notably, the differences across functional groups were more marked for floral visitors than for plant functional groups (the differences between min and max percentiles per position were generally two-three times larger for floral visitors).
@@
 
-[IB: De aqui hay que sacar un ejemplo para el abstract.
+---
+THIS IS A COMMENT
+IB: De aqui hay que sacar un ejemplo para el abstract.
 No hace falta que este en los resultados, pero sí podemos usarlo en la discusión.
@@
 Bees and self icop.
-perenials are over repsented in fan positions, while ...]()
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', out.width="90%",fig.cap="\\textbf{Figure 3.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions.
+perenials are over repsented in fan positions, while ...
+---
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', out.width="80%",fig.cap="\\textbf{Figure 3.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions.
 The different motif positions are dividied by the average path length clasification determined by Simmons et al.
@@
 
+\newpage
+
+**Over- and under-represented funtional group combinations of motifs**
+
 The different observed frequencies on the different motif positions showed a hirarchical order of probabilities for floral visitors (**Figure 4**).
@@
 
-\newpage
-
-**Over- and under-represented funtional group combinations of motifs**
-
-[IB: Me pregunto si el ultimo parrafo es mejor meterlo aquí, por que de hecho, la figura 4 son las expected probabilities, no?
-Se podria empezar diciendo eso, y meter la figura de expected probabilities]()
-
 The statistical comparison with z-scores between the observed and expected functional group combinations showed that we can not recover the observed combinations from its probability of ocurrence.
@@
 
-[IB: Me falta un take home message.
+---
+THIS IS A COMMENT
+
+Alfonso (comentario después de fig 5 donde tenía remarkably y ahora un in addition): Yo creo que todo esto es expected.
+Sin embargo, las explicaciones de por qué lo es probablemente van en la discusión.
+Lo mismo que el ajuste de la Johnson's SU: la cola larga de la derecha la producen la sobreabundancia de motifs de 4 y 5 nodos, en comparación con los de 3.
+
+IB: Me falta un take home message.
 Yo creo que es que no podemos predecir las combinciones por sus probabilidades y eso es muy bestia!
@@
 3) Hay combinaciones de FG que van más alla de pura probabilidad.
-Fin.]()
-
----
-THIS IS A COMMENT
-
-Alfonso (comentario después de fig 5 donde tenía remarkably y ahora un in addition): Yo creo que todo esto es expected.
-Sin embargo, las explicaciones de por qué lo es probablemente van en la discusión.
-Lo mismo que el ajuste de la Johnson's SU: la cola larga de la derecha la producen la sobreabundancia de motifs de 4 y 5 nodos, en comparación con los de 3.
+Fin.
 ---
@@
 ##DISCUSSION
+
+Understanding the global patterns of network structure is key to unravel the processes that govern community dynamics [@bascompte2007; @bastolla2009; @guimaraes2020].
+However, common analytical approaches are unable to capture the full complexity of ecological systems.
+By analysing over- and under-representation of network motifs with a comprehensive dataset of real plant-pollinator networks we have shown that motifs are consistently over- and under-represented indicating the lack of randomness of the patterns of interactions at the meso-scale.
+This has direct implications with
 

### 2021-10-10 Scripts/Scripts_Alfonso/specificity_VS_position_frequencies.R
update specificity position

@@ -164,7 +164,11 @@ plant_means$Broad_categories[plant_means$position %in% asymm_plant] <- "Medium-w
 plant_means$Broad_categories[plant_means$position %in% complete_plant] <- "Strong" 
 plant_means$Broad_categories[plant_means$position %in% core_per_plant] <- "Weak" 
 
-######
+###########################
+# ESTIMATING SPECIFICITY
+###########################
+# Reference: 10.1371/journal.pone.0114674
+
 motif_pattern_connections <- read_csv("Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
 
 number_plant <- motif_pattern_connections %>% group_by(motif_id,plant) %>% 
@@ -193,6 +197,7 @@ specificity_pollinator_aux2 <- specificity_pollinator_aux %>%
 specificity_plant <- specificity_plant_aux2 %>% ungroup %>%
   mutate(s=(number_pollinators-n)/(number_pollinators-1)) %>%
   select(position,s) %>% unique()
+
 specificity_pollinator <- specificity_pollinator_aux2 %>% ungroup %>%
   mutate(s=(number_plants-n)/(number_plants-1)) %>%
   select(position,s) %>% unique()
@@ -202,6 +207,11 @@ plant_means_s <- plant_means %>% left_join(specificity_plant, by = "position")
 
 pollinator_means_reordered_s <- pollinator_means_reordered %>% 
   left_join(specificity_pollinator, by = "position")
+
+
+# We replace NaN of some specialist positions by one
+plant_means_s$s[is.nan(plant_means_s$s)] <- 1.0
+pollinator_means_reordered_s$s[is.nan(pollinator_means_reordered_s$s)] <- 1.0
 
 
 p1 <- ggplot(pollinator_means_reordered_s,aes(x=s,y=mean))+

### 2021-10-10 Scripts/Scripts_Alfonso/specificity_VS_motif_frequencies.R
Create specificity_VS_motif_frequencies.R

@@ -1,0 +1,111 @@
+
+library(lme4)
+library(nlme)
+library(stringi)
+library(tidyverse)
+source("Scripts/Scripts_Alfonso/add_study_id.R")
+d <- read_csv("Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
+d <- add_study_id(d)
+
+
+# Mean percentile and SE taking into account the study system
+motif_codes <- d %>% filter(motif != 1) %>% # We remove links (motif code: 1)
+  select(motif) %>% unique() %>% pull()
+motif_means <- tibble(motif = motif_codes)
+motif_means$mean <- NA
+motif_means$SE <- NA
+
+for(i.motif in 1:length(motif_codes)){
+  
+  m <- lmer(percentil_sizeclass ~ 1+(1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
+            data = subset(d, motif == motif_codes[i.motif]))  
+  
+  motif_means$mean[i.motif] <- fixed.effects(m) %>% unname()
+  motif_means$SE[i.motif] <- sqrt(diag(vcov(m)))
+  
+}
+
+###########################
+# ESTIMATING SPECIFICITY
+###########################
+# Reference: 10.1371/journal.pone.0114674
+
+motif_pattern_connections <- read_csv("Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
+
+number_plant <- motif_pattern_connections %>% group_by(motif_id,plant) %>% 
+  count() %>% group_by(motif_id) %>% count() %>% rename(number_plants = n)
+
+number_pollinator <- motif_pattern_connections %>% group_by(motif_id,pollinator) %>% 
+  count() %>% group_by(motif_id) %>% count() %>% rename(number_pollinators = n)
+
+specificity_plant_aux <- motif_pattern_connections %>% 
+  group_by(motif_id,plant) %>% count()
+
+specificity_pollinator_aux <- motif_pattern_connections %>% 
+  group_by(motif_id,pollinator) %>% count()
+
+specificity_plant_aux$position <- stri_extract_first_regex(specificity_plant_aux$plant,
+                                                           "[0-9]+") %>% as.numeric()
+specificity_pollinator_aux$position <- stri_extract_first_regex(specificity_pollinator_aux$pollinator,
+                                                                "[0-9]+") %>% as.numeric()
+
[…]

### 2021-10-10 Scripts/Scripts_Alfonso/specificity_VS_motif_frequencies.R
Update specificity_VS_motif_frequencies.R

@@ -99,13 +99,23 @@ motif_means_s <- motif_means %>% rename(motif_id = motif) %>%
   left_join(mean_pollinator_motif_s, by = "motif_id") %>%
   rename(mean_frequency = mean)
 
-library(plotly)
-plot_ly(x=motif_means_s$mean_s_plant, 
-        y=motif_means_s$mean_s_pollinator, 
-        z=motif_means_s$mean_frequency, type="scatter3d", mode="markers")
+# library(plotly)
+# plot_ly(x=motif_means_s$mean_s_plant, 
+#         y=motif_means_s$mean_s_pollinator, 
+#         z=motif_means_s$mean_frequency, type="scatter3d", mode="markers")
 
 m_lm <- lm(mean_frequency~mean_s_plant*mean_s_pollinator,motif_means_s)
 summary(m_lm)
 
 library(visreg)
 visreg2d(m_lm, "mean_s_plant", "mean_s_pollinator")
+
+motif_means_s$predicted_freq <- predict(m_lm,motif_means_s)
+
+ggplot(motif_means_s,aes(x=mean_frequency, 
+                        y = predicted_freq))+
+  #geom_point()+
+  geom_abline(slope=1,intercept = 0)+
+  geom_text(label=motif_means_s$motif_id)+
+  theme_bw()+
+  xlim(0,1)+ylim(0,1)

### 2021-10-10 Scripts/Scripts_Alfonso/specificity_VS_motif_frequencies.R
Update specificity_VS_motif_frequencies.R

@@ -104,13 +104,18 @@ motif_means_s <- motif_means %>% rename(motif_id = motif) %>%
 #         y=motif_means_s$mean_s_pollinator, 
 #         z=motif_means_s$mean_frequency, type="scatter3d", mode="markers")
 
-m_lm <- lm(mean_frequency~mean_s_plant*mean_s_pollinator,motif_means_s)
+library(glmmTMB)
+m_lm <- glmmTMB(mean_frequency~mean_s_plant*mean_s_pollinator, data = motif_means_s, family=beta_family())
+#m_lm <- lm(mean_frequency~mean_s_plant*mean_s_pollinator,motif_means_s)
 summary(m_lm)
 
-library(visreg)
-visreg2d(m_lm, "mean_s_plant", "mean_s_pollinator")
+# library(performance)
+# r2(m_lm)
 
-motif_means_s$predicted_freq <- predict(m_lm,motif_means_s)
+library(visreg)
+visreg2d(m_lm, "mean_s_plant", "mean_s_pollinator",scale ="response")
+
+motif_means_s$predicted_freq <- predict(m_lm,motif_means_s,type ="response")
 
 ggplot(motif_means_s,aes(x=mean_frequency, 
                         y = predicted_freq))+

### 2021-10-10 Draft/Draft.Rmd
edits

@@
 Understanding the global patterns of network structure is key to unravel the processes that govern community dynamics [@bascompte2007; @bastolla2009; @guimaraes2020].
-However, common analytical approaches are unable to capture the full complexity of ecological systems.
-By analysing over- and under-representation of network motifs with a comprehensive dataset of real plant-pollinator networks we have shown that motifs are consistently over- and under-represented indicating the lack of randomness of the patterns of interactions at the meso-scale.
-This has direct implications with
-
-1) Emphasis on Global commonalities in ntw patterns, Our main contribution is showing which motifs are under or over repsented.
-Link this to simmons imprints of which processes are opperating.
-End with a generality about those process en nature (e.g.
-niche or neutral process in other systems).
+However, common analytical approaches are unable to capture the full complexity of ecological systems [@simmons2019].
+Because network motifs can capture both direct and indirect interactions, by analysing over- and under-representation of motifs we are able to explore in greater detail ecological interactions.
+We have explored for the first time the overall structure and representation of network motifs in real plant-pollinator networks and shown that the different motifs up to five nodes are consistently over- and under-represented in comparison with simulated networks indicating the presence of ecological processes shaping their structure.
+Despite the presence of multiple ecological processes likely operating at the same time (e.g., neutral effects, morphological matching or phenological overlap), we found a tendency for over-represented structures with more dense connected motifs (i.e., complete, fan and asymmetric complete) suggesting that neutral effects are likely the predominant process governing the structure of these network motifs [@simmons2020] in real plant-pollinator networks.
+
+---
+THIS IS A COMMENT
+IB: End with a generality about those process en nature (e.g. niche or neutral process in other systems).
+
+---
+
+Floral visitor appeared consistently in motifs that implied a generalist role.
+For instance, the comparison between motifs and their mirror image (the inverted version of the motif) always showed higher representation of motifs that were related with a generalist role for pollinators (e.g., Figure 1 and Figure 2 motifs 17 versus 8, 7 versus 4 and 3 versus 2).
+This is in good agreement with the previous evidences at the species level that highlight the generalist nature of pollinators [@waser1996; @olesen2002].
+In accordance with the overall motif structure, we found higher representation of plant and pollinator functional groups in complete, fan and asymmetric complete motifs in contrast to core-peripheral motifs that were under-represented.
+The functional group of bees was the most frequent in the different positions, as expected because of their high [].
+
+As expected, bees, the most abundant group of floral visitors in the different plant-pollinator networks,  was also the most represented in the different motif positions
 
@@
 4) Limitations (but keep it short and simple): FG are hard to describe, bias in sampling worldwide, …
+
+- FG hard to describe: https://doi.org/10.1093/aob/mcp031 and the fenster one
+
+- Paper of Poisot 2020
 

### 2021-10-11 Scripts/Scripts_Alfonso/specificity_VS_motif_frequencies.R
Update specificity_VS_motif_frequencies.R

@@ -109,8 +109,16 @@ m_lm <- glmmTMB(mean_frequency~mean_s_plant*mean_s_pollinator, data = motif_mean
 #m_lm <- lm(mean_frequency~mean_s_plant*mean_s_pollinator,motif_means_s)
 summary(m_lm)
 
-# library(performance)
-# r2(m_lm)
+library(betareg)
+m_lm2 <- betareg(mean_frequency~mean_s_plant*mean_s_pollinator, data = motif_means_s, link = "logit")
+#m_lm <- lm(mean_frequency~mean_s_plant*mean_s_pollinator,motif_means_s)
+summary(m_lm2)
+
+library(performance)
+r2_efron(m_lm)
+r2(m_lm2)
+
+#0.67
 
 library(visreg)
 visreg2d(m_lm, "mean_s_plant", "mean_s_pollinator",scale ="response")

### 2021-10-11 Draft/Draft.Rmd
Paragraphs 1 and 2 of the discussion

--- 2021-10-10 Draft/Draft.Rmd
@@
 Understanding the global patterns of network structure is key to unravel the processes that govern community dynamics [@bascompte2007; @bastolla2009; @guimaraes2020].
-However, common analytical approaches are unable to capture the full complexity of ecological systems.
-By analysing over- and under-representation of network motifs with a comprehensive dataset of real plant-pollinator networks we have shown that motifs are consistently over- and under-represented indicating the lack of randomness of the patterns of interactions at the meso-scale.
-This has direct implications with
-
-1) Emphasis on Global commonalities in ntw patterns, Our main contribution is showing which motifs are under or over repsented.
-Link this to simmons imprints of which processes are opperating.
-End with a generality about those process en nature (e.g.
-niche or neutral process in other systems).
-
-2) Role of FG . Emphasis on fan positions, dig a bit on explaining what this positions imply. Comment that bees are, as expected, prevalent, …
+However, common analytical approaches are unable to capture the full complexity of ecological systems [@simmons2019].
+Because network motifs can capture both direct and indirect interactions, by analysing over- and under-representation of motifs we are able to explore in greater detail ecological interactions.
+We have explored for the first time the overall structure and representation of network motifs in real plant-pollinator networks and shown that the different motifs up to five nodes are consistently over- and under-represented in comparison with simulated networks indicating the presence of ecological processes shaping their structure.
+Despite the presence of multiple ecological processes likely operating at the same time (e.g., neutral effects, morphological matching or phenological overlap), we found a tendency for over-represented structures with more densenly connected motifs (i.e., complete, fan and asymmetric complete) suggesting that neutral effects are likely the predominant processes governing the structure of these network motifs [@simmons2020].
+Thus, as indicated for other network properties like nestedness [@krishna2008; @suweis2013], species relative abundances (i.e., neutral effects) are possibly one of the main determinants of indirect interactions in real plant-pollinator networks.
+
+In accordance with the findings of network motif patterns, we found higher representation of plant and pollinator functional groups in complete, fan and asymmetric complete motifs (more densenly connected) in contrast to core-peripheral motifs (less densenly connected) that were under-represented.
+As expected, the functional group of bees (the one with the highest number of interactions) was the most abundant in the different network motif positions.
+This is likely to be the case for most plant-pollinator systems as bees are generally the main functional group visiting flowers in plant-pollinator communities [@ollerton2017].
+Interestingly, bees were highly over-represented in fan motif positions 4, 16 and 46 (**Figure 3**) which are associated with the highest levels of generalism.
+Further, this generalist tendency was also observed at motif level (e.g., **Figure 2** comparison of the percentiles between mirror image motifs in fan positions that involve pollinator specialization and generalism).
+Despite this in good agreement with the current view of the generalist nature of pollinators [@waser1996; @olesen2002], we found that this over-representation of the generalist network motifs was mainly driven by bees while the rest of functional groups tended to be under-represented in these generalist motifs.
+Further, unlike floral visitors, plant functional groups showed little differences across them on the different motif positions.
+However, the group of self incompatible perennials with large flowers, one of the groups that is expected to have higher levels of outcrossing rate [@goodwillie2010], also showed high over-representation on the same fan motif that bees did but for the plant positions (**Figure 3**).
 
@@
 
-cluster1$traits <- c(rep("Breeding system",3), rep("Compatibility",3), rep("Life form",3),
-                     rep("Life span",2), rep("Flower symmetry",2), rep("Nectar",2))
+cluster1$traits <- c(rep("Breeding sys.",3), rep("Compatibility",3), rep("Life form",3),
+                     rep("Life span",2), rep("F. Symm.",2), rep("Nectar",2))
 
@@
 
-cluster5$traits <- c(rep("Breeding system",3), rep("Compatibility",3), rep("Life form",3),
-                     rep("Life span",2), rep("Flower symmetry",2), rep("Nectar",2))
+cluster5$traits <- c(rep("Breeding syst.",3), rep("Compatibility",3), rep("Life form",3),
+                     rep("Life span",2), rep("F. Symm.",2), rep("Nectar",2))
 c5 <- cluster5 %>% 

### 2021-10-12 Draft/Draft.Rmd
Edits

@@
 Further, this generalist tendency was also observed at motif level (e.g., **Figure 2** comparison of the percentiles between mirror image motifs in fan positions that involve pollinator specialization and generalism).
-Despite this in good agreement with the current view of the generalist nature of pollinators [@waser1996; @olesen2002], we found that this over-representation of the generalist network motifs was mainly driven by bees while the rest of functional groups tended to be under-represented in these generalist motifs.
-Further, unlike floral visitors, plant functional groups showed little differences across them on the different motif positions.
-However, the group of self incompatible perennials with large flowers, one of the groups that is expected to have higher levels of outcrossing rate [@goodwillie2010], also showed high over-representation on the same fan motif that bees did but for the plant positions (**Figure 3**).
-
+Despite this is in good agreement with the current view of the generalist nature of pollinators [@waser1996; @olesen2002], we found that this over-representation of the generalist network motifs was mainly driven by bees while the rest of functional groups tended to be under-represented in these generalist motifs.
+Unlike floral visitors, plant functional groups showed little differences across them on the different motif positions.
+However, the group of self incompatible perennials with large flowers, one of the groups that is expected to have higher levels of outcrossing rate [@goodwillie2010], also showed high over-representation on the same fan motif that bees did (**Figure 3**).
+
+The observed functional group probabilities on the different positions (**Figure 4**) were insufficient to predict most of the observed network motifs (**Figure 5**) suggesting the existance of ecological processes shaping their structure.
+In addition, we found that just 30% of the observed motif combinations took place.
+This restricted set of possible combinations is no surprise, because sampling the full set of interactions is tremendously complex and a large portion of the possible interactions do not take place because of life history constraints [@jordano2016].
+Thus, similarly to the presence of forbidden links, we found the existence of forbidden motifs.
+
+---
+THIS IS A COMMENT
 3) Ecology is complex, combinations not recovered by positions. This is a very cool result, because imply that knowing the probabilities of each position is not enough to predict network realizations.
-
+---
+
+Despite the obvious usefulness of funtional groups in summarizing species ecological roles (e.g., similar reproductive biology and behaviour of pollinators), taxonomical diversity and trait availability limit our ability to properly represent the diverse range of reproductive strategies in natural systems.
+
+---
+THIS IS ACOMMENT
 4) Limitations (but keep it short and simple): FG are hard to describe, bias in sampling worldwide, …
 
+Although functional groups can define
+
 - FG hard to describe: https://doi.org/10.1093/aob/mcp031 and the fenster one
@@
 - Paper of Poisot 2020
-
+---
+
+---
+THIS IS A COMMENT
 5) Future direction and conclusions (also short).
@@
 We not only know now how the building blocks are structures, but also that who conform this building blocks is not random.
+---
 

### 2021-10-12 Scripts/Z-score_percentile_histogram_plot.R

@@ -4,7 +4,7 @@ library(dplyr)
 library(ggplot2)
 library(tidyverse)
 #Read data
-data <- read.csv("../Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
+data <- read.csv("Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
 
 #Check NA's per column
 #data %>%
@@ -20,7 +20,9 @@ data_1 <- data %>%
     between(z_score, -abs(critical_value), abs(critical_value)) ~ "no_diff",
     z_score > abs(critical_value) ~ "over"
   ))
-     
+
+
+nrow(data_1)
 #check levels
 #levels(factor(data_1$infra_over_represented))
 
@@ -47,4 +49,13 @@ ggplot(data_2 %>% filter(round_motif_observed_probability>0), aes(x=z_score, col
                     "No statistical difference", "Over-represented")) +
   scale_color_manual(name="Motif frequencies" ,values=c("coral2", "palegreen3", "cyan3"), labels=c("Under-represented",
                      "No statistical difference", "Over-represented")) + xlab("Z-score")
+
+
+#Forbidden motif calculation
+data_0 <- data_1 %>% filter(round_motif_observed_probability>0)
+nrow(data_0)/nrow(data_1)*100
+data_0 %>% 
+  group_by(infra_over_represented) %>%
+  summarise(no_rows = length(infra_over_represented)) %>%
+  mutate(proportion = no_rows / sum(no_rows))
 

### 2021-10-12 Draft/Draft.Rmd
fixing mistake

@@
 This restricted set of possible combinations is no surprise, because sampling the full set of interactions is tremendously complex and a large portion of the possible interactions do not take place because of life history constraints [@jordano2016].
-Thus, similarly to the presence of forbidden links, we found the existence of forbidden motifs.
+Thus, similarly to the presence of these forbidden interactions, we found also the existence of forbidden motifs.
 
 ---
-THIS IS A COMMENT
+Thus, similarly to forbidden links, we found the existence of forbidden motifs. Hence, trait-matching
+
+Trait matching example and a ref...
+Phenology example with a ref...
+Co-occurence...
+
 3) Ecology is complex, combinations not recovered by positions. This is a very cool result, because imply that knowing the probabilities of each position is not enough to predict network realizations.
----
 
@@
 
----
-THIS IS ACOMMENT
 4) Limitations (but keep it short and simple): FG are hard to describe, bias in sampling worldwide, …
@@
 - Paper of Poisot 2020
----
-
----
-THIS IS A COMMENT
+
 5) Future direction and conclusions (also short).

### 2021-10-12 Scripts/Z-score_percentile_histogram_plot.R

@@ -4,7 +4,7 @@ library(dplyr)
 library(ggplot2)
 library(tidyverse)
 #Read data
-data <- read.csv("Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
+data <- read.csv("../Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
 
 #Check NA's per column
 #data %>%

### 2021-10-12 Draft/Draft.Rmd
some ideas

@@
 We have explored for the first time the overall structure and representation of network motifs in real plant-pollinator networks and shown that the different motifs up to five nodes are consistently over- and under-represented in comparison with simulated networks indicating the presence of ecological processes shaping their structure.
-Despite the presence of multiple ecological processes likely operating at the same time (e.g., neutral effects, morphological matching or phenological overlap), we found a tendency for over-represented structures with more densenly connected motifs (i.e., complete, fan and asymmetric complete) suggesting that neutral effects are likely the predominant processes governing the structure of these network motifs [@simmons2020].
+Despite the presence of multiple ecological processes likely operating at the same time (e.g., neutral effects, morphological matching or phenological overlap), we found a tendency for over-represented structures with more densely connected motifs (i.e., complete, fan and asymmetric complete) suggesting that neutral effects are likely the predominant processes governing the structure of these network motifs [@simmons2020].
 Thus, as indicated for other network properties like nestedness [@krishna2008; @suweis2013], species relative abundances (i.e., neutral effects) are possibly one of the main determinants of indirect interactions in real plant-pollinator networks.
 
-In accordance with the findings of network motif patterns, we found higher representation of plant and pollinator functional groups in complete, fan and asymmetric complete motifs (more densenly connected) in contrast to core-peripheral motifs (less densenly connected) that were under-represented.
+In accordance with the findings of network motif patterns, we found higher representation of plant and pollinator functional groups in complete, fan and asymmetric complete motifs (more densely connected) in contrast to core-peripheral motifs (less densely connected) that were under-represented.
 As expected, the functional group of bees (the one with the highest number of interactions) was the most abundant in the different network motif positions.
@@
 
-The observed functional group probabilities on the different positions (**Figure 4**) were insufficient to predict most of the observed network motifs (**Figure 5**) suggesting the existance of ecological processes shaping their structure.
-In addition, we found that just 30% of the observed motif combinations took place.
+The observed functional group probabilities on the different motif positions (**Figure 4**) were insufficient to predict most of the observed network motifs (**Figure 5**) suggesting the existence of ecological processes shaping their structure.
+(maybe comment on them)
+
+In addition, we found that just 30% of the possible 5,3250 motif combinations took place.
+
+FG combinations, explain briefly...
+
 This restricted set of possible combinations is no surprise, because sampling the full set of interactions is tremendously complex and a large portion of the possible interactions do not take place because of life history constraints [@jordano2016].
-Thus, similarly to the presence of these forbidden interactions, we found also the existence of forbidden motifs.
+Thus, similarly to the presence of these forbidden interactions (or links), we found also the existence of forbidden motifs.
+()
 

### 2021-10-13 Draft/Draft.Rmd
maybe 3rd paragraph done? Jumping to the 4th tomorrow

@@
 However, common analytical approaches are unable to capture the full complexity of ecological systems [@simmons2019].
-Because network motifs can capture both direct and indirect interactions, by analysing over- and under-representation of motifs we are able to explore in greater detail ecological interactions.
+Because network motifs can capture both direct and indirect interactions, by analysing over- and under-representation of motifs we are able to explore in greater detail ecological interactions [@stouffer2007].
 We have explored for the first time the overall structure and representation of network motifs in real plant-pollinator networks and shown that the different motifs up to five nodes are consistently over- and under-represented in comparison with simulated networks indicating the presence of ecological processes shaping their structure.
@@
 
-In accordance with the findings of network motif patterns, we found higher representation of plant and pollinator functional groups in complete, fan and asymmetric complete motifs (more densely connected) in contrast to core-peripheral motifs (less densely connected) that were under-represented.
-As expected, the functional group of bees (the one with the highest number of interactions) was the most abundant in the different network motif positions.
-This is likely to be the case for most plant-pollinator systems as bees are generally the main functional group visiting flowers in plant-pollinator communities [@ollerton2017].
+In accordance with the findings of network motif patterns, we found higher representation of plant and pollinator functional groups in more densely connected motifs in contrast to the less densely connected ones (i.e., core-peripheral).
+As expected, the functional group of bees (the one with the highest number of qualitative interactions) was the most abundant in the different network motif positions.
+This concurs well with other plant-pollinator network studies where bees are the main functional group visiting flowers
+[@ollerton2017].
 Interestingly, bees were highly over-represented in fan motif positions 4, 16 and 46 (**Figure 3**) which are associated with the highest levels of generalism.
-Further, this generalist tendency was also observed at motif level (e.g., **Figure 2** comparison of the percentiles between mirror image motifs in fan positions that involve pollinator specialization and generalism).
+Further, this generalist tendency was also observed at motif level (e.g., **Figure 2** comparison of the percentiles of mirror image motifs that involve the opposed roles of specialization and generalism from a pollinator perpective).
 Despite this is in good agreement with the current view of the generalist nature of pollinators [@waser1996; @olesen2002], we found that this over-representation of the generalist network motifs was mainly driven by bees while the rest of functional groups tended to be under-represented in these generalist motifs.
-Unlike floral visitors, plant functional groups showed little differences across them on the different motif positions.
-However, the group of self incompatible perennials with large flowers, one of the groups that is expected to have higher levels of outcrossing rate [@goodwillie2010], also showed high over-representation on the same fan motif that bees did (**Figure 3**).
-
-The observed functional group probabilities on the different motif positions (**Figure 4**) were insufficient to predict most of the observed network motifs (**Figure 5**) suggesting the existence of ecological processes shaping their structure.
-(maybe comment on them)
-
+Unlike floral visitors, plant functional groups showed little differences between their maximum and minimum percentile on the different motif positions in the comparison with simulated networks, and thus similar probability of appearing on them.
+However, the groups that involved higher levels of outcrossing with perennial lifespan showed a tendency to be more over-represented and probable on the different motif positions.
+For instance, the group of self incompatible perennials with large flowers, one of the groups that is expected to have higher levels of outcrossing rate [@goodwillie2010], showed the highest over-representation of all plant functional groups on the different motif positions (**Figure 3**).
+
+The observed functional group probabilities on the different motif positions (**Figure 4**) were insufficient to predict most of the observed network motifs (**Figure 5**).
+This implies that not just the structure of network motifs but also the identity of the elements of their structure are influenced by ecological processes that determine under- and over-representation of the different motif combinations.
 In addition, we found that just 30% of the possible 5,3250 motif combinations took place.
-
-FG combinations, explain briefly...
-
-This restricted set of possible combinations is no surprise, because sampling the full set of interactions is tremendously complex and a large portion of the possible interactions do not take place because of life history constraints [@jordano2016].
-Thus, similarly to the presence of these forbidden interactions (or links), we found also the existence of forbidden motifs.
-()
+However, this restricted set of possible combinations is no surprise, because plant-pollinator networks (i.e., full network level) have a high percentage of non-realized interactions [@bascompte2013].
+Some of this non-observed motif combinations are likely to be the cause of under-sampling [@olesen2011; @jordano2016].
+However, a large portion of the possible interactions do not take place because of life history constraints [i.e., forbidden links; @olesen2011; @bartomeus2016; @jordano2016].
+Thus, similarly to the presence of these forbidden interactions or links, we found also the existence of forbidden motifs that represent set of indirect interactions that do not take place in natural systems.
+
+Despite the obvious usefulness of funtional groups in summarizing species ecological roles (e.g., similar reproductive biology and behaviour of pollinators), taxonomical diversity and trait availability limit our ability to properly represent the diverse range of reproductive strategies in natural systems.
 
 ---
-Thus, similarly to forbidden links, we found the existence of forbidden motifs. Hence, trait-matching
-
-Trait matching example and a ref...
-Phenology example with a ref...
-Co-occurence...
-
-3) Ecology is complex, combinations not recovered by positions. This is a very cool result, because imply that knowing the probabilities of each position is not enough to predict network realizations.
-
-Despite the obvious usefulness of funtional groups in summarizing species ecological roles (e.g., similar reproductive biology and behaviour of pollinators), taxonomical diversity and trait availability limit our ability to properly represent the diverse range of reproductive strategies in natural systems.
 
@@
 ---
+
+Idea: explore if over-represented and under-represented groups have trait-matching or not...
+As suggested in the literature the more stable (and probably more frequent I guess will have well matched traits...)
 
@@
 Panel A) shows the percentage of the different categories within trait represented with different colours for each functional group.
-Plot B) shows the radar plot of the different quantitative variables standardize on the same scale also coloured with the same patterns of colours as qualitative variables per cluster."}
+Plot B) shows the radar plot of the different quantitative variables standardize on the same scale also coloured with the same patterns of colours as qualitative variables per cluster or functional group.
+Group 1 corresponds to short-lived selfers; group 2 to small outcrossing perennials; group 3 to self-incompatible perennials with large flowers; group 4 to tall plants with small unisexual flowers; and, group 5 to short-lived outcrossers with long zygomorphic flowers."}
 
@@
   ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("sandybrown"))+
+  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("sandybrown"), labels="Group 1")+
   facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
@@
   ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("#7BB0A3"))+
+  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("#7BB0A3"), labels="Group 2")+
   facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
@@
   ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("lightsteelblue2"))+
+  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("lightsteelblue2"), labels="Group 3")+
   facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
@@
   ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("thistle"))+
+  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("thistle"), labels="Group 4")+
   facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
@@
   ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("lightgoldenrod2"))+
+  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("lightgoldenrod2"), labels="Group 5")+
   facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+

### 2021-10-13 Scripts/Z-score_percentile_histogram_plot.R

@@ -59,3 +59,5 @@ data_0 %>%
   summarise(no_rows = length(infra_over_represented)) %>%
   mutate(proportion = no_rows / sum(no_rows))
 
+
+

### 2021-10-14 Draft/Draft.Rmd
Paragrapgh 2 redone...

@@
 
+From a pollinator perpective, we found that generalist network motifs were consistently over-represented (**Figure 2**).
+For instance, when we compare motifs with equal structure but inverted, we found that floral visitors had always over-representation in the positions that implied the highest number of links.
+Despite this is in good agreement with the current view of the generalist tendency of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of the generalist network motifs was largely driven by the functional group of bees (e.g., positions 42, 46, 16, 4, 14 and 35 in motifs 15, 17, 7, 2, 6 and 13, respectively; see **Figure 3** for positions and **Figure 4** for motifs) while the rest of the groups tended to be under-represented in these generalist motifs and over-represented in motif positions with specialist roles (e.g., positions 11, 21, 28 and 34 in motifs 5, 9, 11 and 13, respectively; see **Figure 3** for positions and **Figure 4** for motifs).
+This large effect of bees on the overall patterns, are no surprise as bees were the functional group with largest number of interaction records in the whole set of networks as also recorded for other broad scale plant-pollinator network studies [@ollerton2017; MORE REFS?].
+Unlike floral visitors, plant functional groups showed little differences between their maximum and minimum percentile on the different motif positions in the comparison with simulated networks, and thus similar probability of appearing on them (**Figures 3** and **4**).
+However, the groups that involved higher levels of outcrossing showed a tendency to be more over-represented and probable on the different motif positions.
+For instance, the group of self incompatible perennials with large flowers, one of the groups that is expected to have higher levels of outcrossing rate [@goodwillie2010], showed the highest over-representation of all plant functional groups (**Figure 3**); and the group of tall plants with unisexual flowers, the one that is expected to have the highest levels of pollination contribution to reproduction [@rodger2021] was the most probable on the generalist motif for plant positions.
+
 In accordance with the findings of network motif patterns, we found higher representation of plant and pollinator functional groups in more densely connected motifs in contrast to the less densely connected ones (i.e., core-peripheral).
 As expected, the functional group of bees (the one with the highest number of qualitative interactions) was the most abundant in the different network motif positions.
-This concurs well with other plant-pollinator network studies where bees are the main functional group visiting flowers
-[@ollerton2017].
+This concurs well with other plant-pollinator network studies where bees are the main functional group visiting flowers [@ollerton2017].
 Interestingly, bees were highly over-represented in fan motif positions 4, 16 and 46 (**Figure 3**) which are associated with the highest levels of generalism.
@@
 However, a large portion of the possible interactions do not take place because of life history constraints [i.e., forbidden links; @olesen2011; @bartomeus2016; @jordano2016].
-Thus, similarly to the presence of these forbidden interactions or links, we found also the existence of forbidden motifs that represent set of indirect interactions that do not take place in natural systems.
+Thus, similarly to the presence of forbidden links at the network level, we found also the existence of forbidden motifs that represent set of indirect interactions that do not take place in natural systems.
 

### 2021-10-14 Draft/Draft.Rmd
minor edit
deleting old paragraph

@@
 For instance, the group of self incompatible perennials with large flowers, one of the groups that is expected to have higher levels of outcrossing rate [@goodwillie2010], showed the highest over-representation of all plant functional groups (**Figure 3**); and the group of tall plants with unisexual flowers, the one that is expected to have the highest levels of pollination contribution to reproduction [@rodger2021] was the most probable on the generalist motif for plant positions.
-
-In accordance with the findings of network motif patterns, we found higher representation of plant and pollinator functional groups in more densely connected motifs in contrast to the less densely connected ones (i.e., core-peripheral).
-As expected, the functional group of bees (the one with the highest number of qualitative interactions) was the most abundant in the different network motif positions.
-This concurs well with other plant-pollinator network studies where bees are the main functional group visiting flowers [@ollerton2017].
-Interestingly, bees were highly over-represented in fan motif positions 4, 16 and 46 (**Figure 3**) which are associated with the highest levels of generalism.
-Further, this generalist tendency was also observed at motif level (e.g., **Figure 2** comparison of the percentiles of mirror image motifs that involve the opposed roles of specialization and generalism from a pollinator perpective).
-Despite this is in good agreement with the current view of the generalist nature of pollinators [@waser1996; @olesen2002], we found that this over-representation of the generalist network motifs was mainly driven by bees while the rest of functional groups tended to be under-represented in these generalist motifs.
-Unlike floral visitors, plant functional groups showed little differences between their maximum and minimum percentile on the different motif positions in the comparison with simulated networks, and thus similar probability of appearing on them.
-However, the groups that involved higher levels of outcrossing with perennial lifespan showed a tendency to be more over-represented and probable on the different motif positions.
-For instance, the group of self incompatible perennials with large flowers, one of the groups that is expected to have higher levels of outcrossing rate [@goodwillie2010], showed the highest over-representation of all plant functional groups on the different motif positions (**Figure 3**).
 

### 2021-10-14 Draft/Draft.Rmd
Discussion

@@
 Despite this is in good agreement with the current view of the generalist tendency of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of the generalist network motifs was largely driven by the functional group of bees (e.g., positions 42, 46, 16, 4, 14 and 35 in motifs 15, 17, 7, 2, 6 and 13, respectively; see **Figure 3** for positions and **Figure 4** for motifs) while the rest of the groups tended to be under-represented in these generalist motifs and over-represented in motif positions with specialist roles (e.g., positions 11, 21, 28 and 34 in motifs 5, 9, 11 and 13, respectively; see **Figure 3** for positions and **Figure 4** for motifs).
-This large effect of bees on the overall patterns, are no surprise as bees were the functional group with largest number of interaction records in the whole set of networks as also recorded for other broad scale plant-pollinator network studies [@ollerton2017; MORE REFS?].
-Unlike floral visitors, plant functional groups showed little differences between their maximum and minimum percentile on the different motif positions in the comparison with simulated networks, and thus similar probability of appearing on them (**Figures 3** and **4**).
+This large effect of bees on the overall patterns, are no surprise as bees were the functional group with largest number of interaction records in the whole set of networks as also recorded for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017].
+Unlike floral visitors, plant functional groups showed little differences between their maximum and minimum percentile on the different motif positions in the comparison with simulated networks, and thus similar probability of appearing on them.
 However, the groups that involved higher levels of outcrossing showed a tendency to be more over-represented and probable on the different motif positions.
-For instance, the group of self incompatible perennials with large flowers, one of the groups that is expected to have higher levels of outcrossing rate [@goodwillie2010], showed the highest over-representation of all plant functional groups (**Figure 3**); and the group of tall plants with unisexual flowers, the one that is expected to have the highest levels of pollination contribution to reproduction [@rodger2021] was the most probable on the generalist motif for plant positions.
+For instance, the group of self incompatible perennials with large flowers, one of the groups that is expected to have higher levels of outcrossing rate [@goodwillie2010], showed the highest over-representation of all plant functional groups (**Figure 3**); and the group of tall plants with unisexual flowers, the one that is expected to have the highest dependence of pollinators on reproduction [@rodger2021], was the most probable on the generalist motif for plant positions (i.e, plant nodes with 3 to 4 links).
 
 The observed functional group probabilities on the different motif positions (**Figure 4**) were insufficient to predict most of the observed network motifs (**Figure 5**).
-This implies that not just the structure of network motifs but also the identity of the elements of their structure are influenced by ecological processes that determine under- and over-representation of the different motif combinations.
+This implies that not just the representation of network motifs types but also the identity of the elements of their structure is influenced by ecological processes that determine under- and over-representation of the different motif combinations.
 In addition, we found that just 30% of the possible 5,3250 motif combinations took place.
-However, this restricted set of possible combinations is no surprise, because plant-pollinator networks (i.e., full network level) have a high percentage of non-realized interactions [@bascompte2013].
+As suggested by @simmons2020, exploring the proportion of competitive or facilitative relized indirect interactions is a necessesary next step to improve our understanding of the architecture of biodiversity [@bascompte2007].
+In addition, this restricted set of possible combinations is no surprise, because plant-pollinator networks (i.e., full network level) have a high percentage of non-realized interactions [@jordano2003; @bascompte2013].
 Some of this non-observed motif combinations are likely to be the cause of under-sampling [@olesen2011; @jordano2016].
 However, a large portion of the possible interactions do not take place because of life history constraints [i.e., forbidden links; @olesen2011; @bartomeus2016; @jordano2016].
-Thus, similarly to the presence of forbidden links at the network level, we found also the existence of forbidden motifs that represent set of indirect interactions that do not take place in natural systems.
-
-Despite the obvious usefulness of funtional groups in summarizing species ecological roles (e.g., similar reproductive biology and behaviour of pollinators), taxonomical diversity and trait availability limit our ability to properly represent the diverse range of reproductive strategies in natural systems.
-
----
-
-4) Limitations (but keep it short and simple): FG are hard to describe, bias in sampling worldwide, …
-
-Although functional groups can define
-
-- FG hard to describe: https://doi.org/10.1093/aob/mcp031 and the fenster one
-
-- Paper of Poisot 2020
-
+Thus, similarly to the presence of forbidden links at the network level, we found also the existence of forbidden motifs that represented non-realized combinations of indirect interactions.
+
+4th: Link ideas...
+
+Despite the obvious usefulness of funtional groups in summarizing species ecological roles (e.g., similar reproductive biology and behaviour of pollinators), taxonomical diversity and trait availability limit our ability to properly represent the diverse range of reproductive strategies in natural systems [@dellinger2020].
+
+Further, delimiting both floral visitors and plants with traits could help revealing more trait-matching processes across groups that are not captured when taxonomic rank is used.
+Another limitation is that our study just considers binary interactions (presence-absence) and does not account for the interaction strength between plant and pollinator species which is essential to understand pollinator impact upon plant reproduction [REF].
+
+.
+However, the analysis of quantitative motifs have been just recently develop [@bmotifsimmons2019] and more work is needed to understand their ecological implications in mutualistic networks.
+Moreover, despite the wide geographical coverage of our plant-pollinator dataset, there are major gaps for some regions of the world with a clear bias towards Europe, America and islands which have long interested ecologist [@macarthur1963; @warren2015].
+This biasis are also found in global datasets of networks where the data is highly fragmented across space [@poisot2021] and more efforts are needed to capture global patterns of plant-pollinator networks.
+
+Final one: 
 5) Future direction and conclusions (also short).
@@
 We not only know now how the building blocks are structures, but also that who conform this building blocks is not random.
----
 

### 2021-10-15 Draft/Draft.Rmd
working again with paragraph 3 not happy with the ending

@@
 For instance, when we compare motifs with equal structure but inverted, we found that floral visitors had always over-representation in the positions that implied the highest number of links.
-Despite this is in good agreement with the current view of the generalist tendency of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of the generalist network motifs was largely driven by the functional group of bees (e.g., positions 42, 46, 16, 4, 14 and 35 in motifs 15, 17, 7, 2, 6 and 13, respectively; see **Figure 3** for positions and **Figure 4** for motifs) while the rest of the groups tended to be under-represented in these generalist motifs and over-represented in motif positions with specialist roles (e.g., positions 11, 21, 28 and 34 in motifs 5, 9, 11 and 13, respectively; see **Figure 3** for positions and **Figure 4** for motifs).
-This large effect of bees on the overall patterns, are no surprise as bees were the functional group with largest number of interaction records in the whole set of networks as also recorded for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017].
+Despite this is in good agreement with the current view of the generalist tendency of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of the generalist network motifs was largely driven by the functional group of bees (e.g., positions 42, 46, 16, 4, 14 and 35 in motifs 15, 17, 7, 2, 6 and 13, respectively; see **Figure 3** for positions and **Figure 4** for motifs) while the rest of the functional groups tended to be under-represented in these generalist motifs and over-represented in motif positions with specialist roles (e.g., positions 11, 21, 28 and 34 in motifs 5, 9, 11 and 13, respectively; see **Figure 3** for positions and **Figure 4** for motifs).
+This large effect of bees on the overall patterns is no surprise, as bees were the functional group with largest number of interaction records in the whole set of networks as also recorded for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017].
 Unlike floral visitors, plant functional groups showed little differences between their maximum and minimum percentile on the different motif positions in the comparison with simulated networks, and thus similar probability of appearing on them.
@@
 This implies that not just the representation of network motifs types but also the identity of the elements of their structure is influenced by ecological processes that determine under- and over-representation of the different motif combinations.
+As suggested by @simmons2020, exploring the proportion of these realized network motifs that is competitive or facilitative is a necessary next step to improve our understanding of the architecture of biodiversity [@bascompte2007].
 In addition, we found that just 30% of the possible 5,3250 motif combinations took place.
-As suggested by @simmons2020, exploring the proportion of competitive or facilitative relized indirect interactions is a necessesary next step to improve our understanding of the architecture of biodiversity [@bascompte2007].
-In addition, this restricted set of possible combinations is no surprise, because plant-pollinator networks (i.e., full network level) have a high percentage of non-realized interactions [@jordano2003; @bascompte2013].
-Some of this non-observed motif combinations are likely to be the cause of under-sampling [@olesen2011; @jordano2016].
+This concurs well with the general idea that plant-pollinator networks have a high porportion of non-realized interactions [@jordano2003; @bascompte2013] which can be also infered to indirect interactions.
+@olesen2011 also found a similar porportion of non-realized links in comparison with our findings of non-realized indirect interactions (80% and 70%, respectively).
+Some of this non-observed interactions are propably caused by under-sampling [@olesen2011; @jordano2016].
 However, a large portion of the possible interactions do not take place because of life history constraints [i.e., forbidden links; @olesen2011; @bartomeus2016; @jordano2016].
-Thus, similarly to the presence of forbidden links at the network level, we found also the existence of forbidden motifs that represented non-realized combinations of indirect interactions.
+Thus, similarly to the presence of forbidden links at the network level, we also found the existence of forbidden motifs that represented almost two thirds of the total combinations of indirect interactions.
+
+I NEED A LAST PHRASE HERE
+
+Despite the recent efforts in understanding what are the main drivers of plant-pollinator interactions that ultimately shape competitive and facilitative processes, we lack comprehensive understanding of how these processes affect species direct and ultimately indirect interactions at a macroecological scale.
 

### 2021-10-15 Draft/Draft.Rmd
Conclusions...

@@
 However, the groups that involved higher levels of outcrossing showed a tendency to be more over-represented and probable on the different motif positions.
-For instance, the group of self incompatible perennials with large flowers, one of the groups that is expected to have higher levels of outcrossing rate [@goodwillie2010], showed the highest over-representation of all plant functional groups (**Figure 3**); and the group of tall plants with unisexual flowers, the one that is expected to have the highest dependence of pollinators on reproduction [@rodger2021], was the most probable on the generalist motif for plant positions (i.e, plant nodes with 3 to 4 links).
-
-The observed functional group probabilities on the different motif positions (**Figure 4**) were insufficient to predict most of the observed network motifs (**Figure 5**).
+For instance, the group of self-incompatible perennials with large flowers, one of the groups that is expected to have higher levels of outcrossing rate [@goodwillie2010], showed the highest over-representation of all plant functional groups (**Figure 3**); and the group of tall plants with unisexual flowers, the one that is expected to have the highest dependence of pollinators on reproduction [@rodger2021], was the most probable on the generalist motif for plant positions (i.e., plant nodes with 3 to 4 links; **Figure 4**).
+
+The observed functional group probabilities on the different motif positions were insufficient to predict most of the observed network motifs (**Figure 5**).
 This implies that not just the representation of network motifs types but also the identity of the elements of their structure is influenced by ecological processes that determine under- and over-representation of the different motif combinations.
-As suggested by @simmons2020, exploring the proportion of these realized network motifs that is competitive or facilitative is a necessary next step to improve our understanding of the architecture of biodiversity [@bascompte2007].
-In addition, we found that just 30% of the possible 5,3250 motif combinations took place.
-This concurs well with the general idea that plant-pollinator networks have a high porportion of non-realized interactions [@jordano2003; @bascompte2013] which can be also infered to indirect interactions.
-@olesen2011 also found a similar porportion of non-realized links in comparison with our findings of non-realized indirect interactions (80% and 70%, respectively).
-Some of this non-observed interactions are propably caused by under-sampling [@olesen2011; @jordano2016].
-However, a large portion of the possible interactions do not take place because of life history constraints [i.e., forbidden links; @olesen2011; @bartomeus2016; @jordano2016].
-Thus, similarly to the presence of forbidden links at the network level, we also found the existence of forbidden motifs that represented almost two thirds of the total combinations of indirect interactions.
-
-I NEED A LAST PHRASE HERE
-
-Despite the recent efforts in understanding what are the main drivers of plant-pollinator interactions that ultimately shape competitive and facilitative processes, we lack comprehensive understanding of how these processes affect species direct and ultimately indirect interactions at a macroecological scale.
-
-4th: Link ideas...
-
-Despite the obvious usefulness of funtional groups in summarizing species ecological roles (e.g., similar reproductive biology and behaviour of pollinators), taxonomical diversity and trait availability limit our ability to properly represent the diverse range of reproductive strategies in natural systems [@dellinger2020].
-
-Further, delimiting both floral visitors and plants with traits could help revealing more trait-matching processes across groups that are not captured when taxonomic rank is used.
-Another limitation is that our study just considers binary interactions (presence-absence) and does not account for the interaction strength between plant and pollinator species which is essential to understand pollinator impact upon plant reproduction [REF].
-
-.
-However, the analysis of quantitative motifs have been just recently develop [@bmotifsimmons2019] and more work is needed to understand their ecological implications in mutualistic networks.
+In addition, we found that just 30% of the possible 53,250 motif combinations took place.
+Thus, similarly to the presence of forbidden links at the network level [@olesen2011; @jordano2016], we also found the existence of forbidden motifs that represented almost two thirds of the total combinations of indirect interactions.
+This concurs well with the general idea that plant-pollinator networks have a high porportion of non-realized direct interactions [@jordano2003; @bascompte2013], and as a result, also a high proportion of non-realized combinations of indirect interactions.
+Some of this non-observed interactions are probably due to under-sampling [@dorado2011; @jordano2016].
+However, a large fraction of the possible interactions do not take place because of life history constraints such as species co-occurence, trait matching processes and phenological uncoupling [@olesen2011; @bartomeus2016; @jordano2016].
+Despite the advances in the understanding on the ecological processes that influence species pairwise interactions [@bartomeus2016; @peralta2020], we still know little of how these processes determine competitive and facilitative interactions in mutualistic networks.
+Thus, as suggested by @simmons2020, exploring the proportion of these realized network motifs that is competitive or facilitative is a necessary next step to improve our understanding of the architecture of biodiversity [@bascompte2007].
+
+Despite the obvious usefulness of funtional groups in summarizing species ecological roles (e.g., similar reproductive biology and behaviour of pollinators), delimiting species into functional groups is not often trivial.
+For instance, taxonomic diversity and trait availability limit our ability to properly represent the wide range of reproductive strategies [@dellinger2020] and different clustering analysis can lead to distinct outcomes (e.g., k-means and hierarchical clustering).
+Further, here we divided floral visitors on the taxonomic rank level because it represented adequately the pollinator species ecological roles but further groupings with trait data could help revealing greater relevance of trait-matching processes on indirect interactions.
+Moreover, we analysed network motifs focusing exclusively on presence-absence interactions but as suggested by @simmons2020, further work should account for quantitative measurements of interaction strength.
 Moreover, despite the wide geographical coverage of our plant-pollinator dataset, there are major gaps for some regions of the world with a clear bias towards Europe, America and islands which have long interested ecologist [@macarthur1963; @warren2015].
-This biasis are also found in global datasets of networks where the data is highly fragmented across space [@poisot2021] and more efforts are needed to capture global patterns of plant-pollinator networks.
+These biases are also found in global datasets of networks where the data is highly fragmented across space [@poisot2021] and more efforts are needed to capture global patterns of plant-pollinator networks.
+
+In conclusion, by following the framework of @simmons2020 we have been able to explore competitive and facilitative interactions in plant-pollinator networks worldwide and found that indirect interactions are non-random and are more strongly related to neutral processes than any other ecological process.
+The association between network motifs and functional groups revealead that the combinations of functional groups is also strongly restricted by ecological processes
+
+these groups rely on their ecological role (e.g., generalization versus specialization) and relies also
+
+Further, the different network motifs are associated with different fucntional groups which translates into different ecological roles of these functional groups at macroecological scale.
+
+with specific network motif positions associated to different species ecological roles.
+This work set the stage to help predicting novel interactions beyond pairwise interactions, to explore the overall importance
+
+Further, bees were the only generalist functional group in comparison with the rest floral visitor groups that appeared more frequently in specialist network motifs.
+We also found that the the node position was partly associated to the ecological role of plants but without large differences between groups.
+Our work has explored for the first time worldwide plant-pollinator patterns of indirect interactions and opens the door for predicting novel interactions beyond pairwise interactions.
 
@@
 This opens the door to help predicting novel interactions beyond pairwise interactions.
-We not only know now how the building blocks are structures, but also that who conform this building blocks is not random.
+We not only know now how the building blocks are structured but also that who conform this building blocks is not random.
 

### 2021-10-16 Draft/Draft.Rmd
Conclusion and abstract

@@
 
-##Abstract
+# Abstract
 
@@
 motifs) and those constitute the building blocks of the whole network.
-Here, we have compiled 60 networks from 18 different studies and show that some motifs are consitently under- and over-represented worldwide, suggesting that the building blocks of plant-pollintor networks are not random.
-Interestingly, different functional groups are associated to specific motif position across both trophic levels.
-HERE I WOULD PUT AN EXAMPLE OF E.G.
-FAN POSITIONS, DEFINED BY, TEND TO BE OCCUPIED BY BEES AND WHATEVER TYPE OF PLANTS, RESPECTIVELY.
-This findings open the door to predict how novel interactions will be formed within a community context.
+Here, we have compiled 60 networks from 18 different studies and show that some motifs are consistently under- and over-represented worldwide, suggesting that the building blocks of plant-pollinator networks are not random and are most influenced by species relative abundances.
+Interestingly, network motif combinations are restricted to almost two thirds of all the potential indirect interactions and we found that distinct positions that imply different ecological roles (e.g., specialization versus generalization) are occupied by different functional groups on both trophic levels.
+For instance, bees were consistently on generalist motif positions while the rest of functional groups tended to appear on specialist ones.
+Although for plants these differences were less marked, we found that the species with higher levels of outcrossing had the most number of indirect interactions.
+Our result highlight the non-random structure of indirect interactions in plant-pollinator networks and opens the door to predict novel interactions beyond pairwise interactions within a community context.
 
@@
 
-##INTRODUCTION
+# INTRODUCTION
 
@@
 
-##METHODS
+# METHODS
 
@@
 For this, we used the trait dataset collated in Chapter 1 that comprised a total of 1506 species including the 503 species considered in this study (Supplementary material Chapter 1 **Table S1**).
-This dataset consisted on 8 floral, 4 reproductive and 3 vegetative traits excluding traits with high percentage of missing values (over 30%; **Table S2**).
+This dataset consisted on 8 floral, 4 reproductive and 3 vegetative traits excluding traits with high percentage of missing values (over 30$\%$; **Table S2**).
 We opted to calculate the plant functional groups on this larger set of species because of the higher accuracy when delimiting functional groups with that many variables and species [@dolnicar2014].
@@
 Thus, this allowed us to group floral visitors into functional groups that represented adequately the main life strategies of the possible pollinators: (i) bees (Hymenoptera-Anthophila), (ii) non-bee Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Syrphidae-Diptera), (iv) non-syrphids-Diptera, (v) Lepidoptera and (vi) Coleoptera.
-However, a minor set of species belonged to other functional groups that were considered in analyses but not discussed further because of their low representation in the full set of networks (3.55% of the total interactions recorded).
+However, a minor set of species belonged to other functional groups that were considered in analyses but not discussed further because of their low representation in the full set of networks (3.55$\%$ of the total interactions recorded).
 These functional groups were 'lizards', 'birds' and 'other insects'.
@@
 Prior to analyses, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.
-To test the effect of singletones, we ran all analysis to the same set of networks, but considering only interactions whose frequency was greater than one (64.98% of interactions).
+To test the effect of singletones, we ran all analysis to the same set of networks, but considering only interactions whose frequency was greater than one (64.98$\%$ of interactions).
 Results are qualitatively consistent and are not further discussed in the main text (**Figures S1 and S2**).
@@
 From those random samples, we extracted the mean and the standard deviation of the expected probability of $i$, denoted as $E\left [ p_i^E \right ]$ and $\sigma\left [ p_i^E \right ]$, respectively, and calculated the z-scores of $p_i^O$ as $z_i^O = \left ( p_i^O - E\left [ p_i^E \right ] \right )/\sigma \left [ p_i^E \right ]$, for those motif combinations with $p_i^O > 0$.
-According to the usual interpretation of z-scores, combinations with $z_i^O > 1.96$ are over-represented, whereas those with $z_i^O < -1.96$ are under-represented, at the 95%  confidence level.
+According to the usual interpretation of z-scores, combinations with $z_i^O > 1.96$ are over-represented, whereas those with $z_i^O < -1.96$ are under-represented, at the 95$\%$  confidence level.
 Notice that we focused on combinations with $p_i^O > 10^{-7}$ because, beyond the interest that can arouse the combinations that appear at most once, we do not have enough numerical resolution to accurately detect whether or not those combinations are under-represented (due to the limited size of our random samples).
@@
 
-##RESULTS
+#RESULTS
 
@@
 Finally, the fifth group named 'short-lived outcrossers with long zygomorphic flowers' consisted on small perennial and short-lived herbs with long self-compatible zygomorphic flowers that were unable to self-pollinate.
-
----
-COMMENT
-IB: Note that along the ms (abstract, discusion, etc...), I would discuss the group names ('selfing herbs') and not numbers (Group 1) otherwise we will lost the readers.
----
 
@@
 
----
-THIS IS A COMMENT
-Alfonso sobre la frase "These differences were more marked for floral visitors...": Cómo se infiere esto? Es viendo el dendrograma?
-
-Jose: He modidficado el texto y creo que ahora está más claro
----
-
 ```{r , include=FALSE}
@@
 
-The comparison of the functional group frequencies per motif position between empirical and simulated networks showed a `r over`% and `r under`% of over- (>75$^{th}$) and under- (<25th) represented functional groups in the different positions, respectively (**Figure 3**).
-Floral visitors showed a total of `r poll_over_75`% and `r poll_under_25`% of over- and under-represented functional groups in the different positions and plants `r plant_over_75`% and `r plant_under_25`% of over and under-represented groups, respectively.
+The comparison of the functional group frequencies per motif position between empirical and simulated networks showed a `r over`$\%$ and `r under`$\%$ of over- (>75$^{th}$) and under- (<25th) represented functional groups in the different positions, respectively (**Figure 3**).
+Floral visitors showed a total of `r poll_over_75`$\%$ and `r poll_under_25`$\%$ of over- and under-represented functional groups in the different positions and plants `r plant_over_75`$\%$ and `r plant_under_25`$\%$ of over and under-represented groups, respectively.
 Notably, the differences across functional groups were more marked for floral visitors than for plant functional groups (the differences between min and max percentiles per position were generally two-three times larger for floral visitors).
@@
 
-**Over- and under-represented funtional group combinations of motifs**
-
-The different observed frequencies on the different motif positions showed a hirarchical order of probabilities for floral visitors (**Figure 4**).
+**Over- and under-represented functional group combinations of motifs**
+
+The different observed frequencies on the different motif positions showed a hierarchical order of probabilities for floral visitors (**Figure 4**).
 That is, the functional group of 'bees' was the most abundant one on all motif positions followed by non-syrphid Diptera which was after bees, the second most frequent functional group on all positions.
@@
 
-The statistical comparison with z-scores between the observed and expected functional group combinations showed that we can not recover the observed combinations from its probability of ocurrence.
-In fact, most combinations are under- or over- representedm and follow a modified Gaussian distribution (Johnson's $S_U$) with 65% of under-represented group combinations, 20% of no statistical difference and 15% of under-represented ones (**Figure 5**).
+The statistical comparison with z-scores between the observed and expected functional group combinations showed that we can not recover the observed combinations from its probability of occurrence.
+In fact, most combinations are under- or over- represented and follow a modified Gaussian distribution (Johnson's $S_U$) with 65$\%$ of under-represented group combinations, 20$\%$ of no statistical difference and 15$\%$ of under-represented ones (**Figure 5**).
 In addition, motifs with small node combinations (i.e., 2 and 3 nodes) only appeared as under-represented.
-Motifs with 4 and 5-node combinations appeared in the three statistical categories but 4 node motifs had a higher porportion in the under-represented category (10% in comparison with the 1% and the 3% of the no statiscal difference and over-represented categories, respectively).
-Finally, 5-node motifs were in similar prportions in the no statistical difference and over-represented categories (99% and 97%, respectively) but they appeared in lower porportion in the under-represented category (89%).
-When, we explore the identity on the different positions of the most probable motif combinations we find as expected that the most common functional groups rule these positions on the most probable motif combiantions (lower panel **Figure 5**).
+Motifs with 4 and 5-node combinations appeared in the three statistical categories but 4 node motifs had a higher proportion in the under-represented category (10% in comparison with the 1$\%$ and the 3$\%$ of the no statistical difference and over-represented categories, respectively).
+Finally, 5-node motifs were in similar proportions in the no statistical difference and over-represented categories (99$\%$ and 97$\%$, respectively) but they appeared in lower proportion in the under-represented category (89$\%$).
+When, we explore the identity on the different positions of the most probable motif combinations we find as expected that the most common functional groups rule these positions on the most probable motif combinations (lower panel **Figure 5**).
 
@@
 
-##DISCUSSION
+# DISCUSSION
 
@@
 
-From a pollinator perpective, we found that generalist network motifs were consistently over-represented (**Figure 2**).
+From a pollinator perspective, we found that generalist network motifs were consistently over-represented (**Figure 2**).
 For instance, when we compare motifs with equal structure but inverted, we found that floral visitors had always over-representation in the positions that implied the highest number of links.
@@
 This implies that not just the representation of network motifs types but also the identity of the elements of their structure is influenced by ecological processes that determine under- and over-representation of the different motif combinations.
-In addition, we found that just 30% of the possible 53,250 motif combinations took place.
+In addition, we found that just 30$\%$ of the possible 53,250 motif combinations took place.
 Thus, similarly to the presence of forbidden links at the network level [@olesen2011; @jordano2016], we also found the existence of forbidden motifs that represented almost two thirds of the total combinations of indirect interactions.
-This concurs well with the general idea that plant-pollinator networks have a high porportion of non-realized direct interactions [@jordano2003; @bascompte2013], and as a result, also a high proportion of non-realized combinations of indirect interactions.
+This concurs well with the general idea that plant-pollinator networks have a high proportion of non-realized direct interactions [@jordano2003; @bascompte2013], and as a result, also a high proportion of non-realized combinations of indirect interactions.
 Some of this non-observed interactions are probably due to under-sampling [@dorado2011; @jordano2016].
-However, a large fraction of the possible interactions do not take place because of life history constraints such as species co-occurence, trait matching processes and phenological uncoupling [@olesen2011; @bartomeus2016; @jordano2016].
+However, a large fraction of the possible interactions do not take place because of life history constraints such as species co-occurrence, trait matching processes and phenological uncoupling [@olesen2011; @bartomeus2016; @jordano2016].
 Despite the advances in the understanding on the ecological processes that influence species pairwise interactions [@bartomeus2016; @peralta2020], we still know little of how these processes determine competitive and facilitative interactions in mutualistic networks.
@@
 
-Despite the obvious usefulness of funtional groups in summarizing species ecological roles (e.g., similar reproductive biology and behaviour of pollinators), delimiting species into functional groups is not often trivial.
+Despite the obvious usefulness of functional groups in summarizing species ecological roles (e.g., similar reproductive biology and behaviour of pollinators), delimiting species into functional groups is not often trivial.
 For instance, taxonomic diversity and trait availability limit our ability to properly represent the wide range of reproductive strategies [@dellinger2020] and different clustering analysis can lead to distinct outcomes (e.g., k-means and hierarchical clustering).
-Further, here we divided floral visitors on the taxonomic rank level because it represented adequately the pollinator species ecological roles but further groupings with trait data could help revealing greater relevance of trait-matching processes on indirect interactions.
-Moreover, we analysed network motifs focusing exclusively on presence-absence interactions but as suggested by @simmons2020, further work should account for quantitative measurements of interaction strength.
-Moreover, despite the wide geographical coverage of our plant-pollinator dataset, there are major gaps for some regions of the world with a clear bias towards Europe, America and islands which have long interested ecologist [@macarthur1963; @warren2015].
-These biases are also found in global datasets of networks where the data is highly fragmented across space [@poisot2021] and more efforts are needed to capture global patterns of plant-pollinator networks.
+Further, here we divided floral visitors on the taxonomic rank level because it represented adequately the pollinator species ecological roles without the need of the tremendous effort of compiling trait data for over 1000 species of floral visitors.
+However, further groupings with traits could help revealing greater relevance of trait-matching processes on indirect interactions.
+We believe that this could be investigated by exploring which proportion of over- and under-represented motifs present high and low trait-matching, respectively.
+Moreover, we analysed network motifs focusing exclusively on presence-absence interactions which assume that all interactions are equally important but as suggested by @simmons2020, further work should account for quantitative measurements of the strength of plant-pollinator interactions.
+Moreover, despite the wide geographical coverage of our plant-pollinator dataset, there are major gaps for some regions of the world with a clear bias towards Europe, America and islands which have long been interested ecologist [@macarthur1963; @warren2015].
+These biases are also found in global datasets of networks where the data is highly fragmented across space [@poisot2021] and more efforts are needed to capture global patterns of plant-pollinator interactions.
 
 In conclusion, by following the framework of @simmons2020 we have been able to explore competitive and facilitative interactions in plant-pollinator networks worldwide and found that indirect interactions are non-random and are more strongly related to neutral processes than any other ecological process.
-The association between network motifs and functional groups revealead that the combinations of functional groups is also strongly restricted by ecological processes
-
-these groups rely on their ecological role (e.g., generalization versus specialization) and relies also
-
-Further, the different network motifs are associated with different fucntional groups which translates into different ecological roles of these functional groups at macroecological scale.
-
-with specific network motif positions associated to different species ecological roles.
-This work set the stage to help predicting novel interactions beyond pairwise interactions, to explore the overall importance
-
-Further, bees were the only generalist functional group in comparison with the rest floral visitor groups that appeared more frequently in specialist network motifs.
-We also found that the the node position was partly associated to the ecological role of plants but without large differences between groups.
-Our work has explored for the first time worldwide plant-pollinator patterns of indirect interactions and opens the door for predicting novel interactions beyond pairwise interactions.
-
-Final one: 
-5) Future direction and conclusions (also short).
-This opens the door to help predicting novel interactions beyond pairwise interactions.
-We not only know now how the building blocks are structured but also that who conform this building blocks is not random.
-
-Idea: explore if over-represented and under-represented groups have trait-matching or not...
-As suggested in the literature the more stable (and probably more frequent I guess will have well matched traits...)
-
-##REFERENCES
+Further, we found that motif combinations of functional groups are strongly constrained and that the distinct motif positions are associated with different functional groups with different ecological roles (e.g., generalization versus specialization).
+Although in this study we do not predict indirect interactions, our work is a first step to elucidate novel interactions beyond pairwise interactions.
+
+# REFERENCES
 

### 2021-10-17 Draft/Draft.Rmd
Last read before tehis deposition!

@@
 motifs) and those constitute the building blocks of the whole network.
-Here, we have compiled 60 networks from 18 different studies and show that some motifs are consistently under- and over-represented worldwide, suggesting that the building blocks of plant-pollinator networks are not random and are most influenced by species relative abundances.
-Interestingly, network motif combinations are restricted to almost two thirds of all the potential indirect interactions and we found that distinct positions that imply different ecological roles (e.g., specialization versus generalization) are occupied by different functional groups on both trophic levels.
-For instance, bees were consistently on generalist motif positions while the rest of functional groups tended to appear on specialist ones.
-Although for plants these differences were less marked, we found that the species with higher levels of outcrossing had the most number of indirect interactions.
+Here, we have compiled 60 networks from 18 different studies and show that some motifs are consistently under- and over-represented worldwide, suggesting that the building blocks of plant-pollinator networks are not random [and are most influenced by species relative abundances](esto no lo entiendo, aqui hablas de motifs binarios.
+Yo borraba este final de frase).
+[Interestingly, network motif combinations are restricted to almost two thirds of all the potential indirect interactions](esto tampoco...
+soy yo que estoy espeso?
+si es lo que creo, lo he puesto más abajo).
+Furthermore, we found that distinct motif positions describing species ecological roles (e.g., generalization, indirect interactions) are occupied by different functional groups on both trophic levels.
+For instance, bees appear consistently in generalist motif positions and plants with higher levels of outcrossing tend to have a large number of indirect interactions.
+Interestingly, the realized combinations of different functional groups within a motif can not be retrieved from their joint probability distributions, indicating that functional group combinations are not random.
 Our result highlight the non-random structure of indirect interactions in plant-pollinator networks and opens the door to predict novel interactions beyond pairwise interactions within a community context.
@@
 
----
-THIS IS A COMMENT
-Sugerencia Alfonso (Talking about the last phrase "however,...""): Esta parte de la frase me ha dejado con la pregunta de ¿por qué implica perder info?
-Intentaría dar algún dato que ilustre lo anterior, o la importancia de las relaciones indirectas, aunque esto último lo metes en el siguiente párrafo
-
-Sugerencia Alfonso (next paragraph, desde inicio a "(e.g., nestedness)"):Quizás esto lo intentaría sintetizar y meter al final del párrafo anterior y ya empezar en el segundo párrafo a hablar de motifs, como marco de trabajo/nivel de análisis complementario a los anteriores.
-
-He modificado un poco el texto, yo creo que se lee bien.
----
-
 Traditionally, plant-pollinator research has focused on direct interactions but overlooked indirect interactions (i.e., the mediated effect between two species by a third species), such as facilitative or competitive interactions between plants for pollinators [@moeller2004; @sargent2008].
@@
 Yet, the global patterns of indirect interactions in real plant-pollinator networks are still unknown (e.g., over- and under- represented motifs).
-
----
-THIS IS A COMMENT
-Sugerencia Alfonso: Yo haría un único párrafo hablando del marco de motifs y de sus principales obstáculos: (i) el desconocimiento de los patrones de relaciones indirectas en redes de plantas polinizadores reales y (ii) la desconexión entre las estructuras de los motifs y la ecología de las especies (sus comportamientos, estrategias, etc.).
-Luego pasaría al párrafo de qué hacemos en este trabajo.
-Digo esto porque la última frase del párrafo anterior me parecía que se quedaba algo colgada.+
-
-Yo para esta version lo veo bien. Se puede mejorar la estructura quizas, pero no se si vale la pena ahora.
-
-Alf: Probablemente no valga la pena.
----
 
@@
 
----
-SOLVED COMMENT
-IB: "To control for variation in network, maybe motif?"
-AA-P: "Network it's fine, it ultimately condition motif frequencies"
----
-
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, fig.pos="t", warning=FALSE,out.width="75%",fig.align="center", fig.cap="\\textbf{Figure 1.} Adapted figure of Simmons et al., 2019 with all the possible motifs from two to five species in bipartite networks.
@@
 
-To assess the significance of the observed frequencies, we created 1,000 simulated networks for each binary network using the _nullmodel_ function and the _vaznull_ model in the _bipartite_ package version _xxx_ [@dormann2009].
+To assess the significance of the observed frequencies, we created 1,000 simulated networks for each binary network using the _nullmodel_ function and the _vaznull_ model in the _bipartite_ package version [_xxx_](COMPLETALO) [@dormann2009].
 Generated networks had the same number of plants and floral visitors, as well as the same connectance of their corresponding empirical networks.
@@
 
----
-SOLVED COMMENTS
-IB comment: simulation or null model?
-AA-P: I'd say simulation for consistency with the other sections.
-
-IB: size or possible combinations
-AA-P: I'd say size because we are using 10 million elements that are not sufficiently representative of the numerical resolution
----
-
 #RESULTS
@@
 Although plant functional groups showed less differences between them, there were also more represented functional groups than others, thus from most over- to under-represented groups on the different motif positions we found: self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.
-
----
-THIS IS A COMMENT
-IB: De aqui hay que sacar un ejemplo para el abstract.
-No hace falta que este en los resultados, pero sí podemos usarlo en la discusión.
-Por ejemplo.
-Bees and self icop.
-perenials are over repsented in fan positions, while ...
----
 
@@
 
----
-THIS IS A COMMENT
-
-Alfonso (comentario después de fig 5 donde tenía remarkably y ahora un in addition): Yo creo que todo esto es expected.
-Sin embargo, las explicaciones de por qué lo es probablemente van en la discusión.
-Lo mismo que el ajuste de la Johnson's SU: la cola larga de la derecha la producen la sobreabundancia de motifs de 4 y 5 nodos, en comparación con los de 3.
-
-IB: Me falta un take home message.
-Yo creo que es que no podemos predecir las combinciones por sus probabilidades y eso es muy bestia!
-Lo he añadido ya al inicio de este parrafo, pero dejo el comentario por que es un paper complejo y hay que guiar mucho.
-Cada sección deberia tener un mensage claro ( y ese it a abstract) 1) Los motifs no son al azar.
-2) hay posiciones usadas principalmente por ciertos FG.
-3) Hay combinaciones de FG que van más alla de pura probabilidad.
-Fin.
----
-
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 5.** Z-score comparison (95% confidence level) of the observed and expected frequencies of motif combinations with four specific graphical examples of the most probable motifs of being observed for each category delimited by the z-score critical values: under-represented, no statistical difference and over-represented."}
@@
 Thus, as indicated for other network properties like nestedness [@krishna2008; @suweis2013], species relative abundances (i.e., neutral effects) are possibly one of the main determinants of indirect interactions in real plant-pollinator networks.
-
-From a pollinator perspective, we found that generalist network motifs were consistently over-represented (**Figure 2**).
-For instance, when we compare motifs with equal structure but inverted, we found that floral visitors had always over-representation in the positions that implied the highest number of links.
+[brillante el parrafo!]()
+
+From a pollinator perspective, we found that generalist network motifs were consistently over-represented (e.g.
+fan-type motifs; **Figure 2**).
+For instance, when we compare motifs with equal structure for both trophic levels, we found that floral visitors had always over-representation in the positions that implied the highest number of links.
 Despite this is in good agreement with the current view of the generalist tendency of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of the generalist network motifs was largely driven by the functional group of bees (e.g., positions 42, 46, 16, 4, 14 and 35 in motifs 15, 17, 7, 2, 6 and 13, respectively; see **Figure 3** for positions and **Figure 4** for motifs) while the rest of the functional groups tended to be under-represented in these generalist motifs and over-represented in motif positions with specialist roles (e.g., positions 11, 21, 28 and 34 in motifs 5, 9, 11 and 13, respectively; see **Figure 3** for positions and **Figure 4** for motifs).
 This large effect of bees on the overall patterns is no surprise, as bees were the functional group with largest number of interaction records in the whole set of networks as also recorded for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017].
-Unlike floral visitors, plant functional groups showed little differences between their maximum and minimum percentile on the different motif positions in the comparison with simulated networks, and thus similar probability of appearing on them.
-However, the groups that involved higher levels of outcrossing showed a tendency to be more over-represented and probable on the different motif positions.
+Unlike floral visitors, plant functional groups showed little differences on its appearance in different motif positions, and thus similar probability of appearing on all of them.
+If anything, the groups that involved higher levels of outcrossing showed a tendency to be more over-represented and probable on different motif positions.
 For instance, the group of self-incompatible perennials with large flowers, one of the groups that is expected to have higher levels of outcrossing rate [@goodwillie2010], showed the highest over-representation of all plant functional groups (**Figure 3**); and the group of tall plants with unisexual flowers, the one that is expected to have the highest dependence of pollinators on reproduction [@rodger2021], was the most probable on the generalist motif for plant positions (i.e., plant nodes with 3 to 4 links; **Figure 4**).
 
-The observed functional group probabilities on the different motif positions were insufficient to predict most of the observed network motifs (**Figure 5**).
-This implies that not just the representation of network motifs types but also the identity of the elements of their structure is influenced by ecological processes that determine under- and over-representation of the different motif combinations.
-In addition, we found that just 30$\%$ of the possible 53,250 motif combinations took place.
-Thus, similarly to the presence of forbidden links at the network level [@olesen2011; @jordano2016], we also found the existence of forbidden motifs that represented almost two thirds of the total combinations of indirect interactions.
+The probabilities of appearance of each functional group on the different motif positions were insufficient to predict most of the observed network position combinations (**Figure 5**).
+This implies that not just the representation of network motifs types but also the identity of the elements of their structure is influenced by ecological processes that determine under- and over-representation of the different position combinations.
+In addition, we found that just 30$\%$ of the possible 53,250 motif combinations are realized.
+Thus, similarly to the presence of forbidden links at the network level [@olesen2011; @jordano2016], we also found the existence of forbidden motif positions and those represented almost two thirds of the total posible combinations of indirect interactions.
 This concurs well with the general idea that plant-pollinator networks have a high proportion of non-realized direct interactions [@jordano2003; @bascompte2013], and as a result, also a high proportion of non-realized combinations of indirect interactions.
@@
 Despite the advances in the understanding on the ecological processes that influence species pairwise interactions [@bartomeus2016; @peralta2020], we still know little of how these processes determine competitive and facilitative interactions in mutualistic networks.
-Thus, as suggested by @simmons2020, exploring the proportion of these realized network motifs that is competitive or facilitative is a necessary next step to improve our understanding of the architecture of biodiversity [@bascompte2007].
+Thus, as suggested by @simmons2020, exploring the proportion of these realized network motifs that are competitive or facilitative is a necessary next step to improve our understanding of the architecture of biodiversity [@bascompte2007].
 
@@
 Moreover, we analysed network motifs focusing exclusively on presence-absence interactions which assume that all interactions are equally important but as suggested by @simmons2020, further work should account for quantitative measurements of the strength of plant-pollinator interactions.
-Moreover, despite the wide geographical coverage of our plant-pollinator dataset, there are major gaps for some regions of the world with a clear bias towards Europe, America and islands which have long been interested ecologist [@macarthur1963; @warren2015].
+Finally, despite the wide geographical coverage of our plant-pollinator dataset, there are major gaps for some regions of the world with a clear bias towards Europe, America and islands which have long been interested ecologist [@macarthur1963; @warren2015].
 These biases are also found in global datasets of networks where the data is highly fragmented across space [@poisot2021] and more efforts are needed to capture global patterns of plant-pollinator interactions.

### 2021-10-17 Draft/Draft.Rmd
Title change

@@
 ---
-title: Plant-pollintor networks worldwide are composed by the same specific building
-  blocks
+title: The non-random assembly of functional motifs in plant-pollinator networks worldwide
 editor_options:

### 2021-10-18 Draft/Draft.Rmd
Edit on abstract and adding version

@@
 - \newcommand{\elandscape}{\end{landscape}}
-
 output:
@@
 motifs) and those constitute the building blocks of the whole network.
-Here, we have compiled 60 networks from 18 different studies and show that some motifs are consistently under- and over-represented worldwide, suggesting that the building blocks of plant-pollinator networks are not random [and are most influenced by species relative abundances](esto no lo entiendo, aqui hablas de motifs binarios.
-Yo borraba este final de frase).
-[Interestingly, network motif combinations are restricted to almost two thirds of all the potential indirect interactions](esto tampoco...
-soy yo que estoy espeso?
-si es lo que creo, lo he puesto más abajo).
+Here, we have compiled 60 networks from 18 different studies and show that some motifs are consistently under- and over-represented worldwide, suggesting that the building blocks of plant-pollinator networks are not random.
 Furthermore, we found that distinct motif positions describing species ecological roles (e.g., generalization, indirect interactions) are occupied by different functional groups on both trophic levels.
 For instance, bees appear consistently in generalist motif positions and plants with higher levels of outcrossing tend to have a large number of indirect interactions.
-Interestingly, the realized combinations of different functional groups within a motif can not be retrieved from their joint probability distributions, indicating that functional group combinations are not random.
+Interestingly, the realized combinations of different functional groups within a motif can not be retrieved from their joint probability distributions, indicating that functional group combinations are not random either.
 Our result highlight the non-random structure of indirect interactions in plant-pollinator networks and opens the door to predict novel interactions beyond pairwise interactions within a community context.
@@
 
-To assess the significance of the observed frequencies, we created 1,000 simulated networks for each binary network using the _nullmodel_ function and the _vaznull_ model in the _bipartite_ package version [_xxx_](COMPLETALO) [@dormann2009].
+To assess the significance of the observed frequencies, we created 1,000 simulated networks for each binary network using the _nullmodel_ function and the _vaznull_ model in the _bipartite_ package version _2.14_ [@dormann2009].
 Generated networks had the same number of plants and floral visitors, as well as the same connectance of their corresponding empirical networks.

### 2021-10-22 Draft/Draft.Rmd
adding new paper from Bergamo

@@
 
-Ecological processes leave distinct structural imprints on species interactions shaping the topology of mutualistic networks.
+\singlespacing
+{\normalfont Ecological processes leave distinct structural imprints on species interactions shaping the topology of mutualistic networks.
 Detecting those relationships is not trivial since they go beyond pair-wise interactions, but may get blurred when considering full network descriptors.
@@
 Interestingly, the realized combinations of different functional groups within a motif can not be retrieved from their joint probability distributions, indicating that functional group combinations are not random either.
-Our result highlight the non-random structure of indirect interactions in plant-pollinator networks and opens the door to predict novel interactions beyond pairwise interactions within a community context.
+Our result highlight the non-random structure of indirect interactions in plant-pollinator networks and opens the door to predict novel interactions beyond pairwise interactions within a community context.}
 
@@
 Understanding the global patterns of network structure is key to unravel the processes that govern community dynamics [@bascompte2007; @bastolla2009; @guimaraes2020].
-However, common analytical approaches are unable to capture the full complexity of ecological systems [@simmons2019].
+However, common analytical approaches are unable to capture the full complexity of ecological systems [@simmons2019; @bergamo2021].
 Because network motifs can capture both direct and indirect interactions, by analysing over- and under-representation of motifs we are able to explore in greater detail ecological interactions [@stouffer2007].
@@
 Thus, as indicated for other network properties like nestedness [@krishna2008; @suweis2013], species relative abundances (i.e., neutral effects) are possibly one of the main determinants of indirect interactions in real plant-pollinator networks.
-[brillante el parrafo!]()
 

### 2022-01-03 Manuscript/Main_text_Oikos.Rmd
Preparing Oikos submission

--- 2021-10-22 Draft/Draft.Rmd
@@
 ---
-title: The non-random assembly of functional motifs in plant-pollinator networks worldwide
+title: "The non-random assembly of functional motifs in plant-pollinator networks worldwide"
 editor_options:
@@
 
-__Jose B. Lanuza^1,2^__  | __Alfonso Allen-Perkins^2,3^__ |  __Romina Rader^1^__ | __Ignasi Bartomeus^2^__
-
-1 School of Environmental and Rural Science, University of New England, Armidale, New South Wales 2350, Australia.
-
-2 Estación Biológica de Doñana (EBD-CSIC), E-41092 Seville, Spain.
-
-3 Departamento de Ingeniería Eléctrica, Electrónica, Automática y Física Aplicada, ETSIDI, Universidad Politécnica de Madrid, 28040 Madrid, Spain.
-
 \captionsetup[table]{labelformat=empty}
@@
 {\normalfont Ecological processes leave distinct structural imprints on species interactions shaping the topology of mutualistic networks.
-Detecting those relationships is not trivial since they go beyond pair-wise interactions, but may get blurred when considering full network descriptors.
+Detecting those relationships is not trivial since they go beyond pairwise interactions, but may get blurred when considering full network descriptors.
 However, recent work has shown the network meso-scale can capture this important information.
@@
 
+Keyworkds: Plant-pollinator networks, Plant-pollinator interactions, network motifs, functional groups
+
 \doublespacing
 
-# INTRODUCTION
+# Introduction
 
@@
 
-# METHODS
+# Methods
 
@@
 
-# DISCUSSION
+# Discussion
 
@@
 
-# REFERENCES
+*Acknowledgements* - This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2).
+We thank all researchers that made their data openly available and sent it upon request.
+We also thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza and David Ragel for their help with data collection.
+Finally, JBL also thanks the University of New England for the funding provided to carry out this work.
+
+# Author contributions
+
+IB designed the idea. JBL collected the data. AA-P lead the analysis with contributions of JBL and guidance of IB. JBL wrote the manuscript with contributions of IB and AA-P.
+
+# Data availability statement
+
+All data and code would be deposited at Driad Digital repository upon acceptance.
+
+# References
 
 <div id ="refs"></div>
-
-\newpage
-
-##SUPPLEMENTARY MATERIAL
-
-**TABLES**
-
-**Table S1** List of plant-pollinator network studies.
-
-**Table S2** Type of plant traits used in this study.
-
-**FIGURES**
-
-**Figure S1** Over and under-estimated motif frequencies.
-
-**Figure S2** Over and under-estimated functional groups on motif positions.
-
-**Figure S3** Plant trait composition of functional groups.
-
-**Figure S4** Plant dendrogram with functional groups.
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,fig.width=12,  warning=FALSE}
-##############################
-#TABLE S1. List of studies
-##############################
-
-#Load libraries
-library(kableExtra)
-library(dplyr)
-
-#Create data.frame with references
-
-#vector with number of netw per study
-`Number of networks` <- c("6", #1
-                          "2", #2
-                          "3",#3
-                          "1",#4
-                          "1",#5
-                          "1",#6
-                          "1",#7
-                          "2",#8
-                          "1",#9
-                          "1",#10
-                          "8",#11
-                          "16",#12
-                          "6",#13
-                          "2",#14
-                          "4",#15
-                          "1",#16
-                          "3",#17
-                          "1"#18
-                          )
-
-`First author` <- c("Bartomeus", #1
-                    "Dicks",#2
-                    "Dupont",#3
-                    "Elberling",#4
-                    "Fang",#5
-                    "Inouye",#6
-                    "Lundgren",#7
-                    "Olesen",#8
-                    "Small",#9
-                    "Souza",#10
-                    "Kaiser-Bunbury",#11
-                    "Bartomeus",#12
-                    "Kaiser-Bunbury",#13
-                    "Kaiser-Bunbury",#14
-                    "Peralta",#15
-                    "Burkle",#16
-                    "Arroyo-Correa",#17
-                    "Bundgaard"#18
-                    )
-
-Year <- c(2008,#1
-          2002,#2
-          2003,#3
-          1999,#4
-          2008,#5
-          1988,#6
-          2005,#7
-          2002,#8
-          1976,#9
-          2017,#10
-          2017,#11
-          2015,#12
-          2011,#13
-          2010,#14
-          2006,#15
-          2013,#16
-          2019,#17
-          2003#18
-          )
-
-Country <- c("Spain", #1
-               "England", #2
-               "Denmark", #3
-               "Sweden", #4
-               "China", #5
-               "United States", #6
-               "Denmark (Greenland)", #7
-               "Mauritius and Portugal (Azores)", #8
-               "Japan", #9
-               "Brazil", #10
-               "Seychelles", #11
-               "Spain", #12
-               "Seychelles", #13
-               "Mauritius", #14
-               "Argentina", # 15
-               "United States", #16
-               "New Zealand", #17
-               "Denmark" #18
-               )
-
-DOI <- c("https://doi.org/10.1007/s00442-007-0946-1", #1
-         "https://doi.org/10.1046/j.0021-8790.2001.00572.x", #2
-         "https://doi.org/10.1111/j.1365-2656.2008.01501.x", #3
-         "https://doi.org/10.1111/j.1600-0587.1999.tb00507.x", #4
-         "https://doi.org/10.1111/1749-4877.12190", #5
-         "https://doi.org/10.1111/j.1442-9993.1988.tb00968.x", #6
-         "https://doi.org/10.1657/1523-0430(2005)037[0514:TDAHCW]2.0.CO;2", #7
-         "https://doi.org/10.1046/j.1472-4642.2002.00148.x", #8
-         "/13960/t4km08d21", #9
-         "https://doi.org/10.1111/1365-2745.12978", #10
-         "https://doi.org/10.1038/nature21071", #11
-         "https://github.com/ibartomeus/BeeFunData", #12
-         "https://doi.org/10.1111/j.1365-2745.2010.01732.x", #13
-         "https://doi.org/10.1016/j.ppees.2009.04.001", #14
-         "https://doi.org/10.1111/ele.13510", #15
-         "https://doi.org/10.1126/science.1232728", #16
-         "https://doi.org/10.1111/1365-2745.13332", #17
-         "Unpublished, Master thesis" #18
-         )
-
-references <- data.frame(`First author`, Year, `Number of networks`, Country,   DOI)
-
-colnames(references) <- c("First author", "Year", "Number of networks", "Country",  "DOI")
-
-#Check number of studies
-#nrow(references) # 18 studies
-#check number of networks
-#sum(as.numeric(references$`Number of networks`)) #60
-
-references %>%
-  arrange(`First author`)%>%
-  kable( longtable = T, booktabs = T,linesep = "\\addlinespace",align = c("cccc"),escape = FALSE, caption= "\\textbf{Table S1.} List of studies ordered by author with the year of publication, number of contributed networks and digital object identifier") %>%
-  kable_styling(latex_options = c("repeat_header","striped"),  full_width=F,position = c("center"))
-
-```
-
-\elandscape
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=16, fig.width=12}
-
-library(kableExtra)
-
-library(dplyr)
-library(readxl) #read excel file (trait data)
-library(dplyr) #data manipulation
-library(visdat) #VISUALIZE MISSING DATA
-library(naniar)
-library(tidyverse)
-########################################################################################################################################################
-#1) READ TRAIT DATA
-########################################################################################################################################################
-
-Trait <- c("Plant height (m)", "Flower width (mm)", "Flower length (mm)", "Inflorescence width (mm)", "Style length (mm)", "Ovules per flower",
-           "Flowers per plant",  "Autonomous selfing (fruit set)")
-
-Trait1 <- c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Autonomous selfing", "Compatibility system", "Breeding system", "")
-
-T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub \n Tree", "Brush \n Campanulate \n Capitulum \n Open \n Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic", "None \n Low \n Medium \n High", "Self-incomp.
-\n Partially self-comp.
-\n Self-comp.", "Hermaphrodite \n Monoecious \n Dioecious",""),align = c("l"))
-
-Type <- c("Vegetative", "Floral", "Floral", "Floral", "Floral", "Floral", "Floral","Reproductive")
-
-Type_1 <- c("Vegetative", "Vegetative", "Floral", "Floral", "Reproductive", "Reproductive", "Reproductive", "")
-
-dat <- data.frame(Type, Trait,Type_1, Trait1)
-
-colnames(dat) <- c("Type","Traits","Type", "Traits")
-
-kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c"),caption = "\\textbf{Table S2.} Traits used to delimit the different plant functional groups divided in quantitative and categorical traits.") %>%
-kable_styling(full_width = T,latex_options = c("striped")) %>%
-add_header_above(c("Quantitative traits" = 2,"Categorical traits" = 2),bold=T)  %>%
-    column_spec(c(1,4), bold = T) %>% row_spec(0, bold=T)
-
-```
-
-\clearpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure S1.** Comparison of motif frequencies between empirical and simulated networks grouped by average path length (plots a, b, c and d) as determined in Simmons et al.
-(2020) without considering singletones.
-This is shown with the mean percentage of motif frequencies in empirical networks that were over the motif frequencies of the simulated ones (percentiles).
-This was done by network (light blue dots) and then averaged for all networks (black dots with error bars that correspond to the standard deviation)."}
-library(lme4)
-library(nlme)
-library(tidyverse)
-source("../Scripts/Scripts_Alfonso/add_study_id.R")
-d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models_NOSING/Motifs_frequency_percentile_NOSING.csv")
-d <- add_study_id(d)
-#str(d)
-#head(d)
-
-#ggplot(d %>% filter(motif != 1), aes(percentil_sizeclass))+
-#  geom_histogram(color="black", fill="white")+
-#  facet_wrap(~motif)+
-#  theme_bw()+
-#  labs(x="Sizeclass percentile")
-#
-# Motifs tend to be over- and under-represensented in real networks
-
-# Mean percentile and SE taking into account the study system
-motif_codes <- d %>% filter(motif != 1) %>% # We remove links (motif code: 1)
-  select(motif) %>% unique() %>% pull()
-motif_means <- tibble(motif = motif_codes)
-motif_means$mean <- NA
-motif_means$SE <- NA
-
-for(i.motif in 1:length(motif_codes)){
-
-  m <- lmer(percentil_sizeclass ~ 1+(1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = subset(d, motif == motif_codes[i.motif]))
-
-  motif_means$mean[i.motif] <- fixed.effects(m) %>% unname()
-  motif_means$SE[i.motif] <- sqrt(diag(vcov(m)))
-
-}
-
-#Add categories based on path length set by Simmons 2021 et al., Functional Ecology
-d$Broad_categories[d$motif==2 | d$motif==7 | d$motif==17 | d$motif==3|d$motif==4|d$motif==8] <- "Fan"
-
-d$Broad_categories[d$motif==15 | d$motif==11] <- "Medium-weak"
-
-d$Broad_categories[d$motif==6 | d$motif==16 |  d$motif==12] <- "Strong"
-
-d$Broad_categories[d$motif==5 | d$motif==9 |  d$motif==14|  d$motif==13|  d$motif==10] <- "Weak"
-
-#order the categories from short to long path length
-d$Broad_categories <- factor(d$Broad_categories, levels = c("Strong", "Fan", "Medium-weak", "Weak"))
-
-#Ffilter out two node motifs
-d_1 <- d %>% filter(motif != 1)
-#Merge dataframes to bl able to create facets
-d_2 <- merge(d_1, motif_means, by="motif")
-
-arr <- list('Strong' = expression(bold(paste("Complete (strong, ", bar(x), " = 1.38)"))),
-             'Fan' = expression(bold(paste("Fan (medium-strong, ", bar(x), " = 1.48)"))), 
-             'Medium-weak' = expression(bold(paste("Asymmetric complete (medium-weak, ", bar(x), " = 1.60)"))), 
-             "Weak" =expression(bold(paste("Core-peripheral (weak, ", bar(x), " = 1.85)"))))
-mylabel <- function(val) { return(lapply(val, function(x) arr[x])) }
-
-library(ggforce) #workaround with ggforce to have facets with same sizes
-
-p <- ggplot()+geom_point(data = d_2, aes(y=factor(motif), 100*percentil_sizeclass), shape=21,color="black",fill="azure2",size=1.75, alpha=0.3)+
-  geom_errorbar(data = d_2,aes(y = factor(motif), xmin=100*(mean-SE), xmax=100*(mean+SE)), 
-                width=0.8,size=0.8,color="black") +theme_bw()+
-  geom_point(data = d_2,aes(y = as.factor(motif), x=100*mean), 
-             size=2,color="black")+labs(y="Two to five node motifs", x = "Percentile")+
-  theme( strip.background = element_blank())+
-  theme(strip.text = element_text(face="bold", size=10, hjust=0),
-        panel.border=element_rect(color="black",size=1.2))
-
-p + ggforce::facet_col(vars(Broad_categories), scales = 'free', space = 'free',labeller=mylabel)
-
-#Trying to maintain a gradient from low to high in colors
-
-#Fig 1 Should be a dot plot (or forest plot) of the mean +- SE of the 15 motifs.
-#NICE! Can we put motifs in Y axes, and % in X?
-```
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="\\textbf{Figure S2.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions after removing non-robust links (singletones).
-The different motif positions are dividied by the average path length clasification by Simmons et al.
-(2020).
-The superior dendrogram indicates the differences across groups with the more separated groups showing larger differences."}
-
-library(lme4)
-library(nlme)
-library(tidyverse)
-library(stringi)
-source("../Scripts/Scripts_Alfonso/add_study_id.R")
-
-#############################################
-# EXTRACT MEAN VALUES
-#############################################
-
-all_position_percentiles <- read_csv("../Data/Csv/Motifs_positions_and_null_models_NOSING/GF_positions_frequency_percentile_NOSING.csv")
-
-all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
-                                                              "[0-9]+") %>% as.numeric()
-
-all_position_percentiles <- add_study_id(all_position_percentiles)
-#str(all_position_percentiles)
-#head(all_position_percentiles)
-
-list_plants_FG <- as.character(1:10)
-
-plant_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF)) #ME DA ERROR
-pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF))
-
-# Plants-------------
-
-# Mean percentile and SE taking into account the study system
-plant_codes <- plant_position_percentiles_filtered$position %>% unique()
-plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-plant_means$mean <- NA
-plant_means$SE <- NA
-
-for(i.pos in 1:length(plant_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
-            data = plant_position_percentiles_filtered %>%
-              filter(position == plant_codes[i.pos]))
-
-  temp <- fixed.effects(m) %>% unname()
-  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
-                                                                    temp[1]+temp[2],
-                                                                    temp[1]+temp[3],
-                                                                    temp[1]+temp[4],
-                                                                    temp[1]+temp[5]) ## to get real means per FG
-  temp <- sqrt(diag(vcov(m)))
-  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
-                                                                  temp[1]+temp[2],
-                                                                  temp[1]+temp[3],
-                                                                  temp[1]+temp[4],
-                                                                  temp[1]+temp[5])
-
-}
-
-# Pollinators--------
-
-# Mean percentile and SE taking into account the study system
-pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
-pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-pollinator_means$mean <- NA
-pollinator_means$SE <- NA
-pollinator_means_reordered <- NULL
-
-for(i.pos in 1:length(pollinator_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = pollinator_position_percentiles_filtered %>%
-              filter(position == pollinator_codes[i.pos]),
-            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
-
-  temp <- fixed.effects(m) %>% unname()
-  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)
-
-  pollinator_means_aux$mean <- c(temp[1],
-                                 temp[1]+temp[2],
-                                 temp[1]+temp[3],
-                                 temp[1]+temp[4],
-                                 temp[1]+temp[5],
-                                 temp[1]+temp[6],
-                                 temp[1]+temp[7],
-                                 temp[1]+temp[8],
-                                 temp[1]+temp[9]) ## to get real means per FG
-
-  temp <- sqrt(diag(vcov(m)))
-  pollinator_means_aux$SE <- c(temp[1],
-                               temp[1]+temp[2],
-                               temp[1]+temp[3],
-                               temp[1]+temp[4],
-                               temp[1]+temp[5],
-                               temp[1]+temp[6],
-                               temp[1]+temp[7],
-                               temp[1]+temp[8],
-                               temp[1]+temp[9])
-
-  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)
-
-}
-
-# There are lower limits (mean - SE) smaller than 0 (see Other insects)
-# We set the lower limit of those error bars to zero
-
-pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
-pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
-
-#############################################
-# ADDING BROAD MOTIF CATEGORIES TO POSITIONS
-#############################################
-
-motifs_raw_data <- read_csv("../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-motifs_raw_data$Broad_categories <- NA
-
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(5,9,14,13,10)] <- "Core-peripherical"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(6,16,12)] <- "Complete"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(2,3,7,4,17,8)] <- "Fan"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(15,11)] <- "Asymmetric complete"
-
-motifs_raw_data$plant <- gsub("[^0-9.-]", "", motifs_raw_data$plant)
-motifs_raw_data$pollinator <- gsub("[^0-9.-]", "", motifs_raw_data$pollinator)
-motifs_raw_data$plant <- as.numeric(motifs_raw_data$plant)
-motifs_raw_data$pollinator <- as.numeric(motifs_raw_data$pollinator)
-motifs_raw_data <- motifs_raw_data %>% filter(!is.na(Broad_categories))
-
-fan_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-pollinator_means_reordered$Broad_categories <- NA
-
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% fan_pollinator] <- "Fan" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% asymm_pollinator] <- "Medium-weak" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% complete_pollinator] <- "Strong" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% core_per_pollinator] <- "Weak"
-
-fan_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-plant_means$Broad_categories <- NA
-
-plant_means$Broad_categories[plant_means$position %in% fan_plant] <- "Fan" 
-plant_means$Broad_categories[plant_means$position %in% asymm_plant] <- "Medium-weak" 
-plant_means$Broad_categories[plant_means$position %in% complete_plant] <- "Strong" 
-plant_means$Broad_categories[plant_means$position %in% core_per_plant] <- "Weak"
-
-########################################
-# CREATE HEATMAPS
-########################################
-
-library(ComplexHeatmap)
-
-# PLANTS-----
-
-# Prepare data for heatmap
-heat_plants_aux <- plant_means %>% spread(Node_FG,mean) %>% select(-SE)
-
-heat_plants <- heat_plants_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-heat_plants_fan <- heat_plants %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_fan) <- heat_plants_fan[,1]
-
-heat_plants_Weak <- heat_plants %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Weak) <- heat_plants_Weak[,1]
-
-heat_plants_Strong <- heat_plants %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Strong) <- heat_plants_Strong[,1]
-
-heat_plants_Medium_weak <- heat_plants %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Medium_weak) <- heat_plants_Medium_weak[,1]
-
-# POLLINATORS-----------
-
-filter_rare_groups <- T
-
-if(filter_rare_groups == T){
-  heat_pollinators_aux <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds",
-                                                                                "Lizards",
-                                                                                "Other_insects")) %>% 
-    spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees",            
-                                      "Coleoptera","Lepidoptera","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Syrphids")
-}else{
-  heat_pollinators_aux <- pollinator_means_reordered %>% spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees","Birds",            
-                                      "Coleoptera","Lepidoptera","Lizards","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Other insects","Syrphids")
-}
-
-heat_pollinators <- heat_pollinators_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-heat_pollinators_fan <- heat_pollinators %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_fan) <- heat_pollinators_fan[,1]
-
-heat_pollinators_Weak <- heat_pollinators %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Weak) <- heat_pollinators_Weak[,1]
-
-heat_pollinators_Strong <- heat_pollinators %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Strong) <- heat_pollinators_Strong[,1]
-
-heat_pollinators_Medium_weak <- heat_pollinators %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Medium_weak) <- heat_pollinators_Medium_weak[,1]
-
-##################
-
-#Do not know how to handle this multiplot for creating a panel
-
-# I'm going to create the 4 plots in one, 
-# I'm not sure that the grouping of the functional group is correct
-# when is done separately
-
-#sorry for the mess of libraries that I do below
-
- #Prepare first pollinators
-
-library(tidyr)
-library(data.table)
-long <- melt(setDT(heat_pollinators), id.vars = c("position","Broad_categories"), variable.name = "guilds")
-
-long_1 <- long %>% select(-Broad_categories)
-
-library(reshape2)
-long_m <- acast(long_1, position~guilds, value.var="value")
-
-#set manually the divisions, so far this is the best way I have seen to split the rows by categories
-
-r_split <- c(rep(c("Fan"), 3),rep(c("Core-peripheral"), 2),"Complete",rep(c("Fan"),2),rep(c("Core-peripheral"), 4),
-             rep(c("Asymmetric complete"), 2), "Complete", rep(c("Core-peripheral"), 3),rep(c("Asymmetric complete"), 2),
-             "Complete", "Fan")
-
-#set order of labels that avoids overlapping
-r_split <- factor(r_split, levels=c("Core-peripheral","Complete","Fan","Asymmetric complete"))
-
-#plat a bit with colors, a bit of a more complex set but looks nicer
-library(circlize)
-col_fun = colorRamp2(c(0.05644663,0.25, 0.4673256,0.75, 0.8782047), c("blue","cadetblue3", "azure2", "gold","red"))
-
-h_pol <- Heatmap(long_m, name = "Mean\npercentile", row_split=r_split,cluster_row_slices = FALSE, 
-                 column_title = "Pollinator functional groups",row_names_gp = gpar(fontsize = 10),
-                 col = col_fun,column_names_rot = 45,  column_names_gp = grid::gpar(fontsize = 10),
-                 column_title_gp = gpar(fontsize = 15, fontface = "bold"),
-                 row_title_gp = gpar(fontsize = 10, fontface = "bold"))
-
- #Prepare plants
-
-#long format
-long_plants <- melt(setDT(heat_plants), id.vars = c("position","Broad_categories"), variable.name = "Functional_groups")
-
-#filter for creating matrix
-long_plants_1 <- long_plants %>% select(-Broad_categories)
-
-#set better colnames
-long_plants_1$Functional_groups <- as.character(long_plants_1$Functional_groups)
-
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==1] <- "Selfing herbs" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==2] <- "Small outcrossing\nperennials" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==3] <- "Self-incomp. perennials\nwith large flowers" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==4] <- "Tall plants with small\nunisexual flowers" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==5] <- "Short-lived outcrossers with\nlong zygomorphic flowers"
-
-long_plants_1$Functional_groups <- factor(long_plants_1$Functional_groups, levels=c("Selfing herbs",
-"Small outcrossing\nperennials" ,"Self-incomp. perennials\nwith large flowers",
-"Tall plants with small\nunisexual flowers" ,"Short-lived outcrossers with\nlong zygomorphic flowers" ))
-
-#create matrix with reshape
-long_plants_m <- acast(long_plants_1, position~Functional_groups, value.var="value")
-
-r_split_plants <- c(rep(c("Fan"), 3),rep(c("Core-peripheral"), 2),"Complete",rep(c("Fan"),2),rep(c("Core-peripheral"), 3),
-                    rep(c("Asymmetric complete"), 2), "Complete", rep(c("Core-peripheral"), 4),rep(c("Asymmetric complete"), 2),
-                    "Complete", "Fan")
-
-r_split_plants <- factor(r_split, levels=c("Core-peripheral","Complete","Fan","Asymmetric complete"))
-
-h_plan <- Heatmap(long_plants_m, name = "Mean\npercentile", row_split=r_split_plants,cluster_row_slices = F, 
-                  column_title = "Plant functional groups",row_names_gp = gpar(fontsize = 10),col = col_fun,column_names_rot = 45,  
-                  column_names_gp = grid::gpar(fontsize = 10),column_title_gp = gpar(fontsize = 15, fontface = "bold"),
-                  row_title_gp = gpar(fontsize = 10, fontface = "bold"))
-
-library(patchwork)
-ht_list <- h_pol+h_plan
-
-draw(ht_list, auto_adjust = FALSE, cluster_rows = F)
-
-```
-
-\newpage
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=7, fig.width=12, fig.cap="**Figure S3.** Plant functional group composition separated in qualitative and quantitative variables.
-Panel A) shows the percentage of the different categories within trait represented with different colours for each functional group.
-Plot B) shows the radar plot of the different quantitative variables standardize on the same scale also coloured with the same patterns of colours as qualitative variables per cluster or functional group.
-Group 1 corresponds to short-lived selfers; group 2 to small outcrossing perennials; group 3 to self-incompatible perennials with large flowers; group 4 to tall plants with small unisexual flowers; and, group 5 to short-lived outcrossers with long zygomorphic flowers."}
-
-#CODE TO PLOT FUNCTIONAL GROUPS
-#IT CAN BE PLOT WITH MUCH LESS CODE BUT NO TIME FOR CLEANING IT
-
-##########################################
-#Visualization of plant functional groups#
-##########################################
-
-library(cowplot)
-library(ggplot2)
-library(tidyr)
-library(dplyr)
-library(reshape2)
-library(data.table)
-library(patchwork)
-
-#LOAD DATA
-#read unscaled trait data in order to visualize better the clusters
-d <- read.csv("../Data/Csv/all_species_imputed_trait_data_forest_data.csv")
-
-dat_1 <- read.csv("../Data/Csv/imputed_trait_data_hclust_5_clusters_forest_data.csv", row.names = "X")
-
-d$Clusters <- dat_1$Clusters
-
-#select columns of interest
-t <- d[c("Breeding_system","IMPUTED_Compatibility","Autonomous_selfing_level",
-         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Flowers_per_inflorescence",
-         "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean", "STYLE_IMPUTED", "OVULES_IMPUTED", "life_form", "lifespan",
-         "IMPUTED_plant_height_mean_m", "Nectar_presence_absence", "Clusters")]
-
-##############################################################################################################################
-#Prepare table qualitative variables
-##############################################################################################################################
-
-##############################################################################################################################
-#Breeding system
-t$Breeding_system <- factor(t$Breeding_system, levels=c("Dioecious", "Monoecious", "Hermaphrodite"))
-
-#Summary to create table
-breeding <- t %>%
-  group_by(Clusters,Breeding_system) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-breeding <- breeding[,-3]
-
-breeding <- spread(breeding, Clusters, Percentage)
-
-colnames(breeding)[1] <- "Category"
-
-Trait <- data.frame(Trait= c(rep("Breeding system", 3)))
-
-Breeding_system <- cbind(Trait, breeding)
-
-##############################################################################################################################
-#Compatibility
-str(t)
-t$IMPUTED_Compatibility <- as.character(t$IMPUTED_Compatibility)
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="dioecious"] <- "Unisexual flower"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="monoecious"] <- "Unisexual flower"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_incompatible"] <- "Self incompatible"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="partially_self_compatible"] <- "Partially self compatible"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_compatible"] <- "Self compatible"
-
-t$IMPUTED_Compatibility <- factor(t$IMPUTED_Compatibility, levels=c("Unisexual flower", "Self incompatible", "Partially self compatible", "Self compatible"))
-#Summary to create table
-comp <- t %>%
-  group_by(Clusters,IMPUTED_Compatibility) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-comp <- comp[,-3]
-
-comp <- spread(comp, Clusters, Percentage)
-#Replace Na's with zeros
-comp[is.na(comp)] <- 0
-#Set call name os categories per trait
-colnames(comp)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Compatibility system", 4)))
-#Add column
-Compatibility_system <- cbind(Trait, comp)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system)
-
-############################################################################################################################################
-#Life form
-t$life_form <- as.character(t$life_form)
-t$life_form[t$life_form =="vine"] <- "Shrub"
-t$life_form[t$life_form =="tree"] <- "Tree"
-t$life_form[t$life_form =="herb"] <- "Herb"
-t$life_form[t$life_form =="shrub"] <- "Shrub"
-#Order levels
-t$life_form <- factor(t$life_form, levels=c("Tree", "Shrub", "Herb"))
-#Summary to create table
-life_form <- t %>%
-  group_by(Clusters,life_form) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-life_form <- life_form[,-3]
-#convert to wide
-life_form <- spread(life_form, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(life_form)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Life form", 3)))
-#Add column
-Life_form<- cbind(Trait, life_form)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form)
-
-############################################################################################################################################
-t$lifespan <- factor(t$lifespan, levels=c("Perennial","Short lived"))
-#Summary to create table
-life_span <- t %>%
-  group_by(Clusters,lifespan) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-life_span <- life_span[,-3]
-#convert to wide
-life_span <- spread(life_span, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(life_span)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Life span", 2)))
-#Add column
-Life_span<- cbind(Trait, life_span)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span)
-
-############################################################################################################################################
-t$Flower_morphology <- as.character(t$Flower_morphology)
-t$Flower_morphology[t$Flower_morphology=="Funnelform"] <- "Campanulate"
-t$Flower_morphology[t$Flower_morphology=="Spike"] <- "Brush"
-
-Flower_morphology <- t %>%
-  group_by(Clusters,Flower_morphology) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-Flower_morphology <- Flower_morphology[,-3]
-#convert to wide
-Flower_morphology <- spread(Flower_morphology, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(Flower_morphology)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Flower shape", 6)))
-#Add column
-Flower_morphology<- cbind(Trait, Flower_morphology)
-#Replace Na's with zeros
-Flower_morphology[is.na(Flower_morphology)] <- 0
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology)
-
-############################################################################################################################################
-t$Flower_symmetry <- as.character(t$Flower_symmetry)
-t$Flower_symmetry[t$Flower_symmetry =="actinomorphic"] <- "Actinomorphic"
-t$Flower_symmetry[t$Flower_symmetry =="zygomorphic"] <- "Zygomorphic"
-
-Flower_symmetry <- t %>%
-  group_by(Clusters,Flower_symmetry) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-Flower_symmetry <- Flower_symmetry[,-3]
-#convert to wide
-Flower_symmetry <- spread(Flower_symmetry, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(Flower_symmetry)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Flower symmetry", 2)))
-#Add column
-Flower_symmetry<- cbind(Trait, Flower_symmetry)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology,Flower_symmetry)
-############################################################################################################################################
-t$Autonomous_selfing_level <- as.character(t$Autonomous_selfing_level)
-t$Autonomous_selfing_level[t$Autonomous_selfing_level =="none"] <- "None"
-t$Autonomous_selfing_level[t$Autonomous_selfing_level =="low"] <- "Low"
-t$Autonomous_selfing_level[t$Autonomous_selfing_level =="medium"] <- "Medium"
-t$Autonomous_selfing_level[t$Autonomous_selfing_level =="high"] <- "High"
-
-#Order levels
-t$Autonomous_selfing_level <- factor(t$Autonomous_selfing_level, levels=c("High", "Medium", "Low", "None"))
-
-Selfing <- t %>%
-  group_by(Clusters,Autonomous_selfing_level) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-#delete column to convert to wide
-Selfing <- Selfing[,-3]
-#convert to wide
-Selfing <- spread(Selfing, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(Selfing)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Selfing level", 2)))
-#Replace Na's with zeros
-Selfing[is.na(Selfing)] <- 0
-#Add column
-Selfing_1 <- cbind(Trait, Selfing)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology, Selfing_1)
-
-############################################################################################################################################
-t$Nectar_presence_absence <- as.character(t$Nectar_presence_absence)
-t$Nectar_presence_absence[t$Nectar_presence_absence =="yes"] <- "Yes"
-t$Nectar_presence_absence[t$Nectar_presence_absence =="no"] <- "No"
-
-Nectar <- t %>%
-  group_by(Clusters,Nectar_presence_absence) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-#delete column to convert to wide
-Nectar <- Nectar[,-3]
-#convert to wide
-Nectar <- spread(Nectar, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(Nectar)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Nectar", 2)))
-#Replace Na's with zeros
-Nectar[is.na(Nectar)] <- 0
-#Add column
-Nectar <- cbind(Trait, Nectar)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology, Flower_symmetry,Selfing_1, Nectar)
-
-##############################################################################################################################
-#Prepare table quantitative variables
-##############################################################################################################################
-
-Selfing <-  t %>% group_by(Clusters)%>% 
-  select(Autonomous_selfing_level_fruit_set) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                     # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                    sd = sd))
-
-s1 <- as.data.frame(t(Selfing))
-#set colnames
-colnames(s1) <- c("1","2","3","4","5")
-#remove the cluster row
-s1 <- s1[-1,]
-#convert rownames to 1st columns
-s1 <- setDT(s1, keep.rownames = "TRUE")[]
-colnames(s1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Autonomous selfing", 5)))
-#Add column
-Selfing <- cbind(Trait, s1)
-
-##############################################################################################################################
-flower_number <-  t %>% group_by(Clusters)%>% 
-  select(Flowers_per_plant) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-f1 <- as.data.frame(t(flower_number))
-#set colnames
-colnames(f1) <- c("1","2","3","4","5")
-#remove the cluster row
-f1 <- f1[-1,]
-#convert rownames to 1st columns
-f1 <- setDT(f1, keep.rownames = "TRUE")[]
-colnames(f1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Flower number", 5)))
-#Add column
-Flower_number <- cbind(Trait, f1)
-
-##############################################################################################################################
-Flowers_per_inflorescence <-  t %>% group_by(Clusters)%>% 
-  select(Flowers_per_inflorescence) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-f_i_1 <- as.data.frame(t(Flowers_per_inflorescence))
-#set colnames
-colnames(f_i_1) <- c("1","2","3","4","5")
-#remove the cluster row
-f_i_1 <- f_i_1[-1,]
-#convert rownames to 1st columns
-f_i_1 <- setDT(f_i_1, keep.rownames = "TRUE")[]
-colnames(f_i_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Flowers per inflorescence", 5)))
-#Add column
-Flower_per_inflo <- cbind(Trait, f_i_1)
-
-bind_rows(Selfing, Flower_number, Flower_per_inflo)
-
-##############################################################################################################################
-Floral_unit_width <-  t %>% group_by(Clusters)%>% 
-  select(Floral_unit_width) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-f_u_w_1 <- as.data.frame(t(Floral_unit_width))
-#set colnames
-colnames(f_u_w_1) <- c("1","2","3","4","5")
-#remove the cluster row
-f_u_w_1 <- f_u_w_1[-1,]
-#convert rownames to 1st columns
-f_u_w_1 <- setDT(f_u_w_1, keep.rownames = "TRUE")[]
-colnames(f_u_w_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Inflorescence width", 5)))
-#Add column
-Inflo_width <- cbind(Trait, f_u_w_1)
-
-bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width)
-
-##############################################################################################################################
-Corolla_diameter_mean <-  t %>% group_by(Clusters)%>% 
-  select(Corolla_diameter_mean) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-c_w_1 <- as.data.frame(t(Corolla_diameter_mean))
-#set colnames
-colnames(c_w_1) <- c("1","2","3","4","5")
-#remove the cluster row
-c_w_1 <- c_w_1[-1,]
-#convert rownames to 1st columns
-c_w_1 <- setDT(c_w_1, keep.rownames = "TRUE")[]
-colnames(c_w_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Flower width", 5)))
-#Add column
-Flower_width <- cbind(Trait, c_w_1)
-
-bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width)
-
-##############################################################################################################################
-Corolla_length_mean <-  t %>% group_by(Clusters)%>% 
-  select(Corolla_length_mean) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-c_l_1 <- as.data.frame(t(Corolla_length_mean))
-#set colnames
-colnames(c_l_1) <- c("1","2","3","4","5")
-#remove the cluster row
-c_l_1 <- c_l_1[-1,]
-#convert rownames to 1st columns
-c_l_1 <- setDT(c_l_1, keep.rownames = "TRUE")[]
-colnames(c_l_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Flower length", 5)))
-#Add column
-Flower_length<- cbind(Trait, c_l_1)
-
-bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length)
-
-##############################################################################################################################
-STYLE_IMPUTED <-  t %>% group_by(Clusters)%>% 
-  select(STYLE_IMPUTED) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-s_l_1 <- as.data.frame(t(STYLE_IMPUTED))
-#set colnames
-colnames(s_l_1) <- c("1","2","3","4","5")
-#remove the cluster row
-s_l_1 <- s_l_1[-1,]
-#convert rownames to 1st columns
-s_l_1 <- setDT(s_l_1, keep.rownames = "TRUE")[]
-colnames(s_l_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Style length", 5)))
-#Add column
-Style_length<- cbind(Trait, s_l_1)
-
-bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length, Style_length)
-
-##############################################################################################################################
-
-OVULES_IMPUTED <-  t %>% group_by(Clusters)%>% 
-  select(OVULES_IMPUTED) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-o_n_1 <- as.data.frame(t(OVULES_IMPUTED))
-#set colnames
-colnames(o_n_1) <- c("1","2","3","4","5")
-#remove the cluster row
-o_n_1 <- o_n_1[-1,]
-#convert rownames to 1st columns
-o_n_1 <- setDT(o_n_1, keep.rownames = "TRUE")[]
-colnames(o_n_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Ovule number", 5)))
-#Add column
-Ovule_number <- cbind(Trait, o_n_1)
-
-bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length, Ovule_number)
-
-##############################################################################################################################
-
-IMPUTED_plant_height_mean_m <-  t %>% group_by(Clusters)%>% 
-  select(IMPUTED_plant_height_mean_m) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-p_h_1 <- as.data.frame(t(IMPUTED_plant_height_mean_m))
-#set colnames
-colnames(p_h_1) <- c("1","2","3","4","5")
-#remove the cluster row
-p_h_1 <- p_h_1[-1,]
-#convert rownames to 1st columns
-p_h_1 <- setDT(p_h_1, keep.rownames = "TRUE")[]
-colnames(p_h_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Plant height", 5)))
-#Add column
-Plant_height <- cbind(Trait, p_h_1)
-
-#Bind quantitative and qualitative variables
-Table_all_traits <- bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology, Flower_symmetry,Selfing_1, Nectar,
-          Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length, Style_length, Ovule_number, Plant_height)
-
-#Select just two decimals
-is.num <- sapply(Table_all_traits, is.numeric)
-Table_all_traits[is.num] <- lapply(Table_all_traits[is.num], round, 2)
-
-colnames(Table_all_traits) <- c("Trait", "Category", "Cluster 1", "Cluster 2", "Cluster 3", "Cluster 4", "Cluster 5")
-
-#LOAD LIBRARIES
-#devtools::install_github("ricardo-bion/ggradar", dependencies=TRUE)
-suppressPackageStartupMessages(library(dplyr))
-library(scales)
-library(tibble)
-library(ggradar)
-library(janitor)
-library(grid)
-library(dplyr)
-library(lubridate)
-#QUANTITATIVVE VARIABLES
-
-#generate subset of quantitative variables for plotting
-quant_median <- subset(Table_all_traits, Category=="median")
-
-#delete col number 2
-quant_median <- quant_median[,-2]
-
-#transpose dataframe
-final_df <- as.data.frame(t(quant_median))
-
-#rownames to colnames (1st one)
-final_df_1 <- final_df %>% row_to_names(row_number = 1)
-
-#Convert all variables to numeric
-final_df_2 <- sapply(final_df_1, function(x) as.numeric(as.character(x)))
-
-#set back the missed rownames in the processing
-rownames(final_df_2) <- rownames(final_df_1)
-
-# Convert to dataframe
-final_df_2 <- as.data.frame(final_df_2)
-
-# Scale values and set rowname as column
-final_df_3 <-final_df_2 %>% rownames_to_column( var = "group" ) %>%   mutate_at(vars(-group),funs(rescale))
-
-#Plot Radar
-#ggradar(final_df_3)
-
-#QUALITATIVE VARIABLES
-
-#LOAD DATA
-#read unscaled trait data in order to visualize better the clusters
-d <- read.csv("../Data/Csv/all_species_imputed_trait_data_forest_data.csv")
-
-dat_1 <- read.csv("../Data/Csv/imputed_trait_data_hclust_5_clusters_forest_data.csv", row.names = "X")
-
-d$Clusters <- dat_1$Clusters
-
-#select columns of interest
-t <- d[c("Breeding_system","IMPUTED_Compatibility","Autonomous_selfing_level",
-         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Flowers_per_inflorescence",
-         "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean", "STYLE_IMPUTED", "OVULES_IMPUTED", "life_form", "lifespan",
-         "IMPUTED_plant_height_mean_m", "Nectar_presence_absence", "Clusters")]
-
-##############################################################################################################################
-#Prepare table qualitative variables
-##############################################################################################################################
-
-##############################################################################################################################
-#Breeding system
-t$Breeding_system <- factor(t$Breeding_system, levels=c("Dioecious", "Monoecious", "Hermaphrodite"))
-
-#Summary to create table
-breeding <- t %>%
-  group_by(Clusters,Breeding_system) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-breeding <- breeding[,-3]
-
-breeding <- spread(breeding, Clusters, Percentage)
-
-colnames(breeding)[1] <- "Category"
-
-Trait <- data.frame(Trait= c(rep("Breeding system", 3)))
-
-Breeding_system <- cbind(Trait, breeding)
-
-##############################################################################################################################
-#Compatibility
-str(t)
-t$IMPUTED_Compatibility <- as.character(t$IMPUTED_Compatibility)
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="dioecious"] <- "Self incompatible"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="monoecious"] <- "Self incompatible"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_incompatible"] <- "Self incompatible"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="partially_self_compatible"] <- "Partially self compatible"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_compatible"] <- "Self compatible"
-
-t$IMPUTED_Compatibility <- factor(t$IMPUTED_Compatibility, levels=c("Self incompatible", "Partially self compatible", "Self compatible"))
-#Summary to create table
-comp <- t %>%
-  group_by(Clusters,IMPUTED_Compatibility) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-comp <- comp[,-3]
-
-comp <- spread(comp, Clusters, Percentage)
-#Replace Na's with zeros
-comp[is.na(comp)] <- 0
-#Set call name os categories per trait
-colnames(comp)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Compatibility system", 3)))
-#Add column
-Compatibility_system <- cbind(Trait, comp)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system)
-
-############################################################################################################################################
-#Life form
-t$life_form <- as.character(t$life_form)
-t$life_form[t$life_form =="vine"] <- "Shrub"
-t$life_form[t$life_form =="tree"] <- "Tree"
-t$life_form[t$life_form =="herb"] <- "Herb"
-t$life_form[t$life_form =="shrub"] <- "Shrub"
-#Order levels
-t$life_form <- factor(t$life_form, levels=c("Tree", "Shrub", "Herb"))
-#Summary to create table
-life_form <- t %>%
-  group_by(Clusters,life_form) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-life_form <- life_form[,-3]
-#convert to wide
-life_form <- spread(life_form, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(life_form)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Life form", 3)))
-#Add column
-Life_form<- cbind(Trait, life_form)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form)
-
-############################################################################################################################################
-t$lifespan <- factor(t$lifespan, levels=c("Perennial","Short lived"))
-#Summary to create table
-life_span <- t %>%
-  group_by(Clusters,lifespan) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-life_span <- life_span[,-3]
-#convert to wide
-life_span <- spread(life_span, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(life_span)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Life span", 2)))
-#Add column
-Life_span<- cbind(Trait, life_span)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span)
-
-############################################################################################################################################
-#t$Flower_morphology <- as.character(t$Flower_morphology)
-#t$Flower_morphology[t$Flower_morphology=="Funnelform"] <- "Campanulate"
-#t$Flower_morphology[t$Flower_morphology=="Spike"] <- "Brush"
-#
-#Flower_morphology <- t %>%
-#  group_by(Clusters,Flower_morphology) %>%
-#  summarise (n = n()) %>%
-#  mutate(Percentage = n / sum(n)*100)
-##delete column to convert to wide
-#Flower_morphology <- Flower_morphology[,-3]
-##convert to wide
-#Flower_morphology <- spread(Flower_morphology, Clusters, Percentage)
-##Set call name os categories per trait
-#colnames(Flower_morphology)[1] <- "Category"
-##Create new column
-#Trait <- data.frame(Trait= c(rep("Flower shape", 6)))
-##Add column
-#Flower_morphology<- cbind(Trait, Flower_morphology)
-##Replace Na's with zeros
-#Flower_morphology[is.na(Flower_morphology)] <- 0
-##Bind rows
-#bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology)
-#
-############################################################################################################################################
-t$Flower_symmetry <- as.character(t$Flower_symmetry)
-t$Flower_symmetry[t$Flower_symmetry =="actinomorphic"] <- "Actinomorphic"
-t$Flower_symmetry[t$Flower_symmetry =="zygomorphic"] <- "Zygomorphic"
-
-Flower_symmetry <- t %>%
-  group_by(Clusters,Flower_symmetry) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-Flower_symmetry <- Flower_symmetry[,-3]
-#convert to wide
-Flower_symmetry <- spread(Flower_symmetry, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(Flower_symmetry)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Flower symmetry", 2)))
-#Add column
-Flower_symmetry<- cbind(Trait, Flower_symmetry)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology,Flower_symmetry)
-############################################################################################################################################
-#t$Autonomous_selfing_level <- as.character(t$Autonomous_selfing_level)
-#t$Autonomous_selfing_level[t$Autonomous_selfing_level =="none"] <- "None"
-#t$Autonomous_selfing_level[t$Autonomous_selfing_level =="low"] <- "Low"
-#t$Autonomous_selfing_level[t$Autonomous_selfing_level =="medium"] <- "Medium"
-#t$Autonomous_selfing_level[t$Autonomous_selfing_level =="high"] <- "High"
-#
-##Order levels
-#t$Autonomous_selfing_level <- factor(t$Autonomous_selfing_level, levels=c("High", "Medium", "Low", "None"))
-#
-#Selfing <- t %>%
-#  group_by(Clusters,Autonomous_selfing_level) %>%
-#  summarise (n = n()) %>%
-#  mutate(Percentage = n / sum(n)*100)
-#
-##delete column to convert to wide
-#Selfing <- Selfing[,-3]
-##convert to wide
-#Selfing <- spread(Selfing, Clusters, Percentage)
-##Set call name os categories per trait
-#colnames(Selfing)[1] <- "Category"
-##Create new column
-#Trait <- data.frame(Trait= c(rep("Selfing level", 2)))
-##Replace Na's with zeros
-#Selfing[is.na(Selfing)] <- 0
-##Add column
-#Selfing_1 <- cbind(Trait, Selfing)
-##Bind rows
-#bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology, Selfing_1)
-#
-#############################################################################################################################################
-t$Nectar_presence_absence <- as.character(t$Nectar_presence_absence)
-t$Nectar_presence_absence[t$Nectar_presence_absence =="yes"] <- "Yes"
-t$Nectar_presence_absence[t$Nectar_presence_absence =="no"] <- "No"
-
-Nectar <- t %>%
-  group_by(Clusters,Nectar_presence_absence) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-#delete column to convert to wide
-Nectar <- Nectar[,-3]
-#convert to wide
-Nectar <- spread(Nectar, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(Nectar)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Nectar", 2)))
-#Replace Na's with zeros
-Nectar[is.na(Nectar)] <- 0
-#Add column
-Nectar <- cbind(Trait, Nectar)
-#Bind rows
-data <- bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span, Flower_symmetry, Nectar)
-
-#remove first col
-data_1 <- data[,-1]
-colnames(data_1) <- c("Category", "Cluster 1", "Cluster 2", "Cluster 3", "Cluster 4", "Cluster 5")
-
-#transpose dataframe
-data_2 <- as.data.frame(t(data_1))
-
-#rownames to colnames (1st one)
-data_3 <- data_2 %>% row_to_names(row_number = 1)
-
-#Convert all variables to numeric
-data_4 <- sapply(data_3, function(x) as.numeric(as.character(x)))
-
-#set back the missed rownames in the processing
-rownames(data_4) <- rownames(data_3)
-
-# Convert to dataframe
-data_4 <- as.data.frame(data_4)
-
-# Scale values and set rowname as column
-data_5 <-data_4 %>% rownames_to_column( var = "group" )
-
-data_6 <- melt(data_5)
-
-cluster1 <- subset(data_6, group=="Cluster 1")
-
-cluster1$traits <- c(rep("Breeding sys.",3), rep("Compatibility",3), rep("Life form",3),
-                     rep("Life span",2), rep("F. Symm.",2), rep("Nectar",2))
-
-#Try to achieve the desire output with plot_grid
-
-c1 <- cluster1 %>% 
-  ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("sandybrown"), labels="Group 1")+
-  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())+scale_y_continuous(expand = c(0,0)) +
-  theme(axis.title.x = element_blank(), axis.text.x=element_blank(),plot.title = element_text(size = 18))+ ylab("")+
-  ggtitle("A) Qualitative variables")
-
-cluster2 <- subset(data_6, group=="Cluster 2")
-
-cluster2$traits <- c(rep("Breeding system",3), rep("Compatibility",3), rep("Life form",3),
-                     rep("Life span",2), rep("Flower symmetry",2), rep("Nectar",2))
-
-c2 <- cluster2 %>% 
-  ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("#7BB0A3"), labels="Group 2")+
-  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())+scale_y_continuous(expand = c(0,0)) +
-  theme(strip.background = element_blank(), strip.text = element_blank())+
-  theme(axis.title.x = element_blank(), axis.text.x=element_blank())+ylab("")
-
-cluster3 <- subset(data_6, group=="Cluster 3")
-
-cluster3$traits <- c(rep("Breeding system",3), rep("Compatibility",3), rep("Life form",3),
-                     rep("Life span",2), rep("Flower symmetry",2), rep("Nectar",2))
-
-c3 <- cluster3 %>% 
-  ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("lightsteelblue2"), labels="Group 3")+
-  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())+scale_y_continuous(expand = c(0,0)) +
-  theme(axis.title.x = element_blank(), axis.text.x=element_blank())+
-  theme(strip.background = element_blank(), strip.text = element_blank())+ylab("Percentage")
-
-cluster4 <- subset(data_6, group=="Cluster 4")
-
-cluster4$traits <- c(rep("Breeding system",3), rep("Compatibility",3), rep("Life form",3),
-                     rep("Life span",2), rep("Flower symmetry",2), rep("Nectar",2))
-
-c4 <- cluster4 %>% 
-  ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("thistle"), labels="Group 4")+
-  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())+scale_y_continuous(expand = c(0,0)) +
-  theme(axis.title.x = element_blank(), axis.text.x=element_blank())+
-  theme(strip.background = element_blank(), strip.text = element_blank())+ylab("")
-
-cluster5 <- subset(data_6, group=="Cluster 5")
-
-cluster5$traits <- c(rep("Breeding syst.",3), rep("Compatibility",3), rep("Life form",3),
-                     rep("Life span",2), rep("F. Symm.",2), rep("Nectar",2))
-c5 <- cluster5 %>% 
-  ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("lightgoldenrod2"), labels="Group 5")+
-  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
-  scale_y_continuous(expand = c(0,0)) +
-  theme(axis.text.x = element_text(angle = 45,vjust = 1, hjust=1))+
-  theme(strip.background = element_blank(), strip.text = element_blank())+ylab("")+xlab("")
-
-A <- c1 + c2 + c3 + c4 + c5 + plot_layout(ncol = 1)
-
-colnames(final_df_3) <- c("group","Autonomous selfing", "Flower number", "Flowers per \n inflorescence",
-                "Inflorescence \n width", "Flower length", "Style length", "Ovule number",
-                "Plant height")
-
-B <- ggradar(final_df_3, group.colours=c("sandybrown", "#7BB0A3","lightsteelblue2", "thistle", "lightgoldenrod2"),
-             legend.text.size=5, grid.label.size = 0,legend.position = "none",axis.label.size=3)+ 
-  guides(shape = guide_legend(override.aes = list(size = 0.75)))+ ggtitle("B) Quantitative variables")+
-  theme(plot.title = element_text(size = 18))
-
-patch <- A | B
-
-patch + plot_annotation(title = "Plant functional group composition",theme = theme(plot.title = element_text(size = 20,face="bold")))
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=13, fig.cap="**Figure S4.** Hierarchical clustering dendrogram with the branches coloured by the optimal number of clusters (5).
-The labels of the subgroup of species (N = 524) used in this study are coloured in black in order to show the evenness of the distribution of the species across clusters.
-The rest of species labels are omitted for visualization purposes (N = 982)."}
-
-library(ggplot2)
-library(dendextend)
-library(dplyr)
-
-e.clust_5 <- readRDS("../Data/RData/e.clust_5.rds")
-
-dendro <- as.dendrogram(e.clust_5)
-dendro.col <- dendro %>%
-  set("branches_k_color", k = 5, value =   c("lightsteelblue2", "thistle", "sandybrown", "#7BB0A3", "lightgoldenrod2")) %>%
-  set("branches_lwd", 0.7) %>%
-  set("labels_colors", 
-      value = c("darkslategray")) %>% 
-  set("labels_cex", 0.075)
-
-labels_colors(dendro.col) <- get_leaves_branches_col(dendro.col)
-
-# We use "darkgrey" to color some species
-final_d_1 <- read.csv("../Data/Csv/data_for_motifs_analysis_1.csv")
-
-plant_species <- unique(final_d_1$Plant_species)
-
-index_species_out <- which(names(labels_colors(dendro.col)) %in% plant_species)
-
-'%ni%' <- Negate('%in%')
-
-index_species_in <- which(names(labels_colors(dendro.col)) %ni% plant_species)
-
-labels_colors(dendro.col)[index_species_out] <- "black"
-labels_colors(dendro.col)[index_species_in] <- "white"
-
-ggd1 <- as.ggdend(dendro.col)
-
-ggd1$labels$angle <- 90
-ggd1$labels$vjust <- 1
-ggd1$labels$hjust <- 1
-
-ggplot(ggd1,offset_labels=-0.05) + theme(panel.grid.major = element_blank(),
- axis.text = element_blank(),axis.title = element_blank()) +
-  ggtitle("Plant functional groups")+
-  theme(plot.title = element_text(hjust = 0.5, vjust = -2,size = 20,face="bold"))+
-  annotate("text", x=140, y=1.65, label= "Self-incomp. perennials with large flowers ", size=2.5)+
-  annotate("text", x=380, y=2.15, label= "Tall plants with small unisexual flowers", size=2.5) +
-  annotate("text", x=600, y=3.85, label= "Short-lived selfers", size=2.5) +
-  annotate("text", x=1400, y=2.05, label= "Short-lived outcrossers with \n long zygomorphic flowers", size=2.5) +annotate("text", x=950, y=2.05, label= "Small outcrossing perennials", size=2.5)
-
-```
-
-\elandscape

### 2022-01-03 Manuscript/Supporting_information_Oikos.Rmd
Preparing Oikos submission

--- 2021-10-18 Draft/Draft.Rmd
@@
 ---
-title: The non-random assembly of functional motifs in plant-pollinator networks worldwide
+title: "Supporting Information"
 editor_options:
@@
 always_allow_html: true
-bibliography: bibliography.bib
 ---
 
-__Jose B. Lanuza^1,2^__  | __Alfonso Allen-Perkins^2,3^__ |  __Romina Rader^1^__ | __Ignasi Bartomeus^2^__
-
-1 School of Environmental and Rural Science, University of New England, Armidale, New South Wales 2350, Australia.
-
-2 Estación Biológica de Doñana (EBD-CSIC), E-41092 Seville, Spain.
-
-3 Departamento de Ingeniería Eléctrica, Electrónica, Automática y Física Aplicada, ETSIDI, Universidad Politécnica de Madrid, 28040 Madrid, Spain.
-
 \captionsetup[table]{labelformat=empty}
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
-
-# Abstract
-
-Ecological processes leave distinct structural imprints on species interactions shaping the topology of mutualistic networks.
-Detecting those relationships is not trivial since they go beyond pair-wise interactions, but may get blurred when considering full network descriptors.
-However, recent work has shown the network meso-scale can capture this important information.
-The meso-scale describes network subgraphs representing patterns of interactions between a small number of species (i.e.
-motifs) and those constitute the building blocks of the whole network.
-Here, we have compiled 60 networks from 18 different studies and show that some motifs are consistently under- and over-represented worldwide, suggesting that the building blocks of plant-pollinator networks are not random.
-Furthermore, we found that distinct motif positions describing species ecological roles (e.g., generalization, indirect interactions) are occupied by different functional groups on both trophic levels.
-For instance, bees appear consistently in generalist motif positions and plants with higher levels of outcrossing tend to have a large number of indirect interactions.
-Interestingly, the realized combinations of different functional groups within a motif can not be retrieved from their joint probability distributions, indicating that functional group combinations are not random either.
-Our result highlight the non-random structure of indirect interactions in plant-pollinator networks and opens the door to predict novel interactions beyond pairwise interactions within a community context.
-
-\doublespacing
-
-# INTRODUCTION
-
-Ecological communities are formed by a plethora of interacting species that form networks of interactions.
-Because of the tremendous complexity of these ecological networks, species interactions are generally condensed in metrics that summarize this information [@guimaraes2020].
-Plant-pollinator interactions are no exception, and they are often studied with indices that aggregate the information at the species (micro-scale) or network level (macro-scale).
-For example, plant-pollinator network level approaches have identified common invariant structural properties across networks, including a degree distribution that decays as a power law [@jordano1987], nestedness [@bascompte2003], or modularity [@olesen2007].
-In addition, the local species position within the network can define its degree of specialization [@bluthgen2006] or its role connecting the rest of the community [@olesen2007].
-Despite the unquestionable progress with the use of these metrics at both species and network level, condensing the information into a single metric implies the loss of relevant ecological information that obscure the understanding of the ecological processes [@cirtwill2018; @simmons2019].
-
-Traditionally, plant-pollinator research has focused on direct interactions but overlooked indirect interactions (i.e., the mediated effect between two species by a third species), such as facilitative or competitive interactions between plants for pollinators [@moeller2004; @sargent2008].
-Despite the widespread nature of indirect interactions in ecological communities [@strauss1991], plant-pollinator research often fails to finely capture those indirect interactions with the conventional analytical tools that condense the information either by species (e.g., interaction frequency) or in global topological indices (e.g., nestedness).
-Nonetheless, the emerging framework of network motifs (small sub-networks recorded within a given network) in plant-pollinator research allows to consider both direct and indirect interactions [@simmons2019].
-Motifs are often referred to as the building blocks of a network that depict subsets of interactions [@milo2002].
-The analysis of network motifs in plant-pollinator networks have revealed that the different ecological processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions [@simmons2020].
-Yet, the global patterns of indirect interactions in real plant-pollinator networks are still unknown (e.g., over- and under- represented motifs).
-
-Despite motifs are abstract representations often decoupled from species ecology, linking the structural properties of the meso-scale with the species ecology can help the understanding of ecological processes.
-For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species functional role [@stouffer2012; @baker2015].
-However, it is unclear how the species ecology and life history traits determines the species' functional role within the network of interactions [@coux2016].
-For example, large pollinators can forage larger distances [@greenleaf2007], deposit greater pollen quantities [@foldesi2021] and handle complex zygomorphic flowers in comparison with small pollinators that are restricted to lower floral complexity [@gong2009].
-How this different pollinator behavior translates into their interaction topology is unknown.
-Similarly, recent empirical findings indicate that the meso-scale is the best descriptor of plant reproductive success [@allen2021], but little is known about how plants reproductive strategies shape their position within the network of interactions.
-Although some studies have evaluated plant reproductive strategies in plant-pollinator networks [@tur2013; @lazaro2020], this is an often overlooked aspect in a community context [@devaux2014] and rarely incorporated into plant-pollinator network studies.
-Hence, exploring how the main plant reproductive strategies integrate with the emergent motif framework can shed light on key aspects of ecosystem functioning.
-
-Here, we used 60 plant-pollinator networks from 18 different studies and 14 countries, alongside functional groups of plants and floral visitors based on functional traits and taxonomic rank, respectively.
-To obtain plant functional groups, we used a comprehensive dataset that included floral, reproductive and vegetative traits compiled in a larger set of networks.
-Floral visitor functional groups were divided by the main taxonomic groups that differed in life form and behaviour.
-Once we split the different plant-pollinator networks into their motif elements, we explored: (i) if there is a common invariant structural property in the overall motif networks (i.e.
-over and under-represented motifs); (ii) which functional groups are over and under-represented in the different motif positions; and, (iii) if there are over and under-reprsented functional group combinations within a motif.
-
-# METHODS
-
-**Plant-pollinator studies**
-
-We have compiled 60 plant-pollinator networks from 18 different studies (**Table S1**).
-All studies sampled plant-pollinator interactions in natural systems and were selected based on wide geographical coverage and presence of interaction frequency as a measure of interaction strength.
-In total, there were 503 plant species, 1,111 floral visitors species and 6,248 pairwise interactions registered.
-For ease of data manipulation, plant and floral visitors species names were standardize with the help of the R package _taxize_ version _0.9.99_ [@chamberlain2020].
-All analyses and data manipulation were conducted in R _version 4.0.5_ [@R].
-
-**Plant and floral visitors functional groups**
-
-First, plant species were grouped through hierarchical clustering into the optimal number of functional groups that summarized the main plant reproductive strategies.
-For this, we used the trait dataset collated in Chapter 1 that comprised a total of 1506 species including the 503 species considered in this study (Supplementary material Chapter 1 **Table S1**).
-This dataset consisted on 8 floral, 4 reproductive and 3 vegetative traits excluding traits with high percentage of missing values (over 30$\%$; **Table S2**).
-We opted to calculate the plant functional groups on this larger set of species because of the higher accuracy when delimiting functional groups with that many variables and species [@dolnicar2014].
-To feed the clustering analysis, we calculated the distance between the different qualitative and scaled quantitative variables with Gower distance [@gower1971].
-For this, we used the function _gowdis_ with method _ward.D2_ from the package _FD_ version _1.0-12_ [@laliberte2014].
-Finally, we conducted hierarchical clustering with the function _hclust_ from the _R_ stats package version _4.0.5_ and calculated the optimal number of clusters with the function _kgs_ from the package _maptree_ version _1.4-7_ [@white2009].
-
-Second, floral visitors were grouped into functional groups based on taxonomic rank as done similarly in past plant-pollinator studies [@fenster2004; @ollerton2009].
-We opted to divide floral visitors on the taxonomic rank level and not with functional traits because the main orders of floral visitors differed in form and behaviour and had lower superior taxonomical complexity (i.e., floral visitors had 6 orders versus plants that had 38).
-Thus, this allowed us to group floral visitors into functional groups that represented adequately the main life strategies of the possible pollinators: (i) bees (Hymenoptera-Anthophila), (ii) non-bee Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Syrphidae-Diptera), (iv) non-syrphids-Diptera, (v) Lepidoptera and (vi) Coleoptera.
-However, a minor set of species belonged to other functional groups that were considered in analyses but not discussed further because of their low representation in the full set of networks (3.55$\%$ of the total interactions recorded).
-These functional groups were 'lizards', 'birds' and 'other insects'.
-This last group was formed by a mix of uncommon insect taxa on the full set of networks.
-
-**Overall motif patterns**
-
-Following previous work [@simmons2019; @simmons2020], we broke down the plant-pollinator networks into their constituent motifs.
-Prior to analyses, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.
-To test the effect of singletones, we ran all analysis to the same set of networks, but considering only interactions whose frequency was greater than one (64.98$\%$ of interactions).
-Results are qualitatively consistent and are not further discussed in the main text (**Figures S1 and S2**).
-
-We calculated the frequency of all motifs up to five nodes (see **Figure 1**) for each empirical network, by using the _bmotif_ package version _2.0.2_ [@bmotifsimmons2019].
-To control for variation in network size, motif frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains).
-Like @simmons2020, we just used five-node motifs in our analyses for visualisation, interpretation and computational reasons.
-In addition, we also excluded two-node motifs (or links) from our analyses because their normalised frequencies would always equal one.
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, fig.pos="t", warning=FALSE,out.width="75%",fig.align="center", fig.cap="\\textbf{Figure 1.} Adapted figure of Simmons et al., 2019 with all the possible motifs from two to five species in bipartite networks.
-There is a total of 17 possible motifs with 46 different positions denoted within each node.", fig.width=10,fig.height=8}
-library(tidyverse)
-library(RColorBrewer)
-source("../Scripts/Scripts_Alfonso/plot_motif_positionsV2.R")
-
-motif_number <- 1
-p1 <- plot_motif_positions(motif_number)
-
-motif_number <- 2
-p2 <- plot_motif_positions(motif_number)
-
-motif_number <- 3
-p3 <- plot_motif_positions(motif_number)
-
-motif_number <- 4
-p4 <- plot_motif_positions(motif_number)
-
-motif_number <- 5
-p5 <- plot_motif_positions(motif_number)
-
-motif_number <- 6
-p6 <- plot_motif_positions(motif_number)
-
-motif_number <- 7
-p7 <- plot_motif_positions(motif_number)
-
-motif_number <- 8   
-p8 <- plot_motif_positions(motif_number)
-
-motif_number <- 9
-p9 <- plot_motif_positions(motif_number)
-
-motif_number <- 10
-p10 <- plot_motif_positions(motif_number)
-
-motif_number <- 11
-p11 <- plot_motif_positions(motif_number)
-
-motif_number <- 12
-p12 <- plot_motif_positions(motif_number)
-
-motif_number <- 13
-p13 <- plot_motif_positions(motif_number)
-
-motif_number <- 14
-p14 <- plot_motif_positions(motif_number)
-
-motif_number <- 15
-p15 <- plot_motif_positions(motif_number)
-
-motif_number <- 16
-p16 <- plot_motif_positions(motif_number)
-
-motif_number <- 17
-p17 <- plot_motif_positions(motif_number)
-
-library(patchwork)
-
-(p1 & ylab("2 species")| p2 & ylab("3 species") | p3 )/ (p4 & ylab("4 species")| p5 | p6 | p7)/ (p8  & ylab("5 species")| p9 | p10 | p11 | p12) / (p13 & ylab("5 species")| p14 | p15 | p16 | p17) & theme(axis.title.y = element_text(color="black", size=14, face="bold")) #+
- #plot_annotation(tag_levels = '1')
-
-```
-
-To assess the significance of the observed frequencies, we created 1,000 simulated networks for each binary network using the _nullmodel_ function and the _vaznull_ model in the _bipartite_ package version _2.14_ [@dormann2009].
-Generated networks had the same number of plants and floral visitors, as well as the same connectance of their corresponding empirical networks.
-After extracting the motif frequencies from the simulated networks, for each motif type and empirical network, we calculated the percentage of simulated networks whose frequencies were smaller than the ones observed, that is, we estimated the percentile of the observed motif frequencies.
-Motifs whose percentile is close to 0 or 100 are under- or over-represented in the empirical networks, respectively, and thus they cannot be predicted by connectance and the number of species alone.
-To summarize general patterns across networks, we used an intercept-only linear mixed model (LMM) per motif with the help of the package lmer version _1.1-21_ [@bates2015], where the response variable was the observed motif percentile per network.
-In these models, we used the study identifiers in **Table S1** as a random intercept.
-By doing so, we obtained estimates of the average motif frequency, but controling the variation at the study level.
-
-**Over and under-represented functional groups on motif positions**
-
-We calculated which functional groups were over or under-represented in different motif positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
-To estimate the position frequencies of each functional group in a given network, we added the frequencies of those species that belong to the group, and then, we normalised the resulting frequencies by dividing the position measure for each group by the total number of times that a group appears in any position within the same motif size class.
-Then, we calculated the percentile of the observed position frequencies for each group and network, just like we did with motif frequencies.
-To outline the general patterns of position frequencies across networks and functional groups, we fit a LMM per motif position, where the response variable was the observed position percentile per network.
-We used the functional group identifier as an explanatory variable and the study identifiers as a random intercept.
-By adding the functional group estimates to the model intercept, we assessed the average motif frequency, after controlling the variation at the study level.
-Finally, we visualized with the help of the package _ComplexHeatmap_ version _2.6.2_ [@gu2016] over- and under- representation of plant and pollinator functional groups on the different motif positions.
-
-**Over- and under-represented funtional group combinations of motifs**
-
-Finally, we studied which combinations of functional groups tend to appear together within the same motifs (up to five nodes).
-That is which combinations are over or under-represented.
-This analysis use 57 out of the 60 networks available due to computational limitations to identify all the nodes in the motifs of the three networks with the highest number of links.
-To do so, for each of the 53,250 possible motif combinations, we estimated the observed and the expected probability of finding those combination in empirical networks, respectively.
-Then, we determined whether the observed probabilities are likely to come from the expected probabilities or not.
-To calculate the observed probability ($p_i^O$) of functional groups within a motif $i$ (e.g., motif 3, 'bee' + 'bee' + 'selfing herbs'), we divided the number of times that $i$ appears in our set of empirical networks ($n_i^O$) by the sum of the number of times that each possible combination appeared: $p_i^O = n_i^O / \sum_{k=1}^{53,250} n_k^O$.
-To estimate the expected probability of a given motif combination $i$, $p_i^E$, firstly, we calculated the probability of finding a given functional group $x$ in the position $\alpha$ of $i$, $p_i(x,\alpha)$.
-Then, by assuming the independency of $p_i(x,\alpha)$, we computed the expected probability of the combination $i$ as the product of the probability of its pairs $(x,\alpha)$, that is, $p_i^E = \prod _{(x,\alpha )\in i} p_i(x,\alpha)$.
-To obtain $p_i(x,\alpha)$, we proceeded as follows.
-First, we calculated the number of times that the functional group $x$ appears in the position $\alpha$ in each empirical network $\eta$, denoted as $n_i^{\eta}(x,\alpha)$.
-Then, by controlling the variation at the network level, we assessed the average value of the absolute frequency of functional group $x$ appears in the position $\alpha$, $n_i(x,\alpha) = E\left [ n_i^{\eta}(x,\alpha) \right ]$, and estimated $p_i(x,\alpha)$ as $p_i(x,\alpha) = n_i(x,\alpha)/\sum_{k}n_i(k,\alpha)$.
-To obtain $n_i(x,\alpha)$, we fitted a LMM per motif position, where the response variable was the number of times that a given position was observed per network, the explanatory variable was functional group identifier, and the random intercept was given by network identifiers nested within the study identifiers.
-
-Once we obtained $p_i^O$ and $p_i^E$, we used a simulation approach to determine whether the former is likely to come from the latter or not.
-This approach was preferred since the large number of possible motif combinations and the small probabilities for some of them advise against using an exact test of goodness-of-fit or a Chi-square one.
-Specifically, we created 1,000 random samples with repetition of possible motif combinations, where each sample contained 10 million elements and, for each combination, the probability of being selected was equal to its expected probability.
-From those random samples, we extracted the mean and the standard deviation of the expected probability of $i$, denoted as $E\left [ p_i^E \right ]$ and $\sigma\left [ p_i^E \right ]$, respectively, and calculated the z-scores of $p_i^O$ as $z_i^O = \left ( p_i^O - E\left [ p_i^E \right ] \right )/\sigma \left [ p_i^E \right ]$, for those motif combinations with $p_i^O > 0$.
-According to the usual interpretation of z-scores, combinations with $z_i^O > 1.96$ are over-represented, whereas those with $z_i^O < -1.96$ are under-represented, at the 95$\%$  confidence level.
-Notice that we focused on combinations with $p_i^O > 10^{-7}$ because, beyond the interest that can arouse the combinations that appear at most once, we do not have enough numerical resolution to accurately detect whether or not those combinations are under-represented (due to the limited size of our random samples).
-
-#RESULTS
-
-**Plant and floral visitor functional groups**
-
-The hierarchical cluster analysis divided the dataset into five different groups with different and overlapping characteristics (**Figure S3** and **Figure S4**).
-The first group referred to as 'selfing herbs' consisted on herbs with hermaphroditic flowers with high levels of autonomous selfing.
-The second group named 'small outcrossing perennials' had small perennial species with a mixed of life forms (i.e., trees shrubs and herbs) with outcrossing hermaphroditic flowers.
-The third group referred to as 'self-incompatible perennials with large flowers' comprised perennial species with a mixed of life forms and large self-incompatible hermaphroditic flowers with high number of ovules.
-The fourth group named 'tall plants with small unisexual flowers' had the tallest species, highest proportion of shrub and tree life forms, dioecious and monoecious breeding systems, small flowers and the highest numbers of flowers and inflorescences per plant.
-Finally, the fifth group named 'short-lived outcrossers with long zygomorphic flowers' consisted on small perennial and short-lived herbs with long self-compatible zygomorphic flowers that were unable to self-pollinate.
-
-In total, there were 1,126 species of floral visitor with 6,325 interactions recorded with plants.
-Most plants interacted with bees (2,256 interactions) and non-syrphid Diptera (1,768) followed by syrphids (845), Lepidoptera (437), Coleoptera (432) and non-bee Hymenoptera (362).
-
-**Overall motif patterns**
-
-Most motifs were under- and over-represented (close to the 1st and 99th percentile, respectively) in the comparison between empirical and simulated networks (**Figure 2**).
-Motifs 3, 5, 9, 10 and 14 were under-represented in empirical networks, that is, all were close to the 1st percentile and under the 25th percentile.
-Interestingly, four out of five of these motifs belonged to the largest path length classification (i.e., core-peripheral).
-In addition, motifs 2, 6, 7, 16 and 17 were over-represented, all over the 75th percentile and thus the closest to the 99th percentile.
-In contrast to the under-represented motifs, over-represented motifs belonged to the two shortest path length groups (i.e., complete and fan).
-The remaining motifs (i.e., 4, 8, 11, 12, 13, and 15) were between the 25th and 75th percentile.
-Notably, the exclusion of singletones from this analysis did not change the observed results (**Figure S1**).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure 2.** Comparison of motif frequencies between empirical and simulated networks grouped by average path length (plots a, b, c and d) as determined in Simmons et al.
-(2020).
-This is shown with the mean percentage of motif frequencies in empirical networks that were over the motif frequencies of the simulated ones (percentiles).
-This was done by network (light blue dots) and then averaged for all networks (black dots with error bars that correspond to the standard deviation)."}
-library(lme4)
-library(nlme)
-library(tidyverse)
-source("../Scripts/Scripts_Alfonso/add_study_id.R")
-d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
-d <- add_study_id(d)
-#str(d)
-#head(d)
-
-#ggplot(d %>% filter(motif != 1), aes(percentil_sizeclass))+
-#  geom_histogram(color="black", fill="white")+
-#  facet_wrap(~motif)+
-#  theme_bw()+
-#  labs(x="Sizeclass percentile")
-#
-# Motifs tend to be over- and under-represensented in real networks
-
-# Mean percentile and SE taking into account the study system
-motif_codes <- d %>% filter(motif != 1) %>% # We remove links (motif code: 1)
-  select(motif) %>% unique() %>% pull()
-motif_means <- tibble(motif = motif_codes)
-motif_means$mean <- NA
-motif_means$SE <- NA
-
-for(i.motif in 1:length(motif_codes)){
-
-  m <- lmer(percentil_sizeclass ~ 1+(1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = subset(d, motif == motif_codes[i.motif]))
-
-  motif_means$mean[i.motif] <- fixed.effects(m) %>% unname()
-  motif_means$SE[i.motif] <- sqrt(diag(vcov(m)))
-
-}
-
-#Add categories based on path length set by Simmons 2021 et al., Functional Ecology
-d$Broad_categories[d$motif==2 | d$motif==7 | d$motif==17 | d$motif==3|d$motif==4|d$motif==8] <- "Fan"
-
-d$Broad_categories[d$motif==15 | d$motif==11] <- "Medium-weak"
-
-d$Broad_categories[d$motif==6 | d$motif==16 |  d$motif==12] <- "Strong"
-
-d$Broad_categories[d$motif==5 | d$motif==9 |  d$motif==14|  d$motif==13|  d$motif==10] <- "Weak"
-
-#order the categories from short to long path length
-d$Broad_categories <- factor(d$Broad_categories, levels = c("Strong", "Fan", "Medium-weak", "Weak"))
-
-#Ffilter out two node motifs
-d_1 <- d %>% filter(motif != 1)
-#Merge dataframes to bl able to create facets
-d_2 <- merge(d_1, motif_means, by="motif")
-
-arr <- list('Strong' = expression(bold(paste("(a) Complete (strong, ", bar(x), " = 1.38)"))),
-             'Fan' = expression(bold(paste("(b) Fan (medium-strong, ", bar(x), " = 1.48)"))), 
-             'Medium-weak' = expression(bold(paste("(c) Asymmetric complete (medium-weak, ", bar(x), " = 1.60)"))), 
-             "Weak" =expression(bold(paste("(d) Core-peripheral (weak, ", bar(x), " = 1.85)"))))
-mylabel <- function(val) { return(lapply(val, function(x) arr[x])) }
-
-library(ggforce) #workaround with ggforce to have facets with same sizes
-
-p <- ggplot()+geom_point(data = d_2, aes(y=factor(motif), 100*percentil_sizeclass), shape=21,color="black",fill="azure2",size=1.75, alpha=0.3)+
-  geom_errorbar(data = d_2,aes(y = factor(motif), xmin=100*(mean-SE), xmax=100*(mean+SE)), 
-                width=0.8,size=0.8,color="black") +theme_bw()+
-  geom_point(data = d_2,aes(y = as.factor(motif), x=100*mean), 
-             size=2,color="black")+labs(y="Two to five node motifs", x = "Percentile")+
-  theme( strip.background = element_blank())+
-  theme(strip.text = element_text(face="bold", size=10, hjust=0),
-        panel.border=element_rect(color="black",size=1.2))
-
-p + ggforce::facet_col(vars(Broad_categories), scales = 'free', space = 'free',labeller=mylabel)
-
-#Trying to maintain a gradient from low to high in colors
-
-#Fig 1 Should be a dot plot (or forest plot) of the mean +- SE of the 15 motifs.
-#NICE! Can we put motifs in Y axes, and % in X?
-```
-
-**Over and under-represented functional groups on motif positions**
-
-```{r , include=FALSE}
-
-#SAME SCRIPT AS THE PLOTTING FOR THE HEATMAP BUT I NEED IT HERE TO LOAD THE VARIABLES WITH VALUES ON RESULTS
-
-library(lme4)
-library(nlme)
-library(tidyverse)
-library(stringi)
-source("../Scripts/Scripts_Alfonso/add_study_id.R")
-
-#############################################
-# EXTRACT MEAN VALUES
-#############################################
-all_position_percentiles <- read_csv("../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
-
-all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
-                                                              "[0-9]+") %>% as.numeric()
-
-all_position_percentiles <- add_study_id(all_position_percentiles)
-#str(all_position_percentiles)
-#head(all_position_percentiles)
-
-list_plants_FG <- as.character(1:10)
-
-plant_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF)) #ME DA ERROR
-pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF))
-
-# Plants-------------
-
-# Mean percentile and SE taking into account the study system
-plant_codes <- plant_position_percentiles_filtered$position %>% unique()
-plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-plant_means$mean <- NA
-plant_means$SE <- NA
-
-for(i.pos in 1:length(plant_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
-            data = plant_position_percentiles_filtered %>%
-              filter(position == plant_codes[i.pos]))
-
-  temp <- fixed.effects(m) %>% unname()
-  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
-                                                                    temp[1]+temp[2],
-                                                                    temp[1]+temp[3],
-                                                                    temp[1]+temp[4],
-                                                                    temp[1]+temp[5]) ## to get real means per FG
-  temp <- sqrt(diag(vcov(m)))
-  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
-                                                                  temp[1]+temp[2],
-                                                                  temp[1]+temp[3],
-                                                                  temp[1]+temp[4],
-                                                                  temp[1]+temp[5])
-
-}
-
-# Pollinators--------
-
-# Mean percentile and SE taking into account the study system
-pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
-pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-pollinator_means$mean <- NA
-pollinator_means$SE <- NA
-pollinator_means_reordered <- NULL
-
-for(i.pos in 1:length(pollinator_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = pollinator_position_percentiles_filtered %>%
-              filter(position == pollinator_codes[i.pos]),
-            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
-
-  temp <- fixed.effects(m) %>% unname()
-  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)
-
-  pollinator_means_aux$mean <- c(temp[1],
-                                 temp[1]+temp[2],
-                                 temp[1]+temp[3],
-                                 temp[1]+temp[4],
-                                 temp[1]+temp[5],
-                                 temp[1]+temp[6],
-                                 temp[1]+temp[7],
-                                 temp[1]+temp[8],
-                                 temp[1]+temp[9]) ## to get real means per FG
-
-  temp <- sqrt(diag(vcov(m)))
-  pollinator_means_aux$SE <- c(temp[1],
-                               temp[1]+temp[2],
-                               temp[1]+temp[3],
-                               temp[1]+temp[4],
-                               temp[1]+temp[5],
-                               temp[1]+temp[6],
-                               temp[1]+temp[7],
-                               temp[1]+temp[8],
-                               temp[1]+temp[9])
-
-  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)
-
-}
-
-# There are lower limits (mean - SE) smaller than 0 (see Other insects)
-# We set the lower limit of those error bars to zero
-
-pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
-pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
-
-#############################################
-# ADDING BROAD MOTIF CATEGORIES TO POSITIONS
-#############################################
-
-motifs_raw_data <- read_csv("../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-motifs_raw_data$Broad_categories <- NA
-
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(5,9,14,13,10)] <- "Core-peripherical"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(6,16,12)] <- "Complete"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(2,3,7,4,17,8)] <- "Fan"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(15,11)] <- "Asymmetric complete"
-
-motifs_raw_data$plant <- gsub("[^0-9.-]", "", motifs_raw_data$plant)
-motifs_raw_data$pollinator <- gsub("[^0-9.-]", "", motifs_raw_data$pollinator)
-motifs_raw_data$plant <- as.numeric(motifs_raw_data$plant)
-motifs_raw_data$pollinator <- as.numeric(motifs_raw_data$pollinator)
-motifs_raw_data <- motifs_raw_data %>% filter(!is.na(Broad_categories))
-
-fan_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-pollinator_means_reordered$Broad_categories <- NA
-
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% fan_pollinator] <- "Fan" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% asymm_pollinator] <- "Medium-weak" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% complete_pollinator] <- "Strong" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% core_per_pollinator] <- "Weak"
-
-fan_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-plant_means$Broad_categories <- NA
-
-plant_means$Broad_categories[plant_means$position %in% fan_plant] <- "Fan" 
-plant_means$Broad_categories[plant_means$position %in% asymm_plant] <- "Medium-weak" 
-plant_means$Broad_categories[plant_means$position %in% complete_plant] <- "Strong" 
-plant_means$Broad_categories[plant_means$position %in% core_per_plant] <- "Weak"
-
-################################################################################
-# Alternative code to HEATMAPS to create variables with values to load on text
-# in a reproducible/automated way
-################################################################################
-
-# PLANTS-----
-
-# Prepare data for heatmap
-heat_plants_aux <- plant_means %>% spread(Node_FG,mean) %>% select(-SE)
-
-heat_plants <- heat_plants_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-# POLLINATORS-----------
-
-filter_rare_groups <- T
-
-if(filter_rare_groups == T){
-  heat_pollinators_aux <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds",
-                                                                                "Lizards",
-                                                                                "Other_insects")) %>% 
-    spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees",            
-                                      "Coleoptera","Lepidoptera","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Syrphids")
-}else{
-  heat_pollinators_aux <- pollinator_means_reordered %>% spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees","Birds",            
-                                      "Coleoptera","Lepidoptera","Lizards","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Other insects","Syrphids")
-}
-
-heat_pollinators <- heat_pollinators_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))
-
-#Check percentage of over and under represented
-colMeans(heat_pollinators[,c(3:8)] < 0.25)
-poll_under_25 <- colMeans(heat_pollinators[,c(3:8)] < 0.25)
-poll_under_25 <- specify_decimal((poll_under_25[[1]] + poll_under_25[[2]] + poll_under_25[[3]] +
-poll_under_25[[4]] + poll_under_25[[5]] + poll_under_25[[6]])/6*100,2)
-#[1] 32.57576
-
-colMeans(heat_pollinators[,c(3:8)] > 0.75)
-poll_over_75 <- colMeans(heat_pollinators[,c(3:8)] > 0.75)
-poll_over_75 <- specify_decimal((poll_over_75[[1]] + poll_over_75[[2]] + poll_over_75[[3]] +
-    poll_over_75[[4]] + poll_over_75[[5]] + poll_over_75[[6]])/6*100,2)
-#[1] 4.545455
-
-#################################################################################
-#################################################################################
-
-colnames(heat_plants)<- c("position", "Broad_categories", "one",
-                               "two", "three","four",
-                               "five")
-f <- heat_plants %>%
-  mutate(min = pmin(1,
-                    one, two,three,
-                    four, five))%>%
-  mutate(max = pmax(one,
-                    two, three,four,
-                    five))
-
-diff_1 <- f$max-f$min
-
-cbind(diff,diff_1)
-
-#Check percentage of over and under represented per FG
-colMeans(heat_plants[,c(3:7)] < 0.25)
-plant_under_25 <- colMeans(heat_plants[,c(3:7)] < 0.25)
-plant_under_25 <- specify_decimal((plant_under_25[[1]] + plant_under_25[[2]] + plant_under_25[[3]] + 
-    plant_under_25[[4]] + plant_under_25[[5]])/5*100,2)
-#[1] 18.18182
-colMeans(heat_plants[,c(3:7)] > 0.75)
-plant_over_75 <- colMeans(heat_plants[,c(3:7)] > 0.75)
-plant_over_75 <- specify_decimal((plant_over_75[[1]] + plant_over_75[[2]] + plant_over_75[[3]] + 
-    plant_over_75[[4]] + plant_over_75[[5]])/5*100,2)
-#[1] 8.181818
-
-#overall percentages
-under <- specify_decimal((as.numeric(poll_under_25) + as.numeric(plant_under_25))/2,2)
-over <- specify_decimal((as.numeric(poll_over_75) + as.numeric(plant_over_75))/2,2)
-
-```
-
-The comparison of the functional group frequencies per motif position between empirical and simulated networks showed a `r over`$\%$ and `r under`$\%$ of over- (>75$^{th}$) and under- (<25th) represented functional groups in the different positions, respectively (**Figure 3**).
-Floral visitors showed a total of `r poll_over_75`$\%$ and `r poll_under_25`$\%$ of over- and under-represented functional groups in the different positions and plants `r plant_over_75`$\%$ and `r plant_under_25`$\%$ of over and under-represented groups, respectively.
-Notably, the differences across functional groups were more marked for floral visitors than for plant functional groups (the differences between min and max percentiles per position were generally two-three times larger for floral visitors).
-From most over- to under-represented floral visitors functional groups on the different motif positions (indicated with the dendrogram order in **Figure 3**), we found: bees, non-syrphids Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.
-Although plant functional groups showed less differences between them, there were also more represented functional groups than others, thus from most over- to under-represented groups on the different motif positions we found: self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', out.width="80%",fig.cap="\\textbf{Figure 3.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions.
-The different motif positions are dividied by the average path length clasification determined by Simmons et al.
-(2020).
-The superior dendrogram indicates the differences across groups with the more separated groups showing larger differences."}
-
-library(lme4)
-library(nlme)
-library(tidyverse)
-library(stringi)
-source("../Scripts/Scripts_Alfonso/add_study_id.R")
-
-#############################################
-# EXTRACT MEAN VALUES
-#############################################
-
-all_position_percentiles <- read_csv("../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
-
-all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
-                                                              "[0-9]+") %>% as.numeric()
-
-all_position_percentiles <- add_study_id(all_position_percentiles)
-#str(all_position_percentiles)
-#head(all_position_percentiles)
-
-list_plants_FG <- as.character(1:10)
-
-plant_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF)) #ME DA ERROR
-pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF))
-
-# Plants-------------
-
-# Mean percentile and SE taking into account the study system
-plant_codes <- plant_position_percentiles_filtered$position %>% unique()
-plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-plant_means$mean <- NA
-plant_means$SE <- NA
-
-for(i.pos in 1:length(plant_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
-            data = plant_position_percentiles_filtered %>%
-              filter(position == plant_codes[i.pos]))
-
-  temp <- fixed.effects(m) %>% unname()
-  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
-                                                                    temp[1]+temp[2],
-                                                                    temp[1]+temp[3],
-                                                                    temp[1]+temp[4],
-                                                                    temp[1]+temp[5]) ## to get real means per FG
-  temp <- sqrt(diag(vcov(m)))
-  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
-                                                                  temp[1]+temp[2],
-                                                                  temp[1]+temp[3],
-                                                                  temp[1]+temp[4],
-                                                                  temp[1]+temp[5])
-
-}
-
-# Pollinators--------
-
-# Mean percentile and SE taking into account the study system
-pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
-pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-pollinator_means$mean <- NA
-pollinator_means$SE <- NA
-pollinator_means_reordered <- NULL
-
-for(i.pos in 1:length(pollinator_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = pollinator_position_percentiles_filtered %>%
-              filter(position == pollinator_codes[i.pos]),
-            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
-
-  temp <- fixed.effects(m) %>% unname()
-  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)
-
-  pollinator_means_aux$mean <- c(temp[1],
-                                 temp[1]+temp[2],
-                                 temp[1]+temp[3],
-                                 temp[1]+temp[4],
-                                 temp[1]+temp[5],
-                                 temp[1]+temp[6],
-                                 temp[1]+temp[7],
-                                 temp[1]+temp[8],
-                                 temp[1]+temp[9]) ## to get real means per FG
-
-  temp <- sqrt(diag(vcov(m)))
-  pollinator_means_aux$SE <- c(temp[1],
-                               temp[1]+temp[2],
-                               temp[1]+temp[3],
-                               temp[1]+temp[4],
-                               temp[1]+temp[5],
-                               temp[1]+temp[6],
-                               temp[1]+temp[7],
-                               temp[1]+temp[8],
-                               temp[1]+temp[9])
-
-  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)
-
-}
-
-# There are lower limits (mean - SE) smaller than 0 (see Other insects)
-# We set the lower limit of those error bars to zero
-
-pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
-pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
-
-#############################################
-# ADDING BROAD MOTIF CATEGORIES TO POSITIONS
-#############################################
-
-motifs_raw_data <- read_csv("../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-motifs_raw_data$Broad_categories <- NA
-
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(5,9,14,13,10)] <- "Core-peripherical"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(6,16,12)] <- "Complete"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(2,3,7,4,17,8)] <- "Fan"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(15,11)] <- "Asymmetric complete"
-
-motifs_raw_data$plant <- gsub("[^0-9.-]", "", motifs_raw_data$plant)
-motifs_raw_data$pollinator <- gsub("[^0-9.-]", "", motifs_raw_data$pollinator)
-motifs_raw_data$plant <- as.numeric(motifs_raw_data$plant)
-motifs_raw_data$pollinator <- as.numeric(motifs_raw_data$pollinator)
-motifs_raw_data <- motifs_raw_data %>% filter(!is.na(Broad_categories))
-
-fan_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-pollinator_means_reordered$Broad_categories <- NA
-
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% fan_pollinator] <- "Fan" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% asymm_pollinator] <- "Medium-weak" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% complete_pollinator] <- "Strong" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% core_per_pollinator] <- "Weak"
-
-fan_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-plant_means$Broad_categories <- NA
-
-plant_means$Broad_categories[plant_means$position %in% fan_plant] <- "Fan" 
-plant_means$Broad_categories[plant_means$position %in% asymm_plant] <- "Medium-weak" 
-plant_means$Broad_categories[plant_means$position %in% complete_plant] <- "Strong" 
-plant_means$Broad_categories[plant_means$position %in% core_per_plant] <- "Weak"
-
-########################################
-# CREATE HEATMAPS
-########################################
-
-library(ComplexHeatmap)
-
-# PLANTS-----
-
-# Prepare data for heatmap
-heat_plants_aux <- plant_means %>% spread(Node_FG,mean) %>% select(-SE)
-
-heat_plants <- heat_plants_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-heat_plants_fan <- heat_plants %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_fan) <- heat_plants_fan[,1]
-
-heat_plants_Weak <- heat_plants %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Weak) <- heat_plants_Weak[,1]
-
-heat_plants_Strong <- heat_plants %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Strong) <- heat_plants_Strong[,1]
-
-heat_plants_Medium_weak <- heat_plants %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Medium_weak) <- heat_plants_Medium_weak[,1]
-
-# POLLINATORS-----------
-
-filter_rare_groups <- T
-
-if(filter_rare_groups == T){
-  heat_pollinators_aux <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds",
-                                                                                "Lizards",
-                                                                                "Other_insects")) %>% 
-    spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees",            
-                                      "Coleoptera","Lepidoptera","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Syrphids")
-}else{
-  heat_pollinators_aux <- pollinator_means_reordered %>% spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees","Birds",            
-                                      "Coleoptera","Lepidoptera","Lizards","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Other insects","Syrphids")
-}
-
-heat_pollinators <- heat_pollinators_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-heat_pollinators_fan <- heat_pollinators %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_fan) <- heat_pollinators_fan[,1]
-
-heat_pollinators_Weak <- heat_pollinators %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Weak) <- heat_pollinators_Weak[,1]
-
-heat_pollinators_Strong <- heat_pollinators %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Strong) <- heat_pollinators_Strong[,1]
-
-heat_pollinators_Medium_weak <- heat_pollinators %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Medium_weak) <- heat_pollinators_Medium_weak[,1]
-
-##################
-
-#Do not know how to handle this multiplot for creating a panel
-
-# I'm going to create the 4 plots in one, 
-# I'm not sure that the grouping of the functional group is correct
-# when is done separately
-
-#sorry for the mess of libraries that I do below
-
-#Prepare first pollinators
-
-library(tidyr)
-library(data.table)
-long <- melt(setDT(heat_pollinators), id.vars = c("position","Broad_categories"), variable.name = "guilds")
-
-long_1 <- long %>% select(-Broad_categories)
-
-library(reshape2)
-long_m <- acast(long_1, position~guilds, value.var="value")
-
-#set manually the divisions, so far this is the best way I have seen to split the rows by categories
-
-r_split <- c(rep(c("Fan"), 3),rep(c("Core-peripheral"), 2),"Complete",rep(c("Fan"),2),rep(c("Core-peripheral"), 4),
-             rep(c("Asymmetric complete"), 2), "Complete", rep(c("Core-peripheral"), 3),rep(c("Asymmetric complete"), 2),
-             "Complete", "Fan")
-
-#set order of labels that avoids overlapping
-r_split <- factor(r_split, levels=c("Core-peripheral","Complete","Fan","Asymmetric complete"))
-
-#plat a bit with colors, a bit of a more complex set but looks nicer
-library(circlize)
-col_fun = colorRamp2(c(0.05644663,0.25, 0.4673256,0.75, 0.8782047), c("blue","cadetblue3", "azure2", "gold","red"))
-
-h_pol <- Heatmap(long_m, name = "Mean\npercentile", row_split=r_split,cluster_row_slices = FALSE, 
-                 column_title = "Pollinator functional groups",row_names_gp = gpar(fontsize = 10),
-                 col = col_fun,column_names_rot = 45,  column_names_gp = grid::gpar(fontsize = 10),
-                 column_title_gp = gpar(fontsize = 15, fontface = "bold"),
-                 row_title_gp = gpar(fontsize = 10, fontface = "bold"))
-
-#Prepare plants
-
-#long format
-long_plants <- melt(setDT(heat_plants), id.vars = c("position","Broad_categories"), variable.name = "Functional_groups")
-
-#filter for creating matrix
-long_plants_1 <- long_plants %>% select(-Broad_categories)
-
-#set better colnames
-long_plants_1$Functional_groups <- as.character(long_plants_1$Functional_groups)
-
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==1] <- "Selfing herbs" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==2] <- "Small outcrossing\nperennials" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==3] <- "Self-incomp. perennials\nwith large flowers" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==4] <- "Tall plants with small\nunisexual flowers" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==5] <- "Short-lived outcrossers with\nlong zygomorphic flowers"
-
-long_plants_1$Functional_groups <- factor(long_plants_1$Functional_groups, levels=c("Selfing herbs",
-"Small outcrossing\nperennials" ,"Self-incomp. perennials\nwith large flowers",
-"Tall plants with small\nunisexual flowers" ,"Short-lived outcrossers with\nlong zygomorphic flowers" ))
-
-#create matrix with reshape
-long_plants_m <- acast(long_plants_1, position~Functional_groups, value.var="value")
-
-r_split_plants <- c(rep(c("Fan"), 3),rep(c("Core-peripheral"), 2),"Complete",rep(c("Fan"),2),rep(c("Core-peripheral"), 3),
-                    rep(c("Asymmetric complete"), 2), "Complete", rep(c("Core-peripheral"), 4),rep(c("Asymmetric complete"), 2),
-                    "Complete", "Fan")
-
-r_split_plants <- factor(r_split, levels=c("Core-peripheral","Complete","Fan","Asymmetric complete"))
-
-h_plan <- Heatmap(long_plants_m, name = "Mean\npercentile", row_split=r_split_plants,cluster_row_slices = F, 
-                  column_title = "Plant functional groups",row_names_gp = gpar(fontsize = 10),col = col_fun,column_names_rot = 45,  
-                  column_names_gp = grid::gpar(fontsize = 10),column_title_gp = gpar(fontsize = 15, fontface = "bold"),
-                  row_title_gp = gpar(fontsize = 10, fontface = "bold"))
-
-library(patchwork)
-ht_list <- h_pol+h_plan
-
-draw(ht_list, auto_adjust = FALSE, cluster_rows = F)
-
-#Exploration of min max differences in the percentile position for plants and poll.
-#heat_pollinators[3:8]
-#
-#
-#heat_plants[3:7]
-#
-#
-#library(dplyr)
-#heat_pollinators %>%
-#  mutate(d = pmin())
-#
-#
-#colnames(heat_pollinators)<- c("position", "Broad_categories", "Bee",
-#                               "Coleoptera", "Lepidoptera","non_bee_hymenop",
-#                               "non_syrphid_dip", "syrphid")
-#
-#h <- heat_pollinators %>%
-#  mutate(min = pmin(Bee,
-#                  Coleoptera, Lepidoptera,non_bee_hymenop,
-#                  non_syrphid_dip, syrphid))%>%
-#  mutate(max = pmax(Bee,
-#                    Coleoptera, Lepidoptera,non_bee_hymenop,
-#                    non_syrphid_dip, syrphid))
-#
-#diff <- h$max-h$min
-#
-##################################################################################
-##################################################################################
-#
-#colnames(heat_plants)<- c("position", "Broad_categories", "one",
-#                               "two", "three","four",
-#                               "five")
-#
-#f <- heat_plants %>%
-#  mutate(min = pmin(1,
-#                    one, two,three,
-#                    four, five))%>%
-#  mutate(max = pmax(one,
-#                    two, three,four,
-#                    five))
-#
-#diff_1 <- f$max-f$min
-#
-#cbind(diff,diff_1)
-#
-
-```
-
-\newpage
-
-**Over- and under-represented functional group combinations of motifs**
-
-The different observed frequencies on the different motif positions showed a hierarchical order of probabilities for floral visitors (**Figure 4**).
-That is, the functional group of 'bees' was the most abundant one on all motif positions followed by non-syrphid Diptera which was after bees, the second most frequent functional group on all positions.
-Then, the group of syrphids was the most abundant in all positions but two (positions 28 and 31 from motifs 11 and 12, respectively).
-After syrphids, Coleoptera was the most frequent group on the different positions followed by non-bee Hymenoptera and finally, Lepidoptera which was the less frequent group on all positions but two (positions 12 and 22 from motifs 5 and 9, respectively).
-Remarkably, plant functional groups were more variable on the different motif positions.
-However, there were also predominant functional groups found across the different motif positions.
-The three most frequent groups were 'tall plants with small unisexual flowers', 'self-incompatible perennials with large flowers' and 'small outcrossing perennials'.
-On the contrary, the groups of 'selfing herbs' and 'short lived outcrossers with long zygomorphic flowers' had the lowest probability to be present on the different motifs plant positions.
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 4.** Graphical representation of the probability of finding a given functional group $x$ in the position $\\alpha$ of motif $i$, $p_i(x,\\alpha)$, for all the possible motifs from two to five species in bipartite networks.
-The slices in the nodes for a given functional group $x$ are proportional to the corresponding value of $p_i(x,\\alpha)$."}
-
-library(ggplot2)
-library(scatterpie)
-library(RColorBrewer)
-library(tidyverse)
-
-plant_means_reordered <- read_csv("../Data/Csv/plant_abs_freq_means.csv")
-pollinator_means_reordered <- read_csv("../Data/Csv/pollinator_abs_freq_means.csv")
-#Filter out in order to have just 6 FG'S
-pollinator_means_reordered <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds", "Lizards", "Other_insects"))
-
-# Pollinator--------
-pollinator_pies <- pollinator_means_reordered %>% select(-mean, -SE) %>% 
-  spread(Node_FG,mean_natural_units)
-
-pollinator_pies$x <- 0
-pollinator_pies$y <- 0
-
-#ggplot() + geom_scatterpie(aes(x=x, y=y, group=position,r=5), 
-#                           data = pollinator_pies,
-#                           cols=as.character(c("Bee","Birds","Coleoptera","Lepidoptera",
-#                                               "Lizards","Non-bee-Hymenoptera",
-#                                               "Non-syrphids-diptera","Other_insects",
-#                                               "Syrphids")))+
-#  coord_equal()+
-#  scale_fill_brewer(palette = "Paired")+
-#  facet_wrap(~position,nrow = 3)+
-#  theme_bw()+
-#    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
-#          panel.background = element_blank(),
-#          axis.title.x=element_blank(),axis.text.x=element_blank(),
-#          axis.ticks.x=element_blank(),axis.title.y=element_blank(),
-#          axis.text.y=element_blank(),axis.ticks.y=element_blank(),
-#          legend.position="bottom")+
-#  labs(title = "Pollinator positions",fill=NULL)
-#    
-# plant--------
-plant_pies <- plant_means_reordered %>% select(-mean, -SE) %>% 
-  spread(Node_FG,mean_natural_units)
-
-plant_pies$x <- 0
-plant_pies$y <- 0
-
-#ggplot() + geom_scatterpie(aes(x=x, y=y, group=position,r=5), 
-#                           data = plant_pies,
-#                           cols=as.character(c("1","2","3","4","5")))+
-#  coord_equal()+
-#  scale_fill_brewer(palette = "Dark2")+
-#  facet_wrap(~position,nrow = 3)+
-#  theme_bw()+
-#  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
-#        panel.background = element_blank(),
-#        axis.title.x=element_blank(),axis.text.x=element_blank(),
-#        axis.ticks.x=element_blank(),axis.title.y=element_blank(),
-#        axis.text.y=element_blank(),axis.ticks.y=element_blank(),
-#        legend.position="bottom")+
-#  labs(title = "Plant positions",fill=NULL)
-#
-
-#################################
-# CREATE PIE-MOTIFS
-#################################
-
-equidistribution <- function(number_nodes){
-
-  x_width <- 5.5/(number_nodes+1)
-
-  x_result <- rep(-1.5,number_nodes)
-
-  for(i in 1:number_nodes){
-
-    x_result[i] <- x_result[i] + i*x_width
-
-  }
-
-  return(x_result)
-
-}
-
-plot_pie_motif_positions <- function(motif_number){
-  motifs_raw_data <- read_csv("../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-  motif_data <- motifs_raw_data %>% filter(motif_id == motif_number)
-
-  # Create dataframe with node positions
-
-  labdown = motif_data$plant %>% unique()
-
-  xdown = equidistribution(length(labdown))
-
-  ydown = rep(0,length(labdown))
-
-  labup = motif_data$pollinator %>% unique()
-
-  xup = equidistribution(length(labup))
-
-  yup = rep(2,length(labup))
-
-  d_nodes=data.frame(x=c(xdown,xup),
-                     y=c(ydown,yup),
-                     label = c(labdown,labup))
-
-  # Create a dataframe with links
-
-  plant_positions <- data.frame(plant = labdown,
-                                xdown = xdown,
-                                ydown = ydown)
-
-  pollinator_positions <- data.frame(pollinator = labup,
-                                     xup = xup,
-                                     yup = yup)
-
-  link_df <- motif_data %>% left_join(plant_positions, by = "plant") %>% 
-    left_join(pollinator_positions, by = "pollinator")
-
-  # Before plotting the motif, we remove letters from the node position id
-
-  d_nodes$label <- gsub("[^0-9.-]", "", d_nodes$label)
-  plant_pies_aux <- plant_pies %>% select(-x,-y) %>% mutate(position = as.character(position))
-
-  d_nodes_plant <- d_nodes %>% rename(position = label) %>% 
-    left_join(plant_pies_aux, by = "position") %>% as_tibble() %>%
-    filter(!is.na(`1`))
-
-  pollinator_pies_aux <- pollinator_pies %>% select(-x,-y) %>% mutate(position = as.character(position))
-
-  d_nodes_pollinator <- d_nodes %>% rename(position = label) %>% 
-    left_join(pollinator_pies_aux, by = "position") %>% as_tibble() %>%
-    filter(!is.na(Bee))
-
-  # Define the number of colors you want
- mycolors <- c("#A6CEE3", "chocolate2",  "gold2", "#1F78B4","#B2DF8A",
-                     "gray58", "lightgoldenrod2","thistle2", "burlywood","lightcoral", "olivedrab3")
-
-  ggplot() +
-    scale_shape_identity() +
-    geom_segment(data = link_df, aes(x=xdown, y=ydown, xend = xup, yend = yup), 
-                 size = 1, color = "grey20")+  geom_scatterpie(aes(x=x, y=y, group=position,r=.45), 
-    data = d_nodes_pollinator, cols=as.character(c("Bee","Coleoptera","Lepidoptera","Non-bee-Hymenoptera", "Non-syrphids-diptera","Syrphids"))) +
-    geom_scatterpie(aes(x=x, y=y, group=position,r=0.45), 
-                    data = d_nodes_plant,
-                    cols=as.character(c("1","2","3","4","5")))+
-    coord_fixed()+
-    scale_fill_manual(values = mycolors,"test",
-      breaks=c("Bee","Coleoptera","Lepidoptera",
-               "Non-bee-Hymenoptera", "Non-syrphids-diptera",
-               "Syrphids","1","2","3","4","5"), labels=c("Bees","Coleoptera","Lepidoptera",
-"Non-bee-Hymenoptera", "Non-syrphids-Diptera","Syrphids", 
-          "Selfing herbs","Small outcrossing perennials","Self-incomp. perennials\nwith large flowers",
-          "Tall plants with small\nunisexual flowers","Short-lived outcrossers with\nlong zygomorphic flowers"))+
-    xlim(-1.5,4)+ ylim(-0.5,2.5)+
-    theme(panel.background = element_blank(),
-          axis.text.x=element_blank(),
-          axis.ticks.x=element_blank(),
-          axis.text.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          legend.title = element_text(size=12, face="bold"),legend.background = element_rect(size=0.5, linetype="solid",colour ="black"))+
-    labs(x=NULL,y=NULL)+
-    guides(color = FALSE,fill=guide_legend(title="Functional groups"))+
-    ggtitle(paste0("Motif ",motif_number))+
-    theme(plot.title = element_text(hjust = 0.5),legend.key.size = unit(0.5, 'cm'))+
-    theme(plot.margin=unit(c(0,0,0,0),"cm"))
-}
-
-motif_number <- 1
-p1 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 2
-p2 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 3
-p3 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 4
-p4 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 5
-p5 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 6
-p6 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 7
-p7 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 8   
-p8 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 9
-p9 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 10
-p10 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 11
-p11 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 12
-p12 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 13
-p13 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 14
-p14 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 15
-p15 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 16
-p16 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 17
-p17 <- plot_pie_motif_positions(motif_number)
-
-library(patchwork)
-
-(p1 & ylab("2 species")| p2 & ylab("3 species") | p3  |plot_spacer()|plot_spacer())/ 
-  (p4 & ylab("4 species")| p5 | p6 | p7|plot_spacer())/ 
-  (p8  & ylab("5 species")| p9 | p10 | p11 | p12) / 
-  (p13 & ylab("5 species")| p14 | p15 | p16 | p17) + plot_layout(guides = 'collect') &
-  theme(axis.title.y = element_text(color="black", size=14, face="bold"),legend.position = "bottom")
-
-```
-
-The statistical comparison with z-scores between the observed and expected functional group combinations showed that we can not recover the observed combinations from its probability of occurrence.
-In fact, most combinations are under- or over- represented and follow a modified Gaussian distribution (Johnson's $S_U$) with 65$\%$ of under-represented group combinations, 20$\%$ of no statistical difference and 15$\%$ of under-represented ones (**Figure 5**).
-In addition, motifs with small node combinations (i.e., 2 and 3 nodes) only appeared as under-represented.
-Motifs with 4 and 5-node combinations appeared in the three statistical categories but 4 node motifs had a higher proportion in the under-represented category (10% in comparison with the 1$\%$ and the 3$\%$ of the no statistical difference and over-represented categories, respectively).
-Finally, 5-node motifs were in similar proportions in the no statistical difference and over-represented categories (99$\%$ and 97$\%$, respectively) but they appeared in lower proportion in the under-represented category (89$\%$).
-When, we explore the identity on the different positions of the most probable motif combinations we find as expected that the most common functional groups rule these positions on the most probable motif combinations (lower panel **Figure 5**).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 5.** Z-score comparison (95% confidence level) of the observed and expected frequencies of motif combinations with four specific graphical examples of the most probable motifs of being observed for each category delimited by the z-score critical values: under-represented, no statistical difference and over-represented."}
-
-library(tidyverse)
-library(RColorBrewer)
-
-equidistribution <- function(number_nodes){
-
-  x_width <- 5.5/(number_nodes+1)
-
-  x_result <- rep(-1.5,number_nodes)
-
-  for(i in 1:number_nodes){
-
-    x_result[i] <- x_result[i] + i*x_width
-
-  }
-
-  return(x_result)
-
-}
-
-plot_motif_label <- function(label){
-
-  label_split <- str_split(label,"_")[[1]]
-  motif_number <- as.numeric(label_split[1])
-  nodes <- label_split[2:length(label_split)]
-  plant_nodes <- nodes[nodes %in% plant_means_reordered$Node_FG]
-  pollinator_nodes <- nodes[nodes %in% pollinator_means_reordered$Node_FG]
-
-  motifs_raw_data <- read_csv("../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-  motif_data <- motifs_raw_data %>% filter(motif_id == motif_number)
-
-  # Create dataframe with node positions
-
-  labdown = motif_data$plant %>% unique()
-
-  xdown = equidistribution(length(labdown))
-
-  ydown = rep(0,length(labdown))
-
-  labup = motif_data$pollinator %>% unique()
-
-  xup = equidistribution(length(labup))
-
-  yup = rep(1,length(labup))
-
-  d_nodes=data.frame(x=c(xdown,xup),
-                     y=c(ydown,yup),
-                     label = c(labdown,labup))
-
-  # Create a dataframe with links
-
-  plant_positions <- data.frame(plant = labdown,
-                                xdown = xdown,
-                                ydown = ydown)
-
-  pollinator_positions <- data.frame(pollinator = labup,
-                                     xup = xup,
-                                     yup = yup)
-
-  link_df <- motif_data %>% left_join(plant_positions, by = "plant") %>% 
-    left_join(pollinator_positions, by = "pollinator")
-
-  # Add FG IDs to nodes
-  FG_IDs <- tibble(label = c(sort(labdown),sort(labup)),
-                   FG = c(plant_nodes,pollinator_nodes))
-
-  d_nodes_FG <- d_nodes %>% left_join(FG_IDs, by = "label")
-  levels_FG <- c("Bee","Coleoptera","Lepidoptera",
-                 "Non-bee-Hymenoptera", "Non-syrphids-diptera",
-                 "Syrphids","1","2","3","4","5")
-
-  d_nodes_FG$FG <- factor(d_nodes_FG$FG, levels = levels_FG)
-
-  levels(d_nodes_FG$FG) <- c("Bee","Coleoptera","Lepidoptera",
-                             "Non-bee-Hymenoptera", "Non-syrphids-diptera",
-                             "Syrphids","1","2","3","4","5")
-
-  # Before plotting the motif, we remove letters from the node position id
-
-  d_nodes_FG$label <- gsub("[^0-9.-]", "", d_nodes_FG$label)
-
-  # Define the number of colors you want
- mycolors <- c("#A6CEE3", "chocolate2",  "gold2", "#1F78B4","#B2DF8A",
-                     "gray58", "lightgoldenrod2","thistle2", "burlywood","lightcoral", "olivedrab3")
-
-  ggplot(data=d_nodes_FG, aes(x, y)) +
-    scale_shape_identity() +
-    geom_segment(data = link_df, aes(x=xdown, y=ydown, xend = xup, yend = yup), size = 1, color = "grey20")+
-    geom_point(aes(color = FG), size=7.5)+
-    geom_text(aes(x, y , label = label), size=3)+
-    scale_color_manual(drop = FALSE, values = mycolors,
-                       breaks=c("Bee","Coleoptera","Lepidoptera",
-                                "Non-bee-Hymenoptera", "Non-syrphids-diptera",
-                                "Syrphids","1","2","3","4","5"), 
-                       labels=c("Bees","Coleoptera","Lepidoptera",
-                                "Non-bee-Hymenoptera", "Non-syrphids-Diptera",
-                                "Syrphids", 
-                                "Selfing herbs","Small outcrossing perennials",
-                                "Self-incomp. perennials\nwith large flowers",
-                                "Tall plants with small\nunisexual flowers",
-                                "Short-lived outcrossers with\nlong zygomorphic flowers"))+
-    xlim(-1.5,4)+ ylim(-0.5,1.5)+
-    theme(panel.background = element_blank(),
-          axis.text.x=element_blank(),
-          axis.ticks.x=element_blank(),
-          axis.text.y=element_blank(),
-          axis.ticks.y=element_blank())+
-    labs(x=NULL,y=NULL)+
-    ggtitle(paste0("Motif ",motif_number))+
-    theme(plot.title = element_text(hjust = 0.5,size=10))+
-    guides(color=guide_legend(title="Functional groups"))
-
-}
-
-# Data with pollinator/plant labels
-
-plant_means_reordered <- read_csv("../Data/Csv/plant_abs_freq_means.csv")
-pollinator_means_reordered <- read_csv("../Data/Csv/pollinator_abs_freq_means.csv")
-#Filter out in order to have just 6 FG'S
-pollinator_means_reordered <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds", "Lizards", "Other_insects"))
-
-####################################################################################################
-#Read data to check top 5 motif of each category of observed propabilities
-
-#Under, No signi, Over-rep
-####################################################################################################
-# Check top Z-scores of each group (Under, No diff, Over)
-
-#Read data
-data <- read.csv("../Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
-
-#Find critical value of Z-score
-p <- 0.05 #cutoff probability 95% confidence
-critical_value <- qnorm(p/2) #double tail probability divide by 2
-
-data_1 <- data %>%
-  mutate(infra_over_represented = case_when(
-    z_score < -abs(critical_value) ~ "infra",
-    between(z_score, -abs(critical_value), abs(critical_value)) ~ "no_diff",
-    z_score > abs(critical_value) ~ "over"
-  ))
-
-#data_2 <- filter(data_1, abs(z_score)<2000) 
-#str(data_2)
-
-#Select under-represented by the ones with highest porbability of being observed (top10)
-under_data <- filter(data_1, infra_over_represented=="infra")
-
-under_top_5 <- filter(under_data, row_number(desc(abs(motif_observed_probability)))<= 5) %>%
-  select(motif_functional_ID,motif_observed_probability,counts_observed,z_score)
-
-#Select no statistical difference by the ones with highest porbability of being observed (top5)
-no_diff_data <- filter(data_1, infra_over_represented=="no_diff")
-
-no_diff_top_5 <- filter(no_diff_data, row_number(desc(abs(motif_observed_probability)))<= 5) %>%
-  select(motif_functional_ID,motif_observed_probability,counts_observed,z_score)
-
-#Select over-represenetd by the ones with highest porbability of being observed (top5)
-over_data <- filter(data_1, infra_over_represented=="over")
-
-over_top_5 <- filter(over_data, row_number(desc(abs(motif_observed_probability)))<= 5) %>%
-  select(motif_functional_ID,motif_observed_probability,counts_observed,z_score)
-####################################################################################################
-#Now plot it 
-####################################################################################################
-
-library(patchwork)
-
-#Prepare list of 5 plots for each group
-#Under
-labels_under <- under_top_5$motif_functional_ID
-p_under <- list()
-
-for (i in 1:5){
-
-  p_under[[i]] <- plot_motif_label(labels_under[[i]])
-}
-
-#No signficance
-labels_nodiff <- no_diff_top_5$motif_functional_ID
-p_nodiff <- list()
-
-for (i in 1:5){
-
-  p_nodiff[[i]] <- plot_motif_label(labels_nodiff[[i]])
-}
-
-#Over
-labels_over <- over_top_5$motif_functional_ID
-p_over <- list()
-
-for (i in 1:5){
-
-  p_over[[i]] <- plot_motif_label(labels_over[[i]])
-}
-
-#Run Script with histogram plot
-source("../Scripts/Z-score_percentile_histogram_plot.R")
-
-hist <- ggplot(data_2 %>% filter(round_motif_observed_probability>0), aes(x=z_score, color=infra_over_represented, fill=infra_over_represented)) + 
-  geom_histogram(bins = 93, alpha = 0.5, position = "identity",lwd = 0.25)+
-  geom_vline(xintercept = -abs(critical_value))+
-  geom_vline(xintercept = abs(critical_value))+
-  xlim(-60,60) + ylab("Frequency")+  theme_bw() +
-  scale_fill_manual(name="Motif frequencies" ,values=c("coral2", "palegreen3", "cyan3"), labels=c("Under-represented",
-                                                                                                  "No statistical difference", "Over-represented")) +
-  scale_color_manual(name="Motif frequencies" ,values=c("coral2", "palegreen3", "cyan3"), labels=c("Under-represented",
-                                                                                                   "No statistical difference", "Over-represented")) + xlab("Z-score")
-
-t_col <- function(color, percent = 50, name = NULL) {
-  #      color = color name
-  #    percent = % transparency
-  #       name = an optional name for the color
-
-  ## Get RGB values for named color
-  rgb.val <- col2rgb(color)
-
-  ## Make new color using input color as base and alpha set by transparency
-  t.col <- rgb(rgb.val[1], rgb.val[2], rgb.val[3],
-               max = 255,
-               alpha = (100 - percent) * 255 / 100,
-               names = name)
-
-  ## Save the color
-  invisible(t.col)
-}
-## END
-
-#Prepare panel of plots
-hist / ((p_under[[1]]/p_under[[2]]/p_under[[3]]/p_under[[4]] & theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_rect(fill=t_col("coral2")))) | 
-          (p_nodiff[[1]]/p_nodiff[[2]]/p_nodiff[[3]]/p_nodiff[[4]]& theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_rect(fill=t_col("palegreen3")))) |
-          (p_over[[1]]/p_over[[2]]/p_over[[3]]/p_over[[4]] & theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_rect(fill=t_col("cyan3"))))) + plot_layout(guides = 'collect')
-
-```
-
-# DISCUSSION
-
-Understanding the global patterns of network structure is key to unravel the processes that govern community dynamics [@bascompte2007; @bastolla2009; @guimaraes2020].
-However, common analytical approaches are unable to capture the full complexity of ecological systems [@simmons2019].
-Because network motifs can capture both direct and indirect interactions, by analysing over- and under-representation of motifs we are able to explore in greater detail ecological interactions [@stouffer2007].
-We have explored for the first time the overall structure and representation of network motifs in real plant-pollinator networks and shown that the different motifs up to five nodes are consistently over- and under-represented in comparison with simulated networks indicating the presence of ecological processes shaping their structure.
-Despite the presence of multiple ecological processes likely operating at the same time (e.g., neutral effects, morphological matching or phenological overlap), we found a tendency for over-represented structures with more densely connected motifs (i.e., complete, fan and asymmetric complete) suggesting that neutral effects are likely the predominant processes governing the structure of these network motifs [@simmons2020].
-Thus, as indicated for other network properties like nestedness [@krishna2008; @suweis2013], species relative abundances (i.e., neutral effects) are possibly one of the main determinants of indirect interactions in real plant-pollinator networks.
-[brillante el parrafo!]()
-
-From a pollinator perspective, we found that generalist network motifs were consistently over-represented (e.g.
-fan-type motifs; **Figure 2**).
-For instance, when we compare motifs with equal structure for both trophic levels, we found that floral visitors had always over-representation in the positions that implied the highest number of links.
-Despite this is in good agreement with the current view of the generalist tendency of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of the generalist network motifs was largely driven by the functional group of bees (e.g., positions 42, 46, 16, 4, 14 and 35 in motifs 15, 17, 7, 2, 6 and 13, respectively; see **Figure 3** for positions and **Figure 4** for motifs) while the rest of the functional groups tended to be under-represented in these generalist motifs and over-represented in motif positions with specialist roles (e.g., positions 11, 21, 28 and 34 in motifs 5, 9, 11 and 13, respectively; see **Figure 3** for positions and **Figure 4** for motifs).
-This large effect of bees on the overall patterns is no surprise, as bees were the functional group with largest number of interaction records in the whole set of networks as also recorded for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017].
-Unlike floral visitors, plant functional groups showed little differences on its appearance in different motif positions, and thus similar probability of appearing on all of them.
-If anything, the groups that involved higher levels of outcrossing showed a tendency to be more over-represented and probable on different motif positions.
-For instance, the group of self-incompatible perennials with large flowers, one of the groups that is expected to have higher levels of outcrossing rate [@goodwillie2010], showed the highest over-representation of all plant functional groups (**Figure 3**); and the group of tall plants with unisexual flowers, the one that is expected to have the highest dependence of pollinators on reproduction [@rodger2021], was the most probable on the generalist motif for plant positions (i.e., plant nodes with 3 to 4 links; **Figure 4**).
-
-The probabilities of appearance of each functional group on the different motif positions were insufficient to predict most of the observed network position combinations (**Figure 5**).
-This implies that not just the representation of network motifs types but also the identity of the elements of their structure is influenced by ecological processes that determine under- and over-representation of the different position combinations.
-In addition, we found that just 30$\%$ of the possible 53,250 motif combinations are realized.
-Thus, similarly to the presence of forbidden links at the network level [@olesen2011; @jordano2016], we also found the existence of forbidden motif positions and those represented almost two thirds of the total posible combinations of indirect interactions.
-This concurs well with the general idea that plant-pollinator networks have a high proportion of non-realized direct interactions [@jordano2003; @bascompte2013], and as a result, also a high proportion of non-realized combinations of indirect interactions.
-Some of this non-observed interactions are probably due to under-sampling [@dorado2011; @jordano2016].
-However, a large fraction of the possible interactions do not take place because of life history constraints such as species co-occurrence, trait matching processes and phenological uncoupling [@olesen2011; @bartomeus2016; @jordano2016].
-Despite the advances in the understanding on the ecological processes that influence species pairwise interactions [@bartomeus2016; @peralta2020], we still know little of how these processes determine competitive and facilitative interactions in mutualistic networks.
-Thus, as suggested by @simmons2020, exploring the proportion of these realized network motifs that are competitive or facilitative is a necessary next step to improve our understanding of the architecture of biodiversity [@bascompte2007].
-
-Despite the obvious usefulness of functional groups in summarizing species ecological roles (e.g., similar reproductive biology and behaviour of pollinators), delimiting species into functional groups is not often trivial.
-For instance, taxonomic diversity and trait availability limit our ability to properly represent the wide range of reproductive strategies [@dellinger2020] and different clustering analysis can lead to distinct outcomes (e.g., k-means and hierarchical clustering).
-Further, here we divided floral visitors on the taxonomic rank level because it represented adequately the pollinator species ecological roles without the need of the tremendous effort of compiling trait data for over 1000 species of floral visitors.
-However, further groupings with traits could help revealing greater relevance of trait-matching processes on indirect interactions.
-We believe that this could be investigated by exploring which proportion of over- and under-represented motifs present high and low trait-matching, respectively.
-Moreover, we analysed network motifs focusing exclusively on presence-absence interactions which assume that all interactions are equally important but as suggested by @simmons2020, further work should account for quantitative measurements of the strength of plant-pollinator interactions.
-Finally, despite the wide geographical coverage of our plant-pollinator dataset, there are major gaps for some regions of the world with a clear bias towards Europe, America and islands which have long been interested ecologist [@macarthur1963; @warren2015].
-These biases are also found in global datasets of networks where the data is highly fragmented across space [@poisot2021] and more efforts are needed to capture global patterns of plant-pollinator interactions.
-
-In conclusion, by following the framework of @simmons2020 we have been able to explore competitive and facilitative interactions in plant-pollinator networks worldwide and found that indirect interactions are non-random and are more strongly related to neutral processes than any other ecological process.
-Further, we found that motif combinations of functional groups are strongly constrained and that the distinct motif positions are associated with different functional groups with different ecological roles (e.g., generalization versus specialization).
-Although in this study we do not predict indirect interactions, our work is a first step to elucidate novel interactions beyond pairwise interactions.
-
-# REFERENCES
-
-<div id ="refs"></div>
-
-\newpage
-
-##SUPPLEMENTARY MATERIAL
+**The non-random assembly of functional motifs in plant-pollinator networks worldwide**
+
+Jose B. Lanuza  | Alfonso Allen-Perkins | Ignasi Bartomeus
 

### 2022-01-03 Draft/alternative_fig2_heatmaps.R

@@ -1,397 +1,0 @@
-
-library(lme4)
-library(nlme)
-library(tidyverse)
-library(stringi)
-source("Scripts/Scripts_Alfonso/add_study_id.R")
-
-#############################################
-# EXTRACT MEAN VALUES
-#############################################
-
-
-all_position_percentiles <- read_csv("Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
-
-all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
-                                                              "[0-9]+") %>% as.numeric()
-
-all_position_percentiles <- add_study_id(all_position_percentiles)
-#str(all_position_percentiles)
-#head(all_position_percentiles)
-
-list_plants_FG <- as.character(1:10)
-
-plant_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF)) #ME DA ERROR
-pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF))
-
-
-# Plants-------------
-
-# Mean percentile and SE taking into account the study system
-plant_codes <- plant_position_percentiles_filtered$position %>% unique()
-plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-plant_means$mean <- NA
-plant_means$SE <- NA
-
-
-for(i.pos in 1:length(plant_codes)){
-  
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
-            data = plant_position_percentiles_filtered %>%
-              filter(position == plant_codes[i.pos]))  
-  
-  temp <- fixed.effects(m) %>% unname()
-  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
-                                                                    temp[1]+temp[2],
-                                                                    temp[1]+temp[3],
-                                                                    temp[1]+temp[4],
-                                                                    temp[1]+temp[5]) ## to get real means per FG
[…]

### 2022-01-03 Manuscript/alternative_fig2_heatmaps.R

@@ -1,0 +1,397 @@
+
+library(lme4)
+library(nlme)
+library(tidyverse)
+library(stringi)
+source("Scripts/Scripts_Alfonso/add_study_id.R")
+
+#############################################
+# EXTRACT MEAN VALUES
+#############################################
+
+
+all_position_percentiles <- read_csv("Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
+
+all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
+                                                              "[0-9]+") %>% as.numeric()
+
+all_position_percentiles <- add_study_id(all_position_percentiles)
+#str(all_position_percentiles)
+#head(all_position_percentiles)
+
+list_plants_FG <- as.character(1:10)
+
+plant_position_percentiles_filtered <- all_position_percentiles %>% 
+  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
+         !is.na(expected_freq_its_GF)) #ME DA ERROR
+pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
+  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
+         !is.na(expected_freq_its_GF))
+
+
+# Plants-------------
+
+# Mean percentile and SE taking into account the study system
+plant_codes <- plant_position_percentiles_filtered$position %>% unique()
+plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
+plant_means$mean <- NA
+plant_means$SE <- NA
+
+
+for(i.pos in 1:length(plant_codes)){
+  
+  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
+            data = plant_position_percentiles_filtered %>%
+              filter(position == plant_codes[i.pos]))  
+  
+  temp <- fixed.effects(m) %>% unname()
+  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
+                                                                    temp[1]+temp[2],
+                                                                    temp[1]+temp[3],
+                                                                    temp[1]+temp[4],
+                                                                    temp[1]+temp[5]) ## to get real means per FG
[…]

### 2022-01-03 Manuscript/Main_text_Oikos.Rmd
edits for publication

@@
 
-Keyworkds: Plant-pollinator networks, Plant-pollinator interactions, network motifs, functional groups
+Keyworkds: plant-pollinator networks, plant-pollinator interactions, network motifs, functional groups, plant traits, floral visitors
 
@@
 Once we split the different plant-pollinator networks into their motif elements, we explored: (i) if there is a common invariant structural property in the overall motif networks (i.e.
-over and under-represented motifs); (ii) which functional groups are over and under-represented in the different motif positions; and, (iii) if there are over and under-reprsented functional group combinations within a motif.
+over and under-represented motifs); (ii) which functional groups are over and under-represented in the different motif positions; and, (iii) if there are over- and under-represented functional group combinations within a motif.
 
@@
 First, plant species were grouped through hierarchical clustering into the optimal number of functional groups that summarized the main plant reproductive strategies.
-For this, we used the trait dataset collated in Chapter 1 that comprised a total of 1506 species including the 503 species considered in this study (Supplementary material Chapter 1 **Table S1**).
+For this, we used the trait dataset collated in @lanuza2021 that comprised a total of 1506 species including the 503 species considered in this study (Supplementary material Chapter 1 **Table S1**).
 This dataset consisted on 8 floral, 4 reproductive and 3 vegetative traits excluding traits with high percentage of missing values (over 30$\%$; **Table S2**).

### 2022-01-04 Manuscript/Main_text_Oikos.Rmd
Adding a table with the list of plant species to supp. mat.

@@
 \singlespacing
-{\normalfont Ecological processes leave distinct structural imprints on species interactions shaping the topology of mutualistic networks.
+
+Ecological processes leave distinct structural imprints on species interactions shaping the topology of mutualistic networks.
 Detecting those relationships is not trivial since they go beyond pairwise interactions, but may get blurred when considering full network descriptors.
@@
 Interestingly, the realized combinations of different functional groups within a motif can not be retrieved from their joint probability distributions, indicating that functional group combinations are not random either.
-Our result highlight the non-random structure of indirect interactions in plant-pollinator networks and opens the door to predict novel interactions beyond pairwise interactions within a community context.}
+Our result highlight the non-random structure of indirect interactions in plant-pollinator networks and opens the door to predict novel interactions beyond pairwise interactions within a community context.
 
@@
 Once we split the different plant-pollinator networks into their motif elements, we explored: (i) if there is a common invariant structural property in the overall motif networks (i.e.
-over and under-represented motifs); (ii) which functional groups are over and under-represented in the different motif positions; and, (iii) if there are over- and under-represented functional group combinations within a motif.
+over- and under-represented motifs); (ii) which functional groups are over- and under-represented in the different motif positions; and, (iii) if there are over- and under-represented functional group combinations within a motif.
 
@@
 First, plant species were grouped through hierarchical clustering into the optimal number of functional groups that summarized the main plant reproductive strategies.
-For this, we used the trait dataset collated in @lanuza2021 that comprised a total of 1506 species including the 503 species considered in this study (Supplementary material Chapter 1 **Table S1**).
-This dataset consisted on 8 floral, 4 reproductive and 3 vegetative traits excluding traits with high percentage of missing values (over 30$\%$; **Table S2**).
+For this, we used the trait dataset collated in @lanuza2021 that comprised a total of 1506 species including the 503 species considered in this study (Supplementary material Chapter 1 **Table S2**).
+This dataset consisted on 8 floral, 4 reproductive and 3 vegetative traits excluding traits with high percentage of missing values (over 30$\%$; **Table S3**).
 We opted to calculate the plant functional groups on this larger set of species because of the higher accuracy when delimiting functional groups with that many variables and species [@dolnicar2014].
@@
 
-#RESULTS
+# RESULTS
 

### 2022-01-04 Manuscript/Supporting_information_Oikos.Rmd
Adding a table with the list of plant species to supp. mat.

@@
 
-Jose B. Lanuza  | Alfonso Allen-Perkins | Ignasi Bartomeus
+Jose B. Lanuza, Alfonso Allen-Perkins and Ignasi Bartomeus
+
+\
 
@@
 
-**Table S2** Type of plant traits used in this study.
+**Table S2** List of the plant species used in this study.
+
+**Table S3** Type of plant traits used in this study.
+
+\
 
@@
 
+```{r, echo=FALSE, message=FALSE, cache=FALSE,fig.width=12,  warning=FALSE}
+#Load libraries
+library(tidyverse)
+library(kableExtra)
+
+#Read data
+networks <- read_csv("../Data/Csv/data_for_motifs_analysis_1.csv")
+
+#Subset by interaction greater than 0
+d <- subset(networks, Interaction>0)
+#Create dataframe
+plant_species <- as.data.frame(unique(d$Plant_species))
+#Divide dataset in two
+x <- plant_species[1:168,]
+y <- plant_species[169:336,]
+z <- plant_species[337:503,]
+
+n <- max(length(x), length(y),length(z))
+length(x) <- n                      
+length(y) <- n
+length(z) <- n
+
+#cbind with max length
+d <- as.data.frame(cbind(x, y,z))
+#Convert NA to blank spaces
+d[is.na(d)] <- ""
+#Create table
+kbl(d,booktabs = T,col.names = c("", "List of plant species",""),longtable = T, caption= "\\textbf{Table S2.} List of the 503 plant species used in this study.")%>%column_spec(1,italic = T, )%>%column_spec(2,italic = T) %>%column_spec(3,italic = T)
+
+```
+
+\newpage
+
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=16, fig.width=12}
@@
 
-kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c"),caption = "\\textbf{Table S2.} Traits used to delimit the different plant functional groups divided in quantitative and categorical traits.") %>%
+kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c"),caption = "\\textbf{Table S3.} Traits used to delimit the different plant functional groups divided in quantitative and categorical traits.") %>%
 kable_styling(full_width = T,latex_options = c("striped")) %>%

### 2022-01-04 Scripts/Table_plant_species.R

@@ -1,0 +1,26 @@
+
+#Load libraries
+library(tidyverse)
+library(kableExtra)
+
+#Read data
+networks <- read_csv("Data/Csv/data_for_motifs_analysis_1.csv")
+
+#Subset by interaction greater than 0
+d <- subset(networks, Interaction>0)
+#Create dataframe
+plant_species <- as.data.frame(unique(d$Plant_species))
+#Divide dataset in two
+x <- plant_species[1:252,]
+y <- plant_species[253:503,]
+n <- max(length(x), length(y))
+length(x) <- n                      
+length(y) <- n
+#cbind with max length
+d <- as.data.frame(cbind(x, y))
+#Convert NA to blank spaces
+d[is.na(d)] <- ""
+#Create table
+kbl(d,booktabs = T,col.names = c("Plant species", "Plant species")) %>%
+column_spec(1,italic = T) %>%   column_spec(2,italic = T)
+  

### 2022-01-04 Manuscript/Main_text_Oikos.Rmd
edit on main text

@@
 First, plant species were grouped through hierarchical clustering into the optimal number of functional groups that summarized the main plant reproductive strategies.
-For this, we used the trait dataset collated in @lanuza2021 that comprised a total of 1506 species including the 503 species considered in this study (Supplementary material Chapter 1 **Table S2**).
+For this, we used the trait dataset collated in @lanuza2021 that comprised a total of 1506 species including the 503 species considered in this study (**Table S2**).
 This dataset consisted on 8 floral, 4 reproductive and 3 vegetative traits excluding traits with high percentage of missing values (over 30$\%$; **Table S3**).

### 2022-02-08 Manuscript/Main_text_Oikos.Rmd
Specificity plot ready for supplementary

@@
 bibliography: bibliography.bib
+biblio-style: apalike
+csl: oikos.csl #oikos style from zotero styles
+
 ---
@@
 For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species functional role [@stouffer2012; @baker2015].
-However, it is unclear how the species ecology and life history traits determines the species' functional role within the network of interactions [@coux2016].
+However, it is unclear how the species ecology and life-history traits determines the species' functional role within the network of interactions [@coux2016].
 For example, large pollinators can forage larger distances [@greenleaf2007], deposit greater pollen quantities [@foldesi2021] and handle complex zygomorphic flowers in comparison with small pollinators that are restricted to lower floral complexity [@gong2009].
@@
 
-Here, we used 60 plant-pollinator networks from 18 different studies and 14 countries, alongside functional groups of plants and floral visitors based on functional traits and taxonomic rank, respectively.
+Here, we used 60 plant-pollinator networks from 18 different studies and 14 countries, alongside functional groups of plants and taxonomic groups of floral visitors based on functional traits and taxonomic rank, respectively.
 To obtain plant functional groups, we used a comprehensive dataset that included floral, reproductive and vegetative traits compiled in a larger set of networks.
-Floral visitor functional groups were divided by the main taxonomic groups that differed in life form and behaviour.
+Floral visitor groups were divided by the main taxonomic groups that differed in life form and behaviour.
 Once we split the different plant-pollinator networks into their motif elements, we explored: (i) if there is a common invariant structural property in the overall motif networks (i.e.
-over- and under-represented motifs); (ii) which functional groups are over- and under-represented in the different motif positions; and, (iii) if there are over- and under-represented functional group combinations within a motif.
+over- and under-represented motifs); (ii) which plant and pollinator groups are over- and under-represented in the different motif positions; and, (iii) if there are over- and under-represented plant and pollinator group combinations within a motif.
 
@@
 
-Second, floral visitors were grouped into functional groups based on taxonomic rank as done similarly in past plant-pollinator studies [@fenster2004; @ollerton2009].
+Second, floral visitors were grouped into taxonomic groups based on taxonomic rank as done similarly in past plant-pollinator studies [@fenster2004; @ollerton2009].
 We opted to divide floral visitors on the taxonomic rank level and not with functional traits because the main orders of floral visitors differed in form and behaviour and had lower superior taxonomical complexity (i.e., floral visitors had 6 orders versus plants that had 38).
-Thus, this allowed us to group floral visitors into functional groups that represented adequately the main life strategies of the possible pollinators: (i) bees (Hymenoptera-Anthophila), (ii) non-bee Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Syrphidae-Diptera), (iv) non-syrphids-Diptera, (v) Lepidoptera and (vi) Coleoptera.
-However, a minor set of species belonged to other functional groups that were considered in analyses but not discussed further because of their low representation in the full set of networks (3.55$\%$ of the total interactions recorded).
-These functional groups were 'lizards', 'birds' and 'other insects'.
+Thus, this allowed us to group floral visitors into groups that represented approximately the main life strategies of the possible pollinators: (i) bees (Hymenoptera-Anthophila), (ii) non-bee Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Syrphidae-Diptera), (iv) non-syrphids-Diptera, (v) Lepidoptera and (vi) Coleoptera.
+However, a minor set of species belonged to other taxonomic groups that were considered in analyses but not discussed further because of their low representation in the full set of networks (3.55$\%$ of the total interactions recorded).
+These taxonomic groups were 'lizards', 'birds' and 'other insects'.
 This last group was formed by a mix of uncommon insect taxa on the full set of networks.
@@
 Generated networks had the same number of plants and floral visitors, as well as the same connectance of their corresponding empirical networks.
+**MA FORTUNA, what about degree?**.
 After extracting the motif frequencies from the simulated networks, for each motif type and empirical network, we calculated the percentage of simulated networks whose frequencies were smaller than the ones observed, that is, we estimated the percentile of the observed motif frequencies.
@@
 
-**Over and under-represented functional groups on motif positions**
-
-We calculated which functional groups were over or under-represented in different motif positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
+**Over and under-represented groups on motif positions**
+
+We calculated which plant and pollinator groups were over or under-represented in different motif positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
 To estimate the position frequencies of each functional group in a given network, we added the frequencies of those species that belong to the group, and then, we normalised the resulting frequencies by dividing the position measure for each group by the total number of times that a group appears in any position within the same motif size class.
@@
 
-**Over- and under-represented funtional group combinations of motifs**
+**Over- and under-represented group combinations of motifs**
 
@@
 
-**Plant and floral visitor functional groups**
+**Plant and floral visitor groups**
 
@@
 
-**Over and under-represented functional groups on motif positions**
+**Over and under-represented groups on motif positions**
 
@@
 
-**Over- and under-represented functional group combinations of motifs**
+**Over- and under-represented group combinations of motifs**
 
@@
 Some of this non-observed interactions are probably due to under-sampling [@dorado2011; @jordano2016].
-However, a large fraction of the possible interactions do not take place because of life history constraints such as species co-occurrence, trait matching processes and phenological uncoupling [@olesen2011; @bartomeus2016; @jordano2016].
+However, a large fraction of the possible interactions do not take place because of life-history constraints such as species co-occurrence, trait matching processes and phenological uncoupling [@olesen2011; @bartomeus2016; @jordano2016].
 Despite the advances in the understanding on the ecological processes that influence species pairwise interactions [@bartomeus2016; @peralta2020], we still know little of how these processes determine competitive and facilitative interactions in mutualistic networks.

### 2022-02-08 Manuscript/Supplementary_Material/specificity_VS_position_frequencies.Rmd
Specificity plot ready for supplementary

---
title: ""
output:
  pdf_document: default
  html_document: default
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
---

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=12, fig.width=12}

library(ggplot2)
library(patchwork)

pollinator_means_reordered_s_1 <- read.csv("../../Data/Csv/pollinator_means_reordered_s_1.csv")

plant_means_s <- read.csv("../../Data/Csv/plant_means_s.csv")

p1 <- ggplot(pollinator_means_reordered_s_1,aes(x=s,y=mean))+
  geom_point(alpha=0.5, color="black")+
  geom_smooth(method = "lm",color="black")+
  facet_wrap(~Node_FG)+
  labs(x="Specificty",y="Average frequency per position") +
  theme_bw() + ggtitle("Floral visitors") +
  theme(plot.title = element_text(hjust = 0.5, size = 25),
        axis.text=element_text(size=12),
        axis.title=element_text(size=18),
        strip.text = element_text(size=20))

p2 <- ggplot(plant_means_s,aes(x=s,y=mean))+
  geom_point(alpha=0.5, color="black")+
  geom_smooth(method = "lm", color="black")+
  facet_wrap(~Node_FG)+
  labs(x="Specificty",y="Average frequency per position")+
  theme_bw() + ggtitle("Plants") +
  theme(plot.title = element_text(hjust = 0.5, size = 25),
        axis.text=element_text(size=12),
        axis.title=element_text(size=18),
        strip.text = element_text(size=20))

p1/p2

```

### 2022-02-08 Scripts/Scripts_Alfonso/specificity_VS_position_frequencies.R

@@ -228,3 +228,6 @@ p2 <- ggplot(plant_means_s,aes(x=s,y=mean))+
 
 library(patchwork)
 p1+p2
+
+
+#Preparing plot for publication

### 2022-02-08 Manuscript/Main_text_Oikos.Rmd
keep on this tomorrow

@@
 
-We calculated which plant and pollinator groups were over or under-represented in different motif positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
-To estimate the position frequencies of each functional group in a given network, we added the frequencies of those species that belong to the group, and then, we normalised the resulting frequencies by dividing the position measure for each group by the total number of times that a group appears in any position within the same motif size class.
+We calculated which plant and floral visitor groups were over or under-represented in different motif positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
+To estimate the position frequencies of each group in a given network, we added the frequencies of those species that belong to the group, and then, we normalised the resulting frequencies by dividing the position measure for each group by the total number of times that a group appears in any position within the same motif size class.
 Then, we calculated the percentile of the observed position frequencies for each group and network, just like we did with motif frequencies.
-To outline the general patterns of position frequencies across networks and functional groups, we fit a LMM per motif position, where the response variable was the observed position percentile per network.
-We used the functional group identifier as an explanatory variable and the study identifiers as a random intercept.
-By adding the functional group estimates to the model intercept, we assessed the average motif frequency, after controlling the variation at the study level.
+To outline the general patterns of position frequencies across networks and groups, we fit a LMM per motif position, where the response variable was the observed position percentile per network.
+We used the group identifier as an explanatory variable and the study identifiers as a random intercept.
+By adding the group estimates to the model intercept, we assessed the average motif frequency, after controlling the variation at the study level.
 Finally, we visualized with the help of the package _ComplexHeatmap_ version _2.6.2_ [@gu2016] over- and under- representation of plant and pollinator functional groups on the different motif positions.
 
+**Specificity**
+
+To further explore the role of the different plant and floral visitor groups on the different motif positions we calculated the specificity of the different groups on those positions.
+Following Poisot et al xxxx, specificity ($s_i$) was calculated as the proportion of available species with which a focal species interacts:  $s_i = L - l_i / L - 1$.
+L l
+
+For each species i of the upper level (e.g. parasites), its specificity is given by
+
+where L is the number of lower level species (e.g.
+hosts) found in the network, and li is the number of interaction partners of species i.
+The vector s is the distribution of specificities at the network scale.
+Values of 1 indicate complete specialism (single partner), and values of 0 indicate complete generalism (all possible partners).
+
 **Over- and under-represented group combinations of motifs**
 
-Finally, we studied which combinations of functional groups tend to appear together within the same motifs (up to five nodes).
+Finally, we studied which combinations of plant and floral visitor groups tend to appear together within the same motifs (up to five nodes).
 That is which combinations are over or under-represented.
@@
 Then, we determined whether the observed probabilities are likely to come from the expected probabilities or not.
-To calculate the observed probability ($p_i^O$) of functional groups within a motif $i$ (e.g., motif 3, 'bee' + 'bee' + 'selfing herbs'), we divided the number of times that $i$ appears in our set of empirical networks ($n_i^O$) by the sum of the number of times that each possible combination appeared: $p_i^O = n_i^O / \sum_{k=1}^{53,250} n_k^O$.
-To estimate the expected probability of a given motif combination $i$, $p_i^E$, firstly, we calculated the probability of finding a given functional group $x$ in the position $\alpha$ of $i$, $p_i(x,\alpha)$.
+To calculate the observed probability ($p_i^O$) of the different groups within a motif $i$ (e.g., motif 3, 'bee' + 'bee' + 'selfing herbs'), we divided the number of times that $i$ appears in our set of empirical networks ($n_i^O$) by the sum of the number of times that each possible combination appeared: $p_i^O = n_i^O / \sum_{k=1}^{53,250} n_k^O$.
+To estimate the expected probability of a given motif combination $i$, $p_i^E$, firstly, we calculated the probability of finding a given group $x$ in the position $\alpha$ of $i$, $p_i(x,\alpha)$.
 Then, by assuming the independency of $p_i(x,\alpha)$, we computed the expected probability of the combination $i$ as the product of the probability of its pairs $(x,\alpha)$, that is, $p_i^E = \prod _{(x,\alpha )\in i} p_i(x,\alpha)$.
 To obtain $p_i(x,\alpha)$, we proceeded as follows.
-First, we calculated the number of times that the functional group $x$ appears in the position $\alpha$ in each empirical network $\eta$, denoted as $n_i^{\eta}(x,\alpha)$.
-Then, by controlling the variation at the network level, we assessed the average value of the absolute frequency of functional group $x$ appears in the position $\alpha$, $n_i(x,\alpha) = E\left [ n_i^{\eta}(x,\alpha) \right ]$, and estimated $p_i(x,\alpha)$ as $p_i(x,\alpha) = n_i(x,\alpha)/\sum_{k}n_i(k,\alpha)$.
-To obtain $n_i(x,\alpha)$, we fitted a LMM per motif position, where the response variable was the number of times that a given position was observed per network, the explanatory variable was functional group identifier, and the random intercept was given by network identifiers nested within the study identifiers.
+First, we calculated the number of times that the group $x$ appears in the position $\alpha$ in each empirical network $\eta$, denoted as $n_i^{\eta}(x,\alpha)$.
+Then, by controlling the variation at the network level, we assessed the average value of the absolute frequency of group $x$ appears in the position $\alpha$, $n_i(x,\alpha) = E\left [ n_i^{\eta}(x,\alpha) \right ]$, and estimated $p_i(x,\alpha)$ as $p_i(x,\alpha) = n_i(x,\alpha)/\sum_{k}n_i(k,\alpha)$.
+To obtain $n_i(x,\alpha)$, we fitted a LMM per motif position, where the response variable was the number of times that a given position was observed per network, the explanatory variable was the group identifier, and the random intercept was given by network identifiers nested within the study identifiers.
 

### 2022-02-08 Scripts/Scripts_Alfonso/specificity_VS_position_frequencies.R

@@ -213,21 +213,33 @@ pollinator_means_reordered_s <- pollinator_means_reordered %>%
 plant_means_s$s[is.nan(plant_means_s$s)] <- 1.0
 pollinator_means_reordered_s$s[is.nan(pollinator_means_reordered_s$s)] <- 1.0
 
+library(patchwork)
 
-p1 <- ggplot(pollinator_means_reordered_s,aes(x=s,y=mean))+
-  geom_point(alpha=0.5)+
-  geom_smooth(method = "lm")+
+#select poll functional groups of interest
+levels(factor(pollinator_means_reordered_s$Node_FG))
+vars <- c("Birds","Lizards", "Other_insects")
+pollinator_means_reordered_s_1 <- pollinator_means_reordered_s %>% filter(!Node_FG %in% vars)
+  
+p1 <- ggplot(pollinator_means_reordered_s_1,aes(x=s,y=mean))+
+  geom_point(alpha=0.5, color="black")+
+  geom_smooth(method = "lm",color="black")+
   facet_wrap(~Node_FG)+
-  labs(x="specificty",y="mean average frequency (position)")
+  labs(x="Specificty",y="Average frequency per position") +
+  theme_bw() + ggtitle("Floral visitors") +
+  theme(plot.title = element_text(hjust = 0.5))
 
 p2 <- ggplot(plant_means_s,aes(x=s,y=mean))+
-  geom_point(alpha=0.5)+
-  geom_smooth(method = "lm")+
+  geom_point(alpha=0.5, color="black")+
+  geom_smooth(method = "lm", color="black")+
   facet_wrap(~Node_FG)+
-  labs(x="specificty",y="mean average frequency (position)")
+  labs(x="Specificty",y="Average frequency per position")+
+  theme_bw() + ggtitle("Plants") +
+  theme(plot.title = element_text(hjust = 0.5))
 
-library(patchwork)
-p1+p2
+p1/p2
+
+#save data 
+write.csv(pollinator_means_reordered_s_1, "Data/Csv/pollinator_means_reordered_s_1.csv")
+write.csv(plant_means_s, "Data/Csv/plant_means_s.csv")
 
 
-#Preparing plot for publication

### 2022-02-09 Manuscript/Main_text_Oikos.Rmd
specificity paragraph

@@
 
-**Plant and floral visitors functional groups**
+**Plant and floral visitor groups**
 
@@
 
-**Specificity**
-
-To further explore the role of the different plant and floral visitor groups on the different motif positions we calculated the specificity of the different groups on those positions.
-Following Poisot et al xxxx, specificity ($s_i$) was calculated as the proportion of available species with which a focal species interacts:  $s_i = L - l_i / L - 1$.
-L l
-
-For each species i of the upper level (e.g. parasites), its specificity is given by
-
-where L is the number of lower level species (e.g.
-hosts) found in the network, and li is the number of interaction partners of species i.
-The vector s is the distribution of specificities at the network scale.
-Values of 1 indicate complete specialism (single partner), and values of 0 indicate complete generalism (all possible partners).
+To understand if the different plant and floral visitor groups are associated with motif positions that involve different network roles (e.g., specialization or generalism), we calculated the specificity of the different motif positions and evaluated its association through linear models with the average frequency of the different plant and floral visitor groups as response variable.
+For this, we previously calculated the specificity ($s_i$) of each motif position following @poisot2015 as $s_i = L - l_i / L - 1$, where $L$ is the total number of groups and $l_i$ the number of interaction partners of the group $i$ in a given motif.
+Values of the vector s, range between 1, complete specialization (1 partner within the motif) and 0, complete generalism (all possible partners within the motif).
 
@@
 
-Finally, we studied which combinations of plant and floral visitor groups tend to appear together within the same motifs (up to five nodes).
+We studied which combinations of plant and floral visitor groups tend to appear together within the same motifs (up to five nodes).
 That is which combinations are over or under-represented.

### 2022-02-09 Manuscript/Main_text_Oikos.Rmd
some edits on text and plots to make everything more redable and homogeneous

@@
 In total, there were 503 plant species, 1,111 floral visitors species and 6,248 pairwise interactions registered.
-For ease of data manipulation, plant and floral visitors species names were standardize with the help of the R package _taxize_ version _0.9.99_ [@chamberlain2020].
+For ease of data manipulation, plant and floral visitor species names were standardize with the help of the R package _taxize_ version _0.9.99_ [@chamberlain2020].
 All analyses and data manipulation were conducted in R _version 4.0.5_ [@R].
@@
 To control for variation in network size, motif frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains).
-Like @simmons2020, we just used five-node motifs in our analyses for visualisation, interpretation and computational reasons.
-In addition, we also excluded two-node motifs (or links) from our analyses because their normalised frequencies would always equal one.
+Like @simmons2020, we classified the different motifs by their average path length into four different groups: (i) complete or strong ($\overline{x} = 1.38$), (ii) fan or medium-strong ($\overline{x} = 1.48$), (iii) assymmetric complete or medium-weak ($\overline{x} = 1.60$) and (iv) core-peripheral or weak ($\overline{x} = 1.85$).
+Moreover, we just used five-node motifs in our analyses for visualisation, interpretation and computational reasons.
+Finally, we also excluded two-node motifs (or links) from our analyses because their normalised frequencies would always equal one.
 
@@
 
+**MA FORTUNA, what about degree?**
+
 To assess the significance of the observed frequencies, we created 1,000 simulated networks for each binary network using the _nullmodel_ function and the _vaznull_ model in the _bipartite_ package version _2.14_ [@dormann2009].
 Generated networks had the same number of plants and floral visitors, as well as the same connectance of their corresponding empirical networks.
-**MA FORTUNA, what about degree?**.
 After extracting the motif frequencies from the simulated networks, for each motif type and empirical network, we calculated the percentage of simulated networks whose frequencies were smaller than the ones observed, that is, we estimated the percentile of the observed motif frequencies.
@@
 In these models, we used the study identifiers in **Table S1** as a random intercept.
-By doing so, we obtained estimates of the average motif frequency, but controling the variation at the study level.
-
-**Over and under-represented groups on motif positions**
-
-We calculated which plant and floral visitor groups were over or under-represented in different motif positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
+By doing so, we obtained estimates of the average motif frequency, but controlling the variation at the study level.
+
+**Over- and under-represented groups on motif positions**
+
+We calculated which plant and floral visitor groups were over- or under-represented in the different motif positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
 To estimate the position frequencies of each group in a given network, we added the frequencies of those species that belong to the group, and then, we normalised the resulting frequencies by dividing the position measure for each group by the total number of times that a group appears in any position within the same motif size class.
@@
 By adding the group estimates to the model intercept, we assessed the average motif frequency, after controlling the variation at the study level.
-Finally, we visualized with the help of the package _ComplexHeatmap_ version _2.6.2_ [@gu2016] over- and under- representation of plant and pollinator functional groups on the different motif positions.
+Finally, we visualized with the help of the package _ComplexHeatmap_ version _2.6.2_ [@gu2016] over- and under-representation of plant and floral visitor groups on the different motif positions.
 
@@
 We studied which combinations of plant and floral visitor groups tend to appear together within the same motifs (up to five nodes).
-That is which combinations are over or under-represented.
+That is which combinations are over- or under-represented.
 This analysis use 57 out of the 60 networks available due to computational limitations to identify all the nodes in the motifs of the three networks with the highest number of links.
@@
 According to the usual interpretation of z-scores, combinations with $z_i^O > 1.96$ are over-represented, whereas those with $z_i^O < -1.96$ are under-represented, at the 95$\%$  confidence level.
-Notice that we focused on combinations with $p_i^O > 10^{-7}$ because, beyond the interest that can arouse the combinations that appear at most once, we do not have enough numerical resolution to accurately detect whether or not those combinations are under-represented (due to the limited size of our random samples).
+Notice that we focused on combinations with $p_i^O > 10^{-7}$ because we do not have enough numerical resolution to accurately detect whether combinations that took place only once are under-represented (due to the limited size of our random samples).
 
@@
 
-In total, there were 1,126 species of floral visitor with 6,325 interactions recorded with plants.
+In total, there were 1,126 species of floral visitors with 6,325 interactions recorded with plants.
 Most plants interacted with bees (2,256 interactions) and non-syrphid Diptera (1,768) followed by syrphids (845), Lepidoptera (437), Coleoptera (432) and non-bee Hymenoptera (362).
@@
 
-arr <- list('Strong' = expression(bold(paste("(a) Complete (strong, ", bar(x), " = 1.38)"))),
-             'Fan' = expression(bold(paste("(b) Fan (medium-strong, ", bar(x), " = 1.48)"))), 
-             'Medium-weak' = expression(bold(paste("(c) Asymmetric complete (medium-weak, ", bar(x), " = 1.60)"))), 
-             "Weak" =expression(bold(paste("(d) Core-peripheral (weak, ", bar(x), " = 1.85)"))))
+arr <- list('Strong' = expression(bold(paste("(a) Strong (Complete, ", bar(x), " = 1.38)"))),
+             'Fan' = expression(bold(paste("(b) Medium-strong (fan, ", bar(x), " = 1.48)"))), 
+             'Medium-weak' = expression(bold(paste("(c) Medium-weak (asymmetric complete, ", bar(x), " = 1.60)"))), 
+             "Weak" =expression(bold(paste("(d) Weak (core-peripheral, ", bar(x), " = 1.85)"))))
 mylabel <- function(val) { return(lapply(val, function(x) arr[x])) }
@@
 
-**Over and under-represented groups on motif positions**
+**Over- and under-represented groups on motif positions**
 
@@
 
-The comparison of the functional group frequencies per motif position between empirical and simulated networks showed a `r over`$\%$ and `r under`$\%$ of over- (>75$^{th}$) and under- (<25th) represented functional groups in the different positions, respectively (**Figure 3**).
-Floral visitors showed a total of `r poll_over_75`$\%$ and `r poll_under_25`$\%$ of over- and under-represented functional groups in the different positions and plants `r plant_over_75`$\%$ and `r plant_under_25`$\%$ of over and under-represented groups, respectively.
-Notably, the differences across functional groups were more marked for floral visitors than for plant functional groups (the differences between min and max percentiles per position were generally two-three times larger for floral visitors).
-From most over- to under-represented floral visitors functional groups on the different motif positions (indicated with the dendrogram order in **Figure 3**), we found: bees, non-syrphids Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.
-Although plant functional groups showed less differences between them, there were also more represented functional groups than others, thus from most over- to under-represented groups on the different motif positions we found: self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', out.width="80%",fig.cap="\\textbf{Figure 3.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions.
+The comparison of the plant and floral visitor group frequencies per motif position between empirical and simulated networks showed a `r over`$\%$ and `r under`$\%$ of over- (>75$^{th}$) and under-represented (<25th) groups in the different positions, respectively (**Figure 3**).
+Floral visitors showed a total of `r poll_over_75`$\%$ and `r poll_under_25`$\%$ of over- and under-represented groups in the different positions and plants `r plant_over_75`$\%$ and `r plant_under_25`$\%$ of over- and under-represented groups, respectively.
+Notably, the differences across groups were more marked for floral visitors than for plant groups (the differences between min and max percentiles per position were generally two-three times larger for floral visitors).
+From most over- to under-represented floral visitors groups on the different motif positions (indicated with the dendrogram order in **Figure 3**), we found: bees, non-syrphids Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.
+Although plant functional groups showed less differences between them, there were also more represented groups than others, thus from most over- to under-represented groups on the different motif positions we found: self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', out.width="80%",fig.cap="\\textbf{Figure 3.} Heatmap indicating under- and over-representation of floral visitor and plant groups in the different motif positions.
 The different motif positions are dividied by the average path length clasification determined by Simmons et al.
-(2020).
+(2020) and they are ordered from the most densely connected motifs (strong or complete) to the less connected ones (weak or core-peripheral).
 The superior dendrogram indicates the differences across groups with the more separated groups showing larger differences."}
@@
 
-r_split <- c(rep(c("Fan"), 3),rep(c("Core-peripheral"), 2),"Complete",rep(c("Fan"),2),rep(c("Core-peripheral"), 4),
-             rep(c("Asymmetric complete"), 2), "Complete", rep(c("Core-peripheral"), 3),rep(c("Asymmetric complete"), 2),
-             "Complete", "Fan")
+r_split <- c(rep(c("Medium"), 3),rep(c("Weak"), 2),"Strong",rep(c("Medium"),2),rep(c("Weak"), 4),
+             rep(c("Medium-weak"), 2), "Strong", rep(c("Weak"), 3),rep(c("Medium-weak"), 2),
+             "Strong", "Medium")
 
 #set order of labels that avoids overlapping
-r_split <- factor(r_split, levels=c("Core-peripheral","Complete","Fan","Asymmetric complete"))
+
+r_split <- factor(r_split, levels=c("Strong","Medium","Medium-weak","Weak"))
 
@@
 
-r_split_plants <- c(rep(c("Fan"), 3),rep(c("Core-peripheral"), 2),"Complete",rep(c("Fan"),2),rep(c("Core-peripheral"), 3),
-                    rep(c("Asymmetric complete"), 2), "Complete", rep(c("Core-peripheral"), 4),rep(c("Asymmetric complete"), 2),
-                    "Complete", "Fan")
-
-r_split_plants <- factor(r_split, levels=c("Core-peripheral","Complete","Fan","Asymmetric complete"))
+r_split_plants <- c(rep(c("Medium"), 3),rep(c("Weak"), 2),"Strong",rep(c("Medium"),2),rep(c("Weak"), 3),
+                    rep(c("Medium-weak"), 2), "Strong", rep(c("Weak"), 4),rep(c("Medium-weak"), 2),
+                    "Strong", "Medium")
+
+r_split_plants <- factor(r_split, levels=c("Strong","Medium","Medium-weak","Weak"))
 

### 2022-02-10 Manuscript/Main_text_Oikos.Rmd
edits

@@
 The different observed frequencies on the different motif positions showed a hierarchical order of probabilities for floral visitors (**Figure 4**).
-That is, the functional group of 'bees' was the most abundant one on all motif positions followed by non-syrphid Diptera which was after bees, the second most frequent functional group on all positions.
+That is, the taxonomic group of 'bees' was the most abundant one on all motif positions followed by non-syrphid Diptera which was after bees, the second most frequent group on all positions.
 Then, the group of syrphids was the most abundant in all positions but two (positions 28 and 31 from motifs 11 and 12, respectively).
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 4.** Graphical representation of the probability of finding a given functional group $x$ in the position $\\alpha$ of motif $i$, $p_i(x,\\alpha)$, for all the possible motifs from two to five species in bipartite networks.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 4.** Graphical representation of the probability of finding a given plant and floral visitor group $x$ in the position $\\alpha$ of motif $i$, $p_i(x,\\alpha)$, for all the possible motifs from two to five species in bipartite networks.
 The slices in the nodes for a given functional group $x$ are proportional to the corresponding value of $p_i(x,\\alpha)$."}
@@
 
-The statistical comparison with z-scores between the observed and expected functional group combinations showed that we can not recover the observed combinations from its probability of occurrence.
+The statistical comparison with z-scores between the observed and expected plant and floral visitor group combinations showed that we can not recover the observed combinations from its probability of occurrence.
 In fact, most combinations are under- or over- represented and follow a modified Gaussian distribution (Johnson's $S_U$) with 65$\%$ of under-represented group combinations, 20$\%$ of no statistical difference and 15$\%$ of under-represented ones (**Figure 5**).
@@
 Finally, 5-node motifs were in similar proportions in the no statistical difference and over-represented categories (99$\%$ and 97$\%$, respectively) but they appeared in lower proportion in the under-represented category (89$\%$).
-When, we explore the identity on the different positions of the most probable motif combinations we find as expected that the most common functional groups rule these positions on the most probable motif combinations (lower panel **Figure 5**).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 5.** Z-score comparison (95% confidence level) of the observed and expected frequencies of motif combinations with four specific graphical examples of the most probable motifs of being observed for each category delimited by the z-score critical values: under-represented, no statistical difference and over-represented."}
+When, we explore the identity on the different positions of the most probable motif combinations we find as expected that the most common plant and floral visitor groups rule these positions on the most probable motif combinations (lower panel **Figure 5**).
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 5.** Z-score comparison (95% confidence level) of the observed and expected frequencies of motif combinations with four specific graphical examples of the most probable motifs of being observed for each category delimited by the z-score critical values: under-represented (red), no statistical difference (green) and over-represented (blue)."}
 

### 2022-03-05 Manuscript/Main_text_Oikos.Rmd
text update keep working in other pc

@@
 Detecting those relationships is not trivial since they go beyond pairwise interactions, but may get blurred when considering full network descriptors.
-However, recent work has shown the network meso-scale can capture this important information.
+However, recent work has shown the network meso-scale could capture this important information.
 The meso-scale describes network subgraphs representing patterns of interactions between a small number of species (i.e.
 motifs) and those constitute the building blocks of the whole network.
-Here, we have compiled 60 networks from 18 different studies and show that some motifs are consistently under- and over-represented worldwide, suggesting that the building blocks of plant-pollinator networks are not random.
-Furthermore, we found that distinct motif positions describing species ecological roles (e.g., generalization, indirect interactions) are occupied by different functional groups on both trophic levels.
+Despite the possible implications of network motifs to better capture species interactions, they remain overlooked in natural plant-pollinator networks.
+By exploring 60 networks from 18 different studies with wide geographical coverage we show that some motifs are consistently under- and over-represented worldwide, suggesting that the building blocks of plant-pollinator networks are not random.
+Furthermore, we found that distinct motif positions describing species ecological roles (e.g., generalization, indirect interactions) are occupied by different groups on both trophic levels.
 For instance, bees appear consistently in generalist motif positions and plants with higher levels of outcrossing tend to have a large number of indirect interactions.
-Interestingly, the realized combinations of different functional groups within a motif can not be retrieved from their joint probability distributions, indicating that functional group combinations are not random either.
-Our result highlight the non-random structure of indirect interactions in plant-pollinator networks and opens the door to predict novel interactions beyond pairwise interactions within a community context.
+Interestingly, the realized combinations of different groups within a motif can not be retrieved from their joint probability distributions, indicating that group combinations are not random either.
+Our result highlights the non-random structure of indirect interactions in plant-pollinator networks and opens the door to predict novel interactions beyond pairwise interactions within a community context.
 
@@
 In addition, the local species position within the network can define its degree of specialization [@bluthgen2006] or its role connecting the rest of the community [@olesen2007].
-Despite the unquestionable progress with the use of these metrics at both species and network level, condensing the information into a single metric implies the loss of relevant ecological information that obscure the understanding of the ecological processes [@cirtwill2018; @simmons2019].
+Despite the unquestionable progress with the use of these metrics at both species and network level, condensing the information into a single metric implies the loss of relevant ecological information that obscure the understanding of species interactions [@cirtwill2018; @simmons2019].
 
@@
 
-Despite motifs are abstract representations often decoupled from species ecology, linking the structural properties of the meso-scale with the species ecology can help the understanding of ecological processes.
+Despite motifs are abstract representations often decoupled from species ecology, linking the structural properties of the meso-scale with the species ecology can help the understanding of species interactions.
 For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species functional role [@stouffer2012; @baker2015].
@@
 Although some studies have evaluated plant reproductive strategies in plant-pollinator networks [@tur2013; @lazaro2020], this is an often overlooked aspect in a community context [@devaux2014] and rarely incorporated into plant-pollinator network studies.
-Hence, exploring how the main plant reproductive strategies integrate with the emergent motif framework can shed light on key aspects of ecosystem functioning.
+Hence, exploring how the main plant reproductive strategies integrate with the emergent motif framework can help the understanding of plant-pollinator interactions.
 
@@
 
-Following previous work [@simmons2019; @simmons2020], we broke down the plant-pollinator networks into their constituent motifs.
+Following previous work [@simmons2019b; @simmons2020], we broke down the plant-pollinator networks into their constituent motifs that can capture both direct and indirect interactions.
 Prior to analyses, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.
-To test the effect of singletones, we ran all analysis to the same set of networks, but considering only interactions whose frequency was greater than one (64.98$\%$ of interactions).
-Results are qualitatively consistent and are not further discussed in the main text (**Figures S1 and S2**).
-
-We calculated the frequency of all motifs up to five nodes (see **Figure 1**) for each empirical network, by using the _bmotif_ package version _2.0.2_ [@bmotifsimmons2019].
+All analyses were run with singletons (species with only one interaction detected) but we conducted a second exploration without singletons (64.98$\%$ of interactions) to evaluate the effect of rare species on the observed patterns.
+Results without singletons are qualitatively consistent and are not further discussed in the main text (**Figures S1 and S2**).
+
+We calculated the frequency of all motifs up to five nodes (17 different motifs in total; see **Figure 1**) for each empirical network, by using the _bmotif_ package version _2.0.2_ [@bmotifsimmons2019].
+Throughout the entire manuscript, floral visitors occupy the top nodes of the different motifs and plants the bottom ones.
 To control for variation in network size, motif frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains).
 Like @simmons2020, we classified the different motifs by their average path length into four different groups: (i) complete or strong ($\overline{x} = 1.38$), (ii) fan or medium-strong ($\overline{x} = 1.48$), (iii) assymmetric complete or medium-weak ($\overline{x} = 1.60$) and (iv) core-peripheral or weak ($\overline{x} = 1.85$).
+
 Moreover, we just used five-node motifs in our analyses for visualisation, interpretation and computational reasons.

### 2022-03-05 Manuscript/Main_text_Oikos.Rmd
Update on figure 2 with motifs, quite happy about the outcome!

@@
 library(ggforce) #workaround with ggforce to have facets with same sizes 
-
-p <- ggplot()+geom_point(data = d_2, aes(y=factor(motif), 100*percentil_sizeclass), shape=21,color="black",fill="azure2",size=1.75, alpha=0.3)+
+library(ggtext)
+
+labels <- c("2" = "*Motif 2* <img src='../Images/motif_2.png' width='22'/>" ,
+          "3"= "*Motif 3* <img src='../Images/motif_3.png' width='22'/>",
+          "4"= "*Motif 4* <img src='../Images/motif_4.png' width='22'/>",
+          "5"= "*Motif 5* <img src='../Images/motif_5.png' width='22'/>",
+          "6"= "*Motif 6* <img src='../Images/motif_6.png' width='22'/>",
+          "7"= "*Motif 7* <img src='../Images/motif_7.png' width='22'/>",
+          "8"= "*Motif 8* <img src='../Images/motif_8.png' width='22'/>",
+          "9"= "*Motif 9* <img src='../Images/motif_9.png' width='22'/>",
+          "10"= "*Motif 10* <img src='../Images/motif_10.png' width='22'/>",
+          "11"= "*Motif 11* <img src='../Images/motif_11.png' width='22'/>",
+          "12"= "*Motif 12* <img src='../Images/motif_12.png' width='22'/>",
+          "13"= "*Motif 13* <img src='../Images/motif_13.png' width='22'/>",
+          "14"= "*Motif 14* <img src='../Images/motif_14.png' width='22'/>",
+          "15"= "*Motif 15* <img src='../Images/motif_15.png' width='22'/>",
+          "16"= "*Motif 16* <img src='../Images/motif_16.png' width='22'/>",
+          "17"= "*Motif 17* <img src='../Images/motif_17.png' width='22'/>")
+
+p <- ggplot()+geom_point(data = d_2 , aes(y=factor(motif), 100*percentil_sizeclass), shape=21,color="black",fill="azure2",size=1.75, alpha=0.3)+
   geom_errorbar(data = d_2,aes(y = factor(motif), xmin=100*(mean-SE), xmax=100*(mean+SE)), 
@@
   theme(strip.text = element_text(face="bold", size=10, hjust=0),
-        panel.border=element_rect(color="black",size=1.2))
+        panel.border=element_rect(color="black",size=1.2))+
+  scale_y_discrete(name = NULL,
+                   labels = labels) +
+  theme(axis.text.y = ggtext::element_markdown())
 

### 2022-03-05 Scripts/1_Figure_2.R

@@ -1,0 +1,84 @@
+
+equidistribution <- function(number_nodes){
+  
+  x_width <- 5.5/(number_nodes+1)
+  
+  x_result <- rep(-1.5,number_nodes)
+  
+  for(i in 1:number_nodes){
+    
+    x_result[i] <- x_result[i] + i*x_width
+    
+  }
+  
+  return(x_result)
+  
+}
+
+
+
+plot_motif_positions <- function(motif_number){
+  
+  motifs_raw_data <- read_csv("Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
+  
+  motif_data <- motifs_raw_data %>% filter(motif_id == motif_number)
+  
+  
+  # Create dataframe with node positions
+  
+  labdown = motif_data$plant %>% unique()
+  
+  
+  xdown = equidistribution(length(labdown))
+  
+  ydown = rep(0,length(labdown))
+  
+  labup = motif_data$pollinator %>% unique()
+  
+  xup = equidistribution(length(labup))
+  
+  yup = rep(1,length(labup))
+  
+  d_nodes=data.frame(x=c(xdown,xup),
+                     y=c(ydown,yup),
+                     label = c(labdown,labup))
+  
+  
+  # Create a dataframe with links
+  
+  plant_positions <- data.frame(plant = labdown,
+                                xdown = xdown,
+                                ydown = ydown)
+  
+  pollinator_positions <- data.frame(pollinator = labup,
+                                     xup = xup,
+                                     yup = yup)
+  
+  link_df <- motif_data %>% left_join(plant_positions, by = "plant") %>% 
+    left_join(pollinator_positions, by = "pollinator")
+  
+  # Before plotting the motif, we remove letters from the node position id
+  
+  d_nodes$label <- gsub("[^0-9.-]", "", d_nodes$label)
+  
+  ggplot(data=d_nodes, aes(x, y)) +
+    scale_shape_identity() +
+    geom_segment(data = link_df, aes(x=xdown, y=ydown, xend = xup, yend = yup), size = 2, color = "grey20")+
+    geom_point(aes(color = as.factor(label)),size=32, shape=21,color="black",fill="black")+
+   # geom_text(aes(x, y , label = label),size=4)+
+    #   scale_color_brewer(palette = "Set2")+
+  #  xlim(-1.5,4)+ ylim(-0.5,1.5)+
+    theme(panel.background = element_blank(),
[…]

### 2022-03-05 Scripts/2_Figure_2.R

@@ -1,0 +1,78 @@
+library(tidyverse)
+library(RColorBrewer)
+source("Scripts/trial.R")
+
+motif_number <- 1
+p1 <- plot_motif_positions(motif_number)
+
+ggsave("Images/motif_1.png")
+
+motif_number <- 2
+p2 <- plot_motif_positions(motif_number)
+ggsave("Images/motif_2.png")
+
+motif_number <- 3
+p3 <- plot_motif_positions(motif_number)
+ggsave("Images/motif_3.png")
+
+motif_number <- 4
+p4 <- plot_motif_positions(motif_number)
+ggsave("Images/motif_4.png")
+
+motif_number <- 5
+p5 <- plot_motif_positions(motif_number)
+ggsave("Images/motif_5.png")
+
+motif_number <- 6
+p6 <- plot_motif_positions(motif_number)
+ggsave("Images/motif_6.png")
+
+motif_number <- 7
+p7 <- plot_motif_positions(motif_number)
+ggsave("Images/motif_7.png")
+
+motif_number <- 8   
+p8 <- plot_motif_positions(motif_number)
+ggsave("Images/motif_8.png")
+
+motif_number <- 9
+p9 <- plot_motif_positions(motif_number)
+ggsave("Images/motif_9.png")
+
+motif_number <- 10
+p10 <- plot_motif_positions(motif_number)
+ggsave("Images/motif_10.png")
+
+motif_number <- 11
+p11 <- plot_motif_positions(motif_number)
+ggsave("Images/motif_11.png")
+
+motif_number <- 12
+p12 <- plot_motif_positions(motif_number)
+ggsave("Images/motif_12.png")
+
+motif_number <- 13
+p13 <- plot_motif_positions(motif_number)
+ggsave("Images/motif_13.png")
+
+motif_number <- 14
+p14 <- plot_motif_positions(motif_number)
+ggsave("Images/motif_14.png")
+
+motif_number <- 15
+p15 <- plot_motif_positions(motif_number)
+ggsave("Images/motif_15.png")
+
+motif_number <- 16
+p16 <- plot_motif_positions(motif_number)
+ggsave("Images/motif_16.png")
+
+motif_number <- 17
+p17 <- plot_motif_positions(motif_number)
+ggsave("Images/motif_17.png")
+
+
+library(patchwork)
+
[…]

### 2022-03-05 Manuscript/Main_text_Oikos.Rmd
Edits on text path length classification, good for today...

@@
 Although some studies have evaluated plant reproductive strategies in plant-pollinator networks [@tur2013; @lazaro2020], this is an often overlooked aspect in a community context [@devaux2014] and rarely incorporated into plant-pollinator network studies.
-Hence, exploring how the main plant reproductive strategies integrate with the emergent motif framework can help the understanding of plant-pollinator interactions.
+Hence, exploring how the main plant reproductive strategies integrate with the emergent motif framework could help to progress knowledge on plant-pollinator interactions.
 
@@
 Prior to analyses, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.
-All analyses were run with singletons (species with only one interaction detected) but we conducted a second exploration without singletons (64.98$\%$ of interactions) to evaluate the effect of rare species on the observed patterns.
+All analyses were run considering singletons (species with only one interaction detected) but we conducted a second exploration without singletons (64.98$\%$ of interactions) to evaluate the effect of rare species on the observed patterns.
 Results without singletons are qualitatively consistent and are not further discussed in the main text (**Figures S1 and S2**).
@@
 We calculated the frequency of all motifs up to five nodes (17 different motifs in total; see **Figure 1**) for each empirical network, by using the _bmotif_ package version _2.0.2_ [@bmotifsimmons2019].
+We focused exclusively on motifs up to five nodes in our analyses for computational reasons and the ease of visualization and interpretation of a reduced set of less complex motifs.
 Throughout the entire manuscript, floral visitors occupy the top nodes of the different motifs and plants the bottom ones.
 To control for variation in network size, motif frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains).
-Like @simmons2020, we classified the different motifs by their average path length into four different groups: (i) complete or strong ($\overline{x} = 1.38$), (ii) fan or medium-strong ($\overline{x} = 1.48$), (iii) assymmetric complete or medium-weak ($\overline{x} = 1.60$) and (iv) core-peripheral or weak ($\overline{x} = 1.85$).
-
-Moreover, we just used five-node motifs in our analyses for visualisation, interpretation and computational reasons.
-Finally, we also excluded two-node motifs (or links) from our analyses because their normalised frequencies would always equal one.
+In addition, we excluded two-node motifs (or links) from our analyses because their normalised frequencies would always equal one.
+Like @simmons2020, we classified the different motifs by their average path length (mean number of links between all pairs of nodes) into four different groups: (i) complete or strong ($\overline{x} = 1.38$), (ii) fan or medium-strong ($\overline{x} = 1.48$), (iii) assymmetric complete or medium-weak ($\overline{x} = 1.60$) and (iv) core-peripheral or weak ($\overline{x} = 1.85$).
+More densely connected motifs (e.g., complete or fan groups) experience higher number of indirect interactions in contrast to motifs that are less densely connected (e.g., medium-weak or weak groups).
 

### 2022-03-06 Scripts/Scripts_Alfonso/direct_indirect_interactions_position.R
direct_indirect_interactions

@@ -1,0 +1,27 @@
+
+library(tidyverse)
+
+motifs_raw_data <- read_csv("Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
+
+plant_interactions <- motifs_raw_data %>% group_by(motif_id,nodes,plant) %>% count() %>% 
+  rename(direct_interactions = n, position = plant) %>% 
+  mutate(type = "plant",
+         indirect_interactions = (nodes - 1) - direct_interactions,
+         percentage_indirect_interactions = indirect_interactions/(nodes-1))
+
+pollinator_interactions <- motifs_raw_data %>% group_by(motif_id,nodes,pollinator) %>% count() %>% 
+  rename(direct_interactions = n, position = pollinator) %>% 
+  mutate(type = "pollinator",
+         indirect_interactions = (nodes - 1) - direct_interactions,
+         percentage_indirect_interactions = indirect_interactions/(nodes-1))
+
+motif_interactions_aux <- bind_rows(pollinator_interactions,plant_interactions)
+
+# Remove letters from positions
+motif_interactions_aux$position <- as.numeric(gsub("[^0-9.-]", "", motif_interactions_aux$position))
+motif_interactions <- motif_interactions_aux %>% distinct ()
+
+# Facets per percentage of indirect interactions:
+motif_interactions$percentage_indirect_interactions %>% unique() %>% sort()
+
+write_csv(motif_interactions, "Data/Data_processing/Motifs_connections/motif_interactions.csv")

### 2022-03-06 Manuscript/Main_text_Oikos.Rmd

@@
 
-Despite motifs are abstract representations often decoupled from species ecology, linking the structural properties of the meso-scale with the species ecology can help the understanding of species interactions.
+By linking the structural properties of the meso-scale with the species ecology we can progress knowledge on species interactions.
 For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species functional role [@stouffer2012; @baker2015].
-However, it is unclear how the species ecology and life-history traits determines the species' functional role within the network of interactions [@coux2016].
+Yet, our understanding of the ecological implications of network motifs in real plant-pollinator networks remains in its infancy.
+Moreover, it is unclear how the species ecology and life-history traits determines the species' functional role within the network of interactions [@coux2016].
 For example, large pollinators can forage larger distances [@greenleaf2007], deposit greater pollen quantities [@foldesi2021] and handle complex zygomorphic flowers in comparison with small pollinators that are restricted to lower floral complexity [@gong2009].

### 2022-03-06 Manuscript/Supporting_information_Oikos.Rmd

@@
 library(ggforce) #workaround with ggforce to have facets with same sizes 
+library(ggtext)
+
+labels <- c("2" = "*Motif 2* <img src='../Images/motif_2.png' width='22'/>" ,
+          "3"= "*Motif 3* <img src='../Images/motif_3.png' width='22'/>",
+          "4"= "*Motif 4* <img src='../Images/motif_4.png' width='22'/>",
+          "5"= "*Motif 5* <img src='../Images/motif_5.png' width='22'/>",
+          "6"= "*Motif 6* <img src='../Images/motif_6.png' width='22'/>",
+          "7"= "*Motif 7* <img src='../Images/motif_7.png' width='22'/>",
+          "8"= "*Motif 8* <img src='../Images/motif_8.png' width='22'/>",
+          "9"= "*Motif 9* <img src='../Images/motif_9.png' width='22'/>",
+          "10"= "*Motif 10* <img src='../Images/motif_10.png' width='22'/>",
+          "11"= "*Motif 11* <img src='../Images/motif_11.png' width='22'/>",
+          "12"= "*Motif 12* <img src='../Images/motif_12.png' width='22'/>",
+          "13"= "*Motif 13* <img src='../Images/motif_13.png' width='22'/>",
+          "14"= "*Motif 14* <img src='../Images/motif_14.png' width='22'/>",
+          "15"= "*Motif 15* <img src='../Images/motif_15.png' width='22'/>",
+          "16"= "*Motif 16* <img src='../Images/motif_16.png' width='22'/>",
+          "17"= "*Motif 17* <img src='../Images/motif_17.png' width='22'/>")
 

### 2022-03-06 Scripts/Direct_Indirect.R
Preparing facets

@@ -3,75 +3,52 @@ library(scatterpie)
 library(RColorBrewer)
 library(tidyverse)
 
+
+direct_indirect <- read_csv("Data/Data_processing/Motifs_connections/motif_interactions.csv")
+colnames(direct_indirect)
+direct_indirect <- direct_indirect %>% select(motif_id,position,direct_interactions, indirect_interactions,percentage_indirect_interactions)
+
 plant_means_reordered <- read_csv("Data/Csv/plant_abs_freq_means.csv")
 pollinator_means_reordered <- read_csv("Data/Csv/pollinator_abs_freq_means.csv")
 #Filter out in order to have just 6 FG'S
 pollinator_means_reordered <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds", "Lizards", "Other_insects"))
 
+#Check pol levels
+levels(factor(pollinator_means_reordered$Node_FG))
 
-# Pollinator--------
-pollinator_trial <- pollinator_means_reordered %>% select(-mean, -SE)# %>% 
-  #spread(Node_FG,mean_natural_units)
+#Dplyr merge
+joined_tibble <- left_join(direct_indirect, pollinator_means_reordered)
 
-#Select potions of interest just for 3 species
-s <- c(seq(from=3, to=16))
-#filter dataset
-d <- pollinator_trial %>% filter(position %in% s) %>% filter(Node_FG=="Bee")
-d$indirect <- NA
-#Add number of indirect interactions manually
-#Faster for now, do not know how to code it easily
-
-#3species
-d$indirect[d$position=="3"] <- "1"
-d$indirect[d$position=="4"] <- "0"
-d$indirect[d$position=="5"] <- "0"
-d$indirect[d$position=="6"] <- "1"
-#4species
-d$indirect[d$position=="7"] <- "0"
-d$indirect[d$position=="8"] <- "2"
-d$indirect[d$position=="9"] <- "1"
-d$indirect[d$position=="10"] <- "1"
-d$indirect[d$position=="11"] <- "1"
-d$indirect[d$position=="12"] <- "1"
-d$indirect[d$position=="13"] <- "1"
-d$indirect[d$position=="14"] <- "1"
-d$indirect[d$position=="15"] <- "2"
-d$indirect[d$position=="16"] <- "0"
-#5species
-d$indirect[d$position=="17"] <- "0"
-d$indirect[d$position=="18"] <- "0"
[…]

### 2022-03-07 Scripts/Direct_Indirect.R
keep working in other pc

@@ -27,7 +27,11 @@ bees$position <- as.factor(bees$position)
 bees$percentage_indirect_interactions <- as.factor(bees$percentage_indirect_interactions)
 bee_plot <- ggplot(bees,aes(position,mean_natural_units))+
   geom_col(position = "dodge")+
-  facet_grid(.~percentage_indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Bees")
+  facet_grid(.~percentage_indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Bees")+
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())+
+  ylab("Frequency")
 
 #Coleoptera
 cole <- joined_tibble %>% filter(Node_FG=="Coleoptera")
@@ -37,7 +41,11 @@ cole$position <- as.factor(cole$position)
 cole$percentage_indirect_interactions <- as.factor(cole$percentage_indirect_interactions)
 cole_plot <- ggplot(cole,aes(position,mean_natural_units))+
   geom_col(position = "dodge")+
-  facet_grid(.~percentage_indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Coleoptera")
+  facet_grid(.~percentage_indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Coleoptera")+
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())+
+  ylab("Frequency")
 
 #Lepidoptera
 lepi <- joined_tibble %>% filter(Node_FG=="Lepidoptera")
@@ -47,8 +55,46 @@ lepi$position <- as.factor(lepi$position)
 lepi$percentage_indirect_interactions <- as.factor(lepi$percentage_indirect_interactions)
 lepi_plot <- ggplot(lepi,aes(position,mean_natural_units))+
   geom_col(position = "dodge")+
-  facet_grid(.~percentage_indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Lepidoptera")
+  facet_grid(.~percentage_indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Lepidoptera") +
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())+
+  ylab("Frequency")
 
+#Non-bee-Hymenoptera
[…]

### 2022-03-07 Scripts/Scripts_Alfonso/direct_indirect_interactions_position.R
Update_indirect_direct_interactions_table

@@ -3,17 +3,39 @@ library(tidyverse)
 
 motifs_raw_data <- read_csv("Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
 
-plant_interactions <- motifs_raw_data %>% group_by(motif_id,nodes,plant) %>% count() %>% 
+
+plant_indirect_int_shame_group <- motifs_raw_data %>% select(-pollinator) %>% 
+  distinct () %>% 
+  group_by(motif_id,nodes) %>% count() %>% 
+  rename(indirect_same_type = n) %>% mutate(indirect_same_type = indirect_same_type-1)
+
+plant_interactions_aux <- motifs_raw_data %>% group_by(motif_id,nodes,plant) %>% count() %>% 
   rename(direct_interactions = n, position = plant) %>% 
   mutate(type = "plant",
          indirect_interactions = (nodes - 1) - direct_interactions,
          percentage_indirect_interactions = indirect_interactions/(nodes-1))
 
-pollinator_interactions <- motifs_raw_data %>% group_by(motif_id,nodes,pollinator) %>% count() %>% 
+plant_interactions <- plant_interactions_aux %>% left_join(plant_indirect_int_shame_group,
+                                                           by = c("motif_id","nodes")) %>%
+  mutate(ind_same_type_over_directed_int=indirect_same_type/direct_interactions)
+
+
+pollinator_indirect_int_shame_group <- motifs_raw_data %>% select(-plant) %>% 
+  distinct () %>% 
+  group_by(motif_id,nodes) %>% count() %>% 
+  rename(indirect_same_type = n) %>% mutate(indirect_same_type = indirect_same_type-1)
+
+pollinator_interactions_aux <- motifs_raw_data %>% group_by(motif_id,nodes,pollinator) %>% count() %>% 
   rename(direct_interactions = n, position = pollinator) %>% 
   mutate(type = "pollinator",
          indirect_interactions = (nodes - 1) - direct_interactions,
          percentage_indirect_interactions = indirect_interactions/(nodes-1))
+
+pollinator_interactions <- pollinator_interactions_aux %>% 
+  left_join(pollinator_indirect_int_shame_group,by = c("motif_id","nodes")) %>%
+  mutate(ind_same_type_over_directed_int=indirect_same_type/direct_interactions)
+
+
 
 motif_interactions_aux <- bind_rows(pollinator_interactions,plant_interactions)
 
[…]

### 2022-03-07 Manuscript/Indirect_direct.Rmd
ind/direct plot

---
title: ""
output:
  pdf_document: default
  html_document: default
---

```{r, echo=FALSE, message=FALSE, cache=FALSE, fig.pos="t", warning=FALSE,out.width="75%",fig.align="center", fig.width=10,fig.height=12}

library(ggplot2)
library(scatterpie)
library(RColorBrewer)
library(tidyverse)

direct_indirect <- read_csv("../Data/Data_processing/Motifs_connections/motif_interactions.csv")
direct_indirect <- direct_indirect %>% select(motif_id,position,direct_interactions, indirect_interactions,ind_same_type_over_directed_int)

plant_means_reordered <- read_csv("../Data/Csv/plant_abs_freq_means.csv")
pollinator_means_reordered <- read_csv("../Data/Csv/pollinator_abs_freq_means.csv")
#Filter out in order to have just 6 FG'S
pollinator_means_reordered <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds", "Lizards", "Other_insects"))

#Dplyr merge
joined_tibble <- left_join(direct_indirect, pollinator_means_reordered)

#Bees
bees <- joined_tibble %>% filter(Node_FG=="Bee")
bees$ind_same_type_over_directed_int <- round(bees$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
bees$position <- as.factor(bees$position)
bees$ind_same_type_over_directed_int <- as.factor(bees$ind_same_type_over_directed_int)
bee_plot <- ggplot(bees,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Bees")+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  ylab("Frequency")+theme_bw() + xlab("")

#Coleoptera
cole <- joined_tibble %>% filter(Node_FG=="Coleoptera")
cole$ind_same_type_over_directed_int <- round(cole$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
cole$position <- as.factor(cole$position)
cole$ind_same_type_over_directed_int <- as.factor(cole$ind_same_type_over_directed_int)
cole_plot <- ggplot(cole,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Coleoptera")+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  ylab("Frequency")+theme_bw() + xlab("")

#Lepidoptera
lepi <- joined_tibble %>% filter(Node_FG=="Lepidoptera")
lepi$ind_same_type_over_directed_int <- round(lepi$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
lepi$position <- as.factor(lepi$position)
lepi$ind_same_type_over_directed_int <- as.factor(lepi$ind_same_type_over_directed_int)
lepi_plot <- ggplot(lepi,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Lepidoptera") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  ylab("Frequency")+theme_bw()+ xlab("")

#Non-bee-Hymenoptera
non_bee <- joined_tibble %>% filter(Node_FG=="Non-bee-Hymenoptera")
non_bee$ind_same_type_over_directed_int <- round(non_bee$ind_same_type_over_directed_int, digits = 2)
#Convert to factor
non_bee$position <- as.factor(non_bee$position)
non_bee$ind_same_type_over_directed_int <- as.factor(non_bee$ind_same_type_over_directed_int)
non_bee_plot <- ggplot(non_bee,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Non-bee-Hymenoptera") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  ylab("Frequency")+theme_bw()+ xlab("")

#Non-syrphids-diptera
non_syr <- joined_tibble %>% filter(Node_FG=="Non-syrphids-diptera")
non_syr$ind_same_type_over_directed_int <- round(non_syr$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
non_syr$position <- as.factor(non_syr$position)
non_syr$ind_same_type_over_directed_int <- as.factor(non_syr$ind_same_type_over_directed_int)
non_syr_plot <- ggplot(non_syr,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Non-syrphids-diptera")+
theme(axis.title.x=element_blank(),
      axis.text.x=element_blank(),
      axis.ticks.x=element_blank())+
  ylab("Frequency")+theme_bw()+ xlab("")

#Syrphids
syr <- joined_tibble %>% filter(Node_FG=="Syrphids")
syr$ind_same_type_over_directed_int <- round(syr$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
syr$position <- as.factor(syr$position)
syr$ind_same_type_over_directed_int <- as.factor(syr$ind_same_type_over_directed_int)
syr_plot <- ggplot(syr,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Syrphids") +
   ylab("Frequency")+theme_bw() + xlab("Position within motif")

library(patchwork)
bee_plot / cole_plot / lepi_plot / non_bee_plot / non_syr_plot / syr_plot + plot_annotation(
  title = 'Proportion indirect/direct interactions (0, 0.3, 0.5, 1, 2, 3)',
  theme = theme(plot.title = element_text(size = 18, face="bold")))

```

### 2022-03-08 Manuscript/Figures/Figure_2.Rmd
Edits on text

--- 2022-03-05 Manuscript/Main_text_Oikos.Rmd
@@
 ---
-title: "The non-random assembly of functional motifs in plant-pollinator networks worldwide"
-editor_options:
-  chunk_output_type: console
-header-includes:
-- \usepackage{booktabs}
-- \usepackage{longtable}
-- \usepackage{array}
-- \usepackage{multirow}
-- \usepackage{wrapfig}
-- \usepackage{float}
-- \usepackage{colortbl}
-- \usepackage{pdflscape}
-- \usepackage{tabu}
-- \usepackage{threeparttable}
-- \usepackage{threeparttablex}
-- \usepackage[normalem]{ulem}
-- \usepackage{makecell}
-- \usepackage{xcolor}
-- \usepackage{caption,setspace}
-- \captionsetup[figure]{labelformat=empty}
-- \floatplacement{figure}{H}
-- \usepackage[skip=3pt]{caption}
-- \captionsetup[figure]{labelformat=empty}
-- \usepackage{lscape}
-- \newcommand{\blandscape}{\begin{landscape}}
-- \newcommand{\elandscape}{\end{landscape}}
 output:
@@
   html_document: default
-  word_document: default
-always_allow_html: true
-bibliography: bibliography.bib
-biblio-style: apalike
-csl: oikos.csl #oikos style from zotero styles
-
 ---
-
-\captionsetup[table]{labelformat=empty}
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
-
-# Abstract
-
-\singlespacing
-
-Ecological processes leave distinct structural imprints on species interactions shaping the topology of mutualistic networks.
-Detecting those relationships is not trivial since they go beyond pairwise interactions, but may get blurred when considering full network descriptors.
-However, recent work has shown the network meso-scale could capture this important information.
-The meso-scale describes network subgraphs representing patterns of interactions between a small number of species (i.e.
-motifs) and those constitute the building blocks of the whole network.
-Despite the possible implications of network motifs to better capture species interactions, they remain overlooked in natural plant-pollinator networks.
-By exploring 60 networks from 18 different studies with wide geographical coverage we show that some motifs are consistently under- and over-represented worldwide, suggesting that the building blocks of plant-pollinator networks are not random.
-Furthermore, we found that distinct motif positions describing species ecological roles (e.g., generalization, indirect interactions) are occupied by different groups on both trophic levels.
-For instance, bees appear consistently in generalist motif positions and plants with higher levels of outcrossing tend to have a large number of indirect interactions.
-Interestingly, the realized combinations of different groups within a motif can not be retrieved from their joint probability distributions, indicating that group combinations are not random either.
-Our result highlights the non-random structure of indirect interactions in plant-pollinator networks and opens the door to predict novel interactions beyond pairwise interactions within a community context.
-
-Keyworkds: plant-pollinator networks, plant-pollinator interactions, network motifs, functional groups, plant traits, floral visitors
-
-\doublespacing
-
-# Introduction
-
-Ecological communities are formed by a plethora of interacting species that form networks of interactions.
-Because of the tremendous complexity of these ecological networks, species interactions are generally condensed in metrics that summarize this information [@guimaraes2020].
-Plant-pollinator interactions are no exception, and they are often studied with indices that aggregate the information at the species (micro-scale) or network level (macro-scale).
-For example, plant-pollinator network level approaches have identified common invariant structural properties across networks, including a degree distribution that decays as a power law [@jordano1987], nestedness [@bascompte2003], or modularity [@olesen2007].
-In addition, the local species position within the network can define its degree of specialization [@bluthgen2006] or its role connecting the rest of the community [@olesen2007].
-Despite the unquestionable progress with the use of these metrics at both species and network level, condensing the information into a single metric implies the loss of relevant ecological information that obscure the understanding of species interactions [@cirtwill2018; @simmons2019].
-
-Traditionally, plant-pollinator research has focused on direct interactions but overlooked indirect interactions (i.e., the mediated effect between two species by a third species), such as facilitative or competitive interactions between plants for pollinators [@moeller2004; @sargent2008].
-Despite the widespread nature of indirect interactions in ecological communities [@strauss1991], plant-pollinator research often fails to finely capture those indirect interactions with the conventional analytical tools that condense the information either by species (e.g., interaction frequency) or in global topological indices (e.g., nestedness).
-Nonetheless, the emerging framework of network motifs (small sub-networks recorded within a given network) in plant-pollinator research allows to consider both direct and indirect interactions [@simmons2019].
-Motifs are often referred to as the building blocks of a network that depict subsets of interactions [@milo2002].
-The analysis of network motifs in plant-pollinator networks have revealed that the different ecological processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions [@simmons2020].
-Yet, the global patterns of indirect interactions in real plant-pollinator networks are still unknown (e.g., over- and under- represented motifs).
-
-Despite motifs are abstract representations often decoupled from species ecology, linking the structural properties of the meso-scale with the species ecology can help the understanding of species interactions.
-For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species functional role [@stouffer2012; @baker2015].
-However, it is unclear how the species ecology and life-history traits determines the species' functional role within the network of interactions [@coux2016].
-For example, large pollinators can forage larger distances [@greenleaf2007], deposit greater pollen quantities [@foldesi2021] and handle complex zygomorphic flowers in comparison with small pollinators that are restricted to lower floral complexity [@gong2009].
-How this different pollinator behavior translates into their interaction topology is unknown.
-Similarly, recent empirical findings indicate that the meso-scale is the best descriptor of plant reproductive success [@allen2021], but little is known about how plants reproductive strategies shape their position within the network of interactions.
-Although some studies have evaluated plant reproductive strategies in plant-pollinator networks [@tur2013; @lazaro2020], this is an often overlooked aspect in a community context [@devaux2014] and rarely incorporated into plant-pollinator network studies.
-Hence, exploring how the main plant reproductive strategies integrate with the emergent motif framework can help the understanding of plant-pollinator interactions.
-
-Here, we used 60 plant-pollinator networks from 18 different studies and 14 countries, alongside functional groups of plants and taxonomic groups of floral visitors based on functional traits and taxonomic rank, respectively.
-To obtain plant functional groups, we used a comprehensive dataset that included floral, reproductive and vegetative traits compiled in a larger set of networks.
-Floral visitor groups were divided by the main taxonomic groups that differed in life form and behaviour.
-Once we split the different plant-pollinator networks into their motif elements, we explored: (i) if there is a common invariant structural property in the overall motif networks (i.e.
-over- and under-represented motifs); (ii) which plant and pollinator groups are over- and under-represented in the different motif positions; and, (iii) if there are over- and under-represented plant and pollinator group combinations within a motif.
-
-# Methods
-
-**Plant-pollinator studies**
-
-We have compiled 60 plant-pollinator networks from 18 different studies (**Table S1**).
-All studies sampled plant-pollinator interactions in natural systems and were selected based on wide geographical coverage and presence of interaction frequency as a measure of interaction strength.
-In total, there were 503 plant species, 1,111 floral visitors species and 6,248 pairwise interactions registered.
-For ease of data manipulation, plant and floral visitor species names were standardize with the help of the R package _taxize_ version _0.9.99_ [@chamberlain2020].
-All analyses and data manipulation were conducted in R _version 4.0.5_ [@R].
-
-**Plant and floral visitor groups**
-
-First, plant species were grouped through hierarchical clustering into the optimal number of functional groups that summarized the main plant reproductive strategies.
-For this, we used the trait dataset collated in @lanuza2021 that comprised a total of 1506 species including the 503 species considered in this study (**Table S2**).
-This dataset consisted on 8 floral, 4 reproductive and 3 vegetative traits excluding traits with high percentage of missing values (over 30$\%$; **Table S3**).
-We opted to calculate the plant functional groups on this larger set of species because of the higher accuracy when delimiting functional groups with that many variables and species [@dolnicar2014].
-To feed the clustering analysis, we calculated the distance between the different qualitative and scaled quantitative variables with Gower distance [@gower1971].
-For this, we used the function _gowdis_ with method _ward.D2_ from the package _FD_ version _1.0-12_ [@laliberte2014].
-Finally, we conducted hierarchical clustering with the function _hclust_ from the _R_ stats package version _4.0.5_ and calculated the optimal number of clusters with the function _kgs_ from the package _maptree_ version _1.4-7_ [@white2009].
-
-Second, floral visitors were grouped into taxonomic groups based on taxonomic rank as done similarly in past plant-pollinator studies [@fenster2004; @ollerton2009].
-We opted to divide floral visitors on the taxonomic rank level and not with functional traits because the main orders of floral visitors differed in form and behaviour and had lower superior taxonomical complexity (i.e., floral visitors had 6 orders versus plants that had 38).
-Thus, this allowed us to group floral visitors into groups that represented approximately the main life strategies of the possible pollinators: (i) bees (Hymenoptera-Anthophila), (ii) non-bee Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Syrphidae-Diptera), (iv) non-syrphids-Diptera, (v) Lepidoptera and (vi) Coleoptera.
-However, a minor set of species belonged to other taxonomic groups that were considered in analyses but not discussed further because of their low representation in the full set of networks (3.55$\%$ of the total interactions recorded).
-These taxonomic groups were 'lizards', 'birds' and 'other insects'.
-This last group was formed by a mix of uncommon insect taxa on the full set of networks.
-
-**Overall motif patterns**
-
-Following previous work [@simmons2019b; @simmons2020], we broke down the plant-pollinator networks into their constituent motifs that can capture both direct and indirect interactions.
-Prior to analyses, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.
-All analyses were run with singletons (species with only one interaction detected) but we conducted a second exploration without singletons (64.98$\%$ of interactions) to evaluate the effect of rare species on the observed patterns.
-Results without singletons are qualitatively consistent and are not further discussed in the main text (**Figures S1 and S2**).
-
-We calculated the frequency of all motifs up to five nodes (17 different motifs in total; see **Figure 1**) for each empirical network, by using the _bmotif_ package version _2.0.2_ [@bmotifsimmons2019].
-Throughout the entire manuscript, floral visitors occupy the top nodes of the different motifs and plants the bottom ones.
-To control for variation in network size, motif frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains).
-Like @simmons2020, we classified the different motifs by their average path length into four different groups: (i) complete or strong ($\overline{x} = 1.38$), (ii) fan or medium-strong ($\overline{x} = 1.48$), (iii) assymmetric complete or medium-weak ($\overline{x} = 1.60$) and (iv) core-peripheral or weak ($\overline{x} = 1.85$).
-
-Moreover, we just used five-node motifs in our analyses for visualisation, interpretation and computational reasons.
-Finally, we also excluded two-node motifs (or links) from our analyses because their normalised frequencies would always equal one.
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, fig.pos="t", warning=FALSE,out.width="75%",fig.align="center", fig.cap="\\textbf{Figure 1.} Adapted figure of Simmons et al., 2019 with all the possible motifs from two to five species in bipartite networks.
-There is a total of 17 possible motifs with 46 different positions denoted within each node.", fig.width=10,fig.height=8}
-library(tidyverse)
-library(RColorBrewer)
-source("../Scripts/Scripts_Alfonso/plot_motif_positionsV2.R")
-
-motif_number <- 1
-p1 <- plot_motif_positions(motif_number)
-
-motif_number <- 2
-p2 <- plot_motif_positions(motif_number)
-
-motif_number <- 3
-p3 <- plot_motif_positions(motif_number)
-
-motif_number <- 4
-p4 <- plot_motif_positions(motif_number)
-
-motif_number <- 5
-p5 <- plot_motif_positions(motif_number)
-
-motif_number <- 6
-p6 <- plot_motif_positions(motif_number)
-
-motif_number <- 7
-p7 <- plot_motif_positions(motif_number)
-
-motif_number <- 8   
-p8 <- plot_motif_positions(motif_number)
-
-motif_number <- 9
-p9 <- plot_motif_positions(motif_number)
-
-motif_number <- 10
-p10 <- plot_motif_positions(motif_number)
-
-motif_number <- 11
-p11 <- plot_motif_positions(motif_number)
-
-motif_number <- 12
-p12 <- plot_motif_positions(motif_number)
-
-motif_number <- 13
-p13 <- plot_motif_positions(motif_number)
-
-motif_number <- 14
-p14 <- plot_motif_positions(motif_number)
-
-motif_number <- 15
-p15 <- plot_motif_positions(motif_number)
-
-motif_number <- 16
-p16 <- plot_motif_positions(motif_number)
-
-motif_number <- 17
-p17 <- plot_motif_positions(motif_number)
-
-library(patchwork)
-
-(p1 & ylab("2 species")| p2 & ylab("3 species") | p3 )/ (p4 & ylab("4 species")| p5 | p6 | p7)/ (p8  & ylab("5 species")| p9 | p10 | p11 | p12) / (p13 & ylab("5 species")| p14 | p15 | p16 | p17) & theme(axis.title.y = element_text(color="black", size=14, face="bold")) #+
- #plot_annotation(tag_levels = '1')
-
-```
-
-**MA FORTUNA, what about degree?**
-
-To assess the significance of the observed frequencies, we created 1,000 simulated networks for each binary network using the _nullmodel_ function and the _vaznull_ model in the _bipartite_ package version _2.14_ [@dormann2009].
-Generated networks had the same number of plants and floral visitors, as well as the same connectance of their corresponding empirical networks.
-After extracting the motif frequencies from the simulated networks, for each motif type and empirical network, we calculated the percentage of simulated networks whose frequencies were smaller than the ones observed, that is, we estimated the percentile of the observed motif frequencies.
-Motifs whose percentile is close to 0 or 100 are under- or over-represented in the empirical networks, respectively, and thus they cannot be predicted by connectance and the number of species alone.
-To summarize general patterns across networks, we used an intercept-only linear mixed model (LMM) per motif with the help of the package lmer version _1.1-21_ [@bates2015], where the response variable was the observed motif percentile per network.
-In these models, we used the study identifiers in **Table S1** as a random intercept.
-By doing so, we obtained estimates of the average motif frequency, but controlling the variation at the study level.
-
-**Over- and under-represented groups on motif positions**
-
-We calculated which plant and floral visitor groups were over- or under-represented in the different motif positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
-To estimate the position frequencies of each group in a given network, we added the frequencies of those species that belong to the group, and then, we normalised the resulting frequencies by dividing the position measure for each group by the total number of times that a group appears in any position within the same motif size class.
-Then, we calculated the percentile of the observed position frequencies for each group and network, just like we did with motif frequencies.
-To outline the general patterns of position frequencies across networks and groups, we fit a LMM per motif position, where the response variable was the observed position percentile per network.
-We used the group identifier as an explanatory variable and the study identifiers as a random intercept.
-By adding the group estimates to the model intercept, we assessed the average motif frequency, after controlling the variation at the study level.
-Finally, we visualized with the help of the package _ComplexHeatmap_ version _2.6.2_ [@gu2016] over- and under-representation of plant and floral visitor groups on the different motif positions.
-
-To understand if the different plant and floral visitor groups are associated with motif positions that involve different network roles (e.g., specialization or generalism), we calculated the specificity of the different motif positions and evaluated its association through linear models with the average frequency of the different plant and floral visitor groups as response variable.
-For this, we previously calculated the specificity ($s_i$) of each motif position following @poisot2015 as $s_i = L - l_i / L - 1$, where $L$ is the total number of groups and $l_i$ the number of interaction partners of the group $i$ in a given motif.
-Values of the vector s, range between 1, complete specialization (1 partner within the motif) and 0, complete generalism (all possible partners within the motif).
-
-**Over- and under-represented group combinations of motifs**
-
-We studied which combinations of plant and floral visitor groups tend to appear together within the same motifs (up to five nodes).
-That is which combinations are over- or under-represented.
-This analysis use 57 out of the 60 networks available due to computational limitations to identify all the nodes in the motifs of the three networks with the highest number of links.
-To do so, for each of the 53,250 possible motif combinations, we estimated the observed and the expected probability of finding those combination in empirical networks, respectively.
-Then, we determined whether the observed probabilities are likely to come from the expected probabilities or not.
-To calculate the observed probability ($p_i^O$) of the different groups within a motif $i$ (e.g., motif 3, 'bee' + 'bee' + 'selfing herbs'), we divided the number of times that $i$ appears in our set of empirical networks ($n_i^O$) by the sum of the number of times that each possible combination appeared: $p_i^O = n_i^O / \sum_{k=1}^{53,250} n_k^O$.
-To estimate the expected probability of a given motif combination $i$, $p_i^E$, firstly, we calculated the probability of finding a given group $x$ in the position $\alpha$ of $i$, $p_i(x,\alpha)$.
-Then, by assuming the independency of $p_i(x,\alpha)$, we computed the expected probability of the combination $i$ as the product of the probability of its pairs $(x,\alpha)$, that is, $p_i^E = \prod _{(x,\alpha )\in i} p_i(x,\alpha)$.
-To obtain $p_i(x,\alpha)$, we proceeded as follows.
-First, we calculated the number of times that the group $x$ appears in the position $\alpha$ in each empirical network $\eta$, denoted as $n_i^{\eta}(x,\alpha)$.
-Then, by controlling the variation at the network level, we assessed the average value of the absolute frequency of group $x$ appears in the position $\alpha$, $n_i(x,\alpha) = E\left [ n_i^{\eta}(x,\alpha) \right ]$, and estimated $p_i(x,\alpha)$ as $p_i(x,\alpha) = n_i(x,\alpha)/\sum_{k}n_i(k,\alpha)$.
-To obtain $n_i(x,\alpha)$, we fitted a LMM per motif position, where the response variable was the number of times that a given position was observed per network, the explanatory variable was the group identifier, and the random intercept was given by network identifiers nested within the study identifiers.
-
-Once we obtained $p_i^O$ and $p_i^E$, we used a simulation approach to determine whether the former is likely to come from the latter or not.
-This approach was preferred since the large number of possible motif combinations and the small probabilities for some of them advise against using an exact test of goodness-of-fit or a Chi-square one.
-Specifically, we created 1,000 random samples with repetition of possible motif combinations, where each sample contained 10 million elements and, for each combination, the probability of being selected was equal to its expected probability.
-From those random samples, we extracted the mean and the standard deviation of the expected probability of $i$, denoted as $E\left [ p_i^E \right ]$ and $\sigma\left [ p_i^E \right ]$, respectively, and calculated the z-scores of $p_i^O$ as $z_i^O = \left ( p_i^O - E\left [ p_i^E \right ] \right )/\sigma \left [ p_i^E \right ]$, for those motif combinations with $p_i^O > 0$.
-According to the usual interpretation of z-scores, combinations with $z_i^O > 1.96$ are over-represented, whereas those with $z_i^O < -1.96$ are under-represented, at the 95$\%$  confidence level.
-Notice that we focused on combinations with $p_i^O > 10^{-7}$ because we do not have enough numerical resolution to accurately detect whether combinations that took place only once are under-represented (due to the limited size of our random samples).
-
-# RESULTS
-
-**Plant and floral visitor groups**
-
-The hierarchical cluster analysis divided the dataset into five different groups with different and overlapping characteristics (**Figure S3** and **Figure S4**).
-The first group referred to as 'selfing herbs' consisted on herbs with hermaphroditic flowers with high levels of autonomous selfing.
-The second group named 'small outcrossing perennials' had small perennial species with a mixed of life forms (i.e., trees shrubs and herbs) with outcrossing hermaphroditic flowers.
-The third group referred to as 'self-incompatible perennials with large flowers' comprised perennial species with a mixed of life forms and large self-incompatible hermaphroditic flowers with high number of ovules.
-The fourth group named 'tall plants with small unisexual flowers' had the tallest species, highest proportion of shrub and tree life forms, dioecious and monoecious breeding systems, small flowers and the highest numbers of flowers and inflorescences per plant.
-Finally, the fifth group named 'short-lived outcrossers with long zygomorphic flowers' consisted on small perennial and short-lived herbs with long self-compatible zygomorphic flowers that were unable to self-pollinate.
-
-In total, there were 1,126 species of floral visitors with 6,325 interactions recorded with plants.
-Most plants interacted with bees (2,256 interactions) and non-syrphid Diptera (1,768) followed by syrphids (845), Lepidoptera (437), Coleoptera (432) and non-bee Hymenoptera (362).
-
-**Overall motif patterns**
-
-Most motifs were under- and over-represented (close to the 1st and 99th percentile, respectively) in the comparison between empirical and simulated networks (**Figure 2**).
-Motifs 3, 5, 9, 10 and 14 were under-represented in empirical networks, that is, all were close to the 1st percentile and under the 25th percentile.
-Interestingly, four out of five of these motifs belonged to the largest path length classification (i.e., core-peripheral).
-In addition, motifs 2, 6, 7, 16 and 17 were over-represented, all over the 75th percentile and thus the closest to the 99th percentile.
-In contrast to the under-represented motifs, over-represented motifs belonged to the two shortest path length groups (i.e., complete and fan).
-The remaining motifs (i.e., 4, 8, 11, 12, 13, and 15) were between the 25th and 75th percentile.
-Notably, the exclusion of singletones from this analysis did not change the observed results (**Figure S1**).
 
@@
 ```
-
-**Over- and under-represented groups on motif positions**
-
-```{r , include=FALSE}
-
-#SAME SCRIPT AS THE PLOTTING FOR THE HEATMAP BUT I NEED IT HERE TO LOAD THE VARIABLES WITH VALUES ON RESULTS
-
-library(lme4)
-library(nlme)
-library(tidyverse)
-library(stringi)
-source("../Scripts/Scripts_Alfonso/add_study_id.R")
-
-#############################################
-# EXTRACT MEAN VALUES
-#############################################
-all_position_percentiles <- read_csv("../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
-
-all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
-                                                              "[0-9]+") %>% as.numeric()
-
-all_position_percentiles <- add_study_id(all_position_percentiles)
-#str(all_position_percentiles)
-#head(all_position_percentiles)
-
-list_plants_FG <- as.character(1:10)
-
-plant_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF)) #ME DA ERROR
-pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF))
-
-# Plants-------------
-
-# Mean percentile and SE taking into account the study system
-plant_codes <- plant_position_percentiles_filtered$position %>% unique()
-plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-plant_means$mean <- NA
-plant_means$SE <- NA
-
-for(i.pos in 1:length(plant_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
-            data = plant_position_percentiles_filtered %>%
-              filter(position == plant_codes[i.pos]))
-
-  temp <- fixed.effects(m) %>% unname()
-  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
-                                                                    temp[1]+temp[2],
-                                                                    temp[1]+temp[3],
-                                                                    temp[1]+temp[4],
-                                                                    temp[1]+temp[5]) ## to get real means per FG
-  temp <- sqrt(diag(vcov(m)))
-  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
-                                                                  temp[1]+temp[2],
-                                                                  temp[1]+temp[3],
-                                                                  temp[1]+temp[4],
-                                                                  temp[1]+temp[5])
-
-}
-
-# Pollinators--------
-
-# Mean percentile and SE taking into account the study system
-pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
-pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-pollinator_means$mean <- NA
-pollinator_means$SE <- NA
-pollinator_means_reordered <- NULL
-
-for(i.pos in 1:length(pollinator_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = pollinator_position_percentiles_filtered %>%
-              filter(position == pollinator_codes[i.pos]),
-            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
-
-  temp <- fixed.effects(m) %>% unname()
-  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)
-
-  pollinator_means_aux$mean <- c(temp[1],
-                                 temp[1]+temp[2],
-                                 temp[1]+temp[3],
-                                 temp[1]+temp[4],
-                                 temp[1]+temp[5],
-                                 temp[1]+temp[6],
-                                 temp[1]+temp[7],
-                                 temp[1]+temp[8],
-                                 temp[1]+temp[9]) ## to get real means per FG
-
-  temp <- sqrt(diag(vcov(m)))
-  pollinator_means_aux$SE <- c(temp[1],
-                               temp[1]+temp[2],
-                               temp[1]+temp[3],
-                               temp[1]+temp[4],
-                               temp[1]+temp[5],
-                               temp[1]+temp[6],
-                               temp[1]+temp[7],
-                               temp[1]+temp[8],
-                               temp[1]+temp[9])
-
-  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)
-
-}
-
-# There are lower limits (mean - SE) smaller than 0 (see Other insects)
-# We set the lower limit of those error bars to zero
-
-pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
-pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
-
-#############################################
-# ADDING BROAD MOTIF CATEGORIES TO POSITIONS
-#############################################
-
-motifs_raw_data <- read_csv("../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-motifs_raw_data$Broad_categories <- NA
-
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(5,9,14,13,10)] <- "Core-peripherical"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(6,16,12)] <- "Complete"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(2,3,7,4,17,8)] <- "Fan"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(15,11)] <- "Asymmetric complete"
-
-motifs_raw_data$plant <- gsub("[^0-9.-]", "", motifs_raw_data$plant)
-motifs_raw_data$pollinator <- gsub("[^0-9.-]", "", motifs_raw_data$pollinator)
-motifs_raw_data$plant <- as.numeric(motifs_raw_data$plant)
-motifs_raw_data$pollinator <- as.numeric(motifs_raw_data$pollinator)
-motifs_raw_data <- motifs_raw_data %>% filter(!is.na(Broad_categories))
-
-fan_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-pollinator_means_reordered$Broad_categories <- NA
-
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% fan_pollinator] <- "Fan" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% asymm_pollinator] <- "Medium-weak" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% complete_pollinator] <- "Strong" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% core_per_pollinator] <- "Weak"
-
-fan_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-plant_means$Broad_categories <- NA
-
-plant_means$Broad_categories[plant_means$position %in% fan_plant] <- "Fan" 
-plant_means$Broad_categories[plant_means$position %in% asymm_plant] <- "Medium-weak" 
-plant_means$Broad_categories[plant_means$position %in% complete_plant] <- "Strong" 
-plant_means$Broad_categories[plant_means$position %in% core_per_plant] <- "Weak"
-
-################################################################################
-# Alternative code to HEATMAPS to create variables with values to load on text
-# in a reproducible/automated way
-################################################################################
-
-# PLANTS-----
-
-# Prepare data for heatmap
-heat_plants_aux <- plant_means %>% spread(Node_FG,mean) %>% select(-SE)
-
-heat_plants <- heat_plants_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-# POLLINATORS-----------
-
-filter_rare_groups <- T
-
-if(filter_rare_groups == T){
-  heat_pollinators_aux <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds",
-                                                                                "Lizards",
-                                                                                "Other_insects")) %>% 
-    spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees",            
-                                      "Coleoptera","Lepidoptera","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Syrphids")
-}else{
-  heat_pollinators_aux <- pollinator_means_reordered %>% spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees","Birds",            
-                                      "Coleoptera","Lepidoptera","Lizards","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Other insects","Syrphids")
-}
-
-heat_pollinators <- heat_pollinators_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))
-
-#Check percentage of over and under represented
-colMeans(heat_pollinators[,c(3:8)] < 0.25)
-poll_under_25 <- colMeans(heat_pollinators[,c(3:8)] < 0.25)
-poll_under_25 <- specify_decimal((poll_under_25[[1]] + poll_under_25[[2]] + poll_under_25[[3]] +
-poll_under_25[[4]] + poll_under_25[[5]] + poll_under_25[[6]])/6*100,2)
-#[1] 32.57576
-
-colMeans(heat_pollinators[,c(3:8)] > 0.75)
-poll_over_75 <- colMeans(heat_pollinators[,c(3:8)] > 0.75)
-poll_over_75 <- specify_decimal((poll_over_75[[1]] + poll_over_75[[2]] + poll_over_75[[3]] +
-    poll_over_75[[4]] + poll_over_75[[5]] + poll_over_75[[6]])/6*100,2)
-#[1] 4.545455
-
-#################################################################################
-#################################################################################
-
-colnames(heat_plants)<- c("position", "Broad_categories", "one",
-                               "two", "three","four",
-                               "five")
-f <- heat_plants %>%
-  mutate(min = pmin(1,
-                    one, two,three,
-                    four, five))%>%
-  mutate(max = pmax(one,
-                    two, three,four,
-                    five))
-
-diff_1 <- f$max-f$min
-
-cbind(diff,diff_1)
-
-#Check percentage of over and under represented per FG
-colMeans(heat_plants[,c(3:7)] < 0.25)
-plant_under_25 <- colMeans(heat_plants[,c(3:7)] < 0.25)
-plant_under_25 <- specify_decimal((plant_under_25[[1]] + plant_under_25[[2]] + plant_under_25[[3]] + 
-    plant_under_25[[4]] + plant_under_25[[5]])/5*100,2)
-#[1] 18.18182
-colMeans(heat_plants[,c(3:7)] > 0.75)
-plant_over_75 <- colMeans(heat_plants[,c(3:7)] > 0.75)
-plant_over_75 <- specify_decimal((plant_over_75[[1]] + plant_over_75[[2]] + plant_over_75[[3]] + 
-    plant_over_75[[4]] + plant_over_75[[5]])/5*100,2)
-#[1] 8.181818
-
-#overall percentages
-under <- specify_decimal((as.numeric(poll_under_25) + as.numeric(plant_under_25))/2,2)
-over <- specify_decimal((as.numeric(poll_over_75) + as.numeric(plant_over_75))/2,2)
-
-```
-
-The comparison of the plant and floral visitor group frequencies per motif position between empirical and simulated networks showed a `r over`$\%$ and `r under`$\%$ of over- (>75$^{th}$) and under-represented (<25th) groups in the different positions, respectively (**Figure 3**).
-Floral visitors showed a total of `r poll_over_75`$\%$ and `r poll_under_25`$\%$ of over- and under-represented groups in the different positions and plants `r plant_over_75`$\%$ and `r plant_under_25`$\%$ of over- and under-represented groups, respectively.
-Notably, the differences across groups were more marked for floral visitors than for plant groups (the differences between min and max percentiles per position were generally two-three times larger for floral visitors).
-From most over- to under-represented floral visitors groups on the different motif positions (indicated with the dendrogram order in **Figure 3**), we found: bees, non-syrphids Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.
-Although plant functional groups showed less differences between them, there were also more represented groups than others, thus from most over- to under-represented groups on the different motif positions we found: self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', out.width="80%",fig.cap="\\textbf{Figure 3.} Heatmap indicating under- and over-representation of floral visitor and plant groups in the different motif positions.
-The different motif positions are dividied by the average path length clasification determined by Simmons et al.
-(2020) and they are ordered from the most densely connected motifs (strong or complete) to the less connected ones (weak or core-peripheral).
-The superior dendrogram indicates the differences across groups with the more separated groups showing larger differences."}
-
-library(lme4)
-library(nlme)
-library(tidyverse)
-library(stringi)
-source("../Scripts/Scripts_Alfonso/add_study_id.R")
-
-#############################################
-# EXTRACT MEAN VALUES
-#############################################
-
-all_position_percentiles <- read_csv("../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
-
-all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
-                                                              "[0-9]+") %>% as.numeric()
-
-all_position_percentiles <- add_study_id(all_position_percentiles)
-#str(all_position_percentiles)
-#head(all_position_percentiles)
-
-list_plants_FG <- as.character(1:10)
-
-plant_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF)) #ME DA ERROR
-pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF))
-
-# Plants-------------
-
-# Mean percentile and SE taking into account the study system
-plant_codes <- plant_position_percentiles_filtered$position %>% unique()
-plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-plant_means$mean <- NA
-plant_means$SE <- NA
-
-for(i.pos in 1:length(plant_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
-            data = plant_position_percentiles_filtered %>%
-              filter(position == plant_codes[i.pos]))
-
-  temp <- fixed.effects(m) %>% unname()
-  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
-                                                                    temp[1]+temp[2],
-                                                                    temp[1]+temp[3],
-                                                                    temp[1]+temp[4],
-                                                                    temp[1]+temp[5]) ## to get real means per FG
-  temp <- sqrt(diag(vcov(m)))
-  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
-                                                                  temp[1]+temp[2],
-                                                                  temp[1]+temp[3],
-                                                                  temp[1]+temp[4],
-                                                                  temp[1]+temp[5])
-
-}
-
-# Pollinators--------
-
-# Mean percentile and SE taking into account the study system
-pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
-pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-pollinator_means$mean <- NA
-pollinator_means$SE <- NA
-pollinator_means_reordered <- NULL
-
-for(i.pos in 1:length(pollinator_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = pollinator_position_percentiles_filtered %>%
-              filter(position == pollinator_codes[i.pos]),
-            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
-
-  temp <- fixed.effects(m) %>% unname()
-  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)
-
-  pollinator_means_aux$mean <- c(temp[1],
-                                 temp[1]+temp[2],
-                                 temp[1]+temp[3],
-                                 temp[1]+temp[4],
-                                 temp[1]+temp[5],
-                                 temp[1]+temp[6],
-                                 temp[1]+temp[7],
-                                 temp[1]+temp[8],
-                                 temp[1]+temp[9]) ## to get real means per FG
-
-  temp <- sqrt(diag(vcov(m)))
-  pollinator_means_aux$SE <- c(temp[1],
-                               temp[1]+temp[2],
-                               temp[1]+temp[3],
-                               temp[1]+temp[4],
-                               temp[1]+temp[5],
-                               temp[1]+temp[6],
-                               temp[1]+temp[7],
-                               temp[1]+temp[8],
-                               temp[1]+temp[9])
-
-  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)
-
-}
-
-# There are lower limits (mean - SE) smaller than 0 (see Other insects)
-# We set the lower limit of those error bars to zero
-
-pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
-pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
-
-#############################################
-# ADDING BROAD MOTIF CATEGORIES TO POSITIONS
-#############################################
-
-motifs_raw_data <- read_csv("../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-motifs_raw_data$Broad_categories <- NA
-
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(5,9,14,13,10)] <- "Core-peripherical"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(6,16,12)] <- "Complete"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(2,3,7,4,17,8)] <- "Fan"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(15,11)] <- "Asymmetric complete"
-
-motifs_raw_data$plant <- gsub("[^0-9.-]", "", motifs_raw_data$plant)
-motifs_raw_data$pollinator <- gsub("[^0-9.-]", "", motifs_raw_data$pollinator)
-motifs_raw_data$plant <- as.numeric(motifs_raw_data$plant)
-motifs_raw_data$pollinator <- as.numeric(motifs_raw_data$pollinator)
-motifs_raw_data <- motifs_raw_data %>% filter(!is.na(Broad_categories))
-
-fan_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-pollinator_means_reordered$Broad_categories <- NA
-
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% fan_pollinator] <- "Fan" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% asymm_pollinator] <- "Medium-weak" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% complete_pollinator] <- "Strong" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% core_per_pollinator] <- "Weak"
-
-fan_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-plant_means$Broad_categories <- NA
-
-plant_means$Broad_categories[plant_means$position %in% fan_plant] <- "Fan" 
-plant_means$Broad_categories[plant_means$position %in% asymm_plant] <- "Medium-weak" 
-plant_means$Broad_categories[plant_means$position %in% complete_plant] <- "Strong" 
-plant_means$Broad_categories[plant_means$position %in% core_per_plant] <- "Weak"
-
-########################################
-# CREATE HEATMAPS
-########################################
-
-library(ComplexHeatmap)
-
-# PLANTS-----
-
-# Prepare data for heatmap
-heat_plants_aux <- plant_means %>% spread(Node_FG,mean) %>% select(-SE)
-
-heat_plants <- heat_plants_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-heat_plants_fan <- heat_plants %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_fan) <- heat_plants_fan[,1]
-
-heat_plants_Weak <- heat_plants %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Weak) <- heat_plants_Weak[,1]
-
-heat_plants_Strong <- heat_plants %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Strong) <- heat_plants_Strong[,1]
-
-heat_plants_Medium_weak <- heat_plants %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Medium_weak) <- heat_plants_Medium_weak[,1]
-
-# POLLINATORS-----------
-
-filter_rare_groups <- T
-
-if(filter_rare_groups == T){
-  heat_pollinators_aux <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds",
-                                                                                "Lizards",
-                                                                                "Other_insects")) %>% 
-    spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees",            
-                                      "Coleoptera","Lepidoptera","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Syrphids")
-}else{
-  heat_pollinators_aux <- pollinator_means_reordered %>% spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees","Birds",            
-                                      "Coleoptera","Lepidoptera","Lizards","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Other insects","Syrphids")
-}
-
-heat_pollinators <- heat_pollinators_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-heat_pollinators_fan <- heat_pollinators %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_fan) <- heat_pollinators_fan[,1]
-
-heat_pollinators_Weak <- heat_pollinators %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Weak) <- heat_pollinators_Weak[,1]
-
-heat_pollinators_Strong <- heat_pollinators %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Strong) <- heat_pollinators_Strong[,1]
-
-heat_pollinators_Medium_weak <- heat_pollinators %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Medium_weak) <- heat_pollinators_Medium_weak[,1]
-
-##################
-
-#Do not know how to handle this multiplot for creating a panel
-
-# I'm going to create the 4 plots in one, 
-# I'm not sure that the grouping of the functional group is correct
-# when is done separately
-
-#sorry for the mess of libraries that I do below
-
-#Prepare first pollinators
-
-library(tidyr)
-library(data.table)
-long <- melt(setDT(heat_pollinators), id.vars = c("position","Broad_categories"), variable.name = "guilds")
-
-long_1 <- long %>% select(-Broad_categories)
-
-library(reshape2)
-long_m <- acast(long_1, position~guilds, value.var="value")
-
-#set manually the divisions, so far this is the best way I have seen to split the rows by categories
-
-r_split <- c(rep(c("Medium"), 3),rep(c("Weak"), 2),"Strong",rep(c("Medium"),2),rep(c("Weak"), 4),
-             rep(c("Medium-weak"), 2), "Strong", rep(c("Weak"), 3),rep(c("Medium-weak"), 2),
-             "Strong", "Medium")
-
-#set order of labels that avoids overlapping
-
-r_split <- factor(r_split, levels=c("Strong","Medium","Medium-weak","Weak"))
-
-#plat a bit with colors, a bit of a more complex set but looks nicer
-library(circlize)
-col_fun = colorRamp2(c(0.05644663,0.25, 0.4673256,0.75, 0.8782047), c("blue","cadetblue3", "azure2", "gold","red"))
-
-h_pol <- Heatmap(long_m, name = "Mean\npercentile", row_split=r_split,cluster_row_slices = FALSE, 
-                 column_title = "Pollinator functional groups",row_names_gp = gpar(fontsize = 10),
-                 col = col_fun,column_names_rot = 45,  column_names_gp = grid::gpar(fontsize = 10),
-                 column_title_gp = gpar(fontsize = 15, fontface = "bold"),
-                 row_title_gp = gpar(fontsize = 10, fontface = "bold"))
-
-#Prepare plants
-
-#long format
-long_plants <- melt(setDT(heat_plants), id.vars = c("position","Broad_categories"), variable.name = "Functional_groups")
-
-#filter for creating matrix
-long_plants_1 <- long_plants %>% select(-Broad_categories)
-
-#set better colnames
-long_plants_1$Functional_groups <- as.character(long_plants_1$Functional_groups)
-
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==1] <- "Selfing herbs" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==2] <- "Small outcrossing\nperennials" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==3] <- "Self-incomp. perennials\nwith large flowers" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==4] <- "Tall plants with small\nunisexual flowers" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==5] <- "Short-lived outcrossers with\nlong zygomorphic flowers"
-
-long_plants_1$Functional_groups <- factor(long_plants_1$Functional_groups, levels=c("Selfing herbs",
-"Small outcrossing\nperennials" ,"Self-incomp. perennials\nwith large flowers",
-"Tall plants with small\nunisexual flowers" ,"Short-lived outcrossers with\nlong zygomorphic flowers" ))
-
-#create matrix with reshape
-long_plants_m <- acast(long_plants_1, position~Functional_groups, value.var="value")
-
-r_split_plants <- c(rep(c("Medium"), 3),rep(c("Weak"), 2),"Strong",rep(c("Medium"),2),rep(c("Weak"), 3),
-                    rep(c("Medium-weak"), 2), "Strong", rep(c("Weak"), 4),rep(c("Medium-weak"), 2),
-                    "Strong", "Medium")
-
-r_split_plants <- factor(r_split, levels=c("Strong","Medium","Medium-weak","Weak"))
-
-h_plan <- Heatmap(long_plants_m, name = "Mean\npercentile", row_split=r_split_plants,cluster_row_slices = F, 
-                  column_title = "Plant functional groups",row_names_gp = gpar(fontsize = 10),col = col_fun,column_names_rot = 45,  
-                  column_names_gp = grid::gpar(fontsize = 10),column_title_gp = gpar(fontsize = 15, fontface = "bold"),
-                  row_title_gp = gpar(fontsize = 10, fontface = "bold"))
-
-library(patchwork)
-ht_list <- h_pol+h_plan
-
-draw(ht_list, auto_adjust = FALSE, cluster_rows = F)
-
-#Exploration of min max differences in the percentile position for plants and poll.
-#heat_pollinators[3:8]
-#
-#
-#heat_plants[3:7]
-#
-#
-#library(dplyr)
-#heat_pollinators %>%
-#  mutate(d = pmin())
-#
-#
-#colnames(heat_pollinators)<- c("position", "Broad_categories", "Bee",
-#                               "Coleoptera", "Lepidoptera","non_bee_hymenop",
-#                               "non_syrphid_dip", "syrphid")
-#
-#h <- heat_pollinators %>%
-#  mutate(min = pmin(Bee,
-#                  Coleoptera, Lepidoptera,non_bee_hymenop,
-#                  non_syrphid_dip, syrphid))%>%
-#  mutate(max = pmax(Bee,
-#                    Coleoptera, Lepidoptera,non_bee_hymenop,
-#                    non_syrphid_dip, syrphid))
-#
-#diff <- h$max-h$min
-#
-##################################################################################
-##################################################################################
-#
-#colnames(heat_plants)<- c("position", "Broad_categories", "one",
-#                               "two", "three","four",
-#                               "five")
-#
-#f <- heat_plants %>%
-#  mutate(min = pmin(1,
-#                    one, two,three,
-#                    four, five))%>%
-#  mutate(max = pmax(one,
-#                    two, three,four,
-#                    five))
-#
-#diff_1 <- f$max-f$min
-#
-#cbind(diff,diff_1)
-#
-
-```
-
-\newpage
-
-**Over- and under-represented group combinations of motifs**
-
-The different observed frequencies on the different motif positions showed a hierarchical order of probabilities for floral visitors (**Figure 4**).
-That is, the taxonomic group of 'bees' was the most abundant one on all motif positions followed by non-syrphid Diptera which was after bees, the second most frequent group on all positions.
-Then, the group of syrphids was the most abundant in all positions but two (positions 28 and 31 from motifs 11 and 12, respectively).
-After syrphids, Coleoptera was the most frequent group on the different positions followed by non-bee Hymenoptera and finally, Lepidoptera which was the less frequent group on all positions but two (positions 12 and 22 from motifs 5 and 9, respectively).
-Remarkably, plant functional groups were more variable on the different motif positions.
-However, there were also predominant functional groups found across the different motif positions.
-The three most frequent groups were 'tall plants with small unisexual flowers', 'self-incompatible perennials with large flowers' and 'small outcrossing perennials'.
-On the contrary, the groups of 'selfing herbs' and 'short lived outcrossers with long zygomorphic flowers' had the lowest probability to be present on the different motifs plant positions.
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 4.** Graphical representation of the probability of finding a given plant and floral visitor group $x$ in the position $\\alpha$ of motif $i$, $p_i(x,\\alpha)$, for all the possible motifs from two to five species in bipartite networks.
-The slices in the nodes for a given functional group $x$ are proportional to the corresponding value of $p_i(x,\\alpha)$."}
-
-library(ggplot2)
-library(scatterpie)
-library(RColorBrewer)
-library(tidyverse)
-
-plant_means_reordered <- read_csv("../Data/Csv/plant_abs_freq_means.csv")
-pollinator_means_reordered <- read_csv("../Data/Csv/pollinator_abs_freq_means.csv")
-#Filter out in order to have just 6 FG'S
-pollinator_means_reordered <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds", "Lizards", "Other_insects"))
-
-# Pollinator--------
-pollinator_pies <- pollinator_means_reordered %>% select(-mean, -SE) %>% 
-  spread(Node_FG,mean_natural_units)
-
-pollinator_pies$x <- 0
-pollinator_pies$y <- 0
-
-#ggplot() + geom_scatterpie(aes(x=x, y=y, group=position,r=5), 
-#                           data = pollinator_pies,
-#                           cols=as.character(c("Bee","Birds","Coleoptera","Lepidoptera",
-#                                               "Lizards","Non-bee-Hymenoptera",
-#                                               "Non-syrphids-diptera","Other_insects",
-#                                               "Syrphids")))+
-#  coord_equal()+
-#  scale_fill_brewer(palette = "Paired")+
-#  facet_wrap(~position,nrow = 3)+
-#  theme_bw()+
-#    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
-#          panel.background = element_blank(),
-#          axis.title.x=element_blank(),axis.text.x=element_blank(),
-#          axis.ticks.x=element_blank(),axis.title.y=element_blank(),
-#          axis.text.y=element_blank(),axis.ticks.y=element_blank(),
-#          legend.position="bottom")+
-#  labs(title = "Pollinator positions",fill=NULL)
-#    
-# plant--------
-plant_pies <- plant_means_reordered %>% select(-mean, -SE) %>% 
-  spread(Node_FG,mean_natural_units)
-
-plant_pies$x <- 0
-plant_pies$y <- 0
-
-#ggplot() + geom_scatterpie(aes(x=x, y=y, group=position,r=5), 
-#                           data = plant_pies,
-#                           cols=as.character(c("1","2","3","4","5")))+
-#  coord_equal()+
-#  scale_fill_brewer(palette = "Dark2")+
-#  facet_wrap(~position,nrow = 3)+
-#  theme_bw()+
-#  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
-#        panel.background = element_blank(),
-#        axis.title.x=element_blank(),axis.text.x=element_blank(),
-#        axis.ticks.x=element_blank(),axis.title.y=element_blank(),
-#        axis.text.y=element_blank(),axis.ticks.y=element_blank(),
-#        legend.position="bottom")+
-#  labs(title = "Plant positions",fill=NULL)
-#
-
-#################################
-# CREATE PIE-MOTIFS
-#################################
-
-equidistribution <- function(number_nodes){
-
-  x_width <- 5.5/(number_nodes+1)
-
-  x_result <- rep(-1.5,number_nodes)
-
-  for(i in 1:number_nodes){
-
-    x_result[i] <- x_result[i] + i*x_width
-
-  }
-
-  return(x_result)
-
-}
-
-plot_pie_motif_positions <- function(motif_number){
-  motifs_raw_data <- read_csv("../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-  motif_data <- motifs_raw_data %>% filter(motif_id == motif_number)
-
-  # Create dataframe with node positions
-
-  labdown = motif_data$plant %>% unique()
-
-  xdown = equidistribution(length(labdown))
-
-  ydown = rep(0,length(labdown))
-
-  labup = motif_data$pollinator %>% unique()
-
-  xup = equidistribution(length(labup))
-
-  yup = rep(2,length(labup))
-
-  d_nodes=data.frame(x=c(xdown,xup),
-                     y=c(ydown,yup),
-                     label = c(labdown,labup))
-
-  # Create a dataframe with links
-
-  plant_positions <- data.frame(plant = labdown,
-                                xdown = xdown,
-                                ydown = ydown)
-
-  pollinator_positions <- data.frame(pollinator = labup,
-                                     xup = xup,
-                                     yup = yup)
-
-  link_df <- motif_data %>% left_join(plant_positions, by = "plant") %>% 
-    left_join(pollinator_positions, by = "pollinator")
-
-  # Before plotting the motif, we remove letters from the node position id
-
-  d_nodes$label <- gsub("[^0-9.-]", "", d_nodes$label)
-  plant_pies_aux <- plant_pies %>% select(-x,-y) %>% mutate(position = as.character(position))
-
-  d_nodes_plant <- d_nodes %>% rename(position = label) %>% 
-    left_join(plant_pies_aux, by = "position") %>% as_tibble() %>%
-    filter(!is.na(`1`))
-
-  pollinator_pies_aux <- pollinator_pies %>% select(-x,-y) %>% mutate(position = as.character(position))
-
-  d_nodes_pollinator <- d_nodes %>% rename(position = label) %>% 
-    left_join(pollinator_pies_aux, by = "position") %>% as_tibble() %>%
-    filter(!is.na(Bee))
-
-  # Define the number of colors you want
- mycolors <- c("#A6CEE3", "chocolate2",  "gold2", "#1F78B4","#B2DF8A",
-                     "gray58", "lightgoldenrod2","thistle2", "burlywood","lightcoral", "olivedrab3")
-
-  ggplot() +
-    scale_shape_identity() +
-    geom_segment(data = link_df, aes(x=xdown, y=ydown, xend = xup, yend = yup), 
-                 size = 1, color = "grey20")+  geom_scatterpie(aes(x=x, y=y, group=position,r=.45), 
-    data = d_nodes_pollinator, cols=as.character(c("Bee","Coleoptera","Lepidoptera","Non-bee-Hymenoptera", "Non-syrphids-diptera","Syrphids"))) +
-    geom_scatterpie(aes(x=x, y=y, group=position,r=0.45), 
-                    data = d_nodes_plant,
-                    cols=as.character(c("1","2","3","4","5")))+
-    coord_fixed()+
-    scale_fill_manual(values = mycolors,"test",
-      breaks=c("Bee","Coleoptera","Lepidoptera",
-               "Non-bee-Hymenoptera", "Non-syrphids-diptera",
-               "Syrphids","1","2","3","4","5"), labels=c("Bees","Coleoptera","Lepidoptera",
-"Non-bee-Hymenoptera", "Non-syrphids-Diptera","Syrphids", 
-          "Selfing herbs","Small outcrossing perennials","Self-incomp. perennials\nwith large flowers",
-          "Tall plants with small\nunisexual flowers","Short-lived outcrossers with\nlong zygomorphic flowers"))+
-    xlim(-1.5,4)+ ylim(-0.5,2.5)+
-    theme(panel.background = element_blank(),
-          axis.text.x=element_blank(),
-          axis.ticks.x=element_blank(),
-          axis.text.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          legend.title = element_text(size=12, face="bold"),legend.background = element_rect(size=0.5, linetype="solid",colour ="black"))+
-    labs(x=NULL,y=NULL)+
-    guides(color = FALSE,fill=guide_legend(title="Functional groups"))+
-    ggtitle(paste0("Motif ",motif_number))+
-    theme(plot.title = element_text(hjust = 0.5),legend.key.size = unit(0.5, 'cm'))+
-    theme(plot.margin=unit(c(0,0,0,0),"cm"))
-}
-
-motif_number <- 1
-p1 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 2
-p2 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 3
-p3 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 4
-p4 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 5
-p5 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 6
-p6 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 7
-p7 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 8   
-p8 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 9
-p9 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 10
-p10 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 11
-p11 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 12
-p12 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 13
-p13 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 14
-p14 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 15
-p15 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 16
-p16 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 17
-p17 <- plot_pie_motif_positions(motif_number)
-
-library(patchwork)
-
-(p1 & ylab("2 species")| p2 & ylab("3 species") | p3  |plot_spacer()|plot_spacer())/ 
-  (p4 & ylab("4 species")| p5 | p6 | p7|plot_spacer())/ 
-  (p8  & ylab("5 species")| p9 | p10 | p11 | p12) / 
-  (p13 & ylab("5 species")| p14 | p15 | p16 | p17) + plot_layout(guides = 'collect') &
-  theme(axis.title.y = element_text(color="black", size=14, face="bold"),legend.position = "bottom")
-
-```
-
-The statistical comparison with z-scores between the observed and expected plant and floral visitor group combinations showed that we can not recover the observed combinations from its probability of occurrence.
-In fact, most combinations are under- or over- represented and follow a modified Gaussian distribution (Johnson's $S_U$) with 65$\%$ of under-represented group combinations, 20$\%$ of no statistical difference and 15$\%$ of under-represented ones (**Figure 5**).
-In addition, motifs with small node combinations (i.e., 2 and 3 nodes) only appeared as under-represented.
-Motifs with 4 and 5-node combinations appeared in the three statistical categories but 4 node motifs had a higher proportion in the under-represented category (10% in comparison with the 1$\%$ and the 3$\%$ of the no statistical difference and over-represented categories, respectively).
-Finally, 5-node motifs were in similar proportions in the no statistical difference and over-represented categories (99$\%$ and 97$\%$, respectively) but they appeared in lower proportion in the under-represented category (89$\%$).
-When, we explore the identity on the different positions of the most probable motif combinations we find as expected that the most common plant and floral visitor groups rule these positions on the most probable motif combinations (lower panel **Figure 5**).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 5.** Z-score comparison (95% confidence level) of the observed and expected frequencies of motif combinations with four specific graphical examples of the most probable motifs of being observed for each category delimited by the z-score critical values: under-represented (red), no statistical difference (green) and over-represented (blue)."}
-
-library(tidyverse)
-library(RColorBrewer)
-
-equidistribution <- function(number_nodes){
-
-  x_width <- 5.5/(number_nodes+1)
-
-  x_result <- rep(-1.5,number_nodes)
-
-  for(i in 1:number_nodes){
-
-    x_result[i] <- x_result[i] + i*x_width
-
-  }
-
-  return(x_result)
-
-}
-
-plot_motif_label <- function(label){
-
-  label_split <- str_split(label,"_")[[1]]
-  motif_number <- as.numeric(label_split[1])
-  nodes <- label_split[2:length(label_split)]
-  plant_nodes <- nodes[nodes %in% plant_means_reordered$Node_FG]
-  pollinator_nodes <- nodes[nodes %in% pollinator_means_reordered$Node_FG]
-
-  motifs_raw_data <- read_csv("../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-  motif_data <- motifs_raw_data %>% filter(motif_id == motif_number)
-
-  # Create dataframe with node positions
-
-  labdown = motif_data$plant %>% unique()
-
-  xdown = equidistribution(length(labdown))
-
-  ydown = rep(0,length(labdown))
-
-  labup = motif_data$pollinator %>% unique()
-
-  xup = equidistribution(length(labup))
-
-  yup = rep(1,length(labup))
-
-  d_nodes=data.frame(x=c(xdown,xup),
-                     y=c(ydown,yup),
-                     label = c(labdown,labup))
-
-  # Create a dataframe with links
-
-  plant_positions <- data.frame(plant = labdown,
-                                xdown = xdown,
-                                ydown = ydown)
-
-  pollinator_positions <- data.frame(pollinator = labup,
-                                     xup = xup,
-                                     yup = yup)
-
-  link_df <- motif_data %>% left_join(plant_positions, by = "plant") %>% 
-    left_join(pollinator_positions, by = "pollinator")
-
-  # Add FG IDs to nodes
-  FG_IDs <- tibble(label = c(sort(labdown),sort(labup)),
-                   FG = c(plant_nodes,pollinator_nodes))
-
-  d_nodes_FG <- d_nodes %>% left_join(FG_IDs, by = "label")
-  levels_FG <- c("Bee","Coleoptera","Lepidoptera",
-                 "Non-bee-Hymenoptera", "Non-syrphids-diptera",
-                 "Syrphids","1","2","3","4","5")
-
-  d_nodes_FG$FG <- factor(d_nodes_FG$FG, levels = levels_FG)
-
-  levels(d_nodes_FG$FG) <- c("Bee","Coleoptera","Lepidoptera",
-                             "Non-bee-Hymenoptera", "Non-syrphids-diptera",
-                             "Syrphids","1","2","3","4","5")
-
-  # Before plotting the motif, we remove letters from the node position id
-
-  d_nodes_FG$label <- gsub("[^0-9.-]", "", d_nodes_FG$label)
-
-  # Define the number of colors you want
- mycolors <- c("#A6CEE3", "chocolate2",  "gold2", "#1F78B4","#B2DF8A",
-                     "gray58", "lightgoldenrod2","thistle2", "burlywood","lightcoral", "olivedrab3")
-
-  ggplot(data=d_nodes_FG, aes(x, y)) +
-    scale_shape_identity() +
-    geom_segment(data = link_df, aes(x=xdown, y=ydown, xend = xup, yend = yup), size = 1, color = "grey20")+
-    geom_point(aes(color = FG), size=7.5)+
-    geom_text(aes(x, y , label = label), size=3)+
-    scale_color_manual(drop = FALSE, values = mycolors,
-                       breaks=c("Bee","Coleoptera","Lepidoptera",
-                                "Non-bee-Hymenoptera", "Non-syrphids-diptera",
-                                "Syrphids","1","2","3","4","5"), 
-                       labels=c("Bees","Coleoptera","Lepidoptera",
-                                "Non-bee-Hymenoptera", "Non-syrphids-Diptera",
-                                "Syrphids", 
-                                "Selfing herbs","Small outcrossing perennials",
-                                "Self-incomp. perennials\nwith large flowers",
-                                "Tall plants with small\nunisexual flowers",
-                                "Short-lived outcrossers with\nlong zygomorphic flowers"))+
-    xlim(-1.5,4)+ ylim(-0.5,1.5)+
-    theme(panel.background = element_blank(),
-          axis.text.x=element_blank(),
-          axis.ticks.x=element_blank(),
-          axis.text.y=element_blank(),
-          axis.ticks.y=element_blank())+
-    labs(x=NULL,y=NULL)+
-    ggtitle(paste0("Motif ",motif_number))+
-    theme(plot.title = element_text(hjust = 0.5,size=10))+
-    guides(color=guide_legend(title="Functional groups"))
-
-}
-
-# Data with pollinator/plant labels
-
-plant_means_reordered <- read_csv("../Data/Csv/plant_abs_freq_means.csv")
-pollinator_means_reordered <- read_csv("../Data/Csv/pollinator_abs_freq_means.csv")
-#Filter out in order to have just 6 FG'S
-pollinator_means_reordered <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds", "Lizards", "Other_insects"))
-
-####################################################################################################
-#Read data to check top 5 motif of each category of observed propabilities
-
-#Under, No signi, Over-rep
-####################################################################################################
-# Check top Z-scores of each group (Under, No diff, Over)
-
-#Read data
-data <- read.csv("../Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
-
-#Find critical value of Z-score
-p <- 0.05 #cutoff probability 95% confidence
-critical_value <- qnorm(p/2) #double tail probability divide by 2
-
-data_1 <- data %>%
-  mutate(infra_over_represented = case_when(
-    z_score < -abs(critical_value) ~ "infra",
-    between(z_score, -abs(critical_value), abs(critical_value)) ~ "no_diff",
-    z_score > abs(critical_value) ~ "over"
-  ))
-
-#data_2 <- filter(data_1, abs(z_score)<2000) 
-#str(data_2)
-
-#Select under-represented by the ones with highest porbability of being observed (top10)
-under_data <- filter(data_1, infra_over_represented=="infra")
-
-under_top_5 <- filter(under_data, row_number(desc(abs(motif_observed_probability)))<= 5) %>%
-  select(motif_functional_ID,motif_observed_probability,counts_observed,z_score)
-
-#Select no statistical difference by the ones with highest porbability of being observed (top5)
-no_diff_data <- filter(data_1, infra_over_represented=="no_diff")
-
-no_diff_top_5 <- filter(no_diff_data, row_number(desc(abs(motif_observed_probability)))<= 5) %>%
-  select(motif_functional_ID,motif_observed_probability,counts_observed,z_score)
-
-#Select over-represenetd by the ones with highest porbability of being observed (top5)
-over_data <- filter(data_1, infra_over_represented=="over")
-
-over_top_5 <- filter(over_data, row_number(desc(abs(motif_observed_probability)))<= 5) %>%
-  select(motif_functional_ID,motif_observed_probability,counts_observed,z_score)
-####################################################################################################
-#Now plot it 
-####################################################################################################
-
-library(patchwork)
-
-#Prepare list of 5 plots for each group
-#Under
-labels_under <- under_top_5$motif_functional_ID
-p_under <- list()
-
-for (i in 1:5){
-
-  p_under[[i]] <- plot_motif_label(labels_under[[i]])
-}
-
-#No signficance
-labels_nodiff <- no_diff_top_5$motif_functional_ID
-p_nodiff <- list()
-
-for (i in 1:5){
-
-  p_nodiff[[i]] <- plot_motif_label(labels_nodiff[[i]])
-}
-
-#Over
-labels_over <- over_top_5$motif_functional_ID
-p_over <- list()
-
-for (i in 1:5){
-
-  p_over[[i]] <- plot_motif_label(labels_over[[i]])
-}
-
-#Run Script with histogram plot
-source("../Scripts/Z-score_percentile_histogram_plot.R")
-
-hist <- ggplot(data_2 %>% filter(round_motif_observed_probability>0), aes(x=z_score, color=infra_over_represented, fill=infra_over_represented)) + 
-  geom_histogram(bins = 93, alpha = 0.5, position = "identity",lwd = 0.25)+
-  geom_vline(xintercept = -abs(critical_value))+
-  geom_vline(xintercept = abs(critical_value))+
-  xlim(-60,60) + ylab("Frequency")+  theme_bw() +
-  scale_fill_manual(name="Motif frequencies" ,values=c("coral2", "palegreen3", "cyan3"), labels=c("Under-represented",
-                                                                                                  "No statistical difference", "Over-represented")) +
-  scale_color_manual(name="Motif frequencies" ,values=c("coral2", "palegreen3", "cyan3"), labels=c("Under-represented",
-                                                                                                   "No statistical difference", "Over-represented")) + xlab("Z-score")
-
-t_col <- function(color, percent = 50, name = NULL) {
-  #      color = color name
-  #    percent = % transparency
-  #       name = an optional name for the color
-
-  ## Get RGB values for named color
-  rgb.val <- col2rgb(color)
-
-  ## Make new color using input color as base and alpha set by transparency
-  t.col <- rgb(rgb.val[1], rgb.val[2], rgb.val[3],
-               max = 255,
-               alpha = (100 - percent) * 255 / 100,
-               names = name)
-
-  ## Save the color
-  invisible(t.col)
-}
-## END
-
-#Prepare panel of plots
-hist / ((p_under[[1]]/p_under[[2]]/p_under[[3]]/p_under[[4]] & theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_rect(fill=t_col("coral2")))) | 
-          (p_nodiff[[1]]/p_nodiff[[2]]/p_nodiff[[3]]/p_nodiff[[4]]& theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_rect(fill=t_col("palegreen3")))) |
-          (p_over[[1]]/p_over[[2]]/p_over[[3]]/p_over[[4]] & theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_rect(fill=t_col("cyan3"))))) + plot_layout(guides = 'collect')
-
-```
-
-# Discussion
-
-Understanding the global patterns of network structure is key to unravel the processes that govern community dynamics [@bascompte2007; @bastolla2009; @guimaraes2020].
-However, common analytical approaches are unable to capture the full complexity of ecological systems [@simmons2019; @bergamo2021].
-Because network motifs can capture both direct and indirect interactions, by analysing over- and under-representation of motifs we are able to explore in greater detail ecological interactions [@stouffer2007].
-We have explored for the first time the overall structure and representation of network motifs in real plant-pollinator networks and shown that the different motifs up to five nodes are consistently over- and under-represented in comparison with simulated networks indicating the presence of ecological processes shaping their structure.
-Despite the presence of multiple ecological processes likely operating at the same time (e.g., neutral effects, morphological matching or phenological overlap), we found a tendency for over-represented structures with more densely connected motifs (i.e., complete, fan and asymmetric complete) suggesting that neutral effects are likely the predominant processes governing the structure of these network motifs [@simmons2020].
-Thus, as indicated for other network properties like nestedness [@krishna2008; @suweis2013], species relative abundances (i.e., neutral effects) are possibly one of the main determinants of indirect interactions in real plant-pollinator networks.
-
-From a pollinator perspective, we found that generalist network motifs were consistently over-represented (e.g.
-fan-type motifs; **Figure 2**).
-For instance, when we compare motifs with equal structure for both trophic levels, we found that floral visitors had always over-representation in the positions that implied the highest number of links.
-Despite this is in good agreement with the current view of the generalist tendency of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of the generalist network motifs was largely driven by the functional group of bees (e.g., positions 42, 46, 16, 4, 14 and 35 in motifs 15, 17, 7, 2, 6 and 13, respectively; see **Figure 3** for positions and **Figure 4** for motifs) while the rest of the functional groups tended to be under-represented in these generalist motifs and over-represented in motif positions with specialist roles (e.g., positions 11, 21, 28 and 34 in motifs 5, 9, 11 and 13, respectively; see **Figure 3** for positions and **Figure 4** for motifs).
-This large effect of bees on the overall patterns is no surprise, as bees were the functional group with largest number of interaction records in the whole set of networks as also recorded for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017].
-Unlike floral visitors, plant functional groups showed little differences on its appearance in different motif positions, and thus similar probability of appearing on all of them.
-If anything, the groups that involved higher levels of outcrossing showed a tendency to be more over-represented and probable on different motif positions.
-For instance, the group of self-incompatible perennials with large flowers, one of the groups that is expected to have higher levels of outcrossing rate [@goodwillie2010], showed the highest over-representation of all plant functional groups (**Figure 3**); and the group of tall plants with unisexual flowers, the one that is expected to have the highest dependence of pollinators on reproduction [@rodger2021], was the most probable on the generalist motif for plant positions (i.e., plant nodes with 3 to 4 links; **Figure 4**).
-
-The probabilities of appearance of each functional group on the different motif positions were insufficient to predict most of the observed network position combinations (**Figure 5**).
-This implies that not just the representation of network motifs types but also the identity of the elements of their structure is influenced by ecological processes that determine under- and over-representation of the different position combinations.
-In addition, we found that just 30$\%$ of the possible 53,250 motif combinations are realized.
-Thus, similarly to the presence of forbidden links at the network level [@olesen2011; @jordano2016], we also found the existence of forbidden motif positions and those represented almost two thirds of the total posible combinations of indirect interactions.
-This concurs well with the general idea that plant-pollinator networks have a high proportion of non-realized direct interactions [@jordano2003; @bascompte2013], and as a result, also a high proportion of non-realized combinations of indirect interactions.
-Some of this non-observed interactions are probably due to under-sampling [@dorado2011; @jordano2016].
-However, a large fraction of the possible interactions do not take place because of life-history constraints such as species co-occurrence, trait matching processes and phenological uncoupling [@olesen2011; @bartomeus2016; @jordano2016].
-Despite the advances in the understanding on the ecological processes that influence species pairwise interactions [@bartomeus2016; @peralta2020], we still know little of how these processes determine competitive and facilitative interactions in mutualistic networks.
-Thus, as suggested by @simmons2020, exploring the proportion of these realized network motifs that are competitive or facilitative is a necessary next step to improve our understanding of the architecture of biodiversity [@bascompte2007].
-
-Despite the obvious usefulness of functional groups in summarizing species ecological roles (e.g., similar reproductive biology and behaviour of pollinators), delimiting species into functional groups is not often trivial.
-For instance, taxonomic diversity and trait availability limit our ability to properly represent the wide range of reproductive strategies [@dellinger2020] and different clustering analysis can lead to distinct outcomes (e.g., k-means and hierarchical clustering).
-Further, here we divided floral visitors on the taxonomic rank level because it represented adequately the pollinator species ecological roles without the need of the tremendous effort of compiling trait data for over 1000 species of floral visitors.
-However, further groupings with traits could help revealing greater relevance of trait-matching processes on indirect interactions.
-We believe that this could be investigated by exploring which proportion of over- and under-represented motifs present high and low trait-matching, respectively.
-Moreover, we analysed network motifs focusing exclusively on presence-absence interactions which assume that all interactions are equally important but as suggested by @simmons2020, further work should account for quantitative measurements of the strength of plant-pollinator interactions.
-Finally, despite the wide geographical coverage of our plant-pollinator dataset, there are major gaps for some regions of the world with a clear bias towards Europe, America and islands which have long been interested ecologist [@macarthur1963; @warren2015].
-These biases are also found in global datasets of networks where the data is highly fragmented across space [@poisot2021] and more efforts are needed to capture global patterns of plant-pollinator interactions.
-
-In conclusion, by following the framework of @simmons2020 we have been able to explore competitive and facilitative interactions in plant-pollinator networks worldwide and found that indirect interactions are non-random and are more strongly related to neutral processes than any other ecological process.
-Further, we found that motif combinations of functional groups are strongly constrained and that the distinct motif positions are associated with different functional groups with different ecological roles (e.g., generalization versus specialization).
-Although in this study we do not predict indirect interactions, our work is a first step to elucidate novel interactions beyond pairwise interactions.
-
-*Acknowledgements* - This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2).
-We thank all researchers that made their data openly available and sent it upon request.
-We also thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza and David Ragel for their help with data collection.
-Finally, JBL also thanks the University of New England for the funding provided to carry out this work.
-
-# Author contributions
-
-IB designed the idea. JBL collected the data. AA-P lead the analysis with contributions of JBL and guidance of IB. JBL wrote the manuscript with contributions of IB and AA-P.
-
-# Data availability statement
-
-All data and code would be deposited at Driad Digital repository upon acceptance.
-
-# References
-
-<div id ="refs"></div>

### 2022-03-08 Manuscript/Main_text/Main_text_Oikos.Rmd
Edits on text

--- 2022-03-06 Manuscript/Main_text_Oikos.Rmd
@@
 Detecting those relationships is not trivial since they go beyond pairwise interactions, but may get blurred when considering full network descriptors.
-However, recent work has shown the network meso-scale could capture this important information.
-The meso-scale describes network subgraphs representing patterns of interactions between a small number of species (i.e.
-motifs) and those constitute the building blocks of the whole network.
+However, recent work has shown the network meso-scale can capture this important information.
+The meso-scale describes network subgraphs representing patterns of interactions between a small number of species (i.e., motifs) and those constitute the building blocks of the whole network.
 Despite the possible implications of network motifs to better capture species interactions, they remain overlooked in natural plant-pollinator networks.
 By exploring 60 networks from 18 different studies with wide geographical coverage we show that some motifs are consistently under- and over-represented worldwide, suggesting that the building blocks of plant-pollinator networks are not random.
-Furthermore, we found that distinct motif positions describing species ecological roles (e.g., generalization, indirect interactions) are occupied by different groups on both trophic levels.
-For instance, bees appear consistently in generalist motif positions and plants with higher levels of outcrossing tend to have a large number of indirect interactions.
+Furthermore, we found that distinct motif positions describing species ecological roles (e.g., generalization and number of indirect interactions) are occupied by different groups on both trophic levels.
+Bees and plant species with separated sexes on different or the same individuals (e.g., dioecious or monoecious species) appeared consistently in generalist motif positions with lower number of indirect interactions.
+The rest of floral visitor groups tended to appear with more frequency on motif positions that involved higher specialization and higher number of indirect interactions while the rest of plant groups showed similar frequencies on the different motif positions.
 Interestingly, the realized combinations of different groups within a motif can not be retrieved from their joint probability distributions, indicating that group combinations are not random either.
-Our result highlights the non-random structure of indirect interactions in plant-pollinator networks and opens the door to predict novel interactions beyond pairwise interactions within a community context.
-
-Keyworkds: plant-pollinator networks, plant-pollinator interactions, network motifs, functional groups, plant traits, floral visitors
+Our result highlights the non-random structure of the meso-scale on plant-pollinators networks and the association of different plant and floral visitor groups with certain motifs with different ecological roles at a macro-ecological scale.
+
+Keywords: plant-pollinator networks, plant-pollinator interactions, network motifs, functional groups, plant traits, floral visitors
 
@@
 Once we split the different plant-pollinator networks into their motif elements, we explored: (i) if there is a common invariant structural property in the overall motif networks (i.e.
-over- and under-represented motifs); (ii) which plant and pollinator groups are over- and under-represented in the different motif positions; and, (iii) if there are over- and under-represented plant and pollinator group combinations within a motif.
+over- and under-represented motifs); (ii) which plant and floral visitor groups are over- and under-represented in the different motif positions; and, (iii) if there are over- and under-represented plant and floral visitor group combinations within a motif.
 
@@
 We calculated the frequency of all motifs up to five nodes (17 different motifs in total; see **Figure 1**) for each empirical network, by using the _bmotif_ package version _2.0.2_ [@bmotifsimmons2019].
-We focused exclusively on motifs up to five nodes in our analyses for computational reasons and the ease of visualization and interpretation of a reduced set of less complex motifs.
+We focused exclusively on motifs up to five nodes in our analyses for computational reasons and for the ease of visualization and interpretation of a reduced set of less complex network motifs.
 Throughout the entire manuscript, floral visitors occupy the top nodes of the different motifs and plants the bottom ones.
@@
 Like @simmons2020, we classified the different motifs by their average path length (mean number of links between all pairs of nodes) into four different groups: (i) complete or strong ($\overline{x} = 1.38$), (ii) fan or medium-strong ($\overline{x} = 1.48$), (iii) assymmetric complete or medium-weak ($\overline{x} = 1.60$) and (iv) core-peripheral or weak ($\overline{x} = 1.85$).
-More densely connected motifs (e.g., complete or fan groups) experience higher number of indirect interactions in contrast to motifs that are less densely connected (e.g., medium-weak or weak groups).
+In general terms, plant and floral visitor groups on more densely connected motifs (e.g., complete or fan) will experience lower number of indirect interactions in contrast to groups on less densely connected ones (e.g., medium-weak or weak).
 
@@
 library(RColorBrewer)
-source("../Scripts/Scripts_Alfonso/plot_motif_positionsV2.R")
+source("../../Scripts/Scripts_Alfonso/plot_motif_positionsV2.R")
 
@@
 
-**MA FORTUNA, what about degree?**
-
 To assess the significance of the observed frequencies, we created 1,000 simulated networks for each binary network using the _nullmodel_ function and the _vaznull_ model in the _bipartite_ package version _2.14_ [@dormann2009].
 Generated networks had the same number of plants and floral visitors, as well as the same connectance of their corresponding empirical networks.
+More restricted null models with also degree as constant were also explored but did not allowed sufficient permutations given that many constraints and provided highly similar or identical networks to the original ones.
+
 After extracting the motif frequencies from the simulated networks, for each motif type and empirical network, we calculated the percentage of simulated networks whose frequencies were smaller than the ones observed, that is, we estimated the percentile of the observed motif frequencies.
@@
 library(tidyverse)
-source("../Scripts/Scripts_Alfonso/add_study_id.R")
-d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
+source("../../Scripts/Scripts_Alfonso/add_study_id.R")
+d <- read_csv("../../Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
 d <- add_study_id(d)
@@
 
-labels <- c("2" = "*Motif 2* <img src='../Images/motif_2.png' width='22'/>" ,
-          "3"= "*Motif 3* <img src='../Images/motif_3.png' width='22'/>",
-          "4"= "*Motif 4* <img src='../Images/motif_4.png' width='22'/>",
-          "5"= "*Motif 5* <img src='../Images/motif_5.png' width='22'/>",
-          "6"= "*Motif 6* <img src='../Images/motif_6.png' width='22'/>",
-          "7"= "*Motif 7* <img src='../Images/motif_7.png' width='22'/>",
-          "8"= "*Motif 8* <img src='../Images/motif_8.png' width='22'/>",
-          "9"= "*Motif 9* <img src='../Images/motif_9.png' width='22'/>",
-          "10"= "*Motif 10* <img src='../Images/motif_10.png' width='22'/>",
-          "11"= "*Motif 11* <img src='../Images/motif_11.png' width='22'/>",
-          "12"= "*Motif 12* <img src='../Images/motif_12.png' width='22'/>",
-          "13"= "*Motif 13* <img src='../Images/motif_13.png' width='22'/>",
-          "14"= "*Motif 14* <img src='../Images/motif_14.png' width='22'/>",
-          "15"= "*Motif 15* <img src='../Images/motif_15.png' width='22'/>",
-          "16"= "*Motif 16* <img src='../Images/motif_16.png' width='22'/>",
-          "17"= "*Motif 17* <img src='../Images/motif_17.png' width='22'/>")
+labels <- c("2" = "*Motif 2* <img src='../../Images/motif_2.png' width='22'/>" ,
+          "3"= "*Motif 3* <img src='../../Images/motif_3.png' width='22'/>",
+          "4"= "*Motif 4* <img src='../../Images/motif_4.png' width='22'/>",
+          "5"= "*Motif 5* <img src='../../Images/motif_5.png' width='22'/>",
+          "6"= "*Motif 6* <img src='../../Images/motif_6.png' width='22'/>",
+          "7"= "*Motif 7* <img src='../../Images/motif_7.png' width='22'/>",
+          "8"= "*Motif 8* <img src='../../Images/motif_8.png' width='22'/>",
+          "9"= "*Motif 9* <img src='../../Images/motif_9.png' width='22'/>",
+          "10"= "*Motif 10* <img src='../../Images/motif_10.png' width='22'/>",
+          "11"= "*Motif 11* <img src='../../Images/motif_11.png' width='22'/>",
+          "12"= "*Motif 12* <img src='../../Images/motif_12.png' width='22'/>",
+          "13"= "*Motif 13* <img src='../../Images/motif_13.png' width='22'/>",
+          "14"= "*Motif 14* <img src='../../Images/motif_14.png' width='22'/>",
+          "15"= "*Motif 15* <img src='../../Images/motif_15.png' width='22'/>",
+          "16"= "*Motif 16* <img src='../../Images/motif_16.png' width='22'/>",
+          "17"= "*Motif 17* <img src='../../Images/motif_17.png' width='22'/>")
 
@@
 library(stringi)
-source("../Scripts/Scripts_Alfonso/add_study_id.R")
+source("../../Scripts/Scripts_Alfonso/add_study_id.R")
 
@@
 #############################################
-all_position_percentiles <- read_csv("../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
+all_position_percentiles <- read_csv("../../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
 
@@
 
-motifs_raw_data <- read_csv("../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
+motifs_raw_data <- read_csv("../../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
 
@@
 
-all_position_percentiles <- read_csv("../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
+all_position_percentiles <- read_csv("../../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
 
@@
 
-plant_means_reordered <- read_csv("../Data/Csv/plant_abs_freq_means.csv")
-pollinator_means_reordered <- read_csv("../Data/Csv/pollinator_abs_freq_means.csv")
+plant_means_reordered <- read_csv("../../Data/Csv/plant_abs_freq_means.csv")
+pollinator_means_reordered <- read_csv("../../Data/Csv/pollinator_abs_freq_means.csv")
 #Filter out in order to have just 6 FG'S
@@
 plot_pie_motif_positions <- function(motif_number){
-  motifs_raw_data <- read_csv("../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
+  motifs_raw_data <- read_csv("../../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
 
@@
 
-  motifs_raw_data <- read_csv("../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
+  motifs_raw_data <- read_csv("../../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
 
@@
 #Read data
-data <- read.csv("../Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
+data <- read.csv("../../Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
 
@@
 #Run Script with histogram plot
-source("../Scripts/Z-score_percentile_histogram_plot.R")
+source("../../Scripts/Z-score_percentile_histogram_plot.R")
 

### 2022-03-08 Manuscript/Main_text/Title_page_Oikos.Rmd
Edits on text

--- 2021-10-18 Draft/Draft.Rmd
@@
 ---
-title: The non-random assembly of functional motifs in plant-pollinator networks worldwide
-editor_options:
-  chunk_output_type: console
-header-includes:
-- \usepackage{booktabs}
-- \usepackage{longtable}
-- \usepackage{array}
-- \usepackage{multirow}
-- \usepackage{wrapfig}
-- \usepackage{float}
-- \usepackage{colortbl}
-- \usepackage{pdflscape}
-- \usepackage{tabu}
-- \usepackage{threeparttable}
-- \usepackage{threeparttablex}
-- \usepackage[normalem]{ulem}
-- \usepackage{makecell}
-- \usepackage{xcolor}
-- \usepackage{caption,setspace}
-- \captionsetup[figure]{labelformat=empty}
-- \floatplacement{figure}{H}
-- \usepackage[skip=3pt]{caption}
-- \captionsetup[figure]{labelformat=empty}
-- \usepackage{lscape}
-- \newcommand{\blandscape}{\begin{landscape}}
-- \newcommand{\elandscape}{\end{landscape}}
-output:
-  pdf_document: default
-  html_document: default
-  word_document: default
-always_allow_html: true
-bibliography: bibliography.bib
+title: "The non-random assembly of functional motifs in plant-pollinator networks worldwide"
+output: pdf_document
 ---
 
-__Jose B. Lanuza^1,2^__  | __Alfonso Allen-Perkins^2,3^__ |  __Romina Rader^1^__ | __Ignasi Bartomeus^2^__
+__Jose B. Lanuza^1,2^__  | __Alfonso Allen-Perkins^2,3^__ | __Ignasi Bartomeus^2^__
 
@@
 3 Departamento de Ingeniería Eléctrica, Electrónica, Automática y Física Aplicada, ETSIDI, Universidad Politécnica de Madrid, 28040 Madrid, Spain.
-
-\captionsetup[table]{labelformat=empty}
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
-
-# Abstract
-
-Ecological processes leave distinct structural imprints on species interactions shaping the topology of mutualistic networks.
-Detecting those relationships is not trivial since they go beyond pair-wise interactions, but may get blurred when considering full network descriptors.
-However, recent work has shown the network meso-scale can capture this important information.
-The meso-scale describes network subgraphs representing patterns of interactions between a small number of species (i.e.
-motifs) and those constitute the building blocks of the whole network.
-Here, we have compiled 60 networks from 18 different studies and show that some motifs are consistently under- and over-represented worldwide, suggesting that the building blocks of plant-pollinator networks are not random.
-Furthermore, we found that distinct motif positions describing species ecological roles (e.g., generalization, indirect interactions) are occupied by different functional groups on both trophic levels.
-For instance, bees appear consistently in generalist motif positions and plants with higher levels of outcrossing tend to have a large number of indirect interactions.
-Interestingly, the realized combinations of different functional groups within a motif can not be retrieved from their joint probability distributions, indicating that functional group combinations are not random either.
-Our result highlight the non-random structure of indirect interactions in plant-pollinator networks and opens the door to predict novel interactions beyond pairwise interactions within a community context.
-
-\doublespacing
-
-# INTRODUCTION
-
-Ecological communities are formed by a plethora of interacting species that form networks of interactions.
-Because of the tremendous complexity of these ecological networks, species interactions are generally condensed in metrics that summarize this information [@guimaraes2020].
-Plant-pollinator interactions are no exception, and they are often studied with indices that aggregate the information at the species (micro-scale) or network level (macro-scale).
-For example, plant-pollinator network level approaches have identified common invariant structural properties across networks, including a degree distribution that decays as a power law [@jordano1987], nestedness [@bascompte2003], or modularity [@olesen2007].
-In addition, the local species position within the network can define its degree of specialization [@bluthgen2006] or its role connecting the rest of the community [@olesen2007].
-Despite the unquestionable progress with the use of these metrics at both species and network level, condensing the information into a single metric implies the loss of relevant ecological information that obscure the understanding of the ecological processes [@cirtwill2018; @simmons2019].
-
-Traditionally, plant-pollinator research has focused on direct interactions but overlooked indirect interactions (i.e., the mediated effect between two species by a third species), such as facilitative or competitive interactions between plants for pollinators [@moeller2004; @sargent2008].
-Despite the widespread nature of indirect interactions in ecological communities [@strauss1991], plant-pollinator research often fails to finely capture those indirect interactions with the conventional analytical tools that condense the information either by species (e.g., interaction frequency) or in global topological indices (e.g., nestedness).
-Nonetheless, the emerging framework of network motifs (small sub-networks recorded within a given network) in plant-pollinator research allows to consider both direct and indirect interactions [@simmons2019].
-Motifs are often referred to as the building blocks of a network that depict subsets of interactions [@milo2002].
-The analysis of network motifs in plant-pollinator networks have revealed that the different ecological processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions [@simmons2020].
-Yet, the global patterns of indirect interactions in real plant-pollinator networks are still unknown (e.g., over- and under- represented motifs).
-
-Despite motifs are abstract representations often decoupled from species ecology, linking the structural properties of the meso-scale with the species ecology can help the understanding of ecological processes.
-For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species functional role [@stouffer2012; @baker2015].
-However, it is unclear how the species ecology and life history traits determines the species' functional role within the network of interactions [@coux2016].
-For example, large pollinators can forage larger distances [@greenleaf2007], deposit greater pollen quantities [@foldesi2021] and handle complex zygomorphic flowers in comparison with small pollinators that are restricted to lower floral complexity [@gong2009].
-How this different pollinator behavior translates into their interaction topology is unknown.
-Similarly, recent empirical findings indicate that the meso-scale is the best descriptor of plant reproductive success [@allen2021], but little is known about how plants reproductive strategies shape their position within the network of interactions.
-Although some studies have evaluated plant reproductive strategies in plant-pollinator networks [@tur2013; @lazaro2020], this is an often overlooked aspect in a community context [@devaux2014] and rarely incorporated into plant-pollinator network studies.
-Hence, exploring how the main plant reproductive strategies integrate with the emergent motif framework can shed light on key aspects of ecosystem functioning.
-
-Here, we used 60 plant-pollinator networks from 18 different studies and 14 countries, alongside functional groups of plants and floral visitors based on functional traits and taxonomic rank, respectively.
-To obtain plant functional groups, we used a comprehensive dataset that included floral, reproductive and vegetative traits compiled in a larger set of networks.
-Floral visitor functional groups were divided by the main taxonomic groups that differed in life form and behaviour.
-Once we split the different plant-pollinator networks into their motif elements, we explored: (i) if there is a common invariant structural property in the overall motif networks (i.e.
-over and under-represented motifs); (ii) which functional groups are over and under-represented in the different motif positions; and, (iii) if there are over and under-reprsented functional group combinations within a motif.
-
-# METHODS
-
-**Plant-pollinator studies**
-
-We have compiled 60 plant-pollinator networks from 18 different studies (**Table S1**).
-All studies sampled plant-pollinator interactions in natural systems and were selected based on wide geographical coverage and presence of interaction frequency as a measure of interaction strength.
-In total, there were 503 plant species, 1,111 floral visitors species and 6,248 pairwise interactions registered.
-For ease of data manipulation, plant and floral visitors species names were standardize with the help of the R package _taxize_ version _0.9.99_ [@chamberlain2020].
-All analyses and data manipulation were conducted in R _version 4.0.5_ [@R].
-
-**Plant and floral visitors functional groups**
-
-First, plant species were grouped through hierarchical clustering into the optimal number of functional groups that summarized the main plant reproductive strategies.
-For this, we used the trait dataset collated in Chapter 1 that comprised a total of 1506 species including the 503 species considered in this study (Supplementary material Chapter 1 **Table S1**).
-This dataset consisted on 8 floral, 4 reproductive and 3 vegetative traits excluding traits with high percentage of missing values (over 30$\%$; **Table S2**).
-We opted to calculate the plant functional groups on this larger set of species because of the higher accuracy when delimiting functional groups with that many variables and species [@dolnicar2014].
-To feed the clustering analysis, we calculated the distance between the different qualitative and scaled quantitative variables with Gower distance [@gower1971].
-For this, we used the function _gowdis_ with method _ward.D2_ from the package _FD_ version _1.0-12_ [@laliberte2014].
-Finally, we conducted hierarchical clustering with the function _hclust_ from the _R_ stats package version _4.0.5_ and calculated the optimal number of clusters with the function _kgs_ from the package _maptree_ version _1.4-7_ [@white2009].
-
-Second, floral visitors were grouped into functional groups based on taxonomic rank as done similarly in past plant-pollinator studies [@fenster2004; @ollerton2009].
-We opted to divide floral visitors on the taxonomic rank level and not with functional traits because the main orders of floral visitors differed in form and behaviour and had lower superior taxonomical complexity (i.e., floral visitors had 6 orders versus plants that had 38).
-Thus, this allowed us to group floral visitors into functional groups that represented adequately the main life strategies of the possible pollinators: (i) bees (Hymenoptera-Anthophila), (ii) non-bee Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Syrphidae-Diptera), (iv) non-syrphids-Diptera, (v) Lepidoptera and (vi) Coleoptera.
-However, a minor set of species belonged to other functional groups that were considered in analyses but not discussed further because of their low representation in the full set of networks (3.55$\%$ of the total interactions recorded).
-These functional groups were 'lizards', 'birds' and 'other insects'.
-This last group was formed by a mix of uncommon insect taxa on the full set of networks.
-
-**Overall motif patterns**
-
-Following previous work [@simmons2019; @simmons2020], we broke down the plant-pollinator networks into their constituent motifs.
-Prior to analyses, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.
-To test the effect of singletones, we ran all analysis to the same set of networks, but considering only interactions whose frequency was greater than one (64.98$\%$ of interactions).
-Results are qualitatively consistent and are not further discussed in the main text (**Figures S1 and S2**).
-
-We calculated the frequency of all motifs up to five nodes (see **Figure 1**) for each empirical network, by using the _bmotif_ package version _2.0.2_ [@bmotifsimmons2019].
-To control for variation in network size, motif frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains).
-Like @simmons2020, we just used five-node motifs in our analyses for visualisation, interpretation and computational reasons.
-In addition, we also excluded two-node motifs (or links) from our analyses because their normalised frequencies would always equal one.
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, fig.pos="t", warning=FALSE,out.width="75%",fig.align="center", fig.cap="\\textbf{Figure 1.} Adapted figure of Simmons et al., 2019 with all the possible motifs from two to five species in bipartite networks.
-There is a total of 17 possible motifs with 46 different positions denoted within each node.", fig.width=10,fig.height=8}
-library(tidyverse)
-library(RColorBrewer)
-source("../Scripts/Scripts_Alfonso/plot_motif_positionsV2.R")
-
-motif_number <- 1
-p1 <- plot_motif_positions(motif_number)
-
-motif_number <- 2
-p2 <- plot_motif_positions(motif_number)
-
-motif_number <- 3
-p3 <- plot_motif_positions(motif_number)
-
-motif_number <- 4
-p4 <- plot_motif_positions(motif_number)
-
-motif_number <- 5
-p5 <- plot_motif_positions(motif_number)
-
-motif_number <- 6
-p6 <- plot_motif_positions(motif_number)
-
-motif_number <- 7
-p7 <- plot_motif_positions(motif_number)
-
-motif_number <- 8   
-p8 <- plot_motif_positions(motif_number)
-
-motif_number <- 9
-p9 <- plot_motif_positions(motif_number)
-
-motif_number <- 10
-p10 <- plot_motif_positions(motif_number)
-
-motif_number <- 11
-p11 <- plot_motif_positions(motif_number)
-
-motif_number <- 12
-p12 <- plot_motif_positions(motif_number)
-
-motif_number <- 13
-p13 <- plot_motif_positions(motif_number)
-
-motif_number <- 14
-p14 <- plot_motif_positions(motif_number)
-
-motif_number <- 15
-p15 <- plot_motif_positions(motif_number)
-
-motif_number <- 16
-p16 <- plot_motif_positions(motif_number)
-
-motif_number <- 17
-p17 <- plot_motif_positions(motif_number)
-
-library(patchwork)
-
-(p1 & ylab("2 species")| p2 & ylab("3 species") | p3 )/ (p4 & ylab("4 species")| p5 | p6 | p7)/ (p8  & ylab("5 species")| p9 | p10 | p11 | p12) / (p13 & ylab("5 species")| p14 | p15 | p16 | p17) & theme(axis.title.y = element_text(color="black", size=14, face="bold")) #+
- #plot_annotation(tag_levels = '1')
-
-```
-
-To assess the significance of the observed frequencies, we created 1,000 simulated networks for each binary network using the _nullmodel_ function and the _vaznull_ model in the _bipartite_ package version _2.14_ [@dormann2009].
-Generated networks had the same number of plants and floral visitors, as well as the same connectance of their corresponding empirical networks.
-After extracting the motif frequencies from the simulated networks, for each motif type and empirical network, we calculated the percentage of simulated networks whose frequencies were smaller than the ones observed, that is, we estimated the percentile of the observed motif frequencies.
-Motifs whose percentile is close to 0 or 100 are under- or over-represented in the empirical networks, respectively, and thus they cannot be predicted by connectance and the number of species alone.
-To summarize general patterns across networks, we used an intercept-only linear mixed model (LMM) per motif with the help of the package lmer version _1.1-21_ [@bates2015], where the response variable was the observed motif percentile per network.
-In these models, we used the study identifiers in **Table S1** as a random intercept.
-By doing so, we obtained estimates of the average motif frequency, but controling the variation at the study level.
-
-**Over and under-represented functional groups on motif positions**
-
-We calculated which functional groups were over or under-represented in different motif positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
-To estimate the position frequencies of each functional group in a given network, we added the frequencies of those species that belong to the group, and then, we normalised the resulting frequencies by dividing the position measure for each group by the total number of times that a group appears in any position within the same motif size class.
-Then, we calculated the percentile of the observed position frequencies for each group and network, just like we did with motif frequencies.
-To outline the general patterns of position frequencies across networks and functional groups, we fit a LMM per motif position, where the response variable was the observed position percentile per network.
-We used the functional group identifier as an explanatory variable and the study identifiers as a random intercept.
-By adding the functional group estimates to the model intercept, we assessed the average motif frequency, after controlling the variation at the study level.
-Finally, we visualized with the help of the package _ComplexHeatmap_ version _2.6.2_ [@gu2016] over- and under- representation of plant and pollinator functional groups on the different motif positions.
-
-**Over- and under-represented funtional group combinations of motifs**
-
-Finally, we studied which combinations of functional groups tend to appear together within the same motifs (up to five nodes).
-That is which combinations are over or under-represented.
-This analysis use 57 out of the 60 networks available due to computational limitations to identify all the nodes in the motifs of the three networks with the highest number of links.
-To do so, for each of the 53,250 possible motif combinations, we estimated the observed and the expected probability of finding those combination in empirical networks, respectively.
-Then, we determined whether the observed probabilities are likely to come from the expected probabilities or not.
-To calculate the observed probability ($p_i^O$) of functional groups within a motif $i$ (e.g., motif 3, 'bee' + 'bee' + 'selfing herbs'), we divided the number of times that $i$ appears in our set of empirical networks ($n_i^O$) by the sum of the number of times that each possible combination appeared: $p_i^O = n_i^O / \sum_{k=1}^{53,250} n_k^O$.
-To estimate the expected probability of a given motif combination $i$, $p_i^E$, firstly, we calculated the probability of finding a given functional group $x$ in the position $\alpha$ of $i$, $p_i(x,\alpha)$.
-Then, by assuming the independency of $p_i(x,\alpha)$, we computed the expected probability of the combination $i$ as the product of the probability of its pairs $(x,\alpha)$, that is, $p_i^E = \prod _{(x,\alpha )\in i} p_i(x,\alpha)$.
-To obtain $p_i(x,\alpha)$, we proceeded as follows.
-First, we calculated the number of times that the functional group $x$ appears in the position $\alpha$ in each empirical network $\eta$, denoted as $n_i^{\eta}(x,\alpha)$.
-Then, by controlling the variation at the network level, we assessed the average value of the absolute frequency of functional group $x$ appears in the position $\alpha$, $n_i(x,\alpha) = E\left [ n_i^{\eta}(x,\alpha) \right ]$, and estimated $p_i(x,\alpha)$ as $p_i(x,\alpha) = n_i(x,\alpha)/\sum_{k}n_i(k,\alpha)$.
-To obtain $n_i(x,\alpha)$, we fitted a LMM per motif position, where the response variable was the number of times that a given position was observed per network, the explanatory variable was functional group identifier, and the random intercept was given by network identifiers nested within the study identifiers.
-
-Once we obtained $p_i^O$ and $p_i^E$, we used a simulation approach to determine whether the former is likely to come from the latter or not.
-This approach was preferred since the large number of possible motif combinations and the small probabilities for some of them advise against using an exact test of goodness-of-fit or a Chi-square one.
-Specifically, we created 1,000 random samples with repetition of possible motif combinations, where each sample contained 10 million elements and, for each combination, the probability of being selected was equal to its expected probability.
-From those random samples, we extracted the mean and the standard deviation of the expected probability of $i$, denoted as $E\left [ p_i^E \right ]$ and $\sigma\left [ p_i^E \right ]$, respectively, and calculated the z-scores of $p_i^O$ as $z_i^O = \left ( p_i^O - E\left [ p_i^E \right ] \right )/\sigma \left [ p_i^E \right ]$, for those motif combinations with $p_i^O > 0$.
-According to the usual interpretation of z-scores, combinations with $z_i^O > 1.96$ are over-represented, whereas those with $z_i^O < -1.96$ are under-represented, at the 95$\%$  confidence level.
-Notice that we focused on combinations with $p_i^O > 10^{-7}$ because, beyond the interest that can arouse the combinations that appear at most once, we do not have enough numerical resolution to accurately detect whether or not those combinations are under-represented (due to the limited size of our random samples).
-
-#RESULTS
-
-**Plant and floral visitor functional groups**
-
-The hierarchical cluster analysis divided the dataset into five different groups with different and overlapping characteristics (**Figure S3** and **Figure S4**).
-The first group referred to as 'selfing herbs' consisted on herbs with hermaphroditic flowers with high levels of autonomous selfing.
-The second group named 'small outcrossing perennials' had small perennial species with a mixed of life forms (i.e., trees shrubs and herbs) with outcrossing hermaphroditic flowers.
-The third group referred to as 'self-incompatible perennials with large flowers' comprised perennial species with a mixed of life forms and large self-incompatible hermaphroditic flowers with high number of ovules.
-The fourth group named 'tall plants with small unisexual flowers' had the tallest species, highest proportion of shrub and tree life forms, dioecious and monoecious breeding systems, small flowers and the highest numbers of flowers and inflorescences per plant.
-Finally, the fifth group named 'short-lived outcrossers with long zygomorphic flowers' consisted on small perennial and short-lived herbs with long self-compatible zygomorphic flowers that were unable to self-pollinate.
-
-In total, there were 1,126 species of floral visitor with 6,325 interactions recorded with plants.
-Most plants interacted with bees (2,256 interactions) and non-syrphid Diptera (1,768) followed by syrphids (845), Lepidoptera (437), Coleoptera (432) and non-bee Hymenoptera (362).
-
-**Overall motif patterns**
-
-Most motifs were under- and over-represented (close to the 1st and 99th percentile, respectively) in the comparison between empirical and simulated networks (**Figure 2**).
-Motifs 3, 5, 9, 10 and 14 were under-represented in empirical networks, that is, all were close to the 1st percentile and under the 25th percentile.
-Interestingly, four out of five of these motifs belonged to the largest path length classification (i.e., core-peripheral).
-In addition, motifs 2, 6, 7, 16 and 17 were over-represented, all over the 75th percentile and thus the closest to the 99th percentile.
-In contrast to the under-represented motifs, over-represented motifs belonged to the two shortest path length groups (i.e., complete and fan).
-The remaining motifs (i.e., 4, 8, 11, 12, 13, and 15) were between the 25th and 75th percentile.
-Notably, the exclusion of singletones from this analysis did not change the observed results (**Figure S1**).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure 2.** Comparison of motif frequencies between empirical and simulated networks grouped by average path length (plots a, b, c and d) as determined in Simmons et al.
-(2020).
-This is shown with the mean percentage of motif frequencies in empirical networks that were over the motif frequencies of the simulated ones (percentiles).
-This was done by network (light blue dots) and then averaged for all networks (black dots with error bars that correspond to the standard deviation)."}
-library(lme4)
-library(nlme)
-library(tidyverse)
-source("../Scripts/Scripts_Alfonso/add_study_id.R")
-d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
-d <- add_study_id(d)
-#str(d)
-#head(d)
-
-#ggplot(d %>% filter(motif != 1), aes(percentil_sizeclass))+
-#  geom_histogram(color="black", fill="white")+
-#  facet_wrap(~motif)+
-#  theme_bw()+
-#  labs(x="Sizeclass percentile")
-#
-# Motifs tend to be over- and under-represensented in real networks
-
-# Mean percentile and SE taking into account the study system
-motif_codes <- d %>% filter(motif != 1) %>% # We remove links (motif code: 1)
-  select(motif) %>% unique() %>% pull()
-motif_means <- tibble(motif = motif_codes)
-motif_means$mean <- NA
-motif_means$SE <- NA
-
-for(i.motif in 1:length(motif_codes)){
-
-  m <- lmer(percentil_sizeclass ~ 1+(1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = subset(d, motif == motif_codes[i.motif]))
-
-  motif_means$mean[i.motif] <- fixed.effects(m) %>% unname()
-  motif_means$SE[i.motif] <- sqrt(diag(vcov(m)))
-
-}
-
-#Add categories based on path length set by Simmons 2021 et al., Functional Ecology
-d$Broad_categories[d$motif==2 | d$motif==7 | d$motif==17 | d$motif==3|d$motif==4|d$motif==8] <- "Fan"
-
-d$Broad_categories[d$motif==15 | d$motif==11] <- "Medium-weak"
-
-d$Broad_categories[d$motif==6 | d$motif==16 |  d$motif==12] <- "Strong"
-
-d$Broad_categories[d$motif==5 | d$motif==9 |  d$motif==14|  d$motif==13|  d$motif==10] <- "Weak"
-
-#order the categories from short to long path length
-d$Broad_categories <- factor(d$Broad_categories, levels = c("Strong", "Fan", "Medium-weak", "Weak"))
-
-#Ffilter out two node motifs
-d_1 <- d %>% filter(motif != 1)
-#Merge dataframes to bl able to create facets
-d_2 <- merge(d_1, motif_means, by="motif")
-
-arr <- list('Strong' = expression(bold(paste("(a) Complete (strong, ", bar(x), " = 1.38)"))),
-             'Fan' = expression(bold(paste("(b) Fan (medium-strong, ", bar(x), " = 1.48)"))), 
-             'Medium-weak' = expression(bold(paste("(c) Asymmetric complete (medium-weak, ", bar(x), " = 1.60)"))), 
-             "Weak" =expression(bold(paste("(d) Core-peripheral (weak, ", bar(x), " = 1.85)"))))
-mylabel <- function(val) { return(lapply(val, function(x) arr[x])) }
-
-library(ggforce) #workaround with ggforce to have facets with same sizes
-
-p <- ggplot()+geom_point(data = d_2, aes(y=factor(motif), 100*percentil_sizeclass), shape=21,color="black",fill="azure2",size=1.75, alpha=0.3)+
-  geom_errorbar(data = d_2,aes(y = factor(motif), xmin=100*(mean-SE), xmax=100*(mean+SE)), 
-                width=0.8,size=0.8,color="black") +theme_bw()+
-  geom_point(data = d_2,aes(y = as.factor(motif), x=100*mean), 
-             size=2,color="black")+labs(y="Two to five node motifs", x = "Percentile")+
-  theme( strip.background = element_blank())+
-  theme(strip.text = element_text(face="bold", size=10, hjust=0),
-        panel.border=element_rect(color="black",size=1.2))
-
-p + ggforce::facet_col(vars(Broad_categories), scales = 'free', space = 'free',labeller=mylabel)
-
-#Trying to maintain a gradient from low to high in colors
-
-#Fig 1 Should be a dot plot (or forest plot) of the mean +- SE of the 15 motifs.
-#NICE! Can we put motifs in Y axes, and % in X?
-```
-
-**Over and under-represented functional groups on motif positions**
-
-```{r , include=FALSE}
-
-#SAME SCRIPT AS THE PLOTTING FOR THE HEATMAP BUT I NEED IT HERE TO LOAD THE VARIABLES WITH VALUES ON RESULTS
-
-library(lme4)
-library(nlme)
-library(tidyverse)
-library(stringi)
-source("../Scripts/Scripts_Alfonso/add_study_id.R")
-
-#############################################
-# EXTRACT MEAN VALUES
-#############################################
-all_position_percentiles <- read_csv("../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
-
-all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
-                                                              "[0-9]+") %>% as.numeric()
-
-all_position_percentiles <- add_study_id(all_position_percentiles)
-#str(all_position_percentiles)
-#head(all_position_percentiles)
-
-list_plants_FG <- as.character(1:10)
-
-plant_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF)) #ME DA ERROR
-pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF))
-
-# Plants-------------
-
-# Mean percentile and SE taking into account the study system
-plant_codes <- plant_position_percentiles_filtered$position %>% unique()
-plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-plant_means$mean <- NA
-plant_means$SE <- NA
-
-for(i.pos in 1:length(plant_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
-            data = plant_position_percentiles_filtered %>%
-              filter(position == plant_codes[i.pos]))
-
-  temp <- fixed.effects(m) %>% unname()
-  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
-                                                                    temp[1]+temp[2],
-                                                                    temp[1]+temp[3],
-                                                                    temp[1]+temp[4],
-                                                                    temp[1]+temp[5]) ## to get real means per FG
-  temp <- sqrt(diag(vcov(m)))
-  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
-                                                                  temp[1]+temp[2],
-                                                                  temp[1]+temp[3],
-                                                                  temp[1]+temp[4],
-                                                                  temp[1]+temp[5])
-
-}
-
-# Pollinators--------
-
-# Mean percentile and SE taking into account the study system
-pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
-pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-pollinator_means$mean <- NA
-pollinator_means$SE <- NA
-pollinator_means_reordered <- NULL
-
-for(i.pos in 1:length(pollinator_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = pollinator_position_percentiles_filtered %>%
-              filter(position == pollinator_codes[i.pos]),
-            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
-
-  temp <- fixed.effects(m) %>% unname()
-  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)
-
-  pollinator_means_aux$mean <- c(temp[1],
-                                 temp[1]+temp[2],
-                                 temp[1]+temp[3],
-                                 temp[1]+temp[4],
-                                 temp[1]+temp[5],
-                                 temp[1]+temp[6],
-                                 temp[1]+temp[7],
-                                 temp[1]+temp[8],
-                                 temp[1]+temp[9]) ## to get real means per FG
-
-  temp <- sqrt(diag(vcov(m)))
-  pollinator_means_aux$SE <- c(temp[1],
-                               temp[1]+temp[2],
-                               temp[1]+temp[3],
-                               temp[1]+temp[4],
-                               temp[1]+temp[5],
-                               temp[1]+temp[6],
-                               temp[1]+temp[7],
-                               temp[1]+temp[8],
-                               temp[1]+temp[9])
-
-  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)
-
-}
-
-# There are lower limits (mean - SE) smaller than 0 (see Other insects)
-# We set the lower limit of those error bars to zero
-
-pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
-pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
-
-#############################################
-# ADDING BROAD MOTIF CATEGORIES TO POSITIONS
-#############################################
-
-motifs_raw_data <- read_csv("../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-motifs_raw_data$Broad_categories <- NA
-
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(5,9,14,13,10)] <- "Core-peripherical"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(6,16,12)] <- "Complete"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(2,3,7,4,17,8)] <- "Fan"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(15,11)] <- "Asymmetric complete"
-
-motifs_raw_data$plant <- gsub("[^0-9.-]", "", motifs_raw_data$plant)
-motifs_raw_data$pollinator <- gsub("[^0-9.-]", "", motifs_raw_data$pollinator)
-motifs_raw_data$plant <- as.numeric(motifs_raw_data$plant)
-motifs_raw_data$pollinator <- as.numeric(motifs_raw_data$pollinator)
-motifs_raw_data <- motifs_raw_data %>% filter(!is.na(Broad_categories))
-
-fan_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-pollinator_means_reordered$Broad_categories <- NA
-
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% fan_pollinator] <- "Fan" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% asymm_pollinator] <- "Medium-weak" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% complete_pollinator] <- "Strong" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% core_per_pollinator] <- "Weak"
-
-fan_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-plant_means$Broad_categories <- NA
-
-plant_means$Broad_categories[plant_means$position %in% fan_plant] <- "Fan" 
-plant_means$Broad_categories[plant_means$position %in% asymm_plant] <- "Medium-weak" 
-plant_means$Broad_categories[plant_means$position %in% complete_plant] <- "Strong" 
-plant_means$Broad_categories[plant_means$position %in% core_per_plant] <- "Weak"
-
-################################################################################
-# Alternative code to HEATMAPS to create variables with values to load on text
-# in a reproducible/automated way
-################################################################################
-
-# PLANTS-----
-
-# Prepare data for heatmap
-heat_plants_aux <- plant_means %>% spread(Node_FG,mean) %>% select(-SE)
-
-heat_plants <- heat_plants_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-# POLLINATORS-----------
-
-filter_rare_groups <- T
-
-if(filter_rare_groups == T){
-  heat_pollinators_aux <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds",
-                                                                                "Lizards",
-                                                                                "Other_insects")) %>% 
-    spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees",            
-                                      "Coleoptera","Lepidoptera","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Syrphids")
-}else{
-  heat_pollinators_aux <- pollinator_means_reordered %>% spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees","Birds",            
-                                      "Coleoptera","Lepidoptera","Lizards","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Other insects","Syrphids")
-}
-
-heat_pollinators <- heat_pollinators_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))
-
-#Check percentage of over and under represented
-colMeans(heat_pollinators[,c(3:8)] < 0.25)
-poll_under_25 <- colMeans(heat_pollinators[,c(3:8)] < 0.25)
-poll_under_25 <- specify_decimal((poll_under_25[[1]] + poll_under_25[[2]] + poll_under_25[[3]] +
-poll_under_25[[4]] + poll_under_25[[5]] + poll_under_25[[6]])/6*100,2)
-#[1] 32.57576
-
-colMeans(heat_pollinators[,c(3:8)] > 0.75)
-poll_over_75 <- colMeans(heat_pollinators[,c(3:8)] > 0.75)
-poll_over_75 <- specify_decimal((poll_over_75[[1]] + poll_over_75[[2]] + poll_over_75[[3]] +
-    poll_over_75[[4]] + poll_over_75[[5]] + poll_over_75[[6]])/6*100,2)
-#[1] 4.545455
-
-#################################################################################
-#################################################################################
-
-colnames(heat_plants)<- c("position", "Broad_categories", "one",
-                               "two", "three","four",
-                               "five")
-f <- heat_plants %>%
-  mutate(min = pmin(1,
-                    one, two,three,
-                    four, five))%>%
-  mutate(max = pmax(one,
-                    two, three,four,
-                    five))
-
-diff_1 <- f$max-f$min
-
-cbind(diff,diff_1)
-
-#Check percentage of over and under represented per FG
-colMeans(heat_plants[,c(3:7)] < 0.25)
-plant_under_25 <- colMeans(heat_plants[,c(3:7)] < 0.25)
-plant_under_25 <- specify_decimal((plant_under_25[[1]] + plant_under_25[[2]] + plant_under_25[[3]] + 
-    plant_under_25[[4]] + plant_under_25[[5]])/5*100,2)
-#[1] 18.18182
-colMeans(heat_plants[,c(3:7)] > 0.75)
-plant_over_75 <- colMeans(heat_plants[,c(3:7)] > 0.75)
-plant_over_75 <- specify_decimal((plant_over_75[[1]] + plant_over_75[[2]] + plant_over_75[[3]] + 
-    plant_over_75[[4]] + plant_over_75[[5]])/5*100,2)
-#[1] 8.181818
-
-#overall percentages
-under <- specify_decimal((as.numeric(poll_under_25) + as.numeric(plant_under_25))/2,2)
-over <- specify_decimal((as.numeric(poll_over_75) + as.numeric(plant_over_75))/2,2)
-
-```
-
-The comparison of the functional group frequencies per motif position between empirical and simulated networks showed a `r over`$\%$ and `r under`$\%$ of over- (>75$^{th}$) and under- (<25th) represented functional groups in the different positions, respectively (**Figure 3**).
-Floral visitors showed a total of `r poll_over_75`$\%$ and `r poll_under_25`$\%$ of over- and under-represented functional groups in the different positions and plants `r plant_over_75`$\%$ and `r plant_under_25`$\%$ of over and under-represented groups, respectively.
-Notably, the differences across functional groups were more marked for floral visitors than for plant functional groups (the differences between min and max percentiles per position were generally two-three times larger for floral visitors).
-From most over- to under-represented floral visitors functional groups on the different motif positions (indicated with the dendrogram order in **Figure 3**), we found: bees, non-syrphids Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.
-Although plant functional groups showed less differences between them, there were also more represented functional groups than others, thus from most over- to under-represented groups on the different motif positions we found: self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', out.width="80%",fig.cap="\\textbf{Figure 3.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions.
-The different motif positions are dividied by the average path length clasification determined by Simmons et al.
-(2020).
-The superior dendrogram indicates the differences across groups with the more separated groups showing larger differences."}
-
-library(lme4)
-library(nlme)
-library(tidyverse)
-library(stringi)
-source("../Scripts/Scripts_Alfonso/add_study_id.R")
-
-#############################################
-# EXTRACT MEAN VALUES
-#############################################
-
-all_position_percentiles <- read_csv("../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
-
-all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
-                                                              "[0-9]+") %>% as.numeric()
-
-all_position_percentiles <- add_study_id(all_position_percentiles)
-#str(all_position_percentiles)
-#head(all_position_percentiles)
-
-list_plants_FG <- as.character(1:10)
-
-plant_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF)) #ME DA ERROR
-pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF))
-
-# Plants-------------
-
-# Mean percentile and SE taking into account the study system
-plant_codes <- plant_position_percentiles_filtered$position %>% unique()
-plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-plant_means$mean <- NA
-plant_means$SE <- NA
-
-for(i.pos in 1:length(plant_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
-            data = plant_position_percentiles_filtered %>%
-              filter(position == plant_codes[i.pos]))
-
-  temp <- fixed.effects(m) %>% unname()
-  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
-                                                                    temp[1]+temp[2],
-                                                                    temp[1]+temp[3],
-                                                                    temp[1]+temp[4],
-                                                                    temp[1]+temp[5]) ## to get real means per FG
-  temp <- sqrt(diag(vcov(m)))
-  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
-                                                                  temp[1]+temp[2],
-                                                                  temp[1]+temp[3],
-                                                                  temp[1]+temp[4],
-                                                                  temp[1]+temp[5])
-
-}
-
-# Pollinators--------
-
-# Mean percentile and SE taking into account the study system
-pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
-pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-pollinator_means$mean <- NA
-pollinator_means$SE <- NA
-pollinator_means_reordered <- NULL
-
-for(i.pos in 1:length(pollinator_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = pollinator_position_percentiles_filtered %>%
-              filter(position == pollinator_codes[i.pos]),
-            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
-
-  temp <- fixed.effects(m) %>% unname()
-  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)
-
-  pollinator_means_aux$mean <- c(temp[1],
-                                 temp[1]+temp[2],
-                                 temp[1]+temp[3],
-                                 temp[1]+temp[4],
-                                 temp[1]+temp[5],
-                                 temp[1]+temp[6],
-                                 temp[1]+temp[7],
-                                 temp[1]+temp[8],
-                                 temp[1]+temp[9]) ## to get real means per FG
-
-  temp <- sqrt(diag(vcov(m)))
-  pollinator_means_aux$SE <- c(temp[1],
-                               temp[1]+temp[2],
-                               temp[1]+temp[3],
-                               temp[1]+temp[4],
-                               temp[1]+temp[5],
-                               temp[1]+temp[6],
-                               temp[1]+temp[7],
-                               temp[1]+temp[8],
-                               temp[1]+temp[9])
-
-  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)
-
-}
-
-# There are lower limits (mean - SE) smaller than 0 (see Other insects)
-# We set the lower limit of those error bars to zero
-
-pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
-pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
-
-#############################################
-# ADDING BROAD MOTIF CATEGORIES TO POSITIONS
-#############################################
-
-motifs_raw_data <- read_csv("../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-motifs_raw_data$Broad_categories <- NA
-
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(5,9,14,13,10)] <- "Core-peripherical"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(6,16,12)] <- "Complete"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(2,3,7,4,17,8)] <- "Fan"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(15,11)] <- "Asymmetric complete"
-
-motifs_raw_data$plant <- gsub("[^0-9.-]", "", motifs_raw_data$plant)
-motifs_raw_data$pollinator <- gsub("[^0-9.-]", "", motifs_raw_data$pollinator)
-motifs_raw_data$plant <- as.numeric(motifs_raw_data$plant)
-motifs_raw_data$pollinator <- as.numeric(motifs_raw_data$pollinator)
-motifs_raw_data <- motifs_raw_data %>% filter(!is.na(Broad_categories))
-
-fan_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-pollinator_means_reordered$Broad_categories <- NA
-
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% fan_pollinator] <- "Fan" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% asymm_pollinator] <- "Medium-weak" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% complete_pollinator] <- "Strong" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% core_per_pollinator] <- "Weak"
-
-fan_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-plant_means$Broad_categories <- NA
-
-plant_means$Broad_categories[plant_means$position %in% fan_plant] <- "Fan" 
-plant_means$Broad_categories[plant_means$position %in% asymm_plant] <- "Medium-weak" 
-plant_means$Broad_categories[plant_means$position %in% complete_plant] <- "Strong" 
-plant_means$Broad_categories[plant_means$position %in% core_per_plant] <- "Weak"
-
-########################################
-# CREATE HEATMAPS
-########################################
-
-library(ComplexHeatmap)
-
-# PLANTS-----
-
-# Prepare data for heatmap
-heat_plants_aux <- plant_means %>% spread(Node_FG,mean) %>% select(-SE)
-
-heat_plants <- heat_plants_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-heat_plants_fan <- heat_plants %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_fan) <- heat_plants_fan[,1]
-
-heat_plants_Weak <- heat_plants %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Weak) <- heat_plants_Weak[,1]
-
-heat_plants_Strong <- heat_plants %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Strong) <- heat_plants_Strong[,1]
-
-heat_plants_Medium_weak <- heat_plants %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Medium_weak) <- heat_plants_Medium_weak[,1]
-
-# POLLINATORS-----------
-
-filter_rare_groups <- T
-
-if(filter_rare_groups == T){
-  heat_pollinators_aux <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds",
-                                                                                "Lizards",
-                                                                                "Other_insects")) %>% 
-    spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees",            
-                                      "Coleoptera","Lepidoptera","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Syrphids")
-}else{
-  heat_pollinators_aux <- pollinator_means_reordered %>% spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees","Birds",            
-                                      "Coleoptera","Lepidoptera","Lizards","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Other insects","Syrphids")
-}
-
-heat_pollinators <- heat_pollinators_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-heat_pollinators_fan <- heat_pollinators %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_fan) <- heat_pollinators_fan[,1]
-
-heat_pollinators_Weak <- heat_pollinators %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Weak) <- heat_pollinators_Weak[,1]
-
-heat_pollinators_Strong <- heat_pollinators %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Strong) <- heat_pollinators_Strong[,1]
-
-heat_pollinators_Medium_weak <- heat_pollinators %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Medium_weak) <- heat_pollinators_Medium_weak[,1]
-
-##################
-
-#Do not know how to handle this multiplot for creating a panel
-
-# I'm going to create the 4 plots in one, 
-# I'm not sure that the grouping of the functional group is correct
-# when is done separately
-
-#sorry for the mess of libraries that I do below
-
-#Prepare first pollinators
-
-library(tidyr)
-library(data.table)
-long <- melt(setDT(heat_pollinators), id.vars = c("position","Broad_categories"), variable.name = "guilds")
-
-long_1 <- long %>% select(-Broad_categories)
-
-library(reshape2)
-long_m <- acast(long_1, position~guilds, value.var="value")
-
-#set manually the divisions, so far this is the best way I have seen to split the rows by categories
-
-r_split <- c(rep(c("Fan"), 3),rep(c("Core-peripheral"), 2),"Complete",rep(c("Fan"),2),rep(c("Core-peripheral"), 4),
-             rep(c("Asymmetric complete"), 2), "Complete", rep(c("Core-peripheral"), 3),rep(c("Asymmetric complete"), 2),
-             "Complete", "Fan")
-
-#set order of labels that avoids overlapping
-r_split <- factor(r_split, levels=c("Core-peripheral","Complete","Fan","Asymmetric complete"))
-
-#plat a bit with colors, a bit of a more complex set but looks nicer
-library(circlize)
-col_fun = colorRamp2(c(0.05644663,0.25, 0.4673256,0.75, 0.8782047), c("blue","cadetblue3", "azure2", "gold","red"))
-
-h_pol <- Heatmap(long_m, name = "Mean\npercentile", row_split=r_split,cluster_row_slices = FALSE, 
-                 column_title = "Pollinator functional groups",row_names_gp = gpar(fontsize = 10),
-                 col = col_fun,column_names_rot = 45,  column_names_gp = grid::gpar(fontsize = 10),
-                 column_title_gp = gpar(fontsize = 15, fontface = "bold"),
-                 row_title_gp = gpar(fontsize = 10, fontface = "bold"))
-
-#Prepare plants
-
-#long format
-long_plants <- melt(setDT(heat_plants), id.vars = c("position","Broad_categories"), variable.name = "Functional_groups")
-
-#filter for creating matrix
-long_plants_1 <- long_plants %>% select(-Broad_categories)
-
-#set better colnames
-long_plants_1$Functional_groups <- as.character(long_plants_1$Functional_groups)
-
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==1] <- "Selfing herbs" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==2] <- "Small outcrossing\nperennials" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==3] <- "Self-incomp. perennials\nwith large flowers" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==4] <- "Tall plants with small\nunisexual flowers" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==5] <- "Short-lived outcrossers with\nlong zygomorphic flowers"
-
-long_plants_1$Functional_groups <- factor(long_plants_1$Functional_groups, levels=c("Selfing herbs",
-"Small outcrossing\nperennials" ,"Self-incomp. perennials\nwith large flowers",
-"Tall plants with small\nunisexual flowers" ,"Short-lived outcrossers with\nlong zygomorphic flowers" ))
-
-#create matrix with reshape
-long_plants_m <- acast(long_plants_1, position~Functional_groups, value.var="value")
-
-r_split_plants <- c(rep(c("Fan"), 3),rep(c("Core-peripheral"), 2),"Complete",rep(c("Fan"),2),rep(c("Core-peripheral"), 3),
-                    rep(c("Asymmetric complete"), 2), "Complete", rep(c("Core-peripheral"), 4),rep(c("Asymmetric complete"), 2),
-                    "Complete", "Fan")
-
-r_split_plants <- factor(r_split, levels=c("Core-peripheral","Complete","Fan","Asymmetric complete"))
-
-h_plan <- Heatmap(long_plants_m, name = "Mean\npercentile", row_split=r_split_plants,cluster_row_slices = F, 
-                  column_title = "Plant functional groups",row_names_gp = gpar(fontsize = 10),col = col_fun,column_names_rot = 45,  
-                  column_names_gp = grid::gpar(fontsize = 10),column_title_gp = gpar(fontsize = 15, fontface = "bold"),
-                  row_title_gp = gpar(fontsize = 10, fontface = "bold"))
-
-library(patchwork)
-ht_list <- h_pol+h_plan
-
-draw(ht_list, auto_adjust = FALSE, cluster_rows = F)
-
-#Exploration of min max differences in the percentile position for plants and poll.
-#heat_pollinators[3:8]
-#
-#
-#heat_plants[3:7]
-#
-#
-#library(dplyr)
-#heat_pollinators %>%
-#  mutate(d = pmin())
-#
-#
-#colnames(heat_pollinators)<- c("position", "Broad_categories", "Bee",
-#                               "Coleoptera", "Lepidoptera","non_bee_hymenop",
-#                               "non_syrphid_dip", "syrphid")
-#
-#h <- heat_pollinators %>%
-#  mutate(min = pmin(Bee,
-#                  Coleoptera, Lepidoptera,non_bee_hymenop,
-#                  non_syrphid_dip, syrphid))%>%
-#  mutate(max = pmax(Bee,
-#                    Coleoptera, Lepidoptera,non_bee_hymenop,
-#                    non_syrphid_dip, syrphid))
-#
-#diff <- h$max-h$min
-#
-##################################################################################
-##################################################################################
-#
-#colnames(heat_plants)<- c("position", "Broad_categories", "one",
-#                               "two", "three","four",
-#                               "five")
-#
-#f <- heat_plants %>%
-#  mutate(min = pmin(1,
-#                    one, two,three,
-#                    four, five))%>%
-#  mutate(max = pmax(one,
-#                    two, three,four,
-#                    five))
-#
-#diff_1 <- f$max-f$min
-#
-#cbind(diff,diff_1)
-#
-
-```
-
-\newpage
-
-**Over- and under-represented functional group combinations of motifs**
-
-The different observed frequencies on the different motif positions showed a hierarchical order of probabilities for floral visitors (**Figure 4**).
-That is, the functional group of 'bees' was the most abundant one on all motif positions followed by non-syrphid Diptera which was after bees, the second most frequent functional group on all positions.
-Then, the group of syrphids was the most abundant in all positions but two (positions 28 and 31 from motifs 11 and 12, respectively).
-After syrphids, Coleoptera was the most frequent group on the different positions followed by non-bee Hymenoptera and finally, Lepidoptera which was the less frequent group on all positions but two (positions 12 and 22 from motifs 5 and 9, respectively).
-Remarkably, plant functional groups were more variable on the different motif positions.
-However, there were also predominant functional groups found across the different motif positions.
-The three most frequent groups were 'tall plants with small unisexual flowers', 'self-incompatible perennials with large flowers' and 'small outcrossing perennials'.
-On the contrary, the groups of 'selfing herbs' and 'short lived outcrossers with long zygomorphic flowers' had the lowest probability to be present on the different motifs plant positions.
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 4.** Graphical representation of the probability of finding a given functional group $x$ in the position $\\alpha$ of motif $i$, $p_i(x,\\alpha)$, for all the possible motifs from two to five species in bipartite networks.
-The slices in the nodes for a given functional group $x$ are proportional to the corresponding value of $p_i(x,\\alpha)$."}
-
-library(ggplot2)
-library(scatterpie)
-library(RColorBrewer)
-library(tidyverse)
-
-plant_means_reordered <- read_csv("../Data/Csv/plant_abs_freq_means.csv")
-pollinator_means_reordered <- read_csv("../Data/Csv/pollinator_abs_freq_means.csv")
-#Filter out in order to have just 6 FG'S
-pollinator_means_reordered <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds", "Lizards", "Other_insects"))
-
-# Pollinator--------
-pollinator_pies <- pollinator_means_reordered %>% select(-mean, -SE) %>% 
-  spread(Node_FG,mean_natural_units)
-
-pollinator_pies$x <- 0
-pollinator_pies$y <- 0
-
-#ggplot() + geom_scatterpie(aes(x=x, y=y, group=position,r=5), 
-#                           data = pollinator_pies,
-#                           cols=as.character(c("Bee","Birds","Coleoptera","Lepidoptera",
-#                                               "Lizards","Non-bee-Hymenoptera",
-#                                               "Non-syrphids-diptera","Other_insects",
-#                                               "Syrphids")))+
-#  coord_equal()+
-#  scale_fill_brewer(palette = "Paired")+
-#  facet_wrap(~position,nrow = 3)+
-#  theme_bw()+
-#    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
-#          panel.background = element_blank(),
-#          axis.title.x=element_blank(),axis.text.x=element_blank(),
-#          axis.ticks.x=element_blank(),axis.title.y=element_blank(),
-#          axis.text.y=element_blank(),axis.ticks.y=element_blank(),
-#          legend.position="bottom")+
-#  labs(title = "Pollinator positions",fill=NULL)
-#    
-# plant--------
-plant_pies <- plant_means_reordered %>% select(-mean, -SE) %>% 
-  spread(Node_FG,mean_natural_units)
-
-plant_pies$x <- 0
-plant_pies$y <- 0
-
-#ggplot() + geom_scatterpie(aes(x=x, y=y, group=position,r=5), 
-#                           data = plant_pies,
-#                           cols=as.character(c("1","2","3","4","5")))+
-#  coord_equal()+
-#  scale_fill_brewer(palette = "Dark2")+
-#  facet_wrap(~position,nrow = 3)+
-#  theme_bw()+
-#  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
-#        panel.background = element_blank(),
-#        axis.title.x=element_blank(),axis.text.x=element_blank(),
-#        axis.ticks.x=element_blank(),axis.title.y=element_blank(),
-#        axis.text.y=element_blank(),axis.ticks.y=element_blank(),
-#        legend.position="bottom")+
-#  labs(title = "Plant positions",fill=NULL)
-#
-
-#################################
-# CREATE PIE-MOTIFS
-#################################
-
-equidistribution <- function(number_nodes){
-
-  x_width <- 5.5/(number_nodes+1)
-
-  x_result <- rep(-1.5,number_nodes)
-
-  for(i in 1:number_nodes){
-
-    x_result[i] <- x_result[i] + i*x_width
-
-  }
-
-  return(x_result)
-
-}
-
-plot_pie_motif_positions <- function(motif_number){
-  motifs_raw_data <- read_csv("../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-  motif_data <- motifs_raw_data %>% filter(motif_id == motif_number)
-
-  # Create dataframe with node positions
-
-  labdown = motif_data$plant %>% unique()
-
-  xdown = equidistribution(length(labdown))
-
-  ydown = rep(0,length(labdown))
-
-  labup = motif_data$pollinator %>% unique()
-
-  xup = equidistribution(length(labup))
-
-  yup = rep(2,length(labup))
-
-  d_nodes=data.frame(x=c(xdown,xup),
-                     y=c(ydown,yup),
-                     label = c(labdown,labup))
-
-  # Create a dataframe with links
-
-  plant_positions <- data.frame(plant = labdown,
-                                xdown = xdown,
-                                ydown = ydown)
-
-  pollinator_positions <- data.frame(pollinator = labup,
-                                     xup = xup,
-                                     yup = yup)
-
-  link_df <- motif_data %>% left_join(plant_positions, by = "plant") %>% 
-    left_join(pollinator_positions, by = "pollinator")
-
-  # Before plotting the motif, we remove letters from the node position id
-
-  d_nodes$label <- gsub("[^0-9.-]", "", d_nodes$label)
-  plant_pies_aux <- plant_pies %>% select(-x,-y) %>% mutate(position = as.character(position))
-
-  d_nodes_plant <- d_nodes %>% rename(position = label) %>% 
-    left_join(plant_pies_aux, by = "position") %>% as_tibble() %>%
-    filter(!is.na(`1`))
-
-  pollinator_pies_aux <- pollinator_pies %>% select(-x,-y) %>% mutate(position = as.character(position))
-
-  d_nodes_pollinator <- d_nodes %>% rename(position = label) %>% 
-    left_join(pollinator_pies_aux, by = "position") %>% as_tibble() %>%
-    filter(!is.na(Bee))
-
-  # Define the number of colors you want
- mycolors <- c("#A6CEE3", "chocolate2",  "gold2", "#1F78B4","#B2DF8A",
-                     "gray58", "lightgoldenrod2","thistle2", "burlywood","lightcoral", "olivedrab3")
-
-  ggplot() +
-    scale_shape_identity() +
-    geom_segment(data = link_df, aes(x=xdown, y=ydown, xend = xup, yend = yup), 
-                 size = 1, color = "grey20")+  geom_scatterpie(aes(x=x, y=y, group=position,r=.45), 
-    data = d_nodes_pollinator, cols=as.character(c("Bee","Coleoptera","Lepidoptera","Non-bee-Hymenoptera", "Non-syrphids-diptera","Syrphids"))) +
-    geom_scatterpie(aes(x=x, y=y, group=position,r=0.45), 
-                    data = d_nodes_plant,
-                    cols=as.character(c("1","2","3","4","5")))+
-    coord_fixed()+
-    scale_fill_manual(values = mycolors,"test",
-      breaks=c("Bee","Coleoptera","Lepidoptera",
-               "Non-bee-Hymenoptera", "Non-syrphids-diptera",
-               "Syrphids","1","2","3","4","5"), labels=c("Bees","Coleoptera","Lepidoptera",
-"Non-bee-Hymenoptera", "Non-syrphids-Diptera","Syrphids", 
-          "Selfing herbs","Small outcrossing perennials","Self-incomp. perennials\nwith large flowers",
-          "Tall plants with small\nunisexual flowers","Short-lived outcrossers with\nlong zygomorphic flowers"))+
-    xlim(-1.5,4)+ ylim(-0.5,2.5)+
-    theme(panel.background = element_blank(),
-          axis.text.x=element_blank(),
-          axis.ticks.x=element_blank(),
-          axis.text.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          legend.title = element_text(size=12, face="bold"),legend.background = element_rect(size=0.5, linetype="solid",colour ="black"))+
-    labs(x=NULL,y=NULL)+
-    guides(color = FALSE,fill=guide_legend(title="Functional groups"))+
-    ggtitle(paste0("Motif ",motif_number))+
-    theme(plot.title = element_text(hjust = 0.5),legend.key.size = unit(0.5, 'cm'))+
-    theme(plot.margin=unit(c(0,0,0,0),"cm"))
-}
-
-motif_number <- 1
-p1 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 2
-p2 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 3
-p3 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 4
-p4 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 5
-p5 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 6
-p6 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 7
-p7 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 8   
-p8 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 9
-p9 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 10
-p10 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 11
-p11 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 12
-p12 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 13
-p13 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 14
-p14 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 15
-p15 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 16
-p16 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 17
-p17 <- plot_pie_motif_positions(motif_number)
-
-library(patchwork)
-
-(p1 & ylab("2 species")| p2 & ylab("3 species") | p3  |plot_spacer()|plot_spacer())/ 
-  (p4 & ylab("4 species")| p5 | p6 | p7|plot_spacer())/ 
-  (p8  & ylab("5 species")| p9 | p10 | p11 | p12) / 
-  (p13 & ylab("5 species")| p14 | p15 | p16 | p17) + plot_layout(guides = 'collect') &
-  theme(axis.title.y = element_text(color="black", size=14, face="bold"),legend.position = "bottom")
-
-```
-
-The statistical comparison with z-scores between the observed and expected functional group combinations showed that we can not recover the observed combinations from its probability of occurrence.
-In fact, most combinations are under- or over- represented and follow a modified Gaussian distribution (Johnson's $S_U$) with 65$\%$ of under-represented group combinations, 20$\%$ of no statistical difference and 15$\%$ of under-represented ones (**Figure 5**).
-In addition, motifs with small node combinations (i.e., 2 and 3 nodes) only appeared as under-represented.
-Motifs with 4 and 5-node combinations appeared in the three statistical categories but 4 node motifs had a higher proportion in the under-represented category (10% in comparison with the 1$\%$ and the 3$\%$ of the no statistical difference and over-represented categories, respectively).
-Finally, 5-node motifs were in similar proportions in the no statistical difference and over-represented categories (99$\%$ and 97$\%$, respectively) but they appeared in lower proportion in the under-represented category (89$\%$).
-When, we explore the identity on the different positions of the most probable motif combinations we find as expected that the most common functional groups rule these positions on the most probable motif combinations (lower panel **Figure 5**).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 5.** Z-score comparison (95% confidence level) of the observed and expected frequencies of motif combinations with four specific graphical examples of the most probable motifs of being observed for each category delimited by the z-score critical values: under-represented, no statistical difference and over-represented."}
-
-library(tidyverse)
-library(RColorBrewer)
-
-equidistribution <- function(number_nodes){
-
-  x_width <- 5.5/(number_nodes+1)
-
-  x_result <- rep(-1.5,number_nodes)
-
-  for(i in 1:number_nodes){
-
-    x_result[i] <- x_result[i] + i*x_width
-
-  }
-
-  return(x_result)
-
-}
-
-plot_motif_label <- function(label){
-
-  label_split <- str_split(label,"_")[[1]]
-  motif_number <- as.numeric(label_split[1])
-  nodes <- label_split[2:length(label_split)]
-  plant_nodes <- nodes[nodes %in% plant_means_reordered$Node_FG]
-  pollinator_nodes <- nodes[nodes %in% pollinator_means_reordered$Node_FG]
-
-  motifs_raw_data <- read_csv("../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-  motif_data <- motifs_raw_data %>% filter(motif_id == motif_number)
-
-  # Create dataframe with node positions
-
-  labdown = motif_data$plant %>% unique()
-
-  xdown = equidistribution(length(labdown))
-
-  ydown = rep(0,length(labdown))
-
-  labup = motif_data$pollinator %>% unique()
-
-  xup = equidistribution(length(labup))
-
-  yup = rep(1,length(labup))
-
-  d_nodes=data.frame(x=c(xdown,xup),
-                     y=c(ydown,yup),
-                     label = c(labdown,labup))
-
-  # Create a dataframe with links
-
-  plant_positions <- data.frame(plant = labdown,
-                                xdown = xdown,
-                                ydown = ydown)
-
-  pollinator_positions <- data.frame(pollinator = labup,
-                                     xup = xup,
-                                     yup = yup)
-
-  link_df <- motif_data %>% left_join(plant_positions, by = "plant") %>% 
-    left_join(pollinator_positions, by = "pollinator")
-
-  # Add FG IDs to nodes
-  FG_IDs <- tibble(label = c(sort(labdown),sort(labup)),
-                   FG = c(plant_nodes,pollinator_nodes))
-
-  d_nodes_FG <- d_nodes %>% left_join(FG_IDs, by = "label")
-  levels_FG <- c("Bee","Coleoptera","Lepidoptera",
-                 "Non-bee-Hymenoptera", "Non-syrphids-diptera",
-                 "Syrphids","1","2","3","4","5")
-
-  d_nodes_FG$FG <- factor(d_nodes_FG$FG, levels = levels_FG)
-
-  levels(d_nodes_FG$FG) <- c("Bee","Coleoptera","Lepidoptera",
-                             "Non-bee-Hymenoptera", "Non-syrphids-diptera",
-                             "Syrphids","1","2","3","4","5")
-
-  # Before plotting the motif, we remove letters from the node position id
-
-  d_nodes_FG$label <- gsub("[^0-9.-]", "", d_nodes_FG$label)
-
-  # Define the number of colors you want
- mycolors <- c("#A6CEE3", "chocolate2",  "gold2", "#1F78B4","#B2DF8A",
-                     "gray58", "lightgoldenrod2","thistle2", "burlywood","lightcoral", "olivedrab3")
-
-  ggplot(data=d_nodes_FG, aes(x, y)) +
-    scale_shape_identity() +
-    geom_segment(data = link_df, aes(x=xdown, y=ydown, xend = xup, yend = yup), size = 1, color = "grey20")+
-    geom_point(aes(color = FG), size=7.5)+
-    geom_text(aes(x, y , label = label), size=3)+
-    scale_color_manual(drop = FALSE, values = mycolors,
-                       breaks=c("Bee","Coleoptera","Lepidoptera",
-                                "Non-bee-Hymenoptera", "Non-syrphids-diptera",
-                                "Syrphids","1","2","3","4","5"), 
-                       labels=c("Bees","Coleoptera","Lepidoptera",
-                                "Non-bee-Hymenoptera", "Non-syrphids-Diptera",
-                                "Syrphids", 
-                                "Selfing herbs","Small outcrossing perennials",
-                                "Self-incomp. perennials\nwith large flowers",
-                                "Tall plants with small\nunisexual flowers",
-                                "Short-lived outcrossers with\nlong zygomorphic flowers"))+
-    xlim(-1.5,4)+ ylim(-0.5,1.5)+
-    theme(panel.background = element_blank(),
-          axis.text.x=element_blank(),
-          axis.ticks.x=element_blank(),
-          axis.text.y=element_blank(),
-          axis.ticks.y=element_blank())+
-    labs(x=NULL,y=NULL)+
-    ggtitle(paste0("Motif ",motif_number))+
-    theme(plot.title = element_text(hjust = 0.5,size=10))+
-    guides(color=guide_legend(title="Functional groups"))
-
-}
-
-# Data with pollinator/plant labels
-
-plant_means_reordered <- read_csv("../Data/Csv/plant_abs_freq_means.csv")
-pollinator_means_reordered <- read_csv("../Data/Csv/pollinator_abs_freq_means.csv")
-#Filter out in order to have just 6 FG'S
-pollinator_means_reordered <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds", "Lizards", "Other_insects"))
-
-####################################################################################################
-#Read data to check top 5 motif of each category of observed propabilities
-
-#Under, No signi, Over-rep
-####################################################################################################
-# Check top Z-scores of each group (Under, No diff, Over)
-
-#Read data
-data <- read.csv("../Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
-
-#Find critical value of Z-score
-p <- 0.05 #cutoff probability 95% confidence
-critical_value <- qnorm(p/2) #double tail probability divide by 2
-
-data_1 <- data %>%
-  mutate(infra_over_represented = case_when(
-    z_score < -abs(critical_value) ~ "infra",
-    between(z_score, -abs(critical_value), abs(critical_value)) ~ "no_diff",
-    z_score > abs(critical_value) ~ "over"
-  ))
-
-#data_2 <- filter(data_1, abs(z_score)<2000) 
-#str(data_2)
-
-#Select under-represented by the ones with highest porbability of being observed (top10)
-under_data <- filter(data_1, infra_over_represented=="infra")
-
-under_top_5 <- filter(under_data, row_number(desc(abs(motif_observed_probability)))<= 5) %>%
-  select(motif_functional_ID,motif_observed_probability,counts_observed,z_score)
-
-#Select no statistical difference by the ones with highest porbability of being observed (top5)
-no_diff_data <- filter(data_1, infra_over_represented=="no_diff")
-
-no_diff_top_5 <- filter(no_diff_data, row_number(desc(abs(motif_observed_probability)))<= 5) %>%
-  select(motif_functional_ID,motif_observed_probability,counts_observed,z_score)
-
-#Select over-represenetd by the ones with highest porbability of being observed (top5)
-over_data <- filter(data_1, infra_over_represented=="over")
-
-over_top_5 <- filter(over_data, row_number(desc(abs(motif_observed_probability)))<= 5) %>%
-  select(motif_functional_ID,motif_observed_probability,counts_observed,z_score)
-####################################################################################################
-#Now plot it 
-####################################################################################################
-
-library(patchwork)
-
-#Prepare list of 5 plots for each group
-#Under
-labels_under <- under_top_5$motif_functional_ID
-p_under <- list()
-
-for (i in 1:5){
-
-  p_under[[i]] <- plot_motif_label(labels_under[[i]])
-}
-
-#No signficance
-labels_nodiff <- no_diff_top_5$motif_functional_ID
-p_nodiff <- list()
-
-for (i in 1:5){
-
-  p_nodiff[[i]] <- plot_motif_label(labels_nodiff[[i]])
-}
-
-#Over
-labels_over <- over_top_5$motif_functional_ID
-p_over <- list()
-
-for (i in 1:5){
-
-  p_over[[i]] <- plot_motif_label(labels_over[[i]])
-}
-
-#Run Script with histogram plot
-source("../Scripts/Z-score_percentile_histogram_plot.R")
-
-hist <- ggplot(data_2 %>% filter(round_motif_observed_probability>0), aes(x=z_score, color=infra_over_represented, fill=infra_over_represented)) + 
-  geom_histogram(bins = 93, alpha = 0.5, position = "identity",lwd = 0.25)+
-  geom_vline(xintercept = -abs(critical_value))+
-  geom_vline(xintercept = abs(critical_value))+
-  xlim(-60,60) + ylab("Frequency")+  theme_bw() +
-  scale_fill_manual(name="Motif frequencies" ,values=c("coral2", "palegreen3", "cyan3"), labels=c("Under-represented",
-                                                                                                  "No statistical difference", "Over-represented")) +
-  scale_color_manual(name="Motif frequencies" ,values=c("coral2", "palegreen3", "cyan3"), labels=c("Under-represented",
-                                                                                                   "No statistical difference", "Over-represented")) + xlab("Z-score")
-
-t_col <- function(color, percent = 50, name = NULL) {
-  #      color = color name
-  #    percent = % transparency
-  #       name = an optional name for the color
-
-  ## Get RGB values for named color
-  rgb.val <- col2rgb(color)
-
-  ## Make new color using input color as base and alpha set by transparency
-  t.col <- rgb(rgb.val[1], rgb.val[2], rgb.val[3],
-               max = 255,
-               alpha = (100 - percent) * 255 / 100,
-               names = name)
-
-  ## Save the color
-  invisible(t.col)
-}
-## END
-
-#Prepare panel of plots
-hist / ((p_under[[1]]/p_under[[2]]/p_under[[3]]/p_under[[4]] & theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_rect(fill=t_col("coral2")))) | 
-          (p_nodiff[[1]]/p_nodiff[[2]]/p_nodiff[[3]]/p_nodiff[[4]]& theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_rect(fill=t_col("palegreen3")))) |
-          (p_over[[1]]/p_over[[2]]/p_over[[3]]/p_over[[4]] & theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_rect(fill=t_col("cyan3"))))) + plot_layout(guides = 'collect')
-
-```
-
-# DISCUSSION
-
-Understanding the global patterns of network structure is key to unravel the processes that govern community dynamics [@bascompte2007; @bastolla2009; @guimaraes2020].
-However, common analytical approaches are unable to capture the full complexity of ecological systems [@simmons2019].
-Because network motifs can capture both direct and indirect interactions, by analysing over- and under-representation of motifs we are able to explore in greater detail ecological interactions [@stouffer2007].
-We have explored for the first time the overall structure and representation of network motifs in real plant-pollinator networks and shown that the different motifs up to five nodes are consistently over- and under-represented in comparison with simulated networks indicating the presence of ecological processes shaping their structure.
-Despite the presence of multiple ecological processes likely operating at the same time (e.g., neutral effects, morphological matching or phenological overlap), we found a tendency for over-represented structures with more densely connected motifs (i.e., complete, fan and asymmetric complete) suggesting that neutral effects are likely the predominant processes governing the structure of these network motifs [@simmons2020].
-Thus, as indicated for other network properties like nestedness [@krishna2008; @suweis2013], species relative abundances (i.e., neutral effects) are possibly one of the main determinants of indirect interactions in real plant-pollinator networks.
-[brillante el parrafo!]()
-
-From a pollinator perspective, we found that generalist network motifs were consistently over-represented (e.g.
-fan-type motifs; **Figure 2**).
-For instance, when we compare motifs with equal structure for both trophic levels, we found that floral visitors had always over-representation in the positions that implied the highest number of links.
-Despite this is in good agreement with the current view of the generalist tendency of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of the generalist network motifs was largely driven by the functional group of bees (e.g., positions 42, 46, 16, 4, 14 and 35 in motifs 15, 17, 7, 2, 6 and 13, respectively; see **Figure 3** for positions and **Figure 4** for motifs) while the rest of the functional groups tended to be under-represented in these generalist motifs and over-represented in motif positions with specialist roles (e.g., positions 11, 21, 28 and 34 in motifs 5, 9, 11 and 13, respectively; see **Figure 3** for positions and **Figure 4** for motifs).
-This large effect of bees on the overall patterns is no surprise, as bees were the functional group with largest number of interaction records in the whole set of networks as also recorded for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017].
-Unlike floral visitors, plant functional groups showed little differences on its appearance in different motif positions, and thus similar probability of appearing on all of them.
-If anything, the groups that involved higher levels of outcrossing showed a tendency to be more over-represented and probable on different motif positions.
-For instance, the group of self-incompatible perennials with large flowers, one of the groups that is expected to have higher levels of outcrossing rate [@goodwillie2010], showed the highest over-representation of all plant functional groups (**Figure 3**); and the group of tall plants with unisexual flowers, the one that is expected to have the highest dependence of pollinators on reproduction [@rodger2021], was the most probable on the generalist motif for plant positions (i.e., plant nodes with 3 to 4 links; **Figure 4**).
-
-The probabilities of appearance of each functional group on the different motif positions were insufficient to predict most of the observed network position combinations (**Figure 5**).
-This implies that not just the representation of network motifs types but also the identity of the elements of their structure is influenced by ecological processes that determine under- and over-representation of the different position combinations.
-In addition, we found that just 30$\%$ of the possible 53,250 motif combinations are realized.
-Thus, similarly to the presence of forbidden links at the network level [@olesen2011; @jordano2016], we also found the existence of forbidden motif positions and those represented almost two thirds of the total posible combinations of indirect interactions.
-This concurs well with the general idea that plant-pollinator networks have a high proportion of non-realized direct interactions [@jordano2003; @bascompte2013], and as a result, also a high proportion of non-realized combinations of indirect interactions.
-Some of this non-observed interactions are probably due to under-sampling [@dorado2011; @jordano2016].
-However, a large fraction of the possible interactions do not take place because of life history constraints such as species co-occurrence, trait matching processes and phenological uncoupling [@olesen2011; @bartomeus2016; @jordano2016].
-Despite the advances in the understanding on the ecological processes that influence species pairwise interactions [@bartomeus2016; @peralta2020], we still know little of how these processes determine competitive and facilitative interactions in mutualistic networks.
-Thus, as suggested by @simmons2020, exploring the proportion of these realized network motifs that are competitive or facilitative is a necessary next step to improve our understanding of the architecture of biodiversity [@bascompte2007].
-
-Despite the obvious usefulness of functional groups in summarizing species ecological roles (e.g., similar reproductive biology and behaviour of pollinators), delimiting species into functional groups is not often trivial.
-For instance, taxonomic diversity and trait availability limit our ability to properly represent the wide range of reproductive strategies [@dellinger2020] and different clustering analysis can lead to distinct outcomes (e.g., k-means and hierarchical clustering).
-Further, here we divided floral visitors on the taxonomic rank level because it represented adequately the pollinator species ecological roles without the need of the tremendous effort of compiling trait data for over 1000 species of floral visitors.
-However, further groupings with traits could help revealing greater relevance of trait-matching processes on indirect interactions.
-We believe that this could be investigated by exploring which proportion of over- and under-represented motifs present high and low trait-matching, respectively.
-Moreover, we analysed network motifs focusing exclusively on presence-absence interactions which assume that all interactions are equally important but as suggested by @simmons2020, further work should account for quantitative measurements of the strength of plant-pollinator interactions.
-Finally, despite the wide geographical coverage of our plant-pollinator dataset, there are major gaps for some regions of the world with a clear bias towards Europe, America and islands which have long been interested ecologist [@macarthur1963; @warren2015].
-These biases are also found in global datasets of networks where the data is highly fragmented across space [@poisot2021] and more efforts are needed to capture global patterns of plant-pollinator interactions.
-
-In conclusion, by following the framework of @simmons2020 we have been able to explore competitive and facilitative interactions in plant-pollinator networks worldwide and found that indirect interactions are non-random and are more strongly related to neutral processes than any other ecological process.
-Further, we found that motif combinations of functional groups are strongly constrained and that the distinct motif positions are associated with different functional groups with different ecological roles (e.g., generalization versus specialization).
-Although in this study we do not predict indirect interactions, our work is a first step to elucidate novel interactions beyond pairwise interactions.
-
-# REFERENCES
-
-<div id ="refs"></div>
-
-\newpage
-
-##SUPPLEMENTARY MATERIAL
-
-**TABLES**
-
-**Table S1** List of plant-pollinator network studies.
-
-**Table S2** Type of plant traits used in this study.
-
-**FIGURES**
-
-**Figure S1** Over and under-estimated motif frequencies.
-
-**Figure S2** Over and under-estimated functional groups on motif positions.
-
-**Figure S3** Plant trait composition of functional groups.
-
-**Figure S4** Plant dendrogram with functional groups.
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,fig.width=12,  warning=FALSE}
-##############################
-#TABLE S1. List of studies
-##############################
-
-#Load libraries
-library(kableExtra)
-library(dplyr)
-
-#Create data.frame with references
-
-#vector with number of netw per study
-`Number of networks` <- c("6", #1
-                          "2", #2
-                          "3",#3
-                          "1",#4
-                          "1",#5
-                          "1",#6
-                          "1",#7
-                          "2",#8
-                          "1",#9
-                          "1",#10
-                          "8",#11
-                          "16",#12
-                          "6",#13
-                          "2",#14
-                          "4",#15
-                          "1",#16
-                          "3",#17
-                          "1"#18
-                          )
-
-`First author` <- c("Bartomeus", #1
-                    "Dicks",#2
-                    "Dupont",#3
-                    "Elberling",#4
-                    "Fang",#5
-                    "Inouye",#6
-                    "Lundgren",#7
-                    "Olesen",#8
-                    "Small",#9
-                    "Souza",#10
-                    "Kaiser-Bunbury",#11
-                    "Bartomeus",#12
-                    "Kaiser-Bunbury",#13
-                    "Kaiser-Bunbury",#14
-                    "Peralta",#15
-                    "Burkle",#16
-                    "Arroyo-Correa",#17
-                    "Bundgaard"#18
-                    )
-
-Year <- c(2008,#1
-          2002,#2
-          2003,#3
-          1999,#4
-          2008,#5
-          1988,#6
-          2005,#7
-          2002,#8
-          1976,#9
-          2017,#10
-          2017,#11
-          2015,#12
-          2011,#13
-          2010,#14
-          2006,#15
-          2013,#16
-          2019,#17
-          2003#18
-          )
-
-Country <- c("Spain", #1
-               "England", #2
-               "Denmark", #3
-               "Sweden", #4
-               "China", #5
-               "United States", #6
-               "Denmark (Greenland)", #7
-               "Mauritius and Portugal (Azores)", #8
-               "Japan", #9
-               "Brazil", #10
-               "Seychelles", #11
-               "Spain", #12
-               "Seychelles", #13
-               "Mauritius", #14
-               "Argentina", # 15
-               "United States", #16
-               "New Zealand", #17
-               "Denmark" #18
-               )
-
-DOI <- c("https://doi.org/10.1007/s00442-007-0946-1", #1
-         "https://doi.org/10.1046/j.0021-8790.2001.00572.x", #2
-         "https://doi.org/10.1111/j.1365-2656.2008.01501.x", #3
-         "https://doi.org/10.1111/j.1600-0587.1999.tb00507.x", #4
-         "https://doi.org/10.1111/1749-4877.12190", #5
-         "https://doi.org/10.1111/j.1442-9993.1988.tb00968.x", #6
-         "https://doi.org/10.1657/1523-0430(2005)037[0514:TDAHCW]2.0.CO;2", #7
-         "https://doi.org/10.1046/j.1472-4642.2002.00148.x", #8
-         "/13960/t4km08d21", #9
-         "https://doi.org/10.1111/1365-2745.12978", #10
-         "https://doi.org/10.1038/nature21071", #11
-         "https://github.com/ibartomeus/BeeFunData", #12
-         "https://doi.org/10.1111/j.1365-2745.2010.01732.x", #13
-         "https://doi.org/10.1016/j.ppees.2009.04.001", #14
-         "https://doi.org/10.1111/ele.13510", #15
-         "https://doi.org/10.1126/science.1232728", #16
-         "https://doi.org/10.1111/1365-2745.13332", #17
-         "Unpublished, Master thesis" #18
-         )
-
-references <- data.frame(`First author`, Year, `Number of networks`, Country,   DOI)
-
-colnames(references) <- c("First author", "Year", "Number of networks", "Country",  "DOI")
-
-#Check number of studies
-#nrow(references) # 18 studies
-#check number of networks
-#sum(as.numeric(references$`Number of networks`)) #60
-
-references %>%
-  arrange(`First author`)%>%
-  kable( longtable = T, booktabs = T,linesep = "\\addlinespace",align = c("cccc"),escape = FALSE, caption= "\\textbf{Table S1.} List of studies ordered by author with the year of publication, number of contributed networks and digital object identifier") %>%
-  kable_styling(latex_options = c("repeat_header","striped"),  full_width=F,position = c("center"))
-
-```
-
-\elandscape
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=16, fig.width=12}
-
-library(kableExtra)
-
-library(dplyr)
-library(readxl) #read excel file (trait data)
-library(dplyr) #data manipulation
-library(visdat) #VISUALIZE MISSING DATA
-library(naniar)
-library(tidyverse)
-########################################################################################################################################################
-#1) READ TRAIT DATA
-########################################################################################################################################################
-
-Trait <- c("Plant height (m)", "Flower width (mm)", "Flower length (mm)", "Inflorescence width (mm)", "Style length (mm)", "Ovules per flower",
-           "Flowers per plant",  "Autonomous selfing (fruit set)")
-
-Trait1 <- c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Autonomous selfing", "Compatibility system", "Breeding system", "")
-
-T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub \n Tree", "Brush \n Campanulate \n Capitulum \n Open \n Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic", "None \n Low \n Medium \n High", "Self-incomp.
-\n Partially self-comp.
-\n Self-comp.", "Hermaphrodite \n Monoecious \n Dioecious",""),align = c("l"))
-
-Type <- c("Vegetative", "Floral", "Floral", "Floral", "Floral", "Floral", "Floral","Reproductive")
-
-Type_1 <- c("Vegetative", "Vegetative", "Floral", "Floral", "Reproductive", "Reproductive", "Reproductive", "")
-
-dat <- data.frame(Type, Trait,Type_1, Trait1)
-
-colnames(dat) <- c("Type","Traits","Type", "Traits")
-
-kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c"),caption = "\\textbf{Table S2.} Traits used to delimit the different plant functional groups divided in quantitative and categorical traits.") %>%
-kable_styling(full_width = T,latex_options = c("striped")) %>%
-add_header_above(c("Quantitative traits" = 2,"Categorical traits" = 2),bold=T)  %>%
-    column_spec(c(1,4), bold = T) %>% row_spec(0, bold=T)
-
-```
-
-\clearpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure S1.** Comparison of motif frequencies between empirical and simulated networks grouped by average path length (plots a, b, c and d) as determined in Simmons et al.
-(2020) without considering singletones.
-This is shown with the mean percentage of motif frequencies in empirical networks that were over the motif frequencies of the simulated ones (percentiles).
-This was done by network (light blue dots) and then averaged for all networks (black dots with error bars that correspond to the standard deviation)."}
-library(lme4)
-library(nlme)
-library(tidyverse)
-source("../Scripts/Scripts_Alfonso/add_study_id.R")
-d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models_NOSING/Motifs_frequency_percentile_NOSING.csv")
-d <- add_study_id(d)
-#str(d)
-#head(d)
-
-#ggplot(d %>% filter(motif != 1), aes(percentil_sizeclass))+
-#  geom_histogram(color="black", fill="white")+
-#  facet_wrap(~motif)+
-#  theme_bw()+
-#  labs(x="Sizeclass percentile")
-#
-# Motifs tend to be over- and under-represensented in real networks
-
-# Mean percentile and SE taking into account the study system
-motif_codes <- d %>% filter(motif != 1) %>% # We remove links (motif code: 1)
-  select(motif) %>% unique() %>% pull()
-motif_means <- tibble(motif = motif_codes)
-motif_means$mean <- NA
-motif_means$SE <- NA
-
-for(i.motif in 1:length(motif_codes)){
-
-  m <- lmer(percentil_sizeclass ~ 1+(1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = subset(d, motif == motif_codes[i.motif]))
-
-  motif_means$mean[i.motif] <- fixed.effects(m) %>% unname()
-  motif_means$SE[i.motif] <- sqrt(diag(vcov(m)))
-
-}
-
-#Add categories based on path length set by Simmons 2021 et al., Functional Ecology
-d$Broad_categories[d$motif==2 | d$motif==7 | d$motif==17 | d$motif==3|d$motif==4|d$motif==8] <- "Fan"
-
-d$Broad_categories[d$motif==15 | d$motif==11] <- "Medium-weak"
-
-d$Broad_categories[d$motif==6 | d$motif==16 |  d$motif==12] <- "Strong"
-
-d$Broad_categories[d$motif==5 | d$motif==9 |  d$motif==14|  d$motif==13|  d$motif==10] <- "Weak"
-
-#order the categories from short to long path length
-d$Broad_categories <- factor(d$Broad_categories, levels = c("Strong", "Fan", "Medium-weak", "Weak"))
-
-#Ffilter out two node motifs
-d_1 <- d %>% filter(motif != 1)
-#Merge dataframes to bl able to create facets
-d_2 <- merge(d_1, motif_means, by="motif")
-
-arr <- list('Strong' = expression(bold(paste("Complete (strong, ", bar(x), " = 1.38)"))),
-             'Fan' = expression(bold(paste("Fan (medium-strong, ", bar(x), " = 1.48)"))), 
-             'Medium-weak' = expression(bold(paste("Asymmetric complete (medium-weak, ", bar(x), " = 1.60)"))), 
-             "Weak" =expression(bold(paste("Core-peripheral (weak, ", bar(x), " = 1.85)"))))
-mylabel <- function(val) { return(lapply(val, function(x) arr[x])) }
-
-library(ggforce) #workaround with ggforce to have facets with same sizes
-
-p <- ggplot()+geom_point(data = d_2, aes(y=factor(motif), 100*percentil_sizeclass), shape=21,color="black",fill="azure2",size=1.75, alpha=0.3)+
-  geom_errorbar(data = d_2,aes(y = factor(motif), xmin=100*(mean-SE), xmax=100*(mean+SE)), 
-                width=0.8,size=0.8,color="black") +theme_bw()+
-  geom_point(data = d_2,aes(y = as.factor(motif), x=100*mean), 
-             size=2,color="black")+labs(y="Two to five node motifs", x = "Percentile")+
-  theme( strip.background = element_blank())+
-  theme(strip.text = element_text(face="bold", size=10, hjust=0),
-        panel.border=element_rect(color="black",size=1.2))
-
-p + ggforce::facet_col(vars(Broad_categories), scales = 'free', space = 'free',labeller=mylabel)
-
-#Trying to maintain a gradient from low to high in colors
-
-#Fig 1 Should be a dot plot (or forest plot) of the mean +- SE of the 15 motifs.
-#NICE! Can we put motifs in Y axes, and % in X?
-```
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="\\textbf{Figure S2.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions after removing non-robust links (singletones).
-The different motif positions are dividied by the average path length clasification by Simmons et al.
-(2020).
-The superior dendrogram indicates the differences across groups with the more separated groups showing larger differences."}
-
-library(lme4)
-library(nlme)
-library(tidyverse)
-library(stringi)
-source("../Scripts/Scripts_Alfonso/add_study_id.R")
-
-#############################################
-# EXTRACT MEAN VALUES
-#############################################
-
-all_position_percentiles <- read_csv("../Data/Csv/Motifs_positions_and_null_models_NOSING/GF_positions_frequency_percentile_NOSING.csv")
-
-all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
-                                                              "[0-9]+") %>% as.numeric()
-
-all_position_percentiles <- add_study_id(all_position_percentiles)
-#str(all_position_percentiles)
-#head(all_position_percentiles)
-
-list_plants_FG <- as.character(1:10)
-
-plant_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF)) #ME DA ERROR
-pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF))
-
-# Plants-------------
-
-# Mean percentile and SE taking into account the study system
-plant_codes <- plant_position_percentiles_filtered$position %>% unique()
-plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-plant_means$mean <- NA
-plant_means$SE <- NA
-
-for(i.pos in 1:length(plant_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
-            data = plant_position_percentiles_filtered %>%
-              filter(position == plant_codes[i.pos]))
-
-  temp <- fixed.effects(m) %>% unname()
-  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
-                                                                    temp[1]+temp[2],
-                                                                    temp[1]+temp[3],
-                                                                    temp[1]+temp[4],
-                                                                    temp[1]+temp[5]) ## to get real means per FG
-  temp <- sqrt(diag(vcov(m)))
-  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
-                                                                  temp[1]+temp[2],
-                                                                  temp[1]+temp[3],
-                                                                  temp[1]+temp[4],
-                                                                  temp[1]+temp[5])
-
-}
-
-# Pollinators--------
-
-# Mean percentile and SE taking into account the study system
-pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
-pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-pollinator_means$mean <- NA
-pollinator_means$SE <- NA
-pollinator_means_reordered <- NULL
-
-for(i.pos in 1:length(pollinator_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = pollinator_position_percentiles_filtered %>%
-              filter(position == pollinator_codes[i.pos]),
-            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
-
-  temp <- fixed.effects(m) %>% unname()
-  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)
-
-  pollinator_means_aux$mean <- c(temp[1],
-                                 temp[1]+temp[2],
-                                 temp[1]+temp[3],
-                                 temp[1]+temp[4],
-                                 temp[1]+temp[5],
-                                 temp[1]+temp[6],
-                                 temp[1]+temp[7],
-                                 temp[1]+temp[8],
-                                 temp[1]+temp[9]) ## to get real means per FG
-
-  temp <- sqrt(diag(vcov(m)))
-  pollinator_means_aux$SE <- c(temp[1],
-                               temp[1]+temp[2],
-                               temp[1]+temp[3],
-                               temp[1]+temp[4],
-                               temp[1]+temp[5],
-                               temp[1]+temp[6],
-                               temp[1]+temp[7],
-                               temp[1]+temp[8],
-                               temp[1]+temp[9])
-
-  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)
-
-}
-
-# There are lower limits (mean - SE) smaller than 0 (see Other insects)
-# We set the lower limit of those error bars to zero
-
-pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
-pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
-
-#############################################
-# ADDING BROAD MOTIF CATEGORIES TO POSITIONS
-#############################################
-
-motifs_raw_data <- read_csv("../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-motifs_raw_data$Broad_categories <- NA
-
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(5,9,14,13,10)] <- "Core-peripherical"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(6,16,12)] <- "Complete"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(2,3,7,4,17,8)] <- "Fan"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(15,11)] <- "Asymmetric complete"
-
-motifs_raw_data$plant <- gsub("[^0-9.-]", "", motifs_raw_data$plant)
-motifs_raw_data$pollinator <- gsub("[^0-9.-]", "", motifs_raw_data$pollinator)
-motifs_raw_data$plant <- as.numeric(motifs_raw_data$plant)
-motifs_raw_data$pollinator <- as.numeric(motifs_raw_data$pollinator)
-motifs_raw_data <- motifs_raw_data %>% filter(!is.na(Broad_categories))
-
-fan_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-pollinator_means_reordered$Broad_categories <- NA
-
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% fan_pollinator] <- "Fan" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% asymm_pollinator] <- "Medium-weak" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% complete_pollinator] <- "Strong" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% core_per_pollinator] <- "Weak"
-
-fan_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-plant_means$Broad_categories <- NA
-
-plant_means$Broad_categories[plant_means$position %in% fan_plant] <- "Fan" 
-plant_means$Broad_categories[plant_means$position %in% asymm_plant] <- "Medium-weak" 
-plant_means$Broad_categories[plant_means$position %in% complete_plant] <- "Strong" 
-plant_means$Broad_categories[plant_means$position %in% core_per_plant] <- "Weak"
-
-########################################
-# CREATE HEATMAPS
-########################################
-
-library(ComplexHeatmap)
-
-# PLANTS-----
-
-# Prepare data for heatmap
-heat_plants_aux <- plant_means %>% spread(Node_FG,mean) %>% select(-SE)
-
-heat_plants <- heat_plants_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-heat_plants_fan <- heat_plants %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_fan) <- heat_plants_fan[,1]
-
-heat_plants_Weak <- heat_plants %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Weak) <- heat_plants_Weak[,1]
-
-heat_plants_Strong <- heat_plants %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Strong) <- heat_plants_Strong[,1]
-
-heat_plants_Medium_weak <- heat_plants %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Medium_weak) <- heat_plants_Medium_weak[,1]
-
-# POLLINATORS-----------
-
-filter_rare_groups <- T
-
-if(filter_rare_groups == T){
-  heat_pollinators_aux <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds",
-                                                                                "Lizards",
-                                                                                "Other_insects")) %>% 
-    spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees",            
-                                      "Coleoptera","Lepidoptera","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Syrphids")
-}else{
-  heat_pollinators_aux <- pollinator_means_reordered %>% spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees","Birds",            
-                                      "Coleoptera","Lepidoptera","Lizards","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Other insects","Syrphids")
-}
-
-heat_pollinators <- heat_pollinators_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-heat_pollinators_fan <- heat_pollinators %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_fan) <- heat_pollinators_fan[,1]
-
-heat_pollinators_Weak <- heat_pollinators %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Weak) <- heat_pollinators_Weak[,1]
-
-heat_pollinators_Strong <- heat_pollinators %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Strong) <- heat_pollinators_Strong[,1]
-
-heat_pollinators_Medium_weak <- heat_pollinators %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Medium_weak) <- heat_pollinators_Medium_weak[,1]
-
-##################
-
-#Do not know how to handle this multiplot for creating a panel
-
-# I'm going to create the 4 plots in one, 
-# I'm not sure that the grouping of the functional group is correct
-# when is done separately
-
-#sorry for the mess of libraries that I do below
-
- #Prepare first pollinators
-
-library(tidyr)
-library(data.table)
-long <- melt(setDT(heat_pollinators), id.vars = c("position","Broad_categories"), variable.name = "guilds")
-
-long_1 <- long %>% select(-Broad_categories)
-
-library(reshape2)
-long_m <- acast(long_1, position~guilds, value.var="value")
-
-#set manually the divisions, so far this is the best way I have seen to split the rows by categories
-
-r_split <- c(rep(c("Fan"), 3),rep(c("Core-peripheral"), 2),"Complete",rep(c("Fan"),2),rep(c("Core-peripheral"), 4),
-             rep(c("Asymmetric complete"), 2), "Complete", rep(c("Core-peripheral"), 3),rep(c("Asymmetric complete"), 2),
-             "Complete", "Fan")
-
-#set order of labels that avoids overlapping
-r_split <- factor(r_split, levels=c("Core-peripheral","Complete","Fan","Asymmetric complete"))
-
-#plat a bit with colors, a bit of a more complex set but looks nicer
-library(circlize)
-col_fun = colorRamp2(c(0.05644663,0.25, 0.4673256,0.75, 0.8782047), c("blue","cadetblue3", "azure2", "gold","red"))
-
-h_pol <- Heatmap(long_m, name = "Mean\npercentile", row_split=r_split,cluster_row_slices = FALSE, 
-                 column_title = "Pollinator functional groups",row_names_gp = gpar(fontsize = 10),
-                 col = col_fun,column_names_rot = 45,  column_names_gp = grid::gpar(fontsize = 10),
-                 column_title_gp = gpar(fontsize = 15, fontface = "bold"),
-                 row_title_gp = gpar(fontsize = 10, fontface = "bold"))
-
- #Prepare plants
-
-#long format
-long_plants <- melt(setDT(heat_plants), id.vars = c("position","Broad_categories"), variable.name = "Functional_groups")
-
-#filter for creating matrix
-long_plants_1 <- long_plants %>% select(-Broad_categories)
-
-#set better colnames
-long_plants_1$Functional_groups <- as.character(long_plants_1$Functional_groups)
-
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==1] <- "Selfing herbs" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==2] <- "Small outcrossing\nperennials" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==3] <- "Self-incomp. perennials\nwith large flowers" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==4] <- "Tall plants with small\nunisexual flowers" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==5] <- "Short-lived outcrossers with\nlong zygomorphic flowers"
-
-long_plants_1$Functional_groups <- factor(long_plants_1$Functional_groups, levels=c("Selfing herbs",
-"Small outcrossing\nperennials" ,"Self-incomp. perennials\nwith large flowers",
-"Tall plants with small\nunisexual flowers" ,"Short-lived outcrossers with\nlong zygomorphic flowers" ))
-
-#create matrix with reshape
-long_plants_m <- acast(long_plants_1, position~Functional_groups, value.var="value")
-
-r_split_plants <- c(rep(c("Fan"), 3),rep(c("Core-peripheral"), 2),"Complete",rep(c("Fan"),2),rep(c("Core-peripheral"), 3),
-                    rep(c("Asymmetric complete"), 2), "Complete", rep(c("Core-peripheral"), 4),rep(c("Asymmetric complete"), 2),
-                    "Complete", "Fan")
-
-r_split_plants <- factor(r_split, levels=c("Core-peripheral","Complete","Fan","Asymmetric complete"))
-
-h_plan <- Heatmap(long_plants_m, name = "Mean\npercentile", row_split=r_split_plants,cluster_row_slices = F, 
-                  column_title = "Plant functional groups",row_names_gp = gpar(fontsize = 10),col = col_fun,column_names_rot = 45,  
-                  column_names_gp = grid::gpar(fontsize = 10),column_title_gp = gpar(fontsize = 15, fontface = "bold"),
-                  row_title_gp = gpar(fontsize = 10, fontface = "bold"))
-
-library(patchwork)
-ht_list <- h_pol+h_plan
-
-draw(ht_list, auto_adjust = FALSE, cluster_rows = F)
-
-```
-
-\newpage
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=7, fig.width=12, fig.cap="**Figure S3.** Plant functional group composition separated in qualitative and quantitative variables.
-Panel A) shows the percentage of the different categories within trait represented with different colours for each functional group.
-Plot B) shows the radar plot of the different quantitative variables standardize on the same scale also coloured with the same patterns of colours as qualitative variables per cluster or functional group.
-Group 1 corresponds to short-lived selfers; group 2 to small outcrossing perennials; group 3 to self-incompatible perennials with large flowers; group 4 to tall plants with small unisexual flowers; and, group 5 to short-lived outcrossers with long zygomorphic flowers."}
-
-#CODE TO PLOT FUNCTIONAL GROUPS
-#IT CAN BE PLOT WITH MUCH LESS CODE BUT NO TIME FOR CLEANING IT
-
-##########################################
-#Visualization of plant functional groups#
-##########################################
-
-library(cowplot)
-library(ggplot2)
-library(tidyr)
-library(dplyr)
-library(reshape2)
-library(data.table)
-library(patchwork)
-
-#LOAD DATA
-#read unscaled trait data in order to visualize better the clusters
-d <- read.csv("../Data/Csv/all_species_imputed_trait_data_forest_data.csv")
-
-dat_1 <- read.csv("../Data/Csv/imputed_trait_data_hclust_5_clusters_forest_data.csv", row.names = "X")
-
-d$Clusters <- dat_1$Clusters
-
-#select columns of interest
-t <- d[c("Breeding_system","IMPUTED_Compatibility","Autonomous_selfing_level",
-         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Flowers_per_inflorescence",
-         "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean", "STYLE_IMPUTED", "OVULES_IMPUTED", "life_form", "lifespan",
-         "IMPUTED_plant_height_mean_m", "Nectar_presence_absence", "Clusters")]
-
-##############################################################################################################################
-#Prepare table qualitative variables
-##############################################################################################################################
-
-##############################################################################################################################
-#Breeding system
-t$Breeding_system <- factor(t$Breeding_system, levels=c("Dioecious", "Monoecious", "Hermaphrodite"))
-
-#Summary to create table
-breeding <- t %>%
-  group_by(Clusters,Breeding_system) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-breeding <- breeding[,-3]
-
-breeding <- spread(breeding, Clusters, Percentage)
-
-colnames(breeding)[1] <- "Category"
-
-Trait <- data.frame(Trait= c(rep("Breeding system", 3)))
-
-Breeding_system <- cbind(Trait, breeding)
-
-##############################################################################################################################
-#Compatibility
-str(t)
-t$IMPUTED_Compatibility <- as.character(t$IMPUTED_Compatibility)
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="dioecious"] <- "Unisexual flower"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="monoecious"] <- "Unisexual flower"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_incompatible"] <- "Self incompatible"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="partially_self_compatible"] <- "Partially self compatible"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_compatible"] <- "Self compatible"
-
-t$IMPUTED_Compatibility <- factor(t$IMPUTED_Compatibility, levels=c("Unisexual flower", "Self incompatible", "Partially self compatible", "Self compatible"))
-#Summary to create table
-comp <- t %>%
-  group_by(Clusters,IMPUTED_Compatibility) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-comp <- comp[,-3]
-
-comp <- spread(comp, Clusters, Percentage)
-#Replace Na's with zeros
-comp[is.na(comp)] <- 0
-#Set call name os categories per trait
-colnames(comp)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Compatibility system", 4)))
-#Add column
-Compatibility_system <- cbind(Trait, comp)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system)
-
-############################################################################################################################################
-#Life form
-t$life_form <- as.character(t$life_form)
-t$life_form[t$life_form =="vine"] <- "Shrub"
-t$life_form[t$life_form =="tree"] <- "Tree"
-t$life_form[t$life_form =="herb"] <- "Herb"
-t$life_form[t$life_form =="shrub"] <- "Shrub"
-#Order levels
-t$life_form <- factor(t$life_form, levels=c("Tree", "Shrub", "Herb"))
-#Summary to create table
-life_form <- t %>%
-  group_by(Clusters,life_form) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-life_form <- life_form[,-3]
-#convert to wide
-life_form <- spread(life_form, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(life_form)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Life form", 3)))
-#Add column
-Life_form<- cbind(Trait, life_form)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form)
-
-############################################################################################################################################
-t$lifespan <- factor(t$lifespan, levels=c("Perennial","Short lived"))
-#Summary to create table
-life_span <- t %>%
-  group_by(Clusters,lifespan) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-life_span <- life_span[,-3]
-#convert to wide
-life_span <- spread(life_span, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(life_span)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Life span", 2)))
-#Add column
-Life_span<- cbind(Trait, life_span)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span)
-
-############################################################################################################################################
-t$Flower_morphology <- as.character(t$Flower_morphology)
-t$Flower_morphology[t$Flower_morphology=="Funnelform"] <- "Campanulate"
-t$Flower_morphology[t$Flower_morphology=="Spike"] <- "Brush"
-
-Flower_morphology <- t %>%
-  group_by(Clusters,Flower_morphology) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-Flower_morphology <- Flower_morphology[,-3]
-#convert to wide
-Flower_morphology <- spread(Flower_morphology, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(Flower_morphology)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Flower shape", 6)))
-#Add column
-Flower_morphology<- cbind(Trait, Flower_morphology)
-#Replace Na's with zeros
-Flower_morphology[is.na(Flower_morphology)] <- 0
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology)
-
-############################################################################################################################################
-t$Flower_symmetry <- as.character(t$Flower_symmetry)
-t$Flower_symmetry[t$Flower_symmetry =="actinomorphic"] <- "Actinomorphic"
-t$Flower_symmetry[t$Flower_symmetry =="zygomorphic"] <- "Zygomorphic"
-
-Flower_symmetry <- t %>%
-  group_by(Clusters,Flower_symmetry) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-Flower_symmetry <- Flower_symmetry[,-3]
-#convert to wide
-Flower_symmetry <- spread(Flower_symmetry, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(Flower_symmetry)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Flower symmetry", 2)))
-#Add column
-Flower_symmetry<- cbind(Trait, Flower_symmetry)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology,Flower_symmetry)
-############################################################################################################################################
-t$Autonomous_selfing_level <- as.character(t$Autonomous_selfing_level)
-t$Autonomous_selfing_level[t$Autonomous_selfing_level =="none"] <- "None"
-t$Autonomous_selfing_level[t$Autonomous_selfing_level =="low"] <- "Low"
-t$Autonomous_selfing_level[t$Autonomous_selfing_level =="medium"] <- "Medium"
-t$Autonomous_selfing_level[t$Autonomous_selfing_level =="high"] <- "High"
-
-#Order levels
-t$Autonomous_selfing_level <- factor(t$Autonomous_selfing_level, levels=c("High", "Medium", "Low", "None"))
-
-Selfing <- t %>%
-  group_by(Clusters,Autonomous_selfing_level) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-#delete column to convert to wide
-Selfing <- Selfing[,-3]
-#convert to wide
-Selfing <- spread(Selfing, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(Selfing)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Selfing level", 2)))
-#Replace Na's with zeros
-Selfing[is.na(Selfing)] <- 0
-#Add column
-Selfing_1 <- cbind(Trait, Selfing)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology, Selfing_1)
-
-############################################################################################################################################
-t$Nectar_presence_absence <- as.character(t$Nectar_presence_absence)
-t$Nectar_presence_absence[t$Nectar_presence_absence =="yes"] <- "Yes"
-t$Nectar_presence_absence[t$Nectar_presence_absence =="no"] <- "No"
-
-Nectar <- t %>%
-  group_by(Clusters,Nectar_presence_absence) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-#delete column to convert to wide
-Nectar <- Nectar[,-3]
-#convert to wide
-Nectar <- spread(Nectar, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(Nectar)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Nectar", 2)))
-#Replace Na's with zeros
-Nectar[is.na(Nectar)] <- 0
-#Add column
-Nectar <- cbind(Trait, Nectar)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology, Flower_symmetry,Selfing_1, Nectar)
-
-##############################################################################################################################
-#Prepare table quantitative variables
-##############################################################################################################################
-
-Selfing <-  t %>% group_by(Clusters)%>% 
-  select(Autonomous_selfing_level_fruit_set) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                     # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                    sd = sd))
-
-s1 <- as.data.frame(t(Selfing))
-#set colnames
-colnames(s1) <- c("1","2","3","4","5")
-#remove the cluster row
-s1 <- s1[-1,]
-#convert rownames to 1st columns
-s1 <- setDT(s1, keep.rownames = "TRUE")[]
-colnames(s1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Autonomous selfing", 5)))
-#Add column
-Selfing <- cbind(Trait, s1)
-
-##############################################################################################################################
-flower_number <-  t %>% group_by(Clusters)%>% 
-  select(Flowers_per_plant) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-f1 <- as.data.frame(t(flower_number))
-#set colnames
-colnames(f1) <- c("1","2","3","4","5")
-#remove the cluster row
-f1 <- f1[-1,]
-#convert rownames to 1st columns
-f1 <- setDT(f1, keep.rownames = "TRUE")[]
-colnames(f1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Flower number", 5)))
-#Add column
-Flower_number <- cbind(Trait, f1)
-
-##############################################################################################################################
-Flowers_per_inflorescence <-  t %>% group_by(Clusters)%>% 
-  select(Flowers_per_inflorescence) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-f_i_1 <- as.data.frame(t(Flowers_per_inflorescence))
-#set colnames
-colnames(f_i_1) <- c("1","2","3","4","5")
-#remove the cluster row
-f_i_1 <- f_i_1[-1,]
-#convert rownames to 1st columns
-f_i_1 <- setDT(f_i_1, keep.rownames = "TRUE")[]
-colnames(f_i_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Flowers per inflorescence", 5)))
-#Add column
-Flower_per_inflo <- cbind(Trait, f_i_1)
-
-bind_rows(Selfing, Flower_number, Flower_per_inflo)
-
-##############################################################################################################################
-Floral_unit_width <-  t %>% group_by(Clusters)%>% 
-  select(Floral_unit_width) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-f_u_w_1 <- as.data.frame(t(Floral_unit_width))
-#set colnames
-colnames(f_u_w_1) <- c("1","2","3","4","5")
-#remove the cluster row
-f_u_w_1 <- f_u_w_1[-1,]
-#convert rownames to 1st columns
-f_u_w_1 <- setDT(f_u_w_1, keep.rownames = "TRUE")[]
-colnames(f_u_w_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Inflorescence width", 5)))
-#Add column
-Inflo_width <- cbind(Trait, f_u_w_1)
-
-bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width)
-
-##############################################################################################################################
-Corolla_diameter_mean <-  t %>% group_by(Clusters)%>% 
-  select(Corolla_diameter_mean) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-c_w_1 <- as.data.frame(t(Corolla_diameter_mean))
-#set colnames
-colnames(c_w_1) <- c("1","2","3","4","5")
-#remove the cluster row
-c_w_1 <- c_w_1[-1,]
-#convert rownames to 1st columns
-c_w_1 <- setDT(c_w_1, keep.rownames = "TRUE")[]
-colnames(c_w_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Flower width", 5)))
-#Add column
-Flower_width <- cbind(Trait, c_w_1)
-
-bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width)
-
-##############################################################################################################################
-Corolla_length_mean <-  t %>% group_by(Clusters)%>% 
-  select(Corolla_length_mean) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-c_l_1 <- as.data.frame(t(Corolla_length_mean))
-#set colnames
-colnames(c_l_1) <- c("1","2","3","4","5")
-#remove the cluster row
-c_l_1 <- c_l_1[-1,]
-#convert rownames to 1st columns
-c_l_1 <- setDT(c_l_1, keep.rownames = "TRUE")[]
-colnames(c_l_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Flower length", 5)))
-#Add column
-Flower_length<- cbind(Trait, c_l_1)
-
-bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length)
-
-##############################################################################################################################
-STYLE_IMPUTED <-  t %>% group_by(Clusters)%>% 
-  select(STYLE_IMPUTED) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-s_l_1 <- as.data.frame(t(STYLE_IMPUTED))
-#set colnames
-colnames(s_l_1) <- c("1","2","3","4","5")
-#remove the cluster row
-s_l_1 <- s_l_1[-1,]
-#convert rownames to 1st columns
-s_l_1 <- setDT(s_l_1, keep.rownames = "TRUE")[]
-colnames(s_l_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Style length", 5)))
-#Add column
-Style_length<- cbind(Trait, s_l_1)
-
-bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length, Style_length)
-
-##############################################################################################################################
-
-OVULES_IMPUTED <-  t %>% group_by(Clusters)%>% 
-  select(OVULES_IMPUTED) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-o_n_1 <- as.data.frame(t(OVULES_IMPUTED))
-#set colnames
-colnames(o_n_1) <- c("1","2","3","4","5")
-#remove the cluster row
-o_n_1 <- o_n_1[-1,]
-#convert rownames to 1st columns
-o_n_1 <- setDT(o_n_1, keep.rownames = "TRUE")[]
-colnames(o_n_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Ovule number", 5)))
-#Add column
-Ovule_number <- cbind(Trait, o_n_1)
-
-bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length, Ovule_number)
-
-##############################################################################################################################
-
-IMPUTED_plant_height_mean_m <-  t %>% group_by(Clusters)%>% 
-  select(IMPUTED_plant_height_mean_m) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-p_h_1 <- as.data.frame(t(IMPUTED_plant_height_mean_m))
-#set colnames
-colnames(p_h_1) <- c("1","2","3","4","5")
-#remove the cluster row
-p_h_1 <- p_h_1[-1,]
-#convert rownames to 1st columns
-p_h_1 <- setDT(p_h_1, keep.rownames = "TRUE")[]
-colnames(p_h_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Plant height", 5)))
-#Add column
-Plant_height <- cbind(Trait, p_h_1)
-
-#Bind quantitative and qualitative variables
-Table_all_traits <- bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology, Flower_symmetry,Selfing_1, Nectar,
-          Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length, Style_length, Ovule_number, Plant_height)
-
-#Select just two decimals
-is.num <- sapply(Table_all_traits, is.numeric)
-Table_all_traits[is.num] <- lapply(Table_all_traits[is.num], round, 2)
-
-colnames(Table_all_traits) <- c("Trait", "Category", "Cluster 1", "Cluster 2", "Cluster 3", "Cluster 4", "Cluster 5")
-
-#LOAD LIBRARIES
-#devtools::install_github("ricardo-bion/ggradar", dependencies=TRUE)
-suppressPackageStartupMessages(library(dplyr))
-library(scales)
-library(tibble)
-library(ggradar)
-library(janitor)
-library(grid)
-library(dplyr)
-library(lubridate)
-#QUANTITATIVVE VARIABLES
-
-#generate subset of quantitative variables for plotting
-quant_median <- subset(Table_all_traits, Category=="median")
-
-#delete col number 2
-quant_median <- quant_median[,-2]
-
-#transpose dataframe
-final_df <- as.data.frame(t(quant_median))
-
-#rownames to colnames (1st one)
-final_df_1 <- final_df %>% row_to_names(row_number = 1)
-
-#Convert all variables to numeric
-final_df_2 <- sapply(final_df_1, function(x) as.numeric(as.character(x)))
-
-#set back the missed rownames in the processing
-rownames(final_df_2) <- rownames(final_df_1)
-
-# Convert to dataframe
-final_df_2 <- as.data.frame(final_df_2)
-
-# Scale values and set rowname as column
-final_df_3 <-final_df_2 %>% rownames_to_column( var = "group" ) %>%   mutate_at(vars(-group),funs(rescale))
-
-#Plot Radar
-#ggradar(final_df_3)
-
-#QUALITATIVE VARIABLES
-
-#LOAD DATA
-#read unscaled trait data in order to visualize better the clusters
-d <- read.csv("../Data/Csv/all_species_imputed_trait_data_forest_data.csv")
-
-dat_1 <- read.csv("../Data/Csv/imputed_trait_data_hclust_5_clusters_forest_data.csv", row.names = "X")
-
-d$Clusters <- dat_1$Clusters
-
-#select columns of interest
-t <- d[c("Breeding_system","IMPUTED_Compatibility","Autonomous_selfing_level",
-         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Flowers_per_inflorescence",
-         "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean", "STYLE_IMPUTED", "OVULES_IMPUTED", "life_form", "lifespan",
-         "IMPUTED_plant_height_mean_m", "Nectar_presence_absence", "Clusters")]
-
-##############################################################################################################################
-#Prepare table qualitative variables
-##############################################################################################################################
-
-##############################################################################################################################
-#Breeding system
-t$Breeding_system <- factor(t$Breeding_system, levels=c("Dioecious", "Monoecious", "Hermaphrodite"))
-
-#Summary to create table
-breeding <- t %>%
-  group_by(Clusters,Breeding_system) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-breeding <- breeding[,-3]
-
-breeding <- spread(breeding, Clusters, Percentage)
-
-colnames(breeding)[1] <- "Category"
-
-Trait <- data.frame(Trait= c(rep("Breeding system", 3)))
-
-Breeding_system <- cbind(Trait, breeding)
-
-##############################################################################################################################
-#Compatibility
-str(t)
-t$IMPUTED_Compatibility <- as.character(t$IMPUTED_Compatibility)
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="dioecious"] <- "Self incompatible"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="monoecious"] <- "Self incompatible"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_incompatible"] <- "Self incompatible"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="partially_self_compatible"] <- "Partially self compatible"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_compatible"] <- "Self compatible"
-
-t$IMPUTED_Compatibility <- factor(t$IMPUTED_Compatibility, levels=c("Self incompatible", "Partially self compatible", "Self compatible"))
-#Summary to create table
-comp <- t %>%
-  group_by(Clusters,IMPUTED_Compatibility) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-comp <- comp[,-3]
-
-comp <- spread(comp, Clusters, Percentage)
-#Replace Na's with zeros
-comp[is.na(comp)] <- 0
-#Set call name os categories per trait
-colnames(comp)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Compatibility system", 3)))
-#Add column
-Compatibility_system <- cbind(Trait, comp)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system)
-
-############################################################################################################################################
-#Life form
-t$life_form <- as.character(t$life_form)
-t$life_form[t$life_form =="vine"] <- "Shrub"
-t$life_form[t$life_form =="tree"] <- "Tree"
-t$life_form[t$life_form =="herb"] <- "Herb"
-t$life_form[t$life_form =="shrub"] <- "Shrub"
-#Order levels
-t$life_form <- factor(t$life_form, levels=c("Tree", "Shrub", "Herb"))
-#Summary to create table
-life_form <- t %>%
-  group_by(Clusters,life_form) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-life_form <- life_form[,-3]
-#convert to wide
-life_form <- spread(life_form, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(life_form)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Life form", 3)))
-#Add column
-Life_form<- cbind(Trait, life_form)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form)
-
-############################################################################################################################################
-t$lifespan <- factor(t$lifespan, levels=c("Perennial","Short lived"))
-#Summary to create table
-life_span <- t %>%
-  group_by(Clusters,lifespan) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-life_span <- life_span[,-3]
-#convert to wide
-life_span <- spread(life_span, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(life_span)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Life span", 2)))
-#Add column
-Life_span<- cbind(Trait, life_span)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span)
-
-############################################################################################################################################
-#t$Flower_morphology <- as.character(t$Flower_morphology)
-#t$Flower_morphology[t$Flower_morphology=="Funnelform"] <- "Campanulate"
-#t$Flower_morphology[t$Flower_morphology=="Spike"] <- "Brush"
-#
-#Flower_morphology <- t %>%
-#  group_by(Clusters,Flower_morphology) %>%
-#  summarise (n = n()) %>%
-#  mutate(Percentage = n / sum(n)*100)
-##delete column to convert to wide
-#Flower_morphology <- Flower_morphology[,-3]
-##convert to wide
-#Flower_morphology <- spread(Flower_morphology, Clusters, Percentage)
-##Set call name os categories per trait
-#colnames(Flower_morphology)[1] <- "Category"
-##Create new column
-#Trait <- data.frame(Trait= c(rep("Flower shape", 6)))
-##Add column
-#Flower_morphology<- cbind(Trait, Flower_morphology)
-##Replace Na's with zeros
-#Flower_morphology[is.na(Flower_morphology)] <- 0
-##Bind rows
-#bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology)
-#
-############################################################################################################################################
-t$Flower_symmetry <- as.character(t$Flower_symmetry)
-t$Flower_symmetry[t$Flower_symmetry =="actinomorphic"] <- "Actinomorphic"
-t$Flower_symmetry[t$Flower_symmetry =="zygomorphic"] <- "Zygomorphic"
-
-Flower_symmetry <- t %>%
-  group_by(Clusters,Flower_symmetry) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-Flower_symmetry <- Flower_symmetry[,-3]
-#convert to wide
-Flower_symmetry <- spread(Flower_symmetry, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(Flower_symmetry)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Flower symmetry", 2)))
-#Add column
-Flower_symmetry<- cbind(Trait, Flower_symmetry)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology,Flower_symmetry)
-############################################################################################################################################
-#t$Autonomous_selfing_level <- as.character(t$Autonomous_selfing_level)
-#t$Autonomous_selfing_level[t$Autonomous_selfing_level =="none"] <- "None"
-#t$Autonomous_selfing_level[t$Autonomous_selfing_level =="low"] <- "Low"
-#t$Autonomous_selfing_level[t$Autonomous_selfing_level =="medium"] <- "Medium"
-#t$Autonomous_selfing_level[t$Autonomous_selfing_level =="high"] <- "High"
-#
-##Order levels
-#t$Autonomous_selfing_level <- factor(t$Autonomous_selfing_level, levels=c("High", "Medium", "Low", "None"))
-#
-#Selfing <- t %>%
-#  group_by(Clusters,Autonomous_selfing_level) %>%
-#  summarise (n = n()) %>%
-#  mutate(Percentage = n / sum(n)*100)
-#
-##delete column to convert to wide
-#Selfing <- Selfing[,-3]
-##convert to wide
-#Selfing <- spread(Selfing, Clusters, Percentage)
-##Set call name os categories per trait
-#colnames(Selfing)[1] <- "Category"
-##Create new column
-#Trait <- data.frame(Trait= c(rep("Selfing level", 2)))
-##Replace Na's with zeros
-#Selfing[is.na(Selfing)] <- 0
-##Add column
-#Selfing_1 <- cbind(Trait, Selfing)
-##Bind rows
-#bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology, Selfing_1)
-#
-#############################################################################################################################################
-t$Nectar_presence_absence <- as.character(t$Nectar_presence_absence)
-t$Nectar_presence_absence[t$Nectar_presence_absence =="yes"] <- "Yes"
-t$Nectar_presence_absence[t$Nectar_presence_absence =="no"] <- "No"
-
-Nectar <- t %>%
-  group_by(Clusters,Nectar_presence_absence) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-#delete column to convert to wide
-Nectar <- Nectar[,-3]
-#convert to wide
-Nectar <- spread(Nectar, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(Nectar)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Nectar", 2)))
-#Replace Na's with zeros
-Nectar[is.na(Nectar)] <- 0
-#Add column
-Nectar <- cbind(Trait, Nectar)
-#Bind rows
-data <- bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span, Flower_symmetry, Nectar)
-
-#remove first col
-data_1 <- data[,-1]
-colnames(data_1) <- c("Category", "Cluster 1", "Cluster 2", "Cluster 3", "Cluster 4", "Cluster 5")
-
-#transpose dataframe
-data_2 <- as.data.frame(t(data_1))
-
-#rownames to colnames (1st one)
-data_3 <- data_2 %>% row_to_names(row_number = 1)
-
-#Convert all variables to numeric
-data_4 <- sapply(data_3, function(x) as.numeric(as.character(x)))
-
-#set back the missed rownames in the processing
-rownames(data_4) <- rownames(data_3)
-
-# Convert to dataframe
-data_4 <- as.data.frame(data_4)
-
-# Scale values and set rowname as column
-data_5 <-data_4 %>% rownames_to_column( var = "group" )
-
-data_6 <- melt(data_5)
-
-cluster1 <- subset(data_6, group=="Cluster 1")
-
-cluster1$traits <- c(rep("Breeding sys.",3), rep("Compatibility",3), rep("Life form",3),
-                     rep("Life span",2), rep("F. Symm.",2), rep("Nectar",2))
-
-#Try to achieve the desire output with plot_grid
-
-c1 <- cluster1 %>% 
-  ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("sandybrown"), labels="Group 1")+
-  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())+scale_y_continuous(expand = c(0,0)) +
-  theme(axis.title.x = element_blank(), axis.text.x=element_blank(),plot.title = element_text(size = 18))+ ylab("")+
-  ggtitle("A) Qualitative variables")
-
-cluster2 <- subset(data_6, group=="Cluster 2")
-
-cluster2$traits <- c(rep("Breeding system",3), rep("Compatibility",3), rep("Life form",3),
-                     rep("Life span",2), rep("Flower symmetry",2), rep("Nectar",2))
-
-c2 <- cluster2 %>% 
-  ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("#7BB0A3"), labels="Group 2")+
-  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())+scale_y_continuous(expand = c(0,0)) +
-  theme(strip.background = element_blank(), strip.text = element_blank())+
-  theme(axis.title.x = element_blank(), axis.text.x=element_blank())+ylab("")
-
-cluster3 <- subset(data_6, group=="Cluster 3")
-
-cluster3$traits <- c(rep("Breeding system",3), rep("Compatibility",3), rep("Life form",3),
-                     rep("Life span",2), rep("Flower symmetry",2), rep("Nectar",2))
-
-c3 <- cluster3 %>% 
-  ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("lightsteelblue2"), labels="Group 3")+
-  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())+scale_y_continuous(expand = c(0,0)) +
-  theme(axis.title.x = element_blank(), axis.text.x=element_blank())+
-  theme(strip.background = element_blank(), strip.text = element_blank())+ylab("Percentage")
-
-cluster4 <- subset(data_6, group=="Cluster 4")
-
-cluster4$traits <- c(rep("Breeding system",3), rep("Compatibility",3), rep("Life form",3),
-                     rep("Life span",2), rep("Flower symmetry",2), rep("Nectar",2))
-
-c4 <- cluster4 %>% 
-  ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("thistle"), labels="Group 4")+
-  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())+scale_y_continuous(expand = c(0,0)) +
-  theme(axis.title.x = element_blank(), axis.text.x=element_blank())+
-  theme(strip.background = element_blank(), strip.text = element_blank())+ylab("")
-
-cluster5 <- subset(data_6, group=="Cluster 5")
-
-cluster5$traits <- c(rep("Breeding syst.",3), rep("Compatibility",3), rep("Life form",3),
-                     rep("Life span",2), rep("F. Symm.",2), rep("Nectar",2))
-c5 <- cluster5 %>% 
-  ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("lightgoldenrod2"), labels="Group 5")+
-  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
-  scale_y_continuous(expand = c(0,0)) +
-  theme(axis.text.x = element_text(angle = 45,vjust = 1, hjust=1))+
-  theme(strip.background = element_blank(), strip.text = element_blank())+ylab("")+xlab("")
-
-A <- c1 + c2 + c3 + c4 + c5 + plot_layout(ncol = 1)
-
-colnames(final_df_3) <- c("group","Autonomous selfing", "Flower number", "Flowers per \n inflorescence",
-                "Inflorescence \n width", "Flower length", "Style length", "Ovule number",
-                "Plant height")
-
-B <- ggradar(final_df_3, group.colours=c("sandybrown", "#7BB0A3","lightsteelblue2", "thistle", "lightgoldenrod2"),
-             legend.text.size=5, grid.label.size = 0,legend.position = "none",axis.label.size=3)+ 
-  guides(shape = guide_legend(override.aes = list(size = 0.75)))+ ggtitle("B) Quantitative variables")+
-  theme(plot.title = element_text(size = 18))
-
-patch <- A | B
-
-patch + plot_annotation(title = "Plant functional group composition",theme = theme(plot.title = element_text(size = 20,face="bold")))
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=13, fig.cap="**Figure S4.** Hierarchical clustering dendrogram with the branches coloured by the optimal number of clusters (5).
-The labels of the subgroup of species (N = 524) used in this study are coloured in black in order to show the evenness of the distribution of the species across clusters.
-The rest of species labels are omitted for visualization purposes (N = 982)."}
-
-library(ggplot2)
-library(dendextend)
-library(dplyr)
-
-e.clust_5 <- readRDS("../Data/RData/e.clust_5.rds")
-
-dendro <- as.dendrogram(e.clust_5)
-dendro.col <- dendro %>%
-  set("branches_k_color", k = 5, value =   c("lightsteelblue2", "thistle", "sandybrown", "#7BB0A3", "lightgoldenrod2")) %>%
-  set("branches_lwd", 0.7) %>%
-  set("labels_colors", 
-      value = c("darkslategray")) %>% 
-  set("labels_cex", 0.075)
-
-labels_colors(dendro.col) <- get_leaves_branches_col(dendro.col)
-
-# We use "darkgrey" to color some species
-final_d_1 <- read.csv("../Data/Csv/data_for_motifs_analysis_1.csv")
-
-plant_species <- unique(final_d_1$Plant_species)
-
-index_species_out <- which(names(labels_colors(dendro.col)) %in% plant_species)
-
-'%ni%' <- Negate('%in%')
-
-index_species_in <- which(names(labels_colors(dendro.col)) %ni% plant_species)
-
-labels_colors(dendro.col)[index_species_out] <- "black"
-labels_colors(dendro.col)[index_species_in] <- "white"
-
-ggd1 <- as.ggdend(dendro.col)
-
-ggd1$labels$angle <- 90
-ggd1$labels$vjust <- 1
-ggd1$labels$hjust <- 1
-
-ggplot(ggd1,offset_labels=-0.05) + theme(panel.grid.major = element_blank(),
- axis.text = element_blank(),axis.title = element_blank()) +
-  ggtitle("Plant functional groups")+
-  theme(plot.title = element_text(hjust = 0.5, vjust = -2,size = 20,face="bold"))+
-  annotate("text", x=140, y=1.65, label= "Self-incomp. perennials with large flowers ", size=2.5)+
-  annotate("text", x=380, y=2.15, label= "Tall plants with small unisexual flowers", size=2.5) +
-  annotate("text", x=600, y=3.85, label= "Short-lived selfers", size=2.5) +
-  annotate("text", x=1400, y=2.05, label= "Short-lived outcrossers with \n long zygomorphic flowers", size=2.5) +annotate("text", x=950, y=2.05, label= "Small outcrossing perennials", size=2.5)
-
-```
-
-\elandscape

### 2022-03-08 Manuscript/Supplementary_Material/Indirect_direct_plants.Rmd
Edits on text

---
title: ""
output:
  pdf_document: default
  html_document: default
---

```{r, echo=FALSE, message=FALSE, cache=FALSE, fig.pos="t", warning=FALSE,out.width="75%",fig.align="center", fig.width=10,fig.height=12}

library(ggplot2)
library(scatterpie)
library(RColorBrewer)
library(tidyverse)

direct_indirect <- read_csv("../../Data/Data_processing/Motifs_connections/motif_interactions.csv")
direct_indirect <- direct_indirect %>% select(motif_id,position,direct_interactions, indirect_interactions,ind_same_type_over_directed_int)

plant_means_reordered <- read_csv("../../Data/Csv/plant_abs_freq_means.csv")

#Dplyr merge
joined_tibble <- left_join(direct_indirect, plant_means_reordered)

#1 Selfing herbs
one <- joined_tibble %>% filter(Node_FG=="1")
one$ind_same_type_over_directed_int <- round(one$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
one$position <- as.factor(one$position)
one$ind_same_type_over_directed_int <- as.factor(one$ind_same_type_over_directed_int)
one_plot <- ggplot(one,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Selfing herbs")+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  ylab("Frequency")

#2 Small outcrossing perennials
two <- joined_tibble %>% filter(Node_FG=="2")
two$ind_same_type_over_directed_int <- round(two$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
two$position <- as.factor(two$position)
two$ind_same_type_over_directed_int <- as.factor(two$ind_same_type_over_directed_int)
two_plot <- ggplot(two,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Small outcrossing perennials")+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  ylab("Frequency")

#3 Self-incomp. perennials with large flowers
three <- joined_tibble %>% filter(Node_FG=="3")
three$ind_same_type_over_directed_int <- round(three$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
three$position <- as.factor(three$position)
three$ind_same_type_over_directed_int <- as.factor(three$ind_same_type_over_directed_int)
three_plot <- ggplot(three,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Self-incomp. perennials with large flowers") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  ylab("Frequency")

#4 Tall plants with small unisexual flowers
four <- joined_tibble %>% filter(Node_FG=="4")
four$ind_same_type_over_directed_int <- round(four$ind_same_type_over_directed_int, digits = 2)
#Convert to factor
four$position <- as.factor(four$position)
four$ind_same_type_over_directed_int <- as.factor(four$ind_same_type_over_directed_int)
four_plot <- ggplot(four,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Tall plants with small unisexual flowers") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  ylab("Frequency")

#5 Short-lived outcrossers with long zygomorphic flowers
five <- joined_tibble %>% filter(Node_FG=="5")
five$ind_same_type_over_directed_int <- round(five$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
five$position <- as.factor(five$position)
five$ind_same_type_over_directed_int <- as.factor(five$ind_same_type_over_directed_int)
five_plot <- ggplot(five,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Short-lived outcrossers with long zygomorphic flowers")+
  ylab("Frequency")

library(patchwork)
one_plot / two_plot / three_plot / four_plot / five_plot + plot_annotation(
  title = 'Proportion indirect/direct interactions (0, 0.3, 0.5, 1, 2, 3)',
  theme = theme(plot.title = element_text(size = 18, face="bold")))

```

### 2022-03-08 Manuscript/Supplementary_Material/Indirect_direct_pollinators.Rmd
Edits on text

--- 2022-03-07 Manuscript/Indirect_direct.Rmd
@@
 
-plant_means_reordered <- read_csv("../Data/Csv/plant_abs_freq_means.csv")
 pollinator_means_reordered <- read_csv("../Data/Csv/pollinator_abs_freq_means.csv")

### 2022-03-08 Manuscript/Supplementary_Material/Supporting_information_Oikos.Rmd
Edits on text

--- 2022-03-06 Manuscript/Supporting_information_Oikos.Rmd
@@
 #Read data
-networks <- read_csv("../Data/Csv/data_for_motifs_analysis_1.csv")
+networks <- read_csv("../../Data/Csv/data_for_motifs_analysis_1.csv")
 
@@
 library(tidyverse)
-source("../Scripts/Scripts_Alfonso/add_study_id.R")
-d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models_NOSING/Motifs_frequency_percentile_NOSING.csv")
+source("../../Scripts/Scripts_Alfonso/add_study_id.R")
+d <- read_csv("../../Data/Csv/Motifs_frequencies_and_null_models_NOSING/Motifs_frequency_percentile_NOSING.csv")
 d <- add_study_id(d)
@@
 
-all_position_percentiles <- read_csv("../Data/Csv/Motifs_positions_and_null_models_NOSING/GF_positions_frequency_percentile_NOSING.csv")
+all_position_percentiles <- read_csv("../../Data/Csv/Motifs_positions_and_null_models_NOSING/GF_positions_frequency_percentile_NOSING.csv")
 
@@
 #read unscaled trait data in order to visualize better the clusters
-d <- read.csv("../Data/Csv/all_species_imputed_trait_data_forest_data.csv")
-
-dat_1 <- read.csv("../Data/Csv/imputed_trait_data_hclust_5_clusters_forest_data.csv", row.names = "X")
+d <- read.csv("../../Data/Csv/all_species_imputed_trait_data_forest_data.csv")
+
+dat_1 <- read.csv("../../Data/Csv/imputed_trait_data_hclust_5_clusters_forest_data.csv", row.names = "X")
 
@@
 
-e.clust_5 <- readRDS("../Data/RData/e.clust_5.rds")
+e.clust_5 <- readRDS("../../Data/RData/e.clust_5.rds")
 
@@
 # We use "darkgrey" to color some species
-final_d_1 <- read.csv("../Data/Csv/data_for_motifs_analysis_1.csv")
+final_d_1 <- read.csv("../../Data/Csv/data_for_motifs_analysis_1.csv")
 

### 2022-03-08 Manuscript/Supplementary_Material/Table_plant_species.Rmd
Edits on text

--- 2022-01-04 Manuscript/Supporting_information_Oikos.Rmd
@@
 ---
-title: "Supporting Information"
-editor_options:
-  chunk_output_type: console
-header-includes:
-- \usepackage{booktabs}
-- \usepackage{longtable}
-- \usepackage{array}
-- \usepackage{multirow}
-- \usepackage{wrapfig}
-- \usepackage{float}
-- \usepackage{colortbl}
-- \usepackage{pdflscape}
-- \usepackage{tabu}
-- \usepackage{threeparttable}
-- \usepackage{threeparttablex}
-- \usepackage[normalem]{ulem}
-- \usepackage{makecell}
-- \usepackage{xcolor}
-- \usepackage{caption,setspace}
-- \captionsetup[figure]{labelformat=empty}
-- \floatplacement{figure}{H}
-- \usepackage[skip=3pt]{caption}
-- \captionsetup[figure]{labelformat=empty}
-- \usepackage{lscape}
-- \newcommand{\blandscape}{\begin{landscape}}
-- \newcommand{\elandscape}{\end{landscape}}
+title: "Untitled"
 output:
@@
   html_document: default
-  word_document: default
-always_allow_html: true
 ---
-
-\captionsetup[table]{labelformat=empty}
-
-**The non-random assembly of functional motifs in plant-pollinator networks worldwide**
-
-Jose B. Lanuza, Alfonso Allen-Perkins and Ignasi Bartomeus
-
-\
-
-**TABLES**
-
-**Table S1** List of plant-pollinator network studies.
-
-**Table S2** List of the plant species used in this study.
-
-**Table S3** Type of plant traits used in this study.
-
-\
-
-**FIGURES**
-
-**Figure S1** Over and under-estimated motif frequencies.
-
-**Figure S2** Over and under-estimated functional groups on motif positions.
-
-**Figure S3** Plant trait composition of functional groups.
-
-**Figure S4** Plant dendrogram with functional groups.
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,fig.width=12,  warning=FALSE}
-##############################
-#TABLE S1. List of studies
-##############################
-
-#Load libraries
-library(kableExtra)
-library(dplyr)
-
-#Create data.frame with references
-
-#vector with number of netw per study
-`Number of networks` <- c("6", #1
-                          "2", #2
-                          "3",#3
-                          "1",#4
-                          "1",#5
-                          "1",#6
-                          "1",#7
-                          "2",#8
-                          "1",#9
-                          "1",#10
-                          "8",#11
-                          "16",#12
-                          "6",#13
-                          "2",#14
-                          "4",#15
-                          "1",#16
-                          "3",#17
-                          "1"#18
-                          )
-
-`First author` <- c("Bartomeus", #1
-                    "Dicks",#2
-                    "Dupont",#3
-                    "Elberling",#4
-                    "Fang",#5
-                    "Inouye",#6
-                    "Lundgren",#7
-                    "Olesen",#8
-                    "Small",#9
-                    "Souza",#10
-                    "Kaiser-Bunbury",#11
-                    "Bartomeus",#12
-                    "Kaiser-Bunbury",#13
-                    "Kaiser-Bunbury",#14
-                    "Peralta",#15
-                    "Burkle",#16
-                    "Arroyo-Correa",#17
-                    "Bundgaard"#18
-                    )
-
-Year <- c(2008,#1
-          2002,#2
-          2003,#3
-          1999,#4
-          2008,#5
-          1988,#6
-          2005,#7
-          2002,#8
-          1976,#9
-          2017,#10
-          2017,#11
-          2015,#12
-          2011,#13
-          2010,#14
-          2006,#15
-          2013,#16
-          2019,#17
-          2003#18
-          )
-
-Country <- c("Spain", #1
-               "England", #2
-               "Denmark", #3
-               "Sweden", #4
-               "China", #5
-               "United States", #6
-               "Denmark (Greenland)", #7
-               "Mauritius and Portugal (Azores)", #8
-               "Japan", #9
-               "Brazil", #10
-               "Seychelles", #11
-               "Spain", #12
-               "Seychelles", #13
-               "Mauritius", #14
-               "Argentina", # 15
-               "United States", #16
-               "New Zealand", #17
-               "Denmark" #18
-               )
-
-DOI <- c("https://doi.org/10.1007/s00442-007-0946-1", #1
-         "https://doi.org/10.1046/j.0021-8790.2001.00572.x", #2
-         "https://doi.org/10.1111/j.1365-2656.2008.01501.x", #3
-         "https://doi.org/10.1111/j.1600-0587.1999.tb00507.x", #4
-         "https://doi.org/10.1111/1749-4877.12190", #5
-         "https://doi.org/10.1111/j.1442-9993.1988.tb00968.x", #6
-         "https://doi.org/10.1657/1523-0430(2005)037[0514:TDAHCW]2.0.CO;2", #7
-         "https://doi.org/10.1046/j.1472-4642.2002.00148.x", #8
-         "/13960/t4km08d21", #9
-         "https://doi.org/10.1111/1365-2745.12978", #10
-         "https://doi.org/10.1038/nature21071", #11
-         "https://github.com/ibartomeus/BeeFunData", #12
-         "https://doi.org/10.1111/j.1365-2745.2010.01732.x", #13
-         "https://doi.org/10.1016/j.ppees.2009.04.001", #14
-         "https://doi.org/10.1111/ele.13510", #15
-         "https://doi.org/10.1126/science.1232728", #16
-         "https://doi.org/10.1111/1365-2745.13332", #17
-         "Unpublished, Master thesis" #18
-         )
-
-references <- data.frame(`First author`, Year, `Number of networks`, Country,   DOI)
-
-colnames(references) <- c("First author", "Year", "Number of networks", "Country",  "DOI")
-
-#Check number of studies
-#nrow(references) # 18 studies
-#check number of networks
-#sum(as.numeric(references$`Number of networks`)) #60
-
-references %>%
-  arrange(`First author`)%>%
-  kable( longtable = T, booktabs = T,linesep = "\\addlinespace",align = c("cccc"),escape = FALSE, caption= "\\textbf{Table S1.} List of studies ordered by author with the year of publication, number of contributed networks and digital object identifier") %>%
-  kable_styling(latex_options = c("repeat_header","striped"),  full_width=F,position = c("center"))
-
-```
-
-\elandscape
-
-\newpage
 
@@
 #Create table
-kbl(d,booktabs = T,col.names = c("", "List of plant species",""),longtable = T, caption= "\\textbf{Table S2.} List of the 503 plant species used in this study.")%>%column_spec(1,italic = T, )%>%column_spec(2,italic = T) %>%column_spec(3,italic = T)
+kbl(d,booktabs = T,col.names = c("", "List of plant species",""),longtable = T)%>%column_spec(1,italic = T)%>%column_spec(2,italic = T) %>%column_spec(3,italic = T)
 
 ```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=16, fig.width=12}
-
-library(kableExtra)
-
-library(dplyr)
-library(readxl) #read excel file (trait data)
-library(dplyr) #data manipulation
-library(visdat) #VISUALIZE MISSING DATA
-library(naniar)
-library(tidyverse)
-########################################################################################################################################################
-#1) READ TRAIT DATA
-########################################################################################################################################################
-
-Trait <- c("Plant height (m)", "Flower width (mm)", "Flower length (mm)", "Inflorescence width (mm)", "Style length (mm)", "Ovules per flower",
-           "Flowers per plant",  "Autonomous selfing (fruit set)")
-
-Trait1 <- c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Autonomous selfing", "Compatibility system", "Breeding system", "")
-
-T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub \n Tree", "Brush \n Campanulate \n Capitulum \n Open \n Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic", "None \n Low \n Medium \n High", "Self-incomp.
-\n Partially self-comp.
-\n Self-comp.", "Hermaphrodite \n Monoecious \n Dioecious",""),align = c("l"))
-
-Type <- c("Vegetative", "Floral", "Floral", "Floral", "Floral", "Floral", "Floral","Reproductive")
-
-Type_1 <- c("Vegetative", "Vegetative", "Floral", "Floral", "Reproductive", "Reproductive", "Reproductive", "")
-
-dat <- data.frame(Type, Trait,Type_1, Trait1)
-
-colnames(dat) <- c("Type","Traits","Type", "Traits")
-
-kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c"),caption = "\\textbf{Table S3.} Traits used to delimit the different plant functional groups divided in quantitative and categorical traits.") %>%
-kable_styling(full_width = T,latex_options = c("striped")) %>%
-add_header_above(c("Quantitative traits" = 2,"Categorical traits" = 2),bold=T)  %>%
-    column_spec(c(1,4), bold = T) %>% row_spec(0, bold=T)
-
-```
-
-\clearpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure S1.** Comparison of motif frequencies between empirical and simulated networks grouped by average path length (plots a, b, c and d) as determined in Simmons et al.
-(2020) without considering singletones.
-This is shown with the mean percentage of motif frequencies in empirical networks that were over the motif frequencies of the simulated ones (percentiles).
-This was done by network (light blue dots) and then averaged for all networks (black dots with error bars that correspond to the standard deviation)."}
-library(lme4)
-library(nlme)
-library(tidyverse)
-source("../Scripts/Scripts_Alfonso/add_study_id.R")
-d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models_NOSING/Motifs_frequency_percentile_NOSING.csv")
-d <- add_study_id(d)
-#str(d)
-#head(d)
-
-#ggplot(d %>% filter(motif != 1), aes(percentil_sizeclass))+
-#  geom_histogram(color="black", fill="white")+
-#  facet_wrap(~motif)+
-#  theme_bw()+
-#  labs(x="Sizeclass percentile")
-#
-# Motifs tend to be over- and under-represensented in real networks
-
-# Mean percentile and SE taking into account the study system
-motif_codes <- d %>% filter(motif != 1) %>% # We remove links (motif code: 1)
-  select(motif) %>% unique() %>% pull()
-motif_means <- tibble(motif = motif_codes)
-motif_means$mean <- NA
-motif_means$SE <- NA
-
-for(i.motif in 1:length(motif_codes)){
-
-  m <- lmer(percentil_sizeclass ~ 1+(1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = subset(d, motif == motif_codes[i.motif]))
-
-  motif_means$mean[i.motif] <- fixed.effects(m) %>% unname()
-  motif_means$SE[i.motif] <- sqrt(diag(vcov(m)))
-
-}
-
-#Add categories based on path length set by Simmons 2021 et al., Functional Ecology
-d$Broad_categories[d$motif==2 | d$motif==7 | d$motif==17 | d$motif==3|d$motif==4|d$motif==8] <- "Fan"
-
-d$Broad_categories[d$motif==15 | d$motif==11] <- "Medium-weak"
-
-d$Broad_categories[d$motif==6 | d$motif==16 |  d$motif==12] <- "Strong"
-
-d$Broad_categories[d$motif==5 | d$motif==9 |  d$motif==14|  d$motif==13|  d$motif==10] <- "Weak"
-
-#order the categories from short to long path length
-d$Broad_categories <- factor(d$Broad_categories, levels = c("Strong", "Fan", "Medium-weak", "Weak"))
-
-#Ffilter out two node motifs
-d_1 <- d %>% filter(motif != 1)
-#Merge dataframes to bl able to create facets
-d_2 <- merge(d_1, motif_means, by="motif")
-
-arr <- list('Strong' = expression(bold(paste("Complete (strong, ", bar(x), " = 1.38)"))),
-             'Fan' = expression(bold(paste("Fan (medium-strong, ", bar(x), " = 1.48)"))), 
-             'Medium-weak' = expression(bold(paste("Asymmetric complete (medium-weak, ", bar(x), " = 1.60)"))), 
-             "Weak" =expression(bold(paste("Core-peripheral (weak, ", bar(x), " = 1.85)"))))
-mylabel <- function(val) { return(lapply(val, function(x) arr[x])) }
-
-library(ggforce) #workaround with ggforce to have facets with same sizes
-
-p <- ggplot()+geom_point(data = d_2, aes(y=factor(motif), 100*percentil_sizeclass), shape=21,color="black",fill="azure2",size=1.75, alpha=0.3)+
-  geom_errorbar(data = d_2,aes(y = factor(motif), xmin=100*(mean-SE), xmax=100*(mean+SE)), 
-                width=0.8,size=0.8,color="black") +theme_bw()+
-  geom_point(data = d_2,aes(y = as.factor(motif), x=100*mean), 
-             size=2,color="black")+labs(y="Two to five node motifs", x = "Percentile")+
-  theme( strip.background = element_blank())+
-  theme(strip.text = element_text(face="bold", size=10, hjust=0),
-        panel.border=element_rect(color="black",size=1.2))
-
-p + ggforce::facet_col(vars(Broad_categories), scales = 'free', space = 'free',labeller=mylabel)
-
-#Trying to maintain a gradient from low to high in colors
-
-#Fig 1 Should be a dot plot (or forest plot) of the mean +- SE of the 15 motifs.
-#NICE! Can we put motifs in Y axes, and % in X?
-```
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="\\textbf{Figure S2.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions after removing non-robust links (singletones).
-The different motif positions are dividied by the average path length clasification by Simmons et al.
-(2020).
-The superior dendrogram indicates the differences across groups with the more separated groups showing larger differences."}
-
-library(lme4)
-library(nlme)
-library(tidyverse)
-library(stringi)
-source("../Scripts/Scripts_Alfonso/add_study_id.R")
-
-#############################################
-# EXTRACT MEAN VALUES
-#############################################
-
-all_position_percentiles <- read_csv("../Data/Csv/Motifs_positions_and_null_models_NOSING/GF_positions_frequency_percentile_NOSING.csv")
-
-all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
-                                                              "[0-9]+") %>% as.numeric()
-
-all_position_percentiles <- add_study_id(all_position_percentiles)
-#str(all_position_percentiles)
-#head(all_position_percentiles)
-
-list_plants_FG <- as.character(1:10)
-
-plant_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF)) #ME DA ERROR
-pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF))
-
-# Plants-------------
-
-# Mean percentile and SE taking into account the study system
-plant_codes <- plant_position_percentiles_filtered$position %>% unique()
-plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-plant_means$mean <- NA
-plant_means$SE <- NA
-
-for(i.pos in 1:length(plant_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
-            data = plant_position_percentiles_filtered %>%
-              filter(position == plant_codes[i.pos]))
-
-  temp <- fixed.effects(m) %>% unname()
-  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
-                                                                    temp[1]+temp[2],
-                                                                    temp[1]+temp[3],
-                                                                    temp[1]+temp[4],
-                                                                    temp[1]+temp[5]) ## to get real means per FG
-  temp <- sqrt(diag(vcov(m)))
-  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
-                                                                  temp[1]+temp[2],
-                                                                  temp[1]+temp[3],
-                                                                  temp[1]+temp[4],
-                                                                  temp[1]+temp[5])
-
-}
-
-# Pollinators--------
-
-# Mean percentile and SE taking into account the study system
-pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
-pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-pollinator_means$mean <- NA
-pollinator_means$SE <- NA
-pollinator_means_reordered <- NULL
-
-for(i.pos in 1:length(pollinator_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = pollinator_position_percentiles_filtered %>%
-              filter(position == pollinator_codes[i.pos]),
-            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
-
-  temp <- fixed.effects(m) %>% unname()
-  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)
-
-  pollinator_means_aux$mean <- c(temp[1],
-                                 temp[1]+temp[2],
-                                 temp[1]+temp[3],
-                                 temp[1]+temp[4],
-                                 temp[1]+temp[5],
-                                 temp[1]+temp[6],
-                                 temp[1]+temp[7],
-                                 temp[1]+temp[8],
-                                 temp[1]+temp[9]) ## to get real means per FG
-
-  temp <- sqrt(diag(vcov(m)))
-  pollinator_means_aux$SE <- c(temp[1],
-                               temp[1]+temp[2],
-                               temp[1]+temp[3],
-                               temp[1]+temp[4],
-                               temp[1]+temp[5],
-                               temp[1]+temp[6],
-                               temp[1]+temp[7],
-                               temp[1]+temp[8],
-                               temp[1]+temp[9])
-
-  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)
-
-}
-
-# There are lower limits (mean - SE) smaller than 0 (see Other insects)
-# We set the lower limit of those error bars to zero
-
-pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
-pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
-
-#############################################
-# ADDING BROAD MOTIF CATEGORIES TO POSITIONS
-#############################################
-
-motifs_raw_data <- read_csv("../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-motifs_raw_data$Broad_categories <- NA
-
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(5,9,14,13,10)] <- "Core-peripherical"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(6,16,12)] <- "Complete"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(2,3,7,4,17,8)] <- "Fan"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(15,11)] <- "Asymmetric complete"
-
-motifs_raw_data$plant <- gsub("[^0-9.-]", "", motifs_raw_data$plant)
-motifs_raw_data$pollinator <- gsub("[^0-9.-]", "", motifs_raw_data$pollinator)
-motifs_raw_data$plant <- as.numeric(motifs_raw_data$plant)
-motifs_raw_data$pollinator <- as.numeric(motifs_raw_data$pollinator)
-motifs_raw_data <- motifs_raw_data %>% filter(!is.na(Broad_categories))
-
-fan_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-pollinator_means_reordered$Broad_categories <- NA
-
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% fan_pollinator] <- "Fan" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% asymm_pollinator] <- "Medium-weak" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% complete_pollinator] <- "Strong" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% core_per_pollinator] <- "Weak"
-
-fan_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-plant_means$Broad_categories <- NA
-
-plant_means$Broad_categories[plant_means$position %in% fan_plant] <- "Fan" 
-plant_means$Broad_categories[plant_means$position %in% asymm_plant] <- "Medium-weak" 
-plant_means$Broad_categories[plant_means$position %in% complete_plant] <- "Strong" 
-plant_means$Broad_categories[plant_means$position %in% core_per_plant] <- "Weak"
-
-########################################
-# CREATE HEATMAPS
-########################################
-
-library(ComplexHeatmap)
-
-# PLANTS-----
-
-# Prepare data for heatmap
-heat_plants_aux <- plant_means %>% spread(Node_FG,mean) %>% select(-SE)
-
-heat_plants <- heat_plants_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-heat_plants_fan <- heat_plants %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_fan) <- heat_plants_fan[,1]
-
-heat_plants_Weak <- heat_plants %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Weak) <- heat_plants_Weak[,1]
-
-heat_plants_Strong <- heat_plants %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Strong) <- heat_plants_Strong[,1]
-
-heat_plants_Medium_weak <- heat_plants %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Medium_weak) <- heat_plants_Medium_weak[,1]
-
-# POLLINATORS-----------
-
-filter_rare_groups <- T
-
-if(filter_rare_groups == T){
-  heat_pollinators_aux <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds",
-                                                                                "Lizards",
-                                                                                "Other_insects")) %>% 
-    spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees",            
-                                      "Coleoptera","Lepidoptera","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Syrphids")
-}else{
-  heat_pollinators_aux <- pollinator_means_reordered %>% spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees","Birds",            
-                                      "Coleoptera","Lepidoptera","Lizards","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Other insects","Syrphids")
-}
-
-heat_pollinators <- heat_pollinators_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-heat_pollinators_fan <- heat_pollinators %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_fan) <- heat_pollinators_fan[,1]
-
-heat_pollinators_Weak <- heat_pollinators %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Weak) <- heat_pollinators_Weak[,1]
-
-heat_pollinators_Strong <- heat_pollinators %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Strong) <- heat_pollinators_Strong[,1]
-
-heat_pollinators_Medium_weak <- heat_pollinators %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Medium_weak) <- heat_pollinators_Medium_weak[,1]
-
-##################
-
-#Do not know how to handle this multiplot for creating a panel
-
-# I'm going to create the 4 plots in one, 
-# I'm not sure that the grouping of the functional group is correct
-# when is done separately
-
-#sorry for the mess of libraries that I do below
-
- #Prepare first pollinators
-
-library(tidyr)
-library(data.table)
-long <- melt(setDT(heat_pollinators), id.vars = c("position","Broad_categories"), variable.name = "guilds")
-
-long_1 <- long %>% select(-Broad_categories)
-
-library(reshape2)
-long_m <- acast(long_1, position~guilds, value.var="value")
-
-#set manually the divisions, so far this is the best way I have seen to split the rows by categories
-
-r_split <- c(rep(c("Fan"), 3),rep(c("Core-peripheral"), 2),"Complete",rep(c("Fan"),2),rep(c("Core-peripheral"), 4),
-             rep(c("Asymmetric complete"), 2), "Complete", rep(c("Core-peripheral"), 3),rep(c("Asymmetric complete"), 2),
-             "Complete", "Fan")
-
-#set order of labels that avoids overlapping
-r_split <- factor(r_split, levels=c("Core-peripheral","Complete","Fan","Asymmetric complete"))
-
-#plat a bit with colors, a bit of a more complex set but looks nicer
-library(circlize)
-col_fun = colorRamp2(c(0.05644663,0.25, 0.4673256,0.75, 0.8782047), c("blue","cadetblue3", "azure2", "gold","red"))
-
-h_pol <- Heatmap(long_m, name = "Mean\npercentile", row_split=r_split,cluster_row_slices = FALSE, 
-                 column_title = "Pollinator functional groups",row_names_gp = gpar(fontsize = 10),
-                 col = col_fun,column_names_rot = 45,  column_names_gp = grid::gpar(fontsize = 10),
-                 column_title_gp = gpar(fontsize = 15, fontface = "bold"),
-                 row_title_gp = gpar(fontsize = 10, fontface = "bold"))
-
- #Prepare plants
-
-#long format
-long_plants <- melt(setDT(heat_plants), id.vars = c("position","Broad_categories"), variable.name = "Functional_groups")
-
-#filter for creating matrix
-long_plants_1 <- long_plants %>% select(-Broad_categories)
-
-#set better colnames
-long_plants_1$Functional_groups <- as.character(long_plants_1$Functional_groups)
-
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==1] <- "Selfing herbs" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==2] <- "Small outcrossing\nperennials" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==3] <- "Self-incomp. perennials\nwith large flowers" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==4] <- "Tall plants with small\nunisexual flowers" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==5] <- "Short-lived outcrossers with\nlong zygomorphic flowers"
-
-long_plants_1$Functional_groups <- factor(long_plants_1$Functional_groups, levels=c("Selfing herbs",
-"Small outcrossing\nperennials" ,"Self-incomp. perennials\nwith large flowers",
-"Tall plants with small\nunisexual flowers" ,"Short-lived outcrossers with\nlong zygomorphic flowers" ))
-
-#create matrix with reshape
-long_plants_m <- acast(long_plants_1, position~Functional_groups, value.var="value")
-
-r_split_plants <- c(rep(c("Fan"), 3),rep(c("Core-peripheral"), 2),"Complete",rep(c("Fan"),2),rep(c("Core-peripheral"), 3),
-                    rep(c("Asymmetric complete"), 2), "Complete", rep(c("Core-peripheral"), 4),rep(c("Asymmetric complete"), 2),
-                    "Complete", "Fan")
-
-r_split_plants <- factor(r_split, levels=c("Core-peripheral","Complete","Fan","Asymmetric complete"))
-
-h_plan <- Heatmap(long_plants_m, name = "Mean\npercentile", row_split=r_split_plants,cluster_row_slices = F, 
-                  column_title = "Plant functional groups",row_names_gp = gpar(fontsize = 10),col = col_fun,column_names_rot = 45,  
-                  column_names_gp = grid::gpar(fontsize = 10),column_title_gp = gpar(fontsize = 15, fontface = "bold"),
-                  row_title_gp = gpar(fontsize = 10, fontface = "bold"))
-
-library(patchwork)
-ht_list <- h_pol+h_plan
-
-draw(ht_list, auto_adjust = FALSE, cluster_rows = F)
-
-```
-
-\newpage
-
-\blandscape
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=7, fig.width=12, fig.cap="**Figure S3.** Plant functional group composition separated in qualitative and quantitative variables.
-Panel A) shows the percentage of the different categories within trait represented with different colours for each functional group.
-Plot B) shows the radar plot of the different quantitative variables standardize on the same scale also coloured with the same patterns of colours as qualitative variables per cluster or functional group.
-Group 1 corresponds to short-lived selfers; group 2 to small outcrossing perennials; group 3 to self-incompatible perennials with large flowers; group 4 to tall plants with small unisexual flowers; and, group 5 to short-lived outcrossers with long zygomorphic flowers."}
-
-#CODE TO PLOT FUNCTIONAL GROUPS
-#IT CAN BE PLOT WITH MUCH LESS CODE BUT NO TIME FOR CLEANING IT
-
-##########################################
-#Visualization of plant functional groups#
-##########################################
-
-library(cowplot)
-library(ggplot2)
-library(tidyr)
-library(dplyr)
-library(reshape2)
-library(data.table)
-library(patchwork)
-
-#LOAD DATA
-#read unscaled trait data in order to visualize better the clusters
-d <- read.csv("../Data/Csv/all_species_imputed_trait_data_forest_data.csv")
-
-dat_1 <- read.csv("../Data/Csv/imputed_trait_data_hclust_5_clusters_forest_data.csv", row.names = "X")
-
-d$Clusters <- dat_1$Clusters
-
-#select columns of interest
-t <- d[c("Breeding_system","IMPUTED_Compatibility","Autonomous_selfing_level",
-         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Flowers_per_inflorescence",
-         "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean", "STYLE_IMPUTED", "OVULES_IMPUTED", "life_form", "lifespan",
-         "IMPUTED_plant_height_mean_m", "Nectar_presence_absence", "Clusters")]
-
-##############################################################################################################################
-#Prepare table qualitative variables
-##############################################################################################################################
-
-##############################################################################################################################
-#Breeding system
-t$Breeding_system <- factor(t$Breeding_system, levels=c("Dioecious", "Monoecious", "Hermaphrodite"))
-
-#Summary to create table
-breeding <- t %>%
-  group_by(Clusters,Breeding_system) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-breeding <- breeding[,-3]
-
-breeding <- spread(breeding, Clusters, Percentage)
-
-colnames(breeding)[1] <- "Category"
-
-Trait <- data.frame(Trait= c(rep("Breeding system", 3)))
-
-Breeding_system <- cbind(Trait, breeding)
-
-##############################################################################################################################
-#Compatibility
-str(t)
-t$IMPUTED_Compatibility <- as.character(t$IMPUTED_Compatibility)
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="dioecious"] <- "Unisexual flower"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="monoecious"] <- "Unisexual flower"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_incompatible"] <- "Self incompatible"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="partially_self_compatible"] <- "Partially self compatible"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_compatible"] <- "Self compatible"
-
-t$IMPUTED_Compatibility <- factor(t$IMPUTED_Compatibility, levels=c("Unisexual flower", "Self incompatible", "Partially self compatible", "Self compatible"))
-#Summary to create table
-comp <- t %>%
-  group_by(Clusters,IMPUTED_Compatibility) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-comp <- comp[,-3]
-
-comp <- spread(comp, Clusters, Percentage)
-#Replace Na's with zeros
-comp[is.na(comp)] <- 0
-#Set call name os categories per trait
-colnames(comp)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Compatibility system", 4)))
-#Add column
-Compatibility_system <- cbind(Trait, comp)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system)
-
-############################################################################################################################################
-#Life form
-t$life_form <- as.character(t$life_form)
-t$life_form[t$life_form =="vine"] <- "Shrub"
-t$life_form[t$life_form =="tree"] <- "Tree"
-t$life_form[t$life_form =="herb"] <- "Herb"
-t$life_form[t$life_form =="shrub"] <- "Shrub"
-#Order levels
-t$life_form <- factor(t$life_form, levels=c("Tree", "Shrub", "Herb"))
-#Summary to create table
-life_form <- t %>%
-  group_by(Clusters,life_form) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-life_form <- life_form[,-3]
-#convert to wide
-life_form <- spread(life_form, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(life_form)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Life form", 3)))
-#Add column
-Life_form<- cbind(Trait, life_form)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form)
-
-############################################################################################################################################
-t$lifespan <- factor(t$lifespan, levels=c("Perennial","Short lived"))
-#Summary to create table
-life_span <- t %>%
-  group_by(Clusters,lifespan) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-life_span <- life_span[,-3]
-#convert to wide
-life_span <- spread(life_span, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(life_span)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Life span", 2)))
-#Add column
-Life_span<- cbind(Trait, life_span)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span)
-
-############################################################################################################################################
-t$Flower_morphology <- as.character(t$Flower_morphology)
-t$Flower_morphology[t$Flower_morphology=="Funnelform"] <- "Campanulate"
-t$Flower_morphology[t$Flower_morphology=="Spike"] <- "Brush"
-
-Flower_morphology <- t %>%
-  group_by(Clusters,Flower_morphology) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-Flower_morphology <- Flower_morphology[,-3]
-#convert to wide
-Flower_morphology <- spread(Flower_morphology, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(Flower_morphology)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Flower shape", 6)))
-#Add column
-Flower_morphology<- cbind(Trait, Flower_morphology)
-#Replace Na's with zeros
-Flower_morphology[is.na(Flower_morphology)] <- 0
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology)
-
-############################################################################################################################################
-t$Flower_symmetry <- as.character(t$Flower_symmetry)
-t$Flower_symmetry[t$Flower_symmetry =="actinomorphic"] <- "Actinomorphic"
-t$Flower_symmetry[t$Flower_symmetry =="zygomorphic"] <- "Zygomorphic"
-
-Flower_symmetry <- t %>%
-  group_by(Clusters,Flower_symmetry) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-Flower_symmetry <- Flower_symmetry[,-3]
-#convert to wide
-Flower_symmetry <- spread(Flower_symmetry, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(Flower_symmetry)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Flower symmetry", 2)))
-#Add column
-Flower_symmetry<- cbind(Trait, Flower_symmetry)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology,Flower_symmetry)
-############################################################################################################################################
-t$Autonomous_selfing_level <- as.character(t$Autonomous_selfing_level)
-t$Autonomous_selfing_level[t$Autonomous_selfing_level =="none"] <- "None"
-t$Autonomous_selfing_level[t$Autonomous_selfing_level =="low"] <- "Low"
-t$Autonomous_selfing_level[t$Autonomous_selfing_level =="medium"] <- "Medium"
-t$Autonomous_selfing_level[t$Autonomous_selfing_level =="high"] <- "High"
-
-#Order levels
-t$Autonomous_selfing_level <- factor(t$Autonomous_selfing_level, levels=c("High", "Medium", "Low", "None"))
-
-Selfing <- t %>%
-  group_by(Clusters,Autonomous_selfing_level) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-#delete column to convert to wide
-Selfing <- Selfing[,-3]
-#convert to wide
-Selfing <- spread(Selfing, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(Selfing)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Selfing level", 2)))
-#Replace Na's with zeros
-Selfing[is.na(Selfing)] <- 0
-#Add column
-Selfing_1 <- cbind(Trait, Selfing)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology, Selfing_1)
-
-############################################################################################################################################
-t$Nectar_presence_absence <- as.character(t$Nectar_presence_absence)
-t$Nectar_presence_absence[t$Nectar_presence_absence =="yes"] <- "Yes"
-t$Nectar_presence_absence[t$Nectar_presence_absence =="no"] <- "No"
-
-Nectar <- t %>%
-  group_by(Clusters,Nectar_presence_absence) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-#delete column to convert to wide
-Nectar <- Nectar[,-3]
-#convert to wide
-Nectar <- spread(Nectar, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(Nectar)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Nectar", 2)))
-#Replace Na's with zeros
-Nectar[is.na(Nectar)] <- 0
-#Add column
-Nectar <- cbind(Trait, Nectar)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology, Flower_symmetry,Selfing_1, Nectar)
-
-##############################################################################################################################
-#Prepare table quantitative variables
-##############################################################################################################################
-
-Selfing <-  t %>% group_by(Clusters)%>% 
-  select(Autonomous_selfing_level_fruit_set) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                     # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                    sd = sd))
-
-s1 <- as.data.frame(t(Selfing))
-#set colnames
-colnames(s1) <- c("1","2","3","4","5")
-#remove the cluster row
-s1 <- s1[-1,]
-#convert rownames to 1st columns
-s1 <- setDT(s1, keep.rownames = "TRUE")[]
-colnames(s1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Autonomous selfing", 5)))
-#Add column
-Selfing <- cbind(Trait, s1)
-
-##############################################################################################################################
-flower_number <-  t %>% group_by(Clusters)%>% 
-  select(Flowers_per_plant) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-f1 <- as.data.frame(t(flower_number))
-#set colnames
-colnames(f1) <- c("1","2","3","4","5")
-#remove the cluster row
-f1 <- f1[-1,]
-#convert rownames to 1st columns
-f1 <- setDT(f1, keep.rownames = "TRUE")[]
-colnames(f1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Flower number", 5)))
-#Add column
-Flower_number <- cbind(Trait, f1)
-
-##############################################################################################################################
-Flowers_per_inflorescence <-  t %>% group_by(Clusters)%>% 
-  select(Flowers_per_inflorescence) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-f_i_1 <- as.data.frame(t(Flowers_per_inflorescence))
-#set colnames
-colnames(f_i_1) <- c("1","2","3","4","5")
-#remove the cluster row
-f_i_1 <- f_i_1[-1,]
-#convert rownames to 1st columns
-f_i_1 <- setDT(f_i_1, keep.rownames = "TRUE")[]
-colnames(f_i_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Flowers per inflorescence", 5)))
-#Add column
-Flower_per_inflo <- cbind(Trait, f_i_1)
-
-bind_rows(Selfing, Flower_number, Flower_per_inflo)
-
-##############################################################################################################################
-Floral_unit_width <-  t %>% group_by(Clusters)%>% 
-  select(Floral_unit_width) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-f_u_w_1 <- as.data.frame(t(Floral_unit_width))
-#set colnames
-colnames(f_u_w_1) <- c("1","2","3","4","5")
-#remove the cluster row
-f_u_w_1 <- f_u_w_1[-1,]
-#convert rownames to 1st columns
-f_u_w_1 <- setDT(f_u_w_1, keep.rownames = "TRUE")[]
-colnames(f_u_w_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Inflorescence width", 5)))
-#Add column
-Inflo_width <- cbind(Trait, f_u_w_1)
-
-bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width)
-
-##############################################################################################################################
-Corolla_diameter_mean <-  t %>% group_by(Clusters)%>% 
-  select(Corolla_diameter_mean) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-c_w_1 <- as.data.frame(t(Corolla_diameter_mean))
-#set colnames
-colnames(c_w_1) <- c("1","2","3","4","5")
-#remove the cluster row
-c_w_1 <- c_w_1[-1,]
-#convert rownames to 1st columns
-c_w_1 <- setDT(c_w_1, keep.rownames = "TRUE")[]
-colnames(c_w_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Flower width", 5)))
-#Add column
-Flower_width <- cbind(Trait, c_w_1)
-
-bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width)
-
-##############################################################################################################################
-Corolla_length_mean <-  t %>% group_by(Clusters)%>% 
-  select(Corolla_length_mean) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-c_l_1 <- as.data.frame(t(Corolla_length_mean))
-#set colnames
-colnames(c_l_1) <- c("1","2","3","4","5")
-#remove the cluster row
-c_l_1 <- c_l_1[-1,]
-#convert rownames to 1st columns
-c_l_1 <- setDT(c_l_1, keep.rownames = "TRUE")[]
-colnames(c_l_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Flower length", 5)))
-#Add column
-Flower_length<- cbind(Trait, c_l_1)
-
-bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length)
-
-##############################################################################################################################
-STYLE_IMPUTED <-  t %>% group_by(Clusters)%>% 
-  select(STYLE_IMPUTED) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-s_l_1 <- as.data.frame(t(STYLE_IMPUTED))
-#set colnames
-colnames(s_l_1) <- c("1","2","3","4","5")
-#remove the cluster row
-s_l_1 <- s_l_1[-1,]
-#convert rownames to 1st columns
-s_l_1 <- setDT(s_l_1, keep.rownames = "TRUE")[]
-colnames(s_l_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Style length", 5)))
-#Add column
-Style_length<- cbind(Trait, s_l_1)
-
-bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length, Style_length)
-
-##############################################################################################################################
-
-OVULES_IMPUTED <-  t %>% group_by(Clusters)%>% 
-  select(OVULES_IMPUTED) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-o_n_1 <- as.data.frame(t(OVULES_IMPUTED))
-#set colnames
-colnames(o_n_1) <- c("1","2","3","4","5")
-#remove the cluster row
-o_n_1 <- o_n_1[-1,]
-#convert rownames to 1st columns
-o_n_1 <- setDT(o_n_1, keep.rownames = "TRUE")[]
-colnames(o_n_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Ovule number", 5)))
-#Add column
-Ovule_number <- cbind(Trait, o_n_1)
-
-bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length, Ovule_number)
-
-##############################################################################################################################
-
-IMPUTED_plant_height_mean_m <-  t %>% group_by(Clusters)%>% 
-  select(IMPUTED_plant_height_mean_m) %>% # select variables to summarise
-  summarise_each(funs(min = min,
-                      # q25 = quantile(., 0.25), 
-                      median = median, 
-                      #q75 = quantile(., 0.75), 
-                      max = max,
-                      mean = mean, 
-                      sd = sd))
-
-p_h_1 <- as.data.frame(t(IMPUTED_plant_height_mean_m))
-#set colnames
-colnames(p_h_1) <- c("1","2","3","4","5")
-#remove the cluster row
-p_h_1 <- p_h_1[-1,]
-#convert rownames to 1st columns
-p_h_1 <- setDT(p_h_1, keep.rownames = "TRUE")[]
-colnames(p_h_1)[1] <- "Category"
-#Create data frame to add grouping variable
-Trait <- data.frame(Trait= c(rep("Plant height", 5)))
-#Add column
-Plant_height <- cbind(Trait, p_h_1)
-
-#Bind quantitative and qualitative variables
-Table_all_traits <- bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology, Flower_symmetry,Selfing_1, Nectar,
-          Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length, Style_length, Ovule_number, Plant_height)
-
-#Select just two decimals
-is.num <- sapply(Table_all_traits, is.numeric)
-Table_all_traits[is.num] <- lapply(Table_all_traits[is.num], round, 2)
-
-colnames(Table_all_traits) <- c("Trait", "Category", "Cluster 1", "Cluster 2", "Cluster 3", "Cluster 4", "Cluster 5")
-
-#LOAD LIBRARIES
-#devtools::install_github("ricardo-bion/ggradar", dependencies=TRUE)
-suppressPackageStartupMessages(library(dplyr))
-library(scales)
-library(tibble)
-library(ggradar)
-library(janitor)
-library(grid)
-library(dplyr)
-library(lubridate)
-#QUANTITATIVVE VARIABLES
-
-#generate subset of quantitative variables for plotting
-quant_median <- subset(Table_all_traits, Category=="median")
-
-#delete col number 2
-quant_median <- quant_median[,-2]
-
-#transpose dataframe
-final_df <- as.data.frame(t(quant_median))
-
-#rownames to colnames (1st one)
-final_df_1 <- final_df %>% row_to_names(row_number = 1)
-
-#Convert all variables to numeric
-final_df_2 <- sapply(final_df_1, function(x) as.numeric(as.character(x)))
-
-#set back the missed rownames in the processing
-rownames(final_df_2) <- rownames(final_df_1)
-
-# Convert to dataframe
-final_df_2 <- as.data.frame(final_df_2)
-
-# Scale values and set rowname as column
-final_df_3 <-final_df_2 %>% rownames_to_column( var = "group" ) %>%   mutate_at(vars(-group),funs(rescale))
-
-#Plot Radar
-#ggradar(final_df_3)
-
-#QUALITATIVE VARIABLES
-
-#LOAD DATA
-#read unscaled trait data in order to visualize better the clusters
-d <- read.csv("../Data/Csv/all_species_imputed_trait_data_forest_data.csv")
-
-dat_1 <- read.csv("../Data/Csv/imputed_trait_data_hclust_5_clusters_forest_data.csv", row.names = "X")
-
-d$Clusters <- dat_1$Clusters
-
-#select columns of interest
-t <- d[c("Breeding_system","IMPUTED_Compatibility","Autonomous_selfing_level",
-         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Flowers_per_inflorescence",
-         "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean", "STYLE_IMPUTED", "OVULES_IMPUTED", "life_form", "lifespan",
-         "IMPUTED_plant_height_mean_m", "Nectar_presence_absence", "Clusters")]
-
-##############################################################################################################################
-#Prepare table qualitative variables
-##############################################################################################################################
-
-##############################################################################################################################
-#Breeding system
-t$Breeding_system <- factor(t$Breeding_system, levels=c("Dioecious", "Monoecious", "Hermaphrodite"))
-
-#Summary to create table
-breeding <- t %>%
-  group_by(Clusters,Breeding_system) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-breeding <- breeding[,-3]
-
-breeding <- spread(breeding, Clusters, Percentage)
-
-colnames(breeding)[1] <- "Category"
-
-Trait <- data.frame(Trait= c(rep("Breeding system", 3)))
-
-Breeding_system <- cbind(Trait, breeding)
-
-##############################################################################################################################
-#Compatibility
-str(t)
-t$IMPUTED_Compatibility <- as.character(t$IMPUTED_Compatibility)
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="dioecious"] <- "Self incompatible"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="monoecious"] <- "Self incompatible"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_incompatible"] <- "Self incompatible"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="partially_self_compatible"] <- "Partially self compatible"
-t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_compatible"] <- "Self compatible"
-
-t$IMPUTED_Compatibility <- factor(t$IMPUTED_Compatibility, levels=c("Self incompatible", "Partially self compatible", "Self compatible"))
-#Summary to create table
-comp <- t %>%
-  group_by(Clusters,IMPUTED_Compatibility) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-comp <- comp[,-3]
-
-comp <- spread(comp, Clusters, Percentage)
-#Replace Na's with zeros
-comp[is.na(comp)] <- 0
-#Set call name os categories per trait
-colnames(comp)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Compatibility system", 3)))
-#Add column
-Compatibility_system <- cbind(Trait, comp)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system)
-
-############################################################################################################################################
-#Life form
-t$life_form <- as.character(t$life_form)
-t$life_form[t$life_form =="vine"] <- "Shrub"
-t$life_form[t$life_form =="tree"] <- "Tree"
-t$life_form[t$life_form =="herb"] <- "Herb"
-t$life_form[t$life_form =="shrub"] <- "Shrub"
-#Order levels
-t$life_form <- factor(t$life_form, levels=c("Tree", "Shrub", "Herb"))
-#Summary to create table
-life_form <- t %>%
-  group_by(Clusters,life_form) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-life_form <- life_form[,-3]
-#convert to wide
-life_form <- spread(life_form, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(life_form)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Life form", 3)))
-#Add column
-Life_form<- cbind(Trait, life_form)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form)
-
-############################################################################################################################################
-t$lifespan <- factor(t$lifespan, levels=c("Perennial","Short lived"))
-#Summary to create table
-life_span <- t %>%
-  group_by(Clusters,lifespan) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-life_span <- life_span[,-3]
-#convert to wide
-life_span <- spread(life_span, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(life_span)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Life span", 2)))
-#Add column
-Life_span<- cbind(Trait, life_span)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span)
-
-############################################################################################################################################
-#t$Flower_morphology <- as.character(t$Flower_morphology)
-#t$Flower_morphology[t$Flower_morphology=="Funnelform"] <- "Campanulate"
-#t$Flower_morphology[t$Flower_morphology=="Spike"] <- "Brush"
-#
-#Flower_morphology <- t %>%
-#  group_by(Clusters,Flower_morphology) %>%
-#  summarise (n = n()) %>%
-#  mutate(Percentage = n / sum(n)*100)
-##delete column to convert to wide
-#Flower_morphology <- Flower_morphology[,-3]
-##convert to wide
-#Flower_morphology <- spread(Flower_morphology, Clusters, Percentage)
-##Set call name os categories per trait
-#colnames(Flower_morphology)[1] <- "Category"
-##Create new column
-#Trait <- data.frame(Trait= c(rep("Flower shape", 6)))
-##Add column
-#Flower_morphology<- cbind(Trait, Flower_morphology)
-##Replace Na's with zeros
-#Flower_morphology[is.na(Flower_morphology)] <- 0
-##Bind rows
-#bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology)
-#
-############################################################################################################################################
-t$Flower_symmetry <- as.character(t$Flower_symmetry)
-t$Flower_symmetry[t$Flower_symmetry =="actinomorphic"] <- "Actinomorphic"
-t$Flower_symmetry[t$Flower_symmetry =="zygomorphic"] <- "Zygomorphic"
-
-Flower_symmetry <- t %>%
-  group_by(Clusters,Flower_symmetry) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-#delete column to convert to wide
-Flower_symmetry <- Flower_symmetry[,-3]
-#convert to wide
-Flower_symmetry <- spread(Flower_symmetry, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(Flower_symmetry)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Flower symmetry", 2)))
-#Add column
-Flower_symmetry<- cbind(Trait, Flower_symmetry)
-#Bind rows
-bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology,Flower_symmetry)
-############################################################################################################################################
-#t$Autonomous_selfing_level <- as.character(t$Autonomous_selfing_level)
-#t$Autonomous_selfing_level[t$Autonomous_selfing_level =="none"] <- "None"
-#t$Autonomous_selfing_level[t$Autonomous_selfing_level =="low"] <- "Low"
-#t$Autonomous_selfing_level[t$Autonomous_selfing_level =="medium"] <- "Medium"
-#t$Autonomous_selfing_level[t$Autonomous_selfing_level =="high"] <- "High"
-#
-##Order levels
-#t$Autonomous_selfing_level <- factor(t$Autonomous_selfing_level, levels=c("High", "Medium", "Low", "None"))
-#
-#Selfing <- t %>%
-#  group_by(Clusters,Autonomous_selfing_level) %>%
-#  summarise (n = n()) %>%
-#  mutate(Percentage = n / sum(n)*100)
-#
-##delete column to convert to wide
-#Selfing <- Selfing[,-3]
-##convert to wide
-#Selfing <- spread(Selfing, Clusters, Percentage)
-##Set call name os categories per trait
-#colnames(Selfing)[1] <- "Category"
-##Create new column
-#Trait <- data.frame(Trait= c(rep("Selfing level", 2)))
-##Replace Na's with zeros
-#Selfing[is.na(Selfing)] <- 0
-##Add column
-#Selfing_1 <- cbind(Trait, Selfing)
-##Bind rows
-#bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology, Selfing_1)
-#
-#############################################################################################################################################
-t$Nectar_presence_absence <- as.character(t$Nectar_presence_absence)
-t$Nectar_presence_absence[t$Nectar_presence_absence =="yes"] <- "Yes"
-t$Nectar_presence_absence[t$Nectar_presence_absence =="no"] <- "No"
-
-Nectar <- t %>%
-  group_by(Clusters,Nectar_presence_absence) %>%
-  summarise (n = n()) %>%
-  mutate(Percentage = n / sum(n)*100)
-
-#delete column to convert to wide
-Nectar <- Nectar[,-3]
-#convert to wide
-Nectar <- spread(Nectar, Clusters, Percentage)
-#Set call name os categories per trait
-colnames(Nectar)[1] <- "Category"
-#Create new column
-Trait <- data.frame(Trait= c(rep("Nectar", 2)))
-#Replace Na's with zeros
-Nectar[is.na(Nectar)] <- 0
-#Add column
-Nectar <- cbind(Trait, Nectar)
-#Bind rows
-data <- bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span, Flower_symmetry, Nectar)
-
-#remove first col
-data_1 <- data[,-1]
-colnames(data_1) <- c("Category", "Cluster 1", "Cluster 2", "Cluster 3", "Cluster 4", "Cluster 5")
-
-#transpose dataframe
-data_2 <- as.data.frame(t(data_1))
-
-#rownames to colnames (1st one)
-data_3 <- data_2 %>% row_to_names(row_number = 1)
-
-#Convert all variables to numeric
-data_4 <- sapply(data_3, function(x) as.numeric(as.character(x)))
-
-#set back the missed rownames in the processing
-rownames(data_4) <- rownames(data_3)
-
-# Convert to dataframe
-data_4 <- as.data.frame(data_4)
-
-# Scale values and set rowname as column
-data_5 <-data_4 %>% rownames_to_column( var = "group" )
-
-data_6 <- melt(data_5)
-
-cluster1 <- subset(data_6, group=="Cluster 1")
-
-cluster1$traits <- c(rep("Breeding sys.",3), rep("Compatibility",3), rep("Life form",3),
-                     rep("Life span",2), rep("F. Symm.",2), rep("Nectar",2))
-
-#Try to achieve the desire output with plot_grid
-
-c1 <- cluster1 %>% 
-  ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("sandybrown"), labels="Group 1")+
-  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())+scale_y_continuous(expand = c(0,0)) +
-  theme(axis.title.x = element_blank(), axis.text.x=element_blank(),plot.title = element_text(size = 18))+ ylab("")+
-  ggtitle("A) Qualitative variables")
-
-cluster2 <- subset(data_6, group=="Cluster 2")
-
-cluster2$traits <- c(rep("Breeding system",3), rep("Compatibility",3), rep("Life form",3),
-                     rep("Life span",2), rep("Flower symmetry",2), rep("Nectar",2))
-
-c2 <- cluster2 %>% 
-  ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("#7BB0A3"), labels="Group 2")+
-  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())+scale_y_continuous(expand = c(0,0)) +
-  theme(strip.background = element_blank(), strip.text = element_blank())+
-  theme(axis.title.x = element_blank(), axis.text.x=element_blank())+ylab("")
-
-cluster3 <- subset(data_6, group=="Cluster 3")
-
-cluster3$traits <- c(rep("Breeding system",3), rep("Compatibility",3), rep("Life form",3),
-                     rep("Life span",2), rep("Flower symmetry",2), rep("Nectar",2))
-
-c3 <- cluster3 %>% 
-  ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("lightsteelblue2"), labels="Group 3")+
-  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())+scale_y_continuous(expand = c(0,0)) +
-  theme(axis.title.x = element_blank(), axis.text.x=element_blank())+
-  theme(strip.background = element_blank(), strip.text = element_blank())+ylab("Percentage")
-
-cluster4 <- subset(data_6, group=="Cluster 4")
-
-cluster4$traits <- c(rep("Breeding system",3), rep("Compatibility",3), rep("Life form",3),
-                     rep("Life span",2), rep("Flower symmetry",2), rep("Nectar",2))
-
-c4 <- cluster4 %>% 
-  ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("thistle"), labels="Group 4")+
-  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())+scale_y_continuous(expand = c(0,0)) +
-  theme(axis.title.x = element_blank(), axis.text.x=element_blank())+
-  theme(strip.background = element_blank(), strip.text = element_blank())+ylab("")
-
-cluster5 <- subset(data_6, group=="Cluster 5")
-
-cluster5$traits <- c(rep("Breeding syst.",3), rep("Compatibility",3), rep("Life form",3),
-                     rep("Life span",2), rep("F. Symm.",2), rep("Nectar",2))
-c5 <- cluster5 %>% 
-  ggplot(aes(x = variable,  y = value, fill = group))  +  
-  geom_col(position = "dodge") +   scale_fill_manual(name = NULL,values=c("lightgoldenrod2"), labels="Group 5")+
-  facet_grid(~traits, scales = "free_x", space = "free_x")+theme_bw()+
-  scale_y_continuous(expand = c(0,0)) +
-  theme(axis.text.x = element_text(angle = 45,vjust = 1, hjust=1))+
-  theme(strip.background = element_blank(), strip.text = element_blank())+ylab("")+xlab("")
-
-A <- c1 + c2 + c3 + c4 + c5 + plot_layout(ncol = 1)
-
-colnames(final_df_3) <- c("group","Autonomous selfing", "Flower number", "Flowers per \n inflorescence",
-                "Inflorescence \n width", "Flower length", "Style length", "Ovule number",
-                "Plant height")
-
-B <- ggradar(final_df_3, group.colours=c("sandybrown", "#7BB0A3","lightsteelblue2", "thistle", "lightgoldenrod2"),
-             legend.text.size=5, grid.label.size = 0,legend.position = "none",axis.label.size=3)+ 
-  guides(shape = guide_legend(override.aes = list(size = 0.75)))+ ggtitle("B) Quantitative variables")+
-  theme(plot.title = element_text(size = 18))
-
-patch <- A | B
-
-patch + plot_annotation(title = "Plant functional group composition",theme = theme(plot.title = element_text(size = 20,face="bold")))
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=13, fig.cap="**Figure S4.** Hierarchical clustering dendrogram with the branches coloured by the optimal number of clusters (5).
-The labels of the subgroup of species (N = 524) used in this study are coloured in black in order to show the evenness of the distribution of the species across clusters.
-The rest of species labels are omitted for visualization purposes (N = 982)."}
-
-library(ggplot2)
-library(dendextend)
-library(dplyr)
-
-e.clust_5 <- readRDS("../Data/RData/e.clust_5.rds")
-
-dendro <- as.dendrogram(e.clust_5)
-dendro.col <- dendro %>%
-  set("branches_k_color", k = 5, value =   c("lightsteelblue2", "thistle", "sandybrown", "#7BB0A3", "lightgoldenrod2")) %>%
-  set("branches_lwd", 0.7) %>%
-  set("labels_colors", 
-      value = c("darkslategray")) %>% 
-  set("labels_cex", 0.075)
-
-labels_colors(dendro.col) <- get_leaves_branches_col(dendro.col)
-
-# We use "darkgrey" to color some species
-final_d_1 <- read.csv("../Data/Csv/data_for_motifs_analysis_1.csv")
-
-plant_species <- unique(final_d_1$Plant_species)
-
-index_species_out <- which(names(labels_colors(dendro.col)) %in% plant_species)
-
-'%ni%' <- Negate('%in%')
-
-index_species_in <- which(names(labels_colors(dendro.col)) %ni% plant_species)
-
-labels_colors(dendro.col)[index_species_out] <- "black"
-labels_colors(dendro.col)[index_species_in] <- "white"
-
-ggd1 <- as.ggdend(dendro.col)
-
-ggd1$labels$angle <- 90
-ggd1$labels$vjust <- 1
-ggd1$labels$hjust <- 1
-
-ggplot(ggd1,offset_labels=-0.05) + theme(panel.grid.major = element_blank(),
- axis.text = element_blank(),axis.title = element_blank()) +
-  ggtitle("Plant functional groups")+
-  theme(plot.title = element_text(hjust = 0.5, vjust = -2,size = 20,face="bold"))+
-  annotate("text", x=140, y=1.65, label= "Self-incomp. perennials with large flowers ", size=2.5)+
-  annotate("text", x=380, y=2.15, label= "Tall plants with small unisexual flowers", size=2.5) +
-  annotate("text", x=600, y=3.85, label= "Short-lived selfers", size=2.5) +
-  annotate("text", x=1400, y=2.05, label= "Short-lived outcrossers with \n long zygomorphic flowers", size=2.5) +annotate("text", x=950, y=2.05, label= "Small outcrossing perennials", size=2.5)
-
-```
-
-\elandscape

### 2022-03-08 Scripts/Indirect_direct_plants.R

@@ -1,0 +1,92 @@
+library(ggplot2)
+library(scatterpie)
+library(RColorBrewer)
+library(tidyverse)
+
+
+direct_indirect <- read_csv("Data/Data_processing/Motifs_connections/motif_interactions.csv")
+colnames(direct_indirect)
+direct_indirect <- direct_indirect %>% select(motif_id,position,direct_interactions, indirect_interactions,ind_same_type_over_directed_int)
+
+plant_means_reordered <- read_csv("Data/Csv/plant_abs_freq_means.csv")
+
+#Check pol levels
+levels(factor(plant_means_reordered$Node_FG))
+
+
+#Dplyr merge
+joined_tibble <- left_join(direct_indirect, plant_means_reordered)
+
+#1 Selfing herbs
+one <- joined_tibble %>% filter(Node_FG=="1")
+one$ind_same_type_over_directed_int <- round(one$ind_same_type_over_directed_int, digits = 1)
+#Convert to factor
+one$position <- as.factor(one$position)
+one$ind_same_type_over_directed_int <- as.factor(one$ind_same_type_over_directed_int)
+one_plot <- ggplot(one,aes(position,mean_natural_units))+
+  geom_col(position = "dodge")+
+  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Selfing herbs")+
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())+
+  ylab("Frequency")
+
+#2 Small outcrossing perennials
+two <- joined_tibble %>% filter(Node_FG=="2")
+two$ind_same_type_over_directed_int <- round(two$ind_same_type_over_directed_int, digits = 1)
+#Convert to factor
+two$position <- as.factor(two$position)
+two$ind_same_type_over_directed_int <- as.factor(two$ind_same_type_over_directed_int)
+two_plot <- ggplot(two,aes(position,mean_natural_units))+
+  geom_col(position = "dodge")+
+  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Small outcrossing perennials")+
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())+
+  ylab("Frequency")
+
+#3 Self-incomp. perennials with large flowers
+three <- joined_tibble %>% filter(Node_FG=="3")
[…]

### 2022-03-08 Scripts/Indirect_interactions_by_path_length.R

@@ -1,0 +1,42 @@
+
+#Visualize indirect interactions of motif classes by path length 
+library(ggplot2)
+library(scatterpie)
+library(RColorBrewer)
+library(tidyverse)
+
+
+direct_indirect <- read_csv("Data/Data_processing/Motifs_connections/motif_interactions.csv")
+colnames(direct_indirect)
+direct_indirect <- direct_indirect %>% select(motif_id,position,direct_interactions, indirect_interactions,ind_same_type_over_directed_int,type)
+
+
+#Add path length classification
+direct_indirect$Broad_categories <- NA
+direct_indirect$Broad_categories[direct_indirect$motif_id==2 | direct_indirect$motif_id==7 | 
+                                   direct_indirect$motif_id==17 | direct_indirect$motif_id==3 | 
+                                   direct_indirect$motif_id==4 | direct_indirect$motif_id==8] <- "Fan" 
+
+direct_indirect$Broad_categories[direct_indirect$motif_id==15 | direct_indirect$motif_id==11] <- "Medium-weak" 
+
+direct_indirect$Broad_categories[direct_indirect$motif_id==6 | direct_indirect$motif_id==16 | 
+                                   direct_indirect$motif_id==12] <- "Strong" 
+
+direct_indirect$Broad_categories[direct_indirect$motif_id==5 | direct_indirect$motif_id==9 |  direct_indirect$motif_id==14|  direct_indirect$motif_id==13|  direct_indirect$motif_id==10] <- "Weak" 
+
+
+#Filter motif 1 and convert to factor
+colnames(direct_indirect)
+direct_indirect$Broad_categories <- factor(direct_indirect$Broad_categories, levels=c("Strong", "Fan", "Medium-weak", "Weak"))
+direct_indirect <- direct_indirect %>% filter(!motif_id==1)
+
+#Convert to factor
+direct_indirect$position <- as.factor(direct_indirect$position)
+direct_indirect$motif_id <- as.factor(direct_indirect$motif_id)
+
+direct_indirect$ind_same_type_over_directed_int <- as.factor(direct_indirect$ind_same_type_over_directed_int)
+ ggplot(direct_indirect %>% filter(type == "pollinator"),aes(motif_id,indirect_interactions))+
+  geom_col(position = "dodge")+
+  facet_grid(.~Broad_categories,scale='free_x', space = "free_x") + ggtitle("Pollinator")+
+  ylab("Number of indirect interactions") + xlab("Motif number")
+

### 2022-03-08 Scripts/Scripts_Alfonso/plot_motif_positionsV2.R

@@ -19,7 +19,7 @@ equidistribution <- function(number_nodes){
 
 plot_motif_positions <- function(motif_number){
   
-  motifs_raw_data <- read_csv("../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
+  motifs_raw_data <- read_csv("../../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
   
   motif_data <- motifs_raw_data %>% filter(motif_id == motif_number)
   

### 2022-03-08 Scripts/Z-score_percentile_histogram_plot.R

@@ -4,7 +4,7 @@ library(dplyr)
 library(ggplot2)
 library(tidyverse)
 #Read data
-data <- read.csv("../Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
+data <- read.csv("../../Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
 
 #Check NA's per column
 #data %>%

### 2022-03-09 Manuscript/Main_text/Main_text_Oikos.Rmd
updates on main text

@@
 
-Second, floral visitors were grouped into taxonomic groups based on taxonomic rank as done similarly in past plant-pollinator studies [@fenster2004; @ollerton2009].
+Second, floral visitors were grouped into taxonomic groups based on taxonomic rank as done similarly in other plant-pollinator studies [@fenster2004; @ollerton2009].
 We opted to divide floral visitors on the taxonomic rank level and not with functional traits because the main orders of floral visitors differed in form and behaviour and had lower superior taxonomical complexity (i.e., floral visitors had 6 orders versus plants that had 38).
@@
 More restricted null models with also degree as constant were also explored but did not allowed sufficient permutations given that many constraints and provided highly similar or identical networks to the original ones.
+We discarded null models with more constraints (e.g., degree also constant) because they did not allow sufficient permutations and provided highly similar or identical networks to the original ones.
 
@@
 We calculated which plant and floral visitor groups were over- or under-represented in the different motif positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
-To estimate the position frequencies of each group in a given network, we added the frequencies of those species that belong to the group, and then, we normalised the resulting frequencies by dividing the position measure for each group by the total number of times that a group appears in any position within the same motif size class.
+To estimate the position frequencies of each plant and floral visitor group in a given network, we added the frequencies of those species that belong to the group, and then, we normalised the resulting frequencies by dividing the position measure for each group by the total number of times that a group appears in any position within the same motif size class.
 Then, we calculated the percentile of the observed position frequencies for each group and network, just like we did with motif frequencies.
@@
 
-To understand if the different plant and floral visitor groups are associated with motif positions that involve different network roles (e.g., specialization or generalism), we calculated the specificity of the different motif positions and evaluated its association through linear models with the average frequency of the different plant and floral visitor groups as response variable.
+To understand if the different plant and floral visitor groups are associated with motif positions that involve different network roles (e.g., specialization or generalism and number of indirect interactions).
+First, we calculated the specificity of the different motif positions and evaluated its association through linear models with the average frequency of the different plant and floral visitor groups as response variable.
 For this, we previously calculated the specificity ($s_i$) of each motif position following @poisot2015 as $s_i = L - l_i / L - 1$, where $L$ is the total number of groups and $l_i$ the number of interaction partners of the group $i$ in a given motif.
 Values of the vector s, range between 1, complete specialization (1 partner within the motif) and 0, complete generalism (all possible partners within the motif).
+Second, for each motif position we determined the proportion of indirect-direct interactions, considering indirect interactions exclusively as the mediated effect between two species by a third species.
+Therefore, we account exclusively for the indirect interactions of floral visitors through plants (e.g., floral visitor - plant - floral visitor) and the indirect interactions of plants through floral visitors (e.g., plant - floral visitor - plant).
 

### 2022-03-09 Manuscript/Main_text/Main_text_Oikos.Rmd
edits on main text

@@
 
+For both floral visitor and plant groups we found different frequencies on motif positions that implied different ecological roles.
+First, for floral visitors we found that bees had a tendency to appear with higher frequency on motif position that involved generalism while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) showed the opposite trend with higher frequency on motif positions that implied greater level of specialization (**Figure S2 A**).
+All plant functional groups showed a slight tendency for generalism (**Figure S2 B**).
+Second, regarding the number of indirect interactions, bees and tall plants with unisexual flowers showed greater frequency on motif positions that had low number of indirect interactions but high of direct interactions (**Figure S3 and Figure S4**).
+The rest of floral visitor groups showed the opposite tendency and had higher frequencies on motif positions with high number of indirect interactions but low of direct interactions (**Figure S3**).
+The rest of plant groups did not show major differences on their frequencies on motifs that implied different proportion of indirect-direct interactions (**Figure S4**).
+
 ```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure 2.** Comparison of motif frequencies between empirical and simulated networks grouped by average path length (plots a, b, c and d) as determined in Simmons et al.

### 2022-03-09 Manuscript/Supplementary_Material/Indirect_direct_plants.Rmd
edits on main text

@@
   title = 'Proportion indirect/direct interactions (0, 0.3, 0.5, 1, 2, 3)',
-  theme = theme(plot.title = element_text(size = 18, face="bold")))
+  theme = theme(plot.title = element_text(size = 18, face="bold"))) & theme_bw()
 

### 2022-03-09 Manuscript/Supplementary_Material/Indirect_direct_pollinators.Rmd
edits on main text

@@
 
-direct_indirect <- read_csv("../Data/Data_processing/Motifs_connections/motif_interactions.csv")
+direct_indirect <- read_csv("../../Data/Data_processing/Motifs_connections/motif_interactions.csv")
 direct_indirect <- direct_indirect %>% select(motif_id,position,direct_interactions, indirect_interactions,ind_same_type_over_directed_int)
 
-pollinator_means_reordered <- read_csv("../Data/Csv/pollinator_abs_freq_means.csv")
+pollinator_means_reordered <- read_csv("../../Data/Csv/pollinator_abs_freq_means.csv")
 #Filter out in order to have just 6 FG'S

### 2022-03-09 Manuscript/Supplementary_Material/Supporting_information_Oikos.Rmd
edits on main text

@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="\\textbf{Figure S2.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions after removing non-robust links (singletones).
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=12, fig.width=12, fig.align = 'center', fig.cap="\\textbf{Figure S2.}"}
+
+library(ggplot2)
+library(patchwork)
+
+pollinator_means_reordered_s_1 <- read.csv("../../Data/Csv/pollinator_means_reordered_s_1.csv")
+
+plant_means_s <- read.csv("../../Data/Csv/plant_means_s.csv")
+
+p1 <- ggplot(pollinator_means_reordered_s_1,aes(x=s,y=mean))+
+  geom_point(alpha=0.5, color="black")+
+  geom_smooth(method = "lm",color="black")+
+  facet_wrap(~Node_FG)+
+  labs(x="Specificty",y="Average frequency per motif position") +
+  theme_bw() + ggtitle("Floral visitors") +
+  theme(plot.title = element_text(hjust = 0.5, size = 25),
+        axis.text=element_text(size=12),
+        axis.title=element_text(size=18),
+        strip.text = element_text(size=20))
+
+p2 <- ggplot(plant_means_s,aes(x=s,y=mean))+
+  geom_point(alpha=0.5, color="black")+
+  geom_smooth(method = "lm", color="black")+
+  facet_wrap(~Node_FG)+
+  labs(x="Specificty",y="Average frequency per motif position")+
+  theme_bw() + ggtitle("Plants") +
+  theme(plot.title = element_text(hjust = 0.5, size = 25),
+        axis.text=element_text(size=12),
+        axis.title=element_text(size=18),
+        strip.text = element_text(size=20))
+
+p1/p2 +  plot_annotation(tag_levels = c('A'),  tag_suffix = ')') &  theme(plot.tag = element_text(size = 22))
+
+```
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S3.}"}
+
+library(ggplot2)
+library(scatterpie)
+library(RColorBrewer)
+library(tidyverse)
+
+direct_indirect <- read_csv("../../Data/Data_processing/Motifs_connections/motif_interactions.csv")
+direct_indirect <- direct_indirect %>% select(motif_id,position,direct_interactions, indirect_interactions,ind_same_type_over_directed_int)
+
+pollinator_means_reordered <- read_csv("../../Data/Csv/pollinator_abs_freq_means.csv")
+#Filter out in order to have just 6 FG'S
+pollinator_means_reordered <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds", "Lizards", "Other_insects"))
+
+#Dplyr merge
+joined_tibble <- left_join(direct_indirect, pollinator_means_reordered)
+
+#Bees
+bees <- joined_tibble %>% filter(Node_FG=="Bee")
+bees$ind_same_type_over_directed_int <- round(bees$ind_same_type_over_directed_int, digits = 1)
+#Convert to factor
+bees$position <- as.factor(bees$position)
+bees$ind_same_type_over_directed_int <- as.factor(bees$ind_same_type_over_directed_int)
+bee_plot <- ggplot(bees,aes(position,mean_natural_units))+
+  geom_col(position = "dodge")+
+  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Bees")+
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())+
+  ylab("Frequency")+theme_bw() + xlab("")
+
+#Coleoptera
+cole <- joined_tibble %>% filter(Node_FG=="Coleoptera")
+cole$ind_same_type_over_directed_int <- round(cole$ind_same_type_over_directed_int, digits = 1)
+#Convert to factor
+cole$position <- as.factor(cole$position)
+cole$ind_same_type_over_directed_int <- as.factor(cole$ind_same_type_over_directed_int)
+cole_plot <- ggplot(cole,aes(position,mean_natural_units))+
+  geom_col(position = "dodge")+
+  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Coleoptera")+
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())+
+  ylab("Frequency")+theme_bw() + xlab("")
+
+#Lepidoptera
+lepi <- joined_tibble %>% filter(Node_FG=="Lepidoptera")
+lepi$ind_same_type_over_directed_int <- round(lepi$ind_same_type_over_directed_int, digits = 1)
+#Convert to factor
+lepi$position <- as.factor(lepi$position)
+lepi$ind_same_type_over_directed_int <- as.factor(lepi$ind_same_type_over_directed_int)
+lepi_plot <- ggplot(lepi,aes(position,mean_natural_units))+
+  geom_col(position = "dodge")+
+  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Lepidoptera") +
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())+
+  ylab("Frequency")+theme_bw()+ xlab("")
+
+#Non-bee-Hymenoptera
+non_bee <- joined_tibble %>% filter(Node_FG=="Non-bee-Hymenoptera")
+non_bee$ind_same_type_over_directed_int <- round(non_bee$ind_same_type_over_directed_int, digits = 2)
+#Convert to factor
+non_bee$position <- as.factor(non_bee$position)
+non_bee$ind_same_type_over_directed_int <- as.factor(non_bee$ind_same_type_over_directed_int)
+non_bee_plot <- ggplot(non_bee,aes(position,mean_natural_units))+
+  geom_col(position = "dodge")+
+  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Non-bee-Hymenoptera") +
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())+
+  ylab("Frequency")+theme_bw()+ xlab("")
+
+#Non-syrphids-diptera
+non_syr <- joined_tibble %>% filter(Node_FG=="Non-syrphids-diptera")
+non_syr$ind_same_type_over_directed_int <- round(non_syr$ind_same_type_over_directed_int, digits = 1)
+#Convert to factor
+non_syr$position <- as.factor(non_syr$position)
+non_syr$ind_same_type_over_directed_int <- as.factor(non_syr$ind_same_type_over_directed_int)
+non_syr_plot <- ggplot(non_syr,aes(position,mean_natural_units))+
+  geom_col(position = "dodge")+
+  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Non-syrphids-diptera")+
+theme(axis.title.x=element_blank(),
+      axis.text.x=element_blank(),
+      axis.ticks.x=element_blank())+
+  ylab("Frequency")+theme_bw()+ xlab("")
+
+#Syrphids
+syr <- joined_tibble %>% filter(Node_FG=="Syrphids")
+syr$ind_same_type_over_directed_int <- round(syr$ind_same_type_over_directed_int, digits = 1)
+#Convert to factor
+syr$position <- as.factor(syr$position)
+syr$ind_same_type_over_directed_int <- as.factor(syr$ind_same_type_over_directed_int)
+syr_plot <- ggplot(syr,aes(position,mean_natural_units))+
+  geom_col(position = "dodge")+
+  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Syrphids") +
+   ylab("Frequency")+theme_bw() + xlab("Motif position")
+
+library(patchwork)
+bee_plot / cole_plot / lepi_plot / non_bee_plot / non_syr_plot / syr_plot + plot_annotation(title= 'Floral visitors',
+  subtitle = 'Proportion indirect/direct interactions (0, 0.3, 0.5, 1, 2, 3)',
+  theme = theme(plot.title = element_text(size = 18, face="bold"),plot.subtitle = element_text(size = 18, face="bold")))
+
+```
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S4.}"}
+
+library(ggplot2)
+library(scatterpie)
+library(RColorBrewer)
+library(tidyverse)
+
+direct_indirect <- read_csv("../../Data/Data_processing/Motifs_connections/motif_interactions.csv")
+direct_indirect <- direct_indirect %>% select(motif_id,position,direct_interactions, indirect_interactions,ind_same_type_over_directed_int)
+
+plant_means_reordered <- read_csv("../../Data/Csv/plant_abs_freq_means.csv")
+
+#Dplyr merge
+joined_tibble <- left_join(direct_indirect, plant_means_reordered)
+
+#1 Selfing herbs
+one <- joined_tibble %>% filter(Node_FG=="1")
+one$ind_same_type_over_directed_int <- round(one$ind_same_type_over_directed_int, digits = 1)
+#Convert to factor
+one$position <- as.factor(one$position)
+one$ind_same_type_over_directed_int <- as.factor(one$ind_same_type_over_directed_int)
+one_plot <- ggplot(one,aes(position,mean_natural_units))+
+  geom_col(position = "dodge")+
+  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Selfing herbs")+
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())+
+  ylab("Frequency")+ xlab("") + theme_bw()
+
+#2 Small outcrossing perennials
+two <- joined_tibble %>% filter(Node_FG=="2")
+two$ind_same_type_over_directed_int <- round(two$ind_same_type_over_directed_int, digits = 1)
+#Convert to factor
+two$position <- as.factor(two$position)
+two$ind_same_type_over_directed_int <- as.factor(two$ind_same_type_over_directed_int)
+two_plot <- ggplot(two,aes(position,mean_natural_units))+
+  geom_col(position = "dodge")+
+  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Small outcrossing perennials")+
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())+
+  ylab("Frequency")+ xlab("") + theme_bw()
+
+#3 Self-incomp. perennials with large flowers
+three <- joined_tibble %>% filter(Node_FG=="3")
+three$ind_same_type_over_directed_int <- round(three$ind_same_type_over_directed_int, digits = 1)
+#Convert to factor
+three$position <- as.factor(three$position)
+three$ind_same_type_over_directed_int <- as.factor(three$ind_same_type_over_directed_int)
+three_plot <- ggplot(three,aes(position,mean_natural_units))+
+  geom_col(position = "dodge")+
+  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Self-incomp. perennials with large flowers") +
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())+
+  ylab("Frequency")+ xlab("") + theme_bw()
+
+#4 Tall plants with small unisexual flowers
+four <- joined_tibble %>% filter(Node_FG=="4")
+four$ind_same_type_over_directed_int <- round(four$ind_same_type_over_directed_int, digits = 2)
+#Convert to factor
+four$position <- as.factor(four$position)
+four$ind_same_type_over_directed_int <- as.factor(four$ind_same_type_over_directed_int)
+four_plot <- ggplot(four,aes(position,mean_natural_units))+
+  geom_col(position = "dodge")+
+  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Tall plants with small unisexual flowers") +
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())+
+  ylab("Frequency")+ xlab("") + theme_bw()
+
+#5 Short-lived outcrossers with long zygomorphic flowers
+five <- joined_tibble %>% filter(Node_FG=="5")
+five$ind_same_type_over_directed_int <- round(five$ind_same_type_over_directed_int, digits = 1)
+#Convert to factor
+five$position <- as.factor(five$position)
+five$ind_same_type_over_directed_int <- as.factor(five$ind_same_type_over_directed_int)
+five_plot <- ggplot(five,aes(position,mean_natural_units))+
+  geom_col(position = "dodge")+
+  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Short-lived outcrossers with long zygomorphic flowers")+
+  ylab("Frequency") + xlab("Motif position") + theme_bw()
+
+library(patchwork)
+one_plot / two_plot / three_plot / four_plot / five_plot + plot_annotation(title= 'Plants', subtitle = 'Proportion indirect/direct interactions (0, 0.3, 0.5, 1, 2, 3)',
+  theme = theme(plot.title = element_text(size = 18, face="bold"),plot.subtitle = element_text(size = 18, face="bold")))
+
+```
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="\\textbf{Figure S5.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions after removing non-robust links (singletones).
 The different motif positions are dividied by the average path length clasification by Simmons et al.
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=7, fig.width=12, fig.cap="**Figure S3.** Plant functional group composition separated in qualitative and quantitative variables.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=7, fig.width=12, fig.cap="**Figure S6.** Plant functional group composition separated in qualitative and quantitative variables.
 Panel A) shows the percentage of the different categories within trait represented with different colours for each functional group.
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=13, fig.cap="**Figure S4.** Hierarchical clustering dendrogram with the branches coloured by the optimal number of clusters (5).
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=13, fig.cap="**Figure S7.** Hierarchical clustering dendrogram with the branches coloured by the optimal number of clusters (5).
 The labels of the subgroup of species (N = 524) used in this study are coloured in black in order to show the evenness of the distribution of the species across clusters.

### 2022-03-09 Manuscript/Supplementary_Material/specificity_VS_position_frequencies.Rmd
edits on main text

@@
   facet_wrap(~Node_FG)+
-  labs(x="Specificty",y="Average frequency per position") +
+  labs(x="Specificty",y="Average frequency per motif position") +
   theme_bw() + ggtitle("Floral visitors") +
@@
   facet_wrap(~Node_FG)+
-  labs(x="Specificty",y="Average frequency per position")+
+  labs(x="Specificty",y="Average frequency per motif position")+
   theme_bw() + ggtitle("Plants") +
@@
 
-p1/p2
+p1/p2 +  plot_annotation(tag_levels = c('A'),  tag_suffix = ')') &  theme(plot.tag = element_text(size = 22))
 

### 2022-03-09 Manuscript/Main_text/Main_text_Oikos.Rmd
read again tomorrow but is looking good

@@
 All plant functional groups showed a slight tendency for generalism (**Figure S2 B**).
-Second, regarding the number of indirect interactions, bees and tall plants with unisexual flowers showed greater frequency on motif positions that had low number of indirect interactions but high of direct interactions (**Figure S3 and Figure S4**).
+Second, regarding the number of indirect interactions, bees and tall plants with unisexual flowers showed greater frequency on motif positions that had low number of indirect interactions but high number of direct interactions (**Figure S3 and Figure S4**).
 The rest of floral visitor groups showed the opposite tendency and had higher frequencies on motif positions with high number of indirect interactions but low of direct interactions (**Figure S3**).
@@
 We have explored for the first time the overall structure and representation of network motifs in real plant-pollinator networks and shown that the different motifs up to five nodes are consistently over- and under-represented in comparison with simulated networks indicating the presence of ecological processes shaping their structure.
-Despite the presence of multiple ecological processes likely operating at the same time (e.g., neutral effects, morphological matching or phenological overlap), we found a tendency for over-represented structures with more densely connected motifs (i.e., complete, fan and asymmetric complete) suggesting that neutral effects are likely the predominant processes governing the structure of these network motifs [@simmons2020].
+Despite the presence of multiple ecological processes likely operating at the same time (e.g., neutral effects, morphological matching or phenological overlap), we found a tendency for over-represented structures with more densely connected motifs (i.e., complete, fan and asymmetric complete).
+As suggested in @simmons2020, a higher proportion of more densely connected motifs could reflect that neutral effects are the predominant ecological process governing the structure of these network motifs.
 Thus, as indicated for other network properties like nestedness [@krishna2008; @suweis2013], species relative abundances (i.e., neutral effects) are possibly one of the main determinants of indirect interactions in real plant-pollinator networks.
 
-From a pollinator perspective, we found that generalist network motifs were consistently over-represented (e.g.
+Overall, generalist network motifs for floral visitors were consistently over-represented (e.g.
 fan-type motifs; **Figure 2**).
-For instance, when we compare motifs with equal structure for both trophic levels, we found that floral visitors had always over-representation in the positions that implied the highest number of links.
-Despite this is in good agreement with the current view of the generalist tendency of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of the generalist network motifs was largely driven by the functional group of bees (e.g., positions 42, 46, 16, 4, 14 and 35 in motifs 15, 17, 7, 2, 6 and 13, respectively; see **Figure 3** for positions and **Figure 4** for motifs) while the rest of the functional groups tended to be under-represented in these generalist motifs and over-represented in motif positions with specialist roles (e.g., positions 11, 21, 28 and 34 in motifs 5, 9, 11 and 13, respectively; see **Figure 3** for positions and **Figure 4** for motifs).
-This large effect of bees on the overall patterns is no surprise, as bees were the functional group with largest number of interaction records in the whole set of networks as also recorded for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017].
+For instance, when we compare motifs with equal structure for both trophic levels, we found that floral visitors had always over-representation in the positions that implied the highest number of direct links.
+Despite this is in good agreement with the current view of the generalist tendency of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of the generalist network motifs was only driven by the taxonomic group of bees (**Figure S2**) while the rest of the taxonomic groups tended to be under-represented in these motif that involved generalism and over-represented in motif positions with specialist roles.
+This large effect of bees on the overall patterns is no surprise, as bees were the group with largest number of interaction records in the whole set of networks as also recorded for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017].
+Interestingly, bees also were the group with lower number of indirect interactions while the rest of floral visitor groups showed clearly higher number of indirect interactions indicating that these groups may experience higher levels of competitive interactions due to greater overlap of floral resources [@thomson2020].
 Unlike floral visitors, plant functional groups showed little differences on its appearance in different motif positions, and thus similar probability of appearing on all of them.
-If anything, the groups that involved higher levels of outcrossing showed a tendency to be more over-represented and probable on different motif positions.
-For instance, the group of self-incompatible perennials with large flowers, one of the groups that is expected to have higher levels of outcrossing rate [@goodwillie2010], showed the highest over-representation of all plant functional groups (**Figure 3**); and the group of tall plants with unisexual flowers, the one that is expected to have the highest dependence of pollinators on reproduction [@rodger2021], was the most probable on the generalist motif for plant positions (i.e., plant nodes with 3 to 4 links; **Figure 4**).
+However, the groups that involved higher levels of outcrossing showed a tendency to be more over-represented and probable on the different motif positions.
+Remarkably, the group of tall plants with unisexual flowers, the one that is expected to have the highest dependence of pollinators on reproduction [@rodger2021], showed the lowest level of indirect interactions but the highest frequency of records for all groups which involves a high number of direct interactions that are likely to minimise negative impacts of pollinator sharing (e.g., heterospecific pollen arrival).
 
 The probabilities of appearance of each functional group on the different motif positions were insufficient to predict most of the observed network position combinations (**Figure 5**).
-This implies that not just the representation of network motifs types but also the identity of the elements of their structure is influenced by ecological processes that determine under- and over-representation of the different position combinations.
-In addition, we found that just 30$\%$ of the possible 53,250 motif combinations are realized.
-Thus, similarly to the presence of forbidden links at the network level [@olesen2011; @jordano2016], we also found the existence of forbidden motif positions and those represented almost two thirds of the total posible combinations of indirect interactions.
+This implies that not just the representation of network motifs types but also the identity of the elements of their structure is non-random.
+Notably, we found that just 30$\%$ of the possible 53,250 motif combinations are realized.
+Thus, similarly to the presence of forbidden links at the network level [@olesen2011; @jordano2016], we also found the existence of forbidden motif positions and those represented almost two thirds of the total possible combinations of indirect interactions.
 This concurs well with the general idea that plant-pollinator networks have a high proportion of non-realized direct interactions [@jordano2003; @bascompte2013], and as a result, also a high proportion of non-realized combinations of indirect interactions.
@@
 
+**REWRITE**
+
 In conclusion, by following the framework of @simmons2020 we have been able to explore competitive and facilitative interactions in plant-pollinator networks worldwide and found that indirect interactions are non-random and are more strongly related to neutral processes than any other ecological process.

### 2022-03-09 Manuscript/Supplementary_Material/Supporting_information_Oikos.Rmd
read again tomorrow but is looking good

@@
 
-**Figure S2** Over and under-estimated functional groups on motif positions.
-
-**Figure S3** Plant trait composition of functional groups.
-
-**Figure S4** Plant dendrogram with functional groups.
+**Figure S2** Association between the frequency and specificity of the different groups on motif positions.
+
+**Figure S3** Frequency of floral visitor groups and proportion of indirect-direct interactions.
+
+**Figure S4** Frequency of plant groups per motif and proportion of indirect-direct interactions.
+
+**Figure S5** Over and under-estimated groups on motif positions.
+
+**Figure S6** Plant trait composition of functional groups.
+
+**Figure S7** Dendrogram with plant functional groups.
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=12, fig.width=12, fig.align = 'center', fig.cap="\\textbf{Figure S2.}"}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=12, fig.width=12, fig.align = 'center', fig.cap="\\textbf{Figure S2.} Association between the frequency and specificity on the different motif positions for floral visitor (panel A) and plant (panel B) groups.
+The different numerical categories of the plant groups correspond to: 1 (selfing herbs), 2 (small outcrossing perennials), 3 (self-incompatible perennials with large flowers), 4 (tall plants with small unisexual flowers) and 5 (short-lived outcrossers with long zygomorphic flowers)."}
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S3.}"}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S3.} Frequency of the different floral visitor groups on the different motif positions aggregated by the proportion of indirect-direct interactions for the different motif positions."}
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S4.}"}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S4.} Frequency of the different plant groups on the different motif positions aggregated by the proportion of indirect-direct interactions for the different motif positions."}
 

### 2022-03-10 Manuscript/Main_text/Main_text_Oikos.Rmd
keep tomorrow

@@
 Floral visitor groups were divided by the main taxonomic groups that differed in life form and behaviour.
-Once we split the different plant-pollinator networks into their motif elements, we explored: (i) if there is a common invariant structural property in the overall motif networks (i.e.
-over- and under-represented motifs); (ii) which plant and floral visitor groups are over- and under-represented in the different motif positions; and, (iii) if there are over- and under-represented plant and floral visitor group combinations within a motif.
+Once we split the different plant-pollinator networks into their motif elements, we explored: (i) if there is a common invariant structural property in the overall motif networks (i.e., over- and under-represented motifs); (ii) which plant and floral visitor groups are over- and under-represented in the different motif positions and how these possible differences are associated with different ecological roles; and, (iii) if there are over- and under-represented plant and floral visitor group combinations within a motif.
 
@@
 Generated networks had the same number of plants and floral visitors, as well as the same connectance of their corresponding empirical networks.
-More restricted null models with also degree as constant were also explored but did not allowed sufficient permutations given that many constraints and provided highly similar or identical networks to the original ones.
 We discarded null models with more constraints (e.g., degree also constant) because they did not allow sufficient permutations and provided highly similar or identical networks to the original ones.
-
 After extracting the motif frequencies from the simulated networks, for each motif type and empirical network, we calculated the percentage of simulated networks whose frequencies were smaller than the ones observed, that is, we estimated the percentile of the observed motif frequencies.
@@
 Second, for each motif position we determined the proportion of indirect-direct interactions, considering indirect interactions exclusively as the mediated effect between two species by a third species.
-Therefore, we account exclusively for the indirect interactions of floral visitors through plants (e.g., floral visitor - plant - floral visitor) and the indirect interactions of plants through floral visitors (e.g., plant - floral visitor - plant).
+Therefore, we account exclusively for the indirect interactions of floral visitors via shared plants (e.g., floral visitor - plant - floral visitor) and the indirect interactions of plants through shared floral visitors (e.g., plant - floral visitor - plant).
 
@@
 For both floral visitor and plant groups we found different frequencies on motif positions that implied different ecological roles.
-First, for floral visitors we found that bees had a tendency to appear with higher frequency on motif position that involved generalism while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) showed the opposite trend with higher frequency on motif positions that implied greater level of specialization (**Figure S2 A**).
-All plant functional groups showed a slight tendency for generalism (**Figure S2 B**).
-Second, regarding the number of indirect interactions, bees and tall plants with unisexual flowers showed greater frequency on motif positions that had low number of indirect interactions but high number of direct interactions (**Figure S3 and Figure S4**).
-The rest of floral visitor groups showed the opposite tendency and had higher frequencies on motif positions with high number of indirect interactions but low of direct interactions (**Figure S3**).
+First, for floral visitors, we found that bees had a tendency to appear with higher frequency on motif positions that involved generalism while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) showed the opposite trend with higher frequency on motif positions that implied a greater level of specialization (**Figure S2 A**).
+Although plants did not have marked trends as floral visitors, all plant groups showed a slight tendency for generalism (**Figure S2 B**).
+Second, regarding the number of indirect interactions, bees and tall plants with unisexual flowers showed greater frequency on motif positions that involve low number of indirect interactions but high number of direct interactions (**Figure S3 and Figure S4**).
+The rest of floral visitor groups showed the opposite tendency and had higher frequencies on motif positions with high number of indirect interactions but low number of direct interactions (**Figure S3**).
 The rest of plant groups did not show major differences on their frequencies on motifs that implied different proportion of indirect-direct interactions (**Figure S4**).
@@
 As suggested in @simmons2020, a higher proportion of more densely connected motifs could reflect that neutral effects are the predominant ecological process governing the structure of these network motifs.
-Thus, as indicated for other network properties like nestedness [@krishna2008; @suweis2013], species relative abundances (i.e., neutral effects) are possibly one of the main determinants of indirect interactions in real plant-pollinator networks.
+Thus, as indicated for other network properties like nestedness [@krishna2008; @suweis2013], species relative abundances (i.e., neutral effects) may be the predominant ecological process governing the structure at the meso-scale on plant-pollinator networks.
 
@@
 For instance, when we compare motifs with equal structure for both trophic levels, we found that floral visitors had always over-representation in the positions that implied the highest number of direct links.
-Despite this is in good agreement with the current view of the generalist tendency of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of the generalist network motifs was only driven by the taxonomic group of bees (**Figure S2**) while the rest of the taxonomic groups tended to be under-represented in these motif that involved generalism and over-represented in motif positions with specialist roles.
-This large effect of bees on the overall patterns is no surprise, as bees were the group with largest number of interaction records in the whole set of networks as also recorded for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017].
-Interestingly, bees also were the group with lower number of indirect interactions while the rest of floral visitor groups showed clearly higher number of indirect interactions indicating that these groups may experience higher levels of competitive interactions due to greater overlap of floral resources [@thomson2020].
-Unlike floral visitors, plant functional groups showed little differences on its appearance in different motif positions, and thus similar probability of appearing on all of them.
-However, the groups that involved higher levels of outcrossing showed a tendency to be more over-represented and probable on the different motif positions.
-Remarkably, the group of tall plants with unisexual flowers, the one that is expected to have the highest dependence of pollinators on reproduction [@rodger2021], showed the lowest level of indirect interactions but the highest frequency of records for all groups which involves a high number of direct interactions that are likely to minimise negative impacts of pollinator sharing (e.g., heterospecific pollen arrival).
+Despite this is in good agreement with the current view of the generalist tendency of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of the generalist network motifs was only driven by the taxonomic group of bees (**Figure S2**) while the rest of the taxonomic groups tended to be under-represented in these motif positions that involved generalism but were over-represented in motif positions associated with specialist roles.
+This large effect of bees on the overall patterns is no surprise, as bees were the group with the largest number of interaction records in the whole set of networks as also recorded for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017].
+Interestingly, bees also were the group with lower number of indirect interactions while the rest of floral visitor groups showed clearly higher number of indirect interactions indicating that these different floral visitor groups may experience higher competitive interactions for floral resources [@thomson2020].
+Unlike floral visitors, plant functional groups showed little differences on their frequencies on the different motif positions, and thus similar probability of appearing on all of them.
+However, the plant groups with greater pollinator dependency which are expected to have the higher number of interactions with floral visitors [@lanuza2021] showed a tendency to be more over-represented and probable on motif positions that involved more specialization.
+Notably, just tall plants with small unisexual flowers showed low number of indirect interactions with possible important implications for the reproduction of this group (e.g., high fidelity visits with low foreign pollen transfer) while the rest of plant groups showed similar indirect interactions across motif positions.
 

### 2022-03-11 Manuscript/Main_text/Main_text_Oikos.Rmd
edits

@@
 Despite the presence of multiple ecological processes likely operating at the same time (e.g., neutral effects, morphological matching or phenological overlap), we found a tendency for over-represented structures with more densely connected motifs (i.e., complete, fan and asymmetric complete).
-As suggested in @simmons2020, a higher proportion of more densely connected motifs could reflect that neutral effects are the predominant ecological process governing the structure of these network motifs.
-Thus, as indicated for other network properties like nestedness [@krishna2008; @suweis2013], species relative abundances (i.e., neutral effects) may be the predominant ecological process governing the structure at the meso-scale on plant-pollinator networks.
+As suggested in @simmons2020, a higher proportion of these densely connected motifs could reflect that neutral effects are the predominant ecological process governing the structure of these network motifs.
+Thus, as indicated for other network properties like nestedness at the macro-scale level [@krishna2008; @suweis2013], species relative abundances (i.e., neutral effects) may be also the predominant ecological process governing the meso-scale structure on plant-pollinator networks.
 
@@
 This large effect of bees on the overall patterns is no surprise, as bees were the group with the largest number of interaction records in the whole set of networks as also recorded for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017].
-Interestingly, bees also were the group with lower number of indirect interactions while the rest of floral visitor groups showed clearly higher number of indirect interactions indicating that these different floral visitor groups may experience higher competitive interactions for floral resources [@thomson2020].
-Unlike floral visitors, plant functional groups showed little differences on their frequencies on the different motif positions, and thus similar probability of appearing on all of them.
-However, the plant groups with greater pollinator dependency which are expected to have the higher number of interactions with floral visitors [@lanuza2021] showed a tendency to be more over-represented and probable on motif positions that involved more specialization.
-Notably, just tall plants with small unisexual flowers showed low number of indirect interactions with possible important implications for the reproduction of this group (e.g., high fidelity visits with low foreign pollen transfer) while the rest of plant groups showed similar indirect interactions across motif positions.
+Interestingly, bees also were the group with lower number of indirect interactions while the rest of floral visitor groups showed clearly higher number of indirect interactions possibly indicating that these different floral visitor groups may experience higher competitive interactions for floral resources [@thomson2020].
+Despite plant functional groups showed little differences between them on their motif frequencies, all groups showed a tendency to be more represented on motif positions that were associated with higher levels of specialization.
+This tendency towards specialist roles may be the result of co-evolutionary processes (e.g., trait-matching) between plants and pollinators to optimise pollen transfer.
+Remarkably, just tall plants with small unisexual flowers showed higher frequencies on motifs that were associated with low number of indirect interactions with also possible direct implications on pollen transfer (e.g., high fidelity visits with low heterospecific pollen arrival).
 
@@
 
-**REWRITE**
-
 In conclusion, by following the framework of @simmons2020 we have been able to explore competitive and facilitative interactions in plant-pollinator networks worldwide and found that indirect interactions are non-random and are more strongly related to neutral processes than any other ecological process.
-Further, we found that motif combinations of functional groups are strongly constrained and that the distinct motif positions are associated with different functional groups with different ecological roles (e.g., generalization versus specialization).
+Further, we found that plant and floral visitor groups are associated with different motif positions that involve distinct ecological roles (e.g., generalization versus specialization) and that the different motif combinations are strongly constrained.
 Although in this study we do not predict indirect interactions, our work is a first step to elucidate novel interactions beyond pairwise interactions.

### 2022-03-12 Manuscript/Main_text/Main_text_Oikos.Rmd
ms ready

@@
 Furthermore, we found that distinct motif positions describing species ecological roles (e.g., generalization and number of indirect interactions) are occupied by different groups on both trophic levels.
-Bees and plant species with separated sexes on different or the same individuals (e.g., dioecious or monoecious species) appeared consistently in generalist motif positions with lower number of indirect interactions.
-The rest of floral visitor groups tended to appear with more frequency on motif positions that involved higher specialization and higher number of indirect interactions while the rest of plant groups showed similar frequencies on the different motif positions.
+Bees appeared consistently in generalist motif positions with low number of indirect interactions while the rest of floral visitor groups were associated with more specialised motif positions with higher number of indirect interactions.
+All plant groups showed a tendency for higher frequency on specialised motif positions but just tall plant species with separated sexes (e.g., woody dioecious or monoecious species) were associated with lower number of indirect interactions.
 Interestingly, the realized combinations of different groups within a motif can not be retrieved from their joint probability distributions, indicating that group combinations are not random either.
@@
 \doublespacing
+
+\newpage
 
@@
 Floral visitor groups were divided by the main taxonomic groups that differed in life form and behaviour.
-Once we split the different plant-pollinator networks into their motif elements, we explored: (i) if there is a common invariant structural property in the overall motif networks (i.e., over- and under-represented motifs); (ii) which plant and floral visitor groups are over- and under-represented in the different motif positions and how these possible differences are associated with different ecological roles; and, (iii) if there are over- and under-represented plant and floral visitor group combinations within a motif.
+Once we split the different plant-pollinator networks into their motif elements, we explored: (i) if there is a common invariant structural property in the overall motif networks (i.e., over- and under-represented motifs); (ii) which plant and floral visitor groups are over- and under-represented in the different motif positions; (iii) if there is association between plant and floral visitor groups with motif positions that involve different ecological roles; and, (iv) if there are over- and under-represented plant and floral visitor group combinations within a motif.
 
@@
 
-Following previous work [@simmons2019b; @simmons2020], we broke down the plant-pollinator networks into their constituent motifs that can capture both direct and indirect interactions.
+Following previous work [@simmons2019; @simmons2020], we broke down the plant-pollinator networks into their constituent motifs that can capture both direct and indirect interactions.
 Prior to analyses, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.
@@
 
-To understand if the different plant and floral visitor groups are associated with motif positions that involve different network roles (e.g., specialization or generalism and number of indirect interactions).
+To understand if the different plant and floral visitor groups are associated with motif positions that involve different network roles (e.g., specialization and number of indirect interactions).
 First, we calculated the specificity of the different motif positions and evaluated its association through linear models with the average frequency of the different plant and floral visitor groups as response variable.
@@
 Second, for each motif position we determined the proportion of indirect-direct interactions, considering indirect interactions exclusively as the mediated effect between two species by a third species.
-Therefore, we account exclusively for the indirect interactions of floral visitors via shared plants (e.g., floral visitor - plant - floral visitor) and the indirect interactions of plants through shared floral visitors (e.g., plant - floral visitor - plant).
+Therefore, we accounted only for indirect interactions of floral visitors via shared plants (e.g., floral visitor - plant - floral visitor) and indirect interactions of plants through shared floral visitors (e.g., plant - floral visitor - plant).
+
+\newpage
 
@@
 The remaining motifs (i.e., 4, 8, 11, 12, 13, and 15) were between the 25th and 75th percentile.
-Notably, the exclusion of singletones from this analysis did not change the observed results (**Figure S1**).
 
 For both floral visitor and plant groups we found different frequencies on motif positions that implied different ecological roles.
-First, for floral visitors, we found that bees had a tendency to appear with higher frequency on motif positions that involved generalism while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) showed the opposite trend with higher frequency on motif positions that implied a greater level of specialization (**Figure S2 A**).
-Although plants did not have marked trends as floral visitors, all plant groups showed a slight tendency for generalism (**Figure S2 B**).
-Second, regarding the number of indirect interactions, bees and tall plants with unisexual flowers showed greater frequency on motif positions that involve low number of indirect interactions but high number of direct interactions (**Figure S3 and Figure S4**).
-The rest of floral visitor groups showed the opposite tendency and had higher frequencies on motif positions with high number of indirect interactions but low number of direct interactions (**Figure S3**).
-The rest of plant groups did not show major differences on their frequencies on motifs that implied different proportion of indirect-direct interactions (**Figure S4**).
+First, for floral visitors, we found that bees had a tendency to appear with higher frequency on motif positions that involved generalism while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) showed the opposite trend with higher frequency on motif positions that implied a greater level of specialization (**Figure S5 A**).
+Although plants did not have marked trends as floral visitors, all plant groups showed a slight tendency for generalism (**Figure S5 B**).
+Second, regarding the number of indirect interactions, bees and tall plants with unisexual flowers showed greater frequency on motif positions that involve low number of indirect interactions but high number of direct interactions (**Figure S6 and Figure S7**).
+The rest of floral visitor groups showed the opposite tendency and had higher frequencies on motif positions with high number of indirect interactions but low number of direct interactions (**Figure S6**).
+The rest of plant groups did not show major differences on their frequencies on motifs that implied different proportion of indirect-direct interactions (**Figure S7**).
 
@@
 This is shown with the mean percentage of motif frequencies in empirical networks that were over the motif frequencies of the simulated ones (percentiles).
-This was done by network (light blue dots) and then averaged for all networks (black dots with error bars that correspond to the standard deviation)."}
+This was done by network (light blue transparent dots) and then averaged for all networks (black dots with error bars that correspond to the standard deviation)."}
 library(lme4)
@@
 Because network motifs can capture both direct and indirect interactions, by analysing over- and under-representation of motifs we are able to explore in greater detail ecological interactions [@stouffer2007].
-We have explored for the first time the overall structure and representation of network motifs in real plant-pollinator networks and shown that the different motifs up to five nodes are consistently over- and under-represented in comparison with simulated networks indicating the presence of ecological processes shaping their structure.
+We have explored for the first time the overall structure and representation of network motifs in real plant-pollinator networks at a macro-ecological scale and shown that the different motifs up to five nodes are consistently over- and under-represented in comparison with simulated networks indicating the presence of ecological processes shaping their structure.
 Despite the presence of multiple ecological processes likely operating at the same time (e.g., neutral effects, morphological matching or phenological overlap), we found a tendency for over-represented structures with more densely connected motifs (i.e., complete, fan and asymmetric complete).
@@
 
-Overall, generalist network motifs for floral visitors were consistently over-represented (e.g.
-fan-type motifs; **Figure 2**).
+Overall, generalist network motifs for floral visitors were consistently over-represented (e.g., fan-type motifs; **Figure 2**).
 For instance, when we compare motifs with equal structure for both trophic levels, we found that floral visitors had always over-representation in the positions that implied the highest number of direct links.
-Despite this is in good agreement with the current view of the generalist tendency of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of the generalist network motifs was only driven by the taxonomic group of bees (**Figure S2**) while the rest of the taxonomic groups tended to be under-represented in these motif positions that involved generalism but were over-represented in motif positions associated with specialist roles.
+Despite this is in good agreement with the current view of the generalist tendency of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of the generalist network motifs was only driven by the taxonomic group of bees (**Figure S5**) while the rest of the taxonomic groups tended to be under-represented in these motif positions that involved generalism but were over-represented in motif positions associated with specialist roles.
 This large effect of bees on the overall patterns is no surprise, as bees were the group with the largest number of interaction records in the whole set of networks as also recorded for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017].

### 2022-03-12 Manuscript/Supplementary_Material/Supporting_information_Oikos.Rmd
ms ready

--- 2022-03-09 Manuscript/Supplementary_Material/Supporting_information_Oikos.Rmd
@@
 
-**Figure S2** Over and under-estimated functional groups on motif positions.
+**Figure S2** Over and under-estimated groups on motif positions.
 
@@
 
-**Figure S4** Plant dendrogram with functional groups.
+**Figure S4** Dendrogram with plant functional groups.
+
+**Figure S5** Association between the frequency and specificity of the different groups on motif positions.
+
+**Figure S6** Frequency of floral visitor groups and proportion of indirect-direct interactions.
+
+**Figure S7** Frequency of plant groups per motif and proportion of indirect-direct interactions.
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=12, fig.width=12, fig.align = 'center', fig.cap="\\textbf{Figure S2.}"}
-
-library(ggplot2)
-library(patchwork)
-
-pollinator_means_reordered_s_1 <- read.csv("../../Data/Csv/pollinator_means_reordered_s_1.csv")
-
-plant_means_s <- read.csv("../../Data/Csv/plant_means_s.csv")
-
-p1 <- ggplot(pollinator_means_reordered_s_1,aes(x=s,y=mean))+
-  geom_point(alpha=0.5, color="black")+
-  geom_smooth(method = "lm",color="black")+
-  facet_wrap(~Node_FG)+
-  labs(x="Specificty",y="Average frequency per motif position") +
-  theme_bw() + ggtitle("Floral visitors") +
-  theme(plot.title = element_text(hjust = 0.5, size = 25),
-        axis.text=element_text(size=12),
-        axis.title=element_text(size=18),
-        strip.text = element_text(size=20))
-
-p2 <- ggplot(plant_means_s,aes(x=s,y=mean))+
-  geom_point(alpha=0.5, color="black")+
-  geom_smooth(method = "lm", color="black")+
-  facet_wrap(~Node_FG)+
-  labs(x="Specificty",y="Average frequency per motif position")+
-  theme_bw() + ggtitle("Plants") +
-  theme(plot.title = element_text(hjust = 0.5, size = 25),
-        axis.text=element_text(size=12),
-        axis.title=element_text(size=18),
-        strip.text = element_text(size=20))
-
-p1/p2 +  plot_annotation(tag_levels = c('A'),  tag_suffix = ')') &  theme(plot.tag = element_text(size = 22))
-
-```
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S3.}"}
-
-library(ggplot2)
-library(scatterpie)
-library(RColorBrewer)
-library(tidyverse)
-
-direct_indirect <- read_csv("../../Data/Data_processing/Motifs_connections/motif_interactions.csv")
-direct_indirect <- direct_indirect %>% select(motif_id,position,direct_interactions, indirect_interactions,ind_same_type_over_directed_int)
-
-pollinator_means_reordered <- read_csv("../../Data/Csv/pollinator_abs_freq_means.csv")
-#Filter out in order to have just 6 FG'S
-pollinator_means_reordered <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds", "Lizards", "Other_insects"))
-
-#Dplyr merge
-joined_tibble <- left_join(direct_indirect, pollinator_means_reordered)
-
-#Bees
-bees <- joined_tibble %>% filter(Node_FG=="Bee")
-bees$ind_same_type_over_directed_int <- round(bees$ind_same_type_over_directed_int, digits = 1)
-#Convert to factor
-bees$position <- as.factor(bees$position)
-bees$ind_same_type_over_directed_int <- as.factor(bees$ind_same_type_over_directed_int)
-bee_plot <- ggplot(bees,aes(position,mean_natural_units))+
-  geom_col(position = "dodge")+
-  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Bees")+
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())+
-  ylab("Frequency")+theme_bw() + xlab("")
-
-#Coleoptera
-cole <- joined_tibble %>% filter(Node_FG=="Coleoptera")
-cole$ind_same_type_over_directed_int <- round(cole$ind_same_type_over_directed_int, digits = 1)
-#Convert to factor
-cole$position <- as.factor(cole$position)
-cole$ind_same_type_over_directed_int <- as.factor(cole$ind_same_type_over_directed_int)
-cole_plot <- ggplot(cole,aes(position,mean_natural_units))+
-  geom_col(position = "dodge")+
-  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Coleoptera")+
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())+
-  ylab("Frequency")+theme_bw() + xlab("")
-
-#Lepidoptera
-lepi <- joined_tibble %>% filter(Node_FG=="Lepidoptera")
-lepi$ind_same_type_over_directed_int <- round(lepi$ind_same_type_over_directed_int, digits = 1)
-#Convert to factor
-lepi$position <- as.factor(lepi$position)
-lepi$ind_same_type_over_directed_int <- as.factor(lepi$ind_same_type_over_directed_int)
-lepi_plot <- ggplot(lepi,aes(position,mean_natural_units))+
-  geom_col(position = "dodge")+
-  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Lepidoptera") +
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())+
-  ylab("Frequency")+theme_bw()+ xlab("")
-
-#Non-bee-Hymenoptera
-non_bee <- joined_tibble %>% filter(Node_FG=="Non-bee-Hymenoptera")
-non_bee$ind_same_type_over_directed_int <- round(non_bee$ind_same_type_over_directed_int, digits = 2)
-#Convert to factor
-non_bee$position <- as.factor(non_bee$position)
-non_bee$ind_same_type_over_directed_int <- as.factor(non_bee$ind_same_type_over_directed_int)
-non_bee_plot <- ggplot(non_bee,aes(position,mean_natural_units))+
-  geom_col(position = "dodge")+
-  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Non-bee-Hymenoptera") +
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())+
-  ylab("Frequency")+theme_bw()+ xlab("")
-
-#Non-syrphids-diptera
-non_syr <- joined_tibble %>% filter(Node_FG=="Non-syrphids-diptera")
-non_syr$ind_same_type_over_directed_int <- round(non_syr$ind_same_type_over_directed_int, digits = 1)
-#Convert to factor
-non_syr$position <- as.factor(non_syr$position)
-non_syr$ind_same_type_over_directed_int <- as.factor(non_syr$ind_same_type_over_directed_int)
-non_syr_plot <- ggplot(non_syr,aes(position,mean_natural_units))+
-  geom_col(position = "dodge")+
-  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Non-syrphids-diptera")+
-theme(axis.title.x=element_blank(),
-      axis.text.x=element_blank(),
-      axis.ticks.x=element_blank())+
-  ylab("Frequency")+theme_bw()+ xlab("")
-
-#Syrphids
-syr <- joined_tibble %>% filter(Node_FG=="Syrphids")
-syr$ind_same_type_over_directed_int <- round(syr$ind_same_type_over_directed_int, digits = 1)
-#Convert to factor
-syr$position <- as.factor(syr$position)
-syr$ind_same_type_over_directed_int <- as.factor(syr$ind_same_type_over_directed_int)
-syr_plot <- ggplot(syr,aes(position,mean_natural_units))+
-  geom_col(position = "dodge")+
-  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Syrphids") +
-   ylab("Frequency")+theme_bw() + xlab("Motif position")
-
-library(patchwork)
-bee_plot / cole_plot / lepi_plot / non_bee_plot / non_syr_plot / syr_plot + plot_annotation(title= 'Floral visitors',
-  subtitle = 'Proportion indirect/direct interactions (0, 0.3, 0.5, 1, 2, 3)',
-  theme = theme(plot.title = element_text(size = 18, face="bold"),plot.subtitle = element_text(size = 18, face="bold")))
-
-```
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S4.}"}
-
-library(ggplot2)
-library(scatterpie)
-library(RColorBrewer)
-library(tidyverse)
-
-direct_indirect <- read_csv("../../Data/Data_processing/Motifs_connections/motif_interactions.csv")
-direct_indirect <- direct_indirect %>% select(motif_id,position,direct_interactions, indirect_interactions,ind_same_type_over_directed_int)
-
-plant_means_reordered <- read_csv("../../Data/Csv/plant_abs_freq_means.csv")
-
-#Dplyr merge
-joined_tibble <- left_join(direct_indirect, plant_means_reordered)
-
-#1 Selfing herbs
-one <- joined_tibble %>% filter(Node_FG=="1")
-one$ind_same_type_over_directed_int <- round(one$ind_same_type_over_directed_int, digits = 1)
-#Convert to factor
-one$position <- as.factor(one$position)
-one$ind_same_type_over_directed_int <- as.factor(one$ind_same_type_over_directed_int)
-one_plot <- ggplot(one,aes(position,mean_natural_units))+
-  geom_col(position = "dodge")+
-  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Selfing herbs")+
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())+
-  ylab("Frequency")+ xlab("") + theme_bw()
-
-#2 Small outcrossing perennials
-two <- joined_tibble %>% filter(Node_FG=="2")
-two$ind_same_type_over_directed_int <- round(two$ind_same_type_over_directed_int, digits = 1)
-#Convert to factor
-two$position <- as.factor(two$position)
-two$ind_same_type_over_directed_int <- as.factor(two$ind_same_type_over_directed_int)
-two_plot <- ggplot(two,aes(position,mean_natural_units))+
-  geom_col(position = "dodge")+
-  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Small outcrossing perennials")+
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())+
-  ylab("Frequency")+ xlab("") + theme_bw()
-
-#3 Self-incomp. perennials with large flowers
-three <- joined_tibble %>% filter(Node_FG=="3")
-three$ind_same_type_over_directed_int <- round(three$ind_same_type_over_directed_int, digits = 1)
-#Convert to factor
-three$position <- as.factor(three$position)
-three$ind_same_type_over_directed_int <- as.factor(three$ind_same_type_over_directed_int)
-three_plot <- ggplot(three,aes(position,mean_natural_units))+
-  geom_col(position = "dodge")+
-  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Self-incomp. perennials with large flowers") +
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())+
-  ylab("Frequency")+ xlab("") + theme_bw()
-
-#4 Tall plants with small unisexual flowers
-four <- joined_tibble %>% filter(Node_FG=="4")
-four$ind_same_type_over_directed_int <- round(four$ind_same_type_over_directed_int, digits = 2)
-#Convert to factor
-four$position <- as.factor(four$position)
-four$ind_same_type_over_directed_int <- as.factor(four$ind_same_type_over_directed_int)
-four_plot <- ggplot(four,aes(position,mean_natural_units))+
-  geom_col(position = "dodge")+
-  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Tall plants with small unisexual flowers") +
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())+
-  ylab("Frequency")+ xlab("") + theme_bw()
-
-#5 Short-lived outcrossers with long zygomorphic flowers
-five <- joined_tibble %>% filter(Node_FG=="5")
-five$ind_same_type_over_directed_int <- round(five$ind_same_type_over_directed_int, digits = 1)
-#Convert to factor
-five$position <- as.factor(five$position)
-five$ind_same_type_over_directed_int <- as.factor(five$ind_same_type_over_directed_int)
-five_plot <- ggplot(five,aes(position,mean_natural_units))+
-  geom_col(position = "dodge")+
-  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Short-lived outcrossers with long zygomorphic flowers")+
-  ylab("Frequency") + xlab("Motif position") + theme_bw()
-
-library(patchwork)
-one_plot / two_plot / three_plot / four_plot / five_plot + plot_annotation(title= 'Plants', subtitle = 'Proportion indirect/direct interactions (0, 0.3, 0.5, 1, 2, 3)',
-  theme = theme(plot.title = element_text(size = 18, face="bold"),plot.subtitle = element_text(size = 18, face="bold")))
-
-```
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="\\textbf{Figure S5.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions after removing non-robust links (singletones).
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="\\textbf{Figure S2.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions after removing non-robust links (singletones).
 The different motif positions are dividied by the average path length clasification by Simmons et al.
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=7, fig.width=12, fig.cap="**Figure S6.** Plant functional group composition separated in qualitative and quantitative variables.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=7, fig.width=12, fig.cap="**Figure S3.** Plant functional group composition separated in qualitative and quantitative variables.
 Panel A) shows the percentage of the different categories within trait represented with different colours for each functional group.
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=13, fig.cap="**Figure S7.** Hierarchical clustering dendrogram with the branches coloured by the optimal number of clusters (5).
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=13, fig.cap="**Figure S4.** Hierarchical clustering dendrogram with the branches coloured by the optimal number of clusters (5).
 The labels of the subgroup of species (N = 524) used in this study are coloured in black in order to show the evenness of the distribution of the species across clusters.
@@
 \elandscape
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=12, fig.width=12, fig.align = 'center', fig.cap="\\textbf{Figure S5.} Association between the frequency and specificity on the different motif positions for floral visitor (panel A) and plant (panel B) groups.
+The different numerical categories of the plant groups correspond to: 1 (selfing herbs), 2 (small outcrossing perennials), 3 (self-incompatible perennials with large flowers), 4 (tall plants with small unisexual flowers) and 5 (short-lived outcrossers with long zygomorphic flowers)."}
+
+library(ggplot2)
+library(patchwork)
+
+pollinator_means_reordered_s_1 <- read.csv("../../Data/Csv/pollinator_means_reordered_s_1.csv")
+
+plant_means_s <- read.csv("../../Data/Csv/plant_means_s.csv")
+
+p1 <- ggplot(pollinator_means_reordered_s_1,aes(x=s,y=mean))+
+  geom_point(alpha=0.5, color="black")+
+  geom_smooth(method = "lm",color="black")+
+  facet_wrap(~Node_FG)+
+  labs(x="Specificty",y="Average frequency per motif position") +
+  theme_bw() + ggtitle("Floral visitors") +
+  theme(plot.title = element_text(hjust = 0.5, size = 25),
+        axis.text=element_text(size=12),
+        axis.title=element_text(size=18),
+        strip.text = element_text(size=20))
+
+p2 <- ggplot(plant_means_s,aes(x=s,y=mean))+
+  geom_point(alpha=0.5, color="black")+
+  geom_smooth(method = "lm", color="black")+
+  facet_wrap(~Node_FG)+
+  labs(x="Specificty",y="Average frequency per motif position")+
+  theme_bw() + ggtitle("Plants") +
+  theme(plot.title = element_text(hjust = 0.5, size = 25),
+        axis.text=element_text(size=12),
+        axis.title=element_text(size=18),
+        strip.text = element_text(size=20))
+
+p1/p2 +  plot_annotation(tag_levels = c('A'),  tag_suffix = ')') &  theme(plot.tag = element_text(size = 22))
+
+```
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S6.} Frequency of the different floral visitor groups on the different motif positions aggregated by the proportion of indirect-direct interactions for the different motif positions."}
+
+library(ggplot2)
+library(scatterpie)
+library(RColorBrewer)
+library(tidyverse)
+
+direct_indirect <- read_csv("../../Data/Data_processing/Motifs_connections/motif_interactions.csv")
+direct_indirect <- direct_indirect %>% select(motif_id,position,direct_interactions, indirect_interactions,ind_same_type_over_directed_int)
+
+pollinator_means_reordered <- read_csv("../../Data/Csv/pollinator_abs_freq_means.csv")
+#Filter out in order to have just 6 FG'S
+pollinator_means_reordered <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds", "Lizards", "Other_insects"))
+
+#Dplyr merge
+joined_tibble <- left_join(direct_indirect, pollinator_means_reordered)
+
+#Bees
+bees <- joined_tibble %>% filter(Node_FG=="Bee")
+bees$ind_same_type_over_directed_int <- round(bees$ind_same_type_over_directed_int, digits = 1)
+#Convert to factor
+bees$position <- as.factor(bees$position)
+bees$ind_same_type_over_directed_int <- as.factor(bees$ind_same_type_over_directed_int)
+bee_plot <- ggplot(bees,aes(position,mean_natural_units))+
+  geom_col(position = "dodge")+
+  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Bees")+
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())+
+  ylab("Frequency")+theme_bw() + xlab("")
+
+#Coleoptera
+cole <- joined_tibble %>% filter(Node_FG=="Coleoptera")
+cole$ind_same_type_over_directed_int <- round(cole$ind_same_type_over_directed_int, digits = 1)
+#Convert to factor
+cole$position <- as.factor(cole$position)
+cole$ind_same_type_over_directed_int <- as.factor(cole$ind_same_type_over_directed_int)
+cole_plot <- ggplot(cole,aes(position,mean_natural_units))+
+  geom_col(position = "dodge")+
+  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Coleoptera")+
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())+
+  ylab("Frequency")+theme_bw() + xlab("")
+
+#Lepidoptera
+lepi <- joined_tibble %>% filter(Node_FG=="Lepidoptera")
+lepi$ind_same_type_over_directed_int <- round(lepi$ind_same_type_over_directed_int, digits = 1)
+#Convert to factor
+lepi$position <- as.factor(lepi$position)
+lepi$ind_same_type_over_directed_int <- as.factor(lepi$ind_same_type_over_directed_int)
+lepi_plot <- ggplot(lepi,aes(position,mean_natural_units))+
+  geom_col(position = "dodge")+
+  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Lepidoptera") +
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())+
+  ylab("Frequency")+theme_bw()+ xlab("")
+
+#Non-bee-Hymenoptera
+non_bee <- joined_tibble %>% filter(Node_FG=="Non-bee-Hymenoptera")
+non_bee$ind_same_type_over_directed_int <- round(non_bee$ind_same_type_over_directed_int, digits = 2)
+#Convert to factor
+non_bee$position <- as.factor(non_bee$position)
+non_bee$ind_same_type_over_directed_int <- as.factor(non_bee$ind_same_type_over_directed_int)
+non_bee_plot <- ggplot(non_bee,aes(position,mean_natural_units))+
+  geom_col(position = "dodge")+
+  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Non-bee-Hymenoptera") +
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())+
+  ylab("Frequency")+theme_bw()+ xlab("")
+
+#Non-syrphids-diptera
+non_syr <- joined_tibble %>% filter(Node_FG=="Non-syrphids-diptera")
+non_syr$ind_same_type_over_directed_int <- round(non_syr$ind_same_type_over_directed_int, digits = 1)
+#Convert to factor
+non_syr$position <- as.factor(non_syr$position)
+non_syr$ind_same_type_over_directed_int <- as.factor(non_syr$ind_same_type_over_directed_int)
+non_syr_plot <- ggplot(non_syr,aes(position,mean_natural_units))+
+  geom_col(position = "dodge")+
+  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Non-syrphids-diptera")+
+theme(axis.title.x=element_blank(),
+      axis.text.x=element_blank(),
+      axis.ticks.x=element_blank())+
+  ylab("Frequency")+theme_bw()+ xlab("")
+
+#Syrphids
+syr <- joined_tibble %>% filter(Node_FG=="Syrphids")
+syr$ind_same_type_over_directed_int <- round(syr$ind_same_type_over_directed_int, digits = 1)
+#Convert to factor
+syr$position <- as.factor(syr$position)
+syr$ind_same_type_over_directed_int <- as.factor(syr$ind_same_type_over_directed_int)
+syr_plot <- ggplot(syr,aes(position,mean_natural_units))+
+  geom_col(position = "dodge")+
+  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Syrphids") +
+   ylab("Frequency")+theme_bw() + xlab("Motif position")
+
+library(patchwork)
+bee_plot / cole_plot / lepi_plot / non_bee_plot / non_syr_plot / syr_plot + plot_annotation(title= 'Floral visitors',
+  subtitle = 'Proportion indirect/direct interactions (0, 0.3, 0.5, 1, 2, 3)',
+  theme = theme(plot.title = element_text(size = 18, face="bold"),plot.subtitle = element_text(size = 18, face="bold")))
+
+```
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S7.} Frequency of the different plant groups on the different motif positions aggregated by the proportion of indirect-direct interactions for the different motif positions."}
+
+library(ggplot2)
+library(scatterpie)
+library(RColorBrewer)
+library(tidyverse)
+
+direct_indirect <- read_csv("../../Data/Data_processing/Motifs_connections/motif_interactions.csv")
+direct_indirect <- direct_indirect %>% select(motif_id,position,direct_interactions, indirect_interactions,ind_same_type_over_directed_int)
+
+plant_means_reordered <- read_csv("../../Data/Csv/plant_abs_freq_means.csv")
+
+#Dplyr merge
+joined_tibble <- left_join(direct_indirect, plant_means_reordered)
+
+#1 Selfing herbs
+one <- joined_tibble %>% filter(Node_FG=="1")
+one$ind_same_type_over_directed_int <- round(one$ind_same_type_over_directed_int, digits = 1)
+#Convert to factor
+one$position <- as.factor(one$position)
+one$ind_same_type_over_directed_int <- as.factor(one$ind_same_type_over_directed_int)
+one_plot <- ggplot(one,aes(position,mean_natural_units))+
+  geom_col(position = "dodge")+
+  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Selfing herbs")+
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())+
+  ylab("Frequency")+ xlab("") + theme_bw()
+
+#2 Small outcrossing perennials
+two <- joined_tibble %>% filter(Node_FG=="2")
+two$ind_same_type_over_directed_int <- round(two$ind_same_type_over_directed_int, digits = 1)
+#Convert to factor
+two$position <- as.factor(two$position)
+two$ind_same_type_over_directed_int <- as.factor(two$ind_same_type_over_directed_int)
+two_plot <- ggplot(two,aes(position,mean_natural_units))+
+  geom_col(position = "dodge")+
+  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Small outcrossing perennials")+
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())+
+  ylab("Frequency")+ xlab("") + theme_bw()
+
+#3 Self-incomp. perennials with large flowers
+three <- joined_tibble %>% filter(Node_FG=="3")
+three$ind_same_type_over_directed_int <- round(three$ind_same_type_over_directed_int, digits = 1)
+#Convert to factor
+three$position <- as.factor(three$position)
+three$ind_same_type_over_directed_int <- as.factor(three$ind_same_type_over_directed_int)
+three_plot <- ggplot(three,aes(position,mean_natural_units))+
+  geom_col(position = "dodge")+
+  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Self-incomp. perennials with large flowers") +
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())+
+  ylab("Frequency")+ xlab("") + theme_bw()
+
+#4 Tall plants with small unisexual flowers
+four <- joined_tibble %>% filter(Node_FG=="4")
+four$ind_same_type_over_directed_int <- round(four$ind_same_type_over_directed_int, digits = 2)
+#Convert to factor
+four$position <- as.factor(four$position)
+four$ind_same_type_over_directed_int <- as.factor(four$ind_same_type_over_directed_int)
+four_plot <- ggplot(four,aes(position,mean_natural_units))+
+  geom_col(position = "dodge")+
+  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Tall plants with small unisexual flowers") +
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())+
+  ylab("Frequency")+ xlab("") + theme_bw()
+
+#5 Short-lived outcrossers with long zygomorphic flowers
+five <- joined_tibble %>% filter(Node_FG=="5")
+five$ind_same_type_over_directed_int <- round(five$ind_same_type_over_directed_int, digits = 1)
+#Convert to factor
+five$position <- as.factor(five$position)
+five$ind_same_type_over_directed_int <- as.factor(five$ind_same_type_over_directed_int)
+five_plot <- ggplot(five,aes(position,mean_natural_units))+
+  geom_col(position = "dodge")+
+  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Short-lived outcrossers with long zygomorphic flowers")+
+  ylab("Frequency") + xlab("Motif position") + theme_bw()
+
+library(patchwork)
+one_plot / two_plot / three_plot / four_plot / five_plot + plot_annotation(title= 'Plants', subtitle = 'Proportion indirect/direct interactions (0, 0.3, 0.5, 1, 2, 3)',
+  theme = theme(plot.title = element_text(size = 18, face="bold"),plot.subtitle = element_text(size = 18, face="bold")))
+
+```

### 2022-03-15 Manuscript/Main_text/Main_text_Oikos.Rmd
edits
Nacho's Edits on ms

@@
 csl: oikos.csl #oikos style from zotero styles
-
 ---
@@
 Bees appeared consistently in generalist motif positions with low number of indirect interactions while the rest of floral visitor groups were associated with more specialised motif positions with higher number of indirect interactions.
-All plant groups showed a tendency for higher frequency on specialised motif positions but just tall plant species with separated sexes (e.g., woody dioecious or monoecious species) were associated with lower number of indirect interactions.
-Interestingly, the realized combinations of different groups within a motif can not be retrieved from their joint probability distributions, indicating that group combinations are not random either.
+All plant groups principaly associated with specialised motif positions but only tall plant species with separated sexes (e.g., woody dioecious or monoecious species) were associated with lower number of indirect interactions.
+Interestingly, the realized combinations of different species groups within a motif can not be retrieved from their joint probability distributions, indicating that group combinations are not random either.
 Our result highlights the non-random structure of the meso-scale on plant-pollinators networks and the association of different plant and floral visitor groups with certain motifs with different ecological roles at a macro-ecological scale.
 
-Keywords: plant-pollinator networks, plant-pollinator interactions, network motifs, functional groups, plant traits, floral visitors
+Keywords: plant-pollinator networks, plant-pollinator interactions, network motifs, indirect interactions, plant traits, floral visitors
 
@@
 
-Traditionally, plant-pollinator research has focused on direct interactions but overlooked indirect interactions (i.e., the mediated effect between two species by a third species), such as facilitative or competitive interactions between plants for pollinators [@moeller2004; @sargent2008].
+Traditionally, plant-pollinator research has focused on direct interactions but overlooked indirect interactions (i.e., the mediated effect between two species by a third species), such as facilitative or competitive interactions between plants for pollinators [@moeller2004; @sargent2008 ADD CARVALHEIRO 2014 ELE?].
 Despite the widespread nature of indirect interactions in ecological communities [@strauss1991], plant-pollinator research often fails to finely capture those indirect interactions with the conventional analytical tools that condense the information either by species (e.g., interaction frequency) or in global topological indices (e.g., nestedness).
@@
 
-By linking the structural properties of the meso-scale with the species ecology we can progress knowledge on species interactions.
+By linking the structural properties of the meso-scale with the species ecology we can progress knowledge on the determinants of species interactions.
 For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species functional role [@stouffer2012; @baker2015].
@@
 Here, we used 60 plant-pollinator networks from 18 different studies and 14 countries, alongside functional groups of plants and taxonomic groups of floral visitors based on functional traits and taxonomic rank, respectively.
-To obtain plant functional groups, we used a comprehensive dataset that included floral, reproductive and vegetative traits compiled in a larger set of networks.
+To obtain plant functional groups, we used a comprehensive dataset that included floral, reproductive and vegetative traits compiled in a larger set of plant species.
 Floral visitor groups were divided by the main taxonomic groups that differed in life form and behaviour.
-Once we split the different plant-pollinator networks into their motif elements, we explored: (i) if there is a common invariant structural property in the overall motif networks (i.e., over- and under-represented motifs); (ii) which plant and floral visitor groups are over- and under-represented in the different motif positions; (iii) if there is association between plant and floral visitor groups with motif positions that involve different ecological roles; and, (iv) if there are over- and under-represented plant and floral visitor group combinations within a motif.
+Once we split the different plant-pollinator networks into their motif elements, we explored: (i) if there is a common invariant structural property in the overall motif networks (i.e., over- and under-represented motifs); (ii) which plant and floral visitor groups are over- and under-represented in different motif positions associated with specific ecological roles; and, (iii) if there are over- and under-represented plant and floral visitor group combinations within a motif.
+[Te lo he pasado a tres items, por que sigue el paralelismo de metodos y resultados, he añadido lo de los ecolohgial roles]()
 
@@
 Generated networks had the same number of plants and floral visitors, as well as the same connectance of their corresponding empirical networks.
-We discarded null models with more constraints (e.g., degree also constant) because they did not allow sufficient permutations and provided highly similar or identical networks to the original ones.
+We discarded null models with more constraints (e.g., constraining for species degree) because the permutations did not generate sufficient variablity providing highly similar or identical networks to the original ones.
 After extracting the motif frequencies from the simulated networks, for each motif type and empirical network, we calculated the percentage of simulated networks whose frequencies were smaller than the ones observed, that is, we estimated the percentile of the observed motif frequencies.
@@
 In these models, we used the study identifiers in **Table S1** as a random intercept.
-By doing so, we obtained estimates of the average motif frequency, but controlling the variation at the study level.
+By doing so, we obtained estimates of the average motif frequency, but controlling for the variation at the study level.
 
@@
 We calculated which plant and floral visitor groups were over- or under-represented in the different motif positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
-To estimate the position frequencies of each plant and floral visitor group in a given network, we added the frequencies of those species that belong to the group, and then, we normalised the resulting frequencies by dividing the position measure for each group by the total number of times that a group appears in any position within the same motif size class.
+To estimate the position frequencies of each plant and floral visitor group in a given network, we added the frequencies of those species that belong to the same group, and then, we normalised the resulting frequencies by dividing it by the total number of times that a group appears in any position within the same motif size class [Check the sentence stills makes snese, I edited it for clarity]().
 Then, we calculated the percentile of the observed position frequencies for each group and network, just like we did with motif frequencies.
@@
 We used the group identifier as an explanatory variable and the study identifiers as a random intercept.
-By adding the group estimates to the model intercept, we assessed the average motif frequency, after controlling the variation at the study level.
+Hence, we assessed the average motif frequency per species group, after controlling the variation at the study level [idem, check its correct]().
 Finally, we visualized with the help of the package _ComplexHeatmap_ version _2.6.2_ [@gu2016] over- and under-representation of plant and floral visitor groups on the different motif positions.
 
-To understand if the different plant and floral visitor groups are associated with motif positions that involve different network roles (e.g., specialization and number of indirect interactions).
-First, we calculated the specificity of the different motif positions and evaluated its association through linear models with the average frequency of the different plant and floral visitor groups as response variable.
-For this, we previously calculated the specificity ($s_i$) of each motif position following @poisot2015 as $s_i = L - l_i / L - 1$, where $L$ is the total number of groups and $l_i$ the number of interaction partners of the group $i$ in a given motif.
+To understand if the different plant and floral visitor groups are associated with motif positions that represent different network roles we characterized the network roles of in terms of thier specialization and number of indirect interactions.
+To that end, we calculated the specificity as a measure of specialization and the ratio[?]() of indirect/direct interactions (see below) of the different motif positions and evaluated its association with the average frequency of the different plant and floral visitor groups through linear models using [EXLPLAIN]().
+Specificity ($s_i$) was calculated for each motif position following @poisot2015 as $s_i = L - l_i / L - 1$, where $L$ is the total number of groups and $l_i$ the number of interaction partners of the group $i$ in a given motif.
 Values of the vector s, range between 1, complete specialization (1 partner within the motif) and 0, complete generalism (all possible partners within the motif).
-Second, for each motif position we determined the proportion of indirect-direct interactions, considering indirect interactions exclusively as the mediated effect between two species by a third species.
+The proportion[ratio?]() of indirect/direct interactions [clarify how this is calculated, simply is i/d?]() for each motif position was calculated considering indirect interactions exclusively as the mediated effect between two species by a third species.
 Therefore, we accounted only for indirect interactions of floral visitors via shared plants (e.g., floral visitor - plant - floral visitor) and indirect interactions of plants through shared floral visitors (e.g., plant - floral visitor - plant).
+[esto chequealo, que no es trivial de entender]()
 
@@
 
-We studied which combinations of plant and floral visitor groups tend to appear together within the same motifs (up to five nodes).
+Finally, we studied which combinations of plant and floral visitor groups tend to appear together within the same motifs (up to five nodes).
 That is which combinations are over- or under-represented.
@@
 
-Most motifs were under- and over-represented (close to the 1st and 99th percentile, respectively) in the comparison between empirical and simulated networks (**Figure 2**).
+Most motifs were under- or over-represented (close to the 1st and 99th percentile, respectively) in the comparison between empirical and simulated networks (**Figure 2**).
 Motifs 3, 5, 9, 10 and 14 were under-represented in empirical networks, that is, all were close to the 1st percentile and under the 25th percentile.
 Interestingly, four out of five of these motifs belonged to the largest path length classification (i.e., core-peripheral).
-In addition, motifs 2, 6, 7, 16 and 17 were over-represented, all over the 75th percentile and thus the closest to the 99th percentile.
+In addition, motifs 2, 6, 7, 16 and 17 were over-represented, all over the 75th percentile.
 In contrast to the under-represented motifs, over-represented motifs belonged to the two shortest path length groups (i.e., complete and fan).
@@
 First, for floral visitors, we found that bees had a tendency to appear with higher frequency on motif positions that involved generalism while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) showed the opposite trend with higher frequency on motif positions that implied a greater level of specialization (**Figure S5 A**).
-Although plants did not have marked trends as floral visitors, all plant groups showed a slight tendency for generalism (**Figure S5 B**).
+Although plants did not have as marked trends as floral visitors, all plant groups showed a slight tendency for generalism (**Figure S5 B**).
 Second, regarding the number of indirect interactions, bees and tall plants with unisexual flowers showed greater frequency on motif positions that involve low number of indirect interactions but high number of direct interactions (**Figure S6 and Figure S7**).
@@
 Notably, the differences across groups were more marked for floral visitors than for plant groups (the differences between min and max percentiles per position were generally two-three times larger for floral visitors).
-From most over- to under-represented floral visitors groups on the different motif positions (indicated with the dendrogram order in **Figure 3**), we found: bees, non-syrphids Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.
+From most over- to under-represented floral visitors groups on the different motif positions (indicated with the dendrogram order in **Figure 3**), we found: bees, non-syrphids Diptera [seguro que los ordenes han de ir en mayuscula?
+Pude que si, pero ckeck it](), syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.
 Although plant functional groups showed less differences between them, there were also more represented groups than others, thus from most over- to under-represented groups on the different motif positions we found: self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.
+[POR QUE AQUÍ no hay os resultados de la parte nueva de espcialización y ratio i/d?
+Me pierdo algo?]()
 
@@
 Understanding the global patterns of network structure is key to unravel the processes that govern community dynamics [@bascompte2007; @bastolla2009; @guimaraes2020].
-However, common analytical approaches are unable to capture the full complexity of ecological systems [@simmons2019; @bergamo2021].
+However, common analytical approaches at the node or at the full network level are unable to capture the full complexity of ecological systems [@simmons2019; @bergamo2021].
 Because network motifs can capture both direct and indirect interactions, by analysing over- and under-representation of motifs we are able to explore in greater detail ecological interactions [@stouffer2007].
-We have explored for the first time the overall structure and representation of network motifs in real plant-pollinator networks at a macro-ecological scale and shown that the different motifs up to five nodes are consistently over- and under-represented in comparison with simulated networks indicating the presence of ecological processes shaping their structure.
+We have explored for the first time the overall structure and representation of network motifs in real plant-pollinator networks at a macro-ecological scale and shown that the different motifs up to five nodes are consistently over- or under-represented in comparison with simulated networks indicating the presence of ecological processes shaping their structure.
 Despite the presence of multiple ecological processes likely operating at the same time (e.g., neutral effects, morphological matching or phenological overlap), we found a tendency for over-represented structures with more densely connected motifs (i.e., complete, fan and asymmetric complete).
@@
 For instance, when we compare motifs with equal structure for both trophic levels, we found that floral visitors had always over-representation in the positions that implied the highest number of direct links.
-Despite this is in good agreement with the current view of the generalist tendency of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of the generalist network motifs was only driven by the taxonomic group of bees (**Figure S5**) while the rest of the taxonomic groups tended to be under-represented in these motif positions that involved generalism but were over-represented in motif positions associated with specialist roles.
-This large effect of bees on the overall patterns is no surprise, as bees were the group with the largest number of interaction records in the whole set of networks as also recorded for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017].
-Interestingly, bees also were the group with lower number of indirect interactions while the rest of floral visitor groups showed clearly higher number of indirect interactions possibly indicating that these different floral visitor groups may experience higher competitive interactions for floral resources [@thomson2020].
+Despite this is in good agreement with the current view of the generalist nature of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of generalist network motifs was driven by the taxonomic group of bees (**Figure S5**) while the rest of the taxonomic groups tended to be under-represented.
+In contrast, non-bee groups were over-represented in motif positions associated with specialised roles.
+This large effect of bees on the overall patterns is no surprise, as bees were the group with the largest number of interaction records in the whole set of networks as also shown for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017].
+Interestingly, bees also were the group with lower number of indirect interactions while the rest of floral visitor groups showed clearly higher number of indirect interactions possibly indicating that these non-bee floral visitor groups may experience higher competitive interactions for floral resources [@thomson2020].
 Despite plant functional groups showed little differences between them on their motif frequencies, all groups showed a tendency to be more represented on motif positions that were associated with higher levels of specialization.
-This tendency towards specialist roles may be the result of co-evolutionary processes (e.g., trait-matching) between plants and pollinators to optimise pollen transfer.
-Remarkably, just tall plants with small unisexual flowers showed higher frequencies on motifs that were associated with low number of indirect interactions with also possible direct implications on pollen transfer (e.g., high fidelity visits with low heterospecific pollen arrival).
+This tendency towards specialist roles may be the result of co-evolutionary processes (e.g., trait-matching) between plants and pollinators to optimise pollen transfer [REF?]().
+Remarkably, just tall plants with small unisexual flowers showed higher frequencies on motifs that were associated with low number of indirect interactions with also possible direct implications on pollen transfer (e.g., high fidelity visits with low heterospecific pollen arrival [REF?]()).
 
@@
 
-Despite the obvious usefulness of functional groups in summarizing species ecological roles (e.g., similar reproductive biology and behaviour of pollinators), delimiting species into functional groups is not often trivial.
+Despite the obvious usefulness of functional groups in summarizing species ecological roles (e.g., similar reproductive biology for plants and behaviour for pollinators), delimiting species into functional groups is often not trivial.
 For instance, taxonomic diversity and trait availability limit our ability to properly represent the wide range of reproductive strategies [@dellinger2020] and different clustering analysis can lead to distinct outcomes (e.g., k-means and hierarchical clustering).
@@
 We believe that this could be investigated by exploring which proportion of over- and under-represented motifs present high and low trait-matching, respectively.
-Moreover, we analysed network motifs focusing exclusively on presence-absence interactions which assume that all interactions are equally important but as suggested by @simmons2020, further work should account for quantitative measurements of the strength of plant-pollinator interactions.
+Moreover, we analysed network motifs focusing exclusively on presence-absence interactions which assume that all interactions are equally important but as suggested by @simmons2020, further work should explore how is it possible to account for the quantitative measurements of the strength of plant-pollinator interactions.
 Finally, despite the wide geographical coverage of our plant-pollinator dataset, there are major gaps for some regions of the world with a clear bias towards Europe, America and islands which have long been interested ecologist [@macarthur1963; @warren2015].
@@
 
-IB designed the idea. JBL collected the data. AA-P lead the analysis with contributions of JBL and guidance of IB. JBL wrote the manuscript with contributions of IB and AA-P.
+IB, AA-P and JBL designed the idea. JBL collected the data. AA-P lead the analysis with contributions of JBL and guidance of IB. JBL wrote the manuscript with contributions of IB and AA-P.
 

### 2022-03-16 Manuscript/Main_text/Main_text_Oikos.Rmd
Looked at line 179

@@
 For both floral visitor and plant groups we found different frequencies on motif positions that implied different ecological roles.
-First, for floral visitors, we found that bees had a tendency to appear with higher frequency on motif positions that involved generalism while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) showed the opposite trend with higher frequency on motif positions that implied a greater level of specialization (**Figure S5 A**).
+First, for floral visitors, we found that bees had a tendency to appear with higher frequency on motif positions that involved generalism (i.e.
+lower specificity values) while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) showed the opposite trend with higher frequency on motif positions that implied a greater level of specialization (**Figure S5 A**).
 Although plants did not have as marked trends as floral visitors, all plant groups showed a slight tendency for generalism (**Figure S5 B**).
-Second, regarding the number of indirect interactions, bees and tall plants with unisexual flowers showed greater frequency on motif positions that involve low number of indirect interactions but high number of direct interactions (**Figure S6 and Figure S7**).
+Second, regarding the number of indirect interactions [aqui clarifica la metrcia, que no me ha quedado clara](), bees and tall plants with unisexual flowers showed greater frequency on motif positions that involve low number of indirect interactions but high number of direct interactions (**Figure S6 and Figure S7**).
 The rest of floral visitor groups showed the opposite tendency and had higher frequencies on motif positions with high number of indirect interactions but low number of direct interactions (**Figure S6**).

### 2022-03-16 Manuscript/Main_text/Main_text_Oikos.Rmd
Update on ms and supporting info

@@
 Bees appeared consistently in generalist motif positions with low number of indirect interactions while the rest of floral visitor groups were associated with more specialised motif positions with higher number of indirect interactions.
-All plant groups principaly associated with specialised motif positions but only tall plant species with separated sexes (e.g., woody dioecious or monoecious species) were associated with lower number of indirect interactions.
+All plant groups were principally associated with specialised motif positions but only tall plant species with separated sexes (e.g., woody dioecious or monoecious species) were associated with lower number of indirect interactions.
 Interestingly, the realized combinations of different species groups within a motif can not be retrieved from their joint probability distributions, indicating that group combinations are not random either.
@@
 
-Traditionally, plant-pollinator research has focused on direct interactions but overlooked indirect interactions (i.e., the mediated effect between two species by a third species), such as facilitative or competitive interactions between plants for pollinators [@moeller2004; @sargent2008 ADD CARVALHEIRO 2014 ELE?].
+Traditionally, plant-pollinator research has focused on direct interactions but overlooked indirect interactions (i.e., the mediated effect between two species by a third species), such as facilitative or competitive interactions between plants for pollinators [@moeller2004; @sargent2008; @carvalheiro2014].
 Despite the widespread nature of indirect interactions in ecological communities [@strauss1991], plant-pollinator research often fails to finely capture those indirect interactions with the conventional analytical tools that condense the information either by species (e.g., interaction frequency) or in global topological indices (e.g., nestedness).
@@
 Once we split the different plant-pollinator networks into their motif elements, we explored: (i) if there is a common invariant structural property in the overall motif networks (i.e., over- and under-represented motifs); (ii) which plant and floral visitor groups are over- and under-represented in different motif positions associated with specific ecological roles; and, (iii) if there are over- and under-represented plant and floral visitor group combinations within a motif.
-[Te lo he pasado a tres items, por que sigue el paralelismo de metodos y resultados, he añadido lo de los ecolohgial roles]()
 
@@
 We calculated which plant and floral visitor groups were over- or under-represented in the different motif positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
-To estimate the position frequencies of each plant and floral visitor group in a given network, we added the frequencies of those species that belong to the same group, and then, we normalised the resulting frequencies by dividing it by the total number of times that a group appears in any position within the same motif size class [Check the sentence stills makes snese, I edited it for clarity]().
+To estimate the position frequencies of each plant and floral visitor group in a given network, we added the frequencies of those species that belong to the same group, and then, we normalised the resulting frequencies by dividing it by the total number of times that a group appears in any position within the same motif size class.
 Then, we calculated the percentile of the observed position frequencies for each group and network, just like we did with motif frequencies.
@@
 We used the group identifier as an explanatory variable and the study identifiers as a random intercept.
-Hence, we assessed the average motif frequency per species group, after controlling the variation at the study level [idem, check its correct]().
+Hence, we assessed the average motif frequency per species group, after controlling the variation at the study level.
 Finally, we visualized with the help of the package _ComplexHeatmap_ version _2.6.2_ [@gu2016] over- and under-representation of plant and floral visitor groups on the different motif positions.
 
-To understand if the different plant and floral visitor groups are associated with motif positions that represent different network roles we characterized the network roles of in terms of thier specialization and number of indirect interactions.
-To that end, we calculated the specificity as a measure of specialization and the ratio[?]() of indirect/direct interactions (see below) of the different motif positions and evaluated its association with the average frequency of the different plant and floral visitor groups through linear models using [EXLPLAIN]().
-Specificity ($s_i$) was calculated for each motif position following @poisot2015 as $s_i = L - l_i / L - 1$, where $L$ is the total number of groups and $l_i$ the number of interaction partners of the group $i$ in a given motif.
+To understand if the different plant and floral visitor groups are associated with motif positions that represent different network roles we characterized the network roles of plant and floral visitor groups in terms of their specialization and number of indirect interactions.
+To that end, we calculated the specificity as a measure of specialization and we use the number of indirect interactions of the different motif positions to evaluate the association of these two node metrics and the group frequencies for the different motif positions.
+First, specificity ($s_i$) was calculated for each motif position following @poisot2015 as $s_i = L - l_i / L - 1$, where $L$ is the total number of groups and $l_i$ the number of interaction partners of the group $i$ in a given motif.
 Values of the vector s, range between 1, complete specialization (1 partner within the motif) and 0, complete generalism (all possible partners within the motif).
-The proportion[ratio?]() of indirect/direct interactions [clarify how this is calculated, simply is i/d?]() for each motif position was calculated considering indirect interactions exclusively as the mediated effect between two species by a third species.
-Therefore, we accounted only for indirect interactions of floral visitors via shared plants (e.g., floral visitor - plant - floral visitor) and indirect interactions of plants through shared floral visitors (e.g., plant - floral visitor - plant).
-[esto chequealo, que no es trivial de entender]()
+Then, we explored graphically through linear models the association between the frequency of the different groups (response variable) and specificy (predictor).
+Second, we calculated the number of indirect interactions for each motif position by accounting only for the indirect effect of two species by a third species.
+That is, we explored exclusively indirect interactions within plants though shared floral visitors or within floral visitors though shared plants.
 
@@
 
-For both floral visitor and plant groups we found different frequencies on motif positions that implied different ecological roles.
-First, for floral visitors, we found that bees had a tendency to appear with higher frequency on motif positions that involved generalism (i.e.
-lower specificity values) while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) showed the opposite trend with higher frequency on motif positions that implied a greater level of specialization (**Figure S5 A**).
-Although plants did not have as marked trends as floral visitors, all plant groups showed a slight tendency for generalism (**Figure S5 B**).
-Second, regarding the number of indirect interactions [aqui clarifica la metrcia, que no me ha quedado clara](), bees and tall plants with unisexual flowers showed greater frequency on motif positions that involve low number of indirect interactions but high number of direct interactions (**Figure S6 and Figure S7**).
-The rest of floral visitor groups showed the opposite tendency and had higher frequencies on motif positions with high number of indirect interactions but low number of direct interactions (**Figure S6**).
-The rest of plant groups did not show major differences on their frequencies on motifs that implied different proportion of indirect-direct interactions (**Figure S7**).
-
+F
 ```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure 2.** Comparison of motif frequencies between empirical and simulated networks grouped by average path length (plots a, b, c and d) as determined in Simmons et al.
@@
 Notably, the differences across groups were more marked for floral visitors than for plant groups (the differences between min and max percentiles per position were generally two-three times larger for floral visitors).
-From most over- to under-represented floral visitors groups on the different motif positions (indicated with the dendrogram order in **Figure 3**), we found: bees, non-syrphids Diptera [seguro que los ordenes han de ir en mayuscula?
-Pude que si, pero ckeck it](), syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.
+From most over- to under-represented floral visitors groups on the different motif positions (indicated with the dendrogram order in **Figure 3**), we found: bees, non-syrphids Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.
 Although plant functional groups showed less differences between them, there were also more represented groups than others, thus from most over- to under-represented groups on the different motif positions we found: self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.
-[POR QUE AQUÍ no hay os resultados de la parte nueva de espcialización y ratio i/d?
-Me pierdo algo?]()
+
+For both floral visitor and plant groups we found different frequencies on motif positions that implied different ecological roles.
+First, for floral visitors, we found that bees had a tendency to appear with higher frequency on motif positions that involved generalism (i.e.
+lower specificity values) while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) showed the opposite trend with higher frequency on motif positions that implied a greater level of specialization (**Figure S5 A**).
+Although plants did not have as marked trends as floral visitors, all plant groups showed a slight tendency for generalism (**Figure S5 B**).
+Second, regarding the number of indirect interactions, bees and tall plants with unisexual flowers showed greater frequency on motif positions that involve low number of indirect interactions (**Figure S6 and Figure S7**).
+The rest of floral visitor groups showed the opposite tendency and had higher frequencies on motif positions with high number of indirect interactions (**Figure S6**).
+The rest of plant groups did not show major differences on their frequencies on motifs that implied different number of indirect interactions (**Figure S7**).
 
@@
 Despite plant functional groups showed little differences between them on their motif frequencies, all groups showed a tendency to be more represented on motif positions that were associated with higher levels of specialization.
-This tendency towards specialist roles may be the result of co-evolutionary processes (e.g., trait-matching) between plants and pollinators to optimise pollen transfer [REF?]().
-Remarkably, just tall plants with small unisexual flowers showed higher frequencies on motifs that were associated with low number of indirect interactions with also possible direct implications on pollen transfer (e.g., high fidelity visits with low heterospecific pollen arrival [REF?]()).
+This tendency towards specialist roles may be the result of co-evolutionary processes (e.g., trait-matching) between plants and pollinators to optimise pollen transfer [@moreira2019].
+Remarkably, just tall plants with small unisexual flowers showed higher frequencies on motifs that were associated with low number of indirect interactions with likely direct implications on pollen transfer for this group that needs to guarantee cross-pollination.
 

### 2022-03-16 Manuscript/Supplementary_Material/Indirect_direct_plants.Rmd
Update on ms and supporting info

--- 2022-03-08 Manuscript/Supplementary_Material/Indirect_direct_plants.Rmd
@@
 one$position <- as.factor(one$position)
-one$ind_same_type_over_directed_int <- as.factor(one$ind_same_type_over_directed_int)
+one$indirect_interactions <- as.factor(one$indirect_interactions)
 one_plot <- ggplot(one,aes(position,mean_natural_units))+
   geom_col(position = "dodge")+
-  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Selfing herbs")+
+  facet_grid(.~indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Selfing herbs")+
   theme(axis.title.x=element_blank(),
@@
 two$position <- as.factor(two$position)
-two$ind_same_type_over_directed_int <- as.factor(two$ind_same_type_over_directed_int)
+two$indirect_interactions <- as.factor(two$indirect_interactions)
 two_plot <- ggplot(two,aes(position,mean_natural_units))+
   geom_col(position = "dodge")+
-  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Small outcrossing perennials")+
+  facet_grid(.~indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Small outcrossing perennials")+
   theme(axis.title.x=element_blank(),
@@
 three$position <- as.factor(three$position)
-three$ind_same_type_over_directed_int <- as.factor(three$ind_same_type_over_directed_int)
+three$indirect_interactions <- as.factor(three$indirect_interactions)
 three_plot <- ggplot(three,aes(position,mean_natural_units))+
   geom_col(position = "dodge")+
-  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Self-incomp. perennials with large flowers") +
+  facet_grid(.~indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Self-incomp. perennials with large flowers") +
   theme(axis.title.x=element_blank(),
@@
 four$position <- as.factor(four$position)
-four$ind_same_type_over_directed_int <- as.factor(four$ind_same_type_over_directed_int)
+four$indirect_interactions <- as.factor(four$indirect_interactions)
 four_plot <- ggplot(four,aes(position,mean_natural_units))+
   geom_col(position = "dodge")+
-  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Tall plants with small unisexual flowers") +
+  facet_grid(.~indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Tall plants with small unisexual flowers") +
   theme(axis.title.x=element_blank(),
@@
 five$position <- as.factor(five$position)
-five$ind_same_type_over_directed_int <- as.factor(five$ind_same_type_over_directed_int)
+five$indirect_interactions <- as.factor(five$indirect_interactions)
 five_plot <- ggplot(five,aes(position,mean_natural_units))+
   geom_col(position = "dodge")+
-  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Short-lived outcrossers with long zygomorphic flowers")+
+  facet_grid(.~indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Short-lived outcrossers with long zygomorphic flowers")+
   ylab("Frequency")
@@
 one_plot / two_plot / three_plot / four_plot / five_plot + plot_annotation(
-  title = 'Proportion indirect/direct interactions (0, 0.3, 0.5, 1, 2, 3)',
-  theme = theme(plot.title = element_text(size = 18, face="bold")))
+  title = 'Number of indirect interactions (0, 1, 2, 3)',
+  theme = theme(plot.title = element_text(size = 18, face="bold"))) & theme_bw()
 

### 2022-03-16 Manuscript/Supplementary_Material/Indirect_direct_pollinators.Rmd
Update on ms and supporting info

@@
 bees$position <- as.factor(bees$position)
-bees$ind_same_type_over_directed_int <- as.factor(bees$ind_same_type_over_directed_int)
+bees$indirect_interactions <- as.factor(bees$indirect_interactions)
 bee_plot <- ggplot(bees,aes(position,mean_natural_units))+
   geom_col(position = "dodge")+
-  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Bees")+
+  facet_grid(.~indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Bees")+
   theme(axis.title.x=element_blank(),
@@
 cole$position <- as.factor(cole$position)
-cole$ind_same_type_over_directed_int <- as.factor(cole$ind_same_type_over_directed_int)
+cole$indirect_interactions <- as.factor(cole$indirect_interactions)
 cole_plot <- ggplot(cole,aes(position,mean_natural_units))+
   geom_col(position = "dodge")+
-  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Coleoptera")+
+  facet_grid(.~indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Coleoptera")+
   theme(axis.title.x=element_blank(),
@@
 lepi$position <- as.factor(lepi$position)
-lepi$ind_same_type_over_directed_int <- as.factor(lepi$ind_same_type_over_directed_int)
+lepi$indirect_interactions <- as.factor(lepi$indirect_interactions)
 lepi_plot <- ggplot(lepi,aes(position,mean_natural_units))+
   geom_col(position = "dodge")+
-  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Lepidoptera") +
+  facet_grid(.~indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Lepidoptera") +
   theme(axis.title.x=element_blank(),
@@
 non_bee$position <- as.factor(non_bee$position)
-non_bee$ind_same_type_over_directed_int <- as.factor(non_bee$ind_same_type_over_directed_int)
+non_bee$indirect_interactions <- as.factor(non_bee$indirect_interactions)
 non_bee_plot <- ggplot(non_bee,aes(position,mean_natural_units))+
   geom_col(position = "dodge")+
-  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Non-bee-Hymenoptera") +
+  facet_grid(.~indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Non-bee-Hymenoptera") +
   theme(axis.title.x=element_blank(),
@@
 non_syr$position <- as.factor(non_syr$position)
-non_syr$ind_same_type_over_directed_int <- as.factor(non_syr$ind_same_type_over_directed_int)
+non_syr$indirect_interactions <- as.factor(non_syr$indirect_interactions)
 non_syr_plot <- ggplot(non_syr,aes(position,mean_natural_units))+
   geom_col(position = "dodge")+
-  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Non-syrphids-diptera")+
+  facet_grid(.~indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Non-syrphids-diptera")+
 theme(axis.title.x=element_blank(),
@@
 syr$position <- as.factor(syr$position)
-syr$ind_same_type_over_directed_int <- as.factor(syr$ind_same_type_over_directed_int)
+syr$indirect_interactions <- as.factor(syr$indirect_interactions)
 syr_plot <- ggplot(syr,aes(position,mean_natural_units))+
   geom_col(position = "dodge")+
-  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Syrphids") +
+  facet_grid(.~indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Syrphids") +
    ylab("Frequency")+theme_bw() + xlab("Position within motif")
@@
 bee_plot / cole_plot / lepi_plot / non_bee_plot / non_syr_plot / syr_plot + plot_annotation(
-  title = 'Proportion indirect/direct interactions (0, 0.3, 0.5, 1, 2, 3)',
+  title = 'Number of indirect interactions (0, 1, 2, 3)',
   theme = theme(plot.title = element_text(size = 18, face="bold")))

### 2022-03-16 Manuscript/Supplementary_Material/Supporting_information_Oikos.Rmd
Update on ms and supporting info

@@
 
-**Figure S6** Frequency of floral visitor groups and proportion of indirect-direct interactions.
-
-**Figure S7** Frequency of plant groups per motif and proportion of indirect-direct interactions.
+**Figure S6** Frequency of floral visitor groups and number of indirect interactions per motif positions.
+
+**Figure S7** Frequency of plant groups and number of indirect interactions per motif positions.
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S6.} Frequency of the different floral visitor groups on the different motif positions aggregated by the proportion of indirect-direct interactions for the different motif positions."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S6.} Frequency of the different floral visitor groups on the different motif positions aggregated by the number of indirect interactions for the different motif positions."}
 
@@
 syr$position <- as.factor(syr$position)
-syr$ind_same_type_over_directed_int <- as.factor(syr$ind_same_type_over_directed_int)
+syr$indirect_interactions <- as.factor(syr$indirect_interactions)
 syr_plot <- ggplot(syr,aes(position,mean_natural_units))+
   geom_col(position = "dodge")+
-  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Syrphids") +
+  facet_grid(.~indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Syrphids") +
    ylab("Frequency")+theme_bw() + xlab("Motif position")
@@
 bee_plot / cole_plot / lepi_plot / non_bee_plot / non_syr_plot / syr_plot + plot_annotation(title= 'Floral visitors',
-  subtitle = 'Proportion indirect/direct interactions (0, 0.3, 0.5, 1, 2, 3)',
+  subtitle = 'Number of indirect interactions (0, 1, 2, 3)',
   theme = theme(plot.title = element_text(size = 18, face="bold"),plot.subtitle = element_text(size = 18, face="bold")))
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S7.} Frequency of the different plant groups on the different motif positions aggregated by the proportion of indirect-direct interactions for the different motif positions."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S7.} Frequency of the different plant groups on the different motif positions aggregated by the number of indirect interactions for the different motif positions."}
 
@@
 five$position <- as.factor(five$position)
-five$ind_same_type_over_directed_int <- as.factor(five$ind_same_type_over_directed_int)
+five$indirect_interactions <- as.factor(five$indirect_interactions)
 five_plot <- ggplot(five,aes(position,mean_natural_units))+
   geom_col(position = "dodge")+
-  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Short-lived outcrossers with long zygomorphic flowers")+
+  facet_grid(.~indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Short-lived outcrossers with long zygomorphic flowers")+
   ylab("Frequency") + xlab("Motif position") + theme_bw()
@@
 library(patchwork)
-one_plot / two_plot / three_plot / four_plot / five_plot + plot_annotation(title= 'Plants', subtitle = 'Proportion indirect/direct interactions (0, 0.3, 0.5, 1, 2, 3)',
+one_plot / two_plot / three_plot / four_plot / five_plot + plot_annotation(title= 'Plants', subtitle = 'Number of indirect interactions (0, 1, 2, 3)',
   theme = theme(plot.title = element_text(size = 18, face="bold"),plot.subtitle = element_text(size = 18, face="bold")))

### 2022-03-21 Manuscript/Main_text/Main_text_Oikos.Rmd
edits

@@
 motif_number <- 1
-p1 <- plot_motif_positions(motif_number)
+p1 <- plot_motif_positions(motif_number) +
+geom_point(aes(color = as.factor(label)),size=10,color = "grey90")+
+geom_text(aes(x, y , label = label),size=3)
 
 motif_number <- 2
-p2 <- plot_motif_positions(motif_number)
+p2 <- plot_motif_positions(motif_number)+
+geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
+geom_text(aes(x, y , label = label),size=3)
 
 motif_number <- 3
-p3 <- plot_motif_positions(motif_number)
+p3 <- plot_motif_positions(motif_number)+
+geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
+geom_text(aes(x, y , label = label),size=3)
 
 motif_number <- 4
-p4 <- plot_motif_positions(motif_number)
+p4 <- plot_motif_positions(motif_number)+
+geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
+geom_text(aes(x, y , label = label),size=3)
 
 motif_number <- 5
-p5 <- plot_motif_positions(motif_number)
+p5 <- plot_motif_positions(motif_number)+
+geom_point(aes(color = as.factor(label)),size=10,color = "lightcoral")+
+geom_text(aes(x, y , label = label),size=3)
 
 motif_number <- 6
-p6 <- plot_motif_positions(motif_number)
+p6 <- plot_motif_positions(motif_number) +
+geom_point(aes(color = as.factor(label)),size=10,color = "goldenrod2")+
+geom_text(aes(x, y , label = label),size=3)
 
 motif_number <- 7
-p7 <- plot_motif_positions(motif_number)
+p7 <- plot_motif_positions(motif_number)+
+geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
+geom_text(aes(x, y , label = label),size=3)
 
 motif_number <- 8   
-p8 <- plot_motif_positions(motif_number)
+p8 <- plot_motif_positions(motif_number)+
+geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
+geom_text(aes(x, y , label = label),size=3)
 
 motif_number <- 9
-p9 <- plot_motif_positions(motif_number)
+p9 <- plot_motif_positions(motif_number)+
+geom_point(aes(color = as.factor(label)),size=10,color = "lightcoral")+
+geom_text(aes(x, y , label = label),size=3)
 
 motif_number <- 10
-p10 <- plot_motif_positions(motif_number)
+p10 <- plot_motif_positions(motif_number)+
+geom_point(aes(color = as.factor(label)),size=10,color = "lightcoral")+
+geom_text(aes(x, y , label = label),size=3)
 
 motif_number <- 11
-p11 <- plot_motif_positions(motif_number)
+p11 <- plot_motif_positions(motif_number)+
+geom_point(aes(color = as.factor(label)),size=10,color = "skyblue")+
+geom_text(aes(x, y , label = label),size=3)
 
 motif_number <- 12
-p12 <- plot_motif_positions(motif_number)
+p12 <- plot_motif_positions(motif_number)+
+geom_point(aes(color = as.factor(label)),size=10,color = "goldenrod2")+
+geom_text(aes(x, y , label = label),size=3)
 
 motif_number <- 13
-p13 <- plot_motif_positions(motif_number)
+p13 <- plot_motif_positions(motif_number)+
+geom_point(aes(color = as.factor(label)),size=10,color = "lightcoral")+
+geom_text(aes(x, y , label = label),size=3)
 
 motif_number <- 14
-p14 <- plot_motif_positions(motif_number)
+p14 <- plot_motif_positions(motif_number)+
+geom_point(aes(color = as.factor(label)),size=10,color = "lightcoral")+
+geom_text(aes(x, y , label = label),size=3)
 
 motif_number <- 15
-p15 <- plot_motif_positions(motif_number)
+p15 <- plot_motif_positions(motif_number)+
+geom_point(aes(color = as.factor(label)),size=10,color = "skyblue")+
+geom_text(aes(x, y , label = label),size=3)
 
 motif_number <- 16
-p16 <- plot_motif_positions(motif_number)
+p16 <- plot_motif_positions(motif_number)+
+geom_point(aes(color = as.factor(label)),size=10,color = "goldenrod2")+
+geom_text(aes(x, y , label = label),size=3)
 
 motif_number <- 17
-p17 <- plot_motif_positions(motif_number)
+p17 <- plot_motif_positions(motif_number)+
+geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
+geom_text(aes(x, y , label = label),size=3)
 
@@
 
-(p1 & ylab("2 species")| p2 & ylab("3 species") | p3 )/ (p4 & ylab("4 species")| p5 | p6 | p7)/ (p8  & ylab("5 species")| p9 | p10 | p11 | p12) / (p13 & ylab("5 species")| p14 | p15 | p16 | p17) & theme(axis.title.y = element_text(color="black", size=14, face="bold")) #+
- #plot_annotation(tag_levels = '1')
+p <- (p1 & ylab("2 species")| p2 & ylab("3 species") | p3 ) /
+(p4 & ylab("4 species")| p5 | p6 | p7) / 
+(p8  & ylab("5 species")| p9 | p10 | p11 | p12) /
+(p13 & ylab("5 species")| p14 | p15 | p16 | p17) &
+theme(axis.title.y = element_text(color="black", size=14, face="bold"))
+
+#Create custom legend
+a <- c(1,2,3,4)
+b <- c(1,2,3,4)
+c <- c("a","b", "c", "d")
+abc <- data.frame(a,b,c)
+p1 <- ggplot(abc, aes(x=a,y=b, color=c))+geom_point() + theme_bw() + 
+  scale_colour_manual(name = 'Path length classification', 
+                      values =c(a= 'goldenrod2',b='mediumaquamarine',
+                                c='skyblue', d='lightcoral'), 
+                      labels = c(a='Strong \n mean path length = 1.38', 
+                                 b='Medium-strong \n mean path length = 1.48',
+                                 c='Medium-weak \n mean path length = 1.60',
+                                 d='Weak \n mean path length = 1.85'))+
+theme(legend.position="bottom")+ guides(colour = guide_legend(override.aes = list(size=8),title.position="top", title.hjust = 0.5))
+
+legend <- cowplot::get_legend(p1+ theme(legend.position = "bottom",legend.text = element_text(size=10), legend.title = element_text(size=12, 
+face="bold"),legend.box.background = element_rect(color="black", size=2)))
+
+cowplot::plot_grid(p, legend, ncol = 1, rel_heights = c(12, 1.8))
 
@@
 *Acknowledgements* - This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2).
-We thank all researchers that made their data openly available and sent it upon request.
-We also thank Bryony Wilcox, Greg Bible, Mercedes Sanchez-Lanuza and David Ragel for their help with data collection.
+We would like to thank David García-Callejas for useful comments on the manuscript before submission.
 Finally, JBL also thanks the University of New England for the funding provided to carry out this work.

### 2022-03-21 Scripts/trial_motif_positions2.R

@@ -1,7 +1,6 @@
 library(tidyverse)
 library(RColorBrewer)
-source("../Scripts/Scripts_Alfonso/trial_motif_positions.R")
-
+source("Scripts/trial_motif_positions.R")
 
 motif_number <- 1
 p1 <- plot_motif_positions(motif_number) +
@@ -105,17 +104,18 @@ theme(axis.title.y = element_text(color="black", size=14, face="bold"))
 
 
 #Create custom legend
-a <- c(1,2,3,4,5)
-b <- c(1,2,3,4,5)
-c <- c("a","b", "c", "d", "e")
+a <- c(1,2,3,4)
+b <- c(1,2,3,4)
+c <- c("a","b", "c", "d")
 abc <- data.frame(a,b,c)
 p1 <- ggplot(abc, aes(x=a,y=b, color=c))+geom_point() + theme_bw() + 
   scale_colour_manual(name = 'Path length \n classification', 
-                      values =c('goldenrod2'= 'goldenrod2','mediumaquamarine'='mediumaquamarine',
-                                'skyblue'='skyblue', 'lightcoral'='lightcoral'), 
-                      labels = c('Strong \n mean path length = 1.38', 
-                                 'Medium-strong \n mean path length = 1.48',
-                                 'Medium-weak \n mean path length = 1.60','Weak \n mean path length = 1.85'))+
+                      values =c(a= 'goldenrod2',b='mediumaquamarine',
+                                c='skyblue', d='lightcoral'), 
+                      labels = c(a='Strong \n mean path length = 1.38', 
+                                 b='Medium-strong \n mean path length = 1.48',
+                                 c='Medium-weak \n mean path length = 1.60',
+                                 d='Weak \n mean path length = 1.85'))+
 theme(legend.position="bottom")
 
 legend <- cowplot::get_legend(p1+ theme(legend.position = "bottom"))

### 2022-03-21 Manuscript/Main_text/Main_text_Oikos.Rmd
work in progress

@@
 
+**Overview**
+
+To investigate the structure of the meso-scale in plant-pollinator networks, we have gathered 60 published plant-pollinator networks with worldwide distribution.
+Then, we have divided the plant and floral visitor species from these networks into groups that summarize their main life-history strategies.
+After, we calculated the normalize motif frequencies and investigated if these frequencies are similar to the ones expected by chance with thelp of null models.
+Then, we have also calculated the normalize group frequencies for the different motif positions and investigated also over- and under-representation of the group frequencies.
+
+: (i) gathered 60 published plant-pollinator networks with worldwide distribution; (ii) determined the main plant and floral visitor groups that summarize the principal life-history strategies of the species in these networks; (iii) calculated the normalized motif frequencies and compare them with the expected frequencies from null models from the same set of plant-pollinator networks; (iv) calculated the normalise frequencies of the different plant and floral visitor groups and compare them with the ones from null models; (v) explore the association
+
+the structure of the meso-scale of plant-pollinator networks we have gathered 60 networks with worldwide distribution.
+Then, we have determined for the different plant and floral visitor the main groups that define the principal life-history strategies.
+After, we have calculated the normalize motif frequencies in this same set of plant-pollinator networks and investigated if the overall motif frequencies concur or not with the expected frequencies from null models originated from the same set of networks.
+Then,
+
+After, we have calculated the frequencies of the different plant and floral visitor groups and explore if these frequencies also match the expected from null models or not.
+Finally, we investigate if the plant and floral visitor motif combinations can be retrieve from their expected probability or not by assuming
+
 **Plant-pollinator studies**
@@
 
-F
 ```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure 2.** Comparison of motif frequencies between empirical and simulated networks grouped by average path length (plots a, b, c and d) as determined in Simmons et al.
@@
 This was done by network (light blue transparent dots) and then averaged for all networks (black dots with error bars that correspond to the standard deviation)."}
+
 library(lme4)
@@
 *Acknowledgements* - This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2).
-We would like to thank David García-Callejas for useful comments on the manuscript before submission.
-Finally, JBL also thanks the University of New England for the funding provided to carry out this work.
+JBL also thanks the University of New England for the funding provided to carry out this work.
+Finally, we would like to thank David García-Callejas for his useful comments on the manuscript before submission.
 

### 2022-03-22 Manuscript/Main_text/Main_text_Oikos.Rmd
edits

@@
 
-Ecological processes leave distinct structural imprints on species interactions shaping the topology of mutualistic networks.
-Detecting those relationships is not trivial since they go beyond pairwise interactions, but may get blurred when considering full network descriptors.
-However, recent work has shown the network meso-scale can capture this important information.
-The meso-scale describes network subgraphs representing patterns of interactions between a small number of species (i.e., motifs) and those constitute the building blocks of the whole network.
+Ecological processes leave distinct structural imprints on the species interactions that shape the topology of mutualistic networks.
+Detecting those relationships is not trivial since they go beyond pairwise interactions that may get blurred when considering full network descriptors.
+Recent work has shown the network meso-scale can capture this important information.
+The meso-scale describes network subgraphs representing patterns of interactions between a small number of species (i.e., motifs) that constitute the building blocks of the whole network.
 Despite the possible implications of network motifs to better capture species interactions, they remain overlooked in natural plant-pollinator networks.
-By exploring 60 networks from 18 different studies with wide geographical coverage we show that some motifs are consistently under- and over-represented worldwide, suggesting that the building blocks of plant-pollinator networks are not random.
-Furthermore, we found that distinct motif positions describing species ecological roles (e.g., generalization and number of indirect interactions) are occupied by different groups on both trophic levels.
-Bees appeared consistently in generalist motif positions with low number of indirect interactions while the rest of floral visitor groups were associated with more specialised motif positions with higher number of indirect interactions.
-All plant groups were principally associated with specialised motif positions but only tall plant species with separated sexes (e.g., woody dioecious or monoecious species) were associated with lower number of indirect interactions.
+By exploring 60 empirical plant-pollinator networks from 18 different studies with wide geographical coverage we show that some motifs are consistently under- and over-represented worldwide, suggesting that the building blocks of plant-pollinator networks are not random.
+Furthermore, we find that distinct motif positions describing species ecological roles (e.g., generalization and number of indirect interactions) are occupied by different plant and floral visitor groups on both trophic levels.
+Bees appear consistently in generalist motif positions with low number of indirect interactions while the rest of floral visitor groups are associated with more specialised motif positions with higher number of indirect interactions.
+All plant groups are principally associated with specialised motif positions but only tall plant species with separated sexes (e.g., woody dioecious or monoecious species) are associated with lower number of indirect interactions.
 Interestingly, the realized combinations of different species groups within a motif can not be retrieved from their joint probability distributions, indicating that group combinations are not random either.
-Our result highlights the non-random structure of the meso-scale on plant-pollinators networks and the association of different plant and floral visitor groups with certain motifs with different ecological roles at a macro-ecological scale.
+Our result highlights the non-random structure of the meso-scale on plant-pollinators networks and the association of different plant and floral visitor groups with certain motifs that involve different ecological roles at a macro-ecological scale.
 
@@
 For example, plant-pollinator network level approaches have identified common invariant structural properties across networks, including a degree distribution that decays as a power law [@jordano1987], nestedness [@bascompte2003], or modularity [@olesen2007].
-In addition, the local species position within the network can define its degree of specialization [@bluthgen2006] or its role connecting the rest of the community [@olesen2007].
-Despite the unquestionable progress with the use of these metrics at both species and network level, condensing the information into a single metric implies the loss of relevant ecological information that obscure the understanding of species interactions [@cirtwill2018; @simmons2019].
+In addition, the local species position within the network can define its degree of specialization [@bluthgen2006] or its role in connecting the rest of the community [@olesen2007].
+Despite the unquestionable progress with the use of these metrics at both species and network level, condensing the information into a single metric implies the loss of relevant ecological information that obscures the understanding of species interactions [@cirtwill2018; @simmons2019].
 
@@
 Despite the widespread nature of indirect interactions in ecological communities [@strauss1991], plant-pollinator research often fails to finely capture those indirect interactions with the conventional analytical tools that condense the information either by species (e.g., interaction frequency) or in global topological indices (e.g., nestedness).
-Nonetheless, the emerging framework of network motifs (small sub-networks recorded within a given network) in plant-pollinator research allows to consider both direct and indirect interactions [@simmons2019].
+Nonetheless, the emerging framework of network motifs (small sub-networks observed within a given network) in plant-pollinator research allows to consider both direct and indirect interactions [@simmons2019].
 Motifs are often referred to as the building blocks of a network that depict subsets of interactions [@milo2002].
@@
 
-By linking the structural properties of the meso-scale with the species ecology we can progress knowledge on the determinants of species interactions.
-For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species functional role [@stouffer2012; @baker2015].
+By linking the structural properties of the meso-scale with the species' ecology we can advance in our understanding on the determinants of species interactions.
+For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species' functional role [@stouffer2012; @baker2015].
 Yet, our understanding of the ecological implications of network motifs in real plant-pollinator networks remains in its infancy.
-Moreover, it is unclear how the species ecology and life-history traits determines the species' functional role within the network of interactions [@coux2016].
+Moreover, it is unclear how the species ecology and life-history traits determines its functional role within the network of interactions [@coux2016].
 For example, large pollinators can forage larger distances [@greenleaf2007], deposit greater pollen quantities [@foldesi2021] and handle complex zygomorphic flowers in comparison with small pollinators that are restricted to lower floral complexity [@gong2009].
@@
 
-Here, we used 60 plant-pollinator networks from 18 different studies and 14 countries, alongside functional groups of plants and taxonomic groups of floral visitors based on functional traits and taxonomic rank, respectively.
+Here, we used 60 empirical networks from 18 different studies and 14 countries to evaluate the structure of the meso-scale in plant-pollinator networks.
+From these networks we extracted plant and floral visitors species and determined the principal groups that define their main life-history strategies.
+
+, and for the plant and floral visitor species of these networks we determined
+
+for their plants and floral visitors we determined functional and taxonomic groups that summarize their main life-history strategies.
+
+alongside functional groups of plants and taxonomic groups of floral visitors based on functional traits and taxonomic rank, respectively.
 To obtain plant functional groups, we used a comprehensive dataset that included floral, reproductive and vegetative traits compiled in a larger set of plant species.
@@
 Then, we have divided the plant and floral visitor species from these networks into groups that summarize their main life-history strategies.
-After, we calculated the normalize motif frequencies and investigated if these frequencies are similar to the ones expected by chance with thelp of null models.
-Then, we have also calculated the normalize group frequencies for the different motif positions and investigated also over- and under-representation of the group frequencies.
-
-: (i) gathered 60 published plant-pollinator networks with worldwide distribution; (ii) determined the main plant and floral visitor groups that summarize the principal life-history strategies of the species in these networks; (iii) calculated the normalized motif frequencies and compare them with the expected frequencies from null models from the same set of plant-pollinator networks; (iv) calculated the normalise frequencies of the different plant and floral visitor groups and compare them with the ones from null models; (v) explore the association
-
-the structure of the meso-scale of plant-pollinator networks we have gathered 60 networks with worldwide distribution.
-Then, we have determined for the different plant and floral visitor the main groups that define the principal life-history strategies.
-After, we have calculated the normalize motif frequencies in this same set of plant-pollinator networks and investigated if the overall motif frequencies concur or not with the expected frequencies from null models originated from the same set of networks.
-Then,
-
-After, we have calculated the frequencies of the different plant and floral visitor groups and explore if these frequencies also match the expected from null models or not.
-Finally, we investigate if the plant and floral visitor motif combinations can be retrieve from their expected probability or not by assuming
+After, we have calculated the normalize motif frequencies and investigated if these frequencies are similar or not to the ones expected by chance with th help of null models.
+Then, we have also calculated the normalize group frequencies of plant and floral visitor for the different motif positions and investigated their overall representation and ecological implications by comparing the observed group frequencies on the different motif positions with simulated ones.
+Finally, we have tried to recover the observed motif combinations in empirical networks from their expected probability by assuming non-independence with the help of a simulation approach and z-scores.
 
@@
 We calculated which plant and floral visitor groups were over- or under-represented in the different motif positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
-To estimate the position frequencies of each plant and floral visitor group in a given network, we added the frequencies of those species that belong to the same group, and then, we normalised the resulting frequencies by dividing it by the total number of times that a group appears in any position within the same motif size class.
+To estimate the position frequencies of each plant and floral visitor group in a given network, we added the frequencies of those species that belong to the same group, and then, we normalised the resulting frequencies by dividing them by the total number of times that a corresponding group appears in any position within the same motif size class.
 Then, we calculated the percentile of the observed position frequencies for each group and network, just like we did with motif frequencies.
@@
 Notably, we found that just 30$\%$ of the possible 53,250 motif combinations are realized.
-Thus, similarly to the presence of forbidden links at the network level [@olesen2011; @jordano2016], we also found the existence of forbidden motif positions and those represented almost two thirds of the total possible combinations of indirect interactions.
+Thus, similarly to the presence of forbidden links at the network level [@olesen2011; @jordano2016], we also found the existence of forbidden motif positions and those represented almost two thirds of the total possible motif combinations.
 This concurs well with the general idea that plant-pollinator networks have a high proportion of non-realized direct interactions [@jordano2003; @bascompte2013], and as a result, also a high proportion of non-realized combinations of indirect interactions.
-Some of this non-observed interactions are probably due to under-sampling [@dorado2011; @jordano2016].
+Some of this non-observed direct interactions are probably due to under-sampling [@dorado2011; @jordano2016].
 However, a large fraction of the possible interactions do not take place because of life-history constraints such as species co-occurrence, trait matching processes and phenological uncoupling [@olesen2011; @bartomeus2016; @jordano2016].
@@
 Moreover, we analysed network motifs focusing exclusively on presence-absence interactions which assume that all interactions are equally important but as suggested by @simmons2020, further work should explore how is it possible to account for the quantitative measurements of the strength of plant-pollinator interactions.
-Finally, despite the wide geographical coverage of our plant-pollinator dataset, there are major gaps for some regions of the world with a clear bias towards Europe, America and islands which have long been interested ecologist [@macarthur1963; @warren2015].
+Finally, despite the wide geographical coverage of our plant-pollinator dataset, there are major gaps for some regions of the world with a clear bias towards Europe, America and islands which have long interested ecologist [@macarthur1963; @warren2015].
 These biases are also found in global datasets of networks where the data is highly fragmented across space [@poisot2021] and more efforts are needed to capture global patterns of plant-pollinator interactions.

### 2022-03-23 Manuscript/Main_text/Main_text_Oikos.Rmd
edits

@@
 From these networks we extracted plant and floral visitors species and determined the principal groups that define their main life-history strategies.
-
-, and for the plant and floral visitor species of these networks we determined
-
-for their plants and floral visitors we determined functional and taxonomic groups that summarize their main life-history strategies.
-
-alongside functional groups of plants and taxonomic groups of floral visitors based on functional traits and taxonomic rank, respectively.
-To obtain plant functional groups, we used a comprehensive dataset that included floral, reproductive and vegetative traits compiled in a larger set of plant species.
+To obtain plant groups, we used a comprehensive dataset that included floral, reproductive and vegetative traits compiled in a larger set of plant species.
 Floral visitor groups were divided by the main taxonomic groups that differed in life form and behaviour.
@@
 
-To investigate the structure of the meso-scale in plant-pollinator networks, we have gathered 60 published plant-pollinator networks with worldwide distribution.
+To investigate the structure of the meso-scale in plant-pollinator networks, we have gathered published plant-pollinator networks with worldwide distribution.
 Then, we have divided the plant and floral visitor species from these networks into groups that summarize their main life-history strategies.
-After, we have calculated the normalize motif frequencies and investigated if these frequencies are similar or not to the ones expected by chance with th help of null models.
-Then, we have also calculated the normalize group frequencies of plant and floral visitor for the different motif positions and investigated their overall representation and ecological implications by comparing the observed group frequencies on the different motif positions with simulated ones.
-Finally, we have tried to recover the observed motif combinations in empirical networks from their expected probability by assuming non-independence with the help of a simulation approach and z-scores.
+After, we have calculated the normalize motif frequencies and investigated if these frequencies are similar or not to the ones expected by chance with the help of null models.
+Then, we have also calculated the normalize group frequencies of plant and floral visitor for the different motif positions and investigated their overall representation by comparing these observed frequencies with their simulated counterparts.
+Finally, we have tried to recover the observed motif combinations from the expected frequencies calculated as the product of the probabilities of the different plant and floral visitor groups within each motif.
 
@@
 We have compiled 60 plant-pollinator networks from 18 different studies (**Table S1**).
-All studies sampled plant-pollinator interactions in natural systems and were selected based on wide geographical coverage and presence of interaction frequency as a measure of interaction strength.
+All studies sampled plant-pollinator interactions in natural systems and were selected based on wide geographical coverage (**Figure S1**) and presence of interaction frequency as a measure of interaction strength.
 In total, there were 503 plant species, 1,111 floral visitors species and 6,248 pairwise interactions registered.
@@
 All analyses were run considering singletons (species with only one interaction detected) but we conducted a second exploration without singletons (64.98$\%$ of interactions) to evaluate the effect of rare species on the observed patterns.
-Results without singletons are qualitatively consistent and are not further discussed in the main text (**Figures S1 and S2**).
+Results without singletons are qualitatively consistent and are not further discussed in the main text (**Figures S2 and S3**).
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, fig.pos="t", warning=FALSE,out.width="75%",fig.align="center", fig.cap="\\textbf{Figure 1.} Adapted figure of Simmons et al., 2019 with all the possible motifs from two to five species in bipartite networks.
-There is a total of 17 possible motifs with 46 different positions denoted within each node.", fig.width=10,fig.height=8}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, fig.pos="t", warning=FALSE,out.width="75%",fig.align="center", fig.cap="\\textbf{Figure 1.} (Adapted figure of Simmons et al., 2019).
+All possible motif network structures from two to five species in bipartite networks.
+There is a total of 17 possible motifs with 46 different positions denoted within each node.
+The different motifs are aggregated by their average path length classification wich goes from densely connected motifs (strong motifs coloured in yellow) to less connected motifs (weak motifs coloured in red).", fig.width=10,fig.height=8}
 library(tidyverse)
@@
 We used the group identifier as an explanatory variable and the study identifiers as a random intercept.
-Hence, we assessed the average motif frequency per species group, after controlling the variation at the study level.
+Hence, we assessed the average motif frequency per species group, after controlling for the variation at the study level.
 Finally, we visualized with the help of the package _ComplexHeatmap_ version _2.6.2_ [@gu2016] over- and under-representation of plant and floral visitor groups on the different motif positions.
@@
 
-The hierarchical cluster analysis divided the dataset into five different groups with different and overlapping characteristics (**Figure S3** and **Figure S4**).
+The hierarchical cluster analysis divided the dataset into five different groups with different and overlapping characteristics (**Figure S4** and **Figure S5**).
 The first group referred to as 'selfing herbs' consisted on herbs with hermaphroditic flowers with high levels of autonomous selfing.
@@
 First, for floral visitors, we found that bees had a tendency to appear with higher frequency on motif positions that involved generalism (i.e.
-lower specificity values) while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) showed the opposite trend with higher frequency on motif positions that implied a greater level of specialization (**Figure S5 A**).
-Although plants did not have as marked trends as floral visitors, all plant groups showed a slight tendency for generalism (**Figure S5 B**).
-Second, regarding the number of indirect interactions, bees and tall plants with unisexual flowers showed greater frequency on motif positions that involve low number of indirect interactions (**Figure S6 and Figure S7**).
-The rest of floral visitor groups showed the opposite tendency and had higher frequencies on motif positions with high number of indirect interactions (**Figure S6**).
-The rest of plant groups did not show major differences on their frequencies on motifs that implied different number of indirect interactions (**Figure S7**).
+lower specificity values) while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) showed the opposite trend with higher frequency on motif positions that implied a greater level of specialization (**Figure S6 A**).
+Although plants did not have as marked trends as floral visitors, all plant groups showed a slight tendency for generalism (**Figure S6 B**).
+Second, regarding the number of indirect interactions, bees and tall plants with unisexual flowers showed greater frequency on motif positions that involve low number of indirect interactions (**Figure S7 and Figure S8**).
+The rest of floral visitor groups showed the opposite tendency and had higher frequencies on motif positions with high number of indirect interactions (**Figure S7**).
+The rest of plant groups did not show major differences on their frequencies on motifs that implied different number of indirect interactions (**Figure S8**).
 
@@
 For instance, when we compare motifs with equal structure for both trophic levels, we found that floral visitors had always over-representation in the positions that implied the highest number of direct links.
-Despite this is in good agreement with the current view of the generalist nature of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of generalist network motifs was driven by the taxonomic group of bees (**Figure S5**) while the rest of the taxonomic groups tended to be under-represented.
+Despite this is in good agreement with the current view of the generalist nature of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of generalist network motifs was driven by the taxonomic group of bees (**Figure S6**) while the rest of the taxonomic groups tended to be under-represented.
 In contrast, non-bee groups were over-represented in motif positions associated with specialised roles.
@@
 
+\newpage
+
 # References

### 2022-03-23 Manuscript/Supplementary_Material/Supporting_information_Oikos.Rmd
edits

@@
 
-**Figure S1** Over and under-estimated motif frequencies.
-
-**Figure S2** Over and under-estimated groups on motif positions.
-
-**Figure S3** Plant trait composition of functional groups.
-
-**Figure S4** Dendrogram with plant functional groups.
-
-**Figure S5** Association between the frequency and specificity of the different groups on motif positions.
-
-**Figure S6** Frequency of floral visitor groups and number of indirect interactions per motif positions.
-
-**Figure S7** Frequency of plant groups and number of indirect interactions per motif positions.
+**Figure S1** Map with the plant-pollinator study locations.
+
+**Figure S2** Over and under-estimated motif frequencies.
+
+**Figure S3** Over and under-estimated groups on motif positions.
+
+**Figure S4** Plant trait composition of functional groups.
+
+**Figure S5** Dendrogram with plant functional groups.
+
+**Figure S6** Association between the frequency and specificity of the different groups on motif positions.
+
+**Figure S7** Frequency of floral visitor groups and number of indirect interactions per motif positions.
+
+**Figure S8** Frequency of plant groups and number of indirect interactions per motif positions.
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure S1.** Comparison of motif frequencies between empirical and simulated networks grouped by average path length (plots a, b, c and d) as determined in Simmons et al.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.cap="**Figure S1.** Map with the different locations of the plant-pollinator studies used in this work to explore woldwide patterns at the meso-scale level.
+For each study just one location is shown except for the study of Olesen that was conducted in two very different locations (Mauritius and Azores)."}
+
+#Create coordinate dataset for plotting
+
+longitude <- c("3.296797",  #1
+               "1.575532", #2
+               "9.275556", 
+               "18.5", #4
+               "99.63806", #5
+               "148.266667",
+               "-52", 
+               "-31", "57.43", #8
+               "-75.5", #9
+               "-57.885", #10
+               "55.447778",
+               "-6.16895", #12bart
+               "55.43333", #13
+               "57.733333",
+               "-68.015892", #15
+               "-89.8968771",
+               "171.756111",
+               "10.233333")
+
+latitude <- c("42.315336", #1
+              "52.762395", #2
+              "56.0725",
+              "68.35", #4
+              "27.90139", #5
+              "-36.45", #6
+              "71", #7
+              "39.4", "-20.25", #8
+              "45.4", #9
+              "-21.701111", #10
+              "-4.67",
+              "37.234966", #12bart
+              "-4.666667", #13
+              "-20.4538",
+              "-32.008985", #15
+              "39.278958",
+              "-43.035889",
+              "56.066667")
+
+id <- c("Bartomeus1", #1
+        "Dicks", #2
+        "Dupont", 
+        "Elberling", #4
+        "Fang", #5
+        "Inouye", #6
+        "Lundgren", #7
+        "Olesen", "Olesen", #8
+        "Small", #9
+        "Souza", #10
+        "Kaiser-Bunbury1", #
+        "Bartomeus2", #12
+        "Kaiser-Bunbury2", #13
+        "Kaiser-Bunbury3", #14
+        "Peralta", #15
+        "Burkle",
+        "Arroyo-Correa",
+        "Bundgaard")
+
+d <- data.frame(longitude, latitude, id)
+
+library("ggplot2")
+library("sf")
+library("rnaturalearth")
+library("rnaturalearthdata")
+
+world <- ne_countries(scale = "medium", returnclass = "sf")
+class(world)
+
+d$longitude <- as.numeric(d$longitude)
+d$latitude <- as.numeric(d$latitude)
+
+sf::sf_use_s2(FALSE)
+
+ggplot(data = world) +
+  geom_sf(fill="antiquewhite", color="grey49") +
+  xlab("Longitude") + ylab("Latitude") +
+  geom_jitter(data=d , aes(longitude,latitude, color=id), 
+              shape = 10,  fill = "white",size = 4, 
+              stroke = 1,width = 0.2, height = 3)+ 
+  theme(panel.grid.major = element_line(color = gray(.5), 
+linetype = "dashed", size = 0), panel.background = element_rect(fill = "aliceblue"))+
+  coord_sf(expand = FALSE) +  scale_y_continuous(breaks = c(-50,0, 50)) +
+  scale_x_continuous(breaks = c(-100,0, 100)) +
+  theme(legend.key.size = unit(0.3, 'cm'), legend.text = element_text(size=6),
+         legend.title = element_text(size=12))+
+  scale_colour_discrete(name = "Study \n locations")
+
+```
+
+\clearpage
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure S2.** Comparison of motif frequencies between empirical and simulated networks grouped by average path length (plots a, b, c and d) as determined in Simmons et al.
 (2020) without considering singletones.
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="\\textbf{Figure S2.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions after removing non-robust links (singletones).
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="\\textbf{Figure S3.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions after removing non-robust links (singletones).
 The different motif positions are dividied by the average path length clasification by Simmons et al.
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=7, fig.width=12, fig.cap="**Figure S3.** Plant functional group composition separated in qualitative and quantitative variables.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=7, fig.width=12, fig.cap="**Figure S4.** Plant functional group composition separated in qualitative and quantitative variables.
 Panel A) shows the percentage of the different categories within trait represented with different colours for each functional group.
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=13, fig.cap="**Figure S4.** Hierarchical clustering dendrogram with the branches coloured by the optimal number of clusters (5).
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=13, fig.cap="**Figure S5.** Hierarchical clustering dendrogram with the branches coloured by the optimal number of clusters (5).
 The labels of the subgroup of species (N = 524) used in this study are coloured in black in order to show the evenness of the distribution of the species across clusters.
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=12, fig.width=12, fig.align = 'center', fig.cap="\\textbf{Figure S5.} Association between the frequency and specificity on the different motif positions for floral visitor (panel A) and plant (panel B) groups.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=12, fig.width=12, fig.align = 'center', fig.cap="\\textbf{Figure S6.} Association between the frequency and specificity on the different motif positions for floral visitor (panel A) and plant (panel B) groups.
 The different numerical categories of the plant groups correspond to: 1 (selfing herbs), 2 (small outcrossing perennials), 3 (self-incompatible perennials with large flowers), 4 (tall plants with small unisexual flowers) and 5 (short-lived outcrossers with long zygomorphic flowers)."}
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S6.} Frequency of the different floral visitor groups on the different motif positions aggregated by the number of indirect interactions for the different motif positions."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S7.} Frequency of the different floral visitor groups on the different motif positions aggregated by the number of indirect interactions for the different motif positions."}
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S7.} Frequency of the different plant groups on the different motif positions aggregated by the number of indirect interactions for the different motif positions."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S8.} Frequency of the different plant groups on the different motif positions aggregated by the number of indirect interactions for the different motif positions."}
 

### 2022-03-23 Scripts/Supplementary_Material/Table_S1.R

@@ -30,7 +30,66 @@ DOI <- c("https://doi.org/10.1007/s00442-007-0946-1", "https://doi.org/10.1046/j
          "https://doi.org/10.1126/science.1232728", "https://doi.org/10.1111/1365-2745.13332", "Unpublished, Master thesis")
 
 
-references <- data.frame(`First author`, Year, `Number of networks`,   DOI)
+longitude <- c("3.296797",
+               "1.575532",
+               "9.275556", 
+               "18.5", 
+               "99.63806", 
+               "148.266667",
+               "-52", 
+               "-31", "57.43",
+               "-75.5",
+               "-57.885",
+               "55.447778",
+               "-6.16895",
+               "55.433333",
+               "57.733333",
+               "57.4024",
+               "-68.015892",
+               "-89.8968771",
+               "171.756111",
+               "10.233333")
+
+latitude <- c("42.315336",
+              "52.762395",
+              "56.0725",
+              "68.35", 
+              "27.90139", 
+              "-36.45",
+              "71", 
+              "39.4", "-20.25",
+              "45.4",
+              "-21.701111",
+              "-4.67",
+              "37.234966",
+              "-4.666667",
+              "-22.7",
+              "-20.4538",
+              "-32.008985",
+              "39.278958",
+              "-43.035889",
+              "56.066667")
+
+id <- c("Bartomeus1", 
+        "Dicks",
+        "Dupont", 
+        "Elberling", 
+        "Fang", 
+        "Inouye", 
+        "Lundgren", 
+        "Olesen", "Olesen",
+        "Small",
+        "Souza",
+        "Kaiser-Bunbury1",
+        "Bartomeus2",
+        "Kaiser-Bunbury2",
+        "Kaiser-Bunbury3",
+        "Peralta",
+        "Burkle",
+        "Arroyo-Correa",
+        "Bundgaard")
+
+references <- data.frame(`First author`, Year, `Number of networks`,DOI)
 
 colnames(references) <- c("First author", "Year", "Number of networks",  "DOI")
 

### 2022-03-23 Manuscript/Supplementary_Material/Supporting_information_Oikos.Rmd
edits

@@
               "71", #7
-              "39.4", "-20.25", #8
+              "39.4", "-23.25", #8 #modified for visibility of ovelapping
               "45.4", #9
               "-21.701111", #10
-              "-4.67",
+              "-7.67",#11 #modified for visibility of ovelapping
               "37.234966", #12bart
@@
               "-43.035889",
-              "56.066667")
+              "59.066667")#18 #modified for visibility of ovelapping
 
@@
 
+#these colors come from the library(pals)- labs = c('alphabet')
+
+colors <- c("#FFA405", "#0075DC", "#993F00", "#4C005C", "#5EF1F2", 
+        "#005C31", "#2BCE48", "black", "lightblue", "#94FFB5", 
+        "#8F7C00", "#9DCC00", "#C20088", "#003380", "gold1", 
+        "#FFA8BB", "#426600", "#FF0010", "#191919")
+
+set.seed(12)
 ggplot(data = world) +
@@
   xlab("Longitude") + ylab("Latitude") +
-  geom_jitter(data=d , aes(longitude,latitude, color=id), 
-              shape = 10,  fill = "white",size = 4, 
-              stroke = 1,width = 0.2, height = 3)+ 
+  geom_point(data=d , aes(longitude,latitude,  color=id),  shape=10,
+           size = 3.5, stroke=1)+ 
   theme(panel.grid.major = element_line(color = gray(.5), 
@@
   scale_x_continuous(breaks = c(-100,0, 100)) +
-  theme(legend.key.size = unit(0.3, 'cm'), legend.text = element_text(size=6),
+  theme(legend.key.size = unit(0.5, 'cm'), legend.text = element_text(size=6),
          legend.title = element_text(size=12))+
-  scale_colour_discrete(name = "Study \n locations")
+  scale_colour_discrete(name = "Study \n locations") +   scale_colour_manual(
+    values = colors)
 

### 2022-03-23 Manuscript/Main_text/Main_text_Oikos.Rmd
edits

@@
 We calculated which plant and floral visitor groups were over- or under-represented in the different motif positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
-To estimate the position frequencies of each plant and floral visitor group in a given network, we added the frequencies of those species that belong to the same group, and then, we normalised the resulting frequencies by dividing them by the total number of times that a corresponding group appears in any position within the same motif size class.
+To estimate the position frequencies of each plant and floral visitor group in a given network, we added the frequencies of those species that belong to the same group, and then, we normalised the resulting frequencies by dividing them by the total number of times that a corresponding group appears in any position within the same motif size class (i.e., number of species of a motif).
 Then, we calculated the percentile of the observed position frequencies for each group and network, just like we did with motif frequencies.
@@
 To understand if the different plant and floral visitor groups are associated with motif positions that represent different network roles we characterized the network roles of plant and floral visitor groups in terms of their specialization and number of indirect interactions.
-To that end, we calculated the specificity as a measure of specialization and we use the number of indirect interactions of the different motif positions to evaluate the association of these two node metrics and the group frequencies for the different motif positions.
+To that end, we calculated the specificity as a measure of specialization and we used the number of indirect interactions of the different motif positions to evaluate the association of these two node metrics and the group frequencies for the different motif positions.
 First, specificity ($s_i$) was calculated for each motif position following @poisot2015 as $s_i = L - l_i / L - 1$, where $L$ is the total number of groups and $l_i$ the number of interaction partners of the group $i$ in a given motif.
@@
 Finally, we studied which combinations of plant and floral visitor groups tend to appear together within the same motifs (up to five nodes).
-That is which combinations are over- or under-represented.
-This analysis use 57 out of the 60 networks available due to computational limitations to identify all the nodes in the motifs of the three networks with the highest number of links.
-To do so, for each of the 53,250 possible motif combinations, we estimated the observed and the expected probability of finding those combination in empirical networks, respectively.
+That is, which combinations are over- or under-represented.
+This analysis used 57 out of the 60 networks available due to computational limitations to identify all the nodes in the motifs of the three networks with the highest number of links.
+To do so, for each of the 53,250 possible motif combinations, we estimated the observed and the expected probability of finding those combinations in empirical networks, respectively.
 Then, we determined whether the observed probabilities are likely to come from the expected probabilities or not.
@@
 First, we calculated the number of times that the group $x$ appears in the position $\alpha$ in each empirical network $\eta$, denoted as $n_i^{\eta}(x,\alpha)$.
-Then, by controlling the variation at the network level, we assessed the average value of the absolute frequency of group $x$ appears in the position $\alpha$, $n_i(x,\alpha) = E\left [ n_i^{\eta}(x,\alpha) \right ]$, and estimated $p_i(x,\alpha)$ as $p_i(x,\alpha) = n_i(x,\alpha)/\sum_{k}n_i(k,\alpha)$.
+Then, by controlling for the variation at the network level, we assessed the average value of the absolute frequency with which group $x$ appears in the position $\alpha$, $n_i(x,\alpha) = E\left [ n_i^{\eta}(x,\alpha) \right ]$, and estimated $p_i(x,\alpha)$ as $p_i(x,\alpha) = n_i(x,\alpha)/\sum_{k}n_i(k,\alpha)$.
 To obtain $n_i(x,\alpha)$, we fitted a LMM per motif position, where the response variable was the number of times that a given position was observed per network, the explanatory variable was the group identifier, and the random intercept was given by network identifiers nested within the study identifiers.
@@
 The first group referred to as 'selfing herbs' consisted on herbs with hermaphroditic flowers with high levels of autonomous selfing.
-The second group named 'small outcrossing perennials' had small perennial species with a mixed of life forms (i.e., trees shrubs and herbs) with outcrossing hermaphroditic flowers.
+The second group named 'small outcrossing perennials' had small perennial species with a mix of life forms (i.e., trees shrubs and herbs) with outcrossing hermaphroditic flowers.
 The third group referred to as 'self-incompatible perennials with large flowers' comprised perennial species with a mixed of life forms and large self-incompatible hermaphroditic flowers with high number of ovules.

### 2022-03-23 Manuscript/Main_text/Main_text_Oikos.Rmd
check edits tomorrow

@@
 
-To investigate the structure of the meso-scale in plant-pollinator networks, we have gathered published plant-pollinator networks with worldwide distribution.
-Then, we have divided the plant and floral visitor species from these networks into groups that summarize their main life-history strategies.
-After, we have calculated the normalize motif frequencies and investigated if these frequencies are similar or not to the ones expected by chance with the help of null models.
-Then, we have also calculated the normalize group frequencies of plant and floral visitor for the different motif positions and investigated their overall representation by comparing these observed frequencies with their simulated counterparts.
-Finally, we have tried to recover the observed motif combinations from the expected frequencies calculated as the product of the probabilities of the different plant and floral visitor groups within each motif.
+To investigate the structure of the meso-scale in plant-pollinator networks, we gathered published plant-pollinator networks with worldwide distribution.
+Then, we classified the plant and floral visitor species from these networks into groups that summarize their main life-history strategies.
+After, we calculated the normalized motif frequencies and investigated if these frequencies are similar or not to the ones expected by chance with the help of null models.
+Then, we also calculated the normalized group frequencies of plant and floral visitor for the different motif positions and investigated their overall representation by comparing these observed frequencies with their simulated counterparts.
+Finally, we tried to recover the observed motif combinations from the expected frequencies calculated as the product of the probabilities of the different plant and floral visitor groups within each motif.
 
@@
 However, common analytical approaches at the node or at the full network level are unable to capture the full complexity of ecological systems [@simmons2019; @bergamo2021].
-Because network motifs can capture both direct and indirect interactions, by analysing over- and under-representation of motifs we are able to explore in greater detail ecological interactions [@stouffer2007].
-We have explored for the first time the overall structure and representation of network motifs in real plant-pollinator networks at a macro-ecological scale and shown that the different motifs up to five nodes are consistently over- or under-represented in comparison with simulated networks indicating the presence of ecological processes shaping their structure.
+Because network motifs can capture both direct and indirect interactions, by analysing over- and under-representation of motifs we are able to explore in great detail the structure of interactions of plant-pollinator networks.
+We have explored for the first time the overall structure and representation of network motifs in real plant-pollinator networks at a macro-ecological scale and shown that the different motifs up to five nodes are consistently over- or under-represented in comparison with simulated networks, therefore indicating the presence of ecological processes shaping their structure.
 Despite the presence of multiple ecological processes likely operating at the same time (e.g., neutral effects, morphological matching or phenological overlap), we found a tendency for over-represented structures with more densely connected motifs (i.e., complete, fan and asymmetric complete).
@@
 For instance, when we compare motifs with equal structure for both trophic levels, we found that floral visitors had always over-representation in the positions that implied the highest number of direct links.
-Despite this is in good agreement with the current view of the generalist nature of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of generalist network motifs was driven by the taxonomic group of bees (**Figure S6**) while the rest of the taxonomic groups tended to be under-represented.
+Despite this being in good agreement with the current view of the generalist nature of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of generalist network motifs was driven by the taxonomic group of bees (**Figure S6**) while the rest of the taxonomic groups tended to be under-represented.
 In contrast, non-bee groups were over-represented in motif positions associated with specialised roles.
@@
 For instance, taxonomic diversity and trait availability limit our ability to properly represent the wide range of reproductive strategies [@dellinger2020] and different clustering analysis can lead to distinct outcomes (e.g., k-means and hierarchical clustering).
-Further, here we divided floral visitors on the taxonomic rank level because it represented adequately the pollinator species ecological roles without the need of the tremendous effort of compiling trait data for over 1000 species of floral visitors.
+Further, here we divided floral visitors on the taxonomic rank level because it represented adequately pollinator ecological roles without the tremendous effort of compiling trait data for over 1000 species of floral visitors.
 However, further groupings with traits could help revealing greater relevance of trait-matching processes on indirect interactions.

### 2022-03-24 Manuscript/Main_text/Main_text_Functional_Ecology.Rmd
Project organization

--- 2022-03-23 Manuscript/Main_text/Main_text_Oikos.Rmd
@@
 ---
-title: "The non-random assembly of functional motifs in plant-pollinator networks worldwide"
+title: "The non-random assembly of functional motifs in  \nplant-pollinator networks"
 editor_options:
@@
 Despite the presence of multiple ecological processes likely operating at the same time (e.g., neutral effects, morphological matching or phenological overlap), we found a tendency for over-represented structures with more densely connected motifs (i.e., complete, fan and asymmetric complete).
-As suggested in @simmons2020, a higher proportion of these densely connected motifs could reflect that neutral effects are the predominant ecological process governing the structure of these network motifs.
+As suggested in @simmons2020, a higher proportion of these densely connected motifs could reflect that neutral effects are the predominant ecological process governing the structure of network motifs.
 Thus, as indicated for other network properties like nestedness at the macro-scale level [@krishna2008; @suweis2013], species relative abundances (i.e., neutral effects) may be also the predominant ecological process governing the meso-scale structure on plant-pollinator networks.

### 2022-03-24 Scripts/trial_motif_positions.R

@@ -1,82 +1,0 @@
-
-equidistribution <- function(number_nodes){
-  
-  x_width <- 5.5/(number_nodes+1)
-  
-  x_result <- rep(-1.5,number_nodes)
-  
-  for(i in 1:number_nodes){
-    
-    x_result[i] <- x_result[i] + i*x_width
-    
-  }
-  
-  return(x_result)
-  
-}
-
-
-
-plot_motif_positions <- function(motif_number){
-  
-  motifs_raw_data <- read_csv("Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-  motif_data <- motifs_raw_data %>% filter(motif_id == motif_number)
-  
-  
-  # Create dataframe with node positions
-  
-  labdown = motif_data$plant %>% unique()
-  
-  
-  xdown = equidistribution(length(labdown))
-  
-  ydown = rep(0,length(labdown))
-  
-  labup = motif_data$pollinator %>% unique()
-  
-  xup = equidistribution(length(labup))
-  
-  yup = rep(1,length(labup))
-  
-  d_nodes=data.frame(x=c(xdown,xup),
-                     y=c(ydown,yup),
-                     label = c(labdown,labup))
-  
-  
-  # Create a dataframe with links
-  
-  plant_positions <- data.frame(plant = labdown,
-                                xdown = xdown,
-                                ydown = ydown)
-  
-  pollinator_positions <- data.frame(pollinator = labup,
-                                     xup = xup,
-                                     yup = yup)
-  
-  link_df <- motif_data %>% left_join(plant_positions, by = "plant") %>% 
-    left_join(pollinator_positions, by = "pollinator")
-  
-  # Before plotting the motif, we remove letters from the node position id
-  
-  d_nodes$label <- gsub("[^0-9.-]", "", d_nodes$label)
-  
-  ggplot(data=d_nodes, aes(x, y)) +
-    scale_shape_identity() +
-    geom_segment(data = link_df, aes(x=xdown, y=ydown, xend = xup, yend = yup), size = 1, color = "grey20")+
-    geom_point(aes(color = as.factor(label)),size=10, color = "azure2")+
-    geom_text(aes(x, y , label = label),size=3)+
-    #   scale_color_brewer(palette = "Set2")+
-    xlim(-1.5,4)+ ylim(-0.5,1.5)+
-    theme(panel.background = element_blank(),
-          axis.text.x=element_blank(),
[…]

### 2022-03-24 Manuscript/Main_text/Main_text_Functional_Ecology.Rmd
Functional Ecology bib style

@@
 biblio-style: apalike
-csl: oikos.csl #oikos style from zotero styles
+csl: functional-ecology.csl #funct. ecol. style from zotero styles
 ---
@@
 There is a total of 17 possible motifs with 46 different positions denoted within each node.
-The different motifs are aggregated by their average path length classification wich goes from densely connected motifs (strong motifs coloured in yellow) to less connected motifs (weak motifs coloured in red).", fig.width=10,fig.height=8}
+The different motifs are aggregated by their average path length classification wich goes from densely connected motifs (strong motifs coloured in yellow) to less connected motifs (weak motifs coloured in red).
+Note that two node motifs are excluded from this classification.", fig.width=10,fig.height=8}
 library(tidyverse)
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', out.width="80%",fig.cap="\\textbf{Figure 3.} Heatmap indicating under- and over-representation of floral visitor and plant groups in the different motif positions.
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', out.width="80%",fig.cap="\\textbf{Figure 3.} Heatmap indicating under- and over-representation of floral visitor and plant groups in the different motif positions (numbers on the right of each heatmap).
 The different motif positions are dividied by the average path length clasification determined by Simmons et al.

### 2022-03-24 Scripts/Data_Exploration_Figure_5.R
Project cleaning

@@ -1,99 +1,0 @@
-
-
-library(tidyverse)
-library(RColorBrewer)
-
-# Data with pollinator/plant labels
-
-plant_means_reordered <- read_csv("Data/Csv/plant_abs_freq_means.csv")
-pollinator_means_reordered <- read_csv("Data/Csv/pollinator_abs_freq_means.csv")
-#Filter out in order to have just 6 FG'S
-pollinator_means_reordered <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds", "Lizards", "Other_insects"))
-
-
-####################################################################################################
-#Read data to check top 5 motif of each category of observed propabilities
-
-#Under, No signi, Over-rep
-####################################################################################################
-# Check top Z-scores of each group (Under, No diff, Over)
-
-#Read data
-data <- read.csv("Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
-
-#Find critical value of Z-score
-p <- 0.05 #cutoff probability 95% confidence
-critical_value <- qnorm(p/2) #double tail probability divide by 2
-
-data_1 <- data %>%
-  mutate(infra_over_represented = case_when(
-    z_score < -abs(critical_value) ~ "infra",
-    between(z_score, -abs(critical_value), abs(critical_value)) ~ "no_diff",
-    z_score > abs(critical_value) ~ "over"
-  ))
-
-
-#data_2 <- filter(data_1, abs(z_score)<2000) 
-#str(data_2)
-
-
-#Add number of nodes of each motif
-data_1$N_node
-data_1$N_node[data_1$motif=="1"] <- 2 # 2 SPECIES
-data_1$N_node[data_1$motif=="2"] <- 3 # 3 SPECIES
-data_1$N_node[data_1$motif=="3"] <- 3
-data_1$N_node[data_1$motif=="4"] <- 4 # 4 SPECIES
-data_1$N_node[data_1$motif=="5"] <- 4
-data_1$N_node[data_1$motif=="6"] <- 4
-data_1$N_node[data_1$motif=="7"] <- 4
-data_1$N_node[data_1$motif=="8"] <- 5 # 5 SPECIES 
-data_1$N_node[data_1$motif=="9"] <- 5
-data_1$N_node[data_1$motif=="10"] <- 5
-data_1$N_node[data_1$motif=="11"] <- 5
-data_1$N_node[data_1$motif=="12"] <- 5
[…]

### 2022-03-25 Scripts/Richness_VS_position_frequencies.R
Create Richness_VS_position_frequencies.R

@@ -1,0 +1,47 @@
+
+library(tidyverse)
+library(lme4)
+library(nlme)
+library(RColorBrewer)
+
+# Estimate pollinator richness per network
+
+int.threshold <- 1
+
+networks <- read_csv("Data/Csv/data_for_motifs_analysis_1.csv") %>% select(-X1) %>%
+  filter(Interaction >= int.threshold)
+
+pollinator_richness <- networks %>% select(Network_id,Pollinator_species,Pollinator_functional_group) %>%
+  unique() %>% group_by(Network_id,Pollinator_functional_group) %>% count() %>% 
+  rename(pollinator_richness = n, Node_FG = Pollinator_functional_group)
+
+
+# Extract information about the positions
+file_pos <- "Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv"
+all_position_percentiles <- read_csv(file_pos)
+
+# Create different dataframes for plant and pollinators, and remove data for postions np1 and np2,
+# and leave only those positions that can be occupied either by plants or poll. 
+list_plants_FG <- as.character(1:10)
+
+pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
+  filter(!Node_FG %in% list_plants_FG, !position %in% c("np1","np2"),
+         !is.na(expected_freq_its_GF))
+
+pollinator_position_richness <- pollinator_position_percentiles_filtered %>%
+  left_join(pollinator_richness, by = c("Network_id","Node_FG")) %>%
+  mutate(log10_ob_frec = log10(observed_freq), log10_richness = log10(pollinator_richness))
+
+
+# Plot positions
+
+ggplot(pollinator_position_richness %>% filter(! Node_FG %in% c("Birds","Lizards","Other_insects")), 
+       aes(x = pollinator_richness, y = observed_freq, color = Node_FG))+
+  geom_point(alpha=0.3)+
+  geom_smooth(method = "lm", formula = y~x)+
+  facet_wrap(~position,scales = "free")+
+  scale_color_brewer(palette = "Set1")+
+  labs(x="Richness",y="Observed frequencies", color="Group")+
+  theme_bw()
+
+unique(pollinator_position_richness$Node_FG )

### 2022-03-25 Scripts/Richness_VS_position_frequencies.R
Update Richness_VS_position_frequencies.R

@@ -3,7 +3,7 @@ library(tidyverse)
 library(lme4)
 library(nlme)
 library(RColorBrewer)
-
+library(stringi)
 # Estimate pollinator richness per network
 
 int.threshold <- 1
@@ -32,16 +32,50 @@ pollinator_position_richness <- pollinator_position_percentiles_filtered %>%
   left_join(pollinator_richness, by = c("Network_id","Node_FG")) %>%
   mutate(log10_ob_frec = log10(observed_freq), log10_richness = log10(pollinator_richness))
 
+###########################
+# ESTIMATING SPECIFICITY
+###########################
+# Reference: 10.1371/journal.pone.0114674
+
+motif_pattern_connections <- read_csv("Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
+
+number_plant <- motif_pattern_connections %>% group_by(motif_id,plant) %>% 
+  count() %>% group_by(motif_id) %>% count() %>% rename(number_plants = n)
+
+number_pollinator <- motif_pattern_connections %>% group_by(motif_id,pollinator) %>% 
+  count() %>% group_by(motif_id) %>% count() %>% rename(number_pollinators = n)
+
+specificity_pollinator_aux <- motif_pattern_connections %>% 
+  group_by(motif_id,pollinator) %>% count()
+
+specificity_pollinator_aux$position <- stri_extract_first_regex(specificity_pollinator_aux$pollinator,
+                                                                "[0-9]+") %>% as.numeric()
+
+specificity_pollinator_aux2 <- specificity_pollinator_aux %>% 
+  left_join(number_plant, by = "motif_id")
+
+specificity_pollinator <- specificity_pollinator_aux2 %>% ungroup %>%
+  mutate(s=(number_plants-n)/(number_plants-1)) %>%
+  select(position,s) %>% unique() %>% mutate(position=paste0("np",position))
+
+# We replace NaN of some specialist positions by one
+specificity_pollinator$s[is.nan(specificity_pollinator$s)] <- 1.0
+
+
+pollinator_position_richness_specifity <- pollinator_position_richness %>%
+  left_join(specificity_pollinator, by = c("position"))
 
 # Plot positions
+specificity_pollinator_panels <- unique(pollinator_position_richness_specifity[,c('s','position')])
 
-ggplot(pollinator_position_richness %>% filter(! Node_FG %in% c("Birds","Lizards","Other_insects")), 
[…]

### 2022-03-27 Manuscript/Main_text/Main_text_Functional_Ecology.Rmd
edits
Final comments on my end!

@@
 Ecological processes leave distinct structural imprints on the species interactions that shape the topology of mutualistic networks.
-Detecting those relationships is not trivial since they go beyond pairwise interactions that may get blurred when considering full network descriptors.
+Detecting those relationships is not trivial since they go beyond pairwise interactions, but may get blurred when considering full network descriptors.
 Recent work has shown the network meso-scale can capture this important information.
@@
 Despite the possible implications of network motifs to better capture species interactions, they remain overlooked in natural plant-pollinator networks.
-By exploring 60 empirical plant-pollinator networks from 18 different studies with wide geographical coverage we show that some motifs are consistently under- and over-represented worldwide, suggesting that the building blocks of plant-pollinator networks are not random.
+By exploring 60 empirical plant-pollinator networks from 18 different studies with wide geographical coverage we show that some motifs are consistently under- or over-represented worldwide, suggesting that the building blocks of plant-pollinator networks are not random.
 Furthermore, we find that distinct motif positions describing species ecological roles (e.g., generalization and number of indirect interactions) are occupied by different plant and floral visitor groups on both trophic levels.
-Bees appear consistently in generalist motif positions with low number of indirect interactions while the rest of floral visitor groups are associated with more specialised motif positions with higher number of indirect interactions.
+Bees appear consistently in generalised motif positions with low number of indirect interactions while the rest of floral visitor groups are associated with more specialised motif positions with higher number of indirect interactions.
 All plant groups are principally associated with specialised motif positions but only tall plant species with separated sexes (e.g., woody dioecious or monoecious species) are associated with lower number of indirect interactions.
@@
 In addition, the local species position within the network can define its degree of specialization [@bluthgen2006] or its role in connecting the rest of the community [@olesen2007].
-Despite the unquestionable progress with the use of these metrics at both species and network level, condensing the information into a single metric implies the loss of relevant ecological information that obscures the understanding of species interactions [@cirtwill2018; @simmons2019].
+Despite the unquestionable progress with the use of these metrics at both species and network level, condensing complex information into a single metric implies the loss of relevant ecological information that obscures the understanding of species interactions [@cirtwill2018; @simmons2019].
 
 Traditionally, plant-pollinator research has focused on direct interactions but overlooked indirect interactions (i.e., the mediated effect between two species by a third species), such as facilitative or competitive interactions between plants for pollinators [@moeller2004; @sargent2008; @carvalheiro2014].
-Despite the widespread nature of indirect interactions in ecological communities [@strauss1991], plant-pollinator research often fails to finely capture those indirect interactions with the conventional analytical tools that condense the information either by species (e.g., interaction frequency) or in global topological indices (e.g., nestedness).
+Despite the widespread nature of indirect interactions in ecological communities [@strauss1991], plant-pollinator research often fails to finely capture those indirect interactions with the conventional analytical tools that condense the information either by species (e.g., degree) or in global topological indices (e.g., nestedness).
 Nonetheless, the emerging framework of network motifs (small sub-networks observed within a given network) in plant-pollinator research allows to consider both direct and indirect interactions [@simmons2019].
@@
 After, we calculated the normalized motif frequencies and investigated if these frequencies are similar or not to the ones expected by chance with the help of null models.
-Then, we also calculated the normalized group frequencies of plant and floral visitor for the different motif positions and investigated their overall representation by comparing these observed frequencies with their simulated counterparts.
+Then, we calculated the normalized group frequencies of plant and floral visitor for the different motif positions and investigated their overall representation by comparing these observed frequencies with their simulated counterparts.
 Finally, we tried to recover the observed motif combinations from the expected frequencies calculated as the product of the probabilities of the different plant and floral visitor groups within each motif.
@@
 In addition, we excluded two-node motifs (or links) from our analyses because their normalised frequencies would always equal one.
+Note that the aim is not comparing different networks, which may differ in sampling effort, but correctly describing the structure of each individual network.
 Like @simmons2020, we classified the different motifs by their average path length (mean number of links between all pairs of nodes) into four different groups: (i) complete or strong ($\overline{x} = 1.38$), (ii) fan or medium-strong ($\overline{x} = 1.48$), (iii) assymmetric complete or medium-weak ($\overline{x} = 1.60$) and (iv) core-peripheral or weak ($\overline{x} = 1.85$).
@@
 Generated networks had the same number of plants and floral visitors, as well as the same connectance of their corresponding empirical networks.
-We discarded null models with more constraints (e.g., constraining for species degree) because the permutations did not generate sufficient variablity providing highly similar or identical networks to the original ones.
+We discarded null models with more constraints (e.g., constraining for species degree) because the permutations did not generate sufficient variablity and provided highly similar or identical networks to the original ones.
 After extracting the motif frequencies from the simulated networks, for each motif type and empirical network, we calculated the percentage of simulated networks whose frequencies were smaller than the ones observed, that is, we estimated the percentile of the observed motif frequencies.
@@
 To summarize general patterns across networks, we used an intercept-only linear mixed model (LMM) per motif with the help of the package lmer version _1.1-21_ [@bates2015], where the response variable was the observed motif percentile per network.
+Note that as we are only interestedin modelling the intercept value, no predictors were specified.
 In these models, we used the study identifiers in **Table S1** as a random intercept.
@@
 
-To understand if the different plant and floral visitor groups are associated with motif positions that represent different network roles we characterized the network roles of plant and floral visitor groups in terms of their specialization and number of indirect interactions.
-To that end, we calculated the specificity as a measure of specialization and we used the number of indirect interactions of the different motif positions to evaluate the association of these two node metrics and the group frequencies for the different motif positions.
+To understand if the different plant and floral visitor groups are associated with motif positions that represent different network roles we characterized the roles of each motif positions for plant and floral visitor groups in terms of their specialization and number of indirect interactions.
+To that end, we calculated the specificity of each motif positions as a measure of specialization and we used the number of indirect interactions of the different motif positions to evaluate the association of these two position metrics and the group frequencies for the different motif positions.
 First, specificity ($s_i$) was calculated for each motif position following @poisot2015 as $s_i = L - l_i / L - 1$, where $L$ is the total number of groups and $l_i$ the number of interaction partners of the group $i$ in a given motif.
 Values of the vector s, range between 1, complete specialization (1 partner within the motif) and 0, complete generalism (all possible partners within the motif).
-Then, we explored graphically through linear models the association between the frequency of the different groups (response variable) and specificy (predictor).
+Then, we explored through linear models the association between the frequency of the different groups (response variable) and specificity (predictor) [NO RANDOMS HERE?
+WHY]().
 Second, we calculated the number of indirect interactions for each motif position by accounting only for the indirect effect of two species by a third species.
 That is, we explored exclusively indirect interactions within plants though shared floral visitors or within floral visitors though shared plants.
+[NO ANALYSIS HERE?
+WHY?
+HOW DO YOU USE THIS VALUE?]()
 
@@
 
-For both floral visitor and plant groups we found different frequencies on motif positions that implied different ecological roles.
-First, for floral visitors, we found that bees had a tendency to appear with higher frequency on motif positions that involved generalism (i.e.
+For both floral visitor and plant groups we found that their observed frequencies on motif positions are linked to different ecological roles.
+First, for floral visitors, we found that bees had a tendency to appear in higher frequencies on motif positions that involved generalism (i.e.
 lower specificity values) while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) showed the opposite trend with higher frequency on motif positions that implied a greater level of specialization (**Figure S6 A**).
@@
 The rest of floral visitor groups showed the opposite tendency and had higher frequencies on motif positions with high number of indirect interactions (**Figure S7**).
-The rest of plant groups did not show major differences on their frequencies on motifs that implied different number of indirect interactions (**Figure S8**).
+The rest of plant groups did not show major differences on their frequencies on motifs that implied different number of indirect interactions (**Figure S8**).[Aqui no entiendo por que no haces un solo modelo freq ~ generalism + nº of links]()
 
@@
 As suggested in @simmons2020, a higher proportion of these densely connected motifs could reflect that neutral effects are the predominant ecological process governing the structure of network motifs.
-Thus, as indicated for other network properties like nestedness at the macro-scale level [@krishna2008; @suweis2013], species relative abundances (i.e., neutral effects) may be also the predominant ecological process governing the meso-scale structure on plant-pollinator networks.
+Thus, as indicated for other network properties like nestedness at the macro-scale level [@krishna2008; @suweis2013], or interaction probability at the species level [@bartomeus2016](CHECK), species relative abundances (i.e., neutral effects) may be also the predominant ecological process governing the meso-scale structure on plant-pollinator networks.
 
@@
 In contrast, non-bee groups were over-represented in motif positions associated with specialised roles.
-This large effect of bees on the overall patterns is no surprise, as bees were the group with the largest number of interaction records in the whole set of networks as also shown for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017].
+This large effect of bees on the overall patterns is no surprise, as bees were the group with the largest number of interaction records in the whole set of networks as also shown for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017][can you check if this is worth citing here: https://royalsocietypublishing.org/doi/full/10.1098/rspb.2017.2140]().
 Interestingly, bees also were the group with lower number of indirect interactions while the rest of floral visitor groups showed clearly higher number of indirect interactions possibly indicating that these non-bee floral visitor groups may experience higher competitive interactions for floral resources [@thomson2020].
@@
 This tendency towards specialist roles may be the result of co-evolutionary processes (e.g., trait-matching) between plants and pollinators to optimise pollen transfer [@moreira2019].
-Remarkably, just tall plants with small unisexual flowers showed higher frequencies on motifs that were associated with low number of indirect interactions with likely direct implications on pollen transfer for this group that needs to guarantee cross-pollination.
+Remarkably, only tall plants with small unisexual flowers showed higher frequencies on motifs that were associated with low number of indirect interactions with likely direct implications on pollen transfer for this group that needs to guarantee cross-pollination.
 
@@
 
-In conclusion, by following the framework of @simmons2020 we have been able to explore competitive and facilitative interactions in plant-pollinator networks worldwide and found that indirect interactions are non-random and are more strongly related to neutral processes than any other ecological process.
+In conclusion, by following the framework of @simmons2020 we have been able to explore competitive and facilitative interactions in plant-pollinator networks worldwide and found that indirect interactions are non-random and are more strongly related to neutral processes than to any other ecological process.
 Further, we found that plant and floral visitor groups are associated with different motif positions that involve distinct ecological roles (e.g., generalization versus specialization) and that the different motif combinations are strongly constrained.
-Although in this study we do not predict indirect interactions, our work is a first step to elucidate novel interactions beyond pairwise interactions.
+Global change drivers are reshuffling ecological communities [REF]().
+Although we are still far to predict how this new combinations of species will interact, our work is a first step to elucidate how nove interactions will form beyond pairwise interactions.
 
@@
 All data and code would be deposited at Driad Digital repository upon acceptance.
+For the review process we have added our plant dataset on google sheets and can be accessed with the help of the following link: https://docs.google.com/spreadsheets/d/1q3fFNwHb7k-kpLzxfgnAHGNUrdOiUnCRQU13NKXzTX4/edit?usp=sharing
 

### 2022-03-27 Scripts/Scripts_Alfonso/specificity_VS_position_frequencies.R
Update specificity_VS_position_frequencies.R

@@ -242,4 +242,24 @@ p1/p2
 write.csv(pollinator_means_reordered_s_1, "Data/Csv/pollinator_means_reordered_s_1.csv")
 write.csv(plant_means_s, "Data/Csv/plant_means_s.csv")
 
+library(glmmTMB)
+library(performance)
+m_lm_pos_poll <- glmmTMB(mean~s*Node_FG, data = pollinator_means_reordered_s_1,
+                         family = beta_family())
+summary(m_lm_pos_poll)
+r2(m_lm_pos_poll)
 
+m_lm_pos_poll_rd <- glmmTMB(mean ~ s + (1|Node_FG), data = pollinator_means_reordered_s_1,
+                            family = beta_family())
+
+summary(m_lm_pos_poll_rd)
+r2(m_lm_pos_poll_rd)
+
+library(visreg)
+visreg2d(m_lm_pos_poll, "Node_FG","s",scale ="response")
+visreg(m_lm_pos_poll,"s",scale ="response")
+visreg(m_lm_pos_poll,"Node_FG",scale ="response")
+
+visreg2d(m_lm_pos_poll_rd, "Node_FG","s",scale ="response")
+visreg(m_lm_pos_poll_rd,"s",scale ="response")
+visreg(m_lm_pos_poll_rd,"Node_FG",scale ="response")

### 2022-03-28 Scripts/Scripts_Alfonso/specificity_VS_position_frequencies.R
Update specificity_VS_position_frequencies.R

@@ -263,3 +263,42 @@ visreg(m_lm_pos_poll,"Node_FG",scale ="response")
 visreg2d(m_lm_pos_poll_rd, "Node_FG","s",scale ="response")
 visreg(m_lm_pos_poll_rd,"s",scale ="response")
 visreg(m_lm_pos_poll_rd,"Node_FG",scale ="response")
+
+
+#---------------------------------
+# Analisys with LMMs all obs. freq. per position and study
+library(lme4)
+library(performance)
+
+pollinator_freq_position_s <- pollinator_position_percentiles_filtered %>% 
+  left_join(specificity_pollinator, by = "position") %>% mutate(position=as.factor(position))
+
+pollinator_freq_position_s$s[is.nan(pollinator_freq_position_s$s)] <- 1.0
+
+model_freq_specif1 <- lmer(observed_freq ~ s*Node_FG+(1|Network_id), 
+                             pollinator_freq_position_s)
+
+model_freq_specif2 <- lmer(observed_freq ~ s+(1+s|Node_FG/Network_id), 
+                           pollinator_freq_position_s)
+
+summary(model_freq_specif1)
+r2(model_freq_specif1)
+
+summary(model_freq_specif2)
+r2(model_freq_specif2)
+
+library(visreg)
+visreg2d(model_freq_specif1, "Node_FG","s",scale ="response")
+visreg(model_freq_specif1, "Node_FG", gg=TRUE, ylab="Node_FG")
+
+library(tidyverse)
+library(ggplot2)
+p3 <- ggplot(pollinator_freq_position_s,aes(x=s,y=observed_freq))+
+  geom_point(alpha=0.5, color="black")+
+  geom_smooth(method = "lm",color="black")+
+  facet_wrap(~Node_FG)+
+  labs(x="Specificty",y="Observed frequency per position") +
+  theme_bw() + ggtitle("Floral visitors") +
+  theme(plot.title = element_text(hjust = 0.5))
+
+p1/p3

### 2022-03-28 Scripts/Scripts_Alfonso/specificity_VS_position_frequencies.R
Update specificity_VS_position_frequencies.R

@@ -266,38 +266,44 @@ visreg(m_lm_pos_poll_rd,"Node_FG",scale ="response")
 
 
 #---------------------------------
-# Analisys with LMMs all obs. freq. per position and study
+# Analisys with LMMs
+
+
 library(lme4)
 library(performance)
 
 pollinator_freq_position_s <- pollinator_position_percentiles_filtered %>% 
-  left_join(specificity_pollinator, by = "position") %>% mutate(position=as.factor(position))
+  left_join(specificity_pollinator, by = "position")
 
 pollinator_freq_position_s$s[is.nan(pollinator_freq_position_s$s)] <- 1.0
 
-model_freq_specif1 <- lmer(observed_freq ~ s*Node_FG+(1|Network_id), 
-                             pollinator_freq_position_s)
+# Indirect interaction data
+motif_interactions <- read_csv("Data/Data_processing/Motifs_connections/motif_interactions.csv") %>%
+  select(position,indirect_interactions) %>% unique()
 
-model_freq_specif2 <- lmer(observed_freq ~ s+(1+s|Node_FG/Network_id), 
-                           pollinator_freq_position_s)
+pollinator_freq_position_s_ind <- pollinator_freq_position_s %>% 
+  left_join(motif_interactions, by = "position") %>% 
+  filter(!Node_FG %in% c("Birds","Lizards","Other_insects")) %>%
+  rename(Percentil=percentil_its_GF,Specificity=s,Indirect_interactions=indirect_interactions,Group=Node_FG)
 
-summary(model_freq_specif1)
-r2(model_freq_specif1)
+model_freq_specif_ind <- lmer(Percentil ~ Specificity*Group + Indirect_interactions*Group + (1|study_id), 
+                           pollinator_freq_position_s_ind)
 
-summary(model_freq_specif2)
-r2(model_freq_specif2)
+
+summary(model_freq_specif_ind)
+r2(model_freq_specif_ind)
 
 library(visreg)
-visreg2d(model_freq_specif1, "Node_FG","s",scale ="response")
-visreg(model_freq_specif1, "Node_FG", gg=TRUE, ylab="Node_FG")
+visreg2d(model_freq_specif_ind, "Group","Specificity",scale ="response")
+visreg2d(model_freq_specif_ind, "Group","Indirect_interactions",scale ="response")
 
 library(tidyverse)
 library(ggplot2)
[…]

### 2022-03-28 Manuscript/Main_text/Main_text_Functional_Ecology.Rmd
edits

@@
 Because of the tremendous complexity of these ecological networks, species interactions are generally condensed in metrics that summarize this information [@guimaraes2020].
-Plant-pollinator interactions are no exception, and they are often studied with indices that aggregate the information at the species (micro-scale) or network level (macro-scale).
+Plant-pollinator interactions are no exception, and they are often studied with indices that aggregate the information at the network (macro-scale) and species level (micro-scale).
 For example, plant-pollinator network level approaches have identified common invariant structural properties across networks, including a degree distribution that decays as a power law [@jordano1987], nestedness [@bascompte2003], or modularity [@olesen2007].
 In addition, the local species position within the network can define its degree of specialization [@bluthgen2006] or its role in connecting the rest of the community [@olesen2007].
-Despite the unquestionable progress with the use of these metrics at both species and network level, condensing complex information into a single metric implies the loss of relevant ecological information that obscures the understanding of species interactions [@cirtwill2018; @simmons2019].
+Despite the unquestionable progress with the use of these metrics at both network and species level, condensing complex information into a single metric implies the loss of relevant ecological information that obscures the understanding of species interactions [@cirtwill2018; @simmons2019].
 
@@
 Although some studies have evaluated plant reproductive strategies in plant-pollinator networks [@tur2013; @lazaro2020], this is an often overlooked aspect in a community context [@devaux2014] and rarely incorporated into plant-pollinator network studies.
-Hence, exploring how the main plant reproductive strategies integrate with the emergent motif framework could help to progress knowledge on plant-pollinator interactions.
+Hence, exploring how the main plant and floral visitor life-history strategies integrate with the emergent motif framework could help to progress knowledge on plant-pollinator interactions.
 
@@
 After, we calculated the normalized motif frequencies and investigated if these frequencies are similar or not to the ones expected by chance with the help of null models.
-Then, we calculated the normalized group frequencies of plant and floral visitor for the different motif positions and investigated their overall representation by comparing these observed frequencies with their simulated counterparts.
-Finally, we tried to recover the observed motif combinations from the expected frequencies calculated as the product of the probabilities of the different plant and floral visitor groups within each motif.
+Then, for each group of plants and floral visitors we also calculated the normalized group frequency in the different motif positions and investigated their overall representation by comparing these observed frequencies with their simulated counterparts.
+Finally, we compared if there are differences in the observed frequencies of motif combinations in empirical networks and the expected frequencies of motif combinations calculated as the product of the probabilities of the different plant and floral visitor groups within the motif.
 
@@
 
-Second, floral visitors were grouped into taxonomic groups based on taxonomic rank as done similarly in other plant-pollinator studies [@fenster2004; @ollerton2009].
+Second, floral visitors were aggregated into taxonomic groups based on taxonomic rank as done similarly in other plant-pollinator studies [@fenster2004; @ollerton2009].
 We opted to divide floral visitors on the taxonomic rank level and not with functional traits because the main orders of floral visitors differed in form and behaviour and had lower superior taxonomical complexity (i.e., floral visitors had 6 orders versus plants that had 38).
@@
 Prior to analyses, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.
+This approach was preferred since quantitative motif analysis have been developed just recently and more work is needed to fully understand and interpret the information that they can convey [simmons2020].
 All analyses were run considering singletons (species with only one interaction detected) but we conducted a second exploration without singletons (64.98$\%$ of interactions) to evaluate the effect of rare species on the observed patterns.
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, fig.pos="t", warning=FALSE,out.width="75%",fig.align="center", fig.cap="\\textbf{Figure 1.} (Adapted figure of Simmons et al., 2019).
-All possible motif network structures from two to five species in bipartite networks.
+All possible motif network structures from two to five species in bipartite networks grouped by the different motif classes (2-species, 3-species, 4-species and 5-species).
 There is a total of 17 possible motifs with 46 different positions denoted within each node.
@@
 As suggested in @simmons2020, a higher proportion of these densely connected motifs could reflect that neutral effects are the predominant ecological process governing the structure of network motifs.
-Thus, as indicated for other network properties like nestedness at the macro-scale level [@krishna2008; @suweis2013], or interaction probability at the species level [@bartomeus2016](CHECK), species relative abundances (i.e., neutral effects) may be also the predominant ecological process governing the meso-scale structure on plant-pollinator networks.
+Thus, as indicated for other network properties like nestedness at the macro-scale level [@krishna2008; @suweis2013], or interaction probability at the species level [@bartomeus2016], species relative abundances (i.e., neutral effects) may be also the predominant ecological process governing the meso-scale structure on plant-pollinator networks.
 
@@
 In contrast, non-bee groups were over-represented in motif positions associated with specialised roles.
-This large effect of bees on the overall patterns is no surprise, as bees were the group with the largest number of interaction records in the whole set of networks as also shown for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017][can you check if this is worth citing here: https://royalsocietypublishing.org/doi/full/10.1098/rspb.2017.2140]().
+This large effect of bees on the overall patterns is no surprise, as bees were the group with the largest number of interaction records in the whole set of networks as also shown for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017].
 Interestingly, bees also were the group with lower number of indirect interactions while the rest of floral visitor groups showed clearly higher number of indirect interactions possibly indicating that these non-bee floral visitor groups may experience higher competitive interactions for floral resources [@thomson2020].
@@
 Further, we found that plant and floral visitor groups are associated with different motif positions that involve distinct ecological roles (e.g., generalization versus specialization) and that the different motif combinations are strongly constrained.
-Global change drivers are reshuffling ecological communities [REF]().
-Although we are still far to predict how this new combinations of species will interact, our work is a first step to elucidate how nove interactions will form beyond pairwise interactions.
+Global change drivers are reshuffling ecological communities [@bascompte2019].
+Although we are still far to predict how this new combinations of species will interact, our work is a first step to elucidate how novel interactions will form beyond pairwise interactions.
 

### 2022-03-28 Scripts/Scripts_Alfonso/specificity_VS_position_frequencies.R
Update specificity_VS_position_frequencies.R

@@ -286,8 +286,17 @@ pollinator_freq_position_s_ind <- pollinator_freq_position_s %>%
   filter(!Node_FG %in% c("Birds","Lizards","Other_insects")) %>%
   rename(Percentil=percentil_its_GF,Specificity=s,Indirect_interactions=indirect_interactions,Group=Node_FG)
 
-model_freq_specif_ind <- lmer(Percentil ~ Specificity*Group + Indirect_interactions*Group + (1|study_id), 
-                           pollinator_freq_position_s_ind)
+pollinator_freq_position_s_ind$Percentil[pollinator_freq_position_s_ind$Percentil==0] <- 
+  1e-10
+
+pollinator_freq_position_s_ind$Percentil[pollinator_freq_position_s_ind$Percentil==1] <- 
+  1-1e-10
+
+model_freq_specif_ind <- glmmTMB(Percentil ~ Specificity*Group + 
+                                   Indirect_interactions*Group + 
+                                   (1|study_id), 
+                           pollinator_freq_position_s_ind,
+                           family = beta_family())
 
 
 summary(model_freq_specif_ind)
@@ -297,14 +306,143 @@ library(visreg)
 visreg2d(model_freq_specif_ind, "Group","Specificity",scale ="response")
 visreg2d(model_freq_specif_ind, "Group","Indirect_interactions",scale ="response")
 
-library(tidyverse)
-library(ggplot2)
-p3 <- ggplot(pollinator_freq_position_s,aes(x=s,y=percentil_its_GF))+
-  geom_point(alpha=0.5, color="black")+
-  geom_smooth(method = "lm",color="black")+
-  facet_wrap(~Node_FG)+
-  labs(x="Specificty",y="Percentil per position") +
-  theme_bw() + ggtitle("Floral visitors") +
-  theme(plot.title = element_text(hjust = 0.5))
+########################################3
+#
 
-p1/p3
+
+############################
+#Visualization of slopes by using visreg
+
+library(ggeffects)
+library(scales)
+Bee_freq_position_s_ind <- pollinator_freq_position_s_ind %>% 
+  filter(Group =="Bee")
+
+model_Bee <- glmmTMB(Percentil ~ Specificity + 
+                       Indirect_interactions + 
+                       (1|study_id), Bee_freq_position_s_ind,
[…]

### 2022-03-29 Scripts/Scripts_Alfonso/specificity_VS_position_frequencies.R
Update specificity_VS_position_frequencies.R

@@ -266,7 +266,7 @@ visreg(m_lm_pos_poll_rd,"Node_FG",scale ="response")
 
 
 #---------------------------------
-# Analisys with LMMs
+# Percentil analises with LMMs for Pollinators
 
 
 library(lme4)
@@ -438,6 +438,178 @@ visreg(model_Syrphids,"Indirect_interactions",xlab="I. interactions",ylab="Perce
 points(Percentil ~ Indirect_interactions, data = Syrphids_freq_position_s_ind, 
        col = rgb(red = 0, green = 0, blue = 0, alpha = 0.5),
        pch = 20) 
+
+# save
+#
+#
+#
+#
+#
+dev.off()
+
+
+
+#---------------------------------
+# Percentil analises with LMMs for Plants
+
+
+library(lme4)
+library(performance)
+
+plant_freq_position_s <- plant_position_percentiles_filtered %>% 
+  left_join(specificity_plant, by = "position")
+
+plant_freq_position_s$s[is.nan(plant_freq_position_s$s)] <- 1.0
+
+# Indirect interaction data
+motif_interactions <- read_csv("Data/Data_processing/Motifs_connections/motif_interactions.csv") %>%
+  select(position,indirect_interactions) %>% unique()
+
+plant_freq_position_s_ind <- plant_freq_position_s %>% 
+  left_join(motif_interactions, by = "position") %>% 
+  filter(!Node_FG %in% c("Birds","Lizards","Other_insects")) %>%
+  rename(Percentil=percentil_its_GF,Specificity=s,Indirect_interactions=indirect_interactions,Group=Node_FG)
+
+plant_freq_position_s_ind$Percentil[plant_freq_position_s_ind$Percentil==0] <- 
+  1e-10
+
+plant_freq_position_s_ind$Percentil[plant_freq_position_s_ind$Percentil==1] <- 
+  1-1e-10
+
+model_freq_specif_ind_plant <- glmmTMB(Percentil ~ Specificity*Group + 
+                                   Indirect_interactions*Group + 
+                                   (1|study_id), 
+                                 plant_freq_position_s_ind,
+                                 family = beta_family())
+
+
+summary(model_freq_specif_ind_plant)
+r2(model_freq_specif_ind_plant)
+
+library(visreg)
+visreg2d(model_freq_specif_ind_plant, "Group","Specificity",scale ="response")
[…]

### 2022-03-29 Scripts/Scripts_Alfonso/specificity_VS_position_frequencies.R
Update specificity_VS_position_frequencies.R

@@ -270,6 +270,7 @@ visreg(m_lm_pos_poll_rd,"Node_FG",scale ="response")
 
 
 library(lme4)
+library(glmmTMB)
 library(performance)
 
 pollinator_freq_position_s <- pollinator_position_percentiles_filtered %>% 
@@ -306,12 +307,35 @@ library(visreg)
 visreg2d(model_freq_specif_ind, "Group","Specificity",scale ="response")
 visreg2d(model_freq_specif_ind, "Group","Indirect_interactions",scale ="response")
 
+# Pollinator Model REAL OUTPUTS!!!
+
+pollinators_sp_plot <- visreg(model_freq_specif_ind, "Specificity", by="Group",
+                         strip.names=c("Bee",
+                                       "Coleoptera",
+                                       "Lepidoptera",
+                                       "Non-bee-Hymenoptera",
+                                       "Non-syrphids-diptera",
+                                       "Syrphids"),gg = TRUE)+
+  theme_bw()
+
+pollinators_ind_int_plot <- visreg(model_freq_specif_ind, "Indirect_interactions", by="Group",
+                              strip.names=c("Bee",
+                                            "Coleoptera",
+                                            "Lepidoptera",
+                                            "Non-bee-Hymenoptera",
+                                            "Non-syrphids-diptera",
+                                            "Syrphids"),gg = TRUE)+
+  theme_bw()+xlab("Indirect interactions")
+
+library(patchwork)
+pollinators_sp_plot/pollinators_ind_int_plot
+
 ########################################3
 #
 
 
 ############################
-#Visualization of slopes by using visreg
+#Visualization of slopes by using visreg: This is not OK because I will use individual fits
 
 library(ggeffects)
 library(scales)
@@ -487,8 +511,30 @@ summary(model_freq_specif_ind_plant)
 r2(model_freq_specif_ind_plant)
 
 library(visreg)
+dev.off()
 visreg2d(model_freq_specif_ind_plant, "Group","Specificity",scale ="response")
 visreg2d(model_freq_specif_ind_plant, "Group","Indirect_interactions",scale ="response")
+
+# Plant Model REAL OUTPUTS!!!
+
+plants_sp_plot <- visreg(model_freq_specif_ind_plant, "Specificity", by="Group",
+       strip.names=c("Selfing herbs",
+                     "Small outcrossing perennials",
+                     "Self-incompatible perennials\nwith large flowers",
[…]

### 2022-03-29 Manuscript/Main_text/Main_text_Functional_Ecology.Rmd
Edits

@@
 We calculated which plant and floral visitor groups were over- or under-represented in the different motif positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
-To estimate the position frequencies of each plant and floral visitor group in a given network, we added the frequencies of those species that belong to the same group, and then, we normalised the resulting frequencies by dividing them by the total number of times that a corresponding group appears in any position within the same motif size class (i.e., number of species of a motif).
+To estimate the position frequencies of each plant and floral visitor group in a given network, we added the frequencies of those species that belong to the same group, and then, we normalised the resulting frequencies by dividing them by the total number of times that a corresponding group appears in any position within the same motif size class (i.e., 2, 3, 4 or 5 species motifs).
 Then, we calculated the percentile of the observed position frequencies for each group and network, just like we did with motif frequencies.
@@
 
-To understand if the different plant and floral visitor groups are associated with motif positions that represent different network roles we characterized the roles of each motif positions for plant and floral visitor groups in terms of their specialization and number of indirect interactions.
-To that end, we calculated the specificity of each motif positions as a measure of specialization and we used the number of indirect interactions of the different motif positions to evaluate the association of these two position metrics and the group frequencies for the different motif positions.
-First, specificity ($s_i$) was calculated for each motif position following @poisot2015 as $s_i = L - l_i / L - 1$, where $L$ is the total number of groups and $l_i$ the number of interaction partners of the group $i$ in a given motif.
-Values of the vector s, range between 1, complete specialization (1 partner within the motif) and 0, complete generalism (all possible partners within the motif).
-Then, we explored through linear models the association between the frequency of the different groups (response variable) and specificity (predictor) [NO RANDOMS HERE?
-WHY]().
-Second, we calculated the number of indirect interactions for each motif position by accounting only for the indirect effect of two species by a third species.
-That is, we explored exclusively indirect interactions within plants though shared floral visitors or within floral visitors though shared plants.
-[NO ANALYSIS HERE?
-WHY?
-HOW DO YOU USE THIS VALUE?]()
+To understand if the different plant and floral visitor groups are associated with motif positions that represent different network roles, we characterized the roles of each motif positions for plant and floral visitor groups in terms of their specialization and number of indirect interactions.
+To that end, we calculated the specificity of each motif position following @poisot2015 as $s_i = L - l_i / L - 1$, where $L$ is the total number of groups and $l_i$ the number of interaction partners of the group $i$ in a given motif.
+Values of the vector $si$, range between 1, complete specialization (1 partner within the motif) and 0 complete generalism (all possible partners within the motif).
+Then, we calculated the number of indirect interactions for each motif position and trophic guild (i.e., plants or floral visitors) as $z_i-1$ where $z_i$ is the total number of nodes for a trophic guild in a given motif.
+Because all nodes within a motif are connected, to obtain the total number of indirect interactions for a given position we only have to substract to $z_i$ the motif position of interest that cannot interact indirectly with itself.
+Finally, we analysed in a single model how specialization and the number of indirect interactions are associated with the observed percentiles for each trophic guild and motif position (see paragraph above).
+For this, we implemented a GLMM model with the help of the _glmmTMB_ package [@magnusson2017] version _1.0.2.1_ with a Beta distribution because percentiles have exclusively  positive values.
+The variation at the study system was controlled with the help of the study identifier as a random factor.
 

### 2022-03-29 Scripts/Scripts_Alfonso/specificity_VS_position_frequencies.R
Update specificity_VS_position_frequencies.R

@@ -287,17 +287,18 @@ pollinator_freq_position_s_ind <- pollinator_freq_position_s %>%
   filter(!Node_FG %in% c("Birds","Lizards","Other_insects")) %>%
   rename(Percentil=percentil_its_GF,Specificity=s,Indirect_interactions=indirect_interactions,Group=Node_FG)
 
-pollinator_freq_position_s_ind$Percentil[pollinator_freq_position_s_ind$Percentil==0] <- 
-  1e-10
+# pollinator_freq_position_s_ind$Percentil[pollinator_freq_position_s_ind$Percentil==0] <- 
+#   1e-10
+# 
+# pollinator_freq_position_s_ind$Percentil[pollinator_freq_position_s_ind$Percentil==1] <- 
+#   1-1e-10
 
-pollinator_freq_position_s_ind$Percentil[pollinator_freq_position_s_ind$Percentil==1] <- 
-  1-1e-10
+pollinator_freq_position_s_ind$position <- as.factor(pollinator_freq_position_s_ind$position)
 
-model_freq_specif_ind <- glmmTMB(Percentil ~ Specificity*Group + 
-                                   Indirect_interactions*Group + 
-                                   (1|study_id), 
-                           pollinator_freq_position_s_ind,
-                           family = beta_family())
+model_freq_specif_ind <- lmer(Percentil ~ Specificity*Group +
+                                   scale(Indirect_interactions)*Group + 
+                                   (1|study_id/position),
+                           pollinator_freq_position_s_ind)
 
 
 summary(model_freq_specif_ind)
@@ -330,6 +331,18 @@ pollinators_ind_int_plot <- visreg(model_freq_specif_ind, "Indirect_interactions
 library(patchwork)
 pollinators_sp_plot/pollinators_ind_int_plot
 
+library("DHARMa")
+pollinator_freq_position_s_ind$scale_Indirect_interactions <- scale(pollinator_freq_position_s_ind$Indirect_interactions)
+model_freq_specif_ind2 <- lmer(Percentil ~ Specificity*Group +
+                                 scale_Indirect_interactions*Group + 
[…]

### 2022-03-29 Manuscript/Main_text/Main_text_Functional_Ecology.Rmd
saving model data to plut it in supplementary mat

@@
 Then, we calculated the number of indirect interactions for each motif position and trophic guild (i.e., plants or floral visitors) as $z_i-1$ where $z_i$ is the total number of nodes for a trophic guild in a given motif.
-Because all nodes within a motif are connected, to obtain the total number of indirect interactions for a given position we only have to substract to $z_i$ the motif position of interest that cannot interact indirectly with itself.
-Finally, we analysed in a single model how specialization and the number of indirect interactions are associated with the observed percentiles for each trophic guild and motif position (see paragraph above).
-For this, we implemented a GLMM model with the help of the _glmmTMB_ package [@magnusson2017] version _1.0.2.1_ with a Beta distribution because percentiles have exclusively  positive values.
-The variation at the study system was controlled with the help of the study identifier as a random factor.
+Because all nodes within a motif are connected, to obtain the total number of indirect interactions for a given position we only have to substract from $z_i$ one unit that corresponds to the position of interest.
+Finally, we analysed in a single model how specialization and the number of indirect interactions were associated with the observed percentiles for each trophic guild and motif position (see paragraph above).
+For this, we fitted a LMM model with the help again of the _lmer_ package where we considered specialization and number of indirect interactions as response variables with the interaction by group for the two response variables.
+This allowed us to explore the individual response for the different plant and floral visitor groups.
+Further, the variation at the study system was controlled with the help of the study identifier as a random factor.
 

### 2022-03-29 Scripts/Scripts_Alfonso/specificity_VS_position_frequencies.R

@@ -328,6 +328,11 @@ pollinators_ind_int_plot <- visreg(model_freq_specif_ind, "Indirect_interactions
                                             "Syrphids"),gg = TRUE)+
   theme_bw()+xlab("Indirect interactions")
 
+
+
+#Save model data
+saveRDS(model_freq_specif_ind, "Data/RData/model_freq_specif_ind.RData")
+
 library(patchwork)
 pollinators_sp_plot/pollinators_ind_int_plot
 
@@ -549,6 +554,9 @@ plants_ind_int_plot <- visreg(model_freq_specif_ind_plant, "Indirect_interaction
 
 library(patchwork)
 plants_sp_plot/plants_ind_int_plot
+
+#Save model data
+saveRDS(model_freq_specif_ind_plant, "Data/RData/model_freq_specif_ind_plant.RData")
 
 
 library("DHARMa")

### 2022-03-29 Manuscript/Main_text/Main_text_Functional_Ecology.Rmd
edits

@@
 Then, we calculated the number of indirect interactions for each motif position and trophic guild (i.e., plants or floral visitors) as $z_i-1$ where $z_i$ is the total number of nodes for a trophic guild in a given motif.
-Because all nodes within a motif are connected, to obtain the total number of indirect interactions for a given position we only have to substract from $z_i$ one unit that corresponds to the position of interest.
+Because all nodes within a motif are connected, we only had to subtract the node of interest to $z_i$ to obtain the total number of indirect interactions by position and guild.
 Finally, we analysed in a single model how specialization and the number of indirect interactions were associated with the observed percentiles for each trophic guild and motif position (see paragraph above).
-For this, we fitted a LMM model with the help again of the _lmer_ package where we considered specialization and number of indirect interactions as response variables with the interaction by group for the two response variables.
-This allowed us to explore the individual response for the different plant and floral visitor groups.
-Further, the variation at the study system was controlled with the help of the study identifier as a random factor.
+For this, we fitted a LMM model with the help again of the _lmer_ package where we considered specialization and number of indirect interactions as response variables with the interaction by plant and floral visitor group for both response variables.
+Further, we considered as random factor motif position nested within study system.
+All model diagnostics were conducted with the help of the R package _Dharma_ [@hartig2017] version _0.3.3.0_.
 
@@
 Finally, 5-node motifs were in similar proportions in the no statistical difference and over-represented categories (99$\%$ and 97$\%$, respectively) but they appeared in lower proportion in the under-represented category (89$\%$).
-When, we explore the identity on the different positions of the most probable motif combinations we find as expected that the most common plant and floral visitor groups rule these positions on the most probable motif combinations (lower panel **Figure 5**).
+When we explored the identity on the different positions of the most probable motif combinations we found that the most common plant and floral visitor groups were also the most probable on these motif combinations (lower panel **Figure 5**).
 
@@
 However, common analytical approaches at the node or at the full network level are unable to capture the full complexity of ecological systems [@simmons2019; @bergamo2021].
-Because network motifs can capture both direct and indirect interactions, by analysing over- and under-representation of motifs we are able to explore in great detail the structure of interactions of plant-pollinator networks.
+Because network motifs can capture both direct and indirect interactions, by analysing over- and under-representation of motifs we were able to explore in great detail the structure of interactions of plant-pollinator networks.
 We have explored for the first time the overall structure and representation of network motifs in real plant-pollinator networks at a macro-ecological scale and shown that the different motifs up to five nodes are consistently over- or under-represented in comparison with simulated networks, therefore indicating the presence of ecological processes shaping their structure.
@@
 Overall, generalist network motifs for floral visitors were consistently over-represented (e.g., fan-type motifs; **Figure 2**).
-For instance, when we compare motifs with equal structure for both trophic levels, we found that floral visitors had always over-representation in the positions that implied the highest number of direct links.
+For instance, when we compare motifs with equal structure for both trophic levels, we found that floral visitors had always over-representation in the positions that implied the highest number of direct links (e.g., positions 16 and 46 from motifs 7 and 17, respectively).
 Despite this being in good agreement with the current view of the generalist nature of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of generalist network motifs was driven by the taxonomic group of bees (**Figure S6**) while the rest of the taxonomic groups tended to be under-represented.
@@
 This large effect of bees on the overall patterns is no surprise, as bees were the group with the largest number of interaction records in the whole set of networks as also shown for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017].
-Interestingly, bees also were the group with lower number of indirect interactions while the rest of floral visitor groups showed clearly higher number of indirect interactions possibly indicating that these non-bee floral visitor groups may experience higher competitive interactions for floral resources [@thomson2020].
+Interestingly, bees also were the group with lower number of indirect interactions while the rest of floral visitor groups showed clearly higher number of indirect interactions indicating that these non-bee floral visitor groups may experience higher competitive interactions for floral resources [@thomson2020].
 Despite plant functional groups showed little differences between them on their motif frequencies, all groups showed a tendency to be more represented on motif positions that were associated with higher levels of specialization.
@@
 However, a large fraction of the possible interactions do not take place because of life-history constraints such as species co-occurrence, trait matching processes and phenological uncoupling [@olesen2011; @bartomeus2016; @jordano2016].
-Despite the advances in the understanding on the ecological processes that influence species pairwise interactions [@bartomeus2016; @peralta2020], we still know little of how these processes determine competitive and facilitative interactions in mutualistic networks.
+Despite the advances in the understanding on the ecological processes that influence species pairwise interactions [@bartomeus2016; @peralta2020], we still know little about how these processes determine competitive and facilitative interactions in mutualistic networks.
 Thus, as suggested by @simmons2020, exploring the proportion of these realized network motifs that are competitive or facilitative is a necessary next step to improve our understanding of the architecture of biodiversity [@bascompte2007].
@@
 We believe that this could be investigated by exploring which proportion of over- and under-represented motifs present high and low trait-matching, respectively.
-Moreover, we analysed network motifs focusing exclusively on presence-absence interactions which assume that all interactions are equally important but as suggested by @simmons2020, further work should explore how is it possible to account for the quantitative measurements of the strength of plant-pollinator interactions.
+Moreover, we analysed network motifs focusing exclusively on presence-absence interactions which assume that all interactions are equally important as suggested by @simmons2020, further work should investigate how to account for the quantitative measurements of the strength of plant-pollinator interactions.
 Finally, despite the wide geographical coverage of our plant-pollinator dataset, there are major gaps for some regions of the world with a clear bias towards Europe, America and islands which have long interested ecologist [@macarthur1963; @warren2015].

### 2022-03-29 Manuscript/Supplementary_Material/Specialization_trophic_guild.Rmd
edits

---
title: "Untitled"
output:
  pdf_document: default
  html_document: default
classoption: landscape

---

```{r, echo=FALSE, message=FALSE, cache=FALSE, fig.pos="t", warning=FALSE,out.width="75%",fig.align="center", fig.width=14,fig.height=6, out.width='100%'}

library(ggplot2)
library(glmmTMB)
#Read floral visitor data and model output
model_freq_specif_ind <- readRDS("../../Data/RData/model_freq_specif_ind.RData")
pollinator_freq_position_s_ind <- readRDS("../../Data/RData/pollinator_freq_position_s_ind.RData")
#Read plant data and model output
model_freq_specif_ind_plant <- readRDS("../../Data/RData/model_freq_specif_ind_plant.RData")
plant_freq_position_s_ind <- readRDS("../../Data/RData/plant_freq_position_s_ind.RData")

library(visreg)

# Pollinator Model REAL OUTPUTS!!!

pollinators_sp_plot <- visreg(model_freq_specif_ind, "Specificity", by="Group",line.par = list(col = 'black'),
                         strip.names=c("Bee",
                                       "Coleoptera",
                                       "Lepidoptera",
                                       "Non-bee-Hymenoptera",
                                       "Non-syrphids-diptera",
                                       "Syrphids"),gg = TRUE) + theme_bw() +
  xlab("Specialization") + ylab("Partial residuals \n for percentile")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.5))+ scale_fill_grey(start=0.5, end=0.8)

plants_sp_plot <- visreg(model_freq_specif_ind_plant, "Specificity",line.par = list(col = 'black'), by="Group",
       strip.names=c("Selfing herbs",
                     "Small outcrossing perennials",
                     "Self-incompatible perennials\nwith large flowers",
                     "Tall plants with small\nunisexual flowers",
                     "Short-lived outcrossers with\nlong zygomorphic flowers"),gg = TRUE)+ theme_bw() +
  xlab("Specialization") + ylab("Partial residuals \n for percentile")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.5))

library(patchwork)
pollinators_sp_plot/plants_sp_plot & theme(axis.text=element_text(size=10),
        axis.title=element_text(size=14)) & plot_annotation(tag_levels = c('A'),  tag_suffix = ')') &  theme(plot.tag = element_text(size = 22))

```

### 2022-03-29 Scripts/Scripts_Alfonso/specificity_VS_position_frequencies.R

@@ -255,6 +255,7 @@ m_lm_pos_poll_rd <- glmmTMB(mean ~ s + (1|Node_FG), data = pollinator_means_reor
 summary(m_lm_pos_poll_rd)
 r2(m_lm_pos_poll_rd)
 
+
 library(visreg)
 visreg2d(m_lm_pos_poll, "Node_FG","s",scale ="response")
 visreg(m_lm_pos_poll,"s",scale ="response")
@@ -301,6 +302,17 @@ model_freq_specif_ind <- lmer(Percentil ~ Specificity*Group +
                            pollinator_freq_position_s_ind)
 
 
+model_freq_specif_ind <- glmmTMB(Percentil ~ Specificity*Group +
+                       scale(Indirect_interactions)*Group + 
+                       (1|study_id/position),
+                     pollinator_freq_position_s_ind)
+
+
+#Save model data
+saveRDS(model_freq_specif_ind, "Data/RData/model_freq_specif_ind.RData")
+saveRDS(pollinator_freq_position_s_ind, "Data/RData/pollinator_freq_position_s_ind.RData")
+
+
 summary(model_freq_specif_ind)
 r2(model_freq_specif_ind)
 
@@ -309,6 +321,7 @@ visreg2d(model_freq_specif_ind, "Group","Specificity",scale ="response")
 visreg2d(model_freq_specif_ind, "Group","Indirect_interactions",scale ="response")
 
 # Pollinator Model REAL OUTPUTS!!!
+model_freq_specif_ind <- readRDS("Data/RData/model_freq_specif_ind.RData")
 
 pollinators_sp_plot <- visreg(model_freq_specif_ind, "Specificity", by="Group",
                          strip.names=c("Bee",
@@ -316,8 +329,7 @@ pollinators_sp_plot <- visreg(model_freq_specif_ind, "Specificity", by="Group",
                                        "Lepidoptera",
                                        "Non-bee-Hymenoptera",
                                        "Non-syrphids-diptera",
-                                       "Syrphids"),gg = TRUE)+
-  theme_bw()
+                                       "Syrphids"),gg = TRUE) + theme_bw()
 
 pollinators_ind_int_plot <- visreg(model_freq_specif_ind, "Indirect_interactions", by="Group",
                               strip.names=c("Bee",
@@ -325,13 +337,9 @@ pollinators_ind_int_plot <- visreg(model_freq_specif_ind, "Indirect_interactions
                                             "Lepidoptera",
[…]

### 2022-03-29 Manuscript/Supplementary_Material/Specialization_trophic_guild.Rmd
specialization added to supp. mat

@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, fig.pos="t", warning=FALSE,out.width="75%",fig.align="center", fig.width=14,fig.height=6, out.width='100%'}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, fig.pos="t", warning=FALSE,fig.align="center", fig.width=14,fig.height=7, out.width='100%'}
 
@@
   xlab("Specialization") + ylab("Partial residuals \n for percentile")+
-  scale_x_continuous(breaks = seq(0, 1, by = 0.5))+ scale_fill_grey(start=0.5, end=0.8)
+  scale_x_continuous(breaks = seq(0, 1, by = 0.5))+ scale_fill_grey(start=0.5, end=0.8) +
+   theme(strip.text.x = element_text(size = 12),plot.title = element_text(hjust = 0.5, size = 23))+
+    ggtitle("Floral visitors")
 
@@
   xlab("Specialization") + ylab("Partial residuals \n for percentile")+
-  scale_x_continuous(breaks = seq(0, 1, by = 0.5))
+  scale_x_continuous(breaks = seq(0, 1, by = 0.5))+
+   theme(strip.text.x = element_text(size = 12),plot.title = element_text(hjust = 0.5, size = 23))+
+  ggtitle("Plants")
 
@@
 pollinators_sp_plot/plants_sp_plot & theme(axis.text=element_text(size=10),
-        axis.title=element_text(size=14)) & plot_annotation(tag_levels = c('A'),  tag_suffix = ')') &  theme(plot.tag = element_text(size = 22))
+        axis.title=element_text(size=16)) & plot_annotation(tag_levels = c('A'),  tag_suffix = ')') &  theme(plot.tag = element_text(size = 22))
 

### 2022-03-29 Manuscript/Supplementary_Material/Supporting_information_Functional_Ecology.Rmd
edits
specialization added to supp. mat

--- 2022-03-23 Manuscript/Supplementary_Material/Supporting_information_Oikos.Rmd
@@
 
-**The non-random assembly of functional motifs in plant-pollinator networks worldwide**
-
-Jose B. Lanuza, Alfonso Allen-Perkins and Ignasi Bartomeus
+**The non-random assembly of functional motifs in plant-pollinator networks**
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=12, fig.width=12, fig.align = 'center', fig.cap="\\textbf{Figure S6.} Association between the frequency and specificity on the different motif positions for floral visitor (panel A) and plant (panel B) groups.
-The different numerical categories of the plant groups correspond to: 1 (selfing herbs), 2 (small outcrossing perennials), 3 (self-incompatible perennials with large flowers), 4 (tall plants with small unisexual flowers) and 5 (short-lived outcrossers with long zygomorphic flowers)."}
+\blandscape
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, fig.pos="t", warning=FALSE,fig.align="center", fig.width=14,fig.height=7, out.width='100%'}
 
 library(ggplot2)
+library(glmmTMB)
+#Read floral visitor data and model output
+model_freq_specif_ind <- readRDS("../../Data/RData/model_freq_specif_ind.RData")
+pollinator_freq_position_s_ind <- readRDS("../../Data/RData/pollinator_freq_position_s_ind.RData")
+#Read plant data and model output
+model_freq_specif_ind_plant <- readRDS("../../Data/RData/model_freq_specif_ind_plant.RData")
+plant_freq_position_s_ind <- readRDS("../../Data/RData/plant_freq_position_s_ind.RData")
+
+library(visreg)
+
+# Pollinator Model REAL OUTPUTS!!!
+
+pollinators_sp_plot <- visreg(model_freq_specif_ind, "Specificity", by="Group",line.par = list(col = 'black'),
+                         strip.names=c("Bee",
+                                       "Coleoptera",
+                                       "Lepidoptera",
+                                       "Non-bee-Hymenoptera",
+                                       "Non-syrphids-diptera",
+                                       "Syrphids"),gg = TRUE) + theme_bw() +
+  xlab("Specialization") + ylab("Partial residuals \n for percentile")+
+  scale_x_continuous(breaks = seq(0, 1, by = 0.5))+ scale_fill_grey(start=0.5, end=0.8) +
+   theme(strip.text.x = element_text(size = 12),plot.title = element_text(hjust = 0.5, size = 23))+
+    ggtitle("Floral visitors")
+
+plants_sp_plot <- visreg(model_freq_specif_ind_plant, "Specificity",line.par = list(col = 'black'), by="Group",
+       strip.names=c("Selfing herbs",
+                     "Small outcrossing perennials",
+                     "Self-incompatible perennials\nwith large flowers",
+                     "Tall plants with small\nunisexual flowers",
+                     "Short-lived outcrossers with\nlong zygomorphic flowers"),gg = TRUE)+ theme_bw() +
+  xlab("Specialization") + ylab("Partial residuals \n for percentile")+
+  scale_x_continuous(breaks = seq(0, 1, by = 0.5))+
+   theme(strip.text.x = element_text(size = 12),plot.title = element_text(hjust = 0.5, size = 23))+
+  ggtitle("Plants")
+
 library(patchwork)
-
-pollinator_means_reordered_s_1 <- read.csv("../../Data/Csv/pollinator_means_reordered_s_1.csv")
-
-plant_means_s <- read.csv("../../Data/Csv/plant_means_s.csv")
-
-p1 <- ggplot(pollinator_means_reordered_s_1,aes(x=s,y=mean))+
-  geom_point(alpha=0.5, color="black")+
-  geom_smooth(method = "lm",color="black")+
-  facet_wrap(~Node_FG)+
-  labs(x="Specificty",y="Average frequency per motif position") +
-  theme_bw() + ggtitle("Floral visitors") +
-  theme(plot.title = element_text(hjust = 0.5, size = 25),
-        axis.text=element_text(size=12),
-        axis.title=element_text(size=18),
-        strip.text = element_text(size=20))
-
-p2 <- ggplot(plant_means_s,aes(x=s,y=mean))+
-  geom_point(alpha=0.5, color="black")+
-  geom_smooth(method = "lm", color="black")+
-  facet_wrap(~Node_FG)+
-  labs(x="Specificty",y="Average frequency per motif position")+
-  theme_bw() + ggtitle("Plants") +
-  theme(plot.title = element_text(hjust = 0.5, size = 25),
-        axis.text=element_text(size=12),
-        axis.title=element_text(size=18),
-        strip.text = element_text(size=20))
-
-p1/p2 +  plot_annotation(tag_levels = c('A'),  tag_suffix = ')') &  theme(plot.tag = element_text(size = 22))
+pollinators_sp_plot/plants_sp_plot & theme(axis.text=element_text(size=10),
+        axis.title=element_text(size=16)) & plot_annotation(tag_levels = c('A'),  tag_suffix = ')') &  theme(plot.tag = element_text(size = 22))
 
 ```
+
+\elandscape
 

### 2022-03-29 Manuscript/Supplementary_Material/Indirect_interactions_trophic_guild.Rmd
Number of indirect int plot

--- 2022-03-29 Manuscript/Supplementary_Material/Specialization_trophic_guild.Rmd
@@
 
-pollinators_sp_plot <- visreg(model_freq_specif_ind, "Specificity", by="Group",line.par = list(col = 'black'),
+pollinators_sp_plot <- visreg(model_freq_specif_ind, "Indirect_interactions", by="Group",line.par = list(col = 'black'),
                          strip.names=c("Bee",
@@
                                        "Syrphids"),gg = TRUE) + theme_bw() +
-  xlab("Specialization") + ylab("Partial residuals \n for percentile")+
-  scale_x_continuous(breaks = seq(0, 1, by = 0.5))+ scale_fill_grey(start=0.5, end=0.8) +
+  xlab("Number of indirect interactions") + ylab("Partial residuals \n for percentile")+
+ # scale_x_continuous(breaks = seq(0, 1, by = 0.5))+
+  scale_fill_grey(start=0.5, end=0.8) +
    theme(strip.text.x = element_text(size = 12),plot.title = element_text(hjust = 0.5, size = 23))+
@@
 
-plants_sp_plot <- visreg(model_freq_specif_ind_plant, "Specificity",line.par = list(col = 'black'), by="Group",
+plants_sp_plot <- visreg(model_freq_specif_ind_plant, "Indirect_interactions",line.par = list(col = 'black'), by="Group",
        strip.names=c("Selfing herbs",
@@
                      "Short-lived outcrossers with\nlong zygomorphic flowers"),gg = TRUE)+ theme_bw() +
-  xlab("Specialization") + ylab("Partial residuals \n for percentile")+
-  scale_x_continuous(breaks = seq(0, 1, by = 0.5))+
+  xlab("Number of indirect interactions") + ylab("Partial residuals \n for percentile")+
+  #scale_x_continuous(breaks = seq(0, 1, by = 0.5))+
    theme(strip.text.x = element_text(size = 12),plot.title = element_text(hjust = 0.5, size = 23))+

### 2022-03-30 Manuscript/Supplementary_Material/Supporting_information_Functional_Ecology.Rmd
supporting info updated

@@
 
-**Figure S6** Association between the frequency and specificity of the different groups on motif positions.
-
-**Figure S7** Frequency of floral visitor groups and number of indirect interactions per motif positions.
-
-**Figure S8** Frequency of plant groups and number of indirect interactions per motif positions.
+**Figure S6** Association between the percentile and specificity of the different plant and floral visitor groups on motif positions.
+
+**Figure S7** Association between the percentile and number of indirect interactions of the different plant and floral visitor groups on motif positions.
+
+**Figure S8** Frequency of floral visitor groups and number of indirect interactions per motif positions.
+
+**Figure S9** Frequency of plant groups and number of indirect interactions per motif positions.
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, fig.pos="t", warning=FALSE,fig.align="center", fig.width=14,fig.height=7, out.width='100%'}
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align="center", fig.width=14,fig.height=7, out.width='100%',  fig.cap="\\textbf{Figure S6.} Association between the percentile and specialization of the different plant and floral visitor groups on motif positions"}
 
@@
 
-pollinators_sp_plot <- visreg(model_freq_specif_ind, "Specificity", by="Group",line.par = list(col = 'black'),
+pollinators_sp_plot <- visreg(model_freq_specif_ind, "Specificity",scale="response", by="Group",line.par = list(col = 'black'),points=list(size=0),
                          strip.names=c("Bee",
@@
                                        "Syrphids"),gg = TRUE) + theme_bw() +
-  xlab("Specialization") + ylab("Partial residuals \n for percentile")+
+  xlab("Specialization") + ylab("Percentile")+
   scale_x_continuous(breaks = seq(0, 1, by = 0.5))+ scale_fill_grey(start=0.5, end=0.8) +
    theme(strip.text.x = element_text(size = 12),plot.title = element_text(hjust = 0.5, size = 23))+
-    ggtitle("Floral visitors")
-
-plants_sp_plot <- visreg(model_freq_specif_ind_plant, "Specificity",line.par = list(col = 'black'), by="Group",
+    ggtitle("Floral visitors")+ylim(-0.15,1)+geom_point(data=pollinator_freq_position_s_ind, aes(Specificity,Percentil), alpha=0.5)
+
+plants_sp_plot <- visreg(model_freq_specif_ind_plant, "Specificity",line.par = list(col = 'black'), by="Group",scale="response",points=list(size=0),
        strip.names=c("Selfing herbs",
@@
                      "Short-lived outcrossers with\nlong zygomorphic flowers"),gg = TRUE)+ theme_bw() +
-  xlab("Specialization") + ylab("Partial residuals \n for percentile")+
+  xlab("Specialization") + ylab("Percentile")+
   scale_x_continuous(breaks = seq(0, 1, by = 0.5))+
    theme(strip.text.x = element_text(size = 12),plot.title = element_text(hjust = 0.5, size = 23))+
-  ggtitle("Plants")
+  ggtitle("Plants")+ylim(-0.15,1)+geom_point(data=plant_freq_position_s_ind, aes(Specificity,Percentil), alpha=0.5)
 
@@
 
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align="center", fig.width=14,fig.height=7, out.width='100%', fig.cap="\\textbf{Figure S7.} Association between the percentile and number of indirect interactions of the different plant and floral visitor groups on motif positions"}
+
+library(ggplot2)
+library(glmmTMB)
+#Read floral visitor data and model output
+model_freq_specif_ind <- readRDS("../../Data/RData/model_freq_specif_ind.RData")
+pollinator_freq_position_s_ind <- readRDS("../../Data/RData/pollinator_freq_position_s_ind.RData")
+#Read plant data and model output
+model_freq_specif_ind_plant <- readRDS("../../Data/RData/model_freq_specif_ind_plant.RData")
+plant_freq_position_s_ind <- readRDS("../../Data/RData/plant_freq_position_s_ind.RData")
+
+library(visreg)
+# Pollinator Model REAL OUTPUTS!!!
+
+pollinators_sp_plot <- visreg(model_freq_specif_ind, "Indirect_interactions", scale="response", by="Group",line.par = list(col = 'black'),
+                         strip.names=c("Bee",
+                                       "Coleoptera",
+                                       "Lepidoptera",
+                                       "Non-bee-Hymenoptera",
+                                       "Non-syrphids-diptera",
+                                       "Syrphids"),gg = TRUE) + theme_bw() +
+  xlab("Number of indirect interactions") + ylab("Percentile")+
+ # scale_x_continuous(breaks = seq(0, 1, by = 0.5))+
+  scale_fill_grey(start=0.5, end=0.8) +
+   theme(strip.text.x = element_text(size = 12),plot.title = element_text(hjust = 0.5, size = 23))+
+    ggtitle("Floral visitors") +ylim(-0.15,1)+geom_point(data=pollinator_freq_position_s_ind, aes(Indirect_interactions,Percentil), alpha=0.5)
+
+plants_sp_plot <- visreg(model_freq_specif_ind_plant, "Indirect_interactions",line.par = list(col = 'black'), by="Group",scale="response",
+       strip.names=c("Selfing herbs",
+                     "Small outcrossing perennials",
+                     "Self-incompatible perennials\nwith large flowers",
+                     "Tall plants with small\nunisexual flowers",
+                     "Short-lived outcrossers with\nlong zygomorphic flowers"),gg = TRUE)+ theme_bw() +
+  xlab("Number of indirect interactions") + ylab("Percentile")+
+  #scale_x_continuous(breaks = seq(0, 1, by = 0.5))+
+   theme(strip.text.x = element_text(size = 12),plot.title = element_text(hjust = 0.5, size = 23))+
+  ggtitle("Plants")+ylim(-0.15,1)+geom_point(data=plant_freq_position_s_ind, aes(Indirect_interactions,Percentil), alpha=0.5)
+
+library(patchwork)
+pollinators_sp_plot/plants_sp_plot & theme(axis.text=element_text(size=10),
+        axis.title=element_text(size=16)) & plot_annotation(tag_levels = c('A'),  tag_suffix = ')') &  theme(plot.tag = element_text(size = 22))
+
+```
+
 \elandscape
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S7.} Frequency of the different floral visitor groups on the different motif positions aggregated by the number of indirect interactions for the different motif positions."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S8.} Frequency of the different floral visitor groups on the different motif positions aggregated by the number of indirect interactions for the different motif positions."}
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S8.} Frequency of the different plant groups on the different motif positions aggregated by the number of indirect interactions for the different motif positions."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S9.} Frequency of the different plant groups on the different motif positions aggregated by the number of indirect interactions for the different motif positions."}
 

### 2022-03-30 Manuscript/Supplementary_Material/Supporting_information_Functional_Ecology.Rmd
Update Supporting_information_Functional_Ecology.Rmd

@@
    theme(strip.text.x = element_text(size = 12),plot.title = element_text(hjust = 0.5, size = 23))+
-    ggtitle("Floral visitors")+ylim(-0.15,1)+geom_point(data=pollinator_freq_position_s_ind, aes(Specificity,Percentil), alpha=0.5)
+    ggtitle("Floral visitors")+ylim(-0.15,1)+geom_point(data=pollinator_freq_position_s_ind, aes(Specificity,Percentil), alpha=0.1)
 
@@
    theme(strip.text.x = element_text(size = 12),plot.title = element_text(hjust = 0.5, size = 23))+
-  ggtitle("Plants")+ylim(-0.15,1)+geom_point(data=plant_freq_position_s_ind, aes(Specificity,Percentil), alpha=0.5)
+  ggtitle("Plants")+ylim(-0.15,1)+geom_point(data=plant_freq_position_s_ind, aes(Specificity,Percentil), alpha=0.1)
 

### 2022-03-30 Manuscript/Main_text/Main_text_Functional_Ecology.Rmd
edits

@@
 Bees appear consistently in generalised motif positions with low number of indirect interactions while the rest of floral visitor groups are associated with more specialised motif positions with higher number of indirect interactions.
-All plant groups are principally associated with specialised motif positions but only tall plant species with separated sexes (e.g., woody dioecious or monoecious species) are associated with lower number of indirect interactions.
+All plant groups are over-represented on specialised motif positions but only tall plant species with separated sexes (e.g., woody dioecious or monoecious species) are more frequent on motif positions with low number of indirect interactions.
 Interestingly, the realized combinations of different species groups within a motif can not be retrieved from their joint probability distributions, indicating that group combinations are not random either.
@@
 Prior to analyses, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.
-This approach was preferred since quantitative motif analysis have been developed just recently and more work is needed to fully understand and interpret the information that they can convey [simmons2020].
+This approach was preferred since quantitative motif analysis have been developed just recently and more work is needed to fully understand and interpret the information that they can convey [@simmons2020].
 All analyses were run considering singletons (species with only one interaction detected) but we conducted a second exploration without singletons (64.98$\%$ of interactions) to evaluate the effect of rare species on the observed patterns.
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, fig.pos="t", warning=FALSE,out.width="75%",fig.align="center", fig.cap="\\textbf{Figure 1.} (Adapted figure of Simmons et al., 2019).
+```{r, echo=FALSE, message=FALSE, cache=FALSE, fig.pos="t", warning=FALSE,out.width="75%",fig.align="center", fig.cap="\\textbf{Figure 1.} Adapted figure of Simmons et al., (2019).
 All possible motif network structures from two to five species in bipartite networks grouped by the different motif classes (2-species, 3-species, 4-species and 5-species).
@@
 Motifs whose percentile is close to 0 or 100 are under- or over-represented in the empirical networks, respectively, and thus they cannot be predicted by connectance and the number of species alone.
-To summarize general patterns across networks, we used an intercept-only linear mixed model (LMM) per motif with the help of the package lmer version _1.1-21_ [@bates2015], where the response variable was the observed motif percentile per network.
-Note that as we are only interestedin modelling the intercept value, no predictors were specified.
+To summarize general patterns across networks, we used an intercept-only linear mixed model (LMM) per motif with the help of the _lme4_ package version _1.1-21_ [@bates2015], where the response variable was the observed motif percentile per network.
+Note that as we are only interested in modelling the intercept value, no predictors were specified.
 In these models, we used the study identifiers in **Table S1** as a random intercept.
@@
 Hence, we assessed the average motif frequency per species group, after controlling for the variation at the study level.
-Finally, we visualized with the help of the package _ComplexHeatmap_ version _2.6.2_ [@gu2016] over- and under-representation of plant and floral visitor groups on the different motif positions.
+Finally, we visualized with the help of the _ComplexHeatmap_ package version _2.6.2_ [@gu2016] over- and under-representation of plant and floral visitor groups on the different motif positions.
 
@@
 Values of the vector $si$, range between 1, complete specialization (1 partner within the motif) and 0 complete generalism (all possible partners within the motif).
-Then, we calculated the number of indirect interactions for each motif position and trophic guild (i.e., plants or floral visitors) as $z_i-1$ where $z_i$ is the total number of nodes for a trophic guild in a given motif.
-Because all nodes within a motif are connected, we only had to subtract the node of interest to $z_i$ to obtain the total number of indirect interactions by position and guild.
+Then, because all nodes within a motif are connected, we calculated the number of indirect interactions ($n_i$) for each motif position and trophic guild (i.e., plants or floral visitors) as $n_i=z_i-1$, where $z_i$ is the total number of nodes for a trophic guild in a given motif.
 Finally, we analysed in a single model how specialization and the number of indirect interactions were associated with the observed percentiles for each trophic guild and motif position (see paragraph above).
-For this, we fitted a LMM model with the help again of the _lmer_ package where we considered specialization and number of indirect interactions as response variables with the interaction by plant and floral visitor group for both response variables.
+For this, we fitted a LMM model with the help again of the _lme4_ package where we considered specialization and number of indirect interactions as response variables with the interaction by plant and floral visitor group for both response variables.
 Further, we considered as random factor motif position nested within study system.
-All model diagnostics were conducted with the help of the R package _Dharma_ [@hartig2017] version _0.3.3.0_.
-
-\newpage
+All model diagnostics were conducted with the help of the _Dharma_ package [@hartig2017] version _0.3.3.0_ and model outputs were visualized with the _visreg_ package [@breheny2017] version 2.7.0.
 
@@
 
-For both floral visitor and plant groups we found that their observed frequencies on motif positions are linked to different ecological roles.
-First, for floral visitors, we found that bees had a tendency to appear in higher frequencies on motif positions that involved generalism (i.e.
-lower specificity values) while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) showed the opposite trend with higher frequency on motif positions that implied a greater level of specialization (**Figure S6 A**).
-Although plants did not have as marked trends as floral visitors, all plant groups showed a slight tendency for generalism (**Figure S6 B**).
-Second, regarding the number of indirect interactions, bees and tall plants with unisexual flowers showed greater frequency on motif positions that involve low number of indirect interactions (**Figure S7 and Figure S8**).
-The rest of floral visitor groups showed the opposite tendency and had higher frequencies on motif positions with high number of indirect interactions (**Figure S7**).
-The rest of plant groups did not show major differences on their frequencies on motifs that implied different number of indirect interactions (**Figure S8**).[Aqui no entiendo por que no haces un solo modelo freq ~ generalism + nº of links]()
+For both floral visitor and plant groups we found over- and under-representation on different motif positions that implied different ecological roles.
+First, for floral visitors, we found that bees were over-represented on motif positions that involved generalism (i.e., lower specificity values) while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) showed the opposite trend with over-representation on motif positions that implied a greater level of specialization (**Figure S6 A**).
+Although plants did not have as marked trends as floral visitors, all plant but tall plants with small unisexual flowers had a slight tendency to be over-represented on motif positions that implied a greater level of specialization (**Figure S6 B**).
+Second, regarding the number of indirect interactions, bees were over-represented in motif positions with low number of indirect interactions (**Figure S7 A**) and the rest of floral visitor groups showed no differences across positions in comparison with simulated networks.
+For plants, all groups showed a tendency to be over-represented on motif positions with higher number of indirect interactions (**Figure S7 B**).
+When we further explore the observed frequencies by number of indirect interactions for floral visitor and plant groups, we found that both bees and tall plants with small unisexual flowers were the only groups with high frequencies on motif positions associated with low number interactions in comparison with the other floral visitor and plant groups (**Figure S8 and Figure S9**).
 
@@
 
-\newpage
-
 **Over- and under-represented group combinations of motifs**
@@
 For instance, when we compare motifs with equal structure for both trophic levels, we found that floral visitors had always over-representation in the positions that implied the highest number of direct links (e.g., positions 16 and 46 from motifs 7 and 17, respectively).
-Despite this being in good agreement with the current view of the generalist nature of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of generalist network motifs was driven by the taxonomic group of bees (**Figure S6**) while the rest of the taxonomic groups tended to be under-represented.
+Despite this being in good agreement with the current view of the generalist nature of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of generalist network motifs was driven by the taxonomic group of bees while the rest of the taxonomic groups tended to be under-represented (**Figure S6 A**).
 In contrast, non-bee groups were over-represented in motif positions associated with specialised roles.
@@
 Interestingly, bees also were the group with lower number of indirect interactions while the rest of floral visitor groups showed clearly higher number of indirect interactions indicating that these non-bee floral visitor groups may experience higher competitive interactions for floral resources [@thomson2020].
-Despite plant functional groups showed little differences between them on their motif frequencies, all groups showed a tendency to be more represented on motif positions that were associated with higher levels of specialization.
+Despite plant functional groups showed little differences between them on their motif frequencies, all groups showed a tendency to be over-represented on motif positions that were associated with higher levels of specialization.
 This tendency towards specialist roles may be the result of co-evolutionary processes (e.g., trait-matching) between plants and pollinators to optimise pollen transfer [@moreira2019].
@@
 Further, we found that plant and floral visitor groups are associated with different motif positions that involve distinct ecological roles (e.g., generalization versus specialization) and that the different motif combinations are strongly constrained.
-Global change drivers are reshuffling ecological communities [@bascompte2019].
-Although we are still far to predict how this new combinations of species will interact, our work is a first step to elucidate how novel interactions will form beyond pairwise interactions.
+Although we are still far to predict how species interact, our work is a first step to elucidate interactions beyond pairwise.
 

### 2022-03-30 Manuscript/Main_text/Main_text_Functional_Ecology.Rmd
Edits on main text

@@
 Because network motifs can capture both direct and indirect interactions, by analysing over- and under-representation of motifs we were able to explore in great detail the structure of interactions of plant-pollinator networks.
-We have explored for the first time the overall structure and representation of network motifs in real plant-pollinator networks at a macro-ecological scale and shown that the different motifs up to five nodes are consistently over- or under-represented in comparison with simulated networks, therefore indicating the presence of ecological processes shaping their structure.
-Despite the presence of multiple ecological processes likely operating at the same time (e.g., neutral effects, morphological matching or phenological overlap), we found a tendency for over-represented structures with more densely connected motifs (i.e., complete, fan and asymmetric complete).
+We have explored for the first time the overall structure and representation of network motifs in real plant-pollinator networks at a macro-ecological scale and shown that the different motifs up to five nodes are consistently over- or under-represented in comparison with simulated networks.
+Despite the presence of multiple ecological processes (e.g., neutral effects, morphological matching or phenological overlap) shaping motif structure, we found a tendency for over-represented structures with more densely connected motifs (i.e., complete, fan and asymmetric complete).
 As suggested in @simmons2020, a higher proportion of these densely connected motifs could reflect that neutral effects are the predominant ecological process governing the structure of network motifs.
-Thus, as indicated for other network properties like nestedness at the macro-scale level [@krishna2008; @suweis2013], or interaction probability at the species level [@bartomeus2016], species relative abundances (i.e., neutral effects) may be also the predominant ecological process governing the meso-scale structure on plant-pollinator networks.
+Thus, as indicated for other network properties like nestedness at the macro-scale level [@krishna2008; @suweis2013], or interaction probability at the species level [@bartomeus2016], species relative abundances (i.e., neutral effects) may be also the main driver governing the meso-scale structure on plant-pollinator networks.
 
@@
 Further, we found that plant and floral visitor groups are associated with different motif positions that involve distinct ecological roles (e.g., generalization versus specialization) and that the different motif combinations are strongly constrained.
-Although we are still far to predict how species interact, our work is a first step to elucidate interactions beyond pairwise.
+Although we are still far to predict how species interact, our work is a first step to elucidate beyond pairwise interactions.
 

### 2022-03-31 Manuscript/Main_text/Main_text_Functional_Ecology.Rmd
Updates on main text

@@
 Detecting those relationships is not trivial since they go beyond pairwise interactions, but may get blurred when considering full network descriptors.
-Recent work has shown the network meso-scale can capture this important information.
+Recent work has shown that the network meso-scale can capture this important information.
 The meso-scale describes network subgraphs representing patterns of interactions between a small number of species (i.e., motifs) that constitute the building blocks of the whole network.
@@
 Furthermore, we find that distinct motif positions describing species ecological roles (e.g., generalization and number of indirect interactions) are occupied by different plant and floral visitor groups on both trophic levels.
-Bees appear consistently in generalised motif positions with low number of indirect interactions while the rest of floral visitor groups are associated with more specialised motif positions with higher number of indirect interactions.
-All plant groups are over-represented on specialised motif positions but only tall plant species with separated sexes (e.g., woody dioecious or monoecious species) are more frequent on motif positions with low number of indirect interactions.
+Bees appear less frequently in specialised motif positions with high number of indirect interactions, while the rest of floral visitor groups are infrequent in generalized motif positions with low number of indirect interactions.
+All plant groups tend to be over-represented on specialised motif positions, except tall plant species with separated sexes (e.g., woody dioecious or monoecious species), which are more frequent on motif positions with low number of indirect interactions.
 Interestingly, the realized combinations of different species groups within a motif can not be retrieved from their joint probability distributions, indicating that group combinations are not random either.
@@
 Despite the widespread nature of indirect interactions in ecological communities [@strauss1991], plant-pollinator research often fails to finely capture those indirect interactions with the conventional analytical tools that condense the information either by species (e.g., degree) or in global topological indices (e.g., nestedness).
-Nonetheless, the emerging framework of network motifs (small sub-networks observed within a given network) in plant-pollinator research allows to consider both direct and indirect interactions [@simmons2019].
-Motifs are often referred to as the building blocks of a network that depict subsets of interactions [@milo2002].
+Nonetheless, the emerging framework of network motifs [small sub-networks observed within a given network which are often referred as its building blocks\; @milo2002] allows to consider both direct and indirect interactions [@simmons2019].
 The analysis of network motifs in plant-pollinator networks have revealed that the different ecological processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions [@simmons2020].
@@
 Yet, our understanding of the ecological implications of network motifs in real plant-pollinator networks remains in its infancy.
-Moreover, it is unclear how the species ecology and life-history traits determines its functional role within the network of interactions [@coux2016].
+Moreover, it is unclear how the species ecology and life-history traits determine its functional role within the network of interactions [@coux2016].
 For example, large pollinators can forage larger distances [@greenleaf2007], deposit greater pollen quantities [@foldesi2021] and handle complex zygomorphic flowers in comparison with small pollinators that are restricted to lower floral complexity [@gong2009].
-How this different pollinator behavior translates into their interaction topology is unknown.
+Despite these obvious differences in pollinator behaviour, how contrasting species' ecology translates into different interaction patterns is still unknown.
 Similarly, recent empirical findings indicate that the meso-scale is the best descriptor of plant reproductive success [@allen2021], but little is known about how plants reproductive strategies shape their position within the network of interactions.
 Although some studies have evaluated plant reproductive strategies in plant-pollinator networks [@tur2013; @lazaro2020], this is an often overlooked aspect in a community context [@devaux2014] and rarely incorporated into plant-pollinator network studies.
-Hence, exploring how the main plant and floral visitor life-history strategies integrate with the emergent motif framework could help to progress knowledge on plant-pollinator interactions.
+Hence, exploring how the main plant and floral visitor life-history strategies integrate with the emergent framework of network motifs could help to progress knowledge on the ecological processes that shape plant-pollinator interactions.
 
@@
 To investigate the structure of the meso-scale in plant-pollinator networks, we gathered published plant-pollinator networks with worldwide distribution.
-Then, we classified the plant and floral visitor species from these networks into groups that summarize their main life-history strategies.
-After, we calculated the normalized motif frequencies and investigated if these frequencies are similar or not to the ones expected by chance with the help of null models.
-Then, for each group of plants and floral visitors we also calculated the normalized group frequency in the different motif positions and investigated their overall representation by comparing these observed frequencies with their simulated counterparts.
-Finally, we compared if there are differences in the observed frequencies of motif combinations in empirical networks and the expected frequencies of motif combinations calculated as the product of the probabilities of the different plant and floral visitor groups within the motif.
+Then, we classified the different plant and floral visitor species from these networks into groups that summarise their main life-history strategies.
+After, we calculated the normalised motif frequencies and investigated if these frequencies are similar or not to the ones expected by chance with the help of null models.
+Then, for each group of plants and floral visitors we investigated the ecological implications of their overall representation on the different motif positions, by comparing, on the one hand, the observed (normalised) frequencies of each group in the different motif positions with the frequencies of their simulated counterparts, and, on the other hand, the differences among the patterns of connections of motif positions.
+Finally, we compared if there are differences in the observed frequencies of motif combinations from the empirical networks and the expected frequencies of motif combinations calculated as the product of the probabilities of the different plant and floral visitor groups within the motif.
 
@@
 To feed the clustering analysis, we calculated the distance between the different qualitative and scaled quantitative variables with Gower distance [@gower1971].
-For this, we used the function _gowdis_ with method _ward.D2_ from the package _FD_ version _1.0-12_ [@laliberte2014].
-Finally, we conducted hierarchical clustering with the function _hclust_ from the _R_ stats package version _4.0.5_ and calculated the optimal number of clusters with the function _kgs_ from the package _maptree_ version _1.4-7_ [@white2009].
+For this, we used the function _gowdis_ with method _ward.D2_ from the _FD_ package version _1.0-12_ [@laliberte2014].
+Finally, we conducted hierarchical clustering with the function _hclust_ from the _R_ stats package version _4.0.5_ and calculated the optimal number of clusters with the function _kgs_ from the _maptree_ package version _1.4-7_ [@white2009].
 
 Second, floral visitors were aggregated into taxonomic groups based on taxonomic rank as done similarly in other plant-pollinator studies [@fenster2004; @ollerton2009].
-We opted to divide floral visitors on the taxonomic rank level and not with functional traits because the main orders of floral visitors differed in form and behaviour and had lower superior taxonomical complexity (i.e., floral visitors had 6 orders versus plants that had 38).
+We opted to divide floral visitors on the taxonomic rank level and not with functional traits because the main orders of floral visitors differed in form and behaviour and had lower superior taxonomic complexity (i.e., floral visitors had 6 orders versus plants that had 38).
 Thus, this allowed us to group floral visitors into groups that represented approximately the main life strategies of the possible pollinators: (i) bees (Hymenoptera-Anthophila), (ii) non-bee Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Syrphidae-Diptera), (iv) non-syrphids-Diptera, (v) Lepidoptera and (vi) Coleoptera.
@@
 Throughout the entire manuscript, floral visitors occupy the top nodes of the different motifs and plants the bottom ones.
-To control for variation in network size, motif frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains).
-In addition, we excluded two-node motifs (or links) from our analyses because their normalised frequencies would always equal one.
+To control for variation in network size, motif frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., 2-species motifs, 3-species motifs, 4-species motifs and 5-species motifs).
+In addition, we excluded 2-species (or nodes) motifs from our analyses because its normalised frequencies would always equal one.
 Note that the aim is not comparing different networks, which may differ in sampling effort, but correctly describing the structure of each individual network.
@@
 Then, because all nodes within a motif are connected, we calculated the number of indirect interactions ($n_i$) for each motif position and trophic guild (i.e., plants or floral visitors) as $n_i=z_i-1$, where $z_i$ is the total number of nodes for a trophic guild in a given motif.
+Thus, we considered exclusively indirect interactions within plants though shared floral visitors or within floral visitors though shared plants.
 Finally, we analysed in a single model how specialization and the number of indirect interactions were associated with the observed percentiles for each trophic guild and motif position (see paragraph above).
@@
 To calculate the observed probability ($p_i^O$) of the different groups within a motif $i$ (e.g., motif 3, 'bee' + 'bee' + 'selfing herbs'), we divided the number of times that $i$ appears in our set of empirical networks ($n_i^O$) by the sum of the number of times that each possible combination appeared: $p_i^O = n_i^O / \sum_{k=1}^{53,250} n_k^O$.
-To estimate the expected probability of a given motif combination $i$, $p_i^E$, firstly, we calculated the probability of finding a given group $x$ in the position $\alpha$ of $i$, $p_i(x,\alpha)$.
-Then, by assuming the independency of $p_i(x,\alpha)$, we computed the expected probability of the combination $i$ as the product of the probability of its pairs $(x,\alpha)$, that is, $p_i^E = \prod _{(x,\alpha )\in i} p_i(x,\alpha)$.
-To obtain $p_i(x,\alpha)$, we proceeded as follows.
-First, we calculated the number of times that the group $x$ appears in the position $\alpha$ in each empirical network $\eta$, denoted as $n_i^{\eta}(x,\alpha)$.
-Then, by controlling for the variation at the network level, we assessed the average value of the absolute frequency with which group $x$ appears in the position $\alpha$, $n_i(x,\alpha) = E\left [ n_i^{\eta}(x,\alpha) \right ]$, and estimated $p_i(x,\alpha)$ as $p_i(x,\alpha) = n_i(x,\alpha)/\sum_{k}n_i(k,\alpha)$.
-To obtain $n_i(x,\alpha)$, we fitted a LMM per motif position, where the response variable was the number of times that a given position was observed per network, the explanatory variable was the group identifier, and the random intercept was given by network identifiers nested within the study identifiers.
+To estimate the expected probability ($p_i^E$) of a given motif combination $i$, we assumed that the probability of finding a given group $x$ in the position $\alpha$ is independent of the probabilities associated with other positions and groups in that motif.
+Therefore, the expected probability ($p_i^E$) of the motif combination $i$ is given by the product of the probabilities of its constituents ($p_i^E = \prod _{(x,\alpha )\in i} p_i(x,\alpha)$).
+Then, by controlling for the variation at the network level with an LMM (see below), we calculated the average number of times that the group $x$ appears in the position $\alpha$ (denoted as $n_i(x,\alpha)$).
+To obtain the expected probability $p_i(x,\alpha)$ we divided the number of times that the group $x$ appears in the position $\alpha$ by the the total number of times that any group was observed in that position (that is, $p_i(x,\alpha) = n_i(x,\alpha)/\sum_{k}n_i(k,\alpha)$).
+The average number of times that the group $x$ appears in the position $\alpha$ ($n_i(x,\alpha)$) was calculated with a LMM for each position, where the response variable was the number of times that a group was observed at a given position in each real-world network, the explanatory variable was the group identifier, and the random intercept was given by network identifiers nested within the study identifiers.
 
@@
 For both floral visitor and plant groups we found over- and under-representation on different motif positions that implied different ecological roles.
-First, for floral visitors, we found that bees were over-represented on motif positions that involved generalism (i.e., lower specificity values) while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) showed the opposite trend with over-representation on motif positions that implied a greater level of specialization (**Figure S6 A**).
-Although plants did not have as marked trends as floral visitors, all plant but tall plants with small unisexual flowers had a slight tendency to be over-represented on motif positions that implied a greater level of specialization (**Figure S6 B**).
+First, for floral visitors, we found that bees were less frequent on motif positions that involved specialisation (i.e., lower specificity values) while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) were infrequent in generalized motif positions with low number of indirect interactions (**Figure S6 A**).
+Although plants did not show differences with null models on their frequencies, all plant but tall plants with small unisexual flowers showed a slight tendency to be over-represented on specialised motif positions (**Figure S6 B**).
 Second, regarding the number of indirect interactions, bees were over-represented in motif positions with low number of indirect interactions (**Figure S7 A**) and the rest of floral visitor groups showed no differences across positions in comparison with simulated networks.
-For plants, all groups showed a tendency to be over-represented on motif positions with higher number of indirect interactions (**Figure S7 B**).
+For plants, all groups showed a slight trend to be over-represented on motif positions with higher number of indirect interactions (**Figure S7 B**).
 When we further explore the observed frequencies by number of indirect interactions for floral visitor and plant groups, we found that both bees and tall plants with small unisexual flowers were the only groups with high frequencies on motif positions associated with low number interactions in comparison with the other floral visitor and plant groups (**Figure S8 and Figure S9**).
@@
 In addition, motifs with small node combinations (i.e., 2 and 3 nodes) only appeared as under-represented.
-Motifs with 4 and 5-node combinations appeared in the three statistical categories but 4 node motifs had a higher proportion in the under-represented category (10% in comparison with the 1$\%$ and the 3$\%$ of the no statistical difference and over-represented categories, respectively).
-Finally, 5-node motifs were in similar proportions in the no statistical difference and over-represented categories (99$\%$ and 97$\%$, respectively) but they appeared in lower proportion in the under-represented category (89$\%$).
+Motifs with 4 and 5 node combinations appeared in the three statistical categories but 4 node motifs had a higher proportion in the under-represented category (10% in comparison with the 1$\%$ and the 3$\%$ of the no statistical difference and over-represented categories, respectively).
+Finally, 5 node motifs were in similar proportions in the no statistical difference and over-represented categories (99$\%$ and 97$\%$, respectively) but they appeared in lower proportion in the under-represented category (89$\%$).
 When we explored the identity on the different positions of the most probable motif combinations we found that the most common plant and floral visitor groups were also the most probable on these motif combinations (lower panel **Figure 5**).
@@
 
-All data and code would be deposited at Driad Digital repository upon acceptance.
-For the review process we have added our plant dataset on google sheets and can be accessed with the help of the following link: https://docs.google.com/spreadsheets/d/1q3fFNwHb7k-kpLzxfgnAHGNUrdOiUnCRQU13NKXzTX4/edit?usp=sharing
+All data and code is deposited at GitHub: https://github.com/JoseBSL/FunctionalMotifs.
 

### 2022-03-31 Manuscript/Main_text/Main_text_Functional_Ecology.Rmd
Updates on main text and supp mat

@@
 By exploring 60 empirical plant-pollinator networks from 18 different studies with wide geographical coverage we show that some motifs are consistently under- or over-represented worldwide, suggesting that the building blocks of plant-pollinator networks are not random.
-Furthermore, we find that distinct motif positions describing species ecological roles (e.g., generalization and number of indirect interactions) are occupied by different plant and floral visitor groups on both trophic levels.
-Bees appear less frequently in specialised motif positions with high number of indirect interactions, while the rest of floral visitor groups are infrequent in generalized motif positions with low number of indirect interactions.
+Furthermore, we find that distinct motif positions describing species ecological roles (e.g., generalisation and number of indirect interactions) are occupied by different plant and floral visitor groups on both trophic levels.
+Bees appear less frequently in specialised motif positions with high number of indirect interactions, while the rest of floral visitor groups are infrequent in generalised motif positions with low number of indirect interactions.
 All plant groups tend to be over-represented on specialised motif positions, except tall plant species with separated sexes (e.g., woody dioecious or monoecious species), which are more frequent on motif positions with low number of indirect interactions.
@@
 For example, plant-pollinator network level approaches have identified common invariant structural properties across networks, including a degree distribution that decays as a power law [@jordano1987], nestedness [@bascompte2003], or modularity [@olesen2007].
-In addition, the local species position within the network can define its degree of specialization [@bluthgen2006] or its role in connecting the rest of the community [@olesen2007].
+In addition, the local species position within the network can define its degree of specialisation [@bluthgen2006] or its role in connecting the rest of the community [@olesen2007].
 Despite the unquestionable progress with the use of these metrics at both network and species level, condensing complex information into a single metric implies the loss of relevant ecological information that obscures the understanding of species interactions [@cirtwill2018; @simmons2019].
@@
 
-To understand if the different plant and floral visitor groups are associated with motif positions that represent different network roles, we characterized the roles of each motif positions for plant and floral visitor groups in terms of their specialization and number of indirect interactions.
+To understand if the different plant and floral visitor groups are associated with motif positions that represent different network roles, we characterized the roles of each motif positions for plant and floral visitor groups in terms of their specialisation and number of indirect interactions.
 To that end, we calculated the specificity of each motif position following @poisot2015 as $s_i = L - l_i / L - 1$, where $L$ is the total number of groups and $l_i$ the number of interaction partners of the group $i$ in a given motif.
-Values of the vector $si$, range between 1, complete specialization (1 partner within the motif) and 0 complete generalism (all possible partners within the motif).
+Values of the vector $si$, range between 1, complete specialisation (1 partner within the motif) and 0 complete generalism (all possible partners within the motif).
 Then, because all nodes within a motif are connected, we calculated the number of indirect interactions ($n_i$) for each motif position and trophic guild (i.e., plants or floral visitors) as $n_i=z_i-1$, where $z_i$ is the total number of nodes for a trophic guild in a given motif.
@@
 Further, we considered as random factor motif position nested within study system.
-All model diagnostics were conducted with the help of the _Dharma_ package [@hartig2017] version _0.3.3.0_ and model outputs were visualized with the _visreg_ package [@breheny2017] version 2.7.0.
+All model diagnostics were conducted with the help of the _Dharma_ package [@hartig2017] version _0.3.3.0_ and model outputs were visualized with the _visreg_ package [@breheny2020] version 2.7.0.
 
@@
 For both floral visitor and plant groups we found over- and under-representation on different motif positions that implied different ecological roles.
-First, for floral visitors, we found that bees were less frequent on motif positions that involved specialisation (i.e., lower specificity values) while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) were infrequent in generalized motif positions with low number of indirect interactions (**Figure S6 A**).
+First, for floral visitors, we found that bees were less frequent on motif positions that involved specialization (i.e., lower specificity values) while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) were infrequent in generalised motif positions with low number of indirect interactions (**Figure S6 A**).
 Although plants did not show differences with null models on their frequencies, all plant but tall plants with small unisexual flowers showed a slight tendency to be over-represented on specialised motif positions (**Figure S6 B**).
@@
 Interestingly, bees also were the group with lower number of indirect interactions while the rest of floral visitor groups showed clearly higher number of indirect interactions indicating that these non-bee floral visitor groups may experience higher competitive interactions for floral resources [@thomson2020].
-Despite plant functional groups showed little differences between them on their motif frequencies, all groups showed a tendency to be over-represented on motif positions that were associated with higher levels of specialization.
+Despite plant functional groups showed little differences between them on their motif frequencies, all groups showed a tendency to be over-represented on motif positions that were associated with higher levels of specialisation.
 This tendency towards specialist roles may be the result of co-evolutionary processes (e.g., trait-matching) between plants and pollinators to optimise pollen transfer [@moreira2019].
@@
 In conclusion, by following the framework of @simmons2020 we have been able to explore competitive and facilitative interactions in plant-pollinator networks worldwide and found that indirect interactions are non-random and are more strongly related to neutral processes than to any other ecological process.
-Further, we found that plant and floral visitor groups are associated with different motif positions that involve distinct ecological roles (e.g., generalization versus specialization) and that the different motif combinations are strongly constrained.
+Further, we found that plant and floral visitor groups are associated with different motif positions that involve distinct ecological roles (e.g., generalisation versus specialisation) and that the different motif combinations are strongly constrained.
 Although we are still far to predict how species interact, our work is a first step to elucidate beyond pairwise interactions.

### 2022-03-31 Manuscript/Supplementary_Material/Supporting_information_Functional_Ecology.Rmd
Updates on main text and supp mat

@@
   arrange(`First author`)%>%
-  kable( longtable = T, booktabs = T,linesep = "\\addlinespace",align = c("cccc"),escape = FALSE, caption= "\\textbf{Table S1.} List of studies ordered by author with the year of publication, number of contributed networks and digital object identifier") %>%
+  kable( longtable = T, booktabs = T,linesep = "\\addlinespace",align = c("cccc"),escape = FALSE, caption= "\\textbf{Table S1.} List of studies ordered by author with the year of publication, number of contributed networks and digital object identifier.") %>%
   kable_styling(latex_options = c("repeat_header","striped"),  full_width=F,position = c("center"))
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="\\textbf{Figure S3.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions after removing non-robust links (singletones).
-The different motif positions are dividied by the average path length clasification by Simmons et al.
+The different motif positions are dividied by the average path length clasification determined by Simmons et al.
 (2020).
@@
 Panel A) shows the percentage of the different categories within trait represented with different colours for each functional group.
-Plot B) shows the radar plot of the different quantitative variables standardize on the same scale also coloured with the same patterns of colours as qualitative variables per cluster or functional group.
+Plot B) shows the radar plot of the different quantitative variables standardise on the same scale also coloured with the same patterns of colours as qualitative variables per cluster or functional group.
 Group 1 corresponds to short-lived selfers; group 2 to small outcrossing perennials; group 3 to self-incompatible perennials with large flowers; group 4 to tall plants with small unisexual flowers; and, group 5 to short-lived outcrossers with long zygomorphic flowers."}
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align="center", fig.width=14,fig.height=7, out.width='100%',  fig.cap="\\textbf{Figure S6.} Association between the percentile and specialization of the different plant and floral visitor groups on motif positions"}
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align="center", fig.width=14,fig.height=7, out.width='100%',  fig.cap="\\textbf{Figure S6.} Association between the percentile (see main text) and specialization of the different plant and floral visitor groups on motif positions.
+Here we consider that percentiles over 0.75 indicate over-representation and percentiles under 0.25 under-representation in the comparison among empirical and simulated networks"}
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align="center", fig.width=14,fig.height=7, out.width='100%', fig.cap="\\textbf{Figure S7.} Association between the percentile and number of indirect interactions of the different plant and floral visitor groups on motif positions"}
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align="center", fig.width=14,fig.height=7, out.width='100%', fig.cap="\\textbf{Figure S7.} Association between the percentile (see main text) and number of indirect interactions of the different plant and floral visitor groups on motif positions.
+Here we consider that percentiles over 0.75 indicate over-representation and percentiles under 0.25 under-representation in the comparison among empirical and simulated networks"}
 

### 2022-03-31 Manuscript/Supplementary_Material/Supporting_information_Functional_Ecology.Rmd
Edits on Supp Mat.

@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align="center", fig.width=14,fig.height=7, out.width='100%',  fig.cap="\\textbf{Figure S6.} Association between the percentile (see main text) and specialization of the different plant and floral visitor groups on motif positions.
-Here we consider that percentiles over 0.75 indicate over-representation and percentiles under 0.25 under-representation in the comparison among empirical and simulated networks"}
+Here we consider that percentiles above 0.75 indicate over-representation and percentiles below 0.25 under-representation in the comparison between empirical and simulated networks."}
 
@@
 ```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align="center", fig.width=14,fig.height=7, out.width='100%', fig.cap="\\textbf{Figure S7.} Association between the percentile (see main text) and number of indirect interactions of the different plant and floral visitor groups on motif positions.
-Here we consider that percentiles over 0.75 indicate over-representation and percentiles under 0.25 under-representation in the comparison among empirical and simulated networks"}
+Here we consider that percentiles above 0.75 indicate over-representation and percentiles below 0.25 under-representation in the comparison between empirical and simulated networks."}
 

### 2022-04-01 Manuscript/Main_text/Main_text_Functional_Ecology.Rmd
Update Main_text_Functional_Ecology.Rmd

@@
 To estimate the expected probability ($p_i^E$) of a given motif combination $i$, we assumed that the probability of finding a given group $x$ in the position $\alpha$ is independent of the probabilities associated with other positions and groups in that motif.
-Therefore, the expected probability ($p_i^E$) of the motif combination $i$ is given by the product of the probabilities of its constituents ($p_i^E = \prod _{(x,\alpha )\in i} p_i(x,\alpha)$).
+Therefore, the expected probability ($p_i^E$) of the motif combination $i$ is given by the product of the probabilities of its constituents, i.e., $p_i^E = \prod _{(x,\alpha )\in i} p_i(x,\alpha)$, where $p_i(x,\alpha)$ is the probability of finding a given group $x$ in the position $\alpha$ of $i$.
 Then, by controlling for the variation at the network level with an LMM (see below), we calculated the average number of times that the group $x$ appears in the position $\alpha$ (denoted as $n_i(x,\alpha)$).

### 2022-04-01 Manuscript/Main_text/Main_text_Functional_Ecology.Rmd
Line numbering on main text

@@
 - \newcommand{\elandscape}{\end{landscape}}
+- \usepackage[left]{lineno}
+- \linenumbers
+
 output:
@@
 
-We have compiled 60 plant-pollinator networks from 18 different studies (**Table S1**).
-All studies sampled plant-pollinator interactions in natural systems and were selected based on wide geographical coverage (**Figure S1**) and presence of interaction frequency as a measure of interaction strength.
+We have compiled 60 plant-pollinator networks from 18 different studies (Table S1).
+All studies sampled plant-pollinator interactions in natural systems and were selected based on wide geographical coverage (Fig.
+S1) and presence of interaction frequency as a measure of interaction strength.
 In total, there were 503 plant species, 1,111 floral visitors species and 6,248 pairwise interactions registered.
@@
 First, plant species were grouped through hierarchical clustering into the optimal number of functional groups that summarized the main plant reproductive strategies.
-For this, we used the trait dataset collated in @lanuza2021 that comprised a total of 1506 species including the 503 species considered in this study (**Table S2**).
-This dataset consisted on 8 floral, 4 reproductive and 3 vegetative traits excluding traits with high percentage of missing values (over 30$\%$; **Table S3**).
+For this, we used the trait dataset collated in @lanuza2021 that comprised a total of 1506 species including the 503 species considered in this study (Table S2).
+This dataset consisted on 8 floral, 4 reproductive and 3 vegetative traits excluding traits with high percentage of missing values (over 30$\%$; Table S3).
 We opted to calculate the plant functional groups on this larger set of species because of the higher accuracy when delimiting functional groups with that many variables and species [@dolnicar2014].
@@
 All analyses were run considering singletons (species with only one interaction detected) but we conducted a second exploration without singletons (64.98$\%$ of interactions) to evaluate the effect of rare species on the observed patterns.
-Results without singletons are qualitatively consistent and are not further discussed in the main text (**Figures S2 and S3**).
-
-We calculated the frequency of all motifs up to five nodes (17 different motifs in total; see **Figure 1**) for each empirical network, by using the _bmotif_ package version _2.0.2_ [@bmotifsimmons2019].
+Results without singletons are qualitatively consistent and are not further discussed in the main text (Figs S2 and S3).
+
+We calculated the frequency of all motifs up to five nodes (17 different motifs in total; see Fig.
+1) for each empirical network, by using the _bmotif_ package version _2.0.2_ [@bmotifsimmons2019].
 We focused exclusively on motifs up to five nodes in our analyses for computational reasons and for the ease of visualization and interpretation of a reduced set of less complex network motifs.
@@
 Note that as we are only interested in modelling the intercept value, no predictors were specified.
-In these models, we used the study identifiers in **Table S1** as a random intercept.
+In these models, we used the study identifiers in Table S1 as a random intercept.
 By doing so, we obtained estimates of the average motif frequency, but controlling for the variation at the study level.
@@
 
-The hierarchical cluster analysis divided the dataset into five different groups with different and overlapping characteristics (**Figure S4** and **Figure S5**).
+The hierarchical cluster analysis divided the dataset into five different groups with different and overlapping characteristics (Figs S4 and S5).
 The first group referred to as 'selfing herbs' consisted on herbs with hermaphroditic flowers with high levels of autonomous selfing.
@@
 
-Most motifs were under- or over-represented (close to the 1st and 99th percentile, respectively) in the comparison between empirical and simulated networks (**Figure 2**).
+Most motifs were under- or over-represented (close to the 1st and 99th percentile, respectively) in the comparison between empirical and simulated networks (Fig.
+2).
 Motifs 3, 5, 9, 10 and 14 were under-represented in empirical networks, that is, all were close to the 1st percentile and under the 25th percentile.
@@
 
-The comparison of the plant and floral visitor group frequencies per motif position between empirical and simulated networks showed a `r over`$\%$ and `r under`$\%$ of over- (>75$^{th}$) and under-represented (<25th) groups in the different positions, respectively (**Figure 3**).
+The comparison of the plant and floral visitor group frequencies per motif position between empirical and simulated networks showed a `r over`$\%$ and `r under`$\%$ of over- (>75$^{th}$) and under-represented (<25th) groups in the different positions, respectively (Fig.
+3).
 Floral visitors showed a total of `r poll_over_75`$\%$ and `r poll_under_25`$\%$ of over- and under-represented groups in the different positions and plants `r plant_over_75`$\%$ and `r plant_under_25`$\%$ of over- and under-represented groups, respectively.
 Notably, the differences across groups were more marked for floral visitors than for plant groups (the differences between min and max percentiles per position were generally two-three times larger for floral visitors).
-From most over- to under-represented floral visitors groups on the different motif positions (indicated with the dendrogram order in **Figure 3**), we found: bees, non-syrphids Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.
+From most over- to under-represented floral visitors groups on the different motif positions (indicated with the dendrogram order in Fig.
+3), we found: bees, non-syrphids Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.
 Although plant functional groups showed less differences between them, there were also more represented groups than others, thus from most over- to under-represented groups on the different motif positions we found: self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.
@@
 For both floral visitor and plant groups we found over- and under-representation on different motif positions that implied different ecological roles.
-First, for floral visitors, we found that bees were less frequent on motif positions that involved specialization (i.e., lower specificity values) while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) were infrequent in generalised motif positions with low number of indirect interactions (**Figure S6 A**).
-Although plants did not show differences with null models on their frequencies, all plant but tall plants with small unisexual flowers showed a slight tendency to be over-represented on specialised motif positions (**Figure S6 B**).
-Second, regarding the number of indirect interactions, bees were over-represented in motif positions with low number of indirect interactions (**Figure S7 A**) and the rest of floral visitor groups showed no differences across positions in comparison with simulated networks.
-For plants, all groups showed a slight trend to be over-represented on motif positions with higher number of indirect interactions (**Figure S7 B**).
-When we further explore the observed frequencies by number of indirect interactions for floral visitor and plant groups, we found that both bees and tall plants with small unisexual flowers were the only groups with high frequencies on motif positions associated with low number interactions in comparison with the other floral visitor and plant groups (**Figure S8 and Figure S9**).
+First, for floral visitors, we found that bees were less frequent on motif positions that involved specialization (i.e., lower specificity values) while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) were infrequent in generalised motif positions with low number of indirect interactions (Fig.
+S6 A).
+Although plants did not show differences with null models on their frequencies, all plant but tall plants with small unisexual flowers showed a slight tendency to be over-represented on specialised motif positions (Fig.
+S6 B).
+Second, regarding the number of indirect interactions, bees were over-represented in motif positions with low number of indirect interactions (Fig.
+S7 A) and the rest of floral visitor groups showed no differences across positions in comparison with simulated networks.
+For plants, all groups showed a slight trend to be over-represented on motif positions with higher number of indirect interactions (Fig.
+S7 B).
+When we further explore the observed frequencies by number of indirect interactions for floral visitor and plant groups, we found that both bees and tall plants with small unisexual flowers were the only groups with high frequencies on motif positions associated with low number interactions in comparison with the other floral visitor and plant groups (Figs S8 and S9).
 
@@
 
-The different observed frequencies on the different motif positions showed a hierarchical order of probabilities for floral visitors (**Figure 4**).
+The different observed frequencies on the different motif positions showed a hierarchical order of probabilities for floral visitors (Fig.
+4).
 That is, the taxonomic group of 'bees' was the most abundant one on all motif positions followed by non-syrphid Diptera which was after bees, the second most frequent group on all positions.
@@
 The statistical comparison with z-scores between the observed and expected plant and floral visitor group combinations showed that we can not recover the observed combinations from its probability of occurrence.
-In fact, most combinations are under- or over- represented and follow a modified Gaussian distribution (Johnson's $S_U$) with 65$\%$ of under-represented group combinations, 20$\%$ of no statistical difference and 15$\%$ of under-represented ones (**Figure 5**).
+In fact, most combinations are under- or over- represented and follow a modified Gaussian distribution (Johnson's $S_U$) with 65$\%$ of under-represented group combinations, 20$\%$ of no statistical difference and 15$\%$ of under-represented ones (Fig.
+5).
 In addition, motifs with small node combinations (i.e., 2 and 3 nodes) only appeared as under-represented.
@@
 Finally, 5 node motifs were in similar proportions in the no statistical difference and over-represented categories (99$\%$ and 97$\%$, respectively) but they appeared in lower proportion in the under-represented category (89$\%$).
-When we explored the identity on the different positions of the most probable motif combinations we found that the most common plant and floral visitor groups were also the most probable on these motif combinations (lower panel **Figure 5**).
+When we explored the identity on the different positions of the most probable motif combinations we found that the most common plant and floral visitor groups were also the most probable on these motif combinations (lower panel Fig.
+5).
 
@@
 
-Overall, generalist network motifs for floral visitors were consistently over-represented (e.g., fan-type motifs; **Figure 2**).
+Overall, generalist network motifs for floral visitors were consistently over-represented (e.g., fan-type motifs; Fig.
+2).
 For instance, when we compare motifs with equal structure for both trophic levels, we found that floral visitors had always over-representation in the positions that implied the highest number of direct links (e.g., positions 16 and 46 from motifs 7 and 17, respectively).
-Despite this being in good agreement with the current view of the generalist nature of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of generalist network motifs was driven by the taxonomic group of bees while the rest of the taxonomic groups tended to be under-represented (**Figure S6 A**).
+Despite this being in good agreement with the current view of the generalist nature of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of generalist network motifs was driven by the taxonomic group of bees while the rest of the taxonomic groups tended to be under-represented (Fig.
+S6 A).
 In contrast, non-bee groups were over-represented in motif positions associated with specialised roles.
@@
 
-The probabilities of appearance of each functional group on the different motif positions were insufficient to predict most of the observed network position combinations (**Figure 5**).
+The probabilities of appearance of each functional group on the different motif positions were insufficient to predict most of the observed network position combinations (Fig.
+5).
 This implies that not just the representation of network motifs types but also the identity of the elements of their structure is non-random.

### 2022-04-01 Manuscript/Main_text/Main_text_Lanuza_Allen-Perkins_Bartomeus.Rmd
edits for Preprint

--- 2022-03-31 Manuscript/Main_text/Main_text_Functional_Ecology.Rmd
@@
 
-We have compiled 60 plant-pollinator networks from 18 different studies (**Table S1**).
-All studies sampled plant-pollinator interactions in natural systems and were selected based on wide geographical coverage (**Figure S1**) and presence of interaction frequency as a measure of interaction strength.
+We have compiled 60 plant-pollinator networks from 18 different studies (**Supporting Information Table S1**).
+All studies sampled plant-pollinator interactions in natural systems and were selected based on wide geographical coverage (**Supporting Information Figure S1**) and presence of interaction frequency as a measure of interaction strength.
 In total, there were 503 plant species, 1,111 floral visitors species and 6,248 pairwise interactions registered.
@@
 First, plant species were grouped through hierarchical clustering into the optimal number of functional groups that summarized the main plant reproductive strategies.
-For this, we used the trait dataset collated in @lanuza2021 that comprised a total of 1506 species including the 503 species considered in this study (**Table S2**).
-This dataset consisted on 8 floral, 4 reproductive and 3 vegetative traits excluding traits with high percentage of missing values (over 30$\%$; **Table S3**).
+For this, we used the trait dataset collated in @lanuza2021 that comprised a total of 1506 species including the 503 species considered in this study (**Supporting Information Table S2**).
+This dataset consisted on 8 floral, 4 reproductive and 3 vegetative traits excluding traits with high percentage of missing values (over 30$\%$; **Supporting Information Table S3**).
 We opted to calculate the plant functional groups on this larger set of species because of the higher accuracy when delimiting functional groups with that many variables and species [@dolnicar2014].
@@
 All analyses were run considering singletons (species with only one interaction detected) but we conducted a second exploration without singletons (64.98$\%$ of interactions) to evaluate the effect of rare species on the observed patterns.
-Results without singletons are qualitatively consistent and are not further discussed in the main text (**Figures S2 and S3**).
+Results without singletons are qualitatively consistent and are not further discussed in the main text (**Supporting Information Figures S2 and S3**).
 
@@
 Note that as we are only interested in modelling the intercept value, no predictors were specified.
-In these models, we used the study identifiers in **Table S1** as a random intercept.
+In these models, we used the study identifiers in **Supporting Information Table S1** as a random intercept.
 By doing so, we obtained estimates of the average motif frequency, but controlling for the variation at the study level.
@@
 
-The hierarchical cluster analysis divided the dataset into five different groups with different and overlapping characteristics (**Figure S4** and **Figure S5**).
+The hierarchical cluster analysis divided the dataset into five different groups with different and overlapping characteristics (**Supporting Information Figure S4** and **Figure S5**).
 The first group referred to as 'selfing herbs' consisted on herbs with hermaphroditic flowers with high levels of autonomous selfing.
@@
 For both floral visitor and plant groups we found over- and under-representation on different motif positions that implied different ecological roles.
-First, for floral visitors, we found that bees were less frequent on motif positions that involved specialization (i.e., lower specificity values) while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) were infrequent in generalised motif positions with low number of indirect interactions (**Figure S6 A**).
-Although plants did not show differences with null models on their frequencies, all plant but tall plants with small unisexual flowers showed a slight tendency to be over-represented on specialised motif positions (**Figure S6 B**).
-Second, regarding the number of indirect interactions, bees were over-represented in motif positions with low number of indirect interactions (**Figure S7 A**) and the rest of floral visitor groups showed no differences across positions in comparison with simulated networks.
-For plants, all groups showed a slight trend to be over-represented on motif positions with higher number of indirect interactions (**Figure S7 B**).
-When we further explore the observed frequencies by number of indirect interactions for floral visitor and plant groups, we found that both bees and tall plants with small unisexual flowers were the only groups with high frequencies on motif positions associated with low number interactions in comparison with the other floral visitor and plant groups (**Figure S8 and Figure S9**).
+First, for floral visitors, we found that bees were less frequent on motif positions that involved specialization (i.e., lower specificity values) while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) were infrequent in generalised motif positions with low number of indirect interactions (**Supporting Information Figure S6 A**).
+Although plants did not show differences with null models on their frequencies, all plant but tall plants with small unisexual flowers showed a slight tendency to be over-represented on specialised motif positions (**Supporting Information Figure S6 B**).
+Second, regarding the number of indirect interactions, bees were over-represented in motif positions with low number of indirect interactions (**Supporting Information Figure S7 A**) and the rest of floral visitor groups showed no differences across positions in comparison with simulated networks.
+For plants, all groups showed a slight trend to be over-represented on motif positions with higher number of indirect interactions (**Supporting Information Figure S7 B**).
+When we further explore the observed frequencies by number of indirect interactions for floral visitor and plant groups, we found that both bees and tall plants with small unisexual flowers were the only groups with high frequencies on motif positions associated with low number interactions in comparison with the other floral visitor and plant groups (**Supporting Information Figure S8 and Figure S9**).
 
@@
 For instance, when we compare motifs with equal structure for both trophic levels, we found that floral visitors had always over-representation in the positions that implied the highest number of direct links (e.g., positions 16 and 46 from motifs 7 and 17, respectively).
-Despite this being in good agreement with the current view of the generalist nature of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of generalist network motifs was driven by the taxonomic group of bees while the rest of the taxonomic groups tended to be under-represented (**Figure S6 A**).
+Despite this being in good agreement with the current view of the generalist nature of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of generalist network motifs was driven by the taxonomic group of bees while the rest of the taxonomic groups tended to be under-represented (**Supporting Information Figure S6 A**).
 In contrast, non-bee groups were over-represented in motif positions associated with specialised roles.
@@
 
-*Acknowledgements* - This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2).
+# Acknowledgements
+
+This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2).
 JBL also thanks the University of New England for the funding provided to carry out this work.
@@
 
-# Data availability statement
-
-All data and code is deposited at GitHub: https://github.com/JoseBSL/FunctionalMotifs.
-
 \newpage

### 2022-04-06 Manuscript/Main_text/Main_text_Biorxiv.Rmd
edit

--- 2022-04-01 Manuscript/Main_text/Main_text_Lanuza_Allen-Perkins_Bartomeus.Rmd
@@
 ---
+
+__Jose B. Lanuza^1,2^__  | __Alfonso Allen-Perkins^2,3^__ | __Ignasi Bartomeus^2^__
+
+1 School of Environmental and Rural Science, University of New England, Armidale, New South Wales 2350, Australia.
+
+2 Estación Biológica de Doñana (EBD-CSIC), E-41092 Seville, Spain.
+
+3 Departamento de Ingeniería Eléctrica, Electrónica, Automática y Física Aplicada, ETSIDI, Universidad Politécnica de Madrid, 28040 Madrid, Spain.
 

### 2022-04-06 Manuscript/Main_text/Main_text_Functional_Ecology.Rmd
edit

@@
 - \linenumbers
-
 output:

### 2022-04-12 Manuscript/Main_text/Main_text_Biorxiv.Rmd
Edits for Oikos submission

@@
 always_allow_html: true
-bibliography: bibliography.bib
+bibliography: bibliography_no_doi.bib
 biblio-style: apalike

### 2022-04-12 Manuscript/Main_text/Main_text_Oikos.Rmd
Edits for Oikos submission

@@
 always_allow_html: true
-bibliography: bibliography.bib
+bibliography: bibliography_no_doi.bib
 biblio-style: apalike
-csl: oikos.csl #oikos style from zotero styles
+csl: oikos.csl #funct. ecol. style from zotero styles
 ---
@@
 Ecological processes leave distinct structural imprints on the species interactions that shape the topology of mutualistic networks.
-Detecting those relationships is not trivial since they go beyond pairwise interactions that may get blurred when considering full network descriptors.
-Recent work has shown the network meso-scale can capture this important information.
+Detecting those relationships is not trivial since they go beyond pairwise interactions, but may get blurred when considering full network descriptors.
+Recent work has shown that the network meso-scale can capture this important information.
 The meso-scale describes network subgraphs representing patterns of interactions between a small number of species (i.e., motifs) that constitute the building blocks of the whole network.
 Despite the possible implications of network motifs to better capture species interactions, they remain overlooked in natural plant-pollinator networks.
-By exploring 60 empirical plant-pollinator networks from 18 different studies with wide geographical coverage we show that some motifs are consistently under- and over-represented worldwide, suggesting that the building blocks of plant-pollinator networks are not random.
-Furthermore, we find that distinct motif positions describing species ecological roles (e.g., generalization and number of indirect interactions) are occupied by different plant and floral visitor groups on both trophic levels.
-Bees appear consistently in generalist motif positions with low number of indirect interactions while the rest of floral visitor groups are associated with more specialised motif positions with higher number of indirect interactions.
-All plant groups are principally associated with specialised motif positions but only tall plant species with separated sexes (e.g., woody dioecious or monoecious species) are associated with lower number of indirect interactions.
+By exploring 60 empirical plant-pollinator networks from 18 different studies with wide geographical coverage we show that some motifs are consistently under- or over-represented worldwide, suggesting that the building blocks of plant-pollinator networks are not random.
+Furthermore, we find that distinct motif positions describing species ecological roles (e.g., generalisation and number of indirect interactions) are occupied by different plant and floral visitor groups on both trophic levels.
+Bees appear less frequently in specialised motif positions with high number of indirect interactions, while the rest of floral visitor groups are infrequent in generalised motif positions with low number of indirect interactions.
+All plant groups tend to be over-represented on specialised motif positions, except tall plant species with separated sexes (e.g., woody dioecious or monoecious species), which are more frequent on motif positions with low number of indirect interactions.
 Interestingly, the realized combinations of different species groups within a motif can not be retrieved from their joint probability distributions, indicating that group combinations are not random either.
@@
 Because of the tremendous complexity of these ecological networks, species interactions are generally condensed in metrics that summarize this information [@guimaraes2020].
-Plant-pollinator interactions are no exception, and they are often studied with indices that aggregate the information at the species (micro-scale) or network level (macro-scale).
+Plant-pollinator interactions are no exception, and they are often studied with indices that aggregate the information at the network (macro-scale) and species level (micro-scale).
 For example, plant-pollinator network level approaches have identified common invariant structural properties across networks, including a degree distribution that decays as a power law [@jordano1987], nestedness [@bascompte2003], or modularity [@olesen2007].
-In addition, the local species position within the network can define its degree of specialization [@bluthgen2006] or its role in connecting the rest of the community [@olesen2007].
-Despite the unquestionable progress with the use of these metrics at both species and network level, condensing the information into a single metric implies the loss of relevant ecological information that obscures the understanding of species interactions [@cirtwill2018; @simmons2019].
+In addition, the local species position within the network can define its degree of specialisation [@bluthgen2006] or its role in connecting the rest of the community [@olesen2007].
+Despite the unquestionable progress with the use of these metrics at both network and species level, condensing complex information into a single metric implies the loss of relevant ecological information that obscures the understanding of species interactions [@cirtwill2018; @simmons2019].
 
 Traditionally, plant-pollinator research has focused on direct interactions but overlooked indirect interactions (i.e., the mediated effect between two species by a third species), such as facilitative or competitive interactions between plants for pollinators [@moeller2004; @sargent2008; @carvalheiro2014].
-Despite the widespread nature of indirect interactions in ecological communities [@strauss1991], plant-pollinator research often fails to finely capture those indirect interactions with the conventional analytical tools that condense the information either by species (e.g., interaction frequency) or in global topological indices (e.g., nestedness).
-Nonetheless, the emerging framework of network motifs (small sub-networks observed within a given network) in plant-pollinator research allows to consider both direct and indirect interactions [@simmons2019].
-Motifs are often referred to as the building blocks of a network that depict subsets of interactions [@milo2002].
+Despite the widespread nature of indirect interactions in ecological communities [@strauss1991], plant-pollinator research often fails to finely capture those indirect interactions with the conventional analytical tools that condense the information either by species (e.g., degree) or in global topological indices (e.g., nestedness).
+Nonetheless, the emerging framework of network motifs [small sub-networks observed within a given network which are often referred as its building blocks\; @milo2002] allows to consider both direct and indirect interactions [@simmons2019].
 The analysis of network motifs in plant-pollinator networks have revealed that the different ecological processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions [@simmons2020].
@@
 Yet, our understanding of the ecological implications of network motifs in real plant-pollinator networks remains in its infancy.
-Moreover, it is unclear how the species ecology and life-history traits determines its functional role within the network of interactions [@coux2016].
+Moreover, it is unclear how the species ecology and life-history traits determine its functional role within the network of interactions [@coux2016].
 For example, large pollinators can forage larger distances [@greenleaf2007], deposit greater pollen quantities [@foldesi2021] and handle complex zygomorphic flowers in comparison with small pollinators that are restricted to lower floral complexity [@gong2009].
-How this different pollinator behavior translates into their interaction topology is unknown.
+Despite these obvious differences in pollinator behaviour, how contrasting species' ecology translates into different interaction patterns is still unknown.
 Similarly, recent empirical findings indicate that the meso-scale is the best descriptor of plant reproductive success [@allen2021], but little is known about how plants reproductive strategies shape their position within the network of interactions.
 Although some studies have evaluated plant reproductive strategies in plant-pollinator networks [@tur2013; @lazaro2020], this is an often overlooked aspect in a community context [@devaux2014] and rarely incorporated into plant-pollinator network studies.
-Hence, exploring how the main plant reproductive strategies integrate with the emergent motif framework could help to progress knowledge on plant-pollinator interactions.
+Hence, exploring how the main plant and floral visitor life-history strategies integrate with the emergent framework of network motifs could help to progress knowledge on the ecological processes that shape plant-pollinator interactions.
 
@@
 To investigate the structure of the meso-scale in plant-pollinator networks, we gathered published plant-pollinator networks with worldwide distribution.
-Then, we classified the plant and floral visitor species from these networks into groups that summarize their main life-history strategies.
-After, we calculated the normalized motif frequencies and investigated if these frequencies are similar or not to the ones expected by chance with the help of null models.
-Then, we also calculated the normalized group frequencies of plant and floral visitor for the different motif positions and investigated their overall representation by comparing these observed frequencies with their simulated counterparts.
-Finally, we tried to recover the observed motif combinations from the expected frequencies calculated as the product of the probabilities of the different plant and floral visitor groups within each motif.
+Then, we classified the different plant and floral visitor species from these networks into groups that summarise their main life-history strategies.
+After, we calculated the normalised motif frequencies and investigated if these frequencies are similar or not to the ones expected by chance with the help of null models.
+Then, for each group of plants and floral visitors we investigated the ecological implications of their overall representation on the different motif positions, by comparing, on the one hand, the observed (normalised) frequencies of each group in the different motif positions with the frequencies of their simulated counterparts, and, on the other hand, the differences among the patterns of connections of motif positions.
+Finally, we compared if there are differences in the observed frequencies of motif combinations from the empirical networks and the expected frequencies of motif combinations calculated as the product of the probabilities of the different plant and floral visitor groups within the motif.
 
@@
 First, plant species were grouped through hierarchical clustering into the optimal number of functional groups that summarized the main plant reproductive strategies.
-For this, we used the trait dataset collated in @lanuza2021 that comprised a total of 1506 species including the 503 species considered in this study (**Table S2**).
-This dataset consisted on 8 floral, 4 reproductive and 3 vegetative traits excluding traits with high percentage of missing values (over 30$\%$; **Table S3**).
+For this, we used the trait dataset collated in @lanuza2021 that comprised a total of 1506 species including the 503 species considered in this study (Table S2).
+This dataset consisted on 8 floral, 4 reproductive and 3 vegetative traits excluding traits with high percentage of missing values (over 30$\%$; Table S3).
 We opted to calculate the plant functional groups on this larger set of species because of the higher accuracy when delimiting functional groups with that many variables and species [@dolnicar2014].
 To feed the clustering analysis, we calculated the distance between the different qualitative and scaled quantitative variables with Gower distance [@gower1971].
-For this, we used the function _gowdis_ with method _ward.D2_ from the package _FD_ version _1.0-12_ [@laliberte2014].
-Finally, we conducted hierarchical clustering with the function _hclust_ from the _R_ stats package version _4.0.5_ and calculated the optimal number of clusters with the function _kgs_ from the package _maptree_ version _1.4-7_ [@white2009].
-
-Second, floral visitors were grouped into taxonomic groups based on taxonomic rank as done similarly in other plant-pollinator studies [@fenster2004; @ollerton2009].
-We opted to divide floral visitors on the taxonomic rank level and not with functional traits because the main orders of floral visitors differed in form and behaviour and had lower superior taxonomical complexity (i.e., floral visitors had 6 orders versus plants that had 38).
+For this, we used the function _gowdis_ with method _ward.D2_ from the _FD_ package version _1.0-12_ [@laliberte2014].
+Finally, we conducted hierarchical clustering with the function _hclust_ from the _R_ stats package version _4.0.5_ and calculated the optimal number of clusters with the function _kgs_ from the _maptree_ package version _1.4-7_ [@white2009].
+
+Second, floral visitors were aggregated into taxonomic groups based on taxonomic rank as done similarly in other plant-pollinator studies [@fenster2004; @ollerton2009].
+We opted to divide floral visitors on the taxonomic rank level and not with functional traits because the main orders of floral visitors differed in form and behaviour and had lower superior taxonomic complexity (i.e., floral visitors had 6 orders versus plants that had 38).
 Thus, this allowed us to group floral visitors into groups that represented approximately the main life strategies of the possible pollinators: (i) bees (Hymenoptera-Anthophila), (ii) non-bee Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Syrphidae-Diptera), (iv) non-syrphids-Diptera, (v) Lepidoptera and (vi) Coleoptera.
@@
 Prior to analyses, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.
+This approach was preferred since quantitative motif analysis have been developed just recently and more work is needed to fully understand and interpret the information that they can convey [@simmons2020].
 All analyses were run considering singletons (species with only one interaction detected) but we conducted a second exploration without singletons (64.98$\%$ of interactions) to evaluate the effect of rare species on the observed patterns.
-Results without singletons are qualitatively consistent and are not further discussed in the main text (**Figures S2 and S3**).
-
-We calculated the frequency of all motifs up to five nodes (17 different motifs in total; see **Figure 1**) for each empirical network, by using the _bmotif_ package version _2.0.2_ [@bmotifsimmons2019].
+Results without singletons are qualitatively consistent and are not further discussed in the main text (Figs S2 and S3).
+
+We calculated the frequency of all motifs up to five nodes (17 different motifs in total; see Fig.
+1) for each empirical network, by using the _bmotif_ package version _2.0.2_ [@bmotifsimmons2019].
 We focused exclusively on motifs up to five nodes in our analyses for computational reasons and for the ease of visualization and interpretation of a reduced set of less complex network motifs.
 Throughout the entire manuscript, floral visitors occupy the top nodes of the different motifs and plants the bottom ones.
-To control for variation in network size, motif frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains).
-In addition, we excluded two-node motifs (or links) from our analyses because their normalised frequencies would always equal one.
+To control for variation in network size, motif frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., 2-species motifs, 3-species motifs, 4-species motifs and 5-species motifs).
+In addition, we excluded 2-species (or nodes) motifs from our analyses because its normalised frequencies would always equal one.
+Note that the aim is not comparing different networks, which may differ in sampling effort, but correctly describing the structure of each individual network.
 Like @simmons2020, we classified the different motifs by their average path length (mean number of links between all pairs of nodes) into four different groups: (i) complete or strong ($\overline{x} = 1.38$), (ii) fan or medium-strong ($\overline{x} = 1.48$), (iii) assymmetric complete or medium-weak ($\overline{x} = 1.60$) and (iv) core-peripheral or weak ($\overline{x} = 1.85$).
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, fig.pos="t", warning=FALSE,out.width="75%",fig.align="center", fig.cap="\\textbf{Figure 1.} (Adapted figure of Simmons et al., 2019).
-All possible motif network structures from two to five species in bipartite networks.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, fig.pos="t", warning=FALSE,out.width="75%",fig.align="center", fig.cap="\\textbf{Figure 1.} Adapted figure of Simmons et al., (2019).
+All possible motif network structures from two to five species in bipartite networks grouped by the different motif classes (2-species, 3-species, 4-species and 5-species).
 There is a total of 17 possible motifs with 46 different positions denoted within each node.
-The different motifs are aggregated by their average path length classification wich goes from densely connected motifs (strong motifs coloured in yellow) to less connected motifs (weak motifs coloured in red).", fig.width=10,fig.height=8}
+The different motifs are aggregated by their average path length classification wich goes from densely connected motifs (strong motifs coloured in yellow) to less connected motifs (weak motifs coloured in red).
+Note that two node motifs are excluded from this classification.", fig.width=10,fig.height=8}
 library(tidyverse)
@@
 Generated networks had the same number of plants and floral visitors, as well as the same connectance of their corresponding empirical networks.
-We discarded null models with more constraints (e.g., constraining for species degree) because the permutations did not generate sufficient variablity providing highly similar or identical networks to the original ones.
+We discarded null models with more constraints (e.g., constraining for species degree) because the permutations did not generate sufficient variablity and provided highly similar or identical networks to the original ones.
 After extracting the motif frequencies from the simulated networks, for each motif type and empirical network, we calculated the percentage of simulated networks whose frequencies were smaller than the ones observed, that is, we estimated the percentile of the observed motif frequencies.
 Motifs whose percentile is close to 0 or 100 are under- or over-represented in the empirical networks, respectively, and thus they cannot be predicted by connectance and the number of species alone.
-To summarize general patterns across networks, we used an intercept-only linear mixed model (LMM) per motif with the help of the package lmer version _1.1-21_ [@bates2015], where the response variable was the observed motif percentile per network.
-In these models, we used the study identifiers in **Table S1** as a random intercept.
+To summarize general patterns across networks, we used an intercept-only linear mixed model (LMM) per motif with the help of the _lme4_ package version _1.1-21_ [@bates2015], where the response variable was the observed motif percentile per network.
+Note that as we are only interested in modelling the intercept value, no predictors were specified.
+In these models, we used the study identifiers in Table S1 as a random intercept.
 By doing so, we obtained estimates of the average motif frequency, but controlling for the variation at the study level.
@@
 Hence, we assessed the average motif frequency per species group, after controlling for the variation at the study level.
-Finally, we visualized with the help of the package _ComplexHeatmap_ version _2.6.2_ [@gu2016] over- and under-representation of plant and floral visitor groups on the different motif positions.
-
-To understand if the different plant and floral visitor groups are associated with motif positions that represent different network roles we characterized the network roles of plant and floral visitor groups in terms of their specialization and number of indirect interactions.
-To that end, we calculated the specificity as a measure of specialization and we used the number of indirect interactions of the different motif positions to evaluate the association of these two node metrics and the group frequencies for the different motif positions.
-First, specificity ($s_i$) was calculated for each motif position following @poisot2015 as $s_i = L - l_i / L - 1$, where $L$ is the total number of groups and $l_i$ the number of interaction partners of the group $i$ in a given motif.
-Values of the vector s, range between 1, complete specialization (1 partner within the motif) and 0, complete generalism (all possible partners within the motif).
-Then, we explored graphically through linear models the association between the frequency of the different groups (response variable) and specificy (predictor).
-Second, we calculated the number of indirect interactions for each motif position by accounting only for the indirect effect of two species by a third species.
-That is, we explored exclusively indirect interactions within plants though shared floral visitors or within floral visitors though shared plants.
-
-\newpage
+Finally, we visualized with the help of the _ComplexHeatmap_ package version _2.6.2_ [@gu2016] over- and under-representation of plant and floral visitor groups on the different motif positions.
+
+To understand if the different plant and floral visitor groups are associated with motif positions that represent different network roles, we characterized the roles of each motif positions for plant and floral visitor groups in terms of their specialisation and number of indirect interactions.
+To that end, we calculated the specificity of each motif position following @poisot2015 as $s_i = L - l_i / L - 1$, where $L$ is the total number of groups and $l_i$ the number of interaction partners of the group $i$ in a given motif.
+Values of the vector $si$, range between 1, complete specialisation (1 partner within the motif) and 0 complete generalism (all possible partners within the motif).
+Then, because all nodes within a motif are connected, we calculated the number of indirect interactions ($n_i$) for each motif position and trophic guild (i.e., plants or floral visitors) as $n_i=z_i-1$, where $z_i$ is the total number of nodes for a trophic guild in a given motif.
+Thus, we considered exclusively indirect interactions within plants though shared floral visitors or within floral visitors though shared plants.
+Finally, we analysed in a single model how specialization and the number of indirect interactions were associated with the observed percentiles for each trophic guild and motif position (see paragraph above).
+For this, we fitted a LMM model with the help again of the _lme4_ package where we considered specialization and number of indirect interactions as response variables with the interaction by plant and floral visitor group for both response variables.
+Further, we considered as random factor motif position nested within study system.
+All model diagnostics were conducted with the help of the _Dharma_ package [@hartig2017] version _0.3.3.0_ and model outputs were visualized with the _visreg_ package [@breheny2020] version 2.7.0.
 
@@
 To calculate the observed probability ($p_i^O$) of the different groups within a motif $i$ (e.g., motif 3, 'bee' + 'bee' + 'selfing herbs'), we divided the number of times that $i$ appears in our set of empirical networks ($n_i^O$) by the sum of the number of times that each possible combination appeared: $p_i^O = n_i^O / \sum_{k=1}^{53,250} n_k^O$.
-To estimate the expected probability of a given motif combination $i$, $p_i^E$, firstly, we calculated the probability of finding a given group $x$ in the position $\alpha$ of $i$, $p_i(x,\alpha)$.
-Then, by assuming the independency of $p_i(x,\alpha)$, we computed the expected probability of the combination $i$ as the product of the probability of its pairs $(x,\alpha)$, that is, $p_i^E = \prod _{(x,\alpha )\in i} p_i(x,\alpha)$.
-To obtain $p_i(x,\alpha)$, we proceeded as follows.
-First, we calculated the number of times that the group $x$ appears in the position $\alpha$ in each empirical network $\eta$, denoted as $n_i^{\eta}(x,\alpha)$.
-Then, by controlling for the variation at the network level, we assessed the average value of the absolute frequency with which group $x$ appears in the position $\alpha$, $n_i(x,\alpha) = E\left [ n_i^{\eta}(x,\alpha) \right ]$, and estimated $p_i(x,\alpha)$ as $p_i(x,\alpha) = n_i(x,\alpha)/\sum_{k}n_i(k,\alpha)$.
-To obtain $n_i(x,\alpha)$, we fitted a LMM per motif position, where the response variable was the number of times that a given position was observed per network, the explanatory variable was the group identifier, and the random intercept was given by network identifiers nested within the study identifiers.
+To estimate the expected probability ($p_i^E$) of a given motif combination $i$, we assumed that the probability of finding a given group $x$ in the position $\alpha$ is independent of the probabilities associated with other positions and groups in that motif.
+Therefore, the expected probability ($p_i^E$) of the motif combination $i$ is given by the product of the probabilities of its constituents, i.e., $p_i^E = \prod _{(x,\alpha )\in i} p_i(x,\alpha)$, where $p_i(x,\alpha)$ is the probability of finding a given group $x$ in the position $\alpha$ of $i$.
+Then, by controlling for the variation at the network level with an LMM (see below), we calculated the average number of times that the group $x$ appears in the position $\alpha$ (denoted as $n_i(x,\alpha)$).
+To obtain the expected probability $p_i(x,\alpha)$ we divided the number of times that the group $x$ appears in the position $\alpha$ by the the total number of times that any group was observed in that position (that is, $p_i(x,\alpha) = n_i(x,\alpha)/\sum_{k}n_i(k,\alpha)$).
+The average number of times that the group $x$ appears in the position $\alpha$ ($n_i(x,\alpha)$) was calculated with a LMM for each position, where the response variable was the number of times that a group was observed at a given position in each real-world network, the explanatory variable was the group identifier, and the random intercept was given by network identifiers nested within the study identifiers.
 
@@
 
-The comparison of the plant and floral visitor group frequencies per motif position between empirical and simulated networks showed a `r over`$\%$ and `r under`$\%$ of over- (>75$^{th}$) and under-represented (<25th) groups in the different positions, respectively (**Figure 3**).
+The comparison of the plant and floral visitor group frequencies per motif position between empirical and simulated networks showed a `r over`$\%$ and `r under`$\%$ of over- (>75$^{th}$) and under-represented (<25th) groups in the different positions, respectively (Fig.
+3).
 Floral visitors showed a total of `r poll_over_75`$\%$ and `r poll_under_25`$\%$ of over- and under-represented groups in the different positions and plants `r plant_over_75`$\%$ and `r plant_under_25`$\%$ of over- and under-represented groups, respectively.
 Notably, the differences across groups were more marked for floral visitors than for plant groups (the differences between min and max percentiles per position were generally two-three times larger for floral visitors).
-From most over- to under-represented floral visitors groups on the different motif positions (indicated with the dendrogram order in **Figure 3**), we found: bees, non-syrphids Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.
+From most over- to under-represented floral visitors groups on the different motif positions (indicated with the dendrogram order in Fig.
+3), we found: bees, non-syrphids Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.
 Although plant functional groups showed less differences between them, there were also more represented groups than others, thus from most over- to under-represented groups on the different motif positions we found: self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.
 
-For both floral visitor and plant groups we found different frequencies on motif positions that implied different ecological roles.
-First, for floral visitors, we found that bees had a tendency to appear with higher frequency on motif positions that involved generalism (i.e.
-lower specificity values) while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) showed the opposite trend with higher frequency on motif positions that implied a greater level of specialization (**Figure S6 A**).
-Although plants did not have as marked trends as floral visitors, all plant groups showed a slight tendency for generalism (**Figure S6 B**).
-Second, regarding the number of indirect interactions, bees and tall plants with unisexual flowers showed greater frequency on motif positions that involve low number of indirect interactions (**Figure S7 and Figure S8**).
-The rest of floral visitor groups showed the opposite tendency and had higher frequencies on motif positions with high number of indirect interactions (**Figure S7**).
-The rest of plant groups did not show major differences on their frequencies on motifs that implied different number of indirect interactions (**Figure S8**).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', out.width="80%",fig.cap="\\textbf{Figure 3.} Heatmap indicating under- and over-representation of floral visitor and plant groups in the different motif positions.
+For both floral visitor and plant groups we found over- and under-representation on different motif positions that implied different ecological roles.
+First, for floral visitors, we found that bees were less frequent on motif positions that involved specialization (i.e., lower specificity values) while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) were infrequent in generalised motif positions with low number of indirect interactions (Fig.
+S6 A).
+Although plants did not show differences with null models on their frequencies, all plant but tall plants with small unisexual flowers showed a slight tendency to be over-represented on specialised motif positions (Fig.
+S6 B).
+Second, regarding the number of indirect interactions, bees were over-represented in motif positions with low number of indirect interactions (Fig.
+S7 A) and the rest of floral visitor groups showed no differences across positions in comparison with simulated networks.
+For plants, all groups showed a slight trend to be over-represented on motif positions with higher number of indirect interactions (Fig.
+S7 B).
+When we further explore the observed frequencies by number of indirect interactions for floral visitor and plant groups, we found that both bees and tall plants with small unisexual flowers were the only groups with high frequencies on motif positions associated with low number interactions in comparison with the other floral visitor and plant groups (Figs S8 and S9).
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', out.width="80%",fig.cap="\\textbf{Figure 3.} Heatmap indicating under- and over-representation of floral visitor and plant groups in the different motif positions (numbers on the right of each heatmap).
 The different motif positions are dividied by the average path length clasification determined by Simmons et al.
@@
 
-\newpage
-
 **Over- and under-represented group combinations of motifs**
 
-The different observed frequencies on the different motif positions showed a hierarchical order of probabilities for floral visitors (**Figure 4**).
+The different observed frequencies on the different motif positions showed a hierarchical order of probabilities for floral visitors (Fig.
+4).
 That is, the taxonomic group of 'bees' was the most abundant one on all motif positions followed by non-syrphid Diptera which was after bees, the second most frequent group on all positions.
@@
 The statistical comparison with z-scores between the observed and expected plant and floral visitor group combinations showed that we can not recover the observed combinations from its probability of occurrence.
-In fact, most combinations are under- or over- represented and follow a modified Gaussian distribution (Johnson's $S_U$) with 65$\%$ of under-represented group combinations, 20$\%$ of no statistical difference and 15$\%$ of under-represented ones (**Figure 5**).
+In fact, most combinations are under- or over- represented and follow a modified Gaussian distribution (Johnson's $S_U$) with 65$\%$ of under-represented group combinations, 20$\%$ of no statistical difference and 15$\%$ of under-represented ones (Fig.
+5).
 In addition, motifs with small node combinations (i.e., 2 and 3 nodes) only appeared as under-represented.
-Motifs with 4 and 5-node combinations appeared in the three statistical categories but 4 node motifs had a higher proportion in the under-represented category (10% in comparison with the 1$\%$ and the 3$\%$ of the no statistical difference and over-represented categories, respectively).
-Finally, 5-node motifs were in similar proportions in the no statistical difference and over-represented categories (99$\%$ and 97$\%$, respectively) but they appeared in lower proportion in the under-represented category (89$\%$).
-When, we explore the identity on the different positions of the most probable motif combinations we find as expected that the most common plant and floral visitor groups rule these positions on the most probable motif combinations (lower panel **Figure 5**).
+Motifs with 4 and 5 node combinations appeared in the three statistical categories but 4 node motifs had a higher proportion in the under-represented category (10% in comparison with the 1$\%$ and the 3$\%$ of the no statistical difference and over-represented categories, respectively).
+Finally, 5 node motifs were in similar proportions in the no statistical difference and over-represented categories (99$\%$ and 97$\%$, respectively) but they appeared in lower proportion in the under-represented category (89$\%$).
+When we explored the identity on the different positions of the most probable motif combinations we found that the most common plant and floral visitor groups were also the most probable on these motif combinations (lower panel Fig.
+5).
 
@@
 However, common analytical approaches at the node or at the full network level are unable to capture the full complexity of ecological systems [@simmons2019; @bergamo2021].
-Because network motifs can capture both direct and indirect interactions, by analysing over- and under-representation of motifs we are able to explore in great detail the structure of interactions of plant-pollinator networks.
-We have explored for the first time the overall structure and representation of network motifs in real plant-pollinator networks at a macro-ecological scale and shown that the different motifs up to five nodes are consistently over- or under-represented in comparison with simulated networks, therefore indicating the presence of ecological processes shaping their structure.
-Despite the presence of multiple ecological processes likely operating at the same time (e.g., neutral effects, morphological matching or phenological overlap), we found a tendency for over-represented structures with more densely connected motifs (i.e., complete, fan and asymmetric complete).
-As suggested in @simmons2020, a higher proportion of these densely connected motifs could reflect that neutral effects are the predominant ecological process governing the structure of these network motifs.
-Thus, as indicated for other network properties like nestedness at the macro-scale level [@krishna2008; @suweis2013], species relative abundances (i.e., neutral effects) may be also the predominant ecological process governing the meso-scale structure on plant-pollinator networks.
-
-Overall, generalist network motifs for floral visitors were consistently over-represented (e.g., fan-type motifs; **Figure 2**).
-For instance, when we compare motifs with equal structure for both trophic levels, we found that floral visitors had always over-representation in the positions that implied the highest number of direct links.
-Despite this being in good agreement with the current view of the generalist nature of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of generalist network motifs was driven by the taxonomic group of bees (**Figure S6**) while the rest of the taxonomic groups tended to be under-represented.
+Because network motifs can capture both direct and indirect interactions, by analysing over- and under-representation of motifs we were able to explore in great detail the structure of interactions of plant-pollinator networks.
+We have explored for the first time the overall structure and representation of network motifs in real plant-pollinator networks at a macro-ecological scale and shown that the different motifs up to five nodes are consistently over- or under-represented in comparison with simulated networks.
+Despite the presence of multiple ecological processes (e.g., neutral effects, morphological matching or phenological overlap) shaping motif structure, we found a tendency for over-represented structures with more densely connected motifs (i.e., complete, fan and asymmetric complete).
+As suggested in @simmons2020, a higher proportion of these densely connected motifs could reflect that neutral effects are the predominant ecological process governing the structure of network motifs.
+Thus, as indicated for other network properties like nestedness at the macro-scale level [@krishna2008; @suweis2013], or interaction probability at the species level [@bartomeus2016], species relative abundances (i.e., neutral effects) may be also the main driver governing the meso-scale structure on plant-pollinator networks.
+
+Overall, generalist network motifs for floral visitors were consistently over-represented (e.g., fan-type motifs; Fig.
+2).
+For instance, when we compare motifs with equal structure for both trophic levels, we found that floral visitors had always over-representation in the positions that implied the highest number of direct links (e.g., positions 16 and 46 from motifs 7 and 17, respectively).
+Despite this being in good agreement with the current view of the generalist nature of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of generalist network motifs was driven by the taxonomic group of bees while the rest of the taxonomic groups tended to be under-represented (Fig.
+S6 A).
 In contrast, non-bee groups were over-represented in motif positions associated with specialised roles.
 This large effect of bees on the overall patterns is no surprise, as bees were the group with the largest number of interaction records in the whole set of networks as also shown for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017].
-Interestingly, bees also were the group with lower number of indirect interactions while the rest of floral visitor groups showed clearly higher number of indirect interactions possibly indicating that these non-bee floral visitor groups may experience higher competitive interactions for floral resources [@thomson2020].
-Despite plant functional groups showed little differences between them on their motif frequencies, all groups showed a tendency to be more represented on motif positions that were associated with higher levels of specialization.
+Interestingly, bees also were the group with lower number of indirect interactions while the rest of floral visitor groups showed clearly higher number of indirect interactions indicating that these non-bee floral visitor groups may experience higher competitive interactions for floral resources [@thomson2020].
+Despite plant functional groups showed little differences between them on their motif frequencies, all groups showed a tendency to be over-represented on motif positions that were associated with higher levels of specialisation.
 This tendency towards specialist roles may be the result of co-evolutionary processes (e.g., trait-matching) between plants and pollinators to optimise pollen transfer [@moreira2019].
-Remarkably, just tall plants with small unisexual flowers showed higher frequencies on motifs that were associated with low number of indirect interactions with likely direct implications on pollen transfer for this group that needs to guarantee cross-pollination.
-
-The probabilities of appearance of each functional group on the different motif positions were insufficient to predict most of the observed network position combinations (**Figure 5**).
+Remarkably, only tall plants with small unisexual flowers showed higher frequencies on motifs that were associated with low number of indirect interactions with likely direct implications on pollen transfer for this group that needs to guarantee cross-pollination.
+
+The probabilities of appearance of each functional group on the different motif positions were insufficient to predict most of the observed network position combinations (Fig.
+5).
 This implies that not just the representation of network motifs types but also the identity of the elements of their structure is non-random.
@@
 
-In conclusion, by following the framework of @simmons2020 we have been able to explore competitive and facilitative interactions in plant-pollinator networks worldwide and found that indirect interactions are non-random and are more strongly related to neutral processes than any other ecological process.
-Further, we found that plant and floral visitor groups are associated with different motif positions that involve distinct ecological roles (e.g., generalization versus specialization) and that the different motif combinations are strongly constrained.
-Although in this study we do not predict indirect interactions, our work is a first step to elucidate novel interactions beyond pairwise interactions.
+In conclusion, by following the framework of @simmons2020 we have been able to explore competitive and facilitative interactions in plant-pollinator networks worldwide and found that indirect interactions are non-random and are more strongly related to neutral processes than to any other ecological process.
+Further, we found that plant and floral visitor groups are associated with different motif positions that involve distinct ecological roles (e.g., generalisation versus specialisation) and that the different motif combinations are strongly constrained.
+Although we are still far to predict how species interact, our work is a first step to elucidate beyond pairwise interactions.
 
@@
 
-All data and code would be deposited at Driad Digital repository upon acceptance.
+All data and code is deposited at GitHub: https://github.com/JoseBSL/FunctionalMotifs.
 

### 2022-04-13 Manuscript/Main_text/Main_text_Oikos.Rmd
Edits for Oikos

@@
 
-*Acknowledgements* - This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2).
-JBL also thanks the University of New England for the funding provided to carry out this work.
-Finally, we would like to thank David García-Callejas for his useful comments on the manuscript before submission.
-
-# Author contributions
-
-IB, AA-P and JBL designed the idea. JBL collected the data. AA-P lead the analysis with contributions of JBL and guidance of IB. JBL wrote the manuscript with contributions of IB and AA-P.
-
-# Data availability statement
-
-All data and code is deposited at GitHub: https://github.com/JoseBSL/FunctionalMotifs.
-
 \newpage

### 2022-04-24 Manuscript/Main_text/Main_text_Biorxiv.Rmd
Polish abstract and add a Ref

@@
 
-Ecological processes leave distinct structural imprints on the species interactions that shape the topology of mutualistic networks.
-Detecting those relationships is not trivial since they go beyond pairwise interactions, but may get blurred when considering full network descriptors.
+Ecological processes leave distinct structural imprints on the species interactions that shape the topology of animal-plant mutualistic networks.
+Detecting how direct and indirect interactions between animals and plants are organized is not trivial since they go beyond pairwise interactions, but may get blurred when considering full network descriptors.
 Recent work has shown that the network meso-scale can capture this important information.
-The meso-scale describes network subgraphs representing patterns of interactions between a small number of species (i.e., motifs) that constitute the building blocks of the whole network.
+The meso-scale describes network subgraphs representing patterns of direct and indirect interactions between a small number of species (i.e., motifs) that constitute the building blocks of the whole network.
 Despite the possible implications of network motifs to better capture species interactions, they remain overlooked in natural plant-pollinator networks.
 By exploring 60 empirical plant-pollinator networks from 18 different studies with wide geographical coverage we show that some motifs are consistently under- or over-represented worldwide, suggesting that the building blocks of plant-pollinator networks are not random.
-Furthermore, we find that distinct motif positions describing species ecological roles (e.g., generalisation and number of indirect interactions) are occupied by different plant and floral visitor groups on both trophic levels.
-Bees appear less frequently in specialised motif positions with high number of indirect interactions, while the rest of floral visitor groups are infrequent in generalised motif positions with low number of indirect interactions.
-All plant groups tend to be over-represented on specialised motif positions, except tall plant species with separated sexes (e.g., woody dioecious or monoecious species), which are more frequent on motif positions with low number of indirect interactions.
+We found a higher proportion of densely connected motifs, which could reflect that neutral effects are the predominant ecological process governing the structure of network motifs.
+Furthermore, we find that distinct motif positions describing species ecological roles (e.g., generalisation and number of indirect interactions) are occupied by different floral visitor and plant groups on both trophic levels.
+For example, bees tend to appear in motif positions with a higher number of indirect interactions than the rest of floral visitor groups.
 Interestingly, the realized combinations of different species groups within a motif can not be retrieved from their joint probability distributions, indicating that group combinations are not random either.
-Our result highlights the non-random structure of the meso-scale on plant-pollinators networks and the association of different plant and floral visitor groups with certain motifs that involve different ecological roles at a macro-ecological scale.
-
-Keywords: plant-pollinator networks, plant-pollinator interactions, network motifs, indirect interactions, plant traits, floral visitors
+Our result highlights the non-random structure of the key building blocks shaping plant-pollinators networks and the association of different floral visitor and plant groups with certain motifs.
+
+Keywords: pollinators, plant-pollinator networks, plant-pollinator interactions, network motifs, indirect interactions, floral visitors
 
@@
 
-Traditionally, plant-pollinator research has focused on direct interactions but overlooked indirect interactions (i.e., the mediated effect between two species by a third species), such as facilitative or competitive interactions between plants for pollinators [@moeller2004; @sargent2008; @carvalheiro2014].
+Traditionally, plant-pollinator research has focused on direct interactions but overlooked indirect interactions (i.e., the mediated effect between two species by a third species @holt[JOSE AÑADE ESTA CITA: ](https://www.annualreviews.org/doi/pdf/10.1146/annurev.es.25.110194.002431?casa_token=KpZT3NhbdsMAAAAA:ZeujS0ToLXQpBk8rxma0rO85jkZkqn0dSc0mIknTz9yNmLpFKr1-pIRWNKF6MD0VcO2Wk6-4FmfBLQ)), such as facilitative or competitive interactions between plants for pollinators [@moeller2004; @sargent2008; @carvalheiro2014].
 Despite the widespread nature of indirect interactions in ecological communities [@strauss1991], plant-pollinator research often fails to finely capture those indirect interactions with the conventional analytical tools that condense the information either by species (e.g., degree) or in global topological indices (e.g., nestedness).
@@
 However, common analytical approaches at the node or at the full network level are unable to capture the full complexity of ecological systems [@simmons2019; @bergamo2021].
-Because network motifs can capture both direct and indirect interactions, by analysing over- and under-representation of motifs we were able to explore in great detail the structure of interactions of plant-pollinator networks.
-We have explored for the first time the overall structure and representation of network motifs in real plant-pollinator networks at a macro-ecological scale and shown that the different motifs up to five nodes are consistently over- or under-represented in comparison with simulated networks.
+Because network motifs can capture both direct and indirect interactions, by analysing over- and under-representation of motifs we were able to explore in great detail the structure of interactions between animal pollintors and the plants they visit.
+We have explored for the first time the overall structure and representation of network motifs in real plant-pollinator networks and shown that the different motifs up to five nodes are consistently over- or under-represented in comparison with simulated networks.
 Despite the presence of multiple ecological processes (e.g., neutral effects, morphological matching or phenological overlap) shaping motif structure, we found a tendency for over-represented structures with more densely connected motifs (i.e., complete, fan and asymmetric complete).

### 2022-04-26 Manuscript/Main_text/Main_text_Journal_of_Animal_Ecol.Rmd
adding Nacho's edits

--- 2022-04-01 Manuscript/Main_text/Main_text_Functional_Ecology.Rmd
@@
 ---
-title: "The non-random assembly of functional motifs in  \nplant-pollinator networks"
+title: "The non-random assembly of indirect interactions in  \nplant-pollinator networks"
 editor_options:
@@
 always_allow_html: true
-bibliography: bibliography.bib
+bibliography: bibliography_no_doi.bib
 biblio-style: apalike
-csl: functional-ecology.csl #funct. ecol. style from zotero styles
+csl: JournalOfAnimalEcology.csl #converted from funct ecol style from zotero styles
 ---
+
+__Jose B. Lanuza^1,2^__  | __Alfonso Allen-Perkins^2,3^__ | __Ignasi Bartomeus^2^__
+
+1 School of Environmental and Rural Science, University of New England, Armidale, New South Wales 2350, Australia.
+
+2 Estación Biológica de Doñana (EBD-CSIC), E-41092 Seville, Spain.
+
+3 Departamento de Ingeniería Eléctrica, Electrónica, Automática y Física Aplicada, ETSIDI, Universidad Politécnica de Madrid, 28040 Madrid, Spain.
 
@@
 
-Ecological processes leave distinct structural imprints on the species interactions that shape the topology of mutualistic networks.
-Detecting those relationships is not trivial since they go beyond pairwise interactions, but may get blurred when considering full network descriptors.
+Ecological processes leave distinct structural imprints on the species interactions that shape the topology of animal-plant mutualistic networks.
+Detecting how direct and indirect interactions between animals and plants are organized is not trivial since they go beyond pairwise interactions, but may get blurred when considering full network descriptors.
 Recent work has shown that the network meso-scale can capture this important information.
-The meso-scale describes network subgraphs representing patterns of interactions between a small number of species (i.e., motifs) that constitute the building blocks of the whole network.
+The meso-scale describes network subgraphs representing patterns of direct and indirect interactions between a small number of species (i.e., motifs) that constitute the building blocks of the whole network.
 Despite the possible implications of network motifs to better capture species interactions, they remain overlooked in natural plant-pollinator networks.
 By exploring 60 empirical plant-pollinator networks from 18 different studies with wide geographical coverage we show that some motifs are consistently under- or over-represented worldwide, suggesting that the building blocks of plant-pollinator networks are not random.
-Furthermore, we find that distinct motif positions describing species ecological roles (e.g., generalisation and number of indirect interactions) are occupied by different plant and floral visitor groups on both trophic levels.
-Bees appear less frequently in specialised motif positions with high number of indirect interactions, while the rest of floral visitor groups are infrequent in generalised motif positions with low number of indirect interactions.
-All plant groups tend to be over-represented on specialised motif positions, except tall plant species with separated sexes (e.g., woody dioecious or monoecious species), which are more frequent on motif positions with low number of indirect interactions.
+We found a higher proportion of densely connected motifs, which could reflect that neutral effects are the predominant ecological process governing the structure of network motifs.
+Furthermore, we find that distinct motif positions describing species ecological roles (e.g., generalisation and number of indirect interactions) are occupied by different floral visitor and plant groups on both trophic levels.
+For example, bees tend to appear in motif positions with a lower number of indirect interactions than the rest of floral visitor groups.
 Interestingly, the realized combinations of different species groups within a motif can not be retrieved from their joint probability distributions, indicating that group combinations are not random either.
-Our result highlights the non-random structure of the meso-scale on plant-pollinators networks and the association of different plant and floral visitor groups with certain motifs that involve different ecological roles at a macro-ecological scale.
-
-Keywords: plant-pollinator networks, plant-pollinator interactions, network motifs, indirect interactions, plant traits, floral visitors
+Our result highlight the non-random structure of the key building blocks shaping plant-pollinators networks and the association of different floral visitor and plant groups with certain motifs.
+
+Keywords: pollinators, plant-pollinator networks, plant-pollinator interactions, network motifs, indirect interactions, floral visitors
 
@@
 
-Traditionally, plant-pollinator research has focused on direct interactions but overlooked indirect interactions (i.e., the mediated effect between two species by a third species), such as facilitative or competitive interactions between plants for pollinators [@moeller2004; @sargent2008; @carvalheiro2014].
+Traditionally, plant-pollinator research has focused on direct interactions but overlooked indirect interactions [i.e., the mediated effect between two species by a third species\; @holt1994], such as facilitative or competitive interactions between plants for pollinators [@moeller2004; @sargent2008; @carvalheiro2014].
 Despite the widespread nature of indirect interactions in ecological communities [@strauss1991], plant-pollinator research often fails to finely capture those indirect interactions with the conventional analytical tools that condense the information either by species (e.g., degree) or in global topological indices (e.g., nestedness).
@@
 However, common analytical approaches at the node or at the full network level are unable to capture the full complexity of ecological systems [@simmons2019; @bergamo2021].
-Because network motifs can capture both direct and indirect interactions, by analysing over- and under-representation of motifs we were able to explore in great detail the structure of interactions of plant-pollinator networks.
-We have explored for the first time the overall structure and representation of network motifs in real plant-pollinator networks at a macro-ecological scale and shown that the different motifs up to five nodes are consistently over- or under-represented in comparison with simulated networks.
+Because network motifs can capture both direct and indirect interactions, by analysing over- and under-representation of motifs we were able to explore in great detail the structure of interactions between animal pollinators and the plants they visit.
+We have explored for the first time the overall structure and representation of network motifs in real plant-pollinator networks and shown that the different motifs up to five nodes are consistently over- or under-represented in comparison with simulated networks.
 Despite the presence of multiple ecological processes (e.g., neutral effects, morphological matching or phenological overlap) shaping motif structure, we found a tendency for over-represented structures with more densely connected motifs (i.e., complete, fan and asymmetric complete).
@@
 
-# Data availability statement
-
-All data and code is deposited at GitHub: https://github.com/JoseBSL/FunctionalMotifs.
+# Data Availability Statement
+
+All data and code are publicly available at Github (https://github.com/JoseBSL/FunctionalMotifs) and Zenodo (https://doi.org/10.5281/zenodo.6489213).
 

### 2022-04-26 Manuscript/Main_text/Main_text_Journal_of_Animal_Ecol.Rmd
edits on text

@@
 Interestingly, the realized combinations of different species groups within a motif can not be retrieved from their joint probability distributions, indicating that group combinations are not random either.
-Our result highlight the non-random structure of the key building blocks shaping plant-pollinators networks and the association of different floral visitor and plant groups with certain motifs.
+Our results highlight the non-random structure of the key building blocks shaping plant-pollinators networks and the association of certain motifs with different groups of floral visitors and plants.
 

### 2022-07-20 Manuscript/Main_text/Main_text_Journal_of_Animal_Ecol.Rmd
edits

@@
 For this, we used the trait dataset collated in @lanuza2021 that comprised a total of 1506 species including the 503 species considered in this study (Table S2).
-This dataset consisted on 8 floral, 4 reproductive and 3 vegetative traits excluding traits with high percentage of missing values (over 30$\%$; Table S3).
+This dataset consisted of 8 floral, 4 reproductive and 3 vegetative traits excluding traits with high percentage of missing values (over 30$\%$; Table S3).
 We opted to calculate the plant functional groups on this larger set of species because of the higher accuracy when delimiting functional groups with that many variables and species [@dolnicar2014].
@@
 Generated networks had the same number of plants and floral visitors, as well as the same connectance of their corresponding empirical networks.
-We discarded null models with more constraints (e.g., constraining for species degree) because the permutations did not generate sufficient variablity and provided highly similar or identical networks to the original ones.
+We discarded null models with more constraints (e.g., constraining for species degree) because the permutations did not generate sufficient variability and provided highly similar or identical networks to the original ones.
 After extracting the motif frequencies from the simulated networks, for each motif type and empirical network, we calculated the percentage of simulated networks whose frequencies were smaller than the ones observed, that is, we estimated the percentile of the observed motif frequencies.
@@
 To understand if the different plant and floral visitor groups are associated with motif positions that represent different network roles, we characterized the roles of each motif positions for plant and floral visitor groups in terms of their specialisation and number of indirect interactions.
-To that end, we calculated the specificity of each motif position following @poisot2015 as $s_i = L - l_i / L - 1$, where $L$ is the total number of groups and $l_i$ the number of interaction partners of the group $i$ in a given motif.
+To that end, we calculated the specificity of each motif position following @poisot2015 as $s_i = (L - l_i) / (L - 1)$, where $L$ is the total number of groups and $l_i$ the number of interaction partners of the group $i$ in a given motif.
 Values of the vector $si$, range between 1, complete specialisation (1 partner within the motif) and 0 complete generalism (all possible partners within the motif).
@@
 The hierarchical cluster analysis divided the dataset into five different groups with different and overlapping characteristics (Figs S4 and S5).
-The first group referred to as 'selfing herbs' consisted on herbs with hermaphroditic flowers with high levels of autonomous selfing.
+The first group referred to as 'selfing herbs' consisted of herbs with hermaphroditic flowers with high levels of autonomous selfing.
 The second group named 'small outcrossing perennials' had small perennial species with a mix of life forms (i.e., trees shrubs and herbs) with outcrossing hermaphroditic flowers.
@@
 The fourth group named 'tall plants with small unisexual flowers' had the tallest species, highest proportion of shrub and tree life forms, dioecious and monoecious breeding systems, small flowers and the highest numbers of flowers and inflorescences per plant.
-Finally, the fifth group named 'short-lived outcrossers with long zygomorphic flowers' consisted on small perennial and short-lived herbs with long self-compatible zygomorphic flowers that were unable to self-pollinate.
+Finally, the fifth group named 'short-lived outcrossers with long zygomorphic flowers' consisted of small perennial and short-lived herbs with long self-compatible zygomorphic flowers that were unable to self-pollinate.
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 5.** Z-score comparison (95% confidence level) of the observed and expected frequencies of motif combinations with four specific graphical examples of the most probable motifs of being observed for each category delimited by the z-score critical values: under-represented (red), no statistical difference (green) and over-represented (blue)."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 5.** Distribution of z-scores values after the statistical comparison of the observed probabilities of finding a subgraph combination in real networks and the expected probabilities (obtained by computer simulations).
+The resulting z-scores frequencies of this statiscal comparison are coloured based on a 95% confidence level: under-represented ($z_i^O < -1.96$, red), no statistical difference ($-1.96 \\geq z_i^O \\leq  1.96$, green) and over-represented ($z_i^O > 1.96$, blue).
+For instance, for a z-score value of 0 there were approximately 800 subgraph combinations that showed no statistical difference in the comparison between real and simulated networks.
+In addition, four specific graphical examples of the most probable subgraphs being observed on each category are also provided and the different plant and floral visitor groups are represented with distinct colour codes as indicated in the legend."}
 

### 2022-07-20 Manuscript/Main_text/Main_text_Journal_of_Animal_Ecol.Rmd
edits

@@
 Plant-pollinator interactions are no exception, and they are often studied with indices that aggregate the information at the network (macro-scale) and species level (micro-scale).
-For example, plant-pollinator network level approaches have identified common invariant structural properties across networks, including a degree distribution that decays as a power law [@jordano1987], nestedness [@bascompte2003], or modularity [@olesen2007].
+For example, plant-pollinator network level approaches have identified common invariant structural properties across mutualistic networks, including a degree distribution that decays as a power law [@jordano1987], nestedness [@bascompte2003], or modularity [@olesen2007].
 In addition, the local species position within the network can define its degree of specialisation [@bluthgen2006] or its role in connecting the rest of the community [@olesen2007].

### 2022-07-21 Manuscript/Main_text/Main_text_Journal_of_Animal_Ecol.Rmd
edits

@@
 Nonetheless, the emerging framework of network motifs [small sub-networks observed within a given network which are often referred as its building blocks\; @milo2002] allows to consider both direct and indirect interactions [@simmons2019].
-The analysis of network motifs in plant-pollinator networks have revealed that the different ecological processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions [@simmons2020].
+The analysis of network motifs in plant-pollinator networks have revealed that the different drivers that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions [@simmons2020].
 Yet, the global patterns of indirect interactions in real plant-pollinator networks are still unknown (e.g., over- and under- represented motifs).
@@
 For this, we used the trait dataset collated in @lanuza2021 that comprised a total of 1506 species including the 503 species considered in this study (Table S2).
-This dataset consisted of 8 floral, 4 reproductive and 3 vegetative traits excluding traits with high percentage of missing values (over 30$\%$; Table S3).
+This dataset consisted of 8 floral, 4 reproductive biology and 3 plant morphology traits excluding traits with high percentage of missing values (over 30$\%$; Table S3).
 We opted to calculate the plant functional groups on this larger set of species because of the higher accuracy when delimiting functional groups with that many variables and species [@dolnicar2014].

### 2022-07-21 Scripts/Z-score_percentile_histogram_plot.R

@@ -4,7 +4,7 @@ library(dplyr)
 library(ggplot2)
 library(tidyverse)
 #Read data
-data <- read.csv("../../Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
+data <- read.csv("Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
 
 #Check NA's per column
 #data %>%
@@ -13,6 +13,9 @@ data <- read.csv("../../Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
 #Find critical value of Z-score
 p <- 0.05 #cutoff probability 95% confidence
 critical_value <- qnorm(p/2) #double tail probability divide by 2
+
+
+
 
 data_1 <- data %>%
   mutate(infra_over_represented = case_when(
@@ -40,7 +43,7 @@ data_2 <- filter(data_1, abs(z_score)<2000)
 # Podrian estar underrepresented, pero como con la Chi, si el expected es super bajo, 
 # diferenciar si esta under-represented sera dificil de detectar .
 
-ggplot(data_2 %>% filter(round_motif_observed_probability>0), aes(x=z_score, color=infra_over_represented, fill=infra_over_represented)) + 
+ggplot(data_1, aes(x=z_score, color=infra_over_represented, fill=infra_over_represented)) + 
   geom_histogram(bins = 100, alpha = 0.5, position = "identity",lwd = 0.25)+
   geom_vline(xintercept = -abs(critical_value))+
   geom_vline(xintercept = abs(critical_value))+

### 2022-07-25 Manuscript/Main_text/Main_text_Journal_of_Animal_Ecol.Rmd
Correction of the use of the term motif

@@
 Detecting how direct and indirect interactions between animals and plants are organized is not trivial since they go beyond pairwise interactions, but may get blurred when considering full network descriptors.
-Recent work has shown that the network meso-scale can capture this important information.
-The meso-scale describes network subgraphs representing patterns of direct and indirect interactions between a small number of species (i.e., motifs) that constitute the building blocks of the whole network.
-Despite the possible implications of network motifs to better capture species interactions, they remain overlooked in natural plant-pollinator networks.
-By exploring 60 empirical plant-pollinator networks from 18 different studies with wide geographical coverage we show that some motifs are consistently under- or over-represented worldwide, suggesting that the building blocks of plant-pollinator networks are not random.
-We found a higher proportion of densely connected motifs, which could reflect that neutral effects are the predominant ecological process governing the structure of network motifs.
-Furthermore, we find that distinct motif positions describing species ecological roles (e.g., generalisation and number of indirect interactions) are occupied by different floral visitor and plant groups on both trophic levels.
-For example, bees tend to appear in motif positions with a lower number of indirect interactions than the rest of floral visitor groups.
-Interestingly, the realized combinations of different species groups within a motif can not be retrieved from their joint probability distributions, indicating that group combinations are not random either.
-Our results highlight the non-random structure of the key building blocks shaping plant-pollinators networks and the association of certain motifs with different groups of floral visitors and plants.
+Recent work has shown that the meso-scale, the intermediate level of network complexity between the species and the full network, can capture this important information.
+The meso-scale describes network subgraphs representing patterns of direct and indirect interactions between a small number of species and when these network subgraphs differ statistically from a benchmark, they are often referred to as "network motifs".
+Despite motifs can capture relevant ecological information of species interactions, they remain overlooked in natural plant-pollinator networks.
+By exploring 60 empirical plant-pollinator networks from 18 different studies with wide geographical coverage we show that some network subgraphs are consistently under- or over-represented, suggesting the presence of worldwide network motifs in plant-pollinator networks.
+In addition, we found a higher proportion of densely connected network subgraphs, which could reflect that neutral effects are the predominant ecological process governing the structure of the meso-scale.
+We found that distinct subgraph positions describing species ecological roles (e.g., generalisation and number of indirect interactions) are occupied by different floral visitor and plant groups on both trophic levels.
+For example, bees tend to appear in subgraph positions with a lower number of indirect interactions than the rest of floral visitor groups.
+Interestingly, the realized combinations of different species groups within a network subgraph can not be retrieved from their joint probability distributions, indicating that plant and floral visitor group combinations on network subgraphs are not random.
+Our results highlight the non-random structure of the key building blocks shaping plant-pollinators networks and the association of certain network subgraphs and their positions with specific groups of floral visitors and plants.
 
@@
 Despite the widespread nature of indirect interactions in ecological communities [@strauss1991], plant-pollinator research often fails to finely capture those indirect interactions with the conventional analytical tools that condense the information either by species (e.g., degree) or in global topological indices (e.g., nestedness).
-Nonetheless, the emerging framework of network motifs [small sub-networks observed within a given network which are often referred as its building blocks\; @milo2002] allows to consider both direct and indirect interactions [@simmons2019].
+Nonetheless, the analysis of network subgraphs at the meso-scale, the intermediate level of complexity between the full network and the species level, allows to consider both direct and indirect interactions [@simmons2019].
+The network subgraphs that significantly depart from an expected benchmark are often defined as 'network motifs' [@milo2002].
 The analysis of network motifs in plant-pollinator networks have revealed that the different drivers that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions [@simmons2020].
-Yet, the global patterns of indirect interactions in real plant-pollinator networks are still unknown (e.g., over- and under- represented motifs).
+Yet, the global patterns of indirect interactions in real plant-pollinator networks are still unknown (e.g., over- and under- represented network subgraphs).
 
@@
 Floral visitor groups were divided by the main taxonomic groups that differed in life form and behaviour.
-Once we split the different plant-pollinator networks into their motif elements, we explored: (i) if there is a common invariant structural property in the overall motif networks (i.e., over- and under-represented motifs); (ii) which plant and floral visitor groups are over- and under-represented in different motif positions associated with specific ecological roles; and, (iii) if there are over- and under-represented plant and floral visitor group combinations within a motif.
+Once we split the different plant-pollinator networks into their subgraphs elements, we explored: (i) if there is a common invariant structural property in the overall subgraphs from these networks (i.e., over- and under-represented subgraphs); (ii) which plant and floral visitor groups are over- and under-represented in different subgraphs positions associated with specific ecological roles; and, (iii) if there are over- and under-represented plant and floral visitor group combinations within a subgraph.
 
@@
 Then, we classified the different plant and floral visitor species from these networks into groups that summarise their main life-history strategies.
-After, we calculated the normalised motif frequencies and investigated if these frequencies are similar or not to the ones expected by chance with the help of null models.
-Then, for each group of plants and floral visitors we investigated the ecological implications of their overall representation on the different motif positions, by comparing, on the one hand, the observed (normalised) frequencies of each group in the different motif positions with the frequencies of their simulated counterparts, and, on the other hand, the differences among the patterns of connections of motif positions.
-Finally, we compared if there are differences in the observed frequencies of motif combinations from the empirical networks and the expected frequencies of motif combinations calculated as the product of the probabilities of the different plant and floral visitor groups within the motif.
+After, we calculated the normalised subgraph frequencies and investigated if these frequencies are similar or not to the ones expected by chance with the help of null models.
+Then, for each group of plants and floral visitors we investigated the ecological implications of their overall representation on the different subgraph positions, by comparing, on the one hand, the observed (normalised) frequencies of each group in the different subgraph positions with the frequencies of their simulated counterparts, and, on the other hand, the differences among the patterns of connections of subgraph positions.
+Finally, we compared if there are differences in the observed frequencies of subgraph combinations from empirical networks and the expected frequencies calculated as the product of the probabilities of the different plant and floral visitor groups within the network subgraph.
 
@@
 
-**Overall motif patterns**
-
-Following previous work [@simmons2019; @simmons2020], we broke down the plant-pollinator networks into their constituent motifs that can capture both direct and indirect interactions.
+**Overall network subgraphs patterns**
+
+Following previous work [@simmons2019; @simmons2020], we broke down the plant-pollinator networks into their constituent network subgraphs that can capture both direct and indirect interactions.
 Prior to analyses, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.
-This approach was preferred since quantitative motif analysis have been developed just recently and more work is needed to fully understand and interpret the information that they can convey [@simmons2020].
+This approach was preferred since quantitative subgraph analysis have been developed just recently and more work is needed to fully understand and interpret the information that they can convey [@simmons2020].
 All analyses were run considering singletons (species with only one interaction detected) but we conducted a second exploration without singletons (64.98$\%$ of interactions) to evaluate the effect of rare species on the observed patterns.
@@
 
-We calculated the frequency of all motifs up to five nodes (17 different motifs in total; see Fig.
+We calculated the frequency of all subgraphs up to five nodes (17 different subgraphs in total; see Fig.
 1) for each empirical network, by using the _bmotif_ package version _2.0.2_ [@bmotifsimmons2019].
-We focused exclusively on motifs up to five nodes in our analyses for computational reasons and for the ease of visualization and interpretation of a reduced set of less complex network motifs.
-Throughout the entire manuscript, floral visitors occupy the top nodes of the different motifs and plants the bottom ones.
-To control for variation in network size, motif frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., 2-species motifs, 3-species motifs, 4-species motifs and 5-species motifs).
-In addition, we excluded 2-species (or nodes) motifs from our analyses because its normalised frequencies would always equal one.
+We focused exclusively on subgraphs up to five nodes in our analyses for computational reasons and for the ease of visualization and interpretation of a reduced set of less complex network structures.
+Throughout the entire manuscript, floral visitors occupy the top nodes of the different network subgraphs and plants the bottom ones.
+To control for variation in network size, subgraph frequencies were normalised as a proportion of the total number of subgraphs within each subgraph class (i.e., 2-species, 3-species, 4-species and 5-species network subgraphs).
+In addition, we excluded 2-species (or nodes) subgraphs from our analyses because its normalised frequencies would always equal one.
 Note that the aim is not comparing different networks, which may differ in sampling effort, but correctly describing the structure of each individual network.
-Like @simmons2020, we classified the different motifs by their average path length (mean number of links between all pairs of nodes) into four different groups: (i) complete or strong ($\overline{x} = 1.38$), (ii) fan or medium-strong ($\overline{x} = 1.48$), (iii) assymmetric complete or medium-weak ($\overline{x} = 1.60$) and (iv) core-peripheral or weak ($\overline{x} = 1.85$).
-In general terms, plant and floral visitor groups on more densely connected motifs (e.g., complete or fan) will experience lower number of indirect interactions in contrast to groups on less densely connected ones (e.g., medium-weak or weak).
+Like @simmons2020, we classified the different subgraphs by their average path length (mean number of links between all pairs of nodes) into four different groups: (i) complete or strong ($\overline{x} = 1.38$), (ii) fan or medium-strong ($\overline{x} = 1.48$), (iii) assymmetric complete or medium-weak ($\overline{x} = 1.60$) and (iv) core-peripheral or weak ($\overline{x} = 1.85$).
+In general terms, plant and floral visitor groups on more densely connected network subgraphs (e.g., complete or fan) will experience lower number of indirect interactions in contrast to groups on less densely connected ones (e.g., medium-weak or weak).
 
 ```{r, echo=FALSE, message=FALSE, cache=FALSE, fig.pos="t", warning=FALSE,out.width="75%",fig.align="center", fig.cap="\\textbf{Figure 1.} Adapted figure of Simmons et al., (2019).
-All possible motif network structures from two to five species in bipartite networks grouped by the different motif classes (2-species, 3-species, 4-species and 5-species).
-There is a total of 17 possible motifs with 46 different positions denoted within each node.
-The different motifs are aggregated by their average path length classification wich goes from densely connected motifs (strong motifs coloured in yellow) to less connected motifs (weak motifs coloured in red).
-Note that two node motifs are excluded from this classification.", fig.width=10,fig.height=8}
+All possible network subgraphs from two to five species in bipartite networks grouped by the different subgraph classes (2-species, 3-species, 4-species and 5-species).
+There is a total of 17 possible subgraphs with 46 different positions denoted within each node.
+The different subgraphs are aggregated by their average path length classification wich goes from densely connected (strong subgraphs coloured in yellow) to less connected network structures (weak subgraphs coloured in red).
+Note that two node subgraphs are excluded from this classification.", fig.width=10,fig.height=8}
 library(tidyverse)
@@
 We discarded null models with more constraints (e.g., constraining for species degree) because the permutations did not generate sufficient variability and provided highly similar or identical networks to the original ones.
-After extracting the motif frequencies from the simulated networks, for each motif type and empirical network, we calculated the percentage of simulated networks whose frequencies were smaller than the ones observed, that is, we estimated the percentile of the observed motif frequencies.
-Motifs whose percentile is close to 0 or 100 are under- or over-represented in the empirical networks, respectively, and thus they cannot be predicted by connectance and the number of species alone.
-To summarize general patterns across networks, we used an intercept-only linear mixed model (LMM) per motif with the help of the _lme4_ package version _1.1-21_ [@bates2015], where the response variable was the observed motif percentile per network.
+After extracting the subgraph frequencies from the simulated networks, for each subgraph type and empirical network, we calculated the percentage of simulated networks whose frequencies were smaller than the ones observed, that is, we estimated the percentile of the observed subgraph frequencies.
+Subgraphs whose percentile is close to 0 or 100 are under- or over-represented in empirical networks, respectively, and indicate the presence of network motifs as they differ statistically from the network structures generated with simulated networks.
+To summarize general patterns across networks, we used an intercept-only linear mixed model (LMM) per subgraph with the help of the _lme4_ package version _1.1-21_ [@bates2015], where the response variable was the observed subgraph percentile per network.
 Note that as we are only interested in modelling the intercept value, no predictors were specified.
 In these models, we used the study identifiers in Table S1 as a random intercept.
-By doing so, we obtained estimates of the average motif frequency, but controlling for the variation at the study level.
-
-**Over- and under-represented groups on motif positions**
-
-We calculated which plant and floral visitor groups were over- or under-represented in the different motif positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
-To estimate the position frequencies of each plant and floral visitor group in a given network, we added the frequencies of those species that belong to the same group, and then, we normalised the resulting frequencies by dividing them by the total number of times that a corresponding group appears in any position within the same motif size class (i.e., 2, 3, 4 or 5 species motifs).
-Then, we calculated the percentile of the observed position frequencies for each group and network, just like we did with motif frequencies.
-To outline the general patterns of position frequencies across networks and groups, we fit a LMM per motif position, where the response variable was the observed position percentile per network.
+By doing so, we obtained estimates of the average subgraph frequency, but controlling for the variation at the study level.
+
+**Over- and under-represented groups on subgraph positions**
+
+We calculated which plant and floral visitor groups were over- or under-represented in the different subgraph positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
+To estimate the position frequencies of each plant and floral visitor group in a given network, we added the frequencies of those species that belong to the same group, and then, we normalised the resulting frequencies by dividing them by the total number of times that a corresponding group appears in any position within the same subgraph size class (i.e., 2, 3, 4 or 5 species motifs).
+Then, we calculated the percentile of the observed position frequencies for each group and network, just like we did with subgraph frequencies.
+To outline the general patterns of position frequencies across networks and groups, we fit a LMM per subgraph position, where the response variable was the observed position percentile per network.
 We used the group identifier as an explanatory variable and the study identifiers as a random intercept.
-Hence, we assessed the average motif frequency per species group, after controlling for the variation at the study level.
-Finally, we visualized with the help of the _ComplexHeatmap_ package version _2.6.2_ [@gu2016] over- and under-representation of plant and floral visitor groups on the different motif positions.
-
-To understand if the different plant and floral visitor groups are associated with motif positions that represent different network roles, we characterized the roles of each motif positions for plant and floral visitor groups in terms of their specialisation and number of indirect interactions.
-To that end, we calculated the specificity of each motif position following @poisot2015 as $s_i = (L - l_i) / (L - 1)$, where $L$ is the total number of groups and $l_i$ the number of interaction partners of the group $i$ in a given motif.
-Values of the vector $si$, range between 1, complete specialisation (1 partner within the motif) and 0 complete generalism (all possible partners within the motif).
-Then, because all nodes within a motif are connected, we calculated the number of indirect interactions ($n_i$) for each motif position and trophic guild (i.e., plants or floral visitors) as $n_i=z_i-1$, where $z_i$ is the total number of nodes for a trophic guild in a given motif.
+Hence, we assessed the average subgraph frequency per species group, after controlling for the variation at the study level.
+Finally, we visualized with the help of the _ComplexHeatmap_ package version _2.6.2_ [@gu2016] over- and under-representation of plant and floral visitor groups on the different subgraph positions.
+
+To understand if the different plant and floral visitor groups are associated with subgraph positions that represent different network roles, we characterized the roles of each subgraph position for plant and floral visitor groups in terms of their specialisation and number of indirect interactions.
+To that end, we calculated the specificity of each subgraph position following @poisot2015 as $s_i = (L - l_i) / (L - 1)$, where $L$ is the total number of groups and $l_i$ the number of interaction partners of the group $i$ in a given subgraph.
+Values of the vector $si$, range between 1, complete specialisation (1 partner within the subgraph) and 0 complete generalism (all possible partners within the subgraph).
+Then, because all nodes within a subgraph are connected, we calculated the number of indirect interactions ($n_i$) for each subgraph position and trophic guild (i.e., plants or floral visitors) as $n_i=z_i-1$, where $z_i$ is the total number of nodes for a trophic guild in a given subgraph.
 Thus, we considered exclusively indirect interactions within plants though shared floral visitors or within floral visitors though shared plants.
-Finally, we analysed in a single model how specialization and the number of indirect interactions were associated with the observed percentiles for each trophic guild and motif position (see paragraph above).
+Finally, we analysed in a single model how specialization and the number of indirect interactions were associated with the observed percentiles for each trophic guild and subgraph position (see paragraph above).
 For this, we fitted a LMM model with the help again of the _lme4_ package where we considered specialization and number of indirect interactions as response variables with the interaction by plant and floral visitor group for both response variables.
-Further, we considered as random factor motif position nested within study system.
+Further, we considered as random factor subgraph position nested within study system.
 All model diagnostics were conducted with the help of the _Dharma_ package [@hartig2017] version _0.3.3.0_ and model outputs were visualized with the _visreg_ package [@breheny2020] version 2.7.0.
 
-**Over- and under-represented group combinations of motifs**
-
-Finally, we studied which combinations of plant and floral visitor groups tend to appear together within the same motifs (up to five nodes).
+**Over- and under-represented group combinations of subgraphs**
+
+Finally, we studied which combinations of plant and floral visitor groups tend to appear together within the same subgraphs (up to five nodes).
 That is, which combinations are over- or under-represented.
-This analysis used 57 out of the 60 networks available due to computational limitations to identify all the nodes in the motifs of the three networks with the highest number of links.
-To do so, for each of the 53,250 possible motif combinations, we estimated the observed and the expected probability of finding those combinations in empirical networks, respectively.
+This analysis used 57 out of the 60 networks available due to computational limitations to identify all the nodes in the subgraphs of the three networks with the highest number of links.
+To do so, for each of the 53,250 possible subgraph combinations, we estimated the observed and the expected probability of finding those combinations in empirical networks, respectively.
 Then, we determined whether the observed probabilities are likely to come from the expected probabilities or not.
-To calculate the observed probability ($p_i^O$) of the different groups within a motif $i$ (e.g., motif 3, 'bee' + 'bee' + 'selfing herbs'), we divided the number of times that $i$ appears in our set of empirical networks ($n_i^O$) by the sum of the number of times that each possible combination appeared: $p_i^O = n_i^O / \sum_{k=1}^{53,250} n_k^O$.
-To estimate the expected probability ($p_i^E$) of a given motif combination $i$, we assumed that the probability of finding a given group $x$ in the position $\alpha$ is independent of the probabilities associated with other positions and groups in that motif.
-Therefore, the expected probability ($p_i^E$) of the motif combination $i$ is given by the product of the probabilities of its constituents, i.e., $p_i^E = \prod _{(x,\alpha )\in i} p_i(x,\alpha)$, where $p_i(x,\alpha)$ is the probability of finding a given group $x$ in the position $\alpha$ of $i$.
+To calculate the observed probability ($p_i^O$) of the different groups within a subgraph $i$ (e.g., subgraph 3, 'bee' + 'bee' + 'selfing herbs'), we divided the number of times that $i$ appears in our set of empirical networks ($n_i^O$) by the sum of the number of times that each possible combination appeared: $p_i^O = n_i^O / \sum_{k=1}^{53,250} n_k^O$.
+To estimate the expected probability ($p_i^E$) of a given subgraph combination $i$, we assumed that the probability of finding a given group $x$ in the position $\alpha$ is independent of the probabilities associated with other positions and groups in that subgraph.
+Therefore, the expected probability ($p_i^E$) of the subgraph combination $i$ is given by the product of the probabilities of its constituents, i.e., $p_i^E = \prod _{(x,\alpha )\in i} p_i(x,\alpha)$, where $p_i(x,\alpha)$ is the probability of finding a given group $x$ in the position $\alpha$ of $i$.
 Then, by controlling for the variation at the network level with an LMM (see below), we calculated the average number of times that the group $x$ appears in the position $\alpha$ (denoted as $n_i(x,\alpha)$).
@@
 Once we obtained $p_i^O$ and $p_i^E$, we used a simulation approach to determine whether the former is likely to come from the latter or not.
-This approach was preferred since the large number of possible motif combinations and the small probabilities for some of them advise against using an exact test of goodness-of-fit or a Chi-square one.
-Specifically, we created 1,000 random samples with repetition of possible motif combinations, where each sample contained 10 million elements and, for each combination, the probability of being selected was equal to its expected probability.
+This approach was preferred since the large number of possible subgraph combinations and the small probabilities for some of them advise against using an exact test of goodness-of-fit or a Chi-square one.
+Specifically, we created 1,000 random samples with repetition of possible subgraph combinations, where each sample contained 10 million elements and, for each combination, the probability of being selected was equal to its expected probability.
 From those random samples, we extracted the mean and the standard deviation of the expected probability of $i$, denoted as $E\left [ p_i^E \right ]$ and $\sigma\left [ p_i^E \right ]$, respectively, and calculated the z-scores of $p_i^O$ as $z_i^O = \left ( p_i^O - E\left [ p_i^E \right ] \right )/\sigma \left [ p_i^E \right ]$, for those motif combinations with $p_i^O > 0$.
@@
 
-**Overall motif patterns**
-
-Most motifs were under- or over-represented (close to the 1st and 99th percentile, respectively) in the comparison between empirical and simulated networks (Fig.
+**Overall network subgraphs patterns**
+
+Most network subgraphs were under- or over-represented (close to the 1st and 99th percentile, respectively) in the comparison between empirical and simulated networks (Fig.
 2).
-Motifs 3, 5, 9, 10 and 14 were under-represented in empirical networks, that is, all were close to the 1st percentile and under the 25th percentile.
+Network subgraphs 3, 5, 9, 10 and 14 were under-represented in empirical networks, that is, all were close to the 1st percentile and under the 25th percentile.
 Interestingly, four out of five of these motifs belonged to the largest path length classification (i.e., core-peripheral).
-In addition, motifs 2, 6, 7, 16 and 17 were over-represented, all over the 75th percentile.
+In addition, network subgraphs 2, 6, 7, 16 and 17 were over-represented, all over the 75th percentile.
 In contrast to the under-represented motifs, over-represented motifs belonged to the two shortest path length groups (i.e., complete and fan).
-The remaining motifs (i.e., 4, 8, 11, 12, 13, and 15) were between the 25th and 75th percentile.
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure 2.** Comparison of motif frequencies between empirical and simulated networks grouped by average path length (plots a, b, c and d) as determined in Simmons et al.
+The remaining network subgraphs (i.e., 4, 8, 11, 12, 13, and 15) were between the 25th and 75th percentile.
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure 2.** Comparison of network subgraph frequencies between empirical and simulated networks grouped by average path length (plots a, b, c and d) as determined in Simmons et al.
 (2020).
-This is shown with the mean percentage of motif frequencies in empirical networks that were over the motif frequencies of the simulated ones (percentiles).
+This is shown with the mean percentage of subgraph frequencies in empirical networks that were over the subgraph frequencies of the simulated ones (percentiles).
 This was done by network (light blue transparent dots) and then averaged for all networks (black dots with error bars that correspond to the standard deviation)."}
@@
 
-**Over- and under-represented groups on motif positions**
+**Over- and under-represented groups on subgraph positions**
 
@@
 
-The comparison of the plant and floral visitor group frequencies per motif position between empirical and simulated networks showed a `r over`$\%$ and `r under`$\%$ of over- (>75$^{th}$) and under-represented (<25th) groups in the different positions, respectively (Fig.
+The comparison of the plant and floral visitor group frequencies per subgraph position between empirical and simulated networks showed a `r over`$\%$ and `r under`$\%$ of over- (>75$^{th}$) and under-represented (<25th) groups in the different positions, respectively (Fig.
 3).
@@
 Notably, the differences across groups were more marked for floral visitors than for plant groups (the differences between min and max percentiles per position were generally two-three times larger for floral visitors).
-From most over- to under-represented floral visitors groups on the different motif positions (indicated with the dendrogram order in Fig.
+From most over- to under-represented floral visitors groups on the different subgraph positions (indicated with the dendrogram order in Fig.
 3), we found: bees, non-syrphids Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.
-Although plant functional groups showed less differences between them, there were also more represented groups than others, thus from most over- to under-represented groups on the different motif positions we found: self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.
-
-For both floral visitor and plant groups we found over- and under-representation on different motif positions that implied different ecological roles.
-First, for floral visitors, we found that bees were less frequent on motif positions that involved specialization (i.e., lower specificity values) while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) were infrequent in generalised motif positions with low number of indirect interactions (Fig.
+Although plant functional groups showed less differences between them, there were also more represented groups than others, thus from most over- to under-represented groups on the different subgraph positions we found: self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.
+
+For both floral visitor and plant groups we found over- and under-representation on different subgraph positions that implied different ecological roles.
+First, for floral visitors, we found that bees were less frequent on subgraph positions that involved specialization (i.e., lower specificity values) while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) were infrequent in generalised subgraph positions with low number of indirect interactions (Fig.
 S6 A).
-Although plants did not show differences with null models on their frequencies, all plant but tall plants with small unisexual flowers showed a slight tendency to be over-represented on specialised motif positions (Fig.
+Although plants did not show differences with null models on their frequencies, all plant but tall plants with small unisexual flowers showed a slight tendency to be over-represented on specialised subgraph positions (Fig.
 S6 B).
-Second, regarding the number of indirect interactions, bees were over-represented in motif positions with low number of indirect interactions (Fig.
+Second, regarding the number of indirect interactions, bees were over-represented in subgraph positions with low number of indirect interactions (Fig.
 S7 A) and the rest of floral visitor groups showed no differences across positions in comparison with simulated networks.
-For plants, all groups showed a slight trend to be over-represented on motif positions with higher number of indirect interactions (Fig.
+For plants, all groups showed a slight trend to be over-represented on subgraph positions with higher number of indirect interactions (Fig.
 S7 B).
-When we further explore the observed frequencies by number of indirect interactions for floral visitor and plant groups, we found that both bees and tall plants with small unisexual flowers were the only groups with high frequencies on motif positions associated with low number interactions in comparison with the other floral visitor and plant groups (Figs S8 and S9).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', out.width="80%",fig.cap="\\textbf{Figure 3.} Heatmap indicating under- and over-representation of floral visitor and plant groups in the different motif positions (numbers on the right of each heatmap).
-The different motif positions are dividied by the average path length clasification determined by Simmons et al.
-(2020) and they are ordered from the most densely connected motifs (strong or complete) to the less connected ones (weak or core-peripheral).
+When we further explore the observed frequencies by number of indirect interactions for floral visitor and plant groups, we found that both bees and tall plants with small unisexual flowers were the only groups with high frequencies on subgraph positions associated with low number interactions in comparison with the other floral visitor and plant groups (Figs S8 and S9).
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', out.width="80%",fig.cap="\\textbf{Figure 3.} Heatmap indicating under- and over-representation of floral visitor and plant groups in the different subgraph positions (numbers on the right of each heatmap).
+The different subgraph positions are dividied by the average path length clasification determined by Simmons et al.
+(2020) and they are ordered from the most densely connected network structures (strong or complete) to the less connected ones (weak or core-peripheral).
 The superior dendrogram indicates the differences across groups with the more separated groups showing larger differences."}
@@
 
-**Over- and under-represented group combinations of motifs**
-
-The different observed frequencies on the different motif positions showed a hierarchical order of probabilities for floral visitors (Fig.
+**Over- and under-represented group combinations of subgraphs**
+
+The different observed frequencies on the different subgraph positions showed a hierarchical order of probabilities for floral visitors (Fig.
 4).
-That is, the taxonomic group of 'bees' was the most abundant one on all motif positions followed by non-syrphid Diptera which was after bees, the second most frequent group on all positions.
+That is, the taxonomic group of 'bees' was the most abundant one on all subgraph positions followed by non-syrphid Diptera which was after bees, the second most frequent group on all positions.
 Then, the group of syrphids was the most abundant in all positions but two (positions 28 and 31 from motifs 11 and 12, respectively).
 After syrphids, Coleoptera was the most frequent group on the different positions followed by non-bee Hymenoptera and finally, Lepidoptera which was the less frequent group on all positions but two (positions 12 and 22 from motifs 5 and 9, respectively).
-Remarkably, plant functional groups were more variable on the different motif positions.
-However, there were also predominant functional groups found across the different motif positions.
+Remarkably, plant functional groups were more variable on the different subgraph positions.
+However, there were also predominant functional groups found across the different subgraph positions.
 The three most frequent groups were 'tall plants with small unisexual flowers', 'self-incompatible perennials with large flowers' and 'small outcrossing perennials'.
-On the contrary, the groups of 'selfing herbs' and 'short lived outcrossers with long zygomorphic flowers' had the lowest probability to be present on the different motifs plant positions.
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 4.** Graphical representation of the probability of finding a given plant and floral visitor group $x$ in the position $\\alpha$ of motif $i$, $p_i(x,\\alpha)$, for all the possible motifs from two to five species in bipartite networks.
+On the contrary, the groups of 'selfing herbs' and 'short lived outcrossers with long zygomorphic flowers' had the lowest probability to be present on the different subgraph plant positions.
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 4.** Graphical representation of the probability of finding a given plant and floral visitor group $x$ in the position $\\alpha$ of motif $i$, $p_i(x,\\alpha)$, for all the possible network subgraphs from two to five species in bipartite networks.
 The slices in the nodes for a given functional group $x$ are proportional to the corresponding value of $p_i(x,\\alpha)$."}
@@
 5).
-In addition, motifs with small node combinations (i.e., 2 and 3 nodes) only appeared as under-represented.
-Motifs with 4 and 5 node combinations appeared in the three statistical categories but 4 node motifs had a higher proportion in the under-represented category (10% in comparison with the 1$\%$ and the 3$\%$ of the no statistical difference and over-represented categories, respectively).
-Finally, 5 node motifs were in similar proportions in the no statistical difference and over-represented categories (99$\%$ and 97$\%$, respectively) but they appeared in lower proportion in the under-represented category (89$\%$).
-When we explored the identity on the different positions of the most probable motif combinations we found that the most common plant and floral visitor groups were also the most probable on these motif combinations (lower panel Fig.
+In addition, subgraphs with small node combinations (i.e., 2 and 3 nodes) only appeared as under-represented.
+Network subgraphs with 4 and 5 node combinations appeared in the three statistical categories but 4 node subgraphs had a higher proportion in the under-represented category (10% in comparison with the 1$\%$ and the 3$\%$ of the no statistical difference and over-represented categories, respectively).
+Finally, 5 node subgraphs were in similar proportions in the no statistical difference and over-represented categories (99$\%$ and 97$\%$, respectively) but they appeared in lower proportion in the under-represented category (89$\%$).
+When we explored the identity on the different positions of the most probable subgraph combinations we found that the most common plant and floral visitor groups were also the most probable on these subgraph combinations (lower panel Fig.
 5).
@@
 
-  motifs_raw_data <- read_csv("../../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
+  motifs_raw_data <-read_csv("../../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
 
@@
 However, common analytical approaches at the node or at the full network level are unable to capture the full complexity of ecological systems [@simmons2019; @bergamo2021].
-Because network motifs can capture both direct and indirect interactions, by analysing over- and under-representation of motifs we were able to explore in great detail the structure of interactions between animal pollinators and the plants they visit.
-We have explored for the first time the overall structure and representation of network motifs in real plant-pollinator networks and shown that the different motifs up to five nodes are consistently over- or under-represented in comparison with simulated networks.
-Despite the presence of multiple ecological processes (e.g., neutral effects, morphological matching or phenological overlap) shaping motif structure, we found a tendency for over-represented structures with more densely connected motifs (i.e., complete, fan and asymmetric complete).
-As suggested in @simmons2020, a higher proportion of these densely connected motifs could reflect that neutral effects are the predominant ecological process governing the structure of network motifs.
-Thus, as indicated for other network properties like nestedness at the macro-scale level [@krishna2008; @suweis2013], or interaction probability at the species level [@bartomeus2016], species relative abundances (i.e., neutral effects) may be also the main driver governing the meso-scale structure on plant-pollinator networks.
-
-Overall, generalist network motifs for floral visitors were consistently over-represented (e.g., fan-type motifs; Fig.
+Because network subgraphs can capture both direct and indirect interactions, by analysing their over- and under-representation we were able to explore in great detail the structure of interactions between animal pollinators and the plants they visit.
+We have explored for the first time the overall structure and presence of network motifs in real plant-pollinator networks and shown that the different subgraphs up to five nodes are consistently over- or under-represented in comparison with simulated networks.
+Despite the presence of multiple ecological processes (e.g., neutral effects, morphological matching or phenological overlap) shaping the meso-scale, we found a tendency for over-represented motifs that were more densely connected (i.e., complete, fan and asymmetric complete).
+As suggested in @simmons2020, a higher proportion of these densely connected motifs could reflect that neutral effects are the predominant ecological process governing the structure of the meso-scale.
+Thus, as indicated for other network properties like nestedness at the macro-scale level [@krishna2008; @suweis2013], or interaction probability at the species level [@bartomeus2016], species relative abundances (i.e., neutral effects) may be also the main driver governing this intermediate level of complexity on plant-pollinator networks.
+
+Overall, generalist network motifs for floral visitors were consistently over-represented (e.g., fan-type subgraphs; Fig.
 2).
-For instance, when we compare motifs with equal structure for both trophic levels, we found that floral visitors had always over-representation in the positions that implied the highest number of direct links (e.g., positions 16 and 46 from motifs 7 and 17, respectively).
+For instance, when we compare network subgraphs with equal structure for both trophic levels, we found that floral visitors had always over-representation in the positions that implied the highest number of direct links (e.g., positions 16 and 46 from network subgraphs 7 and 17, respectively).
 Despite this being in good agreement with the current view of the generalist nature of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of generalist network motifs was driven by the taxonomic group of bees while the rest of the taxonomic groups tended to be under-represented (Fig.
 S6 A).
-In contrast, non-bee groups were over-represented in motif positions associated with specialised roles.
+In contrast, non-bee groups were over-represented in subgraph positions associated with specialised roles.
 This large effect of bees on the overall patterns is no surprise, as bees were the group with the largest number of interaction records in the whole set of networks as also shown for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017].
 Interestingly, bees also were the group with lower number of indirect interactions while the rest of floral visitor groups showed clearly higher number of indirect interactions indicating that these non-bee floral visitor groups may experience higher competitive interactions for floral resources [@thomson2020].
-Despite plant functional groups showed little differences between them on their motif frequencies, all groups showed a tendency to be over-represented on motif positions that were associated with higher levels of specialisation.
+Despite plant functional groups showed little differences between them on their subgraph frequencies, all groups showed a tendency to be over-represented on subgraph positions that were associated with higher levels of specialisation.
 This tendency towards specialist roles may be the result of co-evolutionary processes (e.g., trait-matching) between plants and pollinators to optimise pollen transfer [@moreira2019].
-Remarkably, only tall plants with small unisexual flowers showed higher frequencies on motifs that were associated with low number of indirect interactions with likely direct implications on pollen transfer for this group that needs to guarantee cross-pollination.
-
-The probabilities of appearance of each functional group on the different motif positions were insufficient to predict most of the observed network position combinations (Fig.
+Remarkably, only tall plants with small unisexual flowers showed higher frequencies on subgraphs that were associated with low number of indirect interactions with likely direct implications on pollen transfer for this group that needs to guarantee cross-pollination.
+
+The probabilities of appearance of each functional group on the different subgraph positions were insufficient to predict most of the observed network position combinations (Fig.
 5).
-This implies that not just the representation of network motifs types but also the identity of the elements of their structure is non-random.
-Notably, we found that just 30$\%$ of the possible 53,250 motif combinations are realized.
-Thus, similarly to the presence of forbidden links at the network level [@olesen2011; @jordano2016], we also found the existence of forbidden motif positions and those represented almost two thirds of the total possible motif combinations.
+This implies that not just the representation of network subgraphs types but also the identity of the elements of their structure is non-random.
+Notably, we found that just 30$\%$ of the possible 53,250 subgraph combinations are realized.
+Thus, similarly to the presence of forbidden links at the network level [@olesen2011; @jordano2016], we also found the existence of forbidden subgraph positions and those represented almost two thirds of the total possible subgraph combinations.
 This concurs well with the general idea that plant-pollinator networks have a high proportion of non-realized direct interactions [@jordano2003; @bascompte2013], and as a result, also a high proportion of non-realized combinations of indirect interactions.
@@
 Despite the advances in the understanding on the ecological processes that influence species pairwise interactions [@bartomeus2016; @peralta2020], we still know little about how these processes determine competitive and facilitative interactions in mutualistic networks.
-Thus, as suggested by @simmons2020, exploring the proportion of these realized network motifs that are competitive or facilitative is a necessary next step to improve our understanding of the architecture of biodiversity [@bascompte2007].
+Thus, as suggested by @simmons2020, exploring the proportion of these realized network subgraphs that are competitive or facilitative is a necessary next step to improve our understanding of the architecture of biodiversity [@bascompte2007].
 
@@
 We believe that this could be investigated by exploring which proportion of over- and under-represented motifs present high and low trait-matching, respectively.
-Moreover, we analysed network motifs focusing exclusively on presence-absence interactions which assume that all interactions are equally important as suggested by @simmons2020, further work should investigate how to account for the quantitative measurements of the strength of plant-pollinator interactions.
+Moreover, we analysed network subgraphs focusing exclusively on presence-absence interactions which assume that all interactions are equally important as suggested by @simmons2020, further work should investigate how to account for the quantitative measurements of the strength of plant-pollinator interactions.
 Finally, despite the wide geographical coverage of our plant-pollinator dataset, there are major gaps for some regions of the world with a clear bias towards Europe, America and islands which have long interested ecologist [@macarthur1963; @warren2015].
@@
 
-In conclusion, by following the framework of @simmons2020 we have been able to explore competitive and facilitative interactions in plant-pollinator networks worldwide and found that indirect interactions are non-random and are more strongly related to neutral processes than to any other ecological process.
-Further, we found that plant and floral visitor groups are associated with different motif positions that involve distinct ecological roles (e.g., generalisation versus specialisation) and that the different motif combinations are strongly constrained.
+In conclusion, by following the framework of @simmons2020 we have been able to explore competitive and facilitative interactions in plant-pollinator networks worldwide and found the presence of worldwide motifs that highlight the non-random structure of indirect interactions.
+Further, we found that plant and floral visitor groups are associated with different subgraph positions that involve distinct ecological roles (e.g., generalisation versus specialisation) and that the different subgraph combinations are strongly constrained.
 Although we are still far to predict how species interact, our work is a first step to elucidate beyond pairwise interactions.

### 2022-07-25 Scripts/Z-score_percentile_histogram_plot.R

@@ -4,7 +4,7 @@ library(dplyr)
 library(ggplot2)
 library(tidyverse)
 #Read data
-data <- read.csv("Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
+data <- read.csv("../../Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
 
 #Check NA's per column
 #data %>%

### 2022-07-27 Manuscript/Main_text/Main_text_Journal_of_Animal_Ecol.Rmd
response to comment 4

@@
 Note that the aim is not comparing different networks, which may differ in sampling effort, but correctly describing the structure of each individual network.
-Like @simmons2020, we classified the different subgraphs by their average path length (mean number of links between all pairs of nodes) into four different groups: (i) complete or strong ($\overline{x} = 1.38$), (ii) fan or medium-strong ($\overline{x} = 1.48$), (iii) assymmetric complete or medium-weak ($\overline{x} = 1.60$) and (iv) core-peripheral or weak ($\overline{x} = 1.85$).
-In general terms, plant and floral visitor groups on more densely connected network subgraphs (e.g., complete or fan) will experience lower number of indirect interactions in contrast to groups on less densely connected ones (e.g., medium-weak or weak).
+Like @simmons2020, we classified the different subgraphs by their average path length (mean number of links between all pairs of nodes) into four different groups: (i) complete or strong ($\overline{x} = 1.38$), (ii) fan or medium-strong ($\overline{x} = 1.48$), (iii) assymmetric complete or medium-weak ($\overline{x} = 1.60$) and (iv) core-peripheral or weak ($\overline{x} = 1.85$), where $\overline{x}$ represents the mean of the average path length across subgraphs in the same group.
+In general terms, plant and floral visitor groups on more densely connected network subgraphs (e.g., complete or fan) will experience lower number of indirect interactions in contrast to groups on less densely connected structures (e.g., medium-weak or weak).
 
@@
 There is a total of 17 possible subgraphs with 46 different positions denoted within each node.
-The different subgraphs are aggregated by their average path length classification wich goes from densely connected (strong subgraphs coloured in yellow) to less connected network structures (weak subgraphs coloured in red).
-Note that two node subgraphs are excluded from this classification.", fig.width=10,fig.height=8}
+The different subgraphs are aggregated by the broad indirect interaction structures they represent on four different groups (strong, medium-strong, medium-weak and weak).
+For each group, we show in the legend the mean value of the average path length of all subgraphs within it.
+The different path length groups range from densely connected network structures (strong subgraphs where all possible interactions are realised and the mean path length is minimum) to weakly connected ones (weak subgraphs where the mean path length is maximum).", fig.width=10,fig.height=8}
 library(tidyverse)
@@
 Values of the vector $si$, range between 1, complete specialisation (1 partner within the subgraph) and 0 complete generalism (all possible partners within the subgraph).
-Then, because all nodes within a subgraph are connected, we calculated the number of indirect interactions ($n_i$) for each subgraph position and trophic guild (i.e., plants or floral visitors) as $n_i=z_i-1$, where $z_i$ is the total number of nodes for a trophic guild in a given subgraph.
-Thus, we considered exclusively indirect interactions within plants though shared floral visitors or within floral visitors though shared plants.
+Then, because all nodes within a motif are connected, we calculated the number of indirect interactions ($n_i$) for each motif position as $n_i=z_i-k_i-1$, where $z_i$ is the total number of nodes in a given motif, and $k_i$ represents the degree of the corresponding motif position, that is, the total number of links connected to such position.
+Thus, we considered all possible indirect interactions for each position.
 Finally, we analysed in a single model how specialization and the number of indirect interactions were associated with the observed percentiles for each trophic guild and subgraph position (see paragraph above).
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure 2.** Comparison of network subgraph frequencies between empirical and simulated networks grouped by average path length (plots a, b, c and d) as determined in Simmons et al.
-(2020).
-This is shown with the mean percentage of subgraph frequencies in empirical networks that were over the subgraph frequencies of the simulated ones (percentiles).
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure 2.** Comparison of network subgraph frequencies between empirical and simulated networks grouped by average path length (plots a, b, c and d) where $\\overline{x}$ indicates the mean of the average path lengths of all subgraphs within each group (strong, medium-strong, medium-weak and weak).
+This comparison is shown with the mean percentage of subgraph frequencies in empirical networks that were over the subgraph frequencies of the simulated ones (percentiles).
 This was done by network (light blue transparent dots) and then averaged for all networks (black dots with error bars that correspond to the standard deviation)."}

### 2022-08-01 Manuscript/Main_text/Main_text_Journal_of_Animal_Ecol.Rmd
git push

@@
 First, plant species were grouped through hierarchical clustering into the optimal number of functional groups that summarized the main plant reproductive strategies.
-For this, we used the trait dataset collated in @lanuza2021 that comprised a total of 1506 species including the 503 species considered in this study (Table S2).
-This dataset consisted of 8 floral, 4 reproductive biology and 3 plant morphology traits excluding traits with high percentage of missing values (over 30$\%$; Table S3).
-We opted to calculate the plant functional groups on this larger set of species because of the higher accuracy when delimiting functional groups with that many variables and species [@dolnicar2014].
+For this, we used the plant trait dataset compiled in @lanuza2021 that consisted also of plant species that belonged to the same plant-pollinator networks plus some additional meta-networks not considered here in order to use just networks with similar sampling effort (e.g., unique location and flowering season).
+This dataset comprised a total of 1506 plant species including the 503 species considered in this study (Table S2).
+Because most of these plant species are likely to benefit from animal pollination, we used reproductive traits relevant to understand the different plant reproductive strategies and their interactions with pollinators.
+After excluding traits with high percentage of missing values (over 30$\%$), we ended up with 8 floral, 3 reproductive biology and 3 plant morphology traits (see Table S3 for a list of all traits).
+Floral traits included those associated with the size, form and number of floral organs (e.g., style length or ovule number).
+Reproductive biology traits described the reproductive system of the plant (i.e., the breeding, mating and compatibility system) and plant morphology traits were associated with the size and form of the plant (i.e., plant height, lifespan and life form).
+After an extensive search for each plant species on several different resources (e.g., plant databases, online floras, books, journals and images), over 80% of the cells of the whole dataset were filled.
+Thus, to avoid the loss of species with trait missing values, missing trait data was imputed as detailed in @lanuza2021.
+
+We opted to calculate the plant functional groups within a larger set of species because of the higher accuracy when delimiting functional groups with that many variables and species [@dolnicar2014].
 To feed the clustering analysis, we calculated the distance between the different qualitative and scaled quantitative variables with Gower distance [@gower1971].
@@
 Hence, we assessed the average subgraph frequency per species group, after controlling for the variation at the study level.
-Finally, we visualized with the help of the _ComplexHeatmap_ package version _2.6.2_ [@gu2016] over- and under-representation of plant and floral visitor groups on the different subgraph positions.
+Finally, we visualized over- and under-representation of plant and floral visitor groups on the different subgraph positions with the help of the _ComplexHeatmap_ package version _2.6.2_ [@gu2016].
 
@@
 All model diagnostics were conducted with the help of the _Dharma_ package [@hartig2017] version _0.3.3.0_ and model outputs were visualized with the _visreg_ package [@breheny2020] version 2.7.0.
+Finally, to verify that different levels of richness across plant and floral visitor groups are not driving the overall results of indirect interactions and specialization, we conducted the analogous analyses for 1000 random samples of the 60% of the networks.
+We found consistent results that indicate that different richness across groups have negligible effects on the overall patterns (see Figs S4 and S5).
 
@@
 
-The hierarchical cluster analysis divided the dataset into five different groups with different and overlapping characteristics (Figs S4 and S5).
+The hierarchical cluster analysis divided the dataset into five different groups with different and overlapping characteristics (Figs S6 and S7).
 The first group referred to as 'selfing herbs' consisted of herbs with hermaphroditic flowers with high levels of autonomous selfing.
@@
 First, for floral visitors, we found that bees were less frequent on subgraph positions that involved specialization (i.e., lower specificity values) while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) were infrequent in generalised subgraph positions with low number of indirect interactions (Fig.
-S6 A).
+S8 A).
 Although plants did not show differences with null models on their frequencies, all plant but tall plants with small unisexual flowers showed a slight tendency to be over-represented on specialised subgraph positions (Fig.
-S6 B).
+S8 B).
 Second, regarding the number of indirect interactions, bees were over-represented in subgraph positions with low number of indirect interactions (Fig.
-S7 A) and the rest of floral visitor groups showed no differences across positions in comparison with simulated networks.
+S9 A) and the rest of floral visitor groups showed no differences across positions in comparison with simulated networks.
 For plants, all groups showed a slight trend to be over-represented on subgraph positions with higher number of indirect interactions (Fig.
-S7 B).
-When we further explore the observed frequencies by number of indirect interactions for floral visitor and plant groups, we found that both bees and tall plants with small unisexual flowers were the only groups with high frequencies on subgraph positions associated with low number interactions in comparison with the other floral visitor and plant groups (Figs S8 and S9).
+S9 B).
+When we further explore the observed frequencies by number of indirect interactions for floral visitor and plant groups, we found that both bees and tall plants with small unisexual flowers were the only groups with high frequencies on subgraph positions associated with low number interactions in comparison with the other floral visitor and plant groups (Figs S10 and S11).
 

### 2022-08-01 Manuscript/Supplementary_Material/Supporting_information_Journal_of_Animal_Ecology.Rmd
adding Nacho's edits
git push

--- 2022-03-31 Manuscript/Supplementary_Material/Supporting_information_Functional_Ecology.Rmd
@@
 
-**The non-random assembly of functional motifs in plant-pollinator networks**
+**The non-random assembly of indirect interactions in plant-pollinator networks**
 
@@
 
-Trait1 <- c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Autonomous selfing", "Compatibility system", "Breeding system", "")
-
-T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub \n Tree", "Brush \n Campanulate \n Capitulum \n Open \n Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic", "None \n Low \n Medium \n High", "Self-incomp.
+Trait1 <- c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Compatibility system", "Breeding system", "", "")
+
+T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub \n Tree", "Brush \n Campanulate \n Capitulum \n Open \n Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic",  "Self-incomp.
 \n Partially self-comp.
-\n Self-comp.", "Hermaphrodite \n Monoecious \n Dioecious",""),align = c("l"))
+\n Self-comp.", "Hermaphrodite \n Monoecious \n Dioecious","", ""),align = c("l"))
 
@@
 
-Type_1 <- c("Vegetative", "Vegetative", "Floral", "Floral", "Reproductive", "Reproductive", "Reproductive", "")
+Type_1 <- c("Vegetative", "Vegetative", "Floral", "Floral", "Reproductive", "Reproductive", "", "")
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=7, fig.width=12, fig.cap="**Figure S4.** Plant functional group composition separated in qualitative and quantitative variables.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=7, fig.width=12, fig.cap="**Figure S4.** Association between the percentile (frequency comparison between empirical and simulated networks) and specialization of the different plant and floral visitor groups on the distinct motif positions for 1000 random sets that contain the 60% of the whole set of networks each.
+Black lines represent the mean percentile values of random samples and the continuous red line indicates the mean percentile values for the whole set of networks.
+Grey areas show the 95% confidence intervals for random samples, whereas those for the whole set of networks are displayed by using red dashed lines.
+Note that percentiles above 0.75 indicate over-representation and those below 0.25 under-representation in the comparison between empirical and simulated networks."}
+
+library(tidyverse)
+
+# Load data for all datasets------------------------
+
+percentage_studies_load <- 1.0
+repetitions_load <- 1
+
+file_suffix <- paste0("pollinator_sp_plot_",repetitions_load,"_repetitions_",
+                      round(100*percentage_studies_load),"_percent.csv")
+
+shade_data_pollinator_sp_plot_all <- read_csv(paste0("../../Data/Csv/shade_data_",file_suffix))
+mean_line_data_pollinator_sp_plot_all <- read_csv(paste0("../../Data/Csv/mean_line_data_",file_suffix))
+
+file_suffix <- paste0("pollinator_int_plot_",repetitions_load,"_repetitions_",
+                      round(100*percentage_studies_load),"_percent.csv")
+
+shade_data_pollinator_int_plot_all <- read_csv(paste0("../../Data/Csv/shade_data_",file_suffix))
+mean_line_data_pollinator_int_plot_all <- read_csv(paste0("../../Data/Csv/mean_line_data_",file_suffix))
+
+file_suffix <- paste0("plant_sp_plot_",repetitions_load,"_repetitions_",
+                      round(100*percentage_studies_load),"_percent.csv")
+
+shade_data_plant_sp_plot_all <- read_csv(paste0("../../Data/Csv/shade_data_",file_suffix))
+mean_line_data_plant_sp_plot_all <- read_csv(paste0("../../Data/Csv/mean_line_data_",file_suffix))
+
+file_suffix <- paste0("plant_int_plot_",repetitions_load,"_repetitions_",
+                      round(100*percentage_studies_load),"_percent.csv")
+
+shade_data_plant_int_plot_all <- read_csv(paste0("../../Data/Csv/shade_data_",file_suffix))
+mean_line_data_plant_int_plot_all <- read_csv(paste0("../../Data/Csv/mean_line_data_",file_suffix))
+
+# Load data for a fraction of the total datasets-----------------
+
+percentage_studies_load <- .60
+repetitions_load <- 100
+
+file_suffix <- paste0("pollinator_sp_plot_",repetitions_load,"_repetitions_",
+                      round(100*percentage_studies_load),"_percent.csv")
+
+shade_data_pollinator_sp_plot <- read_csv(paste0("../../Data/Csv/shade_data_",file_suffix))
+mean_line_data_pollinator_sp_plot <- read_csv(paste0("../../Data/Csv/mean_line_data_",file_suffix))
+
+file_suffix <- paste0("pollinator_int_plot_",repetitions_load,"_repetitions_",
+                      round(100*percentage_studies_load),"_percent.csv")
+
+shade_data_pollinator_int_plot <- read_csv(paste0("../../Data/Csv/shade_data_",file_suffix))
+mean_line_data_pollinator_int_plot <- read_csv(paste0("../../Data/Csv/mean_line_data_",file_suffix))
+
+file_suffix <- paste0("plant_sp_plot_",repetitions_load,"_repetitions_",
+                      round(100*percentage_studies_load),"_percent.csv")
+
+shade_data_plant_sp_plot <- read_csv(paste0("../../Data/Csv/shade_data_",file_suffix))
+mean_line_data_plant_sp_plot <- read_csv(paste0("../../Data/Csv/mean_line_data_",file_suffix))
+
+file_suffix <- paste0("plant_int_plot_",repetitions_load,"_repetitions_",
+                      round(100*percentage_studies_load),"_percent.csv")
+
+shade_data_plant_int_plot <- read_csv(paste0("../../Data/Csv/shade_data_",file_suffix))
+mean_line_data_plant_int_plot <- read_csv(paste0("../../Data/Csv/mean_line_data_",file_suffix))
+
+pollinator_names <- list(
+  '1'="Bee",
+  '2'="Coleoptera",
+  '3'="Lepidoptera",
+  '4'="Non-bee-Hymenoptera",
+  '5'="Non-syrphids-diptera",
+  '6'="Syrphids"
+)
+
+plant_names <- list(
+  '1'="Selfing herbs",
+  '2'="Small outcrossing perennials",
+  '3'="Self-incompatible perennials\nwith large flowers",
+  '4'="Tall plants with small\nunisexual flowers",
+  '5'="Short-lived outcrossers with\nlong zygomorphic flowers")
+
+pollinator_labeller <- function(variable,value){
+  return(pollinator_names[value])
+}
+
+plant_labeller <- function(variable,value){
+  return(plant_names[value])
+}
+
+final_pollinator_sp_plot <- ggplot(shade_data_pollinator_sp_plot)+
+  geom_ribbon(aes(x=x, ymax=ymax, ymin= ymin, fil = as.factor(repetition)), alpha=1/repetitions_load)+
+  facet_grid( ~ PANEL, labeller=pollinator_labeller)+
+  geom_line(data = mean_line_data_pollinator_sp_plot, 
+            aes(x = x, y = y, co = as.factor(repetition)), alpha=0.5)+
+  geom_line(data = shade_data_pollinator_sp_plot_all,
+              aes(x=x, y=ymax, color ="red"), size = 1.2,linetype = "dashed")+
+  geom_line(data = shade_data_pollinator_sp_plot_all,
+            aes(x=x, y= ymin, color ="red"), size = 1.2, linetype = "dashed")+
+  geom_line(data = mean_line_data_pollinator_sp_plot_all, 
+            aes(x = x, y = y, color ="red"), size = 1.2)+
+  theme_bw()+
+  ggtitle("Floral visitors") +
+  labs(y="Percentile", x =NULL)+
+  theme(legend.position = "none")
+
+final_plant_sp_plot <- ggplot(shade_data_plant_sp_plot)+
+  geom_ribbon(aes(x=x, ymax=ymax, ymin= ymin, fil = as.factor(repetition)), alpha=1/repetitions_load)+
+  facet_grid( ~ PANEL, labeller=plant_labeller)+
+  geom_line(data = mean_line_data_plant_sp_plot, 
+            aes(x = x, y = y, co = as.factor(repetition)), alpha=0.5)+
+  geom_line(data = shade_data_plant_sp_plot_all,
+            aes(x=x, y=ymax, color ="red"), size = 1.2,linetype = "dashed")+
+  geom_line(data = shade_data_plant_sp_plot_all,
+            aes(x=x, y= ymin, color ="red"), size = 1.2, linetype = "dashed")+
+  geom_line(data = mean_line_data_plant_sp_plot_all, 
+            aes(x = x, y = y, color ="red"), size = 1.2)+
+  theme_bw()+
+  ggtitle("Plants")+
+  labs(x = "Specialization", y="Percentile")+
+  theme(legend.position = "none")
+
+library(patchwork)
+
+final_pollinator_sp_plot/final_plant_sp_plot & theme(axis.text=element_text(size=10),
+                                                    axis.title=element_text(size=16)) & 
+  plot_annotation(tag_levels = c('A'),  tag_suffix = ')') &  theme(plot.tag = element_text(size = 22))
+
+```
+
+\newpage
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=7, fig.width=12, fig.cap="**Figure S5.** Association between the percentile (frequency comparison between empirical and simulated networks) and number of indirect interactions of the different plant and floral visitor groups on the distinct motif positions for 1000 random sets that contain the 60% of the whole set of networks each.
+Black lines represent the mean percentile values of random samples and the continuous red line indicates the mean percentile values for the whole set of networks.
+Grey areas show the 95% confidence intervals for random samples, whereas those for the whole set of networks are displayed by using red dashed lines.
+Note that percentiles above 0.75 indicate over-representation and those below 0.25 under-representation in the comparison between empirical and simulated networks.
+"}
+
+library(tidyverse)
+
+# Load data for all datasets------------------------
+
+percentage_studies_load <- 1.0
+repetitions_load <- 1
+
+file_suffix <- paste0("pollinator_sp_plot_",repetitions_load,"_repetitions_",
+                      round(100*percentage_studies_load),"_percent.csv")
+
+shade_data_pollinator_sp_plot_all <- read_csv(paste0("../../Data/Csv/shade_data_",file_suffix))
+mean_line_data_pollinator_sp_plot_all <- read_csv(paste0("../../Data/Csv/mean_line_data_",file_suffix))
+
+file_suffix <- paste0("pollinator_int_plot_",repetitions_load,"_repetitions_",
+                      round(100*percentage_studies_load),"_percent.csv")
+
+shade_data_pollinator_int_plot_all <- read_csv(paste0("../../Data/Csv/shade_data_",file_suffix))
+mean_line_data_pollinator_int_plot_all <- read_csv(paste0("../../Data/Csv/mean_line_data_",file_suffix))
+
+file_suffix <- paste0("plant_sp_plot_",repetitions_load,"_repetitions_",
+                      round(100*percentage_studies_load),"_percent.csv")
+
+shade_data_plant_sp_plot_all <- read_csv(paste0("../../Data/Csv/shade_data_",file_suffix))
+mean_line_data_plant_sp_plot_all <- read_csv(paste0("../../Data/Csv/mean_line_data_",file_suffix))
+
+file_suffix <- paste0("plant_int_plot_",repetitions_load,"_repetitions_",
+                      round(100*percentage_studies_load),"_percent.csv")
+
+shade_data_plant_int_plot_all <- read_csv(paste0("../../Data/Csv/shade_data_",file_suffix))
+mean_line_data_plant_int_plot_all <- read_csv(paste0("../../Data/Csv/mean_line_data_",file_suffix))
+
+# Load data for a fraction of the total datasets-----------------
+
+percentage_studies_load <- .60
+repetitions_load <- 100
+
+file_suffix <- paste0("pollinator_sp_plot_",repetitions_load,"_repetitions_",
+                      round(100*percentage_studies_load),"_percent.csv")
+
+shade_data_pollinator_sp_plot <- read_csv(paste0("../../Data/Csv/shade_data_",file_suffix))
+mean_line_data_pollinator_sp_plot <- read_csv(paste0("../../Data/Csv/mean_line_data_",file_suffix))
+
+file_suffix <- paste0("pollinator_int_plot_",repetitions_load,"_repetitions_",
+                      round(100*percentage_studies_load),"_percent.csv")
+
+shade_data_pollinator_int_plot <- read_csv(paste0("../../Data/Csv/shade_data_",file_suffix))
+mean_line_data_pollinator_int_plot <- read_csv(paste0("../../Data/Csv/mean_line_data_",file_suffix))
+
+file_suffix <- paste0("plant_sp_plot_",repetitions_load,"_repetitions_",
+                      round(100*percentage_studies_load),"_percent.csv")
+
+shade_data_plant_sp_plot <- read_csv(paste0("../../Data/Csv/shade_data_",file_suffix))
+mean_line_data_plant_sp_plot <- read_csv(paste0("../../Data/Csv/mean_line_data_",file_suffix))
+
+file_suffix <- paste0("plant_int_plot_",repetitions_load,"_repetitions_",
+                      round(100*percentage_studies_load),"_percent.csv")
+
+shade_data_plant_int_plot <- read_csv(paste0("../../Data/Csv/shade_data_",file_suffix))
+mean_line_data_plant_int_plot <- read_csv(paste0("../../Data/Csv/mean_line_data_",file_suffix))
+
+pollinator_names <- list(
+  '1'="Bee",
+  '2'="Coleoptera",
+  '3'="Lepidoptera",
+  '4'="Non-bee-Hymenoptera",
+  '5'="Non-syrphids-diptera",
+  '6'="Syrphids"
+)
+
+plant_names <- list(
+  '1'="Selfing herbs",
+  '2'="Small outcrossing perennials",
+  '3'="Self-incompatible perennials\nwith large flowers",
+  '4'="Tall plants with small\nunisexual flowers",
+  '5'="Short-lived outcrossers with\nlong zygomorphic flowers")
+
+pollinator_labeller <- function(variable,value){
+  return(pollinator_names[value])
+}
+
+plant_labeller <- function(variable,value){
+  return(plant_names[value])
+}
+
+final_pollinator_int_plot <- ggplot(shade_data_pollinator_int_plot)+
+  geom_ribbon(aes(x=x, ymax=ymax, ymin= ymin, fil = as.factor(repetition)), alpha=1/repetitions_load)+
+  facet_grid( ~ PANEL, labeller=pollinator_labeller)+
+  geom_line(data = mean_line_data_pollinator_int_plot, 
+            aes(x = x, y = y, co = as.factor(repetition)), alpha=0.5)+
+  geom_line(data = shade_data_pollinator_int_plot_all,
+            aes(x=x, y=ymax, color ="red"), size = 1.2,linetype = "dashed")+
+  geom_line(data = shade_data_pollinator_int_plot_all,
+            aes(x=x, y= ymin, color ="red"), size = 1.2, linetype = "dashed")+
+  geom_line(data = mean_line_data_pollinator_int_plot_all, 
+            aes(x = x, y = y, color ="red"), size = 1.2)+
+  theme_bw()+
+  ggtitle("Floral visitors") +
+  labs(y="Percentile", x =NULL)+
+  theme(legend.position = "none")
+
+final_plant_int_plot <- ggplot(shade_data_plant_int_plot)+
+  geom_ribbon(aes(x=x, ymax=ymax, ymin= ymin, fil = as.factor(repetition)), alpha=1/repetitions_load)+
+  facet_grid( ~ PANEL, labeller=plant_labeller)+
+  geom_line(data = mean_line_data_plant_int_plot, 
+            aes(x = x, y = y, co = as.factor(repetition)), alpha=0.5)+
+  geom_line(data = shade_data_plant_int_plot_all,
+            aes(x=x, y=ymax, color ="red"), size = 1.2,linetype = "dashed")+
+  geom_line(data = shade_data_plant_int_plot_all,
+            aes(x=x, y= ymin, color ="red"), size = 1.2, linetype = "dashed")+
+  geom_line(data = mean_line_data_plant_int_plot_all, 
+            aes(x = x, y = y, color ="red"), size = 1.2)+
+  theme_bw()+
+  ggtitle("Plants")+
+  labs(y="Percentile", x ="Number of indirect interactions")+
+  theme(legend.position = "none")
+
+library(patchwork)
+
+final_pollinator_int_plot/final_plant_int_plot & theme(axis.text=element_text(size=10),
+                                                       axis.title=element_text(size=16)) & 
+  plot_annotation(tag_levels = c('A'),  tag_suffix = ')') &  theme(plot.tag = element_text(size = 22))
+
+```
+
+\newpage
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=7, fig.width=12, fig.cap="**Figure S6.** Plant functional group composition separated in qualitative and quantitative variables.
 Panel A) shows the percentage of the different categories within trait represented with different colours for each functional group.
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=13, fig.cap="**Figure S5.** Hierarchical clustering dendrogram with the branches coloured by the optimal number of clusters (5).
+```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=13, fig.cap="**Figure S7.** Hierarchical clustering dendrogram with the branches coloured by the optimal number of clusters (5).
 The labels of the subgroup of species (N = 524) used in this study are coloured in black in order to show the evenness of the distribution of the species across clusters.
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align="center", fig.width=14,fig.height=7, out.width='100%',  fig.cap="\\textbf{Figure S6.} Association between the percentile (see main text) and specialization of the different plant and floral visitor groups on motif positions.
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align="center", fig.width=14,fig.height=7, out.width='100%',  fig.cap="\\textbf{Figure S8.} Association between the percentile (see main text) and specialization of the different plant and floral visitor groups on motif positions.
 Here we consider that percentiles above 0.75 indicate over-representation and percentiles below 0.25 under-representation in the comparison between empirical and simulated networks."}
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align="center", fig.width=14,fig.height=7, out.width='100%', fig.cap="\\textbf{Figure S7.} Association between the percentile (see main text) and number of indirect interactions of the different plant and floral visitor groups on motif positions.
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align="center", fig.width=14,fig.height=7, out.width='100%', fig.cap="\\textbf{Figure S9.} Association between the percentile (see main text) and number of indirect interactions of the different plant and floral visitor groups on motif positions.
 Here we consider that percentiles above 0.75 indicate over-representation and percentiles below 0.25 under-representation in the comparison between empirical and simulated networks."}
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S8.} Frequency of the different floral visitor groups on the different motif positions aggregated by the number of indirect interactions for the different motif positions."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S10.} Frequency of the different floral visitor groups on the different motif positions aggregated by the number of indirect interactions for the different motif positions."}
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S9.} Frequency of the different plant groups on the different motif positions aggregated by the number of indirect interactions for the different motif positions."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S11.} Frequency of the different plant groups on the different motif positions aggregated by the number of indirect interactions for the different motif positions."}
 

### 2022-08-01 Scripts/Scripts_Alfonso/sensitivity_specificity_VS_position_frequencies.R
Data for sensitivity analysis (1000 random rep)

@@ -14,8 +14,8 @@ library(visreg)
 ############################################
 
 
-percentage_studies <- 1.0
-repetitions <- 1
+percentage_studies <- .60
+repetitions <- 1000
 
 ################################################################################
 # Initializing variables
@@ -516,7 +516,7 @@ mean_line_data_plant_int_plot_all <- read_csv(paste0("Data/Csv/mean_line_data_",
 # Load data for a fraction of the total datasets-----------------
 
 percentage_studies_load <- .60
-repetitions_load <- 100
+repetitions_load <- 1000
 
 file_suffix <- paste0("pollinator_sp_plot_",repetitions_load,"_repetitions_",
                       round(100*percentage_studies_load),"_percent.csv")
@@ -568,10 +568,10 @@ plant_labeller <- function(variable,value){
 
 
 final_pollinator_sp_plot <- ggplot(shade_data_pollinator_sp_plot)+
-  geom_ribbon(aes(x=x, ymax=ymax, ymin= ymin, fil = as.factor(repetition)), alpha=1/repetitions_load)+
+  geom_ribbon(aes(x=x, ymax=ymax, ymin= ymin, fil = as.factor(repetition)), alpha=10/repetitions_load)+
   facet_grid( ~ PANEL, labeller=pollinator_labeller)+
   geom_line(data = mean_line_data_pollinator_sp_plot, 
-            aes(x = x, y = y, co = as.factor(repetition)), alpha=0.5)+
+            aes(x = x, y = y, co = as.factor(repetition)), alpha=0.2)+
   geom_line(data = shade_data_pollinator_sp_plot_all,
               aes(x=x, y=ymax, color ="red"), size = 1.2,linetype = "dashed")+
   geom_line(data = shade_data_pollinator_sp_plot_all,
@@ -585,10 +585,10 @@ final_pollinator_sp_plot <- ggplot(shade_data_pollinator_sp_plot)+
 
 
 final_pollinator_int_plot <- ggplot(shade_data_pollinator_int_plot)+
-  geom_ribbon(aes(x=x, ymax=ymax, ymin= ymin, fil = as.factor(repetition)), alpha=1/repetitions_load)+
+  geom_ribbon(aes(x=x, ymax=ymax, ymin= ymin, fil = as.factor(repetition)), alpha=10/repetitions_load)+
[…]

### 2022-08-02 Manuscript/Supplementary_Material/Supporting_information_Journal_of_Animal_Ecology.Rmd
minor edits
edits on supplementary and upload manuscruipt to google drive

@@
 
+#######################################
+# PLOT GRAPHS
+#######################################
+
 library(tidyverse)
@@
 percentage_studies_load <- .60
-repetitions_load <- 100
+repetitions_load <- 1000
 
@@
 final_pollinator_sp_plot <- ggplot(shade_data_pollinator_sp_plot)+
-  geom_ribbon(aes(x=x, ymax=ymax, ymin= ymin, fil = as.factor(repetition)), alpha=1/repetitions_load)+
+  geom_ribbon(aes(x=x, ymax=ymax, ymin= ymin, fil = as.factor(repetition)), alpha=10/repetitions_load)+
   facet_grid( ~ PANEL, labeller=pollinator_labeller)+
   geom_line(data = mean_line_data_pollinator_sp_plot, 
-            aes(x = x, y = y, co = as.factor(repetition)), alpha=0.5)+
+            aes(x = x, y = y, co = as.factor(repetition)), alpha=0.2)+
   geom_line(data = shade_data_pollinator_sp_plot_all,
@@
 final_plant_sp_plot <- ggplot(shade_data_plant_sp_plot)+
-  geom_ribbon(aes(x=x, ymax=ymax, ymin= ymin, fil = as.factor(repetition)), alpha=1/repetitions_load)+
+  geom_ribbon(aes(x=x, ymax=ymax, ymin= ymin, fil = as.factor(repetition)), alpha=10/repetitions_load)+
   facet_grid( ~ PANEL, labeller=plant_labeller)+
   geom_line(data = mean_line_data_plant_sp_plot, 
-            aes(x = x, y = y, co = as.factor(repetition)), alpha=0.5)+
+            aes(x = x, y = y, co = as.factor(repetition)), alpha=0.2)+
   geom_line(data = shade_data_plant_sp_plot_all,
@@
 Grey areas show the 95% confidence intervals for random samples, whereas those for the whole set of networks are displayed by using red dashed lines.
-Note that percentiles above 0.75 indicate over-representation and those below 0.25 under-representation in the comparison between empirical and simulated networks.
-"}
+Note that percentiles above 0.75 indicate over-representation and those below 0.25 under-representation in the comparison between empirical and simulated networks."}
+
+#######################################
+# PLOT GRAPHS
+#######################################
 
@@
 final_pollinator_int_plot <- ggplot(shade_data_pollinator_int_plot)+
-  geom_ribbon(aes(x=x, ymax=ymax, ymin= ymin, fil = as.factor(repetition)), alpha=1/repetitions_load)+
+  geom_ribbon(aes(x=x, ymax=ymax, ymin= ymin, fil = as.factor(repetition)), alpha=10/repetitions_load)+
   facet_grid( ~ PANEL, labeller=pollinator_labeller)+
   geom_line(data = mean_line_data_pollinator_int_plot, 
-            aes(x = x, y = y, co = as.factor(repetition)), alpha=0.5)+
+            aes(x = x, y = y, co = as.factor(repetition)), alpha=0.2)+
   geom_line(data = shade_data_pollinator_int_plot_all,
@@
 final_plant_int_plot <- ggplot(shade_data_plant_int_plot)+
-  geom_ribbon(aes(x=x, ymax=ymax, ymin= ymin, fil = as.factor(repetition)), alpha=1/repetitions_load)+
+  geom_ribbon(aes(x=x, ymax=ymax, ymin= ymin, fil = as.factor(repetition)), alpha=10/repetitions_load)+
   facet_grid( ~ PANEL, labeller=plant_labeller)+
   geom_line(data = mean_line_data_plant_int_plot, 
-            aes(x = x, y = y, co = as.factor(repetition)), alpha=0.5)+
+            aes(x = x, y = y, co = as.factor(repetition)), alpha=0.2)+
   geom_line(data = shade_data_plant_int_plot_all,

### 2022-08-02 Scripts/Google_drive.R

@@ -1,0 +1,27 @@
+
+#Upload files to google drive
+#install packages
+remotes::install_github("claudiozandonella/trackdown",
+                        build_vignettes = TRUE, force=T)
+
+install.packages("googledrive")
+
+#set google doc
+googledrive::drive_auth()
+
+#load libraries
+library(googledrive)
+library(trackdown)
+
+#upload file
+upload_file(
+  file = "Manuscript/Main_text/Main_text_Journal_of_Animal_Ecol.Rmd", 
+  gfile = "FunctionalMotifs"
+)
+
+
+#download file 
+download_file(
+  file = "Manuscript/Main_text/Main_text_Journal_of_Animal_Ecol.Rmd", 
+  gfile = "FunctionalMotifs"
+)

### 2022-08-08 Manuscript/Main_text/Main_text_Journal_of_Animal_Ecol.Rmd
minor edit in methods
renaming figs

@@
 We have compiled 60 plant-pollinator networks from 18 different studies (Table S1).
-All studies sampled plant-pollinator interactions in natural systems and were selected based on wide geographical coverage (Fig.
+All studies sampled plant-pollinator interactions in natural systems in a single flowering season and were selected based on wide geographical coverage (Fig.
 S1) and presence of interaction frequency as a measure of interaction strength.
@@
 Finally, to verify that different levels of richness across plant and floral visitor groups are not driving the overall results of indirect interactions and specialization, we conducted the analogous analyses for 1000 random samples of the 60% of the networks.
-We found consistent results that indicate that different richness across groups have negligible effects on the overall patterns (see Figs S4 and S5).
+We found consistent results that indicate that different richness across groups have negligible effects on the overall patterns [WORK ON THIS]().
 
@@
 
-The hierarchical cluster analysis divided the dataset into five different groups with different and overlapping characteristics (Figs S6 and S7).
+The hierarchical cluster analysis divided the dataset into five different groups with different and overlapping characteristics (Figs S4 and S5).
 The first group referred to as 'selfing herbs' consisted of herbs with hermaphroditic flowers with high levels of autonomous selfing.
@@
 First, for floral visitors, we found that bees were less frequent on subgraph positions that involved specialization (i.e., lower specificity values) while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) were infrequent in generalised subgraph positions with low number of indirect interactions (Fig.
-S8 A).
+S6 A).
 Although plants did not show differences with null models on their frequencies, all plant but tall plants with small unisexual flowers showed a slight tendency to be over-represented on specialised subgraph positions (Fig.
-S8 B).
+S6 B).
 Second, regarding the number of indirect interactions, bees were over-represented in subgraph positions with low number of indirect interactions (Fig.
-S9 A) and the rest of floral visitor groups showed no differences across positions in comparison with simulated networks.
+S7 A) and the rest of floral visitor groups showed no differences across positions in comparison with simulated networks.
 For plants, all groups showed a slight trend to be over-represented on subgraph positions with higher number of indirect interactions (Fig.
-S9 B).
-When we further explore the observed frequencies by number of indirect interactions for floral visitor and plant groups, we found that both bees and tall plants with small unisexual flowers were the only groups with high frequencies on subgraph positions associated with low number interactions in comparison with the other floral visitor and plant groups (Figs S10 and S11).
+S7 B).
+When we further explore the observed frequencies by number of indirect interactions for floral visitor and plant groups, we found that both bees and tall plants with small unisexual flowers were the only groups with high frequencies on subgraph positions associated with low number interactions in comparison with the other floral visitor and plant groups (Figs S8 and S9).
 

### 2022-08-08 Manuscript/Supplementary_Material/Supporting_information_Journal_of_Animal_Ecology.Rmd
renaming figs

--- 2022-03-31 Manuscript/Supplementary_Material/Supporting_information_Functional_Ecology.Rmd
@@
 \newpage
-
-\blandscape
 
@@
 
-\elandscape
-
 \blandscape

### 2022-10-06 Manuscript/Main_text/Main_text_Journal_of_Animal_Ecol.Rmd
Edits

@@
 always_allow_html: true
-bibliography: bibliography_no_doi.bib
+bibliography: bibliography.bib
 biblio-style: apalike
@@
 Ecological processes leave distinct structural imprints on the species interactions that shape the topology of animal-plant mutualistic networks.
-Detecting how direct and indirect interactions between animals and plants are organized is not trivial since they go beyond pairwise interactions, but may get blurred when considering full network descriptors.
-Recent work has shown that the meso-scale, the intermediate level of network complexity between the species and the full network, can capture this important information.
+Detecting how direct and indirect interactions between animals and plants are organised is not trivial since they go beyond pairwise interactions, but may get blurred when considering global network descriptors.
+Recent work has shown that the meso-scale, the intermediate level of network complexity between the species and the global network, can capture this important information.
 The meso-scale describes network subgraphs representing patterns of direct and indirect interactions between a small number of species and when these network subgraphs differ statistically from a benchmark, they are often referred to as "network motifs".
-Despite motifs can capture relevant ecological information of species interactions, they remain overlooked in natural plant-pollinator networks.
+Although motifs can capture relevant ecological information of species interactions, they remain overlooked in natural plant-pollinator networks.
 By exploring 60 empirical plant-pollinator networks from 18 different studies with wide geographical coverage we show that some network subgraphs are consistently under- or over-represented, suggesting the presence of worldwide network motifs in plant-pollinator networks.
-In addition, we found a higher proportion of densely connected network subgraphs, which could reflect that neutral effects are the predominant ecological process governing the structure of the meso-scale.
-We found that distinct subgraph positions describing species ecological roles (e.g., generalisation and number of indirect interactions) are occupied by different floral visitor and plant groups on both trophic levels.
-For example, bees tend to appear in subgraph positions with a lower number of indirect interactions than the rest of floral visitor groups.
-Interestingly, the realized combinations of different species groups within a network subgraph can not be retrieved from their joint probability distributions, indicating that plant and floral visitor group combinations on network subgraphs are not random.
-Our results highlight the non-random structure of the key building blocks shaping plant-pollinators networks and the association of certain network subgraphs and their positions with specific groups of floral visitors and plants.
+In addition, we found a higher proportion of densely connected network subgraphs that, based on previous findings, could reflect that species relative abundances are the main driver shaping the structure of the meso-scale on plant-pollinator communities.
+Moreover, we found that distinct subgraph positions describing species ecological roles (e.g., generalisation and number of indirect interactions) are occupied by different groups of animal and plant species representing their main life history strategies (i.e., functional groups).
+For instance, we found that the functional group of ‘bees’ was over-represented in subgraph positions with a lower number of indirect interactions in contrast to the rest of floral visitors groups.
+Finally, we show that the observed functional group combinations within a subgraph can not be retrieved from their expected probabilities (i.e., joint probability distributions), indicating that plant and floral visitor associations within subgraphs are not random either.
+Therefore, our results highlight the presence of common motifs in plant-pollinator communities that are formed by a non-random association of plants and floral visitors functional groups.
 
@@
 Ecological communities are formed by a plethora of interacting species that form networks of interactions.
-Because of the tremendous complexity of these ecological networks, species interactions are generally condensed in metrics that summarize this information [@guimaraes2020].
+Because of the tremendous complexity of these ecological networks, species interactions are generally condensed in metrics that summarise this information [@guimaraes2020].
 Plant-pollinator interactions are no exception, and they are often studied with indices that aggregate the information at the network (macro-scale) and species level (micro-scale).
-For example, plant-pollinator network level approaches have identified common invariant structural properties across mutualistic networks, including a degree distribution that decays as a power law [@jordano1987], nestedness [@bascompte2003], or modularity [@olesen2007].
-In addition, the local species position within the network can define its degree of specialisation [@bluthgen2006] or its role in connecting the rest of the community [@olesen2007].
+For example, plant-pollinator network level approaches have identified common invariant structural properties across mutualistic networks, including a degree distribution that decays as a truncated power law [@jordano1987], nestedness [@bascompte2003], or modularity [@olesen2007].
+In addition, the local species position within the network can define its degree of selectiveness [@bluthgen2006] or its role in connecting the rest of the community [@olesen2007].
 Despite the unquestionable progress with the use of these metrics at both network and species level, condensing complex information into a single metric implies the loss of relevant ecological information that obscures the understanding of species interactions [@cirtwill2018; @simmons2019].
 
-Traditionally, plant-pollinator research has focused on direct interactions but overlooked indirect interactions [i.e., the mediated effect between two species by a third species\; @holt1994], such as facilitative or competitive interactions between plants for pollinators [@moeller2004; @sargent2008; @carvalheiro2014].
-Despite the widespread nature of indirect interactions in ecological communities [@strauss1991], plant-pollinator research often fails to finely capture those indirect interactions with the conventional analytical tools that condense the information either by species (e.g., degree) or in global topological indices (e.g., nestedness).
-Nonetheless, the analysis of network subgraphs at the meso-scale, the intermediate level of complexity between the full network and the species level, allows to consider both direct and indirect interactions [@simmons2019].
-The network subgraphs that significantly depart from an expected benchmark are often defined as 'network motifs' [@milo2002].
-The analysis of network motifs in plant-pollinator networks have revealed that the different drivers that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions [@simmons2020].
-Yet, the global patterns of indirect interactions in real plant-pollinator networks are still unknown (e.g., over- and under- represented network subgraphs).
+Indirect interactions, the mediated effect between two species by a third species, are ubiquitous in natural systems [@strauss1991; @holt1994; @wootton1994] and play a key role in shaping community dynamics [@werner2003; @walsh2013].
+Although some of the most studied indirect interactions are the ones caused by trophic cascades with consumer-resource interactions [@abrams1996; @schmitz2001], previous studies often focus on antagonistic interactions and overlook mutualistic ones [@knight2005].
+On the contrary, plant-pollinator research has traditionally investigated direct interactions but neglected indirect effects such as competitive or facilitative processes between plants for pollinators [@moeller2004; @sargent2008; @carvalheiro2014].
+Conventional analytical tools in bipartite networks often discard relevant information about indirect interactions by condensing the information into single indices either at species or network level [@cirtwill2018; @simmons2019].
+However, as previously explored with three species modules in unipartite food webs [@allesina2008; @stouffer2010], the emergent framework of bipartite subgraphs has proven to be a powerful analytical tool to better understand plant-pollinator community dynamics by capturing both direct and indirect effects [@simmons2019].
+These network subgraphs that constitute the meso-scale are often referred to as the building blocks of the network and when their numbers occur at higher frequencies than in randomised networks, those are generally defined as ‘network motifs’ [@milo2002].
+Indeed, the analysis of motifs in simulated plant-pollinator networks has revealed that the different drivers that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect effects [@simmons2020].
+However, the global patterns of indirect interactions in real plant-pollinator networks and their ecological consequences remain unexplored (e.g., over- and under- represented network subgraphs).
 
 By linking the structural properties of the meso-scale with the species' ecology we can advance in our understanding on the determinants of species interactions.
-For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species' functional role [@stouffer2012; @baker2015].
+For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species' functional role [@stouffer2012; @baker2015; @cirtwill2018b].
 Yet, our understanding of the ecological implications of network motifs in real plant-pollinator networks remains in its infancy.
@@
 For example, large pollinators can forage larger distances [@greenleaf2007], deposit greater pollen quantities [@foldesi2021] and handle complex zygomorphic flowers in comparison with small pollinators that are restricted to lower floral complexity [@gong2009].
-Despite these obvious differences in pollinator behaviour, how contrasting species' ecology translates into different interaction patterns is still unknown.
-Similarly, recent empirical findings indicate that the meso-scale is the best descriptor of plant reproductive success [@allen2021], but little is known about how plants reproductive strategies shape their position within the network of interactions.
+Despite these obvious differences in pollinator behaviour, how contrasting species' ecology translates into different network motifs is still poorly known.
+Similarly, recent empirical findings indicate that the meso-scale is the best descriptor of plant reproductive success [@allen2021], but little is known about how plants' reproductive strategies shape their position within the network of interactions.
 Although some studies have evaluated plant reproductive strategies in plant-pollinator networks [@tur2013; @lazaro2020], this is an often overlooked aspect in a community context [@devaux2014] and rarely incorporated into plant-pollinator network studies.
@@
 
-Here, we used 60 empirical networks from 18 different studies and 14 countries to evaluate the structure of the meso-scale in plant-pollinator networks.
-From these networks we extracted plant and floral visitors species and determined the principal groups that define their main life-history strategies.
-To obtain plant groups, we used a comprehensive dataset that included floral, reproductive and vegetative traits compiled in a larger set of plant species.
-Floral visitor groups were divided by the main taxonomic groups that differed in life form and behaviour.
-Once we split the different plant-pollinator networks into their subgraphs elements, we explored: (i) if there is a common invariant structural property in the overall subgraphs from these networks (i.e., over- and under-represented subgraphs); (ii) which plant and floral visitor groups are over- and under-represented in different subgraphs positions associated with specific ecological roles; and, (iii) if there are over- and under-represented plant and floral visitor group combinations within a subgraph.
+Here we evaluate the interaction patterns of the meso-scale and its ecological implications in plant-pollinator networks with the help of 60 empirical networks from 18 different studies distributed across 14 different countries.
+For this, plants and pollinators were divided into functional groups that summarise their main life history strategies and the different networks were split into all their subgraph elements up to five nodes.
+First, based on previous knowledge showing the non random assembly of macro-scale mutualistic networks [@bascompte2003] and food webs [@dunne2002], we test the hypothesis that  the building blocks that constitute the meso-scale in plant-pollinator networks have a non-random structure of interactions with over- and under-represented subgraphs (i.e., motifs) that represent contrasting ecological roles.
+Second, because species relative abundances (i.e., neutral effects) are one of the main drivers of network macro-struture [@krishna2008; @suweis2013; @bartomeus2016], we hypothesise that neutral effects may also govern the interaction patterns of the meso-scale in plant-pollinator networks.
+Finally, we explore if plants and pollinators functional groups are associated with subgraph positions that imply distinct ecological roles and if there are over- and under-represented functional group combinations within the different network subgraphs.
 
@@
 To investigate the structure of the meso-scale in plant-pollinator networks, we gathered published plant-pollinator networks with worldwide distribution.
-Then, we classified the different plant and floral visitor species from these networks into groups that summarise their main life-history strategies.
-After, we calculated the normalised subgraph frequencies and investigated if these frequencies are similar or not to the ones expected by chance with the help of null models.
-Then, for each group of plants and floral visitors we investigated the ecological implications of their overall representation on the different subgraph positions, by comparing, on the one hand, the observed (normalised) frequencies of each group in the different subgraph positions with the frequencies of their simulated counterparts, and, on the other hand, the differences among the patterns of connections of subgraph positions.
-Finally, we compared if there are differences in the observed frequencies of subgraph combinations from empirical networks and the expected frequencies calculated as the product of the probabilities of the different plant and floral visitor groups within the network subgraph.
+Then, we classified the different plant and floral visitor species from these networks into functional groups that summarise their main life-history strategies.
+We calculated the normalised subgraph frequencies and investigated if these frequencies are similar or not to the ones expected by chance with the help of null models.
+Then, for each group of plants and floral visitors we investigated the ecological implications of their overall representation on the different subgraph positions, by comparing, on the one hand, the observed (normalised) frequencies of each group in the different subgraph positions with the frequencies of their simulated counterparts, and, on the other hand, the differences among groups per subgraph position in terms of their number of indirect interactions and specialisation.
+Finally, to understand if the different functional group combinations within a subgraph are structured, we compare if the observed functional group combinations from empirical networks can be retrieved from the joint probability distribution of the expected frequencies of the different plant and floral visitor groups within the network subgraph.
 
@@
 In total, there were 503 plant species, 1,111 floral visitors species and 6,248 pairwise interactions registered.
-For ease of data manipulation, plant and floral visitor species names were standardize with the help of the R package _taxize_ version _0.9.99_ [@chamberlain2020].
-All analyses and data manipulation were conducted in R _version 4.0.5_ [@R].
+For ease of data manipulation, plant and floral visitor species names were standardised with the help of the R package _taxize_ version _0.9.99_ [@chamberlain2020].
 
@@
 
-First, plant species were grouped through hierarchical clustering into the optimal number of functional groups that summarized the main plant reproductive strategies.
-For this, we used the plant trait dataset compiled in @lanuza2021 that consisted also of plant species that belonged to the same plant-pollinator networks plus some additional meta-networks not considered here in order to use just networks with similar sampling effort (e.g., unique location and flowering season).
+First, plant species were grouped through hierarchical clustering into the optimal number of functional groups that summarises the main plant reproductive strategies.
+For this, we used the plant trait dataset compiled in @lanuza2021 that consisted also of plant species that belonged to the same plant-pollinator networks plus some additional meta-networks not considered here.
 This dataset comprised a total of 1506 plant species including the 503 species considered in this study (Table S2).
 Because most of these plant species are likely to benefit from animal pollination, we used reproductive traits relevant to understand the different plant reproductive strategies and their interactions with pollinators.
-After excluding traits with high percentage of missing values (over 30$\%$), we ended up with 8 floral, 3 reproductive biology and 3 plant morphology traits (see Table S3 for a list of all traits).
+After excluding traits with a high percentage of missing values (over 30$\%$), we ended up with 8 floral, 3 reproductive biology and 3 plant morphology traits (see Table S3 for a list of all traits).
 Floral traits included those associated with the size, form and number of floral organs (e.g., style length or ovule number).
-Reproductive biology traits described the reproductive system of the plant (i.e., the breeding, mating and compatibility system) and plant morphology traits were associated with the size and form of the plant (i.e., plant height, lifespan and life form).
+Reproductive biology traits described the reproductive system of the plant (e.g., mating and compatibility systems) and plant morphology traits were associated with the size and form of the plant (i.e., plant height, lifespan and life form).
 After an extensive search for each plant species on several different resources (e.g., plant databases, online floras, books, journals and images), over 80% of the cells of the whole dataset were filled.
@@
 
-Second, floral visitors were aggregated into taxonomic groups based on taxonomic rank as done similarly in other plant-pollinator studies [@fenster2004; @ollerton2009].
+Second, floral visitors were aggregated into taxonomic groups (hereafter referred to as functional groups) based on taxonomic rank as done similarly in other plant-pollinator studies [@fenster2004; @ollerton2009].
 We opted to divide floral visitors on the taxonomic rank level and not with functional traits because the main orders of floral visitors differed in form and behaviour and had lower superior taxonomic complexity (i.e., floral visitors had 6 orders versus plants that had 38).
-Thus, this allowed us to group floral visitors into groups that represented approximately the main life strategies of the possible pollinators: (i) bees (Hymenoptera-Anthophila), (ii) non-bee Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Syrphidae-Diptera), (iv) non-syrphids-Diptera, (v) Lepidoptera and (vi) Coleoptera.
-However, a minor set of species belonged to other taxonomic groups that were considered in analyses but not discussed further because of their low representation in the full set of networks (3.55$\%$ of the total interactions recorded).
+Thus, this allowed us to group floral visitors into functional groups that represented approximately the main life strategies of the possible pollinators: (i) bees (Hymenoptera-Anthophila), (ii) non-bee Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Syrphidae-Diptera), (iv) non-syrphids-Diptera, (v) Lepidoptera and (vi) Coleoptera.
+However, a minor set of species belonged to other functional groups that were considered in analyses but not discussed further because of their low representation in the full set of networks (3.55$\%$ of the total interactions recorded).
 These taxonomic groups were 'lizards', 'birds' and 'other insects'.
-This last group was formed by a mix of uncommon insect taxa on the full set of networks.
+This last functional group was formed by a mix of uncommon insect taxa on the full set of networks.
 
@@
 Prior to analyses, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.
-This approach was preferred since quantitative subgraph analysis have been developed just recently and more work is needed to fully understand and interpret the information that they can convey [@simmons2020].
+This approach was preferred since quantitative subgraph analyses have been developed just recently and more work is needed to fully understand and interpret the information that they can convey [@simmons2020].
 All analyses were run considering singletons (species with only one interaction detected) but we conducted a second exploration without singletons (64.98$\%$ of interactions) to evaluate the effect of rare species on the observed patterns.
@@
 Note that the aim is not comparing different networks, which may differ in sampling effort, but correctly describing the structure of each individual network.
-Like @simmons2020, we classified the different subgraphs by their average path length (mean number of links between all pairs of nodes) into four different groups: (i) complete or strong ($\overline{x} = 1.38$), (ii) fan or medium-strong ($\overline{x} = 1.48$), (iii) assymmetric complete or medium-weak ($\overline{x} = 1.60$) and (iv) core-peripheral or weak ($\overline{x} = 1.85$), where $\overline{x}$ represents the mean of the average path length across subgraphs in the same group.
+Like @simmons2020, we classified the different subgraphs by their average path length (mean number of links between all pairs of nodes) into four different groups: (i) complete or strong ($\overline{x} = 1.38$), (ii) fan or medium-strong ($\overline{x} = 1.48$), (iii) assymmetric complete or medium-weak ($\overline{x} = 1.60$) and (iv) core-peripheral or weak ($\overline{x} = 1.85$), where $\overline{x}$ represents the mean of the average path length across subgraphs within the same group.
 In general terms, plant and floral visitor groups on more densely connected network subgraphs (e.g., complete or fan) will experience lower number of indirect interactions in contrast to groups on less densely connected structures (e.g., medium-weak or weak).
@@
 All possible network subgraphs from two to five species in bipartite networks grouped by the different subgraph classes (2-species, 3-species, 4-species and 5-species).
-There is a total of 17 possible subgraphs with 46 different positions denoted within each node.
+There are a total of 17 possible subgraphs with 46 different positions denoted within each node.
 The different subgraphs are aggregated by the broad indirect interaction structures they represent on four different groups (strong, medium-strong, medium-weak and weak).
@@
 Subgraphs whose percentile is close to 0 or 100 are under- or over-represented in empirical networks, respectively, and indicate the presence of network motifs as they differ statistically from the network structures generated with simulated networks.
-To summarize general patterns across networks, we used an intercept-only linear mixed model (LMM) per subgraph with the help of the _lme4_ package version _1.1-21_ [@bates2015], where the response variable was the observed subgraph percentile per network.
+To summarise general patterns across networks, we used an intercept-only linear mixed model (LMM) per subgraph with the help of the _lme4_ package version _1.1-21_ [@bates2015], where the response variable was the observed subgraph percentile per network.
 Note that as we are only interested in modelling the intercept value, no predictors were specified.
@@
 
-We calculated which plant and floral visitor groups were over- or under-represented in the different subgraph positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
+We calculated which plant and floral visitor functional groups were over- or under-represented in the different subgraph positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
 To estimate the position frequencies of each plant and floral visitor group in a given network, we added the frequencies of those species that belong to the same group, and then, we normalised the resulting frequencies by dividing them by the total number of times that a corresponding group appears in any position within the same subgraph size class (i.e., 2, 3, 4 or 5 species motifs).
-Then, we calculated the percentile of the observed position frequencies for each group and network, just like we did with subgraph frequencies.
+Then, we calculated the percentile of the observed position frequencies for each functional group and network, just like we did with subgraph frequencies.
 To outline the general patterns of position frequencies across networks and groups, we fit a LMM per subgraph position, where the response variable was the observed position percentile per network.
@@
 Hence, we assessed the average subgraph frequency per species group, after controlling for the variation at the study level.
-Finally, we visualized over- and under-representation of plant and floral visitor groups on the different subgraph positions with the help of the _ComplexHeatmap_ package version _2.6.2_ [@gu2016].
-
-To understand if the different plant and floral visitor groups are associated with subgraph positions that represent different network roles, we characterized the roles of each subgraph position for plant and floral visitor groups in terms of their specialisation and number of indirect interactions.
+Finally, we visualised over- and under-representation of plant and floral visitor groups on the different subgraph positions with the help of the _ComplexHeatmap_ package version _2.6.2_ [@gu2016].
+
+To understand if the different plant and floral visitor functional groups are associated with subgraph positions that represent different network roles, we characterised the roles of each subgraph position for the different functional groups in terms of their specialisation and number of indirect interactions.
 To that end, we calculated the specificity of each subgraph position following @poisot2015 as $s_i = (L - l_i) / (L - 1)$, where $L$ is the total number of groups and $l_i$ the number of interaction partners of the group $i$ in a given subgraph.
 Values of the vector $si$, range between 1, complete specialisation (1 partner within the subgraph) and 0 complete generalism (all possible partners within the subgraph).
-Then, because all nodes within a motif are connected, we calculated the number of indirect interactions ($n_i$) for each motif position as $n_i=z_i-k_i-1$, where $z_i$ is the total number of nodes in a given motif, and $k_i$ represents the degree of the corresponding motif position, that is, the total number of links connected to such position.
+Then, because all nodes within a motif are connected, we calculated the number of indirect interactions ($\theta_i$) for each motif position as $\theta_i=m_i-k_i-1$, where $m_i$ is the total number of nodes in a given motif, and $k_i$ represents the degree of the corresponding motif position, that is, the total number of links connected to such position.
 Thus, we considered all possible indirect interactions for each position.
-Finally, we analysed in a single model how specialization and the number of indirect interactions were associated with the observed percentiles for each trophic guild and subgraph position (see paragraph above).
-For this, we fitted a LMM model with the help again of the _lme4_ package where we considered specialization and number of indirect interactions as response variables with the interaction by plant and floral visitor group for both response variables.
+Finally, we analysed in a single model how specialisation and the number of indirect interactions were associated with the observed percentiles for each trophic guild and subgraph position (see paragraph above).
+For this, we fitted again a LMM model with the help of the _lme4_ package where we considered specialisation and number of indirect interactions as response variables with the interaction by plant and floral visitor group for both response variables.
 Further, we considered as random factor subgraph position nested within study system.
-All model diagnostics were conducted with the help of the _Dharma_ package [@hartig2017] version _0.3.3.0_ and model outputs were visualized with the _visreg_ package [@breheny2020] version 2.7.0.
-Finally, to verify that different levels of richness across plant and floral visitor groups are not driving the overall results of indirect interactions and specialization, we conducted the analogous analyses for 1000 random samples of the 60% of the networks.
-We found consistent results that indicate that different richness across groups have negligible effects on the overall patterns [WORK ON THIS]().
 
@@
 
-Finally, we studied which combinations of plant and floral visitor groups tend to appear together within the same subgraphs (up to five nodes).
+Finally, we studied which combinations of plant and floral visitor functional groups tend to appear together within the same subgraphs (up to five nodes).
 That is, which combinations are over- or under-represented.
@@
 To calculate the observed probability ($p_i^O$) of the different groups within a subgraph $i$ (e.g., subgraph 3, 'bee' + 'bee' + 'selfing herbs'), we divided the number of times that $i$ appears in our set of empirical networks ($n_i^O$) by the sum of the number of times that each possible combination appeared: $p_i^O = n_i^O / \sum_{k=1}^{53,250} n_k^O$.
-To estimate the expected probability ($p_i^E$) of a given subgraph combination $i$, we assumed that the probability of finding a given group $x$ in the position $\alpha$ is independent of the probabilities associated with other positions and groups in that subgraph.
-Therefore, the expected probability ($p_i^E$) of the subgraph combination $i$ is given by the product of the probabilities of its constituents, i.e., $p_i^E = \prod _{(x,\alpha )\in i} p_i(x,\alpha)$, where $p_i(x,\alpha)$ is the probability of finding a given group $x$ in the position $\alpha$ of $i$.
-Then, by controlling for the variation at the network level with an LMM (see below), we calculated the average number of times that the group $x$ appears in the position $\alpha$ (denoted as $n_i(x,\alpha)$).
-To obtain the expected probability $p_i(x,\alpha)$ we divided the number of times that the group $x$ appears in the position $\alpha$ by the the total number of times that any group was observed in that position (that is, $p_i(x,\alpha) = n_i(x,\alpha)/\sum_{k}n_i(k,\alpha)$).
+To estimate the expected probability ($p_i^E$) of a given subgraph combination $i$, we assumed that the probability of finding a given functional group $x$ in the position $\alpha$ is independent of the probabilities associated with other positions and groups in that subgraph.
+Therefore, the expected probability ($p_i^E$) of the subgraph combination $i$ is given by the product of the probabilities of its constituents, i.e., $p_i^E = \prod _{(x,\alpha )\in i} p_i(x,\alpha)$, where $p_i(x,\alpha)$ is the probability of finding a given functional group $x$ in the position $\alpha$ of $i$.
+Then, by controlling for the variation at the network level with an LMM (see below), we calculated the average number of times that the functional group $x$ appears in the position $\alpha$ (denoted as $n_i(x,\alpha)$).
+To obtain the expected probability $p_i(x,\alpha)$, we divided the number of times that the group $x$ appears in the position $\alpha$ by the the total number of times that any group was observed in that position (that is, $p_i(x,\alpha) = n_i(x,\alpha)/\sum_{k}n_i(k,\alpha)$).
 The average number of times that the group $x$ appears in the position $\alpha$ ($n_i(x,\alpha)$) was calculated with a LMM for each position, where the response variable was the number of times that a group was observed at a given position in each real-world network, the explanatory variable was the group identifier, and the random intercept was given by network identifiers nested within the study identifiers.
@@
 
+All analyses and data manipulation were conducted in R _version 4.0.5_ [@R].
+In addition, all model diagnostics were conducted with the help of the _Dharma_ package [@hartig2017] version _0.3.3.0_ and model outputs were visualised with the _visreg_ package [@breheny2020] version 2.7.0.
+
 # RESULTS
 
-**Plant and floral visitor groups**
-
-The hierarchical cluster analysis divided the dataset into five different groups with different and overlapping characteristics (Figs S4 and S5).
+**Plant and floral visitor functional groups**
+
+The hierarchical cluster analysis divided the dataset into five different plant functional groups with different and overlapping characteristics (Figs S6 and S7).
 The first group referred to as 'selfing herbs' consisted of herbs with hermaphroditic flowers with high levels of autonomous selfing.
-The second group named 'small outcrossing perennials' had small perennial species with a mix of life forms (i.e., trees shrubs and herbs) with outcrossing hermaphroditic flowers.
+The second group named 'small outcrossing perennials' had small perennial species with a mix of life forms (i.e., trees, shrubs and herbs) with outcrossing hermaphroditic flowers.
 The third group referred to as 'self-incompatible perennials with large flowers' comprised perennial species with a mixed of life forms and large self-incompatible hermaphroditic flowers with high number of ovules.
@@
 
-The comparison of the plant and floral visitor group frequencies per subgraph position between empirical and simulated networks showed a `r over`$\%$ and `r under`$\%$ of over- (>75$^{th}$) and under-represented (<25th) groups in the different positions, respectively (Fig.
+The comparison of the plant and floral visitor functional group frequencies per subgraph position between empirical and simulated networks showed a `r over`$\%$ and `r under`$\%$ of over- (>75$^{th}$) and under-represented (<25th) groups in the different positions, respectively (Fig.
 3).
@@
 3), we found: bees, non-syrphids Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.
-Although plant functional groups showed less differences between them, there were also more represented groups than others, thus from most over- to under-represented groups on the different subgraph positions we found: self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.
+Although plant functional groups showed less differences between them, there were also more represented groups than others, thus from most over- to under-represented functional groups on the different subgraph positions we found: self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.
 
 For both floral visitor and plant groups we found over- and under-representation on different subgraph positions that implied different ecological roles.
-First, for floral visitors, we found that bees were less frequent on subgraph positions that involved specialization (i.e., lower specificity values) while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) were infrequent in generalised subgraph positions with low number of indirect interactions (Fig.
-S6 A).
-Although plants did not show differences with null models on their frequencies, all plant but tall plants with small unisexual flowers showed a slight tendency to be over-represented on specialised subgraph positions (Fig.
-S6 B).
+First, for floral visitors, we found that bees were less frequent on subgraph positions that involved specialisation (i.e., lower specificity values) while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) were infrequent in generalised subgraph positions with low number of indirect interactions (Fig.
+S8 A).
+Although plants did not show differences with null models on their frequencies, all plant groups but tall plants with small unisexual flowers showed a slight tendency to be over-represented on specialised subgraph positions (Fig.
+S8 B).
 Second, regarding the number of indirect interactions, bees were over-represented in subgraph positions with low number of indirect interactions (Fig.
-S7 A) and the rest of floral visitor groups showed no differences across positions in comparison with simulated networks.
-For plants, all groups showed a slight trend to be over-represented on subgraph positions with higher number of indirect interactions (Fig.
-S7 B).
-When we further explore the observed frequencies by number of indirect interactions for floral visitor and plant groups, we found that both bees and tall plants with small unisexual flowers were the only groups with high frequencies on subgraph positions associated with low number interactions in comparison with the other floral visitor and plant groups (Figs S8 and S9).
+S9 A) and the rest of floral visitor functional groups showed no differences across positions in comparison with simulated networks.
+For plants, all functional groups showed a slight trend to be over-represented on subgraph positions with higher number of indirect interactions (Fig.
+S9 B).
+When we further explore the observed frequencies by number of indirect interactions for floral visitor and plant functional groups, we found that both bees and tall plants with small unisexual flowers were the only groups with high frequencies on subgraph positions associated with low number interactions in comparison with the other floral visitor and plant functional groups (Figs S10 and S11).
 
@@
 
-**Over- and under-represented group combinations of subgraphs**
+**Over- and under-represented functional group combinations of subgraphs**
 
@@
 4).
-That is, the taxonomic group of 'bees' was the most abundant one on all subgraph positions followed by non-syrphid Diptera which was after bees, the second most frequent group on all positions.
-Then, the group of syrphids was the most abundant in all positions but two (positions 28 and 31 from motifs 11 and 12, respectively).
-After syrphids, Coleoptera was the most frequent group on the different positions followed by non-bee Hymenoptera and finally, Lepidoptera which was the less frequent group on all positions but two (positions 12 and 22 from motifs 5 and 9, respectively).
-Remarkably, plant functional groups were more variable on the different subgraph positions.
+From the highest to lowest observed probabilities overall, we found: bees, non-syrphid Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.
+On the contrary, plant functional groups were more variable on the different subgraph positions.
 However, there were also predominant functional groups found across the different subgraph positions.
@@
 Finally, 5 node subgraphs were in similar proportions in the no statistical difference and over-represented categories (99$\%$ and 97$\%$, respectively) but they appeared in lower proportion in the under-represented category (89$\%$).
-When we explored the identity on the different positions of the most probable subgraph combinations we found that the most common plant and floral visitor groups were also the most probable on these subgraph combinations (lower panel Fig.
+When we explored the identity on the different positions of the most probable subgraph combinations we found that the most common plant and floral visitor functional groups were also the most probable on these plant and floral visitor combinations within the different subgraphs (lower panel Fig.
 5).
@@
 Understanding the global patterns of network structure is key to unravel the processes that govern community dynamics [@bascompte2007; @bastolla2009; @guimaraes2020].
-However, common analytical approaches at the node or at the full network level are unable to capture the full complexity of ecological systems [@simmons2019; @bergamo2021].
+However, common analytical approaches at the node or at the global network level are unable to capture the full complexity of ecological systems [@simmons2019; @bergamo2021].
 Because network subgraphs can capture both direct and indirect interactions, by analysing their over- and under-representation we were able to explore in great detail the structure of interactions between animal pollinators and the plants they visit.
 We have explored for the first time the overall structure and presence of network motifs in real plant-pollinator networks and shown that the different subgraphs up to five nodes are consistently over- or under-represented in comparison with simulated networks.
-Despite the presence of multiple ecological processes (e.g., neutral effects, morphological matching or phenological overlap) shaping the meso-scale, we found a tendency for over-represented motifs that were more densely connected (i.e., complete, fan and asymmetric complete).
-As suggested in @simmons2020, a higher proportion of these densely connected motifs could reflect that neutral effects are the predominant ecological process governing the structure of the meso-scale.
-Thus, as indicated for other network properties like nestedness at the macro-scale level [@krishna2008; @suweis2013], or interaction probability at the species level [@bartomeus2016], species relative abundances (i.e., neutral effects) may be also the main driver governing this intermediate level of complexity on plant-pollinator networks.
-
-Overall, generalist network motifs for floral visitors were consistently over-represented (e.g., fan-type subgraphs; Fig.
+In addition, we show that for plant-pollinator networks there is a general tendency for over-representation of network subgraphs that are more densely connected (i.e., complete, fan and asymmetric complete).
+Indeed, the work of @simmons2020 has shown with the help of simulated plant-pollinator networks that the main different processes that shape plant-pollinator communities (i.e., neutral effects, trait matching and phenology) generate different patterns of direct and indirect interactions, and that specifically, a higher proportion of these more densely connected subgraphs is associated with neutral effects.
+Therefore, as indicated for other network properties like nestedness at the macro-scale level [@krishna2008; @suweis2013], or interaction probability at the species level [@bartomeus2016], our findings indicate that neutral effects may be also the main driver governing this intermediate level of complexity on plant-pollinator networks.
+
+Overall, generalist network motifs for floral visitors were consistently over-represented (e.g., complete subgraphs; Fig.
 2).
@@
 This large effect of bees on the overall patterns is no surprise, as bees were the group with the largest number of interaction records in the whole set of networks as also shown for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017].
-Interestingly, bees also were the group with lower number of indirect interactions while the rest of floral visitor groups showed clearly higher number of indirect interactions indicating that these non-bee floral visitor groups may experience higher competitive interactions for floral resources [@thomson2020].
+Interestingly, bees also were the group with lower number of indirect interactions while the rest of floral visitor groups showed a clearly higher number of indirect interactions indicating that these non-bee floral visitor groups may experience higher competitive interactions for floral resources [@thomson2020].
 Despite plant functional groups showed little differences between them on their subgraph frequencies, all groups showed a tendency to be over-represented on subgraph positions that were associated with higher levels of specialisation.
@@
 This implies that not just the representation of network subgraphs types but also the identity of the elements of their structure is non-random.
-Notably, we found that just 30$\%$ of the possible 53,250 subgraph combinations are realized.
+Notably, we found that just 30$\%$ of the possible 53,250 subgraph combinations are realised.
 Thus, similarly to the presence of forbidden links at the network level [@olesen2011; @jordano2016], we also found the existence of forbidden subgraph positions and those represented almost two thirds of the total possible subgraph combinations.
 This concurs well with the general idea that plant-pollinator networks have a high proportion of non-realized direct interactions [@jordano2003; @bascompte2013], and as a result, also a high proportion of non-realized combinations of indirect interactions.
-Some of this non-observed direct interactions are probably due to under-sampling [@dorado2011; @jordano2016].
+Some of these non-observed direct interactions are probably due to under-sampling [@dorado2011; @jordano2016].
 However, a large fraction of the possible interactions do not take place because of life-history constraints such as species co-occurrence, trait matching processes and phenological uncoupling [@olesen2011; @bartomeus2016; @jordano2016].
-Despite the advances in the understanding on the ecological processes that influence species pairwise interactions [@bartomeus2016; @peralta2020], we still know little about how these processes determine competitive and facilitative interactions in mutualistic networks.
-Thus, as suggested by @simmons2020, exploring the proportion of these realized network subgraphs that are competitive or facilitative is a necessary next step to improve our understanding of the architecture of biodiversity [@bascompte2007].
-
-Despite the obvious usefulness of functional groups in summarizing species ecological roles (e.g., similar reproductive biology for plants and behaviour for pollinators), delimiting species into functional groups is often not trivial.
+Despite the advances in the understanding of the ecological processes that influence species pairwise interactions [@bartomeus2016; @peralta2020], we still know little about how these processes determine competitive and facilitative interactions in mutualistic networks.
+Thus, as suggested by @simmons2020, exploring the proportion of these realised network subgraphs that are competitive or facilitative is a necessary next step to improve our understanding of the architecture of biodiversity [@bascompte2007].
+
+Despite the obvious usefulness of functional groups in summarising species ecological roles (e.g., similar reproductive biology for plants and behaviour for pollinators), delimiting species into functional groups is often not trivial.
 For instance, taxonomic diversity and trait availability limit our ability to properly represent the wide range of reproductive strategies [@dellinger2020] and different clustering analysis can lead to distinct outcomes (e.g., k-means and hierarchical clustering).
-Further, here we divided floral visitors on the taxonomic rank level because it represented adequately pollinator ecological roles without the tremendous effort of compiling trait data for over 1000 species of floral visitors.
-However, further groupings with traits could help revealing greater relevance of trait-matching processes on indirect interactions.
-We believe that this could be investigated by exploring which proportion of over- and under-represented motifs present high and low trait-matching, respectively.
-Moreover, we analysed network subgraphs focusing exclusively on presence-absence interactions which assume that all interactions are equally important as suggested by @simmons2020, further work should investigate how to account for the quantitative measurements of the strength of plant-pollinator interactions.
-Finally, despite the wide geographical coverage of our plant-pollinator dataset, there are major gaps for some regions of the world with a clear bias towards Europe, America and islands which have long interested ecologist [@macarthur1963; @warren2015].
+We divided floral visitors on the taxonomic rank level because it adequately represented pollinator ecological roles without the tremendous effort of compiling trait data for over 1000 species of floral visitors.
+Indeed, further groupings with traits could help reveal greater relevance of trait-matching processes on indirect interactions.
+Moreover, we analysed network subgraphs focusing exclusively on presence or absence of interactions assuming that all interactions are equally important but further work should investigate how to account for the quantitative measurements of the strength of plant-pollinator interactions.
+Consistent with previous work [@simmons2019; @simmons2020], we characterised network motifs by using null models only constrained for network connectance.
+Although more complex null models are difficult to interpret [@Ulrich2013], they can potentially allow us to separate the mechanisms by which motifs emerge.
+However, we found that null models with more constraints were computationally unfeasible and that connectance, nestedness and degree distribution were significantly correlated (data not shown).
+We highlight the difficulties to explore the potential sources that generate over-representation of network subgraphs and the need to investigate them.
+At the same time, although network subgraphs can capture both direct and indirect interactions, the reduction of network complexity into these different building blocks inevitably convey the loss of information [@simmons2019], for example indirect interactions from large cascading effects.
+Our work explores only interactions between plants and pollinators but a multitrophic context is indeed needed to fully understand community dynamics [@knight2005].
+Finally, despite the wide geographical coverage of our plant-pollinator dataset, there are major gaps for some regions of the world with a clear bias towards Europe, America and islands which have long interested ecologists [@macarthur1963; @warren2015].
 These biases are also found in global datasets of networks where the data is highly fragmented across space [@poisot2021] and more efforts are needed to capture global patterns of plant-pollinator interactions.
@@
 In conclusion, by following the framework of @simmons2020 we have been able to explore competitive and facilitative interactions in plant-pollinator networks worldwide and found the presence of worldwide motifs that highlight the non-random structure of indirect interactions.
-Further, we found that plant and floral visitor groups are associated with different subgraph positions that involve distinct ecological roles (e.g., generalisation versus specialisation) and that the different subgraph combinations are strongly constrained.
-Although we are still far to predict how species interact, our work is a first step to elucidate beyond pairwise interactions.
+This non-random structure might emerge due to neutral effects according to previous modelling work [@simmons2020].
+Further, we found that plant and floral visitor functional groups are associated with different subgraph positions that involve distinct ecological roles (e.g., generalisation versus specialisation) and that the different subgraph combinations are strongly constrained.
+Although we are still far from predicting how species interact, our work is a first step to elucidate beyond pairwise interactions.
 
@@
 
-IB, AA-P and JBL designed the idea. JBL collected the data. AA-P lead the analysis with contributions of JBL and guidance of IB. JBL wrote the manuscript with contributions of IB and AA-P.
+IB, AA-P and JBL designed the idea. JBL collected the data. AA-P led the analysis with contributions of JBL and guidance of IB. JBL wrote the manuscript with contributions of IB and AA-P.
 

### 2022-10-07 Manuscript/Main_text/Main_text_Journal_of_Animal_Ecol.Rmd
supp mat update

@@
 
-__Jose B. Lanuza^1,2^__  | __Alfonso Allen-Perkins^2,3^__ | __Ignasi Bartomeus^2^__
+**Jose B. Lanuza^1,2^** \| **Alfonso Allen-Perkins^2,3^** \| **Ignasi Bartomeus^2^**
 
@@
 In addition, we found a higher proportion of densely connected network subgraphs that, based on previous findings, could reflect that species relative abundances are the main driver shaping the structure of the meso-scale on plant-pollinator communities.
-Moreover, we found that distinct subgraph positions describing species ecological roles (e.g., generalisation and number of indirect interactions) are occupied by different groups of animal and plant species representing their main life history strategies (i.e., functional groups).
-For instance, we found that the functional group of ‘bees’ was over-represented in subgraph positions with a lower number of indirect interactions in contrast to the rest of floral visitors groups.
+Moreover, we found that distinct subgraph positions describing species ecological roles (e.g., generalisation and number of indirect interactions) are occupied by different groups of animal and plant species representing their main life-history strategies (i.e., functional groups).
+For instance, we found that the functional group of 'bees' was over-represented in subgraph positions with a lower number of indirect interactions in contrast to the rest of floral visitors groups.
 Finally, we show that the observed functional group combinations within a subgraph can not be retrieved from their expected probabilities (i.e., joint probability distributions), indicating that plant and floral visitor associations within subgraphs are not random either.
@@
 However, as previously explored with three species modules in unipartite food webs [@allesina2008; @stouffer2010], the emergent framework of bipartite subgraphs has proven to be a powerful analytical tool to better understand plant-pollinator community dynamics by capturing both direct and indirect effects [@simmons2019].
-These network subgraphs that constitute the meso-scale are often referred to as the building blocks of the network and when their numbers occur at higher frequencies than in randomised networks, those are generally defined as ‘network motifs’ [@milo2002].
+These network subgraphs that constitute the meso-scale are often referred to as the building blocks of the network and when their numbers occur at higher frequencies than in randomised networks, those are generally defined as 'network motifs' [@milo2002].
 Indeed, the analysis of motifs in simulated plant-pollinator networks has revealed that the different drivers that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect effects [@simmons2020].
@@
 Here we evaluate the interaction patterns of the meso-scale and its ecological implications in plant-pollinator networks with the help of 60 empirical networks from 18 different studies distributed across 14 different countries.
-For this, plants and pollinators were divided into functional groups that summarise their main life history strategies and the different networks were split into all their subgraph elements up to five nodes.
+For this, plants and pollinators were divided into functional groups that summarise their main life-history strategies and the different networks were split into all their subgraph elements up to five nodes.
 First, based on previous knowledge showing the non random assembly of macro-scale mutualistic networks [@bascompte2003] and food webs [@dunne2002], we test the hypothesis that the building blocks that constitute the meso-scale in plant-pollinator networks have a non-random structure of interactions with over- and under-represented subgraphs (i.e., motifs) that represent contrasting ecological roles.
@@
 Then, for each group of plants and floral visitors we investigated the ecological implications of their overall representation on the different subgraph positions, by comparing, on the one hand, the observed (normalised) frequencies of each group in the different subgraph positions with the frequencies of their simulated counterparts, and, on the other hand, the differences among groups per subgraph position in terms of their number of indirect interactions and specialisation.
-Finally, to understand if the different functional group combinations within a subgraph are structured, we compare if the observed functional group combinations from empirical networks can be retrieved from the joint probability distribution of the expected frequencies of the different plant and floral visitor groups within the network subgraph.
+Finally, to understand if the different functional group combinations within a subgraph are structured, we compare if the observed functional group combinations from empirical networks can be retrieved from the joint probability distribution of the expected frequencies of the different plant and floral visitor groups within network subgraphs.
 
@@
 In total, there were 503 plant species, 1,111 floral visitors species and 6,248 pairwise interactions registered.
-For ease of data manipulation, plant and floral visitor species names were standardised with the help of the R package _taxize_ version _0.9.99_ [@chamberlain2020].
-
-**Plant and floral visitor groups**
+For ease of data manipulation, plant and floral visitor species names were standardised with the help of the R package *taxize* version *0.9.99* [@chamberlain2020].
+
+**Plant and floral visitor functional groups**
 
@@
 To feed the clustering analysis, we calculated the distance between the different qualitative and scaled quantitative variables with Gower distance [@gower1971].
-For this, we used the function _gowdis_ with method _ward.D2_ from the _FD_ package version _1.0-12_ [@laliberte2014].
-Finally, we conducted hierarchical clustering with the function _hclust_ from the _R_ stats package version _4.0.5_ and calculated the optimal number of clusters with the function _kgs_ from the _maptree_ package version _1.4-7_ [@white2009].
+For this, we used the function *gowdis* with method *ward.D2* from the *FD* package version *1.0-12* [@laliberte2014].
+Finally, we conducted hierarchical clustering with the function *hclust* from the *R* stats package version *4.0.5* and calculated the optimal number of clusters with the function *kgs* from the *maptree* package version *1.4-7* [@white2009].
 
@@
 We opted to divide floral visitors on the taxonomic rank level and not with functional traits because the main orders of floral visitors differed in form and behaviour and had lower superior taxonomic complexity (i.e., floral visitors had 6 orders versus plants that had 38).
-Thus, this allowed us to group floral visitors into functional groups that represented approximately the main life strategies of the possible pollinators: (i) bees (Hymenoptera-Anthophila), (ii) non-bee Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Syrphidae-Diptera), (iv) non-syrphids-Diptera, (v) Lepidoptera and (vi) Coleoptera.
+Thus, this allowed us to group floral visitors into functional groups that represented approximately the main life-history strategies of the possible pollinators: (i) bees (Hymenoptera-Anthophila), (ii) non-bee Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Syrphidae-Diptera), (iv) non-syrphids-Diptera, (v) Lepidoptera and (vi) Coleoptera.
 However, a minor set of species belonged to other functional groups that were considered in analyses but not discussed further because of their low representation in the full set of networks (3.55$\%$ of the total interactions recorded).
@@
 We calculated the frequency of all subgraphs up to five nodes (17 different subgraphs in total; see Fig.
-1) for each empirical network, by using the _bmotif_ package version _2.0.2_ [@bmotifsimmons2019].
+1) for each empirical network, by using the *bmotif* package version *2.0.2* [@bmotifsimmons2019].
 We focused exclusively on subgraphs up to five nodes in our analyses for computational reasons and for the ease of visualization and interpretation of a reduced set of less complex network structures.
@@
 
-To assess the significance of the observed frequencies, we created 1,000 simulated networks for each binary network using the _nullmodel_ function and the _vaznull_ model in the _bipartite_ package version _2.14_ [@dormann2009].
+To assess the significance of the observed frequencies, we created 1,000 simulated networks for each binary network using the *nullmodel* function and the *vaznull* model in the *bipartite* package version *2.14* [@dormann2009].
 Generated networks had the same number of plants and floral visitors, as well as the same connectance of their corresponding empirical networks.
@@
 Subgraphs whose percentile is close to 0 or 100 are under- or over-represented in empirical networks, respectively, and indicate the presence of network motifs as they differ statistically from the network structures generated with simulated networks.
-To summarise general patterns across networks, we used an intercept-only linear mixed model (LMM) per subgraph with the help of the _lme4_ package version _1.1-21_ [@bates2015], where the response variable was the observed subgraph percentile per network.
+To summarise general patterns across networks, we used an intercept-only linear mixed model (LMM) per subgraph with the help of the *lme4* package version *1.1-21* [@bates2015], where the response variable was the observed subgraph percentile per network.
 Note that as we are only interested in modelling the intercept value, no predictors were specified.
@@
 
-**Over- and under-represented groups on subgraph positions**
+**Over- and under-represented functional groups on subgraph positions**
 
@@
 Hence, we assessed the average subgraph frequency per species group, after controlling for the variation at the study level.
-Finally, we visualised over- and under-representation of plant and floral visitor groups on the different subgraph positions with the help of the _ComplexHeatmap_ package version _2.6.2_ [@gu2016].
+Finally, we visualised over- and under-representation of plant and floral visitor groups on the different subgraph positions with the help of the *ComplexHeatmap* package version *2.6.2* [@gu2016].
 
@@
 Finally, we analysed in a single model how specialisation and the number of indirect interactions were associated with the observed percentiles for each trophic guild and subgraph position (see paragraph above).
-For this, we fitted again a LMM model with the help of the _lme4_ package where we considered specialisation and number of indirect interactions as response variables with the interaction by plant and floral visitor group for both response variables.
+For this, we fitted again a LMM model with the help of the *lme4* package where we considered specialisation and number of indirect interactions as response variables with the interaction by plant and floral visitor group for both response variables.
 Further, we considered as random factor subgraph position nested within study system.
 
-**Over- and under-represented group combinations of subgraphs**
+**Over- and under-represented functional group combinations of subgraphs**
 
@@
 
-All analyses and data manipulation were conducted in R _version 4.0.5_ [@R].
-In addition, all model diagnostics were conducted with the help of the _Dharma_ package [@hartig2017] version _0.3.3.0_ and model outputs were visualised with the _visreg_ package [@breheny2020] version 2.7.0.
+All analyses and data manipulation were conducted in R *version 4.0.5* [@R].
+In addition, all model diagnostics were conducted with the help of the *Dharma* package [@hartig2017] version *0.3.3.0* and model outputs were visualised with the *visreg* package [@breheny2020] version 2.7.0.
 
@@
 In addition, network subgraphs 2, 6, 7, 16 and 17 were over-represented, all over the 75th percentile.
-In contrast to the under-represented motifs, over-represented motifs belonged to the two shortest path length groups (i.e., complete and fan).
+In contrast to the under-represented network subgraphs, over-represented subgraphs belonged to the two shortest path length groups (i.e., complete and fan).
 The remaining network subgraphs (i.e., 4, 8, 11, 12, 13, and 15) were between the 25th and 75th percentile.
@@
 
-labels <- c("2" = "*Motif 2* <img src='../../Images/motif_2.png' width='22'/>" ,
-          "3"= "*Motif 3* <img src='../../Images/motif_3.png' width='22'/>",
-          "4"= "*Motif 4* <img src='../../Images/motif_4.png' width='22'/>",
-          "5"= "*Motif 5* <img src='../../Images/motif_5.png' width='22'/>",
-          "6"= "*Motif 6* <img src='../../Images/motif_6.png' width='22'/>",
-          "7"= "*Motif 7* <img src='../../Images/motif_7.png' width='22'/>",
-          "8"= "*Motif 8* <img src='../../Images/motif_8.png' width='22'/>",
-          "9"= "*Motif 9* <img src='../../Images/motif_9.png' width='22'/>",
-          "10"= "*Motif 10* <img src='../../Images/motif_10.png' width='22'/>",
-          "11"= "*Motif 11* <img src='../../Images/motif_11.png' width='22'/>",
-          "12"= "*Motif 12* <img src='../../Images/motif_12.png' width='22'/>",
-          "13"= "*Motif 13* <img src='../../Images/motif_13.png' width='22'/>",
-          "14"= "*Motif 14* <img src='../../Images/motif_14.png' width='22'/>",
-          "15"= "*Motif 15* <img src='../../Images/motif_15.png' width='22'/>",
-          "16"= "*Motif 16* <img src='../../Images/motif_16.png' width='22'/>",
-          "17"= "*Motif 17* <img src='../../Images/motif_17.png' width='22'/>")
+labels <- c("2" = "*Subgraph 2* <img src='../../Images/motif_2.png' width='22'/>" ,
+          "3"= "*Subgraph 3* <img src='../../Images/motif_3.png' width='22'/>",
+          "4"= "*Subgraph 4* <img src='../../Images/motif_4.png' width='22'/>",
+          "5"= "*Subgraph 5* <img src='../../Images/motif_5.png' width='22'/>",
+          "6"= "*Subgraph 6* <img src='../../Images/motif_6.png' width='22'/>",
+          "7"= "*Subgraph 7* <img src='../../Images/motif_7.png' width='22'/>",
+          "8"= "*Subgraph 8* <img src='../../Images/motif_8.png' width='22'/>",
+          "9"= "*Subgraph 9* <img src='../../Images/motif_9.png' width='22'/>",
+          "10"= "*Subgraph 10* <img src='../../Images/motif_10.png' width='22'/>",
+          "11"= "*Subgraph 11* <img src='../../Images/motif_11.png' width='22'/>",
+          "12"= "*Subgraph 12* <img src='../../Images/motif_12.png' width='22'/>",
+          "13"= "*Subgraph 13* <img src='../../Images/motif_13.png' width='22'/>",
+          "14"= "*Subgraph 14* <img src='../../Images/motif_14.png' width='22'/>",
+          "15"= "*Subgraph 15* <img src='../../Images/motif_15.png' width='22'/>",
+          "16"= "*Subgraph 16* <img src='../../Images/motif_16.png' width='22'/>",
+          "17"= "*Subgraph 17* <img src='../../Images/motif_17.png' width='22'/>")
 
@@
 
-The comparison of the plant and floral visitor functional group frequencies per subgraph position between empirical and simulated networks showed a `r over`$\%$ and `r under`$\%$ of over- (>75$^{th}$) and under-represented (<25th) groups in the different positions, respectively (Fig.
+The comparison of the plant and floral visitor functional group frequencies per subgraph position between empirical and simulated networks showed a `r over`$\%$ and `r under`$\%$ of over- (>75$^{th}$) and under-represented (\<25th) functional groups in the different positions, respectively (Fig.
 3).
-Floral visitors showed a total of `r poll_over_75`$\%$ and `r poll_under_25`$\%$ of over- and under-represented groups in the different positions and plants `r plant_over_75`$\%$ and `r plant_under_25`$\%$ of over- and under-represented groups, respectively.
-Notably, the differences across groups were more marked for floral visitors than for plant groups (the differences between min and max percentiles per position were generally two-three times larger for floral visitors).
-From most over- to under-represented floral visitors groups on the different subgraph positions (indicated with the dendrogram order in Fig.
+Floral visitors showed a total of `r poll_over_75`$\%$ and `r poll_under_25`$\%$ of over- and under-represented functional groups in the different positions and plants `r plant_over_75`$\%$ and `r plant_under_25`$\%$ of over- and under-represented functional groups, respectively.
+Notably, the differences across functional groups were more marked for floral visitors than for plants (the differences between min and max percentiles per position were generally two-three times larger for floral visitors).
+From most over- to under-represented floral visitors functional groups on the different subgraph positions (indicated with the dendrogram order in Fig.
 3), we found: bees, non-syrphids Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.
-Although plant functional groups showed less differences between them, there were also more represented groups than others, thus from most over- to under-represented functional groups on the different subgraph positions we found: self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.
-
-For both floral visitor and plant groups we found over- and under-representation on different subgraph positions that implied different ecological roles.
-First, for floral visitors, we found that bees were less frequent on subgraph positions that involved specialisation (i.e., lower specificity values) while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) were infrequent in generalised subgraph positions with low number of indirect interactions (Fig.
+Although plant functional groups showed less differences between them, there were also more represented functional groups than others, thus from most over- to under-represented functional groups on the different subgraph positions we found: self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.
+
+For both floral visitor and plant functional groups we found over- and under-representation on different subgraph positions that implied different ecological roles.
+First, for floral visitors, we found that bees were less frequent on subgraph positions that involved specialisation (i.e., lower specificity values) while the rest of functional groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) were infrequent in generalised subgraph positions with low number of indirect interactions (Fig.
 S8 A).
-Although plants did not show differences with null models on their frequencies, all plant groups but tall plants with small unisexual flowers showed a slight tendency to be over-represented on specialised subgraph positions (Fig.
+Although plants did not show differences with null models on their frequencies, all plant functional groups but tall plants with small unisexual flowers showed a slight tendency to be over-represented on specialised subgraph positions (Fig.
 S8 B).
@@
 S9 A) and the rest of floral visitor functional groups showed no differences across positions in comparison with simulated networks.
-For plants, all functional groups showed a slight trend to be over-represented on subgraph positions with higher number of indirect interactions (Fig.
+For plants, all functional groups showed a slight tendency to be over-represented on subgraph positions with higher number of indirect interactions (Fig.
 S9 B).
-When we further explore the observed frequencies by number of indirect interactions for floral visitor and plant functional groups, we found that both bees and tall plants with small unisexual flowers were the only groups with high frequencies on subgraph positions associated with low number interactions in comparison with the other floral visitor and plant functional groups (Figs S10 and S11).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', out.width="80%",fig.cap="\\textbf{Figure 3.} Heatmap indicating under- and over-representation of floral visitor and plant groups in the different subgraph positions (numbers on the right of each heatmap).
+When we further explore the observed frequencies by number of indirect interactions for floral visitor and plant functional groups, we found that both bees and tall plants with small unisexual flowers were the only functional groups with high frequencies on subgraph positions associated with low number interactions in comparison with the other floral visitor and plant functional groups (Figs S10 and S11).
+
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', out.width="80%",fig.cap="\\textbf{Figure 3.} Heatmap indicating under- and over-representation of floral visitor and plant functional groups in the different subgraph positions (numbers on the right of each heatmap).
 The different subgraph positions are dividied by the average path length clasification determined by Simmons et al.
 (2020) and they are ordered from the most densely connected network structures (strong or complete) to the less connected ones (weak or core-peripheral).
-The superior dendrogram indicates the differences across groups with the more separated groups showing larger differences."}
+The superior dendrogram indicates the differences across functional groups with the more separated groups showing larger differences."}
 
@@
 
-The different observed frequencies on the different subgraph positions showed a hierarchical order of probabilities for floral visitors (Fig.
+The different observed frequencies on the different subgraph positions showed a hierarchical order of probabilities for floral visitor functional groups (Fig.
 4).
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 4.** Graphical representation of the probability of finding a given plant and floral visitor group $x$ in the position $\\alpha$ of motif $i$, $p_i(x,\\alpha)$, for all the possible network subgraphs from two to five species in bipartite networks.
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 4.** Graphical representation of the probability of finding a given plant and floral visitor functional group $x$ in the position $\\alpha$ of motif $i$, $p_i(x,\\alpha)$, for all the possible network subgraphs from two to five species in bipartite networks.
 The slices in the nodes for a given functional group $x$ are proportional to the corresponding value of $p_i(x,\\alpha)$."}
@@
 
-The statistical comparison with z-scores between the observed and expected plant and floral visitor group combinations showed that we can not recover the observed combinations from its probability of occurrence.
+The statistical comparison with z-scores between the observed and expected plant and floral visitor functional group combinations showed that we can not recover the observed combinations from its probability of occurrence.
 In fact, most combinations are under- or over- represented and follow a modified Gaussian distribution (Johnson's $S_U$) with 65$\%$ of under-represented group combinations, 20$\%$ of no statistical difference and 15$\%$ of under-represented ones (Fig.
@@
 For instance, for a z-score value of 0 there were approximately 800 subgraph combinations that showed no statistical difference in the comparison between real and simulated networks.
-In addition, four specific graphical examples of the most probable subgraphs being observed on each category are also provided and the different plant and floral visitor groups are represented with distinct colour codes as indicated in the legend."}
+In addition, four specific graphical examples of the most probable subgraphs being observed on each category are also provided and the different plant and floral visitor functional groups are represented with distinct colour codes as indicated in the legend."}
 
@@
 For instance, when we compare network subgraphs with equal structure for both trophic levels, we found that floral visitors had always over-representation in the positions that implied the highest number of direct links (e.g., positions 16 and 46 from network subgraphs 7 and 17, respectively).
-Despite this being in good agreement with the current view of the generalist nature of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of generalist network motifs was driven by the taxonomic group of bees while the rest of the taxonomic groups tended to be under-represented (Fig.
+Despite this being in good agreement with the current view of the generalist nature of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of generalist network motifs was driven by the functional group of bees while the rest of the functional groups tended to be under-represented (Fig.
 S6 A).
@@
 This large effect of bees on the overall patterns is no surprise, as bees were the group with the largest number of interaction records in the whole set of networks as also shown for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017].
+Just syrphids had a relatively similar number of interactions in comparison with bees (1,768 and 2,256 respectively) and similar species richness (343 and 321, respectively).
+However, both functional groups were associated with contrasting ecological roles likely indicating that both number of interactions and richness are not driving the observed interaction patterns for the different functional groups.
 Interestingly, bees also were the group with lower number of indirect interactions while the rest of floral visitor groups showed a clearly higher number of indirect interactions indicating that these non-bee floral visitor groups may experience higher competitive interactions for floral resources [@thomson2020].
@@
 
-All data and code are publicly available at Github (https://github.com/JoseBSL/FunctionalMotifs) and Zenodo (https://doi.org/10.5281/zenodo.6489213).
+All data and code are publicly available at Github (<https://github.com/JoseBSL/FunctionalMotifs>) and Zenodo (<https://doi.org/10.5281/zenodo.6489213>).
 
@@
 
-<div id ="refs"></div>
+::: {#refs}
+:::

### 2022-10-07 Manuscript/Supplementary_Material/Supporting_information_Journal_of_Animal_Ecology.Rmd
supp mat update

@@
 
-**Figure S2** Over and under-estimated motif frequencies.
-
-**Figure S3** Over and under-estimated groups on motif positions.
+**Figure S2** Over and under-estimated network subgraphs frequencies.
+
+**Figure S3** Over and under-estimated functional groups on network subgraphs positions.
 
@@
 
-**Figure S6** Association between the percentile and specificity of the different plant and floral visitor groups on motif positions.
-
-**Figure S7** Association between the percentile and number of indirect interactions of the different plant and floral visitor groups on motif positions.
-
-**Figure S8** Frequency of floral visitor groups and number of indirect interactions per motif positions.
-
-**Figure S9** Frequency of plant groups and number of indirect interactions per motif positions.
+**Figure S6** Association between the percentile and specificity of the different plant and floral visitor functional groups on network subgraph positions.
+
+**Figure S7** Association between the percentile and number of indirect interactions of the different plant and floral visitor functional groups on network subgraph positions.
+
+**Figure S8** Frequency of floral visitor functional groups and number of indirect interactions per network subgraph positions.
+
+**Figure S9** Frequency of plant functional groups and number of indirect interactions per network subgraph positions.
 
@@
 add_header_above(c("Quantitative traits" = 2,"Categorical traits" = 2),bold=T)  %>%
-    column_spec(c(1,4), bold = T) %>% row_spec(0, bold=T)
+    column_spec(c(1,3), bold = T) %>% row_spec(0, bold=T)
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure S2.** Comparison of motif frequencies between empirical and simulated networks grouped by average path length (plots a, b, c and d) as determined in Simmons et al.
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure S2.** Comparison of network subgraph frequencies between empirical and simulated networks grouped by average path length (plots a, b, c and d) as determined in Simmons et al.
 (2020) without considering singletones.
-This is shown with the mean percentage of motif frequencies in empirical networks that were over the motif frequencies of the simulated ones (percentiles).
+This is shown with the mean percentage of network subgraph frequencies in empirical networks that were over the subgraph frequencies of the simulated ones (percentiles).
 This was done by network (light blue dots) and then averaged for all networks (black dots with error bars that correspond to the standard deviation)."}
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="\\textbf{Figure S3.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions after removing non-robust links (singletones).
-The different motif positions are dividied by the average path length clasification determined by Simmons et al.
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="\\textbf{Figure S3.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different network subgraph positions after removing non-robust links (singletones).
+The different subgraph positions are dividied by the average path length clasification determined by Simmons et al.
 (2020).
-The superior dendrogram indicates the differences across groups with the more separated groups showing larger differences."}
+The superior dendrogram indicates the differences across functional groups with the more separated groups showing larger differences."}
 
@@
 Panel A) shows the percentage of the different categories within trait represented with different colours for each functional group.
-Plot B) shows the radar plot of the different quantitative variables standardise on the same scale also coloured with the same patterns of colours as qualitative variables per cluster or functional group.
+Plot B) shows the radar plot of the different scaled quantitative variables.
+Both quantitative and qualitative variables are coloured with the same pattern of colours by functional group.
 Group 1 corresponds to short-lived selfers; group 2 to small outcrossing perennials; group 3 to self-incompatible perennials with large flowers; group 4 to tall plants with small unisexual flowers; and, group 5 to short-lived outcrossers with long zygomorphic flowers."}
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align="center", fig.width=14,fig.height=7, out.width='100%',  fig.cap="\\textbf{Figure S6.} Association between the percentile (see main text) and specialization of the different plant and floral visitor groups on motif positions.
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align="center", fig.width=14,fig.height=7, out.width='100%',  fig.cap="\\textbf{Figure S6.} Association between the percentile (see main text) and specialization of the different plant and floral visitor functional groups on network subgraph positions.
 Here we consider that percentiles above 0.75 indicate over-representation and percentiles below 0.25 under-representation in the comparison between empirical and simulated networks."}
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align="center", fig.width=14,fig.height=7, out.width='100%', fig.cap="\\textbf{Figure S7.} Association between the percentile (see main text) and number of indirect interactions of the different plant and floral visitor groups on motif positions.
+```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align="center", fig.width=14,fig.height=7, out.width='100%', fig.cap="\\textbf{Figure S7.} Association between the percentile (see main text) and number of indirect interactions of the different plant and floral visitor functional groups on network subgraph positions.
 Here we consider that percentiles above 0.75 indicate over-representation and percentiles below 0.25 under-representation in the comparison between empirical and simulated networks."}
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S8.} Frequency of the different floral visitor groups on the different motif positions aggregated by the number of indirect interactions for the different motif positions."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S8.} Frequency of the different floral visitor functional groups on the different network subgraph positions aggregated by the number of indirect interactions for the different subgraph positions."}
 
@@
 
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S9.} Frequency of the different plant groups on the different motif positions aggregated by the number of indirect interactions for the different motif positions."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S9.} Frequency of the different plant functional groups on the different network subgraph positions aggregated by the number of indirect interactions for the different subgraph positions."}
 

### 2022-10-08 Manuscript/Main_text/Main_text_Journal_of_Animal_Ecol.Rmd
Minor edits

@@
 ---
-title: "The non-random assembly of indirect interactions in  \nplant-pollinator networks"
+title: "The non-random assembly of network motifs in  \nplant-pollinator networks"
 editor_options:
@@
 Recent work has shown that the meso-scale, the intermediate level of network complexity between the species and the global network, can capture this important information.
-The meso-scale describes network subgraphs representing patterns of direct and indirect interactions between a small number of species and when these network subgraphs differ statistically from a benchmark, they are often referred to as "network motifs".
+The meso-scale describes network subgraphs representing patterns of direct and indirect interactions between a small number of species, and when these network subgraphs differ statistically from a benchmark, they are often referred to as "network motifs".
 Although motifs can capture relevant ecological information of species interactions, they remain overlooked in natural plant-pollinator networks.
-By exploring 60 empirical plant-pollinator networks from 18 different studies with wide geographical coverage we show that some network subgraphs are consistently under- or over-represented, suggesting the presence of worldwide network motifs in plant-pollinator networks.
+By exploring 60 empirical plant-pollinator networks from 18 different studies with wide geographical coverage, we show that some network subgraphs are consistently under- or over-represented, suggesting the presence of worldwide network motifs in plant-pollinator networks.
 In addition, we found a higher proportion of densely connected network subgraphs that, based on previous findings, could reflect that species relative abundances are the main driver shaping the structure of the meso-scale on plant-pollinator communities.
@@
 Finally, we show that the observed functional group combinations within a subgraph can not be retrieved from their expected probabilities (i.e., joint probability distributions), indicating that plant and floral visitor associations within subgraphs are not random either.
-Therefore, our results highlight the presence of common motifs in plant-pollinator communities that are formed by a non-random association of plants and floral visitors functional groups.
+Therefore, our results highlight the presence of common network motifs in plant-pollinator communities that are formed by a non-random association of plants and floral visitors functional groups.
 
@@
 Indirect interactions, the mediated effect between two species by a third species, are ubiquitous in natural systems [@strauss1991; @holt1994; @wootton1994] and play a key role in shaping community dynamics [@werner2003; @walsh2013].
-Although some of the most studied indirect interactions are the ones caused by trophic cascades with consumer-resource interactions [@abrams1996; @schmitz2001], previous studies often focus on antagonistic interactions and overlook mutualistic ones [@knight2005].
+Some of the most studied indirect interactions are the ones caused by trophic cascades with consumer-resource interactions [@abrams1996; @schmitz2001].
+In fact, previous studies focus on antagonistic interactions and mutualistic interactions are often overlooked [@knight2005].
 On the contrary, plant-pollinator research has traditionally investigated direct interactions but neglected indirect effects such as competitive or facilitative processes between plants for pollinators [@moeller2004; @sargent2008; @carvalheiro2014].
@@
 For this, we used the plant trait dataset compiled in @lanuza2021 that consisted also of plant species that belonged to the same plant-pollinator networks plus some additional meta-networks not considered here.
-This dataset comprised a total of 1506 plant species including the 503 species considered in this study (Table S2).
+This dataset comprised a total of 1,506 plant species including the 503 species considered in this study (Table S2).
 Because most of these plant species are likely to benefit from animal pollination, we used reproductive traits relevant to understand the different plant reproductive strategies and their interactions with pollinators.
@@
 All analyses were run considering singletons (species with only one interaction detected) but we conducted a second exploration without singletons (64.98$\%$ of interactions) to evaluate the effect of rare species on the observed patterns.
-Results without singletons are qualitatively consistent and are not further discussed in the main text (Figs S2 and S3).
+Results without singletons are qualitatively consistent and are not further discussed in the main text (Figs.
+S2 and S3).
 
@@
 To control for variation in network size, subgraph frequencies were normalised as a proportion of the total number of subgraphs within each subgraph class (i.e., 2-species, 3-species, 4-species and 5-species network subgraphs).
-In addition, we excluded 2-species (or nodes) subgraphs from our analyses because its normalised frequencies would always equal one.
+In addition, we excluded 2-species (or 2-nodes) subgraphs from our analyses because its normalised frequencies would always equal one.
 Note that the aim is not comparing different networks, which may differ in sampling effort, but correctly describing the structure of each individual network.
@@
 We calculated which plant and floral visitor functional groups were over- or under-represented in the different subgraph positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
-To estimate the position frequencies of each plant and floral visitor group in a given network, we added the frequencies of those species that belong to the same group, and then, we normalised the resulting frequencies by dividing them by the total number of times that a corresponding group appears in any position within the same subgraph size class (i.e., 2, 3, 4 or 5 species motifs).
+To estimate the position frequencies of each plant and floral visitor group in a given network, we added the frequencies of those species that belong to the same group, and then, we normalised the resulting frequencies by dividing them by the total number of times that a corresponding group appears in any position within the same subgraph size class.
 Then, we calculated the percentile of the observed position frequencies for each functional group and network, just like we did with subgraph frequencies.
@@
 Thus, we considered all possible indirect interactions for each position.
-Finally, we analysed in a single model how specialisation and the number of indirect interactions were associated with the observed percentiles for each trophic guild and subgraph position (see paragraph above).
-For this, we fitted again a LMM model with the help of the *lme4* package where we considered specialisation and number of indirect interactions as response variables with the interaction by plant and floral visitor group for both response variables.
+Finally, we analysed in a single model how specialisation and the number of indirect interactions were associated with the observed percentiles for each trophic guild and subgraph position.
+For this, we fitted again a LMM model with the help of the *lme4* package, where we considered specialisation and number of indirect interactions as response variables with the interaction by plant and floral visitor group for both response variables.
 Further, we considered as random factor subgraph position nested within study system.
@@
 
-The hierarchical cluster analysis divided the dataset into five different plant functional groups with different and overlapping characteristics (Figs S6 and S7).
+The hierarchical cluster analysis divided the dataset into five different plant functional groups with different and overlapping characteristics (Figs.
+S4 and S5).
 The first group referred to as 'selfing herbs' consisted of herbs with hermaphroditic flowers with high levels of autonomous selfing.
@@
 The third group referred to as 'self-incompatible perennials with large flowers' comprised perennial species with a mixed of life forms and large self-incompatible hermaphroditic flowers with high number of ovules.
-The fourth group named 'tall plants with small unisexual flowers' had the tallest species, highest proportion of shrub and tree life forms, dioecious and monoecious breeding systems, small flowers and the highest numbers of flowers and inflorescences per plant.
+The fourth group named 'tall plants with small unisexual flowers' had the tallest species, highest proportion of shrub and tree life forms, dioecious and monoecious breeding systems, small flowers, and the highest numbers of flowers and inflorescences per plant.
 Finally, the fifth group named 'short-lived outcrossers with long zygomorphic flowers' consisted of small perennial and short-lived herbs with long self-compatible zygomorphic flowers that were unable to self-pollinate.
@@
 3).
-Floral visitors showed a total of `r poll_over_75`$\%$ and `r poll_under_25`$\%$ of over- and under-represented functional groups in the different positions and plants `r plant_over_75`$\%$ and `r plant_under_25`$\%$ of over- and under-represented functional groups, respectively.
-Notably, the differences across functional groups were more marked for floral visitors than for plants (the differences between min and max percentiles per position were generally two-three times larger for floral visitors).
+Floral visitors showed a total of `r poll_over_75`$\%$ and `r poll_under_25`$\%$ of over- and under-represented functional groups in the different positions, and plants `r plant_over_75`$\%$ and `r plant_under_25`$\%$ of over- and under-represented functional groups, respectively.
+Notably, the differences across functional groups were more marked for floral visitors than for plants (the differences between the minimum and maximum values of the percentiles per position were generally two-three times larger for floral visitors).
 From most over- to under-represented floral visitors functional groups on the different subgraph positions (indicated with the dendrogram order in Fig.
 3), we found: bees, non-syrphids Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.
-Although plant functional groups showed less differences between them, there were also more represented functional groups than others, thus from most over- to under-represented functional groups on the different subgraph positions we found: self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.
+Although plant functional groups showed less differences between them, there were also more represented functional groups than others.
+Thus, from most over- to under-represented functional groups on the different subgraph positions we found: self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.
 
@@
 First, for floral visitors, we found that bees were less frequent on subgraph positions that involved specialisation (i.e., lower specificity values) while the rest of functional groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) were infrequent in generalised subgraph positions with low number of indirect interactions (Fig.
-S8 A).
+S6 A).
 Although plants did not show differences with null models on their frequencies, all plant functional groups but tall plants with small unisexual flowers showed a slight tendency to be over-represented on specialised subgraph positions (Fig.
-S8 B).
+S6 B).
 Second, regarding the number of indirect interactions, bees were over-represented in subgraph positions with low number of indirect interactions (Fig.
-S9 A) and the rest of floral visitor functional groups showed no differences across positions in comparison with simulated networks.
+S7 A) and the rest of floral visitor functional groups showed no differences across positions in comparison with simulated networks.
 For plants, all functional groups showed a slight tendency to be over-represented on subgraph positions with higher number of indirect interactions (Fig.
-S9 B).
-When we further explore the observed frequencies by number of indirect interactions for floral visitor and plant functional groups, we found that both bees and tall plants with small unisexual flowers were the only functional groups with high frequencies on subgraph positions associated with low number interactions in comparison with the other floral visitor and plant functional groups (Figs S10 and S11).
+S7 B).
+When we further explore the observed frequencies by number of indirect interactions for floral visitor and plant functional groups, we found that both bees and tall plants with small unisexual flowers were the only functional groups with high frequencies on subgraph positions associated with low number of indirect interactions in comparison with the other floral visitor and plant functional groups (Figs.
+S8 and S9).
 
@@
 In addition, subgraphs with small node combinations (i.e., 2 and 3 nodes) only appeared as under-represented.
-Network subgraphs with 4 and 5 node combinations appeared in the three statistical categories but 4 node subgraphs had a higher proportion in the under-represented category (10% in comparison with the 1$\%$ and the 3$\%$ of the no statistical difference and over-represented categories, respectively).
-Finally, 5 node subgraphs were in similar proportions in the no statistical difference and over-represented categories (99$\%$ and 97$\%$, respectively) but they appeared in lower proportion in the under-represented category (89$\%$).
-When we explored the identity on the different positions of the most probable subgraph combinations we found that the most common plant and floral visitor functional groups were also the most probable on these plant and floral visitor combinations within the different subgraphs (lower panel Fig.
+Network subgraphs with 4 and 5 node combinations appeared in the three statistical categories, but 4 node subgraphs had a higher proportion in the under-represented category (10% in comparison with the 1$\%$ and the 3$\%$ of the no statistical difference and over-represented categories, respectively).
+Finally, 5 node subgraphs were in similar proportions in the no statistical difference and over-represented categories (99$\%$ and 97$\%$, respectively), but they appeared in lower proportion in the under-represented category (89$\%$).
+When we explored the identity on the different positions of the most probable subgraph combinations, we found that the most common plant and floral visitor functional groups were also the most probable on these plant and floral visitor combinations within the different subgraphs (lower panel Fig.
 5).
@@
 Because network subgraphs can capture both direct and indirect interactions, by analysing their over- and under-representation we were able to explore in great detail the structure of interactions between animal pollinators and the plants they visit.
-We have explored for the first time the overall structure and presence of network motifs in real plant-pollinator networks and shown that the different subgraphs up to five nodes are consistently over- or under-represented in comparison with simulated networks.
+We have explored for the first time the overall structure and presence of network motifs in real plant-pollinator networks and shown that, according to our first hypothesis, the different subgraphs up to five nodes are consistently over- or under-represented in comparison with simulated networks.
 In addition, we show that for plant-pollinator networks there is a general tendency for over-representation of network subgraphs that are more densely connected (i.e., complete, fan and asymmetric complete).
 Indeed, the work of @simmons2020 has shown with the help of simulated plant-pollinator networks that the main different processes that shape plant-pollinator communities (i.e., neutral effects, trait matching and phenology) generate different patterns of direct and indirect interactions, and that specifically, a higher proportion of these more densely connected subgraphs is associated with neutral effects.
-Therefore, as indicated for other network properties like nestedness at the macro-scale level [@krishna2008; @suweis2013], or interaction probability at the species level [@bartomeus2016], our findings indicate that neutral effects may be also the main driver governing this intermediate level of complexity on plant-pollinator networks.
+Therefore, as indicated for other network properties like nestedness at the macro-scale level [@krishna2008; @suweis2013], or interaction probability at the species level [@bartomeus2016], our findings align with our second hypothesis and indicate that neutral effects may be also the main driver governing this intermediate level of complexity on plant-pollinator networks.
 
@@
 This large effect of bees on the overall patterns is no surprise, as bees were the group with the largest number of interaction records in the whole set of networks as also shown for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017].
-Just syrphids had a relatively similar number of interactions in comparison with bees (1,768 and 2,256 respectively) and similar species richness (343 and 321, respectively).
+Just syrphids had a relatively similar number of interactions in comparison with bees (1,768 and 2,256 interactions, respectively) and similar species richness (343 and 321 species, respectively).
 However, both functional groups were associated with contrasting ecological roles likely indicating that both number of interactions and richness are not driving the observed interaction patterns for the different functional groups.
-Interestingly, bees also were the group with lower number of indirect interactions while the rest of floral visitor groups showed a clearly higher number of indirect interactions indicating that these non-bee floral visitor groups may experience higher competitive interactions for floral resources [@thomson2020].
+Interestingly, bees also were the group with lower number of indirect interactions, while the rest of floral visitor groups showed a clearly higher number of indirect interactions, indicating that these non-bee floral visitor groups may experience higher competitive interactions for floral resources [@thomson2020].
 Despite plant functional groups showed little differences between them on their subgraph frequencies, all groups showed a tendency to be over-represented on subgraph positions that were associated with higher levels of specialisation.
@@
 Thus, similarly to the presence of forbidden links at the network level [@olesen2011; @jordano2016], we also found the existence of forbidden subgraph positions and those represented almost two thirds of the total possible subgraph combinations.
-This concurs well with the general idea that plant-pollinator networks have a high proportion of non-realized direct interactions [@jordano2003; @bascompte2013], and as a result, also a high proportion of non-realized combinations of indirect interactions.
+This concurs well with the general idea that plant-pollinator networks have a high proportion of non-realized direct interactions [@jordano2003; @bascompte2013], and, as a result, also a high proportion of non-realized combinations of indirect interactions.
 Some of these non-observed direct interactions are probably due to under-sampling [@dorado2011; @jordano2016].
-However, a large fraction of the possible interactions do not take place because of life-history constraints such as species co-occurrence, trait matching processes and phenological uncoupling [@olesen2011; @bartomeus2016; @jordano2016].
+However, a large fraction of the possible interactions do not take place because of different constraints such as species co-occurrence, trait matching processes and phenological uncoupling [@olesen2011; @bartomeus2016; @jordano2016].
 Despite the advances in the understanding of the ecological processes that influence species pairwise interactions [@bartomeus2016; @peralta2020], we still know little about how these processes determine competitive and facilitative interactions in mutualistic networks.
@@
 For instance, taxonomic diversity and trait availability limit our ability to properly represent the wide range of reproductive strategies [@dellinger2020] and different clustering analysis can lead to distinct outcomes (e.g., k-means and hierarchical clustering).
-We divided floral visitors on the taxonomic rank level because it adequately represented pollinator ecological roles without the tremendous effort of compiling trait data for over 1000 species of floral visitors.
+We divided floral visitors on the taxonomic rank level because it adequately represented pollinator ecological roles without the tremendous effort of compiling trait data for over 1,000 species of floral visitors.
 Indeed, further groupings with traits could help reveal greater relevance of trait-matching processes on indirect interactions.
-Moreover, we analysed network subgraphs focusing exclusively on presence or absence of interactions assuming that all interactions are equally important but further work should investigate how to account for the quantitative measurements of the strength of plant-pollinator interactions.
+Moreover, we analysed network subgraphs focusing exclusively on presence or absence of interactions, assuming that all interactions are equally important.
+However, further work should investigate how to account for quantitative measurements of plant-pollinator interactions.
 Consistent with previous work [@simmons2019; @simmons2020], we characterised network motifs by using null models only constrained for network connectance.
 Although more complex null models are difficult to interpret [@Ulrich2013], they can potentially allow us to separate the mechanisms by which motifs emerge.
-However, we found that null models with more constraints were computationally unfeasible and that connectance, nestedness and degree distribution were significantly correlated (data not shown).
-We highlight the difficulties to explore the potential sources that generate over-representation of network subgraphs and the need to investigate them.
+However, we found that null models with more constraints generated binary structures that were mostly identical to the original ones.
+In addition, we observed that connectance, nestedness and degree distribution were significantly correlated (data not shown).
+All that highlights the difficulties to disentangle the potential sources that generate over-representation of network subgraphs and the need to investigate them.
 At the same time, although network subgraphs can capture both direct and indirect interactions, the reduction of network complexity into these different building blocks inevitably convey the loss of information [@simmons2019], for example indirect interactions from large cascading effects.
-Our work explores only interactions between plants and pollinators but a multitrophic context is indeed needed to fully understand community dynamics [@knight2005].
 Finally, despite the wide geographical coverage of our plant-pollinator dataset, there are major gaps for some regions of the world with a clear bias towards Europe, America and islands which have long interested ecologists [@macarthur1963; @warren2015].
-These biases are also found in global datasets of networks where the data is highly fragmented across space [@poisot2021] and more efforts are needed to capture global patterns of plant-pollinator interactions.
+These biases are also found in global datasets of networks, where the data is highly fragmented across space [@poisot2021] and more efforts are needed to capture global patterns of plant-pollinator interactions.
 

### 2022-10-08 Manuscript/Main_text/Main_text_Journal_of_Animal_Ecol.Rmd
minor edit matching journal specifications

@@
 All analyses were run considering singletons (species with only one interaction detected) but we conducted a second exploration without singletons (64.98$\%$ of interactions) to evaluate the effect of rare species on the observed patterns.
-Results without singletons are qualitatively consistent and are not further discussed in the main text (Figs.
-S2 and S3).
+Results without singletons are qualitatively consistent and are not further discussed in the main text (Figs S2 and S3).
 
@@
 
-The hierarchical cluster analysis divided the dataset into five different plant functional groups with different and overlapping characteristics (Figs.
-S4 and S5).
+The hierarchical cluster analysis divided the dataset into five different plant functional groups with different and overlapping characteristics (Figs S4 and S5).
 The first group referred to as 'selfing herbs' consisted of herbs with hermaphroditic flowers with high levels of autonomous selfing.
@@
 S7 B).
-When we further explore the observed frequencies by number of indirect interactions for floral visitor and plant functional groups, we found that both bees and tall plants with small unisexual flowers were the only functional groups with high frequencies on subgraph positions associated with low number of indirect interactions in comparison with the other floral visitor and plant functional groups (Figs.
-S8 and S9).
+When we further explore the observed frequencies by number of indirect interactions for floral visitor and plant functional groups, we found that both bees and tall plants with small unisexual flowers were the only functional groups with high frequencies on subgraph positions associated with low number of indirect interactions in comparison with the other floral visitor and plant functional groups (Figs S8 and S9).
 

### 2022-10-08 Manuscript/Main_text/Graphical_abstract.Rmd
Graphical abstract and word doc for word count

--- 2022-10-08 Manuscript/Main_text/Main_text_Journal_of_Animal_Ecol.Rmd
@@
 ---
-title: "The non-random assembly of network motifs in  \nplant-pollinator networks"
-editor_options:
-  chunk_output_type: console
-header-includes:
-- \usepackage{booktabs}
-- \usepackage{longtable}
-- \usepackage{array}
-- \usepackage{multirow}
-- \usepackage{wrapfig}
-- \usepackage{float}
-- \usepackage{colortbl}
-- \usepackage{pdflscape}
-- \usepackage{tabu}
-- \usepackage{threeparttable}
-- \usepackage{threeparttablex}
-- \usepackage[normalem]{ulem}
-- \usepackage{makecell}
-- \usepackage{xcolor}
-- \usepackage{caption,setspace}
-- \captionsetup[figure]{labelformat=empty}
-- \floatplacement{figure}{H}
-- \usepackage[skip=3pt]{caption}
-- \captionsetup[figure]{labelformat=empty}
-- \usepackage{lscape}
-- \newcommand{\blandscape}{\begin{landscape}}
-- \newcommand{\elandscape}{\end{landscape}}
-- \usepackage[left]{lineno}
-- \linenumbers
-output:
-  pdf_document: default
-  html_document: default
-  word_document: default
-always_allow_html: true
-bibliography: bibliography.bib
-biblio-style: apalike
-csl: JournalOfAnimalEcology.csl #converted from funct ecol style from zotero styles
+output: pdf_document
+classoption: landscape
+
 ---
 
-**Jose B. Lanuza^1,2^** \| **Alfonso Allen-Perkins^2,3^** \| **Ignasi Bartomeus^2^**
-
-1 School of Environmental and Rural Science, University of New England, Armidale, New South Wales 2350, Australia.
-
-2 Estación Biológica de Doñana (EBD-CSIC), E-41092 Seville, Spain.
-
-3 Departamento de Ingeniería Eléctrica, Electrónica, Automática y Física Aplicada, ETSIDI, Universidad Politécnica de Madrid, 28040 Madrid, Spain.
-
-\captionsetup[table]{labelformat=empty}
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
-
-# Abstract
-
-\singlespacing
-
-Ecological processes leave distinct structural imprints on the species interactions that shape the topology of animal-plant mutualistic networks.
-Detecting how direct and indirect interactions between animals and plants are organised is not trivial since they go beyond pairwise interactions, but may get blurred when considering global network descriptors.
-Recent work has shown that the meso-scale, the intermediate level of network complexity between the species and the global network, can capture this important information.
-The meso-scale describes network subgraphs representing patterns of direct and indirect interactions between a small number of species, and when these network subgraphs differ statistically from a benchmark, they are often referred to as "network motifs".
-Although motifs can capture relevant ecological information of species interactions, they remain overlooked in natural plant-pollinator networks.
-By exploring 60 empirical plant-pollinator networks from 18 different studies with wide geographical coverage, we show that some network subgraphs are consistently under- or over-represented, suggesting the presence of worldwide network motifs in plant-pollinator networks.
-In addition, we found a higher proportion of densely connected network subgraphs that, based on previous findings, could reflect that species relative abundances are the main driver shaping the structure of the meso-scale on plant-pollinator communities.
-Moreover, we found that distinct subgraph positions describing species ecological roles (e.g., generalisation and number of indirect interactions) are occupied by different groups of animal and plant species representing their main life-history strategies (i.e., functional groups).
-For instance, we found that the functional group of 'bees' was over-represented in subgraph positions with a lower number of indirect interactions in contrast to the rest of floral visitors groups.
-Finally, we show that the observed functional group combinations within a subgraph can not be retrieved from their expected probabilities (i.e., joint probability distributions), indicating that plant and floral visitor associations within subgraphs are not random either.
-Therefore, our results highlight the presence of common network motifs in plant-pollinator communities that are formed by a non-random association of plants and floral visitors functional groups.
-
-Keywords: pollinators, plant-pollinator networks, plant-pollinator interactions, network motifs, indirect interactions, floral visitors
-
-\doublespacing
-
-\newpage
-
-# Introduction
-
-Ecological communities are formed by a plethora of interacting species that form networks of interactions.
-Because of the tremendous complexity of these ecological networks, species interactions are generally condensed in metrics that summarise this information [@guimaraes2020].
-Plant-pollinator interactions are no exception, and they are often studied with indices that aggregate the information at the network (macro-scale) and species level (micro-scale).
-For example, plant-pollinator network level approaches have identified common invariant structural properties across mutualistic networks, including a degree distribution that decays as a truncated power law [@jordano1987], nestedness [@bascompte2003], or modularity [@olesen2007].
-In addition, the local species position within the network can define its degree of selectiveness [@bluthgen2006] or its role in connecting the rest of the community [@olesen2007].
-Despite the unquestionable progress with the use of these metrics at both network and species level, condensing complex information into a single metric implies the loss of relevant ecological information that obscures the understanding of species interactions [@cirtwill2018; @simmons2019].
-
-Indirect interactions, the mediated effect between two species by a third species, are ubiquitous in natural systems [@strauss1991; @holt1994; @wootton1994] and play a key role in shaping community dynamics [@werner2003; @walsh2013].
-Some of the most studied indirect interactions are the ones caused by trophic cascades with consumer-resource interactions [@abrams1996; @schmitz2001].
-In fact, previous studies focus on antagonistic interactions and mutualistic interactions are often overlooked [@knight2005].
-On the contrary, plant-pollinator research has traditionally investigated direct interactions but neglected indirect effects such as competitive or facilitative processes between plants for pollinators [@moeller2004; @sargent2008; @carvalheiro2014].
-Conventional analytical tools in bipartite networks often discard relevant information about indirect interactions by condensing the information into single indices either at species or network level [@cirtwill2018; @simmons2019].
-However, as previously explored with three species modules in unipartite food webs [@allesina2008; @stouffer2010], the emergent framework of bipartite subgraphs has proven to be a powerful analytical tool to better understand plant-pollinator community dynamics by capturing both direct and indirect effects [@simmons2019].
-These network subgraphs that constitute the meso-scale are often referred to as the building blocks of the network and when their numbers occur at higher frequencies than in randomised networks, those are generally defined as 'network motifs' [@milo2002].
-Indeed, the analysis of motifs in simulated plant-pollinator networks has revealed that the different drivers that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect effects [@simmons2020].
-However, the global patterns of indirect interactions in real plant-pollinator networks and their ecological consequences remain unexplored (e.g., over- and under- represented network subgraphs).
-
-By linking the structural properties of the meso-scale with the species' ecology we can advance in our understanding on the determinants of species interactions.
-For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species' functional role [@stouffer2012; @baker2015; @cirtwill2018b].
-Yet, our understanding of the ecological implications of network motifs in real plant-pollinator networks remains in its infancy.
-Moreover, it is unclear how the species ecology and life-history traits determine its functional role within the network of interactions [@coux2016].
-For example, large pollinators can forage larger distances [@greenleaf2007], deposit greater pollen quantities [@foldesi2021] and handle complex zygomorphic flowers in comparison with small pollinators that are restricted to lower floral complexity [@gong2009].
-Despite these obvious differences in pollinator behaviour, how contrasting species' ecology translates into different network motifs is still poorly known.
-Similarly, recent empirical findings indicate that the meso-scale is the best descriptor of plant reproductive success [@allen2021], but little is known about how plants' reproductive strategies shape their position within the network of interactions.
-Although some studies have evaluated plant reproductive strategies in plant-pollinator networks [@tur2013; @lazaro2020], this is an often overlooked aspect in a community context [@devaux2014] and rarely incorporated into plant-pollinator network studies.
-Hence, exploring how the main plant and floral visitor life-history strategies integrate with the emergent framework of network motifs could help to progress knowledge on the ecological processes that shape plant-pollinator interactions.
-
-Here we evaluate the interaction patterns of the meso-scale and its ecological implications in plant-pollinator networks with the help of 60 empirical networks from 18 different studies distributed across 14 different countries.
-For this, plants and pollinators were divided into functional groups that summarise their main life-history strategies and the different networks were split into all their subgraph elements up to five nodes.
-First, based on previous knowledge showing the non random assembly of macro-scale mutualistic networks [@bascompte2003] and food webs [@dunne2002], we test the hypothesis that the building blocks that constitute the meso-scale in plant-pollinator networks have a non-random structure of interactions with over- and under-represented subgraphs (i.e., motifs) that represent contrasting ecological roles.
-Second, because species relative abundances (i.e., neutral effects) are one of the main drivers of network macro-struture [@krishna2008; @suweis2013; @bartomeus2016], we hypothesise that neutral effects may also govern the interaction patterns of the meso-scale in plant-pollinator networks.
-Finally, we explore if plants and pollinators functional groups are associated with subgraph positions that imply distinct ecological roles and if there are over- and under-represented functional group combinations within the different network subgraphs.
-
-# Methods
-
-**Overview**
-
-To investigate the structure of the meso-scale in plant-pollinator networks, we gathered published plant-pollinator networks with worldwide distribution.
-Then, we classified the different plant and floral visitor species from these networks into functional groups that summarise their main life-history strategies.
-We calculated the normalised subgraph frequencies and investigated if these frequencies are similar or not to the ones expected by chance with the help of null models.
-Then, for each group of plants and floral visitors we investigated the ecological implications of their overall representation on the different subgraph positions, by comparing, on the one hand, the observed (normalised) frequencies of each group in the different subgraph positions with the frequencies of their simulated counterparts, and, on the other hand, the differences among groups per subgraph position in terms of their number of indirect interactions and specialisation.
-Finally, to understand if the different functional group combinations within a subgraph are structured, we compare if the observed functional group combinations from empirical networks can be retrieved from the joint probability distribution of the expected frequencies of the different plant and floral visitor groups within network subgraphs.
-
-**Plant-pollinator studies**
-
-We have compiled 60 plant-pollinator networks from 18 different studies (Table S1).
-All studies sampled plant-pollinator interactions in natural systems in a single flowering season and were selected based on wide geographical coverage (Fig.
-S1) and presence of interaction frequency as a measure of interaction strength.
-In total, there were 503 plant species, 1,111 floral visitors species and 6,248 pairwise interactions registered.
-For ease of data manipulation, plant and floral visitor species names were standardised with the help of the R package *taxize* version *0.9.99* [@chamberlain2020].
-
-**Plant and floral visitor functional groups**
-
-First, plant species were grouped through hierarchical clustering into the optimal number of functional groups that summarises the main plant reproductive strategies.
-For this, we used the plant trait dataset compiled in @lanuza2021 that consisted also of plant species that belonged to the same plant-pollinator networks plus some additional meta-networks not considered here.
-This dataset comprised a total of 1,506 plant species including the 503 species considered in this study (Table S2).
-Because most of these plant species are likely to benefit from animal pollination, we used reproductive traits relevant to understand the different plant reproductive strategies and their interactions with pollinators.
-After excluding traits with a high percentage of missing values (over 30$\%$), we ended up with 8 floral, 3 reproductive biology and 3 plant morphology traits (see Table S3 for a list of all traits).
-Floral traits included those associated with the size, form and number of floral organs (e.g., style length or ovule number).
-Reproductive biology traits described the reproductive system of the plant (e.g., mating and compatibility systems) and plant morphology traits were associated with the size and form of the plant (i.e., plant height, lifespan and life form).
-After an extensive search for each plant species on several different resources (e.g., plant databases, online floras, books, journals and images), over 80% of the cells of the whole dataset were filled.
-Thus, to avoid the loss of species with trait missing values, missing trait data was imputed as detailed in @lanuza2021.
-
-We opted to calculate the plant functional groups within a larger set of species because of the higher accuracy when delimiting functional groups with that many variables and species [@dolnicar2014].
-To feed the clustering analysis, we calculated the distance between the different qualitative and scaled quantitative variables with Gower distance [@gower1971].
-For this, we used the function *gowdis* with method *ward.D2* from the *FD* package version *1.0-12* [@laliberte2014].
-Finally, we conducted hierarchical clustering with the function *hclust* from the *R* stats package version *4.0.5* and calculated the optimal number of clusters with the function *kgs* from the *maptree* package version *1.4-7* [@white2009].
-
-Second, floral visitors were aggregated into taxonomic groups (hereafter referred to as functional groups) based on taxonomic rank as done similarly in other plant-pollinator studies [@fenster2004; @ollerton2009].
-We opted to divide floral visitors on the taxonomic rank level and not with functional traits because the main orders of floral visitors differed in form and behaviour and had lower superior taxonomic complexity (i.e., floral visitors had 6 orders versus plants that had 38).
-Thus, this allowed us to group floral visitors into functional groups that represented approximately the main life-history strategies of the possible pollinators: (i) bees (Hymenoptera-Anthophila), (ii) non-bee Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Syrphidae-Diptera), (iv) non-syrphids-Diptera, (v) Lepidoptera and (vi) Coleoptera.
-However, a minor set of species belonged to other functional groups that were considered in analyses but not discussed further because of their low representation in the full set of networks (3.55$\%$ of the total interactions recorded).
-These taxonomic groups were 'lizards', 'birds' and 'other insects'.
-This last functional group was formed by a mix of uncommon insect taxa on the full set of networks.
-
-**Overall network subgraphs patterns**
-
-Following previous work [@simmons2019; @simmons2020], we broke down the plant-pollinator networks into their constituent network subgraphs that can capture both direct and indirect interactions.
-Prior to analyses, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.
-This approach was preferred since quantitative subgraph analyses have been developed just recently and more work is needed to fully understand and interpret the information that they can convey [@simmons2020].
-All analyses were run considering singletons (species with only one interaction detected) but we conducted a second exploration without singletons (64.98$\%$ of interactions) to evaluate the effect of rare species on the observed patterns.
-Results without singletons are qualitatively consistent and are not further discussed in the main text (Figs S2 and S3).
-
-We calculated the frequency of all subgraphs up to five nodes (17 different subgraphs in total; see Fig.
-1) for each empirical network, by using the *bmotif* package version *2.0.2* [@bmotifsimmons2019].
-We focused exclusively on subgraphs up to five nodes in our analyses for computational reasons and for the ease of visualization and interpretation of a reduced set of less complex network structures.
-Throughout the entire manuscript, floral visitors occupy the top nodes of the different network subgraphs and plants the bottom ones.
-To control for variation in network size, subgraph frequencies were normalised as a proportion of the total number of subgraphs within each subgraph class (i.e., 2-species, 3-species, 4-species and 5-species network subgraphs).
-In addition, we excluded 2-species (or 2-nodes) subgraphs from our analyses because its normalised frequencies would always equal one.
-Note that the aim is not comparing different networks, which may differ in sampling effort, but correctly describing the structure of each individual network.
-Like @simmons2020, we classified the different subgraphs by their average path length (mean number of links between all pairs of nodes) into four different groups: (i) complete or strong ($\overline{x} = 1.38$), (ii) fan or medium-strong ($\overline{x} = 1.48$), (iii) assymmetric complete or medium-weak ($\overline{x} = 1.60$) and (iv) core-peripheral or weak ($\overline{x} = 1.85$), where $\overline{x}$ represents the mean of the average path length across subgraphs within the same group.
-In general terms, plant and floral visitor groups on more densely connected network subgraphs (e.g., complete or fan) will experience lower number of indirect interactions in contrast to groups on less densely connected structures (e.g., medium-weak or weak).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, fig.pos="t", warning=FALSE,out.width="75%",fig.align="center", fig.cap="\\textbf{Figure 1.} Adapted figure of Simmons et al., (2019).
-All possible network subgraphs from two to five species in bipartite networks grouped by the different subgraph classes (2-species, 3-species, 4-species and 5-species).
-There are a total of 17 possible subgraphs with 46 different positions denoted within each node.
-The different subgraphs are aggregated by the broad indirect interaction structures they represent on four different groups (strong, medium-strong, medium-weak and weak).
-For each group, we show in the legend the mean value of the average path length of all subgraphs within it.
-The different path length groups range from densely connected network structures (strong subgraphs where all possible interactions are realised and the mean path length is minimum) to weakly connected ones (weak subgraphs where the mean path length is maximum).", fig.width=10,fig.height=8}
-library(tidyverse)
-library(RColorBrewer)
-source("../../Scripts/Scripts_Alfonso/plot_motif_positionsV2.R")
-
-motif_number <- 1
-p1 <- plot_motif_positions(motif_number) +
-geom_point(aes(color = as.factor(label)),size=10,color = "grey90")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 2
-p2 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 3
-p3 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 4
-p4 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 5
-p5 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "lightcoral")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 6
-p6 <- plot_motif_positions(motif_number) +
-geom_point(aes(color = as.factor(label)),size=10,color = "goldenrod2")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 7
-p7 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 8   
-p8 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 9
-p9 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "lightcoral")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 10
-p10 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "lightcoral")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 11
-p11 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "skyblue")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 12
-p12 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "goldenrod2")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 13
-p13 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "lightcoral")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 14
-p14 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "lightcoral")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 15
-p15 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "skyblue")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 16
-p16 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "goldenrod2")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 17
-p17 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
-geom_text(aes(x, y , label = label),size=3)
-
-library(patchwork)
-
-p <- (p1 & ylab("2 species")| p2 & ylab("3 species") | p3 ) /
-(p4 & ylab("4 species")| p5 | p6 | p7) / 
-(p8  & ylab("5 species")| p9 | p10 | p11 | p12) /
-(p13 & ylab("5 species")| p14 | p15 | p16 | p17) &
-theme(axis.title.y = element_text(color="black", size=14, face="bold"))
-
-#Create custom legend
-a <- c(1,2,3,4)
-b <- c(1,2,3,4)
-c <- c("a","b", "c", "d")
-abc <- data.frame(a,b,c)
-p1 <- ggplot(abc, aes(x=a,y=b, color=c))+geom_point() + theme_bw() + 
-  scale_colour_manual(name = 'Path length classification', 
-                      values =c(a= 'goldenrod2',b='mediumaquamarine',
-                                c='skyblue', d='lightcoral'), 
-                      labels = c(a='Strong \n mean path length = 1.38', 
-                                 b='Medium-strong \n mean path length = 1.48',
-                                 c='Medium-weak \n mean path length = 1.60',
-                                 d='Weak \n mean path length = 1.85'))+
-theme(legend.position="bottom")+ guides(colour = guide_legend(override.aes = list(size=8),title.position="top", title.hjust = 0.5))
-
-legend <- cowplot::get_legend(p1+ theme(legend.position = "bottom",legend.text = element_text(size=10), legend.title = element_text(size=12, 
-face="bold"),legend.box.background = element_rect(color="black", size=2)))
-
-cowplot::plot_grid(p, legend, ncol = 1, rel_heights = c(12, 1.8))
-
-```
-
-To assess the significance of the observed frequencies, we created 1,000 simulated networks for each binary network using the *nullmodel* function and the *vaznull* model in the *bipartite* package version *2.14* [@dormann2009].
-Generated networks had the same number of plants and floral visitors, as well as the same connectance of their corresponding empirical networks.
-We discarded null models with more constraints (e.g., constraining for species degree) because the permutations did not generate sufficient variability and provided highly similar or identical networks to the original ones.
-After extracting the subgraph frequencies from the simulated networks, for each subgraph type and empirical network, we calculated the percentage of simulated networks whose frequencies were smaller than the ones observed, that is, we estimated the percentile of the observed subgraph frequencies.
-Subgraphs whose percentile is close to 0 or 100 are under- or over-represented in empirical networks, respectively, and indicate the presence of network motifs as they differ statistically from the network structures generated with simulated networks.
-To summarise general patterns across networks, we used an intercept-only linear mixed model (LMM) per subgraph with the help of the *lme4* package version *1.1-21* [@bates2015], where the response variable was the observed subgraph percentile per network.
-Note that as we are only interested in modelling the intercept value, no predictors were specified.
-In these models, we used the study identifiers in Table S1 as a random intercept.
-By doing so, we obtained estimates of the average subgraph frequency, but controlling for the variation at the study level.
-
-**Over- and under-represented functional groups on subgraph positions**
-
-We calculated which plant and floral visitor functional groups were over- or under-represented in the different subgraph positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
-To estimate the position frequencies of each plant and floral visitor group in a given network, we added the frequencies of those species that belong to the same group, and then, we normalised the resulting frequencies by dividing them by the total number of times that a corresponding group appears in any position within the same subgraph size class.
-Then, we calculated the percentile of the observed position frequencies for each functional group and network, just like we did with subgraph frequencies.
-To outline the general patterns of position frequencies across networks and groups, we fit a LMM per subgraph position, where the response variable was the observed position percentile per network.
-We used the group identifier as an explanatory variable and the study identifiers as a random intercept.
-Hence, we assessed the average subgraph frequency per species group, after controlling for the variation at the study level.
-Finally, we visualised over- and under-representation of plant and floral visitor groups on the different subgraph positions with the help of the *ComplexHeatmap* package version *2.6.2* [@gu2016].
-
-To understand if the different plant and floral visitor functional groups are associated with subgraph positions that represent different network roles, we characterised the roles of each subgraph position for the different functional groups in terms of their specialisation and number of indirect interactions.
-To that end, we calculated the specificity of each subgraph position following @poisot2015 as $s_i = (L - l_i) / (L - 1)$, where $L$ is the total number of groups and $l_i$ the number of interaction partners of the group $i$ in a given subgraph.
-Values of the vector $si$, range between 1, complete specialisation (1 partner within the subgraph) and 0 complete generalism (all possible partners within the subgraph).
-Then, because all nodes within a motif are connected, we calculated the number of indirect interactions ($\theta_i$) for each motif position as $\theta_i=m_i-k_i-1$, where $m_i$ is the total number of nodes in a given motif, and $k_i$ represents the degree of the corresponding motif position, that is, the total number of links connected to such position.
-Thus, we considered all possible indirect interactions for each position.
-Finally, we analysed in a single model how specialisation and the number of indirect interactions were associated with the observed percentiles for each trophic guild and subgraph position.
-For this, we fitted again a LMM model with the help of the *lme4* package, where we considered specialisation and number of indirect interactions as response variables with the interaction by plant and floral visitor group for both response variables.
-Further, we considered as random factor subgraph position nested within study system.
-
-**Over- and under-represented functional group combinations of subgraphs**
-
-Finally, we studied which combinations of plant and floral visitor functional groups tend to appear together within the same subgraphs (up to five nodes).
-That is, which combinations are over- or under-represented.
-This analysis used 57 out of the 60 networks available due to computational limitations to identify all the nodes in the subgraphs of the three networks with the highest number of links.
-To do so, for each of the 53,250 possible subgraph combinations, we estimated the observed and the expected probability of finding those combinations in empirical networks, respectively.
-Then, we determined whether the observed probabilities are likely to come from the expected probabilities or not.
-To calculate the observed probability ($p_i^O$) of the different groups within a subgraph $i$ (e.g., subgraph 3, 'bee' + 'bee' + 'selfing herbs'), we divided the number of times that $i$ appears in our set of empirical networks ($n_i^O$) by the sum of the number of times that each possible combination appeared: $p_i^O = n_i^O / \sum_{k=1}^{53,250} n_k^O$.
-To estimate the expected probability ($p_i^E$) of a given subgraph combination $i$, we assumed that the probability of finding a given functional group $x$ in the position $\alpha$ is independent of the probabilities associated with other positions and groups in that subgraph.
-Therefore, the expected probability ($p_i^E$) of the subgraph combination $i$ is given by the product of the probabilities of its constituents, i.e., $p_i^E = \prod _{(x,\alpha )\in i} p_i(x,\alpha)$, where $p_i(x,\alpha)$ is the probability of finding a given functional group $x$ in the position $\alpha$ of $i$.
-Then, by controlling for the variation at the network level with an LMM (see below), we calculated the average number of times that the functional group $x$ appears in the position $\alpha$ (denoted as $n_i(x,\alpha)$).
-To obtain the expected probability $p_i(x,\alpha)$, we divided the number of times that the group $x$ appears in the position $\alpha$ by the the total number of times that any group was observed in that position (that is, $p_i(x,\alpha) = n_i(x,\alpha)/\sum_{k}n_i(k,\alpha)$).
-The average number of times that the group $x$ appears in the position $\alpha$ ($n_i(x,\alpha)$) was calculated with a LMM for each position, where the response variable was the number of times that a group was observed at a given position in each real-world network, the explanatory variable was the group identifier, and the random intercept was given by network identifiers nested within the study identifiers.
-
-Once we obtained $p_i^O$ and $p_i^E$, we used a simulation approach to determine whether the former is likely to come from the latter or not.
-This approach was preferred since the large number of possible subgraph combinations and the small probabilities for some of them advise against using an exact test of goodness-of-fit or a Chi-square one.
-Specifically, we created 1,000 random samples with repetition of possible subgraph combinations, where each sample contained 10 million elements and, for each combination, the probability of being selected was equal to its expected probability.
-From those random samples, we extracted the mean and the standard deviation of the expected probability of $i$, denoted as $E\left [ p_i^E \right ]$ and $\sigma\left [ p_i^E \right ]$, respectively, and calculated the z-scores of $p_i^O$ as $z_i^O = \left ( p_i^O - E\left [ p_i^E \right ] \right )/\sigma \left [ p_i^E \right ]$, for those motif combinations with $p_i^O > 0$.
-According to the usual interpretation of z-scores, combinations with $z_i^O > 1.96$ are over-represented, whereas those with $z_i^O < -1.96$ are under-represented, at the 95$\%$ confidence level.
-Notice that we focused on combinations with $p_i^O > 10^{-7}$ because we do not have enough numerical resolution to accurately detect whether combinations that took place only once are under-represented (due to the limited size of our random samples).
-
-All analyses and data manipulation were conducted in R *version 4.0.5* [@R].
-In addition, all model diagnostics were conducted with the help of the *Dharma* package [@hartig2017] version *0.3.3.0* and model outputs were visualised with the *visreg* package [@breheny2020] version 2.7.0.
-
-# RESULTS
-
-**Plant and floral visitor functional groups**
-
-The hierarchical cluster analysis divided the dataset into five different plant functional groups with different and overlapping characteristics (Figs S4 and S5).
-The first group referred to as 'selfing herbs' consisted of herbs with hermaphroditic flowers with high levels of autonomous selfing.
-The second group named 'small outcrossing perennials' had small perennial species with a mix of life forms (i.e., trees, shrubs and herbs) with outcrossing hermaphroditic flowers.
-The third group referred to as 'self-incompatible perennials with large flowers' comprised perennial species with a mixed of life forms and large self-incompatible hermaphroditic flowers with high number of ovules.
-The fourth group named 'tall plants with small unisexual flowers' had the tallest species, highest proportion of shrub and tree life forms, dioecious and monoecious breeding systems, small flowers, and the highest numbers of flowers and inflorescences per plant.
-Finally, the fifth group named 'short-lived outcrossers with long zygomorphic flowers' consisted of small perennial and short-lived herbs with long self-compatible zygomorphic flowers that were unable to self-pollinate.
-
-In total, there were 1,126 species of floral visitors with 6,325 interactions recorded with plants.
-Most plants interacted with bees (2,256 interactions) and non-syrphid Diptera (1,768) followed by syrphids (845), Lepidoptera (437), Coleoptera (432) and non-bee Hymenoptera (362).
-
-**Overall network subgraphs patterns**
-
-Most network subgraphs were under- or over-represented (close to the 1st and 99th percentile, respectively) in the comparison between empirical and simulated networks (Fig.
-2).
-Network subgraphs 3, 5, 9, 10 and 14 were under-represented in empirical networks, that is, all were close to the 1st percentile and under the 25th percentile.
-Interestingly, four out of five of these motifs belonged to the largest path length classification (i.e., core-peripheral).
-In addition, network subgraphs 2, 6, 7, 16 and 17 were over-represented, all over the 75th percentile.
-In contrast to the under-represented network subgraphs, over-represented subgraphs belonged to the two shortest path length groups (i.e., complete and fan).
-The remaining network subgraphs (i.e., 4, 8, 11, 12, 13, and 15) were between the 25th and 75th percentile.
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure 2.** Comparison of network subgraph frequencies between empirical and simulated networks grouped by average path length (plots a, b, c and d) where $\\overline{x}$ indicates the mean of the average path lengths of all subgraphs within each group (strong, medium-strong, medium-weak and weak).
-This comparison is shown with the mean percentage of subgraph frequencies in empirical networks that were over the subgraph frequencies of the simulated ones (percentiles).
-This was done by network (light blue transparent dots) and then averaged for all networks (black dots with error bars that correspond to the standard deviation)."}
-
-library(lme4)
-library(nlme)
-library(tidyverse)
-source("../../Scripts/Scripts_Alfonso/add_study_id.R")
-d <- read_csv("../../Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
-d <- add_study_id(d)
-#str(d)
-#head(d)
-
-#ggplot(d %>% filter(motif != 1), aes(percentil_sizeclass))+
-#  geom_histogram(color="black", fill="white")+
-#  facet_wrap(~motif)+
-#  theme_bw()+
-#  labs(x="Sizeclass percentile")
-#
-# Motifs tend to be over- and under-represensented in real networks
-
-# Mean percentile and SE taking into account the study system
-motif_codes <- d %>% filter(motif != 1) %>% # We remove links (motif code: 1)
-  select(motif) %>% unique() %>% pull()
-motif_means <- tibble(motif = motif_codes)
-motif_means$mean <- NA
-motif_means$SE <- NA
-
-for(i.motif in 1:length(motif_codes)){
-
-  m <- lmer(percentil_sizeclass ~ 1+(1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = subset(d, motif == motif_codes[i.motif]))
-
-  motif_means$mean[i.motif] <- fixed.effects(m) %>% unname()
-  motif_means$SE[i.motif] <- sqrt(diag(vcov(m)))
-
-}
-
-#Add categories based on path length set by Simmons 2021 et al., Functional Ecology
-d$Broad_categories[d$motif==2 | d$motif==7 | d$motif==17 | d$motif==3|d$motif==4|d$motif==8] <- "Fan"
-
-d$Broad_categories[d$motif==15 | d$motif==11] <- "Medium-weak"
-
-d$Broad_categories[d$motif==6 | d$motif==16 |  d$motif==12] <- "Strong"
-
-d$Broad_categories[d$motif==5 | d$motif==9 |  d$motif==14|  d$motif==13|  d$motif==10] <- "Weak"
-
-#order the categories from short to long path length
-d$Broad_categories <- factor(d$Broad_categories, levels = c("Strong", "Fan", "Medium-weak", "Weak"))
-
-#Ffilter out two node motifs
-d_1 <- d %>% filter(motif != 1)
-#Merge dataframes to bl able to create facets
-d_2 <- merge(d_1, motif_means, by="motif")
-
-arr <- list('Strong' = expression(bold(paste("(a) Strong (Complete, ", bar(x), " = 1.38)"))),
-             'Fan' = expression(bold(paste("(b) Medium-strong (fan, ", bar(x), " = 1.48)"))), 
-             'Medium-weak' = expression(bold(paste("(c) Medium-weak (asymmetric complete, ", bar(x), " = 1.60)"))), 
-             "Weak" =expression(bold(paste("(d) Weak (core-peripheral, ", bar(x), " = 1.85)"))))
-mylabel <- function(val) { return(lapply(val, function(x) arr[x])) }
-
-library(ggforce) #workaround with ggforce to have facets with same sizes 
-library(ggtext)
-
-labels <- c("2" = "*Subgraph 2* <img src='../../Images/motif_2.png' width='22'/>" ,
-          "3"= "*Subgraph 3* <img src='../../Images/motif_3.png' width='22'/>",
-          "4"= "*Subgraph 4* <img src='../../Images/motif_4.png' width='22'/>",
-          "5"= "*Subgraph 5* <img src='../../Images/motif_5.png' width='22'/>",
-          "6"= "*Subgraph 6* <img src='../../Images/motif_6.png' width='22'/>",
-          "7"= "*Subgraph 7* <img src='../../Images/motif_7.png' width='22'/>",
-          "8"= "*Subgraph 8* <img src='../../Images/motif_8.png' width='22'/>",
-          "9"= "*Subgraph 9* <img src='../../Images/motif_9.png' width='22'/>",
-          "10"= "*Subgraph 10* <img src='../../Images/motif_10.png' width='22'/>",
-          "11"= "*Subgraph 11* <img src='../../Images/motif_11.png' width='22'/>",
-          "12"= "*Subgraph 12* <img src='../../Images/motif_12.png' width='22'/>",
-          "13"= "*Subgraph 13* <img src='../../Images/motif_13.png' width='22'/>",
-          "14"= "*Subgraph 14* <img src='../../Images/motif_14.png' width='22'/>",
-          "15"= "*Subgraph 15* <img src='../../Images/motif_15.png' width='22'/>",
-          "16"= "*Subgraph 16* <img src='../../Images/motif_16.png' width='22'/>",
-          "17"= "*Subgraph 17* <img src='../../Images/motif_17.png' width='22'/>")
-
-p <- ggplot()+geom_point(data = d_2 , aes(y=factor(motif), 100*percentil_sizeclass), shape=21,color="black",fill="azure2",size=1.75, alpha=0.3)+
-  geom_errorbar(data = d_2,aes(y = factor(motif), xmin=100*(mean-SE), xmax=100*(mean+SE)), 
-                width=0.8,size=0.8,color="black") +theme_bw()+
-  geom_point(data = d_2,aes(y = as.factor(motif), x=100*mean), 
-             size=2,color="black")+labs(y="Two to five node motifs", x = "Percentile")+
-  theme( strip.background = element_blank())+
-  theme(strip.text = element_text(face="bold", size=10, hjust=0),
-        panel.border=element_rect(color="black",size=1.2))+
-  scale_y_discrete(name = NULL,
-                   labels = labels) +
-  theme(axis.text.y = ggtext::element_markdown())
-
-p + ggforce::facet_col(vars(Broad_categories), scales = 'free', space = 'free',labeller=mylabel)
-
-#Trying to maintain a gradient from low to high in colors
-
-#Fig 1 Should be a dot plot (or forest plot) of the mean +- SE of the 15 motifs.
-#NICE! Can we put motifs in Y axes, and % in X?
-```
-
-**Over- and under-represented functional groups on subgraph positions**
-
-```{r , include=FALSE}
-
-#SAME SCRIPT AS THE PLOTTING FOR THE HEATMAP BUT I NEED IT HERE TO LOAD THE VARIABLES WITH VALUES ON RESULTS
-
-library(lme4)
-library(nlme)
-library(tidyverse)
-library(stringi)
-source("../../Scripts/Scripts_Alfonso/add_study_id.R")
-
-#############################################
-# EXTRACT MEAN VALUES
-#############################################
-all_position_percentiles <- read_csv("../../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
-
-all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
-                                                              "[0-9]+") %>% as.numeric()
-
-all_position_percentiles <- add_study_id(all_position_percentiles)
-#str(all_position_percentiles)
-#head(all_position_percentiles)
-
-list_plants_FG <- as.character(1:10)
-
-plant_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF)) #ME DA ERROR
-pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF))
-
-# Plants-------------
-
-# Mean percentile and SE taking into account the study system
-plant_codes <- plant_position_percentiles_filtered$position %>% unique()
-plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-plant_means$mean <- NA
-plant_means$SE <- NA
-
-for(i.pos in 1:length(plant_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
-            data = plant_position_percentiles_filtered %>%
-              filter(position == plant_codes[i.pos]))
-
-  temp <- fixed.effects(m) %>% unname()
-  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
-                                                                    temp[1]+temp[2],
-                                                                    temp[1]+temp[3],
-                                                                    temp[1]+temp[4],
-                                                                    temp[1]+temp[5]) ## to get real means per FG
-  temp <- sqrt(diag(vcov(m)))
-  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
-                                                                  temp[1]+temp[2],
-                                                                  temp[1]+temp[3],
-                                                                  temp[1]+temp[4],
-                                                                  temp[1]+temp[5])
-
-}
-
-# Pollinators--------
-
-# Mean percentile and SE taking into account the study system
-pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
-pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-pollinator_means$mean <- NA
-pollinator_means$SE <- NA
-pollinator_means_reordered <- NULL
-
-for(i.pos in 1:length(pollinator_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = pollinator_position_percentiles_filtered %>%
-              filter(position == pollinator_codes[i.pos]),
-            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
-
-  temp <- fixed.effects(m) %>% unname()
-  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)
-
-  pollinator_means_aux$mean <- c(temp[1],
-                                 temp[1]+temp[2],
-                                 temp[1]+temp[3],
-                                 temp[1]+temp[4],
-                                 temp[1]+temp[5],
-                                 temp[1]+temp[6],
-                                 temp[1]+temp[7],
-                                 temp[1]+temp[8],
-                                 temp[1]+temp[9]) ## to get real means per FG
-
-  temp <- sqrt(diag(vcov(m)))
-  pollinator_means_aux$SE <- c(temp[1],
-                               temp[1]+temp[2],
-                               temp[1]+temp[3],
-                               temp[1]+temp[4],
-                               temp[1]+temp[5],
-                               temp[1]+temp[6],
-                               temp[1]+temp[7],
-                               temp[1]+temp[8],
-                               temp[1]+temp[9])
-
-  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)
-
-}
-
-# There are lower limits (mean - SE) smaller than 0 (see Other insects)
-# We set the lower limit of those error bars to zero
-
-pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
-pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
-
-#############################################
-# ADDING BROAD MOTIF CATEGORIES TO POSITIONS
-#############################################
-
-motifs_raw_data <- read_csv("../../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-motifs_raw_data$Broad_categories <- NA
-
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(5,9,14,13,10)] <- "Core-peripherical"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(6,16,12)] <- "Complete"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(2,3,7,4,17,8)] <- "Fan"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(15,11)] <- "Asymmetric complete"
-
-motifs_raw_data$plant <- gsub("[^0-9.-]", "", motifs_raw_data$plant)
-motifs_raw_data$pollinator <- gsub("[^0-9.-]", "", motifs_raw_data$pollinator)
-motifs_raw_data$plant <- as.numeric(motifs_raw_data$plant)
-motifs_raw_data$pollinator <- as.numeric(motifs_raw_data$pollinator)
-motifs_raw_data <- motifs_raw_data %>% filter(!is.na(Broad_categories))
-
-fan_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-pollinator_means_reordered$Broad_categories <- NA
-
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% fan_pollinator] <- "Fan" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% asymm_pollinator] <- "Medium-weak" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% complete_pollinator] <- "Strong" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% core_per_pollinator] <- "Weak"
-
-fan_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-plant_means$Broad_categories <- NA
-
-plant_means$Broad_categories[plant_means$position %in% fan_plant] <- "Fan" 
-plant_means$Broad_categories[plant_means$position %in% asymm_plant] <- "Medium-weak" 
-plant_means$Broad_categories[plant_means$position %in% complete_plant] <- "Strong" 
-plant_means$Broad_categories[plant_means$position %in% core_per_plant] <- "Weak"
-
-################################################################################
-# Alternative code to HEATMAPS to create variables with values to load on text
-# in a reproducible/automated way
-################################################################################
-
-# PLANTS-----
-
-# Prepare data for heatmap
-heat_plants_aux <- plant_means %>% spread(Node_FG,mean) %>% select(-SE)
-
-heat_plants <- heat_plants_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-# POLLINATORS-----------
-
-filter_rare_groups <- T
-
-if(filter_rare_groups == T){
-  heat_pollinators_aux <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds",
-                                                                                "Lizards",
-                                                                                "Other_insects")) %>% 
-    spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees",            
-                                      "Coleoptera","Lepidoptera","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Syrphids")
-}else{
-  heat_pollinators_aux <- pollinator_means_reordered %>% spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees","Birds",            
-                                      "Coleoptera","Lepidoptera","Lizards","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Other insects","Syrphids")
-}
-
-heat_pollinators <- heat_pollinators_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))
-
-#Check percentage of over and under represented
-colMeans(heat_pollinators[,c(3:8)] < 0.25)
-poll_under_25 <- colMeans(heat_pollinators[,c(3:8)] < 0.25)
-poll_under_25 <- specify_decimal((poll_under_25[[1]] + poll_under_25[[2]] + poll_under_25[[3]] +
-poll_under_25[[4]] + poll_under_25[[5]] + poll_under_25[[6]])/6*100,2)
-#[1] 32.57576
-
-colMeans(heat_pollinators[,c(3:8)] > 0.75)
-poll_over_75 <- colMeans(heat_pollinators[,c(3:8)] > 0.75)
-poll_over_75 <- specify_decimal((poll_over_75[[1]] + poll_over_75[[2]] + poll_over_75[[3]] +
-    poll_over_75[[4]] + poll_over_75[[5]] + poll_over_75[[6]])/6*100,2)
-#[1] 4.545455
-
-#################################################################################
-#################################################################################
-
-colnames(heat_plants)<- c("position", "Broad_categories", "one",
-                               "two", "three","four",
-                               "five")
-f <- heat_plants %>%
-  mutate(min = pmin(1,
-                    one, two,three,
-                    four, five))%>%
-  mutate(max = pmax(one,
-                    two, three,four,
-                    five))
-
-diff_1 <- f$max-f$min
-
-cbind(diff,diff_1)
-
-#Check percentage of over and under represented per FG
-colMeans(heat_plants[,c(3:7)] < 0.25)
-plant_under_25 <- colMeans(heat_plants[,c(3:7)] < 0.25)
-plant_under_25 <- specify_decimal((plant_under_25[[1]] + plant_under_25[[2]] + plant_under_25[[3]] + 
-    plant_under_25[[4]] + plant_under_25[[5]])/5*100,2)
-#[1] 18.18182
-colMeans(heat_plants[,c(3:7)] > 0.75)
-plant_over_75 <- colMeans(heat_plants[,c(3:7)] > 0.75)
-plant_over_75 <- specify_decimal((plant_over_75[[1]] + plant_over_75[[2]] + plant_over_75[[3]] + 
-    plant_over_75[[4]] + plant_over_75[[5]])/5*100,2)
-#[1] 8.181818
-
-#overall percentages
-under <- specify_decimal((as.numeric(poll_under_25) + as.numeric(plant_under_25))/2,2)
-over <- specify_decimal((as.numeric(poll_over_75) + as.numeric(plant_over_75))/2,2)
-
-```
-
-The comparison of the plant and floral visitor functional group frequencies per subgraph position between empirical and simulated networks showed a `r over`$\%$ and `r under`$\%$ of over- (>75$^{th}$) and under-represented (\<25th) functional groups in the different positions, respectively (Fig.
-3).
-Floral visitors showed a total of `r poll_over_75`$\%$ and `r poll_under_25`$\%$ of over- and under-represented functional groups in the different positions, and plants `r plant_over_75`$\%$ and `r plant_under_25`$\%$ of over- and under-represented functional groups, respectively.
-Notably, the differences across functional groups were more marked for floral visitors than for plants (the differences between the minimum and maximum values of the percentiles per position were generally two-three times larger for floral visitors).
-From most over- to under-represented floral visitors functional groups on the different subgraph positions (indicated with the dendrogram order in Fig.
-3), we found: bees, non-syrphids Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.
-Although plant functional groups showed less differences between them, there were also more represented functional groups than others.
-Thus, from most over- to under-represented functional groups on the different subgraph positions we found: self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.
-
-For both floral visitor and plant functional groups we found over- and under-representation on different subgraph positions that implied different ecological roles.
-First, for floral visitors, we found that bees were less frequent on subgraph positions that involved specialisation (i.e., lower specificity values) while the rest of functional groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) were infrequent in generalised subgraph positions with low number of indirect interactions (Fig.
-S6 A).
-Although plants did not show differences with null models on their frequencies, all plant functional groups but tall plants with small unisexual flowers showed a slight tendency to be over-represented on specialised subgraph positions (Fig.
-S6 B).
-Second, regarding the number of indirect interactions, bees were over-represented in subgraph positions with low number of indirect interactions (Fig.
-S7 A) and the rest of floral visitor functional groups showed no differences across positions in comparison with simulated networks.
-For plants, all functional groups showed a slight tendency to be over-represented on subgraph positions with higher number of indirect interactions (Fig.
-S7 B).
-When we further explore the observed frequencies by number of indirect interactions for floral visitor and plant functional groups, we found that both bees and tall plants with small unisexual flowers were the only functional groups with high frequencies on subgraph positions associated with low number of indirect interactions in comparison with the other floral visitor and plant functional groups (Figs S8 and S9).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', out.width="80%",fig.cap="\\textbf{Figure 3.} Heatmap indicating under- and over-representation of floral visitor and plant functional groups in the different subgraph positions (numbers on the right of each heatmap).
-The different subgraph positions are dividied by the average path length clasification determined by Simmons et al.
-(2020) and they are ordered from the most densely connected network structures (strong or complete) to the less connected ones (weak or core-peripheral).
-The superior dendrogram indicates the differences across functional groups with the more separated groups showing larger differences."}
-
-library(lme4)
-library(nlme)
-library(tidyverse)
-library(stringi)
-source("../../Scripts/Scripts_Alfonso/add_study_id.R")
-
-#############################################
-# EXTRACT MEAN VALUES
-#############################################
-
-all_position_percentiles <- read_csv("../../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
-
-all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
-                                                              "[0-9]+") %>% as.numeric()
-
-all_position_percentiles <- add_study_id(all_position_percentiles)
-#str(all_position_percentiles)
-#head(all_position_percentiles)
-
-list_plants_FG <- as.character(1:10)
-
-plant_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF)) #ME DA ERROR
-pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF))
-
-# Plants-------------
-
-# Mean percentile and SE taking into account the study system
-plant_codes <- plant_position_percentiles_filtered$position %>% unique()
-plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-plant_means$mean <- NA
-plant_means$SE <- NA
-
-for(i.pos in 1:length(plant_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
-            data = plant_position_percentiles_filtered %>%
-              filter(position == plant_codes[i.pos]))
-
-  temp <- fixed.effects(m) %>% unname()
-  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
-                                                                    temp[1]+temp[2],
-                                                                    temp[1]+temp[3],
-                                                                    temp[1]+temp[4],
-                                                                    temp[1]+temp[5]) ## to get real means per FG
-  temp <- sqrt(diag(vcov(m)))
-  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
-                                                                  temp[1]+temp[2],
-                                                                  temp[1]+temp[3],
-                                                                  temp[1]+temp[4],
-                                                                  temp[1]+temp[5])
-
-}
-
-# Pollinators--------
-
-# Mean percentile and SE taking into account the study system
-pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
-pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-pollinator_means$mean <- NA
-pollinator_means$SE <- NA
-pollinator_means_reordered <- NULL
-
-for(i.pos in 1:length(pollinator_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = pollinator_position_percentiles_filtered %>%
-              filter(position == pollinator_codes[i.pos]),
-            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
-
-  temp <- fixed.effects(m) %>% unname()
-  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)
-
-  pollinator_means_aux$mean <- c(temp[1],
-                                 temp[1]+temp[2],
-                                 temp[1]+temp[3],
-                                 temp[1]+temp[4],
-                                 temp[1]+temp[5],
-                                 temp[1]+temp[6],
-                                 temp[1]+temp[7],
-                                 temp[1]+temp[8],
-                                 temp[1]+temp[9]) ## to get real means per FG
-
-  temp <- sqrt(diag(vcov(m)))
-  pollinator_means_aux$SE <- c(temp[1],
-                               temp[1]+temp[2],
-                               temp[1]+temp[3],
-                               temp[1]+temp[4],
-                               temp[1]+temp[5],
-                               temp[1]+temp[6],
-                               temp[1]+temp[7],
-                               temp[1]+temp[8],
-                               temp[1]+temp[9])
-
-  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)
-
-}
-
-# There are lower limits (mean - SE) smaller than 0 (see Other insects)
-# We set the lower limit of those error bars to zero
-
-pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
-pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
-
-#############################################
-# ADDING BROAD MOTIF CATEGORIES TO POSITIONS
-#############################################
-
-motifs_raw_data <- read_csv("../../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-motifs_raw_data$Broad_categories <- NA
-
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(5,9,14,13,10)] <- "Core-peripherical"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(6,16,12)] <- "Complete"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(2,3,7,4,17,8)] <- "Fan"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(15,11)] <- "Asymmetric complete"
-
-motifs_raw_data$plant <- gsub("[^0-9.-]", "", motifs_raw_data$plant)
-motifs_raw_data$pollinator <- gsub("[^0-9.-]", "", motifs_raw_data$pollinator)
-motifs_raw_data$plant <- as.numeric(motifs_raw_data$plant)
-motifs_raw_data$pollinator <- as.numeric(motifs_raw_data$pollinator)
-motifs_raw_data <- motifs_raw_data %>% filter(!is.na(Broad_categories))
-
-fan_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-pollinator_means_reordered$Broad_categories <- NA
-
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% fan_pollinator] <- "Fan" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% asymm_pollinator] <- "Medium-weak" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% complete_pollinator] <- "Strong" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% core_per_pollinator] <- "Weak"
-
-fan_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-plant_means$Broad_categories <- NA
-
-plant_means$Broad_categories[plant_means$position %in% fan_plant] <- "Fan" 
-plant_means$Broad_categories[plant_means$position %in% asymm_plant] <- "Medium-weak" 
-plant_means$Broad_categories[plant_means$position %in% complete_plant] <- "Strong" 
-plant_means$Broad_categories[plant_means$position %in% core_per_plant] <- "Weak"
-
-########################################
-# CREATE HEATMAPS
-########################################
-
-library(ComplexHeatmap)
-
-# PLANTS-----
-
-# Prepare data for heatmap
-heat_plants_aux <- plant_means %>% spread(Node_FG,mean) %>% select(-SE)
-
-heat_plants <- heat_plants_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-heat_plants_fan <- heat_plants %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_fan) <- heat_plants_fan[,1]
-
-heat_plants_Weak <- heat_plants %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Weak) <- heat_plants_Weak[,1]
-
-heat_plants_Strong <- heat_plants %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Strong) <- heat_plants_Strong[,1]
-
-heat_plants_Medium_weak <- heat_plants %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Medium_weak) <- heat_plants_Medium_weak[,1]
-
-# POLLINATORS-----------
-
-filter_rare_groups <- T
-
-if(filter_rare_groups == T){
-  heat_pollinators_aux <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds",
-                                                                                "Lizards",
-                                                                                "Other_insects")) %>% 
-    spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees",            
-                                      "Coleoptera","Lepidoptera","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Syrphids")
-}else{
-  heat_pollinators_aux <- pollinator_means_reordered %>% spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees","Birds",            
-                                      "Coleoptera","Lepidoptera","Lizards","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Other insects","Syrphids")
-}
-
-heat_pollinators <- heat_pollinators_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-heat_pollinators_fan <- heat_pollinators %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_fan) <- heat_pollinators_fan[,1]
-
-heat_pollinators_Weak <- heat_pollinators %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Weak) <- heat_pollinators_Weak[,1]
-
-heat_pollinators_Strong <- heat_pollinators %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Strong) <- heat_pollinators_Strong[,1]
-
-heat_pollinators_Medium_weak <- heat_pollinators %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Medium_weak) <- heat_pollinators_Medium_weak[,1]
-
-##################
-
-#Do not know how to handle this multiplot for creating a panel
-
-# I'm going to create the 4 plots in one, 
-# I'm not sure that the grouping of the functional group is correct
-# when is done separately
-
-#sorry for the mess of libraries that I do below
-
-#Prepare first pollinators
-
-library(tidyr)
-library(data.table)
-long <- melt(setDT(heat_pollinators), id.vars = c("position","Broad_categories"), variable.name = "guilds")
-
-long_1 <- long %>% select(-Broad_categories)
-
-library(reshape2)
-long_m <- acast(long_1, position~guilds, value.var="value")
-
-#set manually the divisions, so far this is the best way I have seen to split the rows by categories
-
-r_split <- c(rep(c("Medium"), 3),rep(c("Weak"), 2),"Strong",rep(c("Medium"),2),rep(c("Weak"), 4),
-             rep(c("Medium-weak"), 2), "Strong", rep(c("Weak"), 3),rep(c("Medium-weak"), 2),
-             "Strong", "Medium")
-
-#set order of labels that avoids overlapping
-
-r_split <- factor(r_split, levels=c("Strong","Medium","Medium-weak","Weak"))
-
-#plat a bit with colors, a bit of a more complex set but looks nicer
-library(circlize)
-col_fun = colorRamp2(c(0.05644663,0.25, 0.4673256,0.75, 0.8782047), c("blue","cadetblue3", "azure2", "gold","red"))
-
-h_pol <- Heatmap(long_m, name = "Mean\npercentile", row_split=r_split,cluster_row_slices = FALSE, 
-                 column_title = "Pollinator functional groups",row_names_gp = gpar(fontsize = 10),
-                 col = col_fun,column_names_rot = 45,  column_names_gp = grid::gpar(fontsize = 10),
-                 column_title_gp = gpar(fontsize = 15, fontface = "bold"),
-                 row_title_gp = gpar(fontsize = 10, fontface = "bold"))
-
-#Prepare plants
-
-#long format
-long_plants <- melt(setDT(heat_plants), id.vars = c("position","Broad_categories"), variable.name = "Functional_groups")
-
-#filter for creating matrix
-long_plants_1 <- long_plants %>% select(-Broad_categories)
-
-#set better colnames
-long_plants_1$Functional_groups <- as.character(long_plants_1$Functional_groups)
-
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==1] <- "Selfing herbs" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==2] <- "Small outcrossing\nperennials" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==3] <- "Self-incomp. perennials\nwith large flowers" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==4] <- "Tall plants with small\nunisexual flowers" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==5] <- "Short-lived outcrossers with\nlong zygomorphic flowers"
-
-long_plants_1$Functional_groups <- factor(long_plants_1$Functional_groups, levels=c("Selfing herbs",
-"Small outcrossing\nperennials" ,"Self-incomp. perennials\nwith large flowers",
-"Tall plants with small\nunisexual flowers" ,"Short-lived outcrossers with\nlong zygomorphic flowers" ))
-
-#create matrix with reshape
-long_plants_m <- acast(long_plants_1, position~Functional_groups, value.var="value")
-
-r_split_plants <- c(rep(c("Medium"), 3),rep(c("Weak"), 2),"Strong",rep(c("Medium"),2),rep(c("Weak"), 3),
-                    rep(c("Medium-weak"), 2), "Strong", rep(c("Weak"), 4),rep(c("Medium-weak"), 2),
-                    "Strong", "Medium")
-
-r_split_plants <- factor(r_split, levels=c("Strong","Medium","Medium-weak","Weak"))
-
-h_plan <- Heatmap(long_plants_m, name = "Mean\npercentile", row_split=r_split_plants,cluster_row_slices = F, 
-                  column_title = "Plant functional groups",row_names_gp = gpar(fontsize = 10),col = col_fun,column_names_rot = 45,  
-                  column_names_gp = grid::gpar(fontsize = 10),column_title_gp = gpar(fontsize = 15, fontface = "bold"),
-                  row_title_gp = gpar(fontsize = 10, fontface = "bold"))
-
-library(patchwork)
-ht_list <- h_pol+h_plan
-
-draw(ht_list, auto_adjust = FALSE, cluster_rows = F)
-
-#Exploration of min max differences in the percentile position for plants and poll.
-#heat_pollinators[3:8]
-#
-#
-#heat_plants[3:7]
-#
-#
-#library(dplyr)
-#heat_pollinators %>%
-#  mutate(d = pmin())
-#
-#
-#colnames(heat_pollinators)<- c("position", "Broad_categories", "Bee",
-#                               "Coleoptera", "Lepidoptera","non_bee_hymenop",
-#                               "non_syrphid_dip", "syrphid")
-#
-#h <- heat_pollinators %>%
-#  mutate(min = pmin(Bee,
-#                  Coleoptera, Lepidoptera,non_bee_hymenop,
-#                  non_syrphid_dip, syrphid))%>%
-#  mutate(max = pmax(Bee,
-#                    Coleoptera, Lepidoptera,non_bee_hymenop,
-#                    non_syrphid_dip, syrphid))
-#
-#diff <- h$max-h$min
-#
-##################################################################################
-##################################################################################
-#
-#colnames(heat_plants)<- c("position", "Broad_categories", "one",
-#                               "two", "three","four",
-#                               "five")
-#
-#f <- heat_plants %>%
-#  mutate(min = pmin(1,
-#                    one, two,three,
-#                    four, five))%>%
-#  mutate(max = pmax(one,
-#                    two, three,four,
-#                    five))
-#
-#diff_1 <- f$max-f$min
-#
-#cbind(diff,diff_1)
-#
-
-```
-
-**Over- and under-represented functional group combinations of subgraphs**
-
-The different observed frequencies on the different subgraph positions showed a hierarchical order of probabilities for floral visitor functional groups (Fig.
-4).
-From the highest to lowest observed probabilities overall, we found: bees, non-syrphid Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.
-On the contrary, plant functional groups were more variable on the different subgraph positions.
-However, there were also predominant functional groups found across the different subgraph positions.
-The three most frequent groups were 'tall plants with small unisexual flowers', 'self-incompatible perennials with large flowers' and 'small outcrossing perennials'.
-On the contrary, the groups of 'selfing herbs' and 'short lived outcrossers with long zygomorphic flowers' had the lowest probability to be present on the different subgraph plant positions.
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 4.** Graphical representation of the probability of finding a given plant and floral visitor functional group $x$ in the position $\\alpha$ of motif $i$, $p_i(x,\\alpha)$, for all the possible network subgraphs from two to five species in bipartite networks.
-The slices in the nodes for a given functional group $x$ are proportional to the corresponding value of $p_i(x,\\alpha)$."}
+```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=9, fig.width=13, fig.cap=""}
 
@@
 
-(p1 & ylab("2 species")| p2 & ylab("3 species") | p3  |plot_spacer()|plot_spacer())/ 
+patch <- (p1 & ylab("2 species")| p2 & ylab("3 species") | p3  |plot_spacer()|plot_spacer())/ 
   (p4 & ylab("4 species")| p5 | p6 | p7|plot_spacer())/ 
@@
 
-```
+patch + plot_annotation(title = 'MESO-SCALE FUNCTIONAL GROUP PROBABILITIES',
+  theme = theme(plot.title = element_text(size = 18, face="bold"))) + 
+  theme(text = element_text('mono'))
 
-The statistical comparison with z-scores between the observed and expected plant and floral visitor functional group combinations showed that we can not recover the observed combinations from its probability of occurrence.
-In fact, most combinations are under- or over- represented and follow a modified Gaussian distribution (Johnson's $S_U$) with 65$\%$ of under-represented group combinations, 20$\%$ of no statistical difference and 15$\%$ of under-represented ones (Fig.
-5).
-In addition, subgraphs with small node combinations (i.e., 2 and 3 nodes) only appeared as under-represented.
-Network subgraphs with 4 and 5 node combinations appeared in the three statistical categories, but 4 node subgraphs had a higher proportion in the under-represented category (10% in comparison with the 1$\%$ and the 3$\%$ of the no statistical difference and over-represented categories, respectively).
-Finally, 5 node subgraphs were in similar proportions in the no statistical difference and over-represented categories (99$\%$ and 97$\%$, respectively), but they appeared in lower proportion in the under-represented category (89$\%$).
-When we explored the identity on the different positions of the most probable subgraph combinations, we found that the most common plant and floral visitor functional groups were also the most probable on these plant and floral visitor combinations within the different subgraphs (lower panel Fig.
-5).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 5.** Distribution of z-scores values after the statistical comparison of the observed probabilities of finding a subgraph combination in real networks and the expected probabilities (obtained by computer simulations).
-The resulting z-scores frequencies of this statiscal comparison are coloured based on a 95% confidence level: under-represented ($z_i^O < -1.96$, red), no statistical difference ($-1.96 \\geq z_i^O \\leq  1.96$, green) and over-represented ($z_i^O > 1.96$, blue).
-For instance, for a z-score value of 0 there were approximately 800 subgraph combinations that showed no statistical difference in the comparison between real and simulated networks.
-In addition, four specific graphical examples of the most probable subgraphs being observed on each category are also provided and the different plant and floral visitor functional groups are represented with distinct colour codes as indicated in the legend."}
-
-library(tidyverse)
-library(RColorBrewer)
-
-equidistribution <- function(number_nodes){
-
-  x_width <- 5.5/(number_nodes+1)
-
-  x_result <- rep(-1.5,number_nodes)
-
-  for(i in 1:number_nodes){
-
-    x_result[i] <- x_result[i] + i*x_width
-
-  }
-
-  return(x_result)
-
-}
-
-plot_motif_label <- function(label){
-
-  label_split <- str_split(label,"_")[[1]]
-  motif_number <- as.numeric(label_split[1])
-  nodes <- label_split[2:length(label_split)]
-  plant_nodes <- nodes[nodes %in% plant_means_reordered$Node_FG]
-  pollinator_nodes <- nodes[nodes %in% pollinator_means_reordered$Node_FG]
-
-  motifs_raw_data <-read_csv("../../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-  motif_data <- motifs_raw_data %>% filter(motif_id == motif_number)
-
-  # Create dataframe with node positions
-
-  labdown = motif_data$plant %>% unique()
-
-  xdown = equidistribution(length(labdown))
-
-  ydown = rep(0,length(labdown))
-
-  labup = motif_data$pollinator %>% unique()
-
-  xup = equidistribution(length(labup))
-
-  yup = rep(1,length(labup))
-
-  d_nodes=data.frame(x=c(xdown,xup),
-                     y=c(ydown,yup),
-                     label = c(labdown,labup))
-
-  # Create a dataframe with links
-
-  plant_positions <- data.frame(plant = labdown,
-                                xdown = xdown,
-                                ydown = ydown)
-
-  pollinator_positions <- data.frame(pollinator = labup,
-                                     xup = xup,
-                                     yup = yup)
-
-  link_df <- motif_data %>% left_join(plant_positions, by = "plant") %>% 
-    left_join(pollinator_positions, by = "pollinator")
-
-  # Add FG IDs to nodes
-  FG_IDs <- tibble(label = c(sort(labdown),sort(labup)),
-                   FG = c(plant_nodes,pollinator_nodes))
-
-  d_nodes_FG <- d_nodes %>% left_join(FG_IDs, by = "label")
-  levels_FG <- c("Bee","Coleoptera","Lepidoptera",
-                 "Non-bee-Hymenoptera", "Non-syrphids-diptera",
-                 "Syrphids","1","2","3","4","5")
-
-  d_nodes_FG$FG <- factor(d_nodes_FG$FG, levels = levels_FG)
-
-  levels(d_nodes_FG$FG) <- c("Bee","Coleoptera","Lepidoptera",
-                             "Non-bee-Hymenoptera", "Non-syrphids-diptera",
-                             "Syrphids","1","2","3","4","5")
-
-  # Before plotting the motif, we remove letters from the node position id
-
-  d_nodes_FG$label <- gsub("[^0-9.-]", "", d_nodes_FG$label)
-
-  # Define the number of colors you want
- mycolors <- c("#A6CEE3", "chocolate2",  "gold2", "#1F78B4","#B2DF8A",
-                     "gray58", "lightgoldenrod2","thistle2", "burlywood","lightcoral", "olivedrab3")
-
-  ggplot(data=d_nodes_FG, aes(x, y)) +
-    scale_shape_identity() +
-    geom_segment(data = link_df, aes(x=xdown, y=ydown, xend = xup, yend = yup), size = 1, color = "grey20")+
-    geom_point(aes(color = FG), size=7.5)+
-    geom_text(aes(x, y , label = label), size=3)+
-    scale_color_manual(drop = FALSE, values = mycolors,
-                       breaks=c("Bee","Coleoptera","Lepidoptera",
-                                "Non-bee-Hymenoptera", "Non-syrphids-diptera",
-                                "Syrphids","1","2","3","4","5"), 
-                       labels=c("Bees","Coleoptera","Lepidoptera",
-                                "Non-bee-Hymenoptera", "Non-syrphids-Diptera",
-                                "Syrphids", 
-                                "Selfing herbs","Small outcrossing perennials",
-                                "Self-incomp. perennials\nwith large flowers",
-                                "Tall plants with small\nunisexual flowers",
-                                "Short-lived outcrossers with\nlong zygomorphic flowers"))+
-    xlim(-1.5,4)+ ylim(-0.5,1.5)+
-    theme(panel.background = element_blank(),
-          axis.text.x=element_blank(),
-          axis.ticks.x=element_blank(),
-          axis.text.y=element_blank(),
-          axis.ticks.y=element_blank())+
-    labs(x=NULL,y=NULL)+
-    ggtitle(paste0("Motif ",motif_number))+
-    theme(plot.title = element_text(hjust = 0.5,size=10))+
-    guides(color=guide_legend(title="Functional groups"))
-
-}
-
-# Data with pollinator/plant labels
-
-plant_means_reordered <- read_csv("../../Data/Csv/plant_abs_freq_means.csv")
-pollinator_means_reordered <- read_csv("../../Data/Csv/pollinator_abs_freq_means.csv")
-#Filter out in order to have just 6 FG'S
-pollinator_means_reordered <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds", "Lizards", "Other_insects"))
-
-####################################################################################################
-#Read data to check top 5 motif of each category of observed propabilities
-
-#Under, No signi, Over-rep
-####################################################################################################
-# Check top Z-scores of each group (Under, No diff, Over)
-
-#Read data
-data <- read.csv("../../Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
-
-#Find critical value of Z-score
-p <- 0.05 #cutoff probability 95% confidence
-critical_value <- qnorm(p/2) #double tail probability divide by 2
-
-data_1 <- data %>%
-  mutate(infra_over_represented = case_when(
-    z_score < -abs(critical_value) ~ "infra",
-    between(z_score, -abs(critical_value), abs(critical_value)) ~ "no_diff",
-    z_score > abs(critical_value) ~ "over"
-  ))
-
-#data_2 <- filter(data_1, abs(z_score)<2000) 
-#str(data_2)
-
-#Select under-represented by the ones with highest porbability of being observed (top10)
-under_data <- filter(data_1, infra_over_represented=="infra")
-
-under_top_5 <- filter(under_data, row_number(desc(abs(motif_observed_probability)))<= 5) %>%
-  select(motif_functional_ID,motif_observed_probability,counts_observed,z_score)
-
-#Select no statistical difference by the ones with highest porbability of being observed (top5)
-no_diff_data <- filter(data_1, infra_over_represented=="no_diff")
-
-no_diff_top_5 <- filter(no_diff_data, row_number(desc(abs(motif_observed_probability)))<= 5) %>%
-  select(motif_functional_ID,motif_observed_probability,counts_observed,z_score)
-
-#Select over-represenetd by the ones with highest porbability of being observed (top5)
-over_data <- filter(data_1, infra_over_represented=="over")
-
-over_top_5 <- filter(over_data, row_number(desc(abs(motif_observed_probability)))<= 5) %>%
-  select(motif_functional_ID,motif_observed_probability,counts_observed,z_score)
-####################################################################################################
-#Now plot it 
-####################################################################################################
-
-library(patchwork)
-
-#Prepare list of 5 plots for each group
-#Under
-labels_under <- under_top_5$motif_functional_ID
-p_under <- list()
-
-for (i in 1:5){
-
-  p_under[[i]] <- plot_motif_label(labels_under[[i]])
-}
-
-#No signficance
-labels_nodiff <- no_diff_top_5$motif_functional_ID
-p_nodiff <- list()
-
-for (i in 1:5){
-
-  p_nodiff[[i]] <- plot_motif_label(labels_nodiff[[i]])
-}
-
-#Over
-labels_over <- over_top_5$motif_functional_ID
-p_over <- list()
-
-for (i in 1:5){
-
-  p_over[[i]] <- plot_motif_label(labels_over[[i]])
-}
-
-#Run Script with histogram plot
-source("../../Scripts/Z-score_percentile_histogram_plot.R")
-
-hist <- ggplot(data_2 %>% filter(round_motif_observed_probability>0), aes(x=z_score, color=infra_over_represented, fill=infra_over_represented)) + 
-  geom_histogram(bins = 93, alpha = 0.5, position = "identity",lwd = 0.25)+
-  geom_vline(xintercept = -abs(critical_value))+
-  geom_vline(xintercept = abs(critical_value))+
-  xlim(-60,60) + ylab("Frequency")+  theme_bw() +
-  scale_fill_manual(name="Motif frequencies" ,values=c("coral2", "palegreen3", "cyan3"), labels=c("Under-represented",
-                                                                                                  "No statistical difference", "Over-represented")) +
-  scale_color_manual(name="Motif frequencies" ,values=c("coral2", "palegreen3", "cyan3"), labels=c("Under-represented",
-                                                                                                   "No statistical difference", "Over-represented")) + xlab("Z-score")
-
-t_col <- function(color, percent = 50, name = NULL) {
-  #      color = color name
-  #    percent = % transparency
-  #       name = an optional name for the color
-
-  ## Get RGB values for named color
-  rgb.val <- col2rgb(color)
-
-  ## Make new color using input color as base and alpha set by transparency
-  t.col <- rgb(rgb.val[1], rgb.val[2], rgb.val[3],
-               max = 255,
-               alpha = (100 - percent) * 255 / 100,
-               names = name)
-
-  ## Save the color
-  invisible(t.col)
-}
-## END
-
-#Prepare panel of plots
-hist / ((p_under[[1]]/p_under[[2]]/p_under[[3]]/p_under[[4]] & theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_rect(fill=t_col("coral2")))) | 
-          (p_nodiff[[1]]/p_nodiff[[2]]/p_nodiff[[3]]/p_nodiff[[4]]& theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_rect(fill=t_col("palegreen3")))) |
-          (p_over[[1]]/p_over[[2]]/p_over[[3]]/p_over[[4]] & theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_rect(fill=t_col("cyan3"))))) + plot_layout(guides = 'collect')
+ggsave("Figure_4.jpg", dpi=1500)
 
 ```
-
-# Discussion
-
-Understanding the global patterns of network structure is key to unravel the processes that govern community dynamics [@bascompte2007; @bastolla2009; @guimaraes2020].
-However, common analytical approaches at the node or at the global network level are unable to capture the full complexity of ecological systems [@simmons2019; @bergamo2021].
-Because network subgraphs can capture both direct and indirect interactions, by analysing their over- and under-representation we were able to explore in great detail the structure of interactions between animal pollinators and the plants they visit.
-We have explored for the first time the overall structure and presence of network motifs in real plant-pollinator networks and shown that, according to our first hypothesis, the different subgraphs up to five nodes are consistently over- or under-represented in comparison with simulated networks.
-In addition, we show that for plant-pollinator networks there is a general tendency for over-representation of network subgraphs that are more densely connected (i.e., complete, fan and asymmetric complete).
-Indeed, the work of @simmons2020 has shown with the help of simulated plant-pollinator networks that the main different processes that shape plant-pollinator communities (i.e., neutral effects, trait matching and phenology) generate different patterns of direct and indirect interactions, and that specifically, a higher proportion of these more densely connected subgraphs is associated with neutral effects.
-Therefore, as indicated for other network properties like nestedness at the macro-scale level [@krishna2008; @suweis2013], or interaction probability at the species level [@bartomeus2016], our findings align with our second hypothesis and indicate that neutral effects may be also the main driver governing this intermediate level of complexity on plant-pollinator networks.
-
-Overall, generalist network motifs for floral visitors were consistently over-represented (e.g., complete subgraphs; Fig.
-2).
-For instance, when we compare network subgraphs with equal structure for both trophic levels, we found that floral visitors had always over-representation in the positions that implied the highest number of direct links (e.g., positions 16 and 46 from network subgraphs 7 and 17, respectively).
-Despite this being in good agreement with the current view of the generalist nature of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of generalist network motifs was driven by the functional group of bees while the rest of the functional groups tended to be under-represented (Fig.
-S6 A).
-In contrast, non-bee groups were over-represented in subgraph positions associated with specialised roles.
-This large effect of bees on the overall patterns is no surprise, as bees were the group with the largest number of interaction records in the whole set of networks as also shown for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017].
-Just syrphids had a relatively similar number of interactions in comparison with bees (1,768 and 2,256 interactions, respectively) and similar species richness (343 and 321 species, respectively).
-However, both functional groups were associated with contrasting ecological roles likely indicating that both number of interactions and richness are not driving the observed interaction patterns for the different functional groups.
-Interestingly, bees also were the group with lower number of indirect interactions, while the rest of floral visitor groups showed a clearly higher number of indirect interactions, indicating that these non-bee floral visitor groups may experience higher competitive interactions for floral resources [@thomson2020].
-Despite plant functional groups showed little differences between them on their subgraph frequencies, all groups showed a tendency to be over-represented on subgraph positions that were associated with higher levels of specialisation.
-This tendency towards specialist roles may be the result of co-evolutionary processes (e.g., trait-matching) between plants and pollinators to optimise pollen transfer [@moreira2019].
-Remarkably, only tall plants with small unisexual flowers showed higher frequencies on subgraphs that were associated with low number of indirect interactions with likely direct implications on pollen transfer for this group that needs to guarantee cross-pollination.
-
-The probabilities of appearance of each functional group on the different subgraph positions were insufficient to predict most of the observed network position combinations (Fig.
-5).
-This implies that not just the representation of network subgraphs types but also the identity of the elements of their structure is non-random.
-Notably, we found that just 30$\%$ of the possible 53,250 subgraph combinations are realised.
-Thus, similarly to the presence of forbidden links at the network level [@olesen2011; @jordano2016], we also found the existence of forbidden subgraph positions and those represented almost two thirds of the total possible subgraph combinations.
-This concurs well with the general idea that plant-pollinator networks have a high proportion of non-realized direct interactions [@jordano2003; @bascompte2013], and, as a result, also a high proportion of non-realized combinations of indirect interactions.
-Some of these non-observed direct interactions are probably due to under-sampling [@dorado2011; @jordano2016].
-However, a large fraction of the possible interactions do not take place because of different constraints such as species co-occurrence, trait matching processes and phenological uncoupling [@olesen2011; @bartomeus2016; @jordano2016].
-Despite the advances in the understanding of the ecological processes that influence species pairwise interactions [@bartomeus2016; @peralta2020], we still know little about how these processes determine competitive and facilitative interactions in mutualistic networks.
-Thus, as suggested by @simmons2020, exploring the proportion of these realised network subgraphs that are competitive or facilitative is a necessary next step to improve our understanding of the architecture of biodiversity [@bascompte2007].
-
-Despite the obvious usefulness of functional groups in summarising species ecological roles (e.g., similar reproductive biology for plants and behaviour for pollinators), delimiting species into functional groups is often not trivial.
-For instance, taxonomic diversity and trait availability limit our ability to properly represent the wide range of reproductive strategies [@dellinger2020] and different clustering analysis can lead to distinct outcomes (e.g., k-means and hierarchical clustering).
-We divided floral visitors on the taxonomic rank level because it adequately represented pollinator ecological roles without the tremendous effort of compiling trait data for over 1,000 species of floral visitors.
-Indeed, further groupings with traits could help reveal greater relevance of trait-matching processes on indirect interactions.
-Moreover, we analysed network subgraphs focusing exclusively on presence or absence of interactions, assuming that all interactions are equally important.
-However, further work should investigate how to account for quantitative measurements of plant-pollinator interactions.
-Consistent with previous work [@simmons2019; @simmons2020], we characterised network motifs by using null models only constrained for network connectance.
-Although more complex null models are difficult to interpret [@Ulrich2013], they can potentially allow us to separate the mechanisms by which motifs emerge.
-However, we found that null models with more constraints generated binary structures that were mostly identical to the original ones.
-In addition, we observed that connectance, nestedness and degree distribution were significantly correlated (data not shown).
-All that highlights the difficulties to disentangle the potential sources that generate over-representation of network subgraphs and the need to investigate them.
-At the same time, although network subgraphs can capture both direct and indirect interactions, the reduction of network complexity into these different building blocks inevitably convey the loss of information [@simmons2019], for example indirect interactions from large cascading effects.
-Finally, despite the wide geographical coverage of our plant-pollinator dataset, there are major gaps for some regions of the world with a clear bias towards Europe, America and islands which have long interested ecologists [@macarthur1963; @warren2015].
-These biases are also found in global datasets of networks, where the data is highly fragmented across space [@poisot2021] and more efforts are needed to capture global patterns of plant-pollinator interactions.
-
-In conclusion, by following the framework of @simmons2020 we have been able to explore competitive and facilitative interactions in plant-pollinator networks worldwide and found the presence of worldwide motifs that highlight the non-random structure of indirect interactions.
-This non-random structure might emerge due to neutral effects according to previous modelling work [@simmons2020].
-Further, we found that plant and floral visitor functional groups are associated with different subgraph positions that involve distinct ecological roles (e.g., generalisation versus specialisation) and that the different subgraph combinations are strongly constrained.
-Although we are still far from predicting how species interact, our work is a first step to elucidate beyond pairwise interactions.
-
-# Acknowledgements
-
-This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2).
-JBL also thanks the University of New England for the funding provided to carry out this work.
-Finally, we would like to thank David García-Callejas for his useful comments on the manuscript before submission.
-
-# Author contributions
-
-IB, AA-P and JBL designed the idea. JBL collected the data. AA-P led the analysis with contributions of JBL and guidance of IB. JBL wrote the manuscript with contributions of IB and AA-P.
-
-# Data Availability Statement
-
-All data and code are publicly available at Github (<https://github.com/JoseBSL/FunctionalMotifs>) and Zenodo (<https://doi.org/10.5281/zenodo.6489213>).
-
-\newpage
-
-# References
-
-::: {#refs}
-:::

### 2022-10-08 Manuscript/Main_text/for_word_count.Rmd
Graphical abstract and word doc for word count

--- 2022-10-08 Manuscript/Main_text/Main_text_Journal_of_Animal_Ecol.Rmd
@@
 output:
+  word_document: default
+  html_document: default
   pdf_document: default
-  html_document: default
-  word_document: default
 always_allow_html: true
@@
 
+# Conflict of interest declaration.
+
+The authors declare no conflict of interest
+
 # Author contributions

### 2023-01-08 Manuscript/Main_text/Main_text_Journal_of_Animal_Ecol.Rmd
Graphical abstract and word doc for word count
edits

@@
 All that highlights the difficulties to disentangle the potential sources that generate over-representation of network subgraphs and the need to investigate them.
-At the same time, although network subgraphs can capture both direct and indirect interactions, the reduction of network complexity into these different building blocks inevitably convey the loss of information [@simmons2019], for example indirect interactions from large cascading effects.
+At the same time, although network subgraphs can capture both direct and indirect interactions, the reduction of network complexity into these different building blocks inevitably convey the loss of information [@simmons2019].
+For example, network subgraphs neglect indirect effects emerging from large cascading effects that propagate across them.
 Finally, despite the wide geographical coverage of our plant-pollinator dataset, there are major gaps for some regions of the world with a clear bias towards Europe, America and islands which have long interested ecologists [@macarthur1963; @warren2015].
@@
 
+# Conflict of interest declaration
+
+The authors declare no conflict of interest.
+
 # Author contributions

### 2023-01-09 Manuscript/Main_text/Main_text_Journal_of_Animal_Ecol.Rmd
adding some reviewer suggestions

@@
 Indirect interactions, the mediated effect between two species by a third species, are ubiquitous in natural systems [@strauss1991; @holt1994; @wootton1994] and play a key role in shaping community dynamics [@werner2003; @walsh2013].
-Some of the most studied indirect interactions are the ones caused by trophic cascades with consumer-resource interactions [@abrams1996; @schmitz2001].
-In fact, previous studies focus on antagonistic interactions and mutualistic interactions are often overlooked [@knight2005].
-On the contrary, plant-pollinator research has traditionally investigated direct interactions but neglected indirect effects such as competitive or facilitative processes between plants for pollinators [@moeller2004; @sargent2008; @carvalheiro2014].
-Conventional analytical tools in bipartite networks often discard relevant information about indirect interactions by condensing the information into single indices either at species or network level [@cirtwill2018; @simmons2019].
+Although some of the most studied indirect interactions are the ones caused by trophic cascades with consumer-resource interactions [@abrams1996; @schmitz2001; @finke2004], there is also a growing body of work that examines the consequences of indirect effects in mutualistic networks [@knight2005; @bastolla2009; @guimaraes2017].
+Traditionally, the study of animal-plant mutualistic networks has commonly focused on direct interactions and overlooked indirect effects such as competitive or facilitative processes  between plants for pollinators [@moeller2004; @sargent2008; @carvalheiro2014].
+In part because conventional analytical tools in bipartite networks often discard relevant information about indirect interactions by condensing the information into single indices either at species or network level [@cirtwill2018; @simmons2019].
 However, as previously explored with three species modules in unipartite food webs [@allesina2008; @stouffer2010], the emergent framework of bipartite subgraphs has proven to be a powerful analytical tool to better understand plant-pollinator community dynamics by capturing both direct and indirect effects [@simmons2019].

### 2023-01-10 Manuscript/Main_text/Main_text_Journal_of_Animal_Ecol.Rmd
Minor changes on introduction and discussion

@@
 Indirect interactions, the mediated effect between two species by a third species, are ubiquitous in natural systems [@strauss1991; @holt1994; @wootton1994] and play a key role in shaping community dynamics [@werner2003; @walsh2013].
-Although some of the most studied indirect interactions are the ones caused by trophic cascades with consumer-resource interactions [@abrams1996; @schmitz2001; @finke2004], there is also a growing body of work that examines the consequences of indirect effects in mutualistic networks [@knight2005; @bastolla2009; @guimaraes2017].
-Traditionally, the study of animal-plant mutualistic networks has commonly focused on direct interactions and overlooked indirect effects such as competitive or facilitative processes  between plants for pollinators [@moeller2004; @sargent2008; @carvalheiro2014].
+Although some of the most studied indirect interactions are the ones caused by trophic cascades with consumer-resource interactions [@abrams1996; @schmitz2001; @finke2004], there is also a growing body of work that examines the consequences of indirect effects in mutualistic networks [@knight2005; @bastolla2009; @vieira2015; @guimaraes2017].
+Traditionally, the study of animal-plant mutualistic networks has commonly focused on direct interactions and overlooked indirect effects such as competitive or facilitative processes  between plants for pollinators [but see\, @bergamo2021; @moeller2004; @sargent2008; @carvalheiro2014].
 In part because conventional analytical tools in bipartite networks often discard relevant information about indirect interactions by condensing the information into single indices either at species or network level [@cirtwill2018; @simmons2019].

### 2023-01-13 Manuscript/Main_text/Main_text_Journal_of_Animal_Ecol.Rmd
Minor edit on data availability statement

@@
 
-IB, AA-P and JBL designed the idea. JBL collected the data. AA-P led the analysis with contributions of JBL and guidance of IB. JBL wrote the manuscript with contributions of IB and AA-P.
+All authors designed the idea.
+Jose B.
+Lanuza collected the data.
+Alfonso Allen-Perkins led the analysis with contributions of Jose B.
+Lanuza and guidance of Ignasi Bartomeus.
+Jose B.
+Lanuza wrote the manuscript with contributions of Ignasi Bartomeus and Alfonso Allen-Perkins.
 
@@
 
-All data and code are publicly available at Github (<https://github.com/JoseBSL/FunctionalMotifs>) and Zenodo (<https://doi.org/10.5281/zenodo.6489213>).
-
+Data and code available from the online repositories Zenodo  <https://doi.org/10.5281/zenodo.6489213> [@zenodo2022] and Github <https://github.com/JoseBSL/FunctionalMotifs>.
 \newpage

### 2023-01-17 Manuscript/Main_text/Main_text_Journal_of_Animal_Ecol.Rmd
Changing abstract to fit Journal format and changing the term 'motif' per 'subgraph' in figures 1,4 and 5.

@@
 
+1.
 Ecological processes leave distinct structural imprints on the species interactions that shape the topology of animal-plant mutualistic networks.
 Detecting how direct and indirect interactions between animals and plants are organised is not trivial since they go beyond pairwise interactions, but may get blurred when considering global network descriptors.
+
+2.
 Recent work has shown that the meso-scale, the intermediate level of network complexity between the species and the global network, can capture this important information.
@@
 Although motifs can capture relevant ecological information of species interactions, they remain overlooked in natural plant-pollinator networks.
+
+3.
 By exploring 60 empirical plant-pollinator networks from 18 different studies with wide geographical coverage, we show that some network subgraphs are consistently under- or over-represented, suggesting the presence of worldwide network motifs in plant-pollinator networks.
@@
 Finally, we show that the observed functional group combinations within a subgraph can not be retrieved from their expected probabilities (i.e., joint probability distributions), indicating that plant and floral visitor associations within subgraphs are not random either.
-Therefore, our results highlight the presence of common network motifs in plant-pollinator communities that are formed by a non-random association of plants and floral visitors functional groups.
+
+4. Our results highlight the presence of common network motifs in plant-pollinator communities that are formed by a non-random association of plants and floral visitors functional groups.
 
@@
     guides(color = FALSE,fill=guide_legend(title="Functional groups"))+
-    ggtitle(paste0("Motif ",motif_number))+
+    ggtitle(paste0("Subgraph ",motif_number))+
     theme(plot.title = element_text(hjust = 0.5),legend.key.size = unit(0.5, 'cm'))+
@@
     labs(x=NULL,y=NULL)+
-    ggtitle(paste0("Motif ",motif_number))+
+    ggtitle(paste0("Subgraph ",motif_number))+
     theme(plot.title = element_text(hjust = 0.5,size=10))+

### 2023-01-17 Scripts/Scripts_Alfonso/plot_motif_positionsV2.R

@@ -75,7 +75,7 @@ plot_motif_positions <- function(motif_number){
           axis.ticks.y=element_blank())+
     labs(x=NULL,y=NULL)+
     guides(color = FALSE)+
-    ggtitle(paste0("Motif ",motif_number))+
+    ggtitle(paste0("Subgraph ",motif_number))+
     theme(plot.title = element_text(hjust = 0.5))
   
   

### 2023-01-25 Manuscript/Figures/Figure1.Rmd
Word file and independent figures for typesetting

--- 2022-10-08 Manuscript/Main_text/Main_text_Journal_of_Animal_Ecol.Rmd
@@
 ---
-title: "The non-random assembly of network motifs in  \nplant-pollinator networks"
 editor_options:
@@
 always_allow_html: true
-bibliography: bibliography.bib
-biblio-style: apalike
-csl: JournalOfAnimalEcology.csl #converted from funct ecol style from zotero styles
 ---
-
-**Jose B. Lanuza^1,2^** \| **Alfonso Allen-Perkins^2,3^** \| **Ignasi Bartomeus^2^**
-
-1 School of Environmental and Rural Science, University of New England, Armidale, New South Wales 2350, Australia.
-
-2 Estación Biológica de Doñana (EBD-CSIC), E-41092 Seville, Spain.
-
-3 Departamento de Ingeniería Eléctrica, Electrónica, Automática y Física Aplicada, ETSIDI, Universidad Politécnica de Madrid, 28040 Madrid, Spain.
-
-\captionsetup[table]{labelformat=empty}
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
-
-# Abstract
-
-\singlespacing
-
-Ecological processes leave distinct structural imprints on the species interactions that shape the topology of animal-plant mutualistic networks.
-Detecting how direct and indirect interactions between animals and plants are organised is not trivial since they go beyond pairwise interactions, but may get blurred when considering global network descriptors.
-Recent work has shown that the meso-scale, the intermediate level of network complexity between the species and the global network, can capture this important information.
-The meso-scale describes network subgraphs representing patterns of direct and indirect interactions between a small number of species, and when these network subgraphs differ statistically from a benchmark, they are often referred to as "network motifs".
-Although motifs can capture relevant ecological information of species interactions, they remain overlooked in natural plant-pollinator networks.
-By exploring 60 empirical plant-pollinator networks from 18 different studies with wide geographical coverage, we show that some network subgraphs are consistently under- or over-represented, suggesting the presence of worldwide network motifs in plant-pollinator networks.
-In addition, we found a higher proportion of densely connected network subgraphs that, based on previous findings, could reflect that species relative abundances are the main driver shaping the structure of the meso-scale on plant-pollinator communities.
-Moreover, we found that distinct subgraph positions describing species ecological roles (e.g., generalisation and number of indirect interactions) are occupied by different groups of animal and plant species representing their main life-history strategies (i.e., functional groups).
-For instance, we found that the functional group of 'bees' was over-represented in subgraph positions with a lower number of indirect interactions in contrast to the rest of floral visitors groups.
-Finally, we show that the observed functional group combinations within a subgraph can not be retrieved from their expected probabilities (i.e., joint probability distributions), indicating that plant and floral visitor associations within subgraphs are not random either.
-Therefore, our results highlight the presence of common network motifs in plant-pollinator communities that are formed by a non-random association of plants and floral visitors functional groups.
-
-Keywords: pollinators, plant-pollinator networks, plant-pollinator interactions, network motifs, indirect interactions, floral visitors
-
-\doublespacing
-
-\newpage
-
-# Introduction
-
-Ecological communities are formed by a plethora of interacting species that form networks of interactions.
-Because of the tremendous complexity of these ecological networks, species interactions are generally condensed in metrics that summarise this information [@guimaraes2020].
-Plant-pollinator interactions are no exception, and they are often studied with indices that aggregate the information at the network (macro-scale) and species level (micro-scale).
-For example, plant-pollinator network level approaches have identified common invariant structural properties across mutualistic networks, including a degree distribution that decays as a truncated power law [@jordano1987], nestedness [@bascompte2003], or modularity [@olesen2007].
-In addition, the local species position within the network can define its degree of selectiveness [@bluthgen2006] or its role in connecting the rest of the community [@olesen2007].
-Despite the unquestionable progress with the use of these metrics at both network and species level, condensing complex information into a single metric implies the loss of relevant ecological information that obscures the understanding of species interactions [@cirtwill2018; @simmons2019].
-
-Indirect interactions, the mediated effect between two species by a third species, are ubiquitous in natural systems [@strauss1991; @holt1994; @wootton1994] and play a key role in shaping community dynamics [@werner2003; @walsh2013].
-Some of the most studied indirect interactions are the ones caused by trophic cascades with consumer-resource interactions [@abrams1996; @schmitz2001].
-In fact, previous studies focus on antagonistic interactions and mutualistic interactions are often overlooked [@knight2005].
-On the contrary, plant-pollinator research has traditionally investigated direct interactions but neglected indirect effects such as competitive or facilitative processes between plants for pollinators [@moeller2004; @sargent2008; @carvalheiro2014].
-Conventional analytical tools in bipartite networks often discard relevant information about indirect interactions by condensing the information into single indices either at species or network level [@cirtwill2018; @simmons2019].
-However, as previously explored with three species modules in unipartite food webs [@allesina2008; @stouffer2010], the emergent framework of bipartite subgraphs has proven to be a powerful analytical tool to better understand plant-pollinator community dynamics by capturing both direct and indirect effects [@simmons2019].
-These network subgraphs that constitute the meso-scale are often referred to as the building blocks of the network and when their numbers occur at higher frequencies than in randomised networks, those are generally defined as 'network motifs' [@milo2002].
-Indeed, the analysis of motifs in simulated plant-pollinator networks has revealed that the different drivers that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect effects [@simmons2020].
-However, the global patterns of indirect interactions in real plant-pollinator networks and their ecological consequences remain unexplored (e.g., over- and under- represented network subgraphs).
-
-By linking the structural properties of the meso-scale with the species' ecology we can advance in our understanding on the determinants of species interactions.
-For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species' functional role [@stouffer2012; @baker2015; @cirtwill2018b].
-Yet, our understanding of the ecological implications of network motifs in real plant-pollinator networks remains in its infancy.
-Moreover, it is unclear how the species ecology and life-history traits determine its functional role within the network of interactions [@coux2016].
-For example, large pollinators can forage larger distances [@greenleaf2007], deposit greater pollen quantities [@foldesi2021] and handle complex zygomorphic flowers in comparison with small pollinators that are restricted to lower floral complexity [@gong2009].
-Despite these obvious differences in pollinator behaviour, how contrasting species' ecology translates into different network motifs is still poorly known.
-Similarly, recent empirical findings indicate that the meso-scale is the best descriptor of plant reproductive success [@allen2021], but little is known about how plants' reproductive strategies shape their position within the network of interactions.
-Although some studies have evaluated plant reproductive strategies in plant-pollinator networks [@tur2013; @lazaro2020], this is an often overlooked aspect in a community context [@devaux2014] and rarely incorporated into plant-pollinator network studies.
-Hence, exploring how the main plant and floral visitor life-history strategies integrate with the emergent framework of network motifs could help to progress knowledge on the ecological processes that shape plant-pollinator interactions.
-
-Here we evaluate the interaction patterns of the meso-scale and its ecological implications in plant-pollinator networks with the help of 60 empirical networks from 18 different studies distributed across 14 different countries.
-For this, plants and pollinators were divided into functional groups that summarise their main life-history strategies and the different networks were split into all their subgraph elements up to five nodes.
-First, based on previous knowledge showing the non random assembly of macro-scale mutualistic networks [@bascompte2003] and food webs [@dunne2002], we test the hypothesis that the building blocks that constitute the meso-scale in plant-pollinator networks have a non-random structure of interactions with over- and under-represented subgraphs (i.e., motifs) that represent contrasting ecological roles.
-Second, because species relative abundances (i.e., neutral effects) are one of the main drivers of network macro-struture [@krishna2008; @suweis2013; @bartomeus2016], we hypothesise that neutral effects may also govern the interaction patterns of the meso-scale in plant-pollinator networks.
-Finally, we explore if plants and pollinators functional groups are associated with subgraph positions that imply distinct ecological roles and if there are over- and under-represented functional group combinations within the different network subgraphs.
-
-# Methods
-
-**Overview**
-
-To investigate the structure of the meso-scale in plant-pollinator networks, we gathered published plant-pollinator networks with worldwide distribution.
-Then, we classified the different plant and floral visitor species from these networks into functional groups that summarise their main life-history strategies.
-We calculated the normalised subgraph frequencies and investigated if these frequencies are similar or not to the ones expected by chance with the help of null models.
-Then, for each group of plants and floral visitors we investigated the ecological implications of their overall representation on the different subgraph positions, by comparing, on the one hand, the observed (normalised) frequencies of each group in the different subgraph positions with the frequencies of their simulated counterparts, and, on the other hand, the differences among groups per subgraph position in terms of their number of indirect interactions and specialisation.
-Finally, to understand if the different functional group combinations within a subgraph are structured, we compare if the observed functional group combinations from empirical networks can be retrieved from the joint probability distribution of the expected frequencies of the different plant and floral visitor groups within network subgraphs.
-
-**Plant-pollinator studies**
-
-We have compiled 60 plant-pollinator networks from 18 different studies (Table S1).
-All studies sampled plant-pollinator interactions in natural systems in a single flowering season and were selected based on wide geographical coverage (Fig.
-S1) and presence of interaction frequency as a measure of interaction strength.
-In total, there were 503 plant species, 1,111 floral visitors species and 6,248 pairwise interactions registered.
-For ease of data manipulation, plant and floral visitor species names were standardised with the help of the R package *taxize* version *0.9.99* [@chamberlain2020].
-
-**Plant and floral visitor functional groups**
-
-First, plant species were grouped through hierarchical clustering into the optimal number of functional groups that summarises the main plant reproductive strategies.
-For this, we used the plant trait dataset compiled in @lanuza2021 that consisted also of plant species that belonged to the same plant-pollinator networks plus some additional meta-networks not considered here.
-This dataset comprised a total of 1,506 plant species including the 503 species considered in this study (Table S2).
-Because most of these plant species are likely to benefit from animal pollination, we used reproductive traits relevant to understand the different plant reproductive strategies and their interactions with pollinators.
-After excluding traits with a high percentage of missing values (over 30$\%$), we ended up with 8 floral, 3 reproductive biology and 3 plant morphology traits (see Table S3 for a list of all traits).
-Floral traits included those associated with the size, form and number of floral organs (e.g., style length or ovule number).
-Reproductive biology traits described the reproductive system of the plant (e.g., mating and compatibility systems) and plant morphology traits were associated with the size and form of the plant (i.e., plant height, lifespan and life form).
-After an extensive search for each plant species on several different resources (e.g., plant databases, online floras, books, journals and images), over 80% of the cells of the whole dataset were filled.
-Thus, to avoid the loss of species with trait missing values, missing trait data was imputed as detailed in @lanuza2021.
-
-We opted to calculate the plant functional groups within a larger set of species because of the higher accuracy when delimiting functional groups with that many variables and species [@dolnicar2014].
-To feed the clustering analysis, we calculated the distance between the different qualitative and scaled quantitative variables with Gower distance [@gower1971].
-For this, we used the function *gowdis* with method *ward.D2* from the *FD* package version *1.0-12* [@laliberte2014].
-Finally, we conducted hierarchical clustering with the function *hclust* from the *R* stats package version *4.0.5* and calculated the optimal number of clusters with the function *kgs* from the *maptree* package version *1.4-7* [@white2009].
-
-Second, floral visitors were aggregated into taxonomic groups (hereafter referred to as functional groups) based on taxonomic rank as done similarly in other plant-pollinator studies [@fenster2004; @ollerton2009].
-We opted to divide floral visitors on the taxonomic rank level and not with functional traits because the main orders of floral visitors differed in form and behaviour and had lower superior taxonomic complexity (i.e., floral visitors had 6 orders versus plants that had 38).
-Thus, this allowed us to group floral visitors into functional groups that represented approximately the main life-history strategies of the possible pollinators: (i) bees (Hymenoptera-Anthophila), (ii) non-bee Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Syrphidae-Diptera), (iv) non-syrphids-Diptera, (v) Lepidoptera and (vi) Coleoptera.
-However, a minor set of species belonged to other functional groups that were considered in analyses but not discussed further because of their low representation in the full set of networks (3.55$\%$ of the total interactions recorded).
-These taxonomic groups were 'lizards', 'birds' and 'other insects'.
-This last functional group was formed by a mix of uncommon insect taxa on the full set of networks.
-
-**Overall network subgraphs patterns**
-
-Following previous work [@simmons2019; @simmons2020], we broke down the plant-pollinator networks into their constituent network subgraphs that can capture both direct and indirect interactions.
-Prior to analyses, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.
-This approach was preferred since quantitative subgraph analyses have been developed just recently and more work is needed to fully understand and interpret the information that they can convey [@simmons2020].
-All analyses were run considering singletons (species with only one interaction detected) but we conducted a second exploration without singletons (64.98$\%$ of interactions) to evaluate the effect of rare species on the observed patterns.
-Results without singletons are qualitatively consistent and are not further discussed in the main text (Figs S2 and S3).
-
-We calculated the frequency of all subgraphs up to five nodes (17 different subgraphs in total; see Fig.
-1) for each empirical network, by using the *bmotif* package version *2.0.2* [@bmotifsimmons2019].
-We focused exclusively on subgraphs up to five nodes in our analyses for computational reasons and for the ease of visualization and interpretation of a reduced set of less complex network structures.
-Throughout the entire manuscript, floral visitors occupy the top nodes of the different network subgraphs and plants the bottom ones.
-To control for variation in network size, subgraph frequencies were normalised as a proportion of the total number of subgraphs within each subgraph class (i.e., 2-species, 3-species, 4-species and 5-species network subgraphs).
-In addition, we excluded 2-species (or 2-nodes) subgraphs from our analyses because its normalised frequencies would always equal one.
-Note that the aim is not comparing different networks, which may differ in sampling effort, but correctly describing the structure of each individual network.
-Like @simmons2020, we classified the different subgraphs by their average path length (mean number of links between all pairs of nodes) into four different groups: (i) complete or strong ($\overline{x} = 1.38$), (ii) fan or medium-strong ($\overline{x} = 1.48$), (iii) assymmetric complete or medium-weak ($\overline{x} = 1.60$) and (iv) core-peripheral or weak ($\overline{x} = 1.85$), where $\overline{x}$ represents the mean of the average path length across subgraphs within the same group.
-In general terms, plant and floral visitor groups on more densely connected network subgraphs (e.g., complete or fan) will experience lower number of indirect interactions in contrast to groups on less densely connected structures (e.g., medium-weak or weak).
 
@@
 ```
-
-To assess the significance of the observed frequencies, we created 1,000 simulated networks for each binary network using the *nullmodel* function and the *vaznull* model in the *bipartite* package version *2.14* [@dormann2009].
-Generated networks had the same number of plants and floral visitors, as well as the same connectance of their corresponding empirical networks.
-We discarded null models with more constraints (e.g., constraining for species degree) because the permutations did not generate sufficient variability and provided highly similar or identical networks to the original ones.
-After extracting the subgraph frequencies from the simulated networks, for each subgraph type and empirical network, we calculated the percentage of simulated networks whose frequencies were smaller than the ones observed, that is, we estimated the percentile of the observed subgraph frequencies.
-Subgraphs whose percentile is close to 0 or 100 are under- or over-represented in empirical networks, respectively, and indicate the presence of network motifs as they differ statistically from the network structures generated with simulated networks.
-To summarise general patterns across networks, we used an intercept-only linear mixed model (LMM) per subgraph with the help of the *lme4* package version *1.1-21* [@bates2015], where the response variable was the observed subgraph percentile per network.
-Note that as we are only interested in modelling the intercept value, no predictors were specified.
-In these models, we used the study identifiers in Table S1 as a random intercept.
-By doing so, we obtained estimates of the average subgraph frequency, but controlling for the variation at the study level.
-
-**Over- and under-represented functional groups on subgraph positions**
-
-We calculated which plant and floral visitor functional groups were over- or under-represented in the different subgraph positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
-To estimate the position frequencies of each plant and floral visitor group in a given network, we added the frequencies of those species that belong to the same group, and then, we normalised the resulting frequencies by dividing them by the total number of times that a corresponding group appears in any position within the same subgraph size class.
-Then, we calculated the percentile of the observed position frequencies for each functional group and network, just like we did with subgraph frequencies.
-To outline the general patterns of position frequencies across networks and groups, we fit a LMM per subgraph position, where the response variable was the observed position percentile per network.
-We used the group identifier as an explanatory variable and the study identifiers as a random intercept.
-Hence, we assessed the average subgraph frequency per species group, after controlling for the variation at the study level.
-Finally, we visualised over- and under-representation of plant and floral visitor groups on the different subgraph positions with the help of the *ComplexHeatmap* package version *2.6.2* [@gu2016].
-
-To understand if the different plant and floral visitor functional groups are associated with subgraph positions that represent different network roles, we characterised the roles of each subgraph position for the different functional groups in terms of their specialisation and number of indirect interactions.
-To that end, we calculated the specificity of each subgraph position following @poisot2015 as $s_i = (L - l_i) / (L - 1)$, where $L$ is the total number of groups and $l_i$ the number of interaction partners of the group $i$ in a given subgraph.
-Values of the vector $si$, range between 1, complete specialisation (1 partner within the subgraph) and 0 complete generalism (all possible partners within the subgraph).
-Then, because all nodes within a motif are connected, we calculated the number of indirect interactions ($\theta_i$) for each motif position as $\theta_i=m_i-k_i-1$, where $m_i$ is the total number of nodes in a given motif, and $k_i$ represents the degree of the corresponding motif position, that is, the total number of links connected to such position.
-Thus, we considered all possible indirect interactions for each position.
-Finally, we analysed in a single model how specialisation and the number of indirect interactions were associated with the observed percentiles for each trophic guild and subgraph position.
-For this, we fitted again a LMM model with the help of the *lme4* package, where we considered specialisation and number of indirect interactions as response variables with the interaction by plant and floral visitor group for both response variables.
-Further, we considered as random factor subgraph position nested within study system.
-
-**Over- and under-represented functional group combinations of subgraphs**
-
-Finally, we studied which combinations of plant and floral visitor functional groups tend to appear together within the same subgraphs (up to five nodes).
-That is, which combinations are over- or under-represented.
-This analysis used 57 out of the 60 networks available due to computational limitations to identify all the nodes in the subgraphs of the three networks with the highest number of links.
-To do so, for each of the 53,250 possible subgraph combinations, we estimated the observed and the expected probability of finding those combinations in empirical networks, respectively.
-Then, we determined whether the observed probabilities are likely to come from the expected probabilities or not.
-To calculate the observed probability ($p_i^O$) of the different groups within a subgraph $i$ (e.g., subgraph 3, 'bee' + 'bee' + 'selfing herbs'), we divided the number of times that $i$ appears in our set of empirical networks ($n_i^O$) by the sum of the number of times that each possible combination appeared: $p_i^O = n_i^O / \sum_{k=1}^{53,250} n_k^O$.
-To estimate the expected probability ($p_i^E$) of a given subgraph combination $i$, we assumed that the probability of finding a given functional group $x$ in the position $\alpha$ is independent of the probabilities associated with other positions and groups in that subgraph.
-Therefore, the expected probability ($p_i^E$) of the subgraph combination $i$ is given by the product of the probabilities of its constituents, i.e., $p_i^E = \prod _{(x,\alpha )\in i} p_i(x,\alpha)$, where $p_i(x,\alpha)$ is the probability of finding a given functional group $x$ in the position $\alpha$ of $i$.
-Then, by controlling for the variation at the network level with an LMM (see below), we calculated the average number of times that the functional group $x$ appears in the position $\alpha$ (denoted as $n_i(x,\alpha)$).
-To obtain the expected probability $p_i(x,\alpha)$, we divided the number of times that the group $x$ appears in the position $\alpha$ by the the total number of times that any group was observed in that position (that is, $p_i(x,\alpha) = n_i(x,\alpha)/\sum_{k}n_i(k,\alpha)$).
-The average number of times that the group $x$ appears in the position $\alpha$ ($n_i(x,\alpha)$) was calculated with a LMM for each position, where the response variable was the number of times that a group was observed at a given position in each real-world network, the explanatory variable was the group identifier, and the random intercept was given by network identifiers nested within the study identifiers.
-
-Once we obtained $p_i^O$ and $p_i^E$, we used a simulation approach to determine whether the former is likely to come from the latter or not.
-This approach was preferred since the large number of possible subgraph combinations and the small probabilities for some of them advise against using an exact test of goodness-of-fit or a Chi-square one.
-Specifically, we created 1,000 random samples with repetition of possible subgraph combinations, where each sample contained 10 million elements and, for each combination, the probability of being selected was equal to its expected probability.
-From those random samples, we extracted the mean and the standard deviation of the expected probability of $i$, denoted as $E\left [ p_i^E \right ]$ and $\sigma\left [ p_i^E \right ]$, respectively, and calculated the z-scores of $p_i^O$ as $z_i^O = \left ( p_i^O - E\left [ p_i^E \right ] \right )/\sigma \left [ p_i^E \right ]$, for those motif combinations with $p_i^O > 0$.
-According to the usual interpretation of z-scores, combinations with $z_i^O > 1.96$ are over-represented, whereas those with $z_i^O < -1.96$ are under-represented, at the 95$\%$ confidence level.
-Notice that we focused on combinations with $p_i^O > 10^{-7}$ because we do not have enough numerical resolution to accurately detect whether combinations that took place only once are under-represented (due to the limited size of our random samples).
-
-All analyses and data manipulation were conducted in R *version 4.0.5* [@R].
-In addition, all model diagnostics were conducted with the help of the *Dharma* package [@hartig2017] version *0.3.3.0* and model outputs were visualised with the *visreg* package [@breheny2020] version 2.7.0.
-
-# RESULTS
-
-**Plant and floral visitor functional groups**
-
-The hierarchical cluster analysis divided the dataset into five different plant functional groups with different and overlapping characteristics (Figs S4 and S5).
-The first group referred to as 'selfing herbs' consisted of herbs with hermaphroditic flowers with high levels of autonomous selfing.
-The second group named 'small outcrossing perennials' had small perennial species with a mix of life forms (i.e., trees, shrubs and herbs) with outcrossing hermaphroditic flowers.
-The third group referred to as 'self-incompatible perennials with large flowers' comprised perennial species with a mixed of life forms and large self-incompatible hermaphroditic flowers with high number of ovules.
-The fourth group named 'tall plants with small unisexual flowers' had the tallest species, highest proportion of shrub and tree life forms, dioecious and monoecious breeding systems, small flowers, and the highest numbers of flowers and inflorescences per plant.
-Finally, the fifth group named 'short-lived outcrossers with long zygomorphic flowers' consisted of small perennial and short-lived herbs with long self-compatible zygomorphic flowers that were unable to self-pollinate.
-
-In total, there were 1,126 species of floral visitors with 6,325 interactions recorded with plants.
-Most plants interacted with bees (2,256 interactions) and non-syrphid Diptera (1,768) followed by syrphids (845), Lepidoptera (437), Coleoptera (432) and non-bee Hymenoptera (362).
-
-**Overall network subgraphs patterns**
-
-Most network subgraphs were under- or over-represented (close to the 1st and 99th percentile, respectively) in the comparison between empirical and simulated networks (Fig.
-2).
-Network subgraphs 3, 5, 9, 10 and 14 were under-represented in empirical networks, that is, all were close to the 1st percentile and under the 25th percentile.
-Interestingly, four out of five of these motifs belonged to the largest path length classification (i.e., core-peripheral).
-In addition, network subgraphs 2, 6, 7, 16 and 17 were over-represented, all over the 75th percentile.
-In contrast to the under-represented network subgraphs, over-represented subgraphs belonged to the two shortest path length groups (i.e., complete and fan).
-The remaining network subgraphs (i.e., 4, 8, 11, 12, 13, and 15) were between the 25th and 75th percentile.
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure 2.** Comparison of network subgraph frequencies between empirical and simulated networks grouped by average path length (plots a, b, c and d) where $\\overline{x}$ indicates the mean of the average path lengths of all subgraphs within each group (strong, medium-strong, medium-weak and weak).
-This comparison is shown with the mean percentage of subgraph frequencies in empirical networks that were over the subgraph frequencies of the simulated ones (percentiles).
-This was done by network (light blue transparent dots) and then averaged for all networks (black dots with error bars that correspond to the standard deviation)."}
-
-library(lme4)
-library(nlme)
-library(tidyverse)
-source("../../Scripts/Scripts_Alfonso/add_study_id.R")
-d <- read_csv("../../Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
-d <- add_study_id(d)
-#str(d)
-#head(d)
-
-#ggplot(d %>% filter(motif != 1), aes(percentil_sizeclass))+
-#  geom_histogram(color="black", fill="white")+
-#  facet_wrap(~motif)+
-#  theme_bw()+
-#  labs(x="Sizeclass percentile")
-#
-# Motifs tend to be over- and under-represensented in real networks
-
-# Mean percentile and SE taking into account the study system
-motif_codes <- d %>% filter(motif != 1) %>% # We remove links (motif code: 1)
-  select(motif) %>% unique() %>% pull()
-motif_means <- tibble(motif = motif_codes)
-motif_means$mean <- NA
-motif_means$SE <- NA
-
-for(i.motif in 1:length(motif_codes)){
-
-  m <- lmer(percentil_sizeclass ~ 1+(1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = subset(d, motif == motif_codes[i.motif]))
-
-  motif_means$mean[i.motif] <- fixed.effects(m) %>% unname()
-  motif_means$SE[i.motif] <- sqrt(diag(vcov(m)))
-
-}
-
-#Add categories based on path length set by Simmons 2021 et al., Functional Ecology
-d$Broad_categories[d$motif==2 | d$motif==7 | d$motif==17 | d$motif==3|d$motif==4|d$motif==8] <- "Fan"
-
-d$Broad_categories[d$motif==15 | d$motif==11] <- "Medium-weak"
-
-d$Broad_categories[d$motif==6 | d$motif==16 |  d$motif==12] <- "Strong"
-
-d$Broad_categories[d$motif==5 | d$motif==9 |  d$motif==14|  d$motif==13|  d$motif==10] <- "Weak"
-
-#order the categories from short to long path length
-d$Broad_categories <- factor(d$Broad_categories, levels = c("Strong", "Fan", "Medium-weak", "Weak"))
-
-#Ffilter out two node motifs
-d_1 <- d %>% filter(motif != 1)
-#Merge dataframes to bl able to create facets
-d_2 <- merge(d_1, motif_means, by="motif")
-
-arr <- list('Strong' = expression(bold(paste("(a) Strong (Complete, ", bar(x), " = 1.38)"))),
-             'Fan' = expression(bold(paste("(b) Medium-strong (fan, ", bar(x), " = 1.48)"))), 
-             'Medium-weak' = expression(bold(paste("(c) Medium-weak (asymmetric complete, ", bar(x), " = 1.60)"))), 
-             "Weak" =expression(bold(paste("(d) Weak (core-peripheral, ", bar(x), " = 1.85)"))))
-mylabel <- function(val) { return(lapply(val, function(x) arr[x])) }
-
-library(ggforce) #workaround with ggforce to have facets with same sizes 
-library(ggtext)
-
-labels <- c("2" = "*Subgraph 2* <img src='../../Images/motif_2.png' width='22'/>" ,
-          "3"= "*Subgraph 3* <img src='../../Images/motif_3.png' width='22'/>",
-          "4"= "*Subgraph 4* <img src='../../Images/motif_4.png' width='22'/>",
-          "5"= "*Subgraph 5* <img src='../../Images/motif_5.png' width='22'/>",
-          "6"= "*Subgraph 6* <img src='../../Images/motif_6.png' width='22'/>",
-          "7"= "*Subgraph 7* <img src='../../Images/motif_7.png' width='22'/>",
-          "8"= "*Subgraph 8* <img src='../../Images/motif_8.png' width='22'/>",
-          "9"= "*Subgraph 9* <img src='../../Images/motif_9.png' width='22'/>",
-          "10"= "*Subgraph 10* <img src='../../Images/motif_10.png' width='22'/>",
-          "11"= "*Subgraph 11* <img src='../../Images/motif_11.png' width='22'/>",
-          "12"= "*Subgraph 12* <img src='../../Images/motif_12.png' width='22'/>",
-          "13"= "*Subgraph 13* <img src='../../Images/motif_13.png' width='22'/>",
-          "14"= "*Subgraph 14* <img src='../../Images/motif_14.png' width='22'/>",
-          "15"= "*Subgraph 15* <img src='../../Images/motif_15.png' width='22'/>",
-          "16"= "*Subgraph 16* <img src='../../Images/motif_16.png' width='22'/>",
-          "17"= "*Subgraph 17* <img src='../../Images/motif_17.png' width='22'/>")
-
-p <- ggplot()+geom_point(data = d_2 , aes(y=factor(motif), 100*percentil_sizeclass), shape=21,color="black",fill="azure2",size=1.75, alpha=0.3)+
-  geom_errorbar(data = d_2,aes(y = factor(motif), xmin=100*(mean-SE), xmax=100*(mean+SE)), 
-                width=0.8,size=0.8,color="black") +theme_bw()+
-  geom_point(data = d_2,aes(y = as.factor(motif), x=100*mean), 
-             size=2,color="black")+labs(y="Two to five node motifs", x = "Percentile")+
-  theme( strip.background = element_blank())+
-  theme(strip.text = element_text(face="bold", size=10, hjust=0),
-        panel.border=element_rect(color="black",size=1.2))+
-  scale_y_discrete(name = NULL,
-                   labels = labels) +
-  theme(axis.text.y = ggtext::element_markdown())
-
-p + ggforce::facet_col(vars(Broad_categories), scales = 'free', space = 'free',labeller=mylabel)
-
-#Trying to maintain a gradient from low to high in colors
-
-#Fig 1 Should be a dot plot (or forest plot) of the mean +- SE of the 15 motifs.
-#NICE! Can we put motifs in Y axes, and % in X?
-```
-
-**Over- and under-represented functional groups on subgraph positions**
-
-```{r , include=FALSE}
-
-#SAME SCRIPT AS THE PLOTTING FOR THE HEATMAP BUT I NEED IT HERE TO LOAD THE VARIABLES WITH VALUES ON RESULTS
-
-library(lme4)
-library(nlme)
-library(tidyverse)
-library(stringi)
-source("../../Scripts/Scripts_Alfonso/add_study_id.R")
-
-#############################################
-# EXTRACT MEAN VALUES
-#############################################
-all_position_percentiles <- read_csv("../../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
-
-all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
-                                                              "[0-9]+") %>% as.numeric()
-
-all_position_percentiles <- add_study_id(all_position_percentiles)
-#str(all_position_percentiles)
-#head(all_position_percentiles)
-
-list_plants_FG <- as.character(1:10)
-
-plant_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF)) #ME DA ERROR
-pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF))
-
-# Plants-------------
-
-# Mean percentile and SE taking into account the study system
-plant_codes <- plant_position_percentiles_filtered$position %>% unique()
-plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-plant_means$mean <- NA
-plant_means$SE <- NA
-
-for(i.pos in 1:length(plant_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
-            data = plant_position_percentiles_filtered %>%
-              filter(position == plant_codes[i.pos]))
-
-  temp <- fixed.effects(m) %>% unname()
-  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
-                                                                    temp[1]+temp[2],
-                                                                    temp[1]+temp[3],
-                                                                    temp[1]+temp[4],
-                                                                    temp[1]+temp[5]) ## to get real means per FG
-  temp <- sqrt(diag(vcov(m)))
-  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
-                                                                  temp[1]+temp[2],
-                                                                  temp[1]+temp[3],
-                                                                  temp[1]+temp[4],
-                                                                  temp[1]+temp[5])
-
-}
-
-# Pollinators--------
-
-# Mean percentile and SE taking into account the study system
-pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
-pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-pollinator_means$mean <- NA
-pollinator_means$SE <- NA
-pollinator_means_reordered <- NULL
-
-for(i.pos in 1:length(pollinator_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = pollinator_position_percentiles_filtered %>%
-              filter(position == pollinator_codes[i.pos]),
-            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
-
-  temp <- fixed.effects(m) %>% unname()
-  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)
-
-  pollinator_means_aux$mean <- c(temp[1],
-                                 temp[1]+temp[2],
-                                 temp[1]+temp[3],
-                                 temp[1]+temp[4],
-                                 temp[1]+temp[5],
-                                 temp[1]+temp[6],
-                                 temp[1]+temp[7],
-                                 temp[1]+temp[8],
-                                 temp[1]+temp[9]) ## to get real means per FG
-
-  temp <- sqrt(diag(vcov(m)))
-  pollinator_means_aux$SE <- c(temp[1],
-                               temp[1]+temp[2],
-                               temp[1]+temp[3],
-                               temp[1]+temp[4],
-                               temp[1]+temp[5],
-                               temp[1]+temp[6],
-                               temp[1]+temp[7],
-                               temp[1]+temp[8],
-                               temp[1]+temp[9])
-
-  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)
-
-}
-
-# There are lower limits (mean - SE) smaller than 0 (see Other insects)
-# We set the lower limit of those error bars to zero
-
-pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
-pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
-
-#############################################
-# ADDING BROAD MOTIF CATEGORIES TO POSITIONS
-#############################################
-
-motifs_raw_data <- read_csv("../../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-motifs_raw_data$Broad_categories <- NA
-
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(5,9,14,13,10)] <- "Core-peripherical"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(6,16,12)] <- "Complete"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(2,3,7,4,17,8)] <- "Fan"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(15,11)] <- "Asymmetric complete"
-
-motifs_raw_data$plant <- gsub("[^0-9.-]", "", motifs_raw_data$plant)
-motifs_raw_data$pollinator <- gsub("[^0-9.-]", "", motifs_raw_data$pollinator)
-motifs_raw_data$plant <- as.numeric(motifs_raw_data$plant)
-motifs_raw_data$pollinator <- as.numeric(motifs_raw_data$pollinator)
-motifs_raw_data <- motifs_raw_data %>% filter(!is.na(Broad_categories))
-
-fan_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-pollinator_means_reordered$Broad_categories <- NA
-
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% fan_pollinator] <- "Fan" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% asymm_pollinator] <- "Medium-weak" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% complete_pollinator] <- "Strong" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% core_per_pollinator] <- "Weak"
-
-fan_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-plant_means$Broad_categories <- NA
-
-plant_means$Broad_categories[plant_means$position %in% fan_plant] <- "Fan" 
-plant_means$Broad_categories[plant_means$position %in% asymm_plant] <- "Medium-weak" 
-plant_means$Broad_categories[plant_means$position %in% complete_plant] <- "Strong" 
-plant_means$Broad_categories[plant_means$position %in% core_per_plant] <- "Weak"
-
-################################################################################
-# Alternative code to HEATMAPS to create variables with values to load on text
-# in a reproducible/automated way
-################################################################################
-
-# PLANTS-----
-
-# Prepare data for heatmap
-heat_plants_aux <- plant_means %>% spread(Node_FG,mean) %>% select(-SE)
-
-heat_plants <- heat_plants_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-# POLLINATORS-----------
-
-filter_rare_groups <- T
-
-if(filter_rare_groups == T){
-  heat_pollinators_aux <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds",
-                                                                                "Lizards",
-                                                                                "Other_insects")) %>% 
-    spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees",            
-                                      "Coleoptera","Lepidoptera","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Syrphids")
-}else{
-  heat_pollinators_aux <- pollinator_means_reordered %>% spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees","Birds",            
-                                      "Coleoptera","Lepidoptera","Lizards","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Other insects","Syrphids")
-}
-
-heat_pollinators <- heat_pollinators_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))
-
-#Check percentage of over and under represented
-colMeans(heat_pollinators[,c(3:8)] < 0.25)
-poll_under_25 <- colMeans(heat_pollinators[,c(3:8)] < 0.25)
-poll_under_25 <- specify_decimal((poll_under_25[[1]] + poll_under_25[[2]] + poll_under_25[[3]] +
-poll_under_25[[4]] + poll_under_25[[5]] + poll_under_25[[6]])/6*100,2)
-#[1] 32.57576
-
-colMeans(heat_pollinators[,c(3:8)] > 0.75)
-poll_over_75 <- colMeans(heat_pollinators[,c(3:8)] > 0.75)
-poll_over_75 <- specify_decimal((poll_over_75[[1]] + poll_over_75[[2]] + poll_over_75[[3]] +
-    poll_over_75[[4]] + poll_over_75[[5]] + poll_over_75[[6]])/6*100,2)
-#[1] 4.545455
-
-#################################################################################
-#################################################################################
-
-colnames(heat_plants)<- c("position", "Broad_categories", "one",
-                               "two", "three","four",
-                               "five")
-f <- heat_plants %>%
-  mutate(min = pmin(1,
-                    one, two,three,
-                    four, five))%>%
-  mutate(max = pmax(one,
-                    two, three,four,
-                    five))
-
-diff_1 <- f$max-f$min
-
-cbind(diff,diff_1)
-
-#Check percentage of over and under represented per FG
-colMeans(heat_plants[,c(3:7)] < 0.25)
-plant_under_25 <- colMeans(heat_plants[,c(3:7)] < 0.25)
-plant_under_25 <- specify_decimal((plant_under_25[[1]] + plant_under_25[[2]] + plant_under_25[[3]] + 
-    plant_under_25[[4]] + plant_under_25[[5]])/5*100,2)
-#[1] 18.18182
-colMeans(heat_plants[,c(3:7)] > 0.75)
-plant_over_75 <- colMeans(heat_plants[,c(3:7)] > 0.75)
-plant_over_75 <- specify_decimal((plant_over_75[[1]] + plant_over_75[[2]] + plant_over_75[[3]] + 
-    plant_over_75[[4]] + plant_over_75[[5]])/5*100,2)
-#[1] 8.181818
-
-#overall percentages
-under <- specify_decimal((as.numeric(poll_under_25) + as.numeric(plant_under_25))/2,2)
-over <- specify_decimal((as.numeric(poll_over_75) + as.numeric(plant_over_75))/2,2)
-
-```
-
-The comparison of the plant and floral visitor functional group frequencies per subgraph position between empirical and simulated networks showed a `r over`$\%$ and `r under`$\%$ of over- (>75$^{th}$) and under-represented (\<25th) functional groups in the different positions, respectively (Fig.
-3).
-Floral visitors showed a total of `r poll_over_75`$\%$ and `r poll_under_25`$\%$ of over- and under-represented functional groups in the different positions, and plants `r plant_over_75`$\%$ and `r plant_under_25`$\%$ of over- and under-represented functional groups, respectively.
-Notably, the differences across functional groups were more marked for floral visitors than for plants (the differences between the minimum and maximum values of the percentiles per position were generally two-three times larger for floral visitors).
-From most over- to under-represented floral visitors functional groups on the different subgraph positions (indicated with the dendrogram order in Fig.
-3), we found: bees, non-syrphids Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.
-Although plant functional groups showed less differences between them, there were also more represented functional groups than others.
-Thus, from most over- to under-represented functional groups on the different subgraph positions we found: self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.
-
-For both floral visitor and plant functional groups we found over- and under-representation on different subgraph positions that implied different ecological roles.
-First, for floral visitors, we found that bees were less frequent on subgraph positions that involved specialisation (i.e., lower specificity values) while the rest of functional groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) were infrequent in generalised subgraph positions with low number of indirect interactions (Fig.
-S6 A).
-Although plants did not show differences with null models on their frequencies, all plant functional groups but tall plants with small unisexual flowers showed a slight tendency to be over-represented on specialised subgraph positions (Fig.
-S6 B).
-Second, regarding the number of indirect interactions, bees were over-represented in subgraph positions with low number of indirect interactions (Fig.
-S7 A) and the rest of floral visitor functional groups showed no differences across positions in comparison with simulated networks.
-For plants, all functional groups showed a slight tendency to be over-represented on subgraph positions with higher number of indirect interactions (Fig.
-S7 B).
-When we further explore the observed frequencies by number of indirect interactions for floral visitor and plant functional groups, we found that both bees and tall plants with small unisexual flowers were the only functional groups with high frequencies on subgraph positions associated with low number of indirect interactions in comparison with the other floral visitor and plant functional groups (Figs S8 and S9).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', out.width="80%",fig.cap="\\textbf{Figure 3.} Heatmap indicating under- and over-representation of floral visitor and plant functional groups in the different subgraph positions (numbers on the right of each heatmap).
-The different subgraph positions are dividied by the average path length clasification determined by Simmons et al.
-(2020) and they are ordered from the most densely connected network structures (strong or complete) to the less connected ones (weak or core-peripheral).
-The superior dendrogram indicates the differences across functional groups with the more separated groups showing larger differences."}
-
-library(lme4)
-library(nlme)
-library(tidyverse)
-library(stringi)
-source("../../Scripts/Scripts_Alfonso/add_study_id.R")
-
-#############################################
-# EXTRACT MEAN VALUES
-#############################################
-
-all_position_percentiles <- read_csv("../../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
-
-all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
-                                                              "[0-9]+") %>% as.numeric()
-
-all_position_percentiles <- add_study_id(all_position_percentiles)
-#str(all_position_percentiles)
-#head(all_position_percentiles)
-
-list_plants_FG <- as.character(1:10)
-
-plant_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF)) #ME DA ERROR
-pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF))
-
-# Plants-------------
-
-# Mean percentile and SE taking into account the study system
-plant_codes <- plant_position_percentiles_filtered$position %>% unique()
-plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-plant_means$mean <- NA
-plant_means$SE <- NA
-
-for(i.pos in 1:length(plant_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
-            data = plant_position_percentiles_filtered %>%
-              filter(position == plant_codes[i.pos]))
-
-  temp <- fixed.effects(m) %>% unname()
-  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
-                                                                    temp[1]+temp[2],
-                                                                    temp[1]+temp[3],
-                                                                    temp[1]+temp[4],
-                                                                    temp[1]+temp[5]) ## to get real means per FG
-  temp <- sqrt(diag(vcov(m)))
-  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
-                                                                  temp[1]+temp[2],
-                                                                  temp[1]+temp[3],
-                                                                  temp[1]+temp[4],
-                                                                  temp[1]+temp[5])
-
-}
-
-# Pollinators--------
-
-# Mean percentile and SE taking into account the study system
-pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
-pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-pollinator_means$mean <- NA
-pollinator_means$SE <- NA
-pollinator_means_reordered <- NULL
-
-for(i.pos in 1:length(pollinator_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = pollinator_position_percentiles_filtered %>%
-              filter(position == pollinator_codes[i.pos]),
-            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
-
-  temp <- fixed.effects(m) %>% unname()
-  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)
-
-  pollinator_means_aux$mean <- c(temp[1],
-                                 temp[1]+temp[2],
-                                 temp[1]+temp[3],
-                                 temp[1]+temp[4],
-                                 temp[1]+temp[5],
-                                 temp[1]+temp[6],
-                                 temp[1]+temp[7],
-                                 temp[1]+temp[8],
-                                 temp[1]+temp[9]) ## to get real means per FG
-
-  temp <- sqrt(diag(vcov(m)))
-  pollinator_means_aux$SE <- c(temp[1],
-                               temp[1]+temp[2],
-                               temp[1]+temp[3],
-                               temp[1]+temp[4],
-                               temp[1]+temp[5],
-                               temp[1]+temp[6],
-                               temp[1]+temp[7],
-                               temp[1]+temp[8],
-                               temp[1]+temp[9])
-
-  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)
-
-}
-
-# There are lower limits (mean - SE) smaller than 0 (see Other insects)
-# We set the lower limit of those error bars to zero
-
-pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
-pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
-
-#############################################
-# ADDING BROAD MOTIF CATEGORIES TO POSITIONS
-#############################################
-
-motifs_raw_data <- read_csv("../../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-motifs_raw_data$Broad_categories <- NA
-
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(5,9,14,13,10)] <- "Core-peripherical"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(6,16,12)] <- "Complete"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(2,3,7,4,17,8)] <- "Fan"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(15,11)] <- "Asymmetric complete"
-
-motifs_raw_data$plant <- gsub("[^0-9.-]", "", motifs_raw_data$plant)
-motifs_raw_data$pollinator <- gsub("[^0-9.-]", "", motifs_raw_data$pollinator)
-motifs_raw_data$plant <- as.numeric(motifs_raw_data$plant)
-motifs_raw_data$pollinator <- as.numeric(motifs_raw_data$pollinator)
-motifs_raw_data <- motifs_raw_data %>% filter(!is.na(Broad_categories))
-
-fan_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-pollinator_means_reordered$Broad_categories <- NA
-
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% fan_pollinator] <- "Fan" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% asymm_pollinator] <- "Medium-weak" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% complete_pollinator] <- "Strong" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% core_per_pollinator] <- "Weak"
-
-fan_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-plant_means$Broad_categories <- NA
-
-plant_means$Broad_categories[plant_means$position %in% fan_plant] <- "Fan" 
-plant_means$Broad_categories[plant_means$position %in% asymm_plant] <- "Medium-weak" 
-plant_means$Broad_categories[plant_means$position %in% complete_plant] <- "Strong" 
-plant_means$Broad_categories[plant_means$position %in% core_per_plant] <- "Weak"
-
-########################################
-# CREATE HEATMAPS
-########################################
-
-library(ComplexHeatmap)
-
-# PLANTS-----
-
-# Prepare data for heatmap
-heat_plants_aux <- plant_means %>% spread(Node_FG,mean) %>% select(-SE)
-
-heat_plants <- heat_plants_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-heat_plants_fan <- heat_plants %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_fan) <- heat_plants_fan[,1]
-
-heat_plants_Weak <- heat_plants %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Weak) <- heat_plants_Weak[,1]
-
-heat_plants_Strong <- heat_plants %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Strong) <- heat_plants_Strong[,1]
-
-heat_plants_Medium_weak <- heat_plants %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Medium_weak) <- heat_plants_Medium_weak[,1]
-
-# POLLINATORS-----------
-
-filter_rare_groups <- T
-
-if(filter_rare_groups == T){
-  heat_pollinators_aux <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds",
-                                                                                "Lizards",
-                                                                                "Other_insects")) %>% 
-    spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees",            
-                                      "Coleoptera","Lepidoptera","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Syrphids")
-}else{
-  heat_pollinators_aux <- pollinator_means_reordered %>% spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees","Birds",            
-                                      "Coleoptera","Lepidoptera","Lizards","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Other insects","Syrphids")
-}
-
-heat_pollinators <- heat_pollinators_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-heat_pollinators_fan <- heat_pollinators %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_fan) <- heat_pollinators_fan[,1]
-
-heat_pollinators_Weak <- heat_pollinators %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Weak) <- heat_pollinators_Weak[,1]
-
-heat_pollinators_Strong <- heat_pollinators %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Strong) <- heat_pollinators_Strong[,1]
-
-heat_pollinators_Medium_weak <- heat_pollinators %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Medium_weak) <- heat_pollinators_Medium_weak[,1]
-
-##################
-
-#Do not know how to handle this multiplot for creating a panel
-
-# I'm going to create the 4 plots in one, 
-# I'm not sure that the grouping of the functional group is correct
-# when is done separately
-
-#sorry for the mess of libraries that I do below
-
-#Prepare first pollinators
-
-library(tidyr)
-library(data.table)
-long <- melt(setDT(heat_pollinators), id.vars = c("position","Broad_categories"), variable.name = "guilds")
-
-long_1 <- long %>% select(-Broad_categories)
-
-library(reshape2)
-long_m <- acast(long_1, position~guilds, value.var="value")
-
-#set manually the divisions, so far this is the best way I have seen to split the rows by categories
-
-r_split <- c(rep(c("Medium"), 3),rep(c("Weak"), 2),"Strong",rep(c("Medium"),2),rep(c("Weak"), 4),
-             rep(c("Medium-weak"), 2), "Strong", rep(c("Weak"), 3),rep(c("Medium-weak"), 2),
-             "Strong", "Medium")
-
-#set order of labels that avoids overlapping
-
-r_split <- factor(r_split, levels=c("Strong","Medium","Medium-weak","Weak"))
-
-#plat a bit with colors, a bit of a more complex set but looks nicer
-library(circlize)
-col_fun = colorRamp2(c(0.05644663,0.25, 0.4673256,0.75, 0.8782047), c("blue","cadetblue3", "azure2", "gold","red"))
-
-h_pol <- Heatmap(long_m, name = "Mean\npercentile", row_split=r_split,cluster_row_slices = FALSE, 
-                 column_title = "Pollinator functional groups",row_names_gp = gpar(fontsize = 10),
-                 col = col_fun,column_names_rot = 45,  column_names_gp = grid::gpar(fontsize = 10),
-                 column_title_gp = gpar(fontsize = 15, fontface = "bold"),
-                 row_title_gp = gpar(fontsize = 10, fontface = "bold"))
-
-#Prepare plants
-
-#long format
-long_plants <- melt(setDT(heat_plants), id.vars = c("position","Broad_categories"), variable.name = "Functional_groups")
-
-#filter for creating matrix
-long_plants_1 <- long_plants %>% select(-Broad_categories)
-
-#set better colnames
-long_plants_1$Functional_groups <- as.character(long_plants_1$Functional_groups)
-
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==1] <- "Selfing herbs" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==2] <- "Small outcrossing\nperennials" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==3] <- "Self-incomp. perennials\nwith large flowers" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==4] <- "Tall plants with small\nunisexual flowers" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==5] <- "Short-lived outcrossers with\nlong zygomorphic flowers"
-
-long_plants_1$Functional_groups <- factor(long_plants_1$Functional_groups, levels=c("Selfing herbs",
-"Small outcrossing\nperennials" ,"Self-incomp. perennials\nwith large flowers",
-"Tall plants with small\nunisexual flowers" ,"Short-lived outcrossers with\nlong zygomorphic flowers" ))
-
-#create matrix with reshape
-long_plants_m <- acast(long_plants_1, position~Functional_groups, value.var="value")
-
-r_split_plants <- c(rep(c("Medium"), 3),rep(c("Weak"), 2),"Strong",rep(c("Medium"),2),rep(c("Weak"), 3),
-                    rep(c("Medium-weak"), 2), "Strong", rep(c("Weak"), 4),rep(c("Medium-weak"), 2),
-                    "Strong", "Medium")
-
-r_split_plants <- factor(r_split, levels=c("Strong","Medium","Medium-weak","Weak"))
-
-h_plan <- Heatmap(long_plants_m, name = "Mean\npercentile", row_split=r_split_plants,cluster_row_slices = F, 
-                  column_title = "Plant functional groups",row_names_gp = gpar(fontsize = 10),col = col_fun,column_names_rot = 45,  
-                  column_names_gp = grid::gpar(fontsize = 10),column_title_gp = gpar(fontsize = 15, fontface = "bold"),
-                  row_title_gp = gpar(fontsize = 10, fontface = "bold"))
-
-library(patchwork)
-ht_list <- h_pol+h_plan
-
-draw(ht_list, auto_adjust = FALSE, cluster_rows = F)
-
-#Exploration of min max differences in the percentile position for plants and poll.
-#heat_pollinators[3:8]
-#
-#
-#heat_plants[3:7]
-#
-#
-#library(dplyr)
-#heat_pollinators %>%
-#  mutate(d = pmin())
-#
-#
-#colnames(heat_pollinators)<- c("position", "Broad_categories", "Bee",
-#                               "Coleoptera", "Lepidoptera","non_bee_hymenop",
-#                               "non_syrphid_dip", "syrphid")
-#
-#h <- heat_pollinators %>%
-#  mutate(min = pmin(Bee,
-#                  Coleoptera, Lepidoptera,non_bee_hymenop,
-#                  non_syrphid_dip, syrphid))%>%
-#  mutate(max = pmax(Bee,
-#                    Coleoptera, Lepidoptera,non_bee_hymenop,
-#                    non_syrphid_dip, syrphid))
-#
-#diff <- h$max-h$min
-#
-##################################################################################
-##################################################################################
-#
-#colnames(heat_plants)<- c("position", "Broad_categories", "one",
-#                               "two", "three","four",
-#                               "five")
-#
-#f <- heat_plants %>%
-#  mutate(min = pmin(1,
-#                    one, two,three,
-#                    four, five))%>%
-#  mutate(max = pmax(one,
-#                    two, three,four,
-#                    five))
-#
-#diff_1 <- f$max-f$min
-#
-#cbind(diff,diff_1)
-#
-
-```
-
-**Over- and under-represented functional group combinations of subgraphs**
-
-The different observed frequencies on the different subgraph positions showed a hierarchical order of probabilities for floral visitor functional groups (Fig.
-4).
-From the highest to lowest observed probabilities overall, we found: bees, non-syrphid Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.
-On the contrary, plant functional groups were more variable on the different subgraph positions.
-However, there were also predominant functional groups found across the different subgraph positions.
-The three most frequent groups were 'tall plants with small unisexual flowers', 'self-incompatible perennials with large flowers' and 'small outcrossing perennials'.
-On the contrary, the groups of 'selfing herbs' and 'short lived outcrossers with long zygomorphic flowers' had the lowest probability to be present on the different subgraph plant positions.
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 4.** Graphical representation of the probability of finding a given plant and floral visitor functional group $x$ in the position $\\alpha$ of motif $i$, $p_i(x,\\alpha)$, for all the possible network subgraphs from two to five species in bipartite networks.
-The slices in the nodes for a given functional group $x$ are proportional to the corresponding value of $p_i(x,\\alpha)$."}
-
-library(ggplot2)
-library(scatterpie)
-library(RColorBrewer)
-library(tidyverse)
-
-plant_means_reordered <- read_csv("../../Data/Csv/plant_abs_freq_means.csv")
-pollinator_means_reordered <- read_csv("../../Data/Csv/pollinator_abs_freq_means.csv")
-#Filter out in order to have just 6 FG'S
-pollinator_means_reordered <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds", "Lizards", "Other_insects"))
-
-# Pollinator--------
-pollinator_pies <- pollinator_means_reordered %>% select(-mean, -SE) %>% 
-  spread(Node_FG,mean_natural_units)
-
-pollinator_pies$x <- 0
-pollinator_pies$y <- 0
-
-#ggplot() + geom_scatterpie(aes(x=x, y=y, group=position,r=5), 
-#                           data = pollinator_pies,
-#                           cols=as.character(c("Bee","Birds","Coleoptera","Lepidoptera",
-#                                               "Lizards","Non-bee-Hymenoptera",
-#                                               "Non-syrphids-diptera","Other_insects",
-#                                               "Syrphids")))+
-#  coord_equal()+
-#  scale_fill_brewer(palette = "Paired")+
-#  facet_wrap(~position,nrow = 3)+
-#  theme_bw()+
-#    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
-#          panel.background = element_blank(),
-#          axis.title.x=element_blank(),axis.text.x=element_blank(),
-#          axis.ticks.x=element_blank(),axis.title.y=element_blank(),
-#          axis.text.y=element_blank(),axis.ticks.y=element_blank(),
-#          legend.position="bottom")+
-#  labs(title = "Pollinator positions",fill=NULL)
-#    
-# plant--------
-plant_pies <- plant_means_reordered %>% select(-mean, -SE) %>% 
-  spread(Node_FG,mean_natural_units)
-
-plant_pies$x <- 0
-plant_pies$y <- 0
-
-#ggplot() + geom_scatterpie(aes(x=x, y=y, group=position,r=5), 
-#                           data = plant_pies,
-#                           cols=as.character(c("1","2","3","4","5")))+
-#  coord_equal()+
-#  scale_fill_brewer(palette = "Dark2")+
-#  facet_wrap(~position,nrow = 3)+
-#  theme_bw()+
-#  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
-#        panel.background = element_blank(),
-#        axis.title.x=element_blank(),axis.text.x=element_blank(),
-#        axis.ticks.x=element_blank(),axis.title.y=element_blank(),
-#        axis.text.y=element_blank(),axis.ticks.y=element_blank(),
-#        legend.position="bottom")+
-#  labs(title = "Plant positions",fill=NULL)
-#
-
-#################################
-# CREATE PIE-MOTIFS
-#################################
-
-equidistribution <- function(number_nodes){
-
-  x_width <- 5.5/(number_nodes+1)
-
-  x_result <- rep(-1.5,number_nodes)
-
-  for(i in 1:number_nodes){
-
-    x_result[i] <- x_result[i] + i*x_width
-
-  }
-
-  return(x_result)
-
-}
-
-plot_pie_motif_positions <- function(motif_number){
-  motifs_raw_data <- read_csv("../../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-  motif_data <- motifs_raw_data %>% filter(motif_id == motif_number)
-
-  # Create dataframe with node positions
-
-  labdown = motif_data$plant %>% unique()
-
-  xdown = equidistribution(length(labdown))
-
-  ydown = rep(0,length(labdown))
-
-  labup = motif_data$pollinator %>% unique()
-
-  xup = equidistribution(length(labup))
-
-  yup = rep(2,length(labup))
-
-  d_nodes=data.frame(x=c(xdown,xup),
-                     y=c(ydown,yup),
-                     label = c(labdown,labup))
-
-  # Create a dataframe with links
-
-  plant_positions <- data.frame(plant = labdown,
-                                xdown = xdown,
-                                ydown = ydown)
-
-  pollinator_positions <- data.frame(pollinator = labup,
-                                     xup = xup,
-                                     yup = yup)
-
-  link_df <- motif_data %>% left_join(plant_positions, by = "plant") %>% 
-    left_join(pollinator_positions, by = "pollinator")
-
-  # Before plotting the motif, we remove letters from the node position id
-
-  d_nodes$label <- gsub("[^0-9.-]", "", d_nodes$label)
-  plant_pies_aux <- plant_pies %>% select(-x,-y) %>% mutate(position = as.character(position))
-
-  d_nodes_plant <- d_nodes %>% rename(position = label) %>% 
-    left_join(plant_pies_aux, by = "position") %>% as_tibble() %>%
-    filter(!is.na(`1`))
-
-  pollinator_pies_aux <- pollinator_pies %>% select(-x,-y) %>% mutate(position = as.character(position))
-
-  d_nodes_pollinator <- d_nodes %>% rename(position = label) %>% 
-    left_join(pollinator_pies_aux, by = "position") %>% as_tibble() %>%
-    filter(!is.na(Bee))
-
-  # Define the number of colors you want
- mycolors <- c("#A6CEE3", "chocolate2",  "gold2", "#1F78B4","#B2DF8A",
-                     "gray58", "lightgoldenrod2","thistle2", "burlywood","lightcoral", "olivedrab3")
-
-  ggplot() +
-    scale_shape_identity() +
-    geom_segment(data = link_df, aes(x=xdown, y=ydown, xend = xup, yend = yup), 
-                 size = 1, color = "grey20")+  geom_scatterpie(aes(x=x, y=y, group=position,r=.45), 
-    data = d_nodes_pollinator, cols=as.character(c("Bee","Coleoptera","Lepidoptera","Non-bee-Hymenoptera", "Non-syrphids-diptera","Syrphids"))) +
-    geom_scatterpie(aes(x=x, y=y, group=position,r=0.45), 
-                    data = d_nodes_plant,
-                    cols=as.character(c("1","2","3","4","5")))+
-    coord_fixed()+
-    scale_fill_manual(values = mycolors,"test",
-      breaks=c("Bee","Coleoptera","Lepidoptera",
-               "Non-bee-Hymenoptera", "Non-syrphids-diptera",
-               "Syrphids","1","2","3","4","5"), labels=c("Bees","Coleoptera","Lepidoptera",
-"Non-bee-Hymenoptera", "Non-syrphids-Diptera","Syrphids", 
-          "Selfing herbs","Small outcrossing perennials","Self-incomp. perennials\nwith large flowers",
-          "Tall plants with small\nunisexual flowers","Short-lived outcrossers with\nlong zygomorphic flowers"))+
-    xlim(-1.5,4)+ ylim(-0.5,2.5)+
-    theme(panel.background = element_blank(),
-          axis.text.x=element_blank(),
-          axis.ticks.x=element_blank(),
-          axis.text.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          legend.title = element_text(size=12, face="bold"),legend.background = element_rect(size=0.5, linetype="solid",colour ="black"))+
-    labs(x=NULL,y=NULL)+
-    guides(color = FALSE,fill=guide_legend(title="Functional groups"))+
-    ggtitle(paste0("Motif ",motif_number))+
-    theme(plot.title = element_text(hjust = 0.5),legend.key.size = unit(0.5, 'cm'))+
-    theme(plot.margin=unit(c(0,0,0,0),"cm"))
-}
-
-motif_number <- 1
-p1 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 2
-p2 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 3
-p3 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 4
-p4 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 5
-p5 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 6
-p6 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 7
-p7 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 8   
-p8 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 9
-p9 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 10
-p10 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 11
-p11 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 12
-p12 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 13
-p13 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 14
-p14 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 15
-p15 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 16
-p16 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 17
-p17 <- plot_pie_motif_positions(motif_number)
-
-library(patchwork)
-
-(p1 & ylab("2 species")| p2 & ylab("3 species") | p3  |plot_spacer()|plot_spacer())/ 
-  (p4 & ylab("4 species")| p5 | p6 | p7|plot_spacer())/ 
-  (p8  & ylab("5 species")| p9 | p10 | p11 | p12) / 
-  (p13 & ylab("5 species")| p14 | p15 | p16 | p17) + plot_layout(guides = 'collect') &
-  theme(axis.title.y = element_text(color="black", size=14, face="bold"),legend.position = "bottom")
-
-```
-
-The statistical comparison with z-scores between the observed and expected plant and floral visitor functional group combinations showed that we can not recover the observed combinations from its probability of occurrence.
-In fact, most combinations are under- or over- represented and follow a modified Gaussian distribution (Johnson's $S_U$) with 65$\%$ of under-represented group combinations, 20$\%$ of no statistical difference and 15$\%$ of under-represented ones (Fig.
-5).
-In addition, subgraphs with small node combinations (i.e., 2 and 3 nodes) only appeared as under-represented.
-Network subgraphs with 4 and 5 node combinations appeared in the three statistical categories, but 4 node subgraphs had a higher proportion in the under-represented category (10% in comparison with the 1$\%$ and the 3$\%$ of the no statistical difference and over-represented categories, respectively).
-Finally, 5 node subgraphs were in similar proportions in the no statistical difference and over-represented categories (99$\%$ and 97$\%$, respectively), but they appeared in lower proportion in the under-represented category (89$\%$).
-When we explored the identity on the different positions of the most probable subgraph combinations, we found that the most common plant and floral visitor functional groups were also the most probable on these plant and floral visitor combinations within the different subgraphs (lower panel Fig.
-5).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 5.** Distribution of z-scores values after the statistical comparison of the observed probabilities of finding a subgraph combination in real networks and the expected probabilities (obtained by computer simulations).
-The resulting z-scores frequencies of this statiscal comparison are coloured based on a 95% confidence level: under-represented ($z_i^O < -1.96$, red), no statistical difference ($-1.96 \\geq z_i^O \\leq  1.96$, green) and over-represented ($z_i^O > 1.96$, blue).
-For instance, for a z-score value of 0 there were approximately 800 subgraph combinations that showed no statistical difference in the comparison between real and simulated networks.
-In addition, four specific graphical examples of the most probable subgraphs being observed on each category are also provided and the different plant and floral visitor functional groups are represented with distinct colour codes as indicated in the legend."}
-
-library(tidyverse)
-library(RColorBrewer)
-
-equidistribution <- function(number_nodes){
-
-  x_width <- 5.5/(number_nodes+1)
-
-  x_result <- rep(-1.5,number_nodes)
-
-  for(i in 1:number_nodes){
-
-    x_result[i] <- x_result[i] + i*x_width
-
-  }
-
-  return(x_result)
-
-}
-
-plot_motif_label <- function(label){
-
-  label_split <- str_split(label,"_")[[1]]
-  motif_number <- as.numeric(label_split[1])
-  nodes <- label_split[2:length(label_split)]
-  plant_nodes <- nodes[nodes %in% plant_means_reordered$Node_FG]
-  pollinator_nodes <- nodes[nodes %in% pollinator_means_reordered$Node_FG]
-
-  motifs_raw_data <-read_csv("../../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-  motif_data <- motifs_raw_data %>% filter(motif_id == motif_number)
-
-  # Create dataframe with node positions
-
-  labdown = motif_data$plant %>% unique()
-
-  xdown = equidistribution(length(labdown))
-
-  ydown = rep(0,length(labdown))
-
-  labup = motif_data$pollinator %>% unique()
-
-  xup = equidistribution(length(labup))
-
-  yup = rep(1,length(labup))
-
-  d_nodes=data.frame(x=c(xdown,xup),
-                     y=c(ydown,yup),
-                     label = c(labdown,labup))
-
-  # Create a dataframe with links
-
-  plant_positions <- data.frame(plant = labdown,
-                                xdown = xdown,
-                                ydown = ydown)
-
-  pollinator_positions <- data.frame(pollinator = labup,
-                                     xup = xup,
-                                     yup = yup)
-
-  link_df <- motif_data %>% left_join(plant_positions, by = "plant") %>% 
-    left_join(pollinator_positions, by = "pollinator")
-
-  # Add FG IDs to nodes
-  FG_IDs <- tibble(label = c(sort(labdown),sort(labup)),
-                   FG = c(plant_nodes,pollinator_nodes))
-
-  d_nodes_FG <- d_nodes %>% left_join(FG_IDs, by = "label")
-  levels_FG <- c("Bee","Coleoptera","Lepidoptera",
-                 "Non-bee-Hymenoptera", "Non-syrphids-diptera",
-                 "Syrphids","1","2","3","4","5")
-
-  d_nodes_FG$FG <- factor(d_nodes_FG$FG, levels = levels_FG)
-
-  levels(d_nodes_FG$FG) <- c("Bee","Coleoptera","Lepidoptera",
-                             "Non-bee-Hymenoptera", "Non-syrphids-diptera",
-                             "Syrphids","1","2","3","4","5")
-
-  # Before plotting the motif, we remove letters from the node position id
-
-  d_nodes_FG$label <- gsub("[^0-9.-]", "", d_nodes_FG$label)
-
-  # Define the number of colors you want
- mycolors <- c("#A6CEE3", "chocolate2",  "gold2", "#1F78B4","#B2DF8A",
-                     "gray58", "lightgoldenrod2","thistle2", "burlywood","lightcoral", "olivedrab3")
-
-  ggplot(data=d_nodes_FG, aes(x, y)) +
-    scale_shape_identity() +
-    geom_segment(data = link_df, aes(x=xdown, y=ydown, xend = xup, yend = yup), size = 1, color = "grey20")+
-    geom_point(aes(color = FG), size=7.5)+
-    geom_text(aes(x, y , label = label), size=3)+
-    scale_color_manual(drop = FALSE, values = mycolors,
-                       breaks=c("Bee","Coleoptera","Lepidoptera",
-                                "Non-bee-Hymenoptera", "Non-syrphids-diptera",
-                                "Syrphids","1","2","3","4","5"), 
-                       labels=c("Bees","Coleoptera","Lepidoptera",
-                                "Non-bee-Hymenoptera", "Non-syrphids-Diptera",
-                                "Syrphids", 
-                                "Selfing herbs","Small outcrossing perennials",
-                                "Self-incomp. perennials\nwith large flowers",
-                                "Tall plants with small\nunisexual flowers",
-                                "Short-lived outcrossers with\nlong zygomorphic flowers"))+
-    xlim(-1.5,4)+ ylim(-0.5,1.5)+
-    theme(panel.background = element_blank(),
-          axis.text.x=element_blank(),
-          axis.ticks.x=element_blank(),
-          axis.text.y=element_blank(),
-          axis.ticks.y=element_blank())+
-    labs(x=NULL,y=NULL)+
-    ggtitle(paste0("Motif ",motif_number))+
-    theme(plot.title = element_text(hjust = 0.5,size=10))+
-    guides(color=guide_legend(title="Functional groups"))
-
-}
-
-# Data with pollinator/plant labels
-
-plant_means_reordered <- read_csv("../../Data/Csv/plant_abs_freq_means.csv")
-pollinator_means_reordered <- read_csv("../../Data/Csv/pollinator_abs_freq_means.csv")
-#Filter out in order to have just 6 FG'S
-pollinator_means_reordered <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds", "Lizards", "Other_insects"))
-
-####################################################################################################
-#Read data to check top 5 motif of each category of observed propabilities
-
-#Under, No signi, Over-rep
-####################################################################################################
-# Check top Z-scores of each group (Under, No diff, Over)
-
-#Read data
-data <- read.csv("../../Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
-
-#Find critical value of Z-score
-p <- 0.05 #cutoff probability 95% confidence
-critical_value <- qnorm(p/2) #double tail probability divide by 2
-
-data_1 <- data %>%
-  mutate(infra_over_represented = case_when(
-    z_score < -abs(critical_value) ~ "infra",
-    between(z_score, -abs(critical_value), abs(critical_value)) ~ "no_diff",
-    z_score > abs(critical_value) ~ "over"
-  ))
-
-#data_2 <- filter(data_1, abs(z_score)<2000) 
-#str(data_2)
-
-#Select under-represented by the ones with highest porbability of being observed (top10)
-under_data <- filter(data_1, infra_over_represented=="infra")
-
-under_top_5 <- filter(under_data, row_number(desc(abs(motif_observed_probability)))<= 5) %>%
-  select(motif_functional_ID,motif_observed_probability,counts_observed,z_score)
-
-#Select no statistical difference by the ones with highest porbability of being observed (top5)
-no_diff_data <- filter(data_1, infra_over_represented=="no_diff")
-
-no_diff_top_5 <- filter(no_diff_data, row_number(desc(abs(motif_observed_probability)))<= 5) %>%
-  select(motif_functional_ID,motif_observed_probability,counts_observed,z_score)
-
-#Select over-represenetd by the ones with highest porbability of being observed (top5)
-over_data <- filter(data_1, infra_over_represented=="over")
-
-over_top_5 <- filter(over_data, row_number(desc(abs(motif_observed_probability)))<= 5) %>%
-  select(motif_functional_ID,motif_observed_probability,counts_observed,z_score)
-####################################################################################################
-#Now plot it 
-####################################################################################################
-
-library(patchwork)
-
-#Prepare list of 5 plots for each group
-#Under
-labels_under <- under_top_5$motif_functional_ID
-p_under <- list()
-
-for (i in 1:5){
-
-  p_under[[i]] <- plot_motif_label(labels_under[[i]])
-}
-
-#No signficance
-labels_nodiff <- no_diff_top_5$motif_functional_ID
-p_nodiff <- list()
-
-for (i in 1:5){
-
-  p_nodiff[[i]] <- plot_motif_label(labels_nodiff[[i]])
-}
-
-#Over
-labels_over <- over_top_5$motif_functional_ID
-p_over <- list()
-
-for (i in 1:5){
-
-  p_over[[i]] <- plot_motif_label(labels_over[[i]])
-}
-
-#Run Script with histogram plot
-source("../../Scripts/Z-score_percentile_histogram_plot.R")
-
-hist <- ggplot(data_2 %>% filter(round_motif_observed_probability>0), aes(x=z_score, color=infra_over_represented, fill=infra_over_represented)) + 
-  geom_histogram(bins = 93, alpha = 0.5, position = "identity",lwd = 0.25)+
-  geom_vline(xintercept = -abs(critical_value))+
-  geom_vline(xintercept = abs(critical_value))+
-  xlim(-60,60) + ylab("Frequency")+  theme_bw() +
-  scale_fill_manual(name="Motif frequencies" ,values=c("coral2", "palegreen3", "cyan3"), labels=c("Under-represented",
-                                                                                                  "No statistical difference", "Over-represented")) +
-  scale_color_manual(name="Motif frequencies" ,values=c("coral2", "palegreen3", "cyan3"), labels=c("Under-represented",
-                                                                                                   "No statistical difference", "Over-represented")) + xlab("Z-score")
-
-t_col <- function(color, percent = 50, name = NULL) {
-  #      color = color name
-  #    percent = % transparency
-  #       name = an optional name for the color
-
-  ## Get RGB values for named color
-  rgb.val <- col2rgb(color)
-
-  ## Make new color using input color as base and alpha set by transparency
-  t.col <- rgb(rgb.val[1], rgb.val[2], rgb.val[3],
-               max = 255,
-               alpha = (100 - percent) * 255 / 100,
-               names = name)
-
-  ## Save the color
-  invisible(t.col)
-}
-## END
-
-#Prepare panel of plots
-hist / ((p_under[[1]]/p_under[[2]]/p_under[[3]]/p_under[[4]] & theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_rect(fill=t_col("coral2")))) | 
-          (p_nodiff[[1]]/p_nodiff[[2]]/p_nodiff[[3]]/p_nodiff[[4]]& theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_rect(fill=t_col("palegreen3")))) |
-          (p_over[[1]]/p_over[[2]]/p_over[[3]]/p_over[[4]] & theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_rect(fill=t_col("cyan3"))))) + plot_layout(guides = 'collect')
-
-```
-
-# Discussion
-
-Understanding the global patterns of network structure is key to unravel the processes that govern community dynamics [@bascompte2007; @bastolla2009; @guimaraes2020].
-However, common analytical approaches at the node or at the global network level are unable to capture the full complexity of ecological systems [@simmons2019; @bergamo2021].
-Because network subgraphs can capture both direct and indirect interactions, by analysing their over- and under-representation we were able to explore in great detail the structure of interactions between animal pollinators and the plants they visit.
-We have explored for the first time the overall structure and presence of network motifs in real plant-pollinator networks and shown that, according to our first hypothesis, the different subgraphs up to five nodes are consistently over- or under-represented in comparison with simulated networks.
-In addition, we show that for plant-pollinator networks there is a general tendency for over-representation of network subgraphs that are more densely connected (i.e., complete, fan and asymmetric complete).
-Indeed, the work of @simmons2020 has shown with the help of simulated plant-pollinator networks that the main different processes that shape plant-pollinator communities (i.e., neutral effects, trait matching and phenology) generate different patterns of direct and indirect interactions, and that specifically, a higher proportion of these more densely connected subgraphs is associated with neutral effects.
-Therefore, as indicated for other network properties like nestedness at the macro-scale level [@krishna2008; @suweis2013], or interaction probability at the species level [@bartomeus2016], our findings align with our second hypothesis and indicate that neutral effects may be also the main driver governing this intermediate level of complexity on plant-pollinator networks.
-
-Overall, generalist network motifs for floral visitors were consistently over-represented (e.g., complete subgraphs; Fig.
-2).
-For instance, when we compare network subgraphs with equal structure for both trophic levels, we found that floral visitors had always over-representation in the positions that implied the highest number of direct links (e.g., positions 16 and 46 from network subgraphs 7 and 17, respectively).
-Despite this being in good agreement with the current view of the generalist nature of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of generalist network motifs was driven by the functional group of bees while the rest of the functional groups tended to be under-represented (Fig.
-S6 A).
-In contrast, non-bee groups were over-represented in subgraph positions associated with specialised roles.
-This large effect of bees on the overall patterns is no surprise, as bees were the group with the largest number of interaction records in the whole set of networks as also shown for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017].
-Just syrphids had a relatively similar number of interactions in comparison with bees (1,768 and 2,256 interactions, respectively) and similar species richness (343 and 321 species, respectively).
-However, both functional groups were associated with contrasting ecological roles likely indicating that both number of interactions and richness are not driving the observed interaction patterns for the different functional groups.
-Interestingly, bees also were the group with lower number of indirect interactions, while the rest of floral visitor groups showed a clearly higher number of indirect interactions, indicating that these non-bee floral visitor groups may experience higher competitive interactions for floral resources [@thomson2020].
-Despite plant functional groups showed little differences between them on their subgraph frequencies, all groups showed a tendency to be over-represented on subgraph positions that were associated with higher levels of specialisation.
-This tendency towards specialist roles may be the result of co-evolutionary processes (e.g., trait-matching) between plants and pollinators to optimise pollen transfer [@moreira2019].
-Remarkably, only tall plants with small unisexual flowers showed higher frequencies on subgraphs that were associated with low number of indirect interactions with likely direct implications on pollen transfer for this group that needs to guarantee cross-pollination.
-
-The probabilities of appearance of each functional group on the different subgraph positions were insufficient to predict most of the observed network position combinations (Fig.
-5).
-This implies that not just the representation of network subgraphs types but also the identity of the elements of their structure is non-random.
-Notably, we found that just 30$\%$ of the possible 53,250 subgraph combinations are realised.
-Thus, similarly to the presence of forbidden links at the network level [@olesen2011; @jordano2016], we also found the existence of forbidden subgraph positions and those represented almost two thirds of the total possible subgraph combinations.
-This concurs well with the general idea that plant-pollinator networks have a high proportion of non-realized direct interactions [@jordano2003; @bascompte2013], and, as a result, also a high proportion of non-realized combinations of indirect interactions.
-Some of these non-observed direct interactions are probably due to under-sampling [@dorado2011; @jordano2016].
-However, a large fraction of the possible interactions do not take place because of different constraints such as species co-occurrence, trait matching processes and phenological uncoupling [@olesen2011; @bartomeus2016; @jordano2016].
-Despite the advances in the understanding of the ecological processes that influence species pairwise interactions [@bartomeus2016; @peralta2020], we still know little about how these processes determine competitive and facilitative interactions in mutualistic networks.
-Thus, as suggested by @simmons2020, exploring the proportion of these realised network subgraphs that are competitive or facilitative is a necessary next step to improve our understanding of the architecture of biodiversity [@bascompte2007].
-
-Despite the obvious usefulness of functional groups in summarising species ecological roles (e.g., similar reproductive biology for plants and behaviour for pollinators), delimiting species into functional groups is often not trivial.
-For instance, taxonomic diversity and trait availability limit our ability to properly represent the wide range of reproductive strategies [@dellinger2020] and different clustering analysis can lead to distinct outcomes (e.g., k-means and hierarchical clustering).
-We divided floral visitors on the taxonomic rank level because it adequately represented pollinator ecological roles without the tremendous effort of compiling trait data for over 1,000 species of floral visitors.
-Indeed, further groupings with traits could help reveal greater relevance of trait-matching processes on indirect interactions.
-Moreover, we analysed network subgraphs focusing exclusively on presence or absence of interactions, assuming that all interactions are equally important.
-However, further work should investigate how to account for quantitative measurements of plant-pollinator interactions.
-Consistent with previous work [@simmons2019; @simmons2020], we characterised network motifs by using null models only constrained for network connectance.
-Although more complex null models are difficult to interpret [@Ulrich2013], they can potentially allow us to separate the mechanisms by which motifs emerge.
-However, we found that null models with more constraints generated binary structures that were mostly identical to the original ones.
-In addition, we observed that connectance, nestedness and degree distribution were significantly correlated (data not shown).
-All that highlights the difficulties to disentangle the potential sources that generate over-representation of network subgraphs and the need to investigate them.
-At the same time, although network subgraphs can capture both direct and indirect interactions, the reduction of network complexity into these different building blocks inevitably convey the loss of information [@simmons2019], for example indirect interactions from large cascading effects.
-Finally, despite the wide geographical coverage of our plant-pollinator dataset, there are major gaps for some regions of the world with a clear bias towards Europe, America and islands which have long interested ecologists [@macarthur1963; @warren2015].
-These biases are also found in global datasets of networks, where the data is highly fragmented across space [@poisot2021] and more efforts are needed to capture global patterns of plant-pollinator interactions.
-
-In conclusion, by following the framework of @simmons2020 we have been able to explore competitive and facilitative interactions in plant-pollinator networks worldwide and found the presence of worldwide motifs that highlight the non-random structure of indirect interactions.
-This non-random structure might emerge due to neutral effects according to previous modelling work [@simmons2020].
-Further, we found that plant and floral visitor functional groups are associated with different subgraph positions that involve distinct ecological roles (e.g., generalisation versus specialisation) and that the different subgraph combinations are strongly constrained.
-Although we are still far from predicting how species interact, our work is a first step to elucidate beyond pairwise interactions.
-
-# Acknowledgements
-
-This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2).
-JBL also thanks the University of New England for the funding provided to carry out this work.
-Finally, we would like to thank David García-Callejas for his useful comments on the manuscript before submission.
-
-# Author contributions
-
-IB, AA-P and JBL designed the idea. JBL collected the data. AA-P led the analysis with contributions of JBL and guidance of IB. JBL wrote the manuscript with contributions of IB and AA-P.
-
-# Data Availability Statement
-
-All data and code are publicly available at Github (<https://github.com/JoseBSL/FunctionalMotifs>) and Zenodo (<https://doi.org/10.5281/zenodo.6489213>).
-
-\newpage
-
-# References
-
-::: {#refs}
-:::

### 2023-01-25 Manuscript/Figures/Figure2.Rmd
Word file and independent figures for typesetting

--- 2022-10-08 Manuscript/Main_text/Main_text_Journal_of_Animal_Ecol.Rmd
@@
   word_document: default
-always_allow_html: true
-bibliography: bibliography.bib
-biblio-style: apalike
-csl: JournalOfAnimalEcology.csl #converted from funct ecol style from zotero styles
 ---
-
-**Jose B. Lanuza^1,2^** \| **Alfonso Allen-Perkins^2,3^** \| **Ignasi Bartomeus^2^**
-
-1 School of Environmental and Rural Science, University of New England, Armidale, New South Wales 2350, Australia.
-
-2 Estación Biológica de Doñana (EBD-CSIC), E-41092 Seville, Spain.
-
-3 Departamento de Ingeniería Eléctrica, Electrónica, Automática y Física Aplicada, ETSIDI, Universidad Politécnica de Madrid, 28040 Madrid, Spain.
-
-\captionsetup[table]{labelformat=empty}
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
-
-# Abstract
-
-\singlespacing
-
-Ecological processes leave distinct structural imprints on the species interactions that shape the topology of animal-plant mutualistic networks.
-Detecting how direct and indirect interactions between animals and plants are organised is not trivial since they go beyond pairwise interactions, but may get blurred when considering global network descriptors.
-Recent work has shown that the meso-scale, the intermediate level of network complexity between the species and the global network, can capture this important information.
-The meso-scale describes network subgraphs representing patterns of direct and indirect interactions between a small number of species, and when these network subgraphs differ statistically from a benchmark, they are often referred to as "network motifs".
-Although motifs can capture relevant ecological information of species interactions, they remain overlooked in natural plant-pollinator networks.
-By exploring 60 empirical plant-pollinator networks from 18 different studies with wide geographical coverage, we show that some network subgraphs are consistently under- or over-represented, suggesting the presence of worldwide network motifs in plant-pollinator networks.
-In addition, we found a higher proportion of densely connected network subgraphs that, based on previous findings, could reflect that species relative abundances are the main driver shaping the structure of the meso-scale on plant-pollinator communities.
-Moreover, we found that distinct subgraph positions describing species ecological roles (e.g., generalisation and number of indirect interactions) are occupied by different groups of animal and plant species representing their main life-history strategies (i.e., functional groups).
-For instance, we found that the functional group of 'bees' was over-represented in subgraph positions with a lower number of indirect interactions in contrast to the rest of floral visitors groups.
-Finally, we show that the observed functional group combinations within a subgraph can not be retrieved from their expected probabilities (i.e., joint probability distributions), indicating that plant and floral visitor associations within subgraphs are not random either.
-Therefore, our results highlight the presence of common network motifs in plant-pollinator communities that are formed by a non-random association of plants and floral visitors functional groups.
-
-Keywords: pollinators, plant-pollinator networks, plant-pollinator interactions, network motifs, indirect interactions, floral visitors
-
-\doublespacing
-
-\newpage
-
-# Introduction
-
-Ecological communities are formed by a plethora of interacting species that form networks of interactions.
-Because of the tremendous complexity of these ecological networks, species interactions are generally condensed in metrics that summarise this information [@guimaraes2020].
-Plant-pollinator interactions are no exception, and they are often studied with indices that aggregate the information at the network (macro-scale) and species level (micro-scale).
-For example, plant-pollinator network level approaches have identified common invariant structural properties across mutualistic networks, including a degree distribution that decays as a truncated power law [@jordano1987], nestedness [@bascompte2003], or modularity [@olesen2007].
-In addition, the local species position within the network can define its degree of selectiveness [@bluthgen2006] or its role in connecting the rest of the community [@olesen2007].
-Despite the unquestionable progress with the use of these metrics at both network and species level, condensing complex information into a single metric implies the loss of relevant ecological information that obscures the understanding of species interactions [@cirtwill2018; @simmons2019].
-
-Indirect interactions, the mediated effect between two species by a third species, are ubiquitous in natural systems [@strauss1991; @holt1994; @wootton1994] and play a key role in shaping community dynamics [@werner2003; @walsh2013].
-Some of the most studied indirect interactions are the ones caused by trophic cascades with consumer-resource interactions [@abrams1996; @schmitz2001].
-In fact, previous studies focus on antagonistic interactions and mutualistic interactions are often overlooked [@knight2005].
-On the contrary, plant-pollinator research has traditionally investigated direct interactions but neglected indirect effects such as competitive or facilitative processes between plants for pollinators [@moeller2004; @sargent2008; @carvalheiro2014].
-Conventional analytical tools in bipartite networks often discard relevant information about indirect interactions by condensing the information into single indices either at species or network level [@cirtwill2018; @simmons2019].
-However, as previously explored with three species modules in unipartite food webs [@allesina2008; @stouffer2010], the emergent framework of bipartite subgraphs has proven to be a powerful analytical tool to better understand plant-pollinator community dynamics by capturing both direct and indirect effects [@simmons2019].
-These network subgraphs that constitute the meso-scale are often referred to as the building blocks of the network and when their numbers occur at higher frequencies than in randomised networks, those are generally defined as 'network motifs' [@milo2002].
-Indeed, the analysis of motifs in simulated plant-pollinator networks has revealed that the different drivers that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect effects [@simmons2020].
-However, the global patterns of indirect interactions in real plant-pollinator networks and their ecological consequences remain unexplored (e.g., over- and under- represented network subgraphs).
-
-By linking the structural properties of the meso-scale with the species' ecology we can advance in our understanding on the determinants of species interactions.
-For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species' functional role [@stouffer2012; @baker2015; @cirtwill2018b].
-Yet, our understanding of the ecological implications of network motifs in real plant-pollinator networks remains in its infancy.
-Moreover, it is unclear how the species ecology and life-history traits determine its functional role within the network of interactions [@coux2016].
-For example, large pollinators can forage larger distances [@greenleaf2007], deposit greater pollen quantities [@foldesi2021] and handle complex zygomorphic flowers in comparison with small pollinators that are restricted to lower floral complexity [@gong2009].
-Despite these obvious differences in pollinator behaviour, how contrasting species' ecology translates into different network motifs is still poorly known.
-Similarly, recent empirical findings indicate that the meso-scale is the best descriptor of plant reproductive success [@allen2021], but little is known about how plants' reproductive strategies shape their position within the network of interactions.
-Although some studies have evaluated plant reproductive strategies in plant-pollinator networks [@tur2013; @lazaro2020], this is an often overlooked aspect in a community context [@devaux2014] and rarely incorporated into plant-pollinator network studies.
-Hence, exploring how the main plant and floral visitor life-history strategies integrate with the emergent framework of network motifs could help to progress knowledge on the ecological processes that shape plant-pollinator interactions.
-
-Here we evaluate the interaction patterns of the meso-scale and its ecological implications in plant-pollinator networks with the help of 60 empirical networks from 18 different studies distributed across 14 different countries.
-For this, plants and pollinators were divided into functional groups that summarise their main life-history strategies and the different networks were split into all their subgraph elements up to five nodes.
-First, based on previous knowledge showing the non random assembly of macro-scale mutualistic networks [@bascompte2003] and food webs [@dunne2002], we test the hypothesis that the building blocks that constitute the meso-scale in plant-pollinator networks have a non-random structure of interactions with over- and under-represented subgraphs (i.e., motifs) that represent contrasting ecological roles.
-Second, because species relative abundances (i.e., neutral effects) are one of the main drivers of network macro-struture [@krishna2008; @suweis2013; @bartomeus2016], we hypothesise that neutral effects may also govern the interaction patterns of the meso-scale in plant-pollinator networks.
-Finally, we explore if plants and pollinators functional groups are associated with subgraph positions that imply distinct ecological roles and if there are over- and under-represented functional group combinations within the different network subgraphs.
-
-# Methods
-
-**Overview**
-
-To investigate the structure of the meso-scale in plant-pollinator networks, we gathered published plant-pollinator networks with worldwide distribution.
-Then, we classified the different plant and floral visitor species from these networks into functional groups that summarise their main life-history strategies.
-We calculated the normalised subgraph frequencies and investigated if these frequencies are similar or not to the ones expected by chance with the help of null models.
-Then, for each group of plants and floral visitors we investigated the ecological implications of their overall representation on the different subgraph positions, by comparing, on the one hand, the observed (normalised) frequencies of each group in the different subgraph positions with the frequencies of their simulated counterparts, and, on the other hand, the differences among groups per subgraph position in terms of their number of indirect interactions and specialisation.
-Finally, to understand if the different functional group combinations within a subgraph are structured, we compare if the observed functional group combinations from empirical networks can be retrieved from the joint probability distribution of the expected frequencies of the different plant and floral visitor groups within network subgraphs.
-
-**Plant-pollinator studies**
-
-We have compiled 60 plant-pollinator networks from 18 different studies (Table S1).
-All studies sampled plant-pollinator interactions in natural systems in a single flowering season and were selected based on wide geographical coverage (Fig.
-S1) and presence of interaction frequency as a measure of interaction strength.
-In total, there were 503 plant species, 1,111 floral visitors species and 6,248 pairwise interactions registered.
-For ease of data manipulation, plant and floral visitor species names were standardised with the help of the R package *taxize* version *0.9.99* [@chamberlain2020].
-
-**Plant and floral visitor functional groups**
-
-First, plant species were grouped through hierarchical clustering into the optimal number of functional groups that summarises the main plant reproductive strategies.
-For this, we used the plant trait dataset compiled in @lanuza2021 that consisted also of plant species that belonged to the same plant-pollinator networks plus some additional meta-networks not considered here.
-This dataset comprised a total of 1,506 plant species including the 503 species considered in this study (Table S2).
-Because most of these plant species are likely to benefit from animal pollination, we used reproductive traits relevant to understand the different plant reproductive strategies and their interactions with pollinators.
-After excluding traits with a high percentage of missing values (over 30$\%$), we ended up with 8 floral, 3 reproductive biology and 3 plant morphology traits (see Table S3 for a list of all traits).
-Floral traits included those associated with the size, form and number of floral organs (e.g., style length or ovule number).
-Reproductive biology traits described the reproductive system of the plant (e.g., mating and compatibility systems) and plant morphology traits were associated with the size and form of the plant (i.e., plant height, lifespan and life form).
-After an extensive search for each plant species on several different resources (e.g., plant databases, online floras, books, journals and images), over 80% of the cells of the whole dataset were filled.
-Thus, to avoid the loss of species with trait missing values, missing trait data was imputed as detailed in @lanuza2021.
-
-We opted to calculate the plant functional groups within a larger set of species because of the higher accuracy when delimiting functional groups with that many variables and species [@dolnicar2014].
-To feed the clustering analysis, we calculated the distance between the different qualitative and scaled quantitative variables with Gower distance [@gower1971].
-For this, we used the function *gowdis* with method *ward.D2* from the *FD* package version *1.0-12* [@laliberte2014].
-Finally, we conducted hierarchical clustering with the function *hclust* from the *R* stats package version *4.0.5* and calculated the optimal number of clusters with the function *kgs* from the *maptree* package version *1.4-7* [@white2009].
-
-Second, floral visitors were aggregated into taxonomic groups (hereafter referred to as functional groups) based on taxonomic rank as done similarly in other plant-pollinator studies [@fenster2004; @ollerton2009].
-We opted to divide floral visitors on the taxonomic rank level and not with functional traits because the main orders of floral visitors differed in form and behaviour and had lower superior taxonomic complexity (i.e., floral visitors had 6 orders versus plants that had 38).
-Thus, this allowed us to group floral visitors into functional groups that represented approximately the main life-history strategies of the possible pollinators: (i) bees (Hymenoptera-Anthophila), (ii) non-bee Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Syrphidae-Diptera), (iv) non-syrphids-Diptera, (v) Lepidoptera and (vi) Coleoptera.
-However, a minor set of species belonged to other functional groups that were considered in analyses but not discussed further because of their low representation in the full set of networks (3.55$\%$ of the total interactions recorded).
-These taxonomic groups were 'lizards', 'birds' and 'other insects'.
-This last functional group was formed by a mix of uncommon insect taxa on the full set of networks.
-
-**Overall network subgraphs patterns**
-
-Following previous work [@simmons2019; @simmons2020], we broke down the plant-pollinator networks into their constituent network subgraphs that can capture both direct and indirect interactions.
-Prior to analyses, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.
-This approach was preferred since quantitative subgraph analyses have been developed just recently and more work is needed to fully understand and interpret the information that they can convey [@simmons2020].
-All analyses were run considering singletons (species with only one interaction detected) but we conducted a second exploration without singletons (64.98$\%$ of interactions) to evaluate the effect of rare species on the observed patterns.
-Results without singletons are qualitatively consistent and are not further discussed in the main text (Figs S2 and S3).
-
-We calculated the frequency of all subgraphs up to five nodes (17 different subgraphs in total; see Fig.
-1) for each empirical network, by using the *bmotif* package version *2.0.2* [@bmotifsimmons2019].
-We focused exclusively on subgraphs up to five nodes in our analyses for computational reasons and for the ease of visualization and interpretation of a reduced set of less complex network structures.
-Throughout the entire manuscript, floral visitors occupy the top nodes of the different network subgraphs and plants the bottom ones.
-To control for variation in network size, subgraph frequencies were normalised as a proportion of the total number of subgraphs within each subgraph class (i.e., 2-species, 3-species, 4-species and 5-species network subgraphs).
-In addition, we excluded 2-species (or 2-nodes) subgraphs from our analyses because its normalised frequencies would always equal one.
-Note that the aim is not comparing different networks, which may differ in sampling effort, but correctly describing the structure of each individual network.
-Like @simmons2020, we classified the different subgraphs by their average path length (mean number of links between all pairs of nodes) into four different groups: (i) complete or strong ($\overline{x} = 1.38$), (ii) fan or medium-strong ($\overline{x} = 1.48$), (iii) assymmetric complete or medium-weak ($\overline{x} = 1.60$) and (iv) core-peripheral or weak ($\overline{x} = 1.85$), where $\overline{x}$ represents the mean of the average path length across subgraphs within the same group.
-In general terms, plant and floral visitor groups on more densely connected network subgraphs (e.g., complete or fan) will experience lower number of indirect interactions in contrast to groups on less densely connected structures (e.g., medium-weak or weak).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, fig.pos="t", warning=FALSE,out.width="75%",fig.align="center", fig.cap="\\textbf{Figure 1.} Adapted figure of Simmons et al., (2019).
-All possible network subgraphs from two to five species in bipartite networks grouped by the different subgraph classes (2-species, 3-species, 4-species and 5-species).
-There are a total of 17 possible subgraphs with 46 different positions denoted within each node.
-The different subgraphs are aggregated by the broad indirect interaction structures they represent on four different groups (strong, medium-strong, medium-weak and weak).
-For each group, we show in the legend the mean value of the average path length of all subgraphs within it.
-The different path length groups range from densely connected network structures (strong subgraphs where all possible interactions are realised and the mean path length is minimum) to weakly connected ones (weak subgraphs where the mean path length is maximum).", fig.width=10,fig.height=8}
-library(tidyverse)
-library(RColorBrewer)
-source("../../Scripts/Scripts_Alfonso/plot_motif_positionsV2.R")
-
-motif_number <- 1
-p1 <- plot_motif_positions(motif_number) +
-geom_point(aes(color = as.factor(label)),size=10,color = "grey90")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 2
-p2 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 3
-p3 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 4
-p4 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 5
-p5 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "lightcoral")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 6
-p6 <- plot_motif_positions(motif_number) +
-geom_point(aes(color = as.factor(label)),size=10,color = "goldenrod2")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 7
-p7 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 8   
-p8 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 9
-p9 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "lightcoral")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 10
-p10 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "lightcoral")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 11
-p11 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "skyblue")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 12
-p12 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "goldenrod2")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 13
-p13 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "lightcoral")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 14
-p14 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "lightcoral")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 15
-p15 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "skyblue")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 16
-p16 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "goldenrod2")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 17
-p17 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
-geom_text(aes(x, y , label = label),size=3)
-
-library(patchwork)
-
-p <- (p1 & ylab("2 species")| p2 & ylab("3 species") | p3 ) /
-(p4 & ylab("4 species")| p5 | p6 | p7) / 
-(p8  & ylab("5 species")| p9 | p10 | p11 | p12) /
-(p13 & ylab("5 species")| p14 | p15 | p16 | p17) &
-theme(axis.title.y = element_text(color="black", size=14, face="bold"))
-
-#Create custom legend
-a <- c(1,2,3,4)
-b <- c(1,2,3,4)
-c <- c("a","b", "c", "d")
-abc <- data.frame(a,b,c)
-p1 <- ggplot(abc, aes(x=a,y=b, color=c))+geom_point() + theme_bw() + 
-  scale_colour_manual(name = 'Path length classification', 
-                      values =c(a= 'goldenrod2',b='mediumaquamarine',
-                                c='skyblue', d='lightcoral'), 
-                      labels = c(a='Strong \n mean path length = 1.38', 
-                                 b='Medium-strong \n mean path length = 1.48',
-                                 c='Medium-weak \n mean path length = 1.60',
-                                 d='Weak \n mean path length = 1.85'))+
-theme(legend.position="bottom")+ guides(colour = guide_legend(override.aes = list(size=8),title.position="top", title.hjust = 0.5))
-
-legend <- cowplot::get_legend(p1+ theme(legend.position = "bottom",legend.text = element_text(size=10), legend.title = element_text(size=12, 
-face="bold"),legend.box.background = element_rect(color="black", size=2)))
-
-cowplot::plot_grid(p, legend, ncol = 1, rel_heights = c(12, 1.8))
-
-```
-
-To assess the significance of the observed frequencies, we created 1,000 simulated networks for each binary network using the *nullmodel* function and the *vaznull* model in the *bipartite* package version *2.14* [@dormann2009].
-Generated networks had the same number of plants and floral visitors, as well as the same connectance of their corresponding empirical networks.
-We discarded null models with more constraints (e.g., constraining for species degree) because the permutations did not generate sufficient variability and provided highly similar or identical networks to the original ones.
-After extracting the subgraph frequencies from the simulated networks, for each subgraph type and empirical network, we calculated the percentage of simulated networks whose frequencies were smaller than the ones observed, that is, we estimated the percentile of the observed subgraph frequencies.
-Subgraphs whose percentile is close to 0 or 100 are under- or over-represented in empirical networks, respectively, and indicate the presence of network motifs as they differ statistically from the network structures generated with simulated networks.
-To summarise general patterns across networks, we used an intercept-only linear mixed model (LMM) per subgraph with the help of the *lme4* package version *1.1-21* [@bates2015], where the response variable was the observed subgraph percentile per network.
-Note that as we are only interested in modelling the intercept value, no predictors were specified.
-In these models, we used the study identifiers in Table S1 as a random intercept.
-By doing so, we obtained estimates of the average subgraph frequency, but controlling for the variation at the study level.
-
-**Over- and under-represented functional groups on subgraph positions**
-
-We calculated which plant and floral visitor functional groups were over- or under-represented in the different subgraph positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
-To estimate the position frequencies of each plant and floral visitor group in a given network, we added the frequencies of those species that belong to the same group, and then, we normalised the resulting frequencies by dividing them by the total number of times that a corresponding group appears in any position within the same subgraph size class.
-Then, we calculated the percentile of the observed position frequencies for each functional group and network, just like we did with subgraph frequencies.
-To outline the general patterns of position frequencies across networks and groups, we fit a LMM per subgraph position, where the response variable was the observed position percentile per network.
-We used the group identifier as an explanatory variable and the study identifiers as a random intercept.
-Hence, we assessed the average subgraph frequency per species group, after controlling for the variation at the study level.
-Finally, we visualised over- and under-representation of plant and floral visitor groups on the different subgraph positions with the help of the *ComplexHeatmap* package version *2.6.2* [@gu2016].
-
-To understand if the different plant and floral visitor functional groups are associated with subgraph positions that represent different network roles, we characterised the roles of each subgraph position for the different functional groups in terms of their specialisation and number of indirect interactions.
-To that end, we calculated the specificity of each subgraph position following @poisot2015 as $s_i = (L - l_i) / (L - 1)$, where $L$ is the total number of groups and $l_i$ the number of interaction partners of the group $i$ in a given subgraph.
-Values of the vector $si$, range between 1, complete specialisation (1 partner within the subgraph) and 0 complete generalism (all possible partners within the subgraph).
-Then, because all nodes within a motif are connected, we calculated the number of indirect interactions ($\theta_i$) for each motif position as $\theta_i=m_i-k_i-1$, where $m_i$ is the total number of nodes in a given motif, and $k_i$ represents the degree of the corresponding motif position, that is, the total number of links connected to such position.
-Thus, we considered all possible indirect interactions for each position.
-Finally, we analysed in a single model how specialisation and the number of indirect interactions were associated with the observed percentiles for each trophic guild and subgraph position.
-For this, we fitted again a LMM model with the help of the *lme4* package, where we considered specialisation and number of indirect interactions as response variables with the interaction by plant and floral visitor group for both response variables.
-Further, we considered as random factor subgraph position nested within study system.
-
-**Over- and under-represented functional group combinations of subgraphs**
-
-Finally, we studied which combinations of plant and floral visitor functional groups tend to appear together within the same subgraphs (up to five nodes).
-That is, which combinations are over- or under-represented.
-This analysis used 57 out of the 60 networks available due to computational limitations to identify all the nodes in the subgraphs of the three networks with the highest number of links.
-To do so, for each of the 53,250 possible subgraph combinations, we estimated the observed and the expected probability of finding those combinations in empirical networks, respectively.
-Then, we determined whether the observed probabilities are likely to come from the expected probabilities or not.
-To calculate the observed probability ($p_i^O$) of the different groups within a subgraph $i$ (e.g., subgraph 3, 'bee' + 'bee' + 'selfing herbs'), we divided the number of times that $i$ appears in our set of empirical networks ($n_i^O$) by the sum of the number of times that each possible combination appeared: $p_i^O = n_i^O / \sum_{k=1}^{53,250} n_k^O$.
-To estimate the expected probability ($p_i^E$) of a given subgraph combination $i$, we assumed that the probability of finding a given functional group $x$ in the position $\alpha$ is independent of the probabilities associated with other positions and groups in that subgraph.
-Therefore, the expected probability ($p_i^E$) of the subgraph combination $i$ is given by the product of the probabilities of its constituents, i.e., $p_i^E = \prod _{(x,\alpha )\in i} p_i(x,\alpha)$, where $p_i(x,\alpha)$ is the probability of finding a given functional group $x$ in the position $\alpha$ of $i$.
-Then, by controlling for the variation at the network level with an LMM (see below), we calculated the average number of times that the functional group $x$ appears in the position $\alpha$ (denoted as $n_i(x,\alpha)$).
-To obtain the expected probability $p_i(x,\alpha)$, we divided the number of times that the group $x$ appears in the position $\alpha$ by the the total number of times that any group was observed in that position (that is, $p_i(x,\alpha) = n_i(x,\alpha)/\sum_{k}n_i(k,\alpha)$).
-The average number of times that the group $x$ appears in the position $\alpha$ ($n_i(x,\alpha)$) was calculated with a LMM for each position, where the response variable was the number of times that a group was observed at a given position in each real-world network, the explanatory variable was the group identifier, and the random intercept was given by network identifiers nested within the study identifiers.
-
-Once we obtained $p_i^O$ and $p_i^E$, we used a simulation approach to determine whether the former is likely to come from the latter or not.
-This approach was preferred since the large number of possible subgraph combinations and the small probabilities for some of them advise against using an exact test of goodness-of-fit or a Chi-square one.
-Specifically, we created 1,000 random samples with repetition of possible subgraph combinations, where each sample contained 10 million elements and, for each combination, the probability of being selected was equal to its expected probability.
-From those random samples, we extracted the mean and the standard deviation of the expected probability of $i$, denoted as $E\left [ p_i^E \right ]$ and $\sigma\left [ p_i^E \right ]$, respectively, and calculated the z-scores of $p_i^O$ as $z_i^O = \left ( p_i^O - E\left [ p_i^E \right ] \right )/\sigma \left [ p_i^E \right ]$, for those motif combinations with $p_i^O > 0$.
-According to the usual interpretation of z-scores, combinations with $z_i^O > 1.96$ are over-represented, whereas those with $z_i^O < -1.96$ are under-represented, at the 95$\%$ confidence level.
-Notice that we focused on combinations with $p_i^O > 10^{-7}$ because we do not have enough numerical resolution to accurately detect whether combinations that took place only once are under-represented (due to the limited size of our random samples).
-
-All analyses and data manipulation were conducted in R *version 4.0.5* [@R].
-In addition, all model diagnostics were conducted with the help of the *Dharma* package [@hartig2017] version *0.3.3.0* and model outputs were visualised with the *visreg* package [@breheny2020] version 2.7.0.
-
-# RESULTS
-
-**Plant and floral visitor functional groups**
-
-The hierarchical cluster analysis divided the dataset into five different plant functional groups with different and overlapping characteristics (Figs S4 and S5).
-The first group referred to as 'selfing herbs' consisted of herbs with hermaphroditic flowers with high levels of autonomous selfing.
-The second group named 'small outcrossing perennials' had small perennial species with a mix of life forms (i.e., trees, shrubs and herbs) with outcrossing hermaphroditic flowers.
-The third group referred to as 'self-incompatible perennials with large flowers' comprised perennial species with a mixed of life forms and large self-incompatible hermaphroditic flowers with high number of ovules.
-The fourth group named 'tall plants with small unisexual flowers' had the tallest species, highest proportion of shrub and tree life forms, dioecious and monoecious breeding systems, small flowers, and the highest numbers of flowers and inflorescences per plant.
-Finally, the fifth group named 'short-lived outcrossers with long zygomorphic flowers' consisted of small perennial and short-lived herbs with long self-compatible zygomorphic flowers that were unable to self-pollinate.
-
-In total, there were 1,126 species of floral visitors with 6,325 interactions recorded with plants.
-Most plants interacted with bees (2,256 interactions) and non-syrphid Diptera (1,768) followed by syrphids (845), Lepidoptera (437), Coleoptera (432) and non-bee Hymenoptera (362).
-
-**Overall network subgraphs patterns**
-
-Most network subgraphs were under- or over-represented (close to the 1st and 99th percentile, respectively) in the comparison between empirical and simulated networks (Fig.
-2).
-Network subgraphs 3, 5, 9, 10 and 14 were under-represented in empirical networks, that is, all were close to the 1st percentile and under the 25th percentile.
-Interestingly, four out of five of these motifs belonged to the largest path length classification (i.e., core-peripheral).
-In addition, network subgraphs 2, 6, 7, 16 and 17 were over-represented, all over the 75th percentile.
-In contrast to the under-represented network subgraphs, over-represented subgraphs belonged to the two shortest path length groups (i.e., complete and fan).
-The remaining network subgraphs (i.e., 4, 8, 11, 12, 13, and 15) were between the 25th and 75th percentile.
 
@@
 ```
-
-**Over- and under-represented functional groups on subgraph positions**
-
-```{r , include=FALSE}
-
-#SAME SCRIPT AS THE PLOTTING FOR THE HEATMAP BUT I NEED IT HERE TO LOAD THE VARIABLES WITH VALUES ON RESULTS
-
-library(lme4)
-library(nlme)
-library(tidyverse)
-library(stringi)
-source("../../Scripts/Scripts_Alfonso/add_study_id.R")
-
-#############################################
-# EXTRACT MEAN VALUES
-#############################################
-all_position_percentiles <- read_csv("../../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
-
-all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
-                                                              "[0-9]+") %>% as.numeric()
-
-all_position_percentiles <- add_study_id(all_position_percentiles)
-#str(all_position_percentiles)
-#head(all_position_percentiles)
-
-list_plants_FG <- as.character(1:10)
-
-plant_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF)) #ME DA ERROR
-pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF))
-
-# Plants-------------
-
-# Mean percentile and SE taking into account the study system
-plant_codes <- plant_position_percentiles_filtered$position %>% unique()
-plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-plant_means$mean <- NA
-plant_means$SE <- NA
-
-for(i.pos in 1:length(plant_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
-            data = plant_position_percentiles_filtered %>%
-              filter(position == plant_codes[i.pos]))
-
-  temp <- fixed.effects(m) %>% unname()
-  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
-                                                                    temp[1]+temp[2],
-                                                                    temp[1]+temp[3],
-                                                                    temp[1]+temp[4],
-                                                                    temp[1]+temp[5]) ## to get real means per FG
-  temp <- sqrt(diag(vcov(m)))
-  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
-                                                                  temp[1]+temp[2],
-                                                                  temp[1]+temp[3],
-                                                                  temp[1]+temp[4],
-                                                                  temp[1]+temp[5])
-
-}
-
-# Pollinators--------
-
-# Mean percentile and SE taking into account the study system
-pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
-pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-pollinator_means$mean <- NA
-pollinator_means$SE <- NA
-pollinator_means_reordered <- NULL
-
-for(i.pos in 1:length(pollinator_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = pollinator_position_percentiles_filtered %>%
-              filter(position == pollinator_codes[i.pos]),
-            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
-
-  temp <- fixed.effects(m) %>% unname()
-  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)
-
-  pollinator_means_aux$mean <- c(temp[1],
-                                 temp[1]+temp[2],
-                                 temp[1]+temp[3],
-                                 temp[1]+temp[4],
-                                 temp[1]+temp[5],
-                                 temp[1]+temp[6],
-                                 temp[1]+temp[7],
-                                 temp[1]+temp[8],
-                                 temp[1]+temp[9]) ## to get real means per FG
-
-  temp <- sqrt(diag(vcov(m)))
-  pollinator_means_aux$SE <- c(temp[1],
-                               temp[1]+temp[2],
-                               temp[1]+temp[3],
-                               temp[1]+temp[4],
-                               temp[1]+temp[5],
-                               temp[1]+temp[6],
-                               temp[1]+temp[7],
-                               temp[1]+temp[8],
-                               temp[1]+temp[9])
-
-  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)
-
-}
-
-# There are lower limits (mean - SE) smaller than 0 (see Other insects)
-# We set the lower limit of those error bars to zero
-
-pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
-pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
-
-#############################################
-# ADDING BROAD MOTIF CATEGORIES TO POSITIONS
-#############################################
-
-motifs_raw_data <- read_csv("../../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-motifs_raw_data$Broad_categories <- NA
-
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(5,9,14,13,10)] <- "Core-peripherical"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(6,16,12)] <- "Complete"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(2,3,7,4,17,8)] <- "Fan"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(15,11)] <- "Asymmetric complete"
-
-motifs_raw_data$plant <- gsub("[^0-9.-]", "", motifs_raw_data$plant)
-motifs_raw_data$pollinator <- gsub("[^0-9.-]", "", motifs_raw_data$pollinator)
-motifs_raw_data$plant <- as.numeric(motifs_raw_data$plant)
-motifs_raw_data$pollinator <- as.numeric(motifs_raw_data$pollinator)
-motifs_raw_data <- motifs_raw_data %>% filter(!is.na(Broad_categories))
-
-fan_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-pollinator_means_reordered$Broad_categories <- NA
-
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% fan_pollinator] <- "Fan" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% asymm_pollinator] <- "Medium-weak" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% complete_pollinator] <- "Strong" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% core_per_pollinator] <- "Weak"
-
-fan_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-plant_means$Broad_categories <- NA
-
-plant_means$Broad_categories[plant_means$position %in% fan_plant] <- "Fan" 
-plant_means$Broad_categories[plant_means$position %in% asymm_plant] <- "Medium-weak" 
-plant_means$Broad_categories[plant_means$position %in% complete_plant] <- "Strong" 
-plant_means$Broad_categories[plant_means$position %in% core_per_plant] <- "Weak"
-
-################################################################################
-# Alternative code to HEATMAPS to create variables with values to load on text
-# in a reproducible/automated way
-################################################################################
-
-# PLANTS-----
-
-# Prepare data for heatmap
-heat_plants_aux <- plant_means %>% spread(Node_FG,mean) %>% select(-SE)
-
-heat_plants <- heat_plants_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-# POLLINATORS-----------
-
-filter_rare_groups <- T
-
-if(filter_rare_groups == T){
-  heat_pollinators_aux <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds",
-                                                                                "Lizards",
-                                                                                "Other_insects")) %>% 
-    spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees",            
-                                      "Coleoptera","Lepidoptera","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Syrphids")
-}else{
-  heat_pollinators_aux <- pollinator_means_reordered %>% spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees","Birds",            
-                                      "Coleoptera","Lepidoptera","Lizards","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Other insects","Syrphids")
-}
-
-heat_pollinators <- heat_pollinators_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))
-
-#Check percentage of over and under represented
-colMeans(heat_pollinators[,c(3:8)] < 0.25)
-poll_under_25 <- colMeans(heat_pollinators[,c(3:8)] < 0.25)
-poll_under_25 <- specify_decimal((poll_under_25[[1]] + poll_under_25[[2]] + poll_under_25[[3]] +
-poll_under_25[[4]] + poll_under_25[[5]] + poll_under_25[[6]])/6*100,2)
-#[1] 32.57576
-
-colMeans(heat_pollinators[,c(3:8)] > 0.75)
-poll_over_75 <- colMeans(heat_pollinators[,c(3:8)] > 0.75)
-poll_over_75 <- specify_decimal((poll_over_75[[1]] + poll_over_75[[2]] + poll_over_75[[3]] +
-    poll_over_75[[4]] + poll_over_75[[5]] + poll_over_75[[6]])/6*100,2)
-#[1] 4.545455
-
-#################################################################################
-#################################################################################
-
-colnames(heat_plants)<- c("position", "Broad_categories", "one",
-                               "two", "three","four",
-                               "five")
-f <- heat_plants %>%
-  mutate(min = pmin(1,
-                    one, two,three,
-                    four, five))%>%
-  mutate(max = pmax(one,
-                    two, three,four,
-                    five))
-
-diff_1 <- f$max-f$min
-
-cbind(diff,diff_1)
-
-#Check percentage of over and under represented per FG
-colMeans(heat_plants[,c(3:7)] < 0.25)
-plant_under_25 <- colMeans(heat_plants[,c(3:7)] < 0.25)
-plant_under_25 <- specify_decimal((plant_under_25[[1]] + plant_under_25[[2]] + plant_under_25[[3]] + 
-    plant_under_25[[4]] + plant_under_25[[5]])/5*100,2)
-#[1] 18.18182
-colMeans(heat_plants[,c(3:7)] > 0.75)
-plant_over_75 <- colMeans(heat_plants[,c(3:7)] > 0.75)
-plant_over_75 <- specify_decimal((plant_over_75[[1]] + plant_over_75[[2]] + plant_over_75[[3]] + 
-    plant_over_75[[4]] + plant_over_75[[5]])/5*100,2)
-#[1] 8.181818
-
-#overall percentages
-under <- specify_decimal((as.numeric(poll_under_25) + as.numeric(plant_under_25))/2,2)
-over <- specify_decimal((as.numeric(poll_over_75) + as.numeric(plant_over_75))/2,2)
-
-```
-
-The comparison of the plant and floral visitor functional group frequencies per subgraph position between empirical and simulated networks showed a `r over`$\%$ and `r under`$\%$ of over- (>75$^{th}$) and under-represented (\<25th) functional groups in the different positions, respectively (Fig.
-3).
-Floral visitors showed a total of `r poll_over_75`$\%$ and `r poll_under_25`$\%$ of over- and under-represented functional groups in the different positions, and plants `r plant_over_75`$\%$ and `r plant_under_25`$\%$ of over- and under-represented functional groups, respectively.
-Notably, the differences across functional groups were more marked for floral visitors than for plants (the differences between the minimum and maximum values of the percentiles per position were generally two-three times larger for floral visitors).
-From most over- to under-represented floral visitors functional groups on the different subgraph positions (indicated with the dendrogram order in Fig.
-3), we found: bees, non-syrphids Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.
-Although plant functional groups showed less differences between them, there were also more represented functional groups than others.
-Thus, from most over- to under-represented functional groups on the different subgraph positions we found: self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.
-
-For both floral visitor and plant functional groups we found over- and under-representation on different subgraph positions that implied different ecological roles.
-First, for floral visitors, we found that bees were less frequent on subgraph positions that involved specialisation (i.e., lower specificity values) while the rest of functional groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) were infrequent in generalised subgraph positions with low number of indirect interactions (Fig.
-S6 A).
-Although plants did not show differences with null models on their frequencies, all plant functional groups but tall plants with small unisexual flowers showed a slight tendency to be over-represented on specialised subgraph positions (Fig.
-S6 B).
-Second, regarding the number of indirect interactions, bees were over-represented in subgraph positions with low number of indirect interactions (Fig.
-S7 A) and the rest of floral visitor functional groups showed no differences across positions in comparison with simulated networks.
-For plants, all functional groups showed a slight tendency to be over-represented on subgraph positions with higher number of indirect interactions (Fig.
-S7 B).
-When we further explore the observed frequencies by number of indirect interactions for floral visitor and plant functional groups, we found that both bees and tall plants with small unisexual flowers were the only functional groups with high frequencies on subgraph positions associated with low number of indirect interactions in comparison with the other floral visitor and plant functional groups (Figs S8 and S9).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', out.width="80%",fig.cap="\\textbf{Figure 3.} Heatmap indicating under- and over-representation of floral visitor and plant functional groups in the different subgraph positions (numbers on the right of each heatmap).
-The different subgraph positions are dividied by the average path length clasification determined by Simmons et al.
-(2020) and they are ordered from the most densely connected network structures (strong or complete) to the less connected ones (weak or core-peripheral).
-The superior dendrogram indicates the differences across functional groups with the more separated groups showing larger differences."}
-
-library(lme4)
-library(nlme)
-library(tidyverse)
-library(stringi)
-source("../../Scripts/Scripts_Alfonso/add_study_id.R")
-
-#############################################
-# EXTRACT MEAN VALUES
-#############################################
-
-all_position_percentiles <- read_csv("../../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
-
-all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
-                                                              "[0-9]+") %>% as.numeric()
-
-all_position_percentiles <- add_study_id(all_position_percentiles)
-#str(all_position_percentiles)
-#head(all_position_percentiles)
-
-list_plants_FG <- as.character(1:10)
-
-plant_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF)) #ME DA ERROR
-pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF))
-
-# Plants-------------
-
-# Mean percentile and SE taking into account the study system
-plant_codes <- plant_position_percentiles_filtered$position %>% unique()
-plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-plant_means$mean <- NA
-plant_means$SE <- NA
-
-for(i.pos in 1:length(plant_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
-            data = plant_position_percentiles_filtered %>%
-              filter(position == plant_codes[i.pos]))
-
-  temp <- fixed.effects(m) %>% unname()
-  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
-                                                                    temp[1]+temp[2],
-                                                                    temp[1]+temp[3],
-                                                                    temp[1]+temp[4],
-                                                                    temp[1]+temp[5]) ## to get real means per FG
-  temp <- sqrt(diag(vcov(m)))
-  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
-                                                                  temp[1]+temp[2],
-                                                                  temp[1]+temp[3],
-                                                                  temp[1]+temp[4],
-                                                                  temp[1]+temp[5])
-
-}
-
-# Pollinators--------
-
-# Mean percentile and SE taking into account the study system
-pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
-pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-pollinator_means$mean <- NA
-pollinator_means$SE <- NA
-pollinator_means_reordered <- NULL
-
-for(i.pos in 1:length(pollinator_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = pollinator_position_percentiles_filtered %>%
-              filter(position == pollinator_codes[i.pos]),
-            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
-
-  temp <- fixed.effects(m) %>% unname()
-  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)
-
-  pollinator_means_aux$mean <- c(temp[1],
-                                 temp[1]+temp[2],
-                                 temp[1]+temp[3],
-                                 temp[1]+temp[4],
-                                 temp[1]+temp[5],
-                                 temp[1]+temp[6],
-                                 temp[1]+temp[7],
-                                 temp[1]+temp[8],
-                                 temp[1]+temp[9]) ## to get real means per FG
-
-  temp <- sqrt(diag(vcov(m)))
-  pollinator_means_aux$SE <- c(temp[1],
-                               temp[1]+temp[2],
-                               temp[1]+temp[3],
-                               temp[1]+temp[4],
-                               temp[1]+temp[5],
-                               temp[1]+temp[6],
-                               temp[1]+temp[7],
-                               temp[1]+temp[8],
-                               temp[1]+temp[9])
-
-  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)
-
-}
-
-# There are lower limits (mean - SE) smaller than 0 (see Other insects)
-# We set the lower limit of those error bars to zero
-
-pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
-pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
-
-#############################################
-# ADDING BROAD MOTIF CATEGORIES TO POSITIONS
-#############################################
-
-motifs_raw_data <- read_csv("../../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-motifs_raw_data$Broad_categories <- NA
-
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(5,9,14,13,10)] <- "Core-peripherical"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(6,16,12)] <- "Complete"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(2,3,7,4,17,8)] <- "Fan"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(15,11)] <- "Asymmetric complete"
-
-motifs_raw_data$plant <- gsub("[^0-9.-]", "", motifs_raw_data$plant)
-motifs_raw_data$pollinator <- gsub("[^0-9.-]", "", motifs_raw_data$pollinator)
-motifs_raw_data$plant <- as.numeric(motifs_raw_data$plant)
-motifs_raw_data$pollinator <- as.numeric(motifs_raw_data$pollinator)
-motifs_raw_data <- motifs_raw_data %>% filter(!is.na(Broad_categories))
-
-fan_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-pollinator_means_reordered$Broad_categories <- NA
-
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% fan_pollinator] <- "Fan" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% asymm_pollinator] <- "Medium-weak" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% complete_pollinator] <- "Strong" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% core_per_pollinator] <- "Weak"
-
-fan_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-plant_means$Broad_categories <- NA
-
-plant_means$Broad_categories[plant_means$position %in% fan_plant] <- "Fan" 
-plant_means$Broad_categories[plant_means$position %in% asymm_plant] <- "Medium-weak" 
-plant_means$Broad_categories[plant_means$position %in% complete_plant] <- "Strong" 
-plant_means$Broad_categories[plant_means$position %in% core_per_plant] <- "Weak"
-
-########################################
-# CREATE HEATMAPS
-########################################
-
-library(ComplexHeatmap)
-
-# PLANTS-----
-
-# Prepare data for heatmap
-heat_plants_aux <- plant_means %>% spread(Node_FG,mean) %>% select(-SE)
-
-heat_plants <- heat_plants_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-heat_plants_fan <- heat_plants %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_fan) <- heat_plants_fan[,1]
-
-heat_plants_Weak <- heat_plants %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Weak) <- heat_plants_Weak[,1]
-
-heat_plants_Strong <- heat_plants %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Strong) <- heat_plants_Strong[,1]
-
-heat_plants_Medium_weak <- heat_plants %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Medium_weak) <- heat_plants_Medium_weak[,1]
-
-# POLLINATORS-----------
-
-filter_rare_groups <- T
-
-if(filter_rare_groups == T){
-  heat_pollinators_aux <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds",
-                                                                                "Lizards",
-                                                                                "Other_insects")) %>% 
-    spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees",            
-                                      "Coleoptera","Lepidoptera","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Syrphids")
-}else{
-  heat_pollinators_aux <- pollinator_means_reordered %>% spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees","Birds",            
-                                      "Coleoptera","Lepidoptera","Lizards","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Other insects","Syrphids")
-}
-
-heat_pollinators <- heat_pollinators_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-heat_pollinators_fan <- heat_pollinators %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_fan) <- heat_pollinators_fan[,1]
-
-heat_pollinators_Weak <- heat_pollinators %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Weak) <- heat_pollinators_Weak[,1]
-
-heat_pollinators_Strong <- heat_pollinators %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Strong) <- heat_pollinators_Strong[,1]
-
-heat_pollinators_Medium_weak <- heat_pollinators %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Medium_weak) <- heat_pollinators_Medium_weak[,1]
-
-##################
-
-#Do not know how to handle this multiplot for creating a panel
-
-# I'm going to create the 4 plots in one, 
-# I'm not sure that the grouping of the functional group is correct
-# when is done separately
-
-#sorry for the mess of libraries that I do below
-
-#Prepare first pollinators
-
-library(tidyr)
-library(data.table)
-long <- melt(setDT(heat_pollinators), id.vars = c("position","Broad_categories"), variable.name = "guilds")
-
-long_1 <- long %>% select(-Broad_categories)
-
-library(reshape2)
-long_m <- acast(long_1, position~guilds, value.var="value")
-
-#set manually the divisions, so far this is the best way I have seen to split the rows by categories
-
-r_split <- c(rep(c("Medium"), 3),rep(c("Weak"), 2),"Strong",rep(c("Medium"),2),rep(c("Weak"), 4),
-             rep(c("Medium-weak"), 2), "Strong", rep(c("Weak"), 3),rep(c("Medium-weak"), 2),
-             "Strong", "Medium")
-
-#set order of labels that avoids overlapping
-
-r_split <- factor(r_split, levels=c("Strong","Medium","Medium-weak","Weak"))
-
-#plat a bit with colors, a bit of a more complex set but looks nicer
-library(circlize)
-col_fun = colorRamp2(c(0.05644663,0.25, 0.4673256,0.75, 0.8782047), c("blue","cadetblue3", "azure2", "gold","red"))
-
-h_pol <- Heatmap(long_m, name = "Mean\npercentile", row_split=r_split,cluster_row_slices = FALSE, 
-                 column_title = "Pollinator functional groups",row_names_gp = gpar(fontsize = 10),
-                 col = col_fun,column_names_rot = 45,  column_names_gp = grid::gpar(fontsize = 10),
-                 column_title_gp = gpar(fontsize = 15, fontface = "bold"),
-                 row_title_gp = gpar(fontsize = 10, fontface = "bold"))
-
-#Prepare plants
-
-#long format
-long_plants <- melt(setDT(heat_plants), id.vars = c("position","Broad_categories"), variable.name = "Functional_groups")
-
-#filter for creating matrix
-long_plants_1 <- long_plants %>% select(-Broad_categories)
-
-#set better colnames
-long_plants_1$Functional_groups <- as.character(long_plants_1$Functional_groups)
-
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==1] <- "Selfing herbs" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==2] <- "Small outcrossing\nperennials" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==3] <- "Self-incomp. perennials\nwith large flowers" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==4] <- "Tall plants with small\nunisexual flowers" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==5] <- "Short-lived outcrossers with\nlong zygomorphic flowers"
-
-long_plants_1$Functional_groups <- factor(long_plants_1$Functional_groups, levels=c("Selfing herbs",
-"Small outcrossing\nperennials" ,"Self-incomp. perennials\nwith large flowers",
-"Tall plants with small\nunisexual flowers" ,"Short-lived outcrossers with\nlong zygomorphic flowers" ))
-
-#create matrix with reshape
-long_plants_m <- acast(long_plants_1, position~Functional_groups, value.var="value")
-
-r_split_plants <- c(rep(c("Medium"), 3),rep(c("Weak"), 2),"Strong",rep(c("Medium"),2),rep(c("Weak"), 3),
-                    rep(c("Medium-weak"), 2), "Strong", rep(c("Weak"), 4),rep(c("Medium-weak"), 2),
-                    "Strong", "Medium")
-
-r_split_plants <- factor(r_split, levels=c("Strong","Medium","Medium-weak","Weak"))
-
-h_plan <- Heatmap(long_plants_m, name = "Mean\npercentile", row_split=r_split_plants,cluster_row_slices = F, 
-                  column_title = "Plant functional groups",row_names_gp = gpar(fontsize = 10),col = col_fun,column_names_rot = 45,  
-                  column_names_gp = grid::gpar(fontsize = 10),column_title_gp = gpar(fontsize = 15, fontface = "bold"),
-                  row_title_gp = gpar(fontsize = 10, fontface = "bold"))
-
-library(patchwork)
-ht_list <- h_pol+h_plan
-
-draw(ht_list, auto_adjust = FALSE, cluster_rows = F)
-
-#Exploration of min max differences in the percentile position for plants and poll.
-#heat_pollinators[3:8]
-#
-#
-#heat_plants[3:7]
-#
-#
-#library(dplyr)
-#heat_pollinators %>%
-#  mutate(d = pmin())
-#
-#
-#colnames(heat_pollinators)<- c("position", "Broad_categories", "Bee",
-#                               "Coleoptera", "Lepidoptera","non_bee_hymenop",
-#                               "non_syrphid_dip", "syrphid")
-#
-#h <- heat_pollinators %>%
-#  mutate(min = pmin(Bee,
-#                  Coleoptera, Lepidoptera,non_bee_hymenop,
-#                  non_syrphid_dip, syrphid))%>%
-#  mutate(max = pmax(Bee,
-#                    Coleoptera, Lepidoptera,non_bee_hymenop,
-#                    non_syrphid_dip, syrphid))
-#
-#diff <- h$max-h$min
-#
-##################################################################################
-##################################################################################
-#
-#colnames(heat_plants)<- c("position", "Broad_categories", "one",
-#                               "two", "three","four",
-#                               "five")
-#
-#f <- heat_plants %>%
-#  mutate(min = pmin(1,
-#                    one, two,three,
-#                    four, five))%>%
-#  mutate(max = pmax(one,
-#                    two, three,four,
-#                    five))
-#
-#diff_1 <- f$max-f$min
-#
-#cbind(diff,diff_1)
-#
-
-```
-
-**Over- and under-represented functional group combinations of subgraphs**
-
-The different observed frequencies on the different subgraph positions showed a hierarchical order of probabilities for floral visitor functional groups (Fig.
-4).
-From the highest to lowest observed probabilities overall, we found: bees, non-syrphid Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.
-On the contrary, plant functional groups were more variable on the different subgraph positions.
-However, there were also predominant functional groups found across the different subgraph positions.
-The three most frequent groups were 'tall plants with small unisexual flowers', 'self-incompatible perennials with large flowers' and 'small outcrossing perennials'.
-On the contrary, the groups of 'selfing herbs' and 'short lived outcrossers with long zygomorphic flowers' had the lowest probability to be present on the different subgraph plant positions.
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 4.** Graphical representation of the probability of finding a given plant and floral visitor functional group $x$ in the position $\\alpha$ of motif $i$, $p_i(x,\\alpha)$, for all the possible network subgraphs from two to five species in bipartite networks.
-The slices in the nodes for a given functional group $x$ are proportional to the corresponding value of $p_i(x,\\alpha)$."}
-
-library(ggplot2)
-library(scatterpie)
-library(RColorBrewer)
-library(tidyverse)
-
-plant_means_reordered <- read_csv("../../Data/Csv/plant_abs_freq_means.csv")
-pollinator_means_reordered <- read_csv("../../Data/Csv/pollinator_abs_freq_means.csv")
-#Filter out in order to have just 6 FG'S
-pollinator_means_reordered <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds", "Lizards", "Other_insects"))
-
-# Pollinator--------
-pollinator_pies <- pollinator_means_reordered %>% select(-mean, -SE) %>% 
-  spread(Node_FG,mean_natural_units)
-
-pollinator_pies$x <- 0
-pollinator_pies$y <- 0
-
-#ggplot() + geom_scatterpie(aes(x=x, y=y, group=position,r=5), 
-#                           data = pollinator_pies,
-#                           cols=as.character(c("Bee","Birds","Coleoptera","Lepidoptera",
-#                                               "Lizards","Non-bee-Hymenoptera",
-#                                               "Non-syrphids-diptera","Other_insects",
-#                                               "Syrphids")))+
-#  coord_equal()+
-#  scale_fill_brewer(palette = "Paired")+
-#  facet_wrap(~position,nrow = 3)+
-#  theme_bw()+
-#    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
-#          panel.background = element_blank(),
-#          axis.title.x=element_blank(),axis.text.x=element_blank(),
-#          axis.ticks.x=element_blank(),axis.title.y=element_blank(),
-#          axis.text.y=element_blank(),axis.ticks.y=element_blank(),
-#          legend.position="bottom")+
-#  labs(title = "Pollinator positions",fill=NULL)
-#    
-# plant--------
-plant_pies <- plant_means_reordered %>% select(-mean, -SE) %>% 
-  spread(Node_FG,mean_natural_units)
-
-plant_pies$x <- 0
-plant_pies$y <- 0
-
-#ggplot() + geom_scatterpie(aes(x=x, y=y, group=position,r=5), 
-#                           data = plant_pies,
-#                           cols=as.character(c("1","2","3","4","5")))+
-#  coord_equal()+
-#  scale_fill_brewer(palette = "Dark2")+
-#  facet_wrap(~position,nrow = 3)+
-#  theme_bw()+
-#  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
-#        panel.background = element_blank(),
-#        axis.title.x=element_blank(),axis.text.x=element_blank(),
-#        axis.ticks.x=element_blank(),axis.title.y=element_blank(),
-#        axis.text.y=element_blank(),axis.ticks.y=element_blank(),
-#        legend.position="bottom")+
-#  labs(title = "Plant positions",fill=NULL)
-#
-
-#################################
-# CREATE PIE-MOTIFS
-#################################
-
-equidistribution <- function(number_nodes){
-
-  x_width <- 5.5/(number_nodes+1)
-
-  x_result <- rep(-1.5,number_nodes)
-
-  for(i in 1:number_nodes){
-
-    x_result[i] <- x_result[i] + i*x_width
-
-  }
-
-  return(x_result)
-
-}
-
-plot_pie_motif_positions <- function(motif_number){
-  motifs_raw_data <- read_csv("../../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-  motif_data <- motifs_raw_data %>% filter(motif_id == motif_number)
-
-  # Create dataframe with node positions
-
-  labdown = motif_data$plant %>% unique()
-
-  xdown = equidistribution(length(labdown))
-
-  ydown = rep(0,length(labdown))
-
-  labup = motif_data$pollinator %>% unique()
-
-  xup = equidistribution(length(labup))
-
-  yup = rep(2,length(labup))
-
-  d_nodes=data.frame(x=c(xdown,xup),
-                     y=c(ydown,yup),
-                     label = c(labdown,labup))
-
-  # Create a dataframe with links
-
-  plant_positions <- data.frame(plant = labdown,
-                                xdown = xdown,
-                                ydown = ydown)
-
-  pollinator_positions <- data.frame(pollinator = labup,
-                                     xup = xup,
-                                     yup = yup)
-
-  link_df <- motif_data %>% left_join(plant_positions, by = "plant") %>% 
-    left_join(pollinator_positions, by = "pollinator")
-
-  # Before plotting the motif, we remove letters from the node position id
-
-  d_nodes$label <- gsub("[^0-9.-]", "", d_nodes$label)
-  plant_pies_aux <- plant_pies %>% select(-x,-y) %>% mutate(position = as.character(position))
-
-  d_nodes_plant <- d_nodes %>% rename(position = label) %>% 
-    left_join(plant_pies_aux, by = "position") %>% as_tibble() %>%
-    filter(!is.na(`1`))
-
-  pollinator_pies_aux <- pollinator_pies %>% select(-x,-y) %>% mutate(position = as.character(position))
-
-  d_nodes_pollinator <- d_nodes %>% rename(position = label) %>% 
-    left_join(pollinator_pies_aux, by = "position") %>% as_tibble() %>%
-    filter(!is.na(Bee))
-
-  # Define the number of colors you want
- mycolors <- c("#A6CEE3", "chocolate2",  "gold2", "#1F78B4","#B2DF8A",
-                     "gray58", "lightgoldenrod2","thistle2", "burlywood","lightcoral", "olivedrab3")
-
-  ggplot() +
-    scale_shape_identity() +
-    geom_segment(data = link_df, aes(x=xdown, y=ydown, xend = xup, yend = yup), 
-                 size = 1, color = "grey20")+  geom_scatterpie(aes(x=x, y=y, group=position,r=.45), 
-    data = d_nodes_pollinator, cols=as.character(c("Bee","Coleoptera","Lepidoptera","Non-bee-Hymenoptera", "Non-syrphids-diptera","Syrphids"))) +
-    geom_scatterpie(aes(x=x, y=y, group=position,r=0.45), 
-                    data = d_nodes_plant,
-                    cols=as.character(c("1","2","3","4","5")))+
-    coord_fixed()+
-    scale_fill_manual(values = mycolors,"test",
-      breaks=c("Bee","Coleoptera","Lepidoptera",
-               "Non-bee-Hymenoptera", "Non-syrphids-diptera",
-               "Syrphids","1","2","3","4","5"), labels=c("Bees","Coleoptera","Lepidoptera",
-"Non-bee-Hymenoptera", "Non-syrphids-Diptera","Syrphids", 
-          "Selfing herbs","Small outcrossing perennials","Self-incomp. perennials\nwith large flowers",
-          "Tall plants with small\nunisexual flowers","Short-lived outcrossers with\nlong zygomorphic flowers"))+
-    xlim(-1.5,4)+ ylim(-0.5,2.5)+
-    theme(panel.background = element_blank(),
-          axis.text.x=element_blank(),
-          axis.ticks.x=element_blank(),
-          axis.text.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          legend.title = element_text(size=12, face="bold"),legend.background = element_rect(size=0.5, linetype="solid",colour ="black"))+
-    labs(x=NULL,y=NULL)+
-    guides(color = FALSE,fill=guide_legend(title="Functional groups"))+
-    ggtitle(paste0("Motif ",motif_number))+
-    theme(plot.title = element_text(hjust = 0.5),legend.key.size = unit(0.5, 'cm'))+
-    theme(plot.margin=unit(c(0,0,0,0),"cm"))
-}
-
-motif_number <- 1
-p1 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 2
-p2 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 3
-p3 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 4
-p4 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 5
-p5 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 6
-p6 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 7
-p7 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 8   
-p8 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 9
-p9 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 10
-p10 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 11
-p11 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 12
-p12 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 13
-p13 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 14
-p14 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 15
-p15 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 16
-p16 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 17
-p17 <- plot_pie_motif_positions(motif_number)
-
-library(patchwork)
-
-(p1 & ylab("2 species")| p2 & ylab("3 species") | p3  |plot_spacer()|plot_spacer())/ 
-  (p4 & ylab("4 species")| p5 | p6 | p7|plot_spacer())/ 
-  (p8  & ylab("5 species")| p9 | p10 | p11 | p12) / 
-  (p13 & ylab("5 species")| p14 | p15 | p16 | p17) + plot_layout(guides = 'collect') &
-  theme(axis.title.y = element_text(color="black", size=14, face="bold"),legend.position = "bottom")
-
-```
-
-The statistical comparison with z-scores between the observed and expected plant and floral visitor functional group combinations showed that we can not recover the observed combinations from its probability of occurrence.
-In fact, most combinations are under- or over- represented and follow a modified Gaussian distribution (Johnson's $S_U$) with 65$\%$ of under-represented group combinations, 20$\%$ of no statistical difference and 15$\%$ of under-represented ones (Fig.
-5).
-In addition, subgraphs with small node combinations (i.e., 2 and 3 nodes) only appeared as under-represented.
-Network subgraphs with 4 and 5 node combinations appeared in the three statistical categories, but 4 node subgraphs had a higher proportion in the under-represented category (10% in comparison with the 1$\%$ and the 3$\%$ of the no statistical difference and over-represented categories, respectively).
-Finally, 5 node subgraphs were in similar proportions in the no statistical difference and over-represented categories (99$\%$ and 97$\%$, respectively), but they appeared in lower proportion in the under-represented category (89$\%$).
-When we explored the identity on the different positions of the most probable subgraph combinations, we found that the most common plant and floral visitor functional groups were also the most probable on these plant and floral visitor combinations within the different subgraphs (lower panel Fig.
-5).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 5.** Distribution of z-scores values after the statistical comparison of the observed probabilities of finding a subgraph combination in real networks and the expected probabilities (obtained by computer simulations).
-The resulting z-scores frequencies of this statiscal comparison are coloured based on a 95% confidence level: under-represented ($z_i^O < -1.96$, red), no statistical difference ($-1.96 \\geq z_i^O \\leq  1.96$, green) and over-represented ($z_i^O > 1.96$, blue).
-For instance, for a z-score value of 0 there were approximately 800 subgraph combinations that showed no statistical difference in the comparison between real and simulated networks.
-In addition, four specific graphical examples of the most probable subgraphs being observed on each category are also provided and the different plant and floral visitor functional groups are represented with distinct colour codes as indicated in the legend."}
-
-library(tidyverse)
-library(RColorBrewer)
-
-equidistribution <- function(number_nodes){
-
-  x_width <- 5.5/(number_nodes+1)
-
-  x_result <- rep(-1.5,number_nodes)
-
-  for(i in 1:number_nodes){
-
-    x_result[i] <- x_result[i] + i*x_width
-
-  }
-
-  return(x_result)
-
-}
-
-plot_motif_label <- function(label){
-
-  label_split <- str_split(label,"_")[[1]]
-  motif_number <- as.numeric(label_split[1])
-  nodes <- label_split[2:length(label_split)]
-  plant_nodes <- nodes[nodes %in% plant_means_reordered$Node_FG]
-  pollinator_nodes <- nodes[nodes %in% pollinator_means_reordered$Node_FG]
-
-  motifs_raw_data <-read_csv("../../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-  motif_data <- motifs_raw_data %>% filter(motif_id == motif_number)
-
-  # Create dataframe with node positions
-
-  labdown = motif_data$plant %>% unique()
-
-  xdown = equidistribution(length(labdown))
-
-  ydown = rep(0,length(labdown))
-
-  labup = motif_data$pollinator %>% unique()
-
-  xup = equidistribution(length(labup))
-
-  yup = rep(1,length(labup))
-
-  d_nodes=data.frame(x=c(xdown,xup),
-                     y=c(ydown,yup),
-                     label = c(labdown,labup))
-
-  # Create a dataframe with links
-
-  plant_positions <- data.frame(plant = labdown,
-                                xdown = xdown,
-                                ydown = ydown)
-
-  pollinator_positions <- data.frame(pollinator = labup,
-                                     xup = xup,
-                                     yup = yup)
-
-  link_df <- motif_data %>% left_join(plant_positions, by = "plant") %>% 
-    left_join(pollinator_positions, by = "pollinator")
-
-  # Add FG IDs to nodes
-  FG_IDs <- tibble(label = c(sort(labdown),sort(labup)),
-                   FG = c(plant_nodes,pollinator_nodes))
-
-  d_nodes_FG <- d_nodes %>% left_join(FG_IDs, by = "label")
-  levels_FG <- c("Bee","Coleoptera","Lepidoptera",
-                 "Non-bee-Hymenoptera", "Non-syrphids-diptera",
-                 "Syrphids","1","2","3","4","5")
-
-  d_nodes_FG$FG <- factor(d_nodes_FG$FG, levels = levels_FG)
-
-  levels(d_nodes_FG$FG) <- c("Bee","Coleoptera","Lepidoptera",
-                             "Non-bee-Hymenoptera", "Non-syrphids-diptera",
-                             "Syrphids","1","2","3","4","5")
-
-  # Before plotting the motif, we remove letters from the node position id
-
-  d_nodes_FG$label <- gsub("[^0-9.-]", "", d_nodes_FG$label)
-
-  # Define the number of colors you want
- mycolors <- c("#A6CEE3", "chocolate2",  "gold2", "#1F78B4","#B2DF8A",
-                     "gray58", "lightgoldenrod2","thistle2", "burlywood","lightcoral", "olivedrab3")
-
-  ggplot(data=d_nodes_FG, aes(x, y)) +
-    scale_shape_identity() +
-    geom_segment(data = link_df, aes(x=xdown, y=ydown, xend = xup, yend = yup), size = 1, color = "grey20")+
-    geom_point(aes(color = FG), size=7.5)+
-    geom_text(aes(x, y , label = label), size=3)+
-    scale_color_manual(drop = FALSE, values = mycolors,
-                       breaks=c("Bee","Coleoptera","Lepidoptera",
-                                "Non-bee-Hymenoptera", "Non-syrphids-diptera",
-                                "Syrphids","1","2","3","4","5"), 
-                       labels=c("Bees","Coleoptera","Lepidoptera",
-                                "Non-bee-Hymenoptera", "Non-syrphids-Diptera",
-                                "Syrphids", 
-                                "Selfing herbs","Small outcrossing perennials",
-                                "Self-incomp. perennials\nwith large flowers",
-                                "Tall plants with small\nunisexual flowers",
-                                "Short-lived outcrossers with\nlong zygomorphic flowers"))+
-    xlim(-1.5,4)+ ylim(-0.5,1.5)+
-    theme(panel.background = element_blank(),
-          axis.text.x=element_blank(),
-          axis.ticks.x=element_blank(),
-          axis.text.y=element_blank(),
-          axis.ticks.y=element_blank())+
-    labs(x=NULL,y=NULL)+
-    ggtitle(paste0("Motif ",motif_number))+
-    theme(plot.title = element_text(hjust = 0.5,size=10))+
-    guides(color=guide_legend(title="Functional groups"))
-
-}
-
-# Data with pollinator/plant labels
-
-plant_means_reordered <- read_csv("../../Data/Csv/plant_abs_freq_means.csv")
-pollinator_means_reordered <- read_csv("../../Data/Csv/pollinator_abs_freq_means.csv")
-#Filter out in order to have just 6 FG'S
-pollinator_means_reordered <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds", "Lizards", "Other_insects"))
-
-####################################################################################################
-#Read data to check top 5 motif of each category of observed propabilities
-
-#Under, No signi, Over-rep
-####################################################################################################
-# Check top Z-scores of each group (Under, No diff, Over)
-
-#Read data
-data <- read.csv("../../Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
-
-#Find critical value of Z-score
-p <- 0.05 #cutoff probability 95% confidence
-critical_value <- qnorm(p/2) #double tail probability divide by 2
-
-data_1 <- data %>%
-  mutate(infra_over_represented = case_when(
-    z_score < -abs(critical_value) ~ "infra",
-    between(z_score, -abs(critical_value), abs(critical_value)) ~ "no_diff",
-    z_score > abs(critical_value) ~ "over"
-  ))
-
-#data_2 <- filter(data_1, abs(z_score)<2000) 
-#str(data_2)
-
-#Select under-represented by the ones with highest porbability of being observed (top10)
-under_data <- filter(data_1, infra_over_represented=="infra")
-
-under_top_5 <- filter(under_data, row_number(desc(abs(motif_observed_probability)))<= 5) %>%
-  select(motif_functional_ID,motif_observed_probability,counts_observed,z_score)
-
-#Select no statistical difference by the ones with highest porbability of being observed (top5)
-no_diff_data <- filter(data_1, infra_over_represented=="no_diff")
-
-no_diff_top_5 <- filter(no_diff_data, row_number(desc(abs(motif_observed_probability)))<= 5) %>%
-  select(motif_functional_ID,motif_observed_probability,counts_observed,z_score)
-
-#Select over-represenetd by the ones with highest porbability of being observed (top5)
-over_data <- filter(data_1, infra_over_represented=="over")
-
-over_top_5 <- filter(over_data, row_number(desc(abs(motif_observed_probability)))<= 5) %>%
-  select(motif_functional_ID,motif_observed_probability,counts_observed,z_score)
-####################################################################################################
-#Now plot it 
-####################################################################################################
-
-library(patchwork)
-
-#Prepare list of 5 plots for each group
-#Under
-labels_under <- under_top_5$motif_functional_ID
-p_under <- list()
-
-for (i in 1:5){
-
-  p_under[[i]] <- plot_motif_label(labels_under[[i]])
-}
-
-#No signficance
-labels_nodiff <- no_diff_top_5$motif_functional_ID
-p_nodiff <- list()
-
-for (i in 1:5){
-
-  p_nodiff[[i]] <- plot_motif_label(labels_nodiff[[i]])
-}
-
-#Over
-labels_over <- over_top_5$motif_functional_ID
-p_over <- list()
-
-for (i in 1:5){
-
-  p_over[[i]] <- plot_motif_label(labels_over[[i]])
-}
-
-#Run Script with histogram plot
-source("../../Scripts/Z-score_percentile_histogram_plot.R")
-
-hist <- ggplot(data_2 %>% filter(round_motif_observed_probability>0), aes(x=z_score, color=infra_over_represented, fill=infra_over_represented)) + 
-  geom_histogram(bins = 93, alpha = 0.5, position = "identity",lwd = 0.25)+
-  geom_vline(xintercept = -abs(critical_value))+
-  geom_vline(xintercept = abs(critical_value))+
-  xlim(-60,60) + ylab("Frequency")+  theme_bw() +
-  scale_fill_manual(name="Motif frequencies" ,values=c("coral2", "palegreen3", "cyan3"), labels=c("Under-represented",
-                                                                                                  "No statistical difference", "Over-represented")) +
-  scale_color_manual(name="Motif frequencies" ,values=c("coral2", "palegreen3", "cyan3"), labels=c("Under-represented",
-                                                                                                   "No statistical difference", "Over-represented")) + xlab("Z-score")
-
-t_col <- function(color, percent = 50, name = NULL) {
-  #      color = color name
-  #    percent = % transparency
-  #       name = an optional name for the color
-
-  ## Get RGB values for named color
-  rgb.val <- col2rgb(color)
-
-  ## Make new color using input color as base and alpha set by transparency
-  t.col <- rgb(rgb.val[1], rgb.val[2], rgb.val[3],
-               max = 255,
-               alpha = (100 - percent) * 255 / 100,
-               names = name)
-
-  ## Save the color
-  invisible(t.col)
-}
-## END
-
-#Prepare panel of plots
-hist / ((p_under[[1]]/p_under[[2]]/p_under[[3]]/p_under[[4]] & theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_rect(fill=t_col("coral2")))) | 
-          (p_nodiff[[1]]/p_nodiff[[2]]/p_nodiff[[3]]/p_nodiff[[4]]& theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_rect(fill=t_col("palegreen3")))) |
-          (p_over[[1]]/p_over[[2]]/p_over[[3]]/p_over[[4]] & theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_rect(fill=t_col("cyan3"))))) + plot_layout(guides = 'collect')
-
-```
-
-# Discussion
-
-Understanding the global patterns of network structure is key to unravel the processes that govern community dynamics [@bascompte2007; @bastolla2009; @guimaraes2020].
-However, common analytical approaches at the node or at the global network level are unable to capture the full complexity of ecological systems [@simmons2019; @bergamo2021].
-Because network subgraphs can capture both direct and indirect interactions, by analysing their over- and under-representation we were able to explore in great detail the structure of interactions between animal pollinators and the plants they visit.
-We have explored for the first time the overall structure and presence of network motifs in real plant-pollinator networks and shown that, according to our first hypothesis, the different subgraphs up to five nodes are consistently over- or under-represented in comparison with simulated networks.
-In addition, we show that for plant-pollinator networks there is a general tendency for over-representation of network subgraphs that are more densely connected (i.e., complete, fan and asymmetric complete).
-Indeed, the work of @simmons2020 has shown with the help of simulated plant-pollinator networks that the main different processes that shape plant-pollinator communities (i.e., neutral effects, trait matching and phenology) generate different patterns of direct and indirect interactions, and that specifically, a higher proportion of these more densely connected subgraphs is associated with neutral effects.
-Therefore, as indicated for other network properties like nestedness at the macro-scale level [@krishna2008; @suweis2013], or interaction probability at the species level [@bartomeus2016], our findings align with our second hypothesis and indicate that neutral effects may be also the main driver governing this intermediate level of complexity on plant-pollinator networks.
-
-Overall, generalist network motifs for floral visitors were consistently over-represented (e.g., complete subgraphs; Fig.
-2).
-For instance, when we compare network subgraphs with equal structure for both trophic levels, we found that floral visitors had always over-representation in the positions that implied the highest number of direct links (e.g., positions 16 and 46 from network subgraphs 7 and 17, respectively).
-Despite this being in good agreement with the current view of the generalist nature of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of generalist network motifs was driven by the functional group of bees while the rest of the functional groups tended to be under-represented (Fig.
-S6 A).
-In contrast, non-bee groups were over-represented in subgraph positions associated with specialised roles.
-This large effect of bees on the overall patterns is no surprise, as bees were the group with the largest number of interaction records in the whole set of networks as also shown for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017].
-Just syrphids had a relatively similar number of interactions in comparison with bees (1,768 and 2,256 interactions, respectively) and similar species richness (343 and 321 species, respectively).
-However, both functional groups were associated with contrasting ecological roles likely indicating that both number of interactions and richness are not driving the observed interaction patterns for the different functional groups.
-Interestingly, bees also were the group with lower number of indirect interactions, while the rest of floral visitor groups showed a clearly higher number of indirect interactions, indicating that these non-bee floral visitor groups may experience higher competitive interactions for floral resources [@thomson2020].
-Despite plant functional groups showed little differences between them on their subgraph frequencies, all groups showed a tendency to be over-represented on subgraph positions that were associated with higher levels of specialisation.
-This tendency towards specialist roles may be the result of co-evolutionary processes (e.g., trait-matching) between plants and pollinators to optimise pollen transfer [@moreira2019].
-Remarkably, only tall plants with small unisexual flowers showed higher frequencies on subgraphs that were associated with low number of indirect interactions with likely direct implications on pollen transfer for this group that needs to guarantee cross-pollination.
-
-The probabilities of appearance of each functional group on the different subgraph positions were insufficient to predict most of the observed network position combinations (Fig.
-5).
-This implies that not just the representation of network subgraphs types but also the identity of the elements of their structure is non-random.
-Notably, we found that just 30$\%$ of the possible 53,250 subgraph combinations are realised.
-Thus, similarly to the presence of forbidden links at the network level [@olesen2011; @jordano2016], we also found the existence of forbidden subgraph positions and those represented almost two thirds of the total possible subgraph combinations.
-This concurs well with the general idea that plant-pollinator networks have a high proportion of non-realized direct interactions [@jordano2003; @bascompte2013], and, as a result, also a high proportion of non-realized combinations of indirect interactions.
-Some of these non-observed direct interactions are probably due to under-sampling [@dorado2011; @jordano2016].
-However, a large fraction of the possible interactions do not take place because of different constraints such as species co-occurrence, trait matching processes and phenological uncoupling [@olesen2011; @bartomeus2016; @jordano2016].
-Despite the advances in the understanding of the ecological processes that influence species pairwise interactions [@bartomeus2016; @peralta2020], we still know little about how these processes determine competitive and facilitative interactions in mutualistic networks.
-Thus, as suggested by @simmons2020, exploring the proportion of these realised network subgraphs that are competitive or facilitative is a necessary next step to improve our understanding of the architecture of biodiversity [@bascompte2007].
-
-Despite the obvious usefulness of functional groups in summarising species ecological roles (e.g., similar reproductive biology for plants and behaviour for pollinators), delimiting species into functional groups is often not trivial.
-For instance, taxonomic diversity and trait availability limit our ability to properly represent the wide range of reproductive strategies [@dellinger2020] and different clustering analysis can lead to distinct outcomes (e.g., k-means and hierarchical clustering).
-We divided floral visitors on the taxonomic rank level because it adequately represented pollinator ecological roles without the tremendous effort of compiling trait data for over 1,000 species of floral visitors.
-Indeed, further groupings with traits could help reveal greater relevance of trait-matching processes on indirect interactions.
-Moreover, we analysed network subgraphs focusing exclusively on presence or absence of interactions, assuming that all interactions are equally important.
-However, further work should investigate how to account for quantitative measurements of plant-pollinator interactions.
-Consistent with previous work [@simmons2019; @simmons2020], we characterised network motifs by using null models only constrained for network connectance.
-Although more complex null models are difficult to interpret [@Ulrich2013], they can potentially allow us to separate the mechanisms by which motifs emerge.
-However, we found that null models with more constraints generated binary structures that were mostly identical to the original ones.
-In addition, we observed that connectance, nestedness and degree distribution were significantly correlated (data not shown).
-All that highlights the difficulties to disentangle the potential sources that generate over-representation of network subgraphs and the need to investigate them.
-At the same time, although network subgraphs can capture both direct and indirect interactions, the reduction of network complexity into these different building blocks inevitably convey the loss of information [@simmons2019], for example indirect interactions from large cascading effects.
-Finally, despite the wide geographical coverage of our plant-pollinator dataset, there are major gaps for some regions of the world with a clear bias towards Europe, America and islands which have long interested ecologists [@macarthur1963; @warren2015].
-These biases are also found in global datasets of networks, where the data is highly fragmented across space [@poisot2021] and more efforts are needed to capture global patterns of plant-pollinator interactions.
-
-In conclusion, by following the framework of @simmons2020 we have been able to explore competitive and facilitative interactions in plant-pollinator networks worldwide and found the presence of worldwide motifs that highlight the non-random structure of indirect interactions.
-This non-random structure might emerge due to neutral effects according to previous modelling work [@simmons2020].
-Further, we found that plant and floral visitor functional groups are associated with different subgraph positions that involve distinct ecological roles (e.g., generalisation versus specialisation) and that the different subgraph combinations are strongly constrained.
-Although we are still far from predicting how species interact, our work is a first step to elucidate beyond pairwise interactions.
-
-# Acknowledgements
-
-This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2).
-JBL also thanks the University of New England for the funding provided to carry out this work.
-Finally, we would like to thank David García-Callejas for his useful comments on the manuscript before submission.
-
-# Author contributions
-
-IB, AA-P and JBL designed the idea. JBL collected the data. AA-P led the analysis with contributions of JBL and guidance of IB. JBL wrote the manuscript with contributions of IB and AA-P.
-
-# Data Availability Statement
-
-All data and code are publicly available at Github (<https://github.com/JoseBSL/FunctionalMotifs>) and Zenodo (<https://doi.org/10.5281/zenodo.6489213>).
-
-\newpage
-
-# References
-
-::: {#refs}
-:::

### 2023-01-25 Manuscript/Figures/Figure3.Rmd
Word file and independent figures for typesetting

--- 2022-10-08 Manuscript/Main_text/Main_text_Journal_of_Animal_Ecol.Rmd
@@
   word_document: default
-always_allow_html: true
-bibliography: bibliography.bib
-biblio-style: apalike
-csl: JournalOfAnimalEcology.csl #converted from funct ecol style from zotero styles
 ---
-
-**Jose B. Lanuza^1,2^** \| **Alfonso Allen-Perkins^2,3^** \| **Ignasi Bartomeus^2^**
-
-1 School of Environmental and Rural Science, University of New England, Armidale, New South Wales 2350, Australia.
-
-2 Estación Biológica de Doñana (EBD-CSIC), E-41092 Seville, Spain.
-
-3 Departamento de Ingeniería Eléctrica, Electrónica, Automática y Física Aplicada, ETSIDI, Universidad Politécnica de Madrid, 28040 Madrid, Spain.
-
-\captionsetup[table]{labelformat=empty}
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
-
-# Abstract
-
-\singlespacing
-
-Ecological processes leave distinct structural imprints on the species interactions that shape the topology of animal-plant mutualistic networks.
-Detecting how direct and indirect interactions between animals and plants are organised is not trivial since they go beyond pairwise interactions, but may get blurred when considering global network descriptors.
-Recent work has shown that the meso-scale, the intermediate level of network complexity between the species and the global network, can capture this important information.
-The meso-scale describes network subgraphs representing patterns of direct and indirect interactions between a small number of species, and when these network subgraphs differ statistically from a benchmark, they are often referred to as "network motifs".
-Although motifs can capture relevant ecological information of species interactions, they remain overlooked in natural plant-pollinator networks.
-By exploring 60 empirical plant-pollinator networks from 18 different studies with wide geographical coverage, we show that some network subgraphs are consistently under- or over-represented, suggesting the presence of worldwide network motifs in plant-pollinator networks.
-In addition, we found a higher proportion of densely connected network subgraphs that, based on previous findings, could reflect that species relative abundances are the main driver shaping the structure of the meso-scale on plant-pollinator communities.
-Moreover, we found that distinct subgraph positions describing species ecological roles (e.g., generalisation and number of indirect interactions) are occupied by different groups of animal and plant species representing their main life-history strategies (i.e., functional groups).
-For instance, we found that the functional group of 'bees' was over-represented in subgraph positions with a lower number of indirect interactions in contrast to the rest of floral visitors groups.
-Finally, we show that the observed functional group combinations within a subgraph can not be retrieved from their expected probabilities (i.e., joint probability distributions), indicating that plant and floral visitor associations within subgraphs are not random either.
-Therefore, our results highlight the presence of common network motifs in plant-pollinator communities that are formed by a non-random association of plants and floral visitors functional groups.
-
-Keywords: pollinators, plant-pollinator networks, plant-pollinator interactions, network motifs, indirect interactions, floral visitors
-
-\doublespacing
-
-\newpage
-
-# Introduction
-
-Ecological communities are formed by a plethora of interacting species that form networks of interactions.
-Because of the tremendous complexity of these ecological networks, species interactions are generally condensed in metrics that summarise this information [@guimaraes2020].
-Plant-pollinator interactions are no exception, and they are often studied with indices that aggregate the information at the network (macro-scale) and species level (micro-scale).
-For example, plant-pollinator network level approaches have identified common invariant structural properties across mutualistic networks, including a degree distribution that decays as a truncated power law [@jordano1987], nestedness [@bascompte2003], or modularity [@olesen2007].
-In addition, the local species position within the network can define its degree of selectiveness [@bluthgen2006] or its role in connecting the rest of the community [@olesen2007].
-Despite the unquestionable progress with the use of these metrics at both network and species level, condensing complex information into a single metric implies the loss of relevant ecological information that obscures the understanding of species interactions [@cirtwill2018; @simmons2019].
-
-Indirect interactions, the mediated effect between two species by a third species, are ubiquitous in natural systems [@strauss1991; @holt1994; @wootton1994] and play a key role in shaping community dynamics [@werner2003; @walsh2013].
-Some of the most studied indirect interactions are the ones caused by trophic cascades with consumer-resource interactions [@abrams1996; @schmitz2001].
-In fact, previous studies focus on antagonistic interactions and mutualistic interactions are often overlooked [@knight2005].
-On the contrary, plant-pollinator research has traditionally investigated direct interactions but neglected indirect effects such as competitive or facilitative processes between plants for pollinators [@moeller2004; @sargent2008; @carvalheiro2014].
-Conventional analytical tools in bipartite networks often discard relevant information about indirect interactions by condensing the information into single indices either at species or network level [@cirtwill2018; @simmons2019].
-However, as previously explored with three species modules in unipartite food webs [@allesina2008; @stouffer2010], the emergent framework of bipartite subgraphs has proven to be a powerful analytical tool to better understand plant-pollinator community dynamics by capturing both direct and indirect effects [@simmons2019].
-These network subgraphs that constitute the meso-scale are often referred to as the building blocks of the network and when their numbers occur at higher frequencies than in randomised networks, those are generally defined as 'network motifs' [@milo2002].
-Indeed, the analysis of motifs in simulated plant-pollinator networks has revealed that the different drivers that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect effects [@simmons2020].
-However, the global patterns of indirect interactions in real plant-pollinator networks and their ecological consequences remain unexplored (e.g., over- and under- represented network subgraphs).
-
-By linking the structural properties of the meso-scale with the species' ecology we can advance in our understanding on the determinants of species interactions.
-For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species' functional role [@stouffer2012; @baker2015; @cirtwill2018b].
-Yet, our understanding of the ecological implications of network motifs in real plant-pollinator networks remains in its infancy.
-Moreover, it is unclear how the species ecology and life-history traits determine its functional role within the network of interactions [@coux2016].
-For example, large pollinators can forage larger distances [@greenleaf2007], deposit greater pollen quantities [@foldesi2021] and handle complex zygomorphic flowers in comparison with small pollinators that are restricted to lower floral complexity [@gong2009].
-Despite these obvious differences in pollinator behaviour, how contrasting species' ecology translates into different network motifs is still poorly known.
-Similarly, recent empirical findings indicate that the meso-scale is the best descriptor of plant reproductive success [@allen2021], but little is known about how plants' reproductive strategies shape their position within the network of interactions.
-Although some studies have evaluated plant reproductive strategies in plant-pollinator networks [@tur2013; @lazaro2020], this is an often overlooked aspect in a community context [@devaux2014] and rarely incorporated into plant-pollinator network studies.
-Hence, exploring how the main plant and floral visitor life-history strategies integrate with the emergent framework of network motifs could help to progress knowledge on the ecological processes that shape plant-pollinator interactions.
-
-Here we evaluate the interaction patterns of the meso-scale and its ecological implications in plant-pollinator networks with the help of 60 empirical networks from 18 different studies distributed across 14 different countries.
-For this, plants and pollinators were divided into functional groups that summarise their main life-history strategies and the different networks were split into all their subgraph elements up to five nodes.
-First, based on previous knowledge showing the non random assembly of macro-scale mutualistic networks [@bascompte2003] and food webs [@dunne2002], we test the hypothesis that the building blocks that constitute the meso-scale in plant-pollinator networks have a non-random structure of interactions with over- and under-represented subgraphs (i.e., motifs) that represent contrasting ecological roles.
-Second, because species relative abundances (i.e., neutral effects) are one of the main drivers of network macro-struture [@krishna2008; @suweis2013; @bartomeus2016], we hypothesise that neutral effects may also govern the interaction patterns of the meso-scale in plant-pollinator networks.
-Finally, we explore if plants and pollinators functional groups are associated with subgraph positions that imply distinct ecological roles and if there are over- and under-represented functional group combinations within the different network subgraphs.
-
-# Methods
-
-**Overview**
-
-To investigate the structure of the meso-scale in plant-pollinator networks, we gathered published plant-pollinator networks with worldwide distribution.
-Then, we classified the different plant and floral visitor species from these networks into functional groups that summarise their main life-history strategies.
-We calculated the normalised subgraph frequencies and investigated if these frequencies are similar or not to the ones expected by chance with the help of null models.
-Then, for each group of plants and floral visitors we investigated the ecological implications of their overall representation on the different subgraph positions, by comparing, on the one hand, the observed (normalised) frequencies of each group in the different subgraph positions with the frequencies of their simulated counterparts, and, on the other hand, the differences among groups per subgraph position in terms of their number of indirect interactions and specialisation.
-Finally, to understand if the different functional group combinations within a subgraph are structured, we compare if the observed functional group combinations from empirical networks can be retrieved from the joint probability distribution of the expected frequencies of the different plant and floral visitor groups within network subgraphs.
-
-**Plant-pollinator studies**
-
-We have compiled 60 plant-pollinator networks from 18 different studies (Table S1).
-All studies sampled plant-pollinator interactions in natural systems in a single flowering season and were selected based on wide geographical coverage (Fig.
-S1) and presence of interaction frequency as a measure of interaction strength.
-In total, there were 503 plant species, 1,111 floral visitors species and 6,248 pairwise interactions registered.
-For ease of data manipulation, plant and floral visitor species names were standardised with the help of the R package *taxize* version *0.9.99* [@chamberlain2020].
-
-**Plant and floral visitor functional groups**
-
-First, plant species were grouped through hierarchical clustering into the optimal number of functional groups that summarises the main plant reproductive strategies.
-For this, we used the plant trait dataset compiled in @lanuza2021 that consisted also of plant species that belonged to the same plant-pollinator networks plus some additional meta-networks not considered here.
-This dataset comprised a total of 1,506 plant species including the 503 species considered in this study (Table S2).
-Because most of these plant species are likely to benefit from animal pollination, we used reproductive traits relevant to understand the different plant reproductive strategies and their interactions with pollinators.
-After excluding traits with a high percentage of missing values (over 30$\%$), we ended up with 8 floral, 3 reproductive biology and 3 plant morphology traits (see Table S3 for a list of all traits).
-Floral traits included those associated with the size, form and number of floral organs (e.g., style length or ovule number).
-Reproductive biology traits described the reproductive system of the plant (e.g., mating and compatibility systems) and plant morphology traits were associated with the size and form of the plant (i.e., plant height, lifespan and life form).
-After an extensive search for each plant species on several different resources (e.g., plant databases, online floras, books, journals and images), over 80% of the cells of the whole dataset were filled.
-Thus, to avoid the loss of species with trait missing values, missing trait data was imputed as detailed in @lanuza2021.
-
-We opted to calculate the plant functional groups within a larger set of species because of the higher accuracy when delimiting functional groups with that many variables and species [@dolnicar2014].
-To feed the clustering analysis, we calculated the distance between the different qualitative and scaled quantitative variables with Gower distance [@gower1971].
-For this, we used the function *gowdis* with method *ward.D2* from the *FD* package version *1.0-12* [@laliberte2014].
-Finally, we conducted hierarchical clustering with the function *hclust* from the *R* stats package version *4.0.5* and calculated the optimal number of clusters with the function *kgs* from the *maptree* package version *1.4-7* [@white2009].
-
-Second, floral visitors were aggregated into taxonomic groups (hereafter referred to as functional groups) based on taxonomic rank as done similarly in other plant-pollinator studies [@fenster2004; @ollerton2009].
-We opted to divide floral visitors on the taxonomic rank level and not with functional traits because the main orders of floral visitors differed in form and behaviour and had lower superior taxonomic complexity (i.e., floral visitors had 6 orders versus plants that had 38).
-Thus, this allowed us to group floral visitors into functional groups that represented approximately the main life-history strategies of the possible pollinators: (i) bees (Hymenoptera-Anthophila), (ii) non-bee Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Syrphidae-Diptera), (iv) non-syrphids-Diptera, (v) Lepidoptera and (vi) Coleoptera.
-However, a minor set of species belonged to other functional groups that were considered in analyses but not discussed further because of their low representation in the full set of networks (3.55$\%$ of the total interactions recorded).
-These taxonomic groups were 'lizards', 'birds' and 'other insects'.
-This last functional group was formed by a mix of uncommon insect taxa on the full set of networks.
-
-**Overall network subgraphs patterns**
-
-Following previous work [@simmons2019; @simmons2020], we broke down the plant-pollinator networks into their constituent network subgraphs that can capture both direct and indirect interactions.
-Prior to analyses, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.
-This approach was preferred since quantitative subgraph analyses have been developed just recently and more work is needed to fully understand and interpret the information that they can convey [@simmons2020].
-All analyses were run considering singletons (species with only one interaction detected) but we conducted a second exploration without singletons (64.98$\%$ of interactions) to evaluate the effect of rare species on the observed patterns.
-Results without singletons are qualitatively consistent and are not further discussed in the main text (Figs S2 and S3).
-
-We calculated the frequency of all subgraphs up to five nodes (17 different subgraphs in total; see Fig.
-1) for each empirical network, by using the *bmotif* package version *2.0.2* [@bmotifsimmons2019].
-We focused exclusively on subgraphs up to five nodes in our analyses for computational reasons and for the ease of visualization and interpretation of a reduced set of less complex network structures.
-Throughout the entire manuscript, floral visitors occupy the top nodes of the different network subgraphs and plants the bottom ones.
-To control for variation in network size, subgraph frequencies were normalised as a proportion of the total number of subgraphs within each subgraph class (i.e., 2-species, 3-species, 4-species and 5-species network subgraphs).
-In addition, we excluded 2-species (or 2-nodes) subgraphs from our analyses because its normalised frequencies would always equal one.
-Note that the aim is not comparing different networks, which may differ in sampling effort, but correctly describing the structure of each individual network.
-Like @simmons2020, we classified the different subgraphs by their average path length (mean number of links between all pairs of nodes) into four different groups: (i) complete or strong ($\overline{x} = 1.38$), (ii) fan or medium-strong ($\overline{x} = 1.48$), (iii) assymmetric complete or medium-weak ($\overline{x} = 1.60$) and (iv) core-peripheral or weak ($\overline{x} = 1.85$), where $\overline{x}$ represents the mean of the average path length across subgraphs within the same group.
-In general terms, plant and floral visitor groups on more densely connected network subgraphs (e.g., complete or fan) will experience lower number of indirect interactions in contrast to groups on less densely connected structures (e.g., medium-weak or weak).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, fig.pos="t", warning=FALSE,out.width="75%",fig.align="center", fig.cap="\\textbf{Figure 1.} Adapted figure of Simmons et al., (2019).
-All possible network subgraphs from two to five species in bipartite networks grouped by the different subgraph classes (2-species, 3-species, 4-species and 5-species).
-There are a total of 17 possible subgraphs with 46 different positions denoted within each node.
-The different subgraphs are aggregated by the broad indirect interaction structures they represent on four different groups (strong, medium-strong, medium-weak and weak).
-For each group, we show in the legend the mean value of the average path length of all subgraphs within it.
-The different path length groups range from densely connected network structures (strong subgraphs where all possible interactions are realised and the mean path length is minimum) to weakly connected ones (weak subgraphs where the mean path length is maximum).", fig.width=10,fig.height=8}
-library(tidyverse)
-library(RColorBrewer)
-source("../../Scripts/Scripts_Alfonso/plot_motif_positionsV2.R")
-
-motif_number <- 1
-p1 <- plot_motif_positions(motif_number) +
-geom_point(aes(color = as.factor(label)),size=10,color = "grey90")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 2
-p2 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 3
-p3 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 4
-p4 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 5
-p5 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "lightcoral")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 6
-p6 <- plot_motif_positions(motif_number) +
-geom_point(aes(color = as.factor(label)),size=10,color = "goldenrod2")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 7
-p7 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 8   
-p8 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 9
-p9 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "lightcoral")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 10
-p10 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "lightcoral")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 11
-p11 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "skyblue")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 12
-p12 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "goldenrod2")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 13
-p13 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "lightcoral")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 14
-p14 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "lightcoral")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 15
-p15 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "skyblue")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 16
-p16 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "goldenrod2")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 17
-p17 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
-geom_text(aes(x, y , label = label),size=3)
-
-library(patchwork)
-
-p <- (p1 & ylab("2 species")| p2 & ylab("3 species") | p3 ) /
-(p4 & ylab("4 species")| p5 | p6 | p7) / 
-(p8  & ylab("5 species")| p9 | p10 | p11 | p12) /
-(p13 & ylab("5 species")| p14 | p15 | p16 | p17) &
-theme(axis.title.y = element_text(color="black", size=14, face="bold"))
-
-#Create custom legend
-a <- c(1,2,3,4)
-b <- c(1,2,3,4)
-c <- c("a","b", "c", "d")
-abc <- data.frame(a,b,c)
-p1 <- ggplot(abc, aes(x=a,y=b, color=c))+geom_point() + theme_bw() + 
-  scale_colour_manual(name = 'Path length classification', 
-                      values =c(a= 'goldenrod2',b='mediumaquamarine',
-                                c='skyblue', d='lightcoral'), 
-                      labels = c(a='Strong \n mean path length = 1.38', 
-                                 b='Medium-strong \n mean path length = 1.48',
-                                 c='Medium-weak \n mean path length = 1.60',
-                                 d='Weak \n mean path length = 1.85'))+
-theme(legend.position="bottom")+ guides(colour = guide_legend(override.aes = list(size=8),title.position="top", title.hjust = 0.5))
-
-legend <- cowplot::get_legend(p1+ theme(legend.position = "bottom",legend.text = element_text(size=10), legend.title = element_text(size=12, 
-face="bold"),legend.box.background = element_rect(color="black", size=2)))
-
-cowplot::plot_grid(p, legend, ncol = 1, rel_heights = c(12, 1.8))
-
-```
-
-To assess the significance of the observed frequencies, we created 1,000 simulated networks for each binary network using the *nullmodel* function and the *vaznull* model in the *bipartite* package version *2.14* [@dormann2009].
-Generated networks had the same number of plants and floral visitors, as well as the same connectance of their corresponding empirical networks.
-We discarded null models with more constraints (e.g., constraining for species degree) because the permutations did not generate sufficient variability and provided highly similar or identical networks to the original ones.
-After extracting the subgraph frequencies from the simulated networks, for each subgraph type and empirical network, we calculated the percentage of simulated networks whose frequencies were smaller than the ones observed, that is, we estimated the percentile of the observed subgraph frequencies.
-Subgraphs whose percentile is close to 0 or 100 are under- or over-represented in empirical networks, respectively, and indicate the presence of network motifs as they differ statistically from the network structures generated with simulated networks.
-To summarise general patterns across networks, we used an intercept-only linear mixed model (LMM) per subgraph with the help of the *lme4* package version *1.1-21* [@bates2015], where the response variable was the observed subgraph percentile per network.
-Note that as we are only interested in modelling the intercept value, no predictors were specified.
-In these models, we used the study identifiers in Table S1 as a random intercept.
-By doing so, we obtained estimates of the average subgraph frequency, but controlling for the variation at the study level.
-
-**Over- and under-represented functional groups on subgraph positions**
-
-We calculated which plant and floral visitor functional groups were over- or under-represented in the different subgraph positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
-To estimate the position frequencies of each plant and floral visitor group in a given network, we added the frequencies of those species that belong to the same group, and then, we normalised the resulting frequencies by dividing them by the total number of times that a corresponding group appears in any position within the same subgraph size class.
-Then, we calculated the percentile of the observed position frequencies for each functional group and network, just like we did with subgraph frequencies.
-To outline the general patterns of position frequencies across networks and groups, we fit a LMM per subgraph position, where the response variable was the observed position percentile per network.
-We used the group identifier as an explanatory variable and the study identifiers as a random intercept.
-Hence, we assessed the average subgraph frequency per species group, after controlling for the variation at the study level.
-Finally, we visualised over- and under-representation of plant and floral visitor groups on the different subgraph positions with the help of the *ComplexHeatmap* package version *2.6.2* [@gu2016].
-
-To understand if the different plant and floral visitor functional groups are associated with subgraph positions that represent different network roles, we characterised the roles of each subgraph position for the different functional groups in terms of their specialisation and number of indirect interactions.
-To that end, we calculated the specificity of each subgraph position following @poisot2015 as $s_i = (L - l_i) / (L - 1)$, where $L$ is the total number of groups and $l_i$ the number of interaction partners of the group $i$ in a given subgraph.
-Values of the vector $si$, range between 1, complete specialisation (1 partner within the subgraph) and 0 complete generalism (all possible partners within the subgraph).
-Then, because all nodes within a motif are connected, we calculated the number of indirect interactions ($\theta_i$) for each motif position as $\theta_i=m_i-k_i-1$, where $m_i$ is the total number of nodes in a given motif, and $k_i$ represents the degree of the corresponding motif position, that is, the total number of links connected to such position.
-Thus, we considered all possible indirect interactions for each position.
-Finally, we analysed in a single model how specialisation and the number of indirect interactions were associated with the observed percentiles for each trophic guild and subgraph position.
-For this, we fitted again a LMM model with the help of the *lme4* package, where we considered specialisation and number of indirect interactions as response variables with the interaction by plant and floral visitor group for both response variables.
-Further, we considered as random factor subgraph position nested within study system.
-
-**Over- and under-represented functional group combinations of subgraphs**
-
-Finally, we studied which combinations of plant and floral visitor functional groups tend to appear together within the same subgraphs (up to five nodes).
-That is, which combinations are over- or under-represented.
-This analysis used 57 out of the 60 networks available due to computational limitations to identify all the nodes in the subgraphs of the three networks with the highest number of links.
-To do so, for each of the 53,250 possible subgraph combinations, we estimated the observed and the expected probability of finding those combinations in empirical networks, respectively.
-Then, we determined whether the observed probabilities are likely to come from the expected probabilities or not.
-To calculate the observed probability ($p_i^O$) of the different groups within a subgraph $i$ (e.g., subgraph 3, 'bee' + 'bee' + 'selfing herbs'), we divided the number of times that $i$ appears in our set of empirical networks ($n_i^O$) by the sum of the number of times that each possible combination appeared: $p_i^O = n_i^O / \sum_{k=1}^{53,250} n_k^O$.
-To estimate the expected probability ($p_i^E$) of a given subgraph combination $i$, we assumed that the probability of finding a given functional group $x$ in the position $\alpha$ is independent of the probabilities associated with other positions and groups in that subgraph.
-Therefore, the expected probability ($p_i^E$) of the subgraph combination $i$ is given by the product of the probabilities of its constituents, i.e., $p_i^E = \prod _{(x,\alpha )\in i} p_i(x,\alpha)$, where $p_i(x,\alpha)$ is the probability of finding a given functional group $x$ in the position $\alpha$ of $i$.
-Then, by controlling for the variation at the network level with an LMM (see below), we calculated the average number of times that the functional group $x$ appears in the position $\alpha$ (denoted as $n_i(x,\alpha)$).
-To obtain the expected probability $p_i(x,\alpha)$, we divided the number of times that the group $x$ appears in the position $\alpha$ by the the total number of times that any group was observed in that position (that is, $p_i(x,\alpha) = n_i(x,\alpha)/\sum_{k}n_i(k,\alpha)$).
-The average number of times that the group $x$ appears in the position $\alpha$ ($n_i(x,\alpha)$) was calculated with a LMM for each position, where the response variable was the number of times that a group was observed at a given position in each real-world network, the explanatory variable was the group identifier, and the random intercept was given by network identifiers nested within the study identifiers.
-
-Once we obtained $p_i^O$ and $p_i^E$, we used a simulation approach to determine whether the former is likely to come from the latter or not.
-This approach was preferred since the large number of possible subgraph combinations and the small probabilities for some of them advise against using an exact test of goodness-of-fit or a Chi-square one.
-Specifically, we created 1,000 random samples with repetition of possible subgraph combinations, where each sample contained 10 million elements and, for each combination, the probability of being selected was equal to its expected probability.
-From those random samples, we extracted the mean and the standard deviation of the expected probability of $i$, denoted as $E\left [ p_i^E \right ]$ and $\sigma\left [ p_i^E \right ]$, respectively, and calculated the z-scores of $p_i^O$ as $z_i^O = \left ( p_i^O - E\left [ p_i^E \right ] \right )/\sigma \left [ p_i^E \right ]$, for those motif combinations with $p_i^O > 0$.
-According to the usual interpretation of z-scores, combinations with $z_i^O > 1.96$ are over-represented, whereas those with $z_i^O < -1.96$ are under-represented, at the 95$\%$ confidence level.
-Notice that we focused on combinations with $p_i^O > 10^{-7}$ because we do not have enough numerical resolution to accurately detect whether combinations that took place only once are under-represented (due to the limited size of our random samples).
-
-All analyses and data manipulation were conducted in R *version 4.0.5* [@R].
-In addition, all model diagnostics were conducted with the help of the *Dharma* package [@hartig2017] version *0.3.3.0* and model outputs were visualised with the *visreg* package [@breheny2020] version 2.7.0.
-
-# RESULTS
-
-**Plant and floral visitor functional groups**
-
-The hierarchical cluster analysis divided the dataset into five different plant functional groups with different and overlapping characteristics (Figs S4 and S5).
-The first group referred to as 'selfing herbs' consisted of herbs with hermaphroditic flowers with high levels of autonomous selfing.
-The second group named 'small outcrossing perennials' had small perennial species with a mix of life forms (i.e., trees, shrubs and herbs) with outcrossing hermaphroditic flowers.
-The third group referred to as 'self-incompatible perennials with large flowers' comprised perennial species with a mixed of life forms and large self-incompatible hermaphroditic flowers with high number of ovules.
-The fourth group named 'tall plants with small unisexual flowers' had the tallest species, highest proportion of shrub and tree life forms, dioecious and monoecious breeding systems, small flowers, and the highest numbers of flowers and inflorescences per plant.
-Finally, the fifth group named 'short-lived outcrossers with long zygomorphic flowers' consisted of small perennial and short-lived herbs with long self-compatible zygomorphic flowers that were unable to self-pollinate.
-
-In total, there were 1,126 species of floral visitors with 6,325 interactions recorded with plants.
-Most plants interacted with bees (2,256 interactions) and non-syrphid Diptera (1,768) followed by syrphids (845), Lepidoptera (437), Coleoptera (432) and non-bee Hymenoptera (362).
-
-**Overall network subgraphs patterns**
-
-Most network subgraphs were under- or over-represented (close to the 1st and 99th percentile, respectively) in the comparison between empirical and simulated networks (Fig.
-2).
-Network subgraphs 3, 5, 9, 10 and 14 were under-represented in empirical networks, that is, all were close to the 1st percentile and under the 25th percentile.
-Interestingly, four out of five of these motifs belonged to the largest path length classification (i.e., core-peripheral).
-In addition, network subgraphs 2, 6, 7, 16 and 17 were over-represented, all over the 75th percentile.
-In contrast to the under-represented network subgraphs, over-represented subgraphs belonged to the two shortest path length groups (i.e., complete and fan).
-The remaining network subgraphs (i.e., 4, 8, 11, 12, 13, and 15) were between the 25th and 75th percentile.
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure 2.** Comparison of network subgraph frequencies between empirical and simulated networks grouped by average path length (plots a, b, c and d) where $\\overline{x}$ indicates the mean of the average path lengths of all subgraphs within each group (strong, medium-strong, medium-weak and weak).
-This comparison is shown with the mean percentage of subgraph frequencies in empirical networks that were over the subgraph frequencies of the simulated ones (percentiles).
-This was done by network (light blue transparent dots) and then averaged for all networks (black dots with error bars that correspond to the standard deviation)."}
-
-library(lme4)
-library(nlme)
-library(tidyverse)
-source("../../Scripts/Scripts_Alfonso/add_study_id.R")
-d <- read_csv("../../Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
-d <- add_study_id(d)
-#str(d)
-#head(d)
-
-#ggplot(d %>% filter(motif != 1), aes(percentil_sizeclass))+
-#  geom_histogram(color="black", fill="white")+
-#  facet_wrap(~motif)+
-#  theme_bw()+
-#  labs(x="Sizeclass percentile")
-#
-# Motifs tend to be over- and under-represensented in real networks
-
-# Mean percentile and SE taking into account the study system
-motif_codes <- d %>% filter(motif != 1) %>% # We remove links (motif code: 1)
-  select(motif) %>% unique() %>% pull()
-motif_means <- tibble(motif = motif_codes)
-motif_means$mean <- NA
-motif_means$SE <- NA
-
-for(i.motif in 1:length(motif_codes)){
-
-  m <- lmer(percentil_sizeclass ~ 1+(1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = subset(d, motif == motif_codes[i.motif]))
-
-  motif_means$mean[i.motif] <- fixed.effects(m) %>% unname()
-  motif_means$SE[i.motif] <- sqrt(diag(vcov(m)))
-
-}
-
-#Add categories based on path length set by Simmons 2021 et al., Functional Ecology
-d$Broad_categories[d$motif==2 | d$motif==7 | d$motif==17 | d$motif==3|d$motif==4|d$motif==8] <- "Fan"
-
-d$Broad_categories[d$motif==15 | d$motif==11] <- "Medium-weak"
-
-d$Broad_categories[d$motif==6 | d$motif==16 |  d$motif==12] <- "Strong"
-
-d$Broad_categories[d$motif==5 | d$motif==9 |  d$motif==14|  d$motif==13|  d$motif==10] <- "Weak"
-
-#order the categories from short to long path length
-d$Broad_categories <- factor(d$Broad_categories, levels = c("Strong", "Fan", "Medium-weak", "Weak"))
-
-#Ffilter out two node motifs
-d_1 <- d %>% filter(motif != 1)
-#Merge dataframes to bl able to create facets
-d_2 <- merge(d_1, motif_means, by="motif")
-
-arr <- list('Strong' = expression(bold(paste("(a) Strong (Complete, ", bar(x), " = 1.38)"))),
-             'Fan' = expression(bold(paste("(b) Medium-strong (fan, ", bar(x), " = 1.48)"))), 
-             'Medium-weak' = expression(bold(paste("(c) Medium-weak (asymmetric complete, ", bar(x), " = 1.60)"))), 
-             "Weak" =expression(bold(paste("(d) Weak (core-peripheral, ", bar(x), " = 1.85)"))))
-mylabel <- function(val) { return(lapply(val, function(x) arr[x])) }
-
-library(ggforce) #workaround with ggforce to have facets with same sizes 
-library(ggtext)
-
-labels <- c("2" = "*Subgraph 2* <img src='../../Images/motif_2.png' width='22'/>" ,
-          "3"= "*Subgraph 3* <img src='../../Images/motif_3.png' width='22'/>",
-          "4"= "*Subgraph 4* <img src='../../Images/motif_4.png' width='22'/>",
-          "5"= "*Subgraph 5* <img src='../../Images/motif_5.png' width='22'/>",
-          "6"= "*Subgraph 6* <img src='../../Images/motif_6.png' width='22'/>",
-          "7"= "*Subgraph 7* <img src='../../Images/motif_7.png' width='22'/>",
-          "8"= "*Subgraph 8* <img src='../../Images/motif_8.png' width='22'/>",
-          "9"= "*Subgraph 9* <img src='../../Images/motif_9.png' width='22'/>",
-          "10"= "*Subgraph 10* <img src='../../Images/motif_10.png' width='22'/>",
-          "11"= "*Subgraph 11* <img src='../../Images/motif_11.png' width='22'/>",
-          "12"= "*Subgraph 12* <img src='../../Images/motif_12.png' width='22'/>",
-          "13"= "*Subgraph 13* <img src='../../Images/motif_13.png' width='22'/>",
-          "14"= "*Subgraph 14* <img src='../../Images/motif_14.png' width='22'/>",
-          "15"= "*Subgraph 15* <img src='../../Images/motif_15.png' width='22'/>",
-          "16"= "*Subgraph 16* <img src='../../Images/motif_16.png' width='22'/>",
-          "17"= "*Subgraph 17* <img src='../../Images/motif_17.png' width='22'/>")
-
-p <- ggplot()+geom_point(data = d_2 , aes(y=factor(motif), 100*percentil_sizeclass), shape=21,color="black",fill="azure2",size=1.75, alpha=0.3)+
-  geom_errorbar(data = d_2,aes(y = factor(motif), xmin=100*(mean-SE), xmax=100*(mean+SE)), 
-                width=0.8,size=0.8,color="black") +theme_bw()+
-  geom_point(data = d_2,aes(y = as.factor(motif), x=100*mean), 
-             size=2,color="black")+labs(y="Two to five node motifs", x = "Percentile")+
-  theme( strip.background = element_blank())+
-  theme(strip.text = element_text(face="bold", size=10, hjust=0),
-        panel.border=element_rect(color="black",size=1.2))+
-  scale_y_discrete(name = NULL,
-                   labels = labels) +
-  theme(axis.text.y = ggtext::element_markdown())
-
-p + ggforce::facet_col(vars(Broad_categories), scales = 'free', space = 'free',labeller=mylabel)
-
-#Trying to maintain a gradient from low to high in colors
-
-#Fig 1 Should be a dot plot (or forest plot) of the mean +- SE of the 15 motifs.
-#NICE! Can we put motifs in Y axes, and % in X?
-```
-
-**Over- and under-represented functional groups on subgraph positions**
-
-```{r , include=FALSE}
-
-#SAME SCRIPT AS THE PLOTTING FOR THE HEATMAP BUT I NEED IT HERE TO LOAD THE VARIABLES WITH VALUES ON RESULTS
-
-library(lme4)
-library(nlme)
-library(tidyverse)
-library(stringi)
-source("../../Scripts/Scripts_Alfonso/add_study_id.R")
-
-#############################################
-# EXTRACT MEAN VALUES
-#############################################
-all_position_percentiles <- read_csv("../../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
-
-all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
-                                                              "[0-9]+") %>% as.numeric()
-
-all_position_percentiles <- add_study_id(all_position_percentiles)
-#str(all_position_percentiles)
-#head(all_position_percentiles)
-
-list_plants_FG <- as.character(1:10)
-
-plant_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF)) #ME DA ERROR
-pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF))
-
-# Plants-------------
-
-# Mean percentile and SE taking into account the study system
-plant_codes <- plant_position_percentiles_filtered$position %>% unique()
-plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-plant_means$mean <- NA
-plant_means$SE <- NA
-
-for(i.pos in 1:length(plant_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
-            data = plant_position_percentiles_filtered %>%
-              filter(position == plant_codes[i.pos]))
-
-  temp <- fixed.effects(m) %>% unname()
-  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
-                                                                    temp[1]+temp[2],
-                                                                    temp[1]+temp[3],
-                                                                    temp[1]+temp[4],
-                                                                    temp[1]+temp[5]) ## to get real means per FG
-  temp <- sqrt(diag(vcov(m)))
-  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
-                                                                  temp[1]+temp[2],
-                                                                  temp[1]+temp[3],
-                                                                  temp[1]+temp[4],
-                                                                  temp[1]+temp[5])
-
-}
-
-# Pollinators--------
-
-# Mean percentile and SE taking into account the study system
-pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
-pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-pollinator_means$mean <- NA
-pollinator_means$SE <- NA
-pollinator_means_reordered <- NULL
-
-for(i.pos in 1:length(pollinator_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = pollinator_position_percentiles_filtered %>%
-              filter(position == pollinator_codes[i.pos]),
-            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
-
-  temp <- fixed.effects(m) %>% unname()
-  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)
-
-  pollinator_means_aux$mean <- c(temp[1],
-                                 temp[1]+temp[2],
-                                 temp[1]+temp[3],
-                                 temp[1]+temp[4],
-                                 temp[1]+temp[5],
-                                 temp[1]+temp[6],
-                                 temp[1]+temp[7],
-                                 temp[1]+temp[8],
-                                 temp[1]+temp[9]) ## to get real means per FG
-
-  temp <- sqrt(diag(vcov(m)))
-  pollinator_means_aux$SE <- c(temp[1],
-                               temp[1]+temp[2],
-                               temp[1]+temp[3],
-                               temp[1]+temp[4],
-                               temp[1]+temp[5],
-                               temp[1]+temp[6],
-                               temp[1]+temp[7],
-                               temp[1]+temp[8],
-                               temp[1]+temp[9])
-
-  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)
-
-}
-
-# There are lower limits (mean - SE) smaller than 0 (see Other insects)
-# We set the lower limit of those error bars to zero
-
-pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
-pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
-
-#############################################
-# ADDING BROAD MOTIF CATEGORIES TO POSITIONS
-#############################################
-
-motifs_raw_data <- read_csv("../../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-motifs_raw_data$Broad_categories <- NA
-
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(5,9,14,13,10)] <- "Core-peripherical"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(6,16,12)] <- "Complete"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(2,3,7,4,17,8)] <- "Fan"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(15,11)] <- "Asymmetric complete"
-
-motifs_raw_data$plant <- gsub("[^0-9.-]", "", motifs_raw_data$plant)
-motifs_raw_data$pollinator <- gsub("[^0-9.-]", "", motifs_raw_data$pollinator)
-motifs_raw_data$plant <- as.numeric(motifs_raw_data$plant)
-motifs_raw_data$pollinator <- as.numeric(motifs_raw_data$pollinator)
-motifs_raw_data <- motifs_raw_data %>% filter(!is.na(Broad_categories))
-
-fan_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-pollinator_means_reordered$Broad_categories <- NA
-
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% fan_pollinator] <- "Fan" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% asymm_pollinator] <- "Medium-weak" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% complete_pollinator] <- "Strong" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% core_per_pollinator] <- "Weak"
-
-fan_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-plant_means$Broad_categories <- NA
-
-plant_means$Broad_categories[plant_means$position %in% fan_plant] <- "Fan" 
-plant_means$Broad_categories[plant_means$position %in% asymm_plant] <- "Medium-weak" 
-plant_means$Broad_categories[plant_means$position %in% complete_plant] <- "Strong" 
-plant_means$Broad_categories[plant_means$position %in% core_per_plant] <- "Weak"
-
-################################################################################
-# Alternative code to HEATMAPS to create variables with values to load on text
-# in a reproducible/automated way
-################################################################################
-
-# PLANTS-----
-
-# Prepare data for heatmap
-heat_plants_aux <- plant_means %>% spread(Node_FG,mean) %>% select(-SE)
-
-heat_plants <- heat_plants_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-# POLLINATORS-----------
-
-filter_rare_groups <- T
-
-if(filter_rare_groups == T){
-  heat_pollinators_aux <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds",
-                                                                                "Lizards",
-                                                                                "Other_insects")) %>% 
-    spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees",            
-                                      "Coleoptera","Lepidoptera","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Syrphids")
-}else{
-  heat_pollinators_aux <- pollinator_means_reordered %>% spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees","Birds",            
-                                      "Coleoptera","Lepidoptera","Lizards","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Other insects","Syrphids")
-}
-
-heat_pollinators <- heat_pollinators_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))
-
-#Check percentage of over and under represented
-colMeans(heat_pollinators[,c(3:8)] < 0.25)
-poll_under_25 <- colMeans(heat_pollinators[,c(3:8)] < 0.25)
-poll_under_25 <- specify_decimal((poll_under_25[[1]] + poll_under_25[[2]] + poll_under_25[[3]] +
-poll_under_25[[4]] + poll_under_25[[5]] + poll_under_25[[6]])/6*100,2)
-#[1] 32.57576
-
-colMeans(heat_pollinators[,c(3:8)] > 0.75)
-poll_over_75 <- colMeans(heat_pollinators[,c(3:8)] > 0.75)
-poll_over_75 <- specify_decimal((poll_over_75[[1]] + poll_over_75[[2]] + poll_over_75[[3]] +
-    poll_over_75[[4]] + poll_over_75[[5]] + poll_over_75[[6]])/6*100,2)
-#[1] 4.545455
-
-#################################################################################
-#################################################################################
-
-colnames(heat_plants)<- c("position", "Broad_categories", "one",
-                               "two", "three","four",
-                               "five")
-f <- heat_plants %>%
-  mutate(min = pmin(1,
-                    one, two,three,
-                    four, five))%>%
-  mutate(max = pmax(one,
-                    two, three,four,
-                    five))
-
-diff_1 <- f$max-f$min
-
-cbind(diff,diff_1)
-
-#Check percentage of over and under represented per FG
-colMeans(heat_plants[,c(3:7)] < 0.25)
-plant_under_25 <- colMeans(heat_plants[,c(3:7)] < 0.25)
-plant_under_25 <- specify_decimal((plant_under_25[[1]] + plant_under_25[[2]] + plant_under_25[[3]] + 
-    plant_under_25[[4]] + plant_under_25[[5]])/5*100,2)
-#[1] 18.18182
-colMeans(heat_plants[,c(3:7)] > 0.75)
-plant_over_75 <- colMeans(heat_plants[,c(3:7)] > 0.75)
-plant_over_75 <- specify_decimal((plant_over_75[[1]] + plant_over_75[[2]] + plant_over_75[[3]] + 
-    plant_over_75[[4]] + plant_over_75[[5]])/5*100,2)
-#[1] 8.181818
-
-#overall percentages
-under <- specify_decimal((as.numeric(poll_under_25) + as.numeric(plant_under_25))/2,2)
-over <- specify_decimal((as.numeric(poll_over_75) + as.numeric(plant_over_75))/2,2)
-
-```
-
-The comparison of the plant and floral visitor functional group frequencies per subgraph position between empirical and simulated networks showed a `r over`$\%$ and `r under`$\%$ of over- (>75$^{th}$) and under-represented (\<25th) functional groups in the different positions, respectively (Fig.
-3).
-Floral visitors showed a total of `r poll_over_75`$\%$ and `r poll_under_25`$\%$ of over- and under-represented functional groups in the different positions, and plants `r plant_over_75`$\%$ and `r plant_under_25`$\%$ of over- and under-represented functional groups, respectively.
-Notably, the differences across functional groups were more marked for floral visitors than for plants (the differences between the minimum and maximum values of the percentiles per position were generally two-three times larger for floral visitors).
-From most over- to under-represented floral visitors functional groups on the different subgraph positions (indicated with the dendrogram order in Fig.
-3), we found: bees, non-syrphids Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.
-Although plant functional groups showed less differences between them, there were also more represented functional groups than others.
-Thus, from most over- to under-represented functional groups on the different subgraph positions we found: self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.
-
-For both floral visitor and plant functional groups we found over- and under-representation on different subgraph positions that implied different ecological roles.
-First, for floral visitors, we found that bees were less frequent on subgraph positions that involved specialisation (i.e., lower specificity values) while the rest of functional groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) were infrequent in generalised subgraph positions with low number of indirect interactions (Fig.
-S6 A).
-Although plants did not show differences with null models on their frequencies, all plant functional groups but tall plants with small unisexual flowers showed a slight tendency to be over-represented on specialised subgraph positions (Fig.
-S6 B).
-Second, regarding the number of indirect interactions, bees were over-represented in subgraph positions with low number of indirect interactions (Fig.
-S7 A) and the rest of floral visitor functional groups showed no differences across positions in comparison with simulated networks.
-For plants, all functional groups showed a slight tendency to be over-represented on subgraph positions with higher number of indirect interactions (Fig.
-S7 B).
-When we further explore the observed frequencies by number of indirect interactions for floral visitor and plant functional groups, we found that both bees and tall plants with small unisexual flowers were the only functional groups with high frequencies on subgraph positions associated with low number of indirect interactions in comparison with the other floral visitor and plant functional groups (Figs S8 and S9).
 
@@
 ```
-
-**Over- and under-represented functional group combinations of subgraphs**
-
-The different observed frequencies on the different subgraph positions showed a hierarchical order of probabilities for floral visitor functional groups (Fig.
-4).
-From the highest to lowest observed probabilities overall, we found: bees, non-syrphid Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.
-On the contrary, plant functional groups were more variable on the different subgraph positions.
-However, there were also predominant functional groups found across the different subgraph positions.
-The three most frequent groups were 'tall plants with small unisexual flowers', 'self-incompatible perennials with large flowers' and 'small outcrossing perennials'.
-On the contrary, the groups of 'selfing herbs' and 'short lived outcrossers with long zygomorphic flowers' had the lowest probability to be present on the different subgraph plant positions.
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 4.** Graphical representation of the probability of finding a given plant and floral visitor functional group $x$ in the position $\\alpha$ of motif $i$, $p_i(x,\\alpha)$, for all the possible network subgraphs from two to five species in bipartite networks.
-The slices in the nodes for a given functional group $x$ are proportional to the corresponding value of $p_i(x,\\alpha)$."}
-
-library(ggplot2)
-library(scatterpie)
-library(RColorBrewer)
-library(tidyverse)
-
-plant_means_reordered <- read_csv("../../Data/Csv/plant_abs_freq_means.csv")
-pollinator_means_reordered <- read_csv("../../Data/Csv/pollinator_abs_freq_means.csv")
-#Filter out in order to have just 6 FG'S
-pollinator_means_reordered <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds", "Lizards", "Other_insects"))
-
-# Pollinator--------
-pollinator_pies <- pollinator_means_reordered %>% select(-mean, -SE) %>% 
-  spread(Node_FG,mean_natural_units)
-
-pollinator_pies$x <- 0
-pollinator_pies$y <- 0
-
-#ggplot() + geom_scatterpie(aes(x=x, y=y, group=position,r=5), 
-#                           data = pollinator_pies,
-#                           cols=as.character(c("Bee","Birds","Coleoptera","Lepidoptera",
-#                                               "Lizards","Non-bee-Hymenoptera",
-#                                               "Non-syrphids-diptera","Other_insects",
-#                                               "Syrphids")))+
-#  coord_equal()+
-#  scale_fill_brewer(palette = "Paired")+
-#  facet_wrap(~position,nrow = 3)+
-#  theme_bw()+
-#    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
-#          panel.background = element_blank(),
-#          axis.title.x=element_blank(),axis.text.x=element_blank(),
-#          axis.ticks.x=element_blank(),axis.title.y=element_blank(),
-#          axis.text.y=element_blank(),axis.ticks.y=element_blank(),
-#          legend.position="bottom")+
-#  labs(title = "Pollinator positions",fill=NULL)
-#    
-# plant--------
-plant_pies <- plant_means_reordered %>% select(-mean, -SE) %>% 
-  spread(Node_FG,mean_natural_units)
-
-plant_pies$x <- 0
-plant_pies$y <- 0
-
-#ggplot() + geom_scatterpie(aes(x=x, y=y, group=position,r=5), 
-#                           data = plant_pies,
-#                           cols=as.character(c("1","2","3","4","5")))+
-#  coord_equal()+
-#  scale_fill_brewer(palette = "Dark2")+
-#  facet_wrap(~position,nrow = 3)+
-#  theme_bw()+
-#  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
-#        panel.background = element_blank(),
-#        axis.title.x=element_blank(),axis.text.x=element_blank(),
-#        axis.ticks.x=element_blank(),axis.title.y=element_blank(),
-#        axis.text.y=element_blank(),axis.ticks.y=element_blank(),
-#        legend.position="bottom")+
-#  labs(title = "Plant positions",fill=NULL)
-#
-
-#################################
-# CREATE PIE-MOTIFS
-#################################
-
-equidistribution <- function(number_nodes){
-
-  x_width <- 5.5/(number_nodes+1)
-
-  x_result <- rep(-1.5,number_nodes)
-
-  for(i in 1:number_nodes){
-
-    x_result[i] <- x_result[i] + i*x_width
-
-  }
-
-  return(x_result)
-
-}
-
-plot_pie_motif_positions <- function(motif_number){
-  motifs_raw_data <- read_csv("../../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-  motif_data <- motifs_raw_data %>% filter(motif_id == motif_number)
-
-  # Create dataframe with node positions
-
-  labdown = motif_data$plant %>% unique()
-
-  xdown = equidistribution(length(labdown))
-
-  ydown = rep(0,length(labdown))
-
-  labup = motif_data$pollinator %>% unique()
-
-  xup = equidistribution(length(labup))
-
-  yup = rep(2,length(labup))
-
-  d_nodes=data.frame(x=c(xdown,xup),
-                     y=c(ydown,yup),
-                     label = c(labdown,labup))
-
-  # Create a dataframe with links
-
-  plant_positions <- data.frame(plant = labdown,
-                                xdown = xdown,
-                                ydown = ydown)
-
-  pollinator_positions <- data.frame(pollinator = labup,
-                                     xup = xup,
-                                     yup = yup)
-
-  link_df <- motif_data %>% left_join(plant_positions, by = "plant") %>% 
-    left_join(pollinator_positions, by = "pollinator")
-
-  # Before plotting the motif, we remove letters from the node position id
-
-  d_nodes$label <- gsub("[^0-9.-]", "", d_nodes$label)
-  plant_pies_aux <- plant_pies %>% select(-x,-y) %>% mutate(position = as.character(position))
-
-  d_nodes_plant <- d_nodes %>% rename(position = label) %>% 
-    left_join(plant_pies_aux, by = "position") %>% as_tibble() %>%
-    filter(!is.na(`1`))
-
-  pollinator_pies_aux <- pollinator_pies %>% select(-x,-y) %>% mutate(position = as.character(position))
-
-  d_nodes_pollinator <- d_nodes %>% rename(position = label) %>% 
-    left_join(pollinator_pies_aux, by = "position") %>% as_tibble() %>%
-    filter(!is.na(Bee))
-
-  # Define the number of colors you want
- mycolors <- c("#A6CEE3", "chocolate2",  "gold2", "#1F78B4","#B2DF8A",
-                     "gray58", "lightgoldenrod2","thistle2", "burlywood","lightcoral", "olivedrab3")
-
-  ggplot() +
-    scale_shape_identity() +
-    geom_segment(data = link_df, aes(x=xdown, y=ydown, xend = xup, yend = yup), 
-                 size = 1, color = "grey20")+  geom_scatterpie(aes(x=x, y=y, group=position,r=.45), 
-    data = d_nodes_pollinator, cols=as.character(c("Bee","Coleoptera","Lepidoptera","Non-bee-Hymenoptera", "Non-syrphids-diptera","Syrphids"))) +
-    geom_scatterpie(aes(x=x, y=y, group=position,r=0.45), 
-                    data = d_nodes_plant,
-                    cols=as.character(c("1","2","3","4","5")))+
-    coord_fixed()+
-    scale_fill_manual(values = mycolors,"test",
-      breaks=c("Bee","Coleoptera","Lepidoptera",
-               "Non-bee-Hymenoptera", "Non-syrphids-diptera",
-               "Syrphids","1","2","3","4","5"), labels=c("Bees","Coleoptera","Lepidoptera",
-"Non-bee-Hymenoptera", "Non-syrphids-Diptera","Syrphids", 
-          "Selfing herbs","Small outcrossing perennials","Self-incomp. perennials\nwith large flowers",
-          "Tall plants with small\nunisexual flowers","Short-lived outcrossers with\nlong zygomorphic flowers"))+
-    xlim(-1.5,4)+ ylim(-0.5,2.5)+
-    theme(panel.background = element_blank(),
-          axis.text.x=element_blank(),
-          axis.ticks.x=element_blank(),
-          axis.text.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          legend.title = element_text(size=12, face="bold"),legend.background = element_rect(size=0.5, linetype="solid",colour ="black"))+
-    labs(x=NULL,y=NULL)+
-    guides(color = FALSE,fill=guide_legend(title="Functional groups"))+
-    ggtitle(paste0("Motif ",motif_number))+
-    theme(plot.title = element_text(hjust = 0.5),legend.key.size = unit(0.5, 'cm'))+
-    theme(plot.margin=unit(c(0,0,0,0),"cm"))
-}
-
-motif_number <- 1
-p1 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 2
-p2 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 3
-p3 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 4
-p4 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 5
-p5 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 6
-p6 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 7
-p7 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 8   
-p8 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 9
-p9 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 10
-p10 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 11
-p11 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 12
-p12 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 13
-p13 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 14
-p14 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 15
-p15 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 16
-p16 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 17
-p17 <- plot_pie_motif_positions(motif_number)
-
-library(patchwork)
-
-(p1 & ylab("2 species")| p2 & ylab("3 species") | p3  |plot_spacer()|plot_spacer())/ 
-  (p4 & ylab("4 species")| p5 | p6 | p7|plot_spacer())/ 
-  (p8  & ylab("5 species")| p9 | p10 | p11 | p12) / 
-  (p13 & ylab("5 species")| p14 | p15 | p16 | p17) + plot_layout(guides = 'collect') &
-  theme(axis.title.y = element_text(color="black", size=14, face="bold"),legend.position = "bottom")
-
-```
-
-The statistical comparison with z-scores between the observed and expected plant and floral visitor functional group combinations showed that we can not recover the observed combinations from its probability of occurrence.
-In fact, most combinations are under- or over- represented and follow a modified Gaussian distribution (Johnson's $S_U$) with 65$\%$ of under-represented group combinations, 20$\%$ of no statistical difference and 15$\%$ of under-represented ones (Fig.
-5).
-In addition, subgraphs with small node combinations (i.e., 2 and 3 nodes) only appeared as under-represented.
-Network subgraphs with 4 and 5 node combinations appeared in the three statistical categories, but 4 node subgraphs had a higher proportion in the under-represented category (10% in comparison with the 1$\%$ and the 3$\%$ of the no statistical difference and over-represented categories, respectively).
-Finally, 5 node subgraphs were in similar proportions in the no statistical difference and over-represented categories (99$\%$ and 97$\%$, respectively), but they appeared in lower proportion in the under-represented category (89$\%$).
-When we explored the identity on the different positions of the most probable subgraph combinations, we found that the most common plant and floral visitor functional groups were also the most probable on these plant and floral visitor combinations within the different subgraphs (lower panel Fig.
-5).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 5.** Distribution of z-scores values after the statistical comparison of the observed probabilities of finding a subgraph combination in real networks and the expected probabilities (obtained by computer simulations).
-The resulting z-scores frequencies of this statiscal comparison are coloured based on a 95% confidence level: under-represented ($z_i^O < -1.96$, red), no statistical difference ($-1.96 \\geq z_i^O \\leq  1.96$, green) and over-represented ($z_i^O > 1.96$, blue).
-For instance, for a z-score value of 0 there were approximately 800 subgraph combinations that showed no statistical difference in the comparison between real and simulated networks.
-In addition, four specific graphical examples of the most probable subgraphs being observed on each category are also provided and the different plant and floral visitor functional groups are represented with distinct colour codes as indicated in the legend."}
-
-library(tidyverse)
-library(RColorBrewer)
-
-equidistribution <- function(number_nodes){
-
-  x_width <- 5.5/(number_nodes+1)
-
-  x_result <- rep(-1.5,number_nodes)
-
-  for(i in 1:number_nodes){
-
-    x_result[i] <- x_result[i] + i*x_width
-
-  }
-
-  return(x_result)
-
-}
-
-plot_motif_label <- function(label){
-
-  label_split <- str_split(label,"_")[[1]]
-  motif_number <- as.numeric(label_split[1])
-  nodes <- label_split[2:length(label_split)]
-  plant_nodes <- nodes[nodes %in% plant_means_reordered$Node_FG]
-  pollinator_nodes <- nodes[nodes %in% pollinator_means_reordered$Node_FG]
-
-  motifs_raw_data <-read_csv("../../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-  motif_data <- motifs_raw_data %>% filter(motif_id == motif_number)
-
-  # Create dataframe with node positions
-
-  labdown = motif_data$plant %>% unique()
-
-  xdown = equidistribution(length(labdown))
-
-  ydown = rep(0,length(labdown))
-
-  labup = motif_data$pollinator %>% unique()
-
-  xup = equidistribution(length(labup))
-
-  yup = rep(1,length(labup))
-
-  d_nodes=data.frame(x=c(xdown,xup),
-                     y=c(ydown,yup),
-                     label = c(labdown,labup))
-
-  # Create a dataframe with links
-
-  plant_positions <- data.frame(plant = labdown,
-                                xdown = xdown,
-                                ydown = ydown)
-
-  pollinator_positions <- data.frame(pollinator = labup,
-                                     xup = xup,
-                                     yup = yup)
-
-  link_df <- motif_data %>% left_join(plant_positions, by = "plant") %>% 
-    left_join(pollinator_positions, by = "pollinator")
-
-  # Add FG IDs to nodes
-  FG_IDs <- tibble(label = c(sort(labdown),sort(labup)),
-                   FG = c(plant_nodes,pollinator_nodes))
-
-  d_nodes_FG <- d_nodes %>% left_join(FG_IDs, by = "label")
-  levels_FG <- c("Bee","Coleoptera","Lepidoptera",
-                 "Non-bee-Hymenoptera", "Non-syrphids-diptera",
-                 "Syrphids","1","2","3","4","5")
-
-  d_nodes_FG$FG <- factor(d_nodes_FG$FG, levels = levels_FG)
-
-  levels(d_nodes_FG$FG) <- c("Bee","Coleoptera","Lepidoptera",
-                             "Non-bee-Hymenoptera", "Non-syrphids-diptera",
-                             "Syrphids","1","2","3","4","5")
-
-  # Before plotting the motif, we remove letters from the node position id
-
-  d_nodes_FG$label <- gsub("[^0-9.-]", "", d_nodes_FG$label)
-
-  # Define the number of colors you want
- mycolors <- c("#A6CEE3", "chocolate2",  "gold2", "#1F78B4","#B2DF8A",
-                     "gray58", "lightgoldenrod2","thistle2", "burlywood","lightcoral", "olivedrab3")
-
-  ggplot(data=d_nodes_FG, aes(x, y)) +
-    scale_shape_identity() +
-    geom_segment(data = link_df, aes(x=xdown, y=ydown, xend = xup, yend = yup), size = 1, color = "grey20")+
-    geom_point(aes(color = FG), size=7.5)+
-    geom_text(aes(x, y , label = label), size=3)+
-    scale_color_manual(drop = FALSE, values = mycolors,
-                       breaks=c("Bee","Coleoptera","Lepidoptera",
-                                "Non-bee-Hymenoptera", "Non-syrphids-diptera",
-                                "Syrphids","1","2","3","4","5"), 
-                       labels=c("Bees","Coleoptera","Lepidoptera",
-                                "Non-bee-Hymenoptera", "Non-syrphids-Diptera",
-                                "Syrphids", 
-                                "Selfing herbs","Small outcrossing perennials",
-                                "Self-incomp. perennials\nwith large flowers",
-                                "Tall plants with small\nunisexual flowers",
-                                "Short-lived outcrossers with\nlong zygomorphic flowers"))+
-    xlim(-1.5,4)+ ylim(-0.5,1.5)+
-    theme(panel.background = element_blank(),
-          axis.text.x=element_blank(),
-          axis.ticks.x=element_blank(),
-          axis.text.y=element_blank(),
-          axis.ticks.y=element_blank())+
-    labs(x=NULL,y=NULL)+
-    ggtitle(paste0("Motif ",motif_number))+
-    theme(plot.title = element_text(hjust = 0.5,size=10))+
-    guides(color=guide_legend(title="Functional groups"))
-
-}
-
-# Data with pollinator/plant labels
-
-plant_means_reordered <- read_csv("../../Data/Csv/plant_abs_freq_means.csv")
-pollinator_means_reordered <- read_csv("../../Data/Csv/pollinator_abs_freq_means.csv")
-#Filter out in order to have just 6 FG'S
-pollinator_means_reordered <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds", "Lizards", "Other_insects"))
-
-####################################################################################################
-#Read data to check top 5 motif of each category of observed propabilities
-
-#Under, No signi, Over-rep
-####################################################################################################
-# Check top Z-scores of each group (Under, No diff, Over)
-
-#Read data
-data <- read.csv("../../Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
-
-#Find critical value of Z-score
-p <- 0.05 #cutoff probability 95% confidence
-critical_value <- qnorm(p/2) #double tail probability divide by 2
-
-data_1 <- data %>%
-  mutate(infra_over_represented = case_when(
-    z_score < -abs(critical_value) ~ "infra",
-    between(z_score, -abs(critical_value), abs(critical_value)) ~ "no_diff",
-    z_score > abs(critical_value) ~ "over"
-  ))
-
-#data_2 <- filter(data_1, abs(z_score)<2000) 
-#str(data_2)
-
-#Select under-represented by the ones with highest porbability of being observed (top10)
-under_data <- filter(data_1, infra_over_represented=="infra")
-
-under_top_5 <- filter(under_data, row_number(desc(abs(motif_observed_probability)))<= 5) %>%
-  select(motif_functional_ID,motif_observed_probability,counts_observed,z_score)
-
-#Select no statistical difference by the ones with highest porbability of being observed (top5)
-no_diff_data <- filter(data_1, infra_over_represented=="no_diff")
-
-no_diff_top_5 <- filter(no_diff_data, row_number(desc(abs(motif_observed_probability)))<= 5) %>%
-  select(motif_functional_ID,motif_observed_probability,counts_observed,z_score)
-
-#Select over-represenetd by the ones with highest porbability of being observed (top5)
-over_data <- filter(data_1, infra_over_represented=="over")
-
-over_top_5 <- filter(over_data, row_number(desc(abs(motif_observed_probability)))<= 5) %>%
-  select(motif_functional_ID,motif_observed_probability,counts_observed,z_score)
-####################################################################################################
-#Now plot it 
-####################################################################################################
-
-library(patchwork)
-
-#Prepare list of 5 plots for each group
-#Under
-labels_under <- under_top_5$motif_functional_ID
-p_under <- list()
-
-for (i in 1:5){
-
-  p_under[[i]] <- plot_motif_label(labels_under[[i]])
-}
-
-#No signficance
-labels_nodiff <- no_diff_top_5$motif_functional_ID
-p_nodiff <- list()
-
-for (i in 1:5){
-
-  p_nodiff[[i]] <- plot_motif_label(labels_nodiff[[i]])
-}
-
-#Over
-labels_over <- over_top_5$motif_functional_ID
-p_over <- list()
-
-for (i in 1:5){
-
-  p_over[[i]] <- plot_motif_label(labels_over[[i]])
-}
-
-#Run Script with histogram plot
-source("../../Scripts/Z-score_percentile_histogram_plot.R")
-
-hist <- ggplot(data_2 %>% filter(round_motif_observed_probability>0), aes(x=z_score, color=infra_over_represented, fill=infra_over_represented)) + 
-  geom_histogram(bins = 93, alpha = 0.5, position = "identity",lwd = 0.25)+
-  geom_vline(xintercept = -abs(critical_value))+
-  geom_vline(xintercept = abs(critical_value))+
-  xlim(-60,60) + ylab("Frequency")+  theme_bw() +
-  scale_fill_manual(name="Motif frequencies" ,values=c("coral2", "palegreen3", "cyan3"), labels=c("Under-represented",
-                                                                                                  "No statistical difference", "Over-represented")) +
-  scale_color_manual(name="Motif frequencies" ,values=c("coral2", "palegreen3", "cyan3"), labels=c("Under-represented",
-                                                                                                   "No statistical difference", "Over-represented")) + xlab("Z-score")
-
-t_col <- function(color, percent = 50, name = NULL) {
-  #      color = color name
-  #    percent = % transparency
-  #       name = an optional name for the color
-
-  ## Get RGB values for named color
-  rgb.val <- col2rgb(color)
-
-  ## Make new color using input color as base and alpha set by transparency
-  t.col <- rgb(rgb.val[1], rgb.val[2], rgb.val[3],
-               max = 255,
-               alpha = (100 - percent) * 255 / 100,
-               names = name)
-
-  ## Save the color
-  invisible(t.col)
-}
-## END
-
-#Prepare panel of plots
-hist / ((p_under[[1]]/p_under[[2]]/p_under[[3]]/p_under[[4]] & theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_rect(fill=t_col("coral2")))) | 
-          (p_nodiff[[1]]/p_nodiff[[2]]/p_nodiff[[3]]/p_nodiff[[4]]& theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_rect(fill=t_col("palegreen3")))) |
-          (p_over[[1]]/p_over[[2]]/p_over[[3]]/p_over[[4]] & theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_rect(fill=t_col("cyan3"))))) + plot_layout(guides = 'collect')
-
-```
-
-# Discussion
-
-Understanding the global patterns of network structure is key to unravel the processes that govern community dynamics [@bascompte2007; @bastolla2009; @guimaraes2020].
-However, common analytical approaches at the node or at the global network level are unable to capture the full complexity of ecological systems [@simmons2019; @bergamo2021].
-Because network subgraphs can capture both direct and indirect interactions, by analysing their over- and under-representation we were able to explore in great detail the structure of interactions between animal pollinators and the plants they visit.
-We have explored for the first time the overall structure and presence of network motifs in real plant-pollinator networks and shown that, according to our first hypothesis, the different subgraphs up to five nodes are consistently over- or under-represented in comparison with simulated networks.
-In addition, we show that for plant-pollinator networks there is a general tendency for over-representation of network subgraphs that are more densely connected (i.e., complete, fan and asymmetric complete).
-Indeed, the work of @simmons2020 has shown with the help of simulated plant-pollinator networks that the main different processes that shape plant-pollinator communities (i.e., neutral effects, trait matching and phenology) generate different patterns of direct and indirect interactions, and that specifically, a higher proportion of these more densely connected subgraphs is associated with neutral effects.
-Therefore, as indicated for other network properties like nestedness at the macro-scale level [@krishna2008; @suweis2013], or interaction probability at the species level [@bartomeus2016], our findings align with our second hypothesis and indicate that neutral effects may be also the main driver governing this intermediate level of complexity on plant-pollinator networks.
-
-Overall, generalist network motifs for floral visitors were consistently over-represented (e.g., complete subgraphs; Fig.
-2).
-For instance, when we compare network subgraphs with equal structure for both trophic levels, we found that floral visitors had always over-representation in the positions that implied the highest number of direct links (e.g., positions 16 and 46 from network subgraphs 7 and 17, respectively).
-Despite this being in good agreement with the current view of the generalist nature of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of generalist network motifs was driven by the functional group of bees while the rest of the functional groups tended to be under-represented (Fig.
-S6 A).
-In contrast, non-bee groups were over-represented in subgraph positions associated with specialised roles.
-This large effect of bees on the overall patterns is no surprise, as bees were the group with the largest number of interaction records in the whole set of networks as also shown for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017].
-Just syrphids had a relatively similar number of interactions in comparison with bees (1,768 and 2,256 interactions, respectively) and similar species richness (343 and 321 species, respectively).
-However, both functional groups were associated with contrasting ecological roles likely indicating that both number of interactions and richness are not driving the observed interaction patterns for the different functional groups.
-Interestingly, bees also were the group with lower number of indirect interactions, while the rest of floral visitor groups showed a clearly higher number of indirect interactions, indicating that these non-bee floral visitor groups may experience higher competitive interactions for floral resources [@thomson2020].
-Despite plant functional groups showed little differences between them on their subgraph frequencies, all groups showed a tendency to be over-represented on subgraph positions that were associated with higher levels of specialisation.
-This tendency towards specialist roles may be the result of co-evolutionary processes (e.g., trait-matching) between plants and pollinators to optimise pollen transfer [@moreira2019].
-Remarkably, only tall plants with small unisexual flowers showed higher frequencies on subgraphs that were associated with low number of indirect interactions with likely direct implications on pollen transfer for this group that needs to guarantee cross-pollination.
-
-The probabilities of appearance of each functional group on the different subgraph positions were insufficient to predict most of the observed network position combinations (Fig.
-5).
-This implies that not just the representation of network subgraphs types but also the identity of the elements of their structure is non-random.
-Notably, we found that just 30$\%$ of the possible 53,250 subgraph combinations are realised.
-Thus, similarly to the presence of forbidden links at the network level [@olesen2011; @jordano2016], we also found the existence of forbidden subgraph positions and those represented almost two thirds of the total possible subgraph combinations.
-This concurs well with the general idea that plant-pollinator networks have a high proportion of non-realized direct interactions [@jordano2003; @bascompte2013], and, as a result, also a high proportion of non-realized combinations of indirect interactions.
-Some of these non-observed direct interactions are probably due to under-sampling [@dorado2011; @jordano2016].
-However, a large fraction of the possible interactions do not take place because of different constraints such as species co-occurrence, trait matching processes and phenological uncoupling [@olesen2011; @bartomeus2016; @jordano2016].
-Despite the advances in the understanding of the ecological processes that influence species pairwise interactions [@bartomeus2016; @peralta2020], we still know little about how these processes determine competitive and facilitative interactions in mutualistic networks.
-Thus, as suggested by @simmons2020, exploring the proportion of these realised network subgraphs that are competitive or facilitative is a necessary next step to improve our understanding of the architecture of biodiversity [@bascompte2007].
-
-Despite the obvious usefulness of functional groups in summarising species ecological roles (e.g., similar reproductive biology for plants and behaviour for pollinators), delimiting species into functional groups is often not trivial.
-For instance, taxonomic diversity and trait availability limit our ability to properly represent the wide range of reproductive strategies [@dellinger2020] and different clustering analysis can lead to distinct outcomes (e.g., k-means and hierarchical clustering).
-We divided floral visitors on the taxonomic rank level because it adequately represented pollinator ecological roles without the tremendous effort of compiling trait data for over 1,000 species of floral visitors.
-Indeed, further groupings with traits could help reveal greater relevance of trait-matching processes on indirect interactions.
-Moreover, we analysed network subgraphs focusing exclusively on presence or absence of interactions, assuming that all interactions are equally important.
-However, further work should investigate how to account for quantitative measurements of plant-pollinator interactions.
-Consistent with previous work [@simmons2019; @simmons2020], we characterised network motifs by using null models only constrained for network connectance.
-Although more complex null models are difficult to interpret [@Ulrich2013], they can potentially allow us to separate the mechanisms by which motifs emerge.
-However, we found that null models with more constraints generated binary structures that were mostly identical to the original ones.
-In addition, we observed that connectance, nestedness and degree distribution were significantly correlated (data not shown).
-All that highlights the difficulties to disentangle the potential sources that generate over-representation of network subgraphs and the need to investigate them.
-At the same time, although network subgraphs can capture both direct and indirect interactions, the reduction of network complexity into these different building blocks inevitably convey the loss of information [@simmons2019], for example indirect interactions from large cascading effects.
-Finally, despite the wide geographical coverage of our plant-pollinator dataset, there are major gaps for some regions of the world with a clear bias towards Europe, America and islands which have long interested ecologists [@macarthur1963; @warren2015].
-These biases are also found in global datasets of networks, where the data is highly fragmented across space [@poisot2021] and more efforts are needed to capture global patterns of plant-pollinator interactions.
-
-In conclusion, by following the framework of @simmons2020 we have been able to explore competitive and facilitative interactions in plant-pollinator networks worldwide and found the presence of worldwide motifs that highlight the non-random structure of indirect interactions.
-This non-random structure might emerge due to neutral effects according to previous modelling work [@simmons2020].
-Further, we found that plant and floral visitor functional groups are associated with different subgraph positions that involve distinct ecological roles (e.g., generalisation versus specialisation) and that the different subgraph combinations are strongly constrained.
-Although we are still far from predicting how species interact, our work is a first step to elucidate beyond pairwise interactions.
-
-# Acknowledgements
-
-This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2).
-JBL also thanks the University of New England for the funding provided to carry out this work.
-Finally, we would like to thank David García-Callejas for his useful comments on the manuscript before submission.
-
-# Author contributions
-
-IB, AA-P and JBL designed the idea. JBL collected the data. AA-P led the analysis with contributions of JBL and guidance of IB. JBL wrote the manuscript with contributions of IB and AA-P.
-
-# Data Availability Statement
-
-All data and code are publicly available at Github (<https://github.com/JoseBSL/FunctionalMotifs>) and Zenodo (<https://doi.org/10.5281/zenodo.6489213>).
-
-\newpage
-
-# References
-
-::: {#refs}
-:::

### 2023-01-25 Manuscript/Figures/Figure4.Rmd
Word file and independent figures for typesetting

--- 2023-01-17 Manuscript/Main_text/Main_text_Journal_of_Animal_Ecol.Rmd
@@
 always_allow_html: true
-bibliography: bibliography.bib
-biblio-style: apalike
-csl: JournalOfAnimalEcology.csl #converted from funct ecol style from zotero styles
 ---
-
-**Jose B. Lanuza^1,2^** \| **Alfonso Allen-Perkins^2,3^** \| **Ignasi Bartomeus^2^**
-
-1 School of Environmental and Rural Science, University of New England, Armidale, New South Wales 2350, Australia.
-
-2 Estación Biológica de Doñana (EBD-CSIC), E-41092 Seville, Spain.
-
-3 Departamento de Ingeniería Eléctrica, Electrónica, Automática y Física Aplicada, ETSIDI, Universidad Politécnica de Madrid, 28040 Madrid, Spain.
-
-\captionsetup[table]{labelformat=empty}
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
-
-# Abstract
-
-\singlespacing
-
-1.
-Ecological processes leave distinct structural imprints on the species interactions that shape the topology of animal-plant mutualistic networks.
-Detecting how direct and indirect interactions between animals and plants are organised is not trivial since they go beyond pairwise interactions, but may get blurred when considering global network descriptors.
-
-2.
-Recent work has shown that the meso-scale, the intermediate level of network complexity between the species and the global network, can capture this important information.
-The meso-scale describes network subgraphs representing patterns of direct and indirect interactions between a small number of species, and when these network subgraphs differ statistically from a benchmark, they are often referred to as "network motifs".
-Although motifs can capture relevant ecological information of species interactions, they remain overlooked in natural plant-pollinator networks.
-
-3.
-By exploring 60 empirical plant-pollinator networks from 18 different studies with wide geographical coverage, we show that some network subgraphs are consistently under- or over-represented, suggesting the presence of worldwide network motifs in plant-pollinator networks.
-In addition, we found a higher proportion of densely connected network subgraphs that, based on previous findings, could reflect that species relative abundances are the main driver shaping the structure of the meso-scale on plant-pollinator communities.
-Moreover, we found that distinct subgraph positions describing species ecological roles (e.g., generalisation and number of indirect interactions) are occupied by different groups of animal and plant species representing their main life-history strategies (i.e., functional groups).
-For instance, we found that the functional group of 'bees' was over-represented in subgraph positions with a lower number of indirect interactions in contrast to the rest of floral visitors groups.
-Finally, we show that the observed functional group combinations within a subgraph can not be retrieved from their expected probabilities (i.e., joint probability distributions), indicating that plant and floral visitor associations within subgraphs are not random either.
-
-4. Our results highlight the presence of common network motifs in plant-pollinator communities that are formed by a non-random association of plants and floral visitors functional groups.
-
-Keywords: pollinators, plant-pollinator networks, plant-pollinator interactions, network motifs, indirect interactions, floral visitors
-
-\doublespacing
-
-\newpage
-
-# Introduction
-
-Ecological communities are formed by a plethora of interacting species that form networks of interactions.
-Because of the tremendous complexity of these ecological networks, species interactions are generally condensed in metrics that summarise this information [@guimaraes2020].
-Plant-pollinator interactions are no exception, and they are often studied with indices that aggregate the information at the network (macro-scale) and species level (micro-scale).
-For example, plant-pollinator network level approaches have identified common invariant structural properties across mutualistic networks, including a degree distribution that decays as a truncated power law [@jordano1987], nestedness [@bascompte2003], or modularity [@olesen2007].
-In addition, the local species position within the network can define its degree of selectiveness [@bluthgen2006] or its role in connecting the rest of the community [@olesen2007].
-Despite the unquestionable progress with the use of these metrics at both network and species level, condensing complex information into a single metric implies the loss of relevant ecological information that obscures the understanding of species interactions [@cirtwill2018; @simmons2019].
-
-Indirect interactions, the mediated effect between two species by a third species, are ubiquitous in natural systems [@strauss1991; @holt1994; @wootton1994] and play a key role in shaping community dynamics [@werner2003; @walsh2013].
-Although some of the most studied indirect interactions are the ones caused by trophic cascades with consumer-resource interactions [@abrams1996; @schmitz2001; @finke2004], there is also a growing body of work that examines the consequences of indirect effects in mutualistic networks [@knight2005; @bastolla2009; @vieira2015; @guimaraes2017].
-Traditionally, the study of animal-plant mutualistic networks has commonly focused on direct interactions and overlooked indirect effects such as competitive or facilitative processes  between plants for pollinators [but see\, @bergamo2021; @moeller2004; @sargent2008; @carvalheiro2014].
-In part because conventional analytical tools in bipartite networks often discard relevant information about indirect interactions by condensing the information into single indices either at species or network level [@cirtwill2018; @simmons2019].
-However, as previously explored with three species modules in unipartite food webs [@allesina2008; @stouffer2010], the emergent framework of bipartite subgraphs has proven to be a powerful analytical tool to better understand plant-pollinator community dynamics by capturing both direct and indirect effects [@simmons2019].
-These network subgraphs that constitute the meso-scale are often referred to as the building blocks of the network and when their numbers occur at higher frequencies than in randomised networks, those are generally defined as 'network motifs' [@milo2002].
-Indeed, the analysis of motifs in simulated plant-pollinator networks has revealed that the different drivers that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect effects [@simmons2020].
-However, the global patterns of indirect interactions in real plant-pollinator networks and their ecological consequences remain unexplored (e.g., over- and under- represented network subgraphs).
-
-By linking the structural properties of the meso-scale with the species' ecology we can advance in our understanding on the determinants of species interactions.
-For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species' functional role [@stouffer2012; @baker2015; @cirtwill2018b].
-Yet, our understanding of the ecological implications of network motifs in real plant-pollinator networks remains in its infancy.
-Moreover, it is unclear how the species ecology and life-history traits determine its functional role within the network of interactions [@coux2016].
-For example, large pollinators can forage larger distances [@greenleaf2007], deposit greater pollen quantities [@foldesi2021] and handle complex zygomorphic flowers in comparison with small pollinators that are restricted to lower floral complexity [@gong2009].
-Despite these obvious differences in pollinator behaviour, how contrasting species' ecology translates into different network motifs is still poorly known.
-Similarly, recent empirical findings indicate that the meso-scale is the best descriptor of plant reproductive success [@allen2021], but little is known about how plants' reproductive strategies shape their position within the network of interactions.
-Although some studies have evaluated plant reproductive strategies in plant-pollinator networks [@tur2013; @lazaro2020], this is an often overlooked aspect in a community context [@devaux2014] and rarely incorporated into plant-pollinator network studies.
-Hence, exploring how the main plant and floral visitor life-history strategies integrate with the emergent framework of network motifs could help to progress knowledge on the ecological processes that shape plant-pollinator interactions.
-
-Here we evaluate the interaction patterns of the meso-scale and its ecological implications in plant-pollinator networks with the help of 60 empirical networks from 18 different studies distributed across 14 different countries.
-For this, plants and pollinators were divided into functional groups that summarise their main life-history strategies and the different networks were split into all their subgraph elements up to five nodes.
-First, based on previous knowledge showing the non random assembly of macro-scale mutualistic networks [@bascompte2003] and food webs [@dunne2002], we test the hypothesis that the building blocks that constitute the meso-scale in plant-pollinator networks have a non-random structure of interactions with over- and under-represented subgraphs (i.e., motifs) that represent contrasting ecological roles.
-Second, because species relative abundances (i.e., neutral effects) are one of the main drivers of network macro-struture [@krishna2008; @suweis2013; @bartomeus2016], we hypothesise that neutral effects may also govern the interaction patterns of the meso-scale in plant-pollinator networks.
-Finally, we explore if plants and pollinators functional groups are associated with subgraph positions that imply distinct ecological roles and if there are over- and under-represented functional group combinations within the different network subgraphs.
-
-# Methods
-
-**Overview**
-
-To investigate the structure of the meso-scale in plant-pollinator networks, we gathered published plant-pollinator networks with worldwide distribution.
-Then, we classified the different plant and floral visitor species from these networks into functional groups that summarise their main life-history strategies.
-We calculated the normalised subgraph frequencies and investigated if these frequencies are similar or not to the ones expected by chance with the help of null models.
-Then, for each group of plants and floral visitors we investigated the ecological implications of their overall representation on the different subgraph positions, by comparing, on the one hand, the observed (normalised) frequencies of each group in the different subgraph positions with the frequencies of their simulated counterparts, and, on the other hand, the differences among groups per subgraph position in terms of their number of indirect interactions and specialisation.
-Finally, to understand if the different functional group combinations within a subgraph are structured, we compare if the observed functional group combinations from empirical networks can be retrieved from the joint probability distribution of the expected frequencies of the different plant and floral visitor groups within network subgraphs.
-
-**Plant-pollinator studies**
-
-We have compiled 60 plant-pollinator networks from 18 different studies (Table S1).
-All studies sampled plant-pollinator interactions in natural systems in a single flowering season and were selected based on wide geographical coverage (Fig.
-S1) and presence of interaction frequency as a measure of interaction strength.
-In total, there were 503 plant species, 1,111 floral visitors species and 6,248 pairwise interactions registered.
-For ease of data manipulation, plant and floral visitor species names were standardised with the help of the R package *taxize* version *0.9.99* [@chamberlain2020].
-
-**Plant and floral visitor functional groups**
-
-First, plant species were grouped through hierarchical clustering into the optimal number of functional groups that summarises the main plant reproductive strategies.
-For this, we used the plant trait dataset compiled in @lanuza2021 that consisted also of plant species that belonged to the same plant-pollinator networks plus some additional meta-networks not considered here.
-This dataset comprised a total of 1,506 plant species including the 503 species considered in this study (Table S2).
-Because most of these plant species are likely to benefit from animal pollination, we used reproductive traits relevant to understand the different plant reproductive strategies and their interactions with pollinators.
-After excluding traits with a high percentage of missing values (over 30$\%$), we ended up with 8 floral, 3 reproductive biology and 3 plant morphology traits (see Table S3 for a list of all traits).
-Floral traits included those associated with the size, form and number of floral organs (e.g., style length or ovule number).
-Reproductive biology traits described the reproductive system of the plant (e.g., mating and compatibility systems) and plant morphology traits were associated with the size and form of the plant (i.e., plant height, lifespan and life form).
-After an extensive search for each plant species on several different resources (e.g., plant databases, online floras, books, journals and images), over 80% of the cells of the whole dataset were filled.
-Thus, to avoid the loss of species with trait missing values, missing trait data was imputed as detailed in @lanuza2021.
-
-We opted to calculate the plant functional groups within a larger set of species because of the higher accuracy when delimiting functional groups with that many variables and species [@dolnicar2014].
-To feed the clustering analysis, we calculated the distance between the different qualitative and scaled quantitative variables with Gower distance [@gower1971].
-For this, we used the function *gowdis* with method *ward.D2* from the *FD* package version *1.0-12* [@laliberte2014].
-Finally, we conducted hierarchical clustering with the function *hclust* from the *R* stats package version *4.0.5* and calculated the optimal number of clusters with the function *kgs* from the *maptree* package version *1.4-7* [@white2009].
-
-Second, floral visitors were aggregated into taxonomic groups (hereafter referred to as functional groups) based on taxonomic rank as done similarly in other plant-pollinator studies [@fenster2004; @ollerton2009].
-We opted to divide floral visitors on the taxonomic rank level and not with functional traits because the main orders of floral visitors differed in form and behaviour and had lower superior taxonomic complexity (i.e., floral visitors had 6 orders versus plants that had 38).
-Thus, this allowed us to group floral visitors into functional groups that represented approximately the main life-history strategies of the possible pollinators: (i) bees (Hymenoptera-Anthophila), (ii) non-bee Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Syrphidae-Diptera), (iv) non-syrphids-Diptera, (v) Lepidoptera and (vi) Coleoptera.
-However, a minor set of species belonged to other functional groups that were considered in analyses but not discussed further because of their low representation in the full set of networks (3.55$\%$ of the total interactions recorded).
-These taxonomic groups were 'lizards', 'birds' and 'other insects'.
-This last functional group was formed by a mix of uncommon insect taxa on the full set of networks.
-
-**Overall network subgraphs patterns**
-
-Following previous work [@simmons2019; @simmons2020], we broke down the plant-pollinator networks into their constituent network subgraphs that can capture both direct and indirect interactions.
-Prior to analyses, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.
-This approach was preferred since quantitative subgraph analyses have been developed just recently and more work is needed to fully understand and interpret the information that they can convey [@simmons2020].
-All analyses were run considering singletons (species with only one interaction detected) but we conducted a second exploration without singletons (64.98$\%$ of interactions) to evaluate the effect of rare species on the observed patterns.
-Results without singletons are qualitatively consistent and are not further discussed in the main text (Figs S2 and S3).
-
-We calculated the frequency of all subgraphs up to five nodes (17 different subgraphs in total; see Fig.
-1) for each empirical network, by using the *bmotif* package version *2.0.2* [@bmotifsimmons2019].
-We focused exclusively on subgraphs up to five nodes in our analyses for computational reasons and for the ease of visualization and interpretation of a reduced set of less complex network structures.
-Throughout the entire manuscript, floral visitors occupy the top nodes of the different network subgraphs and plants the bottom ones.
-To control for variation in network size, subgraph frequencies were normalised as a proportion of the total number of subgraphs within each subgraph class (i.e., 2-species, 3-species, 4-species and 5-species network subgraphs).
-In addition, we excluded 2-species (or 2-nodes) subgraphs from our analyses because its normalised frequencies would always equal one.
-Note that the aim is not comparing different networks, which may differ in sampling effort, but correctly describing the structure of each individual network.
-Like @simmons2020, we classified the different subgraphs by their average path length (mean number of links between all pairs of nodes) into four different groups: (i) complete or strong ($\overline{x} = 1.38$), (ii) fan or medium-strong ($\overline{x} = 1.48$), (iii) assymmetric complete or medium-weak ($\overline{x} = 1.60$) and (iv) core-peripheral or weak ($\overline{x} = 1.85$), where $\overline{x}$ represents the mean of the average path length across subgraphs within the same group.
-In general terms, plant and floral visitor groups on more densely connected network subgraphs (e.g., complete or fan) will experience lower number of indirect interactions in contrast to groups on less densely connected structures (e.g., medium-weak or weak).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, fig.pos="t", warning=FALSE,out.width="75%",fig.align="center", fig.cap="\\textbf{Figure 1.} Adapted figure of Simmons et al., (2019).
-All possible network subgraphs from two to five species in bipartite networks grouped by the different subgraph classes (2-species, 3-species, 4-species and 5-species).
-There are a total of 17 possible subgraphs with 46 different positions denoted within each node.
-The different subgraphs are aggregated by the broad indirect interaction structures they represent on four different groups (strong, medium-strong, medium-weak and weak).
-For each group, we show in the legend the mean value of the average path length of all subgraphs within it.
-The different path length groups range from densely connected network structures (strong subgraphs where all possible interactions are realised and the mean path length is minimum) to weakly connected ones (weak subgraphs where the mean path length is maximum).", fig.width=10,fig.height=8}
-library(tidyverse)
-library(RColorBrewer)
-source("../../Scripts/Scripts_Alfonso/plot_motif_positionsV2.R")
-
-motif_number <- 1
-p1 <- plot_motif_positions(motif_number) +
-geom_point(aes(color = as.factor(label)),size=10,color = "grey90")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 2
-p2 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 3
-p3 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 4
-p4 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 5
-p5 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "lightcoral")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 6
-p6 <- plot_motif_positions(motif_number) +
-geom_point(aes(color = as.factor(label)),size=10,color = "goldenrod2")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 7
-p7 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 8   
-p8 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 9
-p9 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "lightcoral")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 10
-p10 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "lightcoral")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 11
-p11 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "skyblue")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 12
-p12 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "goldenrod2")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 13
-p13 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "lightcoral")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 14
-p14 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "lightcoral")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 15
-p15 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "skyblue")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 16
-p16 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "goldenrod2")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 17
-p17 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
-geom_text(aes(x, y , label = label),size=3)
-
-library(patchwork)
-
-p <- (p1 & ylab("2 species")| p2 & ylab("3 species") | p3 ) /
-(p4 & ylab("4 species")| p5 | p6 | p7) / 
-(p8  & ylab("5 species")| p9 | p10 | p11 | p12) /
-(p13 & ylab("5 species")| p14 | p15 | p16 | p17) &
-theme(axis.title.y = element_text(color="black", size=14, face="bold"))
-
-#Create custom legend
-a <- c(1,2,3,4)
-b <- c(1,2,3,4)
-c <- c("a","b", "c", "d")
-abc <- data.frame(a,b,c)
-p1 <- ggplot(abc, aes(x=a,y=b, color=c))+geom_point() + theme_bw() + 
-  scale_colour_manual(name = 'Path length classification', 
-                      values =c(a= 'goldenrod2',b='mediumaquamarine',
-                                c='skyblue', d='lightcoral'), 
-                      labels = c(a='Strong \n mean path length = 1.38', 
-                                 b='Medium-strong \n mean path length = 1.48',
-                                 c='Medium-weak \n mean path length = 1.60',
-                                 d='Weak \n mean path length = 1.85'))+
-theme(legend.position="bottom")+ guides(colour = guide_legend(override.aes = list(size=8),title.position="top", title.hjust = 0.5))
-
-legend <- cowplot::get_legend(p1+ theme(legend.position = "bottom",legend.text = element_text(size=10), legend.title = element_text(size=12, 
-face="bold"),legend.box.background = element_rect(color="black", size=2)))
-
-cowplot::plot_grid(p, legend, ncol = 1, rel_heights = c(12, 1.8))
-
-```
-
-To assess the significance of the observed frequencies, we created 1,000 simulated networks for each binary network using the *nullmodel* function and the *vaznull* model in the *bipartite* package version *2.14* [@dormann2009].
-Generated networks had the same number of plants and floral visitors, as well as the same connectance of their corresponding empirical networks.
-We discarded null models with more constraints (e.g., constraining for species degree) because the permutations did not generate sufficient variability and provided highly similar or identical networks to the original ones.
-After extracting the subgraph frequencies from the simulated networks, for each subgraph type and empirical network, we calculated the percentage of simulated networks whose frequencies were smaller than the ones observed, that is, we estimated the percentile of the observed subgraph frequencies.
-Subgraphs whose percentile is close to 0 or 100 are under- or over-represented in empirical networks, respectively, and indicate the presence of network motifs as they differ statistically from the network structures generated with simulated networks.
-To summarise general patterns across networks, we used an intercept-only linear mixed model (LMM) per subgraph with the help of the *lme4* package version *1.1-21* [@bates2015], where the response variable was the observed subgraph percentile per network.
-Note that as we are only interested in modelling the intercept value, no predictors were specified.
-In these models, we used the study identifiers in Table S1 as a random intercept.
-By doing so, we obtained estimates of the average subgraph frequency, but controlling for the variation at the study level.
-
-**Over- and under-represented functional groups on subgraph positions**
-
-We calculated which plant and floral visitor functional groups were over- or under-represented in the different subgraph positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
-To estimate the position frequencies of each plant and floral visitor group in a given network, we added the frequencies of those species that belong to the same group, and then, we normalised the resulting frequencies by dividing them by the total number of times that a corresponding group appears in any position within the same subgraph size class.
-Then, we calculated the percentile of the observed position frequencies for each functional group and network, just like we did with subgraph frequencies.
-To outline the general patterns of position frequencies across networks and groups, we fit a LMM per subgraph position, where the response variable was the observed position percentile per network.
-We used the group identifier as an explanatory variable and the study identifiers as a random intercept.
-Hence, we assessed the average subgraph frequency per species group, after controlling for the variation at the study level.
-Finally, we visualised over- and under-representation of plant and floral visitor groups on the different subgraph positions with the help of the *ComplexHeatmap* package version *2.6.2* [@gu2016].
-
-To understand if the different plant and floral visitor functional groups are associated with subgraph positions that represent different network roles, we characterised the roles of each subgraph position for the different functional groups in terms of their specialisation and number of indirect interactions.
-To that end, we calculated the specificity of each subgraph position following @poisot2015 as $s_i = (L - l_i) / (L - 1)$, where $L$ is the total number of groups and $l_i$ the number of interaction partners of the group $i$ in a given subgraph.
-Values of the vector $si$, range between 1, complete specialisation (1 partner within the subgraph) and 0 complete generalism (all possible partners within the subgraph).
-Then, because all nodes within a motif are connected, we calculated the number of indirect interactions ($\theta_i$) for each motif position as $\theta_i=m_i-k_i-1$, where $m_i$ is the total number of nodes in a given motif, and $k_i$ represents the degree of the corresponding motif position, that is, the total number of links connected to such position.
-Thus, we considered all possible indirect interactions for each position.
-Finally, we analysed in a single model how specialisation and the number of indirect interactions were associated with the observed percentiles for each trophic guild and subgraph position.
-For this, we fitted again a LMM model with the help of the *lme4* package, where we considered specialisation and number of indirect interactions as response variables with the interaction by plant and floral visitor group for both response variables.
-Further, we considered as random factor subgraph position nested within study system.
-
-**Over- and under-represented functional group combinations of subgraphs**
-
-Finally, we studied which combinations of plant and floral visitor functional groups tend to appear together within the same subgraphs (up to five nodes).
-That is, which combinations are over- or under-represented.
-This analysis used 57 out of the 60 networks available due to computational limitations to identify all the nodes in the subgraphs of the three networks with the highest number of links.
-To do so, for each of the 53,250 possible subgraph combinations, we estimated the observed and the expected probability of finding those combinations in empirical networks, respectively.
-Then, we determined whether the observed probabilities are likely to come from the expected probabilities or not.
-To calculate the observed probability ($p_i^O$) of the different groups within a subgraph $i$ (e.g., subgraph 3, 'bee' + 'bee' + 'selfing herbs'), we divided the number of times that $i$ appears in our set of empirical networks ($n_i^O$) by the sum of the number of times that each possible combination appeared: $p_i^O = n_i^O / \sum_{k=1}^{53,250} n_k^O$.
-To estimate the expected probability ($p_i^E$) of a given subgraph combination $i$, we assumed that the probability of finding a given functional group $x$ in the position $\alpha$ is independent of the probabilities associated with other positions and groups in that subgraph.
-Therefore, the expected probability ($p_i^E$) of the subgraph combination $i$ is given by the product of the probabilities of its constituents, i.e., $p_i^E = \prod _{(x,\alpha )\in i} p_i(x,\alpha)$, where $p_i(x,\alpha)$ is the probability of finding a given functional group $x$ in the position $\alpha$ of $i$.
-Then, by controlling for the variation at the network level with an LMM (see below), we calculated the average number of times that the functional group $x$ appears in the position $\alpha$ (denoted as $n_i(x,\alpha)$).
-To obtain the expected probability $p_i(x,\alpha)$, we divided the number of times that the group $x$ appears in the position $\alpha$ by the the total number of times that any group was observed in that position (that is, $p_i(x,\alpha) = n_i(x,\alpha)/\sum_{k}n_i(k,\alpha)$).
-The average number of times that the group $x$ appears in the position $\alpha$ ($n_i(x,\alpha)$) was calculated with a LMM for each position, where the response variable was the number of times that a group was observed at a given position in each real-world network, the explanatory variable was the group identifier, and the random intercept was given by network identifiers nested within the study identifiers.
-
-Once we obtained $p_i^O$ and $p_i^E$, we used a simulation approach to determine whether the former is likely to come from the latter or not.
-This approach was preferred since the large number of possible subgraph combinations and the small probabilities for some of them advise against using an exact test of goodness-of-fit or a Chi-square one.
-Specifically, we created 1,000 random samples with repetition of possible subgraph combinations, where each sample contained 10 million elements and, for each combination, the probability of being selected was equal to its expected probability.
-From those random samples, we extracted the mean and the standard deviation of the expected probability of $i$, denoted as $E\left [ p_i^E \right ]$ and $\sigma\left [ p_i^E \right ]$, respectively, and calculated the z-scores of $p_i^O$ as $z_i^O = \left ( p_i^O - E\left [ p_i^E \right ] \right )/\sigma \left [ p_i^E \right ]$, for those motif combinations with $p_i^O > 0$.
-According to the usual interpretation of z-scores, combinations with $z_i^O > 1.96$ are over-represented, whereas those with $z_i^O < -1.96$ are under-represented, at the 95$\%$ confidence level.
-Notice that we focused on combinations with $p_i^O > 10^{-7}$ because we do not have enough numerical resolution to accurately detect whether combinations that took place only once are under-represented (due to the limited size of our random samples).
-
-All analyses and data manipulation were conducted in R *version 4.0.5* [@R].
-In addition, all model diagnostics were conducted with the help of the *Dharma* package [@hartig2017] version *0.3.3.0* and model outputs were visualised with the *visreg* package [@breheny2020] version 2.7.0.
-
-# RESULTS
-
-**Plant and floral visitor functional groups**
-
-The hierarchical cluster analysis divided the dataset into five different plant functional groups with different and overlapping characteristics (Figs S4 and S5).
-The first group referred to as 'selfing herbs' consisted of herbs with hermaphroditic flowers with high levels of autonomous selfing.
-The second group named 'small outcrossing perennials' had small perennial species with a mix of life forms (i.e., trees, shrubs and herbs) with outcrossing hermaphroditic flowers.
-The third group referred to as 'self-incompatible perennials with large flowers' comprised perennial species with a mixed of life forms and large self-incompatible hermaphroditic flowers with high number of ovules.
-The fourth group named 'tall plants with small unisexual flowers' had the tallest species, highest proportion of shrub and tree life forms, dioecious and monoecious breeding systems, small flowers, and the highest numbers of flowers and inflorescences per plant.
-Finally, the fifth group named 'short-lived outcrossers with long zygomorphic flowers' consisted of small perennial and short-lived herbs with long self-compatible zygomorphic flowers that were unable to self-pollinate.
-
-In total, there were 1,126 species of floral visitors with 6,325 interactions recorded with plants.
-Most plants interacted with bees (2,256 interactions) and non-syrphid Diptera (1,768) followed by syrphids (845), Lepidoptera (437), Coleoptera (432) and non-bee Hymenoptera (362).
-
-**Overall network subgraphs patterns**
-
-Most network subgraphs were under- or over-represented (close to the 1st and 99th percentile, respectively) in the comparison between empirical and simulated networks (Fig.
-2).
-Network subgraphs 3, 5, 9, 10 and 14 were under-represented in empirical networks, that is, all were close to the 1st percentile and under the 25th percentile.
-Interestingly, four out of five of these motifs belonged to the largest path length classification (i.e., core-peripheral).
-In addition, network subgraphs 2, 6, 7, 16 and 17 were over-represented, all over the 75th percentile.
-In contrast to the under-represented network subgraphs, over-represented subgraphs belonged to the two shortest path length groups (i.e., complete and fan).
-The remaining network subgraphs (i.e., 4, 8, 11, 12, 13, and 15) were between the 25th and 75th percentile.
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure 2.** Comparison of network subgraph frequencies between empirical and simulated networks grouped by average path length (plots a, b, c and d) where $\\overline{x}$ indicates the mean of the average path lengths of all subgraphs within each group (strong, medium-strong, medium-weak and weak).
-This comparison is shown with the mean percentage of subgraph frequencies in empirical networks that were over the subgraph frequencies of the simulated ones (percentiles).
-This was done by network (light blue transparent dots) and then averaged for all networks (black dots with error bars that correspond to the standard deviation)."}
-
-library(lme4)
-library(nlme)
-library(tidyverse)
-source("../../Scripts/Scripts_Alfonso/add_study_id.R")
-d <- read_csv("../../Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
-d <- add_study_id(d)
-#str(d)
-#head(d)
-
-#ggplot(d %>% filter(motif != 1), aes(percentil_sizeclass))+
-#  geom_histogram(color="black", fill="white")+
-#  facet_wrap(~motif)+
-#  theme_bw()+
-#  labs(x="Sizeclass percentile")
-#
-# Motifs tend to be over- and under-represensented in real networks
-
-# Mean percentile and SE taking into account the study system
-motif_codes <- d %>% filter(motif != 1) %>% # We remove links (motif code: 1)
-  select(motif) %>% unique() %>% pull()
-motif_means <- tibble(motif = motif_codes)
-motif_means$mean <- NA
-motif_means$SE <- NA
-
-for(i.motif in 1:length(motif_codes)){
-
-  m <- lmer(percentil_sizeclass ~ 1+(1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = subset(d, motif == motif_codes[i.motif]))
-
-  motif_means$mean[i.motif] <- fixed.effects(m) %>% unname()
-  motif_means$SE[i.motif] <- sqrt(diag(vcov(m)))
-
-}
-
-#Add categories based on path length set by Simmons 2021 et al., Functional Ecology
-d$Broad_categories[d$motif==2 | d$motif==7 | d$motif==17 | d$motif==3|d$motif==4|d$motif==8] <- "Fan"
-
-d$Broad_categories[d$motif==15 | d$motif==11] <- "Medium-weak"
-
-d$Broad_categories[d$motif==6 | d$motif==16 |  d$motif==12] <- "Strong"
-
-d$Broad_categories[d$motif==5 | d$motif==9 |  d$motif==14|  d$motif==13|  d$motif==10] <- "Weak"
-
-#order the categories from short to long path length
-d$Broad_categories <- factor(d$Broad_categories, levels = c("Strong", "Fan", "Medium-weak", "Weak"))
-
-#Ffilter out two node motifs
-d_1 <- d %>% filter(motif != 1)
-#Merge dataframes to bl able to create facets
-d_2 <- merge(d_1, motif_means, by="motif")
-
-arr <- list('Strong' = expression(bold(paste("(a) Strong (Complete, ", bar(x), " = 1.38)"))),
-             'Fan' = expression(bold(paste("(b) Medium-strong (fan, ", bar(x), " = 1.48)"))), 
-             'Medium-weak' = expression(bold(paste("(c) Medium-weak (asymmetric complete, ", bar(x), " = 1.60)"))), 
-             "Weak" =expression(bold(paste("(d) Weak (core-peripheral, ", bar(x), " = 1.85)"))))
-mylabel <- function(val) { return(lapply(val, function(x) arr[x])) }
-
-library(ggforce) #workaround with ggforce to have facets with same sizes 
-library(ggtext)
-
-labels <- c("2" = "*Subgraph 2* <img src='../../Images/motif_2.png' width='22'/>" ,
-          "3"= "*Subgraph 3* <img src='../../Images/motif_3.png' width='22'/>",
-          "4"= "*Subgraph 4* <img src='../../Images/motif_4.png' width='22'/>",
-          "5"= "*Subgraph 5* <img src='../../Images/motif_5.png' width='22'/>",
-          "6"= "*Subgraph 6* <img src='../../Images/motif_6.png' width='22'/>",
-          "7"= "*Subgraph 7* <img src='../../Images/motif_7.png' width='22'/>",
-          "8"= "*Subgraph 8* <img src='../../Images/motif_8.png' width='22'/>",
-          "9"= "*Subgraph 9* <img src='../../Images/motif_9.png' width='22'/>",
-          "10"= "*Subgraph 10* <img src='../../Images/motif_10.png' width='22'/>",
-          "11"= "*Subgraph 11* <img src='../../Images/motif_11.png' width='22'/>",
-          "12"= "*Subgraph 12* <img src='../../Images/motif_12.png' width='22'/>",
-          "13"= "*Subgraph 13* <img src='../../Images/motif_13.png' width='22'/>",
-          "14"= "*Subgraph 14* <img src='../../Images/motif_14.png' width='22'/>",
-          "15"= "*Subgraph 15* <img src='../../Images/motif_15.png' width='22'/>",
-          "16"= "*Subgraph 16* <img src='../../Images/motif_16.png' width='22'/>",
-          "17"= "*Subgraph 17* <img src='../../Images/motif_17.png' width='22'/>")
-
-p <- ggplot()+geom_point(data = d_2 , aes(y=factor(motif), 100*percentil_sizeclass), shape=21,color="black",fill="azure2",size=1.75, alpha=0.3)+
-  geom_errorbar(data = d_2,aes(y = factor(motif), xmin=100*(mean-SE), xmax=100*(mean+SE)), 
-                width=0.8,size=0.8,color="black") +theme_bw()+
-  geom_point(data = d_2,aes(y = as.factor(motif), x=100*mean), 
-             size=2,color="black")+labs(y="Two to five node motifs", x = "Percentile")+
-  theme( strip.background = element_blank())+
-  theme(strip.text = element_text(face="bold", size=10, hjust=0),
-        panel.border=element_rect(color="black",size=1.2))+
-  scale_y_discrete(name = NULL,
-                   labels = labels) +
-  theme(axis.text.y = ggtext::element_markdown())
-
-p + ggforce::facet_col(vars(Broad_categories), scales = 'free', space = 'free',labeller=mylabel)
-
-#Trying to maintain a gradient from low to high in colors
-
-#Fig 1 Should be a dot plot (or forest plot) of the mean +- SE of the 15 motifs.
-#NICE! Can we put motifs in Y axes, and % in X?
-```
-
-**Over- and under-represented functional groups on subgraph positions**
-
-```{r , include=FALSE}
-
-#SAME SCRIPT AS THE PLOTTING FOR THE HEATMAP BUT I NEED IT HERE TO LOAD THE VARIABLES WITH VALUES ON RESULTS
-
-library(lme4)
-library(nlme)
-library(tidyverse)
-library(stringi)
-source("../../Scripts/Scripts_Alfonso/add_study_id.R")
-
-#############################################
-# EXTRACT MEAN VALUES
-#############################################
-all_position_percentiles <- read_csv("../../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
-
-all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
-                                                              "[0-9]+") %>% as.numeric()
-
-all_position_percentiles <- add_study_id(all_position_percentiles)
-#str(all_position_percentiles)
-#head(all_position_percentiles)
-
-list_plants_FG <- as.character(1:10)
-
-plant_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF)) #ME DA ERROR
-pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF))
-
-# Plants-------------
-
-# Mean percentile and SE taking into account the study system
-plant_codes <- plant_position_percentiles_filtered$position %>% unique()
-plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-plant_means$mean <- NA
-plant_means$SE <- NA
-
-for(i.pos in 1:length(plant_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
-            data = plant_position_percentiles_filtered %>%
-              filter(position == plant_codes[i.pos]))
-
-  temp <- fixed.effects(m) %>% unname()
-  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
-                                                                    temp[1]+temp[2],
-                                                                    temp[1]+temp[3],
-                                                                    temp[1]+temp[4],
-                                                                    temp[1]+temp[5]) ## to get real means per FG
-  temp <- sqrt(diag(vcov(m)))
-  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
-                                                                  temp[1]+temp[2],
-                                                                  temp[1]+temp[3],
-                                                                  temp[1]+temp[4],
-                                                                  temp[1]+temp[5])
-
-}
-
-# Pollinators--------
-
-# Mean percentile and SE taking into account the study system
-pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
-pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-pollinator_means$mean <- NA
-pollinator_means$SE <- NA
-pollinator_means_reordered <- NULL
-
-for(i.pos in 1:length(pollinator_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = pollinator_position_percentiles_filtered %>%
-              filter(position == pollinator_codes[i.pos]),
-            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
-
-  temp <- fixed.effects(m) %>% unname()
-  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)
-
-  pollinator_means_aux$mean <- c(temp[1],
-                                 temp[1]+temp[2],
-                                 temp[1]+temp[3],
-                                 temp[1]+temp[4],
-                                 temp[1]+temp[5],
-                                 temp[1]+temp[6],
-                                 temp[1]+temp[7],
-                                 temp[1]+temp[8],
-                                 temp[1]+temp[9]) ## to get real means per FG
-
-  temp <- sqrt(diag(vcov(m)))
-  pollinator_means_aux$SE <- c(temp[1],
-                               temp[1]+temp[2],
-                               temp[1]+temp[3],
-                               temp[1]+temp[4],
-                               temp[1]+temp[5],
-                               temp[1]+temp[6],
-                               temp[1]+temp[7],
-                               temp[1]+temp[8],
-                               temp[1]+temp[9])
-
-  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)
-
-}
-
-# There are lower limits (mean - SE) smaller than 0 (see Other insects)
-# We set the lower limit of those error bars to zero
-
-pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
-pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
-
-#############################################
-# ADDING BROAD MOTIF CATEGORIES TO POSITIONS
-#############################################
-
-motifs_raw_data <- read_csv("../../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-motifs_raw_data$Broad_categories <- NA
-
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(5,9,14,13,10)] <- "Core-peripherical"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(6,16,12)] <- "Complete"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(2,3,7,4,17,8)] <- "Fan"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(15,11)] <- "Asymmetric complete"
-
-motifs_raw_data$plant <- gsub("[^0-9.-]", "", motifs_raw_data$plant)
-motifs_raw_data$pollinator <- gsub("[^0-9.-]", "", motifs_raw_data$pollinator)
-motifs_raw_data$plant <- as.numeric(motifs_raw_data$plant)
-motifs_raw_data$pollinator <- as.numeric(motifs_raw_data$pollinator)
-motifs_raw_data <- motifs_raw_data %>% filter(!is.na(Broad_categories))
-
-fan_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-pollinator_means_reordered$Broad_categories <- NA
-
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% fan_pollinator] <- "Fan" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% asymm_pollinator] <- "Medium-weak" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% complete_pollinator] <- "Strong" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% core_per_pollinator] <- "Weak"
-
-fan_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-plant_means$Broad_categories <- NA
-
-plant_means$Broad_categories[plant_means$position %in% fan_plant] <- "Fan" 
-plant_means$Broad_categories[plant_means$position %in% asymm_plant] <- "Medium-weak" 
-plant_means$Broad_categories[plant_means$position %in% complete_plant] <- "Strong" 
-plant_means$Broad_categories[plant_means$position %in% core_per_plant] <- "Weak"
-
-################################################################################
-# Alternative code to HEATMAPS to create variables with values to load on text
-# in a reproducible/automated way
-################################################################################
-
-# PLANTS-----
-
-# Prepare data for heatmap
-heat_plants_aux <- plant_means %>% spread(Node_FG,mean) %>% select(-SE)
-
-heat_plants <- heat_plants_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-# POLLINATORS-----------
-
-filter_rare_groups <- T
-
-if(filter_rare_groups == T){
-  heat_pollinators_aux <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds",
-                                                                                "Lizards",
-                                                                                "Other_insects")) %>% 
-    spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees",            
-                                      "Coleoptera","Lepidoptera","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Syrphids")
-}else{
-  heat_pollinators_aux <- pollinator_means_reordered %>% spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees","Birds",            
-                                      "Coleoptera","Lepidoptera","Lizards","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Other insects","Syrphids")
-}
-
-heat_pollinators <- heat_pollinators_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))
-
-#Check percentage of over and under represented
-colMeans(heat_pollinators[,c(3:8)] < 0.25)
-poll_under_25 <- colMeans(heat_pollinators[,c(3:8)] < 0.25)
-poll_under_25 <- specify_decimal((poll_under_25[[1]] + poll_under_25[[2]] + poll_under_25[[3]] +
-poll_under_25[[4]] + poll_under_25[[5]] + poll_under_25[[6]])/6*100,2)
-#[1] 32.57576
-
-colMeans(heat_pollinators[,c(3:8)] > 0.75)
-poll_over_75 <- colMeans(heat_pollinators[,c(3:8)] > 0.75)
-poll_over_75 <- specify_decimal((poll_over_75[[1]] + poll_over_75[[2]] + poll_over_75[[3]] +
-    poll_over_75[[4]] + poll_over_75[[5]] + poll_over_75[[6]])/6*100,2)
-#[1] 4.545455
-
-#################################################################################
-#################################################################################
-
-colnames(heat_plants)<- c("position", "Broad_categories", "one",
-                               "two", "three","four",
-                               "five")
-f <- heat_plants %>%
-  mutate(min = pmin(1,
-                    one, two,three,
-                    four, five))%>%
-  mutate(max = pmax(one,
-                    two, three,four,
-                    five))
-
-diff_1 <- f$max-f$min
-
-cbind(diff,diff_1)
-
-#Check percentage of over and under represented per FG
-colMeans(heat_plants[,c(3:7)] < 0.25)
-plant_under_25 <- colMeans(heat_plants[,c(3:7)] < 0.25)
-plant_under_25 <- specify_decimal((plant_under_25[[1]] + plant_under_25[[2]] + plant_under_25[[3]] + 
-    plant_under_25[[4]] + plant_under_25[[5]])/5*100,2)
-#[1] 18.18182
-colMeans(heat_plants[,c(3:7)] > 0.75)
-plant_over_75 <- colMeans(heat_plants[,c(3:7)] > 0.75)
-plant_over_75 <- specify_decimal((plant_over_75[[1]] + plant_over_75[[2]] + plant_over_75[[3]] + 
-    plant_over_75[[4]] + plant_over_75[[5]])/5*100,2)
-#[1] 8.181818
-
-#overall percentages
-under <- specify_decimal((as.numeric(poll_under_25) + as.numeric(plant_under_25))/2,2)
-over <- specify_decimal((as.numeric(poll_over_75) + as.numeric(plant_over_75))/2,2)
-
-```
-
-The comparison of the plant and floral visitor functional group frequencies per subgraph position between empirical and simulated networks showed a `r over`$\%$ and `r under`$\%$ of over- (>75$^{th}$) and under-represented (\<25th) functional groups in the different positions, respectively (Fig.
-3).
-Floral visitors showed a total of `r poll_over_75`$\%$ and `r poll_under_25`$\%$ of over- and under-represented functional groups in the different positions, and plants `r plant_over_75`$\%$ and `r plant_under_25`$\%$ of over- and under-represented functional groups, respectively.
-Notably, the differences across functional groups were more marked for floral visitors than for plants (the differences between the minimum and maximum values of the percentiles per position were generally two-three times larger for floral visitors).
-From most over- to under-represented floral visitors functional groups on the different subgraph positions (indicated with the dendrogram order in Fig.
-3), we found: bees, non-syrphids Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.
-Although plant functional groups showed less differences between them, there were also more represented functional groups than others.
-Thus, from most over- to under-represented functional groups on the different subgraph positions we found: self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.
-
-For both floral visitor and plant functional groups we found over- and under-representation on different subgraph positions that implied different ecological roles.
-First, for floral visitors, we found that bees were less frequent on subgraph positions that involved specialisation (i.e., lower specificity values) while the rest of functional groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) were infrequent in generalised subgraph positions with low number of indirect interactions (Fig.
-S6 A).
-Although plants did not show differences with null models on their frequencies, all plant functional groups but tall plants with small unisexual flowers showed a slight tendency to be over-represented on specialised subgraph positions (Fig.
-S6 B).
-Second, regarding the number of indirect interactions, bees were over-represented in subgraph positions with low number of indirect interactions (Fig.
-S7 A) and the rest of floral visitor functional groups showed no differences across positions in comparison with simulated networks.
-For plants, all functional groups showed a slight tendency to be over-represented on subgraph positions with higher number of indirect interactions (Fig.
-S7 B).
-When we further explore the observed frequencies by number of indirect interactions for floral visitor and plant functional groups, we found that both bees and tall plants with small unisexual flowers were the only functional groups with high frequencies on subgraph positions associated with low number of indirect interactions in comparison with the other floral visitor and plant functional groups (Figs S8 and S9).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', out.width="80%",fig.cap="\\textbf{Figure 3.} Heatmap indicating under- and over-representation of floral visitor and plant functional groups in the different subgraph positions (numbers on the right of each heatmap).
-The different subgraph positions are dividied by the average path length clasification determined by Simmons et al.
-(2020) and they are ordered from the most densely connected network structures (strong or complete) to the less connected ones (weak or core-peripheral).
-The superior dendrogram indicates the differences across functional groups with the more separated groups showing larger differences."}
-
-library(lme4)
-library(nlme)
-library(tidyverse)
-library(stringi)
-source("../../Scripts/Scripts_Alfonso/add_study_id.R")
-
-#############################################
-# EXTRACT MEAN VALUES
-#############################################
-
-all_position_percentiles <- read_csv("../../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
-
-all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
-                                                              "[0-9]+") %>% as.numeric()
-
-all_position_percentiles <- add_study_id(all_position_percentiles)
-#str(all_position_percentiles)
-#head(all_position_percentiles)
-
-list_plants_FG <- as.character(1:10)
-
-plant_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF)) #ME DA ERROR
-pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF))
-
-# Plants-------------
-
-# Mean percentile and SE taking into account the study system
-plant_codes <- plant_position_percentiles_filtered$position %>% unique()
-plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-plant_means$mean <- NA
-plant_means$SE <- NA
-
-for(i.pos in 1:length(plant_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
-            data = plant_position_percentiles_filtered %>%
-              filter(position == plant_codes[i.pos]))
-
-  temp <- fixed.effects(m) %>% unname()
-  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
-                                                                    temp[1]+temp[2],
-                                                                    temp[1]+temp[3],
-                                                                    temp[1]+temp[4],
-                                                                    temp[1]+temp[5]) ## to get real means per FG
-  temp <- sqrt(diag(vcov(m)))
-  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
-                                                                  temp[1]+temp[2],
-                                                                  temp[1]+temp[3],
-                                                                  temp[1]+temp[4],
-                                                                  temp[1]+temp[5])
-
-}
-
-# Pollinators--------
-
-# Mean percentile and SE taking into account the study system
-pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
-pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-pollinator_means$mean <- NA
-pollinator_means$SE <- NA
-pollinator_means_reordered <- NULL
-
-for(i.pos in 1:length(pollinator_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = pollinator_position_percentiles_filtered %>%
-              filter(position == pollinator_codes[i.pos]),
-            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
-
-  temp <- fixed.effects(m) %>% unname()
-  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)
-
-  pollinator_means_aux$mean <- c(temp[1],
-                                 temp[1]+temp[2],
-                                 temp[1]+temp[3],
-                                 temp[1]+temp[4],
-                                 temp[1]+temp[5],
-                                 temp[1]+temp[6],
-                                 temp[1]+temp[7],
-                                 temp[1]+temp[8],
-                                 temp[1]+temp[9]) ## to get real means per FG
-
-  temp <- sqrt(diag(vcov(m)))
-  pollinator_means_aux$SE <- c(temp[1],
-                               temp[1]+temp[2],
-                               temp[1]+temp[3],
-                               temp[1]+temp[4],
-                               temp[1]+temp[5],
-                               temp[1]+temp[6],
-                               temp[1]+temp[7],
-                               temp[1]+temp[8],
-                               temp[1]+temp[9])
-
-  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)
-
-}
-
-# There are lower limits (mean - SE) smaller than 0 (see Other insects)
-# We set the lower limit of those error bars to zero
-
-pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
-pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
-
-#############################################
-# ADDING BROAD MOTIF CATEGORIES TO POSITIONS
-#############################################
-
-motifs_raw_data <- read_csv("../../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-motifs_raw_data$Broad_categories <- NA
-
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(5,9,14,13,10)] <- "Core-peripherical"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(6,16,12)] <- "Complete"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(2,3,7,4,17,8)] <- "Fan"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(15,11)] <- "Asymmetric complete"
-
-motifs_raw_data$plant <- gsub("[^0-9.-]", "", motifs_raw_data$plant)
-motifs_raw_data$pollinator <- gsub("[^0-9.-]", "", motifs_raw_data$pollinator)
-motifs_raw_data$plant <- as.numeric(motifs_raw_data$plant)
-motifs_raw_data$pollinator <- as.numeric(motifs_raw_data$pollinator)
-motifs_raw_data <- motifs_raw_data %>% filter(!is.na(Broad_categories))
-
-fan_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-pollinator_means_reordered$Broad_categories <- NA
-
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% fan_pollinator] <- "Fan" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% asymm_pollinator] <- "Medium-weak" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% complete_pollinator] <- "Strong" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% core_per_pollinator] <- "Weak"
-
-fan_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-plant_means$Broad_categories <- NA
-
-plant_means$Broad_categories[plant_means$position %in% fan_plant] <- "Fan" 
-plant_means$Broad_categories[plant_means$position %in% asymm_plant] <- "Medium-weak" 
-plant_means$Broad_categories[plant_means$position %in% complete_plant] <- "Strong" 
-plant_means$Broad_categories[plant_means$position %in% core_per_plant] <- "Weak"
-
-########################################
-# CREATE HEATMAPS
-########################################
-
-library(ComplexHeatmap)
-
-# PLANTS-----
-
-# Prepare data for heatmap
-heat_plants_aux <- plant_means %>% spread(Node_FG,mean) %>% select(-SE)
-
-heat_plants <- heat_plants_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-heat_plants_fan <- heat_plants %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_fan) <- heat_plants_fan[,1]
-
-heat_plants_Weak <- heat_plants %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Weak) <- heat_plants_Weak[,1]
-
-heat_plants_Strong <- heat_plants %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Strong) <- heat_plants_Strong[,1]
-
-heat_plants_Medium_weak <- heat_plants %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Medium_weak) <- heat_plants_Medium_weak[,1]
-
-# POLLINATORS-----------
-
-filter_rare_groups <- T
-
-if(filter_rare_groups == T){
-  heat_pollinators_aux <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds",
-                                                                                "Lizards",
-                                                                                "Other_insects")) %>% 
-    spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees",            
-                                      "Coleoptera","Lepidoptera","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Syrphids")
-}else{
-  heat_pollinators_aux <- pollinator_means_reordered %>% spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees","Birds",            
-                                      "Coleoptera","Lepidoptera","Lizards","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Other insects","Syrphids")
-}
-
-heat_pollinators <- heat_pollinators_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-heat_pollinators_fan <- heat_pollinators %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_fan) <- heat_pollinators_fan[,1]
-
-heat_pollinators_Weak <- heat_pollinators %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Weak) <- heat_pollinators_Weak[,1]
-
-heat_pollinators_Strong <- heat_pollinators %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Strong) <- heat_pollinators_Strong[,1]
-
-heat_pollinators_Medium_weak <- heat_pollinators %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Medium_weak) <- heat_pollinators_Medium_weak[,1]
-
-##################
-
-#Do not know how to handle this multiplot for creating a panel
-
-# I'm going to create the 4 plots in one, 
-# I'm not sure that the grouping of the functional group is correct
-# when is done separately
-
-#sorry for the mess of libraries that I do below
-
-#Prepare first pollinators
-
-library(tidyr)
-library(data.table)
-long <- melt(setDT(heat_pollinators), id.vars = c("position","Broad_categories"), variable.name = "guilds")
-
-long_1 <- long %>% select(-Broad_categories)
-
-library(reshape2)
-long_m <- acast(long_1, position~guilds, value.var="value")
-
-#set manually the divisions, so far this is the best way I have seen to split the rows by categories
-
-r_split <- c(rep(c("Medium"), 3),rep(c("Weak"), 2),"Strong",rep(c("Medium"),2),rep(c("Weak"), 4),
-             rep(c("Medium-weak"), 2), "Strong", rep(c("Weak"), 3),rep(c("Medium-weak"), 2),
-             "Strong", "Medium")
-
-#set order of labels that avoids overlapping
-
-r_split <- factor(r_split, levels=c("Strong","Medium","Medium-weak","Weak"))
-
-#plat a bit with colors, a bit of a more complex set but looks nicer
-library(circlize)
-col_fun = colorRamp2(c(0.05644663,0.25, 0.4673256,0.75, 0.8782047), c("blue","cadetblue3", "azure2", "gold","red"))
-
-h_pol <- Heatmap(long_m, name = "Mean\npercentile", row_split=r_split,cluster_row_slices = FALSE, 
-                 column_title = "Pollinator functional groups",row_names_gp = gpar(fontsize = 10),
-                 col = col_fun,column_names_rot = 45,  column_names_gp = grid::gpar(fontsize = 10),
-                 column_title_gp = gpar(fontsize = 15, fontface = "bold"),
-                 row_title_gp = gpar(fontsize = 10, fontface = "bold"))
-
-#Prepare plants
-
-#long format
-long_plants <- melt(setDT(heat_plants), id.vars = c("position","Broad_categories"), variable.name = "Functional_groups")
-
-#filter for creating matrix
-long_plants_1 <- long_plants %>% select(-Broad_categories)
-
-#set better colnames
-long_plants_1$Functional_groups <- as.character(long_plants_1$Functional_groups)
-
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==1] <- "Selfing herbs" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==2] <- "Small outcrossing\nperennials" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==3] <- "Self-incomp. perennials\nwith large flowers" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==4] <- "Tall plants with small\nunisexual flowers" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==5] <- "Short-lived outcrossers with\nlong zygomorphic flowers"
-
-long_plants_1$Functional_groups <- factor(long_plants_1$Functional_groups, levels=c("Selfing herbs",
-"Small outcrossing\nperennials" ,"Self-incomp. perennials\nwith large flowers",
-"Tall plants with small\nunisexual flowers" ,"Short-lived outcrossers with\nlong zygomorphic flowers" ))
-
-#create matrix with reshape
-long_plants_m <- acast(long_plants_1, position~Functional_groups, value.var="value")
-
-r_split_plants <- c(rep(c("Medium"), 3),rep(c("Weak"), 2),"Strong",rep(c("Medium"),2),rep(c("Weak"), 3),
-                    rep(c("Medium-weak"), 2), "Strong", rep(c("Weak"), 4),rep(c("Medium-weak"), 2),
-                    "Strong", "Medium")
-
-r_split_plants <- factor(r_split, levels=c("Strong","Medium","Medium-weak","Weak"))
-
-h_plan <- Heatmap(long_plants_m, name = "Mean\npercentile", row_split=r_split_plants,cluster_row_slices = F, 
-                  column_title = "Plant functional groups",row_names_gp = gpar(fontsize = 10),col = col_fun,column_names_rot = 45,  
-                  column_names_gp = grid::gpar(fontsize = 10),column_title_gp = gpar(fontsize = 15, fontface = "bold"),
-                  row_title_gp = gpar(fontsize = 10, fontface = "bold"))
-
-library(patchwork)
-ht_list <- h_pol+h_plan
-
-draw(ht_list, auto_adjust = FALSE, cluster_rows = F)
-
-#Exploration of min max differences in the percentile position for plants and poll.
-#heat_pollinators[3:8]
-#
-#
-#heat_plants[3:7]
-#
-#
-#library(dplyr)
-#heat_pollinators %>%
-#  mutate(d = pmin())
-#
-#
-#colnames(heat_pollinators)<- c("position", "Broad_categories", "Bee",
-#                               "Coleoptera", "Lepidoptera","non_bee_hymenop",
-#                               "non_syrphid_dip", "syrphid")
-#
-#h <- heat_pollinators %>%
-#  mutate(min = pmin(Bee,
-#                  Coleoptera, Lepidoptera,non_bee_hymenop,
-#                  non_syrphid_dip, syrphid))%>%
-#  mutate(max = pmax(Bee,
-#                    Coleoptera, Lepidoptera,non_bee_hymenop,
-#                    non_syrphid_dip, syrphid))
-#
-#diff <- h$max-h$min
-#
-##################################################################################
-##################################################################################
-#
-#colnames(heat_plants)<- c("position", "Broad_categories", "one",
-#                               "two", "three","four",
-#                               "five")
-#
-#f <- heat_plants %>%
-#  mutate(min = pmin(1,
-#                    one, two,three,
-#                    four, five))%>%
-#  mutate(max = pmax(one,
-#                    two, three,four,
-#                    five))
-#
-#diff_1 <- f$max-f$min
-#
-#cbind(diff,diff_1)
-#
-
-```
-
-**Over- and under-represented functional group combinations of subgraphs**
-
-The different observed frequencies on the different subgraph positions showed a hierarchical order of probabilities for floral visitor functional groups (Fig.
-4).
-From the highest to lowest observed probabilities overall, we found: bees, non-syrphid Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.
-On the contrary, plant functional groups were more variable on the different subgraph positions.
-However, there were also predominant functional groups found across the different subgraph positions.
-The three most frequent groups were 'tall plants with small unisexual flowers', 'self-incompatible perennials with large flowers' and 'small outcrossing perennials'.
-On the contrary, the groups of 'selfing herbs' and 'short lived outcrossers with long zygomorphic flowers' had the lowest probability to be present on the different subgraph plant positions.
 
@@
 ```
-
-The statistical comparison with z-scores between the observed and expected plant and floral visitor functional group combinations showed that we can not recover the observed combinations from its probability of occurrence.
-In fact, most combinations are under- or over- represented and follow a modified Gaussian distribution (Johnson's $S_U$) with 65$\%$ of under-represented group combinations, 20$\%$ of no statistical difference and 15$\%$ of under-represented ones (Fig.
-5).
-In addition, subgraphs with small node combinations (i.e., 2 and 3 nodes) only appeared as under-represented.
-Network subgraphs with 4 and 5 node combinations appeared in the three statistical categories, but 4 node subgraphs had a higher proportion in the under-represented category (10% in comparison with the 1$\%$ and the 3$\%$ of the no statistical difference and over-represented categories, respectively).
-Finally, 5 node subgraphs were in similar proportions in the no statistical difference and over-represented categories (99$\%$ and 97$\%$, respectively), but they appeared in lower proportion in the under-represented category (89$\%$).
-When we explored the identity on the different positions of the most probable subgraph combinations, we found that the most common plant and floral visitor functional groups were also the most probable on these plant and floral visitor combinations within the different subgraphs (lower panel Fig.
-5).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 5.** Distribution of z-scores values after the statistical comparison of the observed probabilities of finding a subgraph combination in real networks and the expected probabilities (obtained by computer simulations).
-The resulting z-scores frequencies of this statiscal comparison are coloured based on a 95% confidence level: under-represented ($z_i^O < -1.96$, red), no statistical difference ($-1.96 \\geq z_i^O \\leq  1.96$, green) and over-represented ($z_i^O > 1.96$, blue).
-For instance, for a z-score value of 0 there were approximately 800 subgraph combinations that showed no statistical difference in the comparison between real and simulated networks.
-In addition, four specific graphical examples of the most probable subgraphs being observed on each category are also provided and the different plant and floral visitor functional groups are represented with distinct colour codes as indicated in the legend."}
-
-library(tidyverse)
-library(RColorBrewer)
-
-equidistribution <- function(number_nodes){
-
-  x_width <- 5.5/(number_nodes+1)
-
-  x_result <- rep(-1.5,number_nodes)
-
-  for(i in 1:number_nodes){
-
-    x_result[i] <- x_result[i] + i*x_width
-
-  }
-
-  return(x_result)
-
-}
-
-plot_motif_label <- function(label){
-
-  label_split <- str_split(label,"_")[[1]]
-  motif_number <- as.numeric(label_split[1])
-  nodes <- label_split[2:length(label_split)]
-  plant_nodes <- nodes[nodes %in% plant_means_reordered$Node_FG]
-  pollinator_nodes <- nodes[nodes %in% pollinator_means_reordered$Node_FG]
-
-  motifs_raw_data <-read_csv("../../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-  motif_data <- motifs_raw_data %>% filter(motif_id == motif_number)
-
-  # Create dataframe with node positions
-
-  labdown = motif_data$plant %>% unique()
-
-  xdown = equidistribution(length(labdown))
-
-  ydown = rep(0,length(labdown))
-
-  labup = motif_data$pollinator %>% unique()
-
-  xup = equidistribution(length(labup))
-
-  yup = rep(1,length(labup))
-
-  d_nodes=data.frame(x=c(xdown,xup),
-                     y=c(ydown,yup),
-                     label = c(labdown,labup))
-
-  # Create a dataframe with links
-
-  plant_positions <- data.frame(plant = labdown,
-                                xdown = xdown,
-                                ydown = ydown)
-
-  pollinator_positions <- data.frame(pollinator = labup,
-                                     xup = xup,
-                                     yup = yup)
-
-  link_df <- motif_data %>% left_join(plant_positions, by = "plant") %>% 
-    left_join(pollinator_positions, by = "pollinator")
-
-  # Add FG IDs to nodes
-  FG_IDs <- tibble(label = c(sort(labdown),sort(labup)),
-                   FG = c(plant_nodes,pollinator_nodes))
-
-  d_nodes_FG <- d_nodes %>% left_join(FG_IDs, by = "label")
-  levels_FG <- c("Bee","Coleoptera","Lepidoptera",
-                 "Non-bee-Hymenoptera", "Non-syrphids-diptera",
-                 "Syrphids","1","2","3","4","5")
-
-  d_nodes_FG$FG <- factor(d_nodes_FG$FG, levels = levels_FG)
-
-  levels(d_nodes_FG$FG) <- c("Bee","Coleoptera","Lepidoptera",
-                             "Non-bee-Hymenoptera", "Non-syrphids-diptera",
-                             "Syrphids","1","2","3","4","5")
-
-  # Before plotting the motif, we remove letters from the node position id
-
-  d_nodes_FG$label <- gsub("[^0-9.-]", "", d_nodes_FG$label)
-
-  # Define the number of colors you want
- mycolors <- c("#A6CEE3", "chocolate2",  "gold2", "#1F78B4","#B2DF8A",
-                     "gray58", "lightgoldenrod2","thistle2", "burlywood","lightcoral", "olivedrab3")
-
-  ggplot(data=d_nodes_FG, aes(x, y)) +
-    scale_shape_identity() +
-    geom_segment(data = link_df, aes(x=xdown, y=ydown, xend = xup, yend = yup), size = 1, color = "grey20")+
-    geom_point(aes(color = FG), size=7.5)+
-    geom_text(aes(x, y , label = label), size=3)+
-    scale_color_manual(drop = FALSE, values = mycolors,
-                       breaks=c("Bee","Coleoptera","Lepidoptera",
-                                "Non-bee-Hymenoptera", "Non-syrphids-diptera",
-                                "Syrphids","1","2","3","4","5"), 
-                       labels=c("Bees","Coleoptera","Lepidoptera",
-                                "Non-bee-Hymenoptera", "Non-syrphids-Diptera",
-                                "Syrphids", 
-                                "Selfing herbs","Small outcrossing perennials",
-                                "Self-incomp. perennials\nwith large flowers",
-                                "Tall plants with small\nunisexual flowers",
-                                "Short-lived outcrossers with\nlong zygomorphic flowers"))+
-    xlim(-1.5,4)+ ylim(-0.5,1.5)+
-    theme(panel.background = element_blank(),
-          axis.text.x=element_blank(),
-          axis.ticks.x=element_blank(),
-          axis.text.y=element_blank(),
-          axis.ticks.y=element_blank())+
-    labs(x=NULL,y=NULL)+
-    ggtitle(paste0("Subgraph ",motif_number))+
-    theme(plot.title = element_text(hjust = 0.5,size=10))+
-    guides(color=guide_legend(title="Functional groups"))
-
-}
-
-# Data with pollinator/plant labels
-
-plant_means_reordered <- read_csv("../../Data/Csv/plant_abs_freq_means.csv")
-pollinator_means_reordered <- read_csv("../../Data/Csv/pollinator_abs_freq_means.csv")
-#Filter out in order to have just 6 FG'S
-pollinator_means_reordered <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds", "Lizards", "Other_insects"))
-
-####################################################################################################
-#Read data to check top 5 motif of each category of observed propabilities
-
-#Under, No signi, Over-rep
-####################################################################################################
-# Check top Z-scores of each group (Under, No diff, Over)
-
-#Read data
-data <- read.csv("../../Data/Csv/motifs_observed_probability_SIMUL_CI.csv")
-
-#Find critical value of Z-score
-p <- 0.05 #cutoff probability 95% confidence
-critical_value <- qnorm(p/2) #double tail probability divide by 2
-
-data_1 <- data %>%
-  mutate(infra_over_represented = case_when(
-    z_score < -abs(critical_value) ~ "infra",
-    between(z_score, -abs(critical_value), abs(critical_value)) ~ "no_diff",
-    z_score > abs(critical_value) ~ "over"
-  ))
-
-#data_2 <- filter(data_1, abs(z_score)<2000) 
-#str(data_2)
-
-#Select under-represented by the ones with highest porbability of being observed (top10)
-under_data <- filter(data_1, infra_over_represented=="infra")
-
-under_top_5 <- filter(under_data, row_number(desc(abs(motif_observed_probability)))<= 5) %>%
-  select(motif_functional_ID,motif_observed_probability,counts_observed,z_score)
-
-#Select no statistical difference by the ones with highest porbability of being observed (top5)
-no_diff_data <- filter(data_1, infra_over_represented=="no_diff")
-
-no_diff_top_5 <- filter(no_diff_data, row_number(desc(abs(motif_observed_probability)))<= 5) %>%
-  select(motif_functional_ID,motif_observed_probability,counts_observed,z_score)
-
-#Select over-represenetd by the ones with highest porbability of being observed (top5)
-over_data <- filter(data_1, infra_over_represented=="over")
-
-over_top_5 <- filter(over_data, row_number(desc(abs(motif_observed_probability)))<= 5) %>%
-  select(motif_functional_ID,motif_observed_probability,counts_observed,z_score)
-####################################################################################################
-#Now plot it 
-####################################################################################################
-
-library(patchwork)
-
-#Prepare list of 5 plots for each group
-#Under
-labels_under <- under_top_5$motif_functional_ID
-p_under <- list()
-
-for (i in 1:5){
-
-  p_under[[i]] <- plot_motif_label(labels_under[[i]])
-}
-
-#No signficance
-labels_nodiff <- no_diff_top_5$motif_functional_ID
-p_nodiff <- list()
-
-for (i in 1:5){
-
-  p_nodiff[[i]] <- plot_motif_label(labels_nodiff[[i]])
-}
-
-#Over
-labels_over <- over_top_5$motif_functional_ID
-p_over <- list()
-
-for (i in 1:5){
-
-  p_over[[i]] <- plot_motif_label(labels_over[[i]])
-}
-
-#Run Script with histogram plot
-source("../../Scripts/Z-score_percentile_histogram_plot.R")
-
-hist <- ggplot(data_2 %>% filter(round_motif_observed_probability>0), aes(x=z_score, color=infra_over_represented, fill=infra_over_represented)) + 
-  geom_histogram(bins = 93, alpha = 0.5, position = "identity",lwd = 0.25)+
-  geom_vline(xintercept = -abs(critical_value))+
-  geom_vline(xintercept = abs(critical_value))+
-  xlim(-60,60) + ylab("Frequency")+  theme_bw() +
-  scale_fill_manual(name="Motif frequencies" ,values=c("coral2", "palegreen3", "cyan3"), labels=c("Under-represented",
-                                                                                                  "No statistical difference", "Over-represented")) +
-  scale_color_manual(name="Motif frequencies" ,values=c("coral2", "palegreen3", "cyan3"), labels=c("Under-represented",
-                                                                                                   "No statistical difference", "Over-represented")) + xlab("Z-score")
-
-t_col <- function(color, percent = 50, name = NULL) {
-  #      color = color name
-  #    percent = % transparency
-  #       name = an optional name for the color
-
-  ## Get RGB values for named color
-  rgb.val <- col2rgb(color)
-
-  ## Make new color using input color as base and alpha set by transparency
-  t.col <- rgb(rgb.val[1], rgb.val[2], rgb.val[3],
-               max = 255,
-               alpha = (100 - percent) * 255 / 100,
-               names = name)
-
-  ## Save the color
-  invisible(t.col)
-}
-## END
-
-#Prepare panel of plots
-hist / ((p_under[[1]]/p_under[[2]]/p_under[[3]]/p_under[[4]] & theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_rect(fill=t_col("coral2")))) | 
-          (p_nodiff[[1]]/p_nodiff[[2]]/p_nodiff[[3]]/p_nodiff[[4]]& theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_rect(fill=t_col("palegreen3")))) |
-          (p_over[[1]]/p_over[[2]]/p_over[[3]]/p_over[[4]] & theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_rect(fill=t_col("cyan3"))))) + plot_layout(guides = 'collect')
-
-```
-
-# Discussion
-
-Understanding the global patterns of network structure is key to unravel the processes that govern community dynamics [@bascompte2007; @bastolla2009; @guimaraes2020].
-However, common analytical approaches at the node or at the global network level are unable to capture the full complexity of ecological systems [@simmons2019; @bergamo2021].
-Because network subgraphs can capture both direct and indirect interactions, by analysing their over- and under-representation we were able to explore in great detail the structure of interactions between animal pollinators and the plants they visit.
-We have explored for the first time the overall structure and presence of network motifs in real plant-pollinator networks and shown that, according to our first hypothesis, the different subgraphs up to five nodes are consistently over- or under-represented in comparison with simulated networks.
-In addition, we show that for plant-pollinator networks there is a general tendency for over-representation of network subgraphs that are more densely connected (i.e., complete, fan and asymmetric complete).
-Indeed, the work of @simmons2020 has shown with the help of simulated plant-pollinator networks that the main different processes that shape plant-pollinator communities (i.e., neutral effects, trait matching and phenology) generate different patterns of direct and indirect interactions, and that specifically, a higher proportion of these more densely connected subgraphs is associated with neutral effects.
-Therefore, as indicated for other network properties like nestedness at the macro-scale level [@krishna2008; @suweis2013], or interaction probability at the species level [@bartomeus2016], our findings align with our second hypothesis and indicate that neutral effects may be also the main driver governing this intermediate level of complexity on plant-pollinator networks.
-
-Overall, generalist network motifs for floral visitors were consistently over-represented (e.g., complete subgraphs; Fig.
-2).
-For instance, when we compare network subgraphs with equal structure for both trophic levels, we found that floral visitors had always over-representation in the positions that implied the highest number of direct links (e.g., positions 16 and 46 from network subgraphs 7 and 17, respectively).
-Despite this being in good agreement with the current view of the generalist nature of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of generalist network motifs was driven by the functional group of bees while the rest of the functional groups tended to be under-represented (Fig.
-S6 A).
-In contrast, non-bee groups were over-represented in subgraph positions associated with specialised roles.
-This large effect of bees on the overall patterns is no surprise, as bees were the group with the largest number of interaction records in the whole set of networks as also shown for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017].
-Just syrphids had a relatively similar number of interactions in comparison with bees (1,768 and 2,256 interactions, respectively) and similar species richness (343 and 321 species, respectively).
-However, both functional groups were associated with contrasting ecological roles likely indicating that both number of interactions and richness are not driving the observed interaction patterns for the different functional groups.
-Interestingly, bees also were the group with lower number of indirect interactions, while the rest of floral visitor groups showed a clearly higher number of indirect interactions, indicating that these non-bee floral visitor groups may experience higher competitive interactions for floral resources [@thomson2020].
-Despite plant functional groups showed little differences between them on their subgraph frequencies, all groups showed a tendency to be over-represented on subgraph positions that were associated with higher levels of specialisation.
-This tendency towards specialist roles may be the result of co-evolutionary processes (e.g., trait-matching) between plants and pollinators to optimise pollen transfer [@moreira2019].
-Remarkably, only tall plants with small unisexual flowers showed higher frequencies on subgraphs that were associated with low number of indirect interactions with likely direct implications on pollen transfer for this group that needs to guarantee cross-pollination.
-
-The probabilities of appearance of each functional group on the different subgraph positions were insufficient to predict most of the observed network position combinations (Fig.
-5).
-This implies that not just the representation of network subgraphs types but also the identity of the elements of their structure is non-random.
-Notably, we found that just 30$\%$ of the possible 53,250 subgraph combinations are realised.
-Thus, similarly to the presence of forbidden links at the network level [@olesen2011; @jordano2016], we also found the existence of forbidden subgraph positions and those represented almost two thirds of the total possible subgraph combinations.
-This concurs well with the general idea that plant-pollinator networks have a high proportion of non-realized direct interactions [@jordano2003; @bascompte2013], and, as a result, also a high proportion of non-realized combinations of indirect interactions.
-Some of these non-observed direct interactions are probably due to under-sampling [@dorado2011; @jordano2016].
-However, a large fraction of the possible interactions do not take place because of different constraints such as species co-occurrence, trait matching processes and phenological uncoupling [@olesen2011; @bartomeus2016; @jordano2016].
-Despite the advances in the understanding of the ecological processes that influence species pairwise interactions [@bartomeus2016; @peralta2020], we still know little about how these processes determine competitive and facilitative interactions in mutualistic networks.
-Thus, as suggested by @simmons2020, exploring the proportion of these realised network subgraphs that are competitive or facilitative is a necessary next step to improve our understanding of the architecture of biodiversity [@bascompte2007].
-
-Despite the obvious usefulness of functional groups in summarising species ecological roles (e.g., similar reproductive biology for plants and behaviour for pollinators), delimiting species into functional groups is often not trivial.
-For instance, taxonomic diversity and trait availability limit our ability to properly represent the wide range of reproductive strategies [@dellinger2020] and different clustering analysis can lead to distinct outcomes (e.g., k-means and hierarchical clustering).
-We divided floral visitors on the taxonomic rank level because it adequately represented pollinator ecological roles without the tremendous effort of compiling trait data for over 1,000 species of floral visitors.
-Indeed, further groupings with traits could help reveal greater relevance of trait-matching processes on indirect interactions.
-Moreover, we analysed network subgraphs focusing exclusively on presence or absence of interactions, assuming that all interactions are equally important.
-However, further work should investigate how to account for quantitative measurements of plant-pollinator interactions.
-Consistent with previous work [@simmons2019; @simmons2020], we characterised network motifs by using null models only constrained for network connectance.
-Although more complex null models are difficult to interpret [@Ulrich2013], they can potentially allow us to separate the mechanisms by which motifs emerge.
-However, we found that null models with more constraints generated binary structures that were mostly identical to the original ones.
-In addition, we observed that connectance, nestedness and degree distribution were significantly correlated (data not shown).
-All that highlights the difficulties to disentangle the potential sources that generate over-representation of network subgraphs and the need to investigate them.
-At the same time, although network subgraphs can capture both direct and indirect interactions, the reduction of network complexity into these different building blocks inevitably convey the loss of information [@simmons2019].
-For example, network subgraphs neglect indirect effects emerging from large cascading effects that propagate across them.
-Finally, despite the wide geographical coverage of our plant-pollinator dataset, there are major gaps for some regions of the world with a clear bias towards Europe, America and islands which have long interested ecologists [@macarthur1963; @warren2015].
-These biases are also found in global datasets of networks, where the data is highly fragmented across space [@poisot2021] and more efforts are needed to capture global patterns of plant-pollinator interactions.
-
-In conclusion, by following the framework of @simmons2020 we have been able to explore competitive and facilitative interactions in plant-pollinator networks worldwide and found the presence of worldwide motifs that highlight the non-random structure of indirect interactions.
-This non-random structure might emerge due to neutral effects according to previous modelling work [@simmons2020].
-Further, we found that plant and floral visitor functional groups are associated with different subgraph positions that involve distinct ecological roles (e.g., generalisation versus specialisation) and that the different subgraph combinations are strongly constrained.
-Although we are still far from predicting how species interact, our work is a first step to elucidate beyond pairwise interactions.
-
-# Acknowledgements
-
-This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2).
-JBL also thanks the University of New England for the funding provided to carry out this work.
-Finally, we would like to thank David García-Callejas for his useful comments on the manuscript before submission.
-
-# Conflict of interest declaration
-
-The authors declare no conflict of interest.
-
-# Author contributions
-
-All authors designed the idea.
-Jose B.
-Lanuza collected the data.
-Alfonso Allen-Perkins led the analysis with contributions of Jose B.
-Lanuza and guidance of Ignasi Bartomeus.
-Jose B.
-Lanuza wrote the manuscript with contributions of Ignasi Bartomeus and Alfonso Allen-Perkins.
-
-# Data Availability Statement
-
-Data and code available from the online repositories Zenodo  <https://doi.org/10.5281/zenodo.6489213> [@zenodo2022] and Github <https://github.com/JoseBSL/FunctionalMotifs>.
-\newpage
-
-# References
-
-::: {#refs}
-:::

### 2023-01-25 Manuscript/Figures/Figure5.Rmd
Word file and independent figures for typesetting

--- 2022-10-08 Manuscript/Main_text/Main_text_Journal_of_Animal_Ecol.Rmd
@@
 always_allow_html: true
-bibliography: bibliography.bib
-biblio-style: apalike
-csl: JournalOfAnimalEcology.csl #converted from funct ecol style from zotero styles
 ---
-
-**Jose B. Lanuza^1,2^** \| **Alfonso Allen-Perkins^2,3^** \| **Ignasi Bartomeus^2^**
-
-1 School of Environmental and Rural Science, University of New England, Armidale, New South Wales 2350, Australia.
-
-2 Estación Biológica de Doñana (EBD-CSIC), E-41092 Seville, Spain.
-
-3 Departamento de Ingeniería Eléctrica, Electrónica, Automática y Física Aplicada, ETSIDI, Universidad Politécnica de Madrid, 28040 Madrid, Spain.
-
-\captionsetup[table]{labelformat=empty}
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
-
-# Abstract
-
-\singlespacing
-
-Ecological processes leave distinct structural imprints on the species interactions that shape the topology of animal-plant mutualistic networks.
-Detecting how direct and indirect interactions between animals and plants are organised is not trivial since they go beyond pairwise interactions, but may get blurred when considering global network descriptors.
-Recent work has shown that the meso-scale, the intermediate level of network complexity between the species and the global network, can capture this important information.
-The meso-scale describes network subgraphs representing patterns of direct and indirect interactions between a small number of species, and when these network subgraphs differ statistically from a benchmark, they are often referred to as "network motifs".
-Although motifs can capture relevant ecological information of species interactions, they remain overlooked in natural plant-pollinator networks.
-By exploring 60 empirical plant-pollinator networks from 18 different studies with wide geographical coverage, we show that some network subgraphs are consistently under- or over-represented, suggesting the presence of worldwide network motifs in plant-pollinator networks.
-In addition, we found a higher proportion of densely connected network subgraphs that, based on previous findings, could reflect that species relative abundances are the main driver shaping the structure of the meso-scale on plant-pollinator communities.
-Moreover, we found that distinct subgraph positions describing species ecological roles (e.g., generalisation and number of indirect interactions) are occupied by different groups of animal and plant species representing their main life-history strategies (i.e., functional groups).
-For instance, we found that the functional group of 'bees' was over-represented in subgraph positions with a lower number of indirect interactions in contrast to the rest of floral visitors groups.
-Finally, we show that the observed functional group combinations within a subgraph can not be retrieved from their expected probabilities (i.e., joint probability distributions), indicating that plant and floral visitor associations within subgraphs are not random either.
-Therefore, our results highlight the presence of common network motifs in plant-pollinator communities that are formed by a non-random association of plants and floral visitors functional groups.
-
-Keywords: pollinators, plant-pollinator networks, plant-pollinator interactions, network motifs, indirect interactions, floral visitors
-
-\doublespacing
-
-\newpage
-
-# Introduction
-
-Ecological communities are formed by a plethora of interacting species that form networks of interactions.
-Because of the tremendous complexity of these ecological networks, species interactions are generally condensed in metrics that summarise this information [@guimaraes2020].
-Plant-pollinator interactions are no exception, and they are often studied with indices that aggregate the information at the network (macro-scale) and species level (micro-scale).
-For example, plant-pollinator network level approaches have identified common invariant structural properties across mutualistic networks, including a degree distribution that decays as a truncated power law [@jordano1987], nestedness [@bascompte2003], or modularity [@olesen2007].
-In addition, the local species position within the network can define its degree of selectiveness [@bluthgen2006] or its role in connecting the rest of the community [@olesen2007].
-Despite the unquestionable progress with the use of these metrics at both network and species level, condensing complex information into a single metric implies the loss of relevant ecological information that obscures the understanding of species interactions [@cirtwill2018; @simmons2019].
-
-Indirect interactions, the mediated effect between two species by a third species, are ubiquitous in natural systems [@strauss1991; @holt1994; @wootton1994] and play a key role in shaping community dynamics [@werner2003; @walsh2013].
-Some of the most studied indirect interactions are the ones caused by trophic cascades with consumer-resource interactions [@abrams1996; @schmitz2001].
-In fact, previous studies focus on antagonistic interactions and mutualistic interactions are often overlooked [@knight2005].
-On the contrary, plant-pollinator research has traditionally investigated direct interactions but neglected indirect effects such as competitive or facilitative processes between plants for pollinators [@moeller2004; @sargent2008; @carvalheiro2014].
-Conventional analytical tools in bipartite networks often discard relevant information about indirect interactions by condensing the information into single indices either at species or network level [@cirtwill2018; @simmons2019].
-However, as previously explored with three species modules in unipartite food webs [@allesina2008; @stouffer2010], the emergent framework of bipartite subgraphs has proven to be a powerful analytical tool to better understand plant-pollinator community dynamics by capturing both direct and indirect effects [@simmons2019].
-These network subgraphs that constitute the meso-scale are often referred to as the building blocks of the network and when their numbers occur at higher frequencies than in randomised networks, those are generally defined as 'network motifs' [@milo2002].
-Indeed, the analysis of motifs in simulated plant-pollinator networks has revealed that the different drivers that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect effects [@simmons2020].
-However, the global patterns of indirect interactions in real plant-pollinator networks and their ecological consequences remain unexplored (e.g., over- and under- represented network subgraphs).
-
-By linking the structural properties of the meso-scale with the species' ecology we can advance in our understanding on the determinants of species interactions.
-For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species' functional role [@stouffer2012; @baker2015; @cirtwill2018b].
-Yet, our understanding of the ecological implications of network motifs in real plant-pollinator networks remains in its infancy.
-Moreover, it is unclear how the species ecology and life-history traits determine its functional role within the network of interactions [@coux2016].
-For example, large pollinators can forage larger distances [@greenleaf2007], deposit greater pollen quantities [@foldesi2021] and handle complex zygomorphic flowers in comparison with small pollinators that are restricted to lower floral complexity [@gong2009].
-Despite these obvious differences in pollinator behaviour, how contrasting species' ecology translates into different network motifs is still poorly known.
-Similarly, recent empirical findings indicate that the meso-scale is the best descriptor of plant reproductive success [@allen2021], but little is known about how plants' reproductive strategies shape their position within the network of interactions.
-Although some studies have evaluated plant reproductive strategies in plant-pollinator networks [@tur2013; @lazaro2020], this is an often overlooked aspect in a community context [@devaux2014] and rarely incorporated into plant-pollinator network studies.
-Hence, exploring how the main plant and floral visitor life-history strategies integrate with the emergent framework of network motifs could help to progress knowledge on the ecological processes that shape plant-pollinator interactions.
-
-Here we evaluate the interaction patterns of the meso-scale and its ecological implications in plant-pollinator networks with the help of 60 empirical networks from 18 different studies distributed across 14 different countries.
-For this, plants and pollinators were divided into functional groups that summarise their main life-history strategies and the different networks were split into all their subgraph elements up to five nodes.
-First, based on previous knowledge showing the non random assembly of macro-scale mutualistic networks [@bascompte2003] and food webs [@dunne2002], we test the hypothesis that the building blocks that constitute the meso-scale in plant-pollinator networks have a non-random structure of interactions with over- and under-represented subgraphs (i.e., motifs) that represent contrasting ecological roles.
-Second, because species relative abundances (i.e., neutral effects) are one of the main drivers of network macro-struture [@krishna2008; @suweis2013; @bartomeus2016], we hypothesise that neutral effects may also govern the interaction patterns of the meso-scale in plant-pollinator networks.
-Finally, we explore if plants and pollinators functional groups are associated with subgraph positions that imply distinct ecological roles and if there are over- and under-represented functional group combinations within the different network subgraphs.
-
-# Methods
-
-**Overview**
-
-To investigate the structure of the meso-scale in plant-pollinator networks, we gathered published plant-pollinator networks with worldwide distribution.
-Then, we classified the different plant and floral visitor species from these networks into functional groups that summarise their main life-history strategies.
-We calculated the normalised subgraph frequencies and investigated if these frequencies are similar or not to the ones expected by chance with the help of null models.
-Then, for each group of plants and floral visitors we investigated the ecological implications of their overall representation on the different subgraph positions, by comparing, on the one hand, the observed (normalised) frequencies of each group in the different subgraph positions with the frequencies of their simulated counterparts, and, on the other hand, the differences among groups per subgraph position in terms of their number of indirect interactions and specialisation.
-Finally, to understand if the different functional group combinations within a subgraph are structured, we compare if the observed functional group combinations from empirical networks can be retrieved from the joint probability distribution of the expected frequencies of the different plant and floral visitor groups within network subgraphs.
-
-**Plant-pollinator studies**
-
-We have compiled 60 plant-pollinator networks from 18 different studies (Table S1).
-All studies sampled plant-pollinator interactions in natural systems in a single flowering season and were selected based on wide geographical coverage (Fig.
-S1) and presence of interaction frequency as a measure of interaction strength.
-In total, there were 503 plant species, 1,111 floral visitors species and 6,248 pairwise interactions registered.
-For ease of data manipulation, plant and floral visitor species names were standardised with the help of the R package *taxize* version *0.9.99* [@chamberlain2020].
-
-**Plant and floral visitor functional groups**
-
-First, plant species were grouped through hierarchical clustering into the optimal number of functional groups that summarises the main plant reproductive strategies.
-For this, we used the plant trait dataset compiled in @lanuza2021 that consisted also of plant species that belonged to the same plant-pollinator networks plus some additional meta-networks not considered here.
-This dataset comprised a total of 1,506 plant species including the 503 species considered in this study (Table S2).
-Because most of these plant species are likely to benefit from animal pollination, we used reproductive traits relevant to understand the different plant reproductive strategies and their interactions with pollinators.
-After excluding traits with a high percentage of missing values (over 30$\%$), we ended up with 8 floral, 3 reproductive biology and 3 plant morphology traits (see Table S3 for a list of all traits).
-Floral traits included those associated with the size, form and number of floral organs (e.g., style length or ovule number).
-Reproductive biology traits described the reproductive system of the plant (e.g., mating and compatibility systems) and plant morphology traits were associated with the size and form of the plant (i.e., plant height, lifespan and life form).
-After an extensive search for each plant species on several different resources (e.g., plant databases, online floras, books, journals and images), over 80% of the cells of the whole dataset were filled.
-Thus, to avoid the loss of species with trait missing values, missing trait data was imputed as detailed in @lanuza2021.
-
-We opted to calculate the plant functional groups within a larger set of species because of the higher accuracy when delimiting functional groups with that many variables and species [@dolnicar2014].
-To feed the clustering analysis, we calculated the distance between the different qualitative and scaled quantitative variables with Gower distance [@gower1971].
-For this, we used the function *gowdis* with method *ward.D2* from the *FD* package version *1.0-12* [@laliberte2014].
-Finally, we conducted hierarchical clustering with the function *hclust* from the *R* stats package version *4.0.5* and calculated the optimal number of clusters with the function *kgs* from the *maptree* package version *1.4-7* [@white2009].
-
-Second, floral visitors were aggregated into taxonomic groups (hereafter referred to as functional groups) based on taxonomic rank as done similarly in other plant-pollinator studies [@fenster2004; @ollerton2009].
-We opted to divide floral visitors on the taxonomic rank level and not with functional traits because the main orders of floral visitors differed in form and behaviour and had lower superior taxonomic complexity (i.e., floral visitors had 6 orders versus plants that had 38).
-Thus, this allowed us to group floral visitors into functional groups that represented approximately the main life-history strategies of the possible pollinators: (i) bees (Hymenoptera-Anthophila), (ii) non-bee Hymenoptera (Hymenoptera-non-Anthophila), (iii) syrphids (Syrphidae-Diptera), (iv) non-syrphids-Diptera, (v) Lepidoptera and (vi) Coleoptera.
-However, a minor set of species belonged to other functional groups that were considered in analyses but not discussed further because of their low representation in the full set of networks (3.55$\%$ of the total interactions recorded).
-These taxonomic groups were 'lizards', 'birds' and 'other insects'.
-This last functional group was formed by a mix of uncommon insect taxa on the full set of networks.
-
-**Overall network subgraphs patterns**
-
-Following previous work [@simmons2019; @simmons2020], we broke down the plant-pollinator networks into their constituent network subgraphs that can capture both direct and indirect interactions.
-Prior to analyses, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.
-This approach was preferred since quantitative subgraph analyses have been developed just recently and more work is needed to fully understand and interpret the information that they can convey [@simmons2020].
-All analyses were run considering singletons (species with only one interaction detected) but we conducted a second exploration without singletons (64.98$\%$ of interactions) to evaluate the effect of rare species on the observed patterns.
-Results without singletons are qualitatively consistent and are not further discussed in the main text (Figs S2 and S3).
-
-We calculated the frequency of all subgraphs up to five nodes (17 different subgraphs in total; see Fig.
-1) for each empirical network, by using the *bmotif* package version *2.0.2* [@bmotifsimmons2019].
-We focused exclusively on subgraphs up to five nodes in our analyses for computational reasons and for the ease of visualization and interpretation of a reduced set of less complex network structures.
-Throughout the entire manuscript, floral visitors occupy the top nodes of the different network subgraphs and plants the bottom ones.
-To control for variation in network size, subgraph frequencies were normalised as a proportion of the total number of subgraphs within each subgraph class (i.e., 2-species, 3-species, 4-species and 5-species network subgraphs).
-In addition, we excluded 2-species (or 2-nodes) subgraphs from our analyses because its normalised frequencies would always equal one.
-Note that the aim is not comparing different networks, which may differ in sampling effort, but correctly describing the structure of each individual network.
-Like @simmons2020, we classified the different subgraphs by their average path length (mean number of links between all pairs of nodes) into four different groups: (i) complete or strong ($\overline{x} = 1.38$), (ii) fan or medium-strong ($\overline{x} = 1.48$), (iii) assymmetric complete or medium-weak ($\overline{x} = 1.60$) and (iv) core-peripheral or weak ($\overline{x} = 1.85$), where $\overline{x}$ represents the mean of the average path length across subgraphs within the same group.
-In general terms, plant and floral visitor groups on more densely connected network subgraphs (e.g., complete or fan) will experience lower number of indirect interactions in contrast to groups on less densely connected structures (e.g., medium-weak or weak).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, fig.pos="t", warning=FALSE,out.width="75%",fig.align="center", fig.cap="\\textbf{Figure 1.} Adapted figure of Simmons et al., (2019).
-All possible network subgraphs from two to five species in bipartite networks grouped by the different subgraph classes (2-species, 3-species, 4-species and 5-species).
-There are a total of 17 possible subgraphs with 46 different positions denoted within each node.
-The different subgraphs are aggregated by the broad indirect interaction structures they represent on four different groups (strong, medium-strong, medium-weak and weak).
-For each group, we show in the legend the mean value of the average path length of all subgraphs within it.
-The different path length groups range from densely connected network structures (strong subgraphs where all possible interactions are realised and the mean path length is minimum) to weakly connected ones (weak subgraphs where the mean path length is maximum).", fig.width=10,fig.height=8}
-library(tidyverse)
-library(RColorBrewer)
-source("../../Scripts/Scripts_Alfonso/plot_motif_positionsV2.R")
-
-motif_number <- 1
-p1 <- plot_motif_positions(motif_number) +
-geom_point(aes(color = as.factor(label)),size=10,color = "grey90")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 2
-p2 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 3
-p3 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 4
-p4 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 5
-p5 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "lightcoral")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 6
-p6 <- plot_motif_positions(motif_number) +
-geom_point(aes(color = as.factor(label)),size=10,color = "goldenrod2")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 7
-p7 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 8   
-p8 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 9
-p9 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "lightcoral")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 10
-p10 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "lightcoral")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 11
-p11 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "skyblue")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 12
-p12 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "goldenrod2")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 13
-p13 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "lightcoral")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 14
-p14 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "lightcoral")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 15
-p15 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "skyblue")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 16
-p16 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "goldenrod2")+
-geom_text(aes(x, y , label = label),size=3)
-
-motif_number <- 17
-p17 <- plot_motif_positions(motif_number)+
-geom_point(aes(color = as.factor(label)),size=10,color = "mediumaquamarine")+
-geom_text(aes(x, y , label = label),size=3)
-
-library(patchwork)
-
-p <- (p1 & ylab("2 species")| p2 & ylab("3 species") | p3 ) /
-(p4 & ylab("4 species")| p5 | p6 | p7) / 
-(p8  & ylab("5 species")| p9 | p10 | p11 | p12) /
-(p13 & ylab("5 species")| p14 | p15 | p16 | p17) &
-theme(axis.title.y = element_text(color="black", size=14, face="bold"))
-
-#Create custom legend
-a <- c(1,2,3,4)
-b <- c(1,2,3,4)
-c <- c("a","b", "c", "d")
-abc <- data.frame(a,b,c)
-p1 <- ggplot(abc, aes(x=a,y=b, color=c))+geom_point() + theme_bw() + 
-  scale_colour_manual(name = 'Path length classification', 
-                      values =c(a= 'goldenrod2',b='mediumaquamarine',
-                                c='skyblue', d='lightcoral'), 
-                      labels = c(a='Strong \n mean path length = 1.38', 
-                                 b='Medium-strong \n mean path length = 1.48',
-                                 c='Medium-weak \n mean path length = 1.60',
-                                 d='Weak \n mean path length = 1.85'))+
-theme(legend.position="bottom")+ guides(colour = guide_legend(override.aes = list(size=8),title.position="top", title.hjust = 0.5))
-
-legend <- cowplot::get_legend(p1+ theme(legend.position = "bottom",legend.text = element_text(size=10), legend.title = element_text(size=12, 
-face="bold"),legend.box.background = element_rect(color="black", size=2)))
-
-cowplot::plot_grid(p, legend, ncol = 1, rel_heights = c(12, 1.8))
-
-```
-
-To assess the significance of the observed frequencies, we created 1,000 simulated networks for each binary network using the *nullmodel* function and the *vaznull* model in the *bipartite* package version *2.14* [@dormann2009].
-Generated networks had the same number of plants and floral visitors, as well as the same connectance of their corresponding empirical networks.
-We discarded null models with more constraints (e.g., constraining for species degree) because the permutations did not generate sufficient variability and provided highly similar or identical networks to the original ones.
-After extracting the subgraph frequencies from the simulated networks, for each subgraph type and empirical network, we calculated the percentage of simulated networks whose frequencies were smaller than the ones observed, that is, we estimated the percentile of the observed subgraph frequencies.
-Subgraphs whose percentile is close to 0 or 100 are under- or over-represented in empirical networks, respectively, and indicate the presence of network motifs as they differ statistically from the network structures generated with simulated networks.
-To summarise general patterns across networks, we used an intercept-only linear mixed model (LMM) per subgraph with the help of the *lme4* package version *1.1-21* [@bates2015], where the response variable was the observed subgraph percentile per network.
-Note that as we are only interested in modelling the intercept value, no predictors were specified.
-In these models, we used the study identifiers in Table S1 as a random intercept.
-By doing so, we obtained estimates of the average subgraph frequency, but controlling for the variation at the study level.
-
-**Over- and under-represented functional groups on subgraph positions**
-
-We calculated which plant and floral visitor functional groups were over- or under-represented in the different subgraph positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts.
-To estimate the position frequencies of each plant and floral visitor group in a given network, we added the frequencies of those species that belong to the same group, and then, we normalised the resulting frequencies by dividing them by the total number of times that a corresponding group appears in any position within the same subgraph size class.
-Then, we calculated the percentile of the observed position frequencies for each functional group and network, just like we did with subgraph frequencies.
-To outline the general patterns of position frequencies across networks and groups, we fit a LMM per subgraph position, where the response variable was the observed position percentile per network.
-We used the group identifier as an explanatory variable and the study identifiers as a random intercept.
-Hence, we assessed the average subgraph frequency per species group, after controlling for the variation at the study level.
-Finally, we visualised over- and under-representation of plant and floral visitor groups on the different subgraph positions with the help of the *ComplexHeatmap* package version *2.6.2* [@gu2016].
-
-To understand if the different plant and floral visitor functional groups are associated with subgraph positions that represent different network roles, we characterised the roles of each subgraph position for the different functional groups in terms of their specialisation and number of indirect interactions.
-To that end, we calculated the specificity of each subgraph position following @poisot2015 as $s_i = (L - l_i) / (L - 1)$, where $L$ is the total number of groups and $l_i$ the number of interaction partners of the group $i$ in a given subgraph.
-Values of the vector $si$, range between 1, complete specialisation (1 partner within the subgraph) and 0 complete generalism (all possible partners within the subgraph).
-Then, because all nodes within a motif are connected, we calculated the number of indirect interactions ($\theta_i$) for each motif position as $\theta_i=m_i-k_i-1$, where $m_i$ is the total number of nodes in a given motif, and $k_i$ represents the degree of the corresponding motif position, that is, the total number of links connected to such position.
-Thus, we considered all possible indirect interactions for each position.
-Finally, we analysed in a single model how specialisation and the number of indirect interactions were associated with the observed percentiles for each trophic guild and subgraph position.
-For this, we fitted again a LMM model with the help of the *lme4* package, where we considered specialisation and number of indirect interactions as response variables with the interaction by plant and floral visitor group for both response variables.
-Further, we considered as random factor subgraph position nested within study system.
-
-**Over- and under-represented functional group combinations of subgraphs**
-
-Finally, we studied which combinations of plant and floral visitor functional groups tend to appear together within the same subgraphs (up to five nodes).
-That is, which combinations are over- or under-represented.
-This analysis used 57 out of the 60 networks available due to computational limitations to identify all the nodes in the subgraphs of the three networks with the highest number of links.
-To do so, for each of the 53,250 possible subgraph combinations, we estimated the observed and the expected probability of finding those combinations in empirical networks, respectively.
-Then, we determined whether the observed probabilities are likely to come from the expected probabilities or not.
-To calculate the observed probability ($p_i^O$) of the different groups within a subgraph $i$ (e.g., subgraph 3, 'bee' + 'bee' + 'selfing herbs'), we divided the number of times that $i$ appears in our set of empirical networks ($n_i^O$) by the sum of the number of times that each possible combination appeared: $p_i^O = n_i^O / \sum_{k=1}^{53,250} n_k^O$.
-To estimate the expected probability ($p_i^E$) of a given subgraph combination $i$, we assumed that the probability of finding a given functional group $x$ in the position $\alpha$ is independent of the probabilities associated with other positions and groups in that subgraph.
-Therefore, the expected probability ($p_i^E$) of the subgraph combination $i$ is given by the product of the probabilities of its constituents, i.e., $p_i^E = \prod _{(x,\alpha )\in i} p_i(x,\alpha)$, where $p_i(x,\alpha)$ is the probability of finding a given functional group $x$ in the position $\alpha$ of $i$.
-Then, by controlling for the variation at the network level with an LMM (see below), we calculated the average number of times that the functional group $x$ appears in the position $\alpha$ (denoted as $n_i(x,\alpha)$).
-To obtain the expected probability $p_i(x,\alpha)$, we divided the number of times that the group $x$ appears in the position $\alpha$ by the the total number of times that any group was observed in that position (that is, $p_i(x,\alpha) = n_i(x,\alpha)/\sum_{k}n_i(k,\alpha)$).
-The average number of times that the group $x$ appears in the position $\alpha$ ($n_i(x,\alpha)$) was calculated with a LMM for each position, where the response variable was the number of times that a group was observed at a given position in each real-world network, the explanatory variable was the group identifier, and the random intercept was given by network identifiers nested within the study identifiers.
-
-Once we obtained $p_i^O$ and $p_i^E$, we used a simulation approach to determine whether the former is likely to come from the latter or not.
-This approach was preferred since the large number of possible subgraph combinations and the small probabilities for some of them advise against using an exact test of goodness-of-fit or a Chi-square one.
-Specifically, we created 1,000 random samples with repetition of possible subgraph combinations, where each sample contained 10 million elements and, for each combination, the probability of being selected was equal to its expected probability.
-From those random samples, we extracted the mean and the standard deviation of the expected probability of $i$, denoted as $E\left [ p_i^E \right ]$ and $\sigma\left [ p_i^E \right ]$, respectively, and calculated the z-scores of $p_i^O$ as $z_i^O = \left ( p_i^O - E\left [ p_i^E \right ] \right )/\sigma \left [ p_i^E \right ]$, for those motif combinations with $p_i^O > 0$.
-According to the usual interpretation of z-scores, combinations with $z_i^O > 1.96$ are over-represented, whereas those with $z_i^O < -1.96$ are under-represented, at the 95$\%$ confidence level.
-Notice that we focused on combinations with $p_i^O > 10^{-7}$ because we do not have enough numerical resolution to accurately detect whether combinations that took place only once are under-represented (due to the limited size of our random samples).
-
-All analyses and data manipulation were conducted in R *version 4.0.5* [@R].
-In addition, all model diagnostics were conducted with the help of the *Dharma* package [@hartig2017] version *0.3.3.0* and model outputs were visualised with the *visreg* package [@breheny2020] version 2.7.0.
-
-# RESULTS
-
-**Plant and floral visitor functional groups**
-
-The hierarchical cluster analysis divided the dataset into five different plant functional groups with different and overlapping characteristics (Figs S4 and S5).
-The first group referred to as 'selfing herbs' consisted of herbs with hermaphroditic flowers with high levels of autonomous selfing.
-The second group named 'small outcrossing perennials' had small perennial species with a mix of life forms (i.e., trees, shrubs and herbs) with outcrossing hermaphroditic flowers.
-The third group referred to as 'self-incompatible perennials with large flowers' comprised perennial species with a mixed of life forms and large self-incompatible hermaphroditic flowers with high number of ovules.
-The fourth group named 'tall plants with small unisexual flowers' had the tallest species, highest proportion of shrub and tree life forms, dioecious and monoecious breeding systems, small flowers, and the highest numbers of flowers and inflorescences per plant.
-Finally, the fifth group named 'short-lived outcrossers with long zygomorphic flowers' consisted of small perennial and short-lived herbs with long self-compatible zygomorphic flowers that were unable to self-pollinate.
-
-In total, there were 1,126 species of floral visitors with 6,325 interactions recorded with plants.
-Most plants interacted with bees (2,256 interactions) and non-syrphid Diptera (1,768) followed by syrphids (845), Lepidoptera (437), Coleoptera (432) and non-bee Hymenoptera (362).
-
-**Overall network subgraphs patterns**
-
-Most network subgraphs were under- or over-represented (close to the 1st and 99th percentile, respectively) in the comparison between empirical and simulated networks (Fig.
-2).
-Network subgraphs 3, 5, 9, 10 and 14 were under-represented in empirical networks, that is, all were close to the 1st percentile and under the 25th percentile.
-Interestingly, four out of five of these motifs belonged to the largest path length classification (i.e., core-peripheral).
-In addition, network subgraphs 2, 6, 7, 16 and 17 were over-represented, all over the 75th percentile.
-In contrast to the under-represented network subgraphs, over-represented subgraphs belonged to the two shortest path length groups (i.e., complete and fan).
-The remaining network subgraphs (i.e., 4, 8, 11, 12, 13, and 15) were between the 25th and 75th percentile.
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure 2.** Comparison of network subgraph frequencies between empirical and simulated networks grouped by average path length (plots a, b, c and d) where $\\overline{x}$ indicates the mean of the average path lengths of all subgraphs within each group (strong, medium-strong, medium-weak and weak).
-This comparison is shown with the mean percentage of subgraph frequencies in empirical networks that were over the subgraph frequencies of the simulated ones (percentiles).
-This was done by network (light blue transparent dots) and then averaged for all networks (black dots with error bars that correspond to the standard deviation)."}
-
-library(lme4)
-library(nlme)
-library(tidyverse)
-source("../../Scripts/Scripts_Alfonso/add_study_id.R")
-d <- read_csv("../../Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
-d <- add_study_id(d)
-#str(d)
-#head(d)
-
-#ggplot(d %>% filter(motif != 1), aes(percentil_sizeclass))+
-#  geom_histogram(color="black", fill="white")+
-#  facet_wrap(~motif)+
-#  theme_bw()+
-#  labs(x="Sizeclass percentile")
-#
-# Motifs tend to be over- and under-represensented in real networks
-
-# Mean percentile and SE taking into account the study system
-motif_codes <- d %>% filter(motif != 1) %>% # We remove links (motif code: 1)
-  select(motif) %>% unique() %>% pull()
-motif_means <- tibble(motif = motif_codes)
-motif_means$mean <- NA
-motif_means$SE <- NA
-
-for(i.motif in 1:length(motif_codes)){
-
-  m <- lmer(percentil_sizeclass ~ 1+(1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = subset(d, motif == motif_codes[i.motif]))
-
-  motif_means$mean[i.motif] <- fixed.effects(m) %>% unname()
-  motif_means$SE[i.motif] <- sqrt(diag(vcov(m)))
-
-}
-
-#Add categories based on path length set by Simmons 2021 et al., Functional Ecology
-d$Broad_categories[d$motif==2 | d$motif==7 | d$motif==17 | d$motif==3|d$motif==4|d$motif==8] <- "Fan"
-
-d$Broad_categories[d$motif==15 | d$motif==11] <- "Medium-weak"
-
-d$Broad_categories[d$motif==6 | d$motif==16 |  d$motif==12] <- "Strong"
-
-d$Broad_categories[d$motif==5 | d$motif==9 |  d$motif==14|  d$motif==13|  d$motif==10] <- "Weak"
-
-#order the categories from short to long path length
-d$Broad_categories <- factor(d$Broad_categories, levels = c("Strong", "Fan", "Medium-weak", "Weak"))
-
-#Ffilter out two node motifs
-d_1 <- d %>% filter(motif != 1)
-#Merge dataframes to bl able to create facets
-d_2 <- merge(d_1, motif_means, by="motif")
-
-arr <- list('Strong' = expression(bold(paste("(a) Strong (Complete, ", bar(x), " = 1.38)"))),
-             'Fan' = expression(bold(paste("(b) Medium-strong (fan, ", bar(x), " = 1.48)"))), 
-             'Medium-weak' = expression(bold(paste("(c) Medium-weak (asymmetric complete, ", bar(x), " = 1.60)"))), 
-             "Weak" =expression(bold(paste("(d) Weak (core-peripheral, ", bar(x), " = 1.85)"))))
-mylabel <- function(val) { return(lapply(val, function(x) arr[x])) }
-
-library(ggforce) #workaround with ggforce to have facets with same sizes 
-library(ggtext)
-
-labels <- c("2" = "*Subgraph 2* <img src='../../Images/motif_2.png' width='22'/>" ,
-          "3"= "*Subgraph 3* <img src='../../Images/motif_3.png' width='22'/>",
-          "4"= "*Subgraph 4* <img src='../../Images/motif_4.png' width='22'/>",
-          "5"= "*Subgraph 5* <img src='../../Images/motif_5.png' width='22'/>",
-          "6"= "*Subgraph 6* <img src='../../Images/motif_6.png' width='22'/>",
-          "7"= "*Subgraph 7* <img src='../../Images/motif_7.png' width='22'/>",
-          "8"= "*Subgraph 8* <img src='../../Images/motif_8.png' width='22'/>",
-          "9"= "*Subgraph 9* <img src='../../Images/motif_9.png' width='22'/>",
-          "10"= "*Subgraph 10* <img src='../../Images/motif_10.png' width='22'/>",
-          "11"= "*Subgraph 11* <img src='../../Images/motif_11.png' width='22'/>",
-          "12"= "*Subgraph 12* <img src='../../Images/motif_12.png' width='22'/>",
-          "13"= "*Subgraph 13* <img src='../../Images/motif_13.png' width='22'/>",
-          "14"= "*Subgraph 14* <img src='../../Images/motif_14.png' width='22'/>",
-          "15"= "*Subgraph 15* <img src='../../Images/motif_15.png' width='22'/>",
-          "16"= "*Subgraph 16* <img src='../../Images/motif_16.png' width='22'/>",
-          "17"= "*Subgraph 17* <img src='../../Images/motif_17.png' width='22'/>")
-
-p <- ggplot()+geom_point(data = d_2 , aes(y=factor(motif), 100*percentil_sizeclass), shape=21,color="black",fill="azure2",size=1.75, alpha=0.3)+
-  geom_errorbar(data = d_2,aes(y = factor(motif), xmin=100*(mean-SE), xmax=100*(mean+SE)), 
-                width=0.8,size=0.8,color="black") +theme_bw()+
-  geom_point(data = d_2,aes(y = as.factor(motif), x=100*mean), 
-             size=2,color="black")+labs(y="Two to five node motifs", x = "Percentile")+
-  theme( strip.background = element_blank())+
-  theme(strip.text = element_text(face="bold", size=10, hjust=0),
-        panel.border=element_rect(color="black",size=1.2))+
-  scale_y_discrete(name = NULL,
-                   labels = labels) +
-  theme(axis.text.y = ggtext::element_markdown())
-
-p + ggforce::facet_col(vars(Broad_categories), scales = 'free', space = 'free',labeller=mylabel)
-
-#Trying to maintain a gradient from low to high in colors
-
-#Fig 1 Should be a dot plot (or forest plot) of the mean +- SE of the 15 motifs.
-#NICE! Can we put motifs in Y axes, and % in X?
-```
-
-**Over- and under-represented functional groups on subgraph positions**
-
-```{r , include=FALSE}
-
-#SAME SCRIPT AS THE PLOTTING FOR THE HEATMAP BUT I NEED IT HERE TO LOAD THE VARIABLES WITH VALUES ON RESULTS
-
-library(lme4)
-library(nlme)
-library(tidyverse)
-library(stringi)
-source("../../Scripts/Scripts_Alfonso/add_study_id.R")
-
-#############################################
-# EXTRACT MEAN VALUES
-#############################################
-all_position_percentiles <- read_csv("../../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
-
-all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
-                                                              "[0-9]+") %>% as.numeric()
-
-all_position_percentiles <- add_study_id(all_position_percentiles)
-#str(all_position_percentiles)
-#head(all_position_percentiles)
-
-list_plants_FG <- as.character(1:10)
-
-plant_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF)) #ME DA ERROR
-pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF))
-
-# Plants-------------
-
-# Mean percentile and SE taking into account the study system
-plant_codes <- plant_position_percentiles_filtered$position %>% unique()
-plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-plant_means$mean <- NA
-plant_means$SE <- NA
-
-for(i.pos in 1:length(plant_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
-            data = plant_position_percentiles_filtered %>%
-              filter(position == plant_codes[i.pos]))
-
-  temp <- fixed.effects(m) %>% unname()
-  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
-                                                                    temp[1]+temp[2],
-                                                                    temp[1]+temp[3],
-                                                                    temp[1]+temp[4],
-                                                                    temp[1]+temp[5]) ## to get real means per FG
-  temp <- sqrt(diag(vcov(m)))
-  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
-                                                                  temp[1]+temp[2],
-                                                                  temp[1]+temp[3],
-                                                                  temp[1]+temp[4],
-                                                                  temp[1]+temp[5])
-
-}
-
-# Pollinators--------
-
-# Mean percentile and SE taking into account the study system
-pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
-pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-pollinator_means$mean <- NA
-pollinator_means$SE <- NA
-pollinator_means_reordered <- NULL
-
-for(i.pos in 1:length(pollinator_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = pollinator_position_percentiles_filtered %>%
-              filter(position == pollinator_codes[i.pos]),
-            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
-
-  temp <- fixed.effects(m) %>% unname()
-  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)
-
-  pollinator_means_aux$mean <- c(temp[1],
-                                 temp[1]+temp[2],
-                                 temp[1]+temp[3],
-                                 temp[1]+temp[4],
-                                 temp[1]+temp[5],
-                                 temp[1]+temp[6],
-                                 temp[1]+temp[7],
-                                 temp[1]+temp[8],
-                                 temp[1]+temp[9]) ## to get real means per FG
-
-  temp <- sqrt(diag(vcov(m)))
-  pollinator_means_aux$SE <- c(temp[1],
-                               temp[1]+temp[2],
-                               temp[1]+temp[3],
-                               temp[1]+temp[4],
-                               temp[1]+temp[5],
-                               temp[1]+temp[6],
-                               temp[1]+temp[7],
-                               temp[1]+temp[8],
-                               temp[1]+temp[9])
-
-  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)
-
-}
-
-# There are lower limits (mean - SE) smaller than 0 (see Other insects)
-# We set the lower limit of those error bars to zero
-
-pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
-pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
-
-#############################################
-# ADDING BROAD MOTIF CATEGORIES TO POSITIONS
-#############################################
-
-motifs_raw_data <- read_csv("../../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-motifs_raw_data$Broad_categories <- NA
-
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(5,9,14,13,10)] <- "Core-peripherical"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(6,16,12)] <- "Complete"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(2,3,7,4,17,8)] <- "Fan"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(15,11)] <- "Asymmetric complete"
-
-motifs_raw_data$plant <- gsub("[^0-9.-]", "", motifs_raw_data$plant)
-motifs_raw_data$pollinator <- gsub("[^0-9.-]", "", motifs_raw_data$pollinator)
-motifs_raw_data$plant <- as.numeric(motifs_raw_data$plant)
-motifs_raw_data$pollinator <- as.numeric(motifs_raw_data$pollinator)
-motifs_raw_data <- motifs_raw_data %>% filter(!is.na(Broad_categories))
-
-fan_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-pollinator_means_reordered$Broad_categories <- NA
-
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% fan_pollinator] <- "Fan" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% asymm_pollinator] <- "Medium-weak" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% complete_pollinator] <- "Strong" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% core_per_pollinator] <- "Weak"
-
-fan_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-plant_means$Broad_categories <- NA
-
-plant_means$Broad_categories[plant_means$position %in% fan_plant] <- "Fan" 
-plant_means$Broad_categories[plant_means$position %in% asymm_plant] <- "Medium-weak" 
-plant_means$Broad_categories[plant_means$position %in% complete_plant] <- "Strong" 
-plant_means$Broad_categories[plant_means$position %in% core_per_plant] <- "Weak"
-
-################################################################################
-# Alternative code to HEATMAPS to create variables with values to load on text
-# in a reproducible/automated way
-################################################################################
-
-# PLANTS-----
-
-# Prepare data for heatmap
-heat_plants_aux <- plant_means %>% spread(Node_FG,mean) %>% select(-SE)
-
-heat_plants <- heat_plants_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-# POLLINATORS-----------
-
-filter_rare_groups <- T
-
-if(filter_rare_groups == T){
-  heat_pollinators_aux <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds",
-                                                                                "Lizards",
-                                                                                "Other_insects")) %>% 
-    spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees",            
-                                      "Coleoptera","Lepidoptera","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Syrphids")
-}else{
-  heat_pollinators_aux <- pollinator_means_reordered %>% spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees","Birds",            
-                                      "Coleoptera","Lepidoptera","Lizards","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Other insects","Syrphids")
-}
-
-heat_pollinators <- heat_pollinators_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))
-
-#Check percentage of over and under represented
-colMeans(heat_pollinators[,c(3:8)] < 0.25)
-poll_under_25 <- colMeans(heat_pollinators[,c(3:8)] < 0.25)
-poll_under_25 <- specify_decimal((poll_under_25[[1]] + poll_under_25[[2]] + poll_under_25[[3]] +
-poll_under_25[[4]] + poll_under_25[[5]] + poll_under_25[[6]])/6*100,2)
-#[1] 32.57576
-
-colMeans(heat_pollinators[,c(3:8)] > 0.75)
-poll_over_75 <- colMeans(heat_pollinators[,c(3:8)] > 0.75)
-poll_over_75 <- specify_decimal((poll_over_75[[1]] + poll_over_75[[2]] + poll_over_75[[3]] +
-    poll_over_75[[4]] + poll_over_75[[5]] + poll_over_75[[6]])/6*100,2)
-#[1] 4.545455
-
-#################################################################################
-#################################################################################
-
-colnames(heat_plants)<- c("position", "Broad_categories", "one",
-                               "two", "three","four",
-                               "five")
-f <- heat_plants %>%
-  mutate(min = pmin(1,
-                    one, two,three,
-                    four, five))%>%
-  mutate(max = pmax(one,
-                    two, three,four,
-                    five))
-
-diff_1 <- f$max-f$min
-
-cbind(diff,diff_1)
-
-#Check percentage of over and under represented per FG
-colMeans(heat_plants[,c(3:7)] < 0.25)
-plant_under_25 <- colMeans(heat_plants[,c(3:7)] < 0.25)
-plant_under_25 <- specify_decimal((plant_under_25[[1]] + plant_under_25[[2]] + plant_under_25[[3]] + 
-    plant_under_25[[4]] + plant_under_25[[5]])/5*100,2)
-#[1] 18.18182
-colMeans(heat_plants[,c(3:7)] > 0.75)
-plant_over_75 <- colMeans(heat_plants[,c(3:7)] > 0.75)
-plant_over_75 <- specify_decimal((plant_over_75[[1]] + plant_over_75[[2]] + plant_over_75[[3]] + 
-    plant_over_75[[4]] + plant_over_75[[5]])/5*100,2)
-#[1] 8.181818
-
-#overall percentages
-under <- specify_decimal((as.numeric(poll_under_25) + as.numeric(plant_under_25))/2,2)
-over <- specify_decimal((as.numeric(poll_over_75) + as.numeric(plant_over_75))/2,2)
-
-```
-
-The comparison of the plant and floral visitor functional group frequencies per subgraph position between empirical and simulated networks showed a `r over`$\%$ and `r under`$\%$ of over- (>75$^{th}$) and under-represented (\<25th) functional groups in the different positions, respectively (Fig.
-3).
-Floral visitors showed a total of `r poll_over_75`$\%$ and `r poll_under_25`$\%$ of over- and under-represented functional groups in the different positions, and plants `r plant_over_75`$\%$ and `r plant_under_25`$\%$ of over- and under-represented functional groups, respectively.
-Notably, the differences across functional groups were more marked for floral visitors than for plants (the differences between the minimum and maximum values of the percentiles per position were generally two-three times larger for floral visitors).
-From most over- to under-represented floral visitors functional groups on the different subgraph positions (indicated with the dendrogram order in Fig.
-3), we found: bees, non-syrphids Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.
-Although plant functional groups showed less differences between them, there were also more represented functional groups than others.
-Thus, from most over- to under-represented functional groups on the different subgraph positions we found: self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.
-
-For both floral visitor and plant functional groups we found over- and under-representation on different subgraph positions that implied different ecological roles.
-First, for floral visitors, we found that bees were less frequent on subgraph positions that involved specialisation (i.e., lower specificity values) while the rest of functional groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) were infrequent in generalised subgraph positions with low number of indirect interactions (Fig.
-S6 A).
-Although plants did not show differences with null models on their frequencies, all plant functional groups but tall plants with small unisexual flowers showed a slight tendency to be over-represented on specialised subgraph positions (Fig.
-S6 B).
-Second, regarding the number of indirect interactions, bees were over-represented in subgraph positions with low number of indirect interactions (Fig.
-S7 A) and the rest of floral visitor functional groups showed no differences across positions in comparison with simulated networks.
-For plants, all functional groups showed a slight tendency to be over-represented on subgraph positions with higher number of indirect interactions (Fig.
-S7 B).
-When we further explore the observed frequencies by number of indirect interactions for floral visitor and plant functional groups, we found that both bees and tall plants with small unisexual flowers were the only functional groups with high frequencies on subgraph positions associated with low number of indirect interactions in comparison with the other floral visitor and plant functional groups (Figs S8 and S9).
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', out.width="80%",fig.cap="\\textbf{Figure 3.} Heatmap indicating under- and over-representation of floral visitor and plant functional groups in the different subgraph positions (numbers on the right of each heatmap).
-The different subgraph positions are dividied by the average path length clasification determined by Simmons et al.
-(2020) and they are ordered from the most densely connected network structures (strong or complete) to the less connected ones (weak or core-peripheral).
-The superior dendrogram indicates the differences across functional groups with the more separated groups showing larger differences."}
-
-library(lme4)
-library(nlme)
-library(tidyverse)
-library(stringi)
-source("../../Scripts/Scripts_Alfonso/add_study_id.R")
-
-#############################################
-# EXTRACT MEAN VALUES
-#############################################
-
-all_position_percentiles <- read_csv("../../Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")
-
-all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
-                                                              "[0-9]+") %>% as.numeric()
-
-all_position_percentiles <- add_study_id(all_position_percentiles)
-#str(all_position_percentiles)
-#head(all_position_percentiles)
-
-list_plants_FG <- as.character(1:10)
-
-plant_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF)) #ME DA ERROR
-pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
-  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
-         !is.na(expected_freq_its_GF))
-
-# Plants-------------
-
-# Mean percentile and SE taking into account the study system
-plant_codes <- plant_position_percentiles_filtered$position %>% unique()
-plant_means <- plant_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-plant_means$mean <- NA
-plant_means$SE <- NA
-
-for(i.pos in 1:length(plant_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id),
-            data = plant_position_percentiles_filtered %>%
-              filter(position == plant_codes[i.pos]))
-
-  temp <- fixed.effects(m) %>% unname()
-  plant_means$mean[plant_means$position == plant_codes[i.pos]] <- c(temp[1],
-                                                                    temp[1]+temp[2],
-                                                                    temp[1]+temp[3],
-                                                                    temp[1]+temp[4],
-                                                                    temp[1]+temp[5]) ## to get real means per FG
-  temp <- sqrt(diag(vcov(m)))
-  plant_means$SE[plant_means$position == plant_codes[i.pos]] <- c(temp[1], 
-                                                                  temp[1]+temp[2],
-                                                                  temp[1]+temp[3],
-                                                                  temp[1]+temp[4],
-                                                                  temp[1]+temp[5])
-
-}
-
-# Pollinators--------
-
-# Mean percentile and SE taking into account the study system
-pollinator_codes <- pollinator_position_percentiles_filtered$position %>% unique()
-pollinator_means <- pollinator_position_percentiles_filtered %>% select(position,Node_FG) %>% unique()
-pollinator_means$mean <- NA
-pollinator_means$SE <- NA
-pollinator_means_reordered <- NULL
-
-for(i.pos in 1:length(pollinator_codes)){
-
-  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
-            data = pollinator_position_percentiles_filtered %>%
-              filter(position == pollinator_codes[i.pos]),
-            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
-
-  temp <- fixed.effects(m) %>% unname()
-  pollinator_means_aux <- pollinator_means[pollinator_means$position == pollinator_codes[i.pos],] %>% arrange(Node_FG)
-
-  pollinator_means_aux$mean <- c(temp[1],
-                                 temp[1]+temp[2],
-                                 temp[1]+temp[3],
-                                 temp[1]+temp[4],
-                                 temp[1]+temp[5],
-                                 temp[1]+temp[6],
-                                 temp[1]+temp[7],
-                                 temp[1]+temp[8],
-                                 temp[1]+temp[9]) ## to get real means per FG
-
-  temp <- sqrt(diag(vcov(m)))
-  pollinator_means_aux$SE <- c(temp[1],
-                               temp[1]+temp[2],
-                               temp[1]+temp[3],
-                               temp[1]+temp[4],
-                               temp[1]+temp[5],
-                               temp[1]+temp[6],
-                               temp[1]+temp[7],
-                               temp[1]+temp[8],
-                               temp[1]+temp[9])
-
-  pollinator_means_reordered <- bind_rows(pollinator_means_reordered,pollinator_means_aux)
-
-}
-
-# There are lower limits (mean - SE) smaller than 0 (see Other insects)
-# We set the lower limit of those error bars to zero
-
-pollinator_means_reordered <- pollinator_means_reordered %>% mutate(lower = mean-SE)
-pollinator_means_reordered$lower[pollinator_means_reordered$lower < 0] <- 0
-
-#############################################
-# ADDING BROAD MOTIF CATEGORIES TO POSITIONS
-#############################################
-
-motifs_raw_data <- read_csv("../../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-motifs_raw_data$Broad_categories <- NA
-
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(5,9,14,13,10)] <- "Core-peripherical"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(6,16,12)] <- "Complete"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(2,3,7,4,17,8)] <- "Fan"
-motifs_raw_data$Broad_categories[motifs_raw_data$motif_id %in% c(15,11)] <- "Asymmetric complete"
-
-motifs_raw_data$plant <- gsub("[^0-9.-]", "", motifs_raw_data$plant)
-motifs_raw_data$pollinator <- gsub("[^0-9.-]", "", motifs_raw_data$pollinator)
-motifs_raw_data$plant <- as.numeric(motifs_raw_data$plant)
-motifs_raw_data$pollinator <- as.numeric(motifs_raw_data$pollinator)
-motifs_raw_data <- motifs_raw_data %>% filter(!is.na(Broad_categories))
-
-fan_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_pollinator <- motifs_raw_data$pollinator[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-pollinator_means_reordered$Broad_categories <- NA
-
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% fan_pollinator] <- "Fan" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% asymm_pollinator] <- "Medium-weak" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% complete_pollinator] <- "Strong" 
-pollinator_means_reordered$Broad_categories[pollinator_means_reordered$position %in% core_per_pollinator] <- "Weak"
-
-fan_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Fan"] %>% unique()
-core_per_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Core-peripherical"] %>% unique()
-complete_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Complete"] %>% unique()
-asymm_plant <- motifs_raw_data$plant[motifs_raw_data$Broad_categories == "Asymmetric complete"] %>% unique()
-
-plant_means$Broad_categories <- NA
-
-plant_means$Broad_categories[plant_means$position %in% fan_plant] <- "Fan" 
-plant_means$Broad_categories[plant_means$position %in% asymm_plant] <- "Medium-weak" 
-plant_means$Broad_categories[plant_means$position %in% complete_plant] <- "Strong" 
-plant_means$Broad_categories[plant_means$position %in% core_per_plant] <- "Weak"
-
-########################################
-# CREATE HEATMAPS
-########################################
-
-library(ComplexHeatmap)
-
-# PLANTS-----
-
-# Prepare data for heatmap
-heat_plants_aux <- plant_means %>% spread(Node_FG,mean) %>% select(-SE)
-
-heat_plants <- heat_plants_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-heat_plants_fan <- heat_plants %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_fan) <- heat_plants_fan[,1]
-
-heat_plants_Weak <- heat_plants %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Weak) <- heat_plants_Weak[,1]
-
-heat_plants_Strong <- heat_plants %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Strong) <- heat_plants_Strong[,1]
-
-heat_plants_Medium_weak <- heat_plants %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_plants_Medium_weak) <- heat_plants_Medium_weak[,1]
-
-# POLLINATORS-----------
-
-filter_rare_groups <- T
-
-if(filter_rare_groups == T){
-  heat_pollinators_aux <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds",
-                                                                                "Lizards",
-                                                                                "Other_insects")) %>% 
-    spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees",            
-                                      "Coleoptera","Lepidoptera","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Syrphids")
-}else{
-  heat_pollinators_aux <- pollinator_means_reordered %>% spread(Node_FG,mean) %>% select(-SE,-lower)
-
-  colnames(heat_pollinators_aux) <- c("position","Broad_categories","Bees","Birds",            
-                                      "Coleoptera","Lepidoptera","Lizards","Non-bee\nHymenoptera", 
-                                      "Non-syrphids\nDiptera","Other insects","Syrphids")
-}
-
-heat_pollinators <- heat_pollinators_aux %>%
-  group_by(position,Broad_categories) %>% 
-  summarise_all(sum,na.rm = T)
-
-heat_pollinators_fan <- heat_pollinators %>% filter(Broad_categories == "Fan") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_fan) <- heat_pollinators_fan[,1]
-
-heat_pollinators_Weak <- heat_pollinators %>% filter(Broad_categories == "Weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Weak) <- heat_pollinators_Weak[,1]
-
-heat_pollinators_Strong <- heat_pollinators %>% filter(Broad_categories == "Strong") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Strong) <- heat_pollinators_Strong[,1]
-
-heat_pollinators_Medium_weak <- heat_pollinators %>% filter(Broad_categories == "Medium-weak") %>% select(-Broad_categories) %>% 
-  as.matrix()
-
-rownames(heat_pollinators_Medium_weak) <- heat_pollinators_Medium_weak[,1]
-
-##################
-
-#Do not know how to handle this multiplot for creating a panel
-
-# I'm going to create the 4 plots in one, 
-# I'm not sure that the grouping of the functional group is correct
-# when is done separately
-
-#sorry for the mess of libraries that I do below
-
-#Prepare first pollinators
-
-library(tidyr)
-library(data.table)
-long <- melt(setDT(heat_pollinators), id.vars = c("position","Broad_categories"), variable.name = "guilds")
-
-long_1 <- long %>% select(-Broad_categories)
-
-library(reshape2)
-long_m <- acast(long_1, position~guilds, value.var="value")
-
-#set manually the divisions, so far this is the best way I have seen to split the rows by categories
-
-r_split <- c(rep(c("Medium"), 3),rep(c("Weak"), 2),"Strong",rep(c("Medium"),2),rep(c("Weak"), 4),
-             rep(c("Medium-weak"), 2), "Strong", rep(c("Weak"), 3),rep(c("Medium-weak"), 2),
-             "Strong", "Medium")
-
-#set order of labels that avoids overlapping
-
-r_split <- factor(r_split, levels=c("Strong","Medium","Medium-weak","Weak"))
-
-#plat a bit with colors, a bit of a more complex set but looks nicer
-library(circlize)
-col_fun = colorRamp2(c(0.05644663,0.25, 0.4673256,0.75, 0.8782047), c("blue","cadetblue3", "azure2", "gold","red"))
-
-h_pol <- Heatmap(long_m, name = "Mean\npercentile", row_split=r_split,cluster_row_slices = FALSE, 
-                 column_title = "Pollinator functional groups",row_names_gp = gpar(fontsize = 10),
-                 col = col_fun,column_names_rot = 45,  column_names_gp = grid::gpar(fontsize = 10),
-                 column_title_gp = gpar(fontsize = 15, fontface = "bold"),
-                 row_title_gp = gpar(fontsize = 10, fontface = "bold"))
-
-#Prepare plants
-
-#long format
-long_plants <- melt(setDT(heat_plants), id.vars = c("position","Broad_categories"), variable.name = "Functional_groups")
-
-#filter for creating matrix
-long_plants_1 <- long_plants %>% select(-Broad_categories)
-
-#set better colnames
-long_plants_1$Functional_groups <- as.character(long_plants_1$Functional_groups)
-
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==1] <- "Selfing herbs" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==2] <- "Small outcrossing\nperennials" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==3] <- "Self-incomp. perennials\nwith large flowers" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==4] <- "Tall plants with small\nunisexual flowers" 
-long_plants_1$Functional_groups[long_plants_1$Functional_groups==5] <- "Short-lived outcrossers with\nlong zygomorphic flowers"
-
-long_plants_1$Functional_groups <- factor(long_plants_1$Functional_groups, levels=c("Selfing herbs",
-"Small outcrossing\nperennials" ,"Self-incomp. perennials\nwith large flowers",
-"Tall plants with small\nunisexual flowers" ,"Short-lived outcrossers with\nlong zygomorphic flowers" ))
-
-#create matrix with reshape
-long_plants_m <- acast(long_plants_1, position~Functional_groups, value.var="value")
-
-r_split_plants <- c(rep(c("Medium"), 3),rep(c("Weak"), 2),"Strong",rep(c("Medium"),2),rep(c("Weak"), 3),
-                    rep(c("Medium-weak"), 2), "Strong", rep(c("Weak"), 4),rep(c("Medium-weak"), 2),
-                    "Strong", "Medium")
-
-r_split_plants <- factor(r_split, levels=c("Strong","Medium","Medium-weak","Weak"))
-
-h_plan <- Heatmap(long_plants_m, name = "Mean\npercentile", row_split=r_split_plants,cluster_row_slices = F, 
-                  column_title = "Plant functional groups",row_names_gp = gpar(fontsize = 10),col = col_fun,column_names_rot = 45,  
-                  column_names_gp = grid::gpar(fontsize = 10),column_title_gp = gpar(fontsize = 15, fontface = "bold"),
-                  row_title_gp = gpar(fontsize = 10, fontface = "bold"))
-
-library(patchwork)
-ht_list <- h_pol+h_plan
-
-draw(ht_list, auto_adjust = FALSE, cluster_rows = F)
-
-#Exploration of min max differences in the percentile position for plants and poll.
-#heat_pollinators[3:8]
-#
-#
-#heat_plants[3:7]
-#
-#
-#library(dplyr)
-#heat_pollinators %>%
-#  mutate(d = pmin())
-#
-#
-#colnames(heat_pollinators)<- c("position", "Broad_categories", "Bee",
-#                               "Coleoptera", "Lepidoptera","non_bee_hymenop",
-#                               "non_syrphid_dip", "syrphid")
-#
-#h <- heat_pollinators %>%
-#  mutate(min = pmin(Bee,
-#                  Coleoptera, Lepidoptera,non_bee_hymenop,
-#                  non_syrphid_dip, syrphid))%>%
-#  mutate(max = pmax(Bee,
-#                    Coleoptera, Lepidoptera,non_bee_hymenop,
-#                    non_syrphid_dip, syrphid))
-#
-#diff <- h$max-h$min
-#
-##################################################################################
-##################################################################################
-#
-#colnames(heat_plants)<- c("position", "Broad_categories", "one",
-#                               "two", "three","four",
-#                               "five")
-#
-#f <- heat_plants %>%
-#  mutate(min = pmin(1,
-#                    one, two,three,
-#                    four, five))%>%
-#  mutate(max = pmax(one,
-#                    two, three,four,
-#                    five))
-#
-#diff_1 <- f$max-f$min
-#
-#cbind(diff,diff_1)
-#
-
-```
-
-**Over- and under-represented functional group combinations of subgraphs**
-
-The different observed frequencies on the different subgraph positions showed a hierarchical order of probabilities for floral visitor functional groups (Fig.
-4).
-From the highest to lowest observed probabilities overall, we found: bees, non-syrphid Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera.
-On the contrary, plant functional groups were more variable on the different subgraph positions.
-However, there were also predominant functional groups found across the different subgraph positions.
-The three most frequent groups were 'tall plants with small unisexual flowers', 'self-incompatible perennials with large flowers' and 'small outcrossing perennials'.
-On the contrary, the groups of 'selfing herbs' and 'short lived outcrossers with long zygomorphic flowers' had the lowest probability to be present on the different subgraph plant positions.
-
-```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 4.** Graphical representation of the probability of finding a given plant and floral visitor functional group $x$ in the position $\\alpha$ of motif $i$, $p_i(x,\\alpha)$, for all the possible network subgraphs from two to five species in bipartite networks.
-The slices in the nodes for a given functional group $x$ are proportional to the corresponding value of $p_i(x,\\alpha)$."}
-
-library(ggplot2)
-library(scatterpie)
-library(RColorBrewer)
-library(tidyverse)
-
-plant_means_reordered <- read_csv("../../Data/Csv/plant_abs_freq_means.csv")
-pollinator_means_reordered <- read_csv("../../Data/Csv/pollinator_abs_freq_means.csv")
-#Filter out in order to have just 6 FG'S
-pollinator_means_reordered <- pollinator_means_reordered %>% filter(!Node_FG %in% c("Birds", "Lizards", "Other_insects"))
-
-# Pollinator--------
-pollinator_pies <- pollinator_means_reordered %>% select(-mean, -SE) %>% 
-  spread(Node_FG,mean_natural_units)
-
-pollinator_pies$x <- 0
-pollinator_pies$y <- 0
-
-#ggplot() + geom_scatterpie(aes(x=x, y=y, group=position,r=5), 
-#                           data = pollinator_pies,
-#                           cols=as.character(c("Bee","Birds","Coleoptera","Lepidoptera",
-#                                               "Lizards","Non-bee-Hymenoptera",
-#                                               "Non-syrphids-diptera","Other_insects",
-#                                               "Syrphids")))+
-#  coord_equal()+
-#  scale_fill_brewer(palette = "Paired")+
-#  facet_wrap(~position,nrow = 3)+
-#  theme_bw()+
-#    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
-#          panel.background = element_blank(),
-#          axis.title.x=element_blank(),axis.text.x=element_blank(),
-#          axis.ticks.x=element_blank(),axis.title.y=element_blank(),
-#          axis.text.y=element_blank(),axis.ticks.y=element_blank(),
-#          legend.position="bottom")+
-#  labs(title = "Pollinator positions",fill=NULL)
-#    
-# plant--------
-plant_pies <- plant_means_reordered %>% select(-mean, -SE) %>% 
-  spread(Node_FG,mean_natural_units)
-
-plant_pies$x <- 0
-plant_pies$y <- 0
-
-#ggplot() + geom_scatterpie(aes(x=x, y=y, group=position,r=5), 
-#                           data = plant_pies,
-#                           cols=as.character(c("1","2","3","4","5")))+
-#  coord_equal()+
-#  scale_fill_brewer(palette = "Dark2")+
-#  facet_wrap(~position,nrow = 3)+
-#  theme_bw()+
-#  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
-#        panel.background = element_blank(),
-#        axis.title.x=element_blank(),axis.text.x=element_blank(),
-#        axis.ticks.x=element_blank(),axis.title.y=element_blank(),
-#        axis.text.y=element_blank(),axis.ticks.y=element_blank(),
-#        legend.position="bottom")+
-#  labs(title = "Plant positions",fill=NULL)
-#
-
-#################################
-# CREATE PIE-MOTIFS
-#################################
-
-equidistribution <- function(number_nodes){
-
-  x_width <- 5.5/(number_nodes+1)
-
-  x_result <- rep(-1.5,number_nodes)
-
-  for(i in 1:number_nodes){
-
-    x_result[i] <- x_result[i] + i*x_width
-
-  }
-
-  return(x_result)
-
-}
-
-plot_pie_motif_positions <- function(motif_number){
-  motifs_raw_data <- read_csv("../../Data/Data_processing/Motifs_connections/motif_pattern_connections.csv")
-
-  motif_data <- motifs_raw_data %>% filter(motif_id == motif_number)
-
-  # Create dataframe with node positions
-
-  labdown = motif_data$plant %>% unique()
-
-  xdown = equidistribution(length(labdown))
-
-  ydown = rep(0,length(labdown))
-
-  labup = motif_data$pollinator %>% unique()
-
-  xup = equidistribution(length(labup))
-
-  yup = rep(2,length(labup))
-
-  d_nodes=data.frame(x=c(xdown,xup),
-                     y=c(ydown,yup),
-                     label = c(labdown,labup))
-
-  # Create a dataframe with links
-
-  plant_positions <- data.frame(plant = labdown,
-                                xdown = xdown,
-                                ydown = ydown)
-
-  pollinator_positions <- data.frame(pollinator = labup,
-                                     xup = xup,
-                                     yup = yup)
-
-  link_df <- motif_data %>% left_join(plant_positions, by = "plant") %>% 
-    left_join(pollinator_positions, by = "pollinator")
-
-  # Before plotting the motif, we remove letters from the node position id
-
-  d_nodes$label <- gsub("[^0-9.-]", "", d_nodes$label)
-  plant_pies_aux <- plant_pies %>% select(-x,-y) %>% mutate(position = as.character(position))
-
-  d_nodes_plant <- d_nodes %>% rename(position = label) %>% 
-    left_join(plant_pies_aux, by = "position") %>% as_tibble() %>%
-    filter(!is.na(`1`))
-
-  pollinator_pies_aux <- pollinator_pies %>% select(-x,-y) %>% mutate(position = as.character(position))
-
-  d_nodes_pollinator <- d_nodes %>% rename(position = label) %>% 
-    left_join(pollinator_pies_aux, by = "position") %>% as_tibble() %>%
-    filter(!is.na(Bee))
-
-  # Define the number of colors you want
- mycolors <- c("#A6CEE3", "chocolate2",  "gold2", "#1F78B4","#B2DF8A",
-                     "gray58", "lightgoldenrod2","thistle2", "burlywood","lightcoral", "olivedrab3")
-
-  ggplot() +
-    scale_shape_identity() +
-    geom_segment(data = link_df, aes(x=xdown, y=ydown, xend = xup, yend = yup), 
-                 size = 1, color = "grey20")+  geom_scatterpie(aes(x=x, y=y, group=position,r=.45), 
-    data = d_nodes_pollinator, cols=as.character(c("Bee","Coleoptera","Lepidoptera","Non-bee-Hymenoptera", "Non-syrphids-diptera","Syrphids"))) +
-    geom_scatterpie(aes(x=x, y=y, group=position,r=0.45), 
-                    data = d_nodes_plant,
-                    cols=as.character(c("1","2","3","4","5")))+
-    coord_fixed()+
-    scale_fill_manual(values = mycolors,"test",
-      breaks=c("Bee","Coleoptera","Lepidoptera",
-               "Non-bee-Hymenoptera", "Non-syrphids-diptera",
-               "Syrphids","1","2","3","4","5"), labels=c("Bees","Coleoptera","Lepidoptera",
-"Non-bee-Hymenoptera", "Non-syrphids-Diptera","Syrphids", 
-          "Selfing herbs","Small outcrossing perennials","Self-incomp. perennials\nwith large flowers",
-          "Tall plants with small\nunisexual flowers","Short-lived outcrossers with\nlong zygomorphic flowers"))+
-    xlim(-1.5,4)+ ylim(-0.5,2.5)+
-    theme(panel.background = element_blank(),
-          axis.text.x=element_blank(),
-          axis.ticks.x=element_blank(),
-          axis.text.y=element_blank(),
-          axis.ticks.y=element_blank(),
-          legend.title = element_text(size=12, face="bold"),legend.background = element_rect(size=0.5, linetype="solid",colour ="black"))+
-    labs(x=NULL,y=NULL)+
-    guides(color = FALSE,fill=guide_legend(title="Functional groups"))+
-    ggtitle(paste0("Motif ",motif_number))+
-    theme(plot.title = element_text(hjust = 0.5),legend.key.size = unit(0.5, 'cm'))+
-    theme(plot.margin=unit(c(0,0,0,0),"cm"))
-}
-
-motif_number <- 1
-p1 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 2
-p2 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 3
-p3 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 4
-p4 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 5
-p5 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 6
-p6 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 7
-p7 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 8   
-p8 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 9
-p9 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 10
-p10 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 11
-p11 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 12
-p12 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 13
-p13 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 14
-p14 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 15
-p15 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 16
-p16 <- plot_pie_motif_positions(motif_number)
-
-motif_number <- 17
-p17 <- plot_pie_motif_positions(motif_number)
-
-library(patchwork)
-
-(p1 & ylab("2 species")| p2 & ylab("3 species") | p3  |plot_spacer()|plot_spacer())/ 
-  (p4 & ylab("4 species")| p5 | p6 | p7|plot_spacer())/ 
-  (p8  & ylab("5 species")| p9 | p10 | p11 | p12) / 
-  (p13 & ylab("5 species")| p14 | p15 | p16 | p17) + plot_layout(guides = 'collect') &
-  theme(axis.title.y = element_text(color="black", size=14, face="bold"),legend.position = "bottom")
-
-```
-
-The statistical comparison with z-scores between the observed and expected plant and floral visitor functional group combinations showed that we can not recover the observed combinations from its probability of occurrence.
-In fact, most combinations are under- or over- represented and follow a modified Gaussian distribution (Johnson's $S_U$) with 65$\%$ of under-represented group combinations, 20$\%$ of no statistical difference and 15$\%$ of under-represented ones (Fig.
-5).
-In addition, subgraphs with small node combinations (i.e., 2 and 3 nodes) only appeared as under-represented.
-Network subgraphs with 4 and 5 node combinations appeared in the three statistical categories, but 4 node subgraphs had a higher proportion in the under-represented category (10% in comparison with the 1$\%$ and the 3$\%$ of the no statistical difference and over-represented categories, respectively).
-Finally, 5 node subgraphs were in similar proportions in the no statistical difference and over-represented categories (99$\%$ and 97$\%$, respectively), but they appeared in lower proportion in the under-represented category (89$\%$).
-When we explored the identity on the different positions of the most probable subgraph combinations, we found that the most common plant and floral visitor functional groups were also the most probable on these plant and floral visitor combinations within the different subgraphs (lower panel Fig.
-5).
 
@@
     labs(x=NULL,y=NULL)+
-    ggtitle(paste0("Motif ",motif_number))+
-    theme(plot.title = element_text(hjust = 0.5,size=10))+
+    ggtitle(paste0("Subgraph ",motif_number))+
+    theme(plot.title = element_text(hjust = 0.5,size=10), legend.title = element_text(face = "bold"))+
     guides(color=guide_legend(title="Functional groups"))
@@
   xlim(-60,60) + ylab("Frequency")+  theme_bw() + 
+  theme(legend.title = element_text(face = "bold")) +
     scale_fill_manual(name="Motif frequencies" ,values=c("coral2", "palegreen3", "cyan3"), labels=c("Under-represented",
@@
 ```
-
-# Discussion
-
-Understanding the global patterns of network structure is key to unravel the processes that govern community dynamics [@bascompte2007; @bastolla2009; @guimaraes2020].
-However, common analytical approaches at the node or at the global network level are unable to capture the full complexity of ecological systems [@simmons2019; @bergamo2021].
-Because network subgraphs can capture both direct and indirect interactions, by analysing their over- and under-representation we were able to explore in great detail the structure of interactions between animal pollinators and the plants they visit.
-We have explored for the first time the overall structure and presence of network motifs in real plant-pollinator networks and shown that, according to our first hypothesis, the different subgraphs up to five nodes are consistently over- or under-represented in comparison with simulated networks.
-In addition, we show that for plant-pollinator networks there is a general tendency for over-representation of network subgraphs that are more densely connected (i.e., complete, fan and asymmetric complete).
-Indeed, the work of @simmons2020 has shown with the help of simulated plant-pollinator networks that the main different processes that shape plant-pollinator communities (i.e., neutral effects, trait matching and phenology) generate different patterns of direct and indirect interactions, and that specifically, a higher proportion of these more densely connected subgraphs is associated with neutral effects.
-Therefore, as indicated for other network properties like nestedness at the macro-scale level [@krishna2008; @suweis2013], or interaction probability at the species level [@bartomeus2016], our findings align with our second hypothesis and indicate that neutral effects may be also the main driver governing this intermediate level of complexity on plant-pollinator networks.
-
-Overall, generalist network motifs for floral visitors were consistently over-represented (e.g., complete subgraphs; Fig.
-2).
-For instance, when we compare network subgraphs with equal structure for both trophic levels, we found that floral visitors had always over-representation in the positions that implied the highest number of direct links (e.g., positions 16 and 46 from network subgraphs 7 and 17, respectively).
-Despite this being in good agreement with the current view of the generalist nature of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of generalist network motifs was driven by the functional group of bees while the rest of the functional groups tended to be under-represented (Fig.
-S6 A).
-In contrast, non-bee groups were over-represented in subgraph positions associated with specialised roles.
-This large effect of bees on the overall patterns is no surprise, as bees were the group with the largest number of interaction records in the whole set of networks as also shown for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017].
-Just syrphids had a relatively similar number of interactions in comparison with bees (1,768 and 2,256 interactions, respectively) and similar species richness (343 and 321 species, respectively).
-However, both functional groups were associated with contrasting ecological roles likely indicating that both number of interactions and richness are not driving the observed interaction patterns for the different functional groups.
-Interestingly, bees also were the group with lower number of indirect interactions, while the rest of floral visitor groups showed a clearly higher number of indirect interactions, indicating that these non-bee floral visitor groups may experience higher competitive interactions for floral resources [@thomson2020].
-Despite plant functional groups showed little differences between them on their subgraph frequencies, all groups showed a tendency to be over-represented on subgraph positions that were associated with higher levels of specialisation.
-This tendency towards specialist roles may be the result of co-evolutionary processes (e.g., trait-matching) between plants and pollinators to optimise pollen transfer [@moreira2019].
-Remarkably, only tall plants with small unisexual flowers showed higher frequencies on subgraphs that were associated with low number of indirect interactions with likely direct implications on pollen transfer for this group that needs to guarantee cross-pollination.
-
-The probabilities of appearance of each functional group on the different subgraph positions were insufficient to predict most of the observed network position combinations (Fig.
-5).
-This implies that not just the representation of network subgraphs types but also the identity of the elements of their structure is non-random.
-Notably, we found that just 30$\%$ of the possible 53,250 subgraph combinations are realised.
-Thus, similarly to the presence of forbidden links at the network level [@olesen2011; @jordano2016], we also found the existence of forbidden subgraph positions and those represented almost two thirds of the total possible subgraph combinations.
-This concurs well with the general idea that plant-pollinator networks have a high proportion of non-realized direct interactions [@jordano2003; @bascompte2013], and, as a result, also a high proportion of non-realized combinations of indirect interactions.
-Some of these non-observed direct interactions are probably due to under-sampling [@dorado2011; @jordano2016].
-However, a large fraction of the possible interactions do not take place because of different constraints such as species co-occurrence, trait matching processes and phenological uncoupling [@olesen2011; @bartomeus2016; @jordano2016].
-Despite the advances in the understanding of the ecological processes that influence species pairwise interactions [@bartomeus2016; @peralta2020], we still know little about how these processes determine competitive and facilitative interactions in mutualistic networks.
-Thus, as suggested by @simmons2020, exploring the proportion of these realised network subgraphs that are competitive or facilitative is a necessary next step to improve our understanding of the architecture of biodiversity [@bascompte2007].
-
-Despite the obvious usefulness of functional groups in summarising species ecological roles (e.g., similar reproductive biology for plants and behaviour for pollinators), delimiting species into functional groups is often not trivial.
-For instance, taxonomic diversity and trait availability limit our ability to properly represent the wide range of reproductive strategies [@dellinger2020] and different clustering analysis can lead to distinct outcomes (e.g., k-means and hierarchical clustering).
-We divided floral visitors on the taxonomic rank level because it adequately represented pollinator ecological roles without the tremendous effort of compiling trait data for over 1,000 species of floral visitors.
-Indeed, further groupings with traits could help reveal greater relevance of trait-matching processes on indirect interactions.
-Moreover, we analysed network subgraphs focusing exclusively on presence or absence of interactions, assuming that all interactions are equally important.
-However, further work should investigate how to account for quantitative measurements of plant-pollinator interactions.
-Consistent with previous work [@simmons2019; @simmons2020], we characterised network motifs by using null models only constrained for network connectance.
-Although more complex null models are difficult to interpret [@Ulrich2013], they can potentially allow us to separate the mechanisms by which motifs emerge.
-However, we found that null models with more constraints generated binary structures that were mostly identical to the original ones.
-In addition, we observed that connectance, nestedness and degree distribution were significantly correlated (data not shown).
-All that highlights the difficulties to disentangle the potential sources that generate over-representation of network subgraphs and the need to investigate them.
-At the same time, although network subgraphs can capture both direct and indirect interactions, the reduction of network complexity into these different building blocks inevitably convey the loss of information [@simmons2019], for example indirect interactions from large cascading effects.
-Finally, despite the wide geographical coverage of our plant-pollinator dataset, there are major gaps for some regions of the world with a clear bias towards Europe, America and islands which have long interested ecologists [@macarthur1963; @warren2015].
-These biases are also found in global datasets of networks, where the data is highly fragmented across space [@poisot2021] and more efforts are needed to capture global patterns of plant-pollinator interactions.
-
-In conclusion, by following the framework of @simmons2020 we have been able to explore competitive and facilitative interactions in plant-pollinator networks worldwide and found the presence of worldwide motifs that highlight the non-random structure of indirect interactions.
-This non-random structure might emerge due to neutral effects according to previous modelling work [@simmons2020].
-Further, we found that plant and floral visitor functional groups are associated with different subgraph positions that involve distinct ecological roles (e.g., generalisation versus specialisation) and that the different subgraph combinations are strongly constrained.
-Although we are still far from predicting how species interact, our work is a first step to elucidate beyond pairwise interactions.
-
-# Acknowledgements
-
-This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2).
-JBL also thanks the University of New England for the funding provided to carry out this work.
-Finally, we would like to thank David García-Callejas for his useful comments on the manuscript before submission.
-
-# Author contributions
-
-IB, AA-P and JBL designed the idea. JBL collected the data. AA-P led the analysis with contributions of JBL and guidance of IB. JBL wrote the manuscript with contributions of IB and AA-P.
-
-# Data Availability Statement
-
-All data and code are publicly available at Github (<https://github.com/JoseBSL/FunctionalMotifs>) and Zenodo (<https://doi.org/10.5281/zenodo.6489213>).
-
-\newpage
-
-# References
-
-::: {#refs}
-:::
